### 2013-04-10 doc/acknowledgments.tex
Started paper I

We thank Brooke Simmons, David Hogg, XXX and YYY for many useful
conversations about citizen science and gravitational lens detection.
%
PJM was given support by the Royal  Society, in the form of a research
fellowship. He would like to thank the DotAstronomy community for
introducing so many valuable concepts and tools, and David Harris and
Roger Davies for valuable conversations about community-building.
%
% AV \ldots
%
% AM \ldots
%
% Zooniverse / Sloan Foundation.
%
The \sw project is open source, and was developed at
https://github.com/drphilmarshall/SpaceWarps.

### 2013-04-10 doc/addresses.tex
Started paper I

\def\oxford{Dept.\ of Physics, University of Oxford, Keble Road, Oxford, OX1 3RH, UK}
\def\kipac{Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA}
\def\ipmu{Kavli Institute IPMU, University of Tokyo, Japan}
\def\adler{Adler Planetarium, Chicago, IL, USA}
\def\zurich{Department of Physics, University of Zurich, Switzerland}

\def\pjmemail{\tt dr.phil.marshall@gmail.com}

### 2013-04-10 doc/sw-system.tex
Started paper I

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Space Warps I: Experiment Design
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[useAMS,usenatbib,a4paper]{mn2e}
%% letterpaper
%% a4paper

\voffset=-0.6in

% Packages:
\input psfig.sty
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}

% Macros:
\input{macros.tex}
\input{addresses.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[\sw I]
{\SW: Crowd-sourcing the Discovery of Gravitational Lenses. 
I: Experiment Design, and Testing with Simulated Data}

\author[The \SW Collaboration]{%
  The \SW Collaboration:
  Phil~Marshall,$^{1}$\thanks{\pjmemail}
  Aprajita Verma,$^{1}$
  Anupreeta More,$^{2}$
\newauthor{%
  Amit Kapadia,$^{3}$
  David Miller,$^{3}$
  Kelly Borden,$^{3}$
  Arfon Smith,$^{3}$}
\newauthor{%
  Elisabeth Baeten,
  Claude Cornen,
  Cecile Faure,
  Thomas Jennings,
  Rafael Kueng,$^{4}$}
\newauthor{%
  Christine Macmillan,
  Surhud More,$^{2}$
  Prasenjit Saha,$^{4}$
  Julianne Wilcox,
  Layne Wright}
  \medskip\\
  $^1$\oxford\\
  $^2$\ipmu\\
  $^3$\adler\\
  $^4$\zurich
}

% This list is incomplete.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\date{to be submitted to MNRAS? Not necessarily.}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2012}

\maketitle

\label{firstpage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}

\end{abstract}

% Full list of options at http://www.journals.uchicago.edu/ApJ/instruct.key.html

\begin{keywords}
  gravitational lensing   --
  methods: statistical    
\end{keywords}

\setcounter{footnote}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
\label{sec:intro}

Scientific motivation. Applications of lenses: group-scale arcs,
galaxy-galaxy lenses, lensed quasars.

Problem of rarity. Imaging surveys. Problem of purity/false positives.

Review of progress to date. Methods in SL2S, SQLS. Contrast with SLACS.

Scaling to wide field era. Automated methods: problems. Need for good
training sets. Need for quality control: always present.

Novel solution: crowd-sourcing. Brief review of similar problems.
PlanetHunters. \sw as an experiment.

In this paper, we describe the \sw website, an online system that
enables crowd-sourced detection of gravitational lenses. 
Other papers in this series will present new gravitational lenses
discovered in our first imaging survey dataset, and investigate the
differences between lens detections made in \sw and those made with
automated techniques. Here, we try to answer the following questons:
\begin{itemize}

\item How reliably can we find gravitational lenses using the \sw
system? What is the completeness of the sample produced?

\item How noisy is the system? What is the purity of the sample
produced?

\item How accurately can gravitational lenses be located on the sky
during the identification process?

\item How quickly can lenses be detected? How many classifiers are
needed per target, and how quickly can they mobilise?

\end{itemize}

In \Sref{sec:overview} we...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experiment Design}
\label{sec:design}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Data}
\label{sec:data}

Training data and test data. Refer to Paper II for CFHTLS details.

Presentation of images.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Analysis}
\label{sec:analysis}

Interpreting clicks. Online analysis: update model of each volunteer,
and estimate probability of classification.

Training data for tracking learning, and estimating completeness and
purity.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Results}
\label{sec:results}

Understanding crowd, so we can help them learn faster. Understanding
images given the crowd, so we can find lenses.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

\subsection{Learned Behavior}
\label{sec:results:learning}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

\subsection{Sample completeness and purity}
\label{sec:results:learning}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion}
\label{sec:discuss}

Challenges for future.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusions}
\label{sec:conclude}

We draw the following conclusions:

\begin{itemize}

\item Ability to detect lenses

\item What we can say about the next steps

\end{itemize}

Summarize, end.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Acknowledgements}

\input{acknowledgments.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  APPENDICES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Probabilistic Classification Model}
\label{appendix:probmodel}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  REFERENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% MNRAS does not use bibtex, input .bbl file instead. 
% Generate this in the makefile using bubble script in scriptutils:

% bubble -f paper-lcr.tex references.bib 
% \input{paper-lcr.bbl}

\bibliographystyle{apj}
\bibliography{references}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\label{lastpage}
\bsp

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-04-10 analysis/swap/mongodb.py

@@ -16,9 +16,13 @@ class MongoDB(object):
     self.subjects = self.db['spacewarp_subjects']
     self.classifications = self.db['spacewarp_classifications']
     
-    for classification in self.classifications.find():
-      print classification['annotations']
+    # for subject in self.subjects.find():
+    #   print subject
+    
+    # for classification in self.classifications.find():
+    #   print classification['annotations']
 
 if __name__ == '__main__':
   m = MongoDB()
-
+  # print m.subjects
+  # print m.classifications

### 2013-04-10 doc/acknowledgments.tex
Text on identification analysis

@@
-We thank Brooke Simmons, David Hogg, XXX and YYY for many useful
-conversations about citizen science and gravitational lens detection.
+We thank all \Ncollaboration members of the \sw community for their
+contributions to the project so far. A complete list of collaborators is
+given at... In particular we would like to recognise the efforts of XXX,
+YYY etc in moderating the discussion.
+
+We are also grateful to Brooke Simmons, David Hogg, XXX and YYY for many
+useful conversations about citizen science and gravitational lens
+detection. % Need to cross-ref with Zooniverse author list
 %
 PJM was given support by the Royal  Society, in the form of a research
-fellowship. He would like to thank the DotAstronomy community for
-introducing so many valuable concepts and tools, and David Harris and
-Roger Davies for valuable conversations about community-building.
+fellowship. 
+% He would like to thank the DotAstronomy community for
+% introducing so many valuable concepts and tools, and David Harris and
+% Roger Davies for valuable conversations about community-building.
 %

### 2013-04-10 doc/sw-system.tex
Text on identification analysis

@@
 {\SW: Crowd-sourcing the Discovery of Gravitational Lenses. 
-I: Experiment Design, and Testing with Simulated Data}
+I: System Design}
 
@@
   The \SW Collaboration:
-  Phil~Marshall,$^{1}$\thanks{\pjmemail}
-  Aprajita Verma,$^{1}$
-  Anupreeta More,$^{2}$
-\newauthor{%
-  Amit Kapadia,$^{3}$
-  David Miller,$^{3}$
-  Kelly Borden,$^{3}$
-  Arfon Smith,$^{3}$}
-\newauthor{%
-  Elisabeth Baeten,
-  Claude Cornen,
-  Cecile Faure,
-  Thomas Jennings,
-  Rafael Kueng,$^{4}$}
-\newauthor{%
-  Christine Macmillan,
-  Surhud More,$^{2}$
-  Prasenjit Saha,$^{4}$
-  Julianne Wilcox,
-  Layne Wright}
-  \medskip\\
-  $^1$\oxford\\
-  $^2$\ipmu\\
-  $^3$\adler\\
-  $^4$\zurich
+  % \input{authors.tex}
 }
@@
 
-\item How quickly can lenses be detected? How many classifiers are
-needed per target, and how quickly can they mobilise?
+\item How quickly can lenses be detected, and non-lenses be rejected?
+How many classifiers are needed per target, and how quickly can they
+mobilise?
 
@@
 
-In \Sref{sec:overview} we...
+In \Sref{sec:design} we introduce the \sw system, describing and
+explaining its various features. We then briefly
 
@@
 \label{sec:design}
+
+Unfamiliar objects: need to learn what lenses look like, fast. Rare
+objects: need to be able to reject rapidly, and get through sample.
+Confusion with non-lenses: further filtering via scientific discussion
+and further classification (voting).
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Tutorial Material}
+\label{sec:design:tutorial}
+
+Learning what lenses do: Spotter's Guide and LensToy. Learning how
+lenses work (science page, FAQ).
+
+Inline tutorial. Merge into stream. Instant feedback, positive and
+negative. Anecdotal support for this.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{The Classification Interface}
+\label{sec:design:classification}
+
+Image presentation. Consistency in size and appearance.
+
+Interface fast due to pre-loading of images, and minimizing interaction.
+
+Spotting lenses: Markers to be placed. Two reasons: first, to give good
+feedback. Second, to improve quality of discussion later.
+
+Quick dashboard provides simple ways to explore further: zoom, contrast
+controls.
+
+Non-lenses marked? Favourite button instead, enabling serendipitous
+discovery of other interesting things, separate from lenses.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Collaborative Filtering with ``Talk''}
+\label{sec:design:classification}
+
+Feeding in collections, following online analysis. 
+Taking subjects to Talk individually, too.
+
+Mental modeling. Further inspection on Dashboard. Voting.
+
+Final sample generation.
 
@@
 
-Presentation of images.
+Presentation of images. Arcsinh stretch, calibration. Approximately
+optimized.
 
@@
 
-\section{Analysis}
-\label{sec:analysis}
+\section{Identification Analysis}
+\label{sec:IDanalysis}
 
-Interpreting clicks. Online analysis: update model of each volunteer,
-and estimate probability of classification.
+In this section we outline our methodology for interpreting the
+interactions of the volunteers with the identification interface.  Each
+classification made is logged in a database, storing subject IDs,
+(anonymous) volunteer IDs, a timestamp and the classification results. 
+The {\it kind} of subject -- whether it is a training subject (a 
+simulated lens or a known non-lens) or a test subject (an unseen image
+drawn from the survey) -- is also recorded. For all subjects, the
+positions of all Markers are recorded, in pixel coordinates. For
+training subjects, we also store the ``classification'' of the subject
+as a lens, or a non-lens, and also the type of object present in the
+image. These types are summarized in \Tref{tab:objecttypes}. 
+This classification is used to provide instant feedback, but is also the
+basic measurement used in a probabilistic classification of every
+subject based on all image views to date.
 
-Training data for tracking learning, and estimating completeness and
-purity.
+We perform a ``Pseudo-online'' analysis of the classifications, 
+updating a probabilistic model of every (anonymous) volunteer's
+expertise, and every subject (in both the training and test sets), on a
+daily basis. This allows us to track the speed with which the crowd
+learns about lenses, and also gives us a dynamic estimate of the
+posterior probability for  any given  subject being a lens, given all
+classifications of it. Assigning thresholds in this lens probability
+allows us to make good decisions about whether or not to accept a
+subject into the collection of candidates visible in \Talk, and also
+whether or not to  carry on classifying a subject at all.
+
+In this paper we focus on the training data,  investigating  how the 
+crowd's ability to identify gravitational lenses during the course of
+the project, and the completeness and purity of the lens candidate
+sample generated.
+
+Where to describe probabilistic classifier stuff? Here or in an
+appendix? Not sure.
 
@@
 
-\section{Results}
-\label{sec:results}
+\section{Identification Results}
+\label{sec:IDresults}
 
@@
 \label{sec:results:learning}
+
+Vary the acceptance and rejection thresholds, look at completeness and
+purity as a function of this. How much time can be saved by retiring
+subjects into candidate list or rejection list?
 

### 2013-04-16 doc/sw-system.tex
Started prob theory write-up

@@
 \title[\sw I]
-{\SW: Crowd-sourcing the Discovery of Gravitational Lenses. 
-I: System Design}
+{\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses}
 
-\author[The \SW Collaboration]{%
-  The \SW Collaboration:
-  % \input{authors.tex}
+\author[Marshall et al.]{%
+  \input{sw-system-authors.tex}
 }
-
-% This list is incomplete.
 
@@
 
-\date{to be submitted to MNRAS? Not necessarily.}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2012}
+\date{to be submitted to MNRAS}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2013}
 
@@
 \begin{abstract}
+
+\sw is a web-based system that enables the discovery of strong
+gravitational lenses in wide-field imaging surveys by arbitrarily large
+numbers of people. Carefully produced color composite images are
+displayed to the classifiers via a flexible interface, which records
+their estimates of the positions of candidate lensed features. Simulated
+lenses, and expert-classified non-lenses, are inserted into the stream
+at random intervals; this training set is used to give the classifiers
+feedback on their performance as well as estimate a dynamically-updated
+probability for any given image containing a lens. High probability
+systems are filtered into the Zooniverse \Talk discussion system; this
+smaller sample is further classified and analysed by volunteers into a
+final set. We analyze the classification of the training set itself, and
+find that 1) $<$volunteers learn$>$... 2) $<$the filter works$>$...
 
@@
 
+Our aim is to enable the construction of a sample of good lens
+candidates. Since we aspire to making logical  decisions, we define a 
+``good candidate'' as one which has a high posterior probability of
+being a lens, given the data. The data in our case are the pixel values
+of a colour image. However, we can greatly compress these complex,
+noisy  datasets by asking our classifiers what they think about them. A
+complete  classification in \sw consists of a set of Marker positions,
+or none at all. The null set represents the statement from the
+classifier that the image in question is $\saidNOT$ a lens, while the
+placement of any  Markers indicates that the classifier considers this
+image to contain a $\saidLENS$. We simplify the problem ...
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-04-16 doc/sw-system.tex
Finished appendix on probabilistic model

@@
 
-\sw is a web-based system that enables the discovery of strong
+\sw is a web-based service
+ that enables the discovery of strong
 gravitational lenses in wide-field imaging surveys by arbitrarily large
@@
 ``good candidate'' as one which has a high posterior probability of
-being a lens, given the data. The data in our case are the pixel values
-of a colour image. However, we can greatly compress these complex,
-noisy  datasets by asking our classifiers what they think about them. A
+being a lens, given the data: $\pr(\LENS|\data)$. Our problem is to
+approximate this probability. The data in our case are the pixel values
+of a colour image. However, we can greatly compress these complex, noisy
+sets of data by asking each classifier what they think about them. A
 complete  classification in \sw consists of a set of Marker positions,
@@
 placement of any  Markers indicates that the classifier considers this
-image to contain a $\saidLENS$. We simplify the problem ...
+image to contain a $\saidLENS$.
+
+We simplify the problem by only using the Marker positions to assess
+whether the classifier  correctly assigned the classification
+$\saidLENS$ or $\saidNOT$ after viewing (blindly) a member of the
+training set of subjects. We model each classifier's expertise with a
+simple 2 by 2 ``confusion matrix,'' which is updated every time that
+volunteer classifies a training subject using the following 
+very simple estimate:
+\be
+  \pr(``X"|X,T) \approx \frac{N_{``X"}}{N_X}.
+  \label{eq:app:fraction}
+\ee
+Here, $X$ stands for the true classification of the subject, \ie either
+$\LENS$ or $\NOT$, while $``X''$ is the corresponding classification
+made by the classifier on viewing the subject. $N_X$ is the number of
+lenses the classifier has been shown, while $N_{``X"}$ is the number of 
+times the classifier got their classifications right. $T$ stands for all
+$N_{\LENS} + N_{\NOT}$ training data that the classifier has seen to
+date.
+
+The full confusion matrix of the $k^{\rm th}$ classifier is therefore:
+\be
+  \mathcal{M}^k = 
+  \begin{bmatrix}
+    \pr(\saidLENS|\NOT,T_k) & \pr(\saidLENS|\LENS,T_k) \\
+    \pr(\saidNOT |\NOT,T_k) & \pr(\saidNOT |\LENS,T_k)
+  \end{bmatrix}.
+\ee
+Note that these probabilities are normalized, \eg 
+$\pr(\saidNOT |\NOT) = 1 - \pr(\saidLENS|\NOT)$.
+
+Now, when this classifer views a test subject, 
+it is this confusion matrix that will tell us how to update the
+probability of that test subject being a $\LENS$. Let us suppose that
+this subject has never been seen before: the prior probability that it
+is (or contains) a lens is 
+\be
+  \pr(\LENS) = p_0
+\ee
+where we have to assign a value for $p_0$. In the CFHTLS, we might expect
+something like 100 lenses in 430,000 images, so $p_0 = 2\times10^{-4}$
+is a reasonable estimate. The classifier makes a classification $C_k$ 
+($= \saidLENS or \saidNOT$).
+We can apply Bayes' Theorem to update this 
+prior probability into a posterior one using this new information:
+\begin{align}
+  & \pr(\LENS|C_k,T_k) = \\ \notag
+  & \frac{\pr(C_k|\LENS,T_k)\cdot\pr(\LENS)}
+{\left[ \pr(C_k|\LENS,T_k)\cdot\pr(\LENS) + \pr(C_k|\NOT,T_k)\cdot\pr(\NOT) \right]},
+  \label{eq:app:first}
+\end{align}
+which can be evaluated numerically using the elements of the confusion
+matrix.
+
+As an example, suppose we have a {\it perfect} classifier, with
+confusion matrix
+\be
+  \mathcal{M}^{\rm perfect} = 
+  \begin{bmatrix}
+    0.0 & 1.0 \\
+    1.0 & 0.0
+  \end{bmatrix},
+\ee
+who is given a fresh subject that actually is a $\LENS$. 
+They submit $C = \saidLENS$. 
+The resulting posterior probability for the classified
+subject being a $LENS$ would be
+\begin{align}
+  \pr(\LENS|\saidLENS,T_k) &= \frac{1.0 \cdot p_0}
+           {\left[ 1.0\cdot p_0 + 0.0\cdot(1 - p_0) \right]}
+   &= 1.0
+\end{align}
+as expected. Meanwhile, an {\it obtuse} classifier, who always gets it
+wrong and has the column-swapped confusion matrix, 
+\be
+  \mathcal{M}^{\rm obtuse} = 
+  \begin{bmatrix}
+    1.0 & 0.0 \\
+    0.0 & 1.0
+  \end{bmatrix},
+\ee
+would submit $C = \saidNOT$ for this subject, also leading to
+\begin{align}
+  \pr(\LENS|\saidNOT,T_k) &= \frac{1.0 \cdot p_0}
+           {\left[ 1.0\cdot p_0 + 0.0\cdot(1 - p_0) \right]}
+   &= 1.0.
+\end{align}
+This shows that  classifiers who are systematically wrong can 
+nevertheless provide useful information. Indeed, the information content
+of each classification can be estimated before the next classification
+is made, and computed just from the confusion matrix. We define the 
+expected information per classification, or expertise, in bits, as
+\be
+  \langle I_k \rangle = \frac{1}{2} 
+                        \sum_{i} \left( \mathcal{M}^k_{i}  
+              + \mathcal{M}^k_{i}\cdot\log_2{\mathcal{M}^k_i} \right),
+  \label{eq:app:info}
+\ee
+where $i$ runs over all 4 elements of the confusion matrix 
+$\mathcal{M}^k_i$. The second term in the sum is recognisable as a
+negative entropy, while the first term and the factor of 1/2
+account for the way the confusion matrix encodes the results for the
+classification of two types of subject, and that the probabilities
+associated with each type are normalised. \Eref{eq:app:info} gives the
+required result, that 
+both the {\it perfect} and
+{\it obtuse} classifiers contribute 1 bit of information each, per
+classification. 
+The only classifier that contributes the minimum
+information per classification, zero bits, is the {\it random} 
+classifier,
+whose confusion matrix elements are all 0.5.   We conservatively 
+initialise all classifiers' confusion matrices to that of  the random
+classifier, effectively assuming that all users are equally poorly
+informed about what a $\LENS$ is, and what is $\NOT$. Plotting 
+$\langle I_k \rangle$ as a function of time will illustrate the learning
+process undergone by the $k^{\rm th}$ classifier.
+
+Suppose the $k+1^{\rm th}$ classifier now submits a classification,
+on this subject. We can generalise \Eref{eq:app:first} by replacing the
+prior probability with the current posterior probability:
+\begin{align}
+  \pr(\LENS & |C_{k+1},T_{k+1},\data) = \\ \notag
+  & \frac{1}{Z} \pr(C_{k+1}|\LENS,T_{k+1}) \cdot \pr(\LENS|\data) \\ \notag
+{\rm where}\;\; Z = & \pr(C_{k+1}|\LENS,T_{k+1})\cdot\pr(\LENS|\data) \\ \notag
+      & + \pr(C_{k+1}|\NOT,T_{k+1})\cdot\pr(\NOT|\data),
+  \label{eq:app:update}
+\end{align}
+and $\data = \{C_k,T_k\}$ is the set of all previous
+classifications, each given their classifier's training subjects.
+$\pr(\LENS|\data)$ is the fundamental property of each test subject that
+we are seeking. We track $\pr(\LENS|\data)$ as a function of time,
+and by comparing it to a lower or upper thresholds, make decisions about
+whether to retire the subject from the classification interface or
+promote it in \Talk, respectively.
 

### 2013-04-18 analysis/SWAP.py
Notes on online analysis

@@ -19,14 +19,37 @@ def SWAP(argv):
         database, and analyse it.
 
     COMMENTS
-        Amit: can you help us get started please? Ideally I would like
-        us to read in the database as an atpy Table.
-        
-        We have various quality control metrics that need to be 
-        computed, before outputting a ranked list of lens candidates. 
-        The quality control methods make use of the numerous simulated 
-        lenses, and known "dud" fields.
+        The SW analysis is "online" in the statistical sense: we step 
+        through the classifications one by one, updating each
+        classifier's confusion matrix and each subject's lens
+        probability. The main reason for taking this approach is that
+        it is the most logical one; secondarily, it opens up the
+        possibility of performing the analysis in real time (although
+        presumably not with this piece of python).
 
+        Amit: can you help us get started please? Search for the string
+        MONGO to see where I need help extracting information from the
+        mongo DB.
+
+        Currently, the confusion matrices only depend on the
+        classifications of training subjects. Upgrading this would be a
+        nice piece of further work. Likewise, neither the Marker
+        positions, the classification  durations, nor any other
+        parameters are used in estimating lens probability - but they
+        could be. In this version, it's LENS or NOT.
+
+        Standard operation is to update the candidate list by making a
+        new, timestamped catalog of candidates - and the
+        classifications that led to them. This means we have to know
+        when the last update was made - this is done by reading in a
+        pickle of the last classification to be SWAPped. The final
+        sample of candidates could be obtained by reading  in all
+        sample pickles and taking the most up to date characterisation
+        of  each - but we might as well over-write a pickle of this
+        every time too. The crowd we have to always read in in its
+        entirety, because they can reappear any time to update their
+        confusion matrices.
+        
     FLAGS
         -h            Print this message [0]
 
@@ -34,13 +57,16 @@ def SWAP(argv):
         configfile    Plain text file containing SW experiment configuration
 
     OUTPUTS
-        stdout        Useful information, redirect this to a logfile
-        candidates    Catalog of lens candidates, with associated stats
+        stdout
+        theCrowd.pickle
+        theLensSampleFrom.DATE.pickle
+        theClassificationBatchFrom.DATE.pickle
+        theMostRecentClassification.pickle
 
     EXAMPLE
         
         cd workspace
-        SWAP.py CFHTLS-beta.config > CFHTLS-beta_SWAP.log
[…]

### 2013-04-18 analysis/swap/__init__.py

@@ -1,2 +1,3 @@
 from mongodb import *
 from logging import *
+from config import *

### 2013-04-18 analysis/SWAP.py
Crowd implemented

@@ -3,7 +3,7 @@
 
 import swap
 
-import sys,getopt
+import sys,getopt,datetime
 
 # ======================================================================
 
@@ -106,7 +106,8 @@ def SWAP(argv):
         print swap.doubledashedline
         print "SWAP: taking instructions from",configfile
         print "SWAP: for the actual analysis, we need a DB and some code from Amit!"
-        print "SWAP: more soon..."
+        print "SWAP: more on this soon..."
+        print "SWAP: for now, just make some useful objects."
     else:
         print SWAP.__doc__
         return
@@ -116,8 +117,16 @@ def SWAP(argv):
     
     tonights = swap.Configuration(configfile)
     
-    if tonights.parameters['Time'] == 'Now': 
-        print "SWAP: updating all objects."
+    if tonights.parameters['Time'] == 'Now':
+        t2 = datetime.datetime.utcnow()
+        print "SWAP: updating all objects with classifications up to "+t2.__str__()
+    else:
+        raise "SWAP: analysis between 2 points in time not yet implemented"
+    
+    # ------------------------------------------------------------------
+    # Read in, or create, an object representing the crowd:
+    
+    crowd = swap.readPickle(tonights.parameters['crowdfile'],'crowd')
 
     # ------------------------------------------------------------------
 

### 2013-04-18 analysis/swap/__init__.py

@@ -1,3 +1,5 @@
 from mongodb import *
 from logging import *
 from config import *
+from io import *
+from crowd import *

### 2013-04-18 analysis/swap/config.py

@@ -25,8 +25,6 @@ class Configuration(object):
         
         prepare(self): set up workspace
         
-        getLightconePickleName(self,flavor,pointing=None): 
-
     BUGS
 
     AUTHORS

### 2013-04-18 analysis/swap/crowd.py

@@ -1,0 +1,56 @@
+# ===========================================================================
+
+import swap
+
+# ======================================================================
+
+class Crowd(object):
+    """
+    NAME
+        Crowd
+
+    PURPOSE
+        Model a group of classifiers.
+
+    COMMENTS
+        The members of the Crowd are all Classifiers. The Crowd knows
+        how big it is, and could, in principle, also know its mean
+        expertise, and other qualities.
+
+    INITIALISATION
+        From scratch.
+    
+    METHODS
+        Crowd.member(Name)     Returns the Classifier called Name
+        Crowd.size()           Returns the size of the Crowd
+        
+    BUGS
+
+    AUTHORS
+      This file is part of the Space Warps project, and is distributed 
+      under the GPL v2 by the Space Warps Science Team.
+      http://spacewarps.org/
+
+    HISTORY
+      2013-04-17  Started Marshall (Oxford)
+    """
+
+# ----------------------------------------------------------------------------
+
+    def __init__(self):
+        self.name = 'Group of classifiers'
+        self.member = {}
+        return None
+
+# ----------------------------------------------------------------------------
+
+    def __str__(self):
+        return 'Crowd of %d Classifiers' % (self.size())       
+        
+# ----------------------------------------------------------------------------
+
+    def size(self):
+        return len(self.member)
+        
+# ======================================================================
+   

### 2013-04-18 analysis/swap/io.py

@@ -1,0 +1,116 @@
+# ===========================================================================
+
+import swap
+
+import os,cPickle,atpy
+
+# ======================================================================
+
+"""
+    NAME
+        io
+
+    PURPOSE
+        Useful general functions to streamline file input and output.
+
+    COMMENTS
+            
+    FUNCTIONS
+        writePickle(contents,filename):
+        
+        readPickle(filename): returns contents of pickle
+        
+        readCatalog(filename,config): returns table, given column names
+                                      in configuration config
+    
+        rm(filename): silent file removal
+        
+    BUGS
+
+    AUTHORS
+      This file is part of the Space Warps project, and is distributed 
+      under the GPL v2 by the Space Warps Science Team.
+      http://spacewarps.org/
+
+      SWAP io is modelled on that written for the
+      Pangloss project, by Tom Collett (IoA) and Phil Marshall (Oxford).
+      https://github.com/drphilmarshall/Pangloss/blob/master/pangloss/io.py
+
+    HISTORY
+      2013-04-17  Started Marshall (Oxford)
+"""
+
+#=========================================================================
+# Read in an instance of a class, of a given flavour. Create an instance 
+# if the file does not exist.
+
+def readPickle(filename,flavour):
+    
+    try:
+        F = open(filename,"rb")
+        contents = cPickle.load(F)
+        F.close()
+    except IOError:
+
+        if filename != 'None': print "SWAP: "+filename+" does not exist."
+
+        if flavour == 'crowd':
+            contents = swap.Crowd()
+
+        elif flavour == 'collection':
+            # contents = swap.Collection()
+            raise Exception("Collection class not yet implemented")
+        
+        print "SWAP: Made a new",contents
+            
+    return contents
+
+# ----------------------------------------------------------------------------
+# Write out an instance of a class to file.
+def writePickle(contents,filename):
+    F = open(filename,"wb")
+    cPickle.dump(contents,F,protocol=2)
+    F.close()
+    return
+
+# ----------------------------------------------------------------------------
+# 
+# def readCatalog(filename,config):
+# 
+#     table = atpy.Table(filename, type='ascii')
+# 
+#     try: table.rename_column(config.parameters['nRAName'],'nRA')
+#     except: pass
+#     try: table.rename_column(config.parameters['DecName'],'Dec')
+#     except: pass
+# 
+#     # Calibration catalogs:
[…]

### 2013-04-18 analysis/swap/mongodb.py

@@ -1,28 +1,28 @@
 # Hi Amit! If you could dump a mongodb dump class in here, 
 # that would be great! Thanks :-)
 
-import os
-from pymongo import MongoClient
-
-
-class MongoDB(object):
-  
-  def __init__(self):
-    
-    # Connect to the Mongo
-    self.client = MongoClient('localhost', 27017)
-    self.db = self.client['ouroboros_staging']
-    
-    self.subjects = self.db['spacewarp_subjects']
-    self.classifications = self.db['spacewarp_classifications']
-    
-    # for subject in self.subjects.find():
-    #   print subject
-    
-    # for classification in self.classifications.find():
-    #   print classification['annotations']
-
-if __name__ == '__main__':
-  m = MongoDB()
-  # print m.subjects
-  # print m.classifications
+# import os
+# from pymongo import MongoClient
+# 
+# 
+# class MongoDB(object):
+#   
+#   def __init__(self):
+#     
+#     # Connect to the Mongo
+#     self.client = MongoClient('localhost', 27017)
+#     self.db = self.client['ouroboros_staging']
+#     
+#     self.subjects = self.db['spacewarp_subjects']
+#     self.classifications = self.db['spacewarp_classifications']
+#     
+#     # for subject in self.subjects.find():
+#     #   print subject
+#     
+#     # for classification in self.classifications.find():
+#     #   print classification['annotations']
+# 
+# if __name__ == '__main__':
+#   m = MongoDB()
+#   # print m.subjects
+#   # print m.classifications

### 2013-04-19 doc/sw-system.tex
agent-based modeling: latex and python now consistent

--- 2013-04-10 doc/sw-system.tex
@@
 \begin{abstract}
+
+\sw is a web-based service
+ that enables the discovery of strong
+gravitational lenses in wide-field imaging surveys by arbitrarily large
+numbers of people. Carefully produced color composite images are
+displayed to volunteers via a flexible interface, which records
+their estimates of the positions of candidate lensed features. Simulated
+lenses, and expert-classified non-lenses, are inserted into the stream
+at random intervals; this training set is used to give the volunteers
+feedback on their performance as well as estimate a dynamically-updated
+probability for any given image containing a lens. High probability
+systems are filtered into the Zooniverse \Talk discussion system; this
+smaller sample is further classified and analysed by volunteers into a
+final set. We analyze the classification of the training set itself, and
+find that 1) $<$volunteers learn$>$... 2) $<$the filter works$>$...
 
@@
 \item How quickly can lenses be detected, and non-lenses be rejected?
-How many classifiers are needed per target, and how quickly can they
+How many volunteers are needed per target, and how quickly can they
 mobilise?
@@
 
-\section{Probabilistic Classification Model}
+\section{Probabilistic Classification Data Model}
 \label{appendix:probmodel}
+
+Our aim is to enable the construction of a sample of good lens candidates.
+Since we aspire to making logical  decisions, we define a  ``good candidate''
+as one which has a high posterior probability of being a lens, given the data:
+$\pr(\LENS|\data)$. Our problem is to approximate this probability. The data
+in our case are the pixel values of a colour image. However, we can greatly
+compress these complex, noisy sets of data by asking each volunteer what they
+think about them. A complete  classification in \sw consists of a set of
+Marker positions, or none at all. The null set encodes the statement from
+the volunteer that the image in question is $\saidNOT$ a lens, while the
+placement of any  Markers indicates that the volunteer considers this image to
+contain a $\saidLENS$.  We simplify the problem by only using the Marker
+positions to assess whether the volunteer  correctly assigned the
+classification $\saidLENS$ or $\saidNOT$ after viewing (blindly) a member of
+the training set of subjects.
+
+How should we model these compressed data? The circumstances of each
+classification are quite complex: the volunteers learn more about the problem
+as they go, but also inevitably make occasional mistakes (perhaps because a
+lens is difficult to see, or they became distracted by the television). To
+cope with this uncertainty, we assign a software agent to partner each
+volunteer. The agent's task is to interpret their volunteer's classification
+data as best it can, using a model that makes a number of necessary
+approximations. These interpretations will then include uncertainty arising as
+a result of the volunteer's efforts and also the agent's approximations, but
+they will have two important redeeming features. First, the interpretations
+will be quantitative (where before they were qualititative),  and thus will be
+useful in decision-making. Second, the agent will be able to predict, using
+its model, the probability of a test subject being a $\LENS$, given both its
+volunteer's classification, and its volunteer's experience. We now
+describe how each agent works.
+
+Each agent assumes that the probability of a volunteer recognising any given
+simulated lens as a lens is some number, $\pr(\saidLENS|\LENS,T)$, that
+depends only on what the volunteer is currently looking at, and all the
+previous training subjects they have seen (and not on what type of lens it is,
+how faint it is, what time it is, \etc). Likewise, it also assumes that the
+probability of a volunteer recognising any given dud image as a dud is some
+other number, $\pr(\saidNOT|\NOT,T)$, that also depends only on what the volunteer is currently looking at, and all the
+previous training subjects they have seen. These two probabilities define a 
+2 by 2 ``confusion matrix,'' which the agent updates, every time a
+volunteer classifies a training subject, using the following 
+very simple estimate:
+\be
+  \pr(``X"|X,T) \approx \frac{N_{``X"}}{N_X}.
+  \label{eq:app:fraction}
+\ee
+Here, $X$ stands for the true classification of the subject, \ie either
+$\LENS$ or $\NOT$, while $``X''$ is the corresponding classification
+made by the volunteer on viewing the subject. $N_X$ is the number of
+lenses the volunteer has been shown, while $N_{``X"}$ is the number of 
+times the volunteer got their classifications of this type of training subject
+right. $T$ stands for all
+$N_{\LENS} + N_{\NOT}$ training data that the agent has heard about to
+date.
+
+The full confusion matrix of the $k^{\rm th}$ volunteer's agent is therefore:
+\be
+  \mathcal{M}^k = 
+  \begin{bmatrix}
+    \pr(\saidLENS|\NOT,T_k) & \pr(\saidLENS|\LENS,T_k) \\
+    \pr(\saidNOT |\NOT,T_k) & \pr(\saidNOT |\LENS,T_k)
+  \end{bmatrix}.
+\ee
+Note that these probabilities are normalized, such that
+$\pr(\saidNOT |\NOT) = 1 - \pr(\saidLENS|\NOT)$.
+
+Now, when this volunteer views a test subject, 
+it is this confusion matrix that will allow their agent to update the
+probability of that test subject being a $\LENS$. Let us suppose that
+this subject has never been seen before: the agent assigns a 
+prior probability that it is (or contains) a lens is 
+\be
+  \pr(\LENS) = p_0
+\ee
+where we have to assign a value for $p_0$. In the CFHTLS, we might expect
+something like 100 lenses in 430,000 images, so $p_0 = 2\times10^{-4}$
+is a reasonable estimate. The volunteer then makes a classification $C_k$ 
+($= \saidLENS$ or $\saidNOT$).
+We can apply Bayes' Theorem to derive how the agent should
+update this prior probability into a posterior one using this new information:
+\begin{align}
+  \label{eq:app:first}
+  & \pr(\LENS|C_k,T_k) = \\
+  & \frac{\pr(C_k|\LENS,T_k)\cdot\pr(\LENS)}
+{\left[ \pr(C_k|\LENS,T_k)\cdot\pr(\LENS) + \pr(C_k|\NOT,T_k)\cdot\pr(\NOT) \right]},
+  \notag
+\end{align}
+which can be evaluated numerically using the elements of the confusion
+matrix.
+
+As an example, suppose we have a volunteer who is always right about the true
+nature of a training subject. 
+Their agent's confusion matrix would be
+\be
+  \mathcal{M}^{\rm perfect} = 
+  \begin{bmatrix}
+    0.0 & 1.0 \\
+    1.0 & 0.0
+  \end{bmatrix}.
+\ee
+On being given a fresh subject that actually is a $\LENS$,
+this hypothetical volunteer would submit $C = \saidLENS$. 
+Their agent would then calculate the posterior probability for the 
+subject being a $LENS$ to be
+\begin{align}
+  \pr(\LENS|\saidLENS,T_k) &= \frac{1.0 \cdot p_0}
+           {\left[ 1.0\cdot p_0 + 0.0\cdot(1 - p_0) \right]}
+   &= 1.0,
+\end{align}
+as we might expect for such a {\it perfect} classifier. 
+Meanwhile, a hypothetical volunteer who (for some reason) 
+wilfully always submits the wrong 
+classification would have an agent with the column-swapped confusion matrix
+\be
+  \mathcal{M}^{\rm obtuse} = 
+  \begin{bmatrix}
+    1.0 & 0.0 \\
+    0.0 & 1.0
+  \end{bmatrix},
+\ee
+and would submit $C = \saidNOT$ for this subject. However, such a volunteer
+would nevertheless be submitting useful
+information, since given the above confusion matrix, their agent would
+calculate
+\begin{align}
+  \pr(\LENS|\saidNOT,T_k) &= \frac{1.0 \cdot p_0}
+           {\left[ 1.0\cdot p_0 + 0.0\cdot(1 - p_0) \right]}
+   &= 1.0.
+\end{align}
+{\it Obtuse} classifiers are as helpful as {\it perfect} ones!
+
+Indeed, the information content of each classification can be estimated by an
+agent before the next classification is made, just from its confusion matrix.
+We define the expected information per classification, or {\it expertise}, as
+\be
+  \langle I_k \rangle = \frac{1}{2} 
+                        \sum_{i} \left( \mathcal{M}^k_{i}  
+              + \mathcal{M}^k_{i}\cdot\log_2{\mathcal{M}^k_i} \right),
+  \label{eq:app:info}
+\ee
+where $i$ runs over all 4 elements of the confusion matrix 
+$\mathcal{M}^k_i$, and $\langle I_k \rangle$ is measured in ``bits.'' 
+The second term in the sum is recognisable as a
+negative entropy, while the first term and the factor of 1/2
+account for the way the confusion matrix encodes the results for the
+classification of two types of subject, and that the probabilities
+associated with each type are normalised. \Eref{eq:app:info} gives the
+required result, that 
+both the hypothetical {\it perfect} and
+{\it obtuse} classifiers contribute 
+1 bit of information each, per classification.
+
+In fact, the only classifier that contributes the minimum information per
+classification, zero bits, is the {\it random} classifier, whose agent's
+confusion matrix elements are all 0.5.   
+We conservatively initialise all the agents' confusion matrices to be that of
+the random classifier. This makes no allowance for volunteers that actually do
+have previous experience of what gravitational lenses look like, but should
+help prevent large numbers of false positives being assigned high probability.
+Plotting  $\langle I_k \rangle$ as a function of time will, to some extent,
+illustrate the
+learning process undergone by the $k^{\rm th}$ volunteer-agent partnership.
+
+Suppose the $k+1^{\rm th}$ volunteer now submits a classification, on the same
+subject just classified by the $k^{\rm th}$ volunteer. We can generalise
+\Eref{eq:app:first} by replacing the prior probability with the current
+posterior probability:
+\begin{align}
+  \label{eq:app:update}
+  \pr(\LENS & |C_{k+1},T_{k+1},\data) = \\
+  & \frac{1}{Z} \pr(C_{k+1}|\LENS,T_{k+1}) \cdot \pr(\LENS|\data) \\ \notag
+{\rm where}\;\; Z = & \pr(C_{k+1}|\LENS,T_{k+1})\cdot\pr(\LENS|\data) \\ \notag
+      & + \pr(C_{k+1}|\NOT,T_{k+1})\cdot\pr(\NOT|\data), \notag
+\end{align}
+and $\data = \{C_k,T_k\}$ is the set of all previous
+classifications, and the set of training subjects seen by each of those
+volunteers.
+$\pr(\LENS|\data)$ is the fundamental property of each test subject that
+we are trying to infer. We track $\pr(\LENS|\data)$ as a function of time,
+and by comparing it to a lower or upper thresholds, make decisions about
+whether to retire the subject from the classification interface or
+promote it in \Talk, respectively.
 

### 2013-04-19 analysis/SWAP.py

@@ -125,7 +125,8 @@ def SWAP(argv):
         raise "SWAP: analysis between 2 points in time not yet implemented"
     
     # ------------------------------------------------------------------
-    # Read in, or create, an object representing the crowd:
+    # Read in, or create, a bureau of agents who will represent the 
+    # collaboration:
     
     collaboration = swap.read_pickle(tonights.parameters['crowdfile'],'crowd')
 
@@ -148,11 +149,11 @@ def SWAP(argv):
     
         # Pull out a fake classification:
         if k == 0: 
-            Name,ID,category,X,Y = ('Phil1','0001' ,'training','NOT','LENS')
+            Name,ID,category,X,Y = ('Phil1','0001' ,'training','NOT','NOT')
         if k == 1: 
             Name,ID,category,X,Y = ('Phil2','0001' ,'training','LENS','LENS')
         if k == 2: 
-            Name,ID,category,X,Y = ('Phil1','0002' ,'training','LENS','NOT')
+            Name,ID,category,X,Y = ('Phil1','0002' ,'training','LENS','LENS')
         if k == 3: 
             Name,ID,category,X,Y = ('Phil1','0003' ,'training','LENS','LENS')
         if k == 4: 
@@ -160,24 +161,32 @@ def SWAP(argv):
         if k == 5: 
             Name,ID,category,X,Y = ('Phil2','0003' ,'training','NOT','LENS')
 
-        # Register new members:
+        # Register new volunteers, and create an agent for each one:
         if Name not in collaboration.list():  
             collaboration.member[Name] = swap.Classifier(Name)
+            # Note that a collaboration.member is an *agent*, not a 
+            # person. People exist in real life, whereas this is 
+            # just a piece of software!
+        
+        # Register newly-classified subjects:
         if ID not in sample.list():           
             sample.member[ID] = swap.Subject(ID,category,kind=Y)    
 
-        # Update the classifier's confusion matrix:
+        # Update the agent's confusion matrix, based on what it heard:
         if category == 'training':
-            collaboration.member[Name].said(it_was=X,actually_it_was=Y)
+            collaboration.member[Name].heard(it_was=X,actually_it_was=Y)
 
-        # Update the subject's lens probability:
+        # Update the subject's lens probability using input from the 
+        # collaboration member. We send that member's agent to the subject
+        # to do this.  
         sample.member[ID].described(by=collaboration.member[Name],as_kind=X)
 
         # Brag about it:
[…]

### 2013-04-19 analysis/swap/classifier.py

@@ -13,11 +13,13 @@ class Classifier(object):
         Classifier
 
     PURPOSE
-        Model an individual classifier.
+        Provide an agent who will interpret the classifications of an 
+        individual volunteer.
 
     COMMENTS
-        The Classifier is a person, whose Name is either a userid or, if
-        that is not available, an IP address. The Classifier has a
+        A Classifier is an agent who is assigned to represent a 
+        volunteer, whose Name is either a Zooniverse userid or, if
+        that is not available, an IP address. A Classifier has a
         History of N classifications, including ND that turned out to be
         duds and NL that turned out to be lenses. (ND+NL) is the total
         number of training subjects classified, and is equal to N in the
@@ -25,20 +27,33 @@ class Classifier(object):
         "confusion matrix" parameterised by two numbers, PD and PL, the
         meaning of which is as follows:
         
-        When a Classifier sees a subject, they say:
+        A Classifier assumes that its volunteer says:
         
-        | "LENS" when it is "NOT"    "LENS" when it is a "LENS" |
-        | with probability (1-PD)    with probability PL        |
-        |                                                       |
-        | "NOT" when it is "NOT"     "NOT" when it is a "LENS"  |
-        | with probability PD        with probability (1-PL)    |
+        | "LENS" when it is NOT    "LENS" when it is a LENS  |
+        | with probability (1-PD)    with probability PL     |
+        |                                                    |
+        | "NOT" when it is NOT     "NOT" when it is a LENS   |
+        | with probability PD        with probability (1-PL) |
         
-        We make the simplest possible assignment for these
-        probabilities, namely that PX = 0.5 if NX = 0, and then update
-        from there. To make this work, we initialise all Classifiers
-        with NL = ND = 2, implying that they got 1 lens right and 1 dud
-        right before their classifications were begun. Obviously this is
-        a horrible hack. 
+        It makes the simplest possible assignment for these
+        probabilities, namely that PX = 0.5 if NX = 0, and then updates
+        from there using the training subjects such that 
+        PX = NX_correct / NX at all times. For example, if the 
+        volunteer is right about 80% of the simulated lenses they see, 
+        the agent will assign PL = Pr("LENS"|LENS) = 0.8.
+        
+        To make the numbers come out right, we initialise all 
+        Classifiers with NL = ND = 2 as well as PL = PD = 0.5, implying
+        that they got 1 lens right and 1 dud right before their 
[…]

### 2013-04-19 analysis/swap/crowd.py

@@ -12,20 +12,20 @@ class Crowd(object):
         Crowd
 
     PURPOSE
-        Model a group of classifiers.
+        Represent a group of volunteers by assigning each one an agent.
 
     COMMENTS
-        The members of the Crowd are all Classifiers. The Crowd knows
-        how big it is, and could, in principle, also know its mean
-        expertise, and other qualities.
+        The members of a Crowd are all agents known as Classifiers. 
+        The Crowd knows how big it is, and could, in principle, also 
+        know its mean expertise, and other qualities.
 
     INITIALISATION
         From scratch.
     
     METHODS AND VARIABLES
-        Crowd.member(Name)     Returns the Classifier called Name
-        Crowd.list             Returns the Names of the members
-        Crowd.size()           Returns the size of the Crowd
+        Crowd.member(Name)         The agent assigned to Name
+        Crowd.list                 The Names of the Crowd's members
+        Crowd.size()               The size of the Crowd
         Crowd.start_history_plot()
         Crowd.finish_history_plot()
         
@@ -49,7 +49,7 @@ class Crowd(object):
 # ----------------------------------------------------------------------------
 
     def __str__(self):
-        return 'crowd of %d classifiers' % (self.size())       
+        return 'crowd of %d classification agents' % (self.size())       
         
 # ----------------------------------------------------------------------------
 

### 2013-04-25 doc/sw-system.tex
First beta results circulated

@@
 updating a probabilistic model of every (anonymous) volunteer's
-expertise, and every subject (in both the training and test sets), on a
-daily basis. This allows us to track the speed with which the crowd
+data, and also updating the lens probability of each subject 
+(in both the training and test sets), on a
+daily(??) basis. This allows us to track the speed with which the crowd
 learns about lenses, and also gives us a dynamic estimate of the
@@
 agent before the next classification is made, just from its confusion matrix.
-We define the expected information per classification, or {\it expertise}, as
+We define the expected contributed information per classification, as
 \be

### 2013-04-25 analysis/swap/collection.py

@@ -92,7 +92,7 @@ class Collection(object):
         # This is non-trivial, you have to overlay in a different 
         # set of axes, with linear scales...
         hax = fig.add_axes(upperarea)
-        hax.set_xlim(np.log10(1e-8),np.log10(1.0))
+        hax.set_xlim(np.log10(swap.pmin),np.log10(swap.pmax))
         hax.set_ylim(np.log10(50.0),np.log10(0.5))
         for label in hax.get_xticklabels():
             label.set_visible(False)
@@ -105,7 +105,7 @@ class Collection(object):
         # Now overlay a transparent frame to plot the subjects in:
         upper = fig.add_axes(upperarea, frameon=False)
         plt.sca(upper)
-        upper.set_xlim(1e-8,1.0)
+        upper.set_xlim(swap.pmin,swap.pmax)
         upper.set_xscale('log')
         upper.set_ylim(50.0,0.5)
         upper.set_yscale('log')
@@ -120,7 +120,7 @@ class Collection(object):
         # Lower panel: histograms:
         lower = fig.add_axes(lowerarea, sharex=upper)
         plt.sca(lower)
-        lower.set_xlim(1e-8,1.0)
+        lower.set_xlim(swap.pmin,swap.pmax)
         lower.set_xscale('log')
         lower.set_ylim(0.1,0.5*self.size())
         # lower.set_yscale('log')

### 2013-04-25 analysis/swap/config.py

@@ -5,8 +5,8 @@ import os, glob
 # ======================================================================
 # Global parameters:
 
-pmin,pmax = 1e-8,1.0
-
+pmin,pmax = 1e-8,1.5
+Ncmin,Ncmax = 0.5,50
 
 # ======================================================================
 

### 2013-04-25 analysis/swap/subject.py

@@ -126,8 +126,12 @@ class Subject(object):
             colour = 'black'
         
         plt.plot(self.trajectory, N, color=colour, alpha=0.1, linewidth=1.0, linestyle="-")
-        plt.scatter(self.trajectory[-1], N[-1], color=colour, alpha=0.5)
+        NN = N[-1]
+        if NN > swap.Ncmax: NN = swap.Ncmax
+        plt.scatter(self.trajectory[-1], NN, color=colour, alpha=0.5)
         
+        # if self.kind == 'sim': print self.trajectory[-1], N[-1]
+                
         return
 
 # ======================================================================

### 2013-05-06 doc/sw-publication-policy.tex
Exponential enthusiasm distribution implemented in toydb

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Space Warps Publication Policy
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper]{article}

% Packages:
\usepackage{xspace}
\usepackage{verbatim}

% Macros:
\input{macros.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{\SW Collaboration Publication Policy}
\author{Phil Marshall}
\date{April 15, 2013}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract} 
\noindent In this document we define the various types of \sw
collaboration membership, and their meaning in terms of the scientific
papers that \sw contributes to. \sw was conceived as a strong  lens
discovery {\it service}, that any survey science team could make use of
(within the logistical constraints). Here, we discuss the relationship
between the \sw collaboration and the survey teams, and suggest
reasonable guidelines for publication of \sw-enabled discoveries.
\end{abstract}

\setcounter{footnote}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Membership Types}
\label{sec:members}

The \sw website is designed to motivate and  enable tens of thousands of
people to perform the scientific tasks of strong gravitational lens
identification and classification.  The \sw collaboration comprises the
sum total of the volunteers who have logged in and contributed
classifications to the project. (We would include the ones who did not
log in as well, but we don't know who they are.) This means that the
minimal requirement for \sw collaboration membership is a Zooniverse ID,
and some contribution on the site (\ie classifying, or discussing
Subjects in \Talk).

Not all collaboration members will participate in writing journal
papers. Those who have made significant contributions to the site
design, construction and operation, or in data preparation or analysis,
or in writing and editing the papers, will be recognised on the author
lists of journal papers presenting \sw results. The current list of \sw 
authors is given in the \texttt{authors.tex} file and is reprinted
below; this file as shown below is as it is currently configured, ready
to be copied and pasted into the system paper (\sw I).

{\small\verbatiminput{authors.tex}}

\noindent The author categories referred to above form the following
nested set:

\begin{description}

\item{\bf Principals:} These are the PIs of the \sw project (Marshall, 
A.\,More and Verma), and the Zooniverse development team (led by
Kapadia).

\item{\bf Science Team:} This is a core group of scientists, both citizen and
professional, that have helped design, build and test the \sw website
and its initial project. The Science Team includes the PIs. Each member
of the Science Team will be listed on the website with a one paragraph
biography, and their names will appear in the \Talk site listed as
``Science Team.''

\item{\bf Other Authors:} This group makes up the remainder of the author
list, and includes people who have made only minor contributions to the
project. Such contributions might include helping write the initial
Citizen Science Alliance proposal, participating in discussions on
\Talk, writing \sw blog posts, advising on the data analysis, or editing
papers.

\end{description}

\noindent The author list can only grow, not shrink, over time. Within
th eauthor list, movement of, for example, one of the ``other authors''
into the ``Science Team'' could be readily achieved by that author
making a substantial contribution to the project (by, for example,
extensive participation in \Talk during the CFHTLS project). The author
list will be maintained and administered by the \sw PIs.

In the remaining sections we look at the various publications that might
arise from the \sw project, and suggest reasonable guidelines for
deciding on their authorship. First, however, we remind ourselves about data
access via \sw.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Survey Data Use}
\label{sec:data}

\sw is a public website. All images displayed there are by definition in the
public domain, and so must be expected to be downloaded, copied and
redistributed by any \sw user. This is a Good Thing: images of the sky taken
with publically-funded telescopes belong to everyone. It is the responsibility
of the survey science teams to provide images in a way that is consistent
with their own data access rules. There are two things that survey teams can
do to in order to respect any proprietary period that they have imposed on
themselves:
\begin{enumerate}

\item Add a ``LICENSE'' keyword to the FITS and PNG image headers, explaining
what the rules for redistribution of these images are. This will almost
certainly be ignored, but it would be a nice reminder that nothing comes free
of either cost or responsibility. Other keywords could also be included as
well: data provenance is important, and links to useful survey webpages would
be most welcome!

\item Remove all WCS information from all images provided. This would prevent
follow-up of any of the objects in the survey by anyone other than the survey
team. In practice, the objects contained in the \sw images will be too faint
for anyone without access to a large telescope to observe, and will also be
absent from any public catalogs, so the opportunities for follow-up will be
quite limited. Removing the WCS information is an insurance policy against any
competing professional scientists looking to ``scoop'' the survey team,
despite the damage it would do to their reputations. We note that images
with field of view less than about 3~arcminutes in diameter are not solvable
by \texttt{astrometry.net}.

\end{enumerate}

Hopefully, the benefits of using the \sw service will far outweigh the small
inconvenience represented by the above suggestions: the amount of other work
required to prepare an \sw dataset is much greater than this, in any case!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Zooniverse Publications: Letters and Talk }
\label{sec:series}

Any \sw collaboration member, simply by virtue of their Zooniverse
registration, may write a Zooniverse
Letter\footnote{\texttt{http://letters.zooniverse.org}} describing their
investigation of any lens candidate they find in \sw. This, along with
posts in  \Talk, is the primary means by which we expect collaboration
members will publish results of any detailed analysis to the rest of the
astronomical community. The investigation of any \sw images that are
provided without world coordinate system (WCS) information will be
necessarily limited, but the survey scientists who own this proprietary
information will benefit from the understanding gained in the \sw
\Letters, and science will proceed: Zooniverse \Letters are citable
objects, and in some cases will appear listed on ADS.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The \SW Paper Series}
\label{sec:series}

We are planning a short series of papers describing the \sw service, its
first dataset (CFHTLS), and results from its investigation by the
collaboration. These results will likely include a sample of new lenses,
and some comparison studies between the visual and automated
identification of lens systems in this survey. This series will be known
as ``the \sw papers,'' and each one will have a title that starts with ``\sw.''

The Science Team and the Principals will be authors of these papers by
default, but will of course have the right to opt out if they wish. The
other authors may opt in to the author list of any of the \sw papers if
they feel that they have made a substantial contribution to that
investigation. The other authors may also be added to the author list of
any \sw paper; if this happens they will still have (of course) the
right to opt out again.

Beyond these rules, the first author of any given paper will decide, as
usual, on the author list of their own paper. This will include inviting
scientists from outside the list of authors, or from outside the
collaboration. The PIs will act as adjudicators if any disputes arise,
but to be honest we are not expecting any.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Future Survey Papers}
\label{sec:series}

The \sw papers must, by definition, provide a complete description of
the system, and its results from the CFHTLS survey. The science team of
any other survey (such as DES, RCS, KIDS, PS1, HSC \etc) should be able
to read these papers before designing their own \sw project, and must be
able to cite them as justification for some of their decisions.

Implementing a new project based on different survey data will,
nonetheless, require support from the \sw Science Team, in three
respects: 
\begin{enumerate}

\item In {\bf preparing data} for the site, and uploading it onto the
Zooniverse servers. The \sw Science Team can advise on suitable Training
Subjects and image display settings, and also on formatting the data
ready for ingestion and display

\item In {\bf reconfiguring the site itself} ready for the new data. The
survey team will need to include new Spotter's Guide images and text,
modified tutorial content, and additional survey-specific site content;
the \sw Science Team can help with all of this.

\item In {\bf maintaining the site} so that it continues to function
correctly. This will involve technical support from the Zooniverse team,
but will also require the continued engagement of the wider
collaboration by the Science Team in \Talk. Since this social filter is
a key part of the sample refinement, the latter may involve a
significant time commitment.

\end{enumerate}

\noindent Given the above, we suggest that the PIs be able to nominate a
small number of \sw collaboration members as authors on any paper that
presents a lens discovery enabled by the \sw system. We do not yet know
how many people this would be, but it would likely be a fairly small
number (less than ten). All follow-up papers would of course be exempt
from this: the idea is that \sw is purely a gravitational lens discovery
service, but not one that runs by magic.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-05-06 doc/sw-system.tex
Exponential enthusiasm distribution implemented in toydb

@@
 contain a $\saidLENS$.  We simplify the problem by only using the Marker
-positions to assess whether the volunteer  correctly assigned the
+positions to assess whether t
+he volunteer  correctly assigned the
 classification $\saidLENS$ or $\saidNOT$ after viewing (blindly) a member of

### 2013-05-06 analysis/SWAP.py

@@ -172,6 +172,7 @@ def SWAP(argv):
         print "SWAP: where each classifier makes ",db.enthusiasm," classifications, on average"
        
     else:
+    
         db = swap.MongoDB()
 
     # Read in a batch of classifications, made since the aforementioned 
@@ -246,9 +247,10 @@ def SWAP(argv):
         print "SWAP: saving subjects in "+new_samplefile
         swap.write_pickle(sample,new_samplefile)
 
-        new_dbfile = swap.get_new_filename(tonights.parameters,'database')
-        print "SWAP: saving database in "+new_dbfile
-        swap.write_pickle(db,new_dbfile)
+        if practise:
+            new_dbfile = swap.get_new_filename(tonights.parameters,'database')
+            print "SWAP: saving database in "+new_dbfile
+            swap.write_pickle(db,new_dbfile)
 
     # ------------------------------------------------------------------
     # Make plots:

### 2013-05-06 analysis/swap/collection.py

@@ -126,6 +126,10 @@ class Collection(object):
             label.set_visible(False)
         for label in hax.get_yticklabels():
             label.set_visible(False)
+        for tick in hax.xaxis.get_ticklines(): 
+            tick.set_visible(False) 
+        for tick in hax.yaxis.get_ticklines(): 
+            tick.set_visible(False) 
         plt.sca(hax)
         plt.arrow(np.log10(2e-4), np.log10(0.3), 0.0, 0.1, fc="k", ec="k", linewidth=2, head_width=0.2, head_length=0.1)
         # hax.set_axis_off()        

### 2013-05-06 analysis/swap/crowd.py

@@ -123,6 +123,10 @@ class Crowd(object):
             label.set_visible(False)
         for label in hax.get_yticklabels():
             label.set_visible(False)
+        for tick in hax.xaxis.get_ticklines(): 
+            tick.set_visible(False) 
+        for tick in hax.yaxis.get_ticklines(): 
+            tick.set_visible(False) 
             
         plt.hist(logN, bins=bins, histtype='stepfilled', color='yellow', alpha=0.4)
             
@@ -132,8 +136,8 @@ class Crowd(object):
         axes.set_xlim(Nmin,Nmax)
         axes.set_xscale('log')
         axes.set_ylim(0.0,1.0)
-        axes.set_xticks([1,10,100,1000])
-        axes.set_yticks([0.0,0.2,0.4,0.6,0.8,1.0])
+        # axes.set_xticks([1,10,100,1000])
+        # axes.set_yticks([0.0,0.2,0.4,0.6,0.8,1.0])
         axes.set_xlabel('No. of training subjects classified')
         axes.set_ylabel('Contributed information per classification (bits)')
         axes.set_title('Classifier Histories')

### 2013-05-06 analysis/swap/logging.py

@@ -71,10 +71,8 @@ def write_report(pars,crowd,sample):
 
     F.write('\\begin{tabular}{|p{0.65\linewidth}p{0.2\linewidth}|}\n')
     F.write('\hline\n')
-    F.write('No.\ of test subjects seen:             & %d   \\\\ \n' % (np.sum(crowd.Ntest)))
-    F.write('Mean test subjects/classifier:          & %.1f \\\\ \n' % (np.sum(crowd.Ntest)/len(crowd.member)))
-    F.write('Mean class$^{\\rm n}$s/test subject:    & %.1f \\\\ \n' % (np.sum(sample.exposure['test'])/np.sum(crowd.Ntest)))
-    F.write('Mean test class$^{\\rm n}$s/classifier:      & %.1f \\\\ \n' % (np.sum(sample.exposure['test'])/len(crowd.member)))
+    F.write('Mean test class$^{\\rm n}$s/classifier: & %.1f \\\\ \n' % (np.average(crowd.Ntest)))
+    F.write('Mean class$^{\\rm n}$s/test subject:    & %.1f \\\\ \n' % (np.average(sample.exposure['test'])))
     F.write('\hline\n')
     F.write('\end{tabular}\n')
 

### 2013-05-06 analysis/swap/mongodb.py

@@ -213,8 +213,9 @@ class MongoDB(object):
 # Return the size of the classification table:
 
     def size(self):
-        
-        return len(self.classifications)
+        # BUG: I don't actually know how to return the length of the 
+        # classification table...
+        return 1e6
         
 # ----------------------------------------------------------------------------
 

### 2013-05-06 analysis/swap/toydb.py

@@ -167,10 +167,36 @@ class ToyDB(object):
             # Original uniform distribution:
             # k = int(self.population*np.random.rand())
             
-            # Exponential with mean = enthusiasm:
-            k = int(np.random.exponential(scale=self.enthusiasm))
-            if k > len(self.classifiers)-1: k = 0
+            j = 0
+            while (j == 0):
             
+                # Exponential distribution for Nk with mean = enthusiasm:
+                Nk = int(np.random.exponential(scale=self.enthusiasm)) + 1
+                # This is the number of classifications made by the kth classifier
+                # Nk = 1 is the most likely number, it's the bin with the most
+                # classifiers in it. Now find where in the ordered sequence of 
+                # classifiers we are, by drawing randomly from this bin of the 
+                # histogram.
+                
+                mu = self.enthusiasm
+                KK = self.population
+                                
+                # First count the classifiers who will do less than Nk
+                # classifications:
+                i = int((KK/mu)*(mu - (Nk-1.0+mu)*np.exp(-1.0*(Nk-1.0)/mu)))
+                
+                # Now draw a classifier from the Nk column:
+                j = int((KK*Nk/(mu*mu))*np.exp(-1.0*Nk/mu))
+                k = i + int(np.random.rand() * j)
+                
+                # BUG: this should really be a draw without replacement.
+                # No matter - its good enough for a sim.
+                               
+                # print "Classifier: Nk,i,j,k = ",Nk,i,j,k
+                if j == 0 or k >= KK:
+                    # print "Rejecting Classifier: Nk,i,j,k = ",Nk,i,j,k
+                    j = 0
+                        
             something = self.classifiers[k]
 
         

### 2013-05-10 analysis/swap/agent.py
Fixing an initialization of N

@@ -88,7 +88,7 @@ class Agent(object):
         self.PL = pars['initialPL']
         self.ND = pars['initialND']
         self.NL = pars['initialNL']
-        self.N = 0
+        self.N = initialND+initialNL
         self.NT = initialND+initialNL
         self.contribution = self.update_contribution()
         self.traininghistory = {'ID':'tutorial','I':np.array([self.contribution]),'PL':np.array([self.PL]),'PD':np.array([self.PD])}

### 2013-05-10 analysis/swap/agent.py
Initializing N and Nt

@@ -88,8 +88,8 @@ class Agent(object):
         self.PL = pars['initialPL']
         self.ND = pars['initialND']
         self.NL = pars['initialNL']
-        self.N = initialND+initialNL
-        self.NT = initialND+initialNL
+        self.N = 0
+        self.NT = 0
         self.contribution = self.update_contribution()
         self.traininghistory = {'ID':'tutorial','I':np.array([self.contribution]),'PL':np.array([self.PL]),'PD':np.array([self.PD])}
         self.testhistory = {'ID':[],'I':np.array([])}

### 2013-05-10 analysis/swap/logging.py
really strict 95% test

@@ -41,7 +41,7 @@ helloswitch      = '                   SWITCH: the Space Warps Retirement Plan  
 # ======================================================================
 # Write a PDF report, using latex:
 
-def write_report(pars,crowd,sample):
+def write_report(pars,bureau,sample):
 
     tex = pars['dir']+'/'+pars['trunk']+'_report.tex'
 
@@ -63,9 +63,11 @@ def write_report(pars,crowd,sample):
     # First, just count things:
 
     sample.take_stock()
+    bureau.collect_probabilities()
     
-    N = np.sum(sample.exposure['sim'])+np.sum(sample.exposure['dud'])+np.sum(sample.exposure['test'])    
-    Nc = len(crowd.member)
+    Nmade = np.sum(bureau.Ntotal)
+    Nused = np.sum(sample.exposure['sim'])+np.sum(sample.exposure['dud'])+np.sum(sample.exposure['test'])    
+    Nc = len(bureau.member)
     
     # Ns = len(sample.member)
     # assert (Ns == sample.N)
@@ -79,7 +81,8 @@ def write_report(pars,crowd,sample):
 
     F.write('\\begin{tabular}{|p{0.65\linewidth}p{0.2\linewidth}|}\n')
     F.write('\hline\n')
-    F.write('Number of classifications:         & %d   \\\\ \n' % N )
+    F.write('Number of classifications:         & %d   \\\\ \n' % Nmade )
+    F.write('Number of class$^{\\rm n}$s used:  & %d   \\\\ \n' % Nused )
     F.write('Number of classifiers:             & %d   \\\\ \n' % Nc )
     F.write('Number of test subjects:           & %d   \\\\ \n' % Ns )
     F.write('Number of sims:                    & %d   \\\\ \n' % Ntl )
@@ -89,7 +92,7 @@ def write_report(pars,crowd,sample):
 
     # Now, what has the crowd achieved?
     
-    Nc_per_classifier = np.average(crowd.Ntest)
+    Nc_per_classifier = np.average(bureau.Ntest)
     Nc_per_subject    = np.average(sample.exposure['test'])
     Ns_retired = sample.Ns_retired
     Ns_rejected = sample.Ns_rejected

### 2013-05-10 analysis/swap/subject.py

@@ -104,6 +104,9 @@ class Subject(object):
 
     def was_described(self,by=None,as_being=None,at_time=None,ignore=0):
 
+        # Update agent: 
+        by.N += 1
+
         if by==None or as_being==None:
             pass
 
@@ -163,12 +166,12 @@ class Subject(object):
                 elif self.probability > self.detection_threshold:
                     self.status = 'detected'
                     if self.kind == 'test':
-                        self.state = 'inactive'
-                        self.retirement_age = at_time
-                    
+                        # Let's keep the detections live!
+                        # self.state = 'inactive'
+                        # self.retirement_age = at_time
+                        pass
 
                 # Update agent - training history is taken care of elsewhere: 
-                by.N += 1
                 if self.kind == 'test':
                      by.testhistory['ID'] = self.ID
                      by.testhistory['I'] = by.contribution

### 2013-05-10 doc/sw-system.tex

@@
 
-Indeed, the information content of each classification can be estimated by an
-agent before the next classification is made, just from its confusion matrix.
-We define the expected contributed information per classification, as
-\be
-  \langle I_k \rangle = \frac{1}{2} 
-                        \sum_{i} \left( \mathcal{M}^k_{i}  
-              + \mathcal{M}^k_{i}\cdot\log_2{\mathcal{M}^k_i} \right),
-  \label{eq:app:info}
-\ee
-where $i$ runs over all 4 elements of the confusion matrix 
-$\mathcal{M}^k_i$, and $\langle I_k \rangle$ is measured in ``bits.'' 
-The second term in the sum is recognisable as a
-negative entropy, while the first term and the factor of 1/2
-account for the way the confusion matrix encodes the results for the
-classification of two types of subject, and that the probabilities
-associated with each type are normalised. \Eref{eq:app:info} gives the
-required result, that 
-both the hypothetical {\it perfect} and
-{\it obtuse} classifiers contribute 
-1 bit of information each, per classification.
+% This is incorrect, so for the moment commenting it out
+%Indeed, the information content of each classification can be estimated by an
+%agent before the next classification is made, just from its confusion matrix.
+%We define the expected contributed information per classification, as
+%\be
+%  \langle I_k \rangle = \frac{1}{2} 
+%                        \sum_{i} \left( \mathcal{M}^k_{i}  
+%              + \mathcal{M}^k_{i}\cdot\log_2{\mathcal{M}^k_i} \right),
+%  \label{eq:app:info}
+%\ee
+%where $i$ runs over all 4 elements of the confusion matrix 
+%$\mathcal{M}^k_i$, and $\langle I_k \rangle$ is measured in ``bits.'' 
+%The second term in the sum is recognisable as a
+%negative entropy, while the first term and the factor of 1/2
+%account for the way the confusion matrix encodes the results for the
+%classification of two types of subject, and that the probabilities
+%associated with each type are normalised. \Eref{eq:app:info} gives the
+%required result, that 
+%both the hypothetical {\it perfect} and
+%{\it obtuse} classifiers contribute 
+%1 bit of information each, per classification. 
+%
+%In fact, the only classifier that contributes the minimum information per
+%classification, zero bits, is the {\it random} classifier, whose agent's
+%confusion matrix elements are all 0.5.
 
-In fact, the only classifier that contributes the minimum information per
-classification, zero bits, is the {\it random} classifier, whose agent's
-confusion matrix elements are all 0.5.   
 We conservatively initialise all the agents' confusion matrices to be that of
@@
 help prevent large numbers of false positives being assigned high probability.
-Plotting  $\langle I_k \rangle$ as a function of time will, to some extent,
-illustrate the
-learning process undergone by the $k^{\rm th}$ volunteer-agent partnership.
+%Plotting  $\langle I_k \rangle$ as a function of time will, to some extent,
+%illustrate the
+%learning process undergone by the $k^{\rm th}$ volunteer-agent partnership.
 
@@
 promote it in \Talk, respectively.
+
+The confusion matrix obtained from the application of Equation
+(\ref{eq:app:fraction}) has some inherent noise which will reduce as the number
+of training subjects classified by the user increases. For simplicity, the
+discussion thus far assumed the case when the confusion matrix is known
+perfectly. Let us now discuss the case when the noise in the confusion matrix
+is known. For ease of notation, we will denote $\pr(C_k|\LENS,T_k)\equiv p_1$
+and $\pr(C_k|\NOT,T_k)\equiv p_2$. In reality, there is a probability
+distribution for both $p_1$ and $p_2$. Let $p_0$ be the prior probability of
+the subject being a lens. Then the posterior probability, $p_0'$ of the subject
+being a lens after the classification $C_k$ is
+\be
+  \label{eq:app:sec}
+p_0' = \frac{p_1 p_0}{\left[ p_1 p_0 + p_2 (1- p_0) \right]},
+\ee
+In principle, the probability distributions for every agent $p_1,p_2$ and the
+prior probability $p_0$ could be maintained on a fine grid, so that the full
+posterior probability distribution can be obtained by the following
+marginalization procedure:
+\be
+P(p_0') = \int p_0' P(p_1) P(p_2) P(p_0) dp_1 dp_2 dp_0
+\ee
+This marginalization is likely not tractable analytically, but can perhaps be
+implemented in a Monte-Carlo fashion. This needs to be further investigated.
+
+Instead, for simplicity let us make some approximations to reduce each of the
+probability distribution to two numbers its mean and a variance. Let us assume
+that $p_1$ and $p_2$ are Gaussian distributed around some mean value
+$\bar{p}_x$ with a variance equal to $\sigma_x$. We will obtain $\bar{p}_0'$ by
+substituting the mean values $\bar{p}_1$ and $\bar{p_2}$ in Equation
+(\ref{eq:app:sec}) and the variance of $p_0'$ by simple error propagation
+\begin{eqnarray}
+\left(\frac{\sigma_0'}{\bar{p}_0'}\right)^2 =&& \left(\frac{\sigma_1}{p_1}\right)^2 + \left(\frac{\sigma_0}{p_0}\right)^2 \nonumber \\
+&+& \frac{ (p_1\sigma_0)^2 + (\sigma_1p_0)^2 + \sigma_2^2 + (p_2\sigma_0)^2 + (\sigma_2p_0)^2}{ \left[ p_1 p_0 + p_2 (1- p_0)\right]^2 } \nonumber \\
+\end{eqnarray}
+
+Finally, we also need to update the confusion matrix of an agent and obtain the
+variance on each element of the matrix, once a training subject has been
+classified. We would like to derive the posterior probability of the
+probability elements $p_1$ and $p_2$ given their prior probabilities. For this
+purpose, we can again make use of Bayes' theorem,
+\begin{equation}
+P(p_x'|N_{"X"},N_X,T) = \frac{P(N_{``X"}|p_x',N_X,T) P(p_x'|N_X,T)}{\sum_{N_{``X"}} P(N_{``X"}|p_x',N_X,T) P(p_x'|N_X,T)}
+\end{equation}
+We assume that $P(N_{``X"}|p_x',N_X,T)$ is a Poisson distribution, although
+this is not true strictly speaking given that our agents are learning and the
+values of the confusion matrix are moving. Modelling the learning curve of our
+users is yet another complicated extension we could think about.
 

### 2013-05-10 analysis/swap/agent.py
Fixed negative sign in the information

@@ -108,7 +108,7 @@ class Agent(object):
         plogp = np.zeros([2])
         plogp[0] = (self.PD+self.PL)/2.*np.log2((self.PD+self.PL)/2.)
         plogp[1] = (1.-self.PD+1.-self.PL)/2.*np.log2((1.-self.PD+1.-self.PL)/2.)
-        self.contribution = np.sum(plogp)
+        self.contribution = -np.sum(plogp)
         return self.contribution
         
 # ----------------------------------------------------------------------

### 2013-05-16 doc/sw-system.tex
Updated information content by agent, updated plot and startup config

@@
 
-% This is incorrect, so for the moment commenting it out
-%Indeed, the information content of each classification can be estimated by an
-%agent before the next classification is made, just from its confusion matrix.
-%We define the expected contributed information per classification, as
-%\be
-%  \langle I_k \rangle = \frac{1}{2} 
-%                        \sum_{i} \left( \mathcal{M}^k_{i}  
-%              + \mathcal{M}^k_{i}\cdot\log_2{\mathcal{M}^k_i} \right),
-%  \label{eq:app:info}
-%\ee
-%where $i$ runs over all 4 elements of the confusion matrix 
-%$\mathcal{M}^k_i$, and $\langle I_k \rangle$ is measured in ``bits.'' 
-%The second term in the sum is recognisable as a
-%negative entropy, while the first term and the factor of 1/2
-%account for the way the confusion matrix encodes the results for the
-%classification of two types of subject, and that the probabilities
-%associated with each type are normalised. \Eref{eq:app:info} gives the
-%required result, that 
-%both the hypothetical {\it perfect} and
-%{\it obtuse} classifiers contribute 
-%1 bit of information each, per classification. 
-%
-%In fact, the only classifier that contributes the minimum information per
-%classification, zero bits, is the {\it random} classifier, whose agent's
-%confusion matrix elements are all 0.5.
+Indeed, the information content of each classification can be estimated by an
+agent before the next classification is made, just from its confusion matrix.
+We define the expected contributed information per classification, as
+\be
+  \langle I_k \rangle = \frac{1}{2} 
+    \left(
+    \mathcal{M}^k_{d}\cdot\log_2{\mathcal{M}^k_d} +  \mathcal{M}^k_{o}\cdot\log_2{\mathcal{M}^k_o} \right),
+  \label{eq:app:info}
+\ee
+where $\mathcal{M}^k_d$ and $\mathcal{M}^k_o$ is the sum of the diagonal and
+the off-diagonal elements of the confusion matrix and $\langle I_k \rangle$ is
+measured in ``bits.'' The factor of 1/2 accounts for the way the confusion
+matrix encodes the results for the classification, and
+that the probabilities associated with each type are normalised.
+\Eref{eq:app:info} gives the required result, that both the hypothetical {\it
+perfect} and {\it obtuse} classifiers contribute 1 bit of information each, per
+classification.
+
+In fact, the only classifier that contributes the minimum information per
+classification, zero bits, is the {\it random} classifier, whose agent's
+confusion matrix elements are all 0.5.
 

### 2013-05-16 analysis/swap/agent.py

@@ -108,7 +108,7 @@ class Agent(object):
         plogp = np.zeros([2])
         plogp[0] = (self.PD+self.PL)/2.*np.log2((self.PD+self.PL)/2.)
         plogp[1] = (1.-self.PD+1.-self.PL)/2.*np.log2((1.-self.PD+1.-self.PL)/2.)
-        self.contribution = -np.sum(plogp)
+        self.contribution = 1.0+np.sum(plogp)
         return self.contribution
         
 # ----------------------------------------------------------------------

### 2013-05-16 analysis/swap/bureau.py

@@ -204,6 +204,10 @@ class Bureau(object):
         plt.text(0.02,0.96,'"Pessimistic"',color='gray')
         plt.text(0.74,0.02,'"Optimistic"',color='gray')
         plt.text(0.81,0.96,'"Astute"',color='gray')
+        plt.text(0.15,0.87,'"Random classifier"',color='gray',rotation=-45)
+
+        # Plot the random classifier line
+	plt.plot(np.arange(2),1-np.arange(2),color='grey');
         
         # Training received:
         size = 4*self.Ntraining + 6.0

### 2013-06-13 analysis/swap/mongodb.py
Notes, bug fix in mongodb?

@@ -6,7 +6,7 @@ import os,sys,datetime
 try: from pymongo import MongoClient
 except:
     print "MongoDB: pymongo is not installed. You can still --practise though"
-    sys.exit()
+    # sys.exit()
 
 # Hard-coded for all Space Warps datasets? Or just beta?
 testGroup = '5154a3783ae74086ab000001'

### 2013-06-13 doc/sw-system.tex

--- 2013-05-06 doc/sw-system.tex
@@
 \ee
-On being given a fresh subject that actually is a $\LENS$,
-this hypothetical volunteer would submit $C = \saidLENS$. 
-Their agent would then calculate the posterior probability for the 
-subject being a $LENS$ to be
+On being given a fresh subject that actually is a $\LENS$, this hypothetical
+volunteer would submit $C = \saidLENS$.  Their agent would then calculate the
+posterior probability for the subject being a $LENS$ to be
 \begin{align}
@@
 \end{align}
-as we might expect for such a {\it perfect} classifier. 
-Meanwhile, a hypothetical volunteer who (for some reason) 
-wilfully always submits the wrong 
+as we might expect for such a {\it perfect} classifier.  Meanwhile, a
+hypothetical volunteer who (for some reason) wilfully always submits the wrong
 classification would have an agent with the column-swapped confusion matrix
@@
 and would submit $C = \saidNOT$ for this subject. However, such a volunteer
-would nevertheless be submitting useful
-information, since given the above confusion matrix, their agent would
-calculate
+would nevertheless be submitting useful information, since given the above
+confusion matrix, their agent would calculate
 \begin{align}
@@
 agent before the next classification is made, just from its confusion matrix.
-We define the expected contributed information per classification, as
+The Shannon entropy generated by a classifier upon performing a
+classification is
 \be
-  \langle I_k \rangle = \frac{1}{2} 
-                        \sum_{i} \left( \mathcal{M}^k_{i}  
-              + \mathcal{M}^k_{i}\cdot\log_2{\mathcal{M}^k_i} \right),
+  \langle S_k \rangle =  
+   -P_{\rm right}\cdot\log_2{P_{\rm right}} -  P_{\rm wrong}\cdot\log_2P_{\rm wrong}\,,
+\ee
+where $P_{\rm right}$ and $P_{\rm wrong}$ are the averages of the diagonal and
+the off-diagonal elements of the confusion matrix, respectively, and $\langle
+S_k \rangle$ is measured in ``bits.'' These averages represent the probability
+of a classifier to get a classification right or wrong, respectively. We define
+the information contributed by a classifier as
+\begin{equation}
+I_k = 1 - S_k\,.
   \label{eq:app:info}
-\ee
-where $i$ runs over all 4 elements of the confusion matrix 
-$\mathcal{M}^k_i$, and $\langle I_k \rangle$ is measured in ``bits.'' 
-The second term in the sum is recognisable as a
-negative entropy, while the first term and the factor of 1/2
-account for the way the confusion matrix encodes the results for the
-classification of two types of subject, and that the probabilities
-associated with each type are normalised. \Eref{eq:app:info} gives the
-required result, that 
-both the hypothetical {\it perfect} and
-{\it obtuse} classifiers contribute 
-1 bit of information each, per classification.
+\end{equation}
+\Eref{eq:app:info} gives the required result, that both the hypothetical {\it
+perfect} and {\it obtuse} classifiers contribute 1 bit of information each, per
+classification. Classifiers whose agent's confusion matrix is such that $P_{\rm
+right}=P_{\rm wrong}=0.5$, contribute zero bits of information. Such users
+identify a lens correctly with the same probability as they misclassify a dud
+image to contain a lens, and thus their classification is of no value.
 
-In fact, the only classifier that contributes the minimum information per
-classification, zero bits, is the {\it random} classifier, whose agent's
-confusion matrix elements are all 0.5.   
-We conservatively initialise all the agents' confusion matrices to be that of
-the random classifier. This makes no allowance for volunteers that actually do
-have previous experience of what gravitational lenses look like, but should
-help prevent large numbers of false positives being assigned high probability.
-Plotting  $\langle I_k \rangle$ as a function of time will, to some extent,
-illustrate the
-learning process undergone by the $k^{\rm th}$ volunteer-agent partnership.
+We conservatively initialise all the elements of the agents' confusion matrices
+to be 0.5, that of a random classifier. This makes no allowance for volunteers
+that actually do have previous experience of what gravitational lenses look
+like, but should help prevent large numbers of false positives being assigned
+high probability. Plotting  $\langle I_k \rangle$ as a function of time will,
+to some extent, illustrate the learning process undergone by the $k^{\rm th}$
+volunteer-agent partnership.
 
@@
 promote it in \Talk, respectively.
+
+The confusion matrix obtained from the application of Equation
+(\ref{eq:app:fraction}) has some inherent noise which reduces as the number
+of training subjects classified by the user increases. For simplicity, the
+discussion thus far assumed the case when the confusion matrix is known
+perfectly. Let us first discuss how to characterize the noise in the confusion
+matrix. ** This needs work **
+
+For ease of notation, we will denote $\pr(C_k|\LENS,T_k)\equiv p_L$ and
+$\pr(C_k|\NOT,T_k)\equiv p_N$. In reality, there is a probability distribution
+for both $p_L$ and $p_N$. Let $p_0$ be the prior probability of the subject
+being a lens. Then the posterior probability, $p_0'$ of the subject being a
+lens after the classification $C_k$ is
+\be
+  \label{eq:app:sec}
+p_0' = \frac{p_L p_0}{\left[ p_L p_0 + p_N (1- p_0) \right]},
+\ee
+The posterior probability distribution $p_0'$ can be obtained by marginalizing
+over the probability distributions of $p_L$, $p_N$ and the prior probability
+distribution $p_0$ such that,
+\be
+P(p_0') = \int p_0' P(p_L) P(p_N) P(p_0) dp_L dp_N dp_0\,.
+\ee
+This marginalization is not analytically tractable. Therefore, we have
+implemented the following Monte-Carlo solution for this problem.
+
+%Finally, we also need to update the confusion matrix of an agent and obtain the
+%variance on each element of the matrix, once a training subject has been
+%classified. We would like to derive the posterior probability of the
+%probability elements $p_1$ and $p_2$ given their prior probabilities. For this
+%purpose, we can again make use of Bayes' theorem,
+%\begin{equation}
+%P(p_x'|N_{"X"},N_X,T) = \frac{P(N_{``X"}|p_x',N_X,T) P(p_x'|N_X,T)}{\sum_{N_{``X"}} P(N_{``X"}|p_x',N_X,T) P(p_x'|N_X,T)}
+%\end{equation}
+%Here, $P(N_{``X"}|p_x',N_X,T)$ is a binomial distribution, although this is not
+%true strictly speaking given that our agents are learning and the values of the
+%confusion matrix are moving. Modelling the learning curve of our users is yet
+%another complicated extension we could think about.
 

### 2013-12-19 doc/sw-publication-policy-cfhtls.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Space Warps Publication Policy
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper]{article}

% Packages:
\usepackage{xspace}
\usepackage{verbatim}
\usepackage{hyperref}

% Macros:
\input{macros.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{\SW Collaboration Publication Policy: CFHT-LS}
\author{Phil Marshall \& Aprajita Verma}
\date{April 15, 2013}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract} 
\noindent \sw was conceived as a strong lens
discovery {\it service}, that any survey science team can make use of
(within the logistical constraints). 
In this document, we define 
the various types of \sw
collaboration membership, and their meaning in terms of the \sw
paper series. This includes guidelines for publications of \sw-enabled discoveries. We also discuss the \sw data usage policy and outline the first set of \sw papers.

As \sw was developed based on the requirements of the first \sw project, CFHT-LS, the policy for the first project differs from subsequent \sw projects involving new data. This document is written specifically for the CFHT-LS project and subsequent projects should refer to the ``Guidelines and Policy for Surveys using \sw'' document.
\end{abstract}

\setcounter{footnote}{0}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Collaboration Membership Types}
\label{sec:members}

The \sw website is designed to motivate and  enable tens of thousands of
people to perform the scientific tasks of strong gravitational lens
identification and classification.  The \sw collaboration comprises the
sum total of the volunteers who have logged in and contributed
classifications to the project. (We would include those who did not
log in as well, but we don't know who they are.) This means that the
minimal requirement for \sw collaboration membership is classification with a Zooniverse ID,
and some contribution on the site (\ie classifying, or discussing
Subjects in \Talk \footnote{\Talk (found at talk.spacewarps.org) is a forum for \sw collaborators to discuss individual sources and the \sw project in general. Bugs can also be reported. This is the direct portal for communication with the \sw community.}).

The collaboration membership is broadly split into four subsets:

\begin{description}

\item{\bf Principal Investigators:} These are the PIs of the \sw project (P.\,Marshall, 
A.\,More and A.\,Verma)\footnote{The PIs may be collectively contacted via the email address spacewarpspi@googlegroups.com}

\item{\bf Zooniverse:} \sw development team (led by
A.\,Kapadia).

\item{\bf Science Team:} This is a core group of scientists, both citizen and
professional, that helped to design, build and test the \sw website
and the initial CFHT-LS project. The Science Team includes the PIs.

\item{\bf Community} All of the volunteers who have contributed
classifications to the project\footnote{We can only communicate directly with those who have logged in with a Zooniverse ID via \Talk or group e-mail.}.

\item{\bf Affiliated:} This group includes professional scientists who have made some contribution to the \sw project, but smaller than the Science Team. Such contributions might include helping write the initial
Citizen Science Alliance proposal, participating in discussions on
\Talk, writing \sw blog posts, advising on the data analysis, or editing
papers.

\end{description}

In the remaining sections we look at the various publications that might
arise from the \sw project, and suggest reasonable guidelines for
deciding on their authorship.

%First, however, we remind ourselves about data access via \sw.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Survey Data Use}
%\label{sec:data}

%\sw is a public website. All images displayed there are by definition in the
%public domain, and so must be expected to be downloaded, copied and
%redistributed by any \sw user. This is a \textbf{good thing}: images of the sky taken
%with publicly-funded telescopes belong to everyone. It is the responsibility
%of the survey science teams to provide images in a way that is consistent
%with their own data access rules.

%While the CFHT-LS is a public survey, the WCS information has been removed from the provided images. This prevents the follow-up of any of the objects in the survey by anyone other than the \sw
%team. In practice, the objects contained in the \sw images will be too faint
%for anyone without access to a large telescope to observe, and may also be
%absent from any public catalogs, so the opportunities for follow-up will be
%quite limited. Removing the WCS information is an insurance policy against any
%competing professional scientists looking to ``scoop'' the survey team,
%despite the damage it would do to their reputations.\footnote{We cannot exclude the possibility that object co-ordinates are posted in \Talk. For example, co-ordinates of previously published lens candidates or recognisable fields from CFHT-LS have appeared in \Talk.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The \SW Paper Series}
\label{sec:series}

We are planning a short series of journal papers describing the \sw service, its
first dataset (CFHT-LS), and results from its investigation by the
collaboration. These results will likely include a sample of new lenses,
and some comparison studies between the visual and automated
identification of lens systems in this survey. This series will be known
as ``the \sw papers,'' and each one will have a title that starts with ``\sw.''

The initial papers we are planning to write include (in no particular order, and the actual paper series may be split or change in content and order):

\begin{itemize}
\item \sw I: The system paper, describing the project, the interface, the classification analysis methods (SWAP) and results 
\item \sw II: The \sw  simulations and community performance (not selection function), means by which you can compute a selection function for any given analysis. 
\item \sw III: The first new candidates from CFHT-LS \textit{including models, follow-up if feasible}
\item \sw IV: The results from CFHT-LS search including the comparison and analysis of citizen scientist classification versus lens-finding algorithms (maybe split into smaller papers).
\end{itemize}

There maybe further series papers (TBC).\newline

Please email the \sw PIs at spacewarpspi@googlegroups.com if you have any ideas for further \sw series papers (this includes any publications that include a new lens system that was found by \sw). The authorship policy is defined in the next section.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publication Policy}
\label{sec:publ}

\subsection{Journal Papers}
\label{sec:series}
A core team of collaborators will participate in writing journal papers, and many collaborators who have made a \textit{significant contribution} to \sw will be recognised on the author
lists of journal papers presenting \sw results.  However, not all collaboration members will participate in writing journal papers.  \textit{Significant contributions} include those who have contributed to:
\begin{itemize}
\item the site design, construction and operation
\item data preparation or analysis
\item writing and editing the papers. 
\end{itemize}

The current list of \sw authors is given in the \texttt{authors.tex} file and is reprinted
in the appendix to this document (see Appendix \ref{sec:appa}); this file shown is as it is currently configured, ready to be copied and pasted into the \sw system paper (\sw I).

\noindent The author categories are grouped according to collaboration membership (defined above). These groups of authors have either the status to ``opt-out'' or "on contribution" of \sw publications.  ``Opt-out'' means the listed people are authors by default and must explicitly state if they wish for their names to be removed from \sw publications. ``On contribution'' means the people listed are invited to comment on and contribute to publications. The Principal Investigators, Zooniverse development team and \sw Science team all have opt-out status and the \sw Affiliates have on contribution status.

The first author of any \sw paper will decide, as
usual, on the author list of their own paper. This will include adding Affiliates who they think have made a substantial contribution to that investigation, as well as inviting
scientists from outside the list of \sw authors, or from outside the
collaboration.  The PIs will act as adjudicators if any disputes arise,
but to be honest we are not expecting any.

Lead authors of \sw papers should circulate drafts to the list of \sw authors (according to the policy above) and allow a minimum of two weeks to give time for comments and to opt-in. If  ``on contribution'' authors have not provided comments within this time frame they will not be included as authors on the paper. If ``opt-out'' authors have not responded to ask for their names to be removed they will be kept on the author list.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Zooniverse Publications: Letters and Talk }
\label{sec:zoolet}

Any \sw collaboration member, simply by virtue of their Zooniverse
registration, may write a Zooniverse
Letter\footnote{\texttt{http://letters.zooniverse.org}} describing their
investigation of any lens candidate they find in \sw. This, along with
posts in  \Talk, are the primary means by which we expect collaboration
members will communicate their findings to the rest of the
astronomical community. 
The \sw Zooniverse \Letters will contribute to the collective knowledge and understanding of the presented system(s). 
Zooniverse \Letters are citable
objects, and in some cases will appear listed on ADS.\footnote(To be confirmed.)
We strongly encourage community members to write Zooniverse \Letters about their findings. We would be happy to help any member wishing to do this, please just drop us a line at spacewarpspi@googlegroups.com.

As \sw classifications are a community wide activity, it is impossible to attribute the discovery of a candidate to a single community member, or group  of members. Therefore, in recognition of their contribution to the \sw project, all \sw community members will be listed (on their approval) on the \sw members web page (URL: to be added). This web page will be linked to in the acknowledgements of every ensuing \sw publication. If a community member makes a significant contribution e.g.\,in the further investigation of a lens candidate with modelling tools, they are strongly encouraged to write Zooniverse Letters (see Section \ref{sec:zoolet}). This may lead to them being invited to join journal publications by the lead author.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publication Guidelines}
\label{sec:publ}

Any \sw series and \sw enabled discovery papers should include
\begin{itemize}
\item citations to the \sw system papers, \sw I \& II
\item the collaboration should be acknowledged in the acknowledgement section with a link to the collaboration membership page (URL: to be added).
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix
\section{Current Author List: author.tex}
\label{sec:appa}
{\small \verbatiminput{./authors.tex}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-12-19 doc/sw-publication-policy-gen.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Space Warps Publication Policy
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper]{article}

% Packages:
\usepackage{xspace}
\usepackage{verbatim}
\usepackage{hyperref}

% Macros:
\input{macros.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{Guidelines and Policy for Surveys using \SW}
\author{Phil Marshall \& Aprajita Verma}
\date{April 15, 2013}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract} 
\noindent \sw was conceived as a strong lens
discovery {\it service}, that any survey science team can make use of
(within the logistical constraints). In this document we discuss the relationship
between the survey teams and the \sw collaboration. 
This document includes guidelines for data provision, the data policy and for publications of \sw-enabled discoveries.
\end{abstract}

\setcounter{footnote}{0}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction to \sw}

The \sw website is designed to motivate and  enable tens of thousands of
people to perform the scientific tasks of strong gravitational lens
identification and classification.  \sw comprises a primary classification interface (www.spacewarps.org) that allows citizen scientists to inspect images and mark those that contain potential gravitational lenses. In addition, the citizens are shown simulated lenses (appropriate for the survey being conducted) as an interactive training tool that also allows us to establish the Citizens' likelihood of identifying potential lenses and blank fields using the \sw Analysis Pipeline (SWAP).

A key part of the \sw project is the ability for all members of the \sw collaboration (see Section \ref{sec:members}) to communicate with each other and discuss interesting candidates through \Talk\footnote{\Talk (found at \texttt{talk.spacewarps.org}) is a forum for \sw collaborators to discuss individual sources and the \sw project in general. Bugs can also be reported. This is the direct portal for communication with the \sw community.}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Collaboration Membership Types}
\label{sec:members}

The \sw collaboration comprises the \sw science team, development team and all the volunteers who have 
logged in\footnote{with a Zooniverse ID. It is possible to classify anonymously, and we count those classification but as we don't know who they are, we are unable to collaborate with them directly.} and contributed classifications to the project.

An expanded definition of the \sw membership is given in the document ``\sw Publication Policy: CFHT-LS''.  In this document we discuss the relationship between the \sw collaboration and future Survey Science Teams (SST) who are foreseen to liaise with the \sw science and development teams to ingest their survey data into the \sw interface. \sw was established with future surveys in mind and therefore there may be some overlap between current \sw members and the future SSTs.

In the remaining sections we look at discovery publications that might
arise from future \sw projects, and suggest reasonable guidelines for
deciding on their authorship. First, however, we remind ourselves about data
access via \sw.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Survey Data Policy}
\label{sec:data}

\sw is a public website. All images displayed there are by definition in the
public domain, and so must be expected to be downloaded, copied and
redistributed by any \sw user. This is a \textbf{good thing}: images of the sky taken
with publicly-funded telescopes belong to everyone. It is the responsibility
of the SSTs to provide images in a way that is consistent
with their own data access rules. There are two things that SSTs can
do to in order to respect any proprietary period that they have imposed on
themselves:
\begin{enumerate}

\item Add a ``LICENSE'' keyword to the FITS and PNG image headers, explaining
what the rules for redistribution of these images are. This will almost
certainly be ignored, but it would be a nice reminder that nothing comes free
of either cost or responsibility. Other keywords could also be included as
well: data provenance is important, and links to useful survey webpages would
be most welcome!

\item Remove all WCS information from all images provided. The \sw interface ``dashboards'' do allow FITS and JPG files to be downloaded. If images from a proprietary dataset being made available is a concern for an SST, they should remove the WCS. This also has the consequence that it minimises the potential ``scooping'' of potential lens candidate by anyone other than the SST. 
In practice, the objects contained in the \sw images will be too faint
for anyone without access to a large telescope to observe, and may also be
absent from any public catalogs, so the opportunities for follow-up will be
quite limited. Images
with field of view less than about 3~arcminutes in diameter are not solvable
by \texttt{astrometry.net}. Please note, however, that we cannot exclude the possibility that object co-ordinates are posted in \Talk. For example, co-ordinates of previously published lens candidates or recognisable fields from CFHT-LS have appeared in \Talk.

% becuase being ``scooped'' is a concern,  for an SST then this is a means of prevention. We do

%This would prevent
%follow-up of any of the objects in the survey by anyone other than the survey
%team. In practice, the objects contained in the \sw images will be too faint
%for anyone without access to a large telescope to observe, and may also be
%absent from any public catalogs, so the opportunities for follow-up will be
%quite limited. Removing the WCS information is an insurance policy against any
%competing professional scientists looking to ``scoop'' the survey team,
%despite the damage it would do to their reputations\footnote{Please note that we cannot exclude the possibility that object co-ordinates are posted in \Talk. For example, co-ordinates of previously published lens candidates or recognisable fields from CFHT-LS have appeared in \Talk.} . We note that images
%with field of view less than about 3~arcminutes in diameter are not solvable
%by \texttt{astrometry.net}.

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Data Preparation and Publications for Future Survey Teams}
\label{sec:series}

There is a reasonable amount of work in preparing data and images for delivery to \sw. The \sw team will provide assistance to future teams in data preparation. We hope the benefits of using the \sw service will far outweigh the time needed to prepare data.

\subsection{Future Project Proposals}
Any future \sw projects are requested to liaise with the PIs regarding their project. We ask that potential project teams first approach the PIs (Marshall, Verma, More) with a short description of their project that includes the following information.

\begin{itemize}
\item Survey
\item Bands to be included
\item Total number of images to be viewed (approx.)
\item Targeted survey or blind field search \footnote{Targeted: inspection of a list of candidates; Blind: inspection of tiles of a survey area}
\item Brief outline of the overall goal(s) 
\end{itemize}

The \sw PIs will then arrange a hangout/telecon with the SSTs to discuss their project further.

The original \sw papers by definition, provide a complete description of the system, and its results from the CFHTLS survey. The science team of
any other survey (such as DES, RCS, KIDS, PS1, HSC \etc) should be able
to read these papers before designing their own \sw project, and cite them as justification for some of their decisions. As the \sw paper series appears links to the papers will be given in this draft. Prior to publications, draft papers can also be shared on request by the \sw PIs (\href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com})

\subsection{Collaborating with \sw Science Team}

Implementing a new project based on different survey data will require support from the \sw Science Team, in three
respects: 
\begin{enumerate}

\item In {\bf preparing data} for the site, and uploading it onto the
Zooniverse servers. The \sw Science Team can advise on suitable Training
Subjects and image display settings, and also on formatting the data
ready for ingestion and display.

\item In {\bf reconfiguring the site itself} ready for the new data. The
survey team will need to include new Spotter's Guide images and text,
modified tutorial content, and additional survey-specific site content;
the \sw Science Team can help with all of this.

\item In {\bf maintaining the site} so that it continues to function
correctly. This will involve technical support from the Zooniverse team,
but will also require the continued engagement of the wider
collaboration by the Science Team in \Talk. Since this social filter is
a key part of the sample refinement, the latter may involve a
significant time commitment.

\end{enumerate}

\subsection{Resulting Publications}

\subsubsection{Journal Papers}

In return for the work outlined in Section \ref{sec:series} in setting up the new surveys, the \sw PIs will nominate a
small number of core \sw collaboration members as authors on \textbf{papers that
present discovery of a lens or sample of lenses enabled by the \sw system}. A ``discovery'' is defined by the announcement of the source(s) to the astronomical community in a journal paper. We would expect the \sw author list to be a small number (less than ten), primarily the Principal Investigators and a few others working on the ingestion of the new data. All post-discovery follow-up papers would of course be exempt from this: the idea is that \sw is purely a gravitational lens discovery
service, but not one that runs by magic.

We request that authors of \sw-enabled discovery papers should circulate drafts to the list of \sw authors and allow a minimum of two weeks to give time for comments. We also request that any papers based on \sw enabled discoveries should cite the \sw system papers. This policy document will be updated with the correct citations to the \sw system papers when available.

\sw runs an analysis pipeline (SWAP) that will be tailored to the science goals of each new survey. Any large changes to the analysis code will be documented  by the \sw Science Team. The \sw Science Team reserved the right to update the \sw methodology papers.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Zooniverse \Letters}
\label{sec:comm}

Any \sw collaboration member, simply by virtue of their Zooniverse
registration, may write a Zooniverse
Letter\footnote{\texttt{http://letters.zooniverse.org}} describing their
investigation of any lens candidate they find in \sw. This, along with
posts in  \Talk, is the primary means by which we expect collaboration
members will communicate their findings to the rest of the
astronomical community. The investigation of any \sw images that are
provided without world coordinate system (WCS) information will be
necessarily limited but the \sw Zooniverse \Letters will contribute to the collective knowledge and understanding of the presented system(s). Zooniverse \Letters are citable
objects, and in some cases will appear listed on ADS\footnote{To be confirmed.}.

As \sw classifications are a community wide activity, it is impossible to attribute the discovery of a candidate to a single community member, or group  of members. Therefore, in recognition of their contribution to the \sw project, \sw community members will be listed (on their approval) on the \sw members web page. This web page will be linked in every ensuing \sw publication. If a community member makes a significant contribution e.g.\,in the further investigation of a lens candidate with modelling tools, they are strongly encouraged to write Zooniverse \Letters. This may lead to them being invited to join journal publications by the lead author of a ``discovery'' publication.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publication Guidelines}
\label{sec:publ}
Any \sw series and \sw enabled discovery papers should include
\begin{itemize}
\item citations to the \sw system papers, \sw I \& II
\item the collaboration should be acknowledged in the acknowledgement section with a link to the collaboration membership page (URL: to be confirmed when available).
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-02-11 doc/sw-publication-policy-cfhtls.tex
Updated plan for paper 1

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-We are planning a short series of journal papers describing the \sw service, its
-first dataset (CFHT-LS), and results from its investigation by the
-collaboration. These results will likely include a sample of new lenses,
-and some comparison studies between the visual and automated
-identification of lens systems in this survey. This series will be known
-as ``the \sw papers,'' and each one will have a title that starts with ``\sw.''
+We are planning a short series of journal papers describing the \sw service,
+its first dataset (CFHT-LS), and results from its investigation by the
+collaboration. These results will likely include a sample of new lenses, and
+some comparison studies between the visual and automated identification of
+lens systems in this survey. This series will be known as ``the \sw papers,''
+and each one will have a title that starts with ``\sw.''
 
-The initial papers we are planning to write include (in no particular order, and the actual paper series may be split or change in content and order):
+The initial papers we are planning to write include (in no particular order,
+and the actual paper series may be split or change in content and order):
 
 \begin{itemize}
-\item \sw I: The system paper, describing the project, the interface, the classification analysis methods (SWAP) and results 
-\item \sw II: The \sw  simulations and community performance (not selection function), means by which you can compute a selection function for any given analysis. 
-\item \sw III: The first new candidates from CFHT-LS \textit{including models, follow-up if feasible}
-\item \sw IV: The results from CFHT-LS search including the comparison and analysis of citizen scientist classification versus lens-finding algorithms (maybe split into smaller papers).
+\item \sw I: The system paper, describing the project, the interface, the
+classification analysis methods (SWAP) and results 
+\item \sw II: The \sw  simulations and community performance (not selection
+function), means by which you can compute a selection function for any given
+analysis. 
+\item \sw III: The first new candidates from CFHT-LS \textit{including models,
+follow-up if feasible}
+\item \sw IV: The results from CFHT-LS search including the comparison and
+analysis of citizen scientist classification versus lens-finding algorithms
+(maybe split into smaller papers).
 \end{itemize}
@@
 
-Please email the \sw PIs at spacewarpspi@googlegroups.com if you have any ideas for further \sw series papers (this includes any publications that include a new lens system that was found by \sw).
-The authorship policy is defined in the next section.
+Please email the \sw PIs at spacewarpspi@googlegroups.com if you have any
+ideas for further \sw series papers (this includes any publications that
+include a new lens system that was found by \sw). The authorship policy is
+defined in the next section.
 
@@
 \label{sec:series}
-A core team of collaborators will participate in writing journal papers, and many collaborators who have made a \textit{significant contribution} to \sw will be recognised on the author
-lists of journal papers presenting \sw results.
-However, not all collaboration members will participate in writing journal papers.
-\textit{Significant contributions} include those who have contributed to:
+
+A core team of collaborators will participate in writing journal papers, and
+many collaborators who have made a \textit{significant contribution} to \sw
+will be recognised on the author lists of journal papers presenting \sw
+results.  However, not all collaboration members will participate in writing
+journal papers.  \textit{Significant contributions} include those who have
+contributed to:
 \begin{itemize}
@@
 
-The current list of \sw authors is given in the \texttt{authors.tex} file and is reprinted
-in the appendix to this document (see Appendix \ref{sec:appa}); this file shown is as it is currently configured, ready to be copied and pasted into the \sw system paper (\sw I).
+The current list of \sw authors is given in the \texttt{authors.tex} file and
+is reprinted in the appendix to this document (see Appendix \ref{sec:appa});
+this file shown is as it is currently configured, ready to be copied and
+pasted into the \sw system paper (\sw I).
 
-\noindent The author categories are grouped according to collaboration membership (defined above).
-These groups of authors have either the status to ``opt-out'' or "on contribution" of \sw publications.
-``Opt-out'' means the listed people are authors by default and must explicitly state if they wish for their names to be removed from \sw publications.
-``On contribution'' means the people listed are invited to comment on and contribute to publications.
-The Principal Investigators, Zooniverse development team and \sw Science team all have opt-out status and the \sw Affiliates have on contribution status.
+\noindent The author categories are grouped according to collaboration
+membership (defined above). These groups of authors have either  ``opt-out''
+or ``on contribution'' status regarding \sw publications.  ``Opt-out'' means
+the listed people are authors by default and must explicitly state if they
+wish for their names to be removed from \sw publications. ``On contribution''
+indicates people who will be invited to comment on and contribute to
+publications, ``opting in'' to those papers' author lists. The Principal
+Investigators, Zooniverse development team and \sw Science team all have
+opt-out status and the \sw Affiliates have on contribution status.
 
-The first author of any \sw paper will decide, as
-usual, on the author list of their own paper. This will include adding Affiliates who they think have made a substantial contribution to that investigation, as well as inviting
+The first author of any \sw paper will decide, as usual, on the author list of
+their own paper. This will include adding Affiliates who they think have made
+a substantial contribution to that investigation, as well as inviting
 scientists from outside the list of \sw authors, or from outside the
-collaboration.  The PIs will act as adjudicators if any disputes arise,
-but to be honest we are not expecting any.
+collaboration.  The PIs will act as adjudicators if any disputes arise, but to
+be honest we are not expecting any.
 
-Lead authors of \sw papers should circulate drafts to the list of \sw authors (according to the policy above) and allow a minimum of two weeks to give time for comments and to opt-in.
-If  ``on contribution'' authors have not provided comments within this time frame they will not be included as authors on the paper.
-If ``opt-out'' authors have not responded to ask for their names to be removed they will be kept on the author list.
+Lead authors of \sw papers should circulate drafts to the list of \sw authors
+(according to the policy above) and allow a minimum of two weeks to give time
+for comments and to opt-in. If  ``on contribution'' authors have not provided
+comments within this time frame they will not be included as authors on the
+paper. If ``opt-out'' authors have not responded to ask for their names to be
+removed they will be kept on the author list.
 

### 2014-02-11 doc/sw-system.tex
Updated plan for paper 1

@@
 
-\sw is a web-based service
- that enables the discovery of strong
-gravitational lenses in wide-field imaging surveys by arbitrarily large
-numbers of people. Carefully produced color composite images are
-displayed to volunteers via a flexible interface, which records
-their estimates of the positions of candidate lensed features. Simulated
-lenses, and expert-classified non-lenses, are inserted into the stream
-at random intervals; this training set is used to give the volunteers
-feedback on their performance as well as estimate a dynamically-updated
-probability for any given image containing a lens. High probability
-systems are filtered into the Zooniverse \Talk discussion system; this
-smaller sample is further classified and analysed by volunteers into a
-final set. We analyze the classification of the training set itself, and
-find that 1) $<$volunteers learn$>$... 2) $<$the filter works$>$...
+\sw is a web-based service that enables the discovery of strong gravitational
+lenses in wide-field imaging surveys by large numbers of people. Carefully
+produced color composite images are displayed to volunteers via a flexible
+interface, which records their estimates of the positions of candidate lensed
+features. Simulated lenses, and expert-classified non-lenses, are inserted
+into the stream at random intervals; this training set is used to give the
+volunteers feedback on their performance, and to estimate a
+dynamically-updated probability for any given image to contain a lens. Low
+probability systems are retired from the site daily, concentrating the sample
+towards a set of candidates; these are then re-classified by the volunteers in
+a second  refinement stage. Analyzing the classification of the training set,
+we predict that the first stage should yield a sample with C\% completeness
+and P\% purity, while leading to the rejection of R\% of the initial target
+sample. Having divided the 150 square degree CFHTLS imaging survey into 430000
+overlapping 70 by 70 arcminute tiles and displayed them on the site, we were
+joined by 33000 volunteers who contributed X million image classifications
+over the course of N months. The sample was reduced to 3500 stage 1
+candidates; these were then refined to yield a sample of candidates rankable
+by their stage 2 probability. We expect this sample to be X\% complete and Y\%
+pure at a threshold of 95\% classification probability. We estimate the mean
+information contributed per person to be X bits, over a session lasting, on
+average, N classifications per volunteer -- although the distributions of
+these quantities are highly skewed. We comment on the scalability of the \sw
+system, and its potential to operate beyond its design as a supervised
+classification system.
 
@@
   gravitational lensing   --
-  methods: statistical    
+  methods: statistical    --
+  methods: citizen science
 \end{keywords}
@@
 
-In this paper, we describe the \sw website, an online system that
-enables crowd-sourced detection of gravitational lenses. 
-Other papers in this series will present new gravitational lenses
-discovered in our first imaging survey dataset, and investigate the
-differences between lens detections made in \sw and those made with
-automated techniques. Here, we try to answer the following questons:
+In this paper, we describe the \sw website, an online system that enables
+crowd-sourced detection of gravitational lenses.  In a companion paper we will
+present the new gravitational lenses discovered in our first imaging survey
+dataset, and begin to investigate the differences between lens detections made
+in \sw and those made with automated techniques. Here though, we try to answer
+the following questions:
+
 \begin{itemize}
@@
 
-\item How accurately can gravitational lenses be located on the sky
-during the identification process?
+\item How quickly can lenses be detected, and non-lenses be rejected?
+How many classifications, and so how many volunteers are needed per target?
 
-\item How quickly can lenses be detected, and non-lenses be rejected?
-How many volunteers are needed per target, and how quickly can they
-mobilise?
+\item What can we learn about the scalability of the crowd-sourcing approach?
 
@@
 In \Sref{sec:design} we introduce the \sw system, describing and
-explaining its various features. We then briefly
+explaining its various features. We then briefly...
 
@@
 objects: need to be able to reject rapidly, and get through sample.
-Confusion with non-lenses: further filtering via scientific discussion
-and further classification (voting).
+Confusion with non-lenses: further filtering after advanced training, and 
+scientific discussion in Talk.
+
+Intro to Classification Interface. Basic description of site.
 
@@
 
-\subsection{Tutorial Material}
-\label{sec:design:tutorial}
+\subsection{Training}
+\label{sec:design:training}
 
-Learning what lenses do: Spotter's Guide and LensToy. Learning how
+Learning what lenses do: Spotter's Guide. Learning how
 lenses work (science page, FAQ).
 
-Inline tutorial. Merge into stream. Instant feedback, positive and
+More on what lenses do: inline tutorial and feedback. 
+Merge into stream. Instant feedback, positive and
 negative. Anecdotal support for this.
+
+Training requires lenses to be more common than is realistic. How to manage
+expectations, avoid high false positive rate? "Lenses are rare" messaging;
+simulation frequency marker.
 
@@
 
-\subsection{The Classification Interface}
-\label{sec:design:classification}
-
-Image presentation. Consistency in size and appearance.
+\subsection{Stage 1: Initial Classification}
+\label{sec:design:stage1}
 
 Interface fast due to pre-loading of images, and minimizing interaction.
-
-Spotting lenses: Markers to be placed. Two reasons: first, to give good
-feedback. Second, to improve quality of discussion later.
+Trade-off between speed and accuracy. Decreasing training rate.
 
@@
 
+Spotting lenses: Markers to be placed. Two reasons: first, to give good
+feedback. Second, to focus attention.
+
 Non-lenses marked? Favourite button instead, enabling serendipitous
@@
 
+Retirement of low probability systems. Concentrates sample, provides more
+``bacon'' (while slightly skewing "sim frequency"). Note that this feature
+means that everyone contributes to detection of lenses: luck is made for the
+few that happen to see the new lenses, by the masses that did the rejection.
+Group effort.
+
+Sims vs duds leads to inclusive search -- click on anything you think etc...
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 
-\subsection{Collaborative Filtering with ``Talk''}
-\label{sec:design:classification}
+\subsection{Stage 2: Refinement}
+\label{sec:design:stage2}
 
-Feeding in collections, following online analysis. 
-Taking subjects to Talk individually, too.
+Goal: assess candidates, reject false positives by comparing with training set
+of non-obvious non-lenses. Produce a sample rankable by probability.
 
-Mental modeling. Further inspection on Dashboard. Voting.
-
-Final sample generation.
+Reconfigured website: more detailed SG, more detailed feedback. Orange
+background to make it obvious stage 2 is different. Slower image presentation.
+Higher, constant training rate.
 
@@
 
-Training data and test data. Refer to Paper II for CFHTLS details.
+Definitions: training subjects and test subjects. Sims and duds.
 
-Presentation of images. Arcsinh stretch, calibration. Approximately
-optimized.
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{The CFHT Legacy Survey}
+\label{sec:data:CFHTLS}
+
+Describe survey. Refs.
+
+Why this one? Good IQ, deep, colorful, homogeneous. Precursor to Stage III and
+IV imaging surveys, DES, KIDS, LSST etc. Already searched by robots: enables
+comparison of techniques. Lenses not yet found by robots, detectable by
+humans?
+
+Blind search strategy.
+Preparation of data: divide survey into overlapping tiles.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Image Presentation}
+\label{sec:data:display}
+
+Presentation of images. Uniform scales, to build intuition and avoid rescales
+due to bright objects. Arcsinh stretch, to bring out low SB features. 
+Approximately optimized, how? Examples of images.
 
@@
 
-\section{Identification Analysis}
+\section{Classification Analysis}
 \label{sec:IDanalysis}
@@
 
-Where to describe probabilistic classifier stuff? Here or in an
-appendix? Not sure.
+Describe SWAP here. (Move from appendix.)
 
@@
 
-\section{Identification Results}
-\label{sec:IDresults}
+\section{Results}
+\label{sec:results}
 
@@
 
-\subsection{Learned Behavior}
-\label{sec:results:learning}
+\subsection{Crowd Properties}
+\label{sec:results:crowd}
+
+Enthusiasm: histogram of classifications, stage 1 vs stage 2. Information
+contributed. Correlation with number of classifications.
+
+PL and PD as measures of skill. not quite talent, due to possibility of
+learning - but agents assume talent. Performance of crowd re PD and PL.
+Correlations with N classifications.
 
@@
 \subsection{Sample completeness and purity}
-\label{sec:results:learning}
+\label{sec:results:sample}
 
-Vary the acceptance and rejection thresholds, look at completeness and
-purity as a function of this. How much time can be saved by retiring
-subjects into candidate list or rejection list?
+Rejection rate. Completeness and purity at P > retirement, P > 95\%, and 
+as function of probability P. Compare stage 1 and stage 2.
+
+Summarize performance at some fiducial threshold: eg P = 95\%.
 
@@
 
-\item Ability to detect lenses
+\item Crowd-sourced gravitational lens detection works, as shown on sims and duds:
 
-\item What we can say about the next steps
+\item Participation (crowd size, activity rate) enabled project completion
+
+\item Both stages (1 and 2) achieved the required rejection rates
+
+\item Integrated humanpower = X, cf hours taken by small team of experts
+
+\item Nightly processing is inefficient: more classifications were made than
+was necessary during peak participation. Need kafka...
+
+\item Completeness and purity were estimated as C\% and P\%, from sim and dud
+recovery/miss rates Which sims were missed? False negatives
+
+\item The lens-finding crowd shows some interesting properties, with
+consequences for future scalability
+
+\item The information comes predominantly from volunteers with agents with P =
+...
+
+\item The agents show a high mean information per classification, which
+increased/decreased with time; this does/doesn?t correlate with active crowd
+size, showing how the crowd changed over time...
 
@@
 
-Summarize, end.
+Sum up, end.
 

### 2014-05-07 doc/sw-system.tex
Finished SWAP section and appendix

@@
 \title[\sw I]
-{\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses}
+{\SW: Crowd-sourcing the Discovery of Gravitational Lenses}
 
@@
 lenses in wide-field imaging surveys by large numbers of people. Carefully
-produced color composite images are displayed to volunteers via a flexible
-interface, which records their estimates of the positions of candidate lensed
-features. Simulated lenses, and expert-classified non-lenses, are inserted
-into the stream at random intervals; this training set is used to give the
-volunteers feedback on their performance, and to estimate a
+produced color composite images are displayed to volunteers via a
+classification interface which records their estimates of the positions of
+candidate lensed features. Simulated lenses, and expert-classified non-lenses,
+are inserted into the image stream at random intervals; this training set is
+used to give the volunteers feedback on their performance, and to estimate a
 dynamically-updated probability for any given image to contain a lens. Low
-probability systems are retired from the site daily, concentrating the sample
-towards a set of candidates; these are then re-classified by the volunteers in
-a second  refinement stage. Analyzing the classification of the training set,
-we predict that the first stage should yield a sample with C\% completeness
-and P\% purity, while leading to the rejection of R\% of the initial target
-sample. Having divided the 150 square degree CFHTLS imaging survey into 430000
-overlapping 70 by 70 arcminute tiles and displayed them on the site, we were
-joined by 33000 volunteers who contributed X million image classifications
-over the course of N months. The sample was reduced to 3500 stage 1
-candidates; these were then refined to yield a sample of candidates rankable
-by their stage 2 probability. We expect this sample to be X\% complete and Y\%
-pure at a threshold of 95\% classification probability. We estimate the mean
-information contributed per person to be X bits, over a session lasting, on
-average, N classifications per volunteer -- although the distributions of
-these quantities are highly skewed. We comment on the scalability of the \sw
-system, and its potential to operate beyond its design as a supervised
-classification system.
+probability systems are retired from the site periodically, concentrating the
+sample towards a set of candidates; this ``stage 1'' set is then re-classified
+by the volunteers in a second  refinement stage. Analyzing the classification
+of the training set, we predict that the first stage alone should yield a
+sample that is C\% complete, while leading to the rejection of R\% of the
+initial target sample. Having divided the 150 square degree CFHTLS imaging
+survey into 430000 overlapping 70 by 70 arcminute tiles and displayed them on
+the site, we were joined by 33000 volunteers who contributed X million image
+classifications over the course of N months. The sample was reduced to 3500
+stage 1 candidates; these were then refined to yield a sample of 1400
+candidates rankable by their stage 2 probability. We expect this sample to be
+X\% complete and Y\% pure at a threshold of 95\% classification probability.
+We find that, on average, and given the assumptions we make in our analysis,
+we need 9 classifications per image during the first stage, X in the second.
+We estimate the mean information contributed per person to be X bits, over a
+session lasting, on average, N classifications per volunteer, and present the
+highly skewed distributions of these quantities. We comment on the scalability
+of the \sw system to the wide field survey era, and its potential to operate
+beyond its design as a supervised classification system.
 
@@
 \section{Classification Analysis}
-\label{sec:IDanalysis}
+\label{sec:swap}
 
-In this section we outline our methodology for interpreting the
-interactions of the volunteers with the identification interface.  Each
-classification made is logged in a database, storing subject IDs,
-(anonymous) volunteer IDs, a timestamp and the classification results. 
-The {\it kind} of subject -- whether it is a training subject (a 
-simulated lens or a known non-lens) or a test subject (an unseen image
-drawn from the survey) -- is also recorded. For all subjects, the
-positions of all Markers are recorded, in pixel coordinates. For
-training subjects, we also store the ``classification'' of the subject
-as a lens, or a non-lens, and also the type of object present in the
-image. These types are summarized in \Tref{tab:objecttypes}. 
-This classification is used to provide instant feedback, but is also the
-basic measurement used in a probabilistic classification of every
-subject based on all image views to date.
+In this section we outline our methodology for interpreting the interactions
+of the volunteers with the identification interface.  Each classification made
+is logged in a database, storing subject IDs, (anonymous) volunteer IDs, a
+timestamp and the classification results.  The {\it kind} of subject --
+whether it is a training subject (a  simulated lens or a known non-lens) or a
+test subject (an unseen image drawn from the survey) -- is also recorded. For
+all subjects, the positions of all Markers are recorded, in pixel coordinates.
+For training subjects, we also store the ``classification'' of the subject as
+a lens, or a non-lens, and also the type of object present in the image. These
+types are summarized in \Tref{tab:objecttypes}.  This classification is used
+to provide instant feedback, but is also the basic measurement used in a
+probabilistic classification of every subject based on all image views to
+date.
 
-We perform a ``Pseudo-online'' analysis of the classifications, 
-updating a probabilistic model of every (anonymous) volunteer's
-data, and also updating the lens probability of each subject 
-(in both the training and test sets), on a
-daily(??) basis. This allows us to track the speed with which the crowd
-learns about lenses, and also gives us a dynamic estimate of the
-posterior probability for  any given  subject being a lens, given all
-classifications of it. Assigning thresholds in this lens probability
-allows us to make good decisions about whether or not to accept a
-subject into the collection of candidates visible in \Talk, and also
-whether or not to  carry on classifying a subject at all.
+We perform an online analysis of the classifications,  updating a
+probabilistic model of every (anonymous) volunteer's data, and also updating
+the lens probability of each subject  (in both the training and test sets), on
+a daily basis. This gives us a dynamic estimate of the posterior probability
+for  any given  subject being a lens, given all classifications of it to date.
+Assigning thresholds in this lens probability then allows us to make good
+decisions about whether or not to retire a subject from the system, in order to
+focus attention on new images.
 
-In this paper we focus on the training data,  investigating  how the 
-crowd's ability to identify gravitational lenses during the course of
-the project, and the completeness and purity of the lens candidate
-sample generated.
+The details of how the lens probabilities are calculated are given in
+\Aref{appendix:swap}. In summary:
+\begin{itemize}
 
-Describe SWAP here. (Move from appendix.)
+\item Each volunteer is assigned a simple software agent, characterised by a
+confusion matrix. The two independent elements of this matrix are the
+probabilities, as estimated by the agent, that the volunteer is going to be 1)
+correct when they report that an image contains a lens when it really does
+contain a lens, $\pr(\saidLENS|\LENS,T)$, and 2) correct when they report that
+an image does not contain a lens when it really doesn't contain a lens,
+$\pr(\saidNOT|\LENS,T)$.
+
+\item Each agent updates its confusion matrix elements based on the number of
+times its volunteer has been right in each way while classifying subjects from
+the training set, accounting for noise early on due to small number
+statistics: $T$ is the set of all training images seen to date.
+
+\item Each agent uses its confusion matrices to update, via Bayes' theorem,
+the probability of an image from the test set containing a lens,
+$\pr(\LENS|C,T)$, when that image is classified by its volunteer. ($C$ is the
+set of all classifications made of this subject.)
+
+\end{itemize}
+
+In the next section we present results in terms of all three of these
+probabilities, as we investigate the performance of the \SW system.
 
@@
 
-\item Crowd-sourced gravitational lens detection works, as shown on sims and duds:
+\item Crowd-sourced gravitational lens detection works, as shown on sims and
+duds:
 
@@
 \item Completeness and purity were estimated as C\% and P\%, from sim and dud
-recovery/miss rates Which sims were missed? False negatives
+recovery/miss rates. Which sims were missed? False negatives
 
@@
 
-\section{Probabilistic Classification Data Model}
-\label{appendix:probmodel}
+\section{Probabilistic Classification Analysis}
+\label{appendix:swap}
 
@@
 as one which has a high posterior probability of being a lens, given the data:
-$\pr(\LENS|\data)$. Our problem is to approximate this probability. The data
+$\pr(\LENS|\data)$. Our problem is to approximate this probability. The data~$\data$
 in our case are the pixel values of a colour image. However, we can greatly
@@
 contain a $\saidLENS$.  We simplify the problem by only using the Marker
-positions to assess whether t
-he volunteer  correctly assigned the
+positions to assess whether the volunteer  correctly assigned the
 classification $\saidLENS$ or $\saidNOT$ after viewing (blindly) a member of
@@
 How should we model these compressed data? The circumstances of each
-classification are quite complex: the volunteers learn more about the problem
-as they go, but also inevitably make occasional mistakes (perhaps because a
-lens is difficult to see, or they became distracted by the television). To
-cope with this uncertainty, we assign a software agent to partner each
-volunteer. The agent's task is to interpret their volunteer's classification
-data as best it can, using a model that makes a number of necessary
-approximations. These interpretations will then include uncertainty arising as
-a result of the volunteer's efforts and also the agent's approximations, but
-they will have two important redeeming features. First, the interpretations
-will be quantitative (where before they were qualititative),  and thus will be
-useful in decision-making. Second, the agent will be able to predict, using
-its model, the probability of a test subject being a $\LENS$, given both its
-volunteer's classification, and its volunteer's experience. We now
-describe how each agent works.
+classification are quite complex, as are the human classifiers in general: the
+volunteers learn more about the problem as they go, but also inevitably make
+occasional mistakes (perhaps because a lens is difficult to see, or they
+became distracted during the task). To cope with this uncertainty, we assign a
+simple software {\it agent} to partner each volunteer. The agent's task is to
+interpret their volunteer's classification data as best it can, using a model
+that makes a number of necessary approximations. These interpretations will
+then include uncertainty arising as a result of the volunteer's efforts and
+also the agent's approximations, but they will have two important redeeming
+features. First, the interpretations will be quantitative (where before they
+were qualititative),  and thus will be useful in decision-making. Second, the
+agent will be able to predict, using its model, the probability of a test
+subject being a $\LENS$, given both its volunteer's classification, and its
+volunteer's experience. In this appendix we describe how these agents work.
+
+\subsection{Agents and their Confusion Matrices}
+\label{appendix:swap:probabilities}
 
@@
 
-As an example, suppose we have a volunteer who is always right about the true
+\subsection{Examples}
+\label{appendix:swap:examples}
+
+Suppose we have a volunteer who is always right about the true
 nature of a training subject. 
@@
 \end{align}
-{\it Obtuse} classifiers are as helpful as {\it perfect} ones!
+{\it Obtuse} classifiers turn out to be as helpful as {\it perfect} ones.
 
-Indeed, the information content of each classification can be estimated by an
-agent before the next classification is made, just from its confusion matrix.
+\subsection{Information Contribution}
+\label{appendix:swap:examples}
+
+The information likely to be contributed by each agent for a given subject
+can be estimated before the next classification of that subject is made, 
+just from its confusion matrix.
 The Shannon entropy generated by a classifier upon performing a
@@
 
+\subsection{Updating the Subject Probabilities}
+\label{appendix:swap:examples}
+
 Suppose the $k+1^{\rm th}$ volunteer now submits a classification, on the same
@@
 
+\subsection{Uncertainty in the Agent Confusion Matrices}
+\label{appendix:swap:uncertainty}
+
 The confusion matrix obtained from the application of Equation
-(\ref{eq:app:fraction}) has some inherent noise which reduces as the number
-of training subjects classified by the user increases. For simplicity, the
-discussion thus far assumed the case when the confusion matrix is known
-perfectly. Let us first discuss how to characterize the noise in the confusion
-matrix. ** This needs work **
+(\ref{eq:app:fraction}) has some inherent noise which reduces as the number of
+training subjects classified by the agent's volunteer increases. For
+simplicity, the discussion thus far assumed the case when the confusion matrix
+is known perfectly; in practice, we allow for uncertainty in the agent
+confusion matrices by averaging over a small number of samples drawn from
+Binomial distributions characterised by the matrix elements
+$\pr(C_k|\LENS,T_k)$ and  $\pr(C_k|\NOT,T_k)$. The associated standard
+deviation in the estimated subject probability provides an error bar for this
+quantity.
 
-For ease of notation, we will denote $\pr(C_k|\LENS,T_k)\equiv p_L$ and
-$\pr(C_k|\NOT,T_k)\equiv p_N$. In reality, there is a probability distribution
-for both $p_L$ and $p_N$. Let $p_0$ be the prior probability of the subject
-being a lens. Then the posterior probability, $p_0'$ of the subject being a
-lens after the classification $C_k$ is
-\be
-  \label{eq:app:sec}
-p_0' = \frac{p_L p_0}{\left[ p_L p_0 + p_N (1- p_0) \right]},
-\ee
-The posterior probability distribution $p_0'$ can be obtained by marginalizing
-over the probability distributions of $p_L$, $p_N$ and the prior probability
-distribution $p_0$ such that,
-\be
-P(p_0') = \int p_0' P(p_L) P(p_N) P(p_0) dp_L dp_N dp_0\,.
-\ee
-This marginalization is not analytically tractable. Therefore, we have
-implemented the following Monte-Carlo solution for this problem.
+% For ease of notation, we will denote $\pr(C_k|\LENS,T_k)\equiv p_L$ and
+% $\pr(C_k|\NOT,T_k)\equiv p_N$. In reality, there is a probability distribution
+% for both $p_L$ and $p_N$. Let $p_0$ be the prior probability of the subject
+% being a lens. Then the posterior probability, $p_0'$ of the subject being a
+% lens after the classification $C_k$ is
+% \be
+%   \label{eq:app:sec}
+% p_0' = \frac{p_L p_0}{\left[ p_L p_0 + p_N (1- p_0) \right]},
+% \ee
+% The posterior probability distribution $p_0'$ can be obtained by marginalizing
+% over the probability distributions of $p_L$, $p_N$ and the prior probability
+% distribution $p_0$ such that,
+% \be
+% P(p_0') = \int p_0' P(p_L) P(p_N) P(p_0) dp_L dp_N dp_0\,.
+% \ee
+% This marginalization is not analytically tractable. Therefore, we have
+% implemented the following Monte-Carlo solution for this problem.
+%
 

### 2014-05-13 doc/sw-publication-policy-cfhtls.tex
Updated Policy and Author .tex files

--- 2013-12-19 doc/sw-publication-policy-cfhtls.tex
@@
 sum total of the volunteers who have logged in and contributed
-classifications to the project. (We would include those who did not
-log in as well, but we don't know who they are.) This means that the
-minimal requirement for \sw collaboration membership is classification with a Zooniverse ID,
-and some contribution on the site (\ie classifying, or discussing
+classifications to the project (we would include those who did not
+log in as well, but we don't know who they are!). This means that the
+minimal requirement for \sw collaboration membership is logging in with a Zooniverse ID
+and providing some contribution on the site (\ie classifying, or discussing
 Subjects in \Talk \footnote{\Talk (found at talk.spacewarps.org) is a forum for \sw collaborators to discuss individual sources and the \sw project in general.
 Bugs can also be reported.
-This is the direct portal for communication with the \sw community.}).
+This is the direct portal for communication with the \sw community.}).\\
 
@@
 
-\item{\bf Zooniverse:} \sw development team (led by
+\item{\bf Zooniverse:} \sw development team (originally led by
 A.\,Kapadia).
@@
 professional, that helped to design, build and test the \sw website
-and the initial CFHT-LS project. The Science Team includes the PIs.
+and the initial CFHT-LS project. The Science Team includes the \sw PIs.
 
@@
 \end{description}
-
-In the remaining sections we look at the various publications that might
-arise from the \sw project, and suggest reasonable guidelines for
-deciding on their authorship.
 
@@
 
-\section{The \SW Paper Series}
+\section{The \SW Papers}
+
+In the following sections we look at the various publications that might
+arise from the \sw project, and suggest reasonable guidelines for
+deciding on their authorship.
+
+\subsection{The \sw System Paper Series}
 \label{sec:series}
@@
 \item \sw I: The system paper, describing the project, the interface, the classification analysis methods (SWAP) and results 
-\item \sw II: The \sw  simulations and community performance (not selection function), means by which you can compute a selection function for any given analysis. 
-\item \sw III: The first new candidates from CFHT-LS \textit{including models, follow-up if feasible}
-\item \sw IV: The results from CFHT-LS search including the comparison and analysis of citizen scientist classification versus lens-finding algorithms (maybe split into smaller papers).
+\item \sw II: The \sw  first results including simulations and community performance (not selection function), means by which you can compute a selection function for any given analysis, list of candidates.
+\item \sw III: Detailed results on candidates from CFHT-LS \textit{including models, follow-up etc}
+\item \sw IV: Detailed comparison and analysis of citizen scientist classification versus lens-finding
+\item \sw X: New lenses(s) in \sw (authored by collaboration members)
 \end{itemize}
@@
 There maybe further series papers (TBC).\newline
+
+\subsection{\sw Related Papers}
+These are \sw related papers but do not necessarily fall into the \sw paper series
+\begin{itemize}
+\item Lens modelling in \sw (Spaghetti Lens)
+\item New lenses(s) in \sw (authored by persons not part of the \sw collaboration)
+\end{itemize}
 
@@
 
-\noindent The author categories are grouped according to collaboration membership (defined above).
-These groups of authors have either the status to ``opt-out'' or "on contribution" of \sw publications.
-``Opt-out'' means the listed people are authors by default and must explicitly state if they wish for their names to be removed from \sw publications.
-``On contribution'' means the people listed are invited to comment on and contribute to publications.
-The Principal Investigators, Zooniverse development team and \sw Science team all have opt-out status and the \sw Affiliates have on contribution status.
+\noindent The author categories are grouped according to collaboration membership (defined above). These authors have either the status to ``opt-out'' or "opt-in" on \sw publications.  \\
+``Opt-out'' means the listed people are authors by default on \sw series papers and must explicitly state if they wish for their names to be removed from \sw publications. \\
+``Opt-in'' means the people listed should be invited to comment on and contribute to publications however it is the decision of the lead author whether to add their names.
 
-The first author of any \sw paper will decide, as
-usual, on the author list of their own paper. This will include adding Affiliates who they think have made a substantial contribution to that investigation, as well as inviting
-scientists from outside the list of \sw authors, or from outside the
-collaboration.  The PIs will act as adjudicators if any disputes arise,
-but to be honest we are not expecting any.
+The Principal Investigators, Zooniverse development team and \sw Science team all have ``opt-out'' status and the \sw Affiliates have ``opt-in'' status.
 
-Lead authors of \sw papers should circulate drafts to the list of \sw authors (according to the policy above) and allow a minimum of two weeks to give time for comments and to opt-in.
-If  ``on contribution'' authors have not provided comments within this time frame they will not be included as authors on the paper.
+The first author of any \sw paper will decide, as usual, on the author list of their own paper.
+This will include adding Affiliates who they think have made a substantial contribution to that investigation, as well as inviting scientists from outside the list of \sw authors, or from outside the
+collaboration.  The \sw PIs will act as adjudicators if any disputes arise, but to be honest we are not expecting any.
+
+Lead authors of \sw papers should circulate drafts to the list of \sw authors (according to the policy above) and allow a minimum of two weeks to give time for comments.
+If  ``opt-in'' authors have not provided comments within this time frame they will *not* be included as authors on the paper.
 If ``opt-out'' authors have not responded to ask for their names to be removed they will be kept on the author list.
+
+For \sw related papers, the \sw PIs should be contacted for a suggested minimum contingent of collaboration authors to be added to the paper.
+These papers are treated with the same status as the general \sw Please also refer to the general \sw policy document
 
@@
 \item the collaboration should be acknowledged in the acknowledgement section with a link to the collaboration membership page (URL: to be added).
+\item \sw CFHT-LS is based on data processed by CFHT-LS and Terapix, so please add the following acknowledgement to your paper:\\
+\textit{``Based on observations obtained with MegaPrime/MegaCam, a joint project of CFHT and CEA/IRFU, at the Canada-France-Hawaii Telescope (CFHT) which is operated by the National Research Council (NRC) of Canada, the Institut National des Science de l'Univers of the Centre National de la Recherche Scientifique (CNRS) of France, and the University of Hawaii.
+This work is based in part on data products produced at Terapix available at the Canadian Astronomy Data Centre as part of the Canada-France-Hawaii Telescope Legacy Survey, a collaborative project of NRC and CNRS.''}\\
+from http://www.cfht.hawaii.edu/Science/CFHLS/cfhtlspublitext.html
+
 \end{itemize}
@@
 \appendix
-\section{Current Author List: author.tex}
+\section{Current Author List for \sw series papers: author.tex}
 \label{sec:appa}
-{\small \verbatiminput{./authors.tex}}
+{\small \verbatiminput{authors.tex}}
 

### 2014-05-13 doc/sw-publication-policy-gen.tex
Updated Policy and Author .tex files

@@
 redistributed by any \sw user. This is a \textbf{good thing}: images of the sky taken
-with publicly-funded telescopes belong to everyone. It is the responsibility
-of the SSTs to provide images in a way that is consistent
+with publicly-funded telescopes belong to everyone.
+
+However, some surveys come with their own proprietary access policy. It is the responsibility
+of the SSTs to provide images to \sw in a way that is consistent
 with their own data access rules. There are two things that SSTs can
@@
 
-There is a reasonable amount of work in preparing data and images for delivery to \sw.
-The \sw team will provide assistance to future teams in data preparation.
-We hope the benefits of using the \sw service will far outweigh the time needed to prepare data.
-
 \subsection{Future Project Proposals}
 Any future \sw projects are requested to liaise with the PIs regarding their project.
-We ask that potential project teams first approach the PIs (Marshall, Verma, More) with a short description of their project that includes the following information.
+We ask that potential project teams first approach the \sw PIs (Marshall, Verma, More collectively contacted via \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com}) with a short description of their project that includes the following information.
 
@@
 to read these papers before designing their own \sw project, and cite them as justification for some of their decisions.
-As the \sw paper series appears links to the papers will be given in this draft.
+As the \sw paper series get published, links to the papers will be given in this draft.
 Prior to publications, draft papers can also be shared on request by the \sw PIs (\href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com})
@@
 
-Implementing a new project based on different survey data will require support from the \sw Science Team, in three
-respects: 
+Implementing a new project based on different survey data will require support from the \sw Science Team, in three respects:
+
 \begin{enumerate}
@@
 \item In {\bf preparing data} for the site, and uploading it onto the
-Zooniverse servers. The \sw Science Team can advise on suitable Training
+Zooniverse servers.
+There is a reasonable amount of work in preparing data and images by the SSTs for delivery to \sw.
+The \sw team will provide assistance to SSTs in data preparation.
+The benefits of using the \sw service will far outweigh the time needed to prepare data.
+The \sw Science Team can advise on suitable Training
 Subjects and image display settings, and also on formatting the data
@@
 \item In {\bf reconfiguring the site itself} ready for the new data. The
-survey team will need to include new Spotter's Guide images and text,
+SST will need to include new Spotter's Guide images and text,
 modified tutorial content, and additional survey-specific site content;
@@
 \item In {\bf maintaining the site} so that it continues to function
-correctly. This will involve technical support from the Zooniverse team,
+correctly. This will involve technical support from the Zooniverse and \sw science teams,
 but will also require the continued engagement of the wider
-collaboration by the Science Team in \Talk. Since this social filter is
+collaboration by the SST in \Talk. Since this social filter is
 a key part of the sample refinement, the latter may involve a
@@
 We would expect the \sw author list to be a small number (less than ten), primarily the Principal Investigators and a few others working on the ingestion of the new data.
-All post-discovery follow-up papers would of course be exempt from this: the idea is that \sw is purely a gravitational lens discovery
-service, but not one that runs by magic.
+All post-discovery follow-up papers would of course be exempt from this: the idea is that \sw is purely a gravitational lens discovery service, but not one that runs by magic.
 

### 2014-05-13 doc/sw-system.tex

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %
-% Space Warps I: Experiment Design
+% Space Warps System Paper
 %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\title[\sw I]
+\title[\sw]
 {\SW: Crowd-sourcing the Discovery of Gravitational Lenses}
@@
 \date{to be submitted to MNRAS}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2013}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2014}
 
@@
 
-Scientific motivation. Applications of lenses: group-scale arcs,
-galaxy-galaxy lenses, lensed quasars.
+% Scientific motivation. Applications of lenses: group-scale arcs,
+% galaxy-galaxy lenses, lensed quasars.
 
-Problem of rarity. Imaging surveys. Problem of purity/false positives.
+Strong gravitational lensing -- the formation of multiple, magnified images of
+background objects due to the deflection of light by  massive foreground
+objects -- is a very powerful astrophysical tool, enabling a wide range of
+science projects. The image separations and distortions provide information
+about the mass distribution in the lens \citep[e.g.][]{Auger++2011,
+Sonnenfeld++2014}, including on sub-galactic scales
+\citep[e.g.][]{Dalal+Kochanek2004,Vegetti+Koopmans2009,Hezaveh++2012}. Any
+strong lens can provide magnification of a factor of 10 or more, providing a
+deeper, higher resolution view of the distant universe through these ``cosmic
+telescopes'' \citep[e.g.][]{Stark++2009,Newton++2009}. Lensed quasars enable
+cosmography via the time delays between the multiple images' lightcurves
+\citep[e.g.][]{Tewes++2011,Suyu++2011}, and study of the accretion disk itself
+through the microlensing effect \citep[e.g.][]{Morgan++2011}. All of these
+science projects would benefit from being able to draw from a larger sample of
+lenses.
 
-Review of progress to date. Methods in SL2S, SQLS. Contrast with SLACS.
+In the last decade the numbers of detections of these rare cosmic alignments
+has increased by an order of magnitude, thanks to wide field surveys such as
+CLASS \citep[e.g.]{Browne++2003}, SDSS \citep[e.g.][]
+{Bolton++2006,Auger++2010,Treu++2011,Oguri++2010}, CFHTLS
+\citep[e.g.][]{More++2012,Gavazzi++2014}, Herschel \citep[][]{Herschel} and
+SPT \citep[e.g.][]{Vieira++2012}, among others.  As the number of known lenses
+has increased, new types have been discovered, leading to entirely new
+investigations. Compound lenses \citep{Gavazzi++2007,Collett+Auger2014} and
+lensed supernovae \citep{Quimby++2014} are good examples of this.
 
-Scaling to wide field era. Automated methods: problems. Need for good
-training sets. Need for quality control: always present.
+% Problem of rarity. Imaging surveys. Problem of purity/false positives.
+% Review of progress to date. Methods in SL2S, SQLS. Contrast with SLACS.
 
-Novel solution: crowd-sourcing. Brief review of similar problems.
-PlanetHunters. \sw as an experiment.
+Because they are rare, strong lenses are expensive to find. The most efficient
+searches to date have made use of relatively clean signals such as the
+presence of emission or absorption features at two distinct redshifts in the
+same optical spectrum \citep[e.g.][]{Bolton++2004}, or the strong
+``magnification bias'' towards detecting strongly-lensed sources in the sub-mm
+waveband \citep[e.g.][]{Negrello++2010}. Such searches have to be efficient,
+because they require expensive high resolution imaging follow-up; consequently
+they have so far produced yields in the tens to hundreds. An alternative approach
+is to search images of sufficiently high resolution and color contrast, and
+confirm the systems as gravitational lenses by modeling the survey data
+themselves \citep[][]{Marshall++2009}. Several square degrees of HST images
+have been searched, yielding several tens of galaxy-scale lenses
+\citep[e.g.][]{Moustakas++2006,Faure++2009,Jackson++2010,Pawase++2012}.
+Similarly, searches of over a hundred square degrees of CFHT Legacy Survey
+ground-based imaging, also with sub-arcsecond image quality, have revealed a
+smaller number of wider image separation group-scale systems
+\citep[e.g.][]{Cabanac++2007,More++2010}. Detecting galaxy-scale lenses from
+the ground is hard, but feasible albeit lower efficiency and requiring HST or
+spectroscopic follow-up to confirm the candidates as lenses
+\citep[e.g.][]{Gavazzi++2014}.
+
+% Scaling to wide field era. Automated methods: problems. Need for good
+% training sets. Need for quality control: always present.
+
+How can we scale these lens searches up to imaging surveys covering a hundred
+times the sky area, such as the almost-all sky surveys planned with LSST and
+Euclid, while reducing our dependence on expensive follow-up confirmation
+observations? There are two approaches to detecting lenses in imaging surveys.
+The first one is robotic: automated analysis of object catalogs and/or the
+survey images. The candidate samples produced by these methods have, to date,
+not been of high purity  \citep[see
+e.g.][]{Marshall++2009,More++2010,Gavazzi++2014}, with visual inspection by
+teams of humans still required to narrow down the robotically-generated
+samples. In this approach, the image data may or may not be explicitly
+modelled by the robots as if it contained a gravitational lens, but the visual
+inspection can be thought of as a ``mental modeling'' step. Systems classified
+by an inspector to be good lens candidates are deemed as such because the
+features in the image can be explained by a model of what gravitational lenses
+do contained in the inspector's brain. The second approach simply cuts out the
+robot middleman: \citet{Faure++2009,Jackson++2010} and \citet{Pawase++2012}
+all performed entirely visual searches for lenses in HST imaging.
+
+Visual image inspection seems, at present, unavoidable at some level when
+seraching for gravitational lenses. The technique has some drawbacks, however.
+First is that humans are only humans, and they make mistakes. The solution to
+this is to operate in teams, providing multiple classifications of the same
+images in order to catch errors and correct them. Second, and relatedly, is
+that humans get tired. With a well-designed classification interface, a human
+might be able to inspect images at a rate of one astronomical object per
+second (provided the majority are indeed uninteresting). At $10^4$ massive
+galaxies, and 10 lenses, per square degree, visual lens searches in good
+quality imaging data are limited to a few square degrees per inspector per
+day. Scaling to thousands of square degrees therefore means either robotically
+reducing the number of targets for inspection, or increasing the number of
+inspectors, or both.
+
+For example, a $10^4$ square degree survey containing $10^8$
+photometrically-selected massive galaxies and $10^5$ lenses could only be
+searched by 10 inspectors at a mean rate of 1 galaxy per second and 10
+inspections per galaxy in about 14 years. Reducing the inspection time by a
+factor of 400 to two weeks would require a robot to reduce the target sample
+to 25 per square degree. However, at this point the required purity, 40\%,
+would very likely require the average classification time per object to be
+more like 10 seconds per object. Hiring 10 inspectors to assess complex images
+full time full time for five months may not be the most cost-effective or
+reliable strategy. Alternatively, a team of $10^6$ inspectors could, in
+principle, make the required $10^9$ image classifications, $10^3$ each, in a
+few weeks; robotically reducing the target list would lead to a proportional
+decrease in the required team size.
+
+Systematic detection of rare astronomical objects by such ``crowd-sourced''
+visual inspection has recently been achieved by the online citizen science
+project PlanetHunters \citep{PlanetHunters}. PlanetHunters was designed to
+enable the discovery of transiting exoplanets in data taken by the Kepler
+satellite; a community of N inspectors found, after each undergoing a small
+amount of training, N new exoplanet candidates by visual inspection of the
+Kepler lightcurves that were presented in a custom web-based classification
+interface. The older Galaxy Zoo morphological classification project
+\citep{GalaxyZoo} has also enabled the discovery of rare objects, via its
+flexible inspection interface and discussion forum. Indeed, several of us
+(AV,EB,CC,TJ,CM,LW) were active in an informal Galaxy Zoo gravitational lens
+search, an experience which led to the present hypothesis that a systematic
+online visual lens search could be successful.
 
 In this paper, we describe the \sw website, an online system that enables 
-crowd-sourced detection of gravitational lenses.  In a companion paper we will
-present the new gravitational lenses discovered in our first imaging survey
-dataset, and begin to investigate the differences between lens detections made
+crowd-sourced gravitational lens detection.  In a companion paper we will
+present the new gravitational lenses discovered in our first experimental lens
+search, and begin to investigate the differences between lens detections made
 in \sw and those made with automated techniques. Here though, we try to answer

### 2014-05-14 doc/sw-publication-policy-cfhtls.tex
Mostly spelling and grammar, some comments for AV

@@
 
-We are planning a short series of journal papers describing the \sw service, its
-first dataset (CFHT-LS), and results from its investigation by the
-collaboration. These results will likely include a sample of new lenses,
-and some comparison studies between the visual and automated
-identification of lens systems in this survey. This series will be known
-as ``the \sw papers,'' and each one will have a title that starts with ``\sw.''
+We are planning a short series of journal papers describing the \sw service,
+its first dataset (CFHT-LS), and results from its investigation by the
+collaboration. These results will likely include a sample of new lenses, and
+some comparison studies between the visual and automated identification of
+lens systems in this survey. This series will be known as ``the \sw papers,''
+and each one will have a title that starts with ``\sw.''
 
-The initial papers we are planning to write include (in no particular order, and the actual paper series may be split or change in content and order):
+The initial papers we are planning to write include (in no particular order,
+and the actual paper series may be split or change in content and order):
 
 \begin{itemize}
-\item \sw I: The system paper, describing the project, the interface, the classification analysis methods (SWAP) and results 
-\item \sw II: The \sw  first results including simulations and community performance (not selection function), means by which you can compute a selection function for any given analysis, list of candidates.
-\item \sw III: Detailed results on candidates from CFHT-LS \textit{including models, follow-up etc}
-\item \sw IV: Detailed comparison and analysis of citizen scientist classification versus lens-finding
-\item \sw X: New lenses(s) in \sw (authored by collaboration members)
+% Old versions of this list, which caused a conflict when I (PJM) merged in
+% Aprajita's May 2014 edits. Both look out of date to me! Suggested new 
+% version is beneath these.
+% 
+% <<<<<<< HEAD
+% \item \sw I: The system paper, describing the project, the interface, the classification analysis methods (SWAP) and results 
+% \item \sw II: The \sw  first results including simulations and community performance (not selection function), means by which you can compute a selection function for any given analysis, list of candidates.
+% \item \sw III: Detailed results on candidates from CFHT-LS \textit{including models, follow-up etc}
+% \item \sw IV: Detailed comparison and analysis of citizen scientist classification versus lens-finding
+% \item \sw X: New lenses(s) in \sw (authored by collaboration members)
+%
+% =======
+% \item \sw I: The system paper, describing the project, the interface, the
+% classification analysis methods (SWAP) and results 
+% \item \sw II: The \sw  simulations and community performance (not selection
+% function), means by which you can compute a selection function for any given
+% analysis. 
+% \item \sw III: The first new candidates from CFHT-LS \textit{including models,
+% follow-up if feasible}
+% \item \sw IV: The results from CFHT-LS search including the comparison and
+% analysis of citizen scientist classification versus lens-finding algorithms
+% (maybe split into smaller papers).
+% >>>>>>> 34d2fe73486cc68b301665b1b811cff7804137e8
+%
+\item \sw I: The system paper, describing the project, the interface, the
+classification analysis methods (SWAP) and results from classification of the training set. 
+\item \sw II: Results from the CFHTLS project, including new lens candidates, and analysis of \sw compared to previous semi-automatic lens searches in this survey.
+
 \end{itemize}
 
-There maybe further series papers (TBC).\newline
+There maybe further papers written in this series. \newline
 
 \subsection{\sw Related Papers}
-These are \sw related papers but do not necessarily fall into the \sw paper series
+These are \sw related papers but do not necessarily fall into the \sw paper series. Planned examples are:
 \begin{itemize}
-\item Lens modelling in \sw (Spaghetti Lens)
+\item Lens modelling in \sw with {\sc Spaghetti Lens})
 \item New lenses(s) in \sw (authored by persons not part of the \sw collaboration)
@@
 
-Please email the \sw PIs at spacewarpspi@googlegroups.com if you have any ideas for further \sw series papers (this includes any publications that include a new lens system that was found by \sw).
-The authorship policy is defined in the next section.
+% PJM: not sure if this section should be here, it was part of a conflict I 
+% got when I merged... Aprajita?
+Please email the \sw PIs at spacewarpspi@googlegroups.com if you have any
+ideas for further \sw series papers (this includes any publications that
+include a new lens system that was found by \sw). The authorship policy is
+defined in the next section.
 
@@
 
-The current list of \sw authors is given in the \texttt{authors.tex} file and is reprinted
-in the appendix to this document (see Appendix \ref{sec:appa}); this file shown is as it is currently configured, ready to be copied and pasted into the \sw system paper (\sw I).
+% PJM: significant conflict here: I think Aprajita's version is the lower one, so that's uncommented for now. Aprajita, can you delete everything that should not be there please? Thanks!
 
-\noindent The author categories are grouped according to collaboration membership (defined above). These authors have either the status to ``opt-out'' or "opt-in" on \sw publications.  \\
-``Opt-out'' means the listed people are authors by default on \sw series papers and must explicitly state if they wish for their names to be removed from \sw publications. \\
-``Opt-in'' means the people listed should be invited to comment on and contribute to publications however it is the decision of the lead author whether to add their names.
-
-The Principal Investigators, Zooniverse development team and \sw Science team all have ``opt-out'' status and the \sw Affiliates have ``opt-in'' status.
-
-The first author of any \sw paper will decide, as usual, on the author list of their own paper.
+% <<<<<<< HEAD
+% The current list of \sw authors is given in the \texttt{authors.tex} file and is reprinted
+% in the appendix to this document (see Appendix \ref{sec:appa}); this file shown is as it is currently configured, ready to be copied and pasted into the \sw system paper (\sw I). 
+% 
+% \noindent The author categories are grouped according to collaboration membership (defined above). These authors have either the status to ``opt-out'' or "opt-in" on \sw publications.  \\
+% ``Opt-out'' means the listed people are authors by default on \sw series papers and must explicitly state if they wish for their names to be removed from \sw publications. \\
+% ``Opt-in'' means the people listed should be invited to comment on and contribute to publications however it is the decision of the lead author whether to add their names.
+% 
+% The Principal Investigators, Zooniverse development team and \sw Science team all have ``opt-out'' status and the \sw Affiliates have ``opt-in'' status.
+% 
+% The first author of any \sw paper will decide, as usual, on the author list of their own paper.
 This will include adding Affiliates who they think have made a substantial contribution to that investigation, as well as inviting scientists from outside the list of \sw authors, or from outside the
-collaboration.  The \sw PIs will act as adjudicators if any disputes arise, but to be honest we are not expecting any.
-
-Lead authors of \sw papers should circulate drafts to the list of \sw authors (according to the policy above) and allow a minimum of two weeks to give time for comments.
+% collaboration.  The \sw PIs will act as adjudicators if any disputes arise, but to be honest we are not expecting any.
+% 
+% Lead authors of \sw papers should circulate drafts to the list of \sw authors (according to the policy above) and allow a minimum of two weeks to give time for comments.
 If  ``opt-in'' authors have not provided comments within this time frame they will *not* be included as authors on the paper.
 If ``opt-out'' authors have not responded to ask for their names to be removed they will be kept on the author list.
+% 
+% =======
+The current list of \sw authors is given in the \texttt{authors.tex} file and
+is reprinted in the appendix to this document (see Appendix \ref{sec:appa});
+this file shown is as it is currently configured, ready to be copied and
+pasted into the \sw system paper (\sw I).
+
+\noindent The author categories are grouped according to collaboration
+membership (defined above). These groups of authors have either  ``opt-out''
+or ``on contribution'' status regarding \sw publications.  ``Opt-out'' means
+the listed people are authors by default and must explicitly state if they
+wish for their names to be removed from \sw publications. ``On contribution''
+indicates people who will be invited to comment on and contribute to
+publications, ``opting in'' to those papers' author lists. The Principal
+Investigators, Zooniverse development team and \sw Science team all have
+opt-out status and the \sw Affiliates have on contribution status.
+
+The first author of any \sw paper will decide, as usual, on the author list of
+their own paper. This will include adding Affiliates who they think have made
+a substantial contribution to that investigation, as well as inviting
+scientists from outside the list of \sw authors, or from outside the
+collaboration.  The PIs will act as adjudicators if any disputes arise, but to
+be honest we are not expecting any.
+
+Lead authors of \sw papers should circulate drafts to the list of \sw authors
+(according to the policy above) and allow a minimum of two weeks to give time
+for comments and to opt-in. If  ``on contribution'' authors have not provided
+comments within this time frame they will not be included as authors on the
+paper. If ``opt-out'' authors have not responded to ask for their names to be
+removed they will be kept on the author list.
+% >>>>>>> 34d2fe73486cc68b301665b1b811cff7804137e8
 
@@
 \appendix
-\section{Current Author List for \sw series papers: author.tex}
+\section{Current Author List for \sw series papers:}
 \label{sec:appa}
-{\small \verbatiminput{authors.tex}}
+{\small \verbatiminput{authors_core.tex}}
 

### 2014-05-14 doc/sw-publication-policy-gen.tex
Mostly spelling and grammar, some comments for AV

@@
 identification and classification.
-\sw comprises a primary classification interface (www.spacewarps.org) that allows citizen scientists to inspect images and mark those that contain potential gravitational lenses.
-In addition, the citizens are shown simulated lenses (appropriate for the survey being conducted) as an interactive training tool that also allows us to establish the Citizens' likelihood of identifying potential lenses and blank fields using the \sw Analysis Pipeline (SWAP).
+\sw comprises a primary classification interface (http://spacewarps.org) that allows citizen scientists to inspect images and mark those that contain potential gravitational lenses.
+In addition, these volunteers are shown simulated lenses (appropriate for the survey being conducted) as an interactive training tool that also allows us to establish the citizens' likelihood of identifying potential lenses and blank fields using the \sw Analysis Pipeline (SWAP).
 
-A key part of the \sw project is the ability for all members of the \sw collaboration (see Section \ref{sec:members}) to communicate with each other and discuss interesting candidates through \Talk\footnote{\Talk (found at \texttt{talk.spacewarps.org}) is a forum for \sw collaborators to discuss individual sources and the \sw project in general.
+A key part of the \sw project is the ability for all members of the \sw collaboration (see Section \ref{sec:members}) to communicate with each other and discuss interesting candidates through \Talk\footnote{\Talk (found at \texttt{http://talk.spacewarps.org}) is a forum for \sw collaborators to discuss individual sources and the \sw project in general.
 Bugs can also be reported.
@@
 
-The \sw collaboration comprises the \sw science team, development team and all the volunteers who have 
+The \sw collaboration comprises the \sw science team, \sw development team, and all the volunteers who have 
 logged in\footnote{with a Zooniverse ID.
@@
 
-The \sw PIs will then arrange a hangout/telecon with the SSTs to discuss their project further.
+The \sw PIs will then arrange a telecon with the SSTs to discuss their project further.
 
-The original \sw papers by definition, provide a complete description of the system, and its results from the CFHTLS survey. The science team of
+The original \sw papers, by definition, provide a complete description of the system, and its results from the CFHTLS survey. The science team of
 any other survey (such as DES, RCS, KIDS, PS1, HSC \etc) should be able

### 2014-05-14 doc/sw-publication-policy-cfhtls.tex
Further edtis on CFHT-LS policy

--- 2014-05-13 doc/sw-publication-policy-cfhtls.tex
@@
 
-We are planning a short series of journal papers describing the \sw service, its
-first dataset (CFHT-LS), and results from its investigation by the
-collaboration. These results will likely include a sample of new lenses,
-and some comparison studies between the visual and automated
-identification of lens systems in this survey. This series will be known
-as ``the \sw papers,'' and each one will have a title that starts with ``\sw.''
+We are planning a short series of journal papers describing the \sw service,
+its first dataset (CFHT-LS), and results from its investigation by the
+collaboration. These results will likely include a sample of new lenses, and
+some comparison studies between the visual and automated identification of
+lens systems in this survey. This series will be known as ``the \sw papers,''
+and each one will have a title that starts with ``\sw.''
 
-The initial papers we are planning to write include (in no particular order, and the actual paper series may be split or change in content and order):
+The initial papers we are planning to write include (in no particular order,
+and the actual paper series may be split or change in content and order):
 
 \begin{itemize}
-\item \sw I: The system paper, describing the project, the interface, the classification analysis methods (SWAP) and results 
-\item \sw II: The \sw  first results including simulations and community performance (not selection function), means by which you can compute a selection function for any given analysis, list of candidates.
-\item \sw III: Detailed results on candidates from CFHT-LS \textit{including models, follow-up etc}
-\item \sw IV: Detailed comparison and analysis of citizen scientist classification versus lens-finding
-\item \sw X: New lenses(s) in \sw (authored by collaboration members)
+% Old versions of this list, which caused a conflict when I (PJM) merged in
+% Aprajita's May 2014 edits. Both look out of date to me! Suggested new 
+% version is beneath these.
+% 
+% <<<<<<< HEAD
+% \item \sw I: The system paper, describing the project, the interface, the classification analysis methods (SWAP) and results 
+% \item \sw II: The \sw  first results including simulations and community performance (not selection function), means by which you can compute a selection function for any given analysis, list of candidates.
+% \item \sw III: Detailed results on candidates from CFHT-LS \textit{including models, follow-up etc}
+% \item \sw IV: Detailed comparison and analysis of citizen scientist classification versus lens-finding
+% \item \sw X: New lenses(s) in \sw (authored by collaboration members)
+%
+% =======
+% \item \sw I: The system paper, describing the project, the interface, the
+% classification analysis methods (SWAP) and results 
+% \item \sw II: The \sw  simulations and community performance (not selection
+% function), means by which you can compute a selection function for any given
+% analysis. 
+% \item \sw III: The first new candidates from CFHT-LS \textit{including models,
+% follow-up if feasible}
+% \item \sw IV: The results from CFHT-LS search including the comparison and
+% analysis of citizen scientist classification versus lens-finding algorithms
+% (maybe split into smaller papers).
+% >>>>>>> 34d2fe73486cc68b301665b1b811cff7804137e8
+%
+\item \sw I: The system paper, describing the project, the interface & training scheme, the classification analysis methods (SWAP) and results from classification of the training set.
+(Marshall et al.)
+\item \sw II: The \sw CFHTLS project, including description of CFHT-LS specific information (e.g.
+data/subjects, generation of simulated images), results new lens candidates, and preliminary analysis of \sw compared to previous semi-automatic lens searches in this survey.
+(More et al.)
+\item \sw III: Detailed comparison and analysis of citizen scientist classification versus lens-finding. (More et al.)
+%AV to PJM: i thought Anu still wanted the sim-automated serach comparison to be considered in a separate paper
+\item \sw IV-X: Detailed results on candidates from CFHT-LS \textit{inclduing lens models, follow-up etc.} (IV: Verma et al. & authored by collaboration members)
 \end{itemize}
 
-There maybe further series papers (TBC).\newline
+There maybe further papers written in this series. \newline
 
 \subsection{\sw Related Papers}
-These are \sw related papers but do not necessarily fall into the \sw paper series
+These are \sw related papers but do not necessarily fall into the \sw paper series. Planned examples are:
 \begin{itemize}
-\item Lens modelling in \sw (Spaghetti Lens)
+\item Lens modelling in \sw with {\sc Spaghetti Lens})
 \item New lenses(s) in \sw (authored by persons not part of the \sw collaboration)
@@
 
-Please email the \sw PIs at spacewarpspi@googlegroups.com if you have any ideas for further \sw series papers (this includes any publications that include a new lens system that was found by \sw).
-The authorship policy is defined in the next section.
+% PJM: not sure if this section should be here, it was part of a conflict I 
+% got when I merged... Aprajita?
+% AV: It was supposed to be here, is a procedure for collaborators to suggest papers
+
+Please email the \sw PIs at \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com} if you have any
+ideas for further \sw series or related papers.
 
@@
 
+The authorship policy for \sw series and related papers is defined here.
+
 \subsection{Journal Papers}
 \label{sec:series}
-A core team of collaborators will participate in writing journal papers, and many collaborators who have made a \textit{significant contribution} to \sw will be recognised on the author
-lists of journal papers presenting \sw results.
-However, not all collaboration members will participate in writing journal papers.
-\textit{Significant contributions} include those who have contributed to:
+
+A core team of collaborators will participate in writing journal papers, and
+many collaborators who have made a \textit{significant contribution} to \sw
+will be recognised on the author lists of journal papers presenting \sw
+results.  However, not all collaboration members will participate in writing
+journal papers.  \textit{Significant contributions} include those who have
+contributed to:
 \begin{itemize}
@@
 ``Opt-out'' means the listed people are authors by default on \sw series papers and must explicitly state if they wish for their names to be removed from \sw publications. \\
-``Opt-in'' means the people listed should be invited to comment on and contribute to publications however it is the decision of the lead author whether to add their names.
+``Opt-in'' means the people listed should be invited to comment on and contribute to publications however it is the decision of the lead author whether to add their names based on what they have contributed.
 
-The Principal Investigators, Zooniverse development team and \sw Science team all have ``opt-out'' status and the \sw Affiliates have ``opt-in'' status.
+For the CFHT-LS \sw system papers, the Principal Investigators, Zooniverse development team and \sw Science team all have ``opt-out'' status and the \sw Affiliates have ``opt-in'' status.
 
@@
 
-For \sw related papers, the \sw PIs should be contacted for a suggested minimum contingent of collaboration authors to be added to the paper.
-These papers are treated with the same status as the general \sw Please also refer to the general \sw policy document
+For \sw related papers, the \sw PIs should be contacted via \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com} for a suggested minimum contingent of collaboration authors to be added to the paper, consistent with the policy for general/future \sw projects (please see Guidelines and Policy for Surveys using \sw in this directory).
 
@@
 \appendix
-\section{Current Author List for \sw series papers: author.tex}
+\section{Current Author List for \sw series papers:}
 \label{sec:appa}

### 2014-05-14 doc/sw-publication-policy-cfhtls.tex
Further edtis on CFHT-LS policy

@@
 %
-\item \sw I: The system paper, describing the project, the interface & training scheme, the classification analysis methods (SWAP) and results from classification of the training set.
+\item \sw I: The system paper, describing the project, the interface \& training scheme, the classification analysis methods (SWAP) and results from classification of the training set.
 (Marshall et al.)
@@
 %AV to PJM: i thought Anu still wanted the sim-automated serach comparison to be considered in a separate paper
-\item \sw IV-X: Detailed results on candidates from CFHT-LS \textit{inclduing lens models, follow-up etc.} (IV: Verma et al. & authored by collaboration members)
+\item \sw IV-X: Detailed results on candidates from CFHT-LS \textit{including lens models, follow-up etc.} (IV: Verma et al. \& authored by collaboration members)
 \end{itemize}

### 2014-05-14 doc/sw-system.tex
checked through conclusions before writing method section

@@
 
-We draw the following conclusions:
+Summary of system.
+
+Crowd-sourced gravitational lens detection works, in terms of the
+classification of the training set as described here, in the following
+specific ways:
 
 \begin{itemize}
-
-\item Crowd-sourced gravitational lens detection works, as shown on sims and
-duds:
 
@@
 
-\item Integrated humanpower = X, cf hours taken by small team of experts
+\item Integrated humanpower = X (stage 1) and y (stage 2), cf hours taken by
+small team of experts
 
@@
 
-\item Completeness and purity were estimated as C\% and P\%, from sim and dud
-recovery/miss rates. Which sims were missed? False negatives
+\item Retirement rate. False negatives: which sims were missed?
+
+\item The optimal true positive rate (completeness) and false positive rate in
+the training set were estimated to be TPR\% and FPR\% at Stage 1, assuming a
+detection threshold of xxx.
+
+\item In the ``refinement'' stage 2, X\% of the stage 1 candidates were
+rejected (with P less than threshold), and the remainder assigned lens
+``probabilities.'' Ranking
+subjects by their Stage 2 lens probability gives an ROC curve for the system
+with X properties. The optimal true positive rate (completeness) and false
+positive rate in the training set were estimated as TPR\% and FPR\%;
 

### 2014-05-14 doc/sw-system.tex
Halfway through intro refs

@@
 science projects. The image separations and distortions provide information
-about the mass distribution in the lens \citep[e.g.][]{Auger++2011,
-Sonnenfeld++2014}, including on sub-galactic scales
-\citep[e.g.][]{Dalal+Kochanek2004,Vegetti+Koopmans2009,Hezaveh++2012}. Any
+about the mass distribution in the lens \citep[e.g.][]{AugerEtal2010,
+SonnenfeldEtal2012,SonnenfeldEtal2013}, including on sub-galactic scales
+\citep[e.g.][]{Dalal+Kochanek2002,VegettiEtal2010,HezavehEtal2013}. Any
 strong lens can provide magnification of a factor of 10 or more, providing a
 deeper, higher resolution view of the distant universe through these ``cosmic
-telescopes'' \citep[e.g.][]{Stark++2009,Newton++2009}. Lensed quasars enable
+telescopes'' \citep[e.g.][]{StarkEtal2008,NewtonEtal2011}. Lensed quasars enable
 cosmography via the time delays between the multiple images' lightcurves
-\citep[e.g.][]{Tewes++2011,Suyu++2011}, and study of the accretion disk itself
-through the microlensing effect \citep[e.g.][]{Morgan++2011}. All of these
+\citep[e.g.][]{TewesEtal2013,SuyuEtal2013}, and study of the accretion disk itself
+through the microlensing effect \citep[e.g.][]{PoindexterEtal2008}. All of these
 science projects would benefit from being able to draw from a larger sample of
@@
 has increased by an order of magnitude, thanks to wide field surveys such as
-CLASS \citep[e.g.]{Browne++2003}, SDSS \citep[e.g.][]
-{Bolton++2006,Auger++2010,Treu++2011,Oguri++2010}, CFHTLS
-\citep[e.g.][]{More++2012,Gavazzi++2014}, Herschel \citep[][]{Herschel} and
-SPT \citep[e.g.][]{Vieira++2012}, among others.  As the number of known lenses
+CLASS \citep[e.g.]{BrowneEtal2003}, SDSS \citep[e.g.][]
+{BoltonEtal2006,AugerEtal2010b,TreuEtal2011,InadaEtal2012}, CFHTLS
+\citep[e.g.][]{MoreEtal2012,GavazziEtal2014}, Herschel \citep[][]{Herschel} and
+SPT \citep[e.g.][]{VieiraEtal2013}, among others.  As the number of known lenses
 has increased, new types have been discovered, leading to entirely new
-investigations. Compound lenses \citep{Gavazzi++2007,Collett+Auger2014} and
-lensed supernovae \citep{Quimby++2014} are good examples of this.
+investigations. Compound lenses \citep{GavazziEtal2008,Collett+Auger2012} and
+lensed supernovae \citep{QuimbyEtal2014} are good examples of this.
 
@@
 presence of emission or absorption features at two distinct redshifts in the
-same optical spectrum \citep[e.g.][]{Bolton++2004}, or the strong
+same optical spectrum \citep[e.g.][]{BoltonEtal2004}, or the strong
 ``magnification bias'' towards detecting strongly-lensed sources in the sub-mm
-waveband \citep[e.g.][]{Negrello++2010}. Such searches have to be efficient,
+waveband \citep[e.g.][]{NegrelloEtal2010}. Such searches have to be efficient,
 because they require expensive high resolution imaging follow-up; consequently
@@
 confirm the systems as gravitational lenses by modeling the survey data
-themselves \citep[][]{Marshall++2009}. Several square degrees of HST images
+themselves \citep[][]{MarshallEtal2009}. Several square degrees of HST images
 have been searched, yielding several tens of galaxy-scale lenses
-\citep[e.g.][]{Moustakas++2006,Faure++2009,Jackson++2010,Pawase++2012}.
+\citep[e.g.][]{MoustakasEtal2006,FaureEtal2009,JacksonEtal2010,PawaseEtal2012}.
 Similarly, searches of over a hundred square degrees of CFHT Legacy Survey
@@
 smaller number of wider image separation group-scale systems
-\citep[e.g.][]{Cabanac++2007,More++2010}. Detecting galaxy-scale lenses from
+\citep[e.g.][]{CabanacEtal2007,MoreEtal2010}. Detecting galaxy-scale lenses from
 the ground is hard, but feasible albeit lower efficiency and requiring HST or
 spectroscopic follow-up to confirm the candidates as lenses
-\citep[e.g.][]{Gavazzi++2014}.
+\citep[e.g.][]{GavazziEtal2014}.
 
@@
 not been of high purity  \citep[see
-e.g.][]{Marshall++2009,More++2010,Gavazzi++2014}, with visual inspection by
+e.g.][]{MarshallEtal2009,MoreEtal2010,GavazziEtal2014}, with visual inspection by
 teams of humans still required to narrow down the robotically-generated
@@
 do contained in the inspector's brain. The second approach simply cuts out the
-robot middleman: \citet{Faure++2009,Jackson++2010} and \citet{Pawase++2012}
+robot middleman: \citet{FaureEtal2009,JacksonEtal2010} and \citet{PawaseEtal2012}
 all performed entirely visual searches for lenses in HST imaging.

### 2014-05-14 doc/sw-system.tex
All citations now in intro

@@
 {BoltonEtal2006,AugerEtal2010b,TreuEtal2011,InadaEtal2012}, CFHTLS
-\citep[e.g.][]{MoreEtal2012,GavazziEtal2014}, Herschel \citep[][]{Herschel} and
-SPT \citep[e.g.][]{VieiraEtal2013}, among others.  As the number of known lenses
-has increased, new types have been discovered, leading to entirely new
-investigations. Compound lenses \citep{GavazziEtal2008,Collett+Auger2012} and
-lensed supernovae \citep{QuimbyEtal2014} are good examples of this.
+\citep[e.g.][]{MoreEtal2012,GavazziEtal2014}, Herschel
+\citep[][]{NegrelloEtal2014} and SPT \citep[e.g.][]{VieiraEtal2013}, among
+others.  As the number of known lenses has increased, new types have been
+discovered, leading to entirely new investigations. Compound lenses
+\citep{GavazziEtal2008,CollettEtal2012} and lensed supernovae
+\citep{QuimbyEtal2014} are good examples of this.
 
@@
 have been searched, yielding several tens of galaxy-scale lenses
-\citep[e.g.][]{MoustakasEtal2006,FaureEtal2009,JacksonEtal2010,PawaseEtal2012}.
+\citep[e.g.][]{MoustakasEtal2007,FaureEtal2008,Jackson2008,MoreEtal2012,
+PawaseEtal2014}.
 Similarly, searches of over a hundred square degrees of CFHT Legacy Survey
@@
 smaller number of wider image separation group-scale systems
-\citep[e.g.][]{CabanacEtal2007,MoreEtal2010}. Detecting galaxy-scale lenses from
+\citep[e.g.][]{CabanacEtal2007,MoreEtal2012}. Detecting galaxy-scale lenses from
 the ground is hard, but feasible albeit lower efficiency and requiring HST or
@@
 not been of high purity  \citep[see
-e.g.][]{MarshallEtal2009,MoreEtal2010,GavazziEtal2014}, with visual inspection by
+e.g.][]{MarshallEtal2009,MoreEtal2012,GavazziEtal2014}, with visual inspection by
 teams of humans still required to narrow down the robotically-generated
@@
 do contained in the inspector's brain. The second approach simply cuts out the
-robot middleman: \citet{FaureEtal2009,JacksonEtal2010} and \citet{PawaseEtal2012}
+robot middleman: \citet{FaureEtal2008,Jackson2008} and \citet{PawaseEtal2014}
 all performed entirely visual searches for lenses in HST imaging.
@@
 visual inspection has recently been achieved by the online citizen science
-project PlanetHunters \citep{PlanetHunters}. PlanetHunters was designed to
+project PlanetHunters \citep{SchwambEtal2012}. PlanetHunters was designed to
 enable the discovery of transiting exoplanets in data taken by the Kepler
@@
 interface. The older Galaxy Zoo morphological classification project
-\citep{GalaxyZoo} has also enabled the discovery of rare objects, via its
-flexible inspection interface and discussion forum. Indeed, several of us
+\citep{LintottEtal2008} has also enabled the discovery of rare objects, via its
+flexible inspection interface and discussion forum \citep{LintottEtal2009}. Indeed, several of us
 (AV,EB,CC,TJ,CM,LW) were active in an informal Galaxy Zoo gravitational lens

### 2014-05-14 doc/sw-system.tex
Added paper org paragraph to intro

@@
 
-In \Sref{sec:design} we introduce the \sw system, describing and
-explaining its various features. We then briefly...
+This paper is organised as follows. 
+In \Sref{sec:design} we introduce the \sw classification interface,  explain
+how we use training images, and describe our two stage candidate selection
+strategy. We then briefly introduce, in \Sref{sec:data} the particular dataset
+used in the first experimental tests of the \sw system, and how we prepared
+the images prior to displaying them in the web interface. In \Sref{sec:swap}
+we describe our methodology for interpreting the classifications made by the
+volunteers, and then present the results of system performance tests 
+made on the training images in \Sref{sec:results}.
+% In this section, we also investigate the properties of the crowd, to
+% understand where the information is coming from.
+We discuss the implications of our results for future lens searches in
+\Sref{sec:discuss} and draw conclusions in \Sref{sec:conclude}.
+
+% \section{Introduction}
+% \label{sec:intro}
+% \section{Experiment Design}
+% \label{sec:design}
+% \subsection{Training}
+% \label{sec:design:training}
+% \subsection{Stage 1: Initial Classification}
+% \label{sec:design:stage1}
+% \subsection{Stage 2: Refinement}
+% \label{sec:design:stage2}
+% \section{Data}
+% \label{sec:data}
+% \subsection{The CFHT Legacy Survey}
+% \label{sec:data:CFHTLS}
+% \subsection{Image Presentation}
+% \label{sec:data:display}
+% \section{Classification Analysis}
+% \label{sec:swap}
+% \section{Results}
+% \label{sec:results}
+% \subsection{Crowd Properties}
+% \label{sec:results:crowd}
+% \subsection{Sample completeness and purity}
+% \label{sec:results:sample}
+% \section{Discussion}
+% \label{sec:discuss}
+% \section{Conclusions}
+% \label{sec:conclude}
 

### 2014-05-14 doc/sw-system.tex
Description of CI, screenshot fig

@@
 enable the discovery of transiting exoplanets in data taken by the Kepler
-satellite; a community of N inspectors found, after each undergoing a small
-amount of training, N new exoplanet candidates by visual inspection of the
-Kepler lightcurves that were presented in a custom web-based classification
-interface. The older Galaxy Zoo morphological classification project
-\citep{LintottEtal2008} has also enabled the discovery of rare objects, via its
-flexible inspection interface and discussion forum \citep{LintottEtal2009}. Indeed, several of us
-(AV,EB,CC,TJ,CM,LW) were active in an informal Galaxy Zoo gravitational lens
-search, an experience which led to the present hypothesis that a systematic
-online visual lens search could be successful.
+satellite; a community of N inspectors from the general public found, after
+each undergoing a small amount of training, N new exoplanet candidates by
+visual inspection of the Kepler lightcurves that were presented in a custom
+web-based classification interface. The older Galaxy Zoo morphological
+classification project \citep{LintottEtal2008} has also enabled the discovery
+of rare objects, via its flexible inspection interface and discussion forum
+\citep{LintottEtal2009}. Indeed, several of us (AV,EB,CC,TJ,CM,LW) were active
+in an informal Galaxy Zoo gravitational lens search, an experience which led
+to the present hypothesis that a systematic online visual lens search could be
+successful.
 
 In this paper, we describe the \sw website, an online system that enables 
-crowd-sourced gravitational lens detection.  In a companion paper we will
-present the new gravitational lenses discovered in our first experimental lens
-search, and begin to investigate the differences between lens detections made
-in \sw and those made with automated techniques. Here though, we try to answer
-the following questions:
+crowd-sourced gravitational lens detection by inviting volunteers to classify
+astronomical survey images as containing lens candidates or not.  In a
+companion paper we will present the new gravitational lenses discovered in our
+first experimental lens search, and begin to investigate the differences
+between lens detections made in \sw and those made with automated techniques.
+Here though, we try to answer the following questions:
 
@@
 
-This paper is organised as follows. 
-In \Sref{sec:design} we introduce the \sw classification interface,  explain
-how we use training images, and describe our two stage candidate selection
-strategy. We then briefly introduce, in \Sref{sec:data} the particular dataset
-used in the first experimental tests of the \sw system, and how we prepared
-the images prior to displaying them in the web interface. In \Sref{sec:swap}
-we describe our methodology for interpreting the classifications made by the
-volunteers, and then present the results of system performance tests 
-made on the training images in \Sref{sec:results}.
-% In this section, we also investigate the properties of the crowd, to
-% understand where the information is coming from.
-We discuss the implications of our results for future lens searches in
-\Sref{sec:discuss} and draw conclusions in \Sref{sec:conclude}.
+This paper is organised as follows.  In \Sref{sec:design} we introduce the \sw
+classification interface and the volunteers who make up the \sw
+collaboration,  explain how we use training images, and describe our two stage
+candidate selection strategy. We then briefly introduce, in \Sref{sec:data}
+the particular dataset used in the first experimental tests of the \sw system,
+and how we prepared the images prior to displaying them in the web interface.
+In \Sref{sec:swap} we describe our methodology for interpreting the
+classifications made by the volunteers, and then present the results of system
+performance tests  made on the training images in \Sref{sec:results}. % In
+this section, we also investigate the properties of the crowd, to % understand
+where the information is coming from. We discuss the implications of our
+results for future lens searches in \Sref{sec:discuss} and draw conclusions in
+\Sref{sec:conclude}.
 
@@
 
-Unfamiliar objects: need to learn what lenses look like, fast. Rare
-objects: need to be able to reject rapidly, and get through sample.
-Confusion with non-lenses: further filtering after advanced training, and 
-scientific discussion in Talk.
+The basic steps of a visual search for gravitational lenses are: 1) prepare
+images, 2) display them to an inspector, 3) record the inspector's
+classification of each image (as, for example, containing a lens candidate or
+not) and 4) analyzing those classifications (and all others) in order to
+produce a final candidate list. We describe step 1 in \Sref{sec:data} and step
+4 in \Sref{sec:swap}. In this section we take a volunteer's eye view and
+begin by describing the \sw classification interface, the crowd of volunteers,
+and the interactions between the two.
 
-Intro to Classification Interface. Basic description of site.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centerline{
+\includegraphics[width=0.9\linewidth]{sw-system-figs/sw-screengrab-marker+feedback.png}}
+\caption{Screenshot of the \sw classification interface.}
+\label{fig:interface}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Classification Interface}
+\label{sec:design:interface}
+
+A screenshot of the \sw classification interface (CI) is shown in
+\Fref{fig:interface}. The CI is the centrepiece of the \sw website,
+\texttt{http://spacewarps.org}; the web application is written in
+coffeescript, css and html and follows the general design of others written by
+the Zooniverse team.\footnote{The \sw web application code is open source and
+can be accessed from \texttt{https://github.com/zooniverse/Lens-Zoo}}  The
+focus of the CI is a large display of the current pre-prepared PNG image of
+the ``subject'' being inspected.   When the image is clicked on by the
+volunteer, a marker symbol appears where the pointer was. Several markers can
+be placed.  The next image moves rapidly in from a queue formed at the right
+hand side of the screen when the ``Finished marking'' button is pressed. At
+the same time, the positions of the markers are written out to the
+classification database, in an entry that also stores the ID of the subject,
+the username (or IP address) of the volunteer, a timestamp and some other
+metadata.
+
+Gravitational lenses are rare: typically, most of the images will not contain
+a lens candidate, and these need to be quickly rejected by the inspector. The
+queue allows several images to be pre-loaded while the volunteer is
+classifying the current subject, and the rapid movement is designed to
+encourage volunteers to classify rapidly.
+
+For the more interesting subjects, the CI offers two features that  enable
+further investigation of the subjects. First is the ``Quick Dashboard,'' a
+more advanced image viewer. This allows the viewer to compare three different
+contrast and color balance settings, to help bring out subtle features, and to
+zoom in on interesting regions of the image to assess small features. Markers
+can be placed in the Quick Dashboard just the same as in the main CI image
+viewer. The second is a link to that subject's page in the project discussion
+forum, \texttt{http://talk.spacewarps.org}. Here, volunteers can discuss the
+features they have seen either before they submit their classification, or
+after, if they ``favorite'' the subject. There is no ``back'' button, however:
+each volunteer may only classify a given subject once.
 
@@
 \label{sec:design:training}
+
+Gravitational lenses are unfamiliar objects to volunteers who are new
+to the site. New volunteers need to learn what lenses look like as quickly as
+possible, so that they can contribute informative classifications. They also
+need to learn what lenses do not look like, in order to reduce the false
+positive detection rate.
 

### 2014-05-14 doc/sw-system.tex
Notes on Talk, QD

@@
 features they have seen either before they submit their classification, or
-after, if they ``favorite'' the subject. There is no ``back'' button, however:
-each volunteer may only classify a given subject once.
+after, if they ``favorite'' the subject. There is no ``back'' button: each
+volunteer may only classify a given subject once. However, the presence of an
+option to see what others think about any given subject before submitting your
+own classification means that the classifications may not be  strictly
+independent; the advantage of this system is that volunteers can learn from
+others what constitutes a good lens candidate. In practice, we might expect
+this to be a relatively unimportant educational resource, given the explicit
+training we provide for the volunteers, which we describe in the next section.
 

### 2014-05-15 doc/sw-system.tex
Tutorial, instant feedback

@@
 \caption{Screenshot of the \sw classification interface.}
-\label{fig:interface}
+\label{fig:screenshot}
 \end{figure*}
@@
 A screenshot of the \sw classification interface (CI) is shown in
-\Fref{fig:interface}. The CI is the centrepiece of the \sw website,
+\Fref{fig:screenshot}. The CI is the centrepiece of the \sw website,
 \texttt{http://spacewarps.org}; the web application is written in
@@
 For the more interesting subjects, the CI offers two features that  enable
-further investigation of the subjects. First is the ``Quick Dashboard,'' a
+further investigation of the subjects. First is the ``Quick Dashboard'' (QD) a
 more advanced image viewer. This allows the viewer to compare three different
@@
 need to learn what lenses do not look like, in order to reduce the false
-positive detection rate.
+positive detection rate. There are three primary mechanisms in the \sw system
+for teaching the volunteers what to look for. These are, in the order in which
+they are encountered, an inline tutorial, instant feedback,
+and a ``Spotter's Guide.''
+
+\subsubsection{Inline Tutorial}
+
+New volunteers are welcomed to the site with a very short tutorial, in which
+the task is introduced, a typical image containing a simulated lens is
+displayed, and the marking procedure walked through, using pop-up message
+boxes. Subsequent images gradually introduce the more advanced
+features of the classification interface (the QD and Talk buttons), also using
+pop-up messages. The tutorial was purposely kept as short as possible so as to
+provide the minimal barrier to entry.
+
+\subsubsection{Instant Feedback}
+
+The second image viewed after the initial tutorial image is already a survey
+image, in order to get the volunteers engaged in the real task as quickly as
+possible. Training continues beyond the first image tutorial through
+``training subjects'' inserted randomly into the stream.  These training
+subjects are either simulated lenses (known as ``sims''), or survey images
+that were expert-classified (by AV, AM and PM) and found not to contain any
+lens candidates (these images are known as ``duds''). The tutorial explains
+that the volunteers  will be shown such training images. They are also
+informed that they will receive instant feedback about their performance after
+classifying (blind) any of these training subjects. Indeed, after a volunteer
+finishes marking a training subject and hits ``Finished marking,'' a pop-up
+message is generated, containing either positive feedback for a successful
+classification (for example, ``Well done! You spotted a simulated lens,'' as
+in \Fref{fig:screenshot}) or negative feedback for an unsuccessful one (for
+example, ``There is no gravitational lens in this field!'')
+
+\question{PJM}{Does the feedback lead to volunteers leaving the site more 
+quickly, or less quickly? Does negative feedback have more impact than
+positive?}
+
+The initial frequency of the training images is set to be two in five;
+subjects are drawn randomly from the pool of training images with this
+frequency. The pool contains equal numbers of sims and duds, and the draw is
+made without replacement (for that volunteer). As the number of
+classifications made by a volunteer increases, this frequency is decreased, to
+$2/(5\times2^{(\textrm{int}(N_c/20)+1)/2})$ ($\approx 0.3$ for the second 20
+subjects, $0.2$ for the third 20 subjects, and so on).
+
+This training regime means that in the first 60 images viewed, each volunteer
+is shown (on average) 9 simulated gravitational lenses, and 9 empty fields. 
+This is a much higher rate than the natural one: to try and avoid this leading
+to over-optimism among the inspectors (and a resulting high false positive
+rate), we display the current ``Simulation Frequency'' on the classification
+interface (``1 in 5'' in \Fref{fig:screenshot}) and maintain the consistent
+theme in the feedback messages that lenses are rare.
+
+\subsubsection{Spotter's Guide}
 
@@
 lenses work (science page, FAQ).
-
-More on what lenses do: inline tutorial and feedback. 
-Merge into stream. Instant feedback, positive and
-negative. Anecdotal support for this.
-
-Training requires lenses to be more common than is realistic. How to manage
-expectations, avoid high false positive rate? "Lenses are rare" messaging;
-simulation frequency marker.
 

### 2014-05-15 doc/sw-system.tex
Described Spotters Guidee

@@
 
-Learning what lenses do: Spotter's Guide. Learning how
-lenses work (science page, FAQ).
+The instant feedback provides real-time educational responses to the
+volunteers as they start classifying; as well as this dynamic system, \sw
+provides a static reference work for volunteers to consult when in doubt about
+how to perform the task. This ``Spotter's Guide'' is a set of webpages showing
+example lenses, both real and simulated, and also some common false positives,
+drawn from the pool of survey images. The non-lenses were identified by three
+of us (AV, AM and PM) while inspecting a small set of survey images in order
+to define the ``dud'' training images. For easy reference, the lenses are
+divided by type (for example, ``lensed galaxies,'' ``lensed quasars'' and
+``cluster lenses''), as are the false positives (for example, ``Rings and
+Spirals,'' ``Mergers,'' ``Artifacts'' and so on). The example images are
+accompanied by explanatory text. The Spotter's Guide is reached via a button
+on the left hand side, or the hyperlinked thumbnail images of the ``Quick
+Reference'' provided on the right hand side, of the classification interface.
+
+Most of the text of the Spotter's Guide focuses on what lenses do or don't do;
+the website ``Science page'' contains a very brief introduction to how
+gravitational lenses work, which is fleshed out a little on the ``FAQ'' page. 
+This also contains answers to frequently asked questions about the interface
+and the task set.
 

### 2014-05-16 doc/sw-publication-policy-cfhtls.tex
Minor clean-up after merge from AV
Hangout with A&A to sort out author list
Updates to policies, author_core.tex, renew command for \comment

@@
 \item{\bf Principal Investigators:} These are the PIs of the \sw project (P.\,Marshall, 
-A.\,More and A.\,Verma)\footnote{The PIs may be collectively contacted via the email address spacewarpspi@googlegroups.com}
+A.\,More and A.\,Verma)\footnote{The PIs may be collectively contacted via the email address \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com}}
 
@@
 
-\item{\bf Community} All of the volunteers who have contributed
+\item{\bf Community:} All of the volunteers who have contributed
 classifications to the project\footnote{We can only communicate directly with those who have logged in with a Zooniverse ID via \Talk or group e-mail.}.
@@
 \item{\bf Affiliated:} This group includes professional scientists who have made some contribution to the \sw project, but smaller than the Science Team.
-Such contributions might include helping write the initial
-Citizen Science Alliance proposal, participating in discussions on
+Such contributions might include helping write the initial Citizen Science Alliance proposal, participating in discussions on
 \Talk, writing \sw blog posts, advising on the data analysis, or editing
@@
 \end{description}
-
-%First, however, we remind ourselves about data access via \sw.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\section{Survey Data Use}
-%\label{sec:data}
-
-%\sw is a public website. All images displayed there are by definition in the
-%public domain, and so must be expected to be downloaded, copied and
-%redistributed by any \sw user. This is a \textbf{good thing}: images of the sky taken
-%with publicly-funded telescopes belong to everyone. It is the responsibility
-%of the survey science teams to provide images in a way that is consistent
-%with their own data access rules.
-
-%While the CFHT-LS is a public survey, the WCS information has been removed from the provided images. This prevents the follow-up of any of the objects in the survey by anyone other than the \sw
-%team. In practice, the objects contained in the \sw images will be too faint
-%for anyone without access to a large telescope to observe, and may also be
-%absent from any public catalogs, so the opportunities for follow-up will be
-%quite limited. Removing the WCS information is an insurance policy against any
-%competing professional scientists looking to ``scoop'' the survey team,
-%despite the damage it would do to their reputations.\footnote{We cannot exclude the possibility that object co-ordinates are posted in \Talk.
-For example, co-ordinates of previously published lens candidates or recognisable fields from CFHT-LS have appeared in \Talk.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{itemize}
-% Old versions of this list, which caused a conflict when I (PJM) merged in
-% Aprajita's May 2014 edits. Both look out of date to me! Suggested new 
-% version is beneath these.
-% 
-% <<<<<<< HEAD
-% \item \sw I: The system paper, describing the project, the interface, the classification analysis methods (SWAP) and results 
-% \item \sw II: The \sw  first results including simulations and community performance (not selection function), means by which you can compute a selection function for any given analysis, list of candidates.
-% \item \sw III: Detailed results on candidates from CFHT-LS \textit{including models, follow-up etc}
-% \item \sw IV: Detailed comparison and analysis of citizen scientist classification versus lens-finding
-% \item \sw X: New lenses(s) in \sw (authored by collaboration members)
-%
-% =======
-% \item \sw I: The system paper, describing the project, the interface, the
-% classification analysis methods (SWAP) and results 
-% \item \sw II: The \sw  simulations and community performance (not selection
-% function), means by which you can compute a selection function for any given
-% analysis. 
-% \item \sw III: The first new candidates from CFHT-LS \textit{including models,
-% follow-up if feasible}
-% \item \sw IV: The results from CFHT-LS search including the comparison and
-% analysis of citizen scientist classification versus lens-finding algorithms
-% (maybe split into smaller papers).
-% >>>>>>> 34d2fe73486cc68b301665b1b811cff7804137e8
-%
+
 \item \sw I: The system paper, describing the project, the interface \& training scheme, the classification analysis methods (SWAP) and results from classification of the training set.
 (Marshall et al.)
-\item \sw II: The \sw CFHTLS project, including description of CFHT-LS specific information (e.g.
-data/subjects, generation of simulated images), results new lens candidates, and preliminary analysis of \sw compared to previous semi-automatic lens searches in this survey.
+\item \sw II: First results from the \sw CFHTLS project, including description of CFHT-LS specific information (e.g.
+data/subjects, generation of simulated images), new lens candidates, and preliminary analysis of \sw compared to previous semi-automatic lens searches in this survey.
 (More et al.)
-\item \sw III: Detailed comparison and analysis of citizen scientist classification versus lens-finding. (More et al.)
-%AV to PJM: i thought Anu still wanted the sim-automated serach comparison to be considered in a separate paper
-\item \sw IV-X: Detailed results on candidates from CFHT-LS \textit{including lens models, follow-up etc.} (IV: Verma et al. \& authored by collaboration members)
+\item \sw III: Detailed comparison and analysis of citizen scientist classification versus lens-finding algorithms. (More et al.)
+\item \sw IV: Detailed analysis of candidates from CFHT-LS \textit{including lens models, follow-up etc.} (Verma et al.)
+\item \sw X: Detailed results on lens systems from CFHT-LS (authored by \sw collaboration members)
 \end{itemize}
@@
 \begin{itemize}
-\item Lens modelling in \sw with {\sc Spaghetti Lens})
+\item Lens modelling in \sw with {\sc Spaghetti Lens}
 \item New lenses(s) in \sw (authored by persons not part of the \sw collaboration)
 \end{itemize}
-
-% PJM: not sure if this section should be here, it was part of a conflict I 
-% got when I merged... Aprajita?
-% AV: It was supposed to be here, is a procedure for collaborators to suggest papers
 
@@
 
-The current list of \sw authors is given in the \texttt{authors.tex} file and is reprinted
+The current list of \sw authors is given in the \texttt{authors\_core.tex} file and is reprinted
 in the appendix to this document (see Appendix \ref{sec:appa}); this file shown is as it is currently configured, ready to be copied and pasted into the \sw system paper (\sw I).
 
-\noindent The author categories are grouped according to collaboration membership (defined above). These authors have either the status to ``opt-out'' or "opt-in" on \sw publications.  \\
+\noindent The author categories are grouped according to collaboration membership (defined above). Authors have either the status to ``opt-out'' or "opt-in" on \sw publications.  \\
 ``Opt-out'' means the listed people are authors by default on \sw series papers and must explicitly state if they wish for their names to be removed from \sw publications. \\
@@
 
-For the CFHT-LS \sw system papers, the Principal Investigators, Zooniverse development team and \sw Science team all have ``opt-out'' status and the \sw Affiliates have ``opt-in'' status.
+For the CFHT-LS \sw system papers, the core team have ``opt-out'' status, the remainder  and the \sw Affiliates have ``opt-in'' status.
 
@@
 
-Lead authors of \sw papers should circulate drafts to the list of \sw authors (according to the policy above) and allow a minimum of two weeks to give time for comments.
+Lead authors of \sw papers should circulate drafts to the list of authors (and whoever they wish from the affiliates list) and allow a minimum of two weeks to give time for comments.
 If  ``opt-in'' authors have not provided comments within this time frame they will *not* be included as authors on the paper.
@@
 
-For \sw related papers, the \sw PIs should be contacted via \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com} for a suggested minimum contingent of collaboration authors to be added to the paper, consistent with the policy for general/future \sw projects (please see Guidelines and Policy for Surveys using \sw in this directory).
+For \sw related papers, the \sw PIs should be contacted via \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com} for a suggested minimum contingent of collaboration authors to be added to the paper, but the ``opt-out'' authors defined in \texttt{authors\_core.tex} should be included as a minimum.
 
@@
 Zooniverse \Letters are citable
-objects, and in some cases will appear listed on ADS.\footnote(To be confirmed.)
+objects, and in some cases will appear listed on ADS.\footnote{To be confirmed.}
 We strongly encourage community members to write Zooniverse \Letters about their findings.
@@
 \label{sec:appa}
-{\small \verbatiminput{authors.tex}}
+{\small \verbatiminput{authors_core.tex}}
 

### 2014-05-16 doc/sw-publication-policy-cfhtls.tex
Typos, Collett added to authors file

@@
 
-\noindent The author categories are grouped according to collaboration membership (defined above). Authors have either the status to ``opt-out'' or "opt-in" on \sw publications.  \\
+\noindent The author categories are grouped according to collaboration membership (defined above). Authors have either the status to ``opt-out'' or ``opt-in'' on \sw publications.  \\
 ``Opt-out'' means the listed people are authors by default on \sw series papers and must explicitly state if they wish for their names to be removed from \sw publications. \\
@@
 Lead authors of \sw papers should circulate drafts to the list of authors (and whoever they wish from the affiliates list) and allow a minimum of two weeks to give time for comments.
-If  ``opt-in'' authors have not provided comments within this time frame they will *not* be included as authors on the paper.
+If  ``opt-in'' authors have not provided comments within this time frame they will not be included as authors on the paper.
 If ``opt-out'' authors have not responded to ask for their names to be removed they will be kept on the author list.

### 2014-05-22 doc/sw-system.tex
Planned crowd results section with Baumer

@@
 
-Enthusiasm: histogram of classifications, stage 1 vs stage 2. Information
-contributed. Correlation with number of classifications.
+% Enthusiasm: histogram of classifications, stage 1 vs stage 2. Information
+% contributed. Correlation with number of classifications. 
+% 
+% PL and PD as measures of skill. not quite talent, due to possibility of
+% learning - but agents assume talent. Performance of crowd re PD and PL.
+% Correlations with N classifications.
 
-PL and PD as measures of skill. not quite talent, due to possibility of
-learning - but agents assume talent. Performance of crowd re PD and PL.
-Correlations with N classifications.
+What are the properties of the crowd? Corner plots: skill, effort, combine to
+give contribution. Actual information generated. Making your own luck. How do these depend on
+experience (no. of training images). Describe plot features, in stage 1.
+Contrast with stage 2. \Fref{fig:crowd:cornerplot}
+
+Who's doing all the work?
+Cumulative plot of ``contributions'' (applied skill).
+\Fref{fig:crowd:cumulplot}
+
+Information, contribution totals and their interpretation. Inefficiency
+measures? Super-users. 
+\Tref{tab:crowd:contributions} shows contributions at stage 2 and stage 1
+
+Can we predict skill? Early skill vs final skill - some correlation,
+especially in high skill users, but very broad distribution though: not
+possible to predict.
+\Fref{fig:crowd:skillprediction}
+
+Stage 1 skill vs Stage 2 skill. 
+Who continued to do Stage 2? Numbers. 
+\Fref{fig:crowd:stage1vstage2}
 

### 2014-05-22 analysis/SWAP.py
working stage1 plot code

@@ -316,8 +316,8 @@ def SWAP(argv):
 
     # All good things come to an end:
     if count == 0:
-        print "SWAP: something went wrong - 0 classifications found."
-        return
+        print "SWAP: something went wrong? 0 classifications found..."
+        # return
     elif count < count_max: # ie we didn't make it to 10,000 this time!
         more_to_do = False
     else:
@@ -349,7 +349,7 @@ def SWAP(argv):
     # taken care of in io.py. Note that we update the parameters as
     # we go - this will be useful later when we write update.config.
 
-    if tonights.parameters['repickle']:
+    if tonights.parameters['repickle'] and count > 0:
 
         new_bureaufile = swap.get_new_filename(tonights.parameters,'bureau')
         print "SWAP: saving agents to "+new_bureaufile

### 2014-05-22 analysis/swap/agent.py

@@ -94,7 +94,7 @@ class Agent(object):
         # back-compatibility:
         self.contribution = self.skill
         self.traininghistory = {'ID':'tutorial','Skill':np.array([self.skill]),'PL':np.array([self.PL]),'PD':np.array([self.PD])}
-        self.testhistory = {'ID':[],'I':np.array([])}
+        self.testhistory = {'ID':[],'I':np.array([]),'Skill':np.array([])}
         return None
 
 # ----------------------------------------------------------------------

### 2014-05-22 analysis/swap/subject.py

@@ -215,6 +215,7 @@ class Subject(object):
                      # by.testhistory['I'] = np.append(by.testhistory['I'], by.contribution)
                      by.testhistory['I'] = np.append(by.testhistory['I'], swap.informationGain(
                          self.mean_probability, by.PL, by.PD, as_being))
+                     by.testhistory['Skill'] = np.append(by.testhistory['Skill'], swap.expectedInformationGain(0.5,by.PL,by.PD))
 
 
             else:

### 2014-05-22 analysis/swap_analyze_users.py

@@ -7,14 +7,18 @@
 
 from skimage import io
 from subprocess import call
-from colors import blues_r
+#from colors import blues_r
 import numpy as np
 from matplotlib import pyplot as plt
 import swap
 
-cornerplotter_path = '/Users/cpd/SWAP/pappy/CornerPlotter.py'
-bureau_path = '/Users/cpd/SWAP/SpaceWarps/analysis/CFHTLS_bureau.pickle'
-output_directory = '/Users/cpd/SWAP/swap_analysis/'
+#cornerplotter_path = '/Users/cpd/SWAP/pappy/CornerPlotter.py'
+#bureau_path = '/Users/cpd/SWAP/SpaceWarps/analysis/CFHTLS_bureau.pickle'
+#output_directory = '/Users/cpd/SWAP/swap_analysis/'
+
+cornerplotter_path = '/Users/mbaumer/SWAP/pappy/CornerPlotter.py'
+bureau_path = '/Users/mbaumer/SpaceWarps/analysis/CFHTLS_bureau.pickle'
+output_directory = '/Users/mbaumer/SWAP/swap_analysis'
 
 bureau = swap.read_pickle(bureau_path, 'bureau')
 len(bureau.list())

### 2014-06-01 doc/sw-system.tex
Crowd analysis

@@
 \begin{figure*}
-\centerline{
-\includegraphics[width=0.9\linewidth]{sw-system-figs/sw-screengrab-marker+feedback.png}}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/sw-screengrab-marker+feedback.png}
 \caption{Screenshot of the \sw classification interface.}
@@
 
-Understanding crowd, so we can help them learn faster. Understanding
-images given the crowd, so we can find lenses.
+In this section we present our findings about the performance of the  \sw
+system, in terms of the information  contributed by the crowd in
+\Sref{sec:results:crowd}, and the overall classifications of the training set
+that they made.
 
@@
 
-What are the properties of the crowd? Corner plots: skill, effort, combine to
-give contribution. Actual information generated. Making your own luck. How do these depend on
-experience (no. of training images). Describe plot features, in stage 1.
-Contrast with stage 2. \Fref{fig:crowd:cornerplot}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/all_skill_contribution_experience_education.png}
+\caption{Key properties and contributions of the \sw crowd. Plotted are the
+1-D and 2-D marginalized distributions for the logarithms of the 
+properties of the agents described in the text. The stage 1 agents are shown
+in blue, the stage 2 agents in orange.}
+\label{fig:crowd:cornerplot}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Who's doing all the work?
-Cumulative plot of ``contributions'' (applied skill).
-\Fref{fig:crowd:cumulplot}
+We define the following properties of the crowd, as characterised by their
+agents, and plot the distributions of their logarithms in
+\Fref{fig:crowd:cornerplot}. 
+%
+\begin{description}
+%
+\item{\noindent\bf ``Effort:''} The number of test images, $\effort$, classified by a
+volunteer. In stage 1, the mean effort per agent was 259; in the shorter stage
+2 it was 81.
+%
+\item{\noindent\bf ``Experience:''} The number of training images, $\experience$,
+classified by a volunteer. In stage 1, the mean experience per agent was 29;
+in stage 2 (where the training image fequency was set higher) it was 34.
+%
+\item{\noindent\bf ``Skill:''} The expectation value of the information gain, $\skill$
+should  the next subject classified have lens probability 0.5
+\Aref{appendix:swap},  in bits. Random classifiers have $\skill = 0.0$,
+perfect classifiers have $\skill = 1.0$. All agents start with $\skill = 0.0$;
+this increases as training subjects are classified, and the agent's estimates
+of its confusion matrix elements improve. In stage 1, the mean skill per agent
+was 0.04 bits; in  stage 2 it was 0.05.
+%
+\item{\noindent\bf ``Contribution:''} The integrated skill over a volunteer's test
+subject classification history, and represents the total  contribution to the
+project that volunteer (see the appendix for more discussion of this
+quantity). In stage 1, the mean contribution per agent was 34.3 bits; in 
+stage 2 it was 33.5.
+%
+\item{\noindent\bf ``Information:''} The total information $\information$ generated by
+the  agent during the volunteer's classification activity. This quantity
+depends on the value of each subject's lens probability when that subject was 
+presented to the volunteer (\Aref{appendix:swap}), and so there is an element
+of luck involved with this quantity: if you never see a high probability
+subject, it's hard to generate a large amount of information. You make your
+own luck by classifying more subjects.
+%
+\end{description}
 
-Information, contribution totals and their interpretation. Inefficiency
-measures? Super-users. 
-\Tref{tab:crowd:contributions} shows contributions at stage 2 and stage 1
+The leftmost column of \Fref{fig:crowd:cornerplot} shows how the last four of
+these properties depends on the effort expended by the volunteers. We see that
+experience is strongly correlated with effort (as training images are
+presented throughout each stage, albeit at decreasing frequency), and that
+this is also true for skill. In the second row of \Fref{fig:crowd:cornerplot}
+we see that while skills of greater than 0.1 can be attained after just a few
+training images, most agents of such low experience have significantly lower
+skill. The volunteers in question only classify a few subjects before leaving.
+However, at high values of experience and effort, the skill is \emph{always
+high}. There seem to be very few agents logging large numbers of
+classifications at low skill (although there are one or two exceptions). Most
+high effort ``super-users'' have high skill. These two properties are
+reflected in both the contributions these volunteers make (third row) and the
+information they generate (fourth row).
+
+The distributions for the stage 2 agents (orange) are qualitatively similar to
+those for the stage 1 agents (blue). Differences are: 1) the maximum effort
+possible at stage 2 is smaller, because fewer subjects were available to be
+classifed, but 2) the mean effort expended at stage 2 was higher (perhaps
+because the subjects were higher probability, and more compelling); 3) the
+information generated per agent was higher at stage 2, because the subjects
+had higher probability.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_contrib_cumul.png}
+\caption{Narrow cumulutive distributions of the contributions made by the
+agents: for example, 90\% of the stage 2 contributions were made by the
+highest contributing  7\% of the crowd. The stage 1 agents are shown in blue,
+the stage 2 agents in orange. ``Experienced volunteers'' classified 10 or more
+training subjects.}
+\label{fig:crowd:cumulplot}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\Fref{fig:crowd:cornerplot} shows the \sw crowd to have quite broad
+distributions of logarithmic effort, skill, and contribution. To better
+quantify the contributions made by the volunteers, we show their cumulative
+distribution on a linear scale in \Fref{fig:crowd:cumulplot}. This plot shows
+clearly the importance of the hardest-working, most active volunteers: at
+stage 1,  1.0\% of the volunteers -- 374 people -- made 90\% of the
+contribution.  At stage 2, where it was not possible to make as
+many classifications before running out of subjects, 7.2\% of the volunteers
+-- 141 people -- made 90\% of the contribution.
+
+However, it is not the case that only these small groups were capable of
+making this large contribution: 9119 volunteers were ``experienced'' in that
+they had all classified at least 10 training images; the 374 highest
+contributing volunteers make up just 4\% of this experienced volunteer pool.
+The cumulative distribution of agent skill is shown in
+\Fref{fig:crowd:cumulskillplot}: these distributions are significantly broader
+than the corresponding distributions of agent contribution in 
+\Fref{fig:crowd:cumulplot}. The most skilled 20\% of agents possess only  79\%
+of the skill at stage 1, and 77\% at stage 2. The inexperienced volunteers
+also possess a significant fraction of the skill: the most skillful 20\% of
+experienced volunteers (1824 people)  possess just 43\% of the total skill.
+The level of contribution made at \sw by experienced volunteers is largely a
+matter of choice (or perhaps, availability of time!).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_skill_cumul.png}
+\caption{Broad cumulutive distributions of agent skill: 
+the most skilled 20\% of the crowd only possess 79\% of the skill at stage 1.
+The stage 1 agents
+are shown in blue, the stage 2 agents in orange. ``Experienced volunteers''
+classified 10 or more training subjects.}
+\label{fig:crowd:cumulskillplot}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\Tref{tab:crowd:contributions} shows the total effort, contribution, skill and
+information generated in both stage 1 and 2 of the CFHTLS project, with the
+total numbers of agents and subjects for comparison. These numbers allow us to
+quantify the efficiency of the system.
 

### 2014-06-01 analysis/make_crowd_plots.py

@@ -163,6 +163,10 @@ def make_crowd_plots(argv):
     contribution = np.array(contribution)
     contribution_all = np.array(contribution_all)
 
+    print "make_crowd_plots: mean stage 1 volunteer effort = ",phr(np.mean(effort_all))
+    print "make_crowd_plots: mean stage 1 volunteer experience = ",phr(np.mean(experience_all))
+    print "make_crowd_plots: mean stage 1 volunteer contribution = ",phr(np.mean(contribution_all)),"bits"
+    print "make_crowd_plots: mean stage 1 volunteer skill = ",phr(np.mean(final_skill_all),ndp=2),"bits"
 
     #same setup for stage 2, except special class is veteran volunteers rather than "experienced" volunteers
 
@@ -220,10 +224,17 @@ def make_crowd_plots(argv):
     new_s2_effort = np.array(new_s2_effort)
     new_s2_information = np.array(new_s2_information)
 
+    print "make_crowd_plots: mean stage 2 volunteer effort = ",phr(np.mean(effort_all2))
+    print "make_crowd_plots: mean stage 2 volunteer experience = ",phr(np.mean(experience_all2))
+    print "make_crowd_plots: mean stage 2 volunteer contribution = ",phr(np.mean(contribution_all2)),"bits"
+    print "make_crowd_plots: mean stage 2 volunteer skill = ",phr(np.mean(final_skill_all2),ndp=2),"bits"
 
     # ------------------------------------------------------------------
 
-    # Plot #1: cumulative distribution of contribution
+    # Plot 1.1 and 1.2: cumulative distributions of contribution and skill
+    
+    # 1.1 Contribution
+    
     plt.figure(figsize=(10,8))
 
     # All Stage 1 volunteers:
@@ -274,6 +285,56 @@ def make_crowd_plots(argv):
     pngfile = output_directory+'crowd_contrib_cumul.png'
     plt.savefig(pngfile, bbox_inches='tight')
     print "make_crowd_plots: cumulative contribution plot saved to "+pngfile
+
+
+    # 1.2 Skill
+    
+    plt.figure(figsize=(10,8))
+
+    # All Stage 1 volunteers:
+    cumulativeskill1_all = np.cumsum(np.sort(final_skill_all)[::-1])
[…]

### 2014-06-01 doc/sw-system.tex
All crowd figs are in

@@
 \centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_contrib_cumul.png}
-\caption{Narrow cumulutive distributions of the contributions made by the
+\caption{Narrow cumulative distributions of the contributions made by the
 agents: for example, 90\% of the stage 2 contributions were made by the
@@
 \centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_skill_cumul.png}
-\caption{Broad cumulutive distributions of agent skill: 
+\caption{Broad cumulative distributions of agent skill: 
 the most skilled 20\% of the crowd only possess 79\% of the skill at stage 1.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/stage2_veteran_contribution.png}
+\caption{Stage 2 agent properties, separating veterans from stage 1 from new
+volunteers. Point size represents total information generated, dashed lines
+are drawn at the mean values for each sample.}
+\label{fig:crowd:stage1vstage2}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We now look at the transition between stage 1 and stage 2 in more detail. Of
+the 1964 volunteers who took part in the stage 2 classification round, only
+783 were veterans from stage 1. However, these volunteers showed significantly
+higher skill levels than the new users, and also made more classifications
+(and hence made greater contributions. This is illustrated in  
+\Fref{fig:crowd:stage1vstage2}. In this figure, point size is proportional to
+information generated: the higher skill, higher effort stage 1 veterans
+generated most of the information.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/early_vs_final_skill.png}
+\caption{Predictability of final skill from early skill (after 10 training
+classifications) in stage 1 agents. The dashed lines enclose 649 agents with
+early skill greater than 0.1 
+who retain final skill of greater than 0.05.}
+\label{fig:crowd:skillprediction}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Having seen the importance of the high skill volunteers at both stage 1 and
+stage 2, we might ask, can we predict agent skill after, say, the volunteer
+has experienced 10 training subjects? In \Fref{fig:crowd:skillprediction} we
+plot this ``early skill'' against final skill, for all experienced stage 1
+volunteers. The majority of the crowd shows little correlation, but at the
+high early skill end, some predictability appears. The 649 experienced  stage
+1 volunteers who had early skill greater than 0.1 went on to attain a mean
+final skill of 0.22, with 97\% remaining at skill 0.05 or higher. This
+suggests that it might be worth tracking volunteers' skill as a project
+progresses, in order to encourage those showing an aptitude for the task to
+take part in the more difficult activities, such as stage 2 refinement.
+
 \Tref{tab:crowd:contributions} shows the total effort, contribution, skill and
@@
 quantify the efficiency of the system.
-
-Can we predict skill? Early skill vs final skill - some correlation,
-especially in high skill users, but very broad distribution though: not
-possible to predict.
-\Fref{fig:crowd:skillprediction}
-
-Stage 1 skill vs Stage 2 skill. 
-Who continued to do Stage 2? Numbers. 
-\Fref{fig:crowd:stage1vstage2}
 

### 2014-06-01 analysis/make_crowd_plots.py

@@ -338,12 +338,16 @@ def make_crowd_plots(argv):
 
 
     # ------------------------------------------------------------------
-    # Plot 1.5: skill histograms? linear x axis, logarithmic y?
-
-
-    # ------------------------------------------------------------------
 
     # Plot #2: is final skill predicted by early skill?
+
+    N = len(final_skill)
+    prodigies_final_skill = final_skill[np.where(early_skill > 0.1)]
+    Nprodigies = len(prodigies_final_skill)
+    mean_prodigies_skill = np.mean(prodigies_final_skill)
+    Ngood_prodigies = len(np.where(prodigies_final_skill > 0.05)[0])
+    print "make_crowd_plots: the",Nprodigies,"-",phr(100*Nprodigies/N),"% - of experienced stage 1 volunteers who have early skill > 0.1 go on to attain a mean final skill of",phr(mean_prodigies_skill,ndp=2)
+    print "make_crowd_plots: with",phr(100*Ngood_prodigies/Nprodigies),"% of them remaining at skill 0.05 or higher"
 
     plt.figure(figsize=(10,8))
     plt.xlim(-0.02,0.25)
@@ -352,6 +356,8 @@ def make_crowd_plots(argv):
     plt.ylabel('Final Skill, $\langle I \\rangle_{j=N_{\\rm T}}$ / bits')
     size = 400.0
     plt.scatter(early_skill,final_skill,s=size,color='blue',alpha=0.05)
+    plt.plot((0.1, 0.1), (0.05, 0.8),color='black',ls='--')
+    plt.plot((0.1, 0.25), (0.05, 0.05),color='black',ls='--')
     pngfile = output_directory+'early_vs_final_skill.png'
     plt.savefig(pngfile, bbox_inches='tight')
     print "make_crowd_plots: skill-skill plot saved to "+pngfile

### 2014-06-01 doc/sw-system.tex
Included summary table

@@
 total numbers of agents and subjects for comparison. These numbers allow us to
-quantify the efficiency of the system.
+quantify the efficiency of the system. The contribution per classification is
+defined in terms of a hypothetical subject with lens probability of 0.5; one
+bit of information is needed to update such a subject's lens probability to
+either zero or one. This means that a maximally complete classification stage
+would yield a total contribution (summed over all agents) equal to the number
+of subjects. The ratio of this hypthetical optimum to the actual total
+contribution is therefore a measure of the stage's inefficiency. We find our
+inefficiency (by dividing column 2 by column 3) to be 33\% and 17\% in stage 1
+and 2 respectively. In stage 1, this inefficiency is due to the daily
+processing: we were not able to retire subjects fast enough, and so they,
+remained in the system, being over-classified. Only 3644943 classifications
+were needed to retire all the subjects: the ratio of this to the total number
+made is 34\%. (The remaining 1\% is due to not all subjects being classified
+to 1 or 0 probability.) At stage 2, we did not retire any subjects at all; the
+inefficiency in this case was by design, to give everyone a chance to
+appreciate what they had found together!
+
+The total skill of the crowd, computed by summing the skill of all the agents,
+is, similarly, a measure of the effective crowd size: a crowd of perfect
+classifiers would be this size. The stage 1 crowd was equivalent to a team of
+1472.1 perfect classifiers; the stage 2 crowd was equivalent to a team of
+102.4 perfect classifiers.
+
+The total information generated during the survey is harder to interpret,
+because it's exactly the high probability candidates that we leave in the
+system that give rise to most of the information generated. What we can do is
+divide the total information generated by the amount of information it takes
+to classify a \sw subject all the way to the detection threshold (lens
+probability 0.95), divide by this number, and then multiply by the survey
+inefficiency to get a very rough estimate for the effective number of
+detections corresponding to the crowd's contribution. With a prior probability
+of $2\times10^{-4}$, it takes 11.6 bits to make a detection; the effective
+number of detections contributed by the stage 1 and stage 2 volunteers is then
+1736 and 24 respectively. These figures lie roughly between the numbers of
+detections and non-rejections given in column 7 of
+\Tref{tab:crowd:contributions}. The uncertainty in the interpretation of the
+information generated provides further justification for our focus on the
+expected information gain as a measure of volunteer contribution.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table*}
+\begin{center}
+\caption{Total crowd and subject sample properties from the CFHTLS project.}
+\label{tab:crowd:contributions}
+\begin{tabular}{cccccccc}
+  \hline
+  \hline {Stage} & Subjects & Contribution                          & Agents & Skill      & Classifications          & Candidates & Information \\
+                 & $\Ns$    & $\sum_k^{\Nv} \contribution_k$ (bits) & $\Nv$  & $\sum_k^{\Nv} \skill_k$ (bits) & $\sum_k^{\Nv} \thiseffort$ & $\Ncands$  & $\sum_j^{\Ns}\sum_k^{\Nv} \information_{j,k}$ (bits) \\
+  \hline 
+            1    & $423683$ & $1269574.7$ & $36985$ & $1472.1$ & $10654285$ & $43 (3225)$ & $61032.7$ \\
+            2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ & $91 (1391)$ &  $1641.9$ \\
+  \hline \hline
+\end{tabular}
+\medskip\\
+\end{center}
+\end{table*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2014-06-01 analysis/SWAP.py
Ignore subject stage labels to enable re-analysis

@@ -243,14 +243,14 @@ def SWAP(argv):
         if vb: print "#"+str(count+1)+". items = ",items
         if items is None:
             continue # Tutorial subjects fail, as do stage/project mismatches!
-        tstring,Name,ID,ZooID,category,kind,X,Y,location,thisstage = items
+        tstring,Name,ID,ZooID,category,kind,X,Y,location,classification_stage = items
         t = datetime.datetime.strptime(tstring, '%Y-%m-%d_%H:%M:%S')
 
         # If the stage of this classification does not match the stage we are
         # on, skip to the next one!
-        if thisstage != stage:
+        if classification_stage != stage:
             if vb:
-                print "Found classification from different stage: ",thisstage," cf. ",stage,", items = ",items
+                print "Found classification from different stage: ",classification_stage," cf. ",stage,", items = ",items
                 print " "
             continue
         else:

### 2014-06-01 analysis/swap/mongodb.py

@@ -149,10 +149,10 @@ class MongoDB(object):
         # Pull out the annotations and get the stage the classification was made at:
         annotations = classification['annotations']
         
-        stage = 1
+        classification_stage = 1
         for annotation in annotations:
             if annotation.has_key('stage'):
-                stage = annotation['stage']
+                classification_stage = annotation['stage']
         
         # Also get the survey name!
         project = "CFHTLS"
@@ -163,10 +163,10 @@ class MongoDB(object):
         # Check project: ignore this classification by returning None 
         # if classification is from a different project:
         if project != survey:
-            # print "Fail! A classification from "+project+" ( != "+survey+" ), stage = ",stage
+            # print "Fail! A classification from "+project+" ( != "+survey+" ), stage = ",classification_stage
             return None
         # else:
-            # Success! A classification from "+project+" ( = "+survey+" ), stage = ",stage
+            # Success! A classification from "+project+" ( = "+survey+" ), stage = ",classification_stage
         
         # Now pull the subject itself from the subject table:
         subject = self.subjects.find_one({'_id': ID},timeout=False)
@@ -178,22 +178,26 @@ class MongoDB(object):
             # Subject is tutorial and has no group id:
             return None
         
-        metadata = subject['metadata']        
+        subject_metadata = subject['metadata']        
         
-        # Check stage:
-        if metadata.has_key('stage2'):
-            if stage == 1: 
-                # This happens when the data is uploaded, but the site has
-                # not been taken down... Need to ignore these classifications!
-                # print "WARNING: classification labelled stage 1, while subject is stage 2!"
-                return None
+        # Check subject stage:
+        # if subject_metadata.has_key('stage2'):
+        #     if classification_stage == 1: 
+        #         # This happens when the data is uploaded, but the site has
+        #         # not been taken down... Need to ignore these classifications!
+        #         # print "WARNING: classification labelled stage 1, while subject is stage 2!"
+        #         return None
+        
+        # PJM: The above code causes a bug when SWAP is re-run on stage 1 later on!
+        # Commented out, and moved to using timestamps rigorously to delineate 
+        # stage 1 and stage 2, as well as checking classification stage, that is.
        
         
         # What kind of subject was it? Training or test? A sim or a dud?
         kind = ''
         if str(groupId) == trainingGroup:
             category = 'training'
[…]

### 2014-06-02 doc/sw-system.tex
New numbers, from re-run of SWAP to 'correct' end date

@@
 \item{\noindent\bf ``Effort:''} The number of test images, $\effort$, classified by a
-volunteer. In stage 1, the mean effort per agent was 259; in the shorter stage
+volunteer. In stage 1, the mean effort per agent was 263; in the shorter stage
 2 it was 81.
@@
 clearly the importance of the hardest-working, most active volunteers: at
-stage 1,  1.0\% of the volunteers -- 374 people -- made 90\% of the
+stage 1,  1.0\% of the volunteers -- 375 people -- made 90\% of the
 contribution.  At stage 2, where it was not possible to make as
@@
 However, it is not the case that only these small groups were capable of
-making this large contribution: 9119 volunteers were ``experienced'' in that
-they had all classified at least 10 training images; the 374 highest
+making this large contribution: 9097 volunteers were ``experienced'' in that
+they had all classified at least 10 training images; the 375 highest
 contributing volunteers make up just 4\% of this experienced volunteer pool.
@@
 also possess a significant fraction of the skill: the most skillful 20\% of
-experienced volunteers (1824 people)  possess just 43\% of the total skill.
+experienced volunteers (1820 people)  possess just 43\% of the total skill.
 The level of contribution made at \sw by experienced volunteers is largely a
@@
 the 1964 volunteers who took part in the stage 2 classification round, only
-783 were veterans from stage 1. However, these volunteers showed significantly
+774 were veterans from stage 1. However, these volunteers showed significantly
 higher skill levels than the new users, and also made more classifications
@@
 processing: we were not able to retire subjects fast enough, and so they,
-remained in the system, being over-classified. Only 3644943 classifications
+remained in the system, being over-classified. Only 3705704 classifications
 were needed to retire all the subjects: the ratio of this to the total number
@@
 classifiers would be this size. The stage 1 crowd was equivalent to a team of
-1472.1 perfect classifiers; the stage 2 crowd was equivalent to a team of
+1469.9 perfect classifiers; the stage 2 crowd was equivalent to a team of
 102.4 perfect classifiers.
@@
 number of detections contributed by the stage 1 and stage 2 volunteers is then
-1736 and 24 respectively. These figures lie roughly between the numbers of
-detections and non-rejections given in column 7 of
-\Tref{tab:crowd:contributions}. The uncertainty in the interpretation of the
+2670 and 24 respectively. These figures are close to the numbers of detections
+given in column 7 of \Tref{tab:crowd:contributions}. 
+The uncertainty in the interpretation of the
 information generated provides further justification for our focus on the
@@
   \hline 
-            1    & $423683$ & $1269574.7$ & $36985$ & $1472.1$ & $10654285$ & $43 (3225)$ & $61032.7$ \\
-            2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ & $91 (1391)$ &  $1641.9$ \\
+            1    & $427064$ & $1291997.4$ & $36929$ & $1469.9$ & $10768759$ & $3367$ & $91110.7$ \\
+            2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $91$ &  $1641.9$ \\
   \hline \hline

### 2014-06-02 analysis/make_crowd_plots.py
Early vs final skill point size = contribution

@@ -354,8 +354,10 @@ def make_crowd_plots(argv):
     plt.ylim(-0.02,0.8)
     plt.xlabel('Early Skill, $\langle I \\rangle_{j<10}$ / bits')
     plt.ylabel('Final Skill, $\langle I \\rangle_{j=N_{\\rm T}}$ / bits')
-    size = 400.0
-    plt.scatter(early_skill,final_skill,s=size,color='blue',alpha=0.05)
+    # Point size prop to contribution!
+    # size = 400.0
+    size = 20 + 0.01*contribution
+    plt.scatter(early_skill,final_skill,s=size,color='blue',alpha=0.4)
     plt.plot((0.1, 0.1), (0.05, 0.8),color='black',ls='--')
     plt.plot((0.1, 0.25), (0.05, 0.05),color='black',ls='--')
     pngfile = output_directory+'early_vs_final_skill.png'

### 2014-06-04 doc/sw-cfhtls.tex

--- 2014-06-01 doc/sw-system.tex
@@
 %
-% Space Warps System Paper
+% Space Warps CFHTLS Results Paper
 %
@@
 \title[\sw]
-{\SW: Crowd-sourcing the Discovery of Gravitational Lenses}
+{\SW: New Lens Candidates from the CFHT Legacy Survey}
 
-\author[Marshall et al.]{%
-  \input{sw-system-authors.tex}
+\author[More et al.]{%
+  \input{sw-cfhtls-authors.tex}
 }
@@
 
-\sw is a web-based service that enables the discovery of strong gravitational
-lenses in wide-field imaging surveys by large numbers of people. Carefully
-produced color composite images are displayed to volunteers via a
-classification interface which records their estimates of the positions of
-candidate lensed features. Simulated lenses, and expert-classified non-lenses,
-are inserted into the image stream at random intervals; this training set is
-used to give the volunteers feedback on their performance, and to estimate a
-dynamically-updated probability for any given image to contain a lens. Low
-probability systems are retired from the site periodically, concentrating the
-sample towards a set of candidates; this ``stage 1'' set is then re-classified
-by the volunteers in a second  refinement stage. Analyzing the classification
-of the training set, we predict that the first stage alone should yield a
-sample that is C\% complete, while leading to the rejection of R\% of the
-initial target sample. Having divided the 150 square degree CFHTLS imaging
-survey into 430000 overlapping 70 by 70 arcminute tiles and displayed them on
-the site, we were joined by 33000 volunteers who contributed X million image
-classifications over the course of N months. The sample was reduced to 3500
-stage 1 candidates; these were then refined to yield a sample of 1400
-candidates rankable by their stage 2 probability. We expect this sample to be
-X\% complete and Y\% pure at a threshold of 95\% classification probability.
-We find that, on average, and given the assumptions we make in our analysis,
-we need 9 classifications per image during the first stage, X in the second.
-We estimate the mean information contributed per person to be X bits, over a
-session lasting, on average, N classifications per volunteer, and present the
-highly skewed distributions of these quantities. We comment on the scalability
-of the \sw system to the wide field survey era, and its potential to operate
-beyond its design as a supervised classification system.
+We present X new strong gravitational lens candidates found in the CFHT Legacy
+survey by the \sw collaboration.
 
@@
 
-% Scientific motivation. Applications of lenses: group-scale arcs,
-% galaxy-galaxy lenses, lensed quasars.
-
-Strong gravitational lensing -- the formation of multiple, magnified images of
-background objects due to the deflection of light by  massive foreground
-objects -- is a very powerful astrophysical tool, enabling a wide range of
-science projects. The image separations and distortions provide information
-about the mass distribution in the lens \citep[e.g.][]{AugerEtal2010,
-SonnenfeldEtal2012,SonnenfeldEtal2013}, including on sub-galactic scales
-\citep[e.g.][]{Dalal+Kochanek2002,VegettiEtal2010,HezavehEtal2013}. Any
-strong lens can provide magnification of a factor of 10 or more, providing a
-deeper, higher resolution view of the distant universe through these ``cosmic
-telescopes'' \citep[e.g.][]{StarkEtal2008,NewtonEtal2011}. Lensed quasars enable
-cosmography via the time delays between the multiple images' lightcurves
-\citep[e.g.][]{TewesEtal2013,SuyuEtal2013}, and study of the accretion disk itself
-through the microlensing effect \citep[e.g.][]{PoindexterEtal2008}. All of these
-science projects would benefit from being able to draw from a larger sample of
-lenses.
-
-In the last decade the numbers of detections of these rare cosmic alignments
-has increased by an order of magnitude, thanks to wide field surveys such as
-CLASS \citep[e.g.]{BrowneEtal2003}, SDSS \citep[e.g.][]
-{BoltonEtal2006,AugerEtal2010b,TreuEtal2011,InadaEtal2012}, CFHTLS
-\citep[e.g.][]{MoreEtal2012,GavazziEtal2014}, Herschel
-\citep[][]{NegrelloEtal2014} and SPT \citep[e.g.][]{VieiraEtal2013}, among
-others.  As the number of known lenses has increased, new types have been
-discovered, leading to entirely new investigations. Compound lenses
-\citep{GavazziEtal2008,CollettEtal2012} and lensed supernovae
-\citep{QuimbyEtal2014} are good examples of this.
-
-% Problem of rarity. Imaging surveys. Problem of purity/false positives.
-% Review of progress to date. Methods in SL2S, SQLS. Contrast with SLACS.
-
-Because they are rare, strong lenses are expensive to find. The most efficient
-searches to date have made use of relatively clean signals such as the
-presence of emission or absorption features at two distinct redshifts in the
-same optical spectrum \citep[e.g.][]{BoltonEtal2004}, or the strong
-``magnification bias'' towards detecting strongly-lensed sources in the sub-mm
-waveband \citep[e.g.][]{NegrelloEtal2010}. Such searches have to be efficient,
-because they require expensive high resolution imaging follow-up; consequently
-they have so far produced yields in the tens to hundreds. An alternative approach
-is to search images of sufficiently high resolution and color contrast, and
-confirm the systems as gravitational lenses by modeling the survey data
-themselves \citep[][]{MarshallEtal2009}. Several square degrees of HST images
-have been searched, yielding several tens of galaxy-scale lenses
-\citep[e.g.][]{MoustakasEtal2007,FaureEtal2008,Jackson2008,MoreEtal2012,
-PawaseEtal2014}.
-Similarly, searches of over a hundred square degrees of CFHT Legacy Survey
-ground-based imaging, also with sub-arcsecond image quality, have revealed a
-smaller number of wider image separation group-scale systems
-\citep[e.g.][]{CabanacEtal2007,MoreEtal2012}. Detecting galaxy-scale lenses from
-the ground is hard, but feasible albeit lower efficiency and requiring HST or
-spectroscopic follow-up to confirm the candidates as lenses
-\citep[e.g.][]{GavazziEtal2014}.
-
-% Scaling to wide field era. Automated methods: problems. Need for good
-% training sets. Need for quality control: always present.
-
-How can we scale these lens searches up to imaging surveys covering a hundred
-times the sky area, such as the almost-all sky surveys planned with LSST and
-Euclid, while reducing our dependence on expensive follow-up confirmation
-observations? There are two approaches to detecting lenses in imaging surveys.
-The first one is robotic: automated analysis of object catalogs and/or the
-survey images. The candidate samples produced by these methods have, to date,
-not been of high purity  \citep[see
-e.g.][]{MarshallEtal2009,MoreEtal2012,GavazziEtal2014}, with visual inspection by
-teams of humans still required to narrow down the robotically-generated
-samples. In this approach, the image data may or may not be explicitly
-modelled by the robots as if it contained a gravitational lens, but the visual
-inspection can be thought of as a ``mental modeling'' step. Systems classified
-by an inspector to be good lens candidates are deemed as such because the
-features in the image can be explained by a model of what gravitational lenses
-do contained in the inspector's brain. The second approach simply cuts out the
-robot middleman: \citet{FaureEtal2008,Jackson2008} and \citet{PawaseEtal2014}
-all performed entirely visual searches for lenses in HST imaging.
-
-Visual image inspection seems, at present, unavoidable at some level when
-seraching for gravitational lenses. The technique has some drawbacks, however.
-First is that humans are only humans, and they make mistakes. The solution to
-this is to operate in teams, providing multiple classifications of the same
-images in order to catch errors and correct them. Second, and relatedly, is
-that humans get tired. With a well-designed classification interface, a human
-might be able to inspect images at a rate of one astronomical object per
-second (provided the majority are indeed uninteresting). At $10^4$ massive
-galaxies, and 10 lenses, per square degree, visual lens searches in good
-quality imaging data are limited to a few square degrees per inspector per
-day. Scaling to thousands of square degrees therefore means either robotically
-reducing the number of targets for inspection, or increasing the number of
-inspectors, or both.
-
-For example, a $10^4$ square degree survey containing $10^8$
-photometrically-selected massive galaxies and $10^5$ lenses could only be
-searched by 10 inspectors at a mean rate of 1 galaxy per second and 10
-inspections per galaxy in about 14 years. Reducing the inspection time by a
-factor of 400 to two weeks would require a robot to reduce the target sample
-to 25 per square degree. However, at this point the required purity, 40\%,
-would very likely require the average classification time per object to be
-more like 10 seconds per object. Hiring 10 inspectors to assess complex images
-full time full time for five months may not be the most cost-effective or
-reliable strategy. Alternatively, a team of $10^6$ inspectors could, in
-principle, make the required $10^9$ image classifications, $10^3$ each, in a
-few weeks; robotically reducing the target list would lead to a proportional
-decrease in the required team size.
-
-Systematic detection of rare astronomical objects by such ``crowd-sourced''
-visual inspection has recently been achieved by the online citizen science
-project PlanetHunters \citep{SchwambEtal2012}. PlanetHunters was designed to
-enable the discovery of transiting exoplanets in data taken by the Kepler
-satellite; a community of N inspectors from the general public found, after
-each undergoing a small amount of training, N new exoplanet candidates by
-visual inspection of the Kepler lightcurves that were presented in a custom
-web-based classification interface. The older Galaxy Zoo morphological
-classification project \citep{LintottEtal2008} has also enabled the discovery
-of rare objects, via its flexible inspection interface and discussion forum
-\citep{LintottEtal2009}. Indeed, several of us (AV,EB,CC,TJ,CM,LW) were active
-in an informal Galaxy Zoo gravitational lens search, an experience which led
-to the present hypothesis that a systematic online visual lens search could be
-successful.
-
-In this paper, we describe the \sw website, an online system that enables 
-crowd-sourced gravitational lens detection by inviting volunteers to classify
-astronomical survey images as containing lens candidates or not.  In a
-companion paper we will present the new gravitational lenses discovered in our
-first experimental lens search, and begin to investigate the differences
-between lens detections made in \sw and those made with automated techniques.
-Here though, we try to answer the following questions:
+In this paper, we ... try to answer the following questions:
 
@@
 
-\item How reliably can we find gravitational lenses using the \sw
-system? What is the completeness of the sample produced?
+\item ...
 
-\item How noisy is the system? What is the purity of the sample
-produced?
+\item ...
 
-\item How quickly can lenses be detected, and non-lenses be rejected?
-How many classifications, and so how many volunteers are needed per target?
-
-\item What can we learn about the scalability of the crowd-sourcing approach?
+\item ...
 
@@
 
-This paper is organised as follows.  In \Sref{sec:design} we introduce the \sw
-classification interface and the volunteers who make up the \sw
-collaboration,  explain how we use training images, and describe our two stage
-candidate selection strategy. We then briefly introduce, in \Sref{sec:data}
-the particular dataset used in the first experimental tests of the \sw system,
-and how we prepared the images prior to displaying them in the web interface.
-In \Sref{sec:swap} we describe our methodology for interpreting the
-classifications made by the volunteers, and then present the results of system
-performance tests  made on the training images in \Sref{sec:results}. % In
-this section, we also investigate the properties of the crowd, to % understand
-where the information is coming from. We discuss the implications of our
-results for future lens searches in \Sref{sec:discuss} and draw conclusions in
+This paper is organised as follows. In \Sref{sec:sw} we give a brief overview
+of the \sw system, focusing on the aspects most relevant to the interpretation
+of the results of this first lens search. In \Sref{sec:data} we introduce the
+CFHTLS imaging data. ... We discuss the implications of our results for future
+lens searches in \Sref{sec:discuss} and draw conclusions in
 \Sref{sec:conclude}.
-
-% \section{Introduction}
-% \label{sec:intro}
-% \section{Experiment Design}
-% \label{sec:design}
-% \subsection{Training}
-% \label{sec:design:training}
-% \subsection{Stage 1: Initial Classification}
-% \label{sec:design:stage1}
-% \subsection{Stage 2: Refinement}
-% \label{sec:design:stage2}
-% \section{Data}
-% \label{sec:data}
-% \subsection{The CFHT Legacy Survey}
-% \label{sec:data:CFHTLS}
-% \subsection{Image Presentation}
-% \label{sec:data:display}
-% \section{Classification Analysis}
-% \label{sec:swap}
-% \section{Results}
-% \label{sec:results}
-% \subsection{Crowd Properties}
-% \label{sec:results:crowd}
-% \subsection{Sample completeness and purity}
-% \label{sec:results:sample}
-% \section{Discussion}
-% \label{sec:discuss}
-% \section{Conclusions}
-% \label{sec:conclude}
 
@@
 
-\section{Experiment Design}
-\label{sec:design}
-
-The basic steps of a visual search for gravitational lenses are: 1) prepare
-images, 2) display them to an inspector, 3) record the inspector's
-classification of each image (as, for example, containing a lens candidate or
-not) and 4) analyzing those classifications (and all others) in order to
-produce a final candidate list. We describe step 1 in \Sref{sec:data} and step
-4 in \Sref{sec:swap}. In this section we take a volunteer's eye view and
-begin by describing the \sw classification interface, the crowd of volunteers,
-and the interactions between the two.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/sw-screengrab-marker+feedback.png}
-\caption{Screenshot of the \sw classification interface.}
-\label{fig:screenshot}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Classification Interface}
-\label{sec:design:interface}
-
-A screenshot of the \sw classification interface (CI) is shown in
-\Fref{fig:screenshot}. The CI is the centrepiece of the \sw website,
-\texttt{http://spacewarps.org}; the web application is written in
-coffeescript, css and html and follows the general design of others written by
-the Zooniverse team.\footnote{The \sw web application code is open source and
-can be accessed from \texttt{https://github.com/zooniverse/Lens-Zoo}}  The
-focus of the CI is a large display of the current pre-prepared PNG image of
-the ``subject'' being inspected.   When the image is clicked on by the
-volunteer, a marker symbol appears where the pointer was. Several markers can
-be placed.  The next image moves rapidly in from a queue formed at the right
-hand side of the screen when the ``Finished marking'' button is pressed. At
-the same time, the positions of the markers are written out to the
-classification database, in an entry that also stores the ID of the subject,
-the username (or IP address) of the volunteer, a timestamp and some other
-metadata.
-
-Gravitational lenses are rare: typically, most of the images will not contain
-a lens candidate, and these need to be quickly rejected by the inspector. The
-queue allows several images to be pre-loaded while the volunteer is
-classifying the current subject, and the rapid movement is designed to
-encourage volunteers to classify rapidly.
-
-For the more interesting subjects, the CI offers two features that  enable
-further investigation of the subjects. First is the ``Quick Dashboard'' (QD) a
-more advanced image viewer. This allows the viewer to compare three different
-contrast and color balance settings, to help bring out subtle features, and to
-zoom in on interesting regions of the image to assess small features. Markers
-can be placed in the Quick Dashboard just the same as in the main CI image
-viewer. The second is a link to that subject's page in the project discussion
-forum, \texttt{http://talk.spacewarps.org}. Here, volunteers can discuss the
-features they have seen either before they submit their classification, or
-after, if they ``favorite'' the subject. There is no ``back'' button: each
-volunteer may only classify a given subject once. However, the presence of an
-option to see what others think about any given subject before submitting your
-own classification means that the classifications may not be  strictly
-independent; the advantage of this system is that volunteers can learn from
-others what constitutes a good lens candidate. In practice, we might expect
-this to be a relatively unimportant educational resource, given the explicit
-training we provide for the volunteers, which we describe in the next section.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Training}
-\label{sec:design:training}
-
-Gravitational lenses are unfamiliar objects to volunteers who are new
-to the site. New volunteers need to learn what lenses look like as quickly as
-possible, so that they can contribute informative classifications. They also
-need to learn what lenses do not look like, in order to reduce the false
-positive detection rate. There are three primary mechanisms in the \sw system
-for teaching the volunteers what to look for. These are, in the order in which
-they are encountered, an inline tutorial, instant feedback,
-and a ``Spotter's Guide.''
-
-\subsubsection{Inline Tutorial}
-
-New volunteers are welcomed to the site with a very short tutorial, in which
-the task is introduced, a typical image containing a simulated lens is
-displayed, and the marking procedure walked through, using pop-up message
-boxes. Subsequent images gradually introduce the more advanced
-features of the classification interface (the QD and Talk buttons), also using
-pop-up messages. The tutorial was purposely kept as short as possible so as to
-provide the minimal barrier to entry.
-
-\subsubsection{Instant Feedback}
-
-The second image viewed after the initial tutorial image is already a survey
-image, in order to get the volunteers engaged in the real task as quickly as
-possible. Training continues beyond the first image tutorial through
-``training subjects'' inserted randomly into the stream.  These training
-subjects are either simulated lenses (known as ``sims''), or survey images
-that were expert-classified (by AV, AM and PM) and found not to contain any
-lens candidates (these images are known as ``duds''). The tutorial explains
-that the volunteers  will be shown such training images. They are also
-informed that they will receive instant feedback about their performance after
-classifying (blind) any of these training subjects. Indeed, after a volunteer
-finishes marking a training subject and hits ``Finished marking,'' a pop-up
-message is generated, containing either positive feedback for a successful
-classification (for example, ``Well done! You spotted a simulated lens,'' as
-in \Fref{fig:screenshot}) or negative feedback for an unsuccessful one (for
-example, ``There is no gravitational lens in this field!'')
-
-\question{PJM}{Does the feedback lead to volunteers leaving the site more 
-quickly, or less quickly? Does negative feedback have more impact than
-positive?}
-
-The initial frequency of the training images is set to be two in five;
-subjects are drawn randomly from the pool of training images with this
-frequency. The pool contains equal numbers of sims and duds, and the draw is
-made without replacement (for that volunteer). As the number of
-classifications made by a volunteer increases, this frequency is decreased, to
-$2/(5\times2^{(\textrm{int}(N_c/20)+1)/2})$ ($\approx 0.3$ for the second 20
-subjects, $0.2$ for the third 20 subjects, and so on).
-
-This training regime means that in the first 60 images viewed, each volunteer
-is shown (on average) 9 simulated gravitational lenses, and 9 empty fields. 
-This is a much higher rate than the natural one: to try and avoid this leading
-to over-optimism among the inspectors (and a resulting high false positive
-rate), we display the current ``Simulation Frequency'' on the classification
-interface (``1 in 5'' in \Fref{fig:screenshot}) and maintain the consistent
-theme in the feedback messages that lenses are rare.
-
-\subsubsection{Spotter's Guide}
-
-The instant feedback provides real-time educational responses to the
-volunteers as they start classifying; as well as this dynamic system, \sw
-provides a static reference work for volunteers to consult when in doubt about
-how to perform the task. This ``Spotter's Guide'' is a set of webpages showing
-example lenses, both real and simulated, and also some common false positives,
-drawn from the pool of survey images. The non-lenses were identified by three
-of us (AV, AM and PM) while inspecting a small set of survey images in order
-to define the ``dud'' training images. For easy reference, the lenses are
-divided by type (for example, ``lensed galaxies,'' ``lensed quasars'' and
-``cluster lenses''), as are the false positives (for example, ``Rings and
-Spirals,'' ``Mergers,'' ``Artifacts'' and so on). The example images are
-accompanied by explanatory text. The Spotter's Guide is reached via a button
-on the left hand side, or the hyperlinked thumbnail images of the ``Quick
-Reference'' provided on the right hand side, of the classification interface.
-
-Most of the text of the Spotter's Guide focuses on what lenses do or don't do;
-the website ``Science page'' contains a very brief introduction to how
-gravitational lenses work, which is fleshed out a little on the ``FAQ'' page. 
-This also contains answers to frequently asked questions about the interface
-and the task set.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Stage 1: Initial Classification}
-\label{sec:design:stage1}
-
-Interface fast due to pre-loading of images, and minimizing interaction.
-Trade-off between speed and accuracy. Decreasing training rate.
-
-Quick dashboard provides simple ways to explore further: zoom, contrast
-controls.
-
-Spotting lenses: Markers to be placed. Two reasons: first, to give good
-feedback. Second, to focus attention.
-
-Non-lenses marked? Favourite button instead, enabling serendipitous
-discovery of other interesting things, separate from lenses.
-
-Retirement of low probability systems. Concentrates sample, provides more
-``bacon'' (while slightly skewing "sim frequency"). Note that this feature
-means that everyone contributes to detection of lenses: luck is made for the
-few that happen to see the new lenses, by the masses that did the rejection.
-Group effort.
-
-Sims vs duds leads to inclusive search -- click on anything you think etc...
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Stage 2: Refinement}
-\label{sec:design:stage2}
-
-Goal: assess candidates, reject false positives by comparing with training set
-of non-obvious non-lenses. Produce a sample rankable by probability.
-
-Reconfigured website: more detailed SG, more detailed feedback. Orange
-background to make it obvious stage 2 is different. Slower image presentation.
-Higher, constant training rate.
+\section{\sw Overview}
+\label{sec:sw}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 
-\section{Classification Analysis}
-\label{sec:swap}
-
-In this section we outline our methodology for interpreting the interactions
-of the volunteers with the identification interface.  Each classification made
-is logged in a database, storing subject IDs, (anonymous) volunteer IDs, a
-timestamp and the classification results.  The {\it kind} of subject --
-whether it is a training subject (a  simulated lens or a known non-lens) or a
-test subject (an unseen image drawn from the survey) -- is also recorded. For
-all subjects, the positions of all Markers are recorded, in pixel coordinates.
-For training subjects, we also store the ``classification'' of the subject as
-a lens, or a non-lens, and also the type of object present in the image. These
-types are summarized in \Tref{tab:objecttypes}.  This classification is used
-to provide instant feedback, but is also the basic measurement used in a
-probabilistic classification of every subject based on all image views to
-date.
-
-We perform an online analysis of the classifications,  updating a
-probabilistic model of every (anonymous) volunteer's data, and also updating
-the lens probability of each subject  (in both the training and test sets), on
-a daily basis. This gives us a dynamic estimate of the posterior probability
-for  any given  subject being a lens, given all classifications of it to date.
-Assigning thresholds in this lens probability then allows us to make good
-decisions about whether or not to retire a subject from the system, in order to
-focus attention on new images.
-
-The details of how the lens probabilities are calculated are given in
-\Aref{appendix:swap}. In summary:
-\begin{itemize}
-
-\item Each volunteer is assigned a simple software agent, characterised by a
-confusion matrix. The two independent elements of this matrix are the
-probabilities, as estimated by the agent, that the volunteer is going to be 1)
-correct when they report that an image contains a lens when it really does
-contain a lens, $\pr(\saidLENS|\LENS,T)$, and 2) correct when they report that
-an image does not contain a lens when it really doesn't contain a lens,
-$\pr(\saidNOT|\LENS,T)$.
-
-\item Each agent updates its confusion matrix elements based on the number of
-times its volunteer has been right in each way while classifying subjects from
-the training set, accounting for noise early on due to small number
-statistics: $T$ is the set of all training images seen to date.
-
-\item Each agent uses its confusion matrices to update, via Bayes' theorem,
-the probability of an image from the test set containing a lens,
-$\pr(\LENS|C,T)$, when that image is classified by its volunteer. ($C$ is the
-set of all classifications made of this subject.)
-
-\end{itemize}
-
-In the next section we present results in terms of all three of these
-probabilities, as we investigate the performance of the \SW system.
+\subsection{Known Lenses}
+\label{sec:data:knownlenses}
 
@@
 
-In this section we present our findings about the performance of the  \sw
-system, in terms of the information  contributed by the crowd in
-\Sref{sec:results:crowd}, and the overall classifications of the training set
-that they made.
+Completeness and purity with regard to known lenses.
 
@@
 
-\subsection{Crowd Properties}
-\label{sec:results:crowd}
-
-% Enthusiasm: histogram of classifications, stage 1 vs stage 2. Information
-% contributed. Correlation with number of classifications. 
-% 
-% PL and PD as measures of skill. not quite talent, due to possibility of
-% learning - but agents assume talent. Performance of crowd re PD and PL.
-% Correlations with N classifications.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/all_skill_contribution_experience_education.png}
-\caption{Key properties and contributions of the \sw crowd. Plotted are the
-1-D and 2-D marginalized distributions for the logarithms of the 
-properties of the agents described in the text. The stage 1 agents are shown
-in blue, the stage 2 agents in orange.}
-\label{fig:crowd:cornerplot}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We define the following properties of the crowd, as characterised by their
-agents, and plot the distributions of their logarithms in
-\Fref{fig:crowd:cornerplot}. 
-%
-\begin{description}
-%
-\item{\noindent\bf ``Effort:''} The number of test images, $\effort$, classified by a
-volunteer. In stage 1, the mean effort per agent was 259; in the shorter stage
-2 it was 81.
-%
-\item{\noindent\bf ``Experience:''} The number of training images, $\experience$,
-classified by a volunteer. In stage 1, the mean experience per agent was 29;
-in stage 2 (where the training image fequency was set higher) it was 34.
-%
-\item{\noindent\bf ``Skill:''} The expectation value of the information gain, $\skill$
-should  the next subject classified have lens probability 0.5
-\Aref{appendix:swap},  in bits. Random classifiers have $\skill = 0.0$,
-perfect classifiers have $\skill = 1.0$. All agents start with $\skill = 0.0$;
-this increases as training subjects are classified, and the agent's estimates
-of its confusion matrix elements improve. In stage 1, the mean skill per agent
-was 0.04 bits; in  stage 2 it was 0.05.
-%
-\item{\noindent\bf ``Contribution:''} The integrated skill over a volunteer's test
-subject classification history, and represents the total  contribution to the
-project that volunteer (see the appendix for more discussion of this
-quantity). In stage 1, the mean contribution per agent was 34.3 bits; in 
-stage 2 it was 33.5.
-%
-\item{\noindent\bf ``Information:''} The total information $\information$ generated by
-the  agent during the volunteer's classification activity. This quantity
-depends on the value of each subject's lens probability when that subject was 
-presented to the volunteer (\Aref{appendix:swap}), and so there is an element
-of luck involved with this quantity: if you never see a high probability
-subject, it's hard to generate a large amount of information. You make your
-own luck by classifying more subjects.
-%
-\end{description}
-
-The leftmost column of \Fref{fig:crowd:cornerplot} shows how the last four of
-these properties depends on the effort expended by the volunteers. We see that
-experience is strongly correlated with effort (as training images are
-presented throughout each stage, albeit at decreasing frequency), and that
-this is also true for skill. In the second row of \Fref{fig:crowd:cornerplot}
-we see that while skills of greater than 0.1 can be attained after just a few
-training images, most agents of such low experience have significantly lower
-skill. The volunteers in question only classify a few subjects before leaving.
-However, at high values of experience and effort, the skill is \emph{always
-high}. There seem to be very few agents logging large numbers of
-classifications at low skill (although there are one or two exceptions). Most
-high effort ``super-users'' have high skill. These two properties are
-reflected in both the contributions these volunteers make (third row) and the
-information they generate (fourth row).
-
-The distributions for the stage 2 agents (orange) are qualitatively similar to
-those for the stage 1 agents (blue). Differences are: 1) the maximum effort
-possible at stage 2 is smaller, because fewer subjects were available to be
-classifed, but 2) the mean effort expended at stage 2 was higher (perhaps
-because the subjects were higher probability, and more compelling); 3) the
-information generated per agent was higher at stage 2, because the subjects
-had higher probability.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_contrib_cumul.png}
-\caption{Narrow cumulative distributions of the contributions made by the
-agents: for example, 90\% of the stage 2 contributions were made by the
-highest contributing  7\% of the crowd. The stage 1 agents are shown in blue,
-the stage 2 agents in orange. ``Experienced volunteers'' classified 10 or more
-training subjects.}
-\label{fig:crowd:cumulplot}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\Fref{fig:crowd:cornerplot} shows the \sw crowd to have quite broad
-distributions of logarithmic effort, skill, and contribution. To better
-quantify the contributions made by the volunteers, we show their cumulative
-distribution on a linear scale in \Fref{fig:crowd:cumulplot}. This plot shows
-clearly the importance of the hardest-working, most active volunteers: at
-stage 1,  1.0\% of the volunteers -- 374 people -- made 90\% of the
-contribution.  At stage 2, where it was not possible to make as
-many classifications before running out of subjects, 7.2\% of the volunteers
--- 141 people -- made 90\% of the contribution.
-
-However, it is not the case that only these small groups were capable of
-making this large contribution: 9119 volunteers were ``experienced'' in that
-they had all classified at least 10 training images; the 374 highest
-contributing volunteers make up just 4\% of this experienced volunteer pool.
-The cumulative distribution of agent skill is shown in
-\Fref{fig:crowd:cumulskillplot}: these distributions are significantly broader
-than the corresponding distributions of agent contribution in 
-\Fref{fig:crowd:cumulplot}. The most skilled 20\% of agents possess only  79\%
-of the skill at stage 1, and 77\% at stage 2. The inexperienced volunteers
-also possess a significant fraction of the skill: the most skillful 20\% of
-experienced volunteers (1824 people)  possess just 43\% of the total skill.
-The level of contribution made at \sw by experienced volunteers is largely a
-matter of choice (or perhaps, availability of time!).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_skill_cumul.png}
-\caption{Broad cumulative distributions of agent skill: 
-the most skilled 20\% of the crowd only possess 79\% of the skill at stage 1.
-The stage 1 agents
-are shown in blue, the stage 2 agents in orange. ``Experienced volunteers''
-classified 10 or more training subjects.}
-\label{fig:crowd:cumulskillplot}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/stage2_veteran_contribution.png}
-\caption{Stage 2 agent properties, separating veterans from stage 1 from new
-volunteers. Point size represents total information generated, dashed lines
-are drawn at the mean values for each sample.}
-\label{fig:crowd:stage1vstage2}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We now look at the transition between stage 1 and stage 2 in more detail. Of
-the 1964 volunteers who took part in the stage 2 classification round, only
-783 were veterans from stage 1. However, these volunteers showed significantly
-higher skill levels than the new users, and also made more classifications
-(and hence made greater contributions. This is illustrated in  
-\Fref{fig:crowd:stage1vstage2}. In this figure, point size is proportional to
-information generated: the higher skill, higher effort stage 1 veterans
-generated most of the information.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/early_vs_final_skill.png}
-\caption{Predictability of final skill from early skill (after 10 training
-classifications) in stage 1 agents. The dashed lines enclose 649 agents with
-early skill greater than 0.1 
-who retain final skill of greater than 0.05.}
-\label{fig:crowd:skillprediction}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Having seen the importance of the high skill volunteers at both stage 1 and
-stage 2, we might ask, can we predict agent skill after, say, the volunteer
-has experienced 10 training subjects? In \Fref{fig:crowd:skillprediction} we
-plot this ``early skill'' against final skill, for all experienced stage 1
-volunteers. The majority of the crowd shows little correlation, but at the
-high early skill end, some predictability appears. The 649 experienced  stage
-1 volunteers who had early skill greater than 0.1 went on to attain a mean
-final skill of 0.22, with 97\% remaining at skill 0.05 or higher. This
-suggests that it might be worth tracking volunteers' skill as a project
-progresses, in order to encourage those showing an aptitude for the task to
-take part in the more difficult activities, such as stage 2 refinement.
-
-\Tref{tab:crowd:contributions} shows the total effort, contribution, skill and
-information generated in both stage 1 and 2 of the CFHTLS project, with the
-total numbers of agents and subjects for comparison. These numbers allow us to
-quantify the efficiency of the system.
+\subsection{Stage 1 Classification}
+\label{sec:results:stage1}
 
@@
 
-\subsection{Sample completeness and purity}
-\label{sec:results:sample}
+\subsection{Stage 2 Classification}
+\label{sec:results:stage2}
 
-Rejection rate. Completeness and purity at P > retirement, P > 95\%, and 
-as function of probability P. Compare stage 1 and stage 2.
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 
-Summarize performance at some fiducial threshold: eg P = 95\%.
+\subsection{Comparison with ``Expert'' Classification}
+\label{sec:results:experts}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{New Lens Candidates}
+\label{sec:results:newlenses}
 
@@
 
-Challenges for future.
+Differences with robots: what types of lenses are found at \sw?
+
+Selection function. Missing system.
+
+Further work.
 
@@
 
-Summary of system.
+Summary of CFHTLS project.
 
 Crowd-sourced gravitational lens detection works, in terms of the
-classification of the training set as described here, in the following
+classification of the CFHTLS image dataset as described here, in the following
 specific ways:
@@
 
-\item Participation (crowd size, activity rate) enabled project completion
+\item Real (robotically-detected and expert-confirmed) lenses are
+recovered/missed at similar/comparable/different rates to the
+training set.
 
-\item Both stages (1 and 2) achieved the required rejection rates
+\item Completeness, purity of \sw sample to known lenses.
 
-\item Integrated humanpower = X (stage 1) and y (stage 2), cf hours taken by
-small team of experts
+\item Partial test of supervised vs unsupervised learning, comment.
 
-\item Nightly processing is inefficient: more classifications were made than
-was necessary during peak participation. Need kafka...
+\item Which real lenses were missed? False negatives, what we conclude from
+that.
 
-\item Retirement rate. False negatives: which sims were missed?
+\item We found a
+sample of new gravitational lens candidates with the following properties: ...
 
-\item The optimal true positive rate (completeness) and false positive rate in
-the training set were estimated to be TPR\% and FPR\% at Stage 1, assuming a
-detection threshold of xxx.
+\item An expert-graded sample of size N, divided among several types, compares
+as follows.
 
-\item In the ``refinement'' stage 2, X\% of the stage 1 candidates were
-rejected (with P less than threshold), and the remainder assigned lens
-``probabilities.'' Ranking
-subjects by their Stage 2 lens probability gives an ROC curve for the system
-with X properties. The optimal true positive rate (completeness) and false
-positive rate in the training set were estimated as TPR\% and FPR\%;
-
-\item The lens-finding crowd shows some interesting properties, with
-consequences for future scalability
-
-\item The information comes predominantly from volunteers with agents with P =
-...
-
-\item The agents show a high mean information per classification, which
-increased/decreased with time; this does/doesn?t correlate with active crowd
-size, showing how the crowd changed over time...
+\item The SW lenses are different from the robotically (RingFinder and
+ArcFinder) detected lenses, in the following ways.
 
@@
 
-\appendix
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Probabilistic Classification Analysis}
-\label{appendix:swap}
-
-Our aim is to enable the construction of a sample of good lens candidates.
-Since we aspire to making logical  decisions, we define a  ``good candidate''
-as one which has a high posterior probability of being a lens, given the data:
-$\pr(\LENS|\data)$. Our problem is to approximate this probability. The data~$\data$
-in our case are the pixel values of a colour image. However, we can greatly
-compress these complex, noisy sets of data by asking each volunteer what they
-think about them. A complete  classification in \sw consists of a set of
-Marker positions, or none at all. The null set encodes the statement from
-the volunteer that the image in question is $\saidNOT$ a lens, while the
-placement of any  Markers indicates that the volunteer considers this image to
-contain a $\saidLENS$.  We simplify the problem by only using the Marker
-positions to assess whether the volunteer  correctly assigned the
-classification $\saidLENS$ or $\saidNOT$ after viewing (blindly) a member of
-the training set of subjects.
-
-How should we model these compressed data? The circumstances of each
-classification are quite complex, as are the human classifiers in general: the
-volunteers learn more about the problem as they go, but also inevitably make
-occasional mistakes (perhaps because a lens is difficult to see, or they
-became distracted during the task). To cope with this uncertainty, we assign a
-simple software {\it agent} to partner each volunteer. The agent's task is to
-interpret their volunteer's classification data as best it can, using a model
-that makes a number of necessary approximations. These interpretations will
-then include uncertainty arising as a result of the volunteer's efforts and
-also the agent's approximations, but they will have two important redeeming
-features. First, the interpretations will be quantitative (where before they
-were qualititative),  and thus will be useful in decision-making. Second, the
-agent will be able to predict, using its model, the probability of a test
-subject being a $\LENS$, given both its volunteer's classification, and its
-volunteer's experience. In this appendix we describe how these agents work.
-
-\subsection{Agents and their Confusion Matrices}
-\label{appendix:swap:probabilities}
-
-Each agent assumes that the probability of a volunteer recognising any given
-simulated lens as a lens is some number, $\pr(\saidLENS|\LENS,T)$, that
-depends only on what the volunteer is currently looking at, and all the
-previous training subjects they have seen (and not on what type of lens it is,
-how faint it is, what time it is, \etc). Likewise, it also assumes that the
-probability of a volunteer recognising any given dud image as a dud is some
-other number, $\pr(\saidNOT|\NOT,T)$, that also depends only on what the volunteer is currently looking at, and all the
-previous training subjects they have seen. These two probabilities define a 
-2 by 2 ``confusion matrix,'' which the agent updates, every time a
-volunteer classifies a training subject, using the following 
-very simple estimate:
-\be
-  \pr(``X"|X,T) \approx \frac{N_{``X"}}{N_X}.
-  \label{eq:app:fraction}
-\ee
-Here, $X$ stands for the true classification of the subject, \ie either
-$\LENS$ or $\NOT$, while $``X''$ is the corresponding classification
-made by the volunteer on viewing the subject. $N_X$ is the number of
-lenses the volunteer has been shown, while $N_{``X"}$ is the number of 
-times the volunteer got their classifications of this type of training subject
-right. $T$ stands for all
-$N_{\LENS} + N_{\NOT}$ training data that the agent has heard about to
-date.
-
-The full confusion matrix of the $k^{\rm th}$ volunteer's agent is therefore:
-\be
-  \mathcal{M}^k = 
-  \begin{bmatrix}
-    \pr(\saidLENS|\NOT,T_k) & \pr(\saidLENS|\LENS,T_k) \\
-    \pr(\saidNOT |\NOT,T_k) & \pr(\saidNOT |\LENS,T_k)
-  \end{bmatrix}.
-\ee
-Note that these probabilities are normalized, such that
-$\pr(\saidNOT |\NOT) = 1 - \pr(\saidLENS|\NOT)$.
-
-Now, when this volunteer views a test subject, 
-it is this confusion matrix that will allow their agent to update the
-probability of that test subject being a $\LENS$. Let us suppose that
-this subject has never been seen before: the agent assigns a 
-prior probability that it is (or contains) a lens is 
-\be
-  \pr(\LENS) = p_0
-\ee
-where we have to assign a value for $p_0$. In the CFHTLS, we might expect
-something like 100 lenses in 430,000 images, so $p_0 = 2\times10^{-4}$
-is a reasonable estimate. The volunteer then makes a classification $C_k$ 
-($= \saidLENS$ or $\saidNOT$).
-We can apply Bayes' Theorem to derive how the agent should
-update this prior probability into a posterior one using this new information:
-\begin{align}
-  \label{eq:app:first}
-  & \pr(\LENS|C_k,T_k) = \\
-  & \frac{\pr(C_k|\LENS,T_k)\cdot\pr(\LENS)}
-{\left[ \pr(C_k|\LENS,T_k)\cdot\pr(\LENS) + \pr(C_k|\NOT,T_k)\cdot\pr(\NOT) \right]},
-  \notag
-\end{align}
-which can be evaluated numerically using the elements of the confusion
-matrix.
-
-\subsection{Examples}
-\label{appendix:swap:examples}
-
-Suppose we have a volunteer who is always right about the true
-nature of a training subject. 
-Their agent's confusion matrix would be
-\be
-  \mathcal{M}^{\rm perfect} = 
-  \begin{bmatrix}
-    0.0 & 1.0 \\
-    1.0 & 0.0
-  \end{bmatrix}.
-\ee
-On being given a fresh subject that actually is a $\LENS$, this hypothetical
-volunteer would submit $C = \saidLENS$.  Their agent would then calculate the
-posterior probability for the subject being a $LENS$ to be
-\begin{align}
-  \pr(\LENS|\saidLENS,T_k) &= \frac{1.0 \cdot p_0}
-           {\left[ 1.0\cdot p_0 + 0.0\cdot(1 - p_0) \right]}
-   &= 1.0,
-\end{align}
-as we might expect for such a {\it perfect} classifier.  Meanwhile, a
-hypothetical volunteer who (for some reason) wilfully always submits the wrong
-classification would have an agent with the column-swapped confusion matrix
-\be
-  \mathcal{M}^{\rm obtuse} = 
-  \begin{bmatrix}
-    1.0 & 0.0 \\
-    0.0 & 1.0
-  \end{bmatrix},
-\ee
-and would submit $C = \saidNOT$ for this subject. However, such a volunteer
-would nevertheless be submitting useful information, since given the above
-confusion matrix, their agent would calculate
-\begin{align}
-  \pr(\LENS|\saidNOT,T_k) &= \frac{1.0 \cdot p_0}
-           {\left[ 1.0\cdot p_0 + 0.0\cdot(1 - p_0) \right]}
-   &= 1.0.
-\end{align}
-{\it Obtuse} classifiers turn out to be as helpful as {\it perfect} ones.
-
-\subsection{Information Contribution}
-\label{appendix:swap:examples}
-
-The information likely to be contributed by each agent for a given subject
-can be estimated before the next classification of that subject is made, 
-just from its confusion matrix.
-The Shannon entropy generated by a classifier upon performing a
-classification is
-\be
-  \langle S_k \rangle =  
-   -P_{\rm right}\cdot\log_2{P_{\rm right}} -  P_{\rm wrong}\cdot\log_2P_{\rm wrong}\,,
-\ee
-where $P_{\rm right}$ and $P_{\rm wrong}$ are the averages of the diagonal and
-the off-diagonal elements of the confusion matrix, respectively, and $\langle
-S_k \rangle$ is measured in ``bits.'' These averages represent the probability
-of a classifier to get a classification right or wrong, respectively. We define
-the information contributed by a classifier as
-\begin{equation}
-I_k = 1 - S_k\,.
-  \label{eq:app:info}
-\end{equation}
-\Eref{eq:app:info} gives the required result, that both the hypothetical {\it
-perfect} and {\it obtuse} classifiers contribute 1 bit of information each, per
-classification. Classifiers whose agent's confusion matrix is such that $P_{\rm
-right}=P_{\rm wrong}=0.5$, contribute zero bits of information. Such users
-identify a lens correctly with the same probability as they misclassify a dud
-image to contain a lens, and thus their classification is of no value.
-
-We conservatively initialise all the elements of the agents' confusion matrices
-to be 0.5, that of a random classifier. This makes no allowance for volunteers
-that actually do have previous experience of what gravitational lenses look
-like, but should help prevent large numbers of false positives being assigned
-high probability. Plotting  $\langle I_k \rangle$ as a function of time will,
-to some extent, illustrate the learning process undergone by the $k^{\rm th}$
-volunteer-agent partnership.
-
-\subsection{Updating the Subject Probabilities}
-\label{appendix:swap:examples}
-
-Suppose the $k+1^{\rm th}$ volunteer now submits a classification, on the same
-subject just classified by the $k^{\rm th}$ volunteer. We can generalise
-\Eref{eq:app:first} by replacing the prior probability with the current
-posterior probability:
-\begin{align}
-  \label{eq:app:update}
-  \pr(\LENS & |C_{k+1},T_{k+1},\data) = \\
-  & \frac{1}{Z} \pr(C_{k+1}|\LENS,T_{k+1}) \cdot \pr(\LENS|\data) \\ \notag
-{\rm where}\;\; Z = & \pr(C_{k+1}|\LENS,T_{k+1})\cdot\pr(\LENS|\data) \\ \notag
-      & + \pr(C_{k+1}|\NOT,T_{k+1})\cdot\pr(\NOT|\data), \notag
-\end{align}
-and $\data = \{C_k,T_k\}$ is the set of all previous
-classifications, and the set of training subjects seen by each of those
-volunteers.
-$\pr(\LENS|\data)$ is the fundamental property of each test subject that
-we are trying to infer. We track $\pr(\LENS|\data)$ as a function of time,
-and by comparing it to a lower or upper thresholds, make decisions about
-whether to retire the subject from the classification interface or
-promote it in \Talk, respectively.
-
-\subsection{Uncertainty in the Agent Confusion Matrices}
-\label{appendix:swap:uncertainty}
-
-The confusion matrix obtained from the application of Equation
-(\ref{eq:app:fraction}) has some inherent noise which reduces as the number of
-training subjects classified by the agent's volunteer increases. For
-simplicity, the discussion thus far assumed the case when the confusion matrix
-is known perfectly; in practice, we allow for uncertainty in the agent
-confusion matrices by averaging over a small number of samples drawn from
-Binomial distributions characterised by the matrix elements
-$\pr(C_k|\LENS,T_k)$ and  $\pr(C_k|\NOT,T_k)$. The associated standard
-deviation in the estimated subject probability provides an error bar for this
-quantity.
-
-% For ease of notation, we will denote $\pr(C_k|\LENS,T_k)\equiv p_L$ and
-% $\pr(C_k|\NOT,T_k)\equiv p_N$. In reality, there is a probability distribution
-% for both $p_L$ and $p_N$. Let $p_0$ be the prior probability of the subject
-% being a lens. Then the posterior probability, $p_0'$ of the subject being a
-% lens after the classification $C_k$ is
-% \be
-%   \label{eq:app:sec}
-% p_0' = \frac{p_L p_0}{\left[ p_L p_0 + p_N (1- p_0) \right]},
-% \ee
-% The posterior probability distribution $p_0'$ can be obtained by marginalizing
-% over the probability distributions of $p_L$, $p_N$ and the prior probability
-% distribution $p_0$ such that,
-% \be
-% P(p_0') = \int p_0' P(p_L) P(p_N) P(p_0) dp_L dp_N dp_0\,.
-% \ee
-% This marginalization is not analytically tractable. Therefore, we have
-% implemented the following Monte-Carlo solution for this problem.
-%
-
-%Finally, we also need to update the confusion matrix of an agent and obtain the
-%variance on each element of the matrix, once a training subject has been
-%classified. We would like to derive the posterior probability of the
-%probability elements $p_1$ and $p_2$ given their prior probabilities. For this
-%purpose, we can again make use of Bayes' theorem,
-%\begin{equation}
-%P(p_x'|N_{"X"},N_X,T) = \frac{P(N_{``X"}|p_x',N_X,T) P(p_x'|N_X,T)}{\sum_{N_{``X"}} P(N_{``X"}|p_x',N_X,T) P(p_x'|N_X,T)}
-%\end{equation}
-%Here, $P(N_{``X"}|p_x',N_X,T)$ is a binomial distribution, although this is not
-%true strictly speaking given that our agents are learning and the values of the
-%confusion matrix are moving. Modelling the learning curve of our users is yet
-%another complicated extension we could think about.
+% \appendix
 

### 2014-06-04 doc/sw-publication-policy-cfhtls.tex

@@
 
+\subsection{Additional \sw series or related papers}
 Please email the \sw PIs at \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com} if you have any

### 2014-06-04 doc/sw-system.tex
Stage 2 results now match Anu's

@@
 project that volunteer (see the appendix for more discussion of this
-quantity). In stage 1, the mean contribution per agent was 34.3 bits; in 
+quantity). In stage 1, the mean contribution per agent was 34.9 bits; in 
 stage 2 it was 33.5.
@@
 high}. There seem to be very few agents logging large numbers of
-classifications at low skill (although there are one or two exceptions). Most
-high effort ``super-users'' have high skill. These two properties are
+classifications at low skill (although there are one or two exceptions): almost
+all high effort ``super-users'' have high skill. These two properties are
 reflected in both the contributions these volunteers make (third row) and the
@@
 However, it is not the case that only these small groups were capable of
-making this large contribution: 9097 volunteers were ``experienced'' in that
+making this large contribution: 9118 volunteers were ``experienced'' in that
 they had all classified at least 10 training images; the 375 highest
@@
 also possess a significant fraction of the skill: the most skillful 20\% of
-experienced volunteers (1820 people)  possess just 43\% of the total skill.
+experienced volunteers (1824 people)  possess just 43\% of the total skill.
 The level of contribution made at \sw by experienced volunteers is largely a
@@
 early skill greater than 0.1 
-who retain final skill of greater than 0.05.}
+who retain final skill of greater than 0.05. Point size is proportional to
+contribution (plus a constant).}
 \label{fig:crowd:skillprediction}
@@
 take part in the more difficult activities, such as stage 2 refinement.
+However, this would not have done a very good job at identifying the 
+volunteers who went on to make the largest contributions: the point size in 
+\Fref{fig:crowd:skillprediction} is proportional to contribution (plus a constant):
+many of the highest contributors showed relatively low skill early on.
 
@@
 processing: we were not able to retire subjects fast enough, and so they,
-remained in the system, being over-classified. Only 3705704 classifications
+remained in the system, being over-classified. Only 3705745 classifications
 were needed to retire all the subjects: the ratio of this to the total number
@@
   \hline 
-            1    & $427064$ & $1291997.4$ & $36929$ & $1469.9$ & $10768759$ & $3367$ & $91110.7$ \\
-            2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $91$ &  $1641.9$ \\
+            1    & $427064$ & $1292016.3$ & $36982$ & $1471.9$ & $10802125$ & $3368$ & $91122.6$ \\
+            2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $90$ &  $1640.4$ \\
   \hline \hline

### 2014-06-23 analysis/swap/mongodb.py
final commit before pull merge

@@ -1,3 +1,8 @@
+"""
+TODO:
+    Save the whole list of clicks!
+"""
+
 # ======================================================================
 
 import numpy as np

### 2014-06-23 analysis/swap/mongodb.py
finally have all clicks for a given annotation in annotationhistory!

@@ -246,8 +246,8 @@ class MongoDB(object):
         for annotation in annotations:
             if annotation.has_key('x'): 
                 N_markers += 1
-                annotation_x.append(annotation['x'])
-                annotation_y.append(annotation['y'])
+                annotation_x.append(float(annotation['x']))
+                annotation_y.append(float(annotation['y']))
 
         
         # Detect whether sim was found or not:

### 2014-06-23 analysis/swap/subject.py

@@ -115,8 +115,8 @@ class Subject(object):
                             'ItWas': np.array([], dtype=int),
                             'PL': np.array([]),
                             'PD': np.array([]),
-                            'At_X': np.array([]),
-                            'At_Y': np.array([])}
+                            'At_X': [],
+                            'At_Y': []}
 
         return None
 
@@ -246,8 +246,8 @@ class Subject(object):
                 # update the annotation history
                 self.annotationhistory['Name'] = np.append(self.annotationhistory['Name'], by.name)
                 self.annotationhistory['ItWas'] = np.append(self.annotationhistory['ItWas'], as_being_number)
-                self.annotationhistory['At_X'] = np.append(self.annotationhistory['At_X'], (at_x))
-                self.annotationhistory['At_Y'] = np.append(self.annotationhistory['At_Y'], (at_y))
+                self.annotationhistory['At_X'].append(at_x)
+                self.annotationhistory['At_Y'].append(at_y)
                 self.annotationhistory['PL'] = np.append(self.annotationhistory['PL'], by.PL)
                 self.annotationhistory['PD'] = np.append(self.annotationhistory['PD'], by.PD)
 

### 2014-06-25 doc/sw-system.tex
Wrote up information theory from Taipei

@@
 %
-\item{\noindent\bf ``Skill:''} The expectation value of the information gain, $\skill$
+\item{\noindent\bf ``Skill:''} The expectation value of the information gain, 
+$\skill$
 should  the next subject classified have lens probability 0.5
-\Aref{appendix:swap},  in bits. Random classifiers have $\skill = 0.0$,
+(\Aref{appendix:swap}),  in bits. Random classifiers have $\skill = 0.0$,
 perfect classifiers have $\skill = 1.0$. All agents start with $\skill = 0.0$;
@@
 would yield a total contribution (summed over all agents) equal to the number
-of subjects. The ratio of this hypthetical optimum to the actual total
+of subjects. The ratio of this hypothetical optimum to the actual total
 contribution is therefore a measure of the stage's inefficiency. We find our
@@
 detections corresponding to the crowd's contribution. With a prior probability
-of $2\times10^{-4}$, it takes 11.6 bits to make a detection; the effective
+of $2\times10^{-4}$, it takes 12.3 bits to make a detection (see
+\Sref{sec:appendix:infogain} in the appendix); the effective
 number of detections contributed by the stage 1 and stage 2 volunteers is then
-2670 and 24 respectively. These figures are close to the numbers of detections
+2830 and 25 bits respectively. 
+These figures are close to the numbers of detections
 given in column 7 of \Tref{tab:crowd:contributions}. 
@@
 The full confusion matrix of the $k^{\rm th}$ volunteer's agent is therefore:
-\be
-  \mathcal{M}^k = 
+\begin{align}
+  \CM^k &= 
   \begin{bmatrix}
@@
     \pr(\saidNOT |\NOT,T_k) & \pr(\saidNOT |\LENS,T_k)
-  \end{bmatrix}.
-\ee
+  \end{bmatrix}, \notag \\
+        &=
+  \begin{bmatrix}
+    \CM_{LN} & \CM_{LL} \\
+    \CM_{NN} & \CM_{NL}
+  \end{bmatrix}^k.
+  \label{eq:confmat}
+\end{align}
 Note that these probabilities are normalized, such that
@@
 \be
-  \mathcal{M}^{\rm perfect} = 
+  \CM^{\rm perfect} = 
   \begin{bmatrix}
@@
 \be
-  \mathcal{M}^{\rm obtuse} = 
+  \CM^{\rm obtuse} = 
   \begin{bmatrix}
@@
 {\it Obtuse} classifiers turn out to be as helpful as {\it perfect} ones.
-
-\subsection{Information Contribution}
-\label{appendix:swap:examples}
-
-The information likely to be contributed by each agent for a given subject
-can be estimated before the next classification of that subject is made, 
-just from its confusion matrix.
-The Shannon entropy generated by a classifier upon performing a
-classification is
-\be
-  \langle S_k \rangle =  
-   -P_{\rm right}\cdot\log_2{P_{\rm right}} -  P_{\rm wrong}\cdot\log_2P_{\rm wrong}\,,
-\ee
-where $P_{\rm right}$ and $P_{\rm wrong}$ are the averages of the diagonal and
-the off-diagonal elements of the confusion matrix, respectively, and $\langle
-S_k \rangle$ is measured in ``bits.'' These averages represent the probability
-of a classifier to get a classification right or wrong, respectively. We define
-the information contributed by a classifier as
-\begin{equation}
-I_k = 1 - S_k\,.
-  \label{eq:app:info}
-\end{equation}
-\Eref{eq:app:info} gives the required result, that both the hypothetical {\it
-perfect} and {\it obtuse} classifiers contribute 1 bit of information each, per
-classification. Classifiers whose agent's confusion matrix is such that $P_{\rm
-right}=P_{\rm wrong}=0.5$, contribute zero bits of information. Such users
-identify a lens correctly with the same probability as they misclassify a dud
-image to contain a lens, and thus their classification is of no value.
-
-We conservatively initialise all the elements of the agents' confusion matrices
-to be 0.5, that of a random classifier. This makes no allowance for volunteers
-that actually do have previous experience of what gravitational lenses look
-like, but should help prevent large numbers of false positives being assigned
-high probability. Plotting  $\langle I_k \rangle$ as a function of time will,
-to some extent, illustrate the learning process undergone by the $k^{\rm th}$
-volunteer-agent partnership.
 
@@
 
+\subsection{Agent ``Skill'' and ``Contribution''}
+\label{appendix:swap:examples}
+
+% The information likely to be contributed by each agent for a given subject
+% can be estimated before the next classification of that subject is made, 
+% just from its confusion matrix.
+% The Shannon entropy generated by a classifier upon performing a
+% classification is
+% \be
+%   \langle S_k \rangle =  
+%    -P_{\rm right}\cdot\log_2{P_{\rm right}} -  P_{\rm wrong}\cdot\log_2P_{\rm wrong}\,,
+% \ee
+% where $P_{\rm right}$ and $P_{\rm wrong}$ are the averages of the diagonal and
+% the off-diagonal elements of the confusion matrix, respectively, and $\langle
+% S_k \rangle$ is measured in ``bits.'' These averages represent the probability
+% of a classifier to get a classification right or wrong, respectively. We define
+% the information contributed by a classifier as
+% \begin{equation}
+% I_k = 1 - S_k\,.
+%   \label{eq:app:info}
+% \end{equation}
+% \Eref{eq:app:info} gives the required result, that both the hypothetical {\it
+% perfect} and {\it obtuse} classifiers contribute 1 bit of information each, per
+% classification. Classifiers whose agent's confusion matrix is such that $P_{\rm
+% right}=P_{\rm wrong}=0.5$, contribute zero bits of information. Such users
+% identify a lens correctly with the same probability as they misclassify a dud
+% image to contain a lens, and thus their classification is of no value.
+
+With an agent's confusion matrix in hand we can compute the
+\emph{information} generated in any given classification. This will
+depend on the confusion matrix elements (\Eref{eq:confmat}) but also on
+the probability of the subject being classified containing a lens. The
+quantity of interest is the mutual information between the prior and
+posterior probabilities given the submitted classification $C$:
+\begin{align}
+\information =& H(T) - H(T;C) \notag \\ 
+             =& -\pr(\LENS) \log_2 \pr(\LENS) \notag \\
+              & -\pr(\NOT) \log_2 \pr(\NOT) \notag \\
+              & -\pr(\LENS|C) \log_2 \pr(\LENS|C) \notag \\
+              & -\pr(\NOT|C) \log_2 \pr(\NOT|C),
+\end{align}
+where, as above, $C$ can take the values $\saidLENS$ or $\saidNOT$. 
+($H$ is the Shannon [cross] entropy function.) 
+Substituting for the posterior probabilities using \Eref{eq:app:first} we get
+an expression that just depends on the elements of the 
+confusion matrix $\CM$ and the pre-classification subject lens
+probability $\pr(\LENS) = p$:
+\begin{align}
+\information =    & -    p \log_2 p - (1-p) \log_2 (1-p) \notag \\
+                  & - \log_2 \left[ \CM_{CL} p + \CM_{CN} (1-p) \right] \notag \\
+                  & + \frac{1}{p \CM_{CL} + (1-p) \CM_{CN}} \notag \\ 
+     \cdot [  p   & \CM_{CL} \left(\log_2 \CM_{CL} + \log_2 p\right) \notag \\
+         + (1-p)  & \CM_{CN} \left(\log_2 \CM_{CN} + \log_2 (1-p)\right) ].
+  \label{eq:app:infogain}
+\end{align}
+This expression has many interesting features.  If $p$ is either zero or
+one, $\information(C) = 0$  regardless of the value of $C$ or the values
+of the confusion matrix elements: if we know the subject's status with
+certainty, additional classifications supply no new information. If we
+set $p$ to be the prior probability, \Eref{eq:app:infogain} tells us how
+much information is generated by classifying it all the way to $p = 1$
+(which a perfect classifier, with $\CM_{LL} = \CM_{NN} = 1$, can do in
+a single classification). For a prior probability of $2\times 10^{-4}$, 
+12.3 bits are generated in such a ``detection.'' 
+Conversely, only 0.0003 bits
+are generated during the rejection of a subject with the same prior: we
+are already fairly sure that each subject does not contain a lens!
+Imperfect classifiers (with $\CM_{LL}$ and $\CM_{NN}$ less than 1)
+generate less than these maximum amounts of information each
+classification; the only classifiers that generate zero information are
+those that have $\CM_{LL} = 1 - \CM_{NN}$. We might label such
+classifiers as ``random'', since they are as likely to classify a
+subject as a $\saidLENS$ no matter the true content of that subject.
+
+\Eref{eq:app:infogain} suggests a useful information theoretical 
+definition of the classifier skill  perceived by the agent. At a fixed
+value of $p$, we can take the expectation value of the information gain
+$\information$ over  the possible classifications that could be made:
+\begin{align}
+\langle\information\rangle   =& H(T) - \sum_C H(T;C) \pr(C) \notag \\ 
+         &   =     p  \left[ \mathcal{S}(\CM_{LL}) + \mathcal{S}(1-\CM_{LL}) \right] \notag \\
+         &     +(1-p) \left[ \mathcal{S}(\CM_{NN}) + \mathcal{S}(1-\CM_{NN}) \right] \notag \\
+         & - \mathcal{S}\left[ p    \CM_{LL}       + (1-p)(1-\CM_{NN})     \right] \notag \\
+         & - \mathcal{S}\left[ p (1-\CM_{LL})      + (1-p)   \CM_{NN}      \right] 
+\end{align}
+where the function $\mathcal{S}(x) = x \log_2(x)$. If we choose to
+evaluate $\langle\information\rangle$ at $p = 0.5$, the result has some
+useful properties. While random classifiers presented with  $p = 0.5$
+subjects have $\skill = 0.0$  as expected, perfect classifiers appear to
+the agents to have  $\skill = 1.0$. This suggests that  $\skill$, the
+amount of information we expect to  gain when a classifier is presented
+with a 50-50 subject, is a reasonable quantification of 
+\emph{normalised skill}. A consequence of this choice is that the
+integrated skill (over all agents' histories) should come out to be
+equal to the number of subjects in the survey, when the search is
+``complete'' (and all subjects are fully classified). Therefore, a
+particular agent's integrated skill is a measure of that classifier's
+\emph{contribution} to the lens search.
+
+We conservatively initialize both elements of each  agent's confusion
+matrix to be 0.5, that of a maximally ambivalent  random classifier, so
+that all agents start with zero skill. While  this makes no allowance
+for volunteers that actually do have previous experience of what
+gravitational lenses look like, we might expect it to help mitigate
+against false positives. Anyone who classifies more than one image (by
+progressing beyond the tutorial) makes a non-zero information
+contribution to the project.
+
 \subsection{Uncertainty in the Agent Confusion Matrices}
@@
 
-The confusion matrix obtained from the application of Equation
-(\ref{eq:app:fraction}) has some inherent noise which reduces as the number of
-training subjects classified by the agent's volunteer increases. For
-simplicity, the discussion thus far assumed the case when the confusion matrix
-is known perfectly; in practice, we allow for uncertainty in the agent
-confusion matrices by averaging over a small number of samples drawn from
-Binomial distributions characterised by the matrix elements
-$\pr(C_k|\LENS,T_k)$ and  $\pr(C_k|\NOT,T_k)$. The associated standard
-deviation in the estimated subject probability provides an error bar for this
-quantity.
+Finally, the confusion matrix obtained from the application of
+\Eref{eq:app:fraction} has some inherent noise which reduces as the
+number of training subjects classified by the agent's volunteer
+increases. For simplicity, the discussion has thus far assumed the case
+when the confusion matrix is known perfectly; in practice, we allow for
+uncertainty in the agent confusion matrices by averaging over a small
+number of samples drawn from Binomial distributions characterised by the
+matrix elements $\pr(C_k|\LENS,T_k)$ and  $\pr(C_k|\NOT,T_k)$. The
+associated standard deviation in the estimated subject probability
+provides an error bar for this quantity.
 

### 2014-06-26 doc/sw-system.tex
Fixed typo in A11

@@
               & -\pr(\NOT) \log_2 \pr(\NOT) \notag \\
-              & -\pr(\LENS|C) \log_2 \pr(\LENS|C) \notag \\
-              & -\pr(\NOT|C) \log_2 \pr(\NOT|C),
+              & +\pr(\LENS|C) \log_2 \pr(\LENS|C) \notag \\
+              & +\pr(\NOT|C) \log_2 \pr(\NOT|C),
 \end{align}
@@
 \information =    & -    p \log_2 p - (1-p) \log_2 (1-p) \notag \\
-                  & - \log_2 \left[ \CM_{CL} p + \CM_{CN} (1-p) \right] \notag \\
+                  & - \log_2 \left[ p \CM_{CL} + (1-p) \CM_{CN} \right] \notag \\
                   & + \frac{1}{p \CM_{CL} + (1-p) \CM_{CN}} \notag \\ 
@@
 integrated skill (over all agents' histories) should come out to be
+approximately 
 equal to the number of subjects in the survey, when the search is
 ``complete'' (and all subjects are fully classified). Therefore, a
-particular agent's integrated skill is a measure of that classifier's
+particular agent's integrated skill is a reasonable 
+measure of that classifier's
 \emph{contribution} to the lens search.

### 2014-06-26 analysis/swap/shannon.py

@@ -57,7 +57,7 @@ LICENCE
 from numpy import log2, ndarray
 
 # ----------------------------------------------------------------------------
-# The Shannon information, I
+# The Shannon entropy, S
 
 def shannon(x):
     if isinstance(x, ndarray) == False:
@@ -75,6 +75,7 @@ def shannon(x):
 # possible classifications:
 
 def expectedInformationGain(p0, M_ll, M_nn):
+
     p1 = 1-p0
 
     I = p0 * (shannon(M_ll) + shannon(1-M_ll)) + \
@@ -90,6 +91,7 @@ def expectedInformationGain(p0, M_ll, M_nn):
 # as being 'c' (true/false):
 
 def informationGain(p0, M_ll, M_nn, c):
+
     p1 = 1-p0
 
     if c:

### 2014-06-30 analysis/swap/shannon.py
shannon.py updated to include functions defined by Anu and Surhud, latex updated to reflect correct information gain )relative entropy)

@@ -75,6 +75,28 @@ def shannon(x):
     return res
 
 # ----------------------------------------------------------------------------
+# The Shannon entropy, S
+
+def shannonEntropy(x):
+
+    if isinstance(x, np.ndarray) == False:
+
+        if x>0 and (1.-x)>0:
+            res = -x*np.log2(x) - (1.-x)*np.log2(1.-x)
+        else:
+            res = 0.0
+    
+    else:
+    
+        x[x == 0] = 1.0
+        res = -x*np.log2(x)
+
+        x[x == 1] = 0.0
+        res = res - (1.-x)*np.log2(1.-x)
+       
+    return res
+
+# ----------------------------------------------------------------------------
 # Expectation value of the information that would be contributed by an 
 # agent defined by confusion matrix M when presented with a subject
 # having probability p0, over both possible truths and both 
@@ -92,9 +114,9 @@ def expectedInformationGain(p0, M_ll, M_nn):
     return I
 
 # ----------------------------------------------------------------------------
-# The information contributed by an agent, defined by confusion matrix M,
-# having classified a subject, that arrived having probability 'p0', 
-# as being 'c' (true/false):
+# The information gain (relative entropy) contributed by an agent, defined by 
+# confusion matrix M, having classified a subject, that arrived having 
+# probability 'p0', as being 'c' (lens/not = true/false):
 
 def informationGain(p0, M_ll, M_nn, lens):
 
@@ -113,6 +135,46 @@ def informationGain(p0, M_ll, M_nn, lens):
     p1_c = M_cn/pc
 
     I = p0*shannon(p0_c) + p1*shannon(p1_c)
+
+    return I
+
+# ----------------------------------------------------------------------------
+# Bayesian update of the probability of a subject by an agent whose
+# confusion matrix is defined by M
+
+def update(p0,M_ll,M_nn,lens):
+
+    if(lens):
+        M_cl = M_ll
+        M_cn = 1.0 - M_nn
+    else:
+        M_cl = 1.0 - M_ll
+        M_cn = M_nn
+    
+    return p0*M_cl/(p0*M_cl+(1.0-p0)*M_cn)
+    
+# PJM: I re-factored this so that the update eqn was in terms of 
+#      M_cl and M_cn (to match my notes). 
+
+# ----------------------------------------------------------------------------
+# The change in subject entropy transmitted by an agent, having classified a 
[…]

### 2014-06-30 analysis/swap/shannonnew.py

@@ -13,8 +13,11 @@ COMMENTS
 
 METHODS
     shannonEntropy(x)
-    informationGain(p0, p1)
+    entropyChange(p0, M_ll, M_nn, c)
+    mutualInformation(p0, p1)
+    informationGain(p0, M_ll, M_nn, c)
     expectedInformationGain(p0, M_ll, M_nn)
+    update(p0,M_ll,M_nn,c)
 
 BUGS
 
@@ -96,10 +99,11 @@ def shannonEntropy(x):
     return res
 
 # ----------------------------------------------------------------------------
-# The information contributed by an agent having classified a subject, that
-# arrived having probability 'p0' and has new probability 'p1'
+# The change in subject entropy transmitted by an agent, having classified a 
+# subject, that arrived having probability 'p0' and has new 
+# probability 'p1'
 
-def informationGain(p0, M_ll, M_nn, c):
+def entropyChange(p0, M_ll, M_nn, c):
 
     p1 = update(p0,M_ll,M_nn,c)
 
@@ -144,6 +148,31 @@ def expectedInformationGain(p0, M_ll, M_nn):
         + p1 * (shannon(M_nn) + shannon(1-M_nn)) \
         - shannon(M_ll*p0 + (1-M_nn)*p1) \
         - shannon((1-M_ll)*p0 + M_nn*p1)
+
+    return I
+
+# ----------------------------------------------------------------------------
+# The information (relative entropy) contributed by an agent, defined by 
+# confusion matrix M, having classified a subject, that arrived having 
+# probability 'p0', as being 'c' (true/false):
+
+def informationGain(p0, M_ll, M_nn, lens):
+
+    p1 = 1-p0
+
+    if lens:
+        M_cl = M_ll
+        M_cn = 1-M_nn
+    else:
+        M_cl = 1-M_ll
+        M_cn = M_nn
+
+    pc = M_cl*p0 + M_cn*p1
+
+    p0_c = M_cl/pc
+    p1_c = M_cn/pc
+
+    I = p0*shannon(p0_c) + p1*shannon(p1_c)
 
     return I
 

### 2014-06-30 analysis/swap/__init__.py
shannon.py updated to include functions defined by Anu and Surhud, latex updated to reflect correct information gain )relative entropy)

@@ -7,5 +7,4 @@ from collection import *
 from subject import *
 from toydb import *
 from mongodb import *
-#from shannon import *
-from shannonnew import *
+from shannon import *

### 2014-06-30 analysis/swap/shannonnew.py

@@ -1,307 +1,0 @@
-#============================================================================
-"""
-NAME
-    shannon.py
-
-PURPOSE
-    Methods for calculating various information gains during binary 
-    classification.
-
-COMMENTS
-	A different approach to calculating the information gain based on
-    discussions between Anupreeta and Surhud
-
-METHODS
-    shannonEntropy(x)
-    entropyChange(p0, M_ll, M_nn, c)
-    mutualInformation(p0, p1)
-    informationGain(p0, M_ll, M_nn, c)
-    expectedInformationGain(p0, M_ll, M_nn)
-    update(p0,M_ll,M_nn,c)
-
-BUGS
-
-AUTHORS
-  The code in this file was written by Surhud More and Anupreeta More
-  at home in June 2014.
-  This file is part of the Space Warps project, which is distributed 
-  under the GPL v2 by the Space Warps Science Team.
-  http://spacewarps.org/
-
-HISTORY
-  2014-06-20  First version
-  
-LICENCE
-  The MIT License (MIT)
-
-  Copyright (c) 2014 Kavli IPMU
-
-  Permission is hereby granted, free of charge, to any person obtaining a copy
-  of this software and associated documentation files (the "Software"), to deal
-  in the Software without restriction, including without limitation the rights
-  to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
-  copies of the Software, and to permit persons to whom the Software is
-  furnished to do so, subject to the following conditions:
-
-  The above copyright notice and this permission notice shall be included in all
-  copies or substantial portions of the Software.
-
-  THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
-  IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
-  FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
-  AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
[…]

### 2014-07-01 analysis/swap/mongodb.py
fixed empty annotations

@@ -246,8 +246,9 @@ class MongoDB(object):
         for annotation in annotations:
             if annotation.has_key('x'): 
                 N_markers += 1
-                annotation_x.append(float(annotation['x']))
-                annotation_y.append(float(annotation['y']))
+                if len(annotation['x']) > 0:
+                    annotation_x.append(float(annotation['x']))
+                    annotation_y.append(float(annotation['y']))
 
         
         # Detect whether sim was found or not:

### 2014-07-01 doc/sw-system.tex

@@
 Each agent assumes that the probability of a volunteer recognising any given
-simulated lens as a lens is some number, $\pr(\saidLENS|\LENS,T)$, that
+simulated lens as a lens is some number, $\pr(\saidLENS|\LENS,\training)$, that
 depends only on what the volunteer is currently looking at, and all the
@@
 probability of a volunteer recognising any given dud image as a dud is some
-other number, $\pr(\saidNOT|\NOT,T)$, that also depends only on what the volunteer is currently looking at, and all the
+other number, $\pr(\saidNOT|\NOT,\training)$, that also depends only on what the volunteer is currently looking at, and all the
 previous training subjects they have seen. These two probabilities define a 
@@
 \be
-  \pr(``X"|X,T) \approx \frac{N_{``X"}}{N_X}.
+  \pr(``X"|X,\training) \approx \frac{N_{``X"}}{N_X}.
   \label{eq:app:fraction}
@@
 times the volunteer got their classifications of this type of training subject
-right. $T$ stands for all
+right. $\training$ stands for all
 $N_{\LENS} + N_{\NOT}$ training data that the agent has heard about to
@@
   \begin{bmatrix}
-    \pr(\saidLENS|\NOT,T_k) & \pr(\saidLENS|\LENS,T_k) \\
-    \pr(\saidNOT |\NOT,T_k) & \pr(\saidNOT |\LENS,T_k)
+    \pr(\saidLENS|\NOT,\trainingk) & \pr(\saidLENS|\LENS,\trainingk) \\
+    \pr(\saidNOT |\NOT,\trainingk) & \pr(\saidNOT |\LENS,\trainingk)
   \end{bmatrix}, \notag \\
@@
   \label{eq:app:first}
-  & \pr(\LENS|C_k,T_k) = \\
-  & \frac{\pr(C_k|\LENS,T_k)\cdot\pr(\LENS)}
-{\left[ \pr(C_k|\LENS,T_k)\cdot\pr(\LENS) + \pr(C_k|\NOT,T_k)\cdot\pr(\NOT) \right]},
+  & \pr(\LENS|C_k,\trainingk) = \\
+  & \frac{\pr(C_k|\LENS,\trainingk)\cdot\pr(\LENS)}
+{\left[ \pr(C_k|\LENS,\trainingk)\cdot\pr(\LENS) + \pr(C_k|\NOT,\trainingk)\cdot\pr(\NOT) \right]},
   \notag
@@
 \begin{align}
-  \pr(\LENS|\saidLENS,T_k) &= \frac{1.0 \cdot p_0}
+  \pr(\LENS|\saidLENS,\trainingk) &= \frac{1.0 \cdot p_0}
            {\left[ 1.0\cdot p_0 + 0.0\cdot(1 - p_0) \right]}
@@
   \label{eq:app:update}
-  \pr(\LENS & |C_{k+1},T_{k+1},\data) = \\
-  & \frac{1}{Z} \pr(C_{k+1}|\LENS,T_{k+1}) \cdot \pr(\LENS|\data) \\ \notag
-{\rm where}\;\; Z = & \pr(C_{k+1}|\LENS,T_{k+1})\cdot\pr(\LENS|\data) \\ \notag
-      & + \pr(C_{k+1}|\NOT,T_{k+1})\cdot\pr(\NOT|\data), \notag
+  \pr(\LENS & |C_{k+1},\training_{k+1},\data) = \\
+  & \frac{1}{Z} \pr(C_{k+1}|\LENS,\training_{k+1}) \cdot \pr(\LENS|\data) \\ \notag
+{\rm where}\;\; Z = & \pr(C_{k+1}|\LENS,\training_{k+1})\cdot\pr(\LENS|\data) \\ \notag
+      & + \pr(C_{k+1}|\NOT,\training_{k+1})\cdot\pr(\NOT|\data), \notag
 \end{align}
-and $\data = \{C_k,T_k\}$ is the set of all previous
+and $\data = \{C_k,\trainingk\}$ is the set of all previous
 classifications, and the set of training subjects seen by each of those
@@
 
-\subsection{Agent ``Skill'' and ``Contribution''}
+\subsection{Information Gain per Classification, Agent ``Skill'' and ``Contribution''}
 \label{appendix:swap:examples}
-
-% The information likely to be contributed by each agent for a given subject
-% can be estimated before the next classification of that subject is made, 
-% just from its confusion matrix.
-% The Shannon entropy generated by a classifier upon performing a
-% classification is
-% \be
-%   \langle S_k \rangle =  
-%    -P_{\rm right}\cdot\log_2{P_{\rm right}} -  P_{\rm wrong}\cdot\log_2P_{\rm wrong}\,,
-% \ee
-% where $P_{\rm right}$ and $P_{\rm wrong}$ are the averages of the diagonal and
-% the off-diagonal elements of the confusion matrix, respectively, and $\langle
-% S_k \rangle$ is measured in ``bits.'' These averages represent the probability
-% of a classifier to get a classification right or wrong, respectively. We define
-% the information contributed by a classifier as
-% \begin{equation}
-% I_k = 1 - S_k\,.
-%   \label{eq:app:info}
-% \end{equation}
-% \Eref{eq:app:info} gives the required result, that both the hypothetical {\it
-% perfect} and {\it obtuse} classifiers contribute 1 bit of information each, per
-% classification. Classifiers whose agent's confusion matrix is such that $P_{\rm
-% right}=P_{\rm wrong}=0.5$, contribute zero bits of information. Such users
-% identify a lens correctly with the same probability as they misclassify a dud
-% image to contain a lens, and thus their classification is of no value.
 
@@
 the probability of the subject being classified containing a lens. The
-quantity of interest is the mutual information between the prior and
-posterior probabilities given the submitted classification $C$:
+quantity of interest is the relative entropy, or Kullback-Leiber
+divergence, between the prior and
+posterior probabilities for the possible truths $T$
+given the submitted classification $C$:
 \begin{align}
-\information =& H(T) - H(T;C) \notag \\ 
-             =& -\pr(\LENS) \log_2 \pr(\LENS) \notag \\
-              & -\pr(\NOT) \log_2 \pr(\NOT) \notag \\
-              & +\pr(\LENS|C) \log_2 \pr(\LENS|C) \notag \\
-              & +\pr(\NOT|C) \log_2 \pr(\NOT|C),
+\information =& \sum_T \pr(T|C) \log_2 \frac{\pr(T|C)}{\pr(T)}     \notag \\
+             =&    \pr(\LENS|C) \log_2 \frac{\pr(C|\LENS)}{\pr(C)} \notag \\
+             +&    \pr(\NOT|C)  \log_2 \frac{\pr(C|\NOT)}{\pr(C)},
 \end{align}
 where, as above, $C$ can take the values $\saidLENS$ or $\saidNOT$. 
-($H$ is the Shannon [cross] entropy function.) 
 Substituting for the posterior probabilities using \Eref{eq:app:first} we get
@@
 \begin{align}
-\information =    & -    p \log_2 p - (1-p) \log_2 (1-p) \notag \\
-                  & - \log_2 \left[ p \CM_{CL} + (1-p) \CM_{CN} \right] \notag \\
-                  & + \frac{1}{p \CM_{CL} + (1-p) \CM_{CN}} \notag \\ 
-     \cdot [  p   & \CM_{CL} \left(\log_2 \CM_{CL} + \log_2 p\right) \notag \\
-         + (1-p)  & \CM_{CN} \left(\log_2 \CM_{CN} + \log_2 (1-p)\right) ].
+\information =    &     p \frac{\CM_{CL}}{p_c} \log_2 \frac{\CM_{CL}}{p_c}  \notag \\
+                  & +(1-p)\frac{\CM_{CN}}{p_c} \log_2 \frac{\CM_{CN}}{p_c},
   \label{eq:app:infogain}
 \end{align}
-This expression has many interesting features.  If $p$ is either zero or
-one, $\information(C) = 0$  regardless of the value of $C$ or the values
-of the confusion matrix elements: if we know the subject's status with
+where the common denominator $p_c = p\CM_{CL} + (1-p)\CM_{CN}$. This
+expression has many interesting features.  If $p$ is either zero or one,
+$\information(C) = 0$  regardless of the value of $C$ or the values of
+the confusion matrix elements: if we know the subject's status with
 certainty, additional classifications supply no new information. If we
@@
 much information is generated by classifying it all the way to $p = 1$
-(which a perfect classifier, with $\CM_{LL} = \CM_{NN} = 1$, can do in
-a single classification). For a prior probability of $2\times 10^{-4}$, 
-12.3 bits are generated in such a ``detection.'' 
-Conversely, only 0.0003 bits
-are generated during the rejection of a subject with the same prior: we
-are already fairly sure that each subject does not contain a lens!
-Imperfect classifiers (with $\CM_{LL}$ and $\CM_{NN}$ less than 1)
-generate less than these maximum amounts of information each
-classification; the only classifiers that generate zero information are
-those that have $\CM_{LL} = 1 - \CM_{NN}$. We might label such
-classifiers as ``random'', since they are as likely to classify a
-subject as a $\saidLENS$ no matter the true content of that subject.
+(which a perfect classifier, with $\CM_{LL} = \CM_{NN} = 1$, can do in a
+single classification). For a prior probability of $2\times 10^{-4}$, 
+12.3 bits are generated in such a ``detection.''  Conversely, only
+0.0003 bits are generated during the rejection of a subject with the
+same prior: we are already fairly sure that each subject does not
+contain a lens! Imperfect classifiers (with $\CM_{LL}$ and $\CM_{NN}$
+both less than 1)  generate less than these maximum amounts of
+information each classification; the only classifiers that generate zero
+information are those that have $\CM_{LL} = 1 - \CM_{NN}$ (or
+equivalently, $\CM_{CL} = \CM_{CN}$ for all values of $C$). We might
+label such classifiers as ``random'', since they are as likely to
+classify a subject as a $\saidLENS$ no matter the true content of that
+subject.
 
@@
 \begin{align}
-\langle\information\rangle   =& H(T) - \sum_C H(T;C) \pr(C) \notag \\ 
-         &   =     p  \left[ \mathcal{S}(\CM_{LL}) + \mathcal{S}(1-\CM_{LL}) \right] \notag \\
+\langle\information\rangle   =& \sum_C \sum_T \pr(T|C) \pr(C) \log_2 \frac{\pr(T|C)}{\pr(T)} \notag \\ 
+         =& - \sum_T \pr(T) \log_2 \pr(T) \notag \\ 
+          & + \sum_C \pr(C) \sum_T \pr(T|C) \log_2 \pr(T|C) \notag \\ 
+         =&         p  \left[ \mathcal{S}(\CM_{LL}) + \mathcal{S}(1-\CM_{LL}) \right] \notag \\
           &     +(1-p) \left[ \mathcal{S}(\CM_{NN}) + \mathcal{S}(1-\CM_{NN}) \right] \notag \\
@@
 \end{align}
-where the function $\mathcal{S}(x) = x \log_2(x)$. If we choose to
+where $\mathcal{S}(x) = x \log_2{x}$. If we choose to
 evaluate $\langle\information\rangle$ at $p = 0.5$, the result has some
@@
 number of samples drawn from Binomial distributions characterised by the
-matrix elements $\pr(C_k|\LENS,T_k)$ and  $\pr(C_k|\NOT,T_k)$. The
+matrix elements $\pr(C_k|\LENS,\trainingk)$ and  $\pr(C_k|\NOT,\trainingk)$. The
 associated standard deviation in the estimated subject probability

### 2014-07-02 analysis/make_roc_curves.py
made make_roc_curves.py

@@ -1,0 +1,346 @@
+#!/usr/bin/env python
+# ======================================================================
+
+import sys,getopt,numpy as np
+from sklearn.metrics import roc_curve
+
+import matplotlib
+# Force matplotlib to not use any Xwindows backend:
+matplotlib.use('Agg')
+
+# Fonts, latex:
+matplotlib.rc('font',**{'family':'serif', 'serif':['TimesNewRoman']})
+matplotlib.rc('text', usetex=True)
+
+from matplotlib import pyplot as plt
+
+bfs,sfs = 20,16
+params = { 'axes.labelsize': bfs,
+            'text.fontsize': bfs,
+          'legend.fontsize': bfs,
+          'xtick.labelsize': sfs,
+          'ytick.labelsize': sfs}
+plt.rcParams.update(params)
+
+import swap
+
+# ======================================================================
+
+def make_roc_curves(argv):
+    """
+    NAME
+        make_roc_curves
+
+    PURPOSE
+        Given the stage1 and stage2 bureau and collection pickles, this script
+        produces the one roc plot that will be put someplace in the SW system
+        paper. You can also do an Expectation Maximization for offline
+        processing.
+
+    COMMENTS
+        For the offline assessments, see em.pdf in the docs directory.
+
+    FLAGS
+        -h                Print this message
+        -o                Do the offline EM processing
+
+    INPUTS
+        --offline 0/1
+        stage1_bureau.pickle
+        stage2_bureau.pickle
+        stage1_collection.pickle
+        stage2_collection.pickle
+
+    OUTPUTS
+        an roc png plot
+
+    EXAMPLE
+
+    BUGS
+        - Code is not tested yet...
+
+    AUTHORS
+        This file is part of the Space Warps project, and is distributed
+        under the GPL v2 by the Space Warps Science Team.
+        http://spacewarps.org/
+
+    HISTORY
+      2013-07-01  started Davis (KIPAC)
+    """
+
+    # ------------------------------------------------------------------
+
+    try:
+       opts, args = getopt.getopt(argv,"ho",["help","offline"])
+    except getopt.GetoptError, err:
+       print str(err) # will print something like "option -a not recognized"
+       print make_roc_curves.__doc__  # will print the big comment above.
+       return
+
+    offline = 0
+    resurrect = False
+
+    for o,a in opts:
+       if o in ("-h", "--help"):
+          print make_roc_curves.__doc__
+          return
+       elif o in ("-o", "--offline"):
[…]

### 2014-07-29 doc/sw-system.tex
Added ROC curve

@@
 
-\subsection{Sample completeness and purity}
+\subsection{Sample Properties}
 \label{sec:results:sample}
 
-Rejection rate. Completeness and purity at P > retirement, P > 95\%, and 
-as function of probability P. Compare stage 1 and stage 2.
-
-Summarize performance at some fiducial threshold: eg P = 95\%.
+We now quantify the performance of the \sw system in terms of the recovery of
+the training set images. \Fref{fig:results:sample:roc} shows receiver
+operating characteristic (ROC) curves for CFHTLS stage 1 and stage 2.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/roc.png}
+\caption{Receiver operating characteristic curves for the \sw system, using
+the CFHTLS training set.}
+\label{fig:results:sample:roc}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%  ACKNOWLEDGMENTS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2014-08-04 analysis/make_lens_atlas.py
small updates

@@ -1,6 +1,9 @@
 #!/usr/bin/env python
 # ======================================================================
 
+# TODO: when pulling points for zoomed, do the clustering as in catalog (should
+# be deterministic) so you can filter that way
+
 import sys, getopt, numpy as np
 
 import matplotlib
@@ -215,6 +218,7 @@ def make_lens_atlas(args):
              'output_directory': './',
              'output_format': 'png',
              'stamp_size': 50,
+             'dist_max': 30,
              'stamp_min': 10,
              'smooth_click': 3,
              'figsize_stamp': 5,
@@ -307,6 +311,7 @@ def make_lens_atlas(args):
         print "make_lens_atlas: running stamps"
         for lens_i in range(len(catalog)):
             ID = catalog[lens_i][0]
+            kind = catalog[lens_i][1]
             x = catalog[lens_i][2]
             y = catalog[lens_i][3]
             N0 = catalog[lens_i][5]
@@ -326,6 +331,10 @@ def make_lens_atlas(args):
             min_y = np.int(np.max((y - flags['stamp_size'], 0)))
             max_y = np.int(np.min((y + flags['stamp_size'], im.shape[1])))
 
+            min_member_x = np.int(np.max((x - flags['dist_max'], 0)))
+            max_member_x = np.int(np.min((x + flags['dist_max'], im.shape[0])))
+            min_member_y = np.int(np.max((y - flags['dist_max'], 0)))
+            max_member_y = np.int(np.min((y + flags['dist_max'], im.shape[1])))
             if (min_x >= max_x) + (min_y >= max_y):
                 print "make_lens_atlas: misshapen lens for ID ", ID
                 continue
@@ -338,7 +347,19 @@ def make_lens_atlas(args):
                 alpha = None
                 im = im[min_y: max_y, min_x: max_x]
 
-            if (flags['contour']) + (flags['heatmap']):
+            fig = plt.figure(figsize=figsize_stamp)
+            ax = fig.add_subplot(111)
+            ax.imshow(im)
+
+            ax.scatter(x - min_x,
+                       y - min_y,
+                       marker='d',
+                       c=(0, 1.0, 0), s=100,
+                       alpha=0.75)
+
+            if ((flags['contour'])
+                + (flags['heatmap'])
+                + (flags['points'] != 0)):
 
                 itwas = annotationhistory['ItWas']
                 x_all = annotationhistory['At_X']
@@ -348,18 +369,21 @@ def make_lens_atlas(args):
[…]

### 2014-08-04 doc/sw-cfhtls.tex

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %
-% Space Warps CFHTLS Results Paper
+% Space Warps II: CFHTLS 
 %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \usepackage{amsmath}
+\usepackage{longtable}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\title[\sw]
-{\SW: New Lens Candidates from the CFHT Legacy Survey}
+\title[\sw II]
+{\SW: II. Did we beat the lens finding robots in CFHTLS?}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \date{to be submitted to MNRAS}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2014}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2013}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \begin{abstract} 
-
-We present X new strong gravitational lens candidates found in the CFHT Legacy
+We present X new strong gravitational lens candidates found in the CFHT
+Legacy
 survey by the \sw collaboration.
@@
 
-In this paper, we ... try to answer the following questions:
+{\it Describe various lens finding algorithms and the motivation for this
+particular project with \cfhtls. Already searched by robots: enables comparison of techniques. Lenses not
+yet found by robots, detectable by humans? }
 
-\begin{itemize}
+In Paper I, we describe the \sw website, an online system that enables
+crowd-sourced detection of gravitational lenses. In this paper, we
+describe our first lens search with \sw in the \cfhtls data which we
+refer to as Paper II.
 
-\item ...
-
-\item ...
-
-\item ...
-
-\end{itemize}
-
-This paper is organised as follows. In \Sref{sec:sw} we give a brief overview
-of the \sw system, focusing on the aspects most relevant to the interpretation
-of the results of this first lens search. In \Sref{sec:data} we introduce the
-CFHTLS imaging data. ... We discuss the implications of our results for future
-lens searches in \Sref{sec:discuss} and draw conclusions in
-\Sref{sec:conclude}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{\sw Overview}
-\label{sec:sw}
+This paper is organised as follows. In \Sref{sec:sw} we give a brief
+overview of the \sw system, focusing on the aspects most relevant to the
+interpretation of the results of this first lens search. In
+\Sref{sec:data} we introduce the \cfhtls imaging data and the known lens
+samples from the \cfhtls. In \Sref{sec:}, we explain the training sample
+generated to aid the \sw users in the lens search. In
+\Sref{sec:results}, we present the new lens candidates and our findings.
+We discuss the implications of our results for future lens searches in
+\Sref{sec:discuss} and draw conclusions in \Sref{sec:conclude}.
 
@@
 \label{sec:data}
+\subsection{The CFHT Legacy Survey}
+\label{sec:data:cfhtls}
 
-Definitions: training subjects and test subjects. Sims and duds.
+The Canada-France-Hawaii Telescope Legacy Survey (CFHTLS) is a
+photometric survey in five optical bands ($u^*g'r'i'z'$) carried out
+with the wide-field imager MegaPrime which has a 1~deg$^2$ field-of-view
+and a pixel size of 0.186\arcsec. The \cfhtls WIDE covers a total area
+of 171~deg$^2$ on the sky and it consists of four fields W1, W2, W3 and
+W4. The field W1 has the largest sky coverage of 63.65~deg$^2$. The
+fields W2 and W4 have similar sky coverages of 20.32~deg$^2$ and
+20.02~deg$^2$, respectively\footnote{These numbers are estimated from http://terapix.iap.fr/cplt/table\_syn\_T0006.html}.
+The field W3 has a sky coverage of 42.87~deg$^2$ and is more than twice
+as large as W2 and W4.
+
+The \cfhtls imaging is very homogeneous and has great image quality. Most of
+the lensed arcs are much brighter in the $g$ band thus, deep imaging in
+this band is desirable. The limiting magnitude is 25.47 for the $g$ band
+which goes the deepest among all of the five bands. The mean seeing in
+the $g$ band is 0.78\arcsec. The zero point to convert flux to AB
+magnitude for all bands is 30. These characteristics make \cfhtls ideal
+to do visual inspection for finding lenses.  We use the data from the
+final T0007 release taken from the Terapix
+website\footnote{{http://terapix.iap.fr/cplt/T0006-doc.pdf}}
+for this work.
+
+We note that the \cfhtls is a niche survey with a unique combination of
+wide imaging with deep sensitivity. It is a precursor to the ongoing
+wide imaging surveys such as the DES, KIDS and HSC and planned surveys
+such as the LSST. Searching for lenses with \sw in the \cfhtls will
+teach us important lessons and help prepare us for these larger imaging
+surveys.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Known \cfhtls lens samples}
+\label{sec:data:kls}
+
+The \cfhtls data has been searched for lenses using semi-automated
+algorithms, primarily, in the $g$ band which is optimal for finding
+lenses. Here, we briefly mention the lens samples which were known to
+the authors prior to the lens search with \sw.
+The work
+by \citet{Gavazzi2013} looks for bluish features around bright XXX
+galaxies and has found XXX lens candidates at galaxy-scales.  The arc
+finding lens search \citet{More2012} has found 127 lens candidates by
+looking for arcs in $g$ band alone. This sample has both galaxy and
+groups scale lens candidates. The \citet{Sygnet2009} is a search for
+edge-on disk lenses done by selecting the galaxy's profile from the
+Sextractor's output in the $i$~band and has 18 lens candidates.
+
+For the purpose of transparency, the volunteers participating in
+\sw-\cfhtls lens search were made aware of these known lens samples. Images
+containing the lenses from these lens samples were labelled so in the
+forum Talk where volunteers have the opportunity to discuss their
+findings with other volunteers and the science team. XXX some references
+to Paper I ?
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Image Presentation}
+\label{sec:data:impres}
+{\it Preparation of data: divide survey into overlapping tiles.
+
+Presentation of images. Uniform scales, to build intuition and avoid rescales
+due to bright objects. Arcsinh stretch, to bring out low SB features. 
+Approximately optimized, how? Examples of images.}
+
+We carry out a blind search over the \cfhtls fields where we, mainly, use
+the g-r-i color information to look for signs of lensing. We extract
+contiguous cutouts of size 81.84\arcsec\ (440 pixels). The neighbouring
+cutouts have an overlapping region of 10\arcsec (54 pixels). If a
+possible lens candidate is too close to the edge of a cutout, this
+overlap allows the inspector to get a clearer view of the same candidate
+in a neighbouring cutout. We note that since the images are shown
+randomly, a given inspector may not necessarily come across the
+neighbouring cutout unless the inspector classifies a lot of images.
+However, this is not a problem since we our user base is extremely large
+and we get multiple classifications of the same image.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Training sample: Simulated lenses}
+\label{sec:ts}
+
+{\it State the importance}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=1.0]{sw-cfhtls-figs/sim_cgq.pdf}
+\caption{ \label{fig:sim}
+Examples of the three types of simulated lenses.
+}
+\end{center}
+\end{figure*}
+
+\subsection{Methodology}
+\label{sec:simmethod}
+
+We create two main types of simulated lens sample a) galaxy-scale lenses and b)
+group or cluster-scale lenses. The galaxy-scale lenses are further divided into two
+types based on the nature of the background sources, namely, galaxies and
+quasars. Below, we describe how each type of the lens sample was generated.
+
+\subsubsection{Galaxy-scale lenses} 
+\label{sect:gallens}
+
+The $N_{\rm src}$ behind a lens is then calculated by doing the
+following integral,
+
+\be
+\label{eqn:nsrc}
+N_{\rm src} = N_{\rm src}(>L_s,z_s) \int_{z_l}^\infty \sigma_{\rm lens}(\sigma,z_l,z_s,q) D_s^2 (1+z_s)^2 \frac{\rm d\chi}{{\rm d}z_s}
+{\rm d}z_s 
+\ee
+
+\be
+\label{eqn:nlum}
+ N_{\rm src}(>L_s,z_s)= \int_{L_{min}}^\infty \Phi(L_s,z_s) {\rm d}L_s
+\ee
+
+where $\Phi(L_s,z_s)$ is the source luminosity function per unit comoving
+volume, $q$ is the projected axis ratio of the lens ellipticity, $\chi$ and
+$D_s$ are the comoving and angular diameter distances to the source,
+
+We use the elliptical galaxy (LRG) catalog from the \cfhtls XXX to select
+all the foreground galaxies (e.g. $z<1$) that are potential lenses for the
+simulated sample. We exclude all those galaxies whose positions match with the
+lensing galaxies from the known \cfhtls~SL2S lens samples \cite{More2012}
+within 2~arcsec (XXX check).
+
+First, we calculate the luminosity and velocity dispersion of each potential
+lensing galaxy using the CFHT Megacam $g$ and $r$ band magnitudes along with the
+photometric redshift ($z_l$) from the LRG catalog.  The Megacam magnitudes are
+converted to SDSS magnitudes\footnote{
+    http://www3.cadc-ccda.hia-iha.nrc-cnrc.gc.ca/megapipe/docs/filters.html} and
+are further k-corrected to redshift $z=0.1$ \citep{Frei1994}. We assume that the
+evolution of galaxy luminosities is similar to that determined by
+\citep{Faber2007}, that is, a decline of $1.5$ in the $m_{r*}$ from redshift $z=1$
+to $z=0$ (see Eq.~\ref{magstar}).
+
+\be
+\frac{L}{L_{*}}=10.0^{-0.4~(m_{r \rm SDSS}-m_{r*})} 
+\ee
+
+where $m_{r*}$ is
+\be
+\label{magstar}
+m_{r*}=-20.44+ 1.5~(z_{l}-0.1) \,.
+\ee
+
+We use the $L-\sigma$ relation from
+\citep{Parker2007} to get the velocity dispersion as given in Eq.~\ref{magstar2}.
+
+\be
+\label{magstar2}
+\sigma=142 \left(\frac{L}{L_{*}}\right)^{1/3} 
+\ee
+
+Next, in order to decide whether a galaxy is likely to act as a strong lens, we
+calculate the lens cross-section ($\sigma_{\rm lens}$) and the number of sources
+($N_{\rm src}$) that are in the background. Following \citep{Keeton2000a}, the lens
+cross-section is calculated analytically for an isothermal model and is given by
+
+\be
+\sigma_{\rm lens}=b_I^2 \, \int_0^{2\pi} 0.5 r^2(\theta) d\theta
+\ee
+
+where $b_I$ is 
+\be
+b_I = b_{\rm SIS} \epsilon_3/sin^{-1}(\epsilon_3) \,,
+\ee
+
+the eccentricity ($\epsilon_3$) is 
+\be
+\epsilon_3=(1-q_3^2)^{1/2}
+\ee
+
+and the projected axis ratio is given by
+\be
+q_k=\sqrt{q_3^2 {\rm sin}^2i_e+{\rm cos}^2i_e} \,.
+\ee
+
+In the above equations, $q_3$ is the 3d axis ratio of the ellipsoid and $i_e$ is
+the inclination angle. Also, $b_{\rm SIS}= 4\pi
+\frac{c^2}{\sigma^2}\frac{D_{s}}{D_{ls}D_l}$ and is referred to as the
+Einstein radius where $D_s$,$D_l$ and $D_{ls}$ are angular diameter distances to
+the source, the lens and between the lens and source, respectively.
+
+%Comparing \citep{keeton00a} with \citep{kormann94} suggests that $b_I = sqrt(q)*b_{SIS}$
+
+Next, if the foreground galaxy can act as a lens and has at least one source in the
+background, then we determine a redshift ($z_s$) and $i$-band magnitude of the
+background source(s). We assume two types of background sources namely, galaxies
+and quasars. For each source, the redshift and magnitude are generated by drawing randomly from
+the following redshift and luminosity distributions. For
+galaxies, we assume the redshift distribution is
+
+\be
+\label{eqn:ps}
+p_s=\frac{\beta z_s^2 {\rm exp}({\frac{z_s}{z_0(m_{\rm lim})}})^\beta}{\Gamma(3/\beta)z_0^3(m_{\rm lim})}
+\ee
+
+where $\beta=3/2$ and $z_0(m_{\rm lim})=0.13m_{\rm lim} - 2.2$ and the
+luminosity function is
+
+\be
+\label{eqn:ns}
+n_s=\int^{m_{\rm lim}}_{-\infty} \frac{n_0 {\rm d}m}{\sqrt{10^{2a(m_1-m)}+10^{2b(m_1-m)}}}
+\ee
+
+with parameters $a=0.30$, $b=0.56$, $m_1=20$ and $n_0=3\times10^3~deg^{-2}$ as
+given in \citep{Faure2009} and references therein. For quasars, we calculate
+the luminosity function by following the prescription of \citep{Ogur2010} and
+use k-corrections by \citep{Richards2006}.
+
+%alp=-0.5;
+%kcorr=-2.5*(1 + alp)*log10(1+zz);
+%Dlum=cc.Dlofz(zz)/p.hval;
+%DM=5*log10(Dlum);
+%Mabs=mag-kcorr-DM-25.0;
+The luminosity function is expressed as
+\be
+\frac{{\rm d}\Phi}{{\rm d}M}=\frac{\Phi_{*}}{10^{0.4(\alpha+1)(M_{\rm abs}-M_{*})} + 10^{0.4(\beta+1)(M_{\rm abs}-M_{*})} }
+\ee
+
+where the normalization, $\phi_{*}=5.34\times10^{-6} h^3$ Mpc$^{-3}$ and break
+magnitude, $M_*=-20.90 + 5 {\rm log} h - 2.5 {\rm log} f(z)$. The redshift
+dependent factor in $M_*$ is given by
+
+\be
+f(z)=\frac{e^{\zeta z_s}(1+e^{\xi z_*})}{(\sqrt{e^{\xi z_s}}+\sqrt{e^{\xi z_*}})^2} \,.
+\ee
+We adopt the best-fit values $\zeta=2.98$, $\xi=4.05$, $z_{*}=1.60$
+\citep{Oguri2010}. For the faint end slope, we use $\beta=-1.45$ whereas for
+the bright end slope, we use $\alpha=-3.31$ when $z_s<3$ and $\alpha=-2.58$ at
+higher redshifts, as prescribed by \citep{Oguri2010}. 
+respectively. We note that when calculating $N_{\rm src}$, the source
+number density is artificially boosted by a factor (see Table~\ref{tab:thresh})
+to increase the occurrence of simulated lenses. This helps in creating a large
+enough sample to carry out various performance tests.
+
+Next, we determine properties of the background source for every lens. We follow
+similar procedures for both background galaxies and quasars. For simplicity, we
+simulate a single background source behind every lens. In order to select one
+background source from the $N_{\rm src}$ per lens, we do ray-tracing for all of the
+$N_{\rm src}$ sources with {\sc gravlens} \citep{Keeton2000} and choose sources that
+satisfy criteria as given below. We determine fluxes of the lensed images
+and the total magnification of each of the lensed source. We draw a random
+source for which the flux of the second brightest lensed image and the total
+magnification of all lensed images are above the thresholds given in
+Table~\ref{tab:thresh}.
+
+Since we want to produce realistic looking lens systems, we simulate lenses in
+each of the five \cfhtls~filters. The colors of the background galaxies are drawn
+randomly from the photometric CFHTLenS catalog
+\citep{Hildebrandt2012,Erben2013}.  Similarly, we use a quasar catalog from the
+SDSS Data Release 9 \citep{Paris2012} from which colors are drawn to simulate
+quasar lenses. Next, we assume deVaucoleur's profile to account for the size
+and shape of the galaxies. The ellipticity and the position angle are drawn
+randomly between the range given in Table~\ref{tab:thresh}. The effective
+radius of the galaxy is estimated from the Luminosity$-$size relation
+\citep{Bernardi2003} given by 
+\be
+R_{\rm eff}= 10^{0.52} \frac{L_r^{2/3}}{{(1+z_s)}^2}
+\ee
+where $L_r=L_s/10^{10.2}$. On the other hand, quasars are assumed to follow a
+Gaussian profile where the $\sigma$ is equated to that of the median seeing for
+every filter. The median seeing values are taken from Table 4 of the official
+Terapix T0007 release explanatory document \footnote{
+    http://terapix.iap.fr/cplt/T0007/doc/T0007-doc.pdf}.
+
+Once all the parameters are determined for the lens and source models, {\sc
+gravlens} is used to simulate lensed images.  After accounting for the shot
+noise in the lensed images and convolving them with the median seeing in each of
+the filters, the simulated image is added to the real \cfhtls~image centered
+on the lensing galaxy. Note that we ensure that the lensed galaxies and
+lensed quasars do not have the same lensing galaxy in the foreground. Similarly,
+the lensing galaxies from the galaxy-scale lenses are distinct from the central
+galaxies of groups-scale lenses which are described in the following section.
+
+\subsubsection{Groups-scale lenses}
+
+At group or cluster-scales, the brightest group galaxy (BGG) at the center alone
+does not cause strong lensing. We need to account for the extra convergence
+arising from the dark matter component as well as satellite galaxies, at least,
+in the inner regions which are typically responsible for the multiple lensed
+images \citep{Oguri2005,Oguri2006}. Owing to the lack of an appropriate group
+catalog for our purposes, we create a basic group catalog based on the
+magnitudes and photometric redshifts available for the \cfhtls. We select all
+galaxies with 10$^{10.8} M_\odot$ as the BGGs. We select the member galaxies
+such that their photometric redshifts are within $\delta z = 0.01$ of the BGG
+and within an aperture of $250$~Kpc.
+
+We adopt an isothermal ellipsoid for the BGG and members whenever the
+ellipticities are available else we use an isothermal sphere. On the other hand, we
+adopt an NFW profile for the underlying dark matter halo. Assuming a constant
+mass-to-light ratio of $3 \times 0.7$~h~$M_{*}/L_{*}$, we use the BGG luminosity
+to estimate the stellar mass. The stellar mass$-$halo mass relation
+\citep{behroozi13}, including random scatter, is then used to calculate the halo
+mass for the lens. Given the halo mass, other key parameters such as the scale
+radius ($r_s$) and the density at the scale radius ($\rho_s$) can be determined for an
+NFW profile.
+
+As described in Section~\ref{sect:gallens}, we calculate the luminosity and
+velocity dispersion for the BGG and each of the member galaxies. Next, we
+calculate the lens cross-section for each potential lensing group. The
+complexity in the lens models makes it analytically intractable to calculate the
+size of the caustics\footnote{The lens mass distribution determines size and
+shape of the caustics. Any source located within the caustics will form multiple
+lensed images which is the criteria for strong lensing. To further
+understand caustics, see XXX.}.  Hence, we use {\sc
+gravlens} to determine the area covered by the caustics. We consider only
+galaxies as our background source population since group or cluster-scale quasar
+lenses are not expected to be found in the \cfhtls (check XXX).  Following the same
+procedure as described in Section~\ref{sect:gallens}, we calculate the number of
+galaxies expected to lie behind every potential lensing group (see
+Eq.~\ref{eqn:nsrc}). As before, for each background galaxy within the lens cross-section, a
+redshift and an $i$-band magnitude is determined by drawing galaxies randomly
+from the respective distributions (see Eqs.~\ref{eqn:ps}-\ref{eqn:ns}).
+
+All those groups that are found to have no background galaxies within the
+cross-sectional area are rejected and the rest are included as potential lenses.
+As mentioned earlier, we artificially boost the total number of sources behind
+every lens but ensure that (check XXX) the statistical properties such as the profile of the
+image separation distribution are not affected (see \Fref{fig:remudist}). We
+follow the same procedure and apply the same thresholds to determine properties
+of the lensed galaxies for every lens as are described for galaxy-galaxy lenses
+in the previous section. The simulated images are added to the real \cfhtls~images
+with the BGGs as the center.
 
@@
 
-\subsection{The CFHT Legacy Survey}
-\label{sec:data:CFHTLS}
+\subsection{Simulated Lens Sample and Catalog Description}
 
-Describe survey. Refs.
+\begin{table}
+\begin{center}
+\caption{ \label{tab:thresh} 
+Thresholds used in the selection of the simulated lenses. }
+\begin{tabular}{l l l l l}
+\hline
+Name  &  \multicolumn{2}{c} {gal}  & \multicolumn{2}{c}{qso} \\ 
+      & min  &  max  & min & max \\
+\hline
+\hline
+Source Redshift  & 1.0 & 4.0  & 1.0  & 5.9 \\
+Source Magnitude & 21.0 & 25.5 & 21.0 & 25.5 \\
 
-Why this one? Good IQ, deep, colorful, homogeneous. Precursor to Stage III and
-IV imaging surveys, DES, KIDS, LSST etc. Already searched by robots: enables
-comparison of techniques. Lenses not yet found by robots, detectable by
-humans?
+boost factor & 100 (40$\dagger$)  &  & 1200 & \\
 
-Blind search strategy.
-Preparation of data: divide survey into overlapping tiles.
+Second brightest image & 23  & & 23 & \\
+Total magnification & 19 & & 20 & \\
+
+Lens shear strength &  0.001 & 0.02 &  0.001 & 0.02 \\
+Lens shear pa &  0 & 180 & 0 & 180  \\
+Source ellipticity & 0.1 & 0.6 & & \\
+Source PA & 0 & 180 & & \\
+\hline
+\end{tabular}
+{ $\dagger$} -- corresponds to the factor used for Groups scale lenses. 
+\end{center}
+\end{table}
+
+In this section, we describe some of the properties of our simulated sample for
+each of the three types of lens samples.
+
+The \Fref{fig:remudist} shows Einstein radius distribution for the
+galaxy-scale (dashed for background quasars and dotted for background galaxies)
+and groups-scale simulated lenses. For comparison, we show the expected
+distributions (blue dashed-dotted curves) for an SIS-like density profile at
+galaxy-scales and an NFW+Hernquist profile at groups-scales. The 
+theoretical curves are taken from \citep{More2012} wherein the models are
+explained in detail. We note that the model we adopt at groups-scale also
+includes SIS or SIE components for the group members unlike the theoretical
+prediction. The theoretical curves have arbitrary normalizations.
+
+We show the redshift and magnitude distributions of the lensing galaxies in the
+left and right panels of \Fref{fig:lensprop}
+respectively. Furthermore, we overplot the distributions of respective
+properties of the SARCS lenses from \citep{More2012} for comparison with arbitrary
+normalizations. We note qualitative similarities between the simulated and the
+real lens samples.
+
+Similarly, we show the ellipticity and the position angle of the simulated lens
+galaxy population extracted from the T0007 release of the \cfhtls~catalogs in the
+left and right panels of \Fref{fig:lensprop}, respectively. As before, the
+dashed-dotted (blue) curves show the same distribution for the SARCS lens
+population with arbitrary normalization \citep{More2012}.
+
+%We show the source redshift and magnitude distributions for each of the three
+%lens samples in the left and right panels of \Fref{fig:szmdist},
+%respectively. The peak of the source redshift distribution both for the galaxies
+%and quasars is known to be between $2<z<3$ from various lens samples (add
+%references XXX). This consistent with our simulated sample as expected. The
+%magnitude distribution of the simulated sample, on the other hand, is
+%specifically tailored to the requirements of \sw.  The goal was to generate a
+%lens sample that has a fair balance of both bright and faint lensed images since
+%the training sample should neither be too easy nor too difficult for the citizen
+%scientists.
+
+We produce catalogs with lens and source properties for each of the three types
+of lenses. These catalogs are available XXX. The catalogs typically have lens
+position, redshift, magnitudes, Einstein radius, ellipticity (whenever
+available) and shear (for galaxy-scale lenses only). For the background
+sources, we provide the offset from the lens center, redshift, magnitudes,
+total magnification, number of lensed images. Additionally, ellipticity and
+effective radius when the background sources are galaxies.
+
+%magdiff=5*0.1;
+%zdiffq=0.1;
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.85]{sw-cfhtls-figs/distrib_remu.pdf}
+\caption{ \label{fig:remudist}
+Einstein radius distribution for all types of lenses. The dashed-dotted (blue)
+curves show the theoretical prediction assuming an SIS model at galaxy-scales
+and a total (NFW+Hernquist) model at groups-scales taken from \citep{More2012}.
+}
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=1.3]{sw-cfhtls-figs/lensprop.pdf}
+\caption{ \label{fig:lensprop}
+Distributions of properties of the lensing galaxies of the simulated
+sample compared to the known lens sample SARCS XXXX check? 
+}
+\end{center}
+\end{figure*}
+
+%\begin{figure*}
+%\begin{center}
+%\includegraphics[scale=0.95]{sw-cfhtls-figs/distrib_srczmag.eps}
+%\caption{ \label{fig:szmdist}
+%Redshift distribution on the left and magnitude distribution on the right of the
+%simulated sample for the background sources. The different types of lines show the
+%distribution correspond to the three types of simulated lenses galaxy-quasar,
+%galaxy-galaxy and group-galaxy. 
+%}
+%\end{center}
+%\end{figure*}
+%
+%
+%\begin{figure}
+%\begin{center}
+%\includegraphics[scale=0.95]{sw-cfhtls-figs/distrib_reff.eps}
+%\caption{ \label{fig:reffdist}
+%Distributions of magnification (left) and source effective radius in units of
+%pixel (right).
+%}
+%\end{center}
+%\end{figure}
 
@@
 
-\subsection{Image Presentation}
-\label{sec:data:display}
+\section{Training sample: Duds and False positives}
+\label{sec:dfp}
 
-Presentation of images. Uniform scales, to build intuition and avoid rescales
-due to bright objects. Arcsinh stretch, to bring out low SB features. 
-Approximately optimized, how? Examples of images.
+A good training sample consists of a representative set of objects that
+one wants to find and another set of objects which appear to be from the
+former set but are of different origin in reality and which one can
+learn to discard efficiently. Indeed, we wanted to have a good training
+sample for the \sw users so that they can correctly identify the true
+lens candidates. Hence, in addition to the simulated lenses, we
+added a sample of duds and false positives to the training sample. Duds
+are images which have been visually inspected by experts and confirmed
+to contain no lenses.  False positives are systems which look like
+lenses but are not, for example, spiral galaxies, starforming galaxies,
+chance alignments of features arranged in a lensing configuration and
+stars.
 
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Known Lenses}
-\label{sec:data:knownlenses}
-
+We selected a sample of 450 duds for the Stage I classification in \sw
+(see XXX) and a sample of XXX false positives for the Stage II
+inspection (see XXX). The sample of false positives was selected from
+the candidates which passed the Stage I of \sw. We note that this is the
+first time, we have a systematically compiled sample of visually
+inspected false positives by the \sw users and categorized by the
+science team. Such a sample is tremendously helpful for training and
+understanding performances of various lens finding algorithms (refer
+james, sherry's paper ? XXX)
+{\bf TBA data products; make the FP sample available}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Completeness and purity with regard to known lenses.
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
+\subsection{Recovery of lenses}
+\label{sec:results:reco}
 
+{\it Describe which lenses were recovered and explain any cases missed by
+citizen scientists}
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
-
+%
+%\begin{longtable*}{l c c c c c c c l}
+%\caption{ \label{tab:all} 
+%Characteristics of lens candidates from the \SA sample. }\\
+%ID & RA & Dec &  $i$ & $z_{\rm phot}$ & $R_{\rm A}$ & Rank & Type & previous ID  \\
+%    & (hms) & (dms) &  (mag) &   & (arcsec) &  &  & \\ [1.5ex] \hline \\ 
+%\endfirsthead
+%
+%ID & RA & Dec &  $i$ & $z_{\rm phot}$ & $R_{\rm A}$ & Rank & Type & previous ID  \\
+%    & (hms) & (dms) &  (mag) &   & (arcsec) &  &  & \\ [1.5ex] \hline \\ 
+%\endhead
+%
+%\hline  
+%\multicolumn{11}{p{15cm}}{
+%{\bfseries
+%{\bf m:} This galaxy falls within the masked region as per the catalog from
+%which the magnitudes and the redshift are extracted.  {\bf z:} The magnitudes
+%and/or redshift are not from the catalog instead are measured by the author.
+%}  }\\
+%
+%\endlastfoot
+%   SW1  & 02:01:21.89 & $-$09:15:15.09 & 19.90 &  0.46 &  2.2 &   2.0 & A &  SA18 \\ 
+%   SW2  & 02:02:10.50 & $-$11:09:11.68 & 17.80 &  0.48 &  5.0 &   3.7 & A &  SA87 \\ 
+%\end{longtable*}
+%
 \subsection{Stage 1 Classification}
@@
 
-\subsection{New Lens Candidates}
-\label{sec:results:newlenses}
+\subsection{Discovery of lenses}
+\label{sec:results:disc}
+
+{\it Describe the newly found lenses and explain for a few
+cases why they were missed }
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{\cfhtls completeness and purity}
+\label{sec:results:sample}
+
+{\it Rejection rate. Completeness and purity at P > retirement, P > 95\%, and 
+as function of probability P.
+
+Summarize performance at some fiducial threshold: eg P = 95\%.}
 
@@
 
-Differences with robots: what types of lenses are found at \sw?
+{\it Differences with robots: what types of lenses are found at \sw?
 
@@
 
+Describe the importance of this kind of study 
+- being able to quantify the completeness of the lens samples
+- state how this will be used in a future \sw paper }
+
+We looked at the locations of simulated and real lenses from our data
+those were missed by \sw compared to the locations of the lenses that
+got detected. We do not find any obvious dependency in the rate of
+detections as a function of the position of a given lens for both
+simulated and real lens sample. Thus, the completeness of the lens
+sample is not affected by whether a lens is located close to the border
+or well within the center (see  Figure~\ref{fig:comppos}).  {\bf TBD: redo the completeness vs posn
+figure using the final real lens sample}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.95]{sw-cfhtls-figs/completeness_pos.pdf}
+\caption{ \label{fig:comppos}
+Completeness as a function of location of lenses. Simulated (left) and
+real lens (right) samples are shown. {\bf: TBD - Add a third color for
+P$>$ Pthresh which will be defn of "accepted"} Irrespective of whether the
+lenses are detected or rejected and whether they are simulated or real,
+there is no obvious dependency on where the lenses are located. 
+}
+\end{center}
+\end{figure*}
+
+\subsection{Limitations and Caveats of the training sample}
+The simulated sample has certain limitations due to lack of our understanding of
+various phenonmena in the Universe and due to uncertainties in various
+parameters of our model. Here, we describe some of the cases or aspects in which the
+simulations are known to have failed or seem unrealistic.
+
+The parameters required by various scaling relations and the models primarily
+depend on the photometry of the galaxies, groups and quasars detected in the
+survey. For galaxy-scale lenses, the lensing galaxies at higher redshifts or
+which are fainter have poor photometric measurements. This causes relatively
+larger uncertainties in its luminosity and velocity dispersion and leads to
+simulated lenses which look implausible. For example, due to a larger
+uncertainty in the velocity dispersion of the lensing galaxy, the lensed images
+may have larger image separation than what is expected given the visual priors
+from the galaxy.
+
+At group-scales, the photometric and redshift estimates are used when
+defining the group membership. Therefore, errors in redshift estimates generate
+galaxy groups with BGG or member galaxies with dissimilar properties. In some
+cases, low redshift spiral galaxies are incorrectly assigned high redshift.
+Spiral galaxies are typically less massive and low redshift spiral galaxies are
+unlikely to act as gravitational lenses. Hence, the resulting simulated lenses
+are not convincing.
+
+We use single Sersic component to describe the light profiles of background
+galaxies. This is clearly not the most accurate description for galaxies,
+especially, star-forming galaxies which form a significant fraction of the
+lensed galaxy population. Star-forming galaxies have complex structures such as
+star forming knots, spiral arms, bars and disks.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Conclusions}
+\section{Summary and Conclusions}
 \label{sec:conclude}
+In this paper, we describe the framework and procedure used to generate
+simulated lens sample for the blind lens search in the \cfhtls survey in
+collaboration with \sw. The aim of this lens search is to find lenses that have
+been missed by lens finding algorithms. The simulated lens sample is used for
+training the citizen scientists, calibrating their performance and rejecting
+unlikely lenses from the sample based on the classifications of citizen
+scientists. As a result, the simulated lenses need to consist of realistic
+looking lenses.
 
-Summary of CFHTLS project.
+We use the photometric and redshift catalogues for the foreground galaxies and
+additionally, color catalogues for background galaxies and quasars. We
+use scaling relations to relate light properties to properties such as mass and
+size to generate lens models. We further account for the
+instrumental effects such as seeing and noise before creating the final lensed
+images of model background sources. We add the lensed images on top of the real
+galaxies and groups in the \cfhtls data in all filters.
 
-Crowd-sourced gravitational lens detection works, in terms of the
-classification of the CFHTLS image dataset as described here, in the following
-specific ways:
+We draw the following conclusions:
 
@@
 
-\item Real (robotically-detected and expert-confirmed) lenses are
-recovered/missed at similar/comparable/different rates to the
-training set.
+\item Crowd-sourced gravitational lens detection works, as shown in by comparing with real lenses in CFHTLS:
+Real (robotically-detected and expert-confirmed) lenses are
+recovered/missed at similar/comparable/different rates C’\% and P’\% - this is a partial test of supervised vs unsupervised learning
 
-\item Completeness, purity of \sw sample to known lenses.
+%Which real lenses were missed? False negatives
 
-\item Partial test of supervised vs unsupervised learning, comment.
+\item We found a sample of new gravitational lens candidates. An expert-graded sample of size N, divided among several types.
+The SW lenses are different from the robotically (RingFinder and ArcFinder) detected lenses, in the following ways.
 
-\item Which real lenses were missed? False negatives, what we conclude from
-that.
-
-\item We found a
-sample of new gravitational lens candidates with the following properties: ...
-
-\item An expert-graded sample of size N, divided among several types, compares
-as follows.
-
-\item The SW lenses are different from the robotically (RingFinder and
-ArcFinder) detected lenses, in the following ways.
+% An expert-graded sample of size N, divided among several types.
 
 \end{itemize}
-
-Sum up, end.
 
@@
 \input{acknowledgments.tex}
+This work is based on observations obtained with MegaPrime/MegaCam, a joint
+project of CFHT and CEA/IRFU, at the Canada-France-Hawaii Telescope (CFHT) which
+is operated by the National Research Council (NRC) of Canada, the Institut
+National des Sciences de l'Univers of the Centre National de la Recherche
+Scientifique (CNRS) of France, and the University of Hawaii. This research used
+the facilities of the Canadian Astronomy Data Centre operated by the National
+Research Council of Canada with the support of the Canadian Space Agency.
+CFHTLenS data processing was made possible thanks to significant computing
+support from the NSERC Research Tools and Instruments grant program.
+This work was supported by World Premier International Research Center
+Initiative (WPI Initiative), MEXT, Japan.
 
@@
 
-% \appendix
+\appendix
 
@@
 \bibliographystyle{apj}
-\bibliography{references}
+\bibliography{references_cfhtls}
+%\bibliography{references}
 

### 2014-08-04 doc/sw-system.tex

@@
 
-\section{Classification Analysis}
+\section{Classification Stages and Analysis}
 \label{sec:swap}
@@
 In this section we outline our methodology for interpreting the interactions
-of the volunteers with the identification interface.  Each classification made
-is logged in a database, storing subject IDs, (anonymous) volunteer IDs, a
-timestamp and the classification results.  The {\it kind} of subject --
-whether it is a training subject (a  simulated lens or a known non-lens) or a
-test subject (an unseen image drawn from the survey) -- is also recorded. For
-all subjects, the positions of all Markers are recorded, in pixel coordinates.
-For training subjects, we also store the ``classification'' of the subject as
-a lens, or a non-lens, and also the type of object present in the image. These
-types are summarized in \Tref{tab:objecttypes}.  This classification is used
-to provide instant feedback, but is also the basic measurement used in a
-probabilistic classification of every subject based on all image views to
-date.
+of the volunteers with the identification interface, and then describe how we
+applied this methodology in the two classification stages in the CFHTLS
+project.
+
+Each classification made is logged in a database, storing subject IDs,
+(anonymous) volunteer IDs, a timestamp and the classification results.  The
+{\it kind} of subject -- whether it is a training subject (a  simulated lens
+or a known non-lens) or a test subject (an unseen image drawn from the survey)
+-- is also recorded. For all subjects, the positions of all Markers are
+recorded, in pixel coordinates. For training subjects, we also store the
+``classification'' of the subject as a lens, or a non-lens, and also the type
+of object present in the image. These types are summarized in
+\Tref{tab:objecttypes}.  This classification is used to provide instant
+feedback, but is also the basic measurement used in a probabilistic
+classification of every subject based on all image views to date.
 
@@
 
-In the next section we present results in terms of all three of these
-probabilities, as we investigate the performance of the \SW system.
+In \Sref{sec:results} below, we define several quantities based on the 
+probabilities listed above that serve to quantify the performance of the crowd
+in terms of the information they provide via their classifications, and report
+on the performance of the system in returning a sample of lens candidates
+as a function of $\pr(\LENS|C,T)$ threshold.
+
+During stage 1 classification of the CFHTLS images, we assigned a prior
+probability for each image to contain a lens of $2\times10^{-4}$, based on a
+rough estimate of the number of expected lenses in the survey. We then
+assigned two values of the images' posterior probability, $\pr(\LENS|C,T)$, to
+define ``detection'' and ``rejection'' thresholds. These were set to be 0.95
+and (approximately symmetrically in the logarithm of probability), $10^{-7}$.
+Subjects that attained probability of less than the rejection threshold were
+scheduled for retirement and subsequently ignored by the analysis code.
+Subjects crossing the detection threshold were not retired from the website,
+but instead left in the system so that more volunteers could see them.
+The analysis code was run every night during the project, and subjects retired
+in batches after its completion. This introduced some inefficiency, because
+some classifications were accumulated in the time between them crossing the
+rejection threshold and the subject actually being retired from the website.
+As subjects were retired from the site, more subjects were activated. In this
+way, the volunteers who down-voted images for not containing any lensed
+features enabled new images to be shown to other members of the community.
+
+When all the subjects had either been retired, or classified around 10 times
+or more, the web app was paused and reconfigured for stage 2. The sample of
+subjects classified during stage 2 was selected to be all those that passed
+the detection threshold ($\pr(\LENS|C,T) > 0.95$) at stage 1. These were
+classified for one week, with no retirement but a maximum classification
+number of 50 each.
 
@@
 \label{sec:results:crowd}
-
-% Enthusiasm: histogram of classifications, stage 1 vs stage 2. Information
-% contributed. Correlation with number of classifications. 
-% 
-% PL and PD as measures of skill. not quite talent, due to possibility of
-% learning - but agents assume talent. Performance of crowd re PD and PL.
-% Correlations with N classifications.
 

### 2014-08-07 doc/sw-system.tex
Added agent probabilities plot, closes #36

@@
 \end{itemize}
+
+\Fref{fig:agent-probabilities} shows random selection of Agents' confusion
+matrix elements, as they were on a particular day towards the end of the
+CFHTLS project. Many volunteers classify  only a small number of images, and
+so their Agents' confusion matrix elements remain close to their initial
+values of (0.5,0.5). As more images are classified (shown by the yellow point
+size), the Agents' matrix elements tend to move towards higher values, as the
+volunteers attain greater skill levels (green point sizes, see
+\Sref{sec:results} below) and the Agent learns more about them. In this
+quadrant, the Agents perceive their volunteers to be ``astute.''
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_probabilities.png}
+\caption{Typical \SW Agent confusion matrix elements. At a particular
+snapshot, 200 random Agents are shown distributed over the unit plane, with a
+tendency to move towards the ``astute'' region in the upper right hand
+quadrant as the Agents' volunteers view more images. Yellow point size is
+proprtional to the number of images classified; green point size shows
+Agent-perceived ``skill.''}
+\label{fig:swap:agent-probabilities}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\todo{Phil}{Include agent histories plot, discuss}
+
+\todo{Phil}{Include subject trajectories plot, discuss}
 

### 2014-08-07 doc/sw-system.tex
Added agent histories plot, fixes #37

@@
 
-\Fref{fig:agent-probabilities} shows random selection of Agents' confusion
-matrix elements, as they were on a particular day towards the end of the
-CFHTLS project. Many volunteers classify  only a small number of images, and
-so their Agents' confusion matrix elements remain close to their initial
+\Fref{fig:swap:agent-probabilities} shows a random selection of Agents'
+confusion matrix elements, as they were on a particular day towards the end of
+the CFHTLS project. Many volunteers classify  only a small number of images,
+and so their Agents' confusion matrix elements remain close to their initial
 values of (0.5,0.5). As more images are classified (shown by the yellow point
@@
 \Sref{sec:results} below) and the Agent learns more about them. In this
-quadrant, the Agents perceive their volunteers to be ``astute.''
+quadrant, the Agents perceive their volunteers to be ``astute.'' This trend is
+more clearly seen in \Fref{fig:swap:agent-histories}, which shows the skill of
+the same sample of Agents as the number of images classified increases. The
+histogram shows the distribution of classification number: a long tail to very
+high ``effort'' can be seen.
 
@@
 
-\todo{Phil}{Include agent histories plot, discuss}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_histories.png}
+\caption{Typical \SW Agent histories. The ``skill'' of the  same 200 random
+Agents  as in \Fref{fig:swap:agent-probabilities} is plotted in green as a function
+of the number  of subjects classified (``effort''). The yellow histogram in
+the background shows the distribution of effort.}
+\label{fig:swap:agent-histories}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2014-08-07 doc/sw-system.tex

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_probabilities.png}
+\caption{Typical \SW Agent confusion matrix elements. At a particular
+snapshot, 200 random Agents are shown distributed over the unit plane, with a
+tendency to move towards the ``astute'' region in the upper right hand
+quadrant as the Agents' volunteers view more images. Yellow point size is
+proprtional to the number of images classified; green point size shows
+Agent-perceived ``skill.''}
+\label{fig:swap:agent-probabilities}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_histories.png}
+\caption{Typical \SW Agent histories. The ``skill'' of the  same 200 random
+Agents  as in \Fref{fig:swap:agent-probabilities} is plotted in green as a function
+of the number  of subjects classified (``effort''). The yellow histogram in
+the background shows the distribution of effort.}
+\label{fig:swap:agent-histories}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \Fref{fig:swap:agent-probabilities} shows a random selection of Agents'
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_probabilities.png}
-\caption{Typical \SW Agent confusion matrix elements. At a particular
-snapshot, 200 random Agents are shown distributed over the unit plane, with a
-tendency to move towards the ``astute'' region in the upper right hand
-quadrant as the Agents' volunteers view more images. Yellow point size is
-proprtional to the number of images classified; green point size shows
-Agent-perceived ``skill.''}
-\label{fig:swap:agent-probabilities}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_histories.png}
-\caption{Typical \SW Agent histories. The ``skill'' of the  same 200 random
-Agents  as in \Fref{fig:swap:agent-probabilities} is plotted in green as a function
-of the number  of subjects classified (``effort''). The yellow histogram in
-the background shows the distribution of effort.}
-\label{fig:swap:agent-histories}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\todo{Phil}{Include subject trajectories plot, discuss}
-
 In \Sref{sec:results} below, we define several quantities based on the 
@@
 as a function of $\pr(\LENS|C,T)$ threshold.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_trajectories.png}
+\caption{Typical \SW stage 1 subject trajectories. Subjects drift downwards in
+the top panel as they are classified, while being nudged left and right by the
+Agents as they interpret the volunteers input. The dotted vertical lines show
+(left to right) the retirement threshold, prior probability, and the detection
+threshold.}
+\label{fig:swap:subject-trajectories}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Subjects crossing the detection threshold were not retired from the website,
-but instead left in the system so that more volunteers could see them.
+but instead left in the system so that more volunteers could see them. The
+progress of the subjects is illustrated in \Fref{fig:swap:subject-trajectories}.
+Subjects appear on this plot at the tip of the arrow, at zero classifications
+and prior probability; they then drift downwards as they are classified by the
+crowd, with each Agent applying the appropriate kick in probability based on
+what it hears its volunteer say. Encouragingly, sims (blue) tend to end up
+with high probability, while duds (red) pile up at low probability; test
+subjects (black) mostly drift to low probability, but some go the other way.
+The latter will help make up the candidate sample. As this plot shows, around
+10 classifications are required for a subject to reach the retirement
+threshold.
+
 The analysis code was run every night during the project, and subjects retired

### 2014-08-07 analysis/swap/agent.py
Correct information gain call (I think) - repairing code after Anu and Surhud's alternative information suggestion

@@ -195,6 +195,7 @@ class Agent(object):
 
             # Always log progress, even if not learning:
             self.traininghistory['Skill'] = np.append(self.traininghistory['Skill'],self.update_skill())
+            # NB. self.skill is now up to date.
             self.traininghistory['PL'] = np.append(self.traininghistory['PL'],self.PL)
             self.traininghistory['PD'] = np.append(self.traininghistory['PD'],self.PD)
 

### 2014-08-07 analysis/swap/subject.py

@@ -232,20 +232,15 @@ class Subject(object):
                         self.retirement_time = 'not yet'
                         self.retirement_age = 0.0
 
-                # Update agent - training history is taken care of elsewhere:
+                # Update agent - training history is taken care of in agent.heard(), 
+                # which also keeps agent.skill up to date.
                 if self.kind == 'test':
 
-                     by.testhistory['ID'] = np.append(by.testhistory['ID'],
-                                                      self.ID)
-                     # by.testhistory['I'] = np.append(by.testhistory['I'], by.contribution)
-                     #by.testhistory['I'] = np.append(by.testhistory['I'], swap.informationGain(self.mean_probability, by.PL, by.PD, as_being))
-                     informationGain=swap.informationGain(prior_probability,posterior_probability);
-                     by.testhistory['I'] = np.append(by.testhistory['I'], np.mean(informationGain));
-                     # by.testhistory['Skill'] = np.append(by.testhistory['Skill'], swap.expectedInformationGain(0.5,by.PL,by.PD))
+                     by.testhistory['ID'] = np.append(by.testhistory['ID'], self.ID)
+                     by.testhistory['I'] = np.append(by.testhistory['I'], swap.informationGain(self.mean_probability, by.PL, by.PD, as_being))
                      by.testhistory['Skill'] = np.append(by.testhistory['Skill'], by.skill)
-                     by.contribution += by.skill
-
                      by.testhistory['ItWas'] = np.append(by.testhistory['ItWas'], as_being_number)
+                     by.contribution += by.skill
 
                 # update the annotation history
                 self.annotationhistory['Name'] = np.append(self.annotationhistory['Name'], by.name)

### 2014-08-12 doc/sw-system.tex

@@
 
-\subsubsection{Instant Feedback}
+\subsubsection{Training Subjects and Instant Feedback}
 
@@
 
-\question{PJM}{Does the feedback lead to volunteers leaving the site more 
-quickly, or less quickly? Does negative feedback have more impact than
-positive?}
-
 The initial frequency of the training images is set to be two in five;
@@
 
-\subsection{Stage 1: Initial Classification}
-\label{sec:design:stage1}
-
-Interface fast due to pre-loading of images, and minimizing interaction.
-Trade-off between speed and accuracy. Decreasing training rate.
-
-Quick dashboard provides simple ways to explore further: zoom, contrast
-controls.
-
-Spotting lenses: Markers to be placed. Two reasons: first, to give good
-feedback. Second, to focus attention.
-
-Non-lenses marked? Favourite button instead, enabling serendipitous
-discovery of other interesting things, separate from lenses.
-
-Retirement of low probability systems. Concentrates sample, provides more
-``bacon'' (while slightly skewing "sim frequency"). Note that this feature
-means that everyone contributes to detection of lenses: luck is made for the
-few that happen to see the new lenses, by the masses that did the rejection.
-Group effort.
-
-Sims vs duds leads to inclusive search -- click on anything you think etc...
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Stage 2: Refinement}
-\label{sec:design:stage2}
-
-Goal: assess candidates, reject false positives by comparing with training set
-of non-obvious non-lenses. Produce a sample rankable by probability.
-
-Reconfigured website: more detailed SG, more detailed feedback. Orange
-background to make it obvious stage 2 is different. Slower image presentation.
-Higher, constant training rate.
+\subsection{Staged Classification}
+\label{sec:design:stages}
+
+We now describe briefly the two-stage strategy that was employed in the CFHTLS
+project, initial classification (involving the rejection of very large numbers
+of non-lenses), and refinement (to further narrow down the sample). The web
+application was reconfigured between the two stages, to assist in their
+functioning.
+
+\subsubsection{Stage 1: Initial Classification}
+
+The goal of a stage 1 classification is to achieve a high rejection rate,
+while maintaining high completeness.  In this mode, therefore, the pre-loading
+of images was used to make the sliding in of new subjects happen quickly, to
+provide a sense of urgency: initial classification must be done fairly
+quickly for the search to be completed within a reasonable time period.  We
+expect some trade-off between speed and accuracy, which we return to in the
+results section below. Completion of the search requires subjects to be
+``retired'' over time, as a result of their being classified. We do this by
+analyzing the classifications on a daily basis, as described in
+\Sref{sec:swap} below. As subjects are retired, new ones are ingested into
+the web app for classification. This means that the discovery of lens
+candidates in stage 1 is truly a community effort: to detect a lens candidate,
+many non-lenses must first be rejected.
+
+The stage 1 training set was chosen to be quite clear cut, in order to err on
+the side of inclusivity, and so ensure high completeness. For the training
+duds we selected several hundred images at random, and three of us (AV, AM,
+PM) inspected them and discarded anything that could be a lens candidate. The
+remainder were ingested into the site.
+
+\subsubsection{Stage 2: Refinement}
+
+At stage 2, the goal is to define a final sample that has both high
+completeness and high purity. To this end, a more demanding training set was
+defined, where the duds all contain an object identified by one of us (AV, AM
+and PM) as a potential false positive. \Fref{fig:training:gallery} shows some
+example images from the CFHTLS stage 2 training set.
+
+\todo{Phil}{Show some example sims and duds...}
+
+We also attempted to encourage discernment by changing the look and feel of
+the app, slowing down the arrival of new images, and switching the background
+color to bright orange to make it clear that a different task was being set.
+The frequency with which training images were shown was fixed at 1 in 3.
+Finally, the Spotter's Guide was upgraded to include more detailed discussion
+of various possible false positives.
 
@@
 number of 50 each.
+
+\todo{Phil,Chris}{Write about offline analysis here (issue \#40)}
 
@@
 
+\todo{Phil,Chris}{Write about offline analysis here (issue \#40)}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-08-14 doc/sw-system.tex
Added ROC curves to paper

@@
 the training set images. \Fref{fig:results:sample:roc} shows receiver
-operating characteristic (ROC) curves for CFHTLS stage 1 and stage 2.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/roc.png}
+operating characteristic (ROC) curves for CFHTLS stage 1 and stage 2. These
+plots show the true positive rate (TPR), the number of sims correctly detected
+divided by the total number of sims in the training set, and the false
+positive rate (FPR), the number of duds incorrectly detected  divided by total
+number of duds in the training set, both for a given sample of detections defined by
+a particular probability threshold, which varies along the curves.  In both
+stages, these curves show that true positive rates of  around 90\% were
+achieved, at very low false positive rates. For comparison we show the results
+of an analysis where the classifications of  training images were ignored, and
+none of the agents allowed to learn: they were instead assigned initial values
+of their confusion matrices of 0.75 for each element, which then remained
+constant. This emulates a very simple unweighted voting scheme, where all
+classifications are treated equally. In this case, the TPR remains under 80\%
+in stage 1 and 60\% in stage 2, showing the benefit of including training
+images and allowing the agents to learn. The choice of initial confusion
+matrix is not very important: the same 0.75 initial values applied to normal,
+learning agents results in a slightly lower TPR than the default case,
+indicating that initializing the system less conservatively results in
+slightly worse performance.
+
+The dot-dashed curves show the impact of the offline analysis. At stage 1 the
+results are very similar to the online version that was actually run (solid
+line), at stage 2 there seems to be some benefit to doing the analysis in this
+way. Remarkably, over 85\% TPR is achieved at zero FPR. Alternatively, if one
+is willing to accept a false positive rate of 5\%, the true positive rate
+rises to over 95\%, showing that some of the sims that were missed in the
+online analysis can be recovered by doing the analysis offline. The same is
+true at stage 1, but to a much lower degree.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{minipage}{0.45\linewidth}
+  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage1_ROC.png}
+\end{minipage}\hfill
+\begin{minipage}{0.45\linewidth}
+  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage2_ROC.png}
+\end{minipage}
 \caption{Receiver operating characteristic curves for the \sw system, using
-the CFHTLS training set.}
+the CFHTLS training set. Left: stage 1, right: stage 2.}
 \label{fig:results:sample:roc}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Adopting the online stage 1 analysis, and the offline stage 2 analysis, we
+show in \Fref{fig:results:sample:CP} a plot of completeness versus purity in
+the two stages. As in \Fref{fig:results:sample:roc}, the detection threshold
+varies along the curves. Completeness is defined as the number of correctly 
+detected sims divided by the total number of sims in the training set, while
+purity is the number of the number of correctly detected sims divided by the
+number of detections that would be claimed in a realistic sample. The purity
+can only be calculated approximately. First we compute the expected number of
+false positives by multiplying the FPR by the expected number of non-lenses in
+the survey. Then we multiply the TPR by the expected number of lenses in the
+survey, to get the expected number of true positives. The sum of the true
+positives and the false positives gives the expected sample size; dividing the
+expected number of true positives by this sample size gives the purity.
+
+\todo{Chris}{Make completeness vs purity plot and add it here, please!}
 

### 2014-08-14 doc/sw-system.tex
Initial PL/PD symbols used - to match ROC curve plot legend

@@
 We conservatively initialize both elements of each  agent's confusion
-matrix to be 0.5, that of a maximally ambivalent  random classifier, so
+matrix to be $\CM^0_{LL} = \CM^0_{NN} = 0.5$, that of a maximally ambivalent  random classifier, so
 that all agents start with zero skill. While  this makes no allowance

### 2014-08-21 analysis/SWAP.py
Added flavor to subjects - lensing cluster, etc

@@ -259,8 +259,9 @@ def SWAP(argv):
             continue # Tutorial subjects fail, as do stage/project mismatches!
         # t,Name,ID,ZooID,category,kind,X,Y,location,thisstage,P = items
         # X, Y: result,truth (LENS,NOT,UNKNOWN)
-        # cpd 31.5.14: added annotation_x, annotation_y : locations of clicks
-        tstring,Name,ID,ZooID,category,kind,X,Y,location,classification_stage,at_x,at_y = items
+        # CPD 31.5.14: added annotation_x, annotation_y : locations of clicks
+        # PJM 20014-08-21: added "flavor" of subject, 'lensing cluster', len
+        tstring,Name,ID,ZooID,category,kind,flavor,X,Y,location,classification_stage,at_x,at_y = items
 
         # this is probably bad form:
         at_x = eval(at_x)
@@ -292,7 +293,7 @@ def SWAP(argv):
         # Register newly-classified subjects:
         # Old, slow code: if ID not in sample.list():
         try: test = sample.member[ID]
-        except: sample.member[ID] = swap.Subject(ID,ZooID,category,kind,Y,thresholds,location)
+        except: sample.member[ID] = swap.Subject(ID,ZooID,category,kind,flavor,Y,thresholds,location)
 
         # Update the subject's lens probability using input from the
         # classifier. We send that classifier's agent to the subject

### 2014-08-21 analysis/swap/offline.py
allowed EM_algo to customize min,max steps, epsilon for ending

@@ -271,6 +271,7 @@ def Mstep(bureau_offline, pi, taus, training_IDs={}):
 # Expectation Maximization algorithm.
 
 def EM_algorithm(bureau_offline, pi, taus, training_IDs={},
+                 N_min=10, N_max=50, epsilon_min=1e-5,
                  return_information=False):
     epsilon_taus = 10
     N_max = 50

### 2014-08-21 analysis/swap/offline.py
of course, one should not make silly coding errors, too

@@ -274,10 +274,9 @@ def EM_algorithm(bureau_offline, pi, taus, training_IDs={},
                  N_min=10, N_max=50, epsilon_min=1e-5,
                  return_information=False):
     epsilon_taus = 10
-    N_max = 50
-    N_min = 10
+
     N_try = 0
-    epsilon_min = 1e-5
+
     epsilon_list = []
 
     while (epsilon_taus > epsilon_min) * (N_try < N_max) + (N_try < N_min):

### 2014-08-21 doc/sw-system.tex
Even though I need to rerun to make the roc and purity curves, I might as well commit these changes

@@
 
-Adopting the online stage 1 analysis, and the offline stage 2 analysis, we
-show in \Fref{fig:results:sample:CP} a plot of completeness versus purity in
-the two stages. As in \Fref{fig:results:sample:roc}, the detection threshold
-varies along the curves. Completeness is defined as the number of correctly 
-detected sims divided by the total number of sims in the training set, while
-purity is the number of the number of correctly detected sims divided by the
-number of detections that would be claimed in a realistic sample. The purity
-can only be calculated approximately. First we compute the expected number of
-false positives by multiplying the FPR by the expected number of non-lenses in
-the survey. Then we multiply the TPR by the expected number of lenses in the
-survey, to get the expected number of true positives. The sum of the true
-positives and the false positives gives the expected sample size; dividing the
-expected number of true positives by this sample size gives the purity.
-
-\todo{Chris}{Make completeness vs purity plot and add it here, please!}
+Adopting the online stage 1 analysis, and the offline stage 2 analysis, we show
+in \Fref{fig:results:sample:CP} a plot of completeness versus purity in the two
+stages. As in \Fref{fig:results:sample:roc}, the detection threshold varies
+along the curves. Completeness is defined as the number of correctly detected
+sims divided by the total number of sims in the training set, while purity is
+the number of correct detections divided by the total number of detections.
+\footnote{The completeness is equivalent to the TPR and is also known elsewhere
+as the `recall'. The purity is also known as the `precision'.} If the training
+set samples from the same systems as the test set, then the completeness of the
+training set will be equivalent to the completeness of the test set. The purity
+depends on the proportion of sims to duds, and so the purity of the test set
+must be approximated by rescaling the training set to the expected proportion
+of lens systems to not-lens systems in the survey.  First we compute the
+expected number of false positives by multiplying the FPR by the expected
+number of non-lenses in the survey. Then we multiply the TPR by the expected
+number of lenses in the survey, to get the expected number of true positives.
+The sum of the true positives and the false positives gives the expected sample
+size; dividing the expected number of true positives by this sample size gives
+the purity. Note that the completeness is invariant to this transformation.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering\includegraphics[width=\linewidth]{sw-system-figs/completeness_purity.png}
+\caption{Completeness-estimated purity curves for the \sw system, using
+the CFHTLS training set.}
+\label{fig:results:sample:CP}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2014-08-21 doc/sw-system.tex
Skeleton text about offline analysis, for #40

--- 2014-08-14 doc/sw-system.tex
@@
 applied this methodology in the two classification stages in the CFHTLS
-project.
+project in the \sw Analysis Pipeline (SWAP) code.\footnote{The open source 
+SWAP code is available from 
+\texttt{https://github.com/drphilmarshall/SpaceWarps}}
 
@@
 
-We perform an online analysis of the classifications,  updating a
+While the \sw web app is live, and classifications are being made, we 
+perform an online analysis of the classifications,  updating a
 probabilistic model of every (anonymous) volunteer's data, and also updating
@@
 classified for one week, with no retirement but a maximum classification
-number of 50 each.
-
-\todo{Phil,Chris}{Write about offline analysis here (issue \#40)}
+number of 50 each. {\bf The number of subjects at stage 2 was small enough that we
+did not need to retire any: instead, we simply collected classifications for a
+fixed period of time (about 4 weeks). Without the time pressure motivating the
+online analysis, we implemented an ``offline'' version of the analysis that
+performs a joint inference of all Agent confusion matrix elements and subject
+probabilities simultaneously, for comparison. We describe how this differs
+from the online analysis in the appendix. }
+
+\todo{Chris}{Please check and edit the offline analysis description (in bold)
+above -- and then the text in the appendix! (issue \#40)}
 
@@
 subject being a $\LENS$, given both its volunteer's classification, and its
-volunteer's experience. In this appendix we describe how these agents work.
+volunteer's experience. In this appendix we describe how these agents work,
+and other aspects of the \sw analysis pipeline (SWAP).
 
@@
 
-\subsection{Updating the Subject Probabilities}
+\subsection{Online SWAP: Updating the Subject Probabilities}
 \label{appendix:swap:examples}
@@
 
-\todo{Phil,Chris}{Write about offline analysis here (issue \#40)}
+\subsection{Offline SWAP}
+\label{appendix:swap:offline}
+
+The probabilistic model described above does not need to be implemented as an
+online inference. Indeed, it might be more appropriate to perform the inference
+of all Agent confusion matrix elements and Subject probabilities
+simultaneously, so that the early classifications are not effectively
+downweighted as a result of the Agent's ignorance. It might also be that this
+ignorance builds in some conservatism to the system, reducing the noise due
+the early classifications if they are unreliable. In the joint analysis, the
+basic assumption that is built into the Agents, that their volunteers
+have innate and unchanging talent for lens spotting parameterised by two 
+constant confusion matrix elements which simply need to be inferred given the
+data, is implemented in full. The effect is that of applying the time-averaged
+confusion matrices, rather than one that evolves as the Agents (and in the
+real world, the volunteers) learn.
+
+The mathematics of the offline inference are presented elsewhere (in
+preparation). Here we briefly note that we maximize the joint 
+posterior probability distribution for all the model parameters (some 66,000
+confusion matrix elements and 430,000 subject probabilities) with a simple
+expectation-maximisation algorithm. This procedure takes [approximately the
+same | somewhat less | somewhat more] CPU time as the online analysis, because
+[insert reason]. Other comments about the relative performance]. The plots in
+\Sref{sec:results:sample} show the difference in performance between the
+online and offline analyses.
+
+\todo{Chris}{Please check this text and edit appropriately (issue \#40)}
 

### 2014-08-21 doc/sw-cfhtls.tex
Copied files from simpaper directory

@@
 \begin{abstract}
-We present X new strong gravitational lens candidates found in the CFHT
-Legacy
-survey by the \sw collaboration.
+
+The CFHT Legacy Survey has been searched for strong lenses with
+semi-automated algorithms both at galaxy and groups scales. With the aim
+of improving these lens finding robots, we carry out a blind lens search
+in the complete \cfhtls WIDE survey with \sw. We describe the training
+sample used for both training the citizen scientists that participated
+in \sw and calibrating their performance. We generate realistic looking
+simulated samples of lenses both at galaxy and group-scales as part of
+this training sample. We present 74 new strong gravitational lens
+candidates discovered from the \sw-\cfhtls search. Furthermore, we
+compile a sample of false positives which can be used for robot testing,
+first of its kind for the lensing community. The simulated sample is
+also used to make a comparison between human performance against the
+robots. We find that the XX per cent of the known lens sample is
+recovered and the new lens sample has XX completeness with respect to
+the simulated sample. We make available the following data products:
+simulated sample, simulation code and the false positives sample at XXX.
 
@@
 
-{\it Describe various lens finding algorithms and the motivation for this
-particular project with \cfhtls. Already searched by robots: enables comparison of techniques. Lenses not
-yet found by robots, detectable by humans? }
+%{\it Describe various lens finding algorithms and the motivation for this particular project with \cfhtls.
+Already searched by robots: enables comparison of techniques.
+Lenses not yet found by robots, detectable by humans?
+}
 
-In Paper I, we describe the \sw website, an online system that enables
-crowd-sourced detection of gravitational lenses. In this paper, we
-describe our first lens search with \sw in the \cfhtls data which we
-refer to as Paper II.
+The last few decades have seen a rise in the discoveries of strong
+gravitational lenses owing to the plethora of interesting applications
+they have in astrophysics and cosmology. Strong lenses are routinely
+used to probe the dark matter distribution from galaxy (ref) to cluster
+scales (ref), to  study distant young galaxies by using the lensing
+magnification as a natural telescope (ref), to test the cosmological
+model by constraining cosmological parameters such as the Hubble
+constant (ref) and dark energy (ref) and many more. Even though strong
+lenses are rare, since a foreground massive object needs to be
+sufficiently aligned with a distant background source to produce
+multiple images, systematic lens searches have led to discovery of over
+500 lenses till date (XXX add mld url).
+
+Rarity of lenses implies searching for them is a painstaking task.
+Efficient automated methods are thus imperative to finding a reasonably
+complete and pure sample of strong lenses.
+
+Since the inception of the first citizen science project, Galaxy Zoo, to
+classify galaxy morphologies \citep{LintottEtal2008}, several astronomy
+and non-astronomy projects have been launched by the Zooniverse leading
+to many interesting project. For example, PlanetHunters
+has discovered XXX transiting exoplanets \citep{SchwambEtal2012},
+Supernova XXX add ref and XXX add ref
+
+In Paper I, we describe \sw, an online system that enables crowd-sourced
+detection of gravitational lenses. In this paper (referred to as Paper
+II), we describe our first lens search with \sw in the \cfhtls data.
 
@@
 the authors prior to the lens search with \sw.
-The work
-by \citet{Gavazzi2013} looks for bluish features around bright XXX
-galaxies and has found XXX lens candidates at galaxy-scales.  The arc
-finding lens search \citet{More2012} has found 127 lens candidates by
-looking for arcs in $g$ band alone. This sample has both galaxy and
-groups scale lens candidates. The \citet{Sygnet2009} is a search for
-edge-on disk lenses done by selecting the galaxy's profile from the
-Sextractor's output in the $i$~band and has 18 lens candidates.
+
+At galaxy-scales, there are two main types of lens searches. The
+RingFinder \citet{Gavazzi2014} was used for finding compact rings or arcs
+around centers of isolated and massive early-type galaxies. By
+subtracting the PSF-matched i-band images from the g-band, the
+algorithm looks for excess flux in the bluer g-band which is typical of
+the distant lensed star forming galaxies. An object detector measures
+the properties of these residual blue features and candidates meeting a
+length-width ratio and tangential alignment criteria are then visually
+inspected to form the final sample. This rings sample consists of 39
+confirmed lenses and 17 promising candidates.
+
+The second galaxy-scale lens search was to find edge-on galaxy lenses in
+the \cfhtls \citep{Sygnet2010} by selecting the galaxy's profile from the
+output of {\sc Sextractor} in the $i$~band and with low inclination
+angle. This sample has about 3 promising and a total of 18 lens
+candidates.
+
+On the other hand, the {\sc arcfinder} \citet{More2012} was used for
+finding blue arc-like features in the complete \cfhtls data withouth any
+pre-selection on the type of the lensing object. The search was carried
+out in the g-band which is the most efficient wavelength to find typical
+lensing galaxies. This sample, called the SARCS, has 55 promising and a
+total of 127 lens candidates and consists of both galaxy and
+groups/cluster scale lens candidates. Arc finding is better suited for
+lensed images or arcs with larger image separations i.e. more massive
+systems like groups and clusters. Thus, the SARCS sample has mostly
+groups/cluster-scale lenses and a few galaxy-scale lenses.
 
@@
 forum Talk where volunteers have the opportunity to discuss their
-findings with other volunteers and the science team. XXX some references
-to Paper I ?
+findings with other volunteers and the science team.
+
+XXX refer Paper I ?
 
@@
 \label{sec:results}
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
-\subsection{Recovery of lenses}
-\label{sec:results:reco}
+\subsection{Discovery of new lenses from \sw}
+\label{sec:results:disc}
 
-{\it Describe which lenses were recovered and explain any cases missed by
-citizen scientists}
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
+{\it Describe the newly found lenses and explain for a few
+cases why they were missed }
+
 %
@@
 %
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscand_2p0_3p0.pdf}
+\caption{ \label{fig:lch1}
+Sample of promising lens candidates ($R_{avg}>=2.0$)
+}
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscand_2p0_3p0_1.pdf}
+\caption{ \label{fig:lch2}
+contd. - Sample of promising lens candidates ($R_{avg}>=2.0$)
+}
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscand_1p3_1p7.pdf}
+\caption{ \label{fig:lcl}
+Sample of low probability lens candidates ($1.0<R_{avg}<2.0$)
+}
+\end{center}
+\end{figure*}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
+\subsection{Recovery of known \cfhtls lenses from \sw}
+\label{sec:results:reco}
+
+{\it Describe which lenses were recovered and explain any cases missed by
+citizen scientists}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
+\subsection{\cfhtls completeness and purity}
+\label{sec:results:sample}
+
+{\it Rejection rate. Completeness and purity at P > retirement, P > 95\%, and 
+as function of probability P.
+
+Summarize performance at some fiducial threshold: eg P = 95\%.}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
 \subsection{Stage 1 Classification}
@@
 \label{sec:results:experts}
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Discovery of lenses}
-\label{sec:results:disc}
-
-{\it Describe the newly found lenses and explain for a few
-cases why they were missed }
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{\cfhtls completeness and purity}
-\label{sec:results:sample}
-
-{\it Rejection rate. Completeness and purity at P > retirement, P > 95\%, and 
-as function of probability P.
-
-Summarize performance at some fiducial threshold: eg P = 95\%.}
 
@@
 
+{\bf TBD: 
+add section on offline analysis - extra lenses found etc;  
+expand FP section;  
+mention EGS moustakas and other lens samples; 
+comment on any lensed quasars, on any exotic lenses;
+check if some candidates were detected because they were hidden
+underneath the sims ie. from the D11;
+
+}
+
 We looked at the locations of simulated and real lenses from our data
 those were missed by \sw compared to the locations of the lenses that
-got detected. We do not find any obvious dependency in the rate of
-detections as a function of the position of a given lens for both
-simulated and real lens sample. Thus, the completeness of the lens
-sample is not affected by whether a lens is located close to the border
-or well within the center (see  Figure~\ref{fig:comppos}).  {\bf TBD: redo the completeness vs posn
-figure using the final real lens sample}
+got detected. The real lens sample consists of a total of 383 candidates
+which have $P_l>2.e-5$ and received a rank of $R_{avg}>0$ from the
+expert. We do not find any obvious dependency in the rate of detections
+as a function of the position of a given lens for both simulated and
+real lens sample. Thus, the completeness of the lens sample is not
+affected by whether a lens is located close to the border or well within
+the center (see  Figure~\ref{fig:comppos}).
 
@@
 \caption{ \label{fig:comppos}
-Completeness as a function of location of lenses. Simulated (left) and
-real lens (right) samples are shown. {\bf: TBD - Add a third color for
+Completeness as a function of location of lenses. Simulated lenses (left) and
+real lens candidate (right) are shown. {\bf: TBD - Add a third color for
 P$>$ Pthresh which will be defn of "accepted"} Irrespective of whether the
@@
 
-\item We found a sample of new gravitational lens candidates. An expert-graded sample of size N, divided among several types.
+\item We found a sample of new gravitational lens candidates. An
+expert-graded sample of 74 with 44 promising and 30 low probability
+candiates.
+
 The SW lenses are different from the robotically (RingFinder and ArcFinder) detected lenses, in the following ways.
-
-% An expert-graded sample of size N, divided among several types.
+XXXXX
 

### 2014-08-21 doc/acknowledgments.tex
Copied files from simpaper directory

@@
 
-We are also grateful to Brooke Simmons, David Hogg, XXX and YYY for many
-useful conversations about citizen science and gravitational lens
-detection. % Need to cross-ref with Zooniverse author list
+We are also grateful to Brooke Simmons, David Hogg, XXX and YYY for many useful
+conversations about citizen science and gravitational lens detection. % Need to
+cross-ref with Zooniverse author list
 %
 PJM was given support by the Royal  Society, in the form of a research
-fellowship. 
+fellowship, and by the U.S. Department of Energy under contract number DE-AC02-76SF00515.
 % He would like to thank the DotAstronomy community for
@@
 % AM \ldots
+The work of AM and SM was supported by World Premier International Research
+Center Initiative (WPI Initiative), MEXT, Japan.
 %

### 2014-08-22 doc/sw-system.tex
Tweaks

@@
 However, it is not the case that only these small groups were capable of
-making this large contribution: 9118 volunteers were ``experienced'' in that
-they had all classified at least 10 training images; the 375 highest
-contributing volunteers make up just 4\% of this experienced volunteer pool.
+making this large contribution.
+% : 9118 volunteers were ``experienced'' in that
+% they had all classified at least 10 training images; the 375 highest
+% contributing volunteers make up just 4\% of this experienced volunteer pool.
 The cumulative distribution of agent skill is shown in
@@
 
-Adopting the online stage 1 analysis, and the offline stage 2 analysis, we show
-in \Fref{fig:results:sample:CP} a plot of completeness versus purity in the two
-stages. As in \Fref{fig:results:sample:roc}, the detection threshold varies
-along the curves. Completeness is defined as the number of correctly detected
-sims divided by the total number of sims in the training set, while purity is
-the number of correct detections divided by the total number of detections.
-\footnote{The completeness is equivalent to the TPR and is also known elsewhere
-as the `recall'. The purity is also known as the `precision'.} If the training
-set samples from the same systems as the test set, then the completeness of the
-training set will be equivalent to the completeness of the test set. The purity
-depends on the proportion of sims to duds, and so the purity of the test set
-must be approximated by rescaling the training set to the expected proportion
-of lens systems to not-lens systems in the survey.  First we compute the
-expected number of false positives by multiplying the FPR by the expected
-number of non-lenses in the survey. Then we multiply the TPR by the expected
-number of lenses in the survey, to get the expected number of true positives.
-The sum of the true positives and the false positives gives the expected sample
-size; dividing the expected number of true positives by this sample size gives
-the purity. Note that the completeness is invariant to this transformation.
+Adopting the online stage 1 analysis, and the offline stage 2 analysis, we
+show in \Fref{fig:results:sample:CP} a plot of completeness versus purity in
+the two stages. As in \Fref{fig:results:sample:roc}, the detection threshold
+varies along the curves. Completeness is defined as the number of correctly
+detected sims divided by the total number of sims in the training set, while
+purity is the number of correct detections divided by the total number of
+detections. \footnote{The completeness is equivalent to the TPR and is also
+known elsewhere as the `recall'. The purity is also known as the `precision'.}
+If the training set samples from the same systems as the test set, then the
+completeness of the training set will be equivalent to the completeness of the
+test set. The purity depends on the proportion of sims to duds, and so the
+purity of the test set must be approximated by rescaling the training set to
+the expected proportion of lens systems to not-lens systems in the survey. 
+First we compute the expected number of false positives by multiplying the FPR
+by the expected number of non-lenses in the survey. Then we multiply the TPR
+by the expected number of lenses in the survey, to get the expected number of
+true positives. The sum of the true positives and the false positives gives
+the expected sample size; dividing the expected number of true positives by
+this sample size gives the purity. Note that the completeness is invariant to
+this transformation.
 

### 2014-08-25 doc/sw-system.tex
Added some text describing offline analysis for issue #40.

@@
 classified for one week, with no retirement but a maximum classification
-number of 50 each. {\bf The number of subjects at stage 2 was small enough that we
+number of 50 each. The number of subjects at stage 2 was small enough that we
 did not need to retire any: instead, we simply collected classifications for a
@@
 probabilities simultaneously, for comparison. We describe how this differs
-from the online analysis in the appendix. }
-
-\todo{Chris}{Please check and edit the offline analysis description (in bold)
-above -- and then the text in the appendix! (issue \#40)}
+from the online analysis in the appendix.
 
@@
 The mathematics of the offline inference are presented elsewhere (in
-preparation). Here we briefly note that we maximize the joint 
-posterior probability distribution for all the model parameters (some 66,000
-confusion matrix elements and 430,000 subject probabilities) with a simple
-expectation-maximisation algorithm. This procedure takes [approximately the
-same | somewhat less | somewhat more] CPU time as the online analysis, because
-[insert reason]. Other comments about the relative performance]. The plots in
-\Sref{sec:results:sample} show the difference in performance between the
-online and offline analyses.
-
-\todo{Chris}{Please check this text and edit appropriately (issue \#40)}
+preparation). Here we briefly note that we maximize the joint posterior
+probability distribution for all the model parameters (some 66,000 confusion
+matrix elements and 430,000 subject probabilities) with a simple
+expectation-maximisation algorithm. This procedure takes approximately the same
+CPU time as the online analysis, because no matrix inversions are required in
+the algorithm. The algorithm scales well and is actually faster than the online
+analysis with the larger stage 1 dataset. The expectation-maximisation
+algorithm is robust to initial starting parameters in, e.g., initial Agent
+confusion matrix elements and Subject probabilities. The plots in
+\Sref{sec:results:sample} show the difference in performance between the online
+and offline analyses.
 

### 2014-08-25 doc/sw-system.tex
added todo note for myself

@@
 
-Adopting the online stage 1 analysis, and the offline stage 2 analysis, we
-show in \Fref{fig:results:sample:CP} a plot of completeness versus purity in
-the two stages. As in \Fref{fig:results:sample:roc}, the detection threshold
-varies along the curves. Completeness is defined as the number of correctly
-detected sims divided by the total number of sims in the training set, while
-purity is the number of correct detections divided by the total number of
-detections. \footnote{The completeness is equivalent to the TPR and is also
+Adopting the online stage 1 analysis, and the offline stage 2 analysis, we show
+in \Fref{fig:results:sample:CP} a plot of completeness versus purity in the two
+stages. As in \Fref{fig:results:sample:roc}, the detection threshold varies
+along the curves. Completeness is defined as the number of correctly detected
+sims divided by the total number of sims in the training set, while purity is
+the number of correct detections divided by the total number of
+detections.\footnote{The completeness is equivalent to the TPR and is also
 known elsewhere as the `recall'. The purity is also known as the `precision'.}
@@
 First we compute the expected number of false positives by multiplying the FPR
-by the expected number of non-lenses in the survey. Then we multiply the TPR
-by the expected number of lenses in the survey, to get the expected number of
-true positives. The sum of the true positives and the false positives gives
-the expected sample size; dividing the expected number of true positives by
-this sample size gives the purity. Note that the completeness is invariant to
-this transformation.
+by the expected number of non-lenses in the survey. Then we multiply the TPR by
+the expected number of lenses in the survey, to get the expected number of true
+positives. The sum of the true positives and the false positives gives the
+expected sample size; dividing the expected number of true positives by this
+sample size gives the purity. Note that the completeness is invariant to this
+transformation.
+
+\todo{Chris}{Write analysis of completeness purity.}
 

### 2014-09-02 doc/sw-system.tex
Tweaks to tex, added PDFs back in for easier viewing

@@
 matrix elements and 430,000 subject probabilities) with a simple
-expectation-maximisation algorithm. This procedure takes approximately the same
-CPU time as the online analysis, because no matrix inversions are required in
-the algorithm. The algorithm scales well and is actually faster than the online
-analysis with the larger stage 1 dataset. The expectation-maximisation
-algorithm is robust to initial starting parameters in, e.g., initial Agent
-confusion matrix elements and Subject probabilities. The plots in
-\Sref{sec:results:sample} show the difference in performance between the online
-and offline analyses.
+expectation-maximisation algorithm. This procedure takes approximately the
+same CPU time as the stage 2 online analysis, because no matrix inversions are
+required in the algorithm. The algorithm scales well and is actually faster
+than the online analysis with the larger stage 1 dataset. The
+expectation-maximisation algorithm is robust to initial starting parameters
+in, e.g., initial Agent confusion matrix elements and Subject probabilities.
+The plots in \Sref{sec:results:sample} show the difference in performance
+between the online and offline analyses.
 

### 2014-09-02 doc/sw-system.tex
Short piece of text about the P vs C plot, needs numbers from @cpadavis #65

@@
 
+Our basic method in this paper is to analyze the performance of the \sw system
+on a ``training set'' of simulated lenses and known non-lenses. This allows us
+to estimate completeness and purity with respect to gravitational lenses that
+have the same properties of the training set. In the companion paper we carry
+out similar tests but with a sample of known (real) lenses {\it in situ}.
+
 This paper is organised as follows.  In \Sref{sec:design} we introduce the \sw
@@
 classifications made by the volunteers, and then present the results of system
-performance tests  made on the training images in \Sref{sec:results}. % In
-this section, we also investigate the properties of the crowd, to % understand
-where the information is coming from. We discuss the implications of our
-results for future lens searches in \Sref{sec:discuss} and draw conclusions in
-\Sref{sec:conclude}.
+performance tests  made on the training images in \Sref{sec:results}.  We
+discuss the implications of our results for future lens searches in
+\Sref{sec:discuss} and draw conclusions in \Sref{sec:conclude}.
 
@@
 classifications are treated equally. In this case, the TPR remains under 80\%
-in stage 1 and 60\% in stage 2, showing the benefit of including training
+in stage 1 and 60\% in stage 2, thus quantifying 
+the benefit of including training
 images and allowing the agents to learn. The choice of initial confusion
@@
 results are very similar to the online version that was actually run (solid
-line), at stage 2 there seems to be some benefit to doing the analysis in this
-way. Remarkably, over 85\% TPR is achieved at zero FPR. Alternatively, if one
-is willing to accept a false positive rate of 5\%, the true positive rate
-rises to over 95\%, showing that some of the sims that were missed in the
-online analysis can be recovered by doing the analysis offline. The same is
-true at stage 1, but to a much lower degree.
+line). However, at stage 2 there seems to be somewhat greater benefit to doing
+the analysis in this way: over 85\% TPR is achieved at zero FPR.
+Alternatively, if one is willing to accept a false positive rate of 5\%, the
+true positive rate rises to over 95\%, showing that some of the sims that were
+missed in the online analysis can be recovered by doing the analysis offline.
+The same is true at stage 1, but to a lower degree.
 
@@
 
-Adopting the online stage 1 analysis, and the offline stage 2 analysis, we show
-in \Fref{fig:results:sample:CP} a plot of completeness versus purity in the two
-stages. As in \Fref{fig:results:sample:roc}, the detection threshold varies
-along the curves. Completeness is defined as the number of correctly detected
-sims divided by the total number of sims in the training set, while purity is
-the number of correct detections divided by the total number of
+Adopting the online stage 1 analysis, and the offline stage 2 analysis, we
+show in \Fref{fig:results:sample:CP} a plot of the more familiar (to
+astronomers) quantities completeness versus purity in
+the two stages. As in \Fref{fig:results:sample:roc}, the detection threshold
+varies along the curves. Completeness is defined as the number of correctly
+detected sims divided by the total number of sims in the training set, while
+purity is the number of correct detections divided by the total number of
 detections.\footnote{The completeness is equivalent to the TPR and is also
-known elsewhere as the `recall'. The purity is also known as the `precision'.}
-If the training set samples from the same systems as the test set, then the
-completeness of the training set will be equivalent to the completeness of the
-test set. The purity depends on the proportion of sims to duds, and so the
-purity of the test set must be approximated by rescaling the training set to
-the expected proportion of lens systems to not-lens systems in the survey.
-First we compute the expected number of false positives by multiplying the FPR
-by the expected number of non-lenses in the survey. Then we multiply the TPR by
-the expected number of lenses in the survey, to get the expected number of true
-positives. The sum of the true positives and the false positives gives the
-expected sample size; dividing the expected number of true positives by this
-sample size gives the purity. Note that the completeness is invariant to this
-transformation.
-
-\todo{Chris}{Write analysis of completeness purity.}
+known elsewhere as the ``recall.''  The purity is also known as the
+``precision.''} If the training set samples from the same systems as the test
+set, then the completeness of the training set will be equivalent to the
+completeness of the test set. The purity depends on the proportion of sims to
+duds, and so the purity of the test set must be approximated by rescaling the
+training set to the expected proportion of lens systems to not-lens systems in
+the survey. First we compute the expected number of false positives by
+multiplying the FPR by the expected number of non-lenses in the survey. Then
+we multiply the TPR by the expected number of lenses in the survey, to get the
+expected number of true positives. The sum of the true positives and the false
+positives gives the expected sample size; dividing the expected number of true
+positives by this sample size gives the purity. Note that the completeness is
+invariant to this transformation.
+
+The stage 1 curves are truncated by the retirement of subjects in this phase, 
+which sets the minimum size of this sample. We see from the solid blue curve
+that over 90\% completeness was reached, albeit in a sample with around 20\%
+purity. The lensed quasar part of the training set yielded the highest
+completeness, suggesting that these were the easiest sims to spot. The lensed
+galaxies were recovered at understandably lowest completeness, although the
+wider image separation  lensing clusters were not very different. At stage 2,
+where no retirement was carried out, it was possible to reach 100\% purity:
+indeed, the knee of the curve is at just under 90\% completeness. However, the
+purity decreases rapidly if higher completeness than this is sought.
+Interestingly, the lensing clusters can be seen to pose problems for the
+system, with its curve turning over at just 60\% completeness.
+
+The optimal sample in this simulated lens search experiment would have been
+constructed with a threshold value of $\pr(\LENS|C,T) > X.XX$. At 100\% purity
+and 9X\% completeness, it would have contained around N lens candidates.
 

### 2014-09-03 doc/sw-system.tex
\todo items for @cpadavis re #
\todo items for @cpadavis re #65, #66
Starting to address Edwin's efficiency comments #32
Closed #32

@@
 information generated in both stage 1 and 2 of the CFHTLS project, with the
-total numbers of agents and subjects for comparison. These numbers allow us to
-quantify the efficiency of the system. The contribution per classification is
-defined in terms of a hypothetical subject with lens probability of 0.5; one
-bit of information is needed to update such a subject's lens probability to
-either zero or one. This means that a maximally complete classification stage
-would yield a total contribution (summed over all agents) equal to the number
-of subjects. The ratio of this hypothetical optimum to the actual total
+total numbers of agents and subjects for comparison.  These numbers allow us
+to quantify the efficiency of the system.  The contribution per classification
+is defined in terms of a hypothetical subject with lens probability of 0.5;
+one bit of information is needed to update such a subject's lens probability
+to either zero or one. This means that a maximally complete classification
+stage would yield a total contribution (summed over all agents) equal to the
+number of subjects. The ratio of this hypothetical optimum to the actual total
 contribution is therefore a measure of the stage's inefficiency. We find our
@@
 processing: we were not able to retire subjects fast enough, and so they,
-remained in the system, being over-classified. Only 3705745 classifications
-were needed to retire all the subjects: the ratio of this to the total number
-made is 34\%. (The remaining 1\% is due to not all subjects being classified
-to 1 or 0 probability.) At stage 2, we did not retire any subjects at all; the
-inefficiency in this case was by design, to give everyone a chance to
-appreciate what they had found together!
+remained in the system, being over-classified. Indeed, only 3705745
+classifications were needed to retire all the subjects: the ratio of this to
+the total number made is 34\%. (The remaining 1\% is due to not all subjects
+being classified to 1 or 0 probability.) At stage 2, we did not retire any
+subjects at all; the inefficiency in this case was by design, to give everyone
+a chance to appreciate what they had found together!
 
@@
 that over 90\% completeness was reached, albeit in a sample with around 20\%
-purity. The lensed quasar part of the training set yielded the highest
+purity. To investigate the completeness to the three different types of lens
+in the training set, we ...
+
+\todo{Chris}{complete the above sentence to explain what purity means in the
+divided-by-sim-type case. Thanks! \#66}
+
+The lensed quasar part of the training set yielded the highest
 completeness, suggesting that these were the easiest sims to spot. The lensed
@@
 and 9X\% completeness, it would have contained around N lens candidates.
+
+\todo{Chris}{fill in the numbers above, please! :-) \#65}
 

### 2014-09-03 doc/sw-system.tex
Data sesction done, closed #31

@@
 astronomical survey images as containing lens candidates or not.  In a
-companion paper we will present the new gravitational lenses discovered in our
-first experimental lens search, and begin to investigate the differences
-between lens detections made in \sw and those made with automated techniques.
-Here though, we try to answer the following questions:
+companion paper (More et al, in preparation, herafter \papertwo) we will
+present the new gravitational lenses discovered in our first experimental lens
+search, and begin to investigate the differences between lens detections made
+in \sw and those made with automated techniques. Here though, we try to answer
+the following questions:
 
@@
 to estimate completeness and purity with respect to gravitational lenses that
-have the same properties of the training set. In the companion paper we carry
+have the same properties of the training set. In \papertwo we carry
 out similar tests but with a sample of known (real) lenses {\it in situ}.
@@
 viewer. The second is a link to that subject's page in the project discussion
-forum, \texttt{http://talk.spacewarps.org}. Here, volunteers can discuss the
-features they have seen either before they submit their classification, or
-after, if they ``favorite'' the subject. There is no ``back'' button: each
-volunteer may only classify a given subject once. However, the presence of an
-option to see what others think about any given subject before submitting your
-own classification means that the classifications may not be  strictly
-independent; the advantage of this system is that volunteers can learn from
-others what constitutes a good lens candidate. In practice, we might expect
-this to be a relatively unimportant educational resource, given the explicit
-training we provide for the volunteers, which we describe in the next section.
+forum, \texttt{http://talk.spacewarps.org} (known as ``Talk''). Here,
+volunteers can discuss the features they have seen either before they submit
+their classification, or after, if they ``favorite'' the subject. There is no
+``back'' button: each volunteer may only classify a given subject once.
+However, the presence of an option to see what others think about any given
+subject before submitting your own classification means that the
+classifications may not be  strictly independent; the advantage of this system
+is that volunteers can learn from others what constitutes a good lens
+candidate. In practice, we might expect this to be a relatively unimportant
+educational resource, given the explicit training we provide for the
+volunteers, which we describe in the next section.
 
@@
 
+In \Fref{fig:training-gallery} we show 12 example training images from the
+first \sw project (\Sref{sec:data} below).
+
+\todo{Phil, Aprajita}{Make gallery of 6 stage 2 sims and 6 stage 2 duds, to
+give the reader a feel for what the sims look like, and also how the images
+were presented, stretch and scale-wise.}
+
 \subsubsection{Spotter's Guide}
@@
 
+\todo{Phil}{write this section (\#31)}
+
 \section{Data}
@@
 
-Definitions: training subjects and test subjects. Sims and duds.
+We refer the reader to \papertwo for the details of the particular set of
+imaging survey data used in this first \sw project. Here, we summarize very
+briefly the choices that were made, in order to provide the context for our
+general description and illustrations of the \sw system.
 
@@
 
-Describe survey. Refs.
-
-Why this one? Good IQ, deep, colorful, homogeneous. Precursor to Stage III and
-IV imaging surveys, DES, KIDS, LSST etc. Already searched by robots: enables
-comparison of techniques. Lenses not yet found by robots, detectable by
-humans?
-
-Blind search strategy.
-Preparation of data: divide survey into overlapping tiles.
+The CFHT Legacy Survey \citep[CFHTLS,][]{CFHTLS} covered XXX square degrees of
+approximately equatorial sky, in four patches distributed in right ascension,
+over the course of N years. With homegeneous image quality of, typically, X
+arcsec (in the $i$-band), and reaching limiting magnitudes of XX-XX in the
+$ugriz$ filter set, this survey has yielded several dozen new gravitational
+lenses on both galaxy and group scales \citep{}. The quality of the data,
+combined with the presence of these comparison ``known lens'' samples, made
+this a natural choice against which to develop and test the \sw system. The
+CFHTLS is also well-representative of the data quality expected from several
+next-generation sky surveys, such as DES, KiDS, HSC and LSST.
+
+In order to investigate the completeness of the previous, semi-automated, lens
+searches in the CFHTLS area, we designed a ``blind search.'' We divided the
+mosaiced images into some 430,000 equal size, overlapping tiles, approximately
+70~arcsec on a side. Each of these images is a ``test image'' (as opposed to a
+``training image''). In future, larger area projects we expect to implement
+the rather different strategy of producing image tiles centred on particular
+pre-selected ``targets,'' to make for a more efficient (but less complete)
+survey. We do not expect the performance of citizen image inspectors to change
+significantly between these strategies: to first order, both strategies
+require the inspectors to learn what lenses look like, and then search the
+presented images for similar features.
 
@@
 
-Presentation of images. Uniform scales, to build intuition and avoid rescales
-due to bright objects. Arcsinh stretch, to bring out low SB features. 
-Approximately optimized, how? Examples of images.
+The CFHTLS $g$, $r$ and $i$-band images have the greatest depth and best image
+quality, and we chose to focus on this set (although the $u$ and $z$-band
+images were also available for inspection in Talk). We made colour composite
+images using publically-available code\footnote{The open source  colour image
+composition code used in this work is available from
+\texttt{http://github.com/drphilmarshall/HumVI}} following the prescription of
+\citet{LuptonEtal}. Specifically, we first rescaled the pixel values of each
+channel image into flux units, and then applied an arcsinh stretch. The
+stretch parameters were chosen using a small random sample of images, to
+ensure that the background noise was just visible,  and that the centres of
+bright, intermediate resdhift galaxies were not saturated. The color scales
+were chosen to maximize the contrast between faint extended objects. These
+parameters were then fixed during the production of all the tiles, in order to
+allow straightforward comparison between one image and another, and for
+intuition to be built up about the appearance of stars and galaxies across the
+survey. Alternative algorithms, such as adjusting the stretch and scale
+dynamically according to, for example, the root-mean-square pixel value in
+each image, can lead to better presentation of bright objects, but in doing so
+they tend to hide the faint features in those images: we needed to optimize
+the detectability of these faint features.   Examples of CFHTLS training set
+images can be seen in \Fref{fig:training-gallery}.
 
@@
 
-In this section we outline our methodology for interpreting the interactions
+Having described the classification interface, the training images and the
+test images,  we now outline our methodology for interpreting the interactions
 of the volunteers with the identification interface, and then describe how we

### 2014-09-03 doc/sw-system.tex
Discussion section plan in place #44

@@
 beyond its design as a supervised classification system.
+
+\todo{Phil}{revisit abstract (\#29).}
 
@@
 
-Challenges for future.
+\todo{Phil}{write discussion (\#44).}
+
+Preamble. Notes for future. Improvements to system to be investigated.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Improving performance: reducing incompleteness and impurity}
+\label{sec:discuss:performance}
+
+Incompleteness, false negatives. Examples and trajectories, from stage 2
+training set. Generic properties: hard to spot? Or unlucky? Costly mistakes by
+expert classifiers? Or random walk?
+
+Impurity, false positives. Examples and trajectories, from stage 2
+training set. Generic properties. Could also be solved by dynamical
+stage 2? Improve training?
+
+Solutions: dynamical stage 2, to reduce noise. Does stage 1 skill correlate
+with stage 2 skill? Missing group-scale lenses at stage 2. Improve training?
+Educational interventions?
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Improving efficiency}
+\label{sec:discuss:efficiency}
+
+Inefficiency. Move to truly online system: web app to analyse classifications
+as it goes. Place for weekly offline processing? Recovering false negatives by
+``resurrecting'' subjects that scattered down too soon.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Increasing capacity}
+\label{sec:discuss:capacity}
+
+Scaling of system. Factors of ten: 10^4 volunteers, 10^3 achieve high skill,
+10^2 make significant contribution. Good project size is few 10^4 subjects, to
+enable completion by a crowd of this size in short time.
+
+Ways to increase numbers of high-contribution volunteers: 1) increase crowd
+size. Higher exposure through media. Multi-lingual user base - comes with
+problems.  2) Increase engagement rate:  feedback from survey teams.
 
@@
 \label{sec:conclude}
+
+\todo{Phil}{write conclusions (\#45).}
 

### 2014-09-03 doc/sw-system.tex
Drafted performance section of discussion #44

@@
 \begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/stage2_veteran_contribution.png}
-\caption{Stage 2 agent properties, separating veterans from stage 1 from new
-volunteers. Point size represents total information generated, dashed lines
-are drawn at the mean values for each sample.}
-\label{fig:crowd:stage1vstage2}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We now look at the transition between stage 1 and stage 2 in more detail. Of
-the 1964 volunteers who took part in the stage 2 classification round, only
-774 were veterans from stage 1. However, these volunteers showed significantly
-higher skill levels than the new users, and also made more classifications
-(and hence made greater contributions. This is illustrated in  
-\Fref{fig:crowd:stage1vstage2}. In this figure, point size is proportional to
-information generated: the higher skill, higher effort stage 1 veterans
-generated most of the information.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
 \centering\includegraphics[width=0.9\linewidth]{sw-system-figs/early_vs_final_skill.png}
@@
 
-Preamble. Notes for future. Improvements to system to be investigated.
+What can we learn from the results of the previous section, for future
+projects? Potential improvements to the \sw system can be divided into three
+categories, performance, efficiency and capacity.
 
@@
 
-Incompleteness, false negatives. Examples and trajectories, from stage 2
-training set. Generic properties: hard to spot? Or unlucky? Costly mistakes by
-expert classifiers? Or random walk?
-
-Impurity, false positives. Examples and trajectories, from stage 2
-training set. Generic properties. Could also be solved by dynamical
-stage 2? Improve training?
-
-Solutions: dynamical stage 2, to reduce noise. Does stage 1 skill correlate
-with stage 2 skill? Missing group-scale lenses at stage 2. Improve training?
-Educational interventions?
+We first investigate the source of the incompleteness visible in 
+\Fref{fig:results:sample:CP}, by examining the stage 2 false negatives.
+\Fref{fig:discuss:performance:FNgallery} shows N example simulated lenses that
+were missed by the \sw system. In some cases their rejection is
+understandable: the lensed features are faint, or otherwise difficult to see.
+However, in other cases a reasonably obvious lens was passed over. 
+\Fref{fig:discuss:performance:FNtrajectories} shows the probability 
+trajectories of these subjects. \todo{Phil}{Make the FN plots, and look for
+behaviour. Can we see whether the FNs are due to costly mistakes by expert
+classifiers? Or are they just random walking south?}
+
+Is the system's impurity a result of the same behaviour?
+Figures~\ref{fig:discuss:performance:FPgallery}
+and~\ref{fig:discuss:performance:FPtrajectories} show the corresponding
+figures for the false positives -- non-lenses that were incorrectly inferred
+to be lens candidates during stage 2. \todo{Phil}{Make the FP plots, and look
+for behaviour. Can we see whether the FPs are due to costly mistakes by expert
+classifiers? Or are they just random walking south?}
+
+In general, there are three places we can act to improve system performance:
+educating the volunteers, assigning subjects for classification, and
+interpreting the classification data. The plots in this section suggest that
+...
+
+Mistakes by reasonably high skill classifiers cause large jumps in subject
+probability in the wrong direction, as are occasionally visible in the
+trajectory plots in this section. We might wonder whether some of those
+mistakes could have been corrected by the classifiers themselves, had they had
+access to a ``go back'' option. While clearly enabling error reduction, we
+might worry about such a mechanism enabling classifiers to have a guess, then
+go and read the Talk discussion, and then return to the classification
+interface to change their mind to agree with the forum. In fact, this is
+already possible on the current interface -- and indeed, it is not obvious
+that such correlations would necessarily lead to poorer system performance.
+This could be tested by presenting a fraction of the volunteers with a version
+of the site that actively suggested that they take this approach, and then
+tracking the relative performance of ``collaborative'' classifications
+compared with independent ones. We leave this to further work.
+
+Mistakes by both high and low skill classifiers could be reduced by improving
+the training in the system, which could be done in several ways. One is to 
+make more training images available to those who want or need it. A basic
+level of training images are needed for SWAP to build up an accurate picture
+of each classifier's skill -- but one could imagine volunteers {\it choosing}
+to see more training images (still at random) in their stream. Another could
+be to provide more information about what lenses do. In this project, the
+Spotter's Guide was always available on the site, but as a passive background
+resource. We might consider providing more links to this guide in the feedback
+messages shown to the classifiers as they go -- or perhaps extending these
+messages to themselves include more explanations and example images.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/stage2_veteran_contribution.png}
+\caption{Stage 2 agent properties, separating veterans from stage 1 from new
+volunteers. Point size represents total information generated, dashed lines
+are drawn at the mean values for each sample.}
+\label{fig:discuss:performance:stage1vstage2}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Some trajectories show signs of a random walk problem. Those subjects are
+simply ``unlucky:'' they are only seen by low skill classifiers, and  happen
+to be mis-classified  enough times to cross the retirement threshold (in the
+case of the false negatives) or remain in the system (in the case of the false
+positives). While improved training will help reduce this effect, it is here
+that targeted task assignment could help improve system performance. We
+advertised stage 2 of the current project to all registered users; it was
+taken up by stage 1 veterans with a broad range of skill, and also picked up a
+significant number of new users who did not have enough time to aquire high
+skill (since stage 2 was quite short): of
+the 1964 volunteers who took part in the stage 2 classification round, only
+774 were veterans from stage 1. \Fref{fig:discuss:performance:stage1vstage2}
+shows how the stage 1 skill maps on to stage 2 skill and contribution...
+
+\todo{Phil}{Remake figure to show stage 2 skill vs stage 1 skill with point
+size given by stage 2 contribution. Stage 2 newbies will all have 0 +/- small
+stage 1 skill. Then move this figure to here.}
+
+Thsi figure suggests that there may be some benefit to opening stage 2 on the
+basis of agent skill, in order to reduce the noise in the system generated by
+new and low skill volunteers in this more difficult classification stage. A
+simple implementation of this would be to switch the web app to the stage 2
+version when either a certain stage 1 skill (and/or effort) threshold was
+passed. Good strategy would probably be to switch back to stage 1 after some
+number of stage 2 classifications (to avoid losing the high skill users from
+stage 1 entirely), and also to make it very clear which stage the classifier
+was at (since stage 2 requires more careful attention). This is something we
+plan to experiment with in future.
 

### 2014-09-03 doc/sw-system.tex
Compiled

@@
 
-Scaling of system. Factors of ten: 10^4 volunteers, 10^3 achieve high skill,
-10^2 make significant contribution. Good project size is few 10^4 subjects, to
-enable completion by a crowd of this size in short time.
+Scaling of system. Factors of ten: $10^4$ volunteers, $10^3$ achieve high
+skill, $10^2$ make significant contribution. Good project size is few $10^4$
+subjects, to enable completion by a crowd of this size in short time.
 

### 2014-09-03 doc/sw-system.tex
Drafted performance section of discussion #44

@@
 ...
+\todo{Phil}{complete this thought, and update the text below, in the light of
+the FP and the FN figures}
 
@@
 plan to experiment with in future.
+
+Finally, there could be some performance gains to be made by improving the
+SWAP agent model, or its implementation. In a future paper we plan to
+investigate the use of the test images as well as the training images in
+learning the agent confusion matrix elements (Davis et al, in preparation).
+One might also consider looking at introducing more conditional dependences in
+these elements, to allow for some classifiers having greater skill in one type
+of lens than another, or, more generally, as a function of lens property (such
+as color, brightness, and image separation). In the current model, all agents
+are considered to be completely independent, whereas in fact we might expect
+there to be significant clustering of the confusion matrix elements. A
+hierarchical model for the crowd, with hyper-parameters describing the
+distribution of confusion matrix elements across the population, may well
+accelerate the agent learning process by including the notion of one agent
+being likely to be similar to its neighbours. Finally, it is worth noting that
+the model of \citet{IBCC} explicitly avoids the assumption of the agent
+confusion matrix elements being constant in time, allowing the development of
+volunteer skill to be more accurately tracked -- and that they did see some
+time-evolution in the supernova zoo classifiers' skill. Finding a way to
+incorporate such a learning model into SWAP, while retaining its statistically
+online character is an interesting challenge for future work.
 

### 2014-09-03 analysis/make_trajectory_plots.py
Upgraded subject and collection plots to allow 'highlighting' of ID'd subjects, added standalone plotting script. #68

@@ -1,0 +1,156 @@
+#!/usr/bin/env python
+# ======================================================================
+
+import sys,getopt,numpy as np
+
+# import matplotlib
+# # Force matplotlib to not use any Xwindows backend:
+# matplotlib.use('Agg')
+# 
+# # Fonts, latex:
+# matplotlib.rc('font',**{'family':'serif', 'serif':['TimesNewRoman']})
+# matplotlib.rc('text', usetex=True)
+# 
+# from matplotlib import pyplot as plt
+# 
+# bfs,sfs = 20,16
+# params = { 'axes.labelsize': bfs,
+#             'text.fontsize': bfs,
+#           'legend.fontsize': bfs,
+#           'xtick.labelsize': sfs,
+#           'ytick.labelsize': sfs}
+# plt.rcParams.update(params)
+
+import swap
+
+# ======================================================================
+
+def make_trajectory_plots(argv):
+    """
+    NAME
+        make_trajectory_plots
+
+    PURPOSE
+        Given a collection pickle, this script plots a set of 
+        user-specified subject trajectories, possibly against a bacground 
+        of random trajectories.
+
+    COMMENTS
+
+    FLAGS
+        -h                        Print this message
+
+    INPUTS
+        collection.pickle
+        
+    OPTIONAL INPUTS
+        -f list.txt               Plain text list of subject IDs to highlight
+        -b --backdrop             Plot 200 random subjects as a backdrop
+        -t title                  Title for plot
+        --histogram               Include the histogram
+
+    OUTPUTS
+        trajectories.png          PNG plot
+
+    EXAMPLE
+
+    BUGS
+
+    AUTHORS
+        This file is part of the Space Warps project, and is distributed
+        under the GPL v2 by the Space Warps Science Team.
+        http://spacewarps.org/
+
+    HISTORY
+      2013-09-02  started Marshall (KIPAC)
+    """
+
+    # ------------------------------------------------------------------
+
+    try:
+       opts, args = getopt.getopt(argv,"hf:bt:",["help","backdrop","histogram"])
+    except getopt.GetoptError, err:
+       print str(err) # will print something like "option -a not recognized"
+       print make_trajectory_plots.__doc__  # will print the big comment above.
+       return
+
+    listfile = None
+    highlights = False
+    backdrop = False
+    title = 'Example Subject Trajectories'
+    histogram = False
+
+    for o,a in opts:
+       if o in ("-h", "--help"):
[…]

### 2014-09-03 analysis/swap/collection.py

@@ -225,13 +225,18 @@ class Collection(object):
 # ----------------------------------------------------------------------
 # Prepare to plot subjects' trajectories:
 
-    def start_trajectory_plot(self,final=False):
+    def start_trajectory_plot(self,final=False,title=None,histogram=True,logscale=True):
     
-        fig = plt.figure(figsize=(5,8), dpi=300)
-
         left, width = 0.15, 0.8
-        upperarea = [left, 0.4, width, 0.5]# left, bottom, width, height
-        lowerarea = [left, 0.1, width, 0.3]
+
+        if histogram:
+            fig = plt.figure(figsize=(5,8), dpi=300)
+            upperarea = [left, 0.4, width, 0.5] # left, bottom, width, height
+            lowerarea = [left, 0.1, width, 0.3]
+        else:
+            fig = plt.figure(figsize=(5,5), dpi=300)
+            upperarea = [left, left, width, width] # left, bottom, width, height
+            lowerarea = []
 
         # Upper panel: subjects drifting downwards:
 
@@ -250,7 +255,10 @@ class Collection(object):
         for tick in hax.yaxis.get_ticklines(): 
             tick.set_visible(False) 
         plt.sca(hax)
-        plt.arrow(np.log10(2e-4), np.log10(0.3), 0.0, 0.1, fc="k", ec="k", linewidth=2, head_width=0.2, head_length=0.1)
+        if logscale:
+            plt.arrow(np.log10(2e-4), np.log10(0.3), 0.0, 0.1, fc="k", ec="k", linewidth=2, head_width=0.2, head_length=0.1)
+        else:
+            plt.arrow(np.log10(2e-4), -0.8, 0.0, 0.1, fc="k", ec="k", linewidth=2, head_width=0.2, head_length=0.1)
         # hax.set_axis_off()        
 
         # Now overlay a transparent frame to plot the subjects in:
@@ -259,7 +267,8 @@ class Collection(object):
         upper.set_xlim(swap.pmin,swap.pmax)
         upper.set_xscale('log')
         upper.set_ylim(swap.Ncmax,swap.Ncmin)
-        upper.set_yscale('log')
+        if logscale:
+            upper.set_yscale('log')
         
         # Vertical lines to mark prior and detect/rejection thresholds:
         x = self.thresholds()
@@ -268,25 +277,38 @@ class Collection(object):
         plt.axvline(x=x['rejection'],color='red',linestyle='dotted')
 
[…]

### 2014-09-03 analysis/swap/io.py

@@ -2,7 +2,7 @@
 
 import swap
 
-import os,cPickle
+import os,cPickle,numpy as np
 
 # ======================================================================
 
@@ -16,14 +16,17 @@ import os,cPickle
     COMMENTS
 
     FUNCTIONS
-        writePickle(contents,filename):
+        write_pickle(contents,filename):
 
-        readPickle(filename): returns contents of pickle
+        read_pickle(filename):
 
-        readCatalog(filename,config): returns table, given column names
-                                      in configuration config
+        write_list(sample, filename, item=None):
+        
+        read_list(filename):
+     
+        write_catalog(sample, filename, thresholds, kind=kind):
 
-        rm(filename): silent file removal
+        rm(filename):
 
     BUGS
 
@@ -127,6 +130,12 @@ def write_list(sample, filename, item=None):
     F.close()
 
     return count
+
+# ----------------------------------------------------------------------------
+# Read in a simple list of string items.
+
+def read_list(filename):
+    return np.atleast_1d(np.loadtxt(filename,dtype='string'))
 
 # ----------------------------------------------------------------------------
 # Write out a multi-column catalog of high probability candidates.

### 2014-09-03 analysis/swap/subject.py

@@ -1,11 +1,5 @@
 # ======================================================================
 
-"""
-TODO:
-    Figure out how to let there be multiple lenses in a subject...
-
-"""
-
 import swap
 
 import numpy as np
@@ -73,6 +67,11 @@ class Subject(object):
         Subject.plot_trajectory(axes)
 
     BUGS
+
+
+    FEATURE REQUESTS
+        Figure out how to let there be multiple lenses in a subject...
+
 
     AUTHORS
       This file is part of the Space Warps project, and is distributed
@@ -262,7 +261,7 @@ class Subject(object):
 # ----------------------------------------------------------------------
 # Plot subject's trajectory, as an overlay on an existing plot:
 
-    def plot_trajectory(self,axes):
+    def plot_trajectory(self,axes,highlight=False):
 
         plt.sca(axes[0])
         N = np.linspace(0, len(self.trajectory)/Ntrajectory+1, len(self.trajectory)/Ntrajectory, endpoint=True);
@@ -290,12 +289,26 @@ class Subject(object):
         else:
             facecolour = 'white'
 
-        plt.plot(mdn_trajectory,N,color=colour,alpha=0.1,linewidth=1.0, linestyle="-")
+        if highlight:
+            # Thicker, darker line:
+            plt.plot(mdn_trajectory,N,color=colour,alpha=0.5,linewidth=2.0, linestyle="-")
+        else:
+            # Thinner, fainter line:
+            plt.plot(mdn_trajectory,N,color=colour,alpha=0.1,linewidth=1.0, linestyle="-")
 
         NN = N[-1]
         if NN > swap.Ncmax: NN = swap.Ncmax
-        plt.scatter(mdn_trajectory[-1], NN, edgecolors=colour, facecolors=facecolour, alpha=0.5);
-        plt.plot([mdn_trajectory[-1]-sigma_trajectory_m[-1],mdn_trajectory[-1]+sigma_trajectory_p[-1]],[NN,NN],color=colour,alpha=0.3);
+        if highlight:
+            # Heavier symbol:
+            plt.scatter(mdn_trajectory[-1], NN, edgecolors=colour, facecolors=facecolour, alpha=0.8);
+            plt.plot([mdn_trajectory[-1]-sigma_trajectory_m[-1],mdn_trajectory[-1]+sigma_trajectory_p[-1]],[NN,NN],color=colour,alpha=0.5);
+        else:
+            # Fainter symbol:
[…]

### 2014-09-04 doc/sw-system.tex
\todo items for Phil and Chris
Fixed #43 in discussion section (#44) by adding illustrative images and trajectories. Closed #68 as well, in the process

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{minipage}{\linewidth}
+  \begin{minipage}[t]{0.47\linewidth}
+    \begin{minipage}{0.46\linewidth}
+      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0008wyp_gri.png}
+    \end{minipage}\hfill
+    \begin{minipage}{0.50\linewidth}
+      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0008wyp_stage2_trajectory.png}
+    \end{minipage}
+  \end{minipage}\hfill
+  \begin{minipage}[t]{0.47\linewidth}
+    \begin{minipage}{0.46\linewidth}
+      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0006rkx_gri.png}
+    \end{minipage}\hfill
+    \begin{minipage}{0.50\linewidth}
+      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0006rkx_stage1_trajectory.png}
+    \end{minipage}
+  \end{minipage}
+\end{minipage}
+
+\vspace{\baselineskip}
+
+\begin{minipage}{\linewidth}
+  \begin{minipage}[t]{0.47\linewidth}
+    \begin{minipage}{0.46\linewidth}
+      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0000fgj_gri.png}
+    \end{minipage}\hfill
+    \begin{minipage}{0.50\linewidth}
+      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0000fgj_stage1_trajectory.png}
+    \end{minipage}
+  \end{minipage}\hfill
+  \begin{minipage}[t]{0.47\linewidth}
+    \begin{minipage}{0.46\linewidth}
+      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0003j2s_gri.png}
+    \end{minipage}\hfill
+    \begin{minipage}{0.50\linewidth}
+      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0003j2s_stage1_trajectory.png}
+    \end{minipage}
+  \end{minipage}
+\end{minipage}
+\caption{Illustrative examples of 
+false negatives (blue) and false positives (red) from the classification of
+the \sw CFHTLS training set. The trajectory plot for each of the 4 subjects is
+shown to the right of its image. lefthand panels show the most common types of
+trajectories: short step random walks resulting from no high skill classifiers
+viewing the subject. The righthand panels show examples where higher skill
+classifiers have been involved, causing random walks with longer step lengths
+(top) and catastrophic mis-classifications (bottom right).}
+\label{fig:discuss:performance:trajectories}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Improving performance: reducing incompleteness and impurity}
@@
 
-We first investigate the source of the incompleteness visible in 
-\Fref{fig:results:sample:CP}, by examining the stage 2 false negatives.
-\Fref{fig:discuss:performance:FNgallery} shows N example simulated lenses that
-were missed by the \sw system. In some cases their rejection is
-understandable: the lensed features are faint, or otherwise difficult to see.
-However, in other cases a reasonably obvious lens was passed over. 
-\Fref{fig:discuss:performance:FNtrajectories} shows the probability 
-trajectories of these subjects. \todo{Phil}{Make the FN plots, and look for
-behaviour. Can we see whether the FNs are due to costly mistakes by expert
-classifiers? Or are they just random walking south?}
-
-Is the system's impurity a result of the same behaviour?
-Figures~\ref{fig:discuss:performance:FPgallery}
-and~\ref{fig:discuss:performance:FPtrajectories} show the corresponding
-figures for the false positives -- non-lenses that were incorrectly inferred
-to be lens candidates during stage 2. \todo{Phil}{Make the FP plots, and look
-for behaviour. Can we see whether the FPs are due to costly mistakes by expert
-classifiers? Or are they just random walking south?}
-
-In general, there are three places we can act to improve system performance:
-educating the volunteers, assigning subjects for classification, and
-interpreting the classification data. The plots in this section suggest that
-...
-\todo{Phil}{complete this thought, and update the text below, in the light of
-the FP and the FN figures}
-
-Mistakes by reasonably high skill classifiers cause large jumps in subject
-probability in the wrong direction, as are occasionally visible in the
-trajectory plots in this section. We might wonder whether some of those
-mistakes could have been corrected by the classifiers themselves, had they had
-access to a ``go back'' option. While clearly enabling error reduction, we
-might worry about such a mechanism enabling classifiers to have a guess, then
-go and read the Talk discussion, and then return to the classification
-interface to change their mind to agree with the forum. In fact, this is
-already possible on the current interface -- and indeed, it is not obvious
-that such correlations would necessarily lead to poorer system performance.
-This could be tested by presenting a fraction of the volunteers with a version
-of the site that actively suggested that they take this approach, and then
-tracking the relative performance of ``collaborative'' classifications
-compared with independent ones. We leave this to further work.
+We investigated the source of the incompleteness and impurity visible in 
+\Fref{fig:results:sample:CP}, by examining the stage 2 false negatives and
+false positives. \Fref{fig:discuss:performance:trajectories} shows 2 example
+simulated lenses  that were missed ($\pr(\LENS|C,T) < 10^{-5}$) by the \sw
+system, and 2 example non-lenses that were incoreectly flagged as candidates
+($\pr(\LENS|C,T) > 0.95$) by the \sw system.
+
+In some cases the rejection of the false negatives is understandable: the
+lensed features are faint, or otherwise difficult to see. However, in other
+cases a reasonably obvious lens was passed over.  This mainly seems to be due
+to noise in the system: when only low-skill classifiers view a subject, all
+the updates to its posterior probability are small, and if none are very
+confident about the presence of lensing, the subject follows a random walk
+down its trajectory plot. This can be seen in the top left panel of the
+figure.  The false positives show similar behaviour, for example in the bottom
+lefthand panel of the figure. As well as subjects being ``unlucky'' in this
+way, there are two less common failure modes associated with mistakes made by
+higher skill users, illustrated in the righthand column of the figure. In the
+false negative subject shown in the top right-hand panel, several high skill
+classifiers update the subject upwards in log probability by some way each
+time, but other, comparable skill classifiers mis-classify the system to lower
+probability. If we had retired subjects after crossing a high probability
+detection threshold, this subject would have been correctly identified as a
+lens candidate; instead, it was kept in the system and eventually scattered
+down to retirement. The trajectory looks like a random walk, but with bigger
+steps. The bottom righthand panel shows an example of a final, apparently
+rare, failure mode: we see some short-step random walk behaviour, followed by
+a mis-classification by a very high skill ``expert'' classifier after 20
+classifications that promotes the subject to high probability.
+
+There are a number of places where we can address these problems and
+improve system performance: adding flexibility to the classification
+interface, educating the volunteers, assigning subjects for
+classification, and interpreting the classification data.
+
+We might wonder whether some of  the mistakes made by reasonably high skill
+classifiers could have been corrected by those classifiers themselves, had
+they had access to a ``go back'' option. While clearly enabling error
+reduction, we might worry about such a mechanism enabling classifiers to have
+a guess, then go and read the Talk discussion, and then return to the
+classification interface to change their mind to agree with the forum. In
+fact, this is already possible on the current interface -- and indeed, it is
+not obvious that such correlations would necessarily lead to poorer system
+performance. This could be tested by presenting a fraction of the volunteers
+with a version of the site that actively suggested that they take this
+approach, and then tracking the relative performance of ``collaborative''
+classifications compared with independent ones. We leave this to further
+work.
 
@@
 
-Some trajectories show signs of a random walk problem. Those subjects are
-simply ``unlucky:'' they are only seen by low skill classifiers, and  happen
-to be mis-classified  enough times to cross the retirement threshold (in the
-case of the false negatives) or remain in the system (in the case of the false
-positives). While improved training will help reduce this effect, it is here
-that targeted task assignment could help improve system performance. We
-advertised stage 2 of the current project to all registered users; it was
+However, most identification failures (around 60\%) seem to be due to the
+random walk problem. While improved training will help reduce this effect, it
+is here that targeted task assignment could help improve system performance.
+We advertised stage 2 of the current project to all registered users; it was
 taken up by stage 1 veterans with a broad range of skill, and also picked up a
 significant number of new users who did not have enough time to aquire high
-skill (since stage 2 was quite short): of
-the 1964 volunteers who took part in the stage 2 classification round, only
-774 were veterans from stage 1. \Fref{fig:discuss:performance:stage1vstage2}
-shows how the stage 1 skill maps on to stage 2 skill and contribution...
+skill (since stage 2 was quite short): of the 1964 volunteers who took part in
+the stage 2 classification round, only 774 were veterans from stage 1.
+\Fref{fig:discuss:performance:stage1vstage2} shows how the stage 1 skill maps
+on to stage 2 skill and contribution...
 
 \todo{Phil}{Remake figure to show stage 2 skill vs stage 1 skill with point
-size given by stage 2 contribution. Stage 2 newbies will all have 0 +/- small
-stage 1 skill. Then move this figure to here.}
-
-Thsi figure suggests that there may be some benefit to opening stage 2 on the
+size given by stage 2 contribution. Stage 2 newbies will need to be plotted to
+have (0 +/- small) stage 1 skill, to show up as a cloud.}
+
+This figure suggests that there may be some benefit to opening stage 2 on the
 basis of agent skill, in order to reduce the noise in the system generated by

### 2014-09-04 doc/sw-system.tex
Closed #78, performance discussion subsection  now complete (#44)

@@
 \centering\includegraphics[width=0.9\linewidth]{sw-system-figs/stage2_veteran_contribution.png}
-\caption{Stage 2 agent properties, separating veterans from stage 1 from new
-volunteers. Point size represents total information generated, dashed lines
-are drawn at the mean values for each sample.}
+\caption{Stage 2 classifier skill, as a function of their stage 1 skill.
+Veterans from stage 1  are shown in blue, while new volunteers are shown in
+orange. Point size is proportional to the number of stage 2 classifications
+made, while dashed lines are drawn at the mean values for each sample.
+Restricting stage 2 to classifiers with high stage 1 skill could reduce the
+noise in the system.}
 \label{fig:discuss:performance:stage1vstage2}
@@
 \Fref{fig:discuss:performance:stage1vstage2} shows how the stage 1 skill maps
-on to stage 2 skill and contribution...
-
-\todo{Phil}{Remake figure to show stage 2 skill vs stage 1 skill with point
-size given by stage 2 contribution. Stage 2 newbies will need to be plotted to
-have (0 +/- small) stage 1 skill, to show up as a cloud.}
+on to stage 2 skill and contribution.
 

### 2014-09-04 analysis/make_crowd_plots.py

@@ -176,6 +176,9 @@ def make_crowd_plots(argv):
     effort2 = []
     information2 = []
     
+    # stage 1 skill of stage 2 classifiers:
+    final_skill1 = []
+    
     final_skill_all2 = []
     contribution_all2 = []
     experience_all2 = []
@@ -188,7 +191,9 @@ def make_crowd_plots(argv):
     new_s2_information = []
 
     for ID in bureau2.list():
+
         agent = bureau2.member[ID]
+
         final_skill_all2.append(agent.traininghistory['Skill'][-1])
         information_all2.append(agent.testhistory['I'].sum())
         effort_all2.append(agent.N-agent.NT)
@@ -206,6 +211,10 @@ def make_crowd_plots(argv):
         effort2.append(agent.N-agent.NT)
         information2.append(agent.testhistory['I'].sum())
         experience2.append(agent.NT)
+
+        oldagent = bureau1.member[ID]
+        final_skill1.append(oldagent.traininghistory['Skill'][-1])
+        
 
     experience2 = np.array(experience2)
     effort2 = np.array(effort2)
@@ -407,20 +416,33 @@ def make_crowd_plots(argv):
 
     # Plot #4: stage 2 -- new volunteers vs. veterans: contribution.
 
-    plt.figure(figsize=(10,8))
-    plt.xlim(-10.0,895.0)
+    # PJM: updated 2014-09-03 to show stage 1 vs 2 skill, point size shows effort.
+
+    # plt.figure(figsize=(10,8))
+    plt.figure(figsize=(8,8))
+    # plt.xlim(-10.0,895.0)
+    plt.xlim(-0.02,0.85)
     plt.ylim(-0.02,0.85)
-    plt.xlabel('Stage 2 Contribution $\sum_k \langle I \\rangle_k$ / bits')
+    # plt.xlabel('Stage 2 Contribution $\sum_k \langle I \\rangle_k$ / bits')
+    plt.xlabel('Stage 1 Skill $\langle I \\rangle_{j=N_{\\rm T}}$ / bits')
     plt.ylabel('Stage 2 Skill $\langle I \\rangle_{j=N_{\\rm T}}$ / bits')
 
-    # size = 0.5*effort2
-    size = 20 + 10*information2
-    plt.scatter(contribution2, final_skill2, s=size, color='blue', alpha=0.4)
[…]

### 2014-09-04 doc/sw-system.tex
Closed #70 with some brief discussion of nervous classifers in capacity subsection of discussion

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/early_vs_final_skill.png}
-\caption{Predictability of final skill from early skill (after 10 training
-classifications) in stage 1 agents. The dashed lines enclose 649 agents with
-early skill greater than 0.1 
-who retain final skill of greater than 0.05. Point size is proportional to
-contribution (plus a constant).}
-\label{fig:crowd:skillprediction}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Having seen the importance of the high skill volunteers at both stage 1 and
-stage 2, we might ask, can we predict agent skill after, say, the volunteer
-has experienced 10 training subjects? In \Fref{fig:crowd:skillprediction} we
-plot this ``early skill'' against final skill, for all experienced stage 1
-volunteers. The majority of the crowd shows little correlation, but at the
-high early skill end, some predictability appears. The 649 experienced  stage
-1 volunteers who had early skill greater than 0.1 went on to attain a mean
-final skill of 0.22, with 97\% remaining at skill 0.05 or higher. This
-suggests that it might be worth tracking volunteers' skill as a project
-progresses, in order to encourage those showing an aptitude for the task to
-take part in the more difficult activities, such as stage 2 refinement.
-However, this would not have done a very good job at identifying the 
-volunteers who went on to make the largest contributions: the point size in 
-\Fref{fig:crowd:skillprediction} is proportional to contribution (plus a constant):
-many of the highest contributors showed relatively low skill early on.
-
-\Tref{tab:crowd:contributions} shows the total effort, contribution, skill and
-information generated in both stage 1 and 2 of the CFHTLS project, with the
-total numbers of agents and subjects for comparison.  These numbers allow us
-to quantify the efficiency of the system.  The contribution per classification
-is defined in terms of a hypothetical subject with lens probability of 0.5;
-one bit of information is needed to update such a subject's lens probability
-to either zero or one. This means that a maximally complete classification
-stage would yield a total contribution (summed over all agents) equal to the
-number of subjects. The ratio of this hypothetical optimum to the actual total
-contribution is therefore a measure of the stage's inefficiency. We find our
-inefficiency (by dividing column 2 by column 3) to be 33\% and 17\% in stage 1
-and 2 respectively. In stage 1, this inefficiency is due to the daily
-processing: we were not able to retire subjects fast enough, and so they,
-remained in the system, being over-classified. Indeed, only 3705745
-classifications were needed to retire all the subjects: the ratio of this to
-the total number made is 34\%. (The remaining 1\% is due to not all subjects
-being classified to 1 or 0 probability.) At stage 2, we did not retire any
-subjects at all; the inefficiency in this case was by design, to give everyone
-a chance to appreciate what they had found together!
-
-The total skill of the crowd, computed by summing the skill of all the agents,
-is, similarly, a measure of the effective crowd size: a crowd of perfect
-classifiers would be this size. The stage 1 crowd was equivalent to a team of
-1469.9 perfect classifiers; the stage 2 crowd was equivalent to a team of
-102.4 perfect classifiers.
-
-The total information generated during the survey is harder to interpret,
-because it's exactly the high probability candidates that we leave in the
-system that give rise to most of the information generated. What we can do is
-divide the total information generated by the amount of information it takes
-to classify a \sw subject all the way to the detection threshold (lens
-probability 0.95), divide by this number, and then multiply by the survey
-inefficiency to get a very rough estimate for the effective number of
-detections corresponding to the crowd's contribution. With a prior probability
-of $2\times10^{-4}$, it takes 12.3 bits to make a detection (see
-\Sref{sec:appendix:infogain} in the appendix); the effective
-number of detections contributed by the stage 1 and stage 2 volunteers is then
-2830 and 25 bits respectively. 
-These figures are close to the numbers of detections
-given in column 7 of \Tref{tab:crowd:contributions}. 
-The uncertainty in the interpretation of the
-information generated provides further justification for our focus on the
-expected information gain as a measure of volunteer contribution.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table*}
-\begin{center}
-\caption{Total crowd and subject sample properties from the CFHTLS project.}
-\label{tab:crowd:contributions}
-\begin{tabular}{cccccccc}
-  \hline
-  \hline {Stage} & Subjects & Contribution                          & Agents & Skill      & Classifications          & Candidates & Information \\
-                 & $\Ns$    & $\sum_k^{\Nv} \contribution_k$ (bits) & $\Nv$  & $\sum_k^{\Nv} \skill_k$ (bits) & $\sum_k^{\Nv} \thiseffort$ & $\Ncands$  & $\sum_j^{\Ns}\sum_k^{\Nv} \information_{j,k}$ (bits) \\
-  \hline 
-            1    & $427064$ & $1292016.3$ & $36982$ & $1471.9$ & $10802125$ & $3368$ & $91122.6$ \\
-            2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $90$ &  $1640.4$ \\
-  \hline \hline
-\end{tabular}
-\medskip\\
-\end{center}
-\end{table*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \begin{figure}
+% \centering\includegraphics[width=0.9\linewidth]{sw-system-figs/early_vs_final_skill.png}
+% \caption{Predictability of final skill from early skill (after 10 training
+% classifications) in stage 1 agents. The dashed lines enclose 649 agents with
+% early skill greater than 0.1 
+% who retain final skill of greater than 0.05. Point size is proportional to
+% contribution (plus a constant).}
+% \label{fig:crowd:skillprediction}
+% \end{figure}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% 
+% Having seen the importance of the high skill volunteers at both stage 1 and
+% stage 2, we might ask, can we predict agent skill after, say, the volunteer
+% has experienced 10 training subjects? In \Fref{fig:crowd:skillprediction} we
+% plot this ``early skill'' against final skill, for all experienced stage 1
+% volunteers. The majority of the crowd shows little correlation, but at the
+% high early skill end, some predictability appears. The 649 experienced  stage
+% 1 volunteers who had early skill greater than 0.1 went on to attain a mean
+% final skill of 0.22, with 97\% remaining at skill 0.05 or higher. This
+% suggests that it might be worth tracking volunteers' skill as a project
+% progresses, in order to encourage those showing an aptitude for the task to
+% take part in the more difficult activities, such as stage 2 refinement.
+% However, this would not have done a very good job at identifying the 
+% volunteers who went on to make the largest contributions: the point size in 
+% \Fref{fig:crowd:skillprediction} is proportional to contribution (plus a constant):
+% many of the highest contributors showed relatively low skill early on.
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 
-Inefficiency. Move to truly online system: web app to analyse classifications
-as it goes. Place for weekly offline processing? Recovering false negatives by
-``resurrecting'' subjects that scattered down too soon.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table*}
+\begin{center}
+\caption{Total crowd and subject sample properties from the CFHTLS project.}
+\label{tab:crowd:contributions}
+\begin{tabular}{cccccccc}
+  \hline
+  \hline {Stage} & Subjects & Contribution                          & Agents & Skill      & Classifications          & Candidates & Information \\
+                 & $\Ns$    & $\sum_k^{\Nv} \contribution_k$ (bits) & $\Nv$  & $\sum_k^{\Nv} \skill_k$ (bits) & $\sum_k^{\Nv} \thiseffort$ & $\Ncands$  & $\sum_j^{\Ns}\sum_k^{\Nv} \information_{j,k}$ (bits) \\
+  \hline 
+            1    & $427064$ & $1292016.3$ & $36982$ & $1471.9$ & $10802125$ & $3368$ & $91122.6$ \\
+            2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $90$ &  $1640.4$ \\
+  \hline \hline
+\end{tabular}
+\medskip\\
+\end{center}
+\end{table*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\Tref{tab:crowd:contributions} shows the total effort, contribution, skill and
+information generated in both stage 1 and 2 of the CFHTLS project, with the
+total numbers of agents and subjects for comparison.   These numbers allow us
+to quantify the efficiency of the system.
+
+The contribution per classification is defined in terms of a hypothetical
+subject with lens probability of 0.5; one bit of information is needed to
+update such a subject's lens probability to either zero or one. This means
+that a maximally complete classification stage would yield a total
+contribution (summed over all agents) equal to the number of subjects. The
+ratio of this hypothetical optimum to the actual total contribution is
+therefore a measure of the stage's inefficiency. We find our inefficiency (by
+dividing column 2 by column 3) to be 33\% and 17\% in stage 1 and 2
+respectively. In stage 1, this inefficiency is due to the daily processing: we
+were not able to retire subjects fast enough, and so they, remained in the
+system, being over-classified. Indeed, only 3705745 classifications were
+needed to retire all the subjects: the ratio of this to the total number made
+is 34\%. (The remaining 1\% is due to not all subjects being classified to 1
+or 0 probability.) At stage 2, we did not retire any subjects at all; the
+inefficiency in this case was by design, to give everyone a chance to
+appreciate what they had found together. (An unwanted side effect of this
+policy was noted in \Fref{fig:discuss:performance:stage1vstage2} in the
+previous sub-section.)
+
+It is clear that to increase the efficiency of the system we need to reduce
+the time lag between the classification being made and its outcome being
+analyzed. The optimal way to do this would be to have the web app itself
+analyze the classifications in a fully online system. This is under
+investigation for future projects. With the classification data being analyzed
+in real time, there may still be a place for a daily or weekly offline
+analysis: this could potentially reduce the false negative and false positive
+rates by ``resurrecting'' subjects that had been retired by the online system
+before the agents had time to learn enough about their classifier's high
+skill.
 
@@
 
-Scaling of system. Factors of ten: $10^4$ volunteers, $10^3$ achieve high
-skill, $10^2$ make significant contribution. Good project size is few $10^4$
-subjects, to enable completion by a crowd of this size in short time.
-
-Ways to increase numbers of high-contribution volunteers: 1) increase crowd
-size. Higher exposure through media. Multi-lingual user base - comes with
-problems.  2) Increase engagement rate:  feedback from survey teams.
+Finally, we comment on the size of the first \sw crowd, and how the system
+might be scaled up for future surveys. In \Sref{sec:results:crowd} and 
+\Tref{tab:crowd:contributions}, a rough picture emerged for the \sw crowd of
+it containing a few $10^4$ volunteers, with a few $10^3$ achieving
+considerable skill, and a few $10^2$ having the time to make a significant
+contribution. Slightly more quantitively, we might note that  the total skill
+of the crowd, computed by summing the skill of all the agents, is a measure of
+the effective crowd size, in the sense that a crowd of perfect classifiers
+would be of this size. By this measure,the stage 1 crowd was equivalent to a
+team of 1470 perfect classifiers, while the stage 2 crowd was equivalent to a
+team of 102 perfect classifiers. With this same crowd, we can see that surveys
+providing a few $10^4$ subjects would be completed quickly, if the high
+contribution rate of the current crowd were to be repeated.
+
+There are (at least) two ways in which we might increase the numbers of
+high-contribution volunteers for larger projects in future. The first is
+simply to increase the total crowd size, and hope that a similar fraction of
+volunteers make large contributions. Greater exposure of the website to the
+public through mass media woudl help. Another option is to advertise the
+project to new groups of volunteers by translating the website into other
+languages (something which is now supported by the Zooniverse). A
+multi-lingual user base would come with its own set of challenges, especially
+in terms of volunteers' continuing training and interactions on Talk.
+
+The second way to scale up the number of high contribution classifiers is to
+increase the rate at which new volunteers become dedicated volunteers. Based
+on feedback from the wider \sw community, this could potentially be achieved
+through closer collaboration with the science team. It's also possible that
+the dynamic stage 2 system proposed in the previous section may act as an
+incentive to some volunteers to increase their contribution (while gaining
+skill in order to ``reach'' stage 2). Reducing the rate at which  new
+volunteers lose interest could also play a role. Anecdotally, it seems fairly
+common for new volunteers to be wary of classifying at all, for fear of
+introducing errors. Better explanation of how their early classifications are
+analyzed could help assuage these fears: \Sref{sec:results:crowd} shows that
+effectively down-weighting new users' classifications (by setting their
+agents' initial confusion matrix elements to those of a random classifier)
+leads to best performance, a result which shoudl be of some comfort to the
+nervous volunteer.
 
@@
 
+The total information generated during the CFHTLS project is shown in
+\Tref{tab:crowd:contributions}. Interpreting these numbers is not easy, but we
+might do the following. Dividing this by the amount of information it takes to
+classify a \sw subject all the way to the detection threshold (lens
+probability 0.95), and then multiplying by the survey inefficiency gives us a
+very rough estimate for the effective number of detections corresponding to
+the crowd's contribution: these are 2830 and 25 bits for stages 1 and 2
+respectively.  These figures are close to the numbers of detections given in
+column 7 of the table.  
+% The uncertainty in the interpretation of the total
+% information generated provides some justification for our focus on the
+% expected information gain as a measure of volunteer contribution.
+
 \subsection{Uncertainty in the Agent Confusion Matrices}

### 2014-09-04 doc/acknowledgments.tex
AV acknowledgement

@@
 We are also grateful to Brooke Simmons, David Hogg, XXX and YYY for many useful
-conversations about citizen science and gravitational lens detection. % Need to
-cross-ref with Zooniverse author list
+conversations about citizen science and gravitational lens detection. 
 %
@@
 fellowship, and by the U.S. Department of Energy under contract number DE-AC02-76SF00515.
-% He would like to thank the DotAstronomy community for
-% introducing so many valuable concepts and tools, and David Harris and
-% Roger Davies for valuable conversations about community-building.
 %
-% AV \ldots
+AV acknowledges support from the Leverhulme Trust in the form of a research
+fellowship.
 %
-% AM \ldots
 The work of AM and SM was supported by World Premier International Research
@@
 % 
-The \sw project is open source, and was developed at
+% Other authors.
+%
+The \sw project is open source. 
+The web app was developed at https://github.com/Zooniverse/Lens-Zoo
+while the SWAP analysis software was developed at
 https://github.com/drphilmarshall/SpaceWarps.

### 2014-09-04 doc/sw-system.tex
Finished discussion section, closed #44
Responses to discussion feedback from Anu and AV #68

@@
 We now quantify the performance of the \sw system in terms of the recovery of
-the training set images. \Fref{fig:results:sample:roc} shows receiver
-operating characteristic (ROC) curves for CFHTLS stage 1 and stage 2. These
-plots show the true positive rate (TPR), the number of sims correctly detected
-divided by the total number of sims in the training set, and the false
-positive rate (FPR), the number of duds incorrectly detected  divided by total
-number of duds in the training set, both for a given sample of detections defined by
-a particular probability threshold, which varies along the curves.  In both
-stages, these curves show that true positive rates of  around 90\% were
-achieved, at very low false positive rates. For comparison we show the results
-of an analysis where the classifications of  training images were ignored, and
-none of the agents allowed to learn: they were instead assigned initial values
-of their confusion matrices of 0.75 for each element, which then remained
-constant. This emulates a very simple unweighted voting scheme, where all
-classifications are treated equally. In this case, the TPR remains under 80\%
-in stage 1 and 60\% in stage 2, thus quantifying 
-the benefit of including training
-images and allowing the agents to learn. The choice of initial confusion
-matrix is not very important: the same 0.75 initial values applied to normal,
-learning agents results in a slightly lower TPR than the default case,
-indicating that initializing the system less conservatively results in
-slightly worse performance.
+the training set images. At stage 1, this set contains around 5712 simulated
+lenses, and 450 duds; at stage 2, we used 152 simulated lenses and 201 duds.
+\Fref{fig:results:sample:roc} shows receiver operating characteristic (ROC)
+curves for CFHTLS stage 1 and stage 2. These plots show the true positive rate
+(TPR), the number of sims correctly detected divided by the total number of
+sims in the training set, and the false positive rate (FPR), the number of
+duds incorrectly detected  divided by total number of duds in the training
+set, both for a given sample of detections defined by a particular probability
+threshold, which varies along the curves.  In both stages, these curves show
+that true positive rates of  around 90\% were achieved, at very low false
+positive rates. For comparison we show the results of an analysis where the
+classifications of  training images were ignored, and none of the agents
+allowed to learn: they were instead assigned initial values of their confusion
+matrices of 0.75 for each element, which then remained constant. This emulates
+a very simple unweighted voting scheme, where all classifications are treated
+equally. In this case, the TPR remains under 80\% in stage 1 and 60\% in stage
+2, thus quantifying  the benefit of including training images and allowing the
+agents to learn. The choice of initial confusion matrix is not very important:
+the same 0.75 initial values applied to normal, learning agents results in a
+slightly lower TPR than the default case, indicating that initializing the
+system less conservatively results in slightly worse performance.
 
@@
 results are very similar to the online version that was actually run (solid
-line). However, at stage 2 there seems to be somewhat greater benefit to doing
-the analysis in this way: over 85\% TPR is achieved at zero FPR.
-Alternatively, if one is willing to accept a false positive rate of 5\%, the
-true positive rate rises to over 95\%, showing that some of the sims that were
-missed in the online analysis can be recovered by doing the analysis offline.
-The same is true at stage 1, but to a lower degree.
+line). However, at stage 2 there is marginal evidence of there being greater
+benefit to doing the analysis offline. Over 85\% TPR is achieved at zero FPR
+in the offline analysis , while if one is willing to accept a false positive
+rate of 5\%, the true positive rate rises to over 95\%, showing that some of
+the sims that were missed in the online analysis may be being recovered by
+doing the analysis offline. The same is true at stage 1, but to a lower
+degree. Assuming Poisson statistics for the fluctuations in the numbers of
+recovered lenses, the uncertainty in the measured stage 2 TPR values is around
+8\%, but the online and offline samples are highly correlated, such that the
+uncertainty on the difference between the ROC curves is somewhat less than
+this. Still, a larger validation set is needed to test these algorithmic
+choices more rigorously. At stage 1, high TPR can be measured to better than
+1\%.
 
@@
 \label{sec:discuss}
-
-\todo{Phil}{write discussion (\#44).}
 
@@
 \Fref{fig:results:sample:CP}, by examining the stage 2 false negatives and
-false positives. \Fref{fig:discuss:performance:trajectories} shows 2 example
-simulated lenses  that were missed ($\pr(\LENS|C,T) < 10^{-5}$) by the \sw
-system, and 2 example non-lenses that were incoreectly flagged as candidates
-($\pr(\LENS|C,T) > 0.95$) by the \sw system.
+false positives, and their behaviour as they are classified using the online
+analysis trajectory plots introduced in \Sref{sec:swap}
+(\Fref{fig:swap:subject-trajectories}).
+\Fref{fig:discuss:performance:trajectories} shows 2 example simulated lenses 
+that were missed ($\pr(\LENS|C,T) < 10^{-5}$) by the \sw system, and 2 example
+non-lenses that were incorrectly flagged as candidates ($\pr(\LENS|C,T) >
+0.95$) by the \sw system. While the final stage 2 analysis was done offline,
+these trajectory plots still serve to illustrate the approximate
+classification histories of the subjects.
 
 In some cases the rejection of the false negatives is understandable: the
-lensed features are faint, or otherwise difficult to see. However, in other
-cases a reasonably obvious lens was passed over.  This mainly seems to be due
-to noise in the system: when only low-skill classifiers view a subject, all
-the updates to its posterior probability are small, and if none are very
-confident about the presence of lensing, the subject follows a random walk
-down its trajectory plot. This can be seen in the top left panel of the
-figure.  The false positives show similar behaviour, for example in the bottom
+lensed features are faint, or in some cases, somewhat unrealistic as lenses.
+However, in other cases a reasonably obvious lens was passed over.  This
+mainly seems to be due to noise in the system: when only low-skill classifiers
+view a subject, all the updates to its posterior probability are small, and if
+none are very confident about the presence of lensing, the subject follows a
+random walk down its trajectory plot. This can be seen in the top left panel
+of the figure.
+
+The false positives show similar behaviour, for example in the bottom
 lefthand panel of the figure. As well as subjects being ``unlucky'' in this
@@
 of each classifier's skill -- but one could imagine volunteers {\it choosing}
-to see more training images (still at random) in their stream. Another could
-be to provide more information about what lenses do. In this project, the
-Spotter's Guide was always available on the site, but as a passive background
-resource. We might consider providing more links to this guide in the feedback
-messages shown to the classifiers as they go -- or perhaps extending these
-messages to themselves include more explanations and example images.
+to see more training images (still at random) in their stream. We could also
+experiment with providing greater training rates early on for all volunteers;
+the risk associated with this is that retention rates may drop if too few
+``fresh'' test images are shown early on. Another way of improving the
+training could be to provide more information about what lenses do. In this
+project, the Spotter's Guide was always available on the site, but as a
+passive background resource. We might consider providing more links to this
+guide in the feedback messages shown to the classifiers as they go -- or
+perhaps extending these messages to themselves include more explanations and
+example images. We might also investigate a more dynamic Spotter's Guide: a
+set of manipulable model lenses illustrating all the possible image
+configurations that that those deflectors can make could help volunteers gain
+understanding of what lensed features can look like very quickly. Such a toy
+is under development.
 
@@
 However, most identification failures (around 60\%) seem to be due to the
-random walk problem. While improved training will help reduce this effect, it
-is here that targeted task assignment could help improve system performance.
-We advertised stage 2 of the current project to all registered users; it was
+random walk problem. Short, random direction steps arise from low skill
+classifiers, arising from classifier inexperience (\Sref{sec:results:crowd}). 
+While improved training will help reduce this effect, it is here
+that targeted task assignment could also help improve system performance, by
+bringing higher skill volunteers in to the mix. We
+advertised stage 2 of the current project to all registered users; it was
 taken up by stage 1 veterans with a broad range of skill, and also picked up a
@@
 This figure suggests that there may be some benefit to opening stage 2 on the
-basis of agent skill, in order to reduce the noise in the system generated by
-new and low skill volunteers in this more difficult classification stage. A
-simple implementation of this would be to switch the web app to the stage 2
-version when either a certain stage 1 skill (and/or effort) threshold was
-passed. Good strategy would probably be to switch back to stage 1 after some
-number of stage 2 classifications (to avoid losing the high skill users from
-stage 1 entirely), and also to make it very clear which stage the classifier
-was at (since stage 2 requires more careful attention). This is something we
-plan to experiment with in future.
+basis of stage 1 agent skill, in order to reduce the noise in the system
+generated by new and low skill volunteers in this more difficult
+classification stage.  A simple implementation of this would be to switch the
+web app to the stage 2 version when either a certain stage 1 skill (and/or
+effort) threshold was passed. Good strategy would probably be to switch back
+to stage 1 after some number of stage 2 classifications (to avoid losing the
+high skill users from stage 1 entirely), and also to make it very clear which
+stage the classifier was at (since stage 2 requires more careful attention).
+This is something we plan to experiment with in future.
 
 Finally, there could be some performance gains to be made by improving the
-SWAP agent model, or its implementation. In a future paper we plan to
-investigate the use of the test images as well as the training images in
-learning the agent confusion matrix elements (Davis et al, in preparation).
-One might also consider looking at introducing more conditional dependences in
-these elements, to allow for some classifiers having greater skill in one type
-of lens than another, or, more generally, as a function of lens property (such
-as color, brightness, and image separation). In the current model, all agents
-are considered to be completely independent, whereas in fact we might expect
-there to be significant clustering of the confusion matrix elements. A
-hierarchical model for the crowd, with hyper-parameters describing the
-distribution of confusion matrix elements across the population, may well
-accelerate the agent learning process by including the notion of one agent
-being likely to be similar to its neighbours. Finally, it is worth noting that
-the model of \citet{IBCC} explicitly avoids the assumption of the agent
-confusion matrix elements being constant in time, allowing the development of
-volunteer skill to be more accurately tracked -- and that they did see some
-time-evolution in the supernova zoo classifiers' skill. Finding a way to
-incorporate such a learning model into SWAP, while retaining its statistically
-online character is an interesting challenge for future work.
+SWAP agent model, or its implementation. Low skill is typically a result  of
+inexperience (\Sref{sec:results:crowd}), but it could be the agent that is
+inexperienced as well as the classifier or its agent. In a future paper we
+plan to investigate the use of the test images as well as the training images
+in accelerating the agent's learning (Davis et al, in preparation). We also
+plan to investigate the use of offline analysis at Stage 1, for the same
+reason (see also \Sref{sec:discuss:efficiency} below.) 
+One might also consider looking at
+introducing more conditional dependences in the confusion matrix elements, to
+allow for some classifiers having greater skill in spotting one type of lens
+than another, or, more generally, as a function of lens property (such as
+color, brightness, and image separation). In the current model, all agents are
+considered to be completely independent, whereas in fact we might expect there
+to be significant clustering of the confusion matrix elements. A hierarchical
+model for the crowd, with hyper-parameters describing the distribution of
+confusion matrix elements across the population, may well accelerate the agent
+learning process by including the notion of one agent being likely to be
+similar to its neighbours. Finally, it is worth noting that the model of
+\citet{IBCC} explicitly avoids the assumption of the agent confusion matrix
+elements being constant in time, allowing the development of volunteer skill
+to be more accurately tracked -- and that they did see some time-evolution in
+the supernova zoo classifiers' skill. Finding a way to incorporate such a
+learning model into SWAP, while retaining its statistically online character
+is an interesting challenge for future work.
 

### 2014-09-08 doc/sw-cfhtls.tex
Defined RF sample in paper, numbers in Gavazzi et al don't match those from SQL queries, emailing RG. #69

@@
 
-\subsection{Known \cfhtls lens samples}
+\subsection{Existing \cfhtls lens samples}
 \label{sec:data:kls}
 
-The \cfhtls data has been searched for lenses using semi-automated
-algorithms, primarily, in the $g$ band which is optimal for finding
-lenses. Here, we briefly mention the lens samples which were known to
-the authors prior to the lens search with \sw.
+The \cfhtls data has been searched for lenses using semi-automated algorithms,
+primarily, in the $g$ band where the predominantly  faint blue  source
+galaxies are bright compared to the predominantly red deflector galaxies.
+Here, we briefly mention the lens samples which were known to the authors
+prior to the lens search with \sw.
 
-At galaxy-scales, there are two main types of lens searches. The
-RingFinder \citet{Gavazzi2014} was used for finding compact rings or arcs
-around centers of isolated and massive early-type galaxies. By
-subtracting the PSF-matched i-band images from the g-band, the
-algorithm looks for excess flux in the bluer g-band which is typical of
-the distant lensed star forming galaxies. An object detector measures
-the properties of these residual blue features and candidates meeting a
-length-width ratio and tangential alignment criteria are then visually
-inspected to form the final sample. This rings sample consists of 39
-confirmed lenses and 17 promising candidates.
+At galaxy-scales, we focus on two primary lens searches. The RingFinder
+\citep{Gavazzi2014} was used for finding compact rings or arcs around centers
+of isolated and massive early-type galaxies. By subtracting the PSF-matched
+$i$-band images from the $g$-band images, the algorithm looks for excess flux
+in the bluer $g$-band. An object detector measures the properties of these
+residual blue features, and candidates meeting length-width ratio and
+tangential alignment criteria are then visually inspected to form the final
+sample. \citet{Gavazzi2014} first selected some 638,000 targets as either
+photometrically-classified early type galaxies, or objects selected to have
+red centers and blue outer parts. 14370 were found to show detectable blue
+residuals, and 2524 were visually inspected, having passed the automatic
+feature selection process. This led to a sample of 42 good quality
+(\texttt{q\_flag} = 3) and 288 medium quality (\texttt{q\_flag} = 2) lens
+candidates. In addition to this well defined sample, \citet{Gavazzi2014}
+reported a further 71 serendipitously detected lens candidates. 
+From this sample of ``RingFinder candidates,'' the SL2S team found, during
+their follow-up campaign, 39 confirmed lenses (and 17 promising
+candidates). We use this sample of 39 ``confirmed RingFinder lenses'' in our
+completeness analysis.
+
+\todo{Phil}{check with RG about SQL queries for the RF candidates.
+\texttt{q\_flag = 3} returns 55, not 42, systems, and 
+\texttt{q\_flag = 3} returns 346, not 288, systems. This is all issue \#69}
 
@@
 
-For the purpose of transparency, the volunteers participating in
-\sw-\cfhtls lens search were made aware of these known lens samples. Images
-containing the lenses from these lens samples were labelled so in the
-forum Talk where volunteers have the opportunity to discuss their
-findings with other volunteers and the science team.
+For the purposes of transparency and to help a little with their training, 
+the volunteers participating in \sw-\cfhtls lens search were made aware of
+these known lens samples. Images containing the systems from the above samples
+were labelled as ``Known Lens Candidates'' in the Talk forum, where volunteers
+have the opportunity to discuss their findings with other volunteers and the
+science team.
 

### 2014-09-08 doc/sw-cfhtls.tex
Solved it - as in RG's email, you have to select T06 as well as q_flag = 3 or 2. Closed #69

@@
 photometrically-classified early type galaxies, or objects selected to have
-red centers and blue outer parts. 14370 were found to show detectable blue
-residuals, and 2524 were visually inspected, having passed the automatic
-feature selection process. This led to a sample of 42 good quality
-(\texttt{q\_flag} = 3) and 288 medium quality (\texttt{q\_flag} = 2) lens
-candidates. In addition to this well defined sample, \citet{Gavazzi2014}
-reported a further 71 serendipitously detected lens candidates. 
-From this sample of ``RingFinder candidates,'' the SL2S team found, during
-their follow-up campaign, 39 confirmed lenses (and 17 promising
+red centers and blue outer parts, from the T06 CFHTLS data release catalogs. 
+14370 were found to show detectable blue residuals, and 2524 were visually
+inspected, having passed the automatic feature selection process. This led to
+a sample of 42 good quality (\texttt{q\_flag} = 3) and 288 medium quality
+(\texttt{q\_flag} = 2) lens candidates. In addition to this well defined
+sample, \citet{Gavazzi2014} reported a further 71 serendipitously detected
+lens candidates.  From this sample of ``RingFinder candidates,'' the SL2S team
+found, during their follow-up campaign, 39 confirmed lenses (and 17 promising
 candidates). We use this sample of 39 ``confirmed RingFinder lenses'' in our
 completeness analysis.
-
-\todo{Phil}{check with RG about SQL queries for the RF candidates.
-\texttt{q\_flag = 3} returns 55, not 42, systems, and 
-\texttt{q\_flag = 3} returns 346, not 288, systems. This is all issue \#69}
 

### 2014-09-12 analysis/SWAP.py
record old PL, PD, and probabilities

@@ -435,7 +435,9 @@ def SWAP(argv):
             # This is a bit hackish: update mean_probability,
             # median_probability, and do the rejection threshold stuff
             subject = sample.member[ID]
+            subject.online_mean_probability = subject.mean_probability
             subject.mean_probability = offline_probabilities[ID]
+            subject.online_median_probability = subject.median_probability
             subject.median_probability = offline_probabilities[ID]
             # ripped from subject.py
             if subject.mean_probability < subject.rejection_threshold:
@@ -477,7 +479,9 @@ def SWAP(argv):
                 continue
             # update PL, PD, then update_skill
             agent = bureau.member[ID]
+            agent.online_PL = agent.PL
             agent.PL = offline_bureau[ID]['PL']
+            agent.online_PD = agent.PD
             agent.PD = offline_bureau[ID]['PD']
             agent.update_skill()
 

### 2014-09-12 analysis/SWAP.py
record old PL, PD, and probabilities

@@ -431,6 +431,7 @@ def SWAP(argv):
             # just in case any IDs didn't get into offline somehow?!
             if ID not in offline_probabilities:
                 sample.member.pop(ID)
+                print "SWAP: offline popping this ID: ,"ID
                 continue
             # This is a bit hackish: update mean_probability,
             # median_probability, and do the rejection threshold stuff

### 2014-09-12 doc/sw-extended.tex
added sw-extend!

--- 2014-09-04 doc/sw-system.tex
@@
 \title[\sw]
-{\SW: Crowd-sourcing the Discovery of Gravitational Lenses}
-
-\author[Marshall et al.]{%
+{\SW Extended! Snappy Titles!}
+
+\author[Davis et al.]{%
   \input{sw-system-authors.tex}
@@
 
-\date{to be submitted to MNRAS}
+\date{to be submitted to ?!?!}
 \pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2014}
@@
 
-\sw is a web-based service that enables the discovery of strong gravitational
-lenses in wide-field imaging surveys by large numbers of people. Carefully
-produced color composite images are displayed to volunteers via a
-classification interface which records their estimates of the positions of
-candidate lensed features. Simulated lenses, and expert-classified non-lenses,
-are inserted into the image stream at random intervals; this training set is
-used to give the volunteers feedback on their performance, and to estimate a
-dynamically-updated probability for any given image to contain a lens. Low
-probability systems are retired from the site periodically, concentrating the
-sample towards a set of candidates; this ``stage 1'' set is then re-classified
-by the volunteers in a second  refinement stage. Analyzing the classification
-of the training set, we predict that the first stage alone should yield a
-sample that is C\% complete, while leading to the rejection of R\% of the
-initial target sample. Having divided the 150 square degree CFHTLS imaging
-survey into 430000 overlapping 70 by 70 arcminute tiles and displayed them on
-the site, we were joined by 33000 volunteers who contributed X million image
-classifications over the course of N months. The sample was reduced to 3500
-stage 1 candidates; these were then refined to yield a sample of 1400
-candidates rankable by their stage 2 probability. We expect this sample to be
-X\% complete and Y\% pure at a threshold of 95\% classification probability.
-We find that, on average, and given the assumptions we make in our analysis,
-we need 9 classifications per image during the first stage, X in the second.
-We estimate the mean information contributed per person to be X bits, over a
-session lasting, on average, N classifications per volunteer, and present the
-highly skewed distributions of these quantities. We comment on the scalability
-of the \sw system to the wide field survey era, and its potential to operate
-beyond its design as a supervised classification system.
-
-\todo{Phil}{revisit abstract (\#29).}
+\todo{Chris}{Do abstract!}
 
@@
 
-% Scientific motivation. Applications of lenses: group-scale arcs,
-% galaxy-galaxy lenses, lensed quasars.
-
-Strong gravitational lensing -- the formation of multiple, magnified images of
-background objects due to the deflection of light by  massive foreground
-objects -- is a very powerful astrophysical tool, enabling a wide range of
-science projects. The image separations and distortions provide information
-about the mass distribution in the lens \citep[e.g.][]{AugerEtal2010,
-SonnenfeldEtal2012,SonnenfeldEtal2013}, including on sub-galactic scales
-\citep[e.g.][]{Dalal+Kochanek2002,VegettiEtal2010,HezavehEtal2013}. Any
-strong lens can provide magnification of a factor of 10 or more, providing a
-deeper, higher resolution view of the distant universe through these ``cosmic
-telescopes'' \citep[e.g.][]{StarkEtal2008,NewtonEtal2011}. Lensed quasars enable
-cosmography via the time delays between the multiple images' lightcurves
-\citep[e.g.][]{TewesEtal2013,SuyuEtal2013}, and study of the accretion disk itself
-through the microlensing effect \citep[e.g.][]{PoindexterEtal2008}. All of these
-science projects would benefit from being able to draw from a larger sample of
-lenses.
-
-In the last decade the numbers of detections of these rare cosmic alignments
-has increased by an order of magnitude, thanks to wide field surveys such as
-CLASS \citep[e.g.]{BrowneEtal2003}, SDSS \citep[e.g.][]
-{BoltonEtal2006,AugerEtal2010b,TreuEtal2011,InadaEtal2012}, CFHTLS
-\citep[e.g.][]{MoreEtal2012,GavazziEtal2014}, Herschel
-\citep[][]{NegrelloEtal2014} and SPT \citep[e.g.][]{VieiraEtal2013}, among
-others.  As the number of known lenses has increased, new types have been
-discovered, leading to entirely new investigations. Compound lenses
-\citep{GavazziEtal2008,CollettEtal2012} and lensed supernovae
-\citep{QuimbyEtal2014} are good examples of this.
-
-% Problem of rarity. Imaging surveys. Problem of purity/false positives.
-% Review of progress to date. Methods in SL2S, SQLS. Contrast with SLACS.
-
-Because they are rare, strong lenses are expensive to find. The most efficient
-searches to date have made use of relatively clean signals such as the
-presence of emission or absorption features at two distinct redshifts in the
-same optical spectrum \citep[e.g.][]{BoltonEtal2004}, or the strong
-``magnification bias'' towards detecting strongly-lensed sources in the sub-mm
-waveband \citep[e.g.][]{NegrelloEtal2010}. Such searches have to be efficient,
-because they require expensive high resolution imaging follow-up; consequently
-they have so far produced yields in the tens to hundreds. An alternative approach
-is to search images of sufficiently high resolution and color contrast, and
-confirm the systems as gravitational lenses by modeling the survey data
-themselves \citep[][]{MarshallEtal2009}. Several square degrees of HST images
-have been searched, yielding several tens of galaxy-scale lenses
-\citep[e.g.][]{MoustakasEtal2007,FaureEtal2008,Jackson2008,MoreEtal2012,
-PawaseEtal2014}.
-Similarly, searches of over a hundred square degrees of CFHT Legacy Survey
-ground-based imaging, also with sub-arcsecond image quality, have revealed a
-smaller number of wider image separation group-scale systems
-\citep[e.g.][]{CabanacEtal2007,MoreEtal2012}. Detecting galaxy-scale lenses from
-the ground is hard, but feasible albeit lower efficiency and requiring HST or
-spectroscopic follow-up to confirm the candidates as lenses
-\citep[e.g.][]{GavazziEtal2014}.
-
-% Scaling to wide field era. Automated methods: problems. Need for good
-% training sets. Need for quality control: always present.
-
-How can we scale these lens searches up to imaging surveys covering a hundred
-times the sky area, such as the almost-all sky surveys planned with LSST and
-Euclid, while reducing our dependence on expensive follow-up confirmation
-observations? There are two approaches to detecting lenses in imaging surveys.
-The first one is robotic: automated analysis of object catalogs and/or the
-survey images. The candidate samples produced by these methods have, to date,
-not been of high purity  \citep[see
-e.g.][]{MarshallEtal2009,MoreEtal2012,GavazziEtal2014}, with visual inspection by
-teams of humans still required to narrow down the robotically-generated
-samples. In this approach, the image data may or may not be explicitly
-modelled by the robots as if it contained a gravitational lens, but the visual
-inspection can be thought of as a ``mental modeling'' step. Systems classified
-by an inspector to be good lens candidates are deemed as such because the
-features in the image can be explained by a model of what gravitational lenses
-do contained in the inspector's brain. The second approach simply cuts out the
-robot middleman: \citet{FaureEtal2008,Jackson2008} and \citet{PawaseEtal2014}
-all performed entirely visual searches for lenses in HST imaging.
-
-Visual image inspection seems, at present, unavoidable at some level when
-seraching for gravitational lenses. The technique has some drawbacks, however.
-First is that humans are only humans, and they make mistakes. The solution to
-this is to operate in teams, providing multiple classifications of the same
-images in order to catch errors and correct them. Second, and relatedly, is
-that humans get tired. With a well-designed classification interface, a human
-might be able to inspect images at a rate of one astronomical object per
-second (provided the majority are indeed uninteresting). At $10^4$ massive
-galaxies, and 10 lenses, per square degree, visual lens searches in good
-quality imaging data are limited to a few square degrees per inspector per
-day. Scaling to thousands of square degrees therefore means either robotically
-reducing the number of targets for inspection, or increasing the number of
-inspectors, or both.
-
-For example, a $10^4$ square degree survey containing $10^8$
-photometrically-selected massive galaxies and $10^5$ lenses could only be
-searched by 10 inspectors at a mean rate of 1 galaxy per second and 10
-inspections per galaxy in about 14 years. Reducing the inspection time by a
-factor of 400 to two weeks would require a robot to reduce the target sample
-to 25 per square degree. However, at this point the required purity, 40\%,
-would very likely require the average classification time per object to be
-more like 10 seconds per object. Hiring 10 inspectors to assess complex images
-full time full time for five months may not be the most cost-effective or
-reliable strategy. Alternatively, a team of $10^6$ inspectors could, in
-principle, make the required $10^9$ image classifications, $10^3$ each, in a
-few weeks; robotically reducing the target list would lead to a proportional
-decrease in the required team size.
-
-Systematic detection of rare astronomical objects by such ``crowd-sourced''
-visual inspection has recently been achieved by the online citizen science
-project PlanetHunters \citep{SchwambEtal2012}. PlanetHunters was designed to
-enable the discovery of transiting exoplanets in data taken by the Kepler
-satellite; a community of N inspectors from the general public found, after
-each undergoing a small amount of training, N new exoplanet candidates by
-visual inspection of the Kepler lightcurves that were presented in a custom
-web-based classification interface. The older Galaxy Zoo morphological
-classification project \citep{LintottEtal2008} has also enabled the discovery
-of rare objects, via its flexible inspection interface and discussion forum
-\citep{LintottEtal2009}. Indeed, several of us (AV,EB,CC,TJ,CM,LW) were active
-in an informal Galaxy Zoo gravitational lens search, an experience which led
-to the present hypothesis that a systematic online visual lens search could be
-successful.
-
-In this paper, we describe the \sw website, an online system that enables 
-crowd-sourced gravitational lens detection by inviting volunteers to classify
-astronomical survey images as containing lens candidates or not.  In a
-companion paper (More et al, in preparation, herafter \papertwo) we will
-present the new gravitational lenses discovered in our first experimental lens
-search, and begin to investigate the differences between lens detections made
-in \sw and those made with automated techniques. Here though, we try to answer
-the following questions:
-
-\begin{itemize}
-
-\item How reliably can we find gravitational lenses using the \sw
-system? What is the completeness of the sample produced?
-
-\item How noisy is the system? What is the purity of the sample
-produced?
-
-\item How quickly can lenses be detected, and non-lenses be rejected?
-How many classifications, and so how many volunteers are needed per target?
-
-\item What can we learn about the scalability of the crowd-sourcing approach?
-
-\end{itemize}
-
-Our basic method in this paper is to analyze the performance of the \sw system
-on a ``training set'' of simulated lenses and known non-lenses. This allows us
-to estimate completeness and purity with respect to gravitational lenses that
-have the same properties of the training set. In \papertwo we carry
-out similar tests but with a sample of known (real) lenses {\it in situ}.
-
-This paper is organised as follows.  In \Sref{sec:design} we introduce the \sw
-classification interface and the volunteers who make up the \sw
-collaboration,  explain how we use training images, and describe our two stage
-candidate selection strategy. We then briefly introduce, in \Sref{sec:data}
-the particular dataset used in the first experimental tests of the \sw system,
-and how we prepared the images prior to displaying them in the web interface.
-In \Sref{sec:swap} we describe our methodology for interpreting the
-classifications made by the volunteers, and then present the results of system
-performance tests  made on the training images in \Sref{sec:results}.  We
-discuss the implications of our results for future lens searches in
-\Sref{sec:discuss} and draw conclusions in \Sref{sec:conclude}.
-
 % \section{Introduction}
 % \label{sec:intro}
-% \section{Experiment Design}
-% \label{sec:design}
+% \section{Offline \SW}
+% \label{sec:offline}
+% \subsection{Formalism}
+% \label{sec:offline:formalism}
 % \subsection{Training}
 % \label{sec:design:training}
-% \subsection{Stage 1: Initial Classification}
-% \label{sec:design:stage1}
-% \subsection{Stage 2: Refinement}
-% \label{sec:design:stage2}
-% \section{Data}
-% \label{sec:data}
-% \subsection{The CFHT Legacy Survey}
-% \label{sec:data:CFHTLS}
-% \subsection{Image Presentation}
-% \label{sec:data:display}
-% \section{Classification Analysis}
-% \label{sec:swap}
 % \section{Results}
 % \label{sec:results}
-% \subsection{Crowd Properties}
-% \label{sec:results:crowd}
-% \subsection{Sample completeness and purity}
-% \label{sec:results:sample}
 % \section{Discussion}
@@
 
-\section{Experiment Design}
-\label{sec:design}
-
-The basic steps of a visual search for gravitational lenses are: 1) prepare
-images, 2) display them to an inspector, 3) record the inspector's
-classification of each image (as, for example, containing a lens candidate or
-not) and 4) analyzing those classifications (and all others) in order to
-produce a final candidate list. We describe step 1 in \Sref{sec:data} and step
-4 in \Sref{sec:swap}. In this section we take a volunteer's eye view and
-begin by describing the \sw classification interface, the crowd of volunteers,
-and the interactions between the two.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/sw-screengrab-marker+feedback.png}
-\caption{Screenshot of the \sw classification interface.}
-\label{fig:screenshot}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Formalism}
+\label{sec:formalism}
+
+\sw keeps track of the following parameters:
+\begin{itemize}
+  \item{$x_{ij}$, the classification the $i$-th volunteer made of the $j$-th
+      image. $x_{ij}$ may take on three values:
+      0, 1, or empty. Since volunteers do not see most images, the vast
+    majority of $x_{ij}$ are blank.}
+    \item{$PD_{i}$, the probability, given that the image is a dud, that
+        $i$-th the volunteer will classify it as a dud. The
+      probability, given that the image is a dud, that the volunteer will
+    classify it as a lens follows as $1 - PD_{i}$.}
+  \item{$PL_{i}$, the probability, given that the image is actually a
+      lens, that the $i$-th volunteer will classify it as being a lens. The
+      probability, given that the image is a lens, that the volunteer will
+    classify it as a dud follows as $1 - PL_{i}$.}
+  \item{$p_j$, the probability that
+      the $j$-th image $z_{j}$ is a lens given the current observations and skills of the
+  volunteers who classified it.}
+  \item{$p^{0}$, the prior probability that an object is a lens.}
+\end{itemize}
 
@@
 
-\subsection{Classification Interface}
-\label{sec:design:interface}
-
-A screenshot of the \sw classification interface (CI) is shown in
-\Fref{fig:screenshot}. The CI is the centrepiece of the \sw website,
-\texttt{http://spacewarps.org}; the web application is written in
-coffeescript, css and html and follows the general design of others written by
-the Zooniverse team.\footnote{The \sw web application code is open source and
-can be accessed from \texttt{https://github.com/zooniverse/Lens-Zoo}}  The
-focus of the CI is a large display of the current pre-prepared PNG image of
-the ``subject'' being inspected.   When the image is clicked on by the
-volunteer, a marker symbol appears where the pointer was. Several markers can
-be placed.  The next image moves rapidly in from a queue formed at the right
-hand side of the screen when the ``Finished marking'' button is pressed. At
-the same time, the positions of the markers are written out to the
-classification database, in an entry that also stores the ID of the subject,
-the username (or IP address) of the volunteer, a timestamp and some other
-metadata.
-
-Gravitational lenses are rare: typically, most of the images will not contain
-a lens candidate, and these need to be quickly rejected by the inspector. The
-queue allows several images to be pre-loaded while the volunteer is
-classifying the current subject, and the rapid movement is designed to
-encourage volunteers to classify rapidly.
-
-For the more interesting subjects, the CI offers two features that  enable
-further investigation of the subjects. First is the ``Quick Dashboard'' (QD) a
-more advanced image viewer. This allows the viewer to compare three different
-contrast and color balance settings, to help bring out subtle features, and to
-zoom in on interesting regions of the image to assess small features. Markers
-can be placed in the Quick Dashboard just the same as in the main CI image
-viewer. The second is a link to that subject's page in the project discussion
-forum, \texttt{http://talk.spacewarps.org} (known as ``Talk''). Here,
-volunteers can discuss the features they have seen either before they submit
-their classification, or after, if they ``favorite'' the subject. There is no
-``back'' button: each volunteer may only classify a given subject once.
-However, the presence of an option to see what others think about any given
-subject before submitting your own classification means that the
-classifications may not be  strictly independent; the advantage of this system
-is that volunteers can learn from others what constitutes a good lens
-candidate. In practice, we might expect this to be a relatively unimportant
-educational resource, given the explicit training we provide for the
-volunteers, which we describe in the next section.
+\subsection{The Online System}
+\label{sec:formalism:online}
+In \sw, this is fixed at $2 \times 10^{-4}$, or the expectation that
+around 100 lenses will be found in 430,000 images. Because \sw is an online
+system that constantly reevaluates most of the above parameters (except $p_0$
+and any non-blank $x_{ij}$) in order to promote likely lenses\footnote{Note
+that this does not change the probability that a volunteer will actually draw
+said image.} or to retire likely duds,\footnote{Images whose probability of
+being a lens drops below a certain threshold are removed from the active
+dataset.} we augment $p$, $PL$, and $PD$ as $p_j^k$, the evaluation of
+$p_j$ at time $k$. \sw uses Bayes' Theorem to update $p_j^{(k + 1)}$ for
+some new evaluation $x_{ij}$\footnote{There is no superscript for $x_{ij}$
+because each user only sees an image once.}:
+\begin{align}
+  p_j^{(k + 1)} &= \left ( \frac{x_{ij} PL_{i}^{k}
+  }{PL_{i}^{k} p_j^k + (1 - PD_{i}^{k})(1 -
+  p_j^k)}
+  \right. \notag \\ & \; \left . +
+  \frac{(1 - x_{ij}) (1 - PL_{i}^{k})
+  }{(1 - PL_{i}^{k}) p_j^k + PD_{i}^{k}(1 -
+  p_j^k)} \right ) p_j^k \ ,
+\end{align}
+The first term on the right hand side is the probability update for evaluating
+the object to be a lens, while the second term is the probability that the
+image is a lens if the volunteer evaluates it to be a dud.  (For example, an
+obtuse volunteer who always perfectly incorrectly classifies an image will
+actually change the probability exactly the same as one who always perfectly
+correctly classifies an image, given that the estimate of the obtuse
+volunteer's skill ($PL_{i} = 0$) is accurate.)
+
+\sw only updates the volunteer's $PL_{i}$ and $PD_{i}$ after volunteer $x_i$
+classifies a training image:
+
+\begin{align}
+  PL_{i}^{(k + 1)} &= \frac{PL_{i}^{k} (NL_{i}^{k} + M) + \mathbb{I}[x_{ij} =
+  z_{j}]}{NL_{i}^{k} + M + 1} \\
+  PD_{i}^{(k + 1)} &= \frac{PD_{i}^{k} (ND_{i}^{k} + M) + \mathbb{I}[x_{ij} =
+  z_{j}]}{ND_{i}^{k} + M + 1}
+\end{align}
+where $ND_{i}^{k}$ and $NL_{i}^{k}$ refer to the number of training lenses and
+training duds observed by the $i$-th volunteer at time $k$, $z_{j}$ refers
+to the true state of the $j$-th image, and $M = 4$ is a smoothing factor
+empirically derived to smooth the skill classification of new volunteers.
+
+With these update rules plus an initialization of $PD_{i} = PL_{i} = 0.5$ and
+$p^{0} = 2 \times 10^{-4}$, the online update system is fully specified.
 
@@
 
-\subsection{Training}
-\label{sec:design:training}
-
-Gravitational lenses are unfamiliar objects to volunteers who are new
-to the site. New volunteers need to learn what lenses look like as quickly as
-possible, so that they can contribute informative classifications. They also
-need to learn what lenses do not look like, in order to reduce the false
-positive detection rate. There are three primary mechanisms in the \sw system
-for teaching the volunteers what to look for. These are, in the order in which
-they are encountered, an inline tutorial, instant feedback,
-and a ``Spotter's Guide.''
-
-\subsubsection{Inline Tutorial}
-
-New volunteers are welcomed to the site with a very short tutorial, in which
-the task is introduced, a typical image containing a simulated lens is
-displayed, and the marking procedure walked through, using pop-up message
-boxes. Subsequent images gradually introduce the more advanced
-features of the classification interface (the QD and Talk buttons), also using
-pop-up messages. The tutorial was purposely kept as short as possible so as to
-provide the minimal barrier to entry.
-
-\subsubsection{Training Subjects and Instant Feedback}
-
-The second image viewed after the initial tutorial image is already a survey
-image, in order to get the volunteers engaged in the real task as quickly as
-possible. Training continues beyond the first image tutorial through
-``training subjects'' inserted randomly into the stream.  These training
-subjects are either simulated lenses (known as ``sims''), or survey images
-that were expert-classified (by AV, AM and PM) and found not to contain any
-lens candidates (these images are known as ``duds''). The tutorial explains
-that the volunteers  will be shown such training images. They are also
-informed that they will receive instant feedback about their performance after
-classifying (blind) any of these training subjects. Indeed, after a volunteer
-finishes marking a training subject and hits ``Finished marking,'' a pop-up
-message is generated, containing either positive feedback for a successful
-classification (for example, ``Well done! You spotted a simulated lens,'' as
-in \Fref{fig:screenshot}) or negative feedback for an unsuccessful one (for
-example, ``There is no gravitational lens in this field!'')
-
-The initial frequency of the training images is set to be two in five;
-subjects are drawn randomly from the pool of training images with this
-frequency. The pool contains equal numbers of sims and duds, and the draw is
-made without replacement (for that volunteer). As the number of
-classifications made by a volunteer increases, this frequency is decreased, to
-$2/(5\times2^{(\textrm{int}(N_c/20)+1)/2})$ ($\approx 0.3$ for the second 20
-subjects, $0.2$ for the third 20 subjects, and so on).
-
-This training regime means that in the first 60 images viewed, each volunteer
-is shown (on average) 9 simulated gravitational lenses, and 9 empty fields. 
-This is a much higher rate than the natural one: to try and avoid this leading
-to over-optimism among the inspectors (and a resulting high false positive
-rate), we display the current ``Simulation Frequency'' on the classification
-interface (``1 in 5'' in \Fref{fig:screenshot}) and maintain the consistent
-theme in the feedback messages that lenses are rare.
-
-In \Fref{fig:training-gallery} we show 12 example training images from the
-first \sw project (\Sref{sec:data} below).
-
-\todo{Phil, Aprajita}{Make gallery of 6 stage 2 sims and 6 stage 2 duds, to
-give the reader a feel for what the sims look like, and also how the images
-were presented, stretch and scale-wise.}
-
-\subsubsection{Spotter's Guide}
-
-The instant feedback provides real-time educational responses to the
-volunteers as they start classifying; as well as this dynamic system, \sw
-provides a static reference work for volunteers to consult when in doubt about
-how to perform the task. This ``Spotter's Guide'' is a set of webpages showing
-example lenses, both real and simulated, and also some common false positives,
-drawn from the pool of survey images. The non-lenses were identified by three
-of us (AV, AM and PM) while inspecting a small set of survey images in order
-to define the ``dud'' training images. For easy reference, the lenses are
-divided by type (for example, ``lensed galaxies,'' ``lensed quasars'' and
-``cluster lenses''), as are the false positives (for example, ``Rings and
-Spirals,'' ``Mergers,'' ``Artifacts'' and so on). The example images are
-accompanied by explanatory text. The Spotter's Guide is reached via a button
-on the left hand side, or the hyperlinked thumbnail images of the ``Quick
-Reference'' provided on the right hand side, of the classification interface.
-
-Most of the text of the Spotter's Guide focuses on what lenses do or don't do;
-the website ``Science page'' contains a very brief introduction to how
-gravitational lenses work, which is fleshed out a little on the ``FAQ'' page. 
-This also contains answers to frequently asked questions about the interface
-and the task set.
+\subsection{An Offline Expectation Maximization Approach}
+\label{sec:formalism:em}
+Using the above notation but expanding $p^{0}$ to $p_{ij}^{0}$ (allowing, e.g. for
+the distribution of training images to differ for each volunteer, perhaps based on
+the number of images they have observed, or to allow a particular image to be
+more likely to be drawn), the complete log-likelihood for this model may be
+specified:
+\begin{multline}
+  \mathrm{CLL}(x_{ij}, z_{j}, PL_{i}, PD_{i}, p_{ij}^{0}) \\ = \sum_{i} \sum_{j \in \Omega_i} x_{ij} z_{j} \log PL_{i} +
+      (1 - x_{ij}) z_j \log (1 -
+      PL_{i}) \\ + (1 - x_{ij}) (1 - z_j) \log PD_{i} + x_{ij} (1 - z_j) \log (1 - PD_{i}) \\ + z_j \log p_{ij}^{0} +
+      (1 - z_j ) \log(1 - p_{ij}^{0})
+\end{multline}
+where $\Omega_i$ is the set of all images volunteer $i$ has observed in $\Omega$,
+the set of all images in the program.\footnote{Because the probability that a
+  viewer views a given image (given it is a training or test image) is random,
+I choose to simply ignore the unobserved images.} We can use this complete
+log-likelihood to derive an offline expectation maximization algorithm for
+determining the lens probabilities, user skills, and lens priors.
 
@@
 
-\subsection{Staged Classification}
-\label{sec:design:stages}
-
-We now describe briefly the two-stage strategy that was employed in the CFHTLS
-project, initial classification (involving the rejection of very large numbers
-of non-lenses), and refinement (to further narrow down the sample). The web
-application was reconfigured between the two stages, to assist in their
-functioning.
-
-\subsubsection{Stage 1: Initial Classification}
-
-The goal of a stage 1 classification is to achieve a high rejection rate,
-while maintaining high completeness.  In this mode, therefore, the pre-loading
-of images was used to make the sliding in of new subjects happen quickly, to
-provide a sense of urgency: initial classification must be done fairly
-quickly for the search to be completed within a reasonable time period.  We
-expect some trade-off between speed and accuracy, which we return to in the
-results section below. Completion of the search requires subjects to be
-``retired'' over time, as a result of their being classified. We do this by
-analyzing the classifications on a daily basis, as described in
-\Sref{sec:swap} below. As subjects are retired, new ones are ingested into
-the web app for classification. This means that the discovery of lens
-candidates in stage 1 is truly a community effort: to detect a lens candidate,
-many non-lenses must first be rejected.
-
-The stage 1 training set was chosen to be quite clear cut, in order to err on
-the side of inclusivity, and so ensure high completeness. For the training
-duds we selected several hundred images at random, and three of us (AV, AM,
-PM) inspected them and discarded anything that could be a lens candidate. The
-remainder were ingested into the site.
-
-\subsubsection{Stage 2: Refinement}
-
-At stage 2, the goal is to define a final sample that has both high
-completeness and high purity. To this end, a more demanding training set was
-defined, where the duds all contain an object identified by one of us (AV, AM
-and PM) as a potential false positive. \Fref{fig:training:gallery} shows some
-example images from the CFHTLS stage 2 training set.
-
-\todo{Phil}{Show some example sims and duds...}
-
-We also attempted to encourage discernment by changing the look and feel of
-the app, slowing down the arrival of new images, and switching the background
-color to bright orange to make it clear that a different task was being set.
-The frequency with which training images were shown was fixed at 1 in 3.
-Finally, the Spotter's Guide was upgraded to include more detailed discussion
-of various possible false positives.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\todo{Phil}{write this section (\#31)}
-
-\section{Data}
-\label{sec:data}
-
-We refer the reader to \papertwo for the details of the particular set of
-imaging survey data used in this first \sw project. Here, we summarize very
-briefly the choices that were made, in order to provide the context for our
-general description and illustrations of the \sw system.
+\subsubsection{E-Step}
+\label{sec:formalism:em:estep}
+The E-Step is just taking the expected complete log-likelihood, or the
+expectation value over $P(\cdot \ | x, \phi)$. This is equivalent to replacing
+$z_j$ with $p_j$:
+\begin{align}
+  p_j &= \frac{1}{N_j} \sum_{i \in \Omega_j} P(z_j = 1 \ | \ x_{ij} ; \Phi) =
+  \frac{1}{N_j} \sum_{i \in \Omega_j} \frac{ P(x_{ij} \ | \ z_j = 1; \Phi)
+P(z_j = 1 ; \Phi)}{P(x_{ij} ; \Phi)} \\
+&= \frac{1}{N_j} \sum_{i \in \Omega_j} \frac{ PL_{i}^{x_{ij}} (1 - PL_{i})^{(1 -
+x_{ij})} p_{ij}^{0}}{ PL_{i}^{x_{ij}} (1 -
+  PL_{i})^{(1 - x_{ij})} p_{ij}^{0} + PD_{i}^{(1 - x_{ij})} (1 -
+PD_{i})^{x_{ij}} (1 - p_{ij}^{0})}
+\end{align}
+where $i \in \Omega_j$ is now the set of classifications done on the $j$-th
+image and $N_j$ is the number of classifications done on the $j$-th image. This
+makes sense: $p_{ij}^{0}$ is just the prior likelihood of an image being a lens,
+while $PL_{i}$ is how well we would have identified a lens as such.
 
@@
 
-\subsection{The CFHT Legacy Survey}
-\label{sec:data:CFHTLS}
-
-The CFHT Legacy Survey \citep[CFHTLS,][]{CFHTLS} covered XXX square degrees of
-approximately equatorial sky, in four patches distributed in right ascension,
-over the course of N years. With homegeneous image quality of, typically, X
-arcsec (in the $i$-band), and reaching limiting magnitudes of XX-XX in the
-$ugriz$ filter set, this survey has yielded several dozen new gravitational
-lenses on both galaxy and group scales \citep{}. The quality of the data,
-combined with the presence of these comparison ``known lens'' samples, made
-this a natural choice against which to develop and test the \sw system. The
-CFHTLS is also well-representative of the data quality expected from several
-next-generation sky surveys, such as DES, KiDS, HSC and LSST.
-
-In order to investigate the completeness of the previous, semi-automated, lens
-searches in the CFHTLS area, we designed a ``blind search.'' We divided the
-mosaiced images into some 430,000 equal size, overlapping tiles, approximately
-70~arcsec on a side. Each of these images is a ``test image'' (as opposed to a
-``training image''). In future, larger area projects we expect to implement
-the rather different strategy of producing image tiles centred on particular
-pre-selected ``targets,'' to make for a more efficient (but less complete)
-survey. We do not expect the performance of citizen image inspectors to change
-significantly between these strategies: to first order, both strategies
-require the inspectors to learn what lenses look like, and then search the
-presented images for similar features.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Image Presentation}
-\label{sec:data:display}
-
-The CFHTLS $g$, $r$ and $i$-band images have the greatest depth and best image
-quality, and we chose to focus on this set (although the $u$ and $z$-band
-images were also available for inspection in Talk). We made colour composite
-images using publically-available code\footnote{The open source  colour image
-composition code used in this work is available from
-\texttt{http://github.com/drphilmarshall/HumVI}} following the prescription of
-\citet{LuptonEtal}. Specifically, we first rescaled the pixel values of each
-channel image into flux units, and then applied an arcsinh stretch. The
-stretch parameters were chosen using a small random sample of images, to
-ensure that the background noise was just visible,  and that the centres of
-bright, intermediate resdhift galaxies were not saturated. The color scales
-were chosen to maximize the contrast between faint extended objects. These
-parameters were then fixed during the production of all the tiles, in order to
-allow straightforward comparison between one image and another, and for
-intuition to be built up about the appearance of stars and galaxies across the
-survey. Alternative algorithms, such as adjusting the stretch and scale
-dynamically according to, for example, the root-mean-square pixel value in
-each image, can lead to better presentation of bright objects, but in doing so
-they tend to hide the faint features in those images: we needed to optimize
-the detectability of these faint features.   Examples of CFHTLS training set
-images can be seen in \Fref{fig:training-gallery}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Classification Stages and Analysis}
-\label{sec:swap}
-
-Having described the classification interface, the training images and the
-test images,  we now outline our methodology for interpreting the interactions
-of the volunteers with the identification interface, and then describe how we
-applied this methodology in the two classification stages in the CFHTLS
-project in the \sw Analysis Pipeline (SWAP) code.\footnote{The open source 
-SWAP code is available from 
-\texttt{https://github.com/drphilmarshall/SpaceWarps}}
-
-Each classification made is logged in a database, storing subject IDs,
-(anonymous) volunteer IDs, a timestamp and the classification results.  The
-{\it kind} of subject -- whether it is a training subject (a simulated lens
-or a known non-lens) or a test subject (an unseen image drawn from the survey)
--- is also recorded. For all subjects, the positions of all Markers are
-recorded, in pixel coordinates. For training subjects, we also store the
-``classification'' of the subject as a lens, or a non-lens, and also the type
-of object present in the image. These types are summarized in
-\Tref{tab:objecttypes}.  This classification is used to provide instant
-feedback, but is also the basic measurement used in a probabilistic
-classification of every subject based on all image views to date.
-
-While the \sw web app is live, and classifications are being made, we 
-perform an online analysis of the classifications,  updating a
-probabilistic model of every (anonymous) volunteer's data, and also updating
-the lens probability of each subject  (in both the training and test sets), on
-a daily basis. This gives us a dynamic estimate of the posterior probability
-for  any given  subject being a lens, given all classifications of it to date.
-Assigning thresholds in this lens probability then allows us to make good
-decisions about whether or not to retire a subject from the system, in order to
-focus attention on new images.
-
-The details of how the lens probabilities are calculated are given in
-\Aref{appendix:swap}. In summary:
-\begin{itemize}
-
-\item Each volunteer is assigned a simple software agent, characterised by a
-confusion matrix. The two independent elements of this matrix are the
-probabilities, as estimated by the agent, that the volunteer is going to be 1)
-correct when they report that an image contains a lens when it really does
-contain a lens, $\pr(\saidLENS|\LENS,T)$, and 2) correct when they report that
-an image does not contain a lens when it really doesn't contain a lens,
-$\pr(\saidNOT|\LENS,T)$.
-
-\item Each agent updates its confusion matrix elements based on the number of
-times its volunteer has been right in each way while classifying subjects from
-the training set, accounting for noise early on due to small number
-statistics: $T$ is the set of all training images seen to date.
-
-\item Each agent uses its confusion matrices to update, via Bayes' theorem,
-the probability of an image from the test set containing a lens,
-$\pr(\LENS|C,T)$, when that image is classified by its volunteer. ($C$ is the
-set of all classifications made of this subject.)
-
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_probabilities.png}
-\caption{Typical \SW Agent confusion matrix elements. At a particular
-snapshot, 200 random Agents are shown distributed over the unit plane, with a
-tendency to move towards the ``astute'' region in the upper right hand
-quadrant as the Agents' volunteers view more images. Yellow point size is
-proprtional to the number of images classified; green point size shows
-Agent-perceived ``skill.''}
-\label{fig:swap:agent-probabilities}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_histories.png}
-\caption{Typical \SW Agent histories. The ``skill'' of the  same 200 random
-Agents  as in \Fref{fig:swap:agent-probabilities} is plotted in green as a function
-of the number  of subjects classified (``effort''). The yellow histogram in
-the background shows the distribution of effort.}
-\label{fig:swap:agent-histories}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\Fref{fig:swap:agent-probabilities} shows a random selection of Agents'
-confusion matrix elements, as they were on a particular day towards the end of
-the CFHTLS project. Many volunteers classify  only a small number of images,
-and so their Agents' confusion matrix elements remain close to their initial
-values of (0.5,0.5). As more images are classified (shown by the yellow point
-size), the Agents' matrix elements tend to move towards higher values, as the
-volunteers attain greater skill levels (green point sizes, see
-\Sref{sec:results} below) and the Agent learns more about them. In this
-quadrant, the Agents perceive their volunteers to be ``astute.'' This trend is
-more clearly seen in \Fref{fig:swap:agent-histories}, which shows the skill of
-the same sample of Agents as the number of images classified increases. The
-histogram shows the distribution of classification number: a long tail to very
-high ``effort'' can be seen.
-
-In \Sref{sec:results} below, we define several quantities based on the 
-probabilities listed above that serve to quantify the performance of the crowd
-in terms of the information they provide via their classifications, and report
-on the performance of the system in returning a sample of lens candidates
-as a function of $\pr(\LENS|C,T)$ threshold.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_trajectories.png}
-\caption{Typical \SW stage 1 subject trajectories. Subjects drift downwards in
-the top panel as they are classified, while being nudged left and right by the
-Agents as they interpret the volunteers input. The dotted vertical lines show
-(left to right) the retirement threshold, prior probability, and the detection
-threshold.}
-\label{fig:swap:subject-trajectories}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-During stage 1 classification of the CFHTLS images, we assigned a prior
-probability for each image to contain a lens of $2\times10^{-4}$, based on a
-rough estimate of the number of expected lenses in the survey. We then
-assigned two values of the images' posterior probability, $\pr(\LENS|C,T)$, to
-define ``detection'' and ``rejection'' thresholds. These were set to be 0.95
-and (approximately symmetrically in the logarithm of probability), $10^{-7}$.
-Subjects that attained probability of less than the rejection threshold were
-scheduled for retirement and subsequently ignored by the analysis code.
-Subjects crossing the detection threshold were not retired from the website,
-but instead left in the system so that more volunteers could see them. The
-progress of the subjects is illustrated in \Fref{fig:swap:subject-trajectories}.
-Subjects appear on this plot at the tip of the arrow, at zero classifications
-and prior probability; they then drift downwards as they are classified by the
-crowd, with each Agent applying the appropriate kick in probability based on
-what it hears its volunteer say. Encouragingly, sims (blue) tend to end up
-with high probability, while duds (red) pile up at low probability; test
-subjects (black) mostly drift to low probability, but some go the other way.
-The latter will help make up the candidate sample. As this plot shows, around
-10 classifications are required for a subject to reach the retirement
-threshold.
-
-The analysis code was run every night during the project, and subjects retired
-in batches after its completion. This introduced some inefficiency, because
-some classifications were accumulated in the time between them crossing the
-rejection threshold and the subject actually being retired from the website.
-As subjects were retired from the site, more subjects were activated. In this
-way, the volunteers who down-voted images for not containing any lensed
-features enabled new images to be shown to other members of the community.
-
-When all the subjects had either been retired, or classified around 10 times
-or more, the web app was paused and reconfigured for stage 2. The sample of
-subjects classified during stage 2 was selected to be all those that passed
-the detection threshold ($\pr(\LENS|C,T) > 0.95$) at stage 1. These were
-classified for one week, with no retirement but a maximum classification
-number of 50 each. The number of subjects at stage 2 was small enough that we
-did not need to retire any: instead, we simply collected classifications for a
-fixed period of time (about 4 weeks). Without the time pressure motivating the
-online analysis, we implemented an ``offline'' version of the analysis that
-performs a joint inference of all Agent confusion matrix elements and subject
-probabilities simultaneously, for comparison. We describe how this differs
-from the online analysis in the appendix.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
-\label{sec:results}
-
-In this section we present our findings about the performance of the  \sw
-system, in terms of the information  contributed by the crowd in
-\Sref{sec:results:crowd}, and the overall classifications of the training set
-that they made.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Crowd Properties}
-\label{sec:results:crowd}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/all_skill_contribution_experience_education.png}
-\caption{Key properties and contributions of the \sw crowd. Plotted are the
-1-D and 2-D marginalized distributions for the logarithms of the 
-properties of the agents described in the text. The stage 1 agents are shown
-in blue, the stage 2 agents in orange.}
-\label{fig:crowd:cornerplot}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We define the following properties of the crowd, as characterised by their
-agents, and plot the distributions of their logarithms in
-\Fref{fig:crowd:cornerplot}. 
-%
-\begin{description}
-%
-\item{\noindent\bf ``Effort:''} The number of test images, $\effort$, classified by a
-volunteer. In stage 1, the mean effort per agent was 263; in the shorter stage
-2 it was 81.
-%
-\item{\noindent\bf ``Experience:''} The number of training images, $\experience$,
-classified by a volunteer. In stage 1, the mean experience per agent was 29;
-in stage 2 (where the training image fequency was set higher) it was 34.
-%
-\item{\noindent\bf ``Skill:''} The expectation value of the information gain, 
-$\skill$
-should  the next subject classified have lens probability 0.5
-(\Aref{appendix:swap}),  in bits. Random classifiers have $\skill = 0.0$,
-perfect classifiers have $\skill = 1.0$. All agents start with $\skill = 0.0$;
-this increases as training subjects are classified, and the agent's estimates
-of its confusion matrix elements improve. In stage 1, the mean skill per agent
-was 0.04 bits; in  stage 2 it was 0.05.
-%
-\item{\noindent\bf ``Contribution:''} The integrated skill over a volunteer's test
-subject classification history, and represents the total  contribution to the
-project that volunteer (see the appendix for more discussion of this
-quantity). In stage 1, the mean contribution per agent was 34.9 bits; in 
-stage 2 it was 33.5.
-%
-\item{\noindent\bf ``Information:''} The total information $\information$ generated by
-the  agent during the volunteer's classification activity. This quantity
-depends on the value of each subject's lens probability when that subject was 
-presented to the volunteer (\Aref{appendix:swap}), and so there is an element
-of luck involved with this quantity: if you never see a high probability
-subject, it's hard to generate a large amount of information. You make your
-own luck by classifying more subjects.
-%
-\end{description}
-
-The leftmost column of \Fref{fig:crowd:cornerplot} shows how the last four of
-these properties depends on the effort expended by the volunteers. We see that
-experience is strongly correlated with effort (as training images are
-presented throughout each stage, albeit at decreasing frequency), and that
-this is also true for skill. In the second row of \Fref{fig:crowd:cornerplot}
-we see that while skills of greater than 0.1 can be attained after just a few
-training images, most agents of such low experience have significantly lower
-skill. The volunteers in question only classify a few subjects before leaving.
-However, at high values of experience and effort, the skill is \emph{always
-high}. There seem to be very few agents logging large numbers of
-classifications at low skill (although there are one or two exceptions): almost
-all high effort ``super-users'' have high skill. These two properties are
-reflected in both the contributions these volunteers make (third row) and the
-information they generate (fourth row).
-
-The distributions for the stage 2 agents (orange) are qualitatively similar to
-those for the stage 1 agents (blue). Differences are: 1) the maximum effort
-possible at stage 2 is smaller, because fewer subjects were available to be
-classifed, but 2) the mean effort expended at stage 2 was higher (perhaps
-because the subjects were higher probability, and more compelling); 3) the
-information generated per agent was higher at stage 2, because the subjects
-had higher probability.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_contrib_cumul.png}
-\caption{Narrow cumulative distributions of the contributions made by the
-agents: for example, 90\% of the stage 2 contributions were made by the
-highest contributing  7\% of the crowd. The stage 1 agents are shown in blue,
-the stage 2 agents in orange. ``Experienced volunteers'' classified 10 or more
-training subjects.}
-\label{fig:crowd:cumulplot}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\Fref{fig:crowd:cornerplot} shows the \sw crowd to have quite broad
-distributions of logarithmic effort, skill, and contribution. To better
-quantify the contributions made by the volunteers, we show their cumulative
-distribution on a linear scale in \Fref{fig:crowd:cumulplot}. This plot shows
-clearly the importance of the hardest-working, most active volunteers: at
-stage 1,  1.0\% of the volunteers -- 375 people -- made 90\% of the
-contribution.  At stage 2, where it was not possible to make as
-many classifications before running out of subjects, 7.2\% of the volunteers
--- 141 people -- made 90\% of the contribution.
-
-However, it is not the case that only these small groups were capable of
-making this large contribution.
-% : 9118 volunteers were ``experienced'' in that
-% they had all classified at least 10 training images; the 375 highest
-% contributing volunteers make up just 4\% of this experienced volunteer pool.
-The cumulative distribution of agent skill is shown in
-\Fref{fig:crowd:cumulskillplot}: these distributions are significantly broader
-than the corresponding distributions of agent contribution in 
-\Fref{fig:crowd:cumulplot}. The most skilled 20\% of agents possess only  79\%
-of the skill at stage 1, and 77\% at stage 2. The inexperienced volunteers
-also possess a significant fraction of the skill: the most skillful 20\% of
-experienced volunteers (1824 people)  possess just 43\% of the total skill.
-The level of contribution made at \sw by experienced volunteers is largely a
-matter of choice (or perhaps, availability of time!).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_skill_cumul.png}
-\caption{Broad cumulative distributions of agent skill: 
-the most skilled 20\% of the crowd only possess 79\% of the skill at stage 1.
-The stage 1 agents
-are shown in blue, the stage 2 agents in orange. ``Experienced volunteers''
-classified 10 or more training subjects.}
-\label{fig:crowd:cumulskillplot}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/early_vs_final_skill.png}
-\caption{Predictability of final skill from early skill (after 10 training
-classifications) in stage 1 agents. The dashed lines enclose 649 agents with
-early skill greater than 0.1 
-who retain final skill of greater than 0.05. Point size is proportional to
-contribution (plus a constant).}
-\label{fig:crowd:skillprediction}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Having seen the importance of the high skill volunteers at both stage 1 and
-stage 2, we might ask, can we predict agent skill after, say, the volunteer
-has experienced 10 training subjects? In \Fref{fig:crowd:skillprediction} we
-plot this ``early skill'' against final skill, for all experienced stage 1
-volunteers. The majority of the crowd shows little correlation, but at the
-high early skill end, some predictability appears. The 649 experienced  stage
-1 volunteers who had early skill greater than 0.1 went on to attain a mean
-final skill of 0.22, with 97\% remaining at skill 0.05 or higher. This
-suggests that it might be worth tracking volunteers' skill as a project
-progresses, in order to encourage those showing an aptitude for the task to
-take part in the more difficult activities, such as stage 2 refinement.
-However, this would not have done a very good job at identifying the 
-volunteers who went on to make the largest contributions: the point size in 
-\Fref{fig:crowd:skillprediction} is proportional to contribution (plus a constant):
-many of the highest contributors showed relatively low skill early on.
-
-\Tref{tab:crowd:contributions} shows the total effort, contribution, skill and
-information generated in both stage 1 and 2 of the CFHTLS project, with the
-total numbers of agents and subjects for comparison.  These numbers allow us
-to quantify the efficiency of the system.  The contribution per classification
-is defined in terms of a hypothetical subject with lens probability of 0.5;
-one bit of information is needed to update such a subject's lens probability
-to either zero or one. This means that a maximally complete classification
-stage would yield a total contribution (summed over all agents) equal to the
-number of subjects. The ratio of this hypothetical optimum to the actual total
-contribution is therefore a measure of the stage's inefficiency. We find our
-inefficiency (by dividing column 2 by column 3) to be 33\% and 17\% in stage 1
-and 2 respectively. In stage 1, this inefficiency is due to the daily
-processing: we were not able to retire subjects fast enough, and so they,
-remained in the system, being over-classified. Indeed, only 3705745
-classifications were needed to retire all the subjects: the ratio of this to
-the total number made is 34\%. (The remaining 1\% is due to not all subjects
-being classified to 1 or 0 probability.) At stage 2, we did not retire any
-subjects at all; the inefficiency in this case was by design, to give everyone
-a chance to appreciate what they had found together!
-
-The total skill of the crowd, computed by summing the skill of all the agents,
-is, similarly, a measure of the effective crowd size: a crowd of perfect
-classifiers would be this size. The stage 1 crowd was equivalent to a team of
-1469.9 perfect classifiers; the stage 2 crowd was equivalent to a team of
-102.4 perfect classifiers.
-
-The total information generated during the survey is harder to interpret,
-because it's exactly the high probability candidates that we leave in the
-system that give rise to most of the information generated. What we can do is
-divide the total information generated by the amount of information it takes
-to classify a \sw subject all the way to the detection threshold (lens
-probability 0.95), divide by this number, and then multiply by the survey
-inefficiency to get a very rough estimate for the effective number of
-detections corresponding to the crowd's contribution. With a prior probability
-of $2\times10^{-4}$, it takes 12.3 bits to make a detection (see
-\Sref{sec:appendix:infogain} in the appendix); the effective
-number of detections contributed by the stage 1 and stage 2 volunteers is then
-2830 and 25 bits respectively. 
-These figures are close to the numbers of detections
-given in column 7 of \Tref{tab:crowd:contributions}. 
-The uncertainty in the interpretation of the
-information generated provides further justification for our focus on the
-expected information gain as a measure of volunteer contribution.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table*}
-\begin{center}
-\caption{Total crowd and subject sample properties from the CFHTLS project.}
-\label{tab:crowd:contributions}
-\begin{tabular}{cccccccc}
-  \hline
-  \hline {Stage} & Subjects & Contribution                          & Agents & Skill      & Classifications          & Candidates & Information \\
-                 & $\Ns$    & $\sum_k^{\Nv} \contribution_k$ (bits) & $\Nv$  & $\sum_k^{\Nv} \skill_k$ (bits) & $\sum_k^{\Nv} \thiseffort$ & $\Ncands$  & $\sum_j^{\Ns}\sum_k^{\Nv} \information_{j,k}$ (bits) \\
-  \hline 
-            1    & $427064$ & $1292016.3$ & $36982$ & $1471.9$ & $10802125$ & $3368$ & $91122.6$ \\
-            2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $90$ &  $1640.4$ \\
-  \hline \hline
-\end{tabular}
-\medskip\\
-\end{center}
-\end{table*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Sample Properties}
-\label{sec:results:sample}
-
-We now quantify the performance of the \sw system in terms of the recovery of
-the training set images. \Fref{fig:results:sample:roc} shows receiver
-operating characteristic (ROC) curves for CFHTLS stage 1 and stage 2. These
-plots show the true positive rate (TPR), the number of sims correctly detected
-divided by the total number of sims in the training set, and the false
-positive rate (FPR), the number of duds incorrectly detected  divided by total
-number of duds in the training set, both for a given sample of detections defined by
-a particular probability threshold, which varies along the curves.  In both
-stages, these curves show that true positive rates of  around 90\% were
-achieved, at very low false positive rates. For comparison we show the results
-of an analysis where the classifications of  training images were ignored, and
-none of the agents allowed to learn: they were instead assigned initial values
-of their confusion matrices of 0.75 for each element, which then remained
-constant. This emulates a very simple unweighted voting scheme, where all
-classifications are treated equally. In this case, the TPR remains under 80\%
-in stage 1 and 60\% in stage 2, thus quantifying 
-the benefit of including training
-images and allowing the agents to learn. The choice of initial confusion
-matrix is not very important: the same 0.75 initial values applied to normal,
-learning agents results in a slightly lower TPR than the default case,
-indicating that initializing the system less conservatively results in
-slightly worse performance.
-
-The dot-dashed curves show the impact of the offline analysis. At stage 1 the
-results are very similar to the online version that was actually run (solid
-line). However, at stage 2 there seems to be somewhat greater benefit to doing
-the analysis in this way: over 85\% TPR is achieved at zero FPR.
-Alternatively, if one is willing to accept a false positive rate of 5\%, the
-true positive rate rises to over 95\%, showing that some of the sims that were
-missed in the online analysis can be recovered by doing the analysis offline.
-The same is true at stage 1, but to a lower degree.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\begin{minipage}{0.45\linewidth}
-  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage1_ROC.png}
-\end{minipage}\hfill
-\begin{minipage}{0.45\linewidth}
-  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage2_ROC.png}
-\end{minipage}
-\caption{Receiver operating characteristic curves for the \sw system, using
-the CFHTLS training set. Left: stage 1, right: stage 2.}
-\label{fig:results:sample:roc}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Adopting the online stage 1 analysis, and the offline stage 2 analysis, we
-show in \Fref{fig:results:sample:CP} a plot of the more familiar (to
-astronomers) quantities completeness versus purity in
-the two stages. As in \Fref{fig:results:sample:roc}, the detection threshold
-varies along the curves. Completeness is defined as the number of correctly
-detected sims divided by the total number of sims in the training set, while
-purity is the number of correct detections divided by the total number of
-detections.\footnote{The completeness is equivalent to the TPR and is also
-known elsewhere as the ``recall.''  The purity is also known as the
-``precision.''} If the training set samples from the same systems as the test
-set, then the completeness of the training set will be equivalent to the
-completeness of the test set. The purity depends on the proportion of sims to
-duds, and so the purity of the test set must be approximated by rescaling the
-training set to the expected proportion of lens systems to not-lens systems in
-the survey. First we compute the expected number of false positives by
-multiplying the FPR by the expected number of non-lenses in the survey. Then
-we multiply the TPR by the expected number of lenses in the survey, to get the
-expected number of true positives. The sum of the true positives and the false
-positives gives the expected sample size; dividing the expected number of true
-positives by this sample size gives the purity. Note that the completeness is
-invariant to this transformation.
-
-The stage 1 curves are truncated by the retirement of subjects in this phase, 
-which sets the minimum size of this sample. We see from the solid blue curve
-that over 90\% completeness was reached, albeit in a sample with around 20\%
-purity. To investigate the completeness to the three different types of lens
-in the training set, we ...
-
-\todo{Chris}{complete the above sentence to explain what purity means in the
-divided-by-sim-type case. Thanks! \#66}
-
-The lensed quasar part of the training set yielded the highest
-completeness, suggesting that these were the easiest sims to spot. The lensed
-galaxies were recovered at understandably lowest completeness, although the
-wider image separation  lensing clusters were not very different. At stage 2,
-where no retirement was carried out, it was possible to reach 100\% purity:
-indeed, the knee of the curve is at just under 90\% completeness. However, the
-purity decreases rapidly if higher completeness than this is sought.
-Interestingly, the lensing clusters can be seen to pose problems for the
-system, with its curve turning over at just 60\% completeness.
-
-The optimal sample in this simulated lens search experiment would have been
-constructed with a threshold value of $\pr(\LENS|C,T) > X.XX$. At 100\% purity
-and 9X\% completeness, it would have contained around N lens candidates.
-
-\todo{Chris}{fill in the numbers above, please! :-) \#65}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\centering\includegraphics[width=\linewidth]{sw-system-figs/completeness_purity.png}
-\caption{Completeness-estimated purity curves for the \sw system, using
-the CFHTLS training set.}
-\label{fig:results:sample:CP}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}
-\label{sec:discuss}
-
-\todo{Phil}{write discussion (\#44).}
-
-What can we learn from the results of the previous section, for future
-projects? Potential improvements to the \sw system can be divided into three
-categories, performance, efficiency and capacity.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\begin{minipage}{\linewidth}
-  \begin{minipage}[t]{0.47\linewidth}
-    \begin{minipage}{0.46\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0008wyp_gri.png}
-    \end{minipage}\hfill
-    \begin{minipage}{0.50\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0008wyp_stage2_trajectory.png}
-    \end{minipage}
-  \end{minipage}\hfill
-  \begin{minipage}[t]{0.47\linewidth}
-    \begin{minipage}{0.46\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0006rkx_gri.png}
-    \end{minipage}\hfill
-    \begin{minipage}{0.50\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0006rkx_stage1_trajectory.png}
-    \end{minipage}
-  \end{minipage}
-\end{minipage}
-
-\vspace{\baselineskip}
-
-\begin{minipage}{\linewidth}
-  \begin{minipage}[t]{0.47\linewidth}
-    \begin{minipage}{0.46\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0000fgj_gri.png}
-    \end{minipage}\hfill
-    \begin{minipage}{0.50\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0000fgj_stage1_trajectory.png}
-    \end{minipage}
-  \end{minipage}\hfill
-  \begin{minipage}[t]{0.47\linewidth}
-    \begin{minipage}{0.46\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0003j2s_gri.png}
-    \end{minipage}\hfill
-    \begin{minipage}{0.50\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0003j2s_stage1_trajectory.png}
-    \end{minipage}
-  \end{minipage}
-\end{minipage}
-\caption{Illustrative examples of 
-false negatives (blue) and false positives (red) from the classification of
-the \sw CFHTLS training set. The trajectory plot for each of the 4 subjects is
-shown to the right of its image. lefthand panels show the most common types of
-trajectories: short step random walks resulting from no high skill classifiers
-viewing the subject. The righthand panels show examples where higher skill
-classifiers have been involved, causing random walks with longer step lengths
-(top) and catastrophic mis-classifications (bottom right).}
-\label{fig:discuss:performance:trajectories}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Improving performance: reducing incompleteness and impurity}
-\label{sec:discuss:performance}
-
-We investigated the source of the incompleteness and impurity visible in 
-\Fref{fig:results:sample:CP}, by examining the stage 2 false negatives and
-false positives. \Fref{fig:discuss:performance:trajectories} shows 2 example
-simulated lenses  that were missed ($\pr(\LENS|C,T) < 10^{-5}$) by the \sw
-system, and 2 example non-lenses that were incoreectly flagged as candidates
-($\pr(\LENS|C,T) > 0.95$) by the \sw system.
-
-In some cases the rejection of the false negatives is understandable: the
-lensed features are faint, or otherwise difficult to see. However, in other
-cases a reasonably obvious lens was passed over.  This mainly seems to be due
-to noise in the system: when only low-skill classifiers view a subject, all
-the updates to its posterior probability are small, and if none are very
-confident about the presence of lensing, the subject follows a random walk
-down its trajectory plot. This can be seen in the top left panel of the
-figure.  The false positives show similar behaviour, for example in the bottom
-lefthand panel of the figure. As well as subjects being ``unlucky'' in this
-way, there are two less common failure modes associated with mistakes made by
-higher skill users, illustrated in the righthand column of the figure. In the
-false negative subject shown in the top right-hand panel, several high skill
-classifiers update the subject upwards in log probability by some way each
-time, but other, comparable skill classifiers mis-classify the system to lower
-probability. If we had retired subjects after crossing a high probability
-detection threshold, this subject would have been correctly identified as a
-lens candidate; instead, it was kept in the system and eventually scattered
-down to retirement. The trajectory looks like a random walk, but with bigger
-steps. The bottom righthand panel shows an example of a final, apparently
-rare, failure mode: we see some short-step random walk behaviour, followed by
-a mis-classification by a very high skill ``expert'' classifier after 20
-classifications that promotes the subject to high probability.
-
-There are a number of places where we can address these problems and
-improve system performance: adding flexibility to the classification
-interface, educating the volunteers, assigning subjects for
-classification, and interpreting the classification data.
-
-We might wonder whether some of  the mistakes made by reasonably high skill
-classifiers could have been corrected by those classifiers themselves, had
-they had access to a ``go back'' option. While clearly enabling error
-reduction, we might worry about such a mechanism enabling classifiers to have
-a guess, then go and read the Talk discussion, and then return to the
-classification interface to change their mind to agree with the forum. In
-fact, this is already possible on the current interface -- and indeed, it is
-not obvious that such correlations would necessarily lead to poorer system
-performance. This could be tested by presenting a fraction of the volunteers
-with a version of the site that actively suggested that they take this
-approach, and then tracking the relative performance of ``collaborative''
-classifications compared with independent ones. We leave this to further
-work.
-
-Mistakes by both high and low skill classifiers could be reduced by improving
-the training in the system, which could be done in several ways. One is to 
-make more training images available to those who want or need it. A basic
-level of training images are needed for SWAP to build up an accurate picture
-of each classifier's skill -- but one could imagine volunteers {\it choosing}
-to see more training images (still at random) in their stream. Another could
-be to provide more information about what lenses do. In this project, the
-Spotter's Guide was always available on the site, but as a passive background
-resource. We might consider providing more links to this guide in the feedback
-messages shown to the classifiers as they go -- or perhaps extending these
-messages to themselves include more explanations and example images.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/stage2_veteran_contribution.png}
-\caption{Stage 2 classifier skill, as a function of their stage 1 skill.
-Veterans from stage 1  are shown in blue, while new volunteers are shown in
-orange. Point size is proportional to the number of stage 2 classifications
-made, while dashed lines are drawn at the mean values for each sample.
-Restricting stage 2 to classifiers with high stage 1 skill could reduce the
-noise in the system.}
-\label{fig:discuss:performance:stage1vstage2}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-However, most identification failures (around 60\%) seem to be due to the
-random walk problem. While improved training will help reduce this effect, it
-is here that targeted task assignment could help improve system performance.
-We advertised stage 2 of the current project to all registered users; it was
-taken up by stage 1 veterans with a broad range of skill, and also picked up a
-significant number of new users who did not have enough time to aquire high
-skill (since stage 2 was quite short): of the 1964 volunteers who took part in
-the stage 2 classification round, only 774 were veterans from stage 1.
-\Fref{fig:discuss:performance:stage1vstage2} shows how the stage 1 skill maps
-on to stage 2 skill and contribution.
-
-This figure suggests that there may be some benefit to opening stage 2 on the
-basis of agent skill, in order to reduce the noise in the system generated by
-new and low skill volunteers in this more difficult classification stage. A
-simple implementation of this would be to switch the web app to the stage 2
-version when either a certain stage 1 skill (and/or effort) threshold was
-passed. Good strategy would probably be to switch back to stage 1 after some
-number of stage 2 classifications (to avoid losing the high skill users from
-stage 1 entirely), and also to make it very clear which stage the classifier
-was at (since stage 2 requires more careful attention). This is something we
-plan to experiment with in future.
-
-Finally, there could be some performance gains to be made by improving the
-SWAP agent model, or its implementation. In a future paper we plan to
-investigate the use of the test images as well as the training images in
-learning the agent confusion matrix elements (Davis et al, in preparation).
-One might also consider looking at introducing more conditional dependences in
-these elements, to allow for some classifiers having greater skill in one type
-of lens than another, or, more generally, as a function of lens property (such
-as color, brightness, and image separation). In the current model, all agents
-are considered to be completely independent, whereas in fact we might expect
-there to be significant clustering of the confusion matrix elements. A
-hierarchical model for the crowd, with hyper-parameters describing the
-distribution of confusion matrix elements across the population, may well
-accelerate the agent learning process by including the notion of one agent
-being likely to be similar to its neighbours. Finally, it is worth noting that
-the model of \citet{IBCC} explicitly avoids the assumption of the agent
-confusion matrix elements being constant in time, allowing the development of
-volunteer skill to be more accurately tracked -- and that they did see some
-time-evolution in the supernova zoo classifiers' skill. Finding a way to
-incorporate such a learning model into SWAP, while retaining its statistically
-online character is an interesting challenge for future work.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Improving efficiency}
-\label{sec:discuss:efficiency}
-
-Inefficiency. Move to truly online system: web app to analyse classifications
-as it goes. Place for weekly offline processing? Recovering false negatives by
-``resurrecting'' subjects that scattered down too soon.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Increasing capacity}
-\label{sec:discuss:capacity}
-
-Scaling of system. Factors of ten: $10^4$ volunteers, $10^3$ achieve high
-skill, $10^2$ make significant contribution. Good project size is few $10^4$
-subjects, to enable completion by a crowd of this size in short time.
-
-Ways to increase numbers of high-contribution volunteers: 1) increase crowd
-size. Higher exposure through media. Multi-lingual user base - comes with
-problems.  2) Increase engagement rate:  feedback from survey teams.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusions}
-\label{sec:conclude}
-
-\todo{Phil}{write conclusions (\#45).}
-
-Summary of system.
-
-Crowd-sourced gravitational lens detection works, in terms of the
-classification of the training set as described here, in the following
-specific ways:
-
-\begin{itemize}
-
-\item Participation (crowd size, activity rate) enabled project completion
-
-\item Both stages (1 and 2) achieved the required rejection rates
-
-\item Integrated humanpower = X (stage 1) and y (stage 2), cf hours taken by
-small team of experts
-
-\item Nightly processing is inefficient: more classifications were made than
-was necessary during peak participation. Need kafka...
-
-\item Retirement rate. False negatives: which sims were missed?
-
-\item The optimal true positive rate (completeness) and false positive rate in
-the training set were estimated to be TPR\% and FPR\% at Stage 1, assuming a
-detection threshold of xxx.
-
-\item In the ``refinement'' stage 2, X\% of the stage 1 candidates were
-rejected (with P less than threshold), and the remainder assigned lens
-``probabilities.'' Ranking
-subjects by their Stage 2 lens probability gives an ROC curve for the system
-with X properties. The optimal true positive rate (completeness) and false
-positive rate in the training set were estimated as TPR\% and FPR\%;
-
-\item The lens-finding crowd shows some interesting properties, with
-consequences for future scalability
-
-\item The information comes predominantly from volunteers with agents with P =
-...
-
-\item The agents show a high mean information per classification, which
-increased/decreased with time; this does/doesn?t correlate with active crowd
-size, showing how the crowd changed over time...
-
-\end{itemize}
-
-Sum up, end.
+\subsubsection{M-Step}
+\label{sec:formalism:em:mstep}
+The M-Step is done by maximizing the expected complete log-likelihood with
+regard to the input parameters $PD_{i}, PL_{i}, p_{ij}^{0}$. Doing the
+maximization process, we find:
+\begin{align}
+  PL_{i} &= \frac{\sum_{j \in \Omega_i} x_{ij} p_{j}}{\sum_{j \in
+\Omega_i} p_{j}} \\
+  PD_{i} &= \frac{\sum_{j \in \Omega_i} (1 - x_{ij}) (1 - p_{j})}{\sum_{j \in
+\Omega_i} (1 - p_{j})}
+\end{align}
+\begin{align}
+  p_{ij}^{0} &= p_{j} \ , &p_{i}^{0} = \frac{\sum_{j \in \Omega_i}
+p_{j}}{\sum_{j \in \Omega_i} 1} \notag\\
+   p_{j}^{0} &= p_{j} \ , &p^{0} = \frac{\sum_i \sum_{j \in \Omega_i}
+p_{j}}{\sum_i \sum_{j \in
+  \Omega_i} 1} \ ,
+\end{align}
+where the possible specializations of $p_0$ are also given. These mirror quite
+closely the online systems, except that skill is now assessed against
+the majority expectation of the probability of an image being a lens, instead
+of its true value.
+
+In practice we have training images where $p_{j}$ is known. In those
+cases we can use the true value when doing the M-Step.
+
+Finally, we also include Laplace smoothing into the M-Step in order to handle
+pathologic cases, such as when users never identify any lenses ($\sum_{j \in
+\Omega_{i}} p_j = 0$). The estimators for $PL_{i}$ and $PD_{i}$ now become:
+\begin{align}
+  PL_{i} &= \frac{M + \sum_{j \in \Omega_i} x_{ij} p_{j}}{2M + \sum_{j \in
+\Omega_i} p_{j}} \\
+  PD_{i} &= \frac{M + \sum_{j \in \Omega_i} (1 - x_{ij}) (1 - p_{j})}{2M + \sum_{j \in
+\Omega_i} (1 - p_{j})}
+\end{align}
+where for Laplace smoothing, $M = 1$.
+
+We choose to specialize $p^{0}$ to vary with
+image, $p_{j}^{0}$, because images are taken out of the \sw system if they reach
+too low a probability, clearly changing the prior when we evaluate at the end
+of the run; training images also have a
+different prior on being a lens as well. Finally, if the image is a training
+image with known $p_j \in (0,1)$, then the known $p_j$ is used instead of
+the current estimate.
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \begin{figure*}
+% %\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/sw-screengrab-marker+feedback.png}
+% \caption{Screenshot of the \sw classification interface.}
+% \label{fig:screenshot}
+% \end{figure*}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2014-09-12 analysis/SWAP.py
typo!

@@ -431,7 +431,7 @@ def SWAP(argv):
             # just in case any IDs didn't get into offline somehow?!
             if ID not in offline_probabilities:
                 sample.member.pop(ID)
-                print "SWAP: offline popping this ID: ,"ID
+                print "SWAP: offline popping this ID: ",ID
                 continue
             # This is a bit hackish: update mean_probability,
             # median_probability, and do the rejection threshold stuff

### 2014-09-13 doc/sw-cfhtls.tex

@@
 simulated samples of lenses both at galaxy and group-scales as part of
-this training sample. We present 74 new strong gravitational lens
-candidates discovered from the \sw-\cfhtls search. Furthermore, we
-compile a sample of false positives which can be used for robot testing,
-first of its kind for the lensing community. The simulated sample is
-also used to make a comparison between human performance against the
-robots. We find that the XX per cent of the known lens sample is
-recovered and the new lens sample has XX completeness with respect to
-the simulated sample. We make available the following data products:
-simulated sample, simulation code and the false positives sample at XXX.
+this training sample. We present 80 new strong gravitational lens
+candidates discovered from the \sw-\cfhtls search out of which 40
+candidates are promising. Furthermore, we compile a sample of false
+positives which can be used for robot testing, first of its kind for the
+lensing community. The simulated sample is also used to make a
+comparison between human performance against the robots. We find that
+the XX per cent of the known lens sample is recovered and the new lens
+sample has XX completeness with respect to the simulated sample. We make
+available the following data products: simulated sample, simulation code
+and the false positives sample at XXX.
 
@@
 {\bf TBA data products; make the FP sample available}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\onecolumn
+
+\begin{center}
+\begin{longtable}{lcccccccccr}
+\caption{ \label{tab:swcands} 
+Thresholds used in the selection of the simulated lenses. }\\
+\hline
+SW ID & Name & RA & Dec &  $z_{\rm phot}$ & $m_i$ & $R_{\rm A}$ & R$_{avg}$ & ZooID & P & Comments  \\
+  &  & (deg) & (deg) &  & (mag) &  (") &  &  & & \\ 
+\hline
+\endfirsthead
+\hline
+SW ID & Name & RA & Dec &  $z_{\rm phot}$ & $m_i$ & $R_{\rm A}$ & R$_{avg}$ & ZooID & P & Comments  \\
+  &  & (deg) & (deg) &  & (mag) &  (") &  &  & & \\ 
+\hline
+\endhead
+\hline
+\multicolumn{11}{p{18cm}}{
+The column Comments has two type of notes. The first is about the lens
+image configuration where the symbols mean the following A: Arc, D: Double, Q:
+Quad, R: Ring. The second is a comment on the type of lens assessed
+visually. Note that this classification is not based on colors or spectral
+analysis. The symbols are E: Elliptical, S: (face on) Spiral, G: Group-scale, D:
+Edge on disk, R: Red starforming galaxy.  This galaxy falls within the masked region as per the catalog from
+which the magnitudes and the redshift are extracted.  
+}\\  
+\endlastfoot
+ SW1 & CFHTLS J020338-051901 &   30.9097 &   -5.3171 &  0.4 & 18.8 &  1.6 &  2.0 & ASW0001sqw &  0.7  &  D,E   \\ 
+ SW2 & CFHTLS J020341-074722 &   30.9223 &   -7.7897 &  0.5 & 18.8 &  1.6 &  2.0 & ASW000993q &  1.0  &  A,E   \\ 
+ SW3 & CFHTLS J020457-110309 &   31.2392 &  -11.0526 &  0.7 & 20.0 &  1.6 &  2.3 & ASW00099b9 &  1.0  &  A,R   \\ 
+ SW4 & CFHTLS J020642-095157 &   31.6751 &   -9.8659 &  --  &  --  &  0.9 &  2.0 & ASW0001ld7 &  1.0  &  A,R   \\ 
+ SW5 & CFHTLS J020810-040220 &   32.0450 &   -4.0389 &  --  &  --  &  1.8 &  1.3 & ASW0001c3j &  1.0  &  A,R   \\ 
+ SW6 & CFHTLS J020832-043315 &   32.1339 &   -4.5544 &  --  &  --  &  1.6 &  2.3 & ASW0002asp &  1.0  &  A,R   \\ 
+ SW7 & CFHTLS J020848-042427 &   32.2011 &   -4.4076 &  --  &  --  &  1.1 &  2.7 & ASW0002bmc &  1.0  &  D,D   \\ 
+ SW8 & CFHTLS J020849-050429 &   32.2078 &   -5.0748 &  --  &  --  &  0.9 &  2.3 & ASW0002qtn &  1.0  &  A,R   \\ 
+ SW9 & CFHTLS J021021-093415 &   32.5898 &   -9.5711 &  0.4 & 18.4 &  2.7 &  1.3 & ASW0002k40 &  0.5  &  D,S   \\ 
+SW10 & CFHTLS J021057-084450 &   32.7415 &   -8.7474 &  --  &  --  &  2.5 &  1.7 & ASW0002p8y &  0.4  &  A,G   \\ 
+SW11 & CFHTLS J021221-105251 &   33.0881 &  -10.8811 &  0.3 & 17.9 &  1.8 &  2.0 & ASW0002dx7 &  1.0  &  D,E/S   \\ 
+SW12 & CFHTLS J021225-085211 &   33.1051 &   -8.8697 &  0.8 & 19.5 &  2.1 &  1.7 & ASW00024id &  1.0  &  R,R   \\ 
+SW13 & CFHTLS J021230-074727 &   33.1264 &   -7.7909 &  0.9 & 20.3 &  1.7 &  1.7 & ASW0001ze0 &  0.5  &  A,R/G   \\ 
+SW14 & CFHTLS J021317-084819 &   33.3234 &   -8.8055 &  0.5 & 19.8 &  1.3 &  1.3 & ASW00024q6 &  0.6  &  A,R/E   \\ 
+SW15 & CFHTLS J021514-092440 &   33.8109 &   -9.4111 &  0.7 & 19.9 &  2.6 &  1.3 & ASW00021r0 &  0.5  &  A,R/G   \\ 
+SW16 & CFHTLS J022016-102446 &   35.0688 &  -10.4129 &  0.6 & 19.4 &  1.5 &  2.3 & ASW0009a4w &  0.7  &  D,E   \\ 
+SW17 & CFHTLS J022359-083651 &   35.9995 &   -8.6144 &  --  &  --  &  3.1 &  1.3 & ASW0004iye &  0.7  &  A,E   \\ 
+SW18 & CFHTLS J022406-062846 &   36.0256 &   -6.4796 &  0.4 & 19.6 &  0.9 &  2.3 & ASW0003wsu &  1.0  &  A,E   \\ 
+SW19 & CFHTLS J022409-105808 &   36.0398 &  -10.9689 &  --  &  --  &  4.8 &  3.0 & ASW0004dv8 &  1.0  &  A,G   \\ 
+SW20 & CFHTLS J022533-053204 &   36.3888 &   -5.5346 &  0.5 & 19.4 &  3.6 &  2.0 & ASW0004m3x &  0.7  &  A,R/G   \\ 
+SW21 & CFHTLS J022716-105602 &   36.8186 &  -10.9341 &  0.4 & 17.3 &  1.8 &  2.0 & ASW0009ab8 &  0.8  &  A,E/G   \\ 
+SW22 & CFHTLS J022745-062518 &   36.9387 &   -6.4218 &  0.6 & 20.5 &  1.2 &  1.7 & ASW0003s0m &  0.7  &  A,R   \\ 
+SW23 & CFHTLS J022805-051733 &   37.0236 &   -5.2927 &  0.4 & 18.8 &  1.4 &  2.3 & ASW0009ans &  1.0  &  Q,E   \\ 
+SW24 & CFHTLS J022817-080242 &   37.0727 &   -8.0452 &  0.5 & 19.6 &  0.9 &  2.0 & ASW00042d9 &  1.0  &  A,E/R   \\ 
+SW25 & CFHTLS J022843-063316 &   37.1794 &   -6.5547 &  0.5 & 19.1 &  1.8 &  1.3 & ASW0003r6c &  0.4  &  D/A,E   \\ 
+SW26 & CFHTLS J023008-054038 &   37.5359 &   -5.6774 &  0.6 & 19.7 &  1.9 &  2.3 & ASW0003r61 &  0.6  &  A,E   \\ 
+SW27 & CFHTLS J023010-110409 &   37.5420 &  -11.0694 &  0.9 & 20.6 &  1.2 &  1.7 & ASW0004fgb &  0.7  &  A,R   \\ 
+SW28 & CFHTLS J023051-082423 &   37.7141 &   -8.4064 &  --  &  --  &  0.8 &  2.3 & ASW000412m &  0.6  &  A,E   \\ 
+SW29 & CFHTLS J023123-082535 &   37.8468 &   -8.4266 &  --  &  --  &  1.2 &  2.3 & ASW0004xjk &  0.4  &  A,R   \\ 
+SW30 & CFHTLS J023315-042243 &   38.3133 &   -4.3789 &  0.7 & 19.7 &  1.0 &  2.0 & ASW00050sk &  1.0  &  A,R   \\ 
+SW31 & CFHTLS J023325-053104 &   38.3547 &   -5.5178 &  0.5 & 18.8 &  1.3 &  1.7 & ASW0005ire &  1.0  &  Q,M   \\ 
+SW32 & CFHTLS J023453-093032 &   38.7232 &   -9.5089 &  0.5 & 19.8 &  0.7 &  1.7 & ASW00051ld &  0.5  &  A,D   \\ 
+SW33 & CFHTLS J084833-044051 &  132.1385 &   -4.6809 &  0.7 & 20.2 &  0.9 &  1.7 & ASW0004wgd &  0.9  &  A,R   \\ 
+SW34 & CFHTLS J084841-045237 &  132.1708 &   -4.8772 &  0.3 & 19.0 &  1.0 &  2.3 & ASW0004nan &  1.0  &  A,E   \\ 
+SW35 & CFHTLS J084941-051650 &  132.4216 &   -5.2808 &  0.4 & 19.1 &  1.5 &  1.3 & ASW0004nh3 &  0.6  &  A,E/S   \\ 
+SW36 & CFHTLS J085135-052232 &  132.8980 &   -5.3756 &  --  &  --  &  1.9 &  1.3 & ASW0004n2x &  0.7  &  D,R   \\ 
+SW37 & CFHTLS J085317-020312 &  133.3233 &   -2.0535 &  0.7 & 20.6 &  1.2 &  1.3 & ASW0000vtc &  0.7  &  A,R   \\ 
+SW38 & CFHTLS J090218-053924 &  135.5790 &   -5.6567 &  --  &  --  &  2.0 &  1.3 & ASW0000g95 &  1.0  &  A,R/E   \\ 
+SW39 & CFHTLS J090248-010232 &  135.7020 &   -1.0424 &  0.4 & 19.1 &  1.4 &  1.7 & ASW000096t &  0.8  &  D,E   \\ 
+SW40 & CFHTLS J090308-043252 &  135.7840 &   -4.5479 &  --  &  --  &  1.2 &  2.0 & ASW00007mq &  0.8  &  A,E   \\ 
+SW41 & CFHTLS J090319-040146 &  135.8311 &   -4.0297 &  --  & 19.8 &  1.2 &  1.7 & ASW00007ls &  0.6  &  A,R/E   \\ 
+SW42 & CFHTLS J090333-005829 &  135.8890 &   -0.9749 &  --  &  --  &  2.1 &  1.7 & ASW00008a0 &  1.0  &  A/D,E/G   \\ 
+SW43 & CFHTLS J135724+561614 &  209.3540 &   56.2707 &  --  &  --  &  2.6 &  1.3 & ASW0006e0o &  1.0  &  D,E   \\ 
+SW44 & CFHTLS J135755+571722 &  209.4827 &   57.2897 &  0.8 & 20.2 &  1.3 &  2.0 & ASW0005ma2 &  1.0  &  D,D   \\ 
+SW45 & CFHTLS J140027+541028 &  210.1160 &   54.1745 &  --  &  --  &  1.2 &  1.3 & ASW0006a07 &  0.8  &  Q,R/E   \\ 
+SW46 & CFHTLS J140030+574437 &  210.1260 &   57.7437 &  0.4 & 18.2 &  2.0 &  2.3 & ASW0009bp2 &  0.9  &  A,E   \\ 
+SW47 & CFHTLS J140425+520506 &  211.1062 &   52.0850 &  0.4 & 18.9 &  1.4 &  1.3 & ASW0005o0w &  0.9  &  D,E   \\ 
+SW48 & CFHTLS J140522+574333 &  211.3426 &   57.7259 &  0.7 & 19.7 &  1.0 &  2.7 & ASW000619d &  1.0  &  A,R   \\ 
+SW49 & CFHTLS J140622+520942 &  211.5958 &   52.1617 &  0.7 & 20.3 &  1.2 &  2.3 & ASW0005rnb &  1.0  &  A,R   \\ 
+SW50 & CFHTLS J140845+514913 &  212.1907 &   51.8205 &  0.7 & 19.7 &  1.5 &  2.7 & ASW0005o38 &  1.0  &  A,E   \\ 
+SW51 & CFHTLS J141056+533225 &  212.7364 &   53.5405 &  0.6 & 19.4 &  1.7 &  2.0 & ASW0006kjx &  0.6  &  A,R/G   \\ 
+SW52 & CFHTLS J141432+534004 &  213.6372 &   53.6679 &  0.7 & 21.4 &  0.9 &  2.0 & ASW0006jh5 &  1.0  &  A,R   \\ 
+SW53 & CFHTLS J141448+545548 &  213.7010 &   54.9301 &  0.4 & 18.3 &  2.1 &  1.3 & ASW0006zc9 &  0.4  &  A,G   \\ 
+SW54 & CFHTLS J141518+513915 &  213.8290 &   51.6542 &  0.4 & 18.3 &  3.0 &  1.7 & ASW00070vl &  1.0  &  D,E   \\ 
+SW55 & CFHTLS J141927+533919 &  214.8627 &   53.6554 &  0.7 & 20.5 &  2.3 &  1.7 & ASW0006yrw &  0.5  &  A,R/G   \\ 
+SW56 & CFHTLS J142432+550019 &  216.1354 &   55.0055 &  0.5 & 19.5 &  1.1 &  2.0 & ASW0007vx2 &  1.0  &  A,E   \\ 
+SW57 & CFHTLS J142603+511421 &  216.5140 &   51.2393 &  --  &  --  &  4.4 &  2.7 & ASW0006mea &  1.0  &  A,G   \\ 
+SW58 & CFHTLS J142620+561356 &  216.5870 &   56.2323 &  0.4 & 19.5 &  1.3 &  1.3 & ASW0007sez &  1.0  &  A/R,S   \\ 
+SW59 & CFHTLS J142652+560001 &  216.7200 &   56.0004 &  --  &  --  &  1.5 &  1.7 & ASW0007t5y &  1.0  &  R,R   \\ 
+SW60 & CFHTLS J142843+543713 &  217.1815 &   54.6204 &  0.4 & 19.7 &  1.3 &  1.3 & ASW0007pga &  0.9  &  D,D   \\ 
+SW61 & CFHTLS J142934+562541 &  217.3926 &   56.4281 &  0.5 & 19.0 &  5.9 &  2.7 & ASW0009cjs &  1.0  &  A,G   \\ 
+SW62 & CFHTLS J143055+572431 &  217.7333 &   57.4088 &  0.7 & 19.3 &  1.0 &  2.0 & ASW0007wfj &  1.0  &  A,R   \\ 
+SW63 & CFHTLS J143100+564603 &  217.7510 &   56.7675 &  --  &  --  &  1.8 &  1.7 & ASW00086xq &  1.0  &  A,E   \\ 
+SW64 & CFHTLS J143353+542310 &  218.4736 &   54.3862 &  0.8 & 19.8 &  1.6 &  2.0 & ASW0009cox &  0.9  &  A,R/G   \\ 
+SW65 & CFHTLS J143454+522850 &  218.7270 &   52.4808 &  0.6 & 19.4 &  4.4 &  2.3 & ASW0007k4r &  0.4  &  Q,G/R   \\ 
+SW66 & CFHTLS J143627+563832 &  219.1164 &   56.6425 &  0.5 & 19.5 &  1.5 &  2.3 & ASW0008swn &  1.0  &  A,D   \\ 
+SW67 & CFHTLS J143631+571131 &  219.1315 &   57.1922 &  0.7 & 20.9 &  1.3 &  1.3 & ASW0008pag &  0.8  &  D/A,R   \\ 
+SW68 & CFHTLS J143651+530705 &  219.2150 &   53.1183 &  0.6 & 19.2 &  3.1 &  1.3 & ASW0007h27 &  1.0  &  A,E/G   \\ 
+SW69 & CFHTLS J143658+533807 &  219.2425 &   53.6355 &  0.7 & 19.6 &  0.9 &  2.7 & ASW0007hu2 &  0.9  &  D,D   \\ 
+SW70 & CFHTLS J143838+572647 &  219.6589 &   57.4464 &  0.8 & 20.2 &  1.1 &  2.0 & ASW0008qsm &  1.0  &  A,R   \\ 
+SW71 & CFHTLS J143950+544606 &  219.9610 &   54.7686 &  --  &  --  &  1.7 &  1.3 & ASW00085cp &  0.6  &  A,G/R   \\ 
+SW72 & CFHTLS J220215+012124 &  330.5635 &    1.3567 &  0.3 & 17.4 &  4.6 &  1.7 & ASW0005qiz &  0.5  &  rA,G   \\ 
+SW73 & CFHTLS J220256+023432 &  330.7370 &    2.5758 &  --  &  --  &  6.8 &  2.3 & ASW0007e08 &  1.0  &  A,G/C   \\ 
+SW74 & CFHTLS J220722+013610 &  331.8441 &    1.6030 &  0.8 & 20.3 &  1.0 &  2.0 & ASW0001uuz &  0.6  &  A,R   \\ 
+SW75 & CFHTLS J221101+003401 &  332.7582 &    0.5671 &  0.9 & 20.0 &  1.1 &  1.3 & ASW00090l5 &  1.0  &  A,E/R   \\ 
+SW76 & CFHTLS J221306+014708 &  333.2758 &    1.7856 &  --  & 17.1 &  1.4 &  1.7 & ASW0008wmr &  1.0  &  A,S   \\ 
+SW77 & CFHTLS J221513+010240 &  333.8060 &    1.0445 &  --  &  --  &  0.8 &  1.7 & ASW0008dxh &  0.6  &  A,R/G   \\ 
+SW78 & CFHTLS J221519+005758 &  333.8321 &    0.9661 &  0.4 & 20.2 &  1.0 &  1.7 & ASW0008xbu &  1.0  &  A,D   \\ 
+SW79 & CFHTLS J221716+015826 &  334.3189 &    1.9739 &  0.1 & 21.6 &  1.0 &  1.7 & ASW00096rm &  1.0  &  A/R,R   \\ 
+SW80 & CFHTLS J222007-002505 &  335.0307 &   -0.4182 &  0.3 & 21.4 &  1.2 &  2.0 & ASW00094fq &  1.0  &  Q,R/G   \\ 
+\end{longtable}
+\end{center}
+
+\twocolumn
 
@@
 
-%
-%\begin{longtable*}{l c c c c c c c l}
-%\caption{ \label{tab:all} 
-%Characteristics of lens candidates from the \SA sample. }\\
-%ID & RA & Dec &  $i$ & $z_{\rm phot}$ & $R_{\rm A}$ & Rank & Type & previous ID  \\
-%    & (hms) & (dms) &  (mag) &   & (arcsec) &  &  & \\ [1.5ex] \hline \\ 
-%\endfirsthead
-%
-%ID & RA & Dec &  $i$ & $z_{\rm phot}$ & $R_{\rm A}$ & Rank & Type & previous ID  \\
-%    & (hms) & (dms) &  (mag) &   & (arcsec) &  &  & \\ [1.5ex] \hline \\ 
-%\endhead
-%
-%\hline  
-%\multicolumn{11}{p{15cm}}{
-%{\bfseries
-%{\bf m:} This galaxy falls within the masked region as per the catalog from
-%which the magnitudes and the redshift are extracted.  {\bf z:} The magnitudes
-%and/or redshift are not from the catalog instead are measured by the author.
-%}  }\\
-%
-%\endlastfoot
-%   SW1  & 02:01:21.89 & $-$09:15:15.09 & 19.90 &  0.46 &  2.2 &   2.0 & A &  SA18 \\ 
-%   SW2  & 02:02:10.50 & $-$11:09:11.68 & 17.80 &  0.48 &  5.0 &   3.7 & A &  SA87 \\ 
-%\end{longtable*}
-%
-
 \begin{figure*}
@@
 \caption{ \label{fig:lch1}
-Sample of promising lens candidates ($R_{avg}>=2.0$)
-}
-\end{center}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscand_2p0_3p0_1.pdf}
-\caption{ \label{fig:lch2}
-contd. - Sample of promising lens candidates ($R_{avg}>=2.0$)
+Sample of high probability lens candidates ($R_{avg}>=2.0$).
 }
@@
 \caption{ \label{fig:lcl}
-Sample of low probability lens candidates ($1.0<R_{avg}<2.0$)
+Sample of medium probability lens candidates ($1.0<R_{avg}<2.0$).
 }
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
 \subsection{Recovery of known \cfhtls lenses from \sw}

### 2014-09-28 doc/sw-publication-policy-gen.tex
Updates to policies, author_core.tex, renew command for \comment
minor edits

@@
 %
-% Space Warps Publication Policy
+% Space Warps Guidelines & Policy
 %
@@
 (within the logistical constraints). In this document we discuss the relationship
-between the survey teams and the \sw collaboration. 
+between the survey science teams and the \sw collaboration. 
 This document includes guidelines for data provision, the data policy and for publications of \sw-enabled discoveries.
@@
 An expanded definition of the \sw membership is given in the document ``\sw Publication Policy: CFHT-LS''.
-In this document we discuss the relationship between the \sw collaboration and future Survey Science Teams (SST) who are foreseen to liaise with the \sw science and development teams to ingest their survey data into the \sw interface.
+In this document we discuss the relationship between the \sw collaboration and future Survey Science Teams (SST) who wish to use the \sw interface to investigate their data.
+The SSTs will liaise with the \sw science and development teams to ingest their survey data into the \sw interface.
 \sw was established with future surveys in mind and therefore there may be some overlap between current \sw members and the future SSTs.
@@
 If images from a proprietary dataset being made available is a concern for an SST, they should remove the WCS.
-This also has the consequence that it minimises the potential ``scooping'' of potential lens candidate by anyone other than the SST.
+This also has the consequence that it minimises the potential ``scooping'' of  lens candidates by anyone other than the SST.
 In practice, the objects contained in the \sw images will be too faint
@@
 by \texttt{astrometry.net}.
-Please note, however, that we cannot exclude the possibility that object co-ordinates are posted in \Talk.
-For example, co-ordinates of previously published lens candidates or recognisable fields from CFHT-LS have appeared in \Talk.
-
-% becuase being ``scooped'' is a concern,  for an SST then this is a means of prevention. We do
-
-%This would prevent
-%follow-up of any of the objects in the survey by anyone other than the survey
-%team. In practice, the objects contained in the \sw images will be too faint
-%for anyone without access to a large telescope to observe, and may also be
-%absent from any public catalogs, so the opportunities for follow-up will be
-%quite limited. Removing the WCS information is an insurance policy against any
-%competing professional scientists looking to ``scoop'' the survey team,
-%despite the damage it would do to their reputations\footnote{Please note that we cannot exclude the possibility that object co-ordinates are posted in \Talk.
-For example, co-ordinates of previously published lens candidates or recognisable fields from CFHT-LS have appeared in \Talk.} .
-We note that images
-%with field of view less than about 3~arcminutes in diameter are not solvable
-%by \texttt{astrometry.net}.
+\textbf{Please note}, however, that we cannot exclude the possibility that object co-ordinates are posted in \Talk.
+For example, co-ordinates of previously published lens candidates or recognisable fields from CFHT-LS have been posted in \Talk by a very small number of citizens.
 
@@
 \subsection{Future Project Proposals}
-Any future \sw projects are requested to liaise with the PIs regarding their project.
+Any future \sw projects are requested to liaise with the \sw PIs regarding their project.
 We ask that potential project teams first approach the \sw PIs (Marshall, Verma, More collectively contacted via \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com}) with a short description of their project that includes the following information.
@@
 \item Brief outline of the overall goal(s)
+\item Proprietary data issues 
 \end{itemize}
@@
 
-The original \sw papers, by definition, provide a complete description of the system, and its results from the CFHTLS survey. The science team of
+The original \sw papers, by definition, provide a complete description of the system, and its results from the CFHT-LS survey. The science team of
 any other survey (such as DES, RCS, KIDS, PS1, HSC \etc) should be able
-to read these papers before designing their own \sw project, and cite them as justification for some of their decisions.
+to read these papers before designing their own \sw project, and cite them as justification for some of their experimental decisions.
 As the \sw paper series get published, links to the papers will be given in this draft.
@@
 \subsubsection{Journal Papers}
-
+\label{sec:papers}
 In return for the work outlined in Section \ref{sec:series} in setting up the new surveys, the \sw PIs will nominate a
@@
 Any large changes to the analysis code will be documented  by the \sw Science Team.
-The \sw Science Team reserved the right to update the \sw methodology papers.
+The \sw Science Team reserve the right to update the \sw methodology papers.
 
@@
 
-\section{Publication Guidelines}
+\section{Summary of Publication Guidelines}
 \label{sec:publ}
@@
 \item citations to the \sw system papers, \sw I \& II
+\item a small number of \sw authors proposed by the \sw PIs (see \ref{sec:papers}).
 \item the collaboration should be acknowledged in the acknowledgement section with a link to the collaboration membership page (URL: to be confirmed when available).

### 2014-10-28 doc/sw-publication-policy-gen.tex
minor edits to policy gen

@@
 \title{Guidelines and Policy for Surveys using \SW}
-\author{Phil Marshall \& Aprajita Verma}
+\author{Phil Marshall, Aprajita Verma \& Anupreeta More}
 \date{April 15, 2013}
@@
 Any future \sw projects are requested to liaise with the \sw PIs regarding their project.
-We ask that potential project teams first approach the \sw PIs (Marshall, Verma, More collectively contacted via \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com}) with a short description of their project that includes the following information.
+We ask that potential project teams first approach the \sw PIs (Phil Marshall, Anupreeta More, Aprajita Verma, collectively contacted via \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com}) with a short description of their project that includes the following information.
 

### 2014-10-30 doc/acknowledgments.tex
A few notes etc

@@
 The work of AM and SM was supported by World Premier International Research
-Center Initiative (WPI Initiative), MEXT, Japan.
+Center Initiative (WPI Initiative), MEXT, Japan. The work of AM was also supported in
+part by National Science Foundation Grant No. PHYS-1066293 and the hospitality
+of the Aspen Center for Physics. 
 %
@@
 % Other authors.
-%
+PJM and ES thank the Institute of Astronomy and Astrophysics, Academia Sinica
+(ASIAA) and Taiwan's Ministry of Science and Technology (MOST) for their
+financial support of the workshop ``Citizen Science in Astronomy'' in March
+2014, at which some parts of the SWAP analysis was developed.
+
 The \sw project is open source. 

### 2014-10-30 doc/sw-publication-policy-gen.tex

@@
 \author{Phil Marshall, Aprajita Verma \& Anupreeta More}
-\date{April 15, 2013}
+\date{October 27, 2014}
 \maketitle
@@
 This is the direct portal for communication with the \sw community.}).
+
+\vspace{2mm}
+The PIs of the \sw project are the authors of this document, P.\,Marshall, 
+A.\,More and A.\,Verma, please do not hesitate to contact us if you require any further information or have any questions.
+The PIs may be collectively contacted via the email address \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com}
 

### 2014-10-30 doc/sw-system.tex

@@
 purity. To investigate the completeness to the three different types of lens
-in the training set, we ...
-
-\todo{Chris}{complete the above sentence to explain what purity means in the
-divided-by-sim-type case. Thanks! \#66}
+in the training set, we repeat the same procedure, only now we consider only
+the detections of a certain kind of lens and of the non-lenses in the training
+set. We estimate the expected number of lenses and non-lens false positives by
+dividing the lens and dud sets into equal fractions.
+
+\todo{Chris}{That still could be worded better... \# 66}
 
@@
 The optimal sample in this simulated lens search experiment would have been
-constructed with a threshold value of $\pr(\LENS|C,T) > X.XX$. At 100\% purity
-and 9X\% completeness, it would have contained around N lens candidates.
-
-\todo{Chris}{fill in the numbers above, please! :-) \#65}
+constructed with a threshold value of $\pr(\LENS|C,T) > 0.47$. At 100\% purity
+and 89\% completeness, it would have contained around 89 lens candidates.
+% TP + FN ~ 2e-4 * 430000 ~ 100 ~ TP/C ; so TP ~ 89 candidates
 

### 2014-10-30 doc/scripts/simsfig.py
Anu's zoomed-in subject plotting script

@@ -1,0 +1,39 @@
+#!/usr/bin/env python
+from PIL import Image
+from pylab import *
+from mpl_toolkits.axes_grid1.inset_locator import zoomed_inset_axes
+from mpl_toolkits.axes_grid1.inset_locator import mark_inset
+
+##277,299 - lens center
+fnamec="CFHTLS_028_2205_gri.png"
+outputfile="output.pdf"
+halfsize=50;
+
+imgc = Image.open(fnamec)
+
+def pltimg(imname,loca,xl,xh,yh,yl,descrip):
+    ## Main image
+    ax=subplot(3,3,loca);
+    ax.xaxis.set_visible(False)
+    ax.yaxis.set_visible(False)
+    ax.text(0.5,0.1,descrip,transform=ax.transAxes,color="white",weight='bold',horizontalalignment='center',fontsize=8)
+    ax.imshow(imname,cmap="YlOrBr_r");
+    axins=zoomed_inset_axes(ax,2,loc=1)
+    axins.imshow(imname,cmap="YlOrBr_r");
+    
+    ## Inset
+    x1, x2, y1, y2 = xl,xh,yh,yl
+    axins.set_xlim(x1, x2)
+    axins.set_ylim(y1, y2)
+    axins.xaxis.set_visible(False)
+    axins.yaxis.set_visible(False)
+    axins.spines['bottom'].set_color('white')
+    axins.spines['top'].set_color('white')
+    axins.spines['left'].set_color('white')
+    axins.spines['right'].set_color('white')
+    #mark_inset(ax,axins,loc1=2,loc2=4,fc="none",ec="white")
+
+pltimg(imgc,1,277-halfsize,277+halfsize,299+halfsize,299-halfsize,"Group-Galaxy")
+
+subplots_adjust(hspace=1e-1,wspace=0.05)
+savefig(outputfile,bbox_inches="tight");

### 2014-11-04 doc/sw-cfhtls.tex
rearranged and added many sections and figures but are not yet final

@@
 of improving these lens finding robots, we carry out a blind lens search
-in the complete \cfhtls WIDE survey with \sw. We describe the training
+in the complete \cfhtls \textsc{wide} survey with \sw. We describe the training
 sample used for both training the citizen scientists that participated
@@
 with the wide-field imager MegaPrime which has a 1~deg$^2$ field-of-view
-and a pixel size of 0.186\arcsec. The \cfhtls WIDE covers a total area
+and a pixel size of 0.186\arcsec. The \cfhtls \textsc{WIDE} covers a total area
 of 171~deg$^2$ on the sky and it consists of four fields W1, W2, W3 and
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[scale=1.0]{sw-cfhtls-figs/distrib_remu.pdf}
+\caption{ \label{fig:remudist}
+Einstein radius distribution for all types of lenses. The dashed-dotted (blue)
+curves show the theoretical prediction assuming an SIS model at galaxy-scales
+and a total (NFW+Hernquist) model at groups-scales taken from \citep{More2012}.
+}
+\end{center}
+\end{figure}
+
 In this section, we describe some of the properties of our simulated sample for
@@
 %zdiffq=0.1;
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=0.85]{sw-cfhtls-figs/distrib_remu.pdf}
-\caption{ \label{fig:remudist}
-Einstein radius distribution for all types of lenses. The dashed-dotted (blue)
-curves show the theoretical prediction assuming an SIS model at galaxy-scales
-and a total (NFW+Hernquist) model at groups-scales taken from \citep{More2012}.
-}
-\end{center}
-\end{figure*}
 
@@
 
-%\begin{figure*}
-%\begin{center}
-%\includegraphics[scale=0.95]{sw-cfhtls-figs/distrib_srczmag.eps}
-%\caption{ \label{fig:szmdist}
-%Redshift distribution on the left and magnitude distribution on the right of the
-%simulated sample for the background sources. The different types of lines show the
-%distribution correspond to the three types of simulated lenses galaxy-quasar,
-%galaxy-galaxy and group-galaxy. 
-%}
-%\end{center}
-%\end{figure*}
-%
 %
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{\sw Lens Sample}
+
+\subsubsection{Selection of \sw lens candidates}
+\label{sec:results:stage1}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=1.0]{sw-cfhtls-figs/poffl_expr_ncl.pdf}
+\caption{ \label{fig:comp_exp} Comparison of the P(lens) with the expert
+grades and number of classification for each subject.  }
+\end{center}
+\end{figure}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{New lens candidates from \sw}
+\label{sec:results:disc}
+
+{\bf \textcolor{red} {CHANGE THE TABLE, CHECK IF ALL FIGS ARE UPDATED,
+ADD ISD PLOT, CHECK FOR STAGE 1 -- COMPLETENESS OF SIMS AND KNOWN LENSES
+and P value comparison, what about the duplicate lenses near the borders
+- stats on those?, MAKE A STATS TABLE that gives various numbers and
+fractions of (new and known) lens candidates detected at stages 1 and 2.}}
+
+{\it Describe the newly found lenses and explain for a few
+cases why they were missed }
+
+\begin{table}
+\begin{center}
+\caption{ \label{tab:stats} 
+Statistics of detections in \sw }
+\begin{tabular}{l l l l l l}
+\hline
+   &  \multicolumn{2}{c} {Stage I}  & \multicolumn{3}{c}{Stage II} \\ 
+      & KnCa  &  KnCo  & KnCa & KnCo & NeCa \\
+\hline
+\hline
+Number  & 1.0 & 1.0 & 1.0  & 1.0  & 1.0 \\
+Fraction  & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 \\
+P(lens) & 0.95 & 0.95 & 0.3 & 0.3 & 0.3 \\
+
+\hline
+\end{tabular}
+\end{center}
+{KnCa}-- Known lens candidates \\
+{KnCo}-- Known confirmed lenses \\
+{NeCa}-- New lens candidates  \\
+\end{table}
 
@@
 
-\subsection{Discovery of new lenses from \sw}
-\label{sec:results:disc}
-
-{\it Describe the newly found lenses and explain for a few
-cases why they were missed }
-
 \begin{figure*}
 \begin{center}
-\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscand_2p0_3p0.pdf}
+\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscandfin.pdf}
 \caption{ \label{fig:lch1}
-Sample of high probability lens candidates ($R_{avg}>=2.0$).
+Sample of lens candidates with $R_{avg}>=1.3$.
 }
@@
 \begin{center}
-\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscand_1p3_1p7.pdf}
+\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscandfin_1.pdf}
 \caption{ \label{fig:lcl}
-Sample of medium probability lens candidates ($1.0<R_{avg}<2.0$).
+Sample of lens candidates $R_{avg}>=1.3$.
 }
@@
 
-\subsection{Recovery of known \cfhtls lenses from \sw}
-\label{sec:results:reco}
+\subsection{Recovery of known \cfhtls lenses with \sw}
+\label{sec:results:known}
 
@@
 
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
-\subsection{\cfhtls completeness and purity}
-\label{sec:results:sample}
+\begin{figure}
+\begin{center}
+\includegraphics[scale=1.0]{sw-cfhtls-figs/comp_reinst.pdf}
+\caption{ \label{fig:compre} Completeness of simulated and known lens
+samples based on the final \sw sample. }
+\end{center}
+\end{figure}
 
@@
 
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
-\subsection{Stage 1 Classification}
-\label{sec:results:stage1}
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Stage 2 Classification}
-\label{sec:results:stage2}
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Comparison with ``Expert'' Classification}
-\label{sec:results:experts}
+\subsection{Image separation distribution}
+\label{sec:results:isd}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=1.0]{sw-cfhtls-figs/isd_cfhtls_sw.pdf}
+\caption{ \label{fig:isd} Image separation distribution. Comparing
+theoretical predictions with the \cfhtls known lens samples (REF) and
+the same \cfhtls sample after combining with the incremental lens sample
+from \sw }
+\end{center}
+\end{figure}
 
@@
 - state how this will be used in a future \sw paper }
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=1.0]{sw-cfhtls-figs/zlens_reinst.pdf}
+\caption{ \label{fig:zlre}
+Comparison of Lens redshift and Arc radius for all three lens samples,
+namely, from \sw, SARCS and those from the RingFinder.}
+\end{center}
+\end{figure}
 
@@
 }
-
+\subsection{Blind Lens Search}
 We looked at the locations of simulated and real lenses from our data
@@
 support from the NSERC Research Tools and Instruments grant program.
-This work was supported by World Premier International Research Center
-Initiative (WPI Initiative), MEXT, Japan.
 

### 2014-12-11 doc/sw-system.tex
Improved training set image gallery figures. Re-added CFHTLS paper pdf...

@@
 \usepackage{amsmath}
+\usepackage{epsfig}
 
@@
 
-In \Fref{fig:training-gallery} we show 12 example training images from the
+In \Fref{fig:training-gallery} we show 8 example training images from the
 first \sw project (\Sref{sec:data} below).
-
-\todo{Phil, Aprajita}{Make gallery of 6 stage 2 sims and 6 stage 2 duds, to
-give the reader a feel for what the sims look like, and also how the images
-were presented, stretch and scale-wise.}
 
@@
 
-\todo{Phil}{Show some example sims and duds...}
+%%% Sims and Duds from Stage2
+
+\begin{figure*}%[!ht]
+\begin{minipage}[b]{0.24\linewidth}
+\centering\epsfig{file=sw-system-figs/gallery/4.png,width=\linewidth,angle=0,clip=}
+\end{minipage} \hfill
+\begin{minipage}[b]{0.24\linewidth}
+\centering\epsfig{file=sw-system-figs/gallery/5.png,width=\linewidth,angle=0,clip=}
+\end{minipage} \hfill
+\begin{minipage}[b]{0.24\linewidth}
+\centering\epsfig{file=sw-system-figs/gallery/6.png,width=\linewidth,angle=0,clip=}
+\end{minipage} \hfill
+\begin{minipage}[b]{0.24\linewidth}
+\centering\epsfig{file=sw-system-figs/gallery/7.png,width=\linewidth,angle=0,clip=}
+\end{minipage} \hfill
+\caption{Typical \SW ``sims.'' Insets indicate the location of the simulated 
+lens in each of these training
+images. Users needed to click on these specific features in order to make a
+correct classification.} \label{fig:training-gallery:sims}
+\end{figure*}
+
+\begin{figure*}%[!ht]
+\begin{minipage}[b]{0.24\linewidth}
+\centering\epsfig{file=sw-system-figs/gallery/0.png,width=\linewidth,angle=0,clip=}
+\end{minipage} \hfill
+\begin{minipage}[b]{0.24\linewidth}
+\centering\epsfig{file=sw-system-figs/gallery/1.png,width=\linewidth,angle=0,clip=}
+\end{minipage} \hfill
+\begin{minipage}[b]{0.24\linewidth}
+\centering\epsfig{file=sw-system-figs/gallery/2.png,width=\linewidth,angle=0,clip=}
+\end{minipage} \hfill
+\begin{minipage}[b]{0.24\linewidth}
+\centering\epsfig{file=sw-system-figs/gallery/3.png,width=\linewidth,angle=0,clip=}
+\end{minipage} \hfill
+\caption{Typical \SW ``duds.''  All of these subjects were correctly
+classified by the community as not likely to contain gravitational lenses; 
+the insets merely indicate regions where $\sim10\%$ of the volunteers 
+clicked.} \label{fig:training-gallery:duds}
+\end{figure*}
 
@@
 the detectability of these faint features.   Examples of CFHTLS training set
-images can be seen in \Fref{fig:training-gallery}.
+images can be seen in \Fref{fig:training-gallery:duds} and
+\Fref{fig:training-gallery:sims}.
 
@@
 the \sw CFHTLS training set. The trajectory plot for each of the 4 subjects is
-shown to the right of its image. lefthand panels show the most common types of
+shown to the right of its image. Lefthand panels show the most common types of
 trajectories: short step random walks resulting from no high skill classifiers
@@
 classifiers have been involved, causing random walks with longer step lengths
-(top) and catastrophic mis-classifications (bottom right).}
+(top) and catastrophic mis-classifications (bottom right). Insets for the false
+negatives show the lens feature. The inset for the lower righthand panel shows
+where most users believed a lens was located. There is no corresponding inset
+for the lower left panel because no particular feature stood out to users.
+Instead, users clicked many different features.}
 \label{fig:discuss:performance:trajectories}

### 2014-12-16 doc/sw-cfhtls.tex
rearranged and added many sections and figures but are not yet final
add arc magnitude related figs, final gallery, new title

--- 2014-09-08 doc/sw-cfhtls.tex
@@
 \title[\sw II]
-{\SW: II. Did we beat the lens finding robots in CFHTLS?}
+{\SW: II. New lens candidates from the CFHTLS discovered
+through citizen science}
 
@@
 simulated samples of lenses both at galaxy and group-scales as part of
-this training sample. We present 74 new strong gravitational lens
-candidates discovered from the \sw-\cfhtls search. Furthermore, we
-compile a sample of false positives which can be used for robot testing,
-first of its kind for the lensing community. The simulated sample is
-also used to make a comparison between human performance against the
-robots. We find that the XX per cent of the known lens sample is
-recovered and the new lens sample has XX completeness with respect to
-the simulated sample. We make available the following data products:
-simulated sample, simulation code and the false positives sample at XXX.
+this training sample. We present 61 new strong gravitational lens
+candidates discovered from the \sw-\cfhtls search out of which 40
+candidates are promising. Furthermore, we compile a sample of false
+positives which can be used for robot testing, first of its kind for the
+lensing community. The simulated sample is also used to make a
+comparison between human performance against the robots. We find that
+the XX per cent of the known lens sample is recovered and the new lens
+sample has XX completeness with respect to the simulated sample. We make
+available the following data products: simulated sample, simulation code
+and the false positives sample at XXX.
 
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[scale=1.2]{sw-cfhtls-figs/distrib_remu.pdf}
+\caption{ \label{fig:remudist}
+Einstein radius distribution for all types of lenses. The dashed-dotted (blue)
+curves show the theoretical prediction assuming an SIS model at galaxy-scales
+and a total (NFW+Hernquist) model at groups-scales taken from \citep{More2012}.
+}
+\end{center}
+\end{figure}
+
 In this section, we describe some of the properties of our simulated sample for
@@
 
-\subsection{Discovery of new lenses from \sw}
+\subsection{\sw Lens Sample}
+Here, we describe
+
+\subsubsection{Selection of \sw lens candidates}
+\label{sec:results:stage1}
+The images inspected at stage II are assigned P values through the SWAP
+built in the \sw system. Ideally, we would like to have all real lens
+candidates to be assigned high P values. It is not known a priori what
+value of P would give an optimal trade off between high completeness
+and high purity.
+
+Also, since this is the first lens search with \sw, we
+would like to understand how the P correspond to the grades, typically,
+assigned by lens experts.
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=1.2]{sw-cfhtls-figs/poffl_expr_ncl.pdf}
+\caption{ \label{fig:exp_pn} Comparison of the P(lens) with the expert
+grades and number of classification for each subject.  }
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.6]{sw-cfhtls-figs/cand_fp_P.pdf}
+\caption{ \label{fig:stackP} Total number of detections of the known
+candidates, new candidates and the FPs shown relatively for binned
+values of P.
+}
+\end{center}
+\end{figure}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsubsection{New lens candidates from \sw}
 \label{sec:results:disc}
+
+{\bf \textcolor{red} {
+CHECK FOR STAGE 1 -- COMPLETENESS OF SIMS AND KNOWN LENSES
+and P value comparison, what about the duplicate lenses near the borders
+- stats on those?}}
 
@@
 
-%
-%\begin{longtable*}{l c c c c c c c l}
-%\caption{ \label{tab:all} 
-%Characteristics of lens candidates from the \SA sample. }\\
-%ID & RA & Dec &  $i$ & $z_{\rm phot}$ & $R_{\rm A}$ & Rank & Type & previous ID  \\
-%    & (hms) & (dms) &  (mag) &   & (arcsec) &  &  & \\ [1.5ex] \hline \\ 
-%\endfirsthead
-%
-%ID & RA & Dec &  $i$ & $z_{\rm phot}$ & $R_{\rm A}$ & Rank & Type & previous ID  \\
-%    & (hms) & (dms) &  (mag) &   & (arcsec) &  &  & \\ [1.5ex] \hline \\ 
-%\endhead
-%
-%\hline  
-%\multicolumn{11}{p{15cm}}{
-%{\bfseries
-%{\bf m:} This galaxy falls within the masked region as per the catalog from
-%which the magnitudes and the redshift are extracted.  {\bf z:} The magnitudes
-%and/or redshift are not from the catalog instead are measured by the author.
-%}  }\\
-%
-%\endlastfoot
-%   SW1  & 02:01:21.89 & $-$09:15:15.09 & 19.90 &  0.46 &  2.2 &   2.0 & A &  SA18 \\ 
-%   SW2  & 02:02:10.50 & $-$11:09:11.68 & 17.80 &  0.48 &  5.0 &   3.7 & A &  SA87 \\ 
-%\end{longtable*}
-%
+\begin{table}
+\begin{center}
+\caption{ \label{tab:stats} 
+Statistics of detections in \sw }
+\begin{tabular}{l l l l l l}
+\hline
+   &  \multicolumn{2}{c} {Stage I}  & \multicolumn{3}{c}{Stage II} \\ 
+      & KnCa  &  KnCo  & KnCa & KnCo & NeCa \\
+\hline
+\hline
+Number  & 128 & 34 & 107  & 34  & 61 \\
+\%  & 29 & 58 & 25 & 58  & XX \\
+P(lens) & 0.95 & 0.95 & 0.3 & 0.3 & 0.3 \\
+
+%% ####stage1
+%% cand 128/436
+%% conf  34/59
+
+%% ####stage 2
+%% sarcs conf 18/26
+%% sarcs cand  55/106
+%% RF conf 16/33
+%% RF cand  52/330
+
+\hline
+\end{tabular}
+\end{center}
+{KnCa}-- Known lens candidates \\
+{KnCo}-- Known confirmed lenses \\
+{NeCa}-- New lens candidates  \\
+\end{table}
+
+\onecolumn
+
+\begin{center}
+\begin{longtable}{lrrrrrrrrrr}
+\caption{ \label{tab:swcands} 
+Sample of the \sw new lens candidates. }\\
+\hline
+SW ID & Name & RA & Dec &  $z_{\rm phot}$ & $m_i$ & $R_{\rm A}$ & G & ZooID & P & Comments  \\
+  &  & (deg) & (deg) &  & (mag) &  (") &  &  & & \\ 
+\hline
+\endfirsthead
+\hline
+SW ID & Name & RA & Dec &  $z_{\rm phot}$ & $m_i$ & $R_{\rm A}$ & G & ZooID & P & Comments  \\
+  &  & (deg) & (deg) &  & (mag) &  (") &  &  & & \\ 
+\hline
+\endhead
+\hline
+\multicolumn{11}{p{18cm}}{
+The column Comments has two type of notes. The first is about the lens
+image configuration where the symbols mean the following A: Arc, D: Double, Q:
+Quad, R: Ring. The second is a comment on the type of lens assessed
+visually. Note that this classification is not based on colors or spectral
+analysis. The symbols are E: Elliptical, S: (face on) Spiral, G: Group-scale, D:
+Edge on disk, R: Red starforming galaxy.  This galaxy falls within the masked region as per the catalog from
+which the magnitudes and the redshift are extracted.  
+}\\  
+\endlastfoot
+ SW1 & CFHTLS J022409-105807 &   36.0398 &  -10.9688 &  0.0 &  0.0 &  4.8 &  3.0 & ASW0004dv8 &  1.0  &  A,G   \\ 
+ SW2 & CFHTLS J140522+574333 &  211.3426 &   57.7259 &  0.7 & 19.7 &  1.0 &  2.7 & ASW000619d &  0.7  &  A,R   \\ 
+ SW3 & CFHTLS J142603+511420 &  216.5149 &   51.2390 &  0.0 &  0.0 &  4.4 &  2.7 & ASW0006mea &  0.7  &  A,G   \\ 
+ SW4 & CFHTLS J142934+562541 &  217.3926 &   56.4281 &  0.5 & 19.0 &  5.9 &  2.7 & ASW0009cjs &  0.8  &  A,G   \\ 
+ SW5 & CFHTLS J143454+522850 &  218.7270 &   52.4808 &  0.6 & 19.4 &  4.4 &  2.7 & ASW0007k4r &  0.4  &  Q,G/R   \\ 
+ SW6 & CFHTLS J143627+563832 &  219.1164 &   56.6425 &  0.5 & 19.4 &  1.5 &  2.7 & ASW0008swn &  0.9  &  A,D   \\ 
+ SW7 & CFHTLS J220256+023432 &  330.7369 &    2.5758 &  0.0 &  0.0 &  6.8 &  2.7 & ASW0007e08 &  0.8  &  A,G/C   \\ 
+ SW8 & CFHTLS J020832-043315 &   32.1340 &   -4.5543 &  1.0 & 21.0 &  1.6 &  2.3 & ASW0002asp &  1.0  &  A,R   \\ 
+ SW9 & CFHTLS J020848-042427 &   32.2011 &   -4.4075 &  0.8 & 20.5 &  1.1 &  2.3 & ASW0002bmc &  0.9  &  D,D   \\ 
+SW10 & CFHTLS J020849-050429 &   32.2078 &   -5.0749 &  0.8 & 20.6 &  0.9 &  2.3 & ASW0002qtn &  1.0  &  A,R   \\ 
+SW11 & CFHTLS J022406-062846 &   36.0256 &   -6.4796 &  0.4 & 19.6 &  0.9 &  2.3 & ASW0003wsu &  0.7  &  A,E   \\ 
+SW12 & CFHTLS J022805-051733 &   37.0236 &   -5.2927 &  0.4 & 18.8 &  1.4 &  2.3 & ASW0009ans &  1.0  &  Q,E   \\ 
+SW13 & CFHTLS J023123-082535 &   37.8468 &   -8.4266 &  0.0 &  0.0 &  1.2 &  2.3 & ASW0004xjk &  0.3  &  A,R   \\ 
+SW14 & CFHTLS J084841-045237 &  132.1708 &   -4.8772 &  0.3 & 19.0 &  1.0 &  2.3 & ASW0004nan &  1.0  &  A,E   \\ 
+SW15 & CFHTLS J140030+574437 &  210.1260 &   57.7437 &  0.4 & 18.2 &  2.0 &  2.3 & ASW0009bp2 &  0.6  &  A,E   \\ 
+SW16 & CFHTLS J140622+520942 &  211.5958 &   52.1617 &  0.7 & 20.3 &  1.2 &  2.3 & ASW0005rnb &  0.7  &  A,R   \\ 
+SW17 & CFHTLS J143658+533807 &  219.2425 &   53.6355 &  0.7 & 19.6 &  0.9 &  2.3 & ASW0007hu2 &  0.6  &  D,D   \\ 
+SW18 & CFHTLS J020642-095157 &   31.6750 &   -9.8658 &  0.2 & 20.8 &  0.9 &  2.0 & ASW0001ld7 &  0.8  &  A,R   \\ 
+SW19 & CFHTLS J021221-105251 &   33.0881 &  -10.8811 &  0.3 & 17.9 &  1.8 &  2.0 & ASW0002dx7 &  0.8  &  D,E/S   \\ 
+SW20 & CFHTLS J022533-053204 &   36.3888 &   -5.5346 &  0.5 & 19.4 &  3.6 &  2.0 & ASW0004m3x &  0.4  &  A,R/G   \\ 
+SW21 & CFHTLS J022716-105602 &   36.8186 &  -10.9341 &  0.4 & 17.2 &  1.8 &  2.0 & ASW0009ab8 &  0.7  &  A,E/G   \\ 
+SW22 & CFHTLS J023008-054038 &   37.5359 &   -5.6774 &  0.6 & 19.7 &  1.9 &  2.0 & ASW0003r61 &  0.5  &  A,E   \\ 
+SW23 & CFHTLS J023051-082423 &   37.7141 &   -8.4064 &  0.0 &  0.0 &  0.8 &  2.0 & ASW000412m &  0.4  &  A,E   \\ 
+SW24 & CFHTLS J023315-042243 &   38.3133 &   -4.3789 &  0.7 & 19.7 &  1.0 &  2.0 & ASW00050sk &  0.8  &  A,R   \\ 
+SW25 & CFHTLS J090308-043252 &  135.7844 &   -4.5479 &  0.0 &  0.0 &  1.2 &  2.0 & ASW00007mq &  0.6  &  A,E   \\ 
+SW26 & CFHTLS J135755+571722 &  209.4827 &   57.2897 &  0.8 & 20.2 &  1.3 &  2.0 & ASW0005ma2 &  0.8  &  D,D   \\ 
+SW27 & CFHTLS J141432+534004 &  213.6372 &   53.6679 &  0.7 & 21.4 &  0.9 &  2.0 & ASW0006jh5 &  0.8  &  A,R   \\ 
+SW28 & CFHTLS J143055+572431 &  217.7333 &   57.4088 &  0.7 & 19.3 &  1.0 &  2.0 & ASW0007wfj &  0.9  &  A,R   \\ 
+SW29 & CFHTLS J143838+572647 &  219.6589 &   57.4464 &  0.8 & 20.2 &  1.1 &  2.0 & ASW0008qsm &  0.9  &  A,R   \\ 
+SW30 & CFHTLS J021057-084450 &   32.7414 &   -8.7474 &  0.0 &  0.0 &  2.5 &  1.7 & ASW0002p8y &  0.4  &  A,G   \\ 
+SW31 & CFHTLS J021514-092440 &   33.8109 &   -9.4111 &  0.7 & 19.9 &  2.6 &  1.7 & ASW00021r0 &  0.4  &  A,R/G   \\ 
+SW32 & CFHTLS J022359-083651 &   35.9995 &   -8.6143 &  0.0 &  0.0 &  3.1 &  1.7 & ASW0004iye &  0.4  &  A,E   \\ 
+SW33 & CFHTLS J022745-062518 &   36.9387 &   -6.4218 &  0.6 & 20.5 &  1.2 &  1.7 & ASW0003s0m &  0.5  &  A,R   \\ 
+SW34 & CFHTLS J023453-093032 &   38.7232 &   -9.5089 &  0.5 & 19.8 &  0.7 &  1.7 & ASW00051ld &  0.3  &  A,D   \\ 
+SW35 & CFHTLS J084833-044051 &  132.1385 &   -4.6809 &  0.8 & 20.2 &  0.9 &  1.7 & ASW0004wgd &  0.7  &  A,R   \\ 
+SW36 & CFHTLS J090248-010232 &  135.7020 &   -1.0424 &  0.4 & 19.1 &  1.4 &  1.7 & ASW000096t &  0.6  &  D,E   \\ 
+SW37 & CFHTLS J143100+564603 &  217.7511 &   56.7675 &  0.0 &  0.0 &  1.8 &  1.7 & ASW00086xq &  0.8  &  A,E   \\ 
+SW38 & CFHTLS J143353+542310 &  218.4736 &   54.3862 &  0.8 & 19.8 &  1.6 &  1.7 & ASW0009cox &  0.6  &  A,R/G   \\ 
+SW39 & CFHTLS J220215+012124 &  330.5635 &    1.3567 &  0.3 & 17.4 &  4.6 &  1.7 & ASW0005qiz &  0.5  &  rA,G   \\ 
+SW40 & CFHTLS J221306+014708 &  333.2758 &    1.7856 &  0.0 & 17.1 &  1.4 &  1.7 & ASW0008wmr &  0.9  &  A,S   \\ 
+SW41 & CFHTLS J221513+010240 &  333.8056 &    1.0446 &  0.0 &  0.0 &  0.8 &  1.7 & ASW0008dxh &  0.3  &  A,R/G   \\ 
+SW42 & CFHTLS J221519+005758 &  333.8321 &    0.9661 &  0.4 & 20.2 &  1.0 &  1.7 & ASW0008xbu &  0.8  &  A,D   \\ 
+SW43 & CFHTLS J221716+015826 &  334.3189 &    1.9739 &  0.1 & 21.6 &  1.0 &  1.7 & ASW00096rm &  1.0  &  A/R,R   \\ 
+SW44 & CFHTLS J020810-040220 &   32.0450 &   -4.0389 &  1.0 & 20.8 &  1.8 &  1.3 & ASW0001c3j &  0.7  &  A,R   \\ 
+SW45 & CFHTLS J021021-093415 &   32.5898 &   -9.5711 &  0.4 & 18.4 &  2.7 &  1.3 & ASW0002k40 &  0.4  &  D,S   \\ 
+SW46 & CFHTLS J021225-085211 &   33.1051 &   -8.8697 &  0.8 & 19.5 &  2.1 &  1.3 & ASW00024id &  1.0  &  R,R   \\ 
+SW47 & CFHTLS J021317-084819 &   33.3234 &   -8.8055 &  0.5 & 19.8 &  1.3 &  1.3 & ASW00024q6 &  0.4  &  A,R/E   \\ 
+SW48 & CFHTLS J022843-063316 &   37.1794 &   -6.5547 &  0.5 & 19.1 &  1.8 &  1.3 & ASW0003r6c &  0.3  &  D/A,E   \\ 
+SW49 & CFHTLS J090219-053923 &  135.5794 &   -5.6566 &  0.0 &  0.0 &  2.0 &  1.3 & ASW0000g95 &  1.0  &  A,R/E   \\ 
+SW50 & CFHTLS J090319-040146 &  135.8311 &   -4.0297 &  0.0 & 19.8 &  1.2 &  1.3 & ASW00007ls &  0.5  &  A,R/E   \\ 
+SW51 & CFHTLS J090333-005829 &  135.8886 &   -0.9749 &  0.0 &  0.0 &  2.1 &  1.3 & ASW00008a0 &  1.0  &  A/D,E/G   \\ 
+SW52 & CFHTLS J135724+561614 &  209.3536 &   56.2707 &  0.0 &  0.0 &  2.6 &  1.3 & ASW0006e0o &  0.9  &  D,E   \\ 
+SW53 & CFHTLS J140027+541028 &  210.1164 &   54.1746 &  0.0 &  0.0 &  1.2 &  1.3 & ASW0006a07 &  0.6  &  Q,R/E   \\ 
+SW54 & CFHTLS J140425+520506 &  211.1062 &   52.0850 &  0.4 & 18.9 &  1.4 &  1.3 & ASW0005o0w &  0.6  &  D,E   \\ 
+SW55 & CFHTLS J141518+513915 &  213.8290 &   51.6542 &  0.4 & 18.3 &  3.0 &  1.3 & ASW00070vl &  0.8  &  D,E   \\ 
+SW56 & CFHTLS J142620+561356 &  216.5870 &   56.2323 &  0.5 & 19.5 &  1.3 &  1.3 & ASW0007sez &  0.8  &  A/R,S   \\ 
+SW57 & CFHTLS J142652+560002 &  216.7201 &   56.0006 &  0.0 &  0.0 &  1.5 &  1.3 & ASW0007t5y &  1.0  &  R,R   \\ 
+SW58 & CFHTLS J142843+543713 &  217.1815 &   54.6204 &  0.4 & 19.7 &  1.3 &  1.3 & ASW0007pga &  0.6  &  D,D   \\ 
+SW59 & CFHTLS J143631+571131 &  219.1315 &   57.1922 &  0.7 & 20.9 &  1.3 &  1.3 & ASW0008pag &  0.6  &  D/A,R   \\ 
+SW60 & CFHTLS J143651+530705 &  219.2150 &   53.1183 &  0.6 & 19.2 &  3.1 &  1.3 & ASW0007h27 &  1.0  &  A,E/G   \\ 
+SW61 & CFHTLS J143950+544606 &  219.9609 &   54.7686 &  0.0 &  0.0 &  1.7 &  1.3 & ASW00085cp &  0.4  &  A,G/R   \\ 
+\end{longtable}
+\end{center}
+
+\twocolumn
 
@@
 \begin{center}
-\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscand_2p0_3p0.pdf}
-\caption{ \label{fig:lch1}
-Sample of promising lens candidates ($R_{avg}>=2.0$)
+\includegraphics[scale=1.9]{sw-cfhtls-figs/lenscandfin.pdf}
+\caption{ \label{fig:lc}
+Sample of lens candidates with G$>=$1.3.
 }
@@
 \begin{center}
-\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscand_2p0_3p0_1.pdf}
-\caption{ \label{fig:lch2}
-contd. - Sample of promising lens candidates ($R_{avg}>=2.0$)
-}
-\end{center}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscand_1p3_1p7.pdf}
-\caption{ \label{fig:lcl}
-Sample of low probability lens candidates ($1.0<R_{avg}<2.0$)
+\includegraphics[scale=1.9]{sw-cfhtls-figs/lenscandfin_1.pdf}
+\caption{ \label{fig:lc1}
+Sample of lens candidates G$>=1.3$.
 }
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{Recovery of known \cfhtls lenses from \sw}
-\label{sec:results:reco}
+
+\subsection{Recovery of known \cfhtls lenses with \sw}
+\label{sec:results:known}
 
@@
 
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
-\subsection{\cfhtls completeness and purity}
-\label{sec:results:sample}
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=1.0]{sw-cfhtls-figs/comp_reinst_mag.pdf}
+\caption{ \label{fig:compre} Fraction of lens candidates detected by \sw
+as a function of the Einstein radius and arc $g$ band magnitudes for
+three lens samples, namely, simulated lenses, known confirmed lenses and
+the lens candidates sample. XXXX sims are stage1 and real sample values
+are for stage 2. }
+\end{center}
+\end{figure*}
 
@@
 
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
-\subsection{Stage 1 Classification}
-\label{sec:results:stage1}
+\subsection{Image separation distribution}
+\label{sec:results:isd}
 
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Stage 2 Classification}
-\label{sec:results:stage2}
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Comparison with ``Expert'' Classification}
-\label{sec:results:experts}
+\begin{figure}
+\begin{center}
+\includegraphics[scale=1.2]{sw-cfhtls-figs/isd_cfhtls_sw.pdf}
+\caption{ \label{fig:isd} Image separation distribution. Comparing
+theoretical predictions with the \cfhtls known lens samples (REF) and
+the same \cfhtls sample after combining with the incremental lens sample
+from \sw }
+\end{center}
+\end{figure}
 
@@
 
-Further work.
-
 Describe the importance of this kind of study 
@@
 - state how this will be used in a future \sw paper }
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.65]{sw-cfhtls-figs/zl_mg_re.pdf}
+\caption{ \label{fig:zlre}
+Comparison of Lens redshift and magnitude as a function of Arc radius for all three lens samples,
+namely, from \sw, SARCS and those from the RingFinder. Also,
+corresponding histograms are shown.}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.6]{sw-cfhtls-figs/stacked_lenscand_rein.pdf}
+\includegraphics[scale=0.6]{sw-cfhtls-figs/stacked_lenscand_mag.pdf}
+\caption{ \label{fig:stackre}
+Detections by three methods the Ringfinder, \sw and the Arcfinder as a
+function of the Einstein radius and $g$ band magnitude of the lensed
+images. XXXX check how different are the estimates from the different measurement techniques for a given lens candidates. }
+\end{center}
+\end{figure}
 
@@
 underneath the sims ie. from the D11;
-
 }
 
+\subsection{Blind Lens Search}
 We looked at the locations of simulated and real lenses from our data
 those were missed by \sw compared to the locations of the lenses that
-got detected. The real lens sample consists of a total of 383 candidates
-which have $P_l>2.e-5$ and received a rank of $R_{avg}>0$ from the
+got detected. The real lens sample consists of a total of XXXX candidates
+which have $P_l>2.e-5$XXXXX (check this) and received a rank of G$>0$ from the
 expert. We do not find any obvious dependency in the rate of detections

### 2014-12-22 doc/sw-system.tex
todo: look up PH numbers

@@
 SonnenfeldEtal2012,SonnenfeldEtal2013}, including on sub-galactic scales
-\citep[e.g.][]{Dalal+Kochanek2002,VegettiEtal2010,HezavehEtal2013}. Any
-strong lens can provide magnification of a factor of 10 or more, providing a
-deeper, higher resolution view of the distant universe through these ``cosmic
-telescopes'' \citep[e.g.][]{StarkEtal2008,NewtonEtal2011}. Lensed quasars enable
-cosmography via the time delays between the multiple images' lightcurves
-\citep[e.g.][]{TewesEtal2013,SuyuEtal2013}, and study of the accretion disk itself
-through the microlensing effect \citep[e.g.][]{PoindexterEtal2008}. All of these
-science projects would benefit from being able to draw from a larger sample of
-lenses.
+\citep[e.g.][]{Dalal+Kochanek2002,VegettiEtal2010,HezavehEtal2013}. Any strong
+lens can provide magnification of a factor of 10 or more, providing a deeper,
+higher resolution view of the distant universe through these ``cosmic
+telescopes'' \citep[e.g.][]{StarkEtal2008,NewtonEtal2011}. Lensed quasars
+enable cosmography via the time delays between the multiple images'
+lightcurves \citep[e.g.][]{TewesEtal2013,SuyuEtal2013}, and study of the
+accretion disk itself through the microlensing effect
+\citep[e.g.][]{PoindexterEtal2008}. All of these investigations would
+benefit from being able to draw from a larger sample of lenses.
 
 In the last decade the numbers of detections of these rare cosmic alignments
-has increased by an order of magnitude, thanks to wide field surveys such as
+has increased by an order of magnitude, thanks to searches carried out in 
+wide field surveys, such as
 CLASS \citep[e.g.]{BrowneEtal2003}, SDSS \citep[e.g.][]
@@
 \citep{GavazziEtal2008,CollettEtal2012} and lensed supernovae
-\citep{QuimbyEtal2014} are good examples of this.
+\citep{QuimbyEtal2014,KellyEtal2014} are good examples of this.
 
@@
 because they require expensive high resolution imaging follow-up; consequently
-they have so far produced yields in the tens to hundreds. An alternative approach
-is to search images of sufficiently high resolution and color contrast, and
-confirm the systems as gravitational lenses by modeling the survey data
-themselves \citep[][]{MarshallEtal2009}. Several square degrees of HST images
-have been searched, yielding several tens of galaxy-scale lenses
+they have so far produced yields in the tens to hundreds. An alternative
+approach is to search images already of sufficiently high resolution and color
+contrast, and confirm the systems as gravitational lenses by modeling the
+survey data themselves \citep[][]{MarshallEtal2009}. Several square degrees of
+HST images have been searched, yielding several tens of galaxy-scale lenses
 \citep[e.g.][]{MoustakasEtal2007,FaureEtal2008,Jackson2008,MoreEtal2012,
-PawaseEtal2014}.
-Similarly, searches of over a hundred square degrees of CFHT Legacy Survey
-ground-based imaging, also with sub-arcsecond image quality, have revealed a
-smaller number of wider image separation group-scale systems
-\citep[e.g.][]{CabanacEtal2007,MoreEtal2012}. Detecting galaxy-scale lenses from
-the ground is hard, but feasible albeit lower efficiency and requiring HST or
-spectroscopic follow-up to confirm the candidates as lenses
+PawaseEtal2014}. Similarly, searches of over a hundred square degrees of CFHT
+Legacy Survey (CFHTLS) ground-based imaging, also with sub-arcsecond image quality,
+have revealed a smaller number of wider image separation group-scale systems
+\citep[e.g.][]{CabanacEtal2007,MoreEtal2012}. Detecting galaxy-scale lenses
+from the ground is hard, but feasible albeit with lower efficiency and requiring
+HST or spectroscopic follow-up to confirm the candidates as lenses
 \citep[e.g.][]{GavazziEtal2014}.
@@
 observations? There are two approaches to detecting lenses in imaging surveys.
-The first one is robotic: automated analysis of object catalogs and/or the
+The first one is robotic: automated analysis of the object catalogs and the
 survey images. The candidate samples produced by these methods have, to date,
 not been of high purity  \citep[see
-e.g.][]{MarshallEtal2009,MoreEtal2012,GavazziEtal2014}, with visual inspection by
-teams of humans still required to narrow down the robotically-generated
+e.g.][]{MarshallEtal2009,MoreEtal2012,GavazziEtal2014}, with visual inspection
+by teams of humans still required to narrow down the robotically-generated
 samples. In this approach, the image data may or may not be explicitly
@@
 do contained in the inspector's brain. The second approach simply cuts out the
-robot middleman: \citet{FaureEtal2008,Jackson2008} and \citet{PawaseEtal2014}
-all performed entirely visual searches for lenses in HST imaging.
-
-Visual image inspection seems, at present, unavoidable at some level when
-seraching for gravitational lenses. The technique has some drawbacks, however.
-First is that humans are only humans, and they make mistakes. The solution to
-this is to operate in teams, providing multiple classifications of the same
-images in order to catch errors and correct them. Second, and relatedly, is
-that humans get tired. With a well-designed classification interface, a human
-might be able to inspect images at a rate of one astronomical object per
-second (provided the majority are indeed uninteresting). At $10^4$ massive
-galaxies, and 10 lenses, per square degree, visual lens searches in good
-quality imaging data are limited to a few square degrees per inspector per
-day. Scaling to thousands of square degrees therefore means either robotically
-reducing the number of targets for inspection, or increasing the number of
-inspectors, or both.
+robot middleman: \citet{MoustakasEtal2007,FaureEtal2008,Jackson2008} and
+\citet{PawaseEtal2014} all performed successful, entirely visual searches for
+lenses in HST imaging.
+
+Visual image inspection thus seems, at present, unavoidable at some level when
+searching for gravitational lenses. The technique has some drawbacks, however.
+First is that humans are only humans, and they make mistakes. A solution to
+this is for the inspectors to operate in teams, providing multiple
+classifications of the same images in order to catch errors and correct them.
+Second, and relatedly, is that humans get tired. With a well-designed
+classification interface, a human might be able to inspect images at a rate of
+one astronomical object per second (provided the majority are indeed
+uninteresting). At $10^4$ massive galaxies, and 10 lenses, per square degree,
+visual lens searches in good quality imaging data are limited to a few square
+degrees per inspector per day. Scaling to thousands of square degrees
+therefore means either robotically reducing the number of targets for
+inspection, or increasing the number of inspectors, or both.
 
@@
 more like 10 seconds per object. Hiring 10 inspectors to assess complex images
-full time full time for five months may not be the most cost-effective or
+full time for five months may not be the most cost-effective or
 reliable strategy. Alternatively, a team of $10^6$ inspectors could, in
@@
 
-In this paper, we describe the \sw website, an online system that enables 
-crowd-sourced gravitational lens detection by inviting volunteers to classify
-astronomical survey images as containing lens candidates or not.  In a
-companion paper (More et al, in preparation, herafter \papertwo) we will
-present the new gravitational lenses discovered in our first experimental lens
-search, and begin to investigate the differences between lens detections made
-in \sw and those made with automated techniques. Here though, we try to answer
-the following questions:
+\todo{PJM}{Fill in numbers of volunteers and detections from PlanetHunters.}
+
+In this paper, we describe the \sw web application, an online system that
+enables  crowd-sourced gravitational lens detection by inviting volunteers to
+classify astronomical survey images as containing lens candidates or not.  In
+a companion paper (More et al, in preparation, herafter \papertwo) we will
+present the new gravitational lenses discovered in our first, experimental,
+lens search, and begin to investigate the differences between lens detections
+made in \sw and those made with automated techniques. Here though, we simply
+try to answer the following questions:
 
@@
 \item How reliably can we find gravitational lenses using the \sw
-system? What is the completeness of the sample produced?
+system? What is the completeness of the sample produced likely to be?
 
@@
 Our basic method in this paper is to analyze the performance of the \sw system
-on a ``training set'' of simulated lenses and known non-lenses. This allows us
-to estimate completeness and purity with respect to gravitational lenses that
-have the same properties of the training set. In \papertwo we carry
-out similar tests but with a sample of known (real) lenses {\it in situ}.
+on the ``training set'' of simulated lenses and known non-lenses. This allows
+us to estimate completeness and purity with respect to gravitational lenses
+that have the same properties of the training set. In \papertwo we carry out
+similar tests but with a sample of known (real) lenses {\it in situ}.
 
@@
 classification interface and the volunteers who make up the \sw
-collaboration,  explain how we use training images, and describe our two stage
-candidate selection strategy. We then briefly introduce, in \Sref{sec:data}
-the particular dataset used in the first experimental tests of the \sw system,
-and how we prepared the images prior to displaying them in the web interface.
-In \Sref{sec:swap} we describe our methodology for interpreting the
-classifications made by the volunteers, and then present the results of system
-performance tests  made on the training images in \Sref{sec:results}.  We
-discuss the implications of our results for future lens searches in
-\Sref{sec:discuss} and draw conclusions in \Sref{sec:conclude}.
-
-% \section{Introduction}
-% \label{sec:intro}
-% \section{Experiment Design}
-% \label{sec:design}
-% \subsection{Training}
-% \label{sec:design:training}
-% \subsection{Stage 1: Initial Classification}
-% \label{sec:design:stage1}
-% \subsection{Stage 2: Refinement}
-% \label{sec:design:stage2}
-% \section{Data}
-% \label{sec:data}
-% \subsection{The CFHT Legacy Survey}
-% \label{sec:data:CFHTLS}
-% \subsection{Image Presentation}
-% \label{sec:data:display}
-% \section{Classification Analysis}
-% \label{sec:swap}
-% \section{Results}
-% \label{sec:results}
-% \subsection{Crowd Properties}
-% \label{sec:results:crowd}
-% \subsection{Sample completeness and purity}
-% \label{sec:results:sample}
-% \section{Discussion}
-% \label{sec:discuss}
-% \section{Conclusions}
-% \label{sec:conclude}
+collaboration,  explain how we use the training images, and describe our
+two-stage candidate selection strategy. We then briefly introduce, in
+\Sref{sec:data}, the particular dataset used in the first experimental tests
+of the \sw system, and how we prepared the images prior to displaying them in
+the web interface. In \Sref{sec:swap} we describe our methodology for
+interpreting the classifications made by the volunteers, and then present the
+results of system performance tests  made on the training images in
+\Sref{sec:results}.  We discuss the implications of our results for future
+lens searches in \Sref{sec:discuss} and draw conclusions in
+\Sref{sec:conclude}.
 

### 2014-12-22 doc/sw-system.tex
Placeholder section on crowd classification speed

@@
 The basic steps of a visual search for gravitational lenses are: 1) prepare
-images, 2) display them to an inspector, 3) record the inspector's
+the images, 2) display them to an inspector, 3) record the inspector's
 classification of each image (as, for example, containing a lens candidate or
-not) and 4) analyzing those classifications (and all others) in order to
-produce a final candidate list. We describe step 1 in \Sref{sec:data} and step
-4 in \Sref{sec:swap}. In this section we take a volunteer's eye view and
-begin by describing the \sw classification interface, the crowd of volunteers,
-and the interactions between the two.
+not) and 4) analyze that classification along with all others to produce a
+final candidate list. We describe step 1 in \Sref{sec:data} and step 4 in
+\Sref{sec:swap}. In this section we take a volunteer's eye view and begin by
+describing the \sw classification interface, the crowd of volunteers, and the
+interactions between the two.
 
@@
 
-\subsection{Classification Interface}
+\subsection{The Classification Interface}
 \label{sec:design:interface}
@@
 
+% PJM: how quickly? How much clock time per classification?
+
 For the more interesting subjects, the CI offers two features that  enable
-further investigation of the subjects. First is the ``Quick Dashboard'' (QD) a
+further investigation of the subjects. The first is the ``Quick Dashboard'' (QD) a
 more advanced image viewer. This allows the viewer to compare three different
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Classification Speed}
+\label{sec:results:speed}
+
+How fast does the \sw crowd classify subjects? Each agent records the
+timestamp of each classification its volunteer makes; by measuring the time
+lags between successive classifications we can make estimates of each
+volunteer's speed, and that of the crowd.
+
+A histogram of all time lags for all volunteers is shown in
+\Fref{fig:crowd:timelags}, with those of the ``experienced volunteers''
+(those who classified 10 or more training subjects.) overlaid.
+
+\todo{PJM}{Make this histogram, and try and infer the typical inter-session
+lag.}
+
+Defining a new classification session to have started at least X minutes since
+the previous classification, we assign all classifications into sessions, and
+compute the mean intra-session time lag recorded by each agent. This gives
+some measure of classification speed within a session; we also compute the 
+mean session length, and the rate of information contribution. The
+latter is the most relevant measure of speed for future project design. The
+distributions of these speeds are shown in \Fref{fig:crowd:speeddists}, in a corner
+plot that also shows the effort and skill from \Fref{fig:crowd:cornerplot}. We
+see that ...
+
+The overall contribution rate for the \sw crowd was found (by simple average),
+and is plotted as a function of time in \Fref{fig:crowd:speed}. We see that
+...
+
+\todo{Phil, Chris}{Compute classification speeds, make plots, discuss.}
 

### 2015-01-20 analysis/swap/agent.py
Rather major update to the SWAP pipeline. Refactored so that offline analysis can be done in a logical manner. TODOs still include fixing trajectory plots for offline analysis and also discovering and fixing bugs.

@@ -65,6 +65,13 @@ class Agent(object):
         clearly sub-optimal, but might be good enough for a first
         attempt. We'll see!
 
+        Agents now also have a kind attribute. Agents may be 'normal' users,
+        'super' users, or 'banned' users. Currently being a 'super' user does
+        nothing, but maybe in the future they will get harder images.  'banned'
+        agents are ones whose contributions are ignored. Agents do not have a
+        method for converting themselves to 'super' or 'banned' -- that is
+        something for SWAP, or a bureau to do.
+
 
     INITIALISATION
         name
@@ -85,12 +92,14 @@ class Agent(object):
 
     HISTORY
       2013-04-17:  Started Marshall (Oxford)
+      2015-01-19:  Added 'kind'. (CPD)
     """
 
 # ----------------------------------------------------------------------
 
     def __init__(self,name,pars):
         self.name = name
+        self.kind = 'normal'  # normal, super, banned
         self.PD = pars['initialPD']
         self.PL = pars['initialPL']
         self.ND = 2 + pars['skepticism']
@@ -99,7 +108,7 @@ class Agent(object):
         self.NT = 0
         # back-compatibility:
         self.contribution = 0.0*self.update_skill() # This call also sets self.skill, internally
-        self.traininghistory = {'ID':'tutorial', 'Skill':np.array([self.skill]), 'PL':np.array([self.PL]), 'PD':np.array([self.PD]), 'ItWas':np.array([], dtype=int), 'ActuallyItWas':np.array([], dtype=int)}
+        self.traininghistory = {'ID':np.array([]), 'Skill':np.array([self.skill]), 'PL':np.array([self.PL]), 'PD':np.array([self.PD]), 'ItWas':np.array([], dtype=int), 'ActuallyItWas':np.array([], dtype=int)}
         self.testhistory = {'ID':[], 'I':np.array([]), 'Skill':np.array([]), 'ItWas':np.array([], dtype=int)}
 
         return None
@@ -128,7 +137,7 @@ class Agent(object):
 # Update confusion matrix with latest result:
 #   eg.  collaboration.member[Name].heard(it_was='LENS',actually_it_was='NOT',with_probability=P,ignore=False)
 
-    def heard(self,it_was=None,actually_it_was=None,with_probability=1.0,ignore=False):
+    def heard(self,it_was=None,actually_it_was=None,with_probability=1.0,ignore=False,ID=None,record=True):
 
[…]

### 2015-01-20 analysis/swap/collection.py

@@ -222,6 +222,7 @@ class Collection(object):
         
         return the_departed
         
+
 # ----------------------------------------------------------------------
 # Prepare to plot subjects' trajectories:
 

### 2015-01-20 analysis/swap/subject.py

@@ -85,7 +85,7 @@ class Subject(object):
 
 # ----------------------------------------------------------------------
 
-    def __init__(self,ID,ZooID,category,kind,flavor,truth,thresholds,location):
+    def __init__(self,ID,ZooID,category,kind,flavor,truth,thresholds,location,prior=2e-4):
 
         self.ID = ID
         self.ZooID = ZooID
@@ -127,21 +127,22 @@ class Subject(object):
         mean_logp =sum(np.log(self.probability))/Ntrajectory
         error_logp=sum((np.log(self.probability)-mean_logp)**2/Ntrajectory)
         return 'individual (%s) subject, ID %s, Pr(LENS|d) = %.2f \pm %.2f' % \
-               (self.kind,self.ID,exp(mean_logp),exp(mean_logp)*error_logp)
+               (self.kind,self.ID,np.exp(mean_logp),np.exp(mean_logp)*error_logp)
 
 # ----------------------------------------------------------------------
 # Update probability of LENS, given latest classification:
 #   eg.  sample.member[ID].was_described(by=agent,as_being='LENS',at_time=t)
 
-    def was_described(self,by=None,as_being=None,at_time=None,while_ignoring=0,haste=False,at_x=[-1],at_y=[-1]):
+    def was_described(self,by=None,as_being=None,at_time=None,while_ignoring=0,haste=False,at_x=[-1],at_y=[-1],online=True,record=True):
 
         # Rename some variables:
         a_few_at_the_start = while_ignoring
 
-        # Update agent:
-        by.N += 1
+        if online:
+            # Update agent:
+            by.N += 1
 
-        if by==None or as_being==None:
+        if by==None or as_being==None or by.kind == 'banned':
             pass
 
         # Optional: skip straight past inactive subjects.
@@ -165,6 +166,16 @@ class Subject(object):
 
         else:
 
+            # update the annotation history
+            if online:
+                as_being_dict = {'LENS': 1, 'NOT': 0}
+                self.annotationhistory['Name'] = np.append(self.annotationhistory['Name'], by.name)
+                self.annotationhistory['ItWas'] = np.append(self.annotationhistory['ItWas'], as_being_dict[as_being])
+                self.annotationhistory['At_X'].append(at_x)
+                self.annotationhistory['At_Y'].append(at_y)
+                self.annotationhistory['PL'] = np.append(self.annotationhistory['PL'], by.PL)
+                self.annotationhistory['PD'] = np.append(self.annotationhistory['PD'], by.PD)
+
[…]

### 2015-01-20 doc/sw-system.tex
Questions copied and commented to conclusions

--- 2014-12-11 doc/sw-system.tex
@@
 
-In \Fref{fig:training-gallery} we show 8 example training images from the
+In \Fref{fig:training-gallery} we show 12 example training images from the
 first \sw project (\Sref{sec:data} below).
+
+\todo{Phil, Aprajita}{Make gallery of 6 stage 2 sims and 6 stage 2 duds, to
+give the reader a feel for what the sims look like, and also how the images
+were presented, stretch and scale-wise.}
 
@@
 \begin{minipage}[b]{0.24\linewidth}
+\centering\epsfig{file=sw-system-figs/gallery/0.png,width=\linewidth,angle=0,clip=}
+\end{minipage} \hfill
+\begin{minipage}[b]{0.24\linewidth}
+\centering\epsfig{file=sw-system-figs/gallery/1.png,width=\linewidth,angle=0,clip=}
+\end{minipage} \hfill
+\begin{minipage}[b]{0.24\linewidth}
+\centering\epsfig{file=sw-system-figs/gallery/2.png,width=\linewidth,angle=0,clip=}
+\end{minipage} \hfill
+\begin{minipage}[b]{0.24\linewidth}
+\centering\epsfig{file=sw-system-figs/gallery/3.png,width=\linewidth,angle=0,clip=}
+\end{minipage} \hfill
+  \caption{Typical \SW duds. Insets indicate regions where volunteers typically
+  clicked.}
+  \label{fig:training-gallery:duds}
+\end{figure*}
+
+\begin{figure*}%[!ht]
+\begin{minipage}[b]{0.24\linewidth}
 \centering\epsfig{file=sw-system-figs/gallery/4.png,width=\linewidth,angle=0,clip=}
@@
 \end{minipage} \hfill
-\caption{Typical \SW ``sims.'' Insets indicate the location of the simulated 
-lens in each of these training
-images. Users needed to click on these specific features in order to make a
-correct classification.} \label{fig:training-gallery:sims}
-\end{figure*}
-
-\begin{figure*}%[!ht]
-\begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=sw-system-figs/gallery/0.png,width=\linewidth,angle=0,clip=}
-\end{minipage} \hfill
-\begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=sw-system-figs/gallery/1.png,width=\linewidth,angle=0,clip=}
-\end{minipage} \hfill
-\begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=sw-system-figs/gallery/2.png,width=\linewidth,angle=0,clip=}
-\end{minipage} \hfill
-\begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=sw-system-figs/gallery/3.png,width=\linewidth,angle=0,clip=}
-\end{minipage} \hfill
-\caption{Typical \SW ``duds.''  All of these subjects were correctly
-classified by the community as not likely to contain gravitational lenses; 
-the insets merely indicate regions where $\sim10\%$ of the volunteers 
-clicked.} \label{fig:training-gallery:duds}
+  \caption{Typical \SW sims. Insets indicate the location of the lens in the
+  image. Users needed to click on these specific features in order to make a
+correct classification.}
+  \label{fig:training-gallery:sims}
 \end{figure*}

### 2015-01-28 doc/sw-system.tex
Simplified timing analysis section draft to focus on rate plot, as in #95

--- 2014-12-22 doc/sw-system.tex
@@
 
+\subsection{Classification Speed}
+\label{sec:results:speed}
+
+% How fast does the \sw crowd classify subjects? Each agent records the
+% timestamp of each classification its volunteer makes; by measuring the time
+% lags between successive classifications we can make estimates of each
+% volunteer's speed, and that of the crowd.
+% 
+% A histogram of all time lags for all volunteers is shown in
+% \Fref{fig:crowd:timelags}, with those of the ``experienced volunteers''
+% (those who classified 10 or more training subjects.) overlaid. 
+% 
+% \todo{PJM}{Make this histogram, and try and infer the typical inter-session
+% lag.}
+% 
+% Defining a new classification session to have started at least X minutes since
+% the previous classification, we assign all classifications into sessions, and
+% compute the mean intra-session time lag recorded by each agent. This gives
+% some measure of classification speed within a session; we also compute the 
+% mean session length, and the rate of information contribution. The
+% latter is the most relevant measure of speed for future project design. The
+% distributions of these speeds are shown in \Fref{fig:crowd:speeddists}, in a corner
+% plot that also shows the effort and skill from \Fref{fig:crowd:cornerplot}. We
+% see that ...
+
+The overall contribution rate for the \sw crowd was found,
+and is plotted as a function of time in \Fref{fig:crowd:speed}. We see that
+...
+
+\todo{Phil, Chris}{Compute classification speeds, make plots, discuss. \#95}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
 \subsection{Sample Properties}
@@
 
+% Questions we set ourselves in the introduction:
+% \begin{itemize}
+% \item How reliably can we find gravitational lenses using the \sw
+% system? What is the completeness of the sample produced likely to be?
+% \item How noisy is the system? What is the purity of the sample
+% produced?
+% \item How quickly can lenses be detected, and non-lenses be rejected?
+% How many classifications, and so how many volunteers are needed per target?
+% \item What can we learn about the scalability of the crowd-sourcing approach?
+% \end{itemize}
+
 Crowd-sourced gravitational lens detection works, in terms of the
@@
 
-\item Integrated humanpower = X (stage 1) and y (stage 2), cf hours taken by
+\item Integrated humanpower = X (stage 1) and Y (stage 2), cf hours taken by
 small team of experts

### 2015-02-09 doc/sw-extended.tex
updates to agent and subject and sw-extended.tex

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% TODO:
+% Kamal Nigam, Andrew McCallum and Tom Mitchell. Semi-supervised Text Classification Using EM. In Chapelle, O., Zien, A., and Scholkopf, B. (Eds.) Semi-Supervised Learning. MIT Press: Boston. 2006.
+% according to
+% http://www.mblondel.org/journal/2010/06/21/semi-supervised-naive-bayes-in-python/#more-126
+% this paper would be an example of the sort of thinking I had with the EM
+% algorithm (not quite what was implimented in stage 2 at phil's request),
+% where the E step just does the unlabeled, and the M step uses both labeled
+% and unlabeled data
 
@@
 \label{sec:formalism:em:estep}
-The E-Step is just taking the expected complete log-likelihood, or the
-expectation value over $P(\cdot \ | x, \phi)$. This is equivalent to replacing
-$z_j$ with $p_j$:
+% TODO: reword. The maximization here is over the zj's, so word to make that clear.
+% The E-Step is just taking the expected complete log-likelihood, or the
+% expectation value over $P(\cdot \ | x, \phi)$.
+The E-Step is maximizing the complete log-likelihood with respect to the image
+probability $p_j$.  This is equivalent to replacing $z_j$ with $p_j$:
+% TODO: replace this with equivalent like eq1
 \begin{align}
@@
 the current estimate.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\section{Validation of Training}
+\label{sec:validation}
+
+A validation dataset is needed to prevent overfitting training data and to try
+to test how the training data does against real lenses. These need to come in
+two categories: actual lens environments, and simulated lenses. The need for
+two sets arises because of the paucity of actual lenses. In \SW, most training
+objects are explicitly given to a user -- if a user incorrectly identifies a
+training object, they are informed of that failure, and likewise for a correct
+classification.
+
+Problems:
+0. By telling users about failures in the sim/dud, we explicitly break the
+notion that users come in fully-formed. But we also need to give users
+incentives to keep working, by rewarding them for good behavior. Replace by
+current crowd assessments and telling them how they did compared with the
+crowd?
+1. \SW does not have any 'silent' training images which could function as
+validation datasets, since you have broken the training by telling users.
+2. How to manage the difference between 'dud known lens fields' and 'dud sim
+fields'? Just put them together?
+3. If you tell users about the correct sim classification, do you also tell
+them about a correct lens classification, and do you tell them it was a real
+lens?
+4. Can I just use the dud fields?
 

### 2015-02-09 analysis/swap/agent.py

@@ -108,8 +108,16 @@ class Agent(object):
         self.NT = 0
         # back-compatibility:
         self.contribution = 0.0*self.update_skill() # This call also sets self.skill, internally
-        self.traininghistory = {'ID':np.array([]), 'Skill':np.array([self.skill]), 'PL':np.array([self.PL]), 'PD':np.array([self.PD]), 'ItWas':np.array([], dtype=int), 'ActuallyItWas':np.array([], dtype=int)}
-        self.testhistory = {'ID':[], 'I':np.array([]), 'Skill':np.array([]), 'ItWas':np.array([], dtype=int)}
+        self.traininghistory = {'ID':np.array([]),
+                                'Skill':np.array([self.skill]),
+                                'PL':np.array([self.PL]),
+                                'PD':np.array([self.PD]),
+                                'ItWas':np.array([], dtype=int),
+                                'ActuallyItWas':np.array([], dtype=int)}
+        self.testhistory = {'ID':[],
+                            'I':np.array([]),
+                            'Skill':np.array([]),
+                            'ItWas':np.array([], dtype=int)}
 
         return None
 

### 2015-02-09 analysis/swap/subject.py

@@ -183,9 +183,9 @@ class Subject(object):
         # Deal with active subjects. Ignore the classifier until they
         # have seen NT > a_few_at_the_start (ie they've had a
         # certain amount of training - at least one training image, for example):
-            
+
             if by.NT > a_few_at_the_start:
-               
+
                 # Calculate likelihood for all Ntrajectory trajectories, generating as many binomial deviates
                 if realize_confusion:
 
@@ -223,7 +223,7 @@ class Subject(object):
 
                     self.update_state(at_time)
 
-                    # Update agent - training history is taken care of in agent.heard(), 
+                    # Update agent - training history is taken care of in agent.heard(),
                     # which also keeps agent.skill up to date.
                     if self.kind == 'test' and record:
 
@@ -366,9 +366,9 @@ class Subject(object):
             # Fainter symbol:
             plt.scatter(mdn_trajectory[-1], NN, edgecolors=colour, facecolors=facecolour, alpha=0.5);
             plt.plot([mdn_trajectory[-1]-sigma_trajectory_m[-1],mdn_trajectory[-1]+sigma_trajectory_p[-1]],[NN,NN],color=colour,alpha=0.3);
-        
-        
-        
+
+
+
         # if self.kind == 'sim': print self.trajectory[-1], N[-1]
 
         return

### 2015-02-09 analysis/SWAP.py
moved offline to attic, added an at_time parameter to the various histories

@@ -319,21 +319,21 @@ def SWAP(argv):
         if supervised_and_unsupervised:
             # use both training and test images
             if agents_willing_to_learn * ((category == 'test') + (category == 'training')):
-                bureau.member[Name].heard(it_was=X,actually_it_was=Y,with_probability=P,ignore=False,ID=ID)
+                bureau.member[Name].heard(it_was=X,actually_it_was=Y,with_probability=P,ignore=False,ID=ID,at_time=tstring)
             elif ((category == 'test') + (category == 'training')):
-                bureau.member[Name].heard(it_was=X,actually_it_was=Y,with_probability=P,ignore=True,ID=ID)
+                bureau.member[Name].heard(it_was=X,actually_it_was=Y,with_probability=P,ignore=True,ID=ID,at_time=tstring)
         elif supervised:
             # Only use training images!
             if category == 'training' and agents_willing_to_learn:
-                bureau.member[Name].heard(it_was=X,actually_it_was=Y,with_probability=P,ignore=False,ID=ID)
+                bureau.member[Name].heard(it_was=X,actually_it_was=Y,with_probability=P,ignore=False,ID=ID,at_time=tstring)
             elif category == 'training':
-                bureau.member[Name].heard(it_was=X,actually_it_was=Y,with_probability=P,ignore=True,ID=ID)
+                bureau.member[Name].heard(it_was=X,actually_it_was=Y,with_probability=P,ignore=True,ID=ID,at_time=tstring)
         else:
             # Unsupervised: ignore all the training images...
             if category == 'test' and agents_willing_to_learn:
-                bureau.member[Name].heard(it_was=X,actually_it_was=Y,with_probability=P,ignore=False,ID=ID)
+                bureau.member[Name].heard(it_was=X,actually_it_was=Y,with_probability=P,ignore=False,ID=ID,at_time=tstring)
             elif category == 'test':
-                bureau.member[Name].heard(it_was=X,actually_it_was=Y,with_probability=P,ignore=True,ID=ID)
+                bureau.member[Name].heard(it_was=X,actually_it_was=Y,with_probability=P,ignore=True,ID=ID,at_time=tstring)
 
 
         # Brag about it:

### 2015-02-09 analysis/swap/agent.py

@@ -1,8 +1,3 @@
-"""
-TODO:
-    Save the list of clicks!
-"""
-
 # ======================================================================
 
 import swap
@@ -113,11 +108,13 @@ class Agent(object):
                                 'PL':np.array([self.PL]),
                                 'PD':np.array([self.PD]),
                                 'ItWas':np.array([], dtype=int),
-                                'ActuallyItWas':np.array([], dtype=int)}
+                                'ActuallyItWas':np.array([], dtype=int),
+                                'At_Time': np.array([])}
         self.testhistory = {'ID':[],
                             'I':np.array([]),
                             'Skill':np.array([]),
-                            'ItWas':np.array([], dtype=int)}
+                            'ItWas':np.array([], dtype=int),
+                            'At_Time': np.array([])}
 
         return None
 
@@ -145,7 +142,7 @@ class Agent(object):
 # Update confusion matrix with latest result:
 #   eg.  collaboration.member[Name].heard(it_was='LENS',actually_it_was='NOT',with_probability=P,ignore=False)
 
-    def heard(self,it_was=None,actually_it_was=None,with_probability=1.0,ignore=False,ID=None,record=True):
+    def heard(self,it_was=None,actually_it_was=None,with_probability=1.0,ignore=False,ID=None,record=True,at_time=None):
 
         if it_was==None or actually_it_was==None:
             pass
@@ -221,6 +218,7 @@ class Agent(object):
 
                 self.traininghistory['ItWas'] = np.append(self.traininghistory['ItWas'], actually_it_was_dictionary[it_was])
                 self.traininghistory['ActuallyItWas'] = np.append(self.traininghistory['ActuallyItWas'], actually_it_was_dictionary[actually_it_was])
+                self.traininghistory['At_Time'] = np.append(self.traininghistory['At_Time'], at_time)
 
         return
 

### 2015-02-09 analysis/swap/subject.py

@@ -116,7 +116,8 @@ class Subject(object):
                             'PL': np.array([]),
                             'PD': np.array([]),
                             'At_X': [],
-                            'At_Y': []}
+                            'At_Y': [],
+                            'At_Time': []}
 
         return None
 
@@ -179,6 +180,7 @@ class Subject(object):
                 self.annotationhistory['At_Y'].append(at_y)
                 self.annotationhistory['PL'] = np.append(self.annotationhistory['PL'], by.PL)
                 self.annotationhistory['PD'] = np.append(self.annotationhistory['PD'], by.PD)
+                self.annotationhistory['At_Time'].append(at_time)
 
         # Deal with active subjects. Ignore the classifier until they
         # have seen NT > a_few_at_the_start (ie they've had a
@@ -231,6 +233,7 @@ class Subject(object):
                          by.testhistory['I'] = np.append(by.testhistory['I'], swap.informationGain(self.mean_probability, by.PL, by.PD, as_being))
                          by.testhistory['Skill'] = np.append(by.testhistory['Skill'], by.skill)
                          by.testhistory['ItWas'] = np.append(by.testhistory['ItWas'], as_being_number)
+                         by.testhistory['At_Time'] = np.append(by.testhistory['At_Time'], at_time)
                          by.contribution += by.skill
 
                 else:

### 2015-02-24 doc/sw-cfhtls.tex

@@
 Since the inception of the first citizen science project, Galaxy Zoo, to
-classify galaxy morphologies \citep{LintottEtal2008}, several astronomy
+classify galaxy morphologies \citep{Lintott2008}, several astronomy
 and non-astronomy projects have been launched by the Zooniverse leading
 to many interesting project. For example, PlanetHunters
-has discovered XXX transiting exoplanets \citep{SchwambEtal2012},
+has discovered XXX transiting exoplanets \citep{Schwamb2012},
 Supernova XXX add ref and XXX add ref
@@
 
+\subsection{Image Presentation in \sw}
+\label{sec:data:impres}
+%{\it Preparation of data: divide survey into overlapping tiles.
+Presentation of images.
+Uniform scales, to build intuition and avoid rescales due to bright objects.
+Arcsinh stretch, to bring out low SB features.
+Approximately optimized, how?
+Examples of images.}
+
+Our aim is to do a blind lens search over the entire \cfhtls
+\textsc{wide}. We use the $g$, $r$ and $i$-band color imaging which are
+most useful for visual identification of lenses (and provide access to
+the $u$ and $z$ band imaging through dashboard with additional tools
+XXX).
+
+We make color composite images using publically-available
+code\footnote{The open source  color image composition code used in this
+work is available from \texttt{http://github.com/drphilmarshall/HumVI}}
+following the prescription of \citet{Lupton2004}. Specifically, we first
+rescale the pixel values of each channel image into flux units, and
+then apply an arcsinh stretch. The stretch parameters are chosen
+using a small random sample of images, to ensure that the background
+noise is just visible, and that the centres of bright, intermediate
+resdhift galaxies are not saturated. The color scales are chosen to
+maximize the contrast between faint extended objects. These parameters
+are then fixed during the production of all the tiles, in order to
+allow straightforward comparison between one image and another, and for
+intuition to be built up about the appearance of stars and galaxies
+across the survey.
+
+We extract contiguous cutouts of size 81.84\arcsec\ (440 pixels) with an
+overlapping region of 10\arcsec (54 pixels) between the neighbouring
+cutouts resulting into $\sim$ 430 000 cutouts for the entire \cfhtls
+\textsc{wide}. The size of the individual cutout is determined by
+optimising factors such as the typical angular scales of gravitational
+lenses, the number of objects seen in a single cutout and the total
+number of image cutouts in the survey. It is possible that a lens
+candidate happens to be too close to the edge of a cutout, the overlap
+between neighbouring cutout allows the inspector to get a clearer view
+of the same candidate in at least one of the cutouts. We note that since
+the images are shown randomly, an inspector may not necessarily come
+across the neighbouring cutout unless the inspector classifies a large
+number of images. This is not a problem since our user base is extremely
+large and we receive multiple classifications of the same cutout.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Existing \cfhtls lens samples}
@@
 
-At galaxy-scales, we focus on two primary lens searches. The RingFinder
+At galaxy-scales, we focus on two primary lens searches. The \rf
 \citep{Gavazzi2014} was used for finding compact rings or arcs around centers
@@
 sample, \citet{Gavazzi2014} reported a further 71 serendipitously detected
-lens candidates.  From this sample of ``RingFinder candidates,'' the SL2S team
+lens candidates.  From this sample of ``\rf candidates,'' the SL2S team
 found, during their follow-up campaign, 39 confirmed lenses (and 17 promising
-candidates). We use this sample of 39 ``confirmed RingFinder lenses'' in our
+candidates). We use this sample of 39 ``confirmed \rf lenses'' in our
 completeness analysis.
@@
 
-On the other hand, the {\sc arcfinder} \citet{More2012} was used for
+On the other hand, the \af \citet{More2012} was used for
 finding blue arc-like features in the complete \cfhtls data withouth any
@@
 
-XXX refer Paper I ?
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Image Presentation}
-\label{sec:data:impres}
-{\it Preparation of data: divide survey into overlapping tiles.
-
-Presentation of images. Uniform scales, to build intuition and avoid rescales
-due to bright objects. Arcsinh stretch, to bring out low SB features. 
-Approximately optimized, how? Examples of images.}
-
-We carry out a blind search over the \cfhtls fields where we, mainly, use
-the g-r-i color information to look for signs of lensing. We extract
-contiguous cutouts of size 81.84\arcsec\ (440 pixels). The neighbouring
-cutouts have an overlapping region of 10\arcsec (54 pixels). If a
-possible lens candidate is too close to the edge of a cutout, this
-overlap allows the inspector to get a clearer view of the same candidate
-in a neighbouring cutout. We note that since the images are shown
-randomly, a given inspector may not necessarily come across the
-neighbouring cutout unless the inspector classifies a lot of images.
-However, this is not a problem since we our user base is extremely large
-and we get multiple classifications of the same image.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We use the $L-\sigma$ relation from
-\citep{Parker2007} to get the velocity dispersion as given in Eq.~\ref{magstar2}.
+\citep{Parker2005} to get the velocity dispersion as given in Eq.~\ref{magstar2}.
 
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[scale=1.2]{sw-cfhtls-figs/distrib_remu.pdf}
+\caption{ \label{fig:remudist}
+Einstein radius distribution for all types of lenses. The dashed-dotted (blue)
+curves show the theoretical prediction assuming an SIS model at galaxy-scales
+and a total (NFW+Hernquist) model at groups-scales taken from \citep{More2012}.
+}
+\end{center}
+\end{figure}
+
+\begin{table}
+\begin{center}
+\caption{ \label{tab:thresh} 
+Thresholds used in the selection of the simulated lenses. }
+\begin{tabular}{l l l l l}
+\hline
+Name  &  \multicolumn{2}{c} {gal}  & \multicolumn{2}{c}{qso} \\ 
+      & min  &  max  & min & max \\
+\hline
+\hline
+Source Redshift  & 1.0 & 4.0  & 1.0  & 5.9 \\
+Source Magnitude & 21.0 & 25.5 & 21.0 & 25.5 \\
+
+boost factor & 100 (40$\dagger$)  &  & 1200 & \\
+
+Second brightest image & 23  & & 23 & \\
+Total magnification & 19 & & 20 & \\
+
+Lens shear strength &  0.001 & 0.02 &  0.001 & 0.02 \\
+Lens shear pa &  0 & 180 & 0 & 180  \\
+Source ellipticity & 0.1 & 0.6 & & \\
+Source PA & 0 & 180 & & \\
+\hline
+\end{tabular}
+{ $\dagger$} -- corresponds to the factor used for Groups scale lenses. 
+\end{center}
+\end{table}
 \subsubsection{Groups-scale lenses}
@@
 and within an aperture of $250$~Kpc.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=1.3]{sw-cfhtls-figs/lensprop.pdf}
+\caption{ \label{fig:lensprop}
+Distributions of properties of the lensing galaxies of the simulated
+sample compared to the known lens sample SARCS XXXX check? 
+}
+\end{center}
+\end{figure*}
 
@@
 
-\begin{table}
-\begin{center}
-\caption{ \label{tab:thresh} 
-Thresholds used in the selection of the simulated lenses. }
-\begin{tabular}{l l l l l}
-\hline
-Name  &  \multicolumn{2}{c} {gal}  & \multicolumn{2}{c}{qso} \\ 
-      & min  &  max  & min & max \\
-\hline
-\hline
-Source Redshift  & 1.0 & 4.0  & 1.0  & 5.9 \\
-Source Magnitude & 21.0 & 25.5 & 21.0 & 25.5 \\
-
-boost factor & 100 (40$\dagger$)  &  & 1200 & \\
-
-Second brightest image & 23  & & 23 & \\
-Total magnification & 19 & & 20 & \\
-
-Lens shear strength &  0.001 & 0.02 &  0.001 & 0.02 \\
-Lens shear pa &  0 & 180 & 0 & 180  \\
-Source ellipticity & 0.1 & 0.6 & & \\
-Source PA & 0 & 180 & & \\
-\hline
-\end{tabular}
-{ $\dagger$} -- corresponds to the factor used for Groups scale lenses. 
-\end{center}
-\end{table}
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=1.2]{sw-cfhtls-figs/distrib_remu.pdf}
-\caption{ \label{fig:remudist}
-Einstein radius distribution for all types of lenses. The dashed-dotted (blue)
-curves show the theoretical prediction assuming an SIS model at galaxy-scales
-and a total (NFW+Hernquist) model at groups-scales taken from \citep{More2012}.
-}
-\end{center}
-\end{figure}
-
 In this section, we describe some of the properties of our simulated sample for
@@
 %zdiffq=0.1;
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=1.3]{sw-cfhtls-figs/lensprop.pdf}
-\caption{ \label{fig:lensprop}
-Distributions of properties of the lensing galaxies of the simulated
-sample compared to the known lens sample SARCS XXXX check? 
-}
-\end{center}
-\end{figure*}
 
@@
 We selected a sample of 450 duds for the Stage I classification in \sw
-(see XXX) and a sample of XXX false positives for the Stage II
-inspection (see XXX). The sample of false positives was selected from
+and a sample of 500 false positives for the Stage II
+inspection. The sample of false positives was selected from
 the candidates which passed the Stage I of \sw. We note that this is the
@@
 science team. Such a sample is tremendously helpful for training and
-understanding performances of various lens finding algorithms (refer
-james, sherry's paper ? XXX)
-{\bf TBA data products; make the FP sample available}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
-\label{sec:results}
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{\sw Lens Sample}
-Here, we describe
-
-\subsubsection{Selection of \sw lens candidates}
-\label{sec:results:stage1}
-The images inspected at stage II are assigned P values through the SWAP
-built in the \sw system. Ideally, we would like to have all real lens
-candidates to be assigned high P values. It is not known a priori what
-value of P would give an optimal trade off between high completeness
-and high purity.
-
-Also, since this is the first lens search with \sw, we
-would like to understand how the P correspond to the grades, typically,
-assigned by lens experts.
+understanding performances of various lens finding algorithms
+\citep{Chan2014}. {\bf TBA data products; make the duds and FP sample available}
 
@@
 \begin{center}
-\includegraphics[scale=1.2]{sw-cfhtls-figs/poffl_expr_ncl.pdf}
+\includegraphics[scale=1.0]{sw-cfhtls-figs/poffl_expr_ncl.pdf}
 \caption{ \label{fig:exp_pn} Comparison of the P(lens) with the expert
@@
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Results}
+\label{sec:results}
+
+\subsection{\sw Lens Sample}
+
+The \sw works as a single unified neural network which uses the method
+of visual inspection to find gravitational lenses. The citizens are
+shown images at two stages. At stage I, citizens focus on rapid
+inspection and selection of lens candiates ranging from possible lenses
+to almost certain lenses. At stage II, citizens carefully inspect the
+candidates from stage I and select promising lens candidates only. The
+science team consisting of lens experts then categorize and grade the
+lens candidates further purifying the sample of lens candidates. In
+Table~\ref{tab:stats}, we list the total number of detections of the
+known lens candidates, known confirmed lenses and the new lens
+candidates at both stages I and II. The known sample corresponds to the
+combined Ring Finder and Arc Finder samples. We also show their
+fractions with respect to the total number of lens candidates found at
+these stages. We note that all the confirmed lenses found at stage I are
+also recovered at stage II whereas a small fraction of the known lens
+candidates are rejected at stage II. Also, the new lens candidates
+increases the known lens candidates sample by over 50\%.
+
+Below, we describe the steps taken after stage II for selecting the
+final sample of lens candidates.
 
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
-
-\subsubsection{New lens candidates from \sw}
-\label{sec:results:disc}
-
-{\bf \textcolor{red} {
-CHECK FOR STAGE 1 -- COMPLETENESS OF SIMS AND KNOWN LENSES
-and P value comparison, what about the duplicate lenses near the borders
-- stats on those?}}
-
-{\it Describe the newly found lenses and explain for a few
-cases why they were missed }
+\subsubsection{Selection of the \sw lens candidates}
+\label{sec:results:stage1}
+The images inspected in \sw are assigned probabilities (P) through the
+\sw Analysis Pipeline (SWAP), built in the \sw system (see Paper I).
+In an ideal situation, at the end of stage II, all images containing
+lenses would have high P values and those without lenses will have low P
+values. However, practically, a fraction of the real lenses will be
+assigned low P value decreasing the completeness and a fraction of non-lenses
+will be assigned high P value decreasing the purity. Our goal is to find
+a P value which will result in acceptable levels of completeness and
+purity of the final sample of lens candidates.
+
+As this is the first \sw lens search, we explore a large range in the P
+value to understand the balance between the real lens candidates and
+false positives. In \Fref{fig:exp_pn}, we plot the distribution of
+false positives and real lens candidates categorized by the lens experts
+as a function of their P value. As expected, the fraction of real lens
+candidates is higher for higher P values and it decreases for lower P
+values. We note that from P$\sim$0.7 onwards to lower P values, the fraction of
+false positives starts to exceed the fraction of real lens candidates.
+This could be a good threshold to choose to maximize the purity of the final
+sample. However, we choose P$>$0.3 as our threshold to increase the
+completeness of our sample. We achieve further purity by including the
+grades of the lens experts.
 
@@
 Statistics of detections in \sw }
-\begin{tabular}{l l l l l l}
+\begin{tabular}{l l l l l l l}
 \hline
-   &  \multicolumn{2}{c} {Stage I}  & \multicolumn{3}{c}{Stage II} \\ 
-      & KnCa  &  KnCo  & KnCa & KnCo & NeCa \\
+   &  \multicolumn{2}{c} {Stage I}  & \multicolumn{4}{c}{Stage II} \\ 
+      & KC  &  KL  & KC & KL & NC & AC\\
 \hline
 \hline
-Number  & 128 & 34 & 107  & 34  & 61 \\
-\%  & 29 & 58 & 25 & 58  & XX \\
-P(lens) & 0.95 & 0.95 & 0.3 & 0.3 & 0.3 \\
+Number  & 128 & 34 & 107  & 34  & 61 & 168\\
+\%  & 29 & 58 & 25 & 58  & 12 & 34\\
+P$_{\rm thresh}$ & 0.95 & 0.95 & 0.3 & 0.3 & 0.3 & 0.3\\
 
@@
 \end{center}
-{KnCa}-- Known lens candidates \\
-{KnCo}-- Known confirmed lenses \\
-{NeCa}-- New lens candidates  \\
+{KC}-- Known lens candidates \\
+{KL}-- Known confirmed lenses \\
+{NC}-- New lens candidates  \\
+{AC}-- All (known and new) lens candidates  \\
+P$_{\rm thresh}$ -- systems with P above this threshold are selected \\
+Note about \%: For KC and KL, fractions are with respect to the known
+population whereas for NC and AC, fractions are with respect to the
+total population of lens candidates. \\
 \end{table}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsubsection{New lens candidates from \sw}
+\label{sec:results:disc}
+
+All images with P$>$0.3, at the end of stage II, are inspected by three
+lens experts (AM, AV, PJM) and are assigned integral grades from 0,1,2
+or 3 which imply that the candidate is almost certainly not a lens,
+possibly a lens, probably a lens and almost certainly a lens,
+respectively. This process led to a final sample of 61 new lens
+candidates with averaged grade $\ge$1.3 (see Table~\ref{tab:swcands})
+and are shown in \Fref{fig:lc}. For this final sample, we give a \sw ID
+and Name of the lens system, Ra, Dec, photometric redshift ($z_{phot}$),
+$i$ band magnitude of the lensing galaxy, averaged grade from the lens
+experts, zoo ID (identifier used in
+TALK\footnote{http://talk.spacewarps.org/}, the discussion forum for
+\sw), P value at stage II and a visual categorization of type of lensed
+images and the lensing galaxy in the Comments column in
+Table~\ref{tab:swcands}. Whenever available the lens properties are
+taken from the \cfhtls photometric catalog \citep{Coupon2009} otherwise
+the reported lens galaxy positions are measured visually. The visual
+categorization of the lens type is only suggestive and the explanation
+of the notations in the Comments column is given at the bottom of the
+table.
+
+As the first lens search was a blind search with no preselection of
+candidates using any algorithm, we expected to find various types of
+lenses and this is indeed what we find. The final sample consists of
+both galaxy and groups-scale lens candidates. There are detections of
+elongated arcs and point-like quasar lensed images. Most of them are
+brighter in bluer $g$ band but some candidates brighter in the redder
+$i$ band are also found.
+
+{\bf CHECK FOR STAGE 1 -- COMPLETENESS OF SIMS AND KNOWN LENSES
+and P value comparison, what about the duplicate lenses near the borders
+- stats on those?  check the detection plot of arc mag / Reinst and find out why some of
+the bins have unexpected results}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=1.9]{sw-cfhtls-figs/lenscandfin.pdf}
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=1.9]{sw-cfhtls-figs/lenscandfin_1.pdf}
+\caption{ \label{fig:lc}
+Sample of lens candidates with G$>=$1.3.
+}
+\end{center}
+\end{figure*}
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Measurements of lens and arc properties}
+\label{sec:results:meas}
+
+In the subsequent sections, we make comparison of various properties of
+the lens candidates. Here, we describe how we measured those properties,
+namely, the lens redshift, the Einstein radii and the total flux of the
+arcs.
+
+We use the publicly available redshifts for the lens galaxy from the
+\cfhtls photometric catalogs \citep{Coupon2009}. The definition of the
+Einstein radius is different in different cases. For the galaxy-scale
+lenses in the simulated sample, we use the value of the input lens model
+parameter for the $R_{\rm E}$. For groups-scale lenses, since the lens
+model is multi-component, we need to determine the $R_{\rm E}$ from the
+image positions. We use half of the averaged image separations of the
+lensed image counterparts with minimum and maximum image separations.
+For the \rf sample, the arcs are detected in the scaled difference image
+between $g$ and $i$ bands where the lensing galaxy is subtracted
+\citep[for details, see]{Gavazzi2014}. We use the peak position of the
+lensed images measured by running {\sc sextractor} on this difference
+image and identified visually. We calculate the image separation from
+the lens center as an estimate of the $R_{\rm E}$. For the \af (SARCS)
+sample, we use the same definition as above except that the peak
+position is identified either by the \af or visually. For the \sw lens
+sample, the same definition is used where the peak positions are
+identified either with \af or {\sc sextractor}.
+
+The total flux of the arc is measured in the $g$ band. For the simulated
+sample, we multiply the magnification of the second brightest image with
+the source magnitude. For the \rf sample, we use the flux of the lensed
+images measured by {\sc sextractor} from the scaled difference image,
+that is, $g-\alpha i$ and convert it to the $g$ band flux using mean
+colors of the foreground and background population. For the \af and the
+\sw sample, we integrate the flux in the image pixels identified by \af
+or {\sc sextractor}.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Recovery of known \cfhtls lenses with \sw}
+\label{sec:results:known}
+
+We determine what fraction of the known sample of lenses are recovered by \sw. In
+Table~\ref{tab:stats}, we show that $\sim$~25\%-30\% of the known
+candidates and $\sim$~60\% of the known confirmed lenses are found at
+stages I and II in \sw. The left and the middle panels of
+\Fref{fig:compre} show the fraction of detections as a function of arc
+magnitude and the Einstein radius of the lens systems. As expected, we
+find that systems with brighter images and/or with larger Einstein radii
+are detected more often in \sw.
+
+We find that most of the confirmed lenses and candidates that are missed by \sw
+are systems with fainter arcs and smaller Einstein radii and they come
+from the \rf sample. The main reason why \rf found such
+candidates is because their team used lensing
+galaxy-subtracted images to detect the presence of the lensed images
+both during the automated object-finding phase and during the visual
+inspection and classification of their candidates. This approach
+naturally improves the detection efficiency at smaller Einstein radii
+and for fainter systems. The \sw volunteers were not shown any
+galaxy-subtracted images. However, in light of the improved detection
+efficiency, this might be a better strategy to adopt for future lens
+searches at galaxy-scales with \sw. In the Discussion \Sref{sec:fn}, we
+further explore and discuss why the confirmed lenses may have been
+missed in \sw.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=1.0]{sw-cfhtls-figs/comp_reinst_mag.pdf}
+\caption{ \label{fig:compre} Fraction of lens candidates detected by \sw
+as a function of the arc magnitude ($g$ band) and the Einstein radius for
+three lens samples, namely, simulated lenses, known confirmed lenses and
+the lens candidates sample. }
+\end{center}
+\end{figure*}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
+\subsection{Image separation distribution}
+\label{sec:results:isd}
+
+The distribution of image separations (i.e. twice the Einstein radius)
+can be used to probe the average density profile of the lens population
+\citep{Oguri2006,More2012}.  However, the lens sample found
+by the Arc Finder may have incompleteness as a function of the image
+separation. Thus, the lack of understanding of the selection function of
+the lens sample may affect the constraints on the density profile.  A
+blind lens search done by visual inspection alone e.g. by \sw may find
+lenses missed by the Arc Finder search and thereby, improve
+completeness. Furthermore, the completeness of the lens sample found by \sw is
+characterised with the help of the simulated sample. For example, in the
+right most panel of \Fref{fig:compre}, we plot the completeness of the
+simulated sample found at stage I of \sw as a function of the arc
+magnitude and Einstein radius. We find that the sample is more than 80\%
+complete between image separations 2"-10".
+
+In \Fref{fig:isd}, we plot theoretical curves for the image
+separationd distribution corresponding to three density profiles,
+namely, isothermal sphere (IS), NFW \citep{Navarro1997} and Total profile which has
+NFW and Hernquist profiles combined with an adiabatically contracting model for
+dark matter component \citep{Gnedin2004} taken from \citet{More2012}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Discussion}
+\label{sec:discuss}
+
+Finding gravitational lenses is a difficult and complex task. No one
+method is perfect. Each method has some advantages over the other. It
+may be the case that a single method may not be the best means for
+optimising completeness and purity. Visual inspection will likely be
+required for pruning candidates at some stage of lens candidate
+selection even in the future. Therefore, we would like to understand how
+best we should combine the strengths of robots and humans to optimize
+the lens finding method.
+
+In this section, we attempt to understand and compare the lens
+(candidates) that are found by the lens finding robots and missed by humans
+and vice versa.
+
+\subsection{False negatives: known lenses missed by \sw}
+\label{sec:fn}
+Like any lens finding method, the \sw system can fail to detect
+certain kinds of lenses. We explore and discuss why some of the known
+confirmed lenses may have been missed. About 40\% of the known confirmed sample of
+lenses are missed (see \Tref{tab:stats}). And, XXXX
+
+Among the confirmed lenses from the \rf, about 50\% are missed. Out of
+the missed sample of 18 lenses, about half of them are visually
+difficult to detect and the other half seem to show faint blue smudges
+around galaxies which should have been easier to identify.  {\bf Let us
+compare the two samples to see if there are any obvious differences.
+only 2 out of this sample of 18 were detected at stage I (reached high P
+even with fewer classifications) and missed at stage II (P value was low
+even after recieving very many classifications). The rest of the 16
+lenses were rejected right at stage I XXX}
+
+If we consider the \af lenses, only 6 out of the 26 ($\sim$23\%) were
+missed by \sw. One of those 6 lenses was detected at stage I but failed
+to get high enough P value at stage II even after receiving a total of
+50 classifications (set as the upper limit). The rest of the 5 lenses
+are already rejected at stage I. Upon visual inspection of these 5
+systems, they appear to be difficult to identify as lenses because
+either the lensed images are faint, have low curvature, are close to the
+edge and/or are not visible due to proximity to an extremely bright
+galaxy ({\bf show some examples XXX}).
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.65]{sw-cfhtls-figs/zl_mg_re.pdf}
+\caption{ \label{fig:zlre}
+Comparison of the lens redshift and of the arc magnitude with the
+Einstein radius for all of the three lens samples, namely, from the \rf (green dots),
+\sw (all candidates black circles and new candidates only in blue dots)
+and \af (red dots). }
+\end{center}
+\end{figure}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.5]{sw-cfhtls-figs/stacked_lenscand_rein.pdf}
+\includegraphics[scale=0.5]{sw-cfhtls-figs/stacked_lenscand_mag.pdf}
+\caption{ \label{fig:stackre}
+Candidate detections by the \rf, \sw and the \af as a
+function of the Einstein radius and $g$ band magnitude of the lensed
+images. (XXXX check how different are the estimates from the different
+measurement techniques for a given lens candidates.) }
+\end{center}
+\end{figure*}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=1.2]{sw-cfhtls-figs/isd_cfhtls_sw.pdf}
+\caption{ \label{fig:isd} Image separation distribution. Comparing
+theoretical predictions (solid curves) with the \cfhtls known lens
+samples (REF , green points) and the same \cfhtls sample after combining
+with the incremental lens sample from \sw (magenta points). The \sw only
+sample including new and known lens candidates are shown with blue
+points. }
+\end{center}
+\end{figure}
+
+Efficiency of a visual search can vary in different sections of an
+image. Our eyes tend to focus usually at the center of an image and lens
+candidates close to the borders could go undetected. Therefore, it is
+essential to test and understand if \sw tends to miss certain lenses
+because they happen to be close to the borders of the image cutouts.
+
+From the SWAP, the image cutouts inspected by the \sw volunteers receive
+a status of detected (if P$>$P$_{\rm acc_thresh}$), rejected (if
+P$<$P$_{\rm rej_thresh}$) and undecided (if P$_{\rm rej_thresh}$ $<$ P
+$<$ P$_{\rm acc_thresh}$). In \Fref{fig:comppos}, we compare the
+positions of simulated lenses which are detected (red), undecided
+(green) and rejected (blue). We also make the same comparison for the
+known lens candidates in the right panel.  We note that for some cases
+randomly selected subsamples are shown for the ease of visual
+comparison. For example, the absolute number of simulated lenses
+detected is too high compared to the rejected sample. We do not find any
+strong visual correlation in the rate of detections as a function of the
+position for both the simulated and the known lens sample. Thus, the
+completeness of the lens sample does not seem to be significantly
+affected by whether a lens is located close to the border or well within
+the center.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
+\subsection{Why \sw candidates were missed by lens finding robots?}
+
+The new lens candidates discovered by \sw are run through the \rf to
+trace and understand at what stage the algorithm failed to detect them.
+
+At the first step of the \rf algorithm, a galaxy catalog is generated
+based on magnitude, redshift and SED type \citep[see]{Gavazzi2014} to
+select galaxies which are most likely to act as lenses. We find that
+about 40\% of the new \sw candidates fail to meet this initial selection
+criteria e.g. SW1, SW13, SW19, SW22, SW27 and SW30.  All of the lensing
+galaxies are bright enough to satisfy the $i<22$ criterion. However,
+some of them have a bright companion galaxy, some of them do not look
+like E/S0 type galaxies and some are edge on galaxies. {\bf there are a
+few which look regular galaxies so which criteria are they failing??}
+
+%% 13 are under mask so no photoz, 10 have photoz (z>0.2 except for 1).
+
+In the following steps, the flux from the galaxy is subtracted from the
+scaled difference image to enhance the visibility of the faint blue
+lensed features. An object finder is run on this image to quantify the
+lensed image properties. About 50\% of the \sw candidates could not be
+detected by the object finder because properties such as the image area,
+axis ratio, magnitude/color and alignment with respect to the lensing
+galaxy are not satisfied. Some of the candidates missed at this stage
+are e.g. SW4, SW5, SW6, SW26, SW36, SW39 and SW47.
+
+%% 23/61 miss first step, 30/61 miss auto, 5 pass auto but have poor
+%grade from visual classf.
+
+Next, we rerun the \af on the same \sw sample of new candidates. The \af
+is directly run an image to look for elongated arc like objects and does
+not require a list of targets to begin with. Objects are identified by
+placing thresholds on the noise level in the images. Thus, \af
+detections are sensitive to changes in the noise levels. Also, the size
+of the PSF is important to know what dimensions should be expected for
+the arc candidates.
+
+Originally, the \af was run on a large image with an area of $\sim 19400
+\times 19400$ pixels$^2$. For the rerun, we work with much smaller
+images because this is faster but this affects the number and type of
+arc detections. We find that about 30\% of the new candidates are detected
+without changing any of the thresholds in the code because of the change
+in the noise level.
+
+{\bf TBD: 
+comment on any lensed quasars, on any exotic lenses;
+of course, there must be lenses which cannot be detected currently by
+either robots/humans
+check if some candidates were detected because they were hidden
+underneath the sims ie. from the D11;
+}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
+\subsection{Limitations and Caveats of the training sample}
+
+The simulated sample is not perfect because our understanding of various
+phenomena in the Universe is not complete and because of the uncertainties in
+the parameters of our model. Here, we describe some of the cases or
+aspects in which the simulations are known to have failed or seem
+unrealistic.
+
+The parameters required by various scaling relations and the models primarily
+depend on the photometry of the galaxies, groups and quasars detected in the
+survey. For galaxy-scale lenses, the lensing galaxies at higher redshifts or
+which are fainter have poor photometric measurements. This causes relatively
+larger uncertainties in its luminosity and velocity dispersion and leads to
+simulated lenses which look implausible. For example, due to a larger
+uncertainty in the velocity dispersion of the lensing galaxy, the lensed images
+may have larger image separation than what is expected given the visual priors
+from the galaxy.
+
+At group-scales, the photometric and redshift estimates are used when
+defining the group membership. Therefore, errors in redshift estimates generate
+galaxy groups with BGG or member galaxies with dissimilar properties. In some
+cases, low redshift spiral galaxies are incorrectly assigned high redshift.
+Spiral galaxies are typically less massive and low redshift spiral galaxies are
+unlikely to act as gravitational lenses. Hence, the resulting simulated lenses
+are not convincing.
+
+We use single Sersic component to describe the light profiles of background
+galaxies. This is clearly not the most accurate description for galaxies,
+especially, star-forming galaxies which form a significant fraction of the
+lensed galaxy population. Star-forming galaxies have complex structures such as
+star forming knots, spiral arms, bars and disks.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.95]{sw-cfhtls-figs/completeness_pos.pdf}
+\caption{ \label{fig:comppos}
+Completeness as a function of position of lens systems. Simulated lenses
+(left) and real lens candidates (right) are shown. Irrespective of the
+status of the lenses, that is, detected, undecided or rejected, there is
+no strong dependency on where the lenses are located both for the
+simulated and the real sample of lens candidates. }
+\end{center}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Summary and Conclusions}
+\label{sec:conclude}
+In this paper, we describe the framework and procedure used to generate
+simulated lens sample for the blind lens search in the \cfhtls survey in
+collaboration with \sw. The aim of this lens search is to find lenses that have
+been missed by lens finding algorithms. The simulated lens sample is used for
+training the citizen scientists, calibrating their performance and rejecting
+unlikely lenses from the sample based on the classifications of citizen
+scientists. As a result, the simulated lenses need to consist of realistic
+looking lenses.
+
+We use the photometric and redshift catalogues for the foreground galaxies and
+additionally, color catalogues for background galaxies and quasars. We
+use scaling relations to relate light properties to properties such as mass and
+size to generate lens models. We further account for the
+instrumental effects such as seeing and noise before creating the final lensed
+images of model background sources. We add the lensed images on top of the real
+galaxies and groups in the \cfhtls data in all filters.
+
+We draw the following conclusions:
+
+\begin{itemize}
+
+\item Crowd-sourced gravitational lens detection works, as shown in by comparing with real lenses in CFHTLS:
+Real (robotically-detected and expert-confirmed) lenses are
+recovered/missed at similar/comparable/different rates C’\% and P’\% - this is a partial test of supervised vs unsupervised learning
+
+%Which real lenses were missed? False negatives
+
+\item We found a sample of new gravitational lens candidates. An
+expert-graded sample of 74 with 44 promising and 30 low probability
+candiates.
+
+The SW lenses are different from the robotically (\rf and \af) detected lenses, in the following ways.
+XXXXX
+
+\end{itemize}
 
@@
 SW49 & CFHTLS J090219-053923 &  135.5794 &   -5.6566 &  0.0 &  0.0 &  2.0 &  1.3 & ASW0000g95 &  1.0  &  A,R/E   \\ 
-SW50 & CFHTLS J090319-040146 &  135.8311 &   -4.0297 &  0.0 & 19.8 &  1.2 &  1.3 & ASW00007ls &  0.5  &  A,R/E   \\ 
+SW40 & CFHTLS J090319-040146 &  135.8311 &   -4.0297 &  0.0 & 19.8 &  1.2 &  1.3 & ASW00007ls &  0.5  &  A,R/E   \\ 
 SW51 & CFHTLS J090333-005829 &  135.8886 &   -0.9749 &  0.0 &  0.0 &  2.1 &  1.3 & ASW00008a0 &  1.0  &  A/D,E/G   \\ 
@@
 
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=1.9]{sw-cfhtls-figs/lenscandfin.pdf}
-\caption{ \label{fig:lc}
-Sample of lens candidates with G$>=$1.3.
-}
-\end{center}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=1.9]{sw-cfhtls-figs/lenscandfin_1.pdf}
-\caption{ \label{fig:lc1}
-Sample of lens candidates G$>=1.3$.
-}
-\end{center}
-\end{figure*}
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Recovery of known \cfhtls lenses with \sw}
-\label{sec:results:known}
-
-{\it Describe which lenses were recovered and explain any cases missed by
-citizen scientists}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=1.0]{sw-cfhtls-figs/comp_reinst_mag.pdf}
-\caption{ \label{fig:compre} Fraction of lens candidates detected by \sw
-as a function of the Einstein radius and arc $g$ band magnitudes for
-three lens samples, namely, simulated lenses, known confirmed lenses and
-the lens candidates sample. XXXX sims are stage1 and real sample values
-are for stage 2. }
-\end{center}
-\end{figure*}
-
-{\it Rejection rate. Completeness and purity at P > retirement, P > 95\%, and 
-as function of probability P.
-
-Summarize performance at some fiducial threshold: eg P = 95\%.}
-
-\subsection{Image separation distribution}
-\label{sec:results:isd}
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=1.2]{sw-cfhtls-figs/isd_cfhtls_sw.pdf}
-\caption{ \label{fig:isd} Image separation distribution. Comparing
-theoretical predictions with the \cfhtls known lens samples (REF) and
-the same \cfhtls sample after combining with the incremental lens sample
-from \sw }
-\end{center}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}
-\label{sec:discuss}
-
-{\it Differences with robots: what types of lenses are found at \sw?
-
-Selection function. Missing system.
-
-Describe the importance of this kind of study 
-- being able to quantify the completeness of the lens samples
-- state how this will be used in a future \sw paper }
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.65]{sw-cfhtls-figs/zl_mg_re.pdf}
-\caption{ \label{fig:zlre}
-Comparison of Lens redshift and magnitude as a function of Arc radius for all three lens samples,
-namely, from \sw, SARCS and those from the RingFinder. Also,
-corresponding histograms are shown.}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.6]{sw-cfhtls-figs/stacked_lenscand_rein.pdf}
-\includegraphics[scale=0.6]{sw-cfhtls-figs/stacked_lenscand_mag.pdf}
-\caption{ \label{fig:stackre}
-Detections by three methods the Ringfinder, \sw and the Arcfinder as a
-function of the Einstein radius and $g$ band magnitude of the lensed
-images. XXXX check how different are the estimates from the different measurement techniques for a given lens candidates. }
-\end{center}
-\end{figure}
-
-{\bf TBD: 
-add section on offline analysis - extra lenses found etc;  
-expand FP section;  
-mention EGS moustakas and other lens samples; 
-comment on any lensed quasars, on any exotic lenses;
-check if some candidates were detected because they were hidden
-underneath the sims ie. from the D11;
-}
-
-\subsection{Blind Lens Search}
-We looked at the locations of simulated and real lenses from our data
-those were missed by \sw compared to the locations of the lenses that
-got detected. The real lens sample consists of a total of XXXX candidates
-which have $P_l>2.e-5$XXXXX (check this) and received a rank of G$>0$ from the
-expert. We do not find any obvious dependency in the rate of detections
-as a function of the position of a given lens for both simulated and
-real lens sample. Thus, the completeness of the lens sample is not
-affected by whether a lens is located close to the border or well within
-the center (see  Figure~\ref{fig:comppos}).
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=0.95]{sw-cfhtls-figs/completeness_pos.pdf}
-\caption{ \label{fig:comppos}
-Completeness as a function of location of lenses. Simulated lenses (left) and
-real lens candidate (right) are shown. {\bf: TBD - Add a third color for
-P$>$ Pthresh which will be defn of "accepted"} Irrespective of whether the
-lenses are detected or rejected and whether they are simulated or real,
-there is no obvious dependency on where the lenses are located. 
-}
-\end{center}
-\end{figure*}
-
-\subsection{Limitations and Caveats of the training sample}
-The simulated sample has certain limitations due to lack of our understanding of
-various phenonmena in the Universe and due to uncertainties in various
-parameters of our model. Here, we describe some of the cases or aspects in which the
-simulations are known to have failed or seem unrealistic.
-
-The parameters required by various scaling relations and the models primarily
-depend on the photometry of the galaxies, groups and quasars detected in the
-survey. For galaxy-scale lenses, the lensing galaxies at higher redshifts or
-which are fainter have poor photometric measurements. This causes relatively
-larger uncertainties in its luminosity and velocity dispersion and leads to
-simulated lenses which look implausible. For example, due to a larger
-uncertainty in the velocity dispersion of the lensing galaxy, the lensed images
-may have larger image separation than what is expected given the visual priors
-from the galaxy.
-
-At group-scales, the photometric and redshift estimates are used when
-defining the group membership. Therefore, errors in redshift estimates generate
-galaxy groups with BGG or member galaxies with dissimilar properties. In some
-cases, low redshift spiral galaxies are incorrectly assigned high redshift.
-Spiral galaxies are typically less massive and low redshift spiral galaxies are
-unlikely to act as gravitational lenses. Hence, the resulting simulated lenses
-are not convincing.
-
-We use single Sersic component to describe the light profiles of background
-galaxies. This is clearly not the most accurate description for galaxies,
-especially, star-forming galaxies which form a significant fraction of the
-lensed galaxy population. Star-forming galaxies have complex structures such as
-star forming knots, spiral arms, bars and disks.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Summary and Conclusions}
-\label{sec:conclude}
-In this paper, we describe the framework and procedure used to generate
-simulated lens sample for the blind lens search in the \cfhtls survey in
-collaboration with \sw. The aim of this lens search is to find lenses that have
-been missed by lens finding algorithms. The simulated lens sample is used for
-training the citizen scientists, calibrating their performance and rejecting
-unlikely lenses from the sample based on the classifications of citizen
-scientists. As a result, the simulated lenses need to consist of realistic
-looking lenses.
-
-We use the photometric and redshift catalogues for the foreground galaxies and
-additionally, color catalogues for background galaxies and quasars. We
-use scaling relations to relate light properties to properties such as mass and
-size to generate lens models. We further account for the
-instrumental effects such as seeing and noise before creating the final lensed
-images of model background sources. We add the lensed images on top of the real
-galaxies and groups in the \cfhtls data in all filters.
-
-We draw the following conclusions:
-
-\begin{itemize}
-
-\item Crowd-sourced gravitational lens detection works, as shown in by comparing with real lenses in CFHTLS:
-Real (robotically-detected and expert-confirmed) lenses are
-recovered/missed at similar/comparable/different rates C’\% and P’\% - this is a partial test of supervised vs unsupervised learning
-
-%Which real lenses were missed? False negatives
-
-\item We found a sample of new gravitational lens candidates. An
-expert-graded sample of 74 with 44 promising and 30 low probability
-candiates.
-
-The SW lenses are different from the robotically (RingFinder and ArcFinder) detected lenses, in the following ways.
-XXXXX
-
-\end{itemize}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-03-02 doc/sw-cfhtls.tex
rearranged discussion section, added trajectory fig

@@
 
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Limitations of the simulated sample}
+The simulated sample is not perfect because our understanding of various
+phenomena in the Universe is not complete and because of the uncertainties in
+the parameters of our model. Here, we describe some of the cases or
+aspects in which the simulations are known to have failed or seem
+unrealistic.
+
+The parameters required by various scaling relations and the models primarily
+depend on the photometry of the galaxies, groups and quasars detected in the
+survey. For galaxy-scale lenses, the lensing galaxies at higher redshifts or
+which are fainter have poor photometric measurements. This causes relatively
+larger uncertainties in its luminosity and velocity dispersion and leads to
+simulated lenses which look implausible. For example, due to a larger
+uncertainty in the velocity dispersion of the lensing galaxy, the lensed images
+may have larger image separation than what is expected given the visual priors
+from the galaxy.
+
+At group-scales, the photometric and redshift estimates are used when
+defining the group membership. Therefore, errors in redshift estimates generate
+galaxy groups with BGG or member galaxies with dissimilar properties. In some
+cases, low redshift spiral galaxies are incorrectly assigned high redshift.
+Spiral galaxies are typically less massive and low redshift spiral galaxies are
+unlikely to act as gravitational lenses. Hence, the resulting simulated lenses
+are not convincing.
+
+We use single Sersic component to describe the light profiles of background
+galaxies. This is clearly not the most accurate description for galaxies,
+especially, star-forming galaxies which form a significant fraction of the
+lensed galaxy population. Star-forming galaxies have complex structures such as
+star forming knots, spiral arms, bars and disks. 
 %magdiff=5*0.1;
@@
 
+\subsection{Why \sw candidates were missed by lens finding robots?}
+We rerun the \rf and \af on images centered on the new \sw candidates to
+trace and understand at what stage the algorithm failed to detect them.
+
+First, we rerun \rf on the new \sw sample. At the beginning, a galaxy
+catalog is generated based on magnitude, redshift and SED type
+\citep[see]{Gavazzi2014} to select galaxies which are most likely to act
+as lenses. We find that about 40\% of the new \sw candidates fail to
+meet this initial selection criteria e.g. SW1, SW13, SW19, SW22, SW27
+and SW30.  All of the lensing galaxies are bright enough to satisfy the
+$i<22$ criterion. However, some of them have a bright companion galaxy,
+some of them do not look like E/S0 type galaxies and some are edge on
+galaxies. {\bf there are a few which look regular galaxies so which
+criteria are they failing??}
+
+%% 13 are under mask so no photoz, 10 have photoz (z>0.2 except for 1).
+
+In the following steps, the flux from the galaxy is subtracted from the
+scaled difference image to enhance the visibility of the faint blue
+lensed features. An object finder is run on this image to quantify the
+lensed image properties. About 50\% of the \sw candidates could not be
+detected by the object finder because properties such as the image area,
+axis ratio, magnitude/color and alignment with respect to the lensing
+galaxy are not satisfied. Some of the candidates missed at this stage
+are e.g. SW4, SW5, SW6, SW26, SW36, SW39 and SW47.
+
+%% 23/61 miss first step, 30/61 miss auto, 5 pass auto but have poor
+%grade from visual classf.
+
+Next, we rerun the \af on the same \sw sample of new candidates. The \af
+is directly run on images to look for elongated arc like objects and does
+not require a list of targets to begin with. Objects are identified by
+placing thresholds on the noise level in the images. Thus, \af
+detections are sensitive to changes in the noise levels.
+
+Originally, the \af was run on a large image with an area of $\sim 19350
+\times 19350$ pixels$^2$. For the rerun, we work with much smaller
+images because this is faster but this alters the measured
+noise and hence, affects the number and type of arc detections. We find
+that about 30\% of the new candidates are detected without changing any
+of the thresholds in the code because of the change in the noise level.
+{\bf does this make sense?}
+
+The \af code calculates second order brightness moments around every
+pixel to decide if the distribution of flux is elongated in some
+direction in order to detect elongated arc-like objects. An elongation
+estimator is assigned to every pixel. All pixels with a value of the
+estimator above a certain threshold are connected to form the arc
+feature. This is building of the arc candidate. Subsequently, arc
+properties such as the area, mean flux, length and curvature are
+determined. We relax the threshold at the building stage and also relax
+thresholds mainly on the area of the arc which leads to detection of
+about 75\% of the new \sw candidates. We find that relaxing thresholds
+on other arc properties do not improve the detection rate significantly
+and thus are left unchanged.
+
+Typically, the candidates are missed from the \af sample if a) they are
+brighter in the redder band rather than the bluer $g$ band used for arc
+detection because then the arc feature will be at the noise level and
+will fail detection b) the flux of the arc and the galaxy are
+blended in the $g$ band such that the \af mistakenly connects part of the
+galaxy to the pixels belonging to the arc candidate which then results in a
+candidate with no morphological characteristics of an arc or c) if the
+candidate is not elongated which means most of the lensed quasars with
+circular looking lensed images will be missed.
+
+Relaxing the thresholds obviously increases the total number of
+candidate detections which includes a large sample of false positives.
+For example, the number of arc candidate detections increase by a factor
+of $\sim$2 when we relaxed the thresholds in the reruns described above
+whereas the number of false positives increase by a factor of $\sim$5.
+Thus, it is not recommended to relax these thresholds alone. A better
+alternative is to relax the thresholds to increase the completeness and
+cross-correlate the arc candidate positions with a galaxy catalog to
+discard those candidates which are not close to a putative lensing
+galaxy within typical radius in order to reduce the false positives.
+
+%% 19,46 (original and relaxed criteria); 72,338 (smaller image); 1548,7845 (larger image)
+
+{\bf TBD: 
+comment on any lensed quasars, on any exotic lenses;
+of course, there must be lenses which cannot be detected currently by
+either robots/humans
+check if some candidates were detected because they were hidden
+underneath the sims ie. from the D11;
+}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
 \subsection{False negatives: known lenses missed by \sw}
 \label{sec:fn}
-Like any lens finding method, the \sw system can fail to detect
-certain kinds of lenses. We explore and discuss why some of the known
-confirmed lenses may have been missed. About 40\% of the known confirmed sample of
-lenses are missed (see \Tref{tab:stats}). And, XXXX
-
-Among the confirmed lenses from the \rf, about 50\% are missed. Out of
-the missed sample of 18 lenses, about half of them are visually
-difficult to detect and the other half seem to show faint blue smudges
-around galaxies which should have been easier to identify.  {\bf Let us
-compare the two samples to see if there are any obvious differences.
-only 2 out of this sample of 18 were detected at stage I (reached high P
-even with fewer classifications) and missed at stage II (P value was low
-even after recieving very many classifications). The rest of the 16
-lenses were rejected right at stage I XXX}
-
-If we consider the \af lenses, only 6 out of the 26 ($\sim$23\%) were
-missed by \sw. One of those 6 lenses was detected at stage I but failed
-to get high enough P value at stage II even after receiving a total of
-50 classifications (set as the upper limit). The rest of the 5 lenses
-are already rejected at stage I. Upon visual inspection of these 5
-systems, they appear to be difficult to identify as lenses because
-either the lensed images are faint, have low curvature, are close to the
-edge and/or are not visible due to proximity to an extremely bright
-galaxy ({\bf show some examples XXX}).
+Like any lens finding method, the \sw system can fail to detect certain
+kinds of lenses. Here, we explore and discuss why some of the known
+lenses may have been missed.
+
+We find that about 40\% of the known confirmed sample of lenses are
+missed (see \Tref{tab:stats}). While this seems like a fraction, we note
+that many of the missed lenses are from the \rf sample with small
+Einstein radii and faint lensed images (see \Fref{fig:compre}). Among
+the confirmed lenses from the \rf, about 50\% are missed. Out of the
+missed sample of 18 lenses, about half of them are visually difficult to
+detect and the other half appear to have faint blue smudges around
+galaxies which should have been easier to identify. Similarly,
+if we consider the \af lens sample, $\sim$23\% are missed by \sw. This
+is a relatively small sample of $\sim 5$ systems and visual inspection
+suggests that, by and large, either the lensed features are faint
+or they have odd properties which makes them difficult to identify
+correctly.  ({\bf show some
+example images XXX}). For further tests, we combine the \rf and \af sample.
+
+For a lens finding method which uses collective skill, experience and
+knowledge of a group of citizens, it may be difficult to find a single
+factor with certainty which causes a lens candidate to be missed. We
+attempt to understand whether there is indeed a single dominant factor
+that is resulting in the loss of these lenses or the lenses are being
+missed due to a combination of multiple reasons. Below, we consider some
+of the factors that could affect the efficiency of finding lenses.
+
+First, we check if the Nclass is different for the detected and the
+missed sample. Surprisingly, most of the lenses in the known sample have
+few classifications (Nclass<10) which includes both the detected and
+missed lenses. Many of the remaining have between 10 to 20
+classifications. And, only a few subjects have Nclass>20 which continue
+to remain for long in the database because these candidates may have
+been difficult to identify.
+
+%{\bf Let us compare the two samples to see if there are any obvious differences.
+only 2 out of this sample of 18 were detected at stage I (reached high P even with fewer classifications) and missed at stage II (P value was low even after recieving very many classifications).
+The rest of the 16 lenses were rejected right at stage I XXX}
+%One of those 6 lenses was detected at stage I but failed to get high enough P value at stage II even after receiving a total of 50 classifications (set as the upper limit).
+The rest of the 5 lenses are already rejected at stage I.
+Upon visual inspection of these 5 systems, they appear to be difficult to identify as lenses because either the lensed images are faint, have low curvature, are close to the edge and/or are not visible due to proximity to an extremely bright galaxy
 
@@
 
+\subsubsection{Blind lens search}
 Efficiency of a visual search can vary in different sections of an
@@
 From the SWAP, the image cutouts inspected by the \sw volunteers receive
-a status of detected (if P$>$P$_{\rm acc_thresh}$), rejected (if
-P$<$P$_{\rm rej_thresh}$) and undecided (if P$_{\rm rej_thresh}$ $<$ P
-$<$ P$_{\rm acc_thresh}$). In \Fref{fig:comppos}, we compare the
+a status of detected (if P$>$P$_{\rm acc thresh}$), rejected (if
+P$<$P$_{\rm rej thresh}$) and undecided (if P$_{\rm rej thresh}$ $<$ P
+$<$ P$_{\rm acc thresh}$). In \Fref{fig:comppos}, we compare the
 positions of simulated lenses which are detected (red), undecided
@@
 
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
-\subsection{Why \sw candidates were missed by lens finding robots?}
-
-The new lens candidates discovered by \sw are run through the \rf to
-trace and understand at what stage the algorithm failed to detect them.
-
-At the first step of the \rf algorithm, a galaxy catalog is generated
-based on magnitude, redshift and SED type \citep[see]{Gavazzi2014} to
-select galaxies which are most likely to act as lenses. We find that
-about 40\% of the new \sw candidates fail to meet this initial selection
-criteria e.g. SW1, SW13, SW19, SW22, SW27 and SW30.  All of the lensing
-galaxies are bright enough to satisfy the $i<22$ criterion. However,
-some of them have a bright companion galaxy, some of them do not look
-like E/S0 type galaxies and some are edge on galaxies. {\bf there are a
-few which look regular galaxies so which criteria are they failing??}
-
-%% 13 are under mask so no photoz, 10 have photoz (z>0.2 except for 1).
-
-In the following steps, the flux from the galaxy is subtracted from the
-scaled difference image to enhance the visibility of the faint blue
-lensed features. An object finder is run on this image to quantify the
-lensed image properties. About 50\% of the \sw candidates could not be
-detected by the object finder because properties such as the image area,
-axis ratio, magnitude/color and alignment with respect to the lensing
-galaxy are not satisfied. Some of the candidates missed at this stage
-are e.g. SW4, SW5, SW6, SW26, SW36, SW39 and SW47.
-
-%% 23/61 miss first step, 30/61 miss auto, 5 pass auto but have poor
-%grade from visual classf.
-
-Next, we rerun the \af on the same \sw sample of new candidates. The \af
-is directly run an image to look for elongated arc like objects and does
-not require a list of targets to begin with. Objects are identified by
-placing thresholds on the noise level in the images. Thus, \af
-detections are sensitive to changes in the noise levels. Also, the size
-of the PSF is important to know what dimensions should be expected for
-the arc candidates.
-
-Originally, the \af was run on a large image with an area of $\sim 19400
-\times 19400$ pixels$^2$. For the rerun, we work with much smaller
-images because this is faster but this affects the number and type of
-arc detections. We find that about 30\% of the new candidates are detected
-without changing any of the thresholds in the code because of the change
-in the noise level.
-
-{\bf TBD: 
-comment on any lensed quasars, on any exotic lenses;
-of course, there must be lenses which cannot be detected currently by
-either robots/humans
-check if some candidates were detected because they were hidden
-underneath the sims ie. from the D11;
-}
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
-\subsection{Limitations and Caveats of the training sample}
-
-The simulated sample is not perfect because our understanding of various
-phenomena in the Universe is not complete and because of the uncertainties in
-the parameters of our model. Here, we describe some of the cases or
-aspects in which the simulations are known to have failed or seem
-unrealistic.
-
-The parameters required by various scaling relations and the models primarily
-depend on the photometry of the galaxies, groups and quasars detected in the
-survey. For galaxy-scale lenses, the lensing galaxies at higher redshifts or
-which are fainter have poor photometric measurements. This causes relatively
-larger uncertainties in its luminosity and velocity dispersion and leads to
-simulated lenses which look implausible. For example, due to a larger
-uncertainty in the velocity dispersion of the lensing galaxy, the lensed images
-may have larger image separation than what is expected given the visual priors
-from the galaxy.
-
-At group-scales, the photometric and redshift estimates are used when
-defining the group membership. Therefore, errors in redshift estimates generate
-galaxy groups with BGG or member galaxies with dissimilar properties. In some
-cases, low redshift spiral galaxies are incorrectly assigned high redshift.
-Spiral galaxies are typically less massive and low redshift spiral galaxies are
-unlikely to act as gravitational lenses. Hence, the resulting simulated lenses
-are not convincing.
-
-We use single Sersic component to describe the light profiles of background
-galaxies. This is clearly not the most accurate description for galaxies,
-especially, star-forming galaxies which form a significant fraction of the
-lensed galaxy population. Star-forming galaxies have complex structures such as
-star forming knots, spiral arms, bars and disks.
+\subsubsection{Volunteer profile}
+
+Here, we investigate if the skill or experience of volunteers is
+systematically different between the sample of detected and missed
+lenses.
+
+We check how the posterior probability P (see XXXX Paper I) of an image
+or a subject to contain a lens changes as the image receives more
+classifications from multiple users.  In \Fref{fig:detmis}, we show the
+trajectory plots of a few examples of detected lenses (top left panels)
+and missed lenses (bottom left panels) by \sw at stage I. The number of
+classifications (Nclass) for a subject increase from top to bottom.
+Also, every subject is assigned a prior probability P0=2.e-4 (grey
+dashed line) and starts at the middle of the trajectory plot. The P
+value of a subject is updated with every classification from the
+volunteer.  If a volunteer identifies a lens candidate, the trajectory
+moves to the right otherwise moves to the left. A subject is accepted if it
+crosses the blue-dashed line marking the (P$_{\rm acc thresh}=0.95$) on
+the right and is rejected, if it crosses the red-dashed line marking the
+P$_{\rm rej thresh}=1.e-7$ on the left.
+
+By how much the P value will change depends on how well the
+volunteers are performing on the training sample. Thus, more skilled
+volunteers will change the P by a large factor compared to the less
+skilled volunteers. This is evident in the trajectory plots as large and
+small distances in between consequent points.
 
@@
 simulated and the real sample of lens candidates. }
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.6]{sw-cfhtls-figs/det_mis_traj.pdf}
+\includegraphics[scale=0.6]{sw-cfhtls-figs/det_mis_hist.pdf}
+\caption{ \label{fig:detmis}
+Example cases of trajectories of known lenses on the left and histogram
+of the known lenses. The trajectories on the left are lenses that are
+detected by \sw are at the top and lenses that are missed are at the bottom. }
 \end{center}

### 2015-03-17 doc/sw-system.tex
Done intro #96

@@
 
-\sw is a web-based service that enables the discovery of strong gravitational
-lenses in wide-field imaging surveys by large numbers of people. Carefully
+We describe \sw, a novel gravitaional lens discovery service that
+yields samples of high purity and completeness through crowd-sourced
+visual inspection.
+Carefully
 produced color composite images are displayed to volunteers via a
@@
 \citep[e.g.][]{PoindexterEtal2008}. All of these investigations would
-benefit from being able to draw from a larger sample of lenses.
-
-In the last decade the numbers of detections of these rare cosmic alignments
+benefit from being able to draw from a larger and/or more diverse sample of lenses.
+
+In the last decade the number of these rare cosmic alignments known
 has increased by an order of magnitude, thanks to searches carried out in
@@
 
-Because they are rare, strong lenses are expensive to find. The most efficient
+Because they are rare, strong lenses are expensive to find. The highest purity
 searches to date have made use of relatively clean signals such as the
@@
 ``magnification bias'' towards detecting strongly-lensed sources in the sub-mm
-waveband \citep[e.g.][]{NegrelloEtal2010}. Such searches have to be efficient,
+waveband \citep[e.g.][]{NegrelloEtal2010}. Such searches have to yield pure samples,
 because they require expensive high resolution imaging follow-up; consequently
@@
 times the sky area, such as the almost-all sky surveys planned with LSST and
-Euclid, while reducing our dependence on expensive follow-up confirmation
-observations? There are two approaches to detecting lenses in imaging surveys.
+Euclid?  There are two approaches to detecting lenses in imaging surveys.
 The first one is robotic: automated analysis of the object catalogs and the
@@
 searching for gravitational lenses. The technique has some drawbacks, however.
-First is that humans are only humans, and they make mistakes. A solution to
+The first is that humans make mistakes. A solution to
 this is for the inspectors to operate in teams, providing multiple
@@
 visual lens searches in good quality imaging data are limited to a few square
-degrees per inspector per day. Scaling to thousands of square degrees
+degrees per inspector per day (and less, if mre time is spent assessing difficult systems).
+Scaling to thousands of square degrees
 therefore means either robotically reducing the number of targets for
@@
 of rare objects, via its flexible inspection interface and discussion forum
-\citep{LintottEtal2009}. Indeed, several of us (AV,EB,CC,TJ,CM,LW) were active
-in an informal Galaxy Zoo gravitational lens search, an experience which led
+\citep{LintottEtal2009}. Indeed, several of us (AV,CC,CM,EB,PM,TJ,LW) were active
+in an informal Galaxy Zoo gravitational lens search (Verma et al, in preparation),
+an experience which led
 to the present hypothesis that a systematic online visual lens search could be
@@
 
-In this paper, we describe the \sw web application, an online system that
-enables  crowd-sourced gravitational lens detection by inviting volunteers to
-classify astronomical survey images as containing lens candidates or not.  In
-a companion paper (More et al, in preparation, herafter \papertwo) we will
+In this paper, we describe the \sw web application, an
+online system that was conceived to address the visual inspection problem in
+gravitational lens detection for future large surveys via crowd-sourcing, and
+implemented as a Zooniverse project.
+In a companion paper (More et al, in preparation, herafter \papertwo) we will
 present the new gravitational lenses discovered in our first, experimental,
@@
 us to estimate completeness and purity with respect to gravitational lenses
-that have the same properties of the training set. In \papertwo we carry out
-similar tests but with a sample of known (real) lenses {\it in situ}.
+that have the same properties of the training set. In \papertwo,
+we carry out a complementary analysis using a sample of
+``known'' (reported in the literature) lenses.
 

### 2015-03-17 doc/sw-cfhtls.tex

@@
 are images which have been visually inspected by experts and confirmed
-to contain no lenses.  False positives are systems which look like
+to contain no lenses.  False positives (FPs) are systems which look like
 lenses but are not, for example, spiral galaxies, starforming galaxies,
@@
 or they have odd properties which makes them difficult to identify
-correctly.  ({\bf show some
-example images XXX}). For further tests, we combine the \rf and \af sample.
+correctly. For further tests, we combine the \rf and \af sample.
 
@@
 missed sample. Surprisingly, most of the lenses in the known sample have
-few classifications (Nclass<10) which includes both the detected and
+few classifications (Nclass$<$10) which includes both the detected and
 missed lenses. Many of the remaining have between 10 to 20
-classifications. And, only a few subjects have Nclass>20 which continue
+classifications. And, only a few subjects have Nclass$>$20 which continue
 to remain for long in the database because these candidates may have
@@
 a status of detected (if P$>$P$_{\rm acc thresh}$), rejected (if
-P$<$P$_{\rm rej thresh}$) and undecided (if P$_{\rm rej thresh}$ $<$ P
+P$<$P$_{\rm rej thresh}$) and undecided (if P$_{\rm rej thresh}<$ P
 $<$ P$_{\rm acc thresh}$). In \Fref{fig:comppos}, we compare the
@@
 
-Here, we investigate if the skill or experience of volunteers is
-systematically different between the sample of detected and missed
-lenses.
+Here, we investigate if the skill\footnote{see the
+\Aref{appendix:skill} for the choice of this term and how it is
+different from that used in paper I} of volunteers is systematically
+different between the sample of detected and missed lenses.
 
@@
 classifications (Nclass) for a subject increase from top to bottom.
-Also, every subject is assigned a prior probability P0=2.e-4 (grey
+Also, every subject is assigned a prior probability P0$=2\times10^{-4}$ (grey
 dashed line) and starts at the middle of the trajectory plot. The P
@@
 the right and is rejected, if it crosses the red-dashed line marking the
-P$_{\rm rej thresh}=1.e-7$ on the left.
+P$_{\rm rej thresh}=10^{-7}$ on the left.
 
@@
 skilled volunteers. This is evident in the trajectory plots as large and
-small distances in between consequent points.
+small distances in between the consequent points which we refer to as
+kicks. Comparison of the kick sizes between the detected
+and the missed lenses suggests that the missed lenses do not have as
+many volunteers giving large kicks. We also note that most of the large
+kicks seen in the trajectories of the missed lenses seem to be moving
+the subjects to the right. In other words, the more skilled volunteers
+are mostly classifying them as subjects with lens candidates. Further
+qualitative comparison and discussion of the trajectory plots is given
+in \Aref{appendix:traj}.
+
+For a quantitative comparison of the large and small kicks for the
+entire samples of detected and missed known lenses, we show a plot of
+histogram on the right of \Fref{fig:detmis}. Qualitatively, there are
+four types of volunteers making classifications - those causing positive
+large kicks (correct classifications by more skilled volunteers, those
+causing positive small kicks (correct classifications by less skilled
+volunteers), those causing negative small kicks (incorrect
+classifications by less skilled volunteers) and those causing negative
+large kicks (incorrect classifications by more skilled volunteers). The
+four histograms in the figure correspond to these four types of
+volunteers for each sample (that is, detected or missed). The kick size
+is small if $\Delta$ log(P)$=$log (P$_{\rm current}) - $log(P$_{\rm
+previous}) < \Delta$log(P)$_{\rm cut}$ (chosen to be 1.2) and is large
+if greather than $\Delta$log(P)$_{\rm cut}$.
+
+Some of the key differences are i) the ratio of positive large kicks to
+positive small kicks for the detected sample is higher than the missed
+sample suggesting that the fraction of more skilled volunteers is large
+for the detected sample ii) in terms of Nclass, the missed sample is
+dominated by volunteers causing negative small kicks whereas for the
+detected sample there is a comparable contribution from three types of
+volunteers - positive small and large kicks and negative small kicks.
+iii) the Nclass from volunteers with negative large kicks are lower both
+for the detected and the missed samples. this is consistent with our
+expectation that more skilled volunteers should not be making incorrect
+classifications.Therefore, lack of more skilled volunteers classifying
+the missed lenses seems to be one of the major factors.
+
+We rerun SWAP for stage I where we use classifications from volunteers
+who produce $\Delta$ log(P)$>1.2$ only. This obviously means reducing
+the total Nclass per subject by a large fraction. As a result, we also
+need to change the P$_{\rm acc thresh}$ which is chosen to be 0.1 and we
+find that about a third of the missed lenses are detected while all the
+previously detected lenses remain detected too. The others simply do not
+have enough classifications from volunteers producing large positive
+kicks. Thus, it may be possible to detect more promising candidates if
+we preferentially show the rejected systems to a few more skilled
+volunteers. We understand that changing the rejection and acceptance
+thresholds will likely increase the rate of FPs along with
+improved completeness but most probably the increase in FPs will not be
+too significant and that it will still be worth using the new strategy.
 
@@
 \caption{ \label{fig:detmis}
-Example cases of trajectories of known lenses on the left and histogram
-of the known lenses. The trajectories on the left are lenses that are
-detected by \sw are at the top and lenses that are missed are at the bottom. }
+Examples of trajectories of some known lenses (top-left: detected and
+bottom-left: missed) at stage I and histogram of the known lenses for
+different types of volunteers (right).
+}
 \end{center}
@@
 \label{sec:conclude}
-In this paper, we describe the framework and procedure used to generate
-simulated lens sample for the blind lens search in the \cfhtls survey in
-collaboration with \sw. The aim of this lens search is to find lenses that have
-been missed by lens finding algorithms. The simulated lens sample is used for
-training the citizen scientists, calibrating their performance and rejecting
-unlikely lenses from the sample based on the classifications of citizen
-scientists. As a result, the simulated lenses need to consist of realistic
-looking lenses.
-
-We use the photometric and redshift catalogues for the foreground galaxies and
-additionally, color catalogues for background galaxies and quasars. We
-use scaling relations to relate light properties to properties such as mass and
-size to generate lens models. We further account for the
-instrumental effects such as seeing and noise before creating the final lensed
-images of model background sources. We add the lensed images on top of the real
-galaxies and groups in the \cfhtls data in all filters.
+
+We report the discovery of new gravitational lens candidates from the
+the first lens search through \sw. In this search, volunteers are shown
+$g-r-i$ color images of random regions of the sky taken by the CFHT Legacy
+Survey. The aim of this lens search is to find lenses that have been
+missed by previous searches done on the \cfhtls with lens finding
+algorithms. In this search, we use a training sample to train the
+volunteers and calibrate their performance which helps us in more
+efficient pruning of the lens candidates. The training sample has
+simulated lenses, duds and FPs. In this paper, we describe the details
+of the training sample generated and tuned for the \cfhtls data.
+Volunteers receive feedback messages when they click or fail to click on
+the training images during live classification of real images which
+helps them remain focused and improve their performance over time.
+
+The blind lens search in the \cfhtls is done in two stages: stage I and
+stage II. The aim of stage I is to do fast inspection of a large sample
+of $\sim$ 430 000 images and reduce them to a smaller sample of $\sim$
+3000 images with interesting lens candidates. The aim of stage II is to
+carefully reinspect the smaller pool of images to exclude as many FPs as
+possible and reduce the sample to $\sim$~500 candidates. In the next
+step, the images are graded by three lens experts (AM,AV and PJM)
+leaving in systems that are mildly interesting to very promising lens
+candidates.
+
+%For the simulated sample, we use the photometric and redshift
+%catalogues for the foreground galaxies and additionally, color
+%catalogues for background galaxies and quasars. Scaling relations allow
+%us to relate the light properties to properties such as mass and size
+%to generate lens models. We further account for the instrumental
+%effects such as seeing and noise before creating the simulated lensed
+%features of model background sources. We add the simulated lensed
+%features on top of the real galaxies and groups in the \cfhtls data in
+%all filters. A sample of duds and FPs is vetted visually before
+%ingesting them to the database.
 
@@
 
-\item Crowd-sourced gravitational lens detection works, as shown in by comparing with real lenses in CFHTLS:
-Real (robotically-detected and expert-confirmed) lenses are
-recovered/missed at similar/comparable/different rates C’\% and P’\% - this is a partial test of supervised vs unsupervised learning
-
-%Which real lenses were missed? False negatives
-
-\item We found a sample of new gravitational lens candidates. An
-expert-graded sample of 74 with 44 promising and 30 low probability
-candiates.
-
-The SW lenses are different from the robotically (\rf and \af) detected lenses, in the following ways.
-XXXXX
+\item Crowd-sourced gravitational lens detection works. We present a new
+sample of 61 gravitational lens candidates with average expert grade of
+1.3 and above where 1-mildly interesting, 2-probably, a lens and
+3-certainly, a lens.
+
+%Real (robotically-detected and expert-confirmed) lenses are
+%recovered/missed at similar/comparable/different rates C’\% and P’\% -
+%this is a partial test of supervised vs unsupervised learning
+
+\item Compared to the sample of robotically (the \rf and \af) detected
+lens candidates, the \sw sample finds lens systems with similar range in
+the lens redshift and the flux and the Einstein radii of the lensed
+images. However, the \sw search being a purely visual one cannot find
+some of the \rf-identified-lensed images with sub-arcsecond Einstein
+radii because the flux of the typically faint lensed images is obscured
+by the flux from bright lensing galaxies. The \rf finds these candidates
+because it works with lensing galaxy-subtracted images.
+
+\item Qualitatively, the \sw sample finds lens systems with different
+types of lensing galaxies, for example, elliptical, spiral (face on and
+edge on) and small red galaxies unlike those found from robotic
+searches. Similarly, the lensed images too have different colors,
+morphologies and sizes which are again typically missed by any given
+algorithm.
+
+\item
 
@@
 
+\section{Qualitative comparison of detected and missed known lenses}
+\label{appendix:traj}
+
+\section{Skill}
+\label{appendix:skill}
+In paper I, the term skill is given by the expectation value of the
+information gain which is related to the P$_{\rm L}$, the probability to
+correctly identify a lens as a lens and P$_{\rm D}$, the probability to
+correctly identify a dud as a dud. The skill does not have simple
+dependency on P$_{\rm L}$ and P$_{\rm D}$. One can get the same value of
+skill for different combinations of P$_{\rm L}$ and P$_{\rm D}$.
+
+As described in the appendix of paper I, the posterior probability P is
+related to the volunteers skill (or information gain). Also, a volunteer
+with a given skill, will have different positive ($\Delta$~log(P)) and
+negative (-$\Delta$~log(P)) kicks on the trajectory plot. Thus, it is
+not useful to compare classifications of high and low skill volunteers
+to understand if there is a difference in their performance and if the
+high skill volunteers can increase the completeness of the lenses. For
+example, a volunteer who is very good at rejecting duds and not so good
+at identifying lenses will still have a high skill. But such a
+volunteer will fail to detect many of the interesting lenses. Therefore,
+we do not compare high skill vs. low skill volunteers to address this
+issue.
+
+For lack of a better word, we also use the same term skill which has a
+similar meaning to that described in paper I but not identical. We use a
+more qualitative definition implying the ability of the volunteers to
+make correct lens identification.
+
+%%%%%%%%%%%%%%
+XXXXX
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-03-20 doc/sw-system.tex
Up to section 2.3.2 (stage 2) in AV comments #96

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
 % Space Warps System Paper
@@
 times the sky area, such as the almost-all sky surveys planned with LSST and
-Euclid?  There are two approaches to detecting lenses in imaging surveys.
-The first one is robotic: automated analysis of the object catalogs and the
-survey images. The candidate samples produced by these methods have, to date,
-not been of high purity  \citep[see
+Euclid?  There are two approaches to detecting lenses in imaging surveys. The
+first one is robotic: automated analysis of the object catalogs and the survey
+images. The candidate samples produced by these methods have, to date, not been
+of high purity  \citep[see
 e.g.][]{MarshallEtal2009,MoreEtal2012,GavazziEtal2014}, with visual inspection
 by teams of humans still required to narrow down the robotically-generated
-samples. In this approach, the image data may or may not be explicitly
-modelled by the robots as if it contained a gravitational lens, but the visual
-inspection can be thought of as a ``mental modeling'' step. Systems classified
-by an inspector to be good lens candidates are deemed as such because the
-features in the image can be explained by a model of what gravitational lenses
-do contained in the inspector's brain. The second approach simply cuts out the
-robot middleman: \citet{MoustakasEtal2007,FaureEtal2008,Jackson2008} and
+samples. In this approach, the image data may or may not be explicitly modelled
+by the robots as if it contained a gravitational lens, but the visual inspection
+can be thought of as a ``mental modeling'' step. Systems classified by an
+inspector to be good lens candidates are deemed as such because the features in
+the image can be explained by a model of what gravitational lenses do contained
+in the inspector's brain. The second approach simply cuts out the robot
+middleman: \citet{MoustakasEtal2007,FaureEtal2008,Jackson2008} and
 \citet{PawaseEtal2014} all performed successful, entirely visual searches for
@@
 \Fref{fig:screenshot}. The CI is the centrepiece of the \sw website,
-\texttt{http://spacewarps.org}; the web application is written in
-coffeescript, css and html and follows the general design of others written by
-the Zooniverse team.\footnote{The \sw web application code is open source and
-can be accessed from \texttt{https://github.com/zooniverse/Lens-Zoo}}  The
-focus of the CI is a large display of the current pre-prepared PNG image of
-the ``subject'' being inspected.   When the image is clicked on by the
-volunteer, a marker symbol appears where the pointer was. Several markers can
-be placed.  The next image moves rapidly in from a queue formed at the right
-hand side of the screen when the ``Finished marking'' button is pressed. At
-the same time, the positions of the markers are written out to the
-classification database, in an entry that also stores the ID of the subject,
-the username (or IP address) of the volunteer, a timestamp and some other
-metadata.
-
-Gravitational lenses are rare: typically, most of the images will not contain
-a lens candidate, and these need to be quickly rejected by the inspector. The
-queue allows several images to be pre-loaded while the volunteer is
-classifying the current subject, and the rapid movement is designed to
-encourage volunteers to classify rapidly.
-
-% PJM: how quickly? How much clock time per classification?
+\texttt{http://spacewarps.org}; the web application is written in coffeescript,
+css and html and follows the general design of others written by the Zooniverse
+team.\footnote{The \sw web application code is open source and can be accessed
+from \texttt{https://github.com/zooniverse/Lens-Zoo}}  The focus of the CI is a
+large display of a pre-prepared PNG image of the ``subject'' being inspected.
+When the image is clicked on by the volunteer, a marker symbol appears where the
+pointer was. Several markers can be placed.
+
+The next image moves rapidly in from a queue formed at the right hand side of
+the screen when the ``Finished marking'' button is pressed. Gravitational lenses
+are rare: typically, most of the images will not contain a lens candidate, and
+these need to be quickly rejected by the inspector. The queue allows several
+images to be pre-loaded while the volunteer is classifying the current subject,
+and the rapid movement is designed to encourage volunteers to classify rapidly.
+After each classification, the positions of the markers are written out to the
+classification database, in an entry that also stores the ID of the subject, the
+username (or IP address) of the volunteer, a timestamp and some other metadata.
 
 For the more interesting subjects, the CI offers two features that  enable
-further investigation of the subjects. The first is the ``Quick Dashboard'' (QD) a
-more advanced image viewer. This allows the viewer to compare three different
+further investigation of the subjects. The first is the ``Quick Dashboard'' (QD)
+a more advanced image viewer. This allows the viewer to compare three different
 contrast and color balance settings, to help bring out subtle features, and to
-zoom in on interesting regions of the image to assess small features. Markers
-can be placed in the Quick Dashboard just the same as in the main CI image
-viewer. The second is a link to that subject's page in the project discussion
-forum, \texttt{http://talk.spacewarps.org} (known as ``Talk''). Here,
+pan and zoom in on interesting regions of the image to assess small features.
+Markers can be placed in the Quick Dashboard just the same as in the main CI
+image viewer. The second is a link to that subject's page in the project
+discussion forum, \texttt{http://talk.spacewarps.org} (known as ``Talk''). Here,
 volunteers can discuss the features they have seen either before they submit
 their classification, or after, if they ``favorite'' the subject. There is no
-``back'' button: each volunteer may only classify a given subject once.
-However, the presence of an option to see what others think about any given
-subject before submitting your own classification means that the
-classifications may not be  strictly independent; the advantage of this system
-is that volunteers can learn from others what constitutes a good lens
-candidate. In practice, we might expect this to be a relatively unimportant
-educational resource, given the explicit training we provide for the
-volunteers, which we describe in the next section.
+``back'' button: each volunteer may only classify a given subject once. However,
+the presence of an option to see what others think about any given subject
+before submitting your own classification means that the classifications may not
+be strictly independent; the advantage of this system is that volunteers can
+learn from others what constitutes a good lens candidate. This is not, however,
+the primary educational resource; we describe the explicit training that we
+provide for the volunteers in the next section.
 
@@
 they are encountered, an inline tutorial, instant feedback,
-and a ``Spotter's Guide.''
+and a ``Spotter's Guide.'' As well as this, we provide ``About'', ``FAQ'' and ``Science'' pages explaining the physics of gravitational lensing.
+While we expect that the insight from this static material should help volunteers make sense of the features in the images, we focus on the more dynamic, activity-based training early, when engaging new volunteers to participate takes priority.
 
@@
 subjects are either simulated lenses (known as ``sims''), or survey images
-that were expert-classified (by AV, AM and PM) and found not to contain any
+that were expert-classified and found not to contain any
 lens candidates (these images are known as ``duds''). The tutorial explains
@@
 in \Fref{fig:screenshot}) or negative feedback for an unsuccessful one (for
-example, ``There is no gravitational lens in this field!'')
-
-The initial frequency of the training images is set to be two in five;
-subjects are drawn randomly from the pool of training images with this
-frequency. The pool contains equal numbers of sims and duds, and the draw is
-made without replacement (for that volunteer). As the number of
-classifications made by a volunteer increases, this frequency is decreased, to
+example, ``There is no gravitational lens in this field!'').
+
+\todo{PJM}{Insert simulations paragraph here.
+General description of sim generation.
+Principles: use real images, draw from realistic populations, strike balance between easy to see (for education) and realistically difficult (to push sensitivity).
+\#106}.
+
+When a volunteer begins classifying, they are initially shown training images at
+a frequency of two in five; these subjects are drawn at random from a pool
+containing equal numbers of sims and duds, such that that volunteer never sees a given image more than once. As the number of classifications made by a
+volunteer increases, this frequency is decreased, to
 $2/(5\times2^{(\textrm{int}(N_c/20)+1)/2})$ ($\approx 0.3$ for the second 20
@@
 
-In \Fref{fig:training-gallery} we show 8 example training images from the
-first \sw project (\Sref{sec:data} below).
+In Figures~\ref{fig:training-gallery:sims}~and~\ref{fig:training-gallery:duds}
+we show example training images from the first \sw project (\Sref{sec:data}
+below).
 
@@
 We now describe briefly the two-stage strategy that was employed in the CFHTLS
-project, initial classification (involving the rejection of very large numbers
+project: initial classification (involving the rejection of very large numbers
 of non-lenses), and refinement (to further narrow down the sample). The web
@@
 results section below. Completion of the search requires subjects to be
-``retired'' over time, as a result of their being classified. We do this by
+``retired'' over time, as a result of their being classified. We did this by
 analyzing the classifications on a daily basis, as described in
-\Sref{sec:swap} below. As subjects are retired, new ones are ingested into
+\Sref{sec:swap} below. As subjects were retired, new ones were ingested into
 the web app for classification. This means that the discovery of lens
 candidates in stage 1 is truly a community effort: to detect a lens candidate,
-many non-lenses must first be rejected.
+many non-lenses must first be rejected, and several classifications by different inspectors are needed in either case.
 
@@
 the side of inclusivity, and so ensure high completeness. For the training
-duds we selected several hundred images at random, and three of us (AV, AM,
-PM) inspected them and discarded anything that could be a lens candidate. The
-remainder were ingested into the site.
+duds we selected several hundred images at random, and three of us (AM, with AM and PM) inspected them and discarded anything that could be considered a lens candidate.
+
+% PJM IS HERE
 

### 2015-03-22 doc/addresses.tex
Started prob theory write-up
Updated plan for paper 1
updated ipmu affiliation
first draft with all sections, figs, tables and appendix

@@
 \def\kipac{Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA}
-\def\ipmu{Kavli Institute IPMU, University of Tokyo, Japan}
+\def\ipmu{Kavli IPMU (WPI), University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa 277-8583, Japan}
 \def\adler{Adler Planetarium, Chicago, IL, USA}
+\def\lausanne{EPFL, Lausanne, Switzerland}
 \def\zurich{Department of Physics, University of Zurich, Switzerland}
+\def\paris{Institut d’Astrophysique de Paris, UMR7095 CNRS – Universit\'e Pierre et Marie Curie, 98bis bd Arago, 75014 Paris, France}
+\def\icg{Institute of Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Portsmouth P01 3FX, UK}
 
-\def\pjmemail{\tt dr.phil.marshall@gmail.com}
+\def\pjmemail{\tt pjm@slac.stanford.edu}
+\def\amemail{\tt anupreeta.more@ipmu.jp}

### 2015-03-22 doc/sw-cfhtls.tex
first draft with all sections, figs, tables and appendix

@@
 
-The CFHT Legacy Survey has been searched for strong lenses with
-semi-automated algorithms both at galaxy and groups scales. With the aim
-of improving these lens finding robots, we carry out a blind lens search
-in the complete \cfhtls \textsc{wide} survey with \sw. We describe the training
-sample used for both training the citizen scientists that participated
-in \sw and calibrating their performance. We generate realistic looking
-simulated samples of lenses both at galaxy and group-scales as part of
-this training sample. We present 61 new strong gravitational lens
-candidates discovered from the \sw-\cfhtls search out of which 40
-candidates are promising. Furthermore, we compile a sample of false
-positives which can be used for robot testing, first of its kind for the
-lensing community. The simulated sample is also used to make a
-comparison between human performance against the robots. We find that
-the XX per cent of the known lens sample is recovered and the new lens
-sample has XX completeness with respect to the simulated sample. We make
-available the following data products: simulated sample, simulation code
-and the false positives sample at XXX.
+We report the discovery of 61 new lens candidates in the CFHT Legacy Survey data
+(\cfhtls) based on about 11 million classifications performed by citizen
+scientists as part of the first blind lens search undertaken by \sw.  The
+principle goal of this lens search was to identify lenses missed by lens finding
+robots (the \rf on galaxy scales and \af on group/cluster scales), which have
+been previously used to mine the \cfhtls data for lenses.  We compare the
+properties of known lens samples detected by these algorithms to the \sw sample
+and found that they are broadly similar.  The image separation distribution
+calculated from the combined sample of known and new lens candidates shows that
+our previous constraints on the average density profile of the lens population
+are robust.  In addition to recovering about 60\% of the known sample, the new
+\sw candidates possess a richer variety compared to the lenses found by the two
+robots. We find that analyzing only those classifications which are performed by
+the more skilled volunteers, \sw can achieve a detection rate of up to 75\%.
+Training and calibration of the performance of citizen scientists is crucial for
+the success of \sw. We also present the SIMCT pipeline, used for generating a
+sample of realistic simulated lensed images in the CFHTLS, and a sample of duds
+and false positives used in the training.  Such a training sample has a legacy
+value for testing future lens finding algorithms. We make our training sample
+publicly available.
+
+%In summary, \sw
+%has been successful in discovering a large sample of new lens candidates in
+%addition to recovering a substantial fraction of the known lenses in this pilot
+%lens search.
 
 \end{abstract}
+%The simulated sample is also used to make a comparison between human performance against the robots.
 
@@
 gravitational lenses owing to the plethora of interesting applications
-they have in astrophysics and cosmology. Strong lenses are routinely
-used to probe the dark matter distribution from galaxy (ref) to cluster
-scales (ref), to  study distant young galaxies by using the lensing
-magnification as a natural telescope (ref), to test the cosmological
+lenses have in astrophysics and cosmology. Strong lenses are routinely
+used to probe the dark matter distribution from galaxy (REF) to cluster
+scales (REF), to  study distant young galaxies by using the lensing
+magnification as a natural telescope (REF), to test the cosmological
 model by constraining cosmological parameters such as the Hubble
-constant (ref) and dark energy (ref) and many more. Even though strong
-lenses are rare, since a foreground massive object needs to be
+constant (REF) and dark energy (REF) and many more. Strong
+lenses are rare since a foreground massive object needs to be
 sufficiently aligned with a distant background source to produce
-multiple images, systematic lens searches have led to discovery of over
-500 lenses till date (XXX add mld url).
-
-Rarity of lenses implies searching for them is a painstaking task.
-Efficient automated methods are thus imperative to finding a reasonably
-complete and pure sample of strong lenses.
-
-Since the inception of the first citizen science project, Galaxy Zoo, to
-classify galaxy morphologies \citep{Lintott2008}, several astronomy
-and non-astronomy projects have been launched by the Zooniverse leading
-to many interesting project. For example, PlanetHunters
-has discovered XXX transiting exoplanets \citep{Schwamb2012},
-Supernova XXX add ref and XXX add ref
-
-In Paper I, we describe \sw, an online system that enables crowd-sourced
-detection of gravitational lenses. In this paper (referred to as Paper
-II), we describe our first lens search with \sw in the \cfhtls data.
-
-This paper is organised as follows. In \Sref{sec:sw} we give a brief
-overview of the \sw system, focusing on the aspects most relevant to the
-interpretation of the results of this first lens search. In
-\Sref{sec:data} we introduce the \cfhtls imaging data and the known lens
-samples from the \cfhtls. In \Sref{sec:}, we explain the training sample
-generated to aid the \sw users in the lens search. In
-\Sref{sec:results}, we present the new lens candidates and our findings.
-We discuss the implications of our results for future lens searches in
-\Sref{sec:discuss} and draw conclusions in \Sref{sec:conclude}.
+multiple images. Nevertheless, systematic lens searches have led to the
+discovery of over 500 lenses till
+date\footnote{http://masterlens.astro.utah.edu}.
+
+The search for gravitational lenses is a needle-in-a-haystack problem.
+Efficient automated methods are imperative to find a reasonably complete and
+pure sample of strong lenses. Several lens finding algorithms have been
+developed so far for this purpose (REF) but they can not simultaneously capture
+the myriad types of lenses that are known to exist.  For example, the lensed
+images of background galaxies show variety in their surface brightness
+distributions, colors, light profiles, shapes, structures and angular image
+separations.  Moreover, many lensed images appear similar to features found
+commonly in galaxies (such as spiral arms) or to artifacts in astronomical
+images (scattered light around stars).  Almost all lens finding algorithms find
+it difficult to distinguish these from the real lenses and thus, suffer from a
+high rate of false positives.  To minimize this problem, algorithms are often
+restricted to detect a very narrow class of lens systems. However, even after
+such restrictions, robotic lens searches have to always rely on visual screening
+to arrive at a list of plausible candidates.
+
+Recognising patterns amidst an array of noisy pixelated images is one of the
+strengths of human brains (REF). Humans are also capable of dealing with
+multi-tier complex web of questions before arriving at a conclusion which may
+not be always possible to automate. The algorithm by which our brains process a
+task is extremely malleable, self-learning and self-evolving. Therefore it has
+a huge potential for the discovery of exotic objects which do not quite fit a
+set criteria, but are still very likely to be objects of interest. The lens
+finding algorithms are not yet advanced enough to produce better performance
+than visual classifications. Given this, participation of a large community of
+volunteers to help with the visual identification of lenses is extremely
+beneficial for the lensing community. In particular, as we enter the era of
+large area imaging surveys (spanning thousands of square degrees), it is
+the perfect time to tap into the potential of citizen science.
+
+Galaxy Zoo, was the first citizen science project in astronomy which was used to
+classify galaxy morphologies \citep{Lintott2008}.  From the early results based
+on morphological classifications of galaxies, to several new unexpected and
+interesting discoveries, such as that of green pea galaxies and Hanny's
+Voorwerp, Galaxy Zoo has been able to harness the potential of citizen
+scientists.  Since then astronomy and non-astronomy projects have been launched
+under the citizen science web portal Zooniverse (http://zooniverse.org). The task of finding
+gravitational lenses is significantly challenging given the fact that these
+lenses are rare. To add to the challenge, not many citizen scientists are
+expected to be aware of the phenomenon of gravitational lensing, and the
+resulting image configurations.  With these significant challenges at hand, we
+designed the \sw project to enable the discovery of lenses through citizen
+science.  In Paper I (REF), we describe the design of \sw and how the entire
+system functions as a discovery engine.
+
+%
+%\subsection{Paper I: Overview}
+%In Paper I, we give details of the classification interface used by the
+%volunteers. The regular images called test subjects are served randomly from the
+%database. Some of the test subjects are labelled as training subjects because
+%either these have simulated lensed images superposed around real galaxies or
+%there are some false positives in the subjects.  The sample of training subjects
+%is much smaller compared to the sample of test subjects. The training subjects
+%are shown with decreasing frequency to the volunteers depending on how new the
+%volunteers are to the project based on their classification history. However,
+%the frequency of training subjects becomes a constant after XXX classifications
+%from a volunteer.
+%
+%Clicking (or failing to click) on the training subjects results in a
+%pop-up feedback message that congratulates the volunteers or points them
+%to read the Spotter's guide pages. The website has several examples of
+%real lenses and false positives with explanation on the Spotter's guide
+%page. A quick reference to the Spotter's guide is available in the
+%classification interface as well. Additional features to change zoom,
+%contrast and brightness are made available to make a better judgement of
+%the difficult lens candidates.
+%
+%The classification of subjects happens in two serial stages. Stage I is
+%for quick rejection of all uninteresting subjects. Subjects that passed
+%Stage I are then reinspected at Stage II, for a careful selection of
+%most promising lens candidates. In general, subjects are assigned a
+%small prior probability for it to contain a lens. As each subject is
+%seen by multiple volunteers, the posterior probability P is updated by
+%using the weights of the volunteers. The weights are determined based on
+%how well the volunteers perform on the training sample. Once a subject
+%crosses a threshold (acceptance or rejection), it is retired from the
+%database to ensure that rest of the subjects receive sufficient multiple
+%classifications. This is true for stage I with ~10$^5$ subjects but is
+%not required for stage II with only a few thousand subjects.
+%
+%{\bf AM: add one more paragraph that gives some key conclusions and numbers
+%from Paper I}
+%\question{AM}{PJM,AV, should we have this overview section on paper I?}
+%
+
+In this paper ( Paper II hereafter), we describe our first lens search using
+data from the Canada-France-Hawaii Telescope Legacy Survey (\cfhtls, REF).  This
+paper is organised as follows. In \Sref{sec:data}, we introduce the \cfhtls
+imaging data and the known lens samples from the \cfhtls. In \Sref{sec:ts} and
+\Sref{sec:dfp}, we explain the training sample consisting of simulated lenses,
+duds and false positives generated to aid the \sw volunteers in the lens search.
+In \Sref{sec:results}, we present the new lens candidates from \sw and compare
+\sw to two lens finding algorithms which produced the known \cfhtls lens
+samples. Next, we discuss what kind of lenses are detected or missed by the
+algorithms and \sw in \Sref{sec:discuss}. The summary and conclusions are given
+in \Sref{sec:conclude}.
 
@@
 
-The Canada-France-Hawaii Telescope Legacy Survey (CFHTLS) is a
-photometric survey in five optical bands ($u^*g'r'i'z'$) carried out
-with the wide-field imager MegaPrime which has a 1~deg$^2$ field-of-view
-and a pixel size of 0.186\arcsec. The \cfhtls \textsc{WIDE} covers a total area
-of 171~deg$^2$ on the sky and it consists of four fields W1, W2, W3 and
-W4. The field W1 has the largest sky coverage of 63.65~deg$^2$. The
-fields W2 and W4 have similar sky coverages of 20.32~deg$^2$ and
-20.02~deg$^2$, respectively\footnote{These numbers are estimated from http://terapix.iap.fr/cplt/table\_syn\_T0006.html}.
-The field W3 has a sky coverage of 42.87~deg$^2$ and is more than twice
-as large as W2 and W4.
+The \cfhtls is a photometric survey in five optical bands
+($u^*g'r'i'z'$) carried out with the wide-field imager MegaPrime which
+has a 1~deg$^2$ field-of-view and a pixel size of 0.186\arcsec. The
+\cfhtls \textsc{WIDE} covers a total area of 171~deg$^2$ on the sky and
+consists of four fields W1, W2, W3 and W4. The field W1 has the
+largest sky coverage of 63.65~deg$^2$. The fields W2 and W4 have similar
+sky coverages of 20.32~deg$^2$ and 20.02~deg$^2$,
+respectively\footnote{These numbers are estimated from
+http://terapix.iap.fr/cplt/table\_syn\_T0006.html}.  The field W3 has a
+sky coverage of 42.87~deg$^2$ and is more than twice as large as W2 and
+W4.
 
@@
 
-We note that the \cfhtls is a niche survey with a unique combination of
-wide imaging with deep sensitivity. It is a precursor to the ongoing
-wide imaging surveys such as the DES, KIDS and HSC and planned surveys
-such as the LSST. Searching for lenses with \sw in the \cfhtls will
-teach us important lessons and help prepare us for these larger imaging
-surveys.
+We note that the \cfhtls is a niche survey with a unique combination of wide
+imaging with deep sensitivity. It is a precursor to the ongoing wide imaging
+surveys such as the Dark Energy Survey (DES), Kilo Degree Survey (KiDS) and the
+Hyper Suprime-Cam (HSC) survey and other planned future surveys such as the
+Large Synoptic Survey Telescope (LSST) survey.  The search for lenses with \sw
+in the \cfhtls is an important step to learn lessons and prepare for lens
+searched in these larger imaging surveys.
 
@@
 
-Our aim is to do a blind lens search over the entire \cfhtls
-\textsc{wide}. We use the $g$, $r$ and $i$-band color imaging which are
-most useful for visual identification of lenses (and provide access to
-the $u$ and $z$ band imaging through dashboard with additional tools
-XXX).
-
-We make color composite images using publically-available
-code\footnote{The open source  color image composition code used in this
+In order to perform a blind lens search over the entire \cfhtls \textsc{wide},
+we present the users with cutouts of images selected from the survey region. We
+use the $g$, $r$ and $i$-band imaging from \cfhtls which are most useful for visual
+identification of lenses. We also provided access to the $u$ and $z$ band imaging
+data through dashboard, when users wished to take a closer look at a particular system\footnote{The dashboard tool page can be accessed from
+http://tools.zooniverse.org/\#/dashboards/spacewarp}.
+
+We made color composite images using the publicly-available
+code HumVI\footnote{The open source  color image composition code used in this
 work is available from \texttt{http://github.com/drphilmarshall/HumVI}}
-following the prescription of \citet{Lupton2004}. Specifically, we first
-rescale the pixel values of each channel image into flux units, and
-then apply an arcsinh stretch. The stretch parameters are chosen
+following the prescription of \citet{Lupton2004}. The code
+rescales the pixel values of each channel image into flux units, and
+then applies an arcsinh stretch. The stretch parameters are chosen
 using a small random sample of images, to ensure that the background
 noise is just visible, and that the centres of bright, intermediate
-resdhift galaxies are not saturated. The color scales are chosen to
+redshift galaxies are not saturated. The color scales are chosen to
 maximize the contrast between faint extended objects. These parameters
@@
 overlapping region of 10\arcsec (54 pixels) between the neighbouring
-cutouts resulting into $\sim$ 430 000 cutouts for the entire \cfhtls
-\textsc{wide}. The size of the individual cutout is determined by
+cutouts. This  results in a catalog of $\sim$ 430 000 cutouts for the entire \cfhtls
+\textsc{wide} region. The size of the individual cutout is determined by
 optimising factors such as the typical angular scales of gravitational
@@
 number of images. This is not a problem since our user base is extremely
-large and we receive multiple classifications of the same cutout.
+large and we receive multiple classifications for the same cutout.
 
@@
 
-At galaxy-scales, we focus on two primary lens searches. The \rf
-\citep{Gavazzi2014} was used for finding compact rings or arcs around centers
-of isolated and massive early-type galaxies. By subtracting the PSF-matched
-$i$-band images from the $g$-band images, the algorithm looks for excess flux
-in the bluer $g$-band. An object detector measures the properties of these
-residual blue features, and candidates meeting length-width ratio and
-tangential alignment criteria are then visually inspected to form the final
-sample. \citet{Gavazzi2014} first selected some 638,000 targets as either
-photometrically-classified early type galaxies, or objects selected to have
-red centers and blue outer parts, from the T06 CFHTLS data release catalogs. 
-14370 were found to show detectable blue residuals, and 2524 were visually
-inspected, having passed the automatic feature selection process. This led to
-a sample of 42 good quality (\texttt{q\_flag} = 3) and 288 medium quality
-(\texttt{q\_flag} = 2) lens candidates. In addition to this well defined
-sample, \citet{Gavazzi2014} reported a further 71 serendipitously detected
-lens candidates.  From this sample of ``\rf candidates,'' the SL2S team
-found, during their follow-up campaign, 39 confirmed lenses (and 17 promising
-candidates). We use this sample of 39 ``confirmed \rf lenses'' in our
-completeness analysis.
-
-The second galaxy-scale lens search was to find edge-on galaxy lenses in
-the \cfhtls \citep{Sygnet2010} by selecting the galaxy's profile from the
-output of {\sc Sextractor} in the $i$~band and with low inclination
-angle. This sample has about 3 promising and a total of 18 lens
-candidates.
-
-On the other hand, the \af \citet{More2012} was used for
-finding blue arc-like features in the complete \cfhtls data withouth any
-pre-selection on the type of the lensing object. The search was carried
-out in the g-band which is the most efficient wavelength to find typical
-lensing galaxies. This sample, called the SARCS, has 55 promising and a
-total of 127 lens candidates and consists of both galaxy and
-groups/cluster scale lens candidates. Arc finding is better suited for
-lensed images or arcs with larger image separations i.e. more massive
-systems like groups and clusters. Thus, the SARCS sample has mostly
-groups/cluster-scale lenses and a few galaxy-scale lenses.
-
-For the purposes of transparency and to help a little with their training, 
+At galaxy-scales, two primary lens searches have been carried out in
+\cfhtls. The \rf \citep{Gavazzi2014} was used for finding compact rings
+or arcs around centers of isolated and massive early-type galaxies. The
+\rf subtracts the PSF-matched $i$-band images from the $g$-band images,
+and looks for excess flux in the bluer $g$-band. An object detector
+measures the properties of these residual blue features, and candidates
+which meet the length-width ratio and tangential alignment criteria are
+then visually inspected to form the final sample. \citet{Gavazzi2014}
+pre-selected $\sim$638,000 targets as either photometrically-classified
+early type galaxies, or objects selected to have red centers and blue
+outer parts, from the T06 CFHTLS data release catalogs.  14370 were
+found to show detectable blue residuals, and 2524 were visually
+inspected, having passed the automatic feature selection process. This
+led to a total of 330 lens candidates out of which 42 are good quality
+(\texttt{q\_flag} = 3) and 288 are medium quality (\texttt{q\_flag} = 2)
+candidates. In addition to this well defined sample, \citet{Gavazzi2014}
+reported a further 71 serendipitously detected lens candidates.  From
+this sample of ``\rf candidates,'' the SL2S team found, during their
+follow-up campaign, 33 confirmed lenses (and 17 promising candidates).
+{\bf AM: check if any of these are from \cfhtls DEEP?}
+
+The second galaxy-scale lens search was to find edge-on galaxy lenses in the
+\cfhtls \citep{Sygnet2010} by selecting galaxies based on profile fits in the
+$i$-band performed using {\sc Sextractor} and with low inclination angle. This
+sample has about 3 promising and a total of 18 lens candidates.
+{\bf AM: perhaps, this should go in additional samples because this was not
+used as one of the known samples,check ?}
+
+Lastly, the \af \citep{More2012} was used for finding blue arc-like features in
+the complete \cfhtls data without any pre-selection on the type of the lensing
+object. The algorithm measures the second order moments of the flux distribution
+in pixels within small regions to estimate the direction and extent of local
+elongation of features. Pixels with high values of elongation are connected to
+form an arc candidate. Finally, a set of thresholds on arc properties such as
+the area, length, width, curvature and surface brightness are used to select
+arc-like candidates. The search was carried out in the g-band which is the most
+efficient wavelength to find typical lensed features.  This sample, called
+SARCS, has 55 promising and a total of 127 lens candidates which are selected
+from both \cfhtls WIDE and DEEP fields. The SARCS sample consists of some
+galaxy-scale candidates and mostly groups/cluster scale lens candidates. This is
+because more massive systems produce arcs or lensed images with large image
+separation from the lensing galaxy which are easier to detect compared to the
+galaxy-scales.  In the absence of a large systematically followed up
+verification of the candidates, we use the  most promising sample of 26 lens
+candidates as the bonafide known lens sample. And, the sample of 108 candidates
+form the known lens candidates which come from the \cfhtls WIDE alone since the
+\sw lens search is carried out on the WIDE imaging only.
+
+For the purposes of transparency and to help with the training, 
 the volunteers participating in \sw-\cfhtls lens search were made aware of
@@
 were labelled as ``Known Lens Candidates'' in the Talk forum, where volunteers
-have the opportunity to discuss their findings with other volunteers and the
-science team.
+have the opportunity to discuss their findings with fellow volunteers and the
+science team. In this paper, we refer to the sample of 330 \rf and 108
+\af lens candidates as the sample of ``known lens candidates'' and the sample of
+confirmed (or most promising) 33 \rf and 26 \af as the sample of
+``known lenses''.
+
+\question{AM}{AV, add info on other lens samples from the literature?}
 
@@
 
-{\it State the importance}
+In this section, we describe the framework to generate the simulated lens sample
+and give details of the sample itself along with some known limitations. This
+simulated lens sample is an important component for analyzing the
+classifications performed by the citizen scientists.
 
@@
 
-We create two main types of simulated lens sample a) galaxy-scale lenses and b)
-group or cluster-scale lenses. The galaxy-scale lenses are further divided into two
-types based on the nature of the background sources, namely, galaxies and
-quasars. Below, we describe how each type of the lens sample was generated.
+For the purpose of generating simulated gravitational systems, we divide the
+lenses in to two main categories a) galaxy scale lenses b) and group or
+cluster-scale lenses. We further subdivide galaxy scale lenses based on the
+type of the background sources, namely galaxies and quasars. We do not simulate
+group scale quasar lenses as they are expected to be extremely rare. We now
+describe our procedure to generate these different types of lens systems.
 
@@
 
-The $N_{\rm src}$ behind a lens is then calculated by doing the
-following integral,
-
+We begin by considering all elliptical galaxies at $z<1$ in our parent \cfhtls
+catalog as potential lens candidates for the simulated sample. To avoid using a
+known lens galaxy for our simulation purpose, we exclude all those galaxies
+whose positions match with the lensing galaxies from the known \cfhtls~SL2S lens
+samples \cite{More2012} within 2~arcsec (XXX check).
+
+For each galaxy, the average number of source objects (either quasars or
+galaxies) above a minimum luminosity $L_{\rm min}$ in the background that may get lensed
+can be calculated as
 \be
 \label{eqn:nsrc}
-N_{\rm src} = N_{\rm src}(>L_s,z_s) \int_{z_l}^\infty \sigma_{\rm lens}(\sigma,z_l,z_s,q) D_s^2 (1+z_s)^2 \frac{\rm d\chi}{{\rm d}z_s}
+N_{\rm src} = \int_{z_l}^\infty n_{\rm src}(>L_{\rm min},z_s)  \sigma_{\rm
+lens}(\sigma_v,z_l,z_s,q) \frac{\rm d V}{{\rm d}z_s}
 {\rm d}z_s 
 \ee
-
+where
 \be
 \label{eqn:nlum}
- N_{\rm src}(>L_s,z_s)= \int_{L_{min}}^\infty \Phi(L_s,z_s) {\rm d}L_s
+n_{\rm src}(>L_{min},z_s)= \int_{L_{\rm min}}^\infty \Phi(L',z_s) {\rm d}L'
 \ee
-
-where $\Phi(L_s,z_s)$ is the source luminosity function per unit comoving
-volume, $q$ is the projected axis ratio of the lens ellipticity, $\chi$ and
-$D_s$ are the comoving and angular diameter distances to the source,
-
-We use the elliptical galaxy (LRG) catalog from the \cfhtls XXX to select
-all the foreground galaxies (e.g. $z<1$) that are potential lenses for the
-simulated sample. We exclude all those galaxies whose positions match with the
-lensing galaxies from the known \cfhtls~SL2S lens samples \cite{More2012}
-within 2~arcsec (XXX check).
-
-First, we calculate the luminosity and velocity dispersion of each potential
-lensing galaxy using the CFHT Megacam $g$ and $r$ band magnitudes along with the
-photometric redshift ($z_l$) from the LRG catalog.  The Megacam magnitudes are
-converted to SDSS magnitudes\footnote{
-    http://www3.cadc-ccda.hia-iha.nrc-cnrc.gc.ca/megapipe/docs/filters.html} and
-are further k-corrected to redshift $z=0.1$ \citep{Frei1994}. We assume that the
-evolution of galaxy luminosities is similar to that determined by
-\citep{Faber2007}, that is, a decline of $1.5$ in the $m_{r*}$ from redshift $z=1$
-to $z=0$ (see Eq.~\ref{magstar}).
-
-\be
-\frac{L}{L_{*}}=10.0^{-0.4~(m_{r \rm SDSS}-m_{r*})} 
-\ee
-
-where $m_{r*}$ is
-\be
-\label{magstar}
-m_{r*}=-20.44+ 1.5~(z_{l}-0.1) \,.
-\ee
-
-We use the $L-\sigma$ relation from
-\citep{Parker2005} to get the velocity dispersion as given in Eq.~\ref{magstar2}.
-
+Here, $\Phi(L',z_s)$ denotes the source luminosity function per unit comoving
+volume, $\sigma_{\rm lens}$ denotes the angular lens cross-section, which depends upon
+the lens redshift ($z_l$), source redshift ($z_s$), the lens velocity
+dispersion $\sigma_v$ as well as the projected axis ratio of the lens
+ellipticity, $q$.
+
+In order to calculate the lensing cross-section, we first calculate the
+luminosity of each potential lensing galaxy using the photometric redshifts
+($z_l$) from the LRG catalog. We use the $L-\sigma$ scaling relation from the
+bright sample of \citep{Parker2007} to set the velocity dispersion of the halo
+hosting the galaxy which will be later used in the model
 \be
 \label{magstar2}
-\sigma=142 \left(\frac{L}{L_{*}}\right)^{1/3} 
+\sigma_v=142 \left(\frac{L}{L_{*}}\right)^{1/3} \,.
 \ee
-
-Next, in order to decide whether a galaxy is likely to act as a strong lens, we
-calculate the lens cross-section ($\sigma_{\rm lens}$) and the number of sources
-($N_{\rm src}$) that are in the background. Following \citep{Keeton2000a}, the lens
-cross-section is calculated analytically for an isothermal model and is given by
-
+We assume that the knee of the luminosity function of galaxies, $L_*$ evolves
+such that there is a decline of $1.5$ magnitudes between $z=1$ to $z=0$
+\citep{Faber2007}.\footnote{We anchor our $L_*$ evolution at low redshifts using the
+determination of $L_*$ in the r-band by \citet{Blanton:2001}. To maintain
+consistency in magnitude systems, we have converted the CFHT MegaCAM magnitudes
+to SDSS magnitudes and k-corrected them to $z=0.1$.}
+
+%first calculate the
+%luminosity and velocity dispersion of each potential lensing galaxy using the
+%CFHT Megacam $g$ and $r$ band magnitudes along with the photometric redshift
+%($z_l$) from the LRG catalog.  The Megacam magnitudes are converted to SDSS
+%magnitudes\footnote{
+%http://www3.cadc-ccda.hia-iha.nrc-cnrc.gc.ca/megapipe/docs/filters.html} and are
+%further k-corrected to redshift $z=0.1$ \citep{Frei1994}. We assume that the
+%evolution of galaxy luminosities is similar to that determined by
+%\citep{Faber2007}, that is, a decline of $1.5$ in the $m_{r*}$ from redshift
+%$z=1$ to $z=0$ (see Eq.~\ref{magstar}).
+
+%\be
+%\frac{L}{L_{*}}=10.0^{-0.4~(m_{r \rm SDSS}-m_{r*})} 
+%\ee
+%
+%where $m_{r*}$ is
+%\be
+%\label{magstar}
+%m_{r*}=-20.44+ 1.5~(z_{l}-0.1) \,.
+%\ee
+%
+%We use the $L-\sigma$ relation from
+%\citep{Parker2005} to get the velocity dispersion as given in Eq.~\ref{magstar2}.
+
+%\be
+%\label{magstar2}
+%\sigma=142 \left(\frac{L}{L_{*}}\right)^{1/3} 
+%\ee
+
+We assume a singular isothermal ellipsoid model for each of our galaxies
+\citep{Kormann1994}, such that the convergence is given by
 \be
-\sigma_{\rm lens}=b_I^2 \, \int_0^{2\pi} 0.5 r^2(\theta) d\theta
+\kappa (x,y) = \frac{b \sqrt{q}}{2}\frac{1}{\left( \theta_1^2 + q^2\theta_2^2\right)^2}
 \ee
-
-where $b_I$ is 
+Here b is called the Einstein radius, and its dependence on the velocity
+dispersion of the SIE is given by
 \be
-b_I = b_{\rm SIS} \epsilon_3/sin^{-1}(\epsilon_3) \,,
+b = 4\pi\,
+\left(\frac{\sigma_v^2}{c^2}\right)\left(\frac{D_{ls}}{D_{s}}\right) \,.
 \ee
-
-the eccentricity ($\epsilon_3$) is 
+The SIE model results in a caustic and a pseudo-caustic on the source plane:
+which demarcate the regions of different image multiplicities. Parametric
+solutions, $r(\theta)$ (where $\theta$ is the polar angle), for the caustics in
+such a model were given by \citet{Keeton2000b}. We use these parametric
+solutions to obtain the area of the lensing cross-section, $\sigma$, for every
+galaxy,
 \be
-\epsilon_3=(1-q_3^2)^{1/2}
+\sigma_{\rm lens}=\frac{b^2 q}{2} \, \int_0^{2\pi} r^2(\theta) d\theta\,.
 \ee
-
-and the projected axis ratio is given by
-\be
-q_k=\sqrt{q_3^2 {\rm sin}^2i_e+{\rm cos}^2i_e} \,.
-\ee
-
-In the above equations, $q_3$ is the 3d axis ratio of the ellipsoid and $i_e$ is
-the inclination angle. Also, $b_{\rm SIS}= 4\pi
-\frac{c^2}{\sigma^2}\frac{D_{s}}{D_{ls}D_l}$ and is referred to as the
-Einstein radius where $D_s$,$D_l$ and $D_{ls}$ are angular diameter distances to
-the source, the lens and between the lens and source, respectively.
-
-%Comparing \citep{keeton00a} with \citep{kormann94} suggests that $b_I = sqrt(q)*b_{SIS}$
-
-Next, if the foreground galaxy can act as a lens and has at least one source in the
-background, then we determine a redshift ($z_s$) and $i$-band magnitude of the
-background source(s). We assume two types of background sources namely, galaxies
-and quasars. For each source, the redshift and magnitude are generated by drawing randomly from
-the following redshift and luminosity distributions. For
-galaxies, we assume the redshift distribution is
-
+At every polar angle we use the maximum of the radial and tangential caustic for
+the purpose of calculating the cross-section.
+
+%where
+%\be
+%b_I =  \sqrt{q}\, 4\pi\,
+%\left(\frac{\sigma_v^2}{c^2}\right)\left(\frac{D_{ls}}{D_{s}}\right)\,.
+%\ee
+%Here $D_s$ and $D_{ls}$ are angular diameter distances to
+%the source, and between the lens and source, respectively.
+
+%Next, if the foreground galaxy can act as a lens and has at least one source in the
+%background, then we determine a redshift ($z_s$) and $i$-band magnitude of the
+%background source(s). We assume two types of background sources namely, galaxies
+%and quasars. For each source, the redshift and magnitude are generated by drawing randomly from
+%the following redshift and luminosity distributions. For
+%galaxies, we assume the redshift distribution is
+
+We use the results of \citet{Faure2009} to specify the source luminosity
+function of galaxies. We assume that the redshift distribution of sources is
+given by
 \be
@@
 \ee
-
-where $\beta=3/2$ and $z_0(m_{\rm lim})=0.13m_{\rm lim} - 2.2$ and the
-luminosity function is
-
+where $\beta=3/2$ and $z_0(m_{\rm lim})=0.13m_{\rm lim} - 2.2$ and the source
+counts as a function of the limiting magnitude are given by
 \be
@@
 n_s=\int^{m_{\rm lim}}_{-\infty} \frac{n_0 {\rm d}m}{\sqrt{10^{2a(m_1-m)}+10^{2b(m_1-m)}}}
+\,,
 \ee
-
-with parameters $a=0.30$, $b=0.56$, $m_1=20$ and $n_0=3\times10^3~deg^{-2}$ as
-given in \citep{Faure2009} and references therein. For quasars, we calculate
-the luminosity function by following the prescription of \citep{Ogur2010} and
-use k-corrections by \citep{Richards2006}.
-
+with parameters $a=0.30$, $b=0.56$, $m_1=20$ and $n_0=3\times10^3~deg^{-2}$.
+
+For quasars, we assume the luminosity function prescription of \citep{Ogur2010}
+and adopt k-corrections by \citep{Richards2006}. 
 %alp=-0.5;
@@
 \ee
-
 where the normalization, $\phi_{*}=5.34\times10^{-6} h^3$ Mpc$^{-3}$ and break
@@
 dependent factor in $M_*$ is given by
-
 \be
@@
 higher redshifts, as prescribed by \citep{Oguri2010}. 
-respectively. We note that when calculating $N_{\rm src}$, the source
-number density is artificially boosted by a factor (see Table~\ref{tab:thresh})
-to increase the occurrence of simulated lenses. This helps in creating a large
-enough sample to carry out various performance tests.
+respectively.
+
+With the cross-section, and the luminosity functions specified, we calculate the
+expected number of sources behind a candidate galaxy using Equation
+\ref{eqn:nsrc}. We need to generate a large number of simulated lenses (larger
+than the number of real galaxy lenses we expect to find in CFHTLS) in order to
+use it as a training sample as well as for calibrating the performance of our
+citizen scientists (see Paper I). Therefore, we artificially boost the average
+number of sources by a factor (see Table~\ref{tab:thresh}, which increases the
+occurrence of lensing. We draw a Poisson deviate with a mean equal to the
+boosted average number of sources. If the Poisson deviate is greater than zero,
+then we mark this galaxy to act as a lens galaxy. We then draw the properties of
+the lensed source based on the redshift and the luminosity distribution of the
+sources. The source positions with respect to the lens are drawn randomly from
+an area inside the caustic.
 
 Next, we determine properties of the background source for every lens. We follow
-similar procedures for both background galaxies and quasars. For simplicity, we
-simulate a single background source behind every lens. In order to select one
-background source from the $N_{\rm src}$ per lens, we do ray-tracing for all of the
-$N_{\rm src}$ sources with {\sc gravlens} \citep{Keeton2000} and choose sources that
-satisfy criteria as given below. We determine fluxes of the lensed images
-and the total magnification of each of the lensed source. We draw a random
-source for which the flux of the second brightest lensed image and the total
-magnification of all lensed images are above the thresholds given in
-Table~\ref{tab:thresh}.
+similar procedures for both background galaxies and quasars. We perform
+ray-tracing for all of the $N_{\rm src}$ sources using the publicly available
+code {\sc gravlens} \citep{Keeton2000} and choose sources that satisfy our
+selection criteria. We determine fluxes of the lensed images and the total
+magnification of each of the lensed source. We draw a random source for which
+the flux of the second brightest lensed image and the total magnification of all
+lensed images are above the thresholds given in Table~\ref{tab:thresh}.
 
 Since we want to produce realistic looking lens systems, we simulate lenses in
-each of the five \cfhtls~filters. The colors of the background galaxies are drawn
+each of the five \cfhtls~filters. The colors of the background source galaxies are drawn
 randomly from the photometric CFHTLenS catalog
@@
 radius of the galaxy is estimated from the Luminosity$-$size relation
-\citep{Bernardi2003} given by 
+\citep{Bernardi2003} (with a redshift scaling to account for some size
+evolution) given by 
 \be
@@
 
-Once all the parameters are determined for the lens and source models, {\sc
-gravlens} is used to simulate lensed images.  After accounting for the shot
+Once all the parameters are determined for the lens and source models, we once
+again use {\sc gravlens} to generate simulated lensed images.  After accounting for the shot
 noise in the lensed images and convolving them with the median seeing in each of
@@
 and a total (NFW+Hernquist) model at groups-scales taken from \citep{More2012}.
+%{\bf fix the normalization}
 }
@@
 
-At group or cluster-scales, the brightest group galaxy (BGG) at the center alone
-does not cause strong lensing. We need to account for the extra convergence
-arising from the dark matter component as well as satellite galaxies, at least,
-in the inner regions which are typically responsible for the multiple lensed
-images \citep{Oguri2005,Oguri2006}. Owing to the lack of an appropriate group
-catalog for our purposes, we create a basic group catalog based on the
-magnitudes and photometric redshifts available for the \cfhtls. We select all
-galaxies with 10$^{10.8} M_\odot$ as the BGGs. We select the member galaxies
-such that their photometric redshifts are within $\delta z = 0.01$ of the BGG
-and within an aperture of $250$~Kpc.
+At group or cluster-scales, the mass distribution is more complex. The
+convergence in the inner regions, which are typically responsible for the
+multiple lensed images, arises from not only the brightest group galaxy (BGG) at
+the center, but also has contribution from the dark matter component as well as
+the satellite galaxies \citep{Oguri2005,Oguri2006}. We generate a basic group
+catalog based on the magnitudes and photometric redshifts available for the
+\cfhtls. We select all galaxies with 10$^{10.8} M_\odot$ as plausible BGGs. We
+select the member galaxies such that their photometric redshifts are within
+$\delta z = 0.01$ of the BGG and within an aperture of $250$~Kpc. If another BGG
+is found with the aperture, then the fainter BGG is removed from our list of
+BGGs.
 
@@
 Distributions of properties of the lensing galaxies of the simulated
-sample compared to the known lens sample SARCS XXXX check? 
+sample compared to the known lens sample SARCS. 
+%(XXXX confirm what's being plotted? which band - i?) 
 }
@@
 
-We adopt an isothermal ellipsoid for the BGG and members whenever the
-ellipticities are available else we use an isothermal sphere. On the other hand, we
-adopt an NFW profile for the underlying dark matter halo. Assuming a constant
-mass-to-light ratio of $3 \times 0.7$~h~$M_{*}/L_{*}$, we use the BGG luminosity
-to estimate the stellar mass. The stellar mass$-$halo mass relation
-\citep{behroozi13}, including random scatter, is then used to calculate the halo
-mass for the lens. Given the halo mass, other key parameters such as the scale
-radius ($r_s$) and the density at the scale radius ($\rho_s$) can be determined for an
-NFW profile.
-
-As described in Section~\ref{sect:gallens}, we calculate the luminosity and
-velocity dispersion for the BGG and each of the member galaxies. Next, we
-calculate the lens cross-section for each potential lensing group. The
-complexity in the lens models makes it analytically intractable to calculate the
-size of the caustics\footnote{The lens mass distribution determines size and
-shape of the caustics. Any source located within the caustics will form multiple
-lensed images which is the criteria for strong lensing. To further
-understand caustics, see XXX.}.  Hence, we use {\sc
-gravlens} to determine the area covered by the caustics. We consider only
-galaxies as our background source population since group or cluster-scale quasar
-lenses are not expected to be found in the \cfhtls (check XXX).  Following the same
-procedure as described in Section~\ref{sect:gallens}, we calculate the number of
-galaxies expected to lie behind every potential lensing group (see
-Eq.~\ref{eqn:nsrc}). As before, for each background galaxy within the lens cross-section, a
-redshift and an $i$-band magnitude is determined by drawing galaxies randomly
-from the respective distributions (see Eqs.~\ref{eqn:ps}-\ref{eqn:ns}).
+We assume a constant mass-to-light ratio of $3 \times 0.7$~h~$M_{*}/L_{*}$, to
+convert the BGG luminosity to a stellar mass estimate. The stellar mass$-$halo
+mass relation \citep{behroozi13}, including random scatter, is then used to
+calculate the halo mass for the lens. We adopt an NFW density profile for the
+underlying dark matter halo. Given the halo mass, other key parameters such as
+the scale radius ($r_s$) and the density at the scale radius ($\rho_s$) can be
+determined for an NFW profile. In addition, we adopt an isothermal ellipsoid
+model for the BGG and members whenever the ellipticities are available from the
+galaxy catalog (else we use an isothermal sphere).
+
+We calculate the luminosity and velocity dispersion for the BGG and each of the
+member galaxies following the same prescription as in
+Section~\ref{sect:gallens}. To calculate the average number of sources that get
+lensed by such a system, we need to calculate the lensing cross-section for each
+of these potential lensing groups. The complexity in the lens models makes it
+analytically intractable to calculate the size of the caustics\footnote{The lens
+        mass distribution determines size and shape of the caustics. Any source
+located within the caustics will form multiple lensed images which is the
+criteria for strong lensing. To further understand caustics, see XXX.}.
+Therefore, we generate the caustics numerically using {\sc gravlens} and then
+determine the area covered by the caustics. We consider only galaxies as our
+background source population since group or cluster-scale quasar lenses are not
+expected to be extremely rare in the \cfhtls (check XXX).  Following the same procedure
+as described in Section~\ref{sect:gallens}, we calculate the number of galaxies
+expected to lie behind every potential lensing group (see Eq.~\ref{eqn:nsrc}).
+As before, for each background galaxy within the lens cross-section, a redshift
+and an $i$-band magnitude is determined by drawing galaxies randomly from the
+respective distributions (see Eqs.~\ref{eqn:ps}-\ref{eqn:ns}).
 
@@
 of the lensed galaxies for every lens as are described for galaxy-galaxy lenses
-in the previous section. The simulated images are added to the real \cfhtls~images
-with the BGGs as the center.
+in the previous section. The simulated lensed images are then added on top of
+the real \cfhtls~images with the BGGs as the center.
 
@@
 
-The \Fref{fig:remudist} shows Einstein radius distribution for the
+\Fref{fig:remudist} shows the Einstein radius distribution for the
 galaxy-scale (dashed for background quasars and dotted for background galaxies)
@@
 
-We show the redshift and magnitude distributions of the lensing galaxies in the
-left and right panels of \Fref{fig:lensprop}
-respectively. Furthermore, we overplot the distributions of respective
-properties of the SARCS lenses from \citep{More2012} for comparison with arbitrary
-normalizations. We note qualitative similarities between the simulated and the
-real lens samples.
-
-Similarly, we show the ellipticity and the position angle of the simulated lens
-galaxy population extracted from the T0007 release of the \cfhtls~catalogs in the
-left and right panels of \Fref{fig:lensprop}, respectively. As before, the
-dashed-dotted (blue) curves show the same distribution for the SARCS lens
-population with arbitrary normalization \citep{More2012}.
+We show the redshift, magnitude and ellipticity distributions of the lensing
+galaxies in the three panels of \Fref{fig:lensprop}, respectively. We also show
+the distributions of respective properties of the SARCS lenses from
+\citep{More2012} for comparison with arbitrary normalizations. We note the
+qualitative similarities between the simulated and the real lens samples.
+
+%Similarly, we show the ellipticity and the position angle of the simulated lens
+%galaxy population extracted from the T0007 release of the \cfhtls~catalogs in the
+%left and right panels of \Fref{fig:lensprop}, respectively. As before, the
+%dashed-dotted (blue) curves show the same distribution for the SARCS lens
+%population with arbitrary normalization \citep{More2012}.
 
@@
 We produce catalogs with lens and source properties for each of the three types
-of lenses. These catalogs are available XXX. The catalogs typically have lens
+of lenses. These catalogs are available from
+https://github.com/anupreeta27/SIMCT. The catalogs typically have lens
 position, redshift, magnitudes, Einstein radius, ellipticity (whenever
@@
 sources, we provide the offset from the lens center, redshift, magnitudes,
-total magnification, number of lensed images. Additionally, ellipticity and
-effective radius when the background sources are galaxies.
+total magnification, number of lensed images. Additionally, when possible,
+ellipticity and effective radius of the background galaxies have also been
+provided.
 
@@
 \subsection{Limitations of the simulated sample}
-The simulated sample is not perfect because our understanding of various
-phenomena in the Universe is not complete and because of the uncertainties in
-the parameters of our model. Here, we describe some of the cases or
-aspects in which the simulations are known to have failed or seem
-unrealistic.
+The simulated lens sample, although realistic, is not perfect, due to the
+simplicity of the lensing models and our limited understanding of the
+uncertainties in the parameters for the models. Comments from citizen
+scientists were very helpful in order to sort some of these failures. Here, we
+describe some of the cases or aspects in which the simulations were known to
+have failed (or appeared unrealistic). This typically happens for a small
+fraction of the simulated images (roughly 5 percent of
+the cases)\footnote{Based on the hashtag simfail in the discussion forum Talk.}.
 
@@
 survey. For galaxy-scale lenses, the lensing galaxies at higher redshifts or
-which are fainter have poor photometric measurements. This causes relatively
-larger uncertainties in its luminosity and velocity dispersion and leads to
-simulated lenses which look implausible. For example, due to a larger
-uncertainty in the velocity dispersion of the lensing galaxy, the lensed images
-may have larger image separation than what is expected given the visual priors
-from the galaxy.
-
-At group-scales, the photometric and redshift estimates are used when
-defining the group membership. Therefore, errors in redshift estimates generate
-galaxy groups with BGG or member galaxies with dissimilar properties. In some
-cases, low redshift spiral galaxies are incorrectly assigned high redshift.
+which are fainter have poor photometric redshift measurements. Consequently
+these galaxies are assigned a wrong luminosity and velocity dispersion
+estimates, which sometimes result in simulated lenses which look implausible.
+For example, the lensed images for some of the failed simulations have larger
+image separation than expected given the visual priors from the galaxy.
+
+At group-scales, the photometric and redshift estimates are used when define
+the group membership. Therefore, errors in redshift estimates generate galaxy
+groups with BGG or member galaxies with dissimilar properties. In some cases,
+low redshift spiral galaxies have been incorrectly assigned high redshift.
 Spiral galaxies are typically less massive and low redshift spiral galaxies are
-unlikely to act as gravitational lenses. Hence, the resulting simulated lenses
-are not convincing.
-
-We use single Sersic component to describe the light profiles of background
-galaxies. This is clearly not the most accurate description for galaxies,
-especially, star-forming galaxies which form a significant fraction of the
-lensed galaxy population. Star-forming galaxies have complex structures such as
-star forming knots, spiral arms, bars and disks. 
+unlikely to act as gravitational lenses. Hence, some of the simulated lenses
+were not as convincing.
+
+We also use a single Sersic component to describe the light profiles of
+background galaxies. This is clearly not the most accurate description for
+galaxies, especially, star-forming galaxies which form a significant fraction
+of the lensed galaxy population. Star-forming galaxies have complex structures
+such as star forming knots, spiral arms, bars and disks. The simulated lensed
+images do not display these features.
+
 %magdiff=5*0.1;
@@
 
-A good training sample consists of a representative set of objects that
-one wants to find and another set of objects which appear to be from the
-former set but are of different origin in reality and which one can
-learn to discard efficiently. Indeed, we wanted to have a good training
-sample for the \sw users so that they can correctly identify the true
-lens candidates. Hence, in addition to the simulated lenses, we
-added a sample of duds and false positives to the training sample. Duds
-are images which have been visually inspected by experts and confirmed
-to contain no lenses.  False positives (FPs) are systems which look like
-lenses but are not, for example, spiral galaxies, starforming galaxies,
-chance alignments of features arranged in a lensing configuration and
-stars.
+Citizen scientists not only need training to identify gravitational lenses, but
+also to reject images which either contain impostors or have no lenses. Hence,
+in addition to the simulated lenses, we added a sample of duds and false
+positives to the training sample. Duds are images which have been visually
+inspected by experts and confirmed to contain no lenses.  False positives (FPs)
+are systems which look like lenses but are not, for example, spiral galaxies,
+starforming galaxies, chance alignments of features arranged in a lensing
+configuration and stars.
 
 We selected a sample of 450 duds for the Stage I classification in \sw
-and a sample of 500 false positives for the Stage II
-inspection. The sample of false positives was selected from
-the candidates which passed the Stage I of \sw. We note that this is the
-first time, we have a systematically compiled sample of visually
-inspected false positives by the \sw users and categorized by the
-science team. Such a sample is tremendously helpful for training and
-understanding performances of various lens finding algorithms
-\citep{Chan2014}. {\bf TBA data products; make the duds and FP sample available}
+and a sample of 500 false positives for the Stage II inspection. The
+sample of false positives was selected from the candidates which passed
+the Stage I of \sw. We note that this is the first time, we have a
+systematically compiled sample of visually inspected false positives by
+the \sw volunteers and categorized by the science team. The data products are
+available at http://spacewarps.org/\#/projects/CFHTLS/. Such a sample is
+tremendously helpful for training and understanding performances of
+various lens finding algorithms \citep{Chan2014}.
 
@@
 \begin{center}
-\includegraphics[scale=1.0]{sw-cfhtls-figs/poffl_expr_ncl.pdf}
-\caption{ \label{fig:exp_pn} Comparison of the P(lens) with the expert
-grades and number of classification for each subject.  }
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.6]{sw-cfhtls-figs/cand_fp_P.pdf}
-\caption{ \label{fig:stackP} Total number of detections of the known
-candidates, new candidates and the FPs shown relatively for binned
-values of P.
-}
+\includegraphics[scale=0.6]{sw-cfhtls-figs/cand_fp_P_frac.pdf}
+\caption{ \label{fig:stackP}  
+Distribution of different types of candidates as a function of the posterior
+probability P. The types of the candidates are the FPs, the new candidates and
+the known candidates. The new and known candidates have higher detection rate
+for higher values of P, as expected.}
 \end{center}
@@
 
+\question{AM}{PJM,AV, 1. Any preference for which of the following words should be
+used? My preference: volunteers (most of the times) and citizen scientists (some
+times because it suits the context better)
+2. Add anything else to this section?}
+{\bf AM: Check and homogenize use of the words citizen scientists, citizens, users,
+volunteers throughout the text.}
+
 \section{Results}
@@
 
-The \sw works as a single unified neural network which uses the method
-of visual inspection to find gravitational lenses. The citizens are
-shown images at two stages. At stage I, citizens focus on rapid
-inspection and selection of lens candiates ranging from possible lenses
-to almost certain lenses. At stage II, citizens carefully inspect the
-candidates from stage I and select promising lens candidates only. The
-science team consisting of lens experts then categorize and grade the
-lens candidates further purifying the sample of lens candidates. In
-Table~\ref{tab:stats}, we list the total number of detections of the
-known lens candidates, known confirmed lenses and the new lens
-candidates at both stages I and II. The known sample corresponds to the
-combined Ring Finder and Arc Finder samples. We also show their
-fractions with respect to the total number of lens candidates found at
-these stages. We note that all the confirmed lenses found at stage I are
-also recovered at stage II whereas a small fraction of the known lens
-candidates are rejected at stage II. Also, the new lens candidates
-increases the known lens candidates sample by over 50\%.
-
-Below, we describe the steps taken after stage II for selecting the
-final sample of lens candidates.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
-\subsubsection{Selection of the \sw lens candidates}
-\label{sec:results:stage1}
-The images inspected in \sw are assigned probabilities (P) through the
-\sw Analysis Pipeline (SWAP), built in the \sw system (see Paper I).
-In an ideal situation, at the end of stage II, all images containing
-lenses would have high P values and those without lenses will have low P
-values. However, practically, a fraction of the real lenses will be
-assigned low P value decreasing the completeness and a fraction of non-lenses
-will be assigned high P value decreasing the purity. Our goal is to find
-a P value which will result in acceptable levels of completeness and
+The \sw works as a single unified neural network which uses the method of visual
+inspection to find gravitational lenses. The volunteers are shown images at two
+stages. At stage I, volunteers are requested to undertake a rapid inspection to
+select lens candiates ranging from possible lenses to almost certain lenses. At
+stage II, volunteers carefully inspect the candidates from stage I and select only
+promising lens candidates. A daily snapshot of classifications performed by
+volunteers are provided to the science team every night. This daily batch is
+analyzed by the Space Warps Analysis Pipeline (SWAP). The philosophy and the
+details of SWAP are described in detail in Paper I, here we briefly summarize
+how it works.
+
+Each subject (or image cutout) is assigned a prior probability of $2\times10^{-4}$ to
+contain a lens system. Every volunteer or classifier is assigned a $2\times2$
+confusion matrix, which quantifies the volunteer's ability to correctly classify
+an image to contain ($P_L$) or not contain a lens system ($P_D$). The values of
+the confusion matrix are determined based on the performance of the volunteer on
+the training sample, specifically, $P_L$ (and $P_D$) is determined based on the
+fraction of simulated lenses (and duds) correctly classified. After every
+classification, the prior probability of the classified subject is updated
+based on the classification and the volunteer's confusion matrix, according to the
+Bayes theorem.  The volunteer's confusion matrix is updated after the classification
+of every training image. Threshold values for the probabilities to accept (or
+reject) a subject  if it contains (or doesn not contain) a lens can be
+chosen in SWAP. Those images which cross these threshold values are retired and
+are not subsequently shown to the volunteers, so that volunteers can use their
+time efficiently to classify previously unclassified subjects.
+
+SWAP was run nightly during Stage I in order to retire subjects and inject new
+ones in to the classification stream. The subjects that passed the acceptance
+threshold at the end of Stage I are served again at Stage II for careful
+reinspection. Each subject, after Stage II, has an associated posterior
+probability P. In the ideal case, all images containing lenses will have high P
+values and those without lenses will have low P values. In practice, we expect a
+small fraction of the real lenses (or non-lenses) to be assigned low (or high) P
+values and thus, decreasing the completeness (or purity) of the final lens
+sample.  As this is the first candidate search with \sw, we want to find a
+threshold P value which will result in acceptable levels of completeness and
 purity of the final sample of lens candidates.
 
-As this is the first \sw lens search, we explore a large range in the P
-value to understand the balance between the real lens candidates and
-false positives. In \Fref{fig:exp_pn}, we plot the distribution of
-false positives and real lens candidates categorized by the lens experts
-as a function of their P value. As expected, the fraction of real lens
-candidates is higher for higher P values and it decreases for lower P
-values. We note that from P$\sim$0.7 onwards to lower P values, the fraction of
-false positives starts to exceed the fraction of real lens candidates.
-This could be a good threshold to choose to maximize the purity of the final
-sample. However, we choose P$>$0.3 as our threshold to increase the
-completeness of our sample. We achieve further purity by including the
-grades of the lens experts.
+We decide to inspect top few hundreds of subjects from a catalog of descending P
+values as a reasonable sample size for visual inspection. We find 665 subjects
+with P$>0.3$ in the catalog. These subjects are then visually inspected by three
+lens experts (AM, AV, PJM). The subjects are assigned grades on a scale of 0 to
+3, thus dividing the subjects into candidates that almost certainly do not
+contain a lens, possibly a lens, probably a lens and almost certainly a lens,
+respectively. We find XXX candidates with averaged grade $0<$G$<1.3$ (low
+probability sample) and XXX candidates with G$\ge1.3$ (high probability sample).
+Further information on the low probability sample such as their positions and
+images are available at XXX. Among the high probability sample, there are XXX
+known candidates and XXX new candidates. To avoid duplicity, further information
+on the \sw detected known candidates sample is available at XXX whereas the new
+lens candidate sample is presented below in \Sref{sec:results:newcand}.
+
+In Table~\ref{tab:stats}, we give overall statistics of the systems detected at
+stage I and stage II. We give the total number of detections of the known lens
+candidates, known lenses and the new lens candidates at each stage.  We also
+show their fractions with respect to the total number of lens candidates found
+at these stages. We note that most (XXX check) of the confirmed lenses found at
+stage I are also recovered at stage II whereas a small fraction of the known
+lens candidates are rejected at stage II. Also, the sample of new lens
+candidates increases the sample of \cfhtls lens candidates by over 50\%.
+
+In \Fref{fig:stackP}, we plot the distribution of false positives and the high
+probability lens candidates, categorized by the lens experts, as a function of
+the P value assigned by SWAP at the end of Stage II. On average, the fraction of
+lens candidates is indeed an increasing function of P. This shows that the \sw
+generated P values for the subject are roughly correlated with the expert grades
+albeit with quite some scatter.  We note that from P$\sim$0.75 onwards to lower
+P values, the fraction of false positives starts to exceed the fraction of real
+lens candidates. This could be a good threshold to choose to maximize the purity
+of the final sample. However, the choice of P$=$0.3 as the threshold gives a
+more acceptable completeness of XXX for our sample which combined with expert
+grading allows us to achieve further purity of our sample.
+{\bf AM: give some numbers for the completeness/purity ?}
 
@@
 {KC}-- Known lens candidates \\
-{KL}-- Known confirmed lenses \\
+{KL}-- Known lenses \\
 {NC}-- New lens candidates  \\
@@
 \subsubsection{New lens candidates from \sw}
-\label{sec:results:disc}
-
-All images with P$>$0.3, at the end of stage II, are inspected by three
-lens experts (AM, AV, PJM) and are assigned integral grades from 0,1,2
-or 3 which imply that the candidate is almost certainly not a lens,
-possibly a lens, probably a lens and almost certainly a lens,
-respectively. This process led to a final sample of 61 new lens
-candidates with averaged grade $\ge$1.3 (see Table~\ref{tab:swcands})
-and are shown in \Fref{fig:lc}. For this final sample, we give a \sw ID
-and Name of the lens system, Ra, Dec, photometric redshift ($z_{phot}$),
-$i$ band magnitude of the lensing galaxy, averaged grade from the lens
-experts, zoo ID (identifier used in
-TALK\footnote{http://talk.spacewarps.org/}, the discussion forum for
-\sw), P value at stage II and a visual categorization of type of lensed
-images and the lensing galaxy in the Comments column in
-Table~\ref{tab:swcands}. Whenever available the lens properties are
-taken from the \cfhtls photometric catalog \citep{Coupon2009} otherwise
-the reported lens galaxy positions are measured visually. The visual
-categorization of the lens type is only suggestive and the explanation
-of the notations in the Comments column is given at the bottom of the
-table.
-
-As the first lens search was a blind search with no preselection of
-candidates using any algorithm, we expected to find various types of
-lenses and this is indeed what we find. The final sample consists of
-both galaxy and groups-scale lens candidates. There are detections of
-elongated arcs and point-like quasar lensed images. Most of them are
-brighter in bluer $g$ band but some candidates brighter in the redder
-$i$ band are also found.
-
-{\bf CHECK FOR STAGE 1 -- COMPLETENESS OF SIMS AND KNOWN LENSES
-and P value comparison, what about the duplicate lenses near the borders
-- stats on those?  check the detection plot of arc mag / Reinst and find out why some of
-the bins have unexpected results}
+\label{sec:results:newcand}
+
+We give details of the final sample of 61 new lens candidates found by \sw in
+Table~\ref{tab:swcands}. We report the candidates with a \sw ID and Name of the
+lens system. We give their positions (Ra, Dec), photometric redshift
+($z_{phot}$), $i$ band magnitude of the lensing galaxy, averaged grade G from
+the lens experts, zoo ID (identifier used in
+TALK\footnote{http://talk.spacewarps.org/}, the discussion forum for \sw), P
+value at stage II and a visual categorization of type of lensed images and the
+lensing galaxy in the Comments column in Table~\ref{tab:swcands}. Whenever
+available the lens properties are taken from the \cfhtls photometric catalog
+\citep{Coupon2009} otherwise the reported lens galaxy positions are measured
+manually. The visual categorization of the lens type is only suggestive and the
+explanation of the notations in the Comments column is given at the bottom of
+the table.
+
+We show images of our new sample in \Fref{fig:lc} which is arranged first in the
+decreasing order of their grades and then increasing order of their positions.
+As the first lens search was a blind search with no preselection of candidates
+using any algorithm, we find various types of lenses, as expected of such a
+search. The final sample consists of both galaxy and groups-scale lens
+candidates. There are detections of elongated arcs and some interesting
+point-like quasar lensed images (there have been no previously known quasar
+lenses in CFHTLS). {\bf AM: Check literature and then comment about this in the
+abstract?} Most of them are brighter in bluer $g$ band but some candidates
+brighter in the redder $i$ band were also found. Since robotic lens searches
+often look for blue colored lensed features, they are very much likely to miss
+such interesting lens candidates.
+
+%{\bf CHECK FOR STAGE 1 -- COMPLETENESS OF KNOWN LENSES
+%and P value comparison, what about the duplicate lenses near the borders
+%- stats on those?  check the detection plot of arc mag / Reinst and find out why some of
+%the bins have unexpected results. check arc mag vs. reinst plot and
+%understand why some of the very faint/low reinst sw detections are and
+%if it all makes sense.}
 
@@
 \caption{ \label{fig:lc}
-Sample of lens candidates with G$>=$1.3.
+The new \sw lens candidates with expert grade G$>=$1.3. The images are
+30\arcsec on the side. 
 }
@@
 
-\subsection{Measurements of lens and arc properties}
+\subsection{Measurements of properties of the lens and the lensed images}
 \label{sec:results:meas}
 
-In the subsequent sections, we make comparison of various properties of
-the lens candidates. Here, we describe how we measured those properties,
-namely, the lens redshift, the Einstein radii and the total flux of the
+In the subsequent sections, we make comparison of various properties of the lens
+candidates. In this section, we describe how we extract these properties, namely,
+the lens redshift, the Einstein radii and the total flux of the lensed images or
 arcs.
@@
 We use the publicly available redshifts for the lens galaxy from the
-\cfhtls photometric catalogs \citep{Coupon2009}. The definition of the
-Einstein radius is different in different cases. For the galaxy-scale
-lenses in the simulated sample, we use the value of the input lens model
-parameter for the $R_{\rm E}$. For groups-scale lenses, since the lens
-model is multi-component, we need to determine the $R_{\rm E}$ from the
-image positions. We use half of the averaged image separations of the
-lensed image counterparts with minimum and maximum image separations.
-For the \rf sample, the arcs are detected in the scaled difference image
-between $g$ and $i$ bands where the lensing galaxy is subtracted
-\citep[for details, see]{Gavazzi2014}. We use the peak position of the
-lensed images measured by running {\sc sextractor} on this difference
-image and identified visually. We calculate the image separation from
-the lens center as an estimate of the $R_{\rm E}$. For the \af (SARCS)
+\cfhtls photometric catalogs \citep{Coupon2009}. The total flux of the
+lensed image or arc is measured in the $g$ band but the adopted method
+is different for different samples. For the simulated sample, we
+multiply the magnification of the second brightest image with the source
+magnitude. For the \rf sample, the arcs are detected in the scaled
+difference image between $g$ and $i$ bands where the lensing galaxy is
+subtracted \citep[for details, see]{Gavazzi2014}. Here, we use the flux
+of the lensed images measured by {\sc sextractor} from the scaled
+difference image, that is, $g-\alpha i$ and convert it to the $g$ band
+flux using mean colors of the foreground and background population. For
+the \af and the \sw sample, we integrate the flux in the image pixels
+identified by \af or {\sc sextractor}.
+
+The Einstein radius ($R_{\rm E}$) is also measured differently for
+different samples. For the galaxy-scale lenses in the simulated sample,
+we use the value of the input lens model parameter for the $R_{\rm E}$.
+For groups-scale lenses, since the lens model is multi-component, we
+need to determine the $R_{\rm E}$ from the image positions. We use those
+pairs of lensed images that have the smallest and the largest angular
+separations. The $R_{\rm E}$ here is then half of the averaged values of
+these angular image separations.  For the \rf sample, we use the peak
+position of the lensed images measured by running {\sc sextractor} on
+the scaled difference image. We calculate the image separation from the
+lens center as an estimate of the $R_{\rm E}$. For the \af (SARCS)
 sample, we use the same definition as above except that the peak
-position is identified either by the \af or visually. For the \sw lens
+position is identified either by the \af or manually. For the \sw lens
 sample, the same definition is used where the peak positions are
@@
 
-The total flux of the arc is measured in the $g$ band. For the simulated
-sample, we multiply the magnification of the second brightest image with
-the source magnitude. For the \rf sample, we use the flux of the lensed
-images measured by {\sc sextractor} from the scaled difference image,
-that is, $g-\alpha i$ and convert it to the $g$ band flux using mean
-colors of the foreground and background population. For the \af and the
-\sw sample, we integrate the flux in the image pixels identified by \af
-or {\sc sextractor}.
-
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 
-We determine what fraction of the known sample of lenses are recovered by \sw. In
-Table~\ref{tab:stats}, we show that $\sim$~25\%-30\% of the known
-candidates and $\sim$~60\% of the known confirmed lenses are found at
-stages I and II in \sw. The left and the middle panels of
-\Fref{fig:compre} show the fraction of detections as a function of arc
-magnitude and the Einstein radius of the lens systems. As expected, we
-find that systems with brighter images and/or with larger Einstein radii
-are detected more often in \sw.
-
-We find that most of the confirmed lenses and candidates that are missed by \sw
-are systems with fainter arcs and smaller Einstein radii and they come
-from the \rf sample. The main reason why \rf found such
-candidates is because their team used lensing
-galaxy-subtracted images to detect the presence of the lensed images
-both during the automated object-finding phase and during the visual
-inspection and classification of their candidates. This approach
-naturally improves the detection efficiency at smaller Einstein radii
-and for fainter systems. The \sw volunteers were not shown any
-galaxy-subtracted images. However, in light of the improved detection
-efficiency, this might be a better strategy to adopt for future lens
-searches at galaxy-scales with \sw. In the Discussion \Sref{sec:fn}, we
-further explore and discuss why the confirmed lenses may have been
-missed in \sw.
+We determine what fraction of the known sample of lenses are recovered
+by \sw. In Table~\ref{tab:stats}, we show that $\sim$~25\%-30\% of the
+known candidates and $\sim$~60\% of the known lenses are found at stages
+I and II in \sw. The left and the middle panels of \Fref{fig:compre}
+show the fraction of detections as a function of arc magnitude and the
+Einstein radius of the lens systems for the known confirmed lenses and
+lens candidates. As expected, we find that systems with brighter images
+and/or with larger Einstein radii are detected more often in \sw.
+
+We find that most of the confirmed lenses and candidates that are missed
+by \sw are systems with fainter arcs and smaller Einstein radii and they
+come from the \rf sample. The main reason why \rf found such candidates
+is because their team used lensing galaxy-subtracted images to detect
+the presence of the lensed images both during the automated
+object-finding phase and during the visual inspection and classification
+of their candidates. This approach naturally improves the detection
+efficiency at smaller Einstein radii and for fainter systems. The \sw
+volunteers were not shown any galaxy-subtracted images. However, showing
+galaxy subtracted images might be a better strategy to adopt for future
+lens searches at galaxy-scales with \sw. In the Discussion
+\Sref{sec:fn}, we further explore and discuss why some of the confirmed
+lenses are missed by \sw.
 
@@
 \includegraphics[scale=1.0]{sw-cfhtls-figs/comp_reinst_mag.pdf}
-\caption{ \label{fig:compre} Fraction of lens candidates detected by \sw
-as a function of the arc magnitude ($g$ band) and the Einstein radius for
-three lens samples, namely, simulated lenses, known confirmed lenses and
-the lens candidates sample. }
+\caption{ \label{fig:compre} Fraction of lens candidates detected by \sw as a
+function of the arc magnitude ($g$ band) and the Einstein radius for three lens
+samples, namely, the known lenses, the known lens candidates and the simulated
+sample. }
 \end{center}
@@
 can be used to probe the average density profile of the lens population
-\citep{Oguri2006,More2012}.  However, the lens sample found
-by the Arc Finder may have incompleteness as a function of the image
-separation. Thus, the lack of understanding of the selection function of
-the lens sample may affect the constraints on the density profile.  A
-blind lens search done by visual inspection alone e.g. by \sw may find
-lenses missed by the Arc Finder search and thereby, improve
-completeness. Furthermore, the completeness of the lens sample found by \sw is
-characterised with the help of the simulated sample. For example, in the
-right most panel of \Fref{fig:compre}, we plot the completeness of the
-simulated sample found at stage I of \sw as a function of the arc
-magnitude and Einstein radius. We find that the sample is more than 80\%
-complete between image separations 2"-10".
-
-In \Fref{fig:isd}, we plot theoretical curves for the image
-separationd distribution corresponding to three density profiles,
-namely, isothermal sphere (IS), NFW \citep{Navarro1997} and Total profile which has
-NFW and Hernquist profiles combined with an adiabatically contracting model for
-dark matter component \citep{Gnedin2004} taken from \citet{More2012}.
+\citep{Oguri2006,More2012}.  However, the lens sample found by the \af
+may have incompleteness as a function of the image separation. Thus, the
+lack of understanding of the selection function of the lens sample may
+affect the constraints on the density profile. A blind lens search done
+by visual inspection alone e.g. through \sw citizen scientists may find
+lenses missed by the \af search and thereby, improve completeness.
+
+Indeed, we have find several new lens candidates that were not known
+before. In \Fref{fig:isd}, we show the image separation distribution for
+the known sample (green), for the \sw identified (known and new) lens
+sample (blue) only and combined known with the new \sw lens sample
+(magenta). It is interesting to note that both these samples have very
+similar profiles and thus, the profile of the combined sample has not
+changed much. This implies that previous constraints on the image
+separation distribution are robust and the \af selected sample does not
+suffer from significant incompleteness for medium to large Einstein
+radii. This is the regime that probes density profiles of galaxy groups
+to clusters.
+
+In the figure, we also show for comparison the theoretical predictions
+corresponding to three density profiles, namely, isothermal sphere (IS),
+NFW \citep{Navarro1997} and Total profile which has NFW and Hernquist
+profiles combined with an adiabatically contracting model for dark
+matter component \citep{Gnedin2004}. These curves are taken from
+\citet{More2012} which gives details of the calculation of these
+predictions.  With the updated sample of lens candidates, we confirm our
+previous prediction that the mass density profiles of galaxy groups is
+indeed similar to the Total profile.
+
+%Lastly, we attempt to characterize the completeness of the \sw lens
+%sample based on the simulated lens sample. The right most panel of
+%\Fref{fig:compre} shows the completeness of the simulated sample
+%at stage I of \sw as a function of the arc magnitude and Einstein
+%radius. We find that the lens sample is more than XXX\% complete between image
+%separations 2"-10".
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=1.2]{sw-cfhtls-figs/isd_cfhtls_sw.pdf}
+\caption{ \label{fig:isd} Image separation distribution. Comparing theoretical
+predictions (solid curves) with the \cfhtls known lens samples (green)
+and the combined sample of known and \sw lens candidates (magenta). The
+sample of new and the known lens candidates discovered from \sw alone is
+shown in blue. The new updated profile of the isd (magenta) is
+consistent with our previous measurements and strengthens our conclusion
+that the average density profiles of the lenses are similar to the Total
+profile.}
+\end{center}
+\end{figure}
 
@@
 method is perfect. Each method has some advantages over the other. It
-may be the case that a single method may not be the best means for
+may be the case that a single method may never be the best method for
 optimising completeness and purity. Visual inspection will likely be
@@
 
-In this section, we attempt to understand and compare the lens
-(candidates) that are found by the lens finding robots and missed by humans
-and vice versa.
+In this section, we first compare the lens candidates found by
+\sw and the lens finding robots and then attemp to understand why each
+method failed to detect lenses from the other sample.
+
+\subsection{Comparison of the \rf, \sw and \af samples}
+Here, we compare the properties of the lens candidates from each sample
+to understand if there are any clear differences between them. We
+consider the lens redshift, the total flux of the lensed images and the
+Einstein radii of the systems for this purpose.
+
+In \Fref{fig:zlmgre}, we show the lens redshift and the arc flux
+measured in $g$ AB mag as a function of the Einstein radius for the \rf
+(green), the \af (red) and the \sw sample (new candidates only in blue
+and known candidates as black circles). We note that the errors on the
+redshift measurement should not be too different across the samples
+since they are measured by a single method. However, the error on the
+total flux of the lensed images are likely to be different across the
+samples and the types of systematics are also different.  We have not
+attempted to quantify these errors in this work. With that caveat, we
+find that the \sw candidates sample is broadly similar to the
+robotically found lens candidates in terms of the flux of the lensed
+images or the redshift of the lensing galaxies.
+
+Since \sw is visual based search, it is difficult to detect many lens
+candidates with small $R_{\rm E}$ in the presence of a bright lensing
+galaxy. While this is true for algorithms too, the \rf team adopted a
+different method to circumvent this problem whose goal was to find
+galaxy-scale lenses which have small $R_{\rm E}$. The \rf sample is
+generated by working with lensing galaxy $-$subtracted images and this
+led to increased detections of small image separation candidates. The
+\sw lens search did not show any galaxy subtracted images and hence,
+this results in a quantitative difference between the \sw and the \rf
+sample as a function of $R_{\rm E}$.
+
+The \af, on the other hand, is capable of finding smaller image
+separation lenses but a lower limit on $R_{\rm E}$ was imposed by the
+\af team to simplify the selection function of their sample. Thus, we
+can compare the \sw and \af samples at about $R_{\rm E}>2\arcsec$. There
+is a good overlap between the two samples given that most of these are
+candidates and could turn out be not lenses. We again caution the
+readers that the uncertainties on the measurements are not quantified
+and may change the results to some extent.
+
+The properties considered here do not show any clear differences between
+the types of lenses being found by each method. Other properties such as
+the flux of the lensing galaxies and the surface brightness of the
+lensed images may be useful in showing some qualitative differences but
+this is beyond the scope of our current analysis. A more detailed and
+accurate analysis is deferred to the future.
+%{\bf check out of the 55 promising \af how many are missed by \sw ?}
+
+Lastly, in \Fref{fig:stackremg}, we show the relative distribution of
+number of candidates from each sample as a function of the Einstein
+radius and arc magnitude. The light blue color shows the overlap between
+the \sw and the \rf samples and the purple color shows the overlap
+between the \sw candidates and the \af samples. As noted earlier, the
+\rf dominates the small $R_{\rm E} (<2\arcsec)$ range although \sw does
+find modest number of candidates in this range. At larger $R_{\rm E}$,
+\sw sample begins to dominate and is comparable to the \af sample.  As a
+function of the arc magnitudes, all three samples have detections at all
+magnitudes and median magnitudes for all samples is around 24.5.
+Relatively, the \rf sample spans a narrower range compared to the \sw
+and \af sample. However, this can be verified only after understanding
+and accounting for the systematic uncertainties in our measurements.
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.65]{sw-cfhtls-figs/zl_mg_re.pdf}
+\caption{ \label{fig:zlmgre}
+Comparison of the lens redshift and the arc magnitude with the
+Einstein radius for all of the three lens samples, namely, the \rf (green dots),
+\sw (known candidates$-$black circles and new candidates only$-$blue dots)
+and \af (red dots). Alls samples have broadly similar properties.}
+\end{center}
+\end{figure}
 
@@
 some of them do not look like E/S0 type galaxies and some are edge on
-galaxies. {\bf there are a few which look regular galaxies so which
-criteria are they failing??}
-
+galaxies.
+
+%{\bf can we say something qualitatively for why these were missed? there are a few which look regular galaxies so which criteria are they failing??} 
 %% 13 are under mask so no photoz, 10 have photoz (z>0.2 except for 1).
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.5]{sw-cfhtls-figs/stacked_lenscand_rein.pdf}
+\includegraphics[scale=0.5]{sw-cfhtls-figs/stacked_lenscand_mag.pdf}
+\caption{ \label{fig:stackremg}
+Candidate detections by the \rf, \sw and the \af as a
+function of the Einstein radius and $g$ band magnitude of the lensed
+images. 
+%(XXXX check how different are the estimates from the different measurement techniques for a given lens candidates.) 
+}
+\end{center}
+\end{figure*}
 
@@
 of the thresholds in the code because of the change in the noise level.
-{\bf does this make sense?}
+%{\bf does this make sense?}
 
@@
 estimator is assigned to every pixel. All pixels with a value of the
-estimator above a certain threshold are connected to form the arc
+elongation stimator above a certain threshold are connected to form the arc
 feature. This is building of the arc candidate. Subsequently, arc
@@
 
-{\bf TBD: 
-comment on any lensed quasars, on any exotic lenses;
-of course, there must be lenses which cannot be detected currently by
-either robots/humans
-check if some candidates were detected because they were hidden
-underneath the sims ie. from the D11;
-}
+%{\bf TBD: 
+%comment on any lensed quasars, on any exotic lenses;
+%of course, there must be lenses which cannot be detected currently by
+%either robots/humans
+%check if some candidates were detected because they were hidden
+%underneath the sims ie. from the D11;
+%}
 
@@
 Like any lens finding method, the \sw system can fail to detect certain
-kinds of lenses. Here, we explore and discuss why some of the known
-lenses may have been missed.
-
-We find that about 40\% of the known confirmed sample of lenses are
-missed (see \Tref{tab:stats}). While this seems like a fraction, we note
-that many of the missed lenses are from the \rf sample with small
+kinds of lenses.  We find that about 40\% of the known sample of lenses
+are missed both at stage I and II (see \Tref{tab:stats}). In fact, most
+of the known lenses from stage I are discovered at stage II suggesting
+that most lenses are lost right at stage I. Below, we focus on the known
+lens sample at stage I to understand why some of them are being missed
+and possibly find a way to improve the detection rate which can be
+adopted in the future \sw lens searches.
+
+Many of the missed lenses are from the \rf sample with small
 Einstein radii and faint lensed images (see \Fref{fig:compre}). Among
@@
 For a lens finding method which uses collective skill, experience and
-knowledge of a group of citizens, it may be difficult to find a single
+knowledge of a group of volunteers, it may be difficult to find a single
 factor with certainty which causes a lens candidate to be missed. We
@@
 
-First, we check if the Nclass is different for the detected and the
-missed sample. Surprisingly, most of the lenses in the known sample have
-few classifications (Nclass$<$10) which includes both the detected and
-missed lenses. Many of the remaining have between 10 to 20
-classifications. And, only a few subjects have Nclass$>$20 which continue
-to remain for long in the database because these candidates may have
-been difficult to identify.
-
-%{\bf Let us compare the two samples to see if there are any obvious differences.
+\subsubsection{Number of classifications}
+First, we check if the number of classifications (Nclass) is
+significantly lower for the missed sample compared to the detected one.
+Surprisingly, most of the lenses in the known sample have few
+classifications (Nclass$<$10) which includes both the detected and
+missed lenses. Many of the remaining lenses have between 10 to 20
+classifications. And, only a few subjects have Nclass$>$20. They
+continue to remain for long in the database because these candidates are
+possibly difficult to identify. Therefore, the distribution of Nclass
+can not be the reason for losing the lenses from the missed sample.
+
+%{ Let us compare the two samples to see if there are any obvious differences.
 only 2 out of this sample of 18 were detected at stage I (reached high P even with fewer classifications) and missed at stage II (P value was low even after recieving very many classifications).
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.65]{sw-cfhtls-figs/zl_mg_re.pdf}
-\caption{ \label{fig:zlre}
-Comparison of the lens redshift and of the arc magnitude with the
-Einstein radius for all of the three lens samples, namely, from the \rf (green dots),
-\sw (all candidates black circles and new candidates only in blue dots)
-and \af (red dots). }
-\end{center}
-\end{figure}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=0.5]{sw-cfhtls-figs/stacked_lenscand_rein.pdf}
-\includegraphics[scale=0.5]{sw-cfhtls-figs/stacked_lenscand_mag.pdf}
-\caption{ \label{fig:stackre}
-Candidate detections by the \rf, \sw and the \af as a
-function of the Einstein radius and $g$ band magnitude of the lensed
-images. (XXXX check how different are the estimates from the different
-measurement techniques for a given lens candidates.) }
-\end{center}
-\end{figure*}
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=1.2]{sw-cfhtls-figs/isd_cfhtls_sw.pdf}
-\caption{ \label{fig:isd} Image separation distribution. Comparing
-theoretical predictions (solid curves) with the \cfhtls known lens
-samples (REF , green points) and the same \cfhtls sample after combining
-with the incremental lens sample from \sw (magenta points). The \sw only
-sample including new and known lens candidates are shown with blue
-points. }
-\end{center}
-\end{figure}
-
 \subsubsection{Blind lens search}
@@
 candidates close to the borders could go undetected. Therefore, it is
-essential to test and understand if \sw tends to miss certain lenses
+essential to test and understand if \sw is missing some of the known lenses
 because they happen to be close to the borders of the image cutouts.
@@
 a status of detected (if P$>$P$_{\rm acc thresh}$), rejected (if
-P$<$P$_{\rm rej thresh}$) and undecided (if P$_{\rm rej thresh}<$ P
-$<$ P$_{\rm acc thresh}$). In \Fref{fig:comppos}, we compare the
-positions of simulated lenses which are detected (red), undecided
-(green) and rejected (blue). We also make the same comparison for the
-known lens candidates in the right panel.  We note that for some cases
-randomly selected subsamples are shown for the ease of visual
-comparison. For example, the absolute number of simulated lenses
-detected is too high compared to the rejected sample. We do not find any
-strong visual correlation in the rate of detections as a function of the
-position for both the simulated and the known lens sample. Thus, the
-completeness of the lens sample does not seem to be significantly
-affected by whether a lens is located close to the border or well within
-the center.
-
+P$<$P$_{\rm rej thresh}$) and undecided (if P$_{\rm rej thresh}<$ P $<$
+P$_{\rm acc thresh}$). In \Fref{fig:comppos}, we compare the positions
+of lenses which are detected (red), undecided (green) and rejected
+(blue). The left and the right panels have the simulated lens sample and
+the known lens candidates sample, respectively. We note that the density
+of points do not represent the actual number of detections because, for some
+cases, randomly selected subsamples are shown for the ease of visual
+comparison.
+
+We do not find any strong visual correlation in the detection rate of
+lenses as a function of their positions in the image for both the
+simulated and the known lens sample. Thus, the completeness of the lens
+sample is most likely not significantly affected by whether a lens is
+located close to the border or well within the center.
+
+%%{\bf plot the locations of detected and missed lenses explicitly to see the difference}
 \subsubsection{Volunteer profile}
@@
 
-We check how the posterior probability P (see XXXX Paper I) of an image
-or a subject to contain a lens changes as the image receives more
-classifications from multiple users.  In \Fref{fig:detmis}, we show the
-trajectory plots of a few examples of detected lenses (top left panels)
-and missed lenses (bottom left panels) by \sw at stage I. The number of
-classifications (Nclass) for a subject increase from top to bottom.
-Also, every subject is assigned a prior probability P0$=2\times10^{-4}$ (grey
-dashed line) and starts at the middle of the trajectory plot. The P
-value of a subject is updated with every classification from the
-volunteer.  If a volunteer identifies a lens candidate, the trajectory
-moves to the right otherwise moves to the left. A subject is accepted if it
-crosses the blue-dashed line marking the (P$_{\rm acc thresh}=0.95$) on
-the right and is rejected, if it crosses the red-dashed line marking the
-P$_{\rm rej thresh}=10^{-7}$ on the left.
+We check how the posterior probability P (see Paper I for the
+mathematical definition) of an image or a subject to contain a lens
+changes as the image receives more classifications from multiple
+volunteers.  In \Fref{fig:detmis}, we show the trajectory plots of a few
+examples of detected lenses (top left panels) and missed lenses (bottom
+left panels) by \sw at stage I. The number of classifications (Nclass)
+for a subject increase from top to bottom.  Also, every subject is
+assigned a prior probability P0$=2\times10^{-4}$ (grey dashed line) and
+starts at the middle of the trajectory plot. The P value of a subject is
+updated with every classification from the volunteer.  If a volunteer
+identifies a lens candidate, the trajectory moves to the right otherwise
+moves to the left. A subject is accepted if it crosses the blue-dashed
+line marking the (P$_{\rm acc thresh}=0.95$) on the right and is
+rejected, if it crosses the red-dashed line marking the P$_{\rm rej
+thresh}=10^{-7}$ on the left.
 
@@
 \caption{ \label{fig:comppos}
-Completeness as a function of position of lens systems. Simulated lenses
+Completeness as a function of the positions of the lens systems. Simulated lenses
 (left) and real lens candidates (right) are shown. Irrespective of the
 status of the lenses, that is, detected, undecided or rejected, there is
-no strong dependency on where the lenses are located both for the
-simulated and the real sample of lens candidates. }
+no strong dependency on the location of the lenses, both for the
+simulated and the real sample of candidates. }
+%{\bf check this for the known lens sample only}
 \end{center}
@@
 bottom-left: missed) at stage I and histogram of the known lenses for
-different types of volunteers (right).
+different types of volunteers (right). Among the sample of missed
+lenses, most classifications are from the less skilled volunteers
+identifying these images incorrectly (i.e. $-\Delta$~logP) which
+overshadows the small number of correct identifications (i.e.
+$\Delta$~logP) coming from both the less and the more skilled volunteers
+combined. For the detected lens sample, most classifications are correct
+identifications coming from both less and more skilled volunteers.
 }
@@
 The blind lens search in the \cfhtls is done in two stages: stage I and
-stage II. The aim of stage I is to do fast inspection of a large sample
-of $\sim$ 430 000 images and reduce them to a smaller sample of $\sim$
-3000 images with interesting lens candidates. The aim of stage II is to
-carefully reinspect the smaller pool of images to exclude as many FPs as
-possible and reduce the sample to $\sim$~500 candidates. In the next
-step, the images are graded by three lens experts (AM,AV and PJM)
-leaving in systems that are mildly interesting to very promising lens
-candidates.
+stage II. In stage I, volunteers inspected $\sim$ 430 000 subjects and
+selected a smaller sample of $\sim$ 3000 subjects with interesting lens
+candidates. In stage II, after a careful reinspection of the candidates
+from stage I, a smaller pool of more pure sample of $\sim$~500
+candidates is obtained. In the next step, the images are graded by three
+lens experts (AM, AV and PJM) producing candidates that range from
+mildly interesting to certainly a lens system.
 
@@
 We draw the following conclusions:
-
 \begin{itemize}
 
-\item Crowd-sourced gravitational lens detection works. We present a new
-sample of 61 gravitational lens candidates with average expert grade of
-1.3 and above where 1-mildly interesting, 2-probably, a lens and
-3-certainly, a lens.
+\item \sw works well as a discovery engine for gravitational lenses
+through citizen science. While a targeted visual search may be more
+efficient, we show that the blind search works reasonably well too.
+
+\item We present a sample of 61 {\bf new} gravitational lens candidates
+with average expert grade of 1.3 and above where 1-mildly interesting,
+2-probably, a lens and 3-certainly, a lens. Another sample of over 100
+lens candidates is recovered from previously known samples of lens
+candidates.
+%{\bf comment on duplicated lens candidates near the edges - what fraction of them are
+%detected}
 
@@
 lens candidates, the \sw sample finds lens systems with similar range in
-the lens redshift and the flux and the Einstein radii of the lensed
-images. However, the \sw search being a purely visual one cannot find
-some of the \rf-identified-lensed images with sub-arcsecond Einstein
-radii because the flux of the typically faint lensed images is obscured
-by the flux from bright lensing galaxies. The \rf finds these candidates
-because it works with lensing galaxy-subtracted images.
+the lens redshift and properties of the lensed images such as the total
+magnitude and the Einstein radii. However, the \sw search being a purely
+visual one cannot find some of the \rf-identified-lensed images with
+sub-arcsecond Einstein radii because the flux of the typically faint
+lensed images is obscured by the flux from bright lensing galaxies. The
+\rf finds these candidates because it works with lensing
+galaxy-subtracted images.
 
@@
 
-\item
+\item Based on the known sample of lenses and lens candidates, we find
+that we lose a very small fraction of them as we go from Stage I to
+Stage II. In other words, it is more important to improve the lens
+detection efficiency right at Stage I to increase the overall
+completeness of the final lens sample
+
+\item From the sample of known lenses, \sw missed about 40\% at Stage I.
+Among the missed sample of about 20 lenses, roughly half of them are
+visually difficult to identify because most of them are faint with small
+image separations which are identified through the \rf
+
+\item If we use the classifications from more skilled volunteers alone
+at Stage I, then we recover over 30\% of the lenses from the missed
+sample. Thus, it is possible to improve the completeness of lenses by
+changing the strategy of when and who is shown an image.
 
@@
 
+\question{AM}{PJM and AV, ideas/suggestions/comments on future steps or future lens
+searches?}
+
 \onecolumn
-
 \begin{center}
@@
 \twocolumn
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+The bottom panels show the missed or rejected lenses. The green (and red)
+trajectories show visually easier (and more difficult) to identify
+lenses. In spite of some mild qualitative differences, both set of
+trajectories have very similar behaviour. The trajectories in panel e
+are typical of this sample in terms of Nclass and the dominance of short
+negative kicks. The panel f represents a small fraction of this sample
+where the kics are only short and negative. The panel g shows how some
+lenses receive a bunch of large positive kicks which are led to
+rejection by still mostly negative short kicks. Finally, panel h shows
+those cases of lenses which received almost sufficient number of large
+positive kicks to be detected but ended up being rejected.
+
+The top panels show the detected lenses. The cases shown with green trajectories
+in each panel can be thought of counterparts of the trajectories of the missed
+lenses in the corresponding bottom panel except that the type of volunteers are
+different. Most detected lenses are similar to the case in panel a which are
+detected within a few classifications but coming from large positive kicks.
+Panel b represents a few odd cases which are dominated mainly by short positive
+kicks. Panel c shows a lens getting more classifications because of the tug
+between positive and negative kicks whereas the panel d represents the extreme
+cases when the subjects are on the verge of being rejected but are saved thanks
+to a series of large positive kicks. The red trajectories are some more
+examples of randomly selected cases which demonstrate how having sufficient
+number of large positive kicks allows lenses to be detected in spite of several
+short negative kicks.
+
 \section{Skill}
@@
 correctly identify a lens as a lens and P$_{\rm D}$, the probability to
-correctly identify a dud as a dud. The skill does not have simple
-dependency on P$_{\rm L}$ and P$_{\rm D}$. One can get the same value of
-skill for different combinations of P$_{\rm L}$ and P$_{\rm D}$.
+correctly identify a dud as a dud. The skill is not linearly related to
+ P$_{\rm L}$ and P$_{\rm D}$. One can get the same value of
+skill for different combinations of P$_{\rm L}$ and P$_{\rm D}$ (see
+Fig. XXX).
+
+\question{AM}{PJM, Is it useful to have this description, any other comments on
+this section?}
+{\bf AM: add figure and polish this further upon suggestion from PJM}
 
@@
 For lack of a better word, we also use the same term skill which has a
-similar meaning to that described in paper I but not identical. We use a
+similar meaning to that described in Paper I but not identical. We use a
 more qualitative definition implying the ability of the volunteers to
@@
 
+%{\bf todo: run swap and extract the status of all the known lens candidates
+%-- because the undecided are not known otherwise. fig will have to be
+%updated for the blind lens search section; also check what happened to
+%those AF lenses which were labelled sims - look at the D11 counterparts
+%and their status in stage 1 swap}
+
+%%{\bf there are 70 images which have both sims and known lenses. for
+%the sims ID, 69 det and 1 rej (nearly 100% detected) whereas the
+%corresponding test IDs 30det-30rej (nearly 50% detected and 50%lost)}
+
 %%%%%%%%%%%%%%
-XXXXX
 

### 2015-03-23 doc/sw-system.tex
Short speed section done. Closes #107

@@
 
-% How fast does the \sw crowd classify subjects? Each agent records the
-% timestamp of each classification its volunteer makes; by measuring the time
-% lags between successive classifications we can make estimates of each
-% volunteer's speed, and that of the crowd.
-%
-% A histogram of all time lags for all volunteers is shown in
-% \Fref{fig:crowd:timelags}, with those of the ``experienced volunteers''
-% (those who classified 10 or more training subjects.) overlaid.
-%
-% \todo{PJM}{Make this histogram, and try and infer the typical inter-session
-% lag.}
-%
-% Defining a new classification session to have started at least X minutes since
-% the previous classification, we assign all classifications into sessions, and
-% compute the mean intra-session time lag recorded by each agent. This gives
-% some measure of classification speed within a session; we also compute the
-% mean session length, and the rate of information contribution. The
-% latter is the most relevant measure of speed for future project design. The
-% distributions of these speeds are shown in \Fref{fig:crowd:speeddists}, in a corner
-% plot that also shows the effort and skill from \Fref{fig:crowd:cornerplot}. We
-% see that ...
-
-The overall contribution rate for the \sw crowd was found,
-and is plotted as a function of time in \Fref{fig:crowd:speed}. We see that
-...
-
-\todo{Phil, Chris}{Compute classification speeds, make plots, discuss. \#95}
+How fast does the \sw crowd classify subjects? Each agent records the timestamp
+of each classification its volunteer makes; by measuring the time lags between
+successive classifications we can make estimates of the crowd's classification
+and contribution speed. We plot these two quantities for both Stage 1 and Stage
+2 in \Fref{fig:results:speed}, normalizing the speed and time axes to the
+respective totals.
+The fractional classification rates in each stage of the survey fall off in approximately the same way, despite the factor of nearly 20 difference in crowd size.
+Stage 1 (consisting of $\sim430,000$ subjects) was completed in around 5000 hours (by some 37,000 participants), with classification rates in the first few days averaging at $\sim10^4$ per hour, stimulated by various forms of advertising (press releases, and emails to registered Zooniverse users).
+The asymptotic classification rate was $\sim10^3$ per hour.
+The average skill was found to be approximately constant over the lifetime of Stage 1, leading to a contribution rate that tracks closely the classification rate.
+(A 10\% increase in average skill was seen over the first 40 days, and a decrease of the same amount in the last 40 days -- not enough to cause a significant difference between classification and contribution rate behavior, but perhaps reflecting a learning period at the start and a decrease in participation late on.) Stage 2 (3700 subjects) was completed in around 600 hours by around 2000 participants, with classification rates starting at $~\sim2000$ per hour and decaying to $\sim100$ per hour.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering\includegraphics[width=\linewidth]{sw-system-figs/rate_classification.png}
+\caption{Fractional classification rate in the \SW CFHTLS survey.}
+\label{fig:results:speed}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The similarities between Stage 1 and 2, suggest that these numbers could be scaled to estimate the speed of future \SW projects (or at least those following a similar blind search strategy).
+For example, the completion time for a \SW project could be approximated as
+\begin{equation}
+    \tau \approx 18\,{\rm days} \left(\frac{10^4}{N_p}\right)
+                               \left(\frac{N_s}{10^4}\right),
+\end{equation}
+where $N_s$ is the number of subjects to be classified, and $N_p$ is the number of volunteers in the crowd.
 

### 2015-03-25 doc/sw-system.tex
Up to section 3... #96

@@
 The stage 1 training set was chosen to be quite clear cut, in order to err on
-the side of inclusivity, and so ensure high completeness. For the training
-duds we selected several hundred images at random, and three of us (AM, with AM and PM) inspected them and discarded anything that could be considered a lens candidate.
-
-% PJM IS HERE
+the side of inclusivity, and so ensure high completeness. For the training duds
+we selected several hundred images at random, and three of us (AM, with AV and
+PM) inspected them and discarded anything that could be considered a lens
+candidate: this meant that objects that looks similar to lenses, such as galaxy
+mergers, tidal tails and spiral arms, pairs of blue stars and so on, were
+specifically excluded from the training set, and so we expect some of those
+types of object to appear in the stage 1 candidate list. The training sims for
+stage 1 were also selected to be relatively straightforward to spot, as we sought a balance between sensitivity to faint or difficult lenses, and the need to educate the volunteers in what gravitational lenses look like.
+We return to this balance below.
 
@@
 
-At stage 2, the goal is to define a final sample that has both high
-completeness and high purity. To this end, a more demanding training set was
-defined, where the duds all contain an object identified by one of us (AV, AM
-and PM) as a potential false positive. \Fref{fig:training:gallery} shows some
-example images from the CFHTLS stage 2 training set.
+The design of the stage 1 classification task, and its training set, should lead
+to sample of lens candidates that has high completeness but may have low purity.
+To refine this sample to higher purity, we need to reject more non-lenses, which
+means providing the volunteers with a more realistic and challenging training
+set as they re-classify it. The more demanding stage 2 training set was
+generated as follows. The stage 2 duds were selected from the image pool by at
+least one of three of us  (AV, AM and PM) as being a potential false positive,
+while the stage 2 sims were chosen to be a subset of stage 1 sims, none of which
+were deemed ``obvious'' by the same expert classifiers.
+\Fref{fig:training:gallery} shows some example images from the resulting CFHTLS
+stage 2 training set.
 
@@
 \end{minipage} \hfill
-\caption{Typical \SW ``sims.'' Insets indicate the location of the simulated
-lens in each of these training
-images. Users needed to click on these specific features in order to make a
-correct classification.} \label{fig:training-gallery:sims}
+\caption{Typical \SW ``sims'' from the stage 2 training set. Insets indicate the
+location of the simulated lens in each of these training images. Users needed to
+click on these specific features in order to make a correct classification.}
+\label{fig:training-gallery:sims}
 \end{figure*}
@@
 \end{minipage} \hfill
-\caption{Typical \SW ``duds.''  All of these subjects were correctly
-classified by the community as not likely to contain gravitational lenses;
-the insets merely indicate regions where $\sim10\%$ of the volunteers
-clicked.} \label{fig:training-gallery:duds}
+\caption{Typical \SW ``duds'' from the stage 2 training set. All of these
+subjects were correctly classified by the community as not likely to contain
+gravitational lenses; the insets merely indicate regions where $\sim10\%$ of the
+volunteers clicked.} \label{fig:training-gallery:duds}
 \end{figure*}
@@
 The frequency with which training images were shown was fixed at 1 in 3.
-Finally, the Spotter's Guide was upgraded to include more detailed discussion
-of various possible false positives.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\todo{Phil}{write this section (\#31)}
+Finally, the Spotter's Guide was upgraded to include more examples
+of various possible false positives, divided into sub-classes.
+
+% PJM IS HERE
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-03-25 doc/sw-system.tex
Up to section 4 working through AV comments #96

@@
 a more advanced image viewer. This allows the viewer to compare three different
-contrast and color balance settings, to help bring out subtle features, and to
+contrast and colour balance settings, to help bring out subtle features, and to
 pan and zoom in on interesting regions of the image to assess small features.
@@
 provide for the volunteers in the next section.
+The FITS images of the subject can be further explored with Zooniverse ``Dashboard Tools,'' using a more powerful image viewer that enables dynamic variation of the colour balance and contrast (stretch), and for any given view to be shared via unique URL back to Talk.
 
@@
 
-% PJM IS HERE
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The CFHT Legacy Survey \citep[CFHTLS,][]{CFHTLS} covered XXX square degrees of
-approximately equatorial sky, in four patches distributed in right ascension,
-over the course of N years. With homegeneous image quality of, typically, X
-arcsec (in the $i$-band), and reaching limiting magnitudes of XX-XX in the
-$ugriz$ filter set, this survey has yielded several dozen new gravitational
-lenses on both galaxy and group scales \citep{}. The quality of the data,
-combined with the presence of these comparison ``known lens'' samples, made
-this a natural choice against which to develop and test the \sw system. The
-CFHTLS is also well-representative of the data quality expected from several
-next-generation sky surveys, such as DES, KiDS, HSC and LSST.
+The CFHT Legacy Survey \citep[CFHTLS,][]{CFHTLS} covered 171 square degrees of
+approximately equatorial sky, in four patches distributed in right ascension.
+With high and homogeneous image quality (the mean seeing in the $g$-band is
+0.78''), and reaching limiting magnitudes of around 25 across the $ugriz$ filter
+set, this survey has yielded several dozen new gravitational lenses on both
+galaxy and group scales
+\citep{GavazziEtal2014,SonnenfeldEtal13,CabanacEtal2007,MoreEtal2012}. The
+quality of the data, combined with the presence of these comparison ``known
+lens'' samples, makes this a natural choice against which to develop and test
+the \sw system. The CFHTLS is also well-representative of the data quality
+expected from several next-generation sky surveys, such as DES, KiDS, HSC and
+LSST.
 
@@
 mosaiced images into some 430,000 equal size, overlapping tiles, approximately
-70~arcsec on a side. Each of these images is a ``test image'' (as opposed to a
-``training image''). In future, larger area projects we expect to implement
-the rather different strategy of producing image tiles centred on particular
+70~arcsec on a side. We refer to these images as ``test images'' (as opposed to
+``training images''). In future, larger area projects we expect to implement the
+rather different strategy of producing image tiles centred on particular
 pre-selected ``targets,'' to make for a more efficient (but less complete)
 survey. We do not expect the performance of citizen image inspectors to change
-significantly between these strategies: to first order, both strategies
-require the inspectors to learn what lenses look like, and then search the
-presented images for similar features.
+significantly between these strategies: to first order, both strategies require
+the inspectors to learn what lenses look like, and then search the presented
+images for similar features.
 
@@
 The CFHTLS $g$, $r$ and $i$-band images have the greatest depth and best image
-quality, and we chose to focus on this set (although the $u$ and $z$-band
-images were also available for inspection in Talk). We made colour composite
-images using publically-available code\footnote{The open source  colour image
-composition code used in this work is available from
-\texttt{http://github.com/drphilmarshall/HumVI}} following the prescription of
-\citet{LuptonEtal}. Specifically, we first rescaled the pixel values of each
-channel image into flux units, and then applied an arcsinh stretch. The
-stretch parameters were chosen using a small random sample of images, to
-ensure that the background noise was just visible,  and that the centres of
-bright, intermediate resdhift galaxies were not saturated. The color scales
-were chosen to maximize the contrast between faint extended objects. These
-parameters were then fixed during the production of all the tiles, in order to
-allow straightforward comparison between one image and another, and for
-intuition to be built up about the appearance of stars and galaxies across the
-survey. Alternative algorithms, such as adjusting the stretch and scale
-dynamically according to, for example, the root-mean-square pixel value in
-each image, can lead to better presentation of bright objects, but in doing so
-they tend to hide the faint features in those images: we needed to optimize
-the detectability of these faint features.   Examples of CFHTLS training set
-images can be seen in \Fref{fig:training-gallery:duds} and
-\Fref{fig:training-gallery:sims}.
+quality, and we chose to focus on this set (although the $u$ and $z$-band images
+were also available for perusal in Talk). We made colour composite PNG format
+images\footnote{The open source colour image composition code used in this work
+is available from \texttt{http://github.com/drphilmarshall/HumVI}} following the
+prescription of \citet{LuptonEtal2004} \citep[with extensions
+by]{WherryEtal2004}. Specifically, we first rescaled the pixel values of each
+channel image into flux units, and then applied an arcsinh stretch. The stretch
+parameters were optimized by visually inspecting a small randomly-selected
+sample of images, to ensure that the background noise was just visible,  and
+that the centres of bright, intermediate redshift galaxies were not saturated.
+The color scales were chosen to maximize the contrast between faint extended
+objects. These parameters were then fixed during the production of all the
+tiles, in order to allow straightforward comparison between one image and
+another, and for intuition to be built up about the appearance of stars and
+galaxies across the survey. Alternative algorithms, such as adjusting the
+stretch and scale dynamically according to, for example, the root-mean-square
+pixel value in each image, can lead to better presentation of bright objects,
+but in doing so they tend to hide the faint features in those images: we needed
+to optimize the detectability of these faint features.   Examples of CFHTLS
+training set images prepared in this way can be seen in the galleries of the
+previous section (Figures~\ref{fig:training-gallery:sims}
+and~\ref{fig:training-gallery:duds}).
+We also defined two alternative sets of visualization parameters, to display a ``bluer'' image and a ``brighter'' image in the classification interface Quick Dashboard (\Sref{sec:design:interface}).
+The QD code performs the same image composition as just described, but dynamically on FITS images in the browser.
+These FITS images are also available for viewing in Talk, via the main Zooniverse Dashboard image display tool, which again offers the same stretch settings, as a starting point for image exploration.
+
+% PJM IS HERE.
 

### 2015-03-25 doc/sw-cfhtls.tex
Implemented \StageOne and \StageTwo macros, closes #109

@@
 %
-% Space Warps II: CFHTLS 
+% Space Warps Paper II: CFHTLS
 %
@@
 %
-%The classification of subjects happens in two serial stages. Stage I is
+%The classification of subjects happens in two serial stages. \StageOne is
 %for quick rejection of all uninteresting subjects. Subjects that passed
-%Stage I are then reinspected at Stage II, for a careful selection of
+%\StageOne are then reinspected at \StageTwo, for a careful selection of
 %most promising lens candidates. In general, subjects are assigned a
@@
 %database to ensure that rest of the subjects receive sufficient multiple
-%classifications. This is true for stage I with ~10$^5$ subjects but is
-%not required for stage II with only a few thousand subjects.
+%classifications. This is true for \StageOne with ~10$^5$ subjects but is
+%not required for \StageTwo with only a few thousand subjects.
 %
@@
 
-We selected a sample of 450 duds for the Stage I classification in \sw
-and a sample of 500 false positives for the Stage II inspection. The
+We selected a sample of 450 duds for the \StageOne classification in \sw
+and a sample of 500 false positives for the \StageTwo inspection. The
 sample of false positives was selected from the candidates which passed
-the Stage I of \sw. We note that this is the first time, we have a
+the \StageOne of \sw. We note that this is the first time, we have a
 systematically compiled sample of visually inspected false positives by
@@
 inspection to find gravitational lenses. The volunteers are shown images at two
-stages. At stage I, volunteers are requested to undertake a rapid inspection to
+stages. At \StageOne, volunteers are requested to undertake a rapid inspection to
 select lens candiates ranging from possible lenses to almost certain lenses. At
-stage II, volunteers carefully inspect the candidates from stage I and select only
+\StageTwo, volunteers carefully inspect the candidates from \StageOne and select only
 promising lens candidates. A daily snapshot of classifications performed by
@@
 
-SWAP was run nightly during Stage I in order to retire subjects and inject new
+SWAP was run nightly during \StageOne in order to retire subjects and inject new
 ones in to the classification stream. The subjects that passed the acceptance
-threshold at the end of Stage I are served again at Stage II for careful
-reinspection. Each subject, after Stage II, has an associated posterior
+threshold at the end of \StageOne are served again at \StageTwo for careful
+reinspection. Each subject, after \StageTwo, has an associated posterior
 probability P. In the ideal case, all images containing lenses will have high P
@@
 In Table~\ref{tab:stats}, we give overall statistics of the systems detected at
-stage I and stage II. We give the total number of detections of the known lens
+\StageOne and \StageTwo. We give the total number of detections of the known lens
 candidates, known lenses and the new lens candidates at each stage.  We also
@@
 at these stages. We note that most (XXX check) of the confirmed lenses found at
-stage I are also recovered at stage II whereas a small fraction of the known
-lens candidates are rejected at stage II. Also, the sample of new lens
+\StageOne are also recovered at \StageTwo whereas a small fraction of the known
+lens candidates are rejected at \StageTwo. Also, the sample of new lens
 candidates increases the sample of \cfhtls lens candidates by over 50\%.
@@
 probability lens candidates, categorized by the lens experts, as a function of
-the P value assigned by SWAP at the end of Stage II. On average, the fraction of
+the P value assigned by SWAP at the end of \StageTwo. On average, the fraction of
 lens candidates is indeed an increasing function of P. This shows that the \sw
@@
 \hline
-   &  \multicolumn{2}{c} {Stage I}  & \multicolumn{4}{c}{Stage II} \\ 
+   &  \multicolumn{2}{c} {\StageOne}  & \multicolumn{4}{c}{\StageTwo} \\
       & KC  &  KL  & KC & KL & NC & AC\\
@@
 TALK\footnote{http://talk.spacewarps.org/}, the discussion forum for \sw), P
-value at stage II and a visual categorization of type of lensed images and the
+value at \StageTwo and a visual categorization of type of lensed images and the
 lensing galaxy in the Comments column in Table~\ref{tab:swcands}. Whenever
@@
 by \sw. In Table~\ref{tab:stats}, we show that $\sim$~25\%-30\% of the
-known candidates and $\sim$~60\% of the known lenses are found at stages
-I and II in \sw. The left and the middle panels of \Fref{fig:compre}
+known candidates and $\sim$~60\% of the known lenses are found at \StageOne and \StageTwo in \sw. The left and the middle panels of \Fref{fig:compre}
 show the fraction of detections as a function of arc magnitude and the
@@
 %\Fref{fig:compre} shows the completeness of the simulated sample
-%at stage I of \sw as a function of the arc magnitude and Einstein
+%at \StageOne of \sw as a function of the arc magnitude and Einstein
 %radius. We find that the lens sample is more than XXX\% complete between image
@@
 kinds of lenses.  We find that about 40\% of the known sample of lenses
-are missed both at stage I and II (see \Tref{tab:stats}). In fact, most
-of the known lenses from stage I are discovered at stage II suggesting
-that most lenses are lost right at stage I. Below, we focus on the known
-lens sample at stage I to understand why some of them are being missed
+are missed both at \StageOne and II (see \Tref{tab:stats}). In fact, most
+of the known lenses from \StageOne are discovered at \StageTwo suggesting
+that most lenses are lost right at \StageOne. Below, we focus on the known
+lens sample at \StageOne to understand why some of them are being missed
 and possibly find a way to improve the detection rate which can be
@@
 %{ Let us compare the two samples to see if there are any obvious differences.
-only 2 out of this sample of 18 were detected at stage I (reached high P even with fewer classifications) and missed at stage II (P value was low even after recieving very many classifications).
-The rest of the 16 lenses were rejected right at stage I XXX}
-%One of those 6 lenses was detected at stage I but failed to get high enough P value at stage II even after receiving a total of 50 classifications (set as the upper limit).
-The rest of the 5 lenses are already rejected at stage I.
+only 2 out of this sample of 18 were detected at \StageOne (reached high P even with fewer classifications) and missed at \StageTwo (P value was low even after recieving very many classifications).
+The rest of the 16 lenses were rejected right at \StageOne XXX}
+%One of those 6 lenses was detected at \StageOne but failed to get high enough P value at \StageTwo even after receiving a total of 50 classifications (set as the upper limit).
+The rest of the 5 lenses are already rejected at \StageOne.
 Upon visual inspection of these 5 systems, they appear to be difficult to identify as lenses because either the lensed images are faint, have low curvature, are close to the edge and/or are not visible due to proximity to an extremely bright galaxy
@@
 examples of detected lenses (top left panels) and missed lenses (bottom
-left panels) by \sw at stage I. The number of classifications (Nclass)
+left panels) by \sw at \StageOne. The number of classifications (Nclass)
 for a subject increase from top to bottom.  Also, every subject is
@@
 
-We rerun SWAP for stage I where we use classifications from volunteers
+We rerun SWAP for \StageOne where we use classifications from volunteers
 who produce $\Delta$ log(P)$>1.2$ only. This obviously means reducing
@@
 Examples of trajectories of some known lenses (top-left: detected and
-bottom-left: missed) at stage I and histogram of the known lenses for
+bottom-left: missed) at \StageOne and histogram of the known lenses for
 different types of volunteers (right). Among the sample of missed
@@
 
-The blind lens search in the \cfhtls is done in two stages: stage I and
-stage II. In stage I, volunteers inspected $\sim$ 430 000 subjects and
+The blind lens search in the \cfhtls is done in two stages: \StageOne and
+\StageTwo. In \StageOne, volunteers inspected $\sim$ 430 000 subjects and
 selected a smaller sample of $\sim$ 3000 subjects with interesting lens
-candidates. In stage II, after a careful reinspection of the candidates
-from stage I, a smaller pool of more pure sample of $\sim$~500
+candidates. In \StageTwo, after a careful reinspection of the candidates
+from \StageOne, a smaller pool of more pure sample of $\sim$~500
 candidates is obtained. In the next step, the images are graded by three
@@
 \item Based on the known sample of lenses and lens candidates, we find
-that we lose a very small fraction of them as we go from Stage I to
-Stage II. In other words, it is more important to improve the lens
-detection efficiency right at Stage I to increase the overall
+that we lose a very small fraction of them as we go from \StageOne to
+\StageTwo. In other words, it is more important to improve the lens
+detection efficiency right at \StageOne to increase the overall
 completeness of the final lens sample
 
-\item From the sample of known lenses, \sw missed about 40\% at Stage I.
+\item From the sample of known lenses, \sw missed about 40\% at \StageOne.
 Among the missed sample of about 20 lenses, roughly half of them are
@@
 \item If we use the classifications from more skilled volunteers alone
-at Stage I, then we recover over 30\% of the lenses from the missed
+at \StageOne, then we recover over 30\% of the lenses from the missed
 sample. Thus, it is possible to improve the completeness of lenses by
@@
 %those AF lenses which were labelled sims - look at the D11 counterparts
-%and their status in stage 1 swap}
+%and their status in \StageOne swap}
 

### 2015-03-25 doc/sw-system.tex
Implemented \StageOne and \StageTwo macros, closes #109

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Space Warps System Paper
+% 
+% Space Warps Paper I: System
 %
@@
 probability systems are retired from the site periodically, concentrating the
-sample towards a set of candidates; this ``stage 1'' set is then re-classified
+sample towards a set of candidates; this ``\StageOne'' set is then re-classified
 by the volunteers in a second  refinement stage. Analyzing the classification
@@
 classifications over the course of N months. The sample was reduced to 3500
-stage 1 candidates; these were then refined to yield a sample of 1400
-candidates rankable by their stage 2 probability. We expect this sample to be
+\StageOne candidates; these were then refined to yield a sample of 1400
+candidates rankable by their \StageTwo probability. We expect this sample to be
 X\% complete and Y\% pure at a threshold of 95\% classification probability.
@@
 implemented as a Zooniverse project.
-In a companion paper (More et al, in preparation, herafter \papertwo) we will
+In a companion paper (More et al, in preparation, herafter \PaperTwo) we will
 present the new gravitational lenses discovered in our first, experimental,
@@
 us to estimate completeness and purity with respect to gravitational lenses
-that have the same properties of the training set. In \papertwo,
+that have the same properties of the training set. In \PaperTwo,
 we carry out a complementary analysis using a sample of
@@
 
-\subsubsection{Stage 1: Initial Classification}
-
-The goal of a stage 1 classification is to achieve a high rejection rate,
+\subsubsection{\StageOne: Initial Classification}
+
+The goal of a \StageOne classification is to achieve a high rejection rate,
 while maintaining high completeness.  In this mode, therefore, the pre-loading
@@
 the web app for classification. This means that the discovery of lens
-candidates in stage 1 is truly a community effort: to detect a lens candidate,
+candidates in \StageOne is truly a community effort: to detect a lens candidate,
 many non-lenses must first be rejected, and several classifications by different inspectors are needed in either case.
 
-The stage 1 training set was chosen to be quite clear cut, in order to err on
+The \StageOne training set was chosen to be quite clear cut, in order to err on
 the side of inclusivity, and so ensure high completeness. For the training duds
@@
 specifically excluded from the training set, and so we expect some of those
-types of object to appear in the stage 1 candidate list. The training sims for
-stage 1 were also selected to be relatively straightforward to spot, as we sought a balance between sensitivity to faint or difficult lenses, and the need to educate the volunteers in what gravitational lenses look like.
+types of object to appear in the \StageOne candidate list. The training sims for
+\StageOne were also selected to be relatively straightforward to spot, as we sought a balance between sensitivity to faint or difficult lenses, and the need to educate the volunteers in what gravitational lenses look like.
 We return to this balance below.
 
-\subsubsection{Stage 2: Refinement}
-
-The design of the stage 1 classification task, and its training set, should lead
+\subsubsection{\StageTwo: Refinement}
+
+The design of the \StageOne classification task, and its training set, should lead
 to sample of lens candidates that has high completeness but may have low purity.
@@
 means providing the volunteers with a more realistic and challenging training
-set as they re-classify it. The more demanding stage 2 training set was
-generated as follows. The stage 2 duds were selected from the image pool by at
+set as they re-classify it. The more demanding \StageTwo training set was
+generated as follows. The \StageTwo duds were selected from the image pool by at
 least one of three of us  (AV, AM and PM) as being a potential false positive,
-while the stage 2 sims were chosen to be a subset of stage 1 sims, none of which
+while the \StageTwo sims were chosen to be a subset of \StageOne sims, none of which
 were deemed ``obvious'' by the same expert classifiers.
 \Fref{fig:training:gallery} shows some example images from the resulting CFHTLS
-stage 2 training set.
+\StageTwo training set.
 
@@
 \end{minipage} \hfill
-\caption{Typical \SW ``sims'' from the stage 2 training set. Insets indicate the
+\caption{Typical \SW ``sims'' from the \StageTwo training set. Insets indicate the
 location of the simulated lens in each of these training images. Users needed to
@@
 \end{minipage} \hfill
-\caption{Typical \SW ``duds'' from the stage 2 training set. All of these
+\caption{Typical \SW ``duds'' from the \StageTwo training set. All of these
 subjects were correctly classified by the community as not likely to contain
@@
 
-We refer the reader to \papertwo for the details of the particular set of
+We refer the reader to \PaperTwo for the details of the particular set of
 imaging survey data used in this first \sw project. Here, we summarize very
@@
 \centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_trajectories.png}
-\caption{Typical \SW stage 1 subject trajectories. Subjects drift downwards in
+\caption{Typical \SW \StageOne subject trajectories. Subjects drift downwards in
 the top panel as they are classified, while being nudged left and right by the
@@
 
-During stage 1 classification of the CFHTLS images, we assigned a prior
+During \StageOne classification of the CFHTLS images, we assigned a prior
 probability for each image to contain a lens of $2\times10^{-4}$, based on a
@@
 When all the subjects had either been retired, or classified around 10 times
-or more, the web app was paused and reconfigured for stage 2. The sample of
-subjects classified during stage 2 was selected to be all those that passed
-the detection threshold ($\pr(\LENS|C,T) > 0.95$) at stage 1. These were
+or more, the web app was paused and reconfigured for \StageTwo. The sample of
+subjects classified during \StageTwo was selected to be all those that passed
+the detection threshold ($\pr(\LENS|C,T) > 0.95$) at \StageOne. These were
 classified for one week, with no retirement but a maximum classification
-number of 50 each. The number of subjects at stage 2 was small enough that we
+number of 50 each. The number of subjects at \StageTwo was small enough that we
 did not need to retire any: instead, we simply collected classifications for a
@@
 1-D and 2-D marginalized distributions for the logarithms of the
-properties of the agents described in the text. The stage 1 agents are shown
-in blue, the stage 2 agents in orange.}
+properties of the agents described in the text. The \StageOne agents are shown
+in blue, the \StageTwo agents in orange.}
 \label{fig:crowd:cornerplot}
@@
 \item{\noindent\bf ``Effort:''} The number of test images, $\effort$, classified by a
-volunteer. In stage 1, the mean effort per agent was 263; in the shorter stage
-2 it was 81.
+volunteer. In \StageOne, the mean effort per agent was 263; in the shorter \StageTwo it was 81.
 %
 \item{\noindent\bf ``Experience:''} The number of training images, $\experience$,
-classified by a volunteer. In stage 1, the mean experience per agent was 29;
-in stage 2 (where the training image fequency was set higher) it was 34.
+classified by a volunteer. In \StageOne, the mean experience per agent was 29;
+in \StageTwo (where the training image fequency was set higher) it was 34.
 %
@@
 this increases as training subjects are classified, and the agent's estimates
-of its confusion matrix elements improve. In stage 1, the mean skill per agent
-was 0.04 bits; in  stage 2 it was 0.05.
+of its confusion matrix elements improve. In \StageOne, the mean skill per agent
+was 0.04 bits; in  \StageTwo it was 0.05.
 %
@@
 project that volunteer (see the appendix for more discussion of this
-quantity). In stage 1, the mean contribution per agent was 34.9 bits; in
-stage 2 it was 33.5.
+quantity). In \StageOne, the mean contribution per agent was 34.9 bits; in
+\StageTwo it was 33.5.
 %
@@
 
-The distributions for the stage 2 agents (orange) are qualitatively similar to
-those for the stage 1 agents (blue). Differences are: 1) the maximum effort
-possible at stage 2 is smaller, because fewer subjects were available to be
-classifed, but 2) the mean effort expended at stage 2 was higher (perhaps
+The distributions for the \StageTwo agents (orange) are qualitatively similar to
+those for the \StageOne agents (blue). Differences are: 1) the maximum effort
+possible at \StageTwo is smaller, because fewer subjects were available to be
+classifed, but 2) the mean effort expended at \StageTwo was higher (perhaps
 because the subjects were higher probability, and more compelling); 3) the
-information generated per agent was higher at stage 2, because the subjects
+information generated per agent was higher at \StageTwo, because the subjects
 had higher probability.
@@
 \caption{Narrow cumulative distributions of the contributions made by the
-agents: for example, 90\% of the stage 2 contributions were made by the
-highest contributing  7\% of the crowd. The stage 1 agents are shown in blue,
-the stage 2 agents in orange. ``Experienced volunteers'' classified 10 or more
+agents: for example, 90\% of the \StageTwo contributions were made by the
+highest contributing  7\% of the crowd. The \StageOne agents are shown in blue,
+the \StageTwo agents in orange. ``Experienced volunteers'' classified 10 or more
 training subjects.}
@@
 clearly the importance of the hardest-working, most active volunteers: at
-stage 1,  1.0\% of the volunteers -- 375 people -- made 90\% of the
-contribution.  At stage 2, where it was not possible to make as
+\StageOne,  1.0\% of the volunteers -- 375 people -- made 90\% of the
+contribution.  At \StageTwo, where it was not possible to make as
 many classifications before running out of subjects, 7.2\% of the volunteers
@@
 \Fref{fig:crowd:cumulplot}. The most skilled 20\% of agents possess only  79\%
-of the skill at stage 1, and 77\% at stage 2. The inexperienced volunteers
+of the skill at \StageOne, and 77\% at \StageTwo. The inexperienced volunteers
 also possess a significant fraction of the skill: the most skillful 20\% of
@@
 \caption{Broad cumulative distributions of agent skill:
-the most skilled 20\% of the crowd only possess 79\% of the skill at stage 1.
-The stage 1 agents
-are shown in blue, the stage 2 agents in orange. ``Experienced volunteers''
+the most skilled 20\% of the crowd only possess 79\% of the skill at \StageOne.
+The \StageOne agents
+are shown in blue, the \StageTwo agents in orange. ``Experienced volunteers''
 classified 10 or more training subjects.}
@@
 successive classifications we can make estimates of the crowd's classification
-and contribution speed. We plot these two quantities for both Stage 1 and Stage
-2 in \Fref{fig:results:speed}, normalizing the speed and time axes to the
+and contribution speed. We plot these two quantities for both \StageOne and \StageTwo in \Fref{fig:results:speed}, normalizing the speed and time axes to the
 respective totals.
 The fractional classification rates in each stage of the survey fall off in approximately the same way, despite the factor of nearly 20 difference in crowd size.
-Stage 1 (consisting of $\sim430,000$ subjects) was completed in around 5000 hours (by some 37,000 participants), with classification rates in the first few days averaging at $\sim10^4$ per hour, stimulated by various forms of advertising (press releases, and emails to registered Zooniverse users).
+\StageOne (consisting of $\sim430,000$ subjects) was completed in around 5000 hours (by some 37,000 participants), with classification rates in the first few days averaging at $\sim10^4$ per hour, stimulated by various forms of advertising (press releases, and emails to registered Zooniverse users).
 The asymptotic classification rate was $\sim10^3$ per hour.
-The average skill was found to be approximately constant over the lifetime of Stage 1, leading to a contribution rate that tracks closely the classification rate.
-(A 10\% increase in average skill was seen over the first 40 days, and a decrease of the same amount in the last 40 days -- not enough to cause a significant difference between classification and contribution rate behavior, but perhaps reflecting a learning period at the start and a decrease in participation late on.) Stage 2 (3700 subjects) was completed in around 600 hours by around 2000 participants, with classification rates starting at $~\sim2000$ per hour and decaying to $\sim100$ per hour.
+The average skill was found to be approximately constant over the lifetime of \StageOne, leading to a contribution rate that tracks closely the classification rate.
+(A 10\% increase in average skill was seen over the first 40 days, and a decrease of the same amount in the last 40 days -- not enough to cause a significant difference between classification and contribution rate behavior, but perhaps reflecting a learning period at the start and a decrease in participation late on.) \StageTwo (3700 subjects) was completed in around 600 hours by around 2000 participants, with classification rates starting at $~\sim2000$ per hour and decaying to $\sim100$ per hour.
 
@@
 
-The similarities between Stage 1 and 2, suggest that these numbers could be scaled to estimate the speed of future \SW projects (or at least those following a similar blind search strategy).
+The similarities between \StageOne and 2, suggest that these numbers could be scaled to estimate the speed of future \SW projects (or at least those following a similar blind search strategy).
 For example, the completion time for a \SW project could be approximated as
@@
 We now quantify the performance of the \sw system in terms of the recovery of
-the training set images. At stage 1, this set contains around 5712 simulated
-lenses, and 450 duds; at stage 2, we used 152 simulated lenses and 201 duds.
+the training set images. At \StageOne, this set contains around 5712 simulated
+lenses, and 450 duds; at \StageTwo, we used 152 simulated lenses and 201 duds.
 \Fref{fig:results:sample:roc} shows receiver operating characteristic (ROC)
-curves for CFHTLS stage 1 and stage 2. These plots show the true positive rate
-(TPR), the number of sims correctly detected divided by the total number of
-sims in the training set, and the false positive rate (FPR), the number of
-duds incorrectly detected  divided by total number of duds in the training
-set, both for a given sample of detections defined by a particular probability
-threshold, which varies along the curves.  In both stages, these curves show
-that true positive rates of  around 90\% were achieved, at very low false
-positive rates. For comparison we show the results of an analysis where the
-classifications of  training images were ignored, and none of the agents
-allowed to learn: they were instead assigned initial values of their confusion
-matrices of 0.75 for each element, which then remained constant. This emulates
-a very simple unweighted voting scheme, where all classifications are treated
-equally. In this case, the TPR remains under 80\% in stage 1 and 60\% in stage
-2, thus quantifying  the benefit of including training images and allowing the
-agents to learn. The choice of initial confusion matrix is not very important:
-the same 0.75 initial values applied to normal, learning agents results in a
-slightly lower TPR than the default case, indicating that initializing the
-system less conservatively results in slightly worse performance.
-
-The dot-dashed curves show the impact of the offline analysis. At stage 1 the
+curves for CFHTLS \StageOne and \StageTwo. These plots show the true positive
+rate (TPR), the number of sims correctly detected divided by the total number of
+sims in the training set, and the false positive rate (FPR), the number of duds
+incorrectly detected  divided by total number of duds in the training set, both
+for a given sample of detections defined by a particular probability threshold,
+which varies along the curves.  In both stages, these curves show that true
+positive rates of  around 90\% were achieved, at very low false positive rates.
+For comparison we show the results of an analysis where the classifications of
+training images were ignored, and none of the agents allowed to learn: they were
+instead assigned initial values of their confusion matrices of 0.75 for each
+element, which then remained constant. This emulates a very simple unweighted
+voting scheme, where all classifications are treated equally. In this case, the
+TPR remains under 80\% in \StageOne and 60\% in \StageTwo, thus quantifying  the
+benefit of including training images and allowing the agents to learn. The
+choice of initial confusion matrix is not very important: the same 0.75 initial
+values applied to normal, learning agents results in a slightly lower TPR than
+the default case, indicating that initializing the system less conservatively
+results in slightly worse performance.
+
+The dot-dashed curves show the impact of the offline analysis. At \StageOne the
 results are very similar to the online version that was actually run (solid
-line). However, at stage 2 there is marginal evidence of there being greater
+line). However, at \StageTwo there is marginal evidence of there being greater
 benefit to doing the analysis offline. Over 85\% TPR is achieved at zero FPR
@@
 the sims that were missed in the online analysis may be being recovered by
-doing the analysis offline. The same is true at stage 1, but to a lower
+doing the analysis offline. The same is true at \StageOne, but to a lower
 degree. Assuming Poisson statistics for the fluctuations in the numbers of
-recovered lenses, the uncertainty in the measured stage 2 TPR values is around
+recovered lenses, the uncertainty in the measured \StageTwo TPR values is around
 8\%, but the online and offline samples are highly correlated, such that the
@@
 this. Still, a larger validation set is needed to test these algorithmic
-choices more rigorously. At stage 1, high TPR can be measured to better than
+choices more rigorously. At \StageOne, high TPR can be measured to better than
 1\%.
@@
 \caption{Receiver operating characteristic curves for the \sw system, using
-the CFHTLS training set. Left: stage 1, right: stage 2.}
+the CFHTLS training set. Left: \StageOne, right: \StageTwo.}
 \label{fig:results:sample:roc}
@@
 
-Adopting the online stage 1 analysis, and the offline stage 2 analysis, we
+Adopting the online \StageOne analysis, and the offline \StageTwo analysis, we
 show in \Fref{fig:results:sample:CP} a plot of the more familiar (to
@@
 
-The stage 1 curves are truncated by the retirement of subjects in this phase,
+The \StageOne curves are truncated by the retirement of subjects in this phase,
 which sets the minimum size of this sample. We see from the solid blue curve
@@
 galaxies were recovered at understandably lowest completeness, although the
-wider image separation  lensing clusters were not very different. At stage 2,
+wider image separation  lensing clusters were not very different. At \StageTwo,
 where no retirement was carried out, it was possible to reach 100\% purity:
@@
 We investigated the source of the incompleteness and impurity visible in
-\Fref{fig:results:sample:CP}, by examining the stage 2 false negatives and
+\Fref{fig:results:sample:CP}, by examining the \StageTwo false negatives and
 false positives, and their behaviour as they are classified using the online
@@
 non-lenses that were incorrectly flagged as candidates ($\pr(\LENS|C,T) >
-0.95$) by the \sw system. While the final stage 2 analysis was done offline,
+0.95$) by the \sw system. While the final \StageTwo analysis was done offline,
 these trajectory plots still serve to illustrate the approximate
@@
 \centering\includegraphics[width=0.9\linewidth]{sw-system-figs/stage2_veteran_contribution.png}
-\caption{Stage 2 classifier skill, as a function of their stage 1 skill.
-Veterans from stage 1  are shown in blue, while new volunteers are shown in
-orange. Point size is proportional to the number of stage 2 classifications
+\caption{\StageTwo classifier skill, as a function of their \StageOne skill.
+Veterans from \StageOne  are shown in blue, while new volunteers are shown in
+orange. Point size is proportional to the number of \StageTwo classifications
 made, while dashed lines are drawn at the mean values for each sample.
-Restricting stage 2 to classifiers with high stage 1 skill could reduce the
+Restricting \StageTwo to classifiers with high \StageOne skill could reduce the
 noise in the system.}
@@
 bringing higher skill volunteers in to the mix. We
-advertised stage 2 of the current project to all registered users; it was
-taken up by stage 1 veterans with a broad range of skill, and also picked up a
+advertised \StageTwo of the current project to all registered users; it was
+taken up by \StageOne veterans with a broad range of skill, and also picked up a
 significant number of new users who did not have enough time to aquire high
-skill (since stage 2 was quite short): of the 1964 volunteers who took part in
-the stage 2 classification round, only 774 were veterans from stage 1.
-\Fref{fig:discuss:performance:stage1vstage2} shows how the stage 1 skill maps
-on to stage 2 skill and contribution.
-
-This figure suggests that there may be some benefit to opening stage 2 on the
-basis of stage 1 agent skill, in order to reduce the noise in the system
+skill (since \StageTwo was quite short): of the 1964 volunteers who took part in
+the \StageTwo classification round, only 774 were veterans from \StageOne.
+\Fref{fig:discuss:performance:stage1vstage2} shows how the \StageOne skill maps
+on to \StageTwo skill and contribution.
+
+This figure suggests that there may be some benefit to opening \StageTwo on the
+basis of \StageOne agent skill, in order to reduce the noise in the system
 generated by new and low skill volunteers in this more difficult
 classification stage.  A simple implementation of this would be to switch the
-web app to the stage 2 version when either a certain stage 1 skill (and/or
+web app to the \StageTwo version when either a certain \StageOne skill (and/or
 effort) threshold was passed. Good strategy would probably be to switch back
-to stage 1 after some number of stage 2 classifications (to avoid losing the
-high skill users from stage 1 entirely), and also to make it very clear which
-stage the classifier was at (since stage 2 requires more careful attention).
+to \StageOne after some number of \StageTwo classifications (to avoid losing the
+high skill users from \StageOne entirely), and also to make it very clear which
+stage the classifier was at (since \StageTwo requires more careful attention).
 This is something we plan to experiment with in future.
@@
 in accelerating the agent's learning (Davis et al, in preparation). We also
-plan to investigate the use of offline analysis at Stage 1, for the same
+plan to investigate the use of offline analysis at \StageOne, for the same
 reason (see also \Sref{sec:discuss:efficiency} below.)
@@
 % \caption{Predictability of final skill from early skill (after 10 training
-% classifications) in stage 1 agents. The dashed lines enclose 649 agents with
+% classifications) in \StageOne agents. The dashed lines enclose 649 agents with
 % early skill greater than 0.1
@@
 %
-% Having seen the importance of the high skill volunteers at both stage 1 and
-% stage 2, we might ask, can we predict agent skill after, say, the volunteer
+% Having seen the importance of the high skill volunteers at both \StageOne and
+% \StageTwo, we might ask, can we predict agent skill after, say, the volunteer
 % has experienced 10 training subjects? In \Fref{fig:crowd:skillprediction} we
-% plot this ``early skill'' against final skill, for all experienced stage 1
+% plot this ``early skill'' against final skill, for all experienced \StageOne
 % volunteers. The majority of the crowd shows little correlation, but at the
-% high early skill end, some predictability appears. The 649 experienced  stage
-% 1 volunteers who had early skill greater than 0.1 went on to attain a mean
+% high early skill end, some predictability appears. The 649 experienced \StageOne
+% volunteers who had early skill greater than 0.1 went on to attain a mean
 % final skill of 0.22, with 97\% remaining at skill 0.05 or higher. This
@@
 % progresses, in order to encourage those showing an aptitude for the task to
-% take part in the more difficult activities, such as stage 2 refinement.
+% take part in the more difficult activities, such as \StageTwo refinement.
 % However, this would not have done a very good job at identifying the
@@
 \Tref{tab:crowd:contributions} shows the total effort, contribution, skill and
-information generated in both stage 1 and 2 of the CFHTLS project, with the
+information generated in both \StageOne and 2 of the CFHTLS project, with the
 total numbers of agents and subjects for comparison.   These numbers allow us
@@
 therefore a measure of the stage's inefficiency. We find our inefficiency (by
-dividing column 2 by column 3) to be 33\% and 17\% in stage 1 and 2
-respectively. In stage 1, this inefficiency is due to the daily processing: we
+dividing column 2 by column 3) to be 33\% and 17\% in \StageOne and \StageTwo
+respectively. In \StageOne, this inefficiency is due to the daily processing: we
 were not able to retire subjects fast enough, and so they, remained in the
@@
 is 34\%. (The remaining 1\% is due to not all subjects being classified to 1
-or 0 probability.) At stage 2, we did not retire any subjects at all; the
+or 0 probability.) At \StageTwo, we did not retire any subjects at all; the
 inefficiency in this case was by design, to give everyone a chance to
@@
 the effective crowd size, in the sense that a crowd of perfect classifiers
-would be of this size. By this measure,the stage 1 crowd was equivalent to a
-team of 1470 perfect classifiers, while the stage 2 crowd was equivalent to a
+would be of this size. By this measure,the \StageOne crowd was equivalent to a
+team of 1470 perfect classifiers, while the \StageTwo crowd was equivalent to a
 team of 102 perfect classifiers. With this same crowd, we can see that surveys
@@
 through closer collaboration with the science team. It's also possible that
-the dynamic stage 2 system proposed in the previous section may act as an
+the dynamic \StageTwo system proposed in the previous section may act as an
 incentive to some volunteers to increase their contribution (while gaining
-skill in order to ``reach'' stage 2). Reducing the rate at which  new
+skill in order to ``reach'' \StageTwo). Reducing the rate at which  new
 volunteers lose interest could also play a role. Anecdotally, it seems fairly
@@
 
-\item Both stages (1 and 2) achieved the required rejection rates
-
-\item Integrated humanpower = X (stage 1) and Y (stage 2), cf hours taken by
+\item Both \StageOne and \StageTwo achieved the required rejection rates
+
+\item Integrated humanpower = X (\StageOne) and Y (\StageTwo), cf hours taken by
 small team of experts
@@
 \item The optimal true positive rate (completeness) and false positive rate in
-the training set were estimated to be TPR\% and FPR\% at Stage 1, assuming a
+the training set were estimated to be TPR\% and FPR\% at \StageOne, assuming a
 detection threshold of xxx.
 
-\item In the ``refinement'' stage 2, X\% of the stage 1 candidates were
+\item In the ``refinement'' \StageTwo, X\% of the \StageOne candidates were
 rejected (with P less than threshold), and the remainder assigned lens
 ``probabilities.'' Ranking
-subjects by their Stage 2 lens probability gives an ROC curve for the system
+subjects by their \StageTwo lens probability gives an ROC curve for the system
 with X properties. The optimal true positive rate (completeness) and false
@@
 very rough estimate for the effective number of detections corresponding to
-the crowd's contribution: these are 2830 and 25 bits for stages 1 and 2
+the crowd's contribution: these are 2830 and 25 bits for \StageOne and \StageTwo
 respectively.  These figures are close to the numbers of detections given in
@@
 expectation-maximisation algorithm. This procedure takes approximately the
-same CPU time as the stage 2 online analysis, because no matrix inversions are
+same CPU time as the \StageTwo online analysis, because no matrix inversions are
 required in the algorithm. The algorithm scales well and is actually faster
-than the online analysis with the larger stage 1 dataset. The
+than the online analysis with the larger \StageOne dataset. The
 expectation-maximisation algorithm is robust to initial starting parameters

### 2015-03-25 doc/sw-system.tex
More AV comments...

@@
 \end{minipage} \hfill
-\caption{Typical \SW ``sims'' from the \StageTwo training set. Insets indicate the
+\caption{Typical \SW ``sims'' from the \StageTwo training set. The top right-hand corner insets indicate the
 location of the simulated lens in each of these training images. Users needed to
@@
 subjects were correctly classified by the community as not likely to contain
-gravitational lenses; the insets merely indicate regions where $\sim10\%$ of the
+gravitational lenses; the top right-hand corner insets merely indicate regions where a minority ($\sim10\%$) of the
 volunteers clicked.} \label{fig:training-gallery:duds}
@@
 
-\section{Classification Stages and Analysis}
+\section{Classification Analysis}
 \label{sec:swap}
@@
 Each classification made is logged in a database, storing subject IDs,
-(anonymous) volunteer IDs, a timestamp and the classification results.  The
-{\it kind} of subject -- whether it is a training subject (a simulated lens
-or a known non-lens) or a test subject (an unseen image drawn from the survey)
--- is also recorded. For all subjects, the positions of all Markers are
+(anonymous) volunteer IDs, a timestamp and the classification results (the image pixel-coordinate positions of every marker placed).  The
+``category'' of subject -- whether it is a ``training'' subject (a simulated
+lens or a known non-lens) or a ``test'' subject (an unseen image drawn from the
+survey) -- is also recorded. For all subjects, the positions of all Markers are
 recorded, in pixel coordinates. For training subjects, we also store the
-``classification'' of the subject as a lens, or a non-lens, and also the type
-of object present in the image. These types are summarized in
-\Tref{tab:objecttypes}.  This classification is used to provide instant
-feedback, but is also the basic measurement used in a probabilistic
+``kind'' of the subject as a lens (``sim''), or a non-lens (``dud''), and also
+the ``flavor'' of lens object if one is present in the image (``lensed galaxy'',
+``lensed quasar'' or ``cluster lens'').  This classification is used to provide
+instant feedback, but is also the basic measurement used in a probabilistic
 classification of every subject based on all image views to date.
 
-While the \sw web app is live, and classifications are being made, we
-perform an online analysis of the classifications,  updating a
-probabilistic model of every (anonymous) volunteer's data, and also updating
-the lens probability of each subject  (in both the training and test sets), on
-a daily basis. This gives us a dynamic estimate of the posterior probability
-for  any given  subject being a lens, given all classifications of it to date.
-Assigning thresholds in this lens probability then allows us to make good
-decisions about whether or not to retire a subject from the system, in order to
-focus attention on new images.
+While the \sw web app is live, and classifications are being made, we perform an
+online analysis of the classifications,  updating a probabilistic model of every
+(anonymous) volunteer's data, and also updating the posterior probability that
+each subject (in both the training and test sets) contains a lens, on a daily
+basis. This gives us a dynamic estimate of the posterior probability for  any
+given  subject being a lens, given all classifications of it to date. Assigning
+thresholds in this lens probability then allows us to make good decisions about
+whether or not to retire a subject from the system, in order to focus attention
+on new images.
 
@@
 \item Each agent updates its confusion matrix elements based on the number of
-times its volunteer has been right in each way while classifying subjects from
-the training set, accounting for noise early on due to small number
-statistics: $T$ is the set of all training images seen to date.
+times its volunteer has been right in each way (about both the sims and the
+duds) while classifying subjects from the training set, accounting for noise
+early on due to small number statistics: $T$ is the set of all training images
+seen to date.
 
@@
 \caption{Typical \SW Agent confusion matrix elements. At a particular
-snapshot, 200 random Agents are shown distributed over the unit plane, with a
+snapshot, 200 randomly-selected agents are shown distributed over the unit plane, with a
 tendency to move towards the ``astute'' region in the upper right hand
-quadrant as the Agents' volunteers view more images. Yellow point size is
+quadrant as each agent's volunteer views more images. Yellow point size is
 proprtional to the number of images classified; green point size shows
-Agent-perceived ``skill.''}
+agent-perceived ``skill.''}
 \label{fig:swap:agent-probabilities}
@@
 
-\Fref{fig:swap:agent-probabilities} shows a random selection of Agents'
-confusion matrix elements, as they were on a particular day towards the end of
-the CFHTLS project. Many volunteers classify  only a small number of images,
-and so their Agents' confusion matrix elements remain close to their initial
-values of (0.5,0.5). As more images are classified (shown by the yellow point
-size), the Agents' matrix elements tend to move towards higher values, as the
+\Fref{fig:swap:agent-probabilities} shows the confusion matrix elements of 200
+randomly-selected agents, as they were on a particular day towards the end of
+the CFHTLS project. Many volunteers classify  only a small number of images, and
+so their agents' confusion matrix elements remain close to their initial values
+of (0.5,0.5). As more images are classified (shown by the yellow point size),
+the agents' matrix elements tend to move towards higher values, as the
 volunteers attain greater skill levels (green point sizes, see
-\Sref{sec:results} below) and the Agent learns more about them. In this
-quadrant, the Agents perceive their volunteers to be ``astute.'' This trend is
+\Sref{sec:results} below) and the agent learns more about them. In this
+quadrant, the agents perceive their volunteers to be ``astute.'' This trend is
 more clearly seen in \Fref{fig:swap:agent-histories}, which shows the skill of
-the same sample of Agents as the number of images classified increases. The
+the same sample of agents as the number of images classified increases. The
 histogram shows the distribution of classification number: a long tail to very

### 2015-03-25 doc/sw-cfhtls.tex
Merged bib files into one giant file. Closes #109
Re-worded appendix to use Power instead of Skill, #110

@@
 Here, we investigate if the skill\footnote{see the
-\Aref{appendix:skill} for the choice of this term and how it is
+\Aref{appendix:power} for the choice of this term and how it is
 different from that used in paper I} of volunteers is systematically
@@
 
-\section{Skill}
-\label{appendix:skill}
-In paper I, the term skill is given by the expectation value of the
-information gain which is related to the P$_{\rm L}$, the probability to
-correctly identify a lens as a lens and P$_{\rm D}$, the probability to
-correctly identify a dud as a dud. The skill is not linearly related to
- P$_{\rm L}$ and P$_{\rm D}$. One can get the same value of
-skill for different combinations of P$_{\rm L}$ and P$_{\rm D}$ (see
-Fig. XXX).
-
-\question{AM}{PJM, Is it useful to have this description, any other comments on
-this section?}
-{\bf AM: add figure and polish this further upon suggestion from PJM}
-
-As described in the appendix of paper I, the posterior probability P is
-related to the volunteers skill (or information gain). Also, a volunteer
-with a given skill, will have different positive ($\Delta$~log(P)) and
-negative (-$\Delta$~log(P)) kicks on the trajectory plot. Thus, it is
-not useful to compare classifications of high and low skill volunteers
-to understand if there is a difference in their performance and if the
-high skill volunteers can increase the completeness of the lenses. For
-example, a volunteer who is very good at rejecting duds and not so good
-at identifying lenses will still have a high skill. But such a
-volunteer will fail to detect many of the interesting lenses. Therefore,
-we do not compare high skill vs. low skill volunteers to address this
-issue.
-
-For lack of a better word, we also use the same term skill which has a
-similar meaning to that described in Paper I but not identical. We use a
-more qualitative definition implying the ability of the volunteers to
-make correct lens identification.
+\section{Lens Detection Power}
+\label{appendix:power}
+
+In \PaperOne, we defined the ``Skill'' of an agent as being given by the
+expectation value of the information gain per classification. This quantity is a
+non-linear function of both the $P_{\rm L}$, the probability of correctly
+identifying a lens as a lens and $P_{\rm D}$, the probability of correctly
+identifying a dud as a dud. This means that one can get the same value of Skill
+for different combinations of $P_{\rm L}$ and $P_{\rm D}$ (see Fig. XXX) -- it
+reflect the all-round ability of a classifier to contribute information.
+
+As described in the appendix of \PaperOne, the posterior probability $P$ of a
+subject is determined by the $P_{\rm L}$ and $P_{\rm D}$ of all the volunteers
+who marked it, via Bayes' Theorem. Each agent will apply a different ``kick'' to
+the subject probability, $\Delta\log(P)$, which can be either positive (if the
+classifier thinks it contains a lens) or negative (if they don't). These kicks
+appear as steps on the subject's trajectory plot. This kick magnitude gives a useful measure of an agent's ``Power'' to move subjects closer to detection.
+Note that a volunteer who is very good at rejecting duds, but not so good
+at identifying lenses, may have a high Skill but a low Power (since they may fail to detect many of the interesting lenses): Power provides a more precise quantification of a classifier's ability to detect lenses.
 
@@
 \bibliographystyle{apj}
-\bibliography{references_cfhtls}
+\bibliography{references}
 %\bibliography{references}

### 2015-03-26 doc/sw-system.tex
Now up to section 5... #96

@@
 \caption{Typical \SW Agent histories. The ``skill'' of the  same 200 random
-Agents  as in \Fref{fig:swap:agent-probabilities} is plotted in green as a function
+agents  as in \Fref{fig:swap:agent-probabilities} is plotted in green as a function
 of the number  of subjects classified (``effort''). The yellow histogram in
@@
 the top panel as they are classified, while being nudged left and right by the
-Agents as they interpret the volunteers input. The dotted vertical lines show
+agents as they interpret the volunteers input. The dotted vertical lines show
 (left to right) the retirement threshold, prior probability, and the detection
@@
 probability for each image to contain a lens of $2\times10^{-4}$, based on a
-rough estimate of the number of expected lenses in the survey. We then
-assigned two values of the images' posterior probability, $\pr(\LENS|C,T)$, to
-define ``detection'' and ``rejection'' thresholds. These were set to be 0.95
-and (approximately symmetrically in the logarithm of probability), $10^{-7}$.
-Subjects that attained probability of less than the rejection threshold were
-scheduled for retirement and subsequently ignored by the analysis code.
-Subjects crossing the detection threshold were not retired from the website,
-but instead left in the system so that more volunteers could see them. The
-progress of the subjects is illustrated in \Fref{fig:swap:subject-trajectories}.
-Subjects appear on this plot at the tip of the arrow, at zero classifications
-and prior probability; they then drift downwards as they are classified by the
-crowd, with each Agent applying the appropriate kick in probability based on
-what it hears its volunteer say. Encouragingly, sims (blue) tend to end up
-with high probability, while duds (red) pile up at low probability; test
-subjects (black) mostly drift to low probability, but some go the other way.
-The latter will help make up the candidate sample. As this plot shows, around
-10 classifications are required for a subject to reach the retirement
-threshold.
+rough estimate of the number of expected lenses in the survey, and the fraction
+of the survey area covered by each image. We then assigned two values of the
+images' posterior probability, $\pr(\LENS|C,T)$, to define ``detection'' and
+``rejection'' thresholds. These were set to be 0.95 and (approximately
+symmetrically in the logarithm of probability), $10^{-7}$. Subjects that
+attained probability of less than the rejection threshold were scheduled for
+retirement and subsequently ignored by the analysis code. Subjects crossing the
+detection threshold were not retired from the website, but instead left in the
+system so that more volunteers could see them (and continue to update their
+probabilities). The progress of the subjects is illustrated in
+\Fref{fig:swap:subject-trajectories}. Subjects appear on this plot at the tip of
+the arrow, at zero classifications and prior probability; they then drift
+downwards as they are classified by the crowd, with each agent applying the
+appropriate kick in probability based on what it hears its volunteer say.
+Encouragingly, sims (blue) tend to end up with high probability, while duds
+(red) pile up at low probability; test subjects (black) mostly drift to low
+probability, but some go the other way. The latter will help make up the
+candidate sample. As this plot shows, around 10 classifications are typically required for a subject to reach the retirement (or detection) threshold.
 
@@
 online analysis, we implemented an ``offline'' version of the analysis that
-performs a joint inference of all Agent confusion matrix elements and subject
+performs a joint inference of all agent confusion matrix elements and subject
 probabilities simultaneously, for comparison. We describe how this differs
@@
 online inference. Indeed, it might be more appropriate to perform the inference
-of all Agent confusion matrix elements and Subject probabilities
+of all agent confusion matrix elements and Subject probabilities
 simultaneously, so that the early classifications are not effectively
-downweighted as a result of the Agent's ignorance. It might also be that this
+downweighted as a result of the agent's ignorance. It might also be that this
 ignorance builds in some conservatism to the system, reducing the noise due
 the early classifications if they are unreliable. In the joint analysis, the
-basic assumption that is built into the Agents, that their volunteers
+basic assumption that is built into the agents, that their volunteers
 have innate and unchanging talent for lens spotting parameterised by two
@@
 data, is implemented in full. The effect is that of applying the time-averaged
-confusion matrices, rather than one that evolves as the Agents (and in the
+confusion matrices, rather than one that evolves as the agents (and in the
 real world, the volunteers) learn.
@@
 expectation-maximisation algorithm is robust to initial starting parameters
-in, e.g., initial Agent confusion matrix elements and Subject probabilities.
+in, e.g., initial agent confusion matrix elements and Subject probabilities.
 The plots in \Sref{sec:results:sample} show the difference in performance

### 2015-03-26 doc/sw-cfhtls.tex
PlanetHunters numbers, \PH and \GZ macros

@@
 
-Galaxy Zoo, was the first citizen science project in astronomy which was used to
-classify galaxy morphologies \citep{Lintott2008}.  From the early results based
-on morphological classifications of galaxies, to several new unexpected and
-interesting discoveries, such as that of green pea galaxies and Hanny's
-Voorwerp, Galaxy Zoo has been able to harness the potential of citizen
-scientists.  Since then astronomy and non-astronomy projects have been launched
-under the citizen science web portal Zooniverse (http://zooniverse.org). The task of finding
+\GZ was the first citizen science project in astronomy, and addressed the
+problem of how to  classify large numbers of galaxies by their morphology
+\citep{Lintott2008}.  From the early results based on morphological
+classifications of galaxies, to several new unexpected and interesting
+discoveries, such as that of green pea galaxies and Hanny's Voorwerp, \GZ
+has been able to harness the potential of citizen scientists.  Since then
+astronomy and non-astronomy projects have been launched under the citizen
+science web portal Zooniverse (http://zooniverse.org). The task of finding
 gravitational lenses is significantly challenging given the fact that these

### 2015-03-26 doc/sw-system.tex
PlanetHunters numbers, \PH and \GZ macros

@@
 visual inspection has recently been achieved by the online citizen science
-project PlanetHunters \citep{SchwambEtal2012}. PlanetHunters was designed to
-enable the discovery of transiting exoplanets in data taken by the Kepler
-satellite; a community of N inspectors from the general public found, after
-each undergoing a small amount of training, N new exoplanet candidates by
-visual inspection of the Kepler lightcurves that were presented in a custom
-web-based classification interface. The older Galaxy Zoo morphological
-classification project \citep{LintottEtal2008} has also enabled the discovery
-of rare objects, via its flexible inspection interface and discussion forum
-\citep{LintottEtal2009}. Indeed, several of us (AV,CC,CM,EB,PM,TJ,LW) were active
-in an informal Galaxy Zoo gravitational lens search (Verma et al, in preparation),
-an experience which led
-to the present hypothesis that a systematic online visual lens search could be
-successful.
-
-\todo{PJM}{Fill in numbers of volunteers and detections from PlanetHunters.}
-
-In this paper, we describe the \sw web application, an
-online system that was conceived to address the visual inspection problem in
-gravitational lens detection for future large surveys via crowd-sourcing, and
-implemented as a Zooniverse project.
-In a companion paper (More et al, in preparation, herafter \PaperTwo) we will
-present the new gravitational lenses discovered in our first, experimental,
-lens search, and begin to investigate the differences between lens detections
-made in \sw and those made with automated techniques. Here though, we simply
-try to answer the following questions:
+project \PH \citep{SchwambEtal2012}. \PH was designed to enable the discovery of
+transiting exoplanets in data taken by the Kepler satellite; a community of over
+200,000 inspectors from the general public found, after each undergoing a small
+amount of training, over 40 new exoplanet candidates, by visual inspection of
+the Kepler lightcurves that were presented in a custom web-based classification
+interface \citep{WangEtal2013}. The older \GZ morphological classification
+project \citep{LintottEtal2008} has also enabled the discovery of rare objects,
+via its flexible inspection interface and discussion forum
+\citep{LintottEtal2009}. Indeed, several of us (AV,CC,CM,EB,PM,TJ,LW) were
+active in an informal \GZ gravitational lens search (Verma et al, in
+preparation), an experience which led to the present hypothesis that a
+systematic online visual lens search could be successful.
+
+In this paper, we describe the \sw web application, an online system that was
+conceived to address the visual inspection problem in gravitational lens
+detection for future large surveys via crowd-sourcing, and implemented as a
+Zooniverse project. In a companion paper (More et al, in preparation, herafter
+\PaperTwo) we will present the new gravitational lenses discovered in our first,
+experimental, lens search, and begin to investigate the differences between lens
+detections made in \sw and those made with automated techniques. Here though, we
+simply try to answer the following questions:
 
@@
 
-% PJM IS HERE.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% PJM IS HERE.
 

### 2015-03-26 doc/sw-system.tex
Added notes to intro and conclusions. Fixes #104

@@
 
-In this paper, we describe the \sw web application, an online system that was
-conceived to address the visual inspection problem in gravitational lens
-detection for future large surveys via crowd-sourcing, and implemented as a
-Zooniverse project. In a companion paper (More et al, in preparation, herafter
-\PaperTwo) we will present the new gravitational lenses discovered in our first,
-experimental, lens search, and begin to investigate the differences between lens
-detections made in \sw and those made with automated techniques. Here though, we
-simply try to answer the following questions:
+In this paper, we describe the \sw project, an web-based system  conceived to
+address the visual inspection problem in gravitational lens detection for future
+large surveys via crowd-sourcing. Implemented as a Zooniverse project, it is
+designed to provide a {\it gravitational lens discovery service} to survey teams
+looking for lenses in wide field imaging data. In a companion paper (More et al,
+in preparation, herafter \PaperTwo) we will present the new gravitational lenses
+discovered in our first, experimental, lens search, and begin to investigate the
+differences between lens detections made in \sw and those made with automated
+techniques. Here though, we simply try to answer the following questions:
 
@@
 Our basic method in this paper is to analyze the performance of the \sw system
-on the ``training set'' of simulated lenses and known non-lenses. This allows
-us to estimate completeness and purity with respect to gravitational lenses
-that have the same properties of the training set. In \PaperTwo,
-we carry out a complementary analysis using a sample of
-``known'' (reported in the literature) lenses.
+on the ``training set'' of simulated lenses and known non-lenses. This allows us
+to estimate completeness and purity with respect to gravitational lenses that
+have the same properties of the training set. In \PaperTwo, we carry out a
+complementary analysis using a sample of ``known'' (reported in the literature)
+lenses.
 
@@
 
-Sum up, end.
+Sum up, end. \SW provides a lens candidate detection service, crowd-sourcing the
+time-consuming work of visually inspecting astronomical images for
+gravitationally-lensed features. We invite survey teams searching for lenses in
+their wide-field imaging data to contact us if they would like our help.
 

### 2015-03-26 doc/sw-publication-policy-des.tex
SW-DES policy doc

--- 2014-10-30 doc/sw-publication-policy-gen.tex
@@
 
-\documentclass[a4paper]{article}
+\documentclass[a4paper,twocolumn]{article}
 
@@
 
-\title{Guidelines and Policy for Surveys using \SW}
-\author{Phil Marshall, Aprajita Verma \& Anupreeta More}
-\date{October 27, 2014}
+\title{Guidelines and Policy for the Dark Energy Survey Strong Lensing Science Team using \SW}
+\author{Aprajita Verma, Phil Marshall \& Anupreeta More}
+\date{March 25, 2015}
 \maketitle
@@
 \noindent \sw was conceived as a strong lens
-discovery {\it service}, that any survey science team can make use of
-(within the logistical constraints). In this document we discuss the relationship
-between the survey science teams and the \sw collaboration. 
-This document includes guidelines for data provision, the data policy and for publications of \sw-enabled discoveries.
+discovery {\it service} by harnessing the power of citizen scientists. The the DES strong lensing group (hereafter DES survey science team or DES SST) can make use of
+(within the logistical constraints). In this document we discuss how the DES SST can become involved with \sw and the relationship
+between the DES survey science team and the \sw collaboration. 
+This document includes guidelines for proposing projects, data provision, data policy and for publications of \sw-enabled discoveries.
 \end{abstract}
@@
 \sw comprises a primary classification interface (http://spacewarps.org) that allows citizen scientists to inspect images and mark those that contain potential gravitational lenses.
-In addition, these volunteers are shown simulated lenses (appropriate for the survey being conducted) as an interactive training tool that also allows us to establish the citizens' likelihood of identifying potential lenses and blank fields using the \sw Analysis Pipeline (SWAP).
+In addition, these volunteers are shown simulated lenses (appropriate for the survey being conducted) as an interactive training tool that also allows us to establish the citizens' likelihood of identifying potential lenses and blank fields using the \sw Analysis Pipeline (SWAPR).
 
@@
 This is the direct portal for communication with the \sw community.}).
+
+In order to use \sw interface, the DES Survey Science Team \textbf{must define and propose a project to the \sw PIs} who will establish whether the use of the \sw interface is appropriate and liaise with the DES Survey Science Team to implement their project in the \sw interface.
+Details are given in  Section \ref{sec:project}.
 
@@
 
-\section{Collaboration Membership Types}
+\section{Definition of collaboration member types}
 \label{sec:members}
 
-The \sw collaboration comprises the \sw science team, \sw development team, and all the volunteers who have 
+In this document, we will refer to the entirety of the DES strong lensing science group and the STRIDES team as the DES Survey Science Team (DES SST) to encompass all of the DES strong lensing community.
+
+We now discuss the relationship between the \sw collaboration and the DES SST, who wish to use the \sw interface to investigate their data.
+The DES SSTs will liaise with the \sw science and development teams to ingest their survey data into the \sw interface.
+There may be some overlap between current \sw members and the future SSTs.
+In the case of DES, \sw PI Anupreeta More is a member of both the \sw collaboration and the DES Strong Lensing Science Group.
+
+When we refer to the \sw collaboration, it comprises the \sw science team, \sw development team, and all the volunteers who have 
 logged in\footnote{with a Zooniverse ID.
@@
 
-An expanded definition of the \sw membership is given in the document ``\sw Publication Policy: CFHT-LS''.
-In this document we discuss the relationship between the \sw collaboration and future Survey Science Teams (SST) who wish to use the \sw interface to investigate their data.
-The SSTs will liaise with the \sw science and development teams to ingest their survey data into the \sw interface.
-\sw was established with future surveys in mind and therefore there may be some overlap between current \sw members and the future SSTs.
+If required, an expanded definition of the \sw membership is given in the document ``\sw Publication Policy: CFHT-LS''., however this will not be relevant for publications, see Section \ref{sec:papers} for details.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Defining a suitable \sw science project}
+\label{sec:project}
+
+The DES SST is expected to propose a project to the \sw collaboration that can be best or only be done using the power of citizen scientists.
+Typically this involves visual inspection tasks that are too time consuming for the SST themselves to execute.
+As such any science programme conducted through \sw should be complementary, not in competition, to the lens finding activities being carried out by the SST.
+
+For example, in the first \sw project, the \sw collaboration conducted a lens finding search with \sw over the entire CFHT-LS survey area.
+The goal was to increase the completeness of strong lenses in the survey areas.
+Both RingFinder and ArcFinder algorithms had been used to discover lenses of different types.
+\sw complemented these searches with the potential to find strong lenses missed by these algorithms.
+The method, proposed by Anupreeta More (who served as the SST for this project), was to inspect the entire survey area by getting citizens to inspect $\sim$430,000 tiles of the survey area.
+This was a \textit{blind} search.
+Such a search could not be conducted by a normal sized SST.
+
+\textit{Targeted} searches are also possible, as we performed in the second \sw project on the VICS82 survey area.
+Here we inspected $\sim$40,000 images from the VICS82 survey centred on likely strong lens targets, e.g.
+LRGs, groups, clusters, quasars.
+Again this was more images than the SST could manage to inspect alone.
+
+Another approach is to use the \sw service to inspect the typically large output from automated algorithms or searches that are typically dominated by false positives.
+
+\subsection{DES specific thoughts}
+In the case of DES, with its long data release plan and large strong lens group, we request the team consider the following:
+\begin{enumerate}
+\item The \sw facility should be used for science projects that cannot be completed by the Strong Lens Group itself. 
+\item Any \sw search should be complementary, not in competition, to the lens finding being conducted by the DES SST itself.
+\item While \sw uses citizen science, its primary goal is \textbf{not outreach}, it is harnessing manual power for visual classifications (and eventually modelling) power by citizens to perform science.
+\item We should be careful not to propose a duplicate project provided there is a reasonable scientific motivation behind to do so 
+\item \sw requires volunteers/citizens to give up their personal time to conduct the experiment, this should not be taken lightly, the crowd are motivated by contributing to real science not just doing things for the sake of them.
+This is the reason the suitability of the project for citizen scientists should be carefully considered.
+The \sw PIs will be able to discuss any planned \sw-DES projects with the DES SST.
+\item The success of \sw-DES will rely on input from the DES SST working with the \sw collaboration, dedicated effort is required for this and the DES SST should identify resource for this before embarking on a project.
+The \sw PIs will help to establish the main efforts required that depend on the actual project put forward by the SST (i.e.
+image preparation, simulations).
+\end{enumerate}
+
+\textbf{As such, \sw should be considered to be an integral part of the DES SST lens finding strategy, rather than an alternative method.}
+
+The scientific project, process and outcome is the domain of the SST, the \sw collaboration enables this work by making it a live project on the website.
+We do not, per se, expect the \sw collaboration lead the resultant papers, we just request some of us are included on discovery papers in return for our help, see Section \ref{sec:papers} for more details on the publication policy.
+
+Please do remember that \sw is setup to provide a service to help your team find lenses, any discovery in \sw-DES is the DES SSTs discovery.
+The \sw PIs or the \sw collaboration are not interested in scooping your targets.
+Using SWAP we will send you lists of the candidates selected by the citizens (when you require or at the end of a project).
+If you wish to have our input or collaboratively work on targets we are happy to become more involved (the \sw Pis have strong lensing science interests) but we will not do anything with the sources found through \sw other than provide it to the DES SST.
+We are happy to then work with you as you wish.
+
+Note all possible candidates are in the public domain as all images are available online (but without WCS information).
+These targets may be discussed by citizens on \sw TALK that the DES SST are expected to engage in discussions with citizens.
+
+\subsection{Previewing images}
+We are aware that there is some interest in the DES SST for using \sw to preview images for the SST themselves.
+As this is not the function of the \sw interface or the Zooniverse, this woud only be possible under certain conditions
+(a) the images inspected are destined to be seen by the crowd either in parallel with the SST or immediately following the SST inspection
+(b) the framework of the image presentation (i.e the \sw interface) is the same as the interface presented to the user (image clicks only and no comments or ranking possible)
+(c) all SST inspectors would have to register with the Zooniverse to classify
+(d) While we would not distribute the URL to community, we cannot password protect the site.
+Note the data can still be stripped of WCS information (please see Section \ref{sec:data} for more information.)
+
+Anupreeta More's \textit{visapp} might be a more suitable tool for the SST to use.
+
+\subsection{Possible \sw-DES survey strategies}
+
+We strongly recommend that the majority of the DES SST are behind a search for strong lenses with \sw so we would like that the actual \sw project is discussed with all, highlighting where \sw can complement ongoing or planned searches by teams within the DES SST.
+We are here to assist your science!
+While we can't expect the entirety of the DES Strong Lensing Group or the STRIDES consortium to be behind \sw-DES, all should be made aware of the projects being undertaken and planned with \sw.
+
+In particular for the first potential \sw-DES project (probably on the Y1 data) we encourage the DES SST to strongly consider the timing for when they wish to ingest the images into \sw.
+This could be delayed until the SST has performed all the visual inspection or automated algorithms they wish to to avoid any issue of competition with \sw (if that is a concern).
+
+Possible projects for the DES SST could consider (just to get a flavour of what can be done)
+\begin{enumerate}
+\item \textbf{New Data}:Inspection of areas (targeted or blind) that the SST has not had time to inspect, i.e. use the crowd to increase the speed at which potential lens candidates are discovered
+\item \textbf{Comparison of Expert vs Citizen Classification}: DES SST and citizen's view images in parallel (targeted or blind)
+\item \textbf{Completeness of Expert Classification}: Citizen's classify images already inspected by the DES SST (targeted or blind)
+\item \textbf{Helping the robots}: Use citizens to weed out false positives from candidate samples generated by algorithm based searches
+\item other...
+\end{enumerate}
+
+Note that the projects that you propose to \sw need not be one of the above.
+You can also suggest multiple projects that we could run in a mixture or phased set of experiments.
+Please do consider your timeline with reference to data release and the searches the DES SST want to make themselves.
+
+If the DES SST wants to inspect targets within the consortium and is concerned about being scooped, we suggest that this should happen first before images are passed to \sw.
+We then label any images containing lenses already discovered by the SST as `known lenses'.
+This applies to visually inspected by the SST or algorithm searched images.
+
+\subsection{What to do next: Project Proposals}
+Once you have narrowed down what search you would like to do with \sw, please approach the \sw PIs (Phil Marshall, Anupreeta More, Aprajita Verma, collectively contacted via \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com}) with a short description of their project that includes the following information.
+
+\begin{itemize}
+\item Survey area
+\item Bands to be included
+\item Total number of images to be viewed (approx.)
+\item Targeted survey or blind field search \footnote{Targeted: inspection of a list of candidates; Blind: inspection of tiles of a survey area}
+\item Brief outline of the overall goal(s) of that inspection, highlighting how this is complementary (not competing) with the goals of the DES lens finding group
+\item Proprietary data issues 
+\end{itemize}
+
+Note, the proposed science project(s) should harness citizen classification power to achieve your science goals.
+
+The \sw PIs will then arrange a telecon with the SSTs to discuss their project further.
+
+The original \sw papers, by definition, provide a complete description of the system, and its results from the CFHT-LS survey. The SST will be able
+to read these papers before designing their own \sw project, and cite them as justification for some of their experimental decisions.
+As the \sw paper series get published, links to the papers will be given in this draft.
+Prior to publications, draft papers can also be shared on request by the \sw PIs (\href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com})
 
@@
 
-However, some surveys come with their own proprietary access policy. It is the responsibility
-of the SSTs to provide images to \sw in a way that is consistent
+However, some surveys including DES come with their own proprietary access policy. It is the responsibility
+of the DES SST to provide images to \sw in a way that is consistent
 with their own data access rules. There are two things that SSTs can
@@
 
-\section{Data Preparation and Publications for Future Survey Teams}
-\label{sec:series}
-
-\subsection{Future Project Proposals}
-Any future \sw projects are requested to liaise with the \sw PIs regarding their project.
-We ask that potential project teams first approach the \sw PIs (Phil Marshall, Anupreeta More, Aprajita Verma, collectively contacted via \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com}) with a short description of their project that includes the following information.
-
-\begin{itemize}
-\item Survey
-\item Bands to be included
-\item Total number of images to be viewed (approx.)
-\item Targeted survey or blind field search \footnote{Targeted: inspection of a list of candidates; Blind: inspection of tiles of a survey area}
-\item Brief outline of the overall goal(s)
-\item Proprietary data issues 
-\end{itemize}
-
-The \sw PIs will then arrange a telecon with the SSTs to discuss their project further.
-
-The original \sw papers, by definition, provide a complete description of the system, and its results from the CFHT-LS survey. The science team of
-any other survey (such as DES, RCS, KIDS, PS1, HSC \etc) should be able
-to read these papers before designing their own \sw project, and cite them as justification for some of their experimental decisions.
-As the \sw paper series get published, links to the papers will be given in this draft.
-Prior to publications, draft papers can also be shared on request by the \sw PIs (\href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com})
+\section{Data Preparation and Publications for the DES SST}
+\label{sec:data}
 
@@
 Zooniverse servers.
-There is a reasonable amount of work in preparing data and images by the SSTs for delivery to \sw.
-The \sw team will provide assistance to SSTs in data preparation.
+There is a reasonable amount of work in preparing data and images by the DES SST for delivery to \sw.
+The \sw team will provide assistance to the DES SST in data preparation.
 The benefits of using the \sw service will far outweigh the time needed to prepare data.
@@
 
-\item In {\bf reconfiguring the site itself} ready for the new data. The
+\item In {\bf reconfiguring the site itself} ready for the new data. The DES
 SST will need to include new Spotter's Guide images and text,
@@
 
-\subsection{Resulting Publications}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\subsubsection{Journal Papers}
+\section{Resulting publications for \sw-DES }
+\label{sec:series}
+
+\subsection{Journal Papers}
 \label{sec:papers}
@@
 
-\sw runs an analysis pipeline (SWAP) that will be tailored to the science goals of each new survey.
+\sw runs an analysis pipeline (SWAPR) that will be tailored to the science goals of each new survey.
 Any large changes to the analysis code will be documented  by the \sw Science Team.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Zooniverse \Letters}
+\subsection{Zooniverse \Letters}
 \label{sec:comm}

### 2015-03-28 doc/sw-publication-policy-des.tex
SW-DES policy doc

--- 2014-10-28 doc/sw-publication-policy-gen.tex
@@
 \usepackage{hyperref}
+\usepackage{enumitem}
 
@@
 
-\title{Guidelines and Policy for Surveys using \SW}
-\author{Phil Marshall, Aprajita Verma \& Anupreeta More}
-\date{April 15, 2013}
+\title{Guidelines and Policy for the Dark Energy Survey Strong Lensing Science Team using \SW}
+\author{Aprajita Verma, Phil Marshall \& Anupreeta More}
+\date{March 25, 2015}
 \maketitle
@@
 \begin{abstract} 
-\noindent \sw was conceived as a strong lens
-discovery {\it service}, that any survey science team can make use of
-(within the logistical constraints). In this document we discuss the relationship
-between the survey science teams and the \sw collaboration. 
-This document includes guidelines for data provision, the data policy and for publications of \sw-enabled discoveries.
+\noindent \SW was conceived as a strong lens
+discovery {\it service} by harnessing the power of citizen scientists that the DES strong lensing group (hereafter DES survey science team or DES SST) can make use of
+(within the logistical constraints). In this document we discuss how the DES SST can become involved with \SW and the relationship
+between the DES survey science team and the \SW collaboration. 
+This document includes guidelines for proposing projects, data provision, data policy and for publications of \SW-enabled discoveries.
 \end{abstract}
@@
 
-\section{Introduction to \sw}
+\section{Introduction to \SW}
 
-The \sw website is designed to motivate and  enable tens of thousands of
+The \SW website is designed to motivate and  enable tens of thousands of
 people to perform the scientific tasks of strong gravitational lens
-identification and classification.
-\sw comprises a primary classification interface (http://spacewarps.org) that allows citizen scientists to inspect images and mark those that contain potential gravitational lenses.
-In addition, these volunteers are shown simulated lenses (appropriate for the survey being conducted) as an interactive training tool that also allows us to establish the citizens' likelihood of identifying potential lenses and blank fields using the \sw Analysis Pipeline (SWAP).
+identification.
+\SW comprises a primary `classification' interface (\texttt{http://spacewarps.org}) that allows citizen scientists to inspect images and mark those that contain potential gravitational lenses.
+In addition, these volunteers are shown simulated lenses (appropriate for the survey being conducted) as an interactive training tool that also allows us to establish the citizens' likelihood of identifying potential lenses and blank fields using the \SW Analysis Pipeline (SWAPR).
 
-A key part of the \sw project is the ability for all members of the \sw collaboration (see Section \ref{sec:members}) to communicate with each other and discuss interesting candidates through \Talk\footnote{\Talk (found at \texttt{http://talk.spacewarps.org}) is a forum for \sw collaborators to discuss individual sources and the \sw project in general.
+A key part of the \SW project is the ability for all members of the \SW collaboration (see Section \ref{sec:members}) to communicate with each other and discuss interesting candidates through \Talk\footnote{\Talk (found at \texttt{http://talk.spacewarps.org}) is a forum for \SW collaborators to discuss individual sources and the \SW project in general.
 Bugs can also be reported.
-This is the direct portal for communication with the \sw community.}).
+This is the direct portal for communication with the \SW community.}).
+
+In order to use \SW interface, the DES Survey Science Team \textbf{must define and propose a project to the \SW PIs} who will establish whether the use of the \SW interface is appropriate and liaise with the DES Survey Science Team to implement their project in the \SW interface.
+Details are given in  Section \ref{sec:project}.
+
+\vspace{2mm}
+The PIs of the \SW project are the authors of this document, P.\,Marshall, 
+A.\,More and A.\,Verma, please do not hesitate to contact us if you require any further information or have any questions.
+The PIs may be collectively contacted via the email address \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com}
 
@@
 
-\section{Collaboration Membership Types}
+\section{Definition of collaboration member types}
 \label{sec:members}
 
-The \sw collaboration comprises the \sw science team, \sw development team, and all the volunteers who have 
+In this document, we will refer to the entirety of the DES strong lensing science group and the STRIDES team as the DES Survey Science Team (DES SST) to encompass all of the DES strong lensing community.
+
+We now discuss the relationship between the \SW collaboration and the DES SST, who wish to use the \SW interface to investigate their data.
+The DES SSTs will liaise with the \SW science and development teams to ingest their survey data into the \SW interface.
+There may be some overlap between current \SW members and SSTs.
+In the case of DES, \SW PI Anupreeta More is a member of both the \SW collaboration and the DES Strong Lensing Science Group.
+
+When we refer to the \SW collaboration, it comprises the \SW science team, \SW development team, and all the volunteers who have 
 logged in\footnote{with a Zooniverse ID.
@@
 
-An expanded definition of the \sw membership is given in the document ``\sw Publication Policy: CFHT-LS''.
-In this document we discuss the relationship between the \sw collaboration and future Survey Science Teams (SST) who wish to use the \sw interface to investigate their data.
-The SSTs will liaise with the \sw science and development teams to ingest their survey data into the \sw interface.
-\sw was established with future surveys in mind and therefore there may be some overlap between current \sw members and the future SSTs.
+If required, an expanded definition of the \SW membership is given in the document ``\SW Publication Policy: CFHT-LS''\footnote{available from \texttt{\url{https://github.com/drphilmarshall/SpaceWarps/blob/master/doc/sw-publication-policy-cfhtls.pdf}}}, however this will not be relevant for publications, see Section \ref{sec:papers} for details.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Defining a suitable \SW science project}
+\label{sec:project}
+
+The DES SST is expected to propose a project to the \SW collaboration that can be best or only be done using the power of citizen scientists.
+Typically this involves visual inspection tasks that are too time consuming for the SST themselves to execute.
+As such any science programme conducted through \SW should be complementary, not in competition, to the lens finding activities being carried out by the SST.
+
+For example, in the first \SW project, the \SW collaboration conducted a lens finding search with \SW over the entire CFHT-LS survey area.
+The goal was to increase the completeness of strong lenses in the survey areas.
+Both RingFinder and ArcFinder algorithms had been used to discover lenses of different types.
+\SW complemented these searches with the potential to find strong lenses missed by these algorithms.
+The method, proposed by Anupreeta More (who served as the SST for this project), was to inspect the entire survey area by getting citizens to inspect $\sim$430,000 tiles of the survey area.
+This was a \textit{blind} search.
+Such a search could not be conducted by a normal sized SST.
+
+\textit{Targeted} searches are also possible, as we performed in the second \SW project on the VICS82 survey area.
+Here we inspected $\sim$40,000 images from the VICS82 survey centred on likely strong lens targets, e.g.
+LRGs, groups, clusters, quasars.
+Again this was more images than the SST could manage to inspect alone.
+
+Another approach is to use the \SW service to inspect the typically large output from automated algorithms or searches that are typically dominated by false positives.
+
+\subsection{DES specific thoughts}
+In the case of DES, with its long data release plan and large strong lens group, we request the SST to consider the following:
+\begin{enumerate}
+\item The \SW facility should be used for science projects that cannot be completed by the Strong Lens Group itself. 
+\item Any \SW search should be complementary, not in competition, to the lens finding being conducted by the DES SST itself.
+\item While \SW uses citizen science, its primary goal is \textbf{not outreach}, it is harnessing citizen power for visual classifications (and eventually modelling) powered by citizens to perform science.
+\item A duplicate project is not encouraged provided there is sufficient scientific motivation and justification to do so.
+\item \SW requires volunteers/citizens to give up their personal time to conduct the experiment, this should not be taken lightly, the crowd are motivated by contributing to real science not just doing things for the sake of them.
+This is the reason the suitability of the project for citizen scientists should be carefully considered.
+The \SW PIs will be able to discuss any planned \SW-DES projects with the DES SST.
+\item The success of \SW-DES will rely on input from the DES SST working with the \SW collaboration, dedicated effort is required for this and the DES SST should identify team members who can commit time to the \SW-DES tasks for this before embarking on a project.
+The \SW PIs will help to establish the main efforts required, these will depend on the actual project put forward by the DES SST (e.g.
+image preparation, simulations).
+\end{enumerate}
+
+\textbf{As such, \SW should be considered to be an integral part of the DES SST lens finding strategy, rather than an alternative method.}
+
+The scientific project, process and outcome is the domain of the SST, the \SW collaboration enables this work by making it a live project on the website.
+We do not, per se, expect the \SW collaboration lead the resultant papers, we just request some of us are included on discovery papers in return for our help, see Section \ref{sec:papers} for more details on the publication policy.
+
+Please do remember that \SW is setup to provide a service to help your team find lenses, any discovery in \SW-DES is the DES SSTs discovery.
+The goal of the \SW PIs or the \SW collaboration is to enable your science project and make it work.
+Using SWAP we will send the DES SST lists of the candidates selected by the citizens (at some regular intervals or at the end of a project).
+If the DES SST wish to have the \SW Pis input or to collaboratively work on targets the \SW team are happy to become more involved (the \SW Pis have strong lensing science interests) but we will not do anything with the sources found through \SW other than provide it to the DES SST.
+We are happy to then work with you as you wish.
+
+The primary duty of SW PIs is to enable the discovery of lenses through citizen science and forward the catalog of candidates to the SST (the latter part essentially happens automatically through the pipeline SWAPR).
+The SW team is happy to help with further grading of the candidates or assist with any scientific investigations and follow-up of the candidates, if the DES SST so requests.
+
+Note all possible candidates are in the public domain as all images are available online (but without WCS information).
+These targets may be discussed by citizens on \SW\,\Talk.
+Members of the DES SST are expected to engage in discussions with citizens through \Talk, which in turn has the very positive effect of motivating the citizens to contribute further.
+
+\subsection{Previewing images}
+We are aware that there is some interest in the DES SST for using \SW web interface to preview images for the SST themselves.
+As this is not the function of the \SW interface or the Zooniverse, this would only be possible under certain conditions:
+\begin{enumerate}[label=(\alph*)]
+\item the images inspected are destined to be seen by the crowd either in parallel with the SST;
+\item the framework of the image presentation (i.e the \SW interface) is the same as the interface presented to the user (image clicks only and no comments or ranking possible);
+\item all SST inspectors would have to register with the Zooniverse to classify;
+\item While we would not distribute the URL to community, we cannot password protect the site.
+Note the data can still be stripped of WCS information (please see Section \ref{sec:data} for more information.).
+\end{enumerate}
+
+\subsection{Possible \SW-DES survey strategies}
+
+In our experience, a citizen science project like SW cannot function successfully without significant support and co-ordination of the SST.
+Thus, we recommend the all DES members with an nterest in strong lensing are told about \SW and how it can complement their lens finding effort.
+We are here to assist your science!
+While we can't expect the entirety of the DES Strong Lensing Group or the STRIDES consortium to be behind \SW-DES, all should be made aware of the projects being undertaken and planned with \SW.
+
+In particular, for the first potential \SW-DES project (probably on the Y1 data) we encourage the DES SST to strongly consider the timing for when they wish to ingest the images into \SW.
+This could be delayed until the SST has performed all the visual inspection or automated algorithms they wish to to avoid any issue of competition with \SW (if that is a concern).
+
+Possible projects for the DES SST could consider (just to get a flavour of what can be done)
+\begin{itemize}
+\item \textbf{New Data}:Inspection of areas (targeted or blind) that the SST has not had time to inspect, i.e. use the crowd to increase the speed at which potential lens candidates are discovered
+\item \textbf{Comparison of Expert vs Citizen Classification}: DES SST and citizen's view images in parallel (targeted or blind)
+\item \textbf{Completeness of Expert Classification}: Citizen's classify images already inspected by the DES SST (targeted or blind)
+\item \textbf{Helping the robots}: Use citizens to weed out false positives from candidate samples generated by algorithm based searches
+\item \textbf{Training sets}: Blind inspection to generate a large training set for  machine learning algorithms.
+\end{itemize}
+
+Note that the projects that you propose to \SW need not be one of the above.
+You can also suggest multiple projects that we could run in a mixture or phased set of experiments.
+Please do consider your timeline with reference to data release and the searches the DES SST want to make themselves.
+
+If the DES SST wants to inspect targets within the consortium and is concerned about being scooped, we suggest that this should happen first before images are passed to \SW.
+We would then label any images containing candidate lenses already discovered by the SST as `known lens candidates'.
+This applies to visually inspected by the SST or algorithm searched images.
+
+\subsection{What to do next: Project Proposals}
+Once you have narrowed down what search you would like to do with \SW, please approach the \SW PIs (Phil Marshall, Anupreeta More, Aprajita Verma, collectively contacted via \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com}) with a short description of their project that includes the following information.
+
+\begin{itemize}
+\item Survey area
+\item Bands to be included
+\item Total number of images to be viewed (approx.)
+\item Targeted survey or blind field search \footnote{Targeted: inspection of a list of candidates; Blind: inspection of tiles of a survey area}
+\item Brief outline of the overall goal(s) of that inspection, highlighting how this is complementary (not competing) with the goals of the DES lens finding group
+\item Proprietary data issues 
+\item identify a core team who will lead and work closely with \SW
+\end{itemize}
+
+Note, the proposed science project(s) should harness citizen classification power to achieve your science goals.
+
+The \SW PIs will then arrange a telecon with the DES SST to discuss the project further. This includes discussing effort required and roles for the the SST team for expected tasks.
+
+The original \SW papers, by definition, provide a complete description of the system, and its results from the CFHT-LS survey. The SST will be able
+to read these papers before designing their own \SW project, and cite them as justification for some of their experimental decisions.
+As the \SW paper series get published, links to the papers will be given in this draft.
+Prior to publications, draft papers can also be shared on request by the \SW PIs (\href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com})
 
 In the remaining sections we look at discovery publications that might
-arise from future \sw projects, and suggest reasonable guidelines for
+arise from future \SW projects, and suggest reasonable guidelines for
 deciding on their authorship. First, however, we remind ourselves about data
-access via \sw.
+access via \SW.
 
@@
 
-\sw is a public website. All images displayed there are by definition in the
+\SW is a public website. All images displayed there are by definition in the
 public domain, and so must be expected to be downloaded, copied and
-redistributed by any \sw user. This is a \textbf{good thing}: images of the sky taken
+redistributed by any \SW user. This is a \textbf{good thing}: images of the sky taken
 with publicly-funded telescopes belong to everyone.
 
-However, some surveys come with their own proprietary access policy. It is the responsibility
-of the SSTs to provide images to \sw in a way that is consistent
+However, some surveys including DES come with their own proprietary access policy. It is the responsibility
+of the DES SST to provide images to \SW in a way that is consistent
 with their own data access rules. There are two things that SSTs can
@@
 \item Remove all WCS information from all images provided.
-The \sw interface ``dashboards'' do allow FITS and JPG files to be downloaded.
+The \SW interface ``dashboards'' do allow FITS and JPG files to be downloaded.
 If images from a proprietary dataset being made available is a concern for an SST, they should remove the WCS.
 This also has the consequence that it minimises the potential ``scooping'' of  lens candidates by anyone other than the SST.
-In practice, the objects contained in the \sw images will be too faint
+In practice, the objects contained in the \SW images will be too faint
 for anyone without access to a large telescope to observe, and may also be
@@
 
-\section{Data Preparation and Publications for Future Survey Teams}
-\label{sec:series}
+\section{Data Preparation \& \SW interface}
+\label{sec:data}
 
-\subsection{Future Project Proposals}
-Any future \sw projects are requested to liaise with the \sw PIs regarding their project.
-We ask that potential project teams first approach the \sw PIs (Phil Marshall, Anupreeta More, Aprajita Verma, collectively contacted via \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com}) with a short description of their project that includes the following information.
+\subsection{Collaborating with \SW Science Team}
 
-\begin{itemize}
-\item Survey
-\item Bands to be included
-\item Total number of images to be viewed (approx.)
-\item Targeted survey or blind field search \footnote{Targeted: inspection of a list of candidates; Blind: inspection of tiles of a survey area}
-\item Brief outline of the overall goal(s)
-\item Proprietary data issues 
-\end{itemize}
-
-The \sw PIs will then arrange a telecon with the SSTs to discuss their project further.
-
-The original \sw papers, by definition, provide a complete description of the system, and its results from the CFHT-LS survey. The science team of
-any other survey (such as DES, RCS, KIDS, PS1, HSC \etc) should be able
-to read these papers before designing their own \sw project, and cite them as justification for some of their experimental decisions.
-As the \sw paper series get published, links to the papers will be given in this draft.
-Prior to publications, draft papers can also be shared on request by the \sw PIs (\href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com})
-
-\subsection{Collaborating with \sw Science Team}
-
-Implementing a new project based on different survey data will require support from the \sw Science Team, in three respects:
+Implementing a new project based on different survey data will require support from the \SW Science Team, in three respects:
 
@@
 Zooniverse servers.
-There is a reasonable amount of work in preparing data and images by the SSTs for delivery to \sw.
-The \sw team will provide assistance to SSTs in data preparation.
-The benefits of using the \sw service will far outweigh the time needed to prepare data.
-The \sw Science Team can advise on suitable Training
-Subjects and image display settings, and also on formatting the data
-ready for ingestion and display.
+There is a reasonable amount of work in preparing data and images by the DES SST for delivery to \SW.
+The \SW team will provide assistance to the DES SST in data preparation.
+The benefits of using the \SW service will far outweigh the time needed to prepare data.
+The \SW Science Team can advise on suitable Training
+Subjects (images of simulations and false positives) and image display settings, and also on formatting the data
+ready for ingestion and display. A mandatory element of the training subjects is the production of large samples of simulated lenses. \SW will provide resources to assist generating these simulations.
 
-\item In {\bf reconfiguring the site itself} ready for the new data. The
+\item In {\bf reconfiguring the site itself} ready for the new data. The DES
 SST will need to include new Spotter's Guide images and text,
 modified tutorial content, and additional survey-specific site content;
-the \sw Science Team can help with all of this.
+the \SW Science Team can help with all of this.
 
-\item In {\bf maintaining the site} so that it continues to function
-correctly. This will involve technical support from the Zooniverse and \sw science teams,
+\item In {\bf maintaining the site} so that it continues to function and deliver
+correctly. This will involve technical support from the Zooniverse and \SW science teams,
 but will also require the continued engagement of the wider
@@
 
+\item In {\bf running the \SW analysis pipeline} which will be our responsibility. This will provide candidates to be sent o the DES SST.
+
 \end{enumerate}
-
-\subsection{Resulting Publications}
-
-\subsubsection{Journal Papers}
-\label{sec:papers}
-In return for the work outlined in Section \ref{sec:series} in setting up the new surveys, the \sw PIs will nominate a
-small number of core \sw collaboration members as authors on \textbf{papers that
-present discovery of a lens or sample of lenses enabled by the \sw system}.
-A ``discovery'' is defined by the announcement of the source(s) to the astronomical community in a journal paper.
-We would expect the \sw author list to be a small number (less than ten), primarily the Principal Investigators and a few others working on the ingestion of the new data.
-All post-discovery follow-up papers would of course be exempt from this: the idea is that \sw is purely a gravitational lens discovery service, but not one that runs by magic.
-
-We request that authors of \sw-enabled discovery papers should circulate drafts to the list of \sw authors and allow a minimum of two weeks to give time for comments.
-We also request that any papers based on \sw enabled discoveries should cite the \sw system papers.
-This policy document will be updated with the correct citations to the \sw system papers when available.
-
-\sw runs an analysis pipeline (SWAP) that will be tailored to the science goals of each new survey.
-Any large changes to the analysis code will be documented  by the \sw Science Team.
-The \sw Science Team reserve the right to update the \sw methodology papers.
 
@@
 
-\subsubsection{Zooniverse \Letters}
+\section{Resulting publications for \SW-DES }
+\label{sec:series}
+
+\subsection{Journal Papers}
+\label{sec:papers}
+In return for the work outlined in Section \ref{sec:data} in setting up the new surveys, the \SW PIs will nominate a
+small number of core \SW collaboration members as authors on \textbf{papers that
+present discovery of a lens or sample of lenses enabled by the \SW system}.
+A ``discovery'' is defined by the announcement of the source(s) to the astronomical community in a journal paper.
+We would expect the \SW author list to be a small number (less than ten), primarily the Principal Investigators, a few others working on the ingestion of the new data or moderating \Talk.
+All post-discovery follow-up papers would of course be exempt from this: the idea is that \SW is purely a gravitational lens discovery service, but not one that runs by magic.
+
+We request that authors of \SW-enabled discovery papers should circulate drafts to the list of \SW authors and allow a minimum of two weeks to give time for comments.
+We also request that any papers based on \SW enabled discoveries should cite the \SW system papers.
+This policy document will be updated with the correct citations to the \SW system papers when available.
+
+\SW runs an analysis pipeline (SWAPR) that will be tailored to the science goals of each new survey.
+Any large changes to the analysis code will be documented  by the \SW Science Team.
+The \SW Science Team reserve the right to update the \SW methodology papers.
+
+\subsection{Zooniverse \Letters}
 \label{sec:comm}
 
-Any \sw collaboration member, simply by virtue of their Zooniverse
+Any \SW collaboration member, simply by virtue of their Zooniverse
 registration, may write a Zooniverse
 Letter\footnote{\texttt{http://letters.zooniverse.org}} describing their
-investigation of any lens candidate they find in \sw. This, along with
-posts in  \Talk, is the primary means by which we expect collaboration
+investigation of any lens candidate they find in \SW. This, along with
+posts in  \Talk, is the primary means by which we expect \SW-DES collaboration
 members will communicate their findings to the rest of the
-astronomical community. The investigation of any \sw images that are
+astronomical community. The investigation of any \SW images that are
 provided without world coordinate system (WCS) information will be
-necessarily limited but the \sw Zooniverse \Letters will contribute to the collective knowledge and understanding of the presented system(s). Zooniverse \Letters are citable
+necessarily limited but the \SW Zooniverse \Letters will contribute to the collective knowledge and understanding of the presented system(s). Zooniverse \Letters are citable\SW
 objects, and in some cases will appear listed on ADS\footnote{To be confirmed.}.
 
-As \sw classifications are a community wide activity, it is impossible to attribute the discovery of a candidate to a single community member, or group  of members.
-Therefore, in recognition of their contribution to the \sw project, \sw community members will be listed (on their approval) on the \sw members web page.
-This web page will be linked in every ensuing \sw publication.
+As \SW classifications are a community wide activity, it is impossible to attribute the discovery of a candidate to a single community member, or group  of members.
+Therefore, in recognition of their contribution to the \SW project, \SW community members will be listed (on their approval) on the \SW members web page.
+This web page will be linked in every ensuing \SW publication.
 If a community member makes a significant contribution e.g.\,in the further investigation of a lens candidate with modelling tools, they are strongly encouraged to write Zooniverse \Letters.
@@
 \label{sec:publ}
-Any \sw series and \sw enabled discovery papers should include
+Any \SW series and \SW enabled discovery papers should include
 \begin{itemize}
-\item citations to the \sw system papers, \sw I \& II
-\item a small number of \sw authors proposed by the \sw PIs (see \ref{sec:papers}).
+\item citations to the \SW system papers, \SW I \& II
+\item a small number of \SW authors proposed by the \SW PIs (see \ref{sec:papers}).
 \item the collaboration should be acknowledged in the acknowledgement section with a link to the collaboration membership page (URL: to be confirmed when available).

### 2015-03-28 doc/sw-publication-policy-des.tex
SW-DES policy doc

@@
 \begin{enumerate}[label=(\alph*)]
-\item the images inspected are destined to be seen by the crowd either in parallel with the SST;
-\item the framework of the image presentation (i.e the \SW interface) is the same as the interface presented to the user (image clicks only and no comments or ranking possible);
-\item all SST inspectors would have to register with the Zooniverse to classify;
-\item While we would not distribute the URL to community, we cannot password protect the site.
-Note the data can still be stripped of WCS information (please see Section \ref{sec:data} for more information.).
+\item the images\footnote{can still be stripped of WCS information (please see Section \ref{sec:data}} inspected are destined to be seen by the crowd  \textbf{in parallel} with the SST, therefore the URL for the inspection will be publicly available.;
+\item the framework of the image presentation (i.e the \SW interface) is the same as the interface presented to the volunteers (image clicks only and no comments or ranking possible);
+\item all SST inspectors would have to register with the Zooniverse to classify.
 \end{enumerate}

### 2015-03-29 doc/sw-system.tex
removed panels in dud figure. Closes #111

@@
 \begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=sw-system-figs/gallery/0.png,width=\linewidth,angle=0,clip=}
+\centering\epsfig{file=sw-system-figs/gallery/0_ASW0009dgn.png,width=\linewidth,angle=0,clip=}
 \end{minipage} \hfill
 \begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=sw-system-figs/gallery/1.png,width=\linewidth,angle=0,clip=}
+\centering\epsfig{file=sw-system-figs/gallery/1_ASW0009dgo.png,width=\linewidth,angle=0,clip=}
 \end{minipage} \hfill
 \begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=sw-system-figs/gallery/2.png,width=\linewidth,angle=0,clip=}
+\centering\epsfig{file=sw-system-figs/gallery/2_ASW0009dgy.png,width=\linewidth,angle=0,clip=}
 \end{minipage} \hfill
 \begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=sw-system-figs/gallery/3.png,width=\linewidth,angle=0,clip=}
+\centering\epsfig{file=sw-system-figs/gallery/3_ASW0009dh0.png,width=\linewidth,angle=0,clip=}
 \end{minipage} \hfill
@@
 subjects were correctly classified by the community as not likely to contain
-gravitational lenses; the top right-hand corner insets merely indicate regions where a minority ($\sim10\%$) of the
-volunteers clicked.} \label{fig:training-gallery:duds}
+gravitational lenses.} \label{fig:training-gallery:duds}
 \end{figure*}
@@
 dividing the lens and dud sets into equal fractions.
-
-\todo{Chris}{That still could be worded better... \# 66}
 

### 2015-03-30 doc/sw-system.tex
Starting to rejig table

--- 2015-03-26 doc/sw-system.tex
@@
 
-\title[\sw]
+\title[\SW]
 {\SW: Crowd-sourcing the Discovery of Gravitational Lenses}
@@
 
-We describe \sw, a novel gravitaional lens discovery service that
+We describe \SW, a novel gravitaional lens discovery service that
 yields samples of high purity and completeness through crowd-sourced
@@
 highly skewed distributions of these quantities. We comment on the scalability
-of the \sw system to the wide field survey era, and its potential to operate
+of the \SW system to the wide field survey era, and its potential to operate
 beyond its design as a supervised classification system.
@@
 
-In this paper, we describe the \sw project, an web-based system  conceived to
+In this paper, we describe the \SW project, an web-based system  conceived to
 address the visual inspection problem in gravitational lens detection for future
@@
 discovered in our first, experimental, lens search, and begin to investigate the
-differences between lens detections made in \sw and those made with automated
+differences between lens detections made in \SW and those made with automated
 techniques. Here though, we simply try to answer the following questions:
@@
 
-\item How reliably can we find gravitational lenses using the \sw
+\item How reliably can we find gravitational lenses using the \SW
 system? What is the completeness of the sample produced likely to be?
@@
 
-Our basic method in this paper is to analyze the performance of the \sw system
+Our basic method in this paper is to analyze the performance of the \SW system
 on the ``training set'' of simulated lenses and known non-lenses. This allows us
@@
 
-This paper is organised as follows.  In \Sref{sec:design} we introduce the \sw
-classification interface and the volunteers who make up the \sw
+This paper is organised as follows.  In \Sref{sec:design} we introduce the \SW
+classification interface and the volunteers who make up the \SW
 collaboration,  explain how we use the training images, and describe our
@@
 \Sref{sec:data}, the particular dataset used in the first experimental tests
-of the \sw system, and how we prepared the images prior to displaying them in
+of the \SW system, and how we prepared the images prior to displaying them in
 the web interface. In \Sref{sec:swap} we describe our methodology for
@@
 \Sref{sec:swap}. In this section we take a volunteer's eye view and begin by
-describing the \sw classification interface, the crowd of volunteers, and the
+describing the \SW classification interface, the crowd of volunteers, and the
 interactions between the two.
@@
 \centering\includegraphics[width=0.9\linewidth]{sw-system-figs/sw-screengrab-marker+feedback.png}
-\caption{Screenshot of the \sw classification interface.}
+\caption{Screenshot of the \SW classification interface.}
 \label{fig:screenshot}
@@
 
-A screenshot of the \sw classification interface (CI) is shown in
-\Fref{fig:screenshot}. The CI is the centrepiece of the \sw website,
+A screenshot of the \SW classification interface (CI) is shown in
+\Fref{fig:screenshot}. The CI is the centrepiece of the \SW website,
 \texttt{http://spacewarps.org}; the web application is written in coffeescript,
 css and html and follows the general design of others written by the Zooniverse
-team.\footnote{The \sw web application code is open source and can be accessed
+team.\footnote{The \SW web application code is open source and can be accessed
 from \texttt{https://github.com/zooniverse/Lens-Zoo}}  The focus of the CI is a
@@
 need to learn what lenses do not look like, in order to reduce the false
-positive detection rate. There are three primary mechanisms in the \sw system
+positive detection rate. There are three primary mechanisms in the \SW system
 for teaching the volunteers what to look for. These are, in the order in which
@@
 In Figures~\ref{fig:training-gallery:sims}~and~\ref{fig:training-gallery:duds}
-we show example training images from the first \sw project (\Sref{sec:data}
+we show example training images from the first \SW project (\Sref{sec:data}
 below).
@@
 The instant feedback provides real-time educational responses to the
-volunteers as they start classifying; as well as this dynamic system, \sw
+volunteers as they start classifying; as well as this dynamic system, \SW
 provides a static reference work for volunteers to consult when in doubt about
@@
 We refer the reader to \PaperTwo for the details of the particular set of
-imaging survey data used in this first \sw project. Here, we summarize very
+imaging survey data used in this first \SW project. Here, we summarize very
 briefly the choices that were made, in order to provide the context for our
-general description and illustrations of the \sw system.
+general description and illustrations of the \SW system.
 
@@
 lens'' samples, makes this a natural choice against which to develop and test
-the \sw system. The CFHTLS is also well-representative of the data quality
+the \SW system. The CFHTLS is also well-representative of the data quality
 expected from several next-generation sky surveys, such as DES, KiDS, HSC and
@@
 applied this methodology in the two classification stages in the CFHTLS
-project in the \sw Analysis Pipeline (SWAP) code.\footnote{The open source
+project in the \SW Analysis Pipeline (SWAP) code.\footnote{The open source
 SWAP code is available from
@@
 
-While the \sw web app is live, and classifications are being made, we perform an
+While the \SW web app is live, and classifications are being made, we perform an
 online analysis of the classifications,  updating a probabilistic model of every
@@
 \centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_probabilities.png}
-\caption{Typical \SW Agent confusion matrix elements. At a particular
+\caption{Typical \SW agent confusion matrix elements. At a particular
 snapshot, 200 randomly-selected agents are shown distributed over the unit plane, with a
@@
 \centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_histories.png}
-\caption{Typical \SW Agent histories. The ``skill'' of the  same 200 random
+\caption{Typical \SW agent histories. The ``skill'' of the  same 200 random
 agents  as in \Fref{fig:swap:agent-probabilities} is plotted in green as a function
@@
 
-In this section we present our findings about the performance of the  \sw
+In this section we present our findings about the performance of the \SW
 system, in terms of the information  contributed by the crowd in
@@
 \centering\includegraphics[width=0.9\linewidth]{sw-system-figs/all_skill_contribution_experience_education.png}
-\caption{Key properties and contributions of the \sw crowd. Plotted are the
+\caption{Key properties and contributions of the \SW crowd. Plotted are the
 1-D and 2-D marginalized distributions for the logarithms of the
@@
 
-\Fref{fig:crowd:cornerplot} shows the \sw crowd to have quite broad
+\Fref{fig:crowd:cornerplot} shows the \SW crowd to have quite broad
 distributions of logarithmic effort, skill, and contribution. To better
@@
 experienced volunteers (1824 people)  possess just 43\% of the total skill.
-The level of contribution made at \sw by experienced volunteers is largely a
+The level of contribution made at \SW by experienced volunteers is largely a
 matter of choice (or perhaps, availability of time!).
@@
 
-How fast does the \sw crowd classify subjects? Each agent records the timestamp
+How fast does the \SW crowd classify subjects? Each agent records the timestamp
 of each classification its volunteer makes; by measuring the time lags between
@@
 
-We now quantify the performance of the \sw system in terms of the recovery of
+We now quantify the performance of the \SW system in terms of the recovery of
 the training set images. At \StageOne, this set contains around 5712 simulated
@@
 \end{minipage}
-\caption{Receiver operating characteristic curves for the \sw system, using
+\caption{Receiver operating characteristic curves for the \SW system, using
 the CFHTLS training set. Left: \StageOne, right: \StageTwo.}
@@
 \centering\includegraphics[width=\linewidth]{sw-system-figs/completeness_purity.png}
-\caption{Completeness-estimated purity curves for the \sw system, using
+\caption{Completeness-estimated purity curves for the \SW system, using
 the CFHTLS training set.}
@@
 What can we learn from the results of the previous section, for future
-projects? Potential improvements to the \sw system can be divided into three
+projects? Potential improvements to the \SW system can be divided into three
 categories, performance, efficiency and capacity.
@@
 false negatives (blue) and false positives (red) from the classification of
-the \sw CFHTLS training set. The trajectory plot for each of the 4 subjects is
+the \SW CFHTLS training set. The trajectory plot for each of the 4 subjects is
 shown to the right of its image. Lefthand panels show the most common types of
@@
 \Fref{fig:discuss:performance:trajectories} shows 2 example simulated lenses
-that were missed ($\pr(\LENS|C,T) < 10^{-5}$) by the \sw system, and 2 example
+that were missed ($\pr(\LENS|C,T) < 10^{-5}$) by the \SW system, and 2 example
 non-lenses that were incorrectly flagged as candidates ($\pr(\LENS|C,T) >
-0.95$) by the \sw system. While the final \StageTwo analysis was done offline,
+0.95$) by the \SW system. While the final \StageTwo analysis was done offline,
 these trajectory plots still serve to illustrate the approximate
@@
   \hline
+  % \hline {Stage} & Subjects & Contribution                          & Agents & Skill      & Classifications          & Candidates & Information \\
+  %                & $\Ns$    & $\sum_k^{\Nv} \contribution_k$ (bits) & $\Nv$  & $\sum_k^{\Nv} \skill_k$ (bits) & $\sum_k^{\Nv} \thiseffort$ & $\Ncands$  & $\sum_j^{\Ns}\sum_k^{\Nv} \information_{j,k}$ (bits) \\
+  % \hline
+  %           1    & $427064$ & $1292016.3$ & $36982$ & $1471.9$ & $10802125$ & $3368$ & $91122.6$ \\
+  %           2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $90$ &  $1640.4$ \\
   \hline {Stage} & Subjects & Contribution                          & Agents & Skill      & Classifications          & Candidates & Information \\
@@
 
-Finally, we comment on the size of the first \sw crowd, and how the system
+Finally, we comment on the size of the first \SW crowd, and how the system
 might be scaled up for future surveys. In \Sref{sec:results:crowd} and
-\Tref{tab:crowd:contributions}, a rough picture emerged for the \sw crowd of
+\Tref{tab:crowd:contributions}, a rough picture emerged for the \SW crowd of
 it containing a few $10^4$ volunteers, with a few $10^3$ achieving
@@
 increase the rate at which new volunteers become dedicated volunteers. Based
-on feedback from the wider \sw community, this could potentially be achieved
+on feedback from the wider \SW community, this could potentially be achieved
 through closer collaboration with the science team. It's also possible that
@@
 % \begin{itemize}
-% \item How reliably can we find gravitational lenses using the \sw
+% \item How reliably can we find gravitational lenses using the \SW
 % system? What is the completeness of the sample produced likely to be?
@@
 compress these complex, noisy sets of data by asking each volunteer what they
-think about them. A complete  classification in \sw consists of a set of
+think about them. A complete  classification in \SW consists of a set of
 Marker positions, or none at all. The null set encodes the statement from
@@
 volunteer's experience. In this appendix we describe how these agents work,
-and other aspects of the \sw analysis pipeline (SWAP).
+and other aspects of the \SW analysis pipeline (SWAP).
 
@@
 might do the following. Dividing this by the amount of information it takes to
-classify a \sw subject all the way to the detection threshold (lens
+classify a \SW subject all the way to the detection threshold (lens
 probability 0.95), and then multiplying by the survey inefficiency gives us a

### 2015-03-30 doc/sw-publication-policy-des.tex

@@
 (within the logistical constraints). In this document we discuss how the DES SST can become involved with \SW and the relationship
-between the DES survey science team and the \SW collaboration. 
+between the DES SST and the \SW collaboration. 
 This document includes guidelines for proposing projects, data provision, data policy and for publications of \SW-enabled discoveries.
@@
 
-\section{Introduction to \SW}
+\section{Introduction to \sw}
 
@@
 
-\section{Defining a suitable \SW science project}
+\section{Defining a suitable \sw science project}
 \label{sec:project}
@@
 LRGs, groups, clusters, quasars.
-Again this was more images than the SST could manage to inspect alone.
+Again this was more images than the VICS82-SST could manage to inspect alone.
 
@@
 \item Any \SW search should be complementary, not in competition, to the lens finding being conducted by the DES SST itself.
-\item While \SW uses citizen science, its primary goal is \textbf{not outreach}, it is harnessing citizen power for visual classifications (and eventually modelling) powered by citizens to perform science.
+\item While \SW uses citizen science, its primary goal is \textbf{not outreach}, it is harnessing citizen power for visual classifications (and eventually modelling) to perform science.
 \item A duplicate project is not encouraged provided there is sufficient scientific motivation and justification to do so.
@@
 The \SW PIs will be able to discuss any planned \SW-DES projects with the DES SST.
+It is important to bear this in mind for long-term surveys like DES, if needed the crowd needs to be engaged and feel like they are contributing while the entire \SW-DES project runs.
 \item The success of \SW-DES will rely on input from the DES SST working with the \SW collaboration, dedicated effort is required for this and the DES SST should identify team members who can commit time to the \SW-DES tasks for this before embarking on a project.
 The \SW PIs will help to establish the main efforts required, these will depend on the actual project put forward by the DES SST (e.g.
-image preparation, simulations).
+image preparation, simulations, interacting with volunteers on \Talk).
 \end{enumerate}
@@
 
-Please do remember that \SW is setup to provide a service to help your team find lenses, any discovery in \SW-DES is the DES SSTs discovery.
+Please do remember that \SW is setup to provide a service to help your team find lenses.
+Any discovery in \SW-DES is the DES SSTs discovery.
 The goal of the \SW PIs or the \SW collaboration is to enable your science project and make it work.
-Using SWAP we will send the DES SST lists of the candidates selected by the citizens (at some regular intervals or at the end of a project).
-If the DES SST wish to have the \SW Pis input or to collaboratively work on targets the \SW team are happy to become more involved (the \SW Pis have strong lensing science interests) but we will not do anything with the sources found through \SW other than provide it to the DES SST.
-We are happy to then work with you as you wish.
+Using the automatic analysis pipeline (SWAPR) we will send the DES SST lists of the candidates selected by the citizens (at some regular intervals or at the end of a project).
 
-The primary duty of SW PIs is to enable the discovery of lenses through citizen science and forward the catalog of candidates to the SST (the latter part essentially happens automatically through the pipeline SWAPR).
-The SW team is happy to help with further grading of the candidates or assist with any scientific investigations and follow-up of the candidates, if the DES SST so requests.
+If the DES SST wish to have the \SW PIs input or to collaboratively work on targets the \SW team are happy to become more involved (the \SW PIs have strong lensing science interests).  
+The \SW team is happy to help with further grading of the candidates or assist with any scientific investigations and follow-up of the candidates, if the DES SST so requests.
 
-Note all possible candidates are in the public domain as all images are available online (but without WCS information).
-These targets may be discussed by citizens on \SW\,\Talk.
-Members of the DES SST are expected to engage in discussions with citizens through \Talk, which in turn has the very positive effect of motivating the citizens to contribute further.
+\subsection{Previewing images and \Talk}
+We are aware that there is some interest in the DES SST for using the \SW web interface to preview images for the SST themselves.
+This is not the function or purpose of the \SW interface or the Zooniverse.
+However  it will be possible for DES SST members to view the images in parallel with the crowd through the public interface.
+The DES SST members who wish to do this will need to register with the Zooniverse to classify.
+We can extract the classifications of SSTs only to provide and expert selected sample, if required.
+The images marked by any inspector (SST or citizen)  are automatically recorded in an individual's \SW/Zooniverse account.
+These can be accessed through the \SW interface and as a 'collection' in \Talk.
+This collection can be explored (and discussed if required) through the \Talk interface.
 
-\subsection{Previewing images}
-We are aware that there is some interest in the DES SST for using \SW web interface to preview images for the SST themselves.
-As this is not the function of the \SW interface or the Zooniverse, this would only be possible under certain conditions:
-\begin{enumerate}[label=(\alph*)]
-\item the images\footnote{can still be stripped of WCS information (please see Section \ref{sec:data}} inspected are destined to be seen by the crowd  \textbf{in parallel} with the SST, therefore the URL for the inspection will be publicly available.;
-\item the framework of the image presentation (i.e the \SW interface) is the same as the interface presented to the volunteers (image clicks only and no comments or ranking possible);
-\item all SST inspectors would have to register with the Zooniverse to classify.
-\end{enumerate}
+\SW \Talk is a key and integral part of \SW.
+The DES SST are strongly encouraged to interact with the volunteers on \Talk.
+This exchange allows the crowd to learn from the experts, this in turn has the very positive effect of motivating the citizens to contriute further.
+In addition it also results in better and informed classification when they return to that task.
+
+Note that all possible candidates are in the public domain as all images are available online (but without WCS information).
 
@@
 In our experience, a citizen science project like SW cannot function successfully without significant support and co-ordination of the SST.
-Thus, we recommend the all DES members with an nterest in strong lensing are told about \SW and how it can complement their lens finding effort.
+Thus, we recommend that all DES members with an interest in strong lensing are told about \SW and how it can complement their lens finding effort.
 We are here to assist your science!
@@
 
-In particular, for the first potential \SW-DES project (probably on the Y1 data) we encourage the DES SST to strongly consider the timing for when they wish to ingest the images into \SW.
-This could be delayed until the SST has performed all the visual inspection or automated algorithms they wish to to avoid any issue of competition with \SW (if that is a concern).
+We encourage the DES SST to strongly consider the timing for when they wish to ingest the images into \SW so that it is in line with the interests of the DES SST and consortium.
 
@@
 \item Proprietary data issues 
-\item identify a core team who will lead and work closely with \SW
+\item identify an initial core team who will lead and work closely with \SW
 \end{itemize}
@@
 
-\section{Data Preparation \& \SW interface}
+\section{Data Preparation \& the \SW interface}
 \label{sec:data}
@@
 
-\item In {\bf running the \SW analysis pipeline} which will be our responsibility. This will provide candidates to be sent o the DES SST.
+\item In {\bf running the \SW analysis pipeline} which will be our responsibility. This will provide citizen selected candidates to be sent to the DES SST.
 
@@
 \label{sec:papers}
-In return for the work outlined in Section \ref{sec:data} in setting up the new surveys, the \SW PIs will nominate a
-small number of core \SW collaboration members as authors on \textbf{papers that
+In return for the work outlined in Section \ref{sec:data} in setting up the new surveys, the \SW PIs will nominate a core \SW collaboration members as authors on \textbf{papers that
 present discovery of a lens or sample of lenses enabled by the \SW system}.
 A ``discovery'' is defined by the announcement of the source(s) to the astronomical community in a journal paper.
-We would expect the \SW author list to be a small number (less than ten), primarily the Principal Investigators, a few others working on the ingestion of the new data or moderating \Talk.
-All post-discovery follow-up papers would of course be exempt from this: the idea is that \SW is purely a gravitational lens discovery service, but not one that runs by magic.
+We would expect the \SW author list to be a small number (approx.
+ten), primarily the Principal Investigators, a few others working on the ingestion of the new data or moderating \Talk.
+All post-discovery follow-up papers would of course be exempt from this (unless individuals from \sw team had contributed sufficiently such that the lead author wished to include them).
 
-We request that authors of \SW-enabled discovery papers should circulate drafts to the list of \SW authors and allow a minimum of two weeks to give time for comments.
+We request that authors of \SW-enabled discovery papers should circulate drafts to the list of \SW authors and, if possible, allow a minimum of two weeks to give time for comments.
 We also request that any papers based on \SW enabled discoveries should cite the \SW system papers.

### 2015-04-08 doc/sw-system.tex
Brief description of sims, and discussion of strategy, added to section 2.2.2 and flagged in blue for comment. Closes #106

--- 2015-03-29 doc/sw-system.tex
@@
 
-Gravitational lenses are unfamiliar objects to volunteers who are new
-to the site. New volunteers need to learn what lenses look like as quickly as
-possible, so that they can contribute informative classifications. They also
-need to learn what lenses do not look like, in order to reduce the false
-positive detection rate. There are three primary mechanisms in the \sw system
-for teaching the volunteers what to look for. These are, in the order in which
-they are encountered, an inline tutorial, instant feedback,
-and a ``Spotter's Guide.'' As well as this, we provide ``About'', ``FAQ'' and ``Science'' pages explaining the physics of gravitational lensing.
-While we expect that the insight from this static material should help volunteers make sense of the features in the images, we focus on the more dynamic, activity-based training early, when engaging new volunteers to participate takes priority.
+Gravitational lenses are largely unfamiliar objects to the general public. 
+New volunteers need to learn what lenses look like as quickly as possible, so
+that they can contribute informative classifications. They also need to learn
+what lenses do not look like, in order to reduce the false positive detection
+rate. There are three primary mechanisms in the \sw system for teaching the
+volunteers what to look for. These are, in the order in which they are
+encountered, an inline tutorial, instant feedback on ``training images''
+inserted into the stream of images presented to them, and a ``Spotter's
+Guide.'' As well as this, we provide ``About'', ``FAQ'' and ``Science'' pages
+explaining the physics of gravitational lensing. While we expect that the
+insight from this static material should help volunteers make sense of the
+features in the images, we focus on the more dynamic, activity-based training
+early, when engaging new volunteers to participate takes priority.
 
@@
 displayed, and the marking procedure walked through, using pop-up message
-boxes. Subsequent images gradually introduce the more advanced
-features of the classification interface (the QD and Talk buttons), also using
-pop-up messages. The tutorial was purposely kept as short as possible so as to
+boxes. Subsequent images gradually introduce the more advanced features of the
+classification interface (the QD and Talk buttons), also using pop-up
+messages. The tutorial was purposely kept as short as possible so as to
 provide the minimal barrier to entry.
@@
 image, in order to get the volunteers engaged in the real task as quickly as
-possible. Training continues beyond the first image tutorial through
-``training subjects'' inserted randomly into the stream.  These training
-subjects are either simulated lenses (known as ``sims''), or survey images
-that were expert-classified and found not to contain any
-lens candidates (these images are known as ``duds''). The tutorial explains
-that the volunteers  will be shown such training images. They are also
-informed that they will receive instant feedback about their performance after
+possible. However, training then continues, beyond the first image tutorial,
+through ``training subjects'' inserted randomly into the stream.  These
+training subjects are either simulated lenses (known as ``sims''), or survey
+images that were expert-classified and found not to contain any lens
+candidates (these images are known as ``duds''). The tutorial explains that
+the volunteers  will be shown such training images. They are also informed
+that they will receive instant feedback about their performance after
 classifying (blind) any of these training subjects. Indeed, after a volunteer
@@
 
-\todo{PJM}{Insert simulations paragraph here.
-General description of sim generation.
-Principles: use real images, draw from realistic populations, strike balance between easy to see (for education) and realistically difficult (to push sensitivity).
-\#106}.
+\new{Because we include a training set of images in amongst the survey ``test''
+images in this way, \sw can be viewed as a {\it supervised learning} system. 
+Consequently, we should expect to find lens candidates that look like the sims
+that we put in the training set, and so the design of this training set is
+quite important. The training images must look realistic, in two ways. First,
+apart from the simulated lenses they contain, they must look like all the
+other survey images -- otherwise they could be identified as training images
+without the volunteer learning anything about what lenses look like. For this
+reason, we make the sims by {\it adding in} simulated lensed features to real
+images drawn from the survey. It also means that each dataset presented for
+inspection in the \sw interface needs to come with its own training set.}
+
+\new{Second, the lensed features themselves must be realistic; if they did not
+resemble real lenses, we could not expect to find real lenses in the test
+images. The details of how we generated the sims for the CFHTLS project are
+given in \PaperTwo, where we also carry out performance tests relative to real
+lens candidates in the survey fields. Here, we merely note the following
+aspects to place this paper's results in context.}
+
+\new{We start by selecting massive galaxies and groups in the CFHTLS catalogs,
+by color, brightness and photometric redshift. We then assign plausible mass
+distributions to these ``potential lenses:'' a singular isothermal ellipsoid
+model for each massive galaxy, and an additional NFW profile dark matter halo
+for groups and clusters. The mass distributions are centred, elongated and
+aligned with the measured optical properties of the galaxies present. We then
+draw a source from a plausible background population, of either galaxies (for
+the group or galaxy lenses) or quasars (for the galaxy-scale lenses). The
+source redshift, luminosity and size distributions are all chosen to match
+those observed, while the source abundance is artificially increased such that
+each potential lens has a high probability of having a source occur at a
+position that will lead to it being  highly magnified. Source galaxies are
+given plausible surface brightness profiles and ellipticities. We then compute
+the predicted multiple images of the source using the \gravlens ray-tracing
+code \citep{Keeton2000}.}
+
+\new{At this point, the distribution of lens and source properties are quite
+realistic. At this point, we chose to make several cuts, to reject sims that
+were likely to be difficult to spot. While this ensured the educational value
+of the sims when giving feedback, it meant that we should only {\it expect} to
+detect real lens candidates that also pass these cuts. Any real lenses
+candidates we find with properties outside the ranges of the sims may in some
+sense be considered bonuses, a product of the {\it imagination} of the crowd
+in extrapolating their understanding of gravitational lenses into a regime
+where they have not seen any before. In the CFHTLS project, the most important
+selection cuts were to only keep sims with a)  second brightest image brighter
+that $i = 23$ and b) magnification greater than 20 (\PaperTwo, Table 1).}
 

### 2015-04-08 doc/sw-system.tex
Reduced size of figure 12, put to-do note in text #113

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
+\begin{figure}
 \centering\includegraphics[width=\linewidth]{sw-system-figs/completeness_purity.png}
@@
 \label{fig:results:sample:CP}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\todo{Chris}{Can you please remake \Fref{fig:results:sample:CP} with a simpler
+legend? We can take it as read that Stage 1 was online, Stage 2 was offline,
+and the starting values of the matrix elements is 0.5-- and then let's leave
+out the different lens types: I think we might just postpone all of that
+discussion to \PaperTwo. Last thing: can you make the inset bigger please, to
+show us reaching 90\% completeness at 30\% purity? \#113}
 

### 2015-04-09 doc/sw-system.tex
fixes and close #113.
Added full description of HumVI settings top section 3.2, closes #117

--- 2015-04-08 doc/sw-system.tex
@@
 The CFHTLS $g$, $r$ and $i$-band images have the greatest depth and best image
-quality, and we chose to focus on this set (although the $u$ and $z$-band images
-were also available for perusal in Talk). We made colour composite PNG format
-images\footnote{The open source colour image composition code used in this work
-is available from \texttt{http://github.com/drphilmarshall/HumVI}} following the
-prescription of \citet{LuptonEtal2004} \citep[with extensions
-by]{WherryEtal2004}. Specifically, we first rescaled the pixel values of each
-channel image into flux units, and then applied an arcsinh stretch. The stretch
-parameters were optimized by visually inspecting a small randomly-selected
-sample of images, to ensure that the background noise was just visible,  and
-that the centres of bright, intermediate redshift galaxies were not saturated.
-The color scales were chosen to maximize the contrast between faint extended
-objects. These parameters were then fixed during the production of all the
-tiles, in order to allow straightforward comparison between one image and
-another, and for intuition to be built up about the appearance of stars and
-galaxies across the survey. Alternative algorithms, such as adjusting the
-stretch and scale dynamically according to, for example, the root-mean-square
-pixel value in each image, can lead to better presentation of bright objects,
-but in doing so they tend to hide the faint features in those images: we needed
-to optimize the detectability of these faint features.   Examples of CFHTLS
-training set images prepared in this way can be seen in the galleries of the
-previous section (Figures~\ref{fig:training-gallery:sims}
-and~\ref{fig:training-gallery:duds}).
-We also defined two alternative sets of visualization parameters, to display a ``bluer'' image and a ``brighter'' image in the classification interface Quick Dashboard (\Sref{sec:design:interface}).
-The QD code performs the same image composition as just described, but dynamically on FITS images in the browser.
-These FITS images are also available for viewing in Talk, via the main Zooniverse Dashboard image display tool, which again offers the same stretch settings, as a starting point for image exploration.
+quality, and we chose to focus on this set (although the $u$ and $z$-band
+images were also available for perusal in Talk). \new{We made colour composite PNG
+format images
+following the prescription of \citet{LuptonEtal2004} \citep[with extensions
+by][and some particular choices of our own]{WherryEtal2004}, using the \humvi
+software.\footnote{The \humvi colour image composition code used in
+this work is open source and available from \texttt{http://github.com/drphilmarshall/HumVI}} Specifically, we
+first rescaled the pixel values of each image, in the notation of
+\citeauthor{LuptonEtal2004}) into flux units (``picomaggies,''), via the image
+AB zeropoint $m_0$ and the pixel value calibration factor $f$  given by
+$\log_{10}{f} = 0.4(30.0 - m_0)$. We then applied further aesthetic
+``scales'' $s_{i,r,g}$ before computing the intensity image $I$ and applying
+an arcsinh stretch. (The scales are re-normalized to sum to one.) Thus, the red
+($R$), green ($G$) and blue ($B$) channel images correspond to the CFHTLS $i$,
+$r$ and $g$-band images in the following way:
+\bea
+I & = & (i \cdot s_i + r \cdot s_r + g \cdot s_g), \notag \\
+R & = & i \cdot s_i \cdot \frac{{\rm asinh}\left(\alpha \cdot Q \cdot I\right)}{Q \cdot I}, \notag \\
+G & = & r \cdot s_r \cdot \frac{{\rm asinh}\left(\alpha \cdot Q \cdot I\right)}{Q \cdot I}, \notag \\
+B & = & g \cdot s_g \cdot \frac{{\rm asinh}\left(\alpha \cdot Q \cdot I\right)}{Q \cdot I}. \notag \\
+\eea
+We chose to allow the composite image formed from these channel images to
+saturate to white: any pixels in any of the channel images lying outside the
+range 0 to 1 was assigned the value 0 or 1 appropriately. This was not the
+recommendation of \citet{LuptonEtal2004}, but we found it to give very
+informative but also familiar-looking astronomical images.}
+
+\new{The non-linearity parameters $Q$ and $\alpha$ control the brightness and
+contrast of the images. We first tuned $\alpha$ (which acts as an additional
+scale factor) until the background noise was just visible. Then we tuned the
+colour scales $s$ to find a balance between exposing the low surface
+brightness blue features (important for lens spotting!), and having the noise
+appear to have equal red, green and blue components. Non-linearity sets in at
+about $1/(Q \alpha)$ in the  scaled intensity image: finally, tuning $Q$ at
+fixed $\alpha$ determines the appearance of bright galaxies, which we need to
+be suppressed enough to allow the low surface brightness features to show
+through, but not so much that they no longer looked like massive galaxies.}
+
+These parameters were then fixed during the production of all the tiles, in
+order to allow straightforward comparison between one image and another, and
+for intuition to be built up about the appearance of stars and galaxies across
+the survey. Alternative algorithms, such as adjusting the stretch and scale
+dynamically according to, for example, the root-mean-square pixel value in
+each image, can lead to better presentation of bright objects, but in doing so
+they tend to hide the faint features in those images: we needed to optimize
+the detectability of these faint features.   Examples of CFHTLS training set
+images prepared in this way can be seen in the galleries of the previous
+section (Figures~\ref{fig:training-gallery:sims}
+and~\ref{fig:training-gallery:duds}). We also defined two alternative sets of
+visualization parameters, to display a ``bluer'' image and a ``brighter''
+image in the classification interface Quick Dashboard
+(\Sref{sec:design:interface}). The QD code performs the same image composition
+as just described, but dynamically on FITS images in the browser. These FITS
+images are also available for viewing in Talk, via the main Zooniverse
+Dashboard image display tool, which again offers the same stretch settings, as
+a starting point for image exploration. Our parameter choices are given in
+\Tref{tab:data:humvi}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}
+\begin{center}
+\caption{Example \humvi image display parameters, for the CFHTLS images.}
+\label{tab:data:humvi}
+\begin{tabular}{cccc}
+  \hline
+  \hline {Image} & Scales ${s_i,s_r,s_g}$ & $\alpha$ & $Q$ \\                         
+  \hline
+    ``Standard'' &    ${0.4,0.6,1.7}$     &   0.09   & 1.0 \\
+    ``Brighter'' &    ${0.4,0.6,1.7}$     &   0.17   & 1.0 \\
+       ``Bluer'' &    ${0.4,0.6,2.5}$     &   0.11   & 2.0 \\
+  \hline \hline
+\end{tabular}
+\medskip\\
+\end{center}
+\end{table}
+% Quck Dashboard code: https://github.com/zooniverse/Lens-Zoo/blob/vics82/app/controllers/quick_dashboard.coffee
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\centering\includegraphics[width=\linewidth]{sw-system-figs/completeness_purity.png}
+\begin{figure}
+\centering\includegraphics[width=\linewidth]{sw-system-figs/completeness_purity_simple.png}
 \caption{Completeness-estimated purity curves for the \sw system, using
@@
 \label{fig:results:sample:CP}
-\end{figure*}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-04-09 doc/sw-cfhtls.tex
rearranged results section and added a few para on citizens value; phil and i will make edits together on this version

@@
 
-We report the discovery of 61 new lens candidates in the CFHT Legacy Survey data
-(\cfhtls) based on about 11 million classifications performed by citizen
-scientists as part of the first blind lens search undertaken by \sw.  The
-principle goal of this lens search was to identify lenses missed by lens finding
-robots (the \rf on galaxy scales and \af on group/cluster scales), which have
-been previously used to mine the \cfhtls data for lenses.  We compare the
-properties of known lens samples detected by these algorithms to the \sw sample
-and found that they are broadly similar.  The image separation distribution
-calculated from the combined sample of known and new lens candidates shows that
-our previous constraints on the average density profile of the lens population
-are robust.  In addition to recovering about 60\% of the known sample, the new
-\sw candidates possess a richer variety compared to the lenses found by the two
-robots. We find that analyzing only those classifications which are performed by
-the more skilled volunteers, \sw can achieve a detection rate of up to 75\%.
-Training and calibration of the performance of citizen scientists is crucial for
-the success of \sw. We also present the SIMCT pipeline, used for generating a
-sample of realistic simulated lensed images in the CFHTLS, and a sample of duds
-and false positives used in the training.  Such a training sample has a legacy
-value for testing future lens finding algorithms. We make our training sample
+%%% ENSURE WORD LIMIT IS 250
+We report the discovery of 28 promising and 58 total new lens candidates
+in the CFHT Legacy Survey data (\cfhtls) based on about 11 million
+classifications performed by citizen scientists as part of the first
+blind lens search undertaken by \sw.  The principle goal of this lens
+search was to identify lenses missed by lens finding robots (the \rf on
+galaxy scales and \af on group/cluster scales), which have been
+previously used to mine the \cfhtls data for lenses.  We compare the
+properties of known lens samples detected by these algorithms to the \sw
+sample and found that they are broadly similar.  The image separation
+distribution calculated from the combined sample of known and new lens
+candidates shows that our previous constraints on the average density
+profile of the lens population are robust.  In addition to recovering
+about 60\% of the known sample, the new \sw candidates possess a richer
+variety compared to the lenses found by the two robots. We find that
+analyzing only those classifications which are performed by the more
+skilled volunteers, \sw can achieve a detection rate of up to 75\% for
+the known lens sample.  Training and calibration of the performance of
+citizen scientists is crucial for the success of \sw. We also present
+the SIMCT pipeline, used for generating a sample of realistic simulated
+lensed images in the CFHTLS, and a sample of duds and false positives
+used in the training.  Such a training sample has a legacy value for
+testing future lens finding algorithms. We make our training sample
 publicly available.
 
-%In summary, \sw
-%has been successful in discovering a large sample of new lens candidates in
-%addition to recovering a substantial fraction of the known lenses in this pilot
-%lens search.
-
 \end{abstract}
-%The simulated sample is also used to make a comparison between human performance against the robots.
 
@@
 lenses have in astrophysics and cosmology. Strong lenses are routinely
-used to probe the dark matter distribution from galaxy (REF) to cluster
-scales (REF), to  study distant young galaxies by using the lensing
-magnification as a natural telescope (REF), to test the cosmological
-model by constraining cosmological parameters such as the Hubble
-constant (REF) and dark energy (REF) and many more. Strong
+used to probe the dark matter distribution from galaxy
+\citep[e.g.][]{Koopmans2006,Barnabe2009,Sonnenfeld2015} to groups-cluster
+scales
+\citep[e.g.][]{Limousin2008,Zitrin2011,Oguri2012,More2012,Newman2013}, to
+study distant young galaxies by using the lensing magnification as a
+natural telescope \citep[e.g.][]{Zitrin2009,Zheng2012,Whitaker2014}, to
+test the cosmological model by constraining cosmological parameters such
+as the Hubble constant and dark energy
+\citep[e.g.][]{Suyu2010,Collett2012,Collett2014,Sereno2014} and many more. Strong
 lenses are rare since a foreground massive object needs to be
@@
 The search for gravitational lenses is a needle-in-a-haystack problem.
-Efficient automated methods are imperative to find a reasonably complete and
-pure sample of strong lenses. Several lens finding algorithms have been
-developed so far for this purpose (REF) but they can not simultaneously capture
-the myriad types of lenses that are known to exist.  For example, the lensed
-images of background galaxies show variety in their surface brightness
-distributions, colors, light profiles, shapes, structures and angular image
-separations.  Moreover, many lensed images appear similar to features found
-commonly in galaxies (such as spiral arms) or to artifacts in astronomical
-images (scattered light around stars).  Almost all lens finding algorithms find
-it difficult to distinguish these from the real lenses and thus, suffer from a
-high rate of false positives.  To minimize this problem, algorithms are often
-restricted to detect a very narrow class of lens systems. However, even after
-such restrictions, robotic lens searches have to always rely on visual screening
-to arrive at a list of plausible candidates.
+Efficient automated methods are imperative to find a reasonably complete
+and pure sample of strong lenses. Several lens finding algorithms have
+been developed so far for this purpose
+\citep[e.g.][]{Lenzen2004,Alard2006,Seidel2007,More2012,Gavazzi2014} but they can not
+simultaneously capture the myriad types of lenses that are known to
+exist. For example, the lensed images of background galaxies show
+variety in their surface brightness distributions, colors, light
+profiles, shapes, structures and angular image separations.  Moreover,
+many lensed images appear similar to features found commonly in galaxies
+(such as spiral arms) or to artifacts in astronomical images (scattered
+light around stars).  Almost all lens finding algorithms find it
+difficult to distinguish these from the real lenses and thus, suffer
+from a high rate of false positives.  To minimize this problem,
+algorithms are often restricted to detect a very narrow class of lens
+systems. However, even after such restrictions, robotic lens searches
+have to always rely on visual screening to arrive at a list of plausible
+candidates.
 
 Recognising patterns amidst an array of noisy pixelated images is one of the
-strengths of human brains (REF). Humans are also capable of dealing with
+strengths of human brains. Humans are also capable of dealing with
 multi-tier complex web of questions before arriving at a conclusion which may
@@
 designed the \sw project to enable the discovery of lenses through citizen
-science.  In Paper I (REF), we describe the design of \sw and how the entire
-system functions as a discovery engine.
+science.  In Paper I \citep{Marshall2015}, we describe the design of \sw and how the entire
+system functions as a discovery service.
 
@@
 %
-%{\bf AM: add one more paragraph that gives some key conclusions and numbers
-%from Paper I}
 %\question{AM}{PJM,AV, should we have this overview section on paper I?}
@@
 In this paper ( Paper II hereafter), we describe our first lens search using
-data from the Canada-France-Hawaii Telescope Legacy Survey (\cfhtls, REF).  This
+data from the Canada-France-Hawaii Telescope Legacy Survey
+\citep[CFHTLS,][]{Gwyn2012}. This
 paper is organised as follows. In \Sref{sec:data}, we introduce the \cfhtls
@@
 has a 1~deg$^2$ field-of-view and a pixel size of 0.186\arcsec. The
-\cfhtls \textsc{WIDE} covers a total area of 171~deg$^2$ on the sky and
-consists of four fields W1, W2, W3 and W4. The field W1 has the
-largest sky coverage of 63.65~deg$^2$. The fields W2 and W4 have similar
-sky coverages of 20.32~deg$^2$ and 20.02~deg$^2$,
+\cfhtls \textsc{WIDE} covers a total non-overlapping area of 150~deg$^2$
+on the sky and consists of four fields W1, W2, W3 and W4. The field W1
+has the largest sky coverage of 63.65~deg$^2$. The fields W2 and W4 have
+similar sky coverages of 20.32~deg$^2$ and 20.02~deg$^2$,
 respectively\footnote{These numbers are estimated from
@@
 
-The \cfhtls imaging is very homogeneous and has great image quality. Most of
+The \cfhtls imaging is very homogeneous and has good image quality. Most of
 the lensed arcs are much brighter in the $g$ band thus, deep imaging in
@@
 
-\subsection{Image Presentation in \sw}
-\label{sec:data:impres}
-%{\it Preparation of data: divide survey into overlapping tiles.
-Presentation of images.
-Uniform scales, to build intuition and avoid rescales due to bright objects.
-Arcsinh stretch, to bring out low SB features.
-Approximately optimized, how?
-Examples of images.}
-
-In order to perform a blind lens search over the entire \cfhtls \textsc{wide},
-we present the users with cutouts of images selected from the survey region. We
-use the $g$, $r$ and $i$-band imaging from \cfhtls which are most useful for visual
-identification of lenses. We also provided access to the $u$ and $z$ band imaging
-data through dashboard, when users wished to take a closer look at a particular system\footnote{The dashboard tool page can be accessed from
-http://tools.zooniverse.org/\#/dashboards/spacewarp}.
-
-We made color composite images using the publicly-available
-code HumVI\footnote{The open source  color image composition code used in this
-work is available from \texttt{http://github.com/drphilmarshall/HumVI}}
-following the prescription of \citet{Lupton2004}. The code
-rescales the pixel values of each channel image into flux units, and
-then applies an arcsinh stretch. The stretch parameters are chosen
-using a small random sample of images, to ensure that the background
-noise is just visible, and that the centres of bright, intermediate
-redshift galaxies are not saturated. The color scales are chosen to
-maximize the contrast between faint extended objects. These parameters
-are then fixed during the production of all the tiles, in order to
-allow straightforward comparison between one image and another, and for
-intuition to be built up about the appearance of stars and galaxies
-across the survey.
-
-We extract contiguous cutouts of size 81.84\arcsec\ (440 pixels) with an
-overlapping region of 10\arcsec (54 pixels) between the neighbouring
-cutouts. This  results in a catalog of $\sim$ 430 000 cutouts for the entire \cfhtls
-\textsc{wide} region. The size of the individual cutout is determined by
-optimising factors such as the typical angular scales of gravitational
-lenses, the number of objects seen in a single cutout and the total
-number of image cutouts in the survey. It is possible that a lens
-candidate happens to be too close to the edge of a cutout, the overlap
-between neighbouring cutout allows the inspector to get a clearer view
-of the same candidate in at least one of the cutouts. We note that since
-the images are shown randomly, an inspector may not necessarily come
-across the neighbouring cutout unless the inspector classifies a large
-number of images. This is not a problem since our user base is extremely
-large and we receive multiple classifications for the same cutout.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Existing \cfhtls lens samples}
+\subsection{Previously published lens samples from the \cfhtls}
 \label{sec:data:kls}
 
-The \cfhtls data has been searched for lenses using semi-automated algorithms,
-primarily, in the $g$ band where the predominantly  faint blue  source
-galaxies are bright compared to the predominantly red deflector galaxies.
-Here, we briefly mention the lens samples which were known to the authors
-prior to the lens search with \sw.
-
-At galaxy-scales, two primary lens searches have been carried out in
-\cfhtls. The \rf \citep{Gavazzi2014} was used for finding compact rings
-or arcs around centers of isolated and massive early-type galaxies. The
-\rf subtracts the PSF-matched $i$-band images from the $g$-band images,
-and looks for excess flux in the bluer $g$-band. An object detector
-measures the properties of these residual blue features, and candidates
-which meet the length-width ratio and tangential alignment criteria are
-then visually inspected to form the final sample. \citet{Gavazzi2014}
-pre-selected $\sim$638,000 targets as either photometrically-classified
-early type galaxies, or objects selected to have red centers and blue
-outer parts, from the T06 CFHTLS data release catalogs.  14370 were
-found to show detectable blue residuals, and 2524 were visually
-inspected, having passed the automatic feature selection process. This
-led to a total of 330 lens candidates out of which 42 are good quality
-(\texttt{q\_flag} = 3) and 288 are medium quality (\texttt{q\_flag} = 2)
-candidates. In addition to this well defined sample, \citet{Gavazzi2014}
-reported a further 71 serendipitously detected lens candidates.  From
-this sample of ``\rf candidates,'' the SL2S team found, during their
-follow-up campaign, 33 confirmed lenses (and 17 promising candidates).
-{\bf AM: check if any of these are from \cfhtls DEEP?}
-
-The second galaxy-scale lens search was to find edge-on galaxy lenses in the
-\cfhtls \citep{Sygnet2010} by selecting galaxies based on profile fits in the
-$i$-band performed using {\sc Sextractor} and with low inclination angle. This
-sample has about 3 promising and a total of 18 lens candidates.
-{\bf AM: perhaps, this should go in additional samples because this was not
-used as one of the known samples,check ?}
-
-Lastly, the \af \citep{More2012} was used for finding blue arc-like features in
+The \cfhtls has been searched for lenses using various lens finding
+methods and algorithms. Here, we give a brief summary of previously published lens
+samples in chronological order.
+
+In the thesis dissertation of \citet{Thanjavur2009}, 9 promising and 2
+low probability candidates are reported which were discovered
+serendipitiously. These detections were made during the visual
+inspection of the \cfhtls images as part of data reduction procedures
+for the Weak Lensing survey \citep{Benjamin2007}.
+
+\citet{Sygnet2010} carried out a search for edge-on galaxy lenses in the
+\cfhtls WIDE. They identified galaxies, using {\sc Sextractor}, which
+have $18<i<21$ and only those with inclination angle $<25$~deg. With a
+few more selection criteria and visual inspection, they found about 3
+promising and a total of 18 lens candidates.
+
+The \af \citep{More2012} was used for finding blue arc-like features in
 the complete \cfhtls data without any pre-selection on the type of the lensing
@@
 
-For the purposes of transparency and to help with the training,
-the volunteers participating in \sw-\cfhtls lens search were made aware of
-these known lens samples. Images containing the systems from the above samples
-were labelled as ``Known Lens Candidates'' in the Talk forum, where volunteers
-have the opportunity to discuss their findings with fellow volunteers and the
-science team. In this paper, we refer to the sample of 330 \rf and 108
-\af lens candidates as the sample of ``known lens candidates'' and the sample of
-confirmed (or most promising) 33 \rf and 26 \af as the sample of
-``known lenses''.
-
-\question{AM}{AV, add info on other lens samples from the literature?}
+In \citet{Elyiv2013}, they visually inspected a sample of 5500 optical
+counterparts of X-ray point-like sources identified in the XMM-LSS
+imaging of the \cfhtls W1 field. The goal was to discover lensed
+quasars. They find 3 very promising and a total of 18 candidates.
+
+The \rf \citep{Gavazzi2014} was used for finding compact rings or arcs
+around centers of isolated and massive early-type galaxies. The \rf
+subtracts the PSF-matched $i$-band images from the $g$-band images, and
+looks for excess flux in the bluer $g$-band. An object detector measures
+the properties of these residual blue features, and candidates which
+meet the length-width ratio and tangential alignment criteria are then
+visually inspected to form the final sample. \citet{Gavazzi2014}
+pre-selected $\sim$638,000 targets as either photometrically-classified
+early type galaxies, or objects selected to have red centers and blue
+outer parts, from the T06 CFHTLS data release catalogs.  14370 were
+found to show detectable blue residuals, and 2524 were visually
+inspected, having passed the automatic feature selection process. This
+led to a total of 330 lens candidates out of which 42 are good quality
+(\texttt{q\_flag} = 3) and 288 are medium quality (\texttt{q\_flag} = 2)
+candidates. In addition to the main well-defined sample,
+\citet{Gavazzi2014} reported a further 71 candidates were reported
+detected by earlier version of the \rf or from the \cfhtls DEEP.  From
+the main sample of ``\rf candidates,'' the SL2S team found, during their
+follow-up campaign, 33 confirmed lenses (and 17 promising candidates).
+
+The work by \citet{Maturi2014} used the arc finding code of
+\citet{Seidel2007} and color properties of typical arcs to optimize arc
+detection. This new approach was tested on the CFHTLS-Archive-Research
+Survey \citep[CARS,][]{Erben2009} which covers an area of only 37~sq.~deg
+and the entire data was visually inspected to estimate completeness and
+purity of their robotic search. They found 29 candidates with the
+algorithm and 41 candidates through visual inspection alone some of
+which are known from previous searches. Most of these candidates are low
+probability\footnote{http://www.ita.uni-heidelberg.de/˜maturi/Public/arcs}.
+
+The \rf and the \af searches are the only searches that make use of a
+lens finding algorithm that has been run on the entire \cfhtls imaging.
+Thus, these can be considered as the known reference sample from robotic
+searches.  For the purposes of transparency and to help with the
+training, the volunteers participating in \sw-\cfhtls lens search were
+made aware of these two known lens samples. Images containing the
+systems from the \rf and the \af samples were labelled as ``Known Lens
+Candidates'' in the Talk forum, where volunteers have the opportunity to
+discuss their findings with fellow volunteers and the science team. In
+this paper, we refer to the sample of 330 \rf and 108 \af lens
+candidates as the sample of ``known lens candidates'' and the sample of
+confirmed (or most promising) 33 \rf and 26 \af as the sample of ``known
+lenses''. Note that the ``known lens'' sample is a subset of the ``known lens
+candidates'' sample.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Image Presentation in \sw}
+\label{sec:data:impres}
+%{\it Preparation of data: divide survey into overlapping tiles.
+Presentation of images.
+Uniform scales, to build intuition and avoid rescales due to bright objects.
+Arcsinh stretch, to bring out low SB features.
+Approximately optimized, how?
+Examples of images.}
+
+In order to perform a blind lens search over the entire \cfhtls
+\textsc{wide}, we present the volunteers with cutouts of images selected
+from the survey region. We briefly describe the image presentation here
+for completeness but more information can be found in Paper I. We use
+the $g$, $r$ and $i$-band imaging from \cfhtls which are most useful for
+visual identification of lenses.  We made color composite images using
+the publicly-available code, HumVI\footnote{The open source  color image
+composition code used in this work is available from
+\texttt{http://github.com/drphilmarshall/HumVI}} following the
+prescription of \citet{Lupton2004}. The color scales are chosen to
+maximize the contrast between faint extended objects. These parameters
+are then fixed during the production of all the tiles, in order to allow
+straightforward comparison between one image and another, and for
+intuition to be built up about the appearance of stars and galaxies
+across the survey.
+
+We extract contiguous cutouts of size 81.84\arcsec\ (440 pixels) with an
+overlapping region of 10\arcsec (54 pixels) between the neighbouring
+cutouts. This  results in a catalog of $\sim$ 430 000 cutouts for the entire \cfhtls
+\textsc{wide} region. The size of the individual cutout is determined by
+optimising factors such as the typical angular scales of gravitational
+lenses, the number of objects seen in a single cutout and the total
+number of image cutouts in the survey. It is possible that a lens
+candidate happens to be too close to the edge of a cutout, the overlap
+between neighbouring cutout allows the inspector to get a clearer view
+of the same candidate in at least one of the cutouts. We note that since
+the images are shown randomly, an inspector may not necessarily come
+across the neighbouring cutout unless the inspector classifies a large
+number of images. This is not a problem since our user base is extremely
+large and we receive multiple classifications for the same cutout.
+%We also provided access to the $u$ and $z$ band imaging
+%data through dashboard, when the volunteers wished to take a closer look at a particular system\footnote{The dashboard tool page can be accessed from
+%http://tools.zooniverse.org/\#/dashboards/spacewarp}.
+
+%The code rescales the pixel values of each channel image into flux units, and
+%then applies an arcsinh stretch. The stretch parameters are chosen
+%using a small random sample of images, to ensure that the background
+%noise is just visible, and that the centres of bright, intermediate
+%redshift galaxies are not saturated.
 
@@
 known lens galaxy for our simulation purpose, we exclude all those galaxies
-whose positions match with the lensing galaxies from the known \cfhtls~SL2S lens
-samples \cite{More2012} within 2~arcsec (XXX check).
+whose positions match with the lensing galaxies from the SARCS
+samples within 2~arcsec (XXX check).
 
@@
 ($z_l$) from the LRG catalog. We use the $L-\sigma$ scaling relation from the
-bright sample of \citep{Parker2007} to set the velocity dispersion of the halo
+bright sample of \citep{Parker2005} to set the velocity dispersion of the halo
 hosting the galaxy which will be later used in the model
@@
 \end{table}
+%{\bf check the units and confirm the numbers in this table etc.}
+
 \subsubsection{Groups-scale lenses}
@@
 \end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\question{AM}{PJM,AV, 1. Any preference for which of the following words should be
-used? My preference: volunteers (most of the times) and citizen scientists (some
-times because it suits the context better)
-2. Add anything else to this section?}
-{\bf AM: Check and homogenize use of the words citizen scientists, citizens, users,
-volunteers throughout the text.}
-
-\section{Results}
-\label{sec:results}
-
-\subsection{\sw Lens Sample}
+\section{Methodology to produce the \sw-\cfhtls Lens Sample}
 
@@
 
-Each subject (or image cutout) is assigned a prior probability of $2\times10^{-4}$ to
-contain a lens system. Every volunteer or classifier is assigned a $2\times2$
-confusion matrix, which quantifies the volunteer's ability to correctly classify
-an image to contain ($P_L$) or not contain a lens system ($P_D$). The values of
-the confusion matrix are determined based on the performance of the volunteer on
-the training sample, specifically, $P_L$ (and $P_D$) is determined based on the
-fraction of simulated lenses (and duds) correctly classified. After every
-classification, the prior probability of the classified subject is updated
-based on the classification and the volunteer's confusion matrix, according to the
-Bayes theorem.  The volunteer's confusion matrix is updated after the classification
-of every training image. Threshold values for the probabilities to accept (or
-reject) a subject  if it contains (or doesn not contain) a lens can be
-chosen in SWAP. Those images which cross these threshold values are retired and
-are not subsequently shown to the volunteers, so that volunteers can use their
-time efficiently to classify previously unclassified subjects.
+Each subject (or image cutout) is assigned a prior probability of
+$2\times10^{-4}$ to contain a lens system. Every volunteer or classifier
+is assigned an agent characterised by a $2\times2$ confusion matrix,
+which quantifies the volunteer's ability to correctly classify an image
+to contain ($P_L$) or not contain a lens system ($P_D$). The values of
+the confusion matrix are determined based on the performance of the
+volunteer on the training sample, specifically, $P_L$ (and $P_D$) is
+determined based on the fraction of simulated lenses (and duds)
+correctly classified. After every classification, the agent updates the
+prior probability of the classified subject based on the classification
+and the volunteer's confusion matrix, according to the Bayes theorem.
+Note that the volunteer's confusion matrix is updated after the
+classification of every training image. Threshold values for the
+probabilities to accept (or reject) a subject  if it contains (or doesn
+not contain) a lens can be chosen in SWAP. Those images which cross
+these threshold values are retired and are not subsequently shown to the
+volunteers, so that volunteers can use their time efficiently to
+classify previously unclassified subjects.
 
@@
 
-We decide to inspect top few hundreds of subjects from a catalog of descending P
-values as a reasonable sample size for visual inspection. We find 665 subjects
-with P$>0.3$ in the catalog. These subjects are then visually inspected by three
-lens experts (AM, AV, PJM). The subjects are assigned grades on a scale of 0 to
-3, thus dividing the subjects into candidates that almost certainly do not
-contain a lens, possibly a lens, probably a lens and almost certainly a lens,
-respectively. We find XXX candidates with averaged grade $0<$G$<1.3$ (low
-probability sample) and XXX candidates with G$\ge1.3$ (high probability sample).
-Further information on the low probability sample such as their positions and
-images are available at XXX. Among the high probability sample, there are XXX
-known candidates and XXX new candidates. To avoid duplicity, further information
-on the \sw detected known candidates sample is available at XXX whereas the new
-lens candidate sample is presented below in \Sref{sec:results:newcand}.
+We decided to inspect the top few hundreds of images from a catalog of
+descending P values as a reasonable sample size for visual inspection.
+We find a total of 665 subjects with P$>0.3$ in the catalog. These
+images were then visually inspected by three lens experts (AM, AV, PJM).
+The images are assigned grades on a scale of 0 to 3, thus dividing the
+subjects into candidates that almost certainly do not contain a lens,
+possibly a lens, probably a lens and almost certainly a lens,
+respectively. The final sample of \sw-\cfhtls lens candidates (see
+\Sref{sec:swlens}) is produced by selecting candidates above some
+threshold on the averaged grades.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}
+\label{sec:results}
+
+\subsection{\sw-\cfhtls Lens Sample}
+\label{sec:swlens}
+
+In this section, we describe the \sw-\cfhtls lens sample (henceforth,
+called the \sw lens sample). We find a total of XXX (and XXX new)
+candidates with averaged grade $0<$G$<1.3$ (low probability sample)
+which means at least one of the inspector gave a grade of 1 and the
+maximum grade given by all three inspectors was 1\footnote{If grades
+from the inspectors were found to be discrepant by 2 or more, these were
+discussed and re-graded to resolve the discrepancy}. Further information
+on the low probability sample such as their positions and images are
+available at http://spacewarps.org/\#/projects/CFHTLS/.
+
+There are a total of XXX candidates with $1.3\le$G$<2$ (medium
+probability sample) out of which 30 are new. These grades suggest that,
+most of the times, at least one of the inspectors gave a grade of 2 and
+the maximum grade by all of the inspectors was below 2. Among our high
+probability sample (G$\ge$2), there are a total of XXX candidates out of
+which 28 are new which means at least two of the inspectors gave a grade
+of 2 or higher. To avoid duplication, further information on \sw
+candidates that were previously identified in the literature is
+available at http://spacewarps.org/\#/projects/CFHTLS/ whereas the new
+lens candidate sample of medium-high probability is presented in this
+paper (see \Sref{sec:results:newcand}).
 
@@
 grading allows us to achieve further purity of our sample.
-{\bf AM: give some numbers for the completeness/purity ?}
+%{\bf AM: give some numbers for the completeness/purity ? I will check what grades we gave to the stage 2 detected KLs and comment on it.}
 
@@
 Statistics of detections in \sw }
-\begin{tabular}{l l l l l l l}
+\begin{tabular}{l l l l l}
 \hline
-   &  \multicolumn{2}{c} {\StageOne}  & \multicolumn{4}{c}{\StageTwo} \\
-      & KC  &  KL  & KC & KL & NC & AC\\
+   &  \multicolumn{2}{c} {\StageOne}  & \multicolumn{2}{c}{\StageTwo} \\
+      & KC  &  KL  & KC & KL \\
 \hline
 \hline
-Number  & 128 & 34 & 107  & 34  & 61 & 168\\
-\%  & 29 & 58 & 25 & 58  & 12 & 34\\
-P$_{\rm thresh}$ & 0.95 & 0.95 & 0.3 & 0.3 & 0.3 & 0.3\\
+Number  & 128 & 34 & 107  & 34  \\
+Percentage  & & & & \\
+of recovery & 29 & 58 & 25 & 58  \\
+P$_{\rm thresh}$ & 0.95 & 0.95 & 0.3 & 0.3 \\
+\hline
+   &  \multicolumn{2}{c} {\StageTwo}  &   & \\
+      & NC  &  AC  &  & \\
+\hline
+\hline
+Number  & 58 & 168 &  & \\
+Percentage & & & & \\
+of detection & 12 & 34 &  & \\
+P$_{\rm thresh}$ & 0.3 & 0.3 &  & \\
 
@@
 P$_{\rm thresh}$ -- systems with P above this threshold are selected \\
-Note about \%: For KC and KL, fractions are with respect to the known
-population whereas for NC and AC, fractions are with respect to the
+Note: For KC and KL, Percentages are with respect to the known
+population whereas for NC and AC, percentages are with respect to the
 total population of lens candidates. \\
@@
 
-\subsubsection{New lens candidates from \sw}
+\subsection{New lens candidates from \sw}
 \label{sec:results:newcand}
 
-We give details of the final sample of 61 new lens candidates found by \sw in
+We give basic information about the final sample of 58 new lens
+candidates (medium-high probability) found by \sw in
 Table~\ref{tab:swcands}. We report the candidates with a \sw ID and Name of the
@@
 
-We show images of our new sample in \Fref{fig:lc} which is arranged first in the
-decreasing order of their grades and then increasing order of their positions.
-As the first lens search was a blind search with no preselection of candidates
-using any algorithm, we find various types of lenses, as expected of such a
-search. The final sample consists of both galaxy and groups-scale lens
-candidates. There are detections of elongated arcs and some interesting
-point-like quasar lensed images (there have been no previously known quasar
-lenses in CFHTLS). {\bf AM: Check literature and then comment about this in the
-abstract?} Most of them are brighter in bluer $g$ band but some candidates
-brighter in the redder $i$ band were also found. Since robotic lens searches
-often look for blue colored lensed features, they are very much likely to miss
-such interesting lens candidates.
+We show images of our new sample in \Fref{fig:lc} which is arranged
+first in the decreasing order of their grades and then increasing order
+of their positions. As the first lens search was a blind search with no
+preselection of candidates from any algorithm, we find various types of
+lenses, as expected from such a search. The final sample consists of both
+galaxy and groups-scale lens candidates. There are detections of
+elongated arcs and some interesting point-like quasar lensed images.
+Most of them are brighter in bluer $g$ band but some candidates brighter
+in the redder $i$ band are also found. Since robotic lens searches
+often look for blue colored lensed features, they are very much likely
+to miss such interesting lens candidates.
+
+The new \sw lens sample presented here shows the advantages of having
+citizen scientists find lenses through visual inspection. An algorithm,
+by definition will find objects that adhere to a selection criteria that
+uses either geometry or flux information from an image. On the other
+hand, citizen scientists can do amazing amount of interpolation or
+extrapolation over the basic selection criteria provided to them. 
+For example,  the lower blue arc in SW7 is split by a small red galaxy.
+An algorithm typically fails to detect such arcs because the arc is
+broken into smaller arclets which then falls below the minimum length or
+area allowed for an arc to be detected typically. Human brains have no
+problem in interpolating over the broken blue arc over the red galaxy
+and understand that it is a single long arc. The system SW19 has
+point-like lensed images which cannot be detected by arc finding
+algorithm whereas the ring finding algorithm may miss this because of
+atypical color and structure of the galaxy.
+
+The power of citizen scientists lies in the high dynamic range that
+allows us to detect systems with very from small-to-large arcs, from
+highly compact-to-low surface brightness images, from round and
+point-like to elongated and curved images, from blue-to-red, from
+regular-to-exotic kinds of lenses while keeping the false positive rate
+comparatively low. Further detailed qualitative and quantitative
+analysis of the properties of the entire \sw sample (new and previously
+identified candidates) and the mass modelling analyses for the new
+candidates is deferred to a subsequent \sw paper, Paper III.
 
@@
 
-\subsection{Recovery of known \cfhtls lenses with \sw}
+\subsection{Recovery of known lens samples from the \cfhtls by \sw}
 \label{sec:results:known}
@@
 We determine what fraction of the known sample of lenses are recovered
-by \sw. In Table~\ref{tab:stats}, we show that $\sim$~25\%-30\% of the
-known candidates and $\sim$~60\% of the known lenses are found at \StageOne and \StageTwo in \sw. The left and the middle panels of \Fref{fig:compre}
-show the fraction of detections as a function of arc magnitude and the
-Einstein radius of the lens systems for the known confirmed lenses and
-lens candidates. As expected, we find that systems with brighter images
+by \sw. Note that this sample corresponds to the \rf and \af samples
+combined, as mentioned in \Sref{sec:data:kls}. In Table~\ref{tab:stats},
+we show that $\sim$~25\%-30\% of the known lens candidates and
+$\sim$~60\% of the known lenses are found at \StageOne and \StageTwo in
+\sw. The left and the middle panels of \Fref{fig:compre} show the
+fraction of detections as a function of arc magnitude and the Einstein
+radius of the lens systems for the known confirmed lenses and lens
+candidates. As expected, we find that systems with brighter images
 and/or with larger Einstein radii are detected more often in \sw.
@@
 \includegraphics[scale=1.0]{sw-cfhtls-figs/comp_reinst_mag.pdf}
-\caption{ \label{fig:compre} Fraction of lens candidates detected by \sw as a
+\caption{ \label{fig:compre} Fraction of lens candidates recovered by \sw as a
 function of the arc magnitude ($g$ band) and the Einstein radius for three lens
@@
 affect the constraints on the density profile. A blind lens search done
-by visual inspection alone e.g. through \sw citizen scientists may find
+by visual inspection alone, for example, through \sw citizen scientists may find
 lenses missed by the \af search and thereby, improve completeness.
@@
 to clusters.
+%%{\bf AM: understand what Phil wanted to say about AF's (in)completeness}
 
@@
 as lenses. We find that about 40\% of the new \sw candidates fail to
-meet this initial selection criteria e.g. SW1, SW13, SW19, SW22, SW27
-and SW30.  All of the lensing galaxies are bright enough to satisfy the
+meet this initial selection criteria, for example, SW1, SW13, SW19, SW22, SW26
+and SW29.  All of the lensing galaxies are bright enough to satisfy the
 $i<22$ criterion. However, some of them have a bright companion galaxy,
@@
 galaxy are not satisfied. Some of the candidates missed at this stage
-are e.g. SW4, SW5, SW6, SW26, SW36, SW39 and SW47.
+are, for example, SW4, SW5, SW6, SW25, SW35, SW38 and SW45.
 
@@
 
-%%{\bf plot the locations of detected and missed lenses explicitly to see the difference}
 \subsubsection{Volunteer profile}
 
-Here, we investigate if the skill\footnote{see the
-\Aref{appendix:power} for the choice of this term and how it is
-different from that used in paper I} of volunteers is systematically
+Here, we investigate if the power\footnote{see the
+\Aref{appendix:power} for the meaning of this term and how it is
+different from the ``Skill'' defined in paper I} of volunteers is systematically
 different between the sample of detected and missed lenses.
@@
 By how much the P value will change depends on how well the
-volunteers are performing on the training sample. Thus, more skilled
-volunteers will change the P by a large factor compared to the less
-skilled volunteers. This is evident in the trajectory plots as large and
+volunteers are performing on the training sample. Thus, high power
+volunteers will change the P by a large factor compared to the low
+power volunteers. This is evident in the trajectory plots as large and
 small distances in between the consequent points which we refer to as
@@
 kicks seen in the trajectories of the missed lenses seem to be moving
-the subjects to the right. In other words, the more skilled volunteers
+the subjects to the right. In other words, the high power volunteers
 are mostly classifying them as subjects with lens candidates. Further
@@
 four types of volunteers making classifications - those causing positive
-large kicks (correct classifications by more skilled volunteers, those
-causing positive small kicks (correct classifications by less skilled
+large kicks (correct classifications by high power volunteers, those
+causing positive small kicks (correct classifications by low power
 volunteers), those causing negative small kicks (incorrect
-classifications by less skilled volunteers) and those causing negative
-large kicks (incorrect classifications by more skilled volunteers). The
+classifications by low power volunteers) and those causing negative
+large kicks (incorrect classifications by high power volunteers). The
 four histograms in the figure correspond to these four types of
@@
 positive small kicks for the detected sample is higher than the missed
-sample suggesting that the fraction of more skilled volunteers is large
+sample suggesting that the fraction of high power volunteers is large
 for the detected sample ii) in terms of Nclass, the missed sample is
@@
 for the detected and the missed samples. this is consistent with our
-expectation that more skilled volunteers should not be making incorrect
-classifications.Therefore, lack of more skilled volunteers classifying
+expectation that high power volunteers should not be making incorrect
+classifications.Therefore, lack of high power volunteers classifying
 the missed lenses seems to be one of the major factors.
@@
 kicks. Thus, it may be possible to detect more promising candidates if
-we preferentially show the rejected systems to a few more skilled
+we preferentially show the rejected systems to a few high power
 volunteers. We understand that changing the rejection and acceptance
@@
 different types of volunteers (right). Among the sample of missed
-lenses, most classifications are from the less skilled volunteers
+lenses, most classifications are from the low power volunteers
 identifying these images incorrectly (i.e. $-\Delta$~logP) which
 overshadows the small number of correct identifications (i.e.
-$\Delta$~logP) coming from both the less and the more skilled volunteers
+$\Delta$~logP) coming from both the less and the high power volunteers
 combined. For the detected lens sample, most classifications are correct
-identifications coming from both less and more skilled volunteers.
+identifications coming from both low and high power volunteers.
 }
@@
 $g-r-i$ color images of random regions of the sky taken by the CFHT Legacy
-Survey. The aim of this lens search is to find lenses that have been
+Survey. The aim of this blind lens search is to find lenses that have been
 missed by previous searches done on the \cfhtls with lens finding
@@
 the training images during live classification of real images which
-helps them remain focused and improve their performance over time.
+helps them remain focused and improve their performance over time. More
+details about the design of \sw system and how it works are given in the
+companion paper, Paper I.
 
@@
 
-%For the simulated sample, we use the photometric and redshift
-%catalogues for the foreground galaxies and additionally, color
-%catalogues for background galaxies and quasars. Scaling relations allow
-%us to relate the light properties to properties such as mass and size
-%to generate lens models. We further account for the instrumental
-%effects such as seeing and noise before creating the simulated lensed
-%features of model background sources. We add the simulated lensed
-%features on top of the real galaxies and groups in the \cfhtls data in
-%all filters. A sample of duds and FPs is vetted visually before
-%ingesting them to the database.
-
-We draw the following conclusions:
+In this paper (Paper II), we present the new \sw sample and compare this
+with the previously known samples from two robotic searches from the
+\cfhtls namely, the \rf and \af. And, further details about the new
+sample such as any follow up confirmation and investigations including
+mass modelling analysis will be presented in a subsequent \sw paper
+(Paper III).
+
+Below, we give some of our conclusions from the first \sw lens search
+and the comparison with robotic searches:
 \begin{itemize}
@@
 
-\item We present a sample of 61 {\bf new} gravitational lens candidates
-with average expert grade of 1.3 and above where 1-mildly interesting,
+\item We present a sample of 58 {\bf new} gravitational lens candidates
+out of which 28 are more promising systems. These candidates received
+averaged grades, G$\ge$1.3 from three experts where 1-mildly interesting,
 2-probably, a lens and 3-certainly, a lens. Another sample of over 100
@@
 
-\question{AM}{PJM and AV, ideas/suggestions/comments on future steps or future lens
-searches?}
-
 \onecolumn
 \begin{center}
-\begin{longtable}{lrrrrrrrrrr}
+\begin{longtable}{llrrrrrrlrr}
 \caption{ \label{tab:swcands}
@@
 which the magnitudes and the redshift are extracted.
+%{\bf Note:} $\dagger$ are systems found in \citet{Gavazzi2014} as part of the additional
+%sample and $\ast$ is found in \citet{Maturi2014} sample.
 }\\
@@
 SW22 & CFHTLS J023008-054038 &   37.5359 &   -5.6774 &  0.6 & 19.7 &  1.9 &  2.0 & ASW0003r61 &  0.5  &  A,E   \\
-SW23 & CFHTLS J023051-082423 &   37.7141 &   -8.4064 &  0.0 &  0.0 &  0.8 &  2.0 & ASW000412m &  0.4  &  A,E   \\
-SW24 & CFHTLS J023315-042243 &   38.3133 &   -4.3789 &  0.7 & 19.7 &  1.0 &  2.0 & ASW00050sk &  0.8  &  A,R   \\
-SW25 & CFHTLS J090308-043252 &  135.7844 &   -4.5479 &  0.0 &  0.0 &  1.2 &  2.0 & ASW00007mq &  0.6  &  A,E   \\
-SW26 & CFHTLS J135755+571722 &  209.4827 &   57.2897 &  0.8 & 20.2 &  1.3 &  2.0 & ASW0005ma2 &  0.8  &  D,D   \\
-SW27 & CFHTLS J141432+534004 &  213.6372 &   53.6679 &  0.7 & 21.4 &  0.9 &  2.0 & ASW0006jh5 &  0.8  &  A,R   \\
-SW28 & CFHTLS J143055+572431 &  217.7333 &   57.4088 &  0.7 & 19.3 &  1.0 &  2.0 & ASW0007wfj &  0.9  &  A,R   \\
-SW29 & CFHTLS J143838+572647 &  219.6589 &   57.4464 &  0.8 & 20.2 &  1.1 &  2.0 & ASW0008qsm &  0.9  &  A,R   \\
-SW30 & CFHTLS J021057-084450 &   32.7414 &   -8.7474 &  0.0 &  0.0 &  2.5 &  1.7 & ASW0002p8y &  0.4  &  A,G   \\
-SW31 & CFHTLS J021514-092440 &   33.8109 &   -9.4111 &  0.7 & 19.9 &  2.6 &  1.7 & ASW00021r0 &  0.4  &  A,R/G   \\
-SW32 & CFHTLS J022359-083651 &   35.9995 &   -8.6143 &  0.0 &  0.0 &  3.1 &  1.7 & ASW0004iye &  0.4  &  A,E   \\
-SW33 & CFHTLS J022745-062518 &   36.9387 &   -6.4218 &  0.6 & 20.5 &  1.2 &  1.7 & ASW0003s0m &  0.5  &  A,R   \\
-SW34 & CFHTLS J023453-093032 &   38.7232 &   -9.5089 &  0.5 & 19.8 &  0.7 &  1.7 & ASW00051ld &  0.3  &  A,D   \\
-SW35 & CFHTLS J084833-044051 &  132.1385 &   -4.6809 &  0.8 & 20.2 &  0.9 &  1.7 & ASW0004wgd &  0.7  &  A,R   \\
-SW36 & CFHTLS J090248-010232 &  135.7020 &   -1.0424 &  0.4 & 19.1 &  1.4 &  1.7 & ASW000096t &  0.6  &  D,E   \\
-SW37 & CFHTLS J143100+564603 &  217.7511 &   56.7675 &  0.0 &  0.0 &  1.8 &  1.7 & ASW00086xq &  0.8  &  A,E   \\
-SW38 & CFHTLS J143353+542310 &  218.4736 &   54.3862 &  0.8 & 19.8 &  1.6 &  1.7 & ASW0009cox &  0.6  &  A,R/G   \\
-SW39 & CFHTLS J220215+012124 &  330.5635 &    1.3567 &  0.3 & 17.4 &  4.6 &  1.7 & ASW0005qiz &  0.5  &  rA,G   \\
-SW40 & CFHTLS J221306+014708 &  333.2758 &    1.7856 &  0.0 & 17.1 &  1.4 &  1.7 & ASW0008wmr &  0.9  &  A,S   \\
-SW41 & CFHTLS J221513+010240 &  333.8056 &    1.0446 &  0.0 &  0.0 &  0.8 &  1.7 & ASW0008dxh &  0.3  &  A,R/G   \\
-SW42 & CFHTLS J221519+005758 &  333.8321 &    0.9661 &  0.4 & 20.2 &  1.0 &  1.7 & ASW0008xbu &  0.8  &  A,D   \\
-SW43 & CFHTLS J221716+015826 &  334.3189 &    1.9739 &  0.1 & 21.6 &  1.0 &  1.7 & ASW00096rm &  1.0  &  A/R,R   \\
-SW44 & CFHTLS J020810-040220 &   32.0450 &   -4.0389 &  1.0 & 20.8 &  1.8 &  1.3 & ASW0001c3j &  0.7  &  A,R   \\
-SW45 & CFHTLS J021021-093415 &   32.5898 &   -9.5711 &  0.4 & 18.4 &  2.7 &  1.3 & ASW0002k40 &  0.4  &  D,S   \\
-SW46 & CFHTLS J021225-085211 &   33.1051 &   -8.8697 &  0.8 & 19.5 &  2.1 &  1.3 & ASW00024id &  1.0  &  R,R   \\
-SW47 & CFHTLS J021317-084819 &   33.3234 &   -8.8055 &  0.5 & 19.8 &  1.3 &  1.3 & ASW00024q6 &  0.4  &  A,R/E   \\
-SW48 & CFHTLS J022843-063316 &   37.1794 &   -6.5547 &  0.5 & 19.1 &  1.8 &  1.3 & ASW0003r6c &  0.3  &  D/A,E   \\
-SW49 & CFHTLS J090219-053923 &  135.5794 &   -5.6566 &  0.0 &  0.0 &  2.0 &  1.3 & ASW0000g95 &  1.0  &  A,R/E   \\
-SW40 & CFHTLS J090319-040146 &  135.8311 &   -4.0297 &  0.0 & 19.8 &  1.2 &  1.3 & ASW00007ls &  0.5  &  A,R/E   \\
-SW51 & CFHTLS J090333-005829 &  135.8886 &   -0.9749 &  0.0 &  0.0 &  2.1 &  1.3 & ASW00008a0 &  1.0  &  A/D,E/G   \\
-SW52 & CFHTLS J135724+561614 &  209.3536 &   56.2707 &  0.0 &  0.0 &  2.6 &  1.3 & ASW0006e0o &  0.9  &  D,E   \\
-SW53 & CFHTLS J140027+541028 &  210.1164 &   54.1746 &  0.0 &  0.0 &  1.2 &  1.3 & ASW0006a07 &  0.6  &  Q,R/E   \\
-SW54 & CFHTLS J140425+520506 &  211.1062 &   52.0850 &  0.4 & 18.9 &  1.4 &  1.3 & ASW0005o0w &  0.6  &  D,E   \\
-SW55 & CFHTLS J141518+513915 &  213.8290 &   51.6542 &  0.4 & 18.3 &  3.0 &  1.3 & ASW00070vl &  0.8  &  D,E   \\
-SW56 & CFHTLS J142620+561356 &  216.5870 &   56.2323 &  0.5 & 19.5 &  1.3 &  1.3 & ASW0007sez &  0.8  &  A/R,S   \\
-SW57 & CFHTLS J142652+560002 &  216.7201 &   56.0006 &  0.0 &  0.0 &  1.5 &  1.3 & ASW0007t5y &  1.0  &  R,R   \\
-SW58 & CFHTLS J142843+543713 &  217.1815 &   54.6204 &  0.4 & 19.7 &  1.3 &  1.3 & ASW0007pga &  0.6  &  D,D   \\
-SW59 & CFHTLS J143631+571131 &  219.1315 &   57.1922 &  0.7 & 20.9 &  1.3 &  1.3 & ASW0008pag &  0.6  &  D/A,R   \\
-SW60 & CFHTLS J143651+530705 &  219.2150 &   53.1183 &  0.6 & 19.2 &  3.1 &  1.3 & ASW0007h27 &  1.0  &  A,E/G   \\
-SW61 & CFHTLS J143950+544606 &  219.9609 &   54.7686 &  0.0 &  0.0 &  1.7 &  1.3 & ASW00085cp &  0.4  &  A,G/R   \\
+SW23 & CFHTLS J023315-042243 &   38.3133 &   -4.3789 &  0.7 & 19.7 &  1.0 &  2.0 & ASW00050sk &  0.8  &  A,R   \\
+SW24 & CFHTLS J090308-043252 &  135.7844 &   -4.5479 &  0.0 &  0.0 &  1.2 &  2.0 & ASW00007mq &  0.6  &  A,E   \\
+SW25 & CFHTLS J135755+571722 &  209.4827 &   57.2897 &  0.8 & 20.2 &  1.3 &  2.0 & ASW0005ma2 &  0.8  &  D,D   \\
+SW26 & CFHTLS J141432+534004 &  213.6372 &   53.6679 &  0.7 & 21.4 &  0.9 &  2.0 & ASW0006jh5 &  0.8  &  A,R   \\
+SW27 & CFHTLS J143055+572431 &  217.7333 &   57.4088 &  0.7 & 19.3 &  1.0 &  2.0 & ASW0007wfj &  0.9  &  A,R   \\
+SW28 & CFHTLS J143838+572647 &  219.6589 &   57.4464 &  0.8 & 20.2 &  1.1 &  2.0 & ASW0008qsm &  0.9  &  A,R   \\
+SW29 & CFHTLS J021057-084450 &   32.7414 &   -8.7474 &  0.0 &  0.0 &  2.5 &  1.7 & ASW0002p8y &  0.4  &  A,G   \\
+SW30 & CFHTLS J021514-092440 &   33.8109 &   -9.4111 &  0.7 & 19.9 &  2.6 &  1.7 & ASW00021r0 &  0.4  &  A,R/G   \\
+SW31 & CFHTLS J022359-083651 &   35.9995 &   -8.6143 &  0.0 &  0.0 &  3.1 &  1.7 & ASW0004iye &  0.4  &  A,E   \\
+SW32 & CFHTLS J022745-062518 &   36.9387 &   -6.4218 &  0.6 & 20.5 &  1.2 &  1.7 & ASW0003s0m &  0.5  &  A,R   \\
+SW33 & CFHTLS J023453-093032 &   38.7232 &   -9.5089 &  0.5 & 19.8 &  0.7 &  1.7 & ASW00051ld &  0.3  &  A,D   \\
+SW34 & CFHTLS J084833-044051 &  132.1385 &   -4.6809 &  0.8 & 20.2 &  0.9 &  1.7 & ASW0004wgd &  0.7  &  A,R   \\
+SW35 & CFHTLS J090248-010232 &  135.7020 &   -1.0424 &  0.4 & 19.1 &  1.4 &  1.7 & ASW000096t &  0.6  &  D,E   \\
+SW36 & CFHTLS J143100+564603 &  217.7511 &   56.7675 &  0.0 &  0.0 &  1.8 &  1.7 & ASW00086xq &  0.8  &  A,E   \\
+SW37 & CFHTLS J143353+542310 &  218.4736 &   54.3862 &  0.8 & 19.8 &  1.6 &  1.7 & ASW0009cox &  0.6  &  A,R/G   \\
+SW38 & CFHTLS J220215+012124 &  330.5635 &    1.3567 &  0.3 & 17.4 &  4.6 &  1.7 & ASW0005qiz &  0.5  &  rA,G   \\
+SW39 & CFHTLS J221306+014708 &  333.2758 &    1.7856 &  0.0 & 17.1 &  1.4 &  1.7 & ASW0008wmr &  0.9  &  A,S   \\
+SW40 & CFHTLS J221519+005758 &  333.8321 &    0.9661 &  0.4 & 20.2 &  1.0 &  1.7 & ASW0008xbu &  0.8  &  A,D   \\
+SW41 & CFHTLS J221716+015826 &  334.3189 &    1.9739 &  0.1 & 21.6 &  1.0 &  1.7 & ASW00096rm &  1.0  &  A/R,R   \\
+SW42 & CFHTLS J020810-040220 &   32.0450 &   -4.0389 &  1.0 & 20.8 &  1.8 &  1.3 & ASW0001c3j &  0.7  &  A,R   \\
+SW43 & CFHTLS J021021-093415 &   32.5898 &   -9.5711 &  0.4 & 18.4 &  2.7 &  1.3 & ASW0002k40 &  0.4  &  D,S   \\
+SW44 & CFHTLS J021225-085211 &   33.1051 &   -8.8697 &  0.8 & 19.5 &  2.1 &  1.3 & ASW00024id &  1.0  &  R,R   \\
+SW45 & CFHTLS J021317-084819 &   33.3234 &   -8.8055 &  0.5 & 19.8 &  1.3 &  1.3 & ASW00024q6 &  0.4  &  A,R/E   \\
+SW46 & CFHTLS J022843-063316 &   37.1794 &   -6.5547 &  0.5 & 19.1 &  1.8 &  1.3 & ASW0003r6c &  0.3  &  D/A,E   \\
+SW47 & CFHTLS J090219-053923 &  135.5794 &   -5.6566 &  0.0 &  0.0 &  2.0 &  1.3 & ASW0000g95 &  1.0  &  A,R/E   \\
+SW48 & CFHTLS J090319-040146 &  135.8311 &   -4.0297 &  0.0 & 19.8 &  1.2 &  1.3 & ASW00007ls &  0.5  &  A,R/E   \\
+SW49 & CFHTLS J090333-005829 &  135.8886 &   -0.9749 &  0.0 &  0.0 &  2.1 &  1.3 & ASW00008a0 &  1.0  &  A/D,E/G   \\
+SW50 & CFHTLS J135724+561614 &  209.3536 &   56.2707 &  0.0 &  0.0 &  2.6 &  1.3 & ASW0006e0o &  0.9  &  D,E   \\
+SW51 & CFHTLS J140027+541028 &  210.1164 &   54.1746 &  0.0 &  0.0 &  1.2 &  1.3 & ASW0006a07 &  0.6  &  Q,R/E   \\
+SW52 & CFHTLS J141518+513915 &  213.8290 &   51.6542 &  0.4 & 18.3 &  3.0 &  1.3 & ASW00070vl &  0.8  &  D,E   \\
+SW53 & CFHTLS J142620+561356 &  216.5870 &   56.2323 &  0.5 & 19.5 &  1.3 &  1.3 & ASW0007sez &  0.8  &  A/R,S   \\
+SW54 & CFHTLS J142652+560002 &  216.7201 &   56.0006 &  0.0 &  0.0 &  1.5 &  1.3 & ASW0007t5y &  1.0  &  R,R   \\
+SW55 & CFHTLS J142843+543713 &  217.1815 &   54.6204 &  0.4 & 19.7 &  1.3 &  1.3 & ASW0007pga &  0.6  &  D,D   \\
+SW56 & CFHTLS J143631+571131 &  219.1315 &   57.1922 &  0.7 & 20.9 &  1.3 &  1.3 & ASW0008pag &  0.6  &  D/A,R   \\
+SW57 & CFHTLS J143651+530705 &  219.2150 &   53.1183 &  0.6 & 19.2 &  3.1 &  1.3 & ASW0007h27 &  1.0  &  A,E/G   \\
+SW58 & CFHTLS J143950+544606 &  219.9609 &   54.7686 &  0.0 &  0.0 &  1.7 &  1.3 & ASW00085cp &  0.4  &  A,G/R   \\
+
 \end{longtable}
@@
 
+%%SW23$^{\dagger}$ & CFHTLS J023051-082423 &   37.7141 &   -8.4064 &  0.0 &  0.0 &  0.8 &  2.0 & ASW000412m &  0.4  &  A,E   \\
+%%SW41$^{\ast}$ & CFHTLS J221513+010240 &  333.8056 &    1.0446 &  0.0 &  0.0 &  0.8 &  1.7 & ASW0008dxh &  0.3  &  A,R/G   \\
+%%SW54$^{\dagger}$ & CFHTLS J140425+520506 &  211.1062 &   52.0850 &  0.4 & 18.9 &  1.4 &  1.3 & ASW0005o0w &  0.6  &  D,E   \\
 \twocolumn
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section*{Acknowledgements}
@@
 In \PaperOne, we defined the ``Skill'' of an agent as being given by the
-expectation value of the information gain per classification. This quantity is a
-non-linear function of both the $P_{\rm L}$, the probability of correctly
-identifying a lens as a lens and $P_{\rm D}$, the probability of correctly
-identifying a dud as a dud. This means that one can get the same value of Skill
-for different combinations of $P_{\rm L}$ and $P_{\rm D}$ (see Fig. XXX) -- it
-reflect the all-round ability of a classifier to contribute information.
-
-As described in the appendix of \PaperOne, the posterior probability $P$ of a
-subject is determined by the $P_{\rm L}$ and $P_{\rm D}$ of all the volunteers
-who marked it, via Bayes' Theorem. Each agent will apply a different ``kick'' to
-the subject probability, $\Delta\log(P)$, which can be either positive (if the
-classifier thinks it contains a lens) or negative (if they don't). These kicks
-appear as steps on the subject's trajectory plot. This kick magnitude gives a useful measure of an agent's ``Power'' to move subjects closer to detection.
-Note that a volunteer who is very good at rejecting duds, but not so good
-at identifying lenses, may have a high Skill but a low Power (since they may fail to detect many of the interesting lenses): Power provides a more precise quantification of a classifier's ability to detect lenses.
+expectation value of the information gain per classification. This
+quantity is a non-linear function of both the $P_{\rm L}$, the
+probability of correctly identifying a lens as a lens and $P_{\rm D}$,
+the probability of correctly identifying a dud as a dud. This means that
+one can get the same value of Skill for different combinations of
+$P_{\rm L}$ and $P_{\rm D}$ (see the left panel of
+\Fref{fig:skilldlnp}). The skill reflects the all-round ability of a
+classifier to contribute information.
+
+As described in the appendix of \PaperOne, the posterior probability $P$
+of a subject is determined by the $P_{\rm L}$ and $P_{\rm D}$ of all the
+volunteers who clicked on the subject, via Bayes' Theorem. Each agent
+will apply a ``kick'' of a different size to the subject probability,
+$\Delta\log(P)$, which can be either positive (if the classifier thinks
+the subject contains a lens) or negative (if the classifier thinks the
+subject does not contain a lens). For instance, given a subject
+(not) containing a lens, a volunteer with high ($P_{\rm D}$) $P_{\rm L}$
+implies a large (negative) positive kick irrespective the value of
+($P_{\rm L}$) $P_{\rm D}$ as shown in the (right most) middle panel of
+\Fref{fig:skilldlnp}. However, large (negative) positive kicks are
+still possible for a volunteer located in the (lower) upper triangle
+with different combinations of ($P_{\rm L}$,$P_{\rm D}$) suggesting that
+the kick is not a simple function of ($P_{\rm L}$,$P_{\rm D}$).
+
+The kicks appear as steps on the subject's trajectory plot. This kick
+magnitude gives a useful measure of an agent's ``Power'' to move
+subjects closer to detection.  Note that a volunteer who is very good at
+rejecting duds, but not so good at identifying lenses, may have a high
+Skill but a low Power (since they may fail to detect many of the
+interesting lenses): Power provides a more precise quantification of a
+classifier's ability to detect lenses (compared to rejecting non-lenses).
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=1.0]{sw-cfhtls-figs/dlnp_skill.pdf}
+\caption{ \label{fig:skilldlnp}
+Skill of the volunteers, $\Delta\log(P)$ given a lens or not a lens in
+an image as a function of $P_{\rm L}$ and $P_{\rm D}$. Each of these
+quantities represent ability of the Volunteers but do not have a simple
+linear relation with $P_{\rm L}$ and $P_{\rm D}$.  
+\question{AM}{PJM, should we just use power everywhere instead of the
+$\Delta\log(P)$? This figure and this section still needs to be
+polished.}
+}
+\end{center}
+\end{figure*}
 
@@
 %the sims ID, 69 det and 1 rej (nearly 100% detected) whereas the
-%corresponding test IDs 30det-30rej (nearly 50% detected and 50%lost)}
+%corresponding test IDs 30det-30rej (nearly 50% detected and 50%lost) --
+%what does this mean?}
 
@@
 \bibliographystyle{apj}
-\bibliography{references}
 %\bibliography{references}
+\bibliography{references_cfhtls}
 

### 2015-04-10 doc/sw-cfhtls.tex
went through Sect 1-2, changed last fig.

@@
 %%% ENSURE WORD LIMIT IS 250
-We report the discovery of 28 promising and 58 total new lens candidates
-in the CFHT Legacy Survey data (\cfhtls) based on about 11 million
-classifications performed by citizen scientists as part of the first
-blind lens search undertaken by \sw.  The principle goal of this lens
-search was to identify lenses missed by lens finding robots (the \rf on
-galaxy scales and \af on group/cluster scales), which have been
-previously used to mine the \cfhtls data for lenses.  We compare the
-properties of known lens samples detected by these algorithms to the \sw
-sample and found that they are broadly similar.  The image separation
-distribution calculated from the combined sample of known and new lens
-candidates shows that our previous constraints on the average density
-profile of the lens population are robust.  In addition to recovering
-about 60\% of the known sample, the new \sw candidates possess a richer
-variety compared to the lenses found by the two robots. We find that
-analyzing only those classifications which are performed by the more
-skilled volunteers, \sw can achieve a detection rate of up to 75\% for
-the known lens sample.  Training and calibration of the performance of
-citizen scientists is crucial for the success of \sw. We also present
-the SIMCT pipeline, used for generating a sample of realistic simulated
-lensed images in the CFHTLS, and a sample of duds and false positives
-used in the training.  Such a training sample has a legacy value for
-testing future lens finding algorithms. We make our training sample
-publicly available.
+We report the discovery of 28 promising and a total of 58 new lens
+candidates from the CFHT Legacy Survey (\cfhtls) based on about 11
+million classifications performed by citizen scientists as part of the
+first \sw lens search.  The goal of the blind lens search was to
+identify lenses missed by lens finding robots (the \rf on galaxy scales
+and \af on group/cluster scales), which have been previously used to
+mine the \cfhtls for lenses.  We compare some properties of lens samples
+detected by these algorithms to the \sw sample and found that they are
+broadly similar.  The image separation distribution calculated from the
+\sw discovered sample shows that our previous constraints on the average
+density profile of the lens population are robust. \sw recovers about
+60\% of the known sample and the new candidates show a richer variety
+compared to the lenses found by the two robots. We find that analyzing
+only those classifications which are performed by the high power
+volunteers, \sw can achieve a detection rate of up to 75\% of the known
+lens sample.  Training and calibration of the performance of citizen
+scientists is crucial for the success of \sw. We also present the SIMCT
+pipeline, used for generating a sample of realistic simulated lensed
+images in the CFHTLS, and a sample of duds and false positives used in
+the training.  Such a training sample has a legacy value for testing
+future lens finding algorithms. We make our training sample publicly
+available.
+%%% ENSURE WORD LIMIT IS 250
 
@@
 \label{sec:intro}
-
-%{\it Describe various lens finding algorithms and the motivation for this particular project with \cfhtls.
-Already searched by robots: enables comparison of techniques.
-Lenses not yet found by robots, detectable by humans?
-}
 
@@
 and pure sample of strong lenses. Several lens finding algorithms have
-been developed so far for this purpose
+been developed so far 
 \citep[e.g.][]{Lenzen2004,Alard2006,Seidel2007,More2012,Gavazzi2014} but they can not
@@
 difficult to distinguish these from the real lenses and thus, suffer
-from a high rate of false positives.  To minimize this problem,
+from the problems of high rate of false positives.  To minimize this problem,
 algorithms are often restricted to detect a very narrow class of lens
 systems. However, even after such restrictions, robotic lens searches
-have to always rely on visual screening to arrive at a list of plausible
-candidates.
+have to always rely on visual screening to find a sample of plausible
+lens candidates.
 
@@
 strengths of human brains. Humans are also capable of dealing with
-multi-tier complex web of questions before arriving at a conclusion which may
+multi-tiered complex web of questions before arriving at a conclusion which may
 not be always possible to automate. The algorithm by which our brains process a
@@
 finding algorithms are not yet advanced enough to produce better performance
-than visual classifications. Given this, participation of a large community of
+than visual classifications. Therefore, participation of a large community of
 volunteers to help with the visual identification of lenses is extremely
@@
 large area imaging surveys (spanning thousands of square degrees), it is
-the perfect time to tap into the potential of citizen science.
-
-\GZ was the first citizen science project in astronomy, and addressed the
-problem of how to  classify large numbers of galaxies by their morphology
-\citep{Lintott2008}.  From the early results based on morphological
-classifications of galaxies, to several new unexpected and interesting
-discoveries, such as that of green pea galaxies and Hanny's Voorwerp, \GZ
-has been able to harness the potential of citizen scientists.  Since then
-astronomy and non-astronomy projects have been launched under the citizen
-science web portal Zooniverse (http://zooniverse.org). The task of finding
-gravitational lenses is significantly challenging given the fact that these
-lenses are rare. To add to the challenge, not many citizen scientists are
-expected to be aware of the phenomenon of gravitational lensing, and the
-resulting image configurations.  With these significant challenges at hand, we
-designed the \sw project to enable the discovery of lenses through citizen
-science.  In Paper I \citep{Marshall2015}, we describe the design of \sw and how the entire
-system functions as a discovery service.
-
-%
-%\subsection{Paper I: Overview}
-%In Paper I, we give details of the classification interface used by the
-%volunteers. The regular images called test subjects are served randomly from the
-%database. Some of the test subjects are labelled as training subjects because
-%either these have simulated lensed images superposed around real galaxies or
-%there are some false positives in the subjects.  The sample of training subjects
-%is much smaller compared to the sample of test subjects. The training subjects
-%are shown with decreasing frequency to the volunteers depending on how new the
-%volunteers are to the project based on their classification history. However,
-%the frequency of training subjects becomes a constant after XXX classifications
-%from a volunteer.
-%
-%Clicking (or failing to click) on the training subjects results in a
-%pop-up feedback message that congratulates the volunteers or points them
-%to read the Spotter's guide pages. The website has several examples of
-%real lenses and false positives with explanation on the Spotter's guide
-%page. A quick reference to the Spotter's guide is available in the
-%classification interface as well. Additional features to change zoom,
-%contrast and brightness are made available to make a better judgement of
-%the difficult lens candidates.
-%
-%The classification of subjects happens in two serial stages. \StageOne is
-%for quick rejection of all uninteresting subjects. Subjects that passed
-%\StageOne are then reinspected at \StageTwo, for a careful selection of
-%most promising lens candidates. In general, subjects are assigned a
-%small prior probability for it to contain a lens. As each subject is
-%seen by multiple volunteers, the posterior probability P is updated by
-%using the weights of the volunteers. The weights are determined based on
-%how well the volunteers perform on the training sample. Once a subject
-%crosses a threshold (acceptance or rejection), it is retired from the
-%database to ensure that rest of the subjects receive sufficient multiple
-%classifications. This is true for \StageOne with ~10$^5$ subjects but is
-%not required for \StageTwo with only a few thousand subjects.
-%
-%\question{AM}{PJM,AV, should we have this overview section on paper I?}
-%
-
-In this paper ( Paper II hereafter), we describe our first lens search using
-data from the Canada-France-Hawaii Telescope Legacy Survey
-\citep[CFHTLS,][]{Gwyn2012}. This
-paper is organised as follows. In \Sref{sec:data}, we introduce the \cfhtls
-imaging data and the known lens samples from the \cfhtls. In \Sref{sec:ts} and
-\Sref{sec:dfp}, we explain the training sample consisting of simulated lenses,
-duds and false positives generated to aid the \sw volunteers in the lens search.
-In \Sref{sec:results}, we present the new lens candidates from \sw and compare
-\sw to two lens finding algorithms which produced the known \cfhtls lens
-samples. Next, we discuss what kind of lenses are detected or missed by the
-algorithms and \sw in \Sref{sec:discuss}. The summary and conclusions are given
-in \Sref{sec:conclude}.
+a perfect time to tap into the potential of citizen science.
+
+\GZ was the first citizen science project in astronomy, and addressed
+the problem of how to  classify large numbers of galaxies by their
+morphology \citep{Lintott2008}.  From the early results based on
+morphological classifications of galaxies, to several new unexpected and
+interesting discoveries, such as that of green pea galaxies
+\citep{Cardamone2009,Jaskot2013} and Hanny's Voorwerp
+\citep{Lintott2009,Keel2012}, \GZ has been able to harness the potential
+of citizen scientists.  Since then astronomy and non-astronomy projects
+have been launched under the citizen science web portal Zooniverse
+(http://zooniverse.org). The task of finding gravitational lenses is
+significantly challenging given that the lens systems show such
+complexity and that they are rare. To add to the challenge, not many
+citizen scientists are expected to be aware of the phenomenon of
+gravitational lensing, and the resulting image configurations.  With
+these significant challenges at hand, we designed the \sw project to
+enable the discovery of lenses through citizen science.  In a companion
+paper, Paper I (Marshall et al., in prep.), we describe the design of
+\sw and how the entire system functions as a discovery service.
+
+In this paper (Paper II hereafter), we describe our first lens search
+using data from the Canada-France-Hawaii Telescope Legacy Survey
+(\cfhtls). This paper is organised as follows. In
+\Sref{sec:data}, we introduce the \cfhtls imaging data and the
+previously published lens samples from the \cfhtls. We generated a training sample, 
+consisting of simulated lenses, duds and false positives, in order to
+aid the \sw volunteers in the process of finding lenses. We give details of this
+training sample in \Sref{sec:ts} and \Sref{sec:dfp}. In \Sref{sec:swap},
+we briefly describe how the classifications of images from the volunteers are
+turned into a catalog of plausible candidates (for further details, see
+Paper I). In \Sref{sec:results}, we present the new lens candidates from \sw and
+compare it to the lens samples produced by a few robotic searches from
+the \cfhtls in the past. Next, we discuss what kind of lenses are detected
+or missed by the algorithms and \sw in \Sref{sec:discuss}. The summary
+and conclusions are given in \Sref{sec:conclude}.
 
@@
 ($u^*g'r'i'z'$) carried out with the wide-field imager MegaPrime which
-has a 1~deg$^2$ field-of-view and a pixel size of 0.186\arcsec. The
-\cfhtls \textsc{WIDE} covers a total non-overlapping area of 150~deg$^2$
-on the sky and consists of four fields W1, W2, W3 and W4. The field W1
-has the largest sky coverage of 63.65~deg$^2$. The fields W2 and W4 have
-similar sky coverages of 20.32~deg$^2$ and 20.02~deg$^2$,
-respectively\footnote{These numbers are estimated from
-http://terapix.iap.fr/cplt/table\_syn\_T0006.html}.  The field W3 has a
-sky coverage of 42.87~deg$^2$ and is more than twice as large as W2 and
-W4.
-
-The \cfhtls imaging is very homogeneous and has good image quality. Most of
-the lensed arcs are much brighter in the $g$ band thus, deep imaging in
-this band is desirable. The limiting magnitude is 25.47 for the $g$ band
-which goes the deepest among all of the five bands. The mean seeing in
-the $g$ band is 0.78\arcsec. The zero point to convert flux to AB
+has a 1~deg$^2$ field-of-view and a pixel size of 0.186\arcsec
+\citep{Gwyn2012}. The \cfhtls \textsc{WIDE} covers a total
+non-overlapping area of 150~deg$^2$ on the sky and consists of four
+fields W1, W2, W3 and W4. The field W1 has the largest sky coverage of
+63.65~deg$^2$. The fields W2 and W4 have similar sky coverages of
+20.32~deg$^2$ and 20.02~deg$^2$, respectively\footnote{These numbers are
+estimated from http://terapix.iap.fr/cplt/table\_syn\_T0006.html}.  The
+field W3 has a sky coverage of 42.87~deg$^2$ and is more than twice as
+large as W2 and W4.
+
+The \cfhtls imaging is very homogeneous and has good image quality. Most
+of the lensed arcs are much brighter in the $g$ band thus, deep imaging
+in this band is desirable. The limiting magnitude is 25.47 for the $g$
+band which goes the deepest among all of the five bands. The mean seeing
+in the $g$ band is 0.78\arcsec. The zero point to convert flux to AB
 magnitude for all bands is 30. These characteristics make \cfhtls ideal
-to do visual inspection for finding lenses.  We use the data from the
-final T0007 release taken from the Terapix
-website\footnote{{http://terapix.iap.fr/cplt/T0006-doc.pdf}}
-for this work.
+to do visual inspection for finding lenses.  We use the stacked images
+from the final T0007 release taken from the Terapix
+website\footnote{{http://terapix.iap.fr/cplt/T0006-doc.pdf}} for this
+work.
 
@@
 in the \cfhtls is an important step to learn lessons and prepare for lens
-searched in these larger imaging surveys.
+searches in these larger imaging surveys.
 
@@
 methods and algorithms. Here, we give a brief summary of previously published lens
-samples in chronological order.
+samples in the chronological order.
 
@@
 \cfhtls WIDE. They identified galaxies, using {\sc Sextractor}, which
-have $18<i<21$ and only those with inclination angle $<25$~deg. With a
-few more selection criteria and visual inspection, they found about 3
-promising and a total of 18 lens candidates.
+had $18<i<21$ and inclination angle $<25$~deg. After applying few more
+selection criteria and visual inspection, they found about 3 promising
+and a total of 18 lens candidates.
 
 The \af \citep{More2012} was used for finding blue arc-like features in
-the complete \cfhtls data without any pre-selection on the type of the lensing
+the entire \cfhtls imaging without any pre-selection on the type of the lensing
 object. The algorithm measures the second order moments of the flux distribution
@@
 galaxy-scales. In the absence of a large systematically followed up
-verification of the candidates, we use the  most promising sample of 26 lens
-candidates as the bonafide known lens sample. And, the sample of 108 candidates
-form the known lens candidates which come from the \cfhtls WIDE alone since the
-\sw lens search is carried out on the WIDE imaging only.
-
-In \citet{Elyiv2013}, they visually inspected a sample of 5500 optical
+verified sample of candidates, we choose the most promising 26 systems
+as our bonafide lens sample from the \cfhtls WIDE. Also, the total
+number of lens candidates is 108 from the \cfhtls WIDE alone.
+
+In \citet{Elyiv2013}, the authors visually inspected a sample of 5500 optical
 counterparts of X-ray point-like sources identified in the XMM-LSS
-imaging of the \cfhtls W1 field. The goal was to discover lensed
-quasars. They find 3 very promising and a total of 18 candidates.
+imaging of the \cfhtls W1 field. The goal was to find instances
+of lensed quasars. Their sample consists of a total of 18 candidates out
+of which 3 candidates are found to be promising.
 
@@
 early type galaxies, or objects selected to have red centers and blue
-outer parts, from the T06 CFHTLS data release catalogs.  14370 were
-found to show detectable blue residuals, and 2524 were visually
-inspected, having passed the automatic feature selection process. This
-led to a total of 330 lens candidates out of which 42 are good quality
-(\texttt{q\_flag} = 3) and 288 are medium quality (\texttt{q\_flag} = 2)
-candidates. In addition to the main well-defined sample,
-\citet{Gavazzi2014} reported a further 71 candidates were reported
-detected by earlier version of the \rf or from the \cfhtls DEEP.  From
-the main sample of ``\rf candidates,'' the SL2S team found, during their
-follow-up campaign, 33 confirmed lenses (and 17 promising candidates).
+outer parts, from the T0006 CFHTLS data release catalogs. A total of
+14370 galaxies were found to show detectable blue residuals, and 2524
+were visually inspected, having passed the automatic feature selection
+process. This led to a total of 330 lens candidates out of which 42 are
+good quality (\texttt{q\_flag} = 3) and 288 are medium quality
+(\texttt{q\_flag} = 2) candidates. In addition to the main well-defined
+sample of \citet{Gavazzi2014}, a further 71 candidates were reported to
+be detected by earlier version of the \rf or from the \cfhtls DEEP.
+From the main sample of ``\rf candidates,'' the SL2S team found, during
+their follow-up campaign, 33 confirmed lenses.
+%(and 17 promising candidates) AM: PJM, what is this sample of 17 ?
 
@@
 detection. This new approach was tested on the CFHTLS-Archive-Research
-Survey \citep[CARS,][]{Erben2009} which covers an area of only 37~sq.~deg
-and the entire data was visually inspected to estimate completeness and
-purity of their robotic search. They found 29 candidates with the
-algorithm and 41 candidates through visual inspection alone some of
-which are known from previous searches. Most of these candidates are low
+Survey \citep[CARS,][]{Erben2009} which covers an area of 37~sq.~deg
+only and this entire data was also visually inspected by the authors to
+estimate completeness and purity of their robotic search. They found 29
+candidates with the robotic search alone and 41 candidates through pure
+visual inspection some of which are known from previous searches. Most
+of these candidates are medium-low
 probability\footnote{http://www.ita.uni-heidelberg.de/˜maturi/Public/arcs}.
@@
 The \rf and the \af searches are the only searches that make use of a
-lens finding algorithm that has been run on the entire \cfhtls imaging.
-Thus, these can be considered as the known reference sample from robotic
-searches.  For the purposes of transparency and to help with the
-training, the volunteers participating in \sw-\cfhtls lens search were
-made aware of these two known lens samples. Images containing the
-systems from the \rf and the \af samples were labelled as ``Known Lens
-Candidates'' in the Talk forum, where volunteers have the opportunity to
-discuss their findings with fellow volunteers and the science team. In
-this paper, we refer to the sample of 330 \rf and 108 \af lens
-candidates as the sample of ``known lens candidates'' and the sample of
-confirmed (or most promising) 33 \rf and 26 \af as the sample of ``known
-lenses''. Note that the ``known lens'' sample is a subset of the ``known lens
-candidates'' sample.
+lens finding algorithm and that has been run on the entire \cfhtls
+imaging.  Thus, these can be considered as our reference sample of known
+lenses from robotic searches. For the purposes of transparency and to
+help with the training, the volunteers participating in \sw-\cfhtls lens
+search were made aware of these two known lens samples. Images
+containing the systems from the \rf and the \af samples were labelled as
+``Known Lens Candidates'' in the \sw discussion forum,
+TALK\footnote{http://talk.spacewarps.org/}, where volunteers have the
+opportunity to discuss their findings with fellow volunteers and the
+science team. In this paper, we refer to the sample of 330 \rf and 108
+\af lens candidates as the sample of ``known lens candidates'' and the
+sample of confirmed (or most promising) 33 \rf and 26 \af as the sample
+of ``known lenses''. Note that the ``known lens'' sample is a subset of
+the ``known lens candidates'' sample.
 
@@
 visual identification of lenses.  We made color composite images using
-the publicly-available code, HumVI\footnote{The open source  color image
+the publicly-available code, \humvi\footnote{The open source  color image
 composition code used in this work is available from
@@
 lenses, the number of objects seen in a single cutout and the total
-number of image cutouts in the survey. It is possible that a lens
-candidate happens to be too close to the edge of a cutout, the overlap
-between neighbouring cutout allows the inspector to get a clearer view
+number of image cutouts in the survey. If a lens
+candidate happens to be too close to the edge of a cutout, then the overlap
+between neighbouring cutout allows a volunteer to get a clearer view
 of the same candidate in at least one of the cutouts. We note that since
-the images are shown randomly, an inspector may not necessarily come
-across the neighbouring cutout unless the inspector classifies a large
+the images are shown randomly, a volunteer may not necessarily come
+across the neighbouring cutout unless the volunteer classifies a large
 number of images. This is not a problem since our user base is extremely
@@
 
-In this section, we describe the framework to generate the simulated lens sample
-and give details of the sample itself along with some known limitations. This
-simulated lens sample is an important component for analyzing the
-classifications performed by the citizen scientists.
+The simulated lenses are important to train citizen scientists who are
+novice to the task of finding lenses but they are also crucial for
+analyzing the classifications performed by the citizen scientists (more
+details can be found in Paper I but see \Sref{sec:swap} for a brief
+summary). In this section, we describe the framework used for generating the
+simulated lens sample and give details of the sample itself along with
+some known limitations.
 
@@
 
-For the purpose of generating simulated gravitational systems, we divide the
-lenses in to two main categories a) galaxy scale lenses b) and group or
+For the purpose of generating simulated lens systems, we divide them
+in to two main categories a) galaxy scale lenses b) and group or
 cluster-scale lenses. We further subdivide galaxy scale lenses based on the
 type of the background sources, namely galaxies and quasars. We do not simulate
-group scale quasar lenses as they are expected to be extremely rare. We now
+group scale - quasar lenses as they are expected to be even more rare. We now
 describe our procedure to generate these different types of lens systems.
@@
 \citep{Faber2007}.\footnote{We anchor our $L_*$ evolution at low redshifts using the
-determination of $L_*$ in the r-band by \citet{Blanton:2001}. To maintain
+determination of $L_*$ in the r-band by \citet{Blanton2001}. To maintain
 consistency in magnitude systems, we have converted the CFHT MegaCAM magnitudes
@@
 
-For quasars, we assume the luminosity function prescription of \citep{Ogur2010}
+For quasars, we assume the luminosity function prescription of \citep{Oguri2010}
 and adopt k-corrections by \citep{Richards2006}.
@@
 ray-tracing for all of the $N_{\rm src}$ sources using the publicly available
-code {\sc gravlens} \citep{Keeton2000} and choose sources that satisfy our
+code \gravlens \citep{Keeton2000} and choose sources that satisfy our
 selection criteria. We determine fluxes of the lensed images and the total
@@
 quasar lenses. Next, we assume deVaucoleur's profile to account for the size
-and shape of the galaxies. The ellipticity and the position angle are drawn
+and shape of the galaxies. The ellipticity and the position angle (PA) are drawn
 randomly between the range given in Table~\ref{tab:thresh}. The effective
@@
 Once all the parameters are determined for the lens and source models, we once
-again use {\sc gravlens} to generate simulated lensed images.  After accounting for the shot
+again use \gravlens to generate simulated lensed images.  After accounting for the shot
 noise in the lensed images and convolving them with the median seeing in each of
@@
 \hline
-Name  &  \multicolumn{2}{c} {gal}  & \multicolumn{2}{c}{qso} \\
+Name  &  \multicolumn{2}{c} {Gal-Gal (Grp-Gal)}  & \multicolumn{2}{c}{Gal-Qua} \\
       & min  &  max  & min & max \\
@@
 Source Redshift  & 1.0 & 4.0  & 1.0  & 5.9 \\
-Source Magnitude & 21.0 & 25.5 & 21.0 & 25.5 \\
-
-boost factor & 100 (40$\dagger$)  &  & 1200 & \\
-
-Second brightest image & 23  & & 23 & \\
-Total magnification & 19 & & 20 & \\
-
-Lens shear strength &  0.001 & 0.02 &  0.001 & 0.02 \\
-Lens shear pa &  0 & 180 & 0 & 180  \\
-Source ellipticity & 0.1 & 0.6 & & \\
-Source PA & 0 & 180 & & \\
+Source Flux      & 21.0 & 25.5 & 21.0 & 25.5 \\
+Source ellipticity & 0.1 & 0.6 & - & - \\
+Source PA & 0 & 180 & - & - \\
+Lens Redshift  & - & 0.9  & -  & 0.9 \\
+Lens shear strength &  0.001 (-) & 0.02 (-) &  0.001 & 0.02 \\
+Lens shear PA &  0 (-) & 180 (-) & 0 & 180  \\
+Einstein radius (arcsec) & 1.2 (2) & 5 (-) & 1.2 & 5 \\
+\hline
+boost factor     & $=$100 (40)  &  & $=$1200 & \\
+Image Flux$_{\rm 2B}$ & $>$23  & & $>$23 & \\
+Image Flux$_{\rm tot}$ & $<$19 & & $<$20 & \\
 \hline
 \end{tabular}
-{ $\dagger$} -- corresponds to the factor used for Groups scale lenses.
 \end{center}
+a) () -- corresponds to quantities used for Grp-Gal scale lenses, if they
+are different from Gal-Gal.
+b) $_{\rm 2B}$ --  the second brightest lensed image.
+c) $_{\rm tot}$ -- total flux integrated over all of the lensed images.
+d) All fluxes are in AB mag. PA is in degrees measured East of North.
 \end{table}
-%{\bf check the units and confirm the numbers in this table etc.}
 
@@
 Distributions of properties of the lensing galaxies of the simulated
-sample compared to the known lens sample SARCS.
-%(XXXX confirm what's being plotted? which band - i?)
+sample compared to the known lens sample SARCS. %(XXXX confirm what's being plotted? which band - i?)
 }
@@
 convert the BGG luminosity to a stellar mass estimate. The stellar mass$-$halo
-mass relation \citep{behroozi13}, including random scatter, is then used to
+mass relation \citep{Behroozi2013}, including random scatter, is then used to
 calculate the halo mass for the lens. We adopt an NFW density profile for the
@@
 criteria for strong lensing. To further understand caustics, see XXX.}.
-Therefore, we generate the caustics numerically using {\sc gravlens} and then
+Therefore, we generate the caustics numerically using \gravlens and then
 determine the area covered by the caustics. We consider only galaxies as our
@@
 fraction of the simulated images (roughly 5 percent of
-the cases)\footnote{Based on the hashtag simfail in the discussion forum Talk.}.
+the cases)\footnote{Based on the hashtag simfail in the discussion forum
+TALK.}.
 
@@
 \section{Methodology to produce the \sw-\cfhtls Lens Sample}
-
+\label{sec:swap}
 The \sw works as a single unified neural network which uses the method of visual
@@
 ($z_{phot}$), $i$ band magnitude of the lensing galaxy, averaged grade G from
-the lens experts, zoo ID (identifier used in
-TALK\footnote{http://talk.spacewarps.org/}, the discussion forum for \sw), P
+the lens experts, zoo ID (identifier used in TALK), P
 value at \StageTwo and a visual categorization of type of lensed images and the
@@
 preselection of candidates from any algorithm, we find various types of
-lenses, as expected from such a search. The final sample consists of both
-galaxy and groups-scale lens candidates. There are detections of
+lenses, as expected from such a search. The final sample consists of
+both galaxy and groups-scale lens candidates. There are detections of
 elongated arcs and some interesting point-like quasar lensed images.
 Most of them are brighter in bluer $g$ band but some candidates brighter
-in the redder $i$ band are also found. Since robotic lens searches
-often look for blue colored lensed features, they are very much likely
-to miss such interesting lens candidates.
+in the redder $i$ band are also found. Since robotic lens searches often
+look for blue colored lensed features, they are very much likely to miss
+such interesting lens candidates.  We did not find any examples of
+exotic lens candidates from the visually inspected P$>0.3$ sample. There
+may be some interesting candidates lurking in TALK but these will have
+to be sifted through ({\bf is there someone actively looking into this
+whose work should be referred here ?}).
 
@@
 identified candidates) and the mass modelling analyses for the new
-candidates is deferred to a subsequent \sw paper, Paper III.
-
-%{\bf CHECK FOR STAGE 1 -- COMPLETENESS OF KNOWN LENSES
-%and P value comparison, what about the duplicate lenses near the borders
-%- stats on those?  check the detection plot of arc mag / Reinst and find out why some of
-%the bins have unexpected results. check arc mag vs. reinst plot and
-%understand why some of the very faint/low reinst sw detections are and
-%if it all makes sense.}
+candidates will be presented in a subsequent \sw paper, Paper III.
+
+%{\bf CHECK FOR STAGE 1 -- COMPLETENESS OF KNOWN LENSES and P value comparison,
+
+% what about the duplicate lenses near the borders -- stats on those?
+
+% check the detection plot of arc mag / Reinst and find out why some of
+%the bins have unexpected results.
+
+%check if some candidates were detected because they were hidden
+%underneath the sims ie. from the D11;
+%}
 
@@
 
-%Lastly, we attempt to characterize the completeness of the \sw lens
-%sample based on the simulated lens sample. The right most panel of
-%\Fref{fig:compre} shows the completeness of the simulated sample
-%at \StageOne of \sw as a function of the arc magnitude and Einstein
-%radius. We find that the lens sample is more than XXX\% complete between image
-%separations 2"-10".
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %% 19,46 (original and relaxed criteria); 72,338 (smaller image); 1548,7845 (larger image)
-
-%{\bf TBD:
-%comment on any lensed quasars, on any exotic lenses;
-%of course, there must be lenses which cannot be detected currently by
-%either robots/humans
-%check if some candidates were detected because they were hidden
-%underneath the sims ie. from the D11;
-%}
 
@@
 simulated and the real sample of candidates. }
-%{\bf check this for the known lens sample only}
 \end{center}
@@
 candidates.
-%{\bf comment on duplicated lens candidates near the edges - what fraction of them are
-%detected}
-
-%Real (robotically-detected and expert-confirmed) lenses are
-%recovered/missed at similar/comparable/different rates C’\% and P’\% -
-%this is a partial test of supervised vs unsupervised learning
 
@@
 
-%{\bf todo: run swap and extract the status of all the known lens candidates
-%-- because the undecided are not known otherwise. fig will have to be
-%updated for the blind lens search section; also check what happened to
+%{\bf todo: 
+%check what happened to
 %those AF lenses which were labelled sims - look at the D11 counterparts

### 2015-04-10 doc/sw-cfhtls.tex
read through and fixed text in Sec 3-5

@@
 
-We begin by considering all elliptical galaxies at $z<1$ in our parent \cfhtls
-catalog as potential lens candidates for the simulated sample. To avoid using a
-known lens galaxy for our simulation purpose, we exclude all those galaxies
-whose positions match with the lensing galaxies from the SARCS
+We begin by considering all elliptical galaxies at $z<1$ in our parent
+\cfhtls catalog \citep[(XXX confirm with Raphael)]{Gavazzi2014} as
+potential lens candidates for the simulated sample. To avoid using a
+known lens galaxy for our simulation purpose, we exclude all those
+galaxies whose positions match with the lensing galaxies from the SARCS
 samples within 2~arcsec (XXX check).
@@
 \label{eqn:nlum}
-n_{\rm src}(>L_{min},z_s)= \int_{L_{\rm min}}^\infty \Phi(L',z_s) {\rm d}L'
+n_{\rm src}(>L_{\rm min},z_s)= \int_{L_{\rm min}}^\infty \Phi(L',z_s) {\rm d}L' \,.
 \ee
+
 Here, $\Phi(L',z_s)$ denotes the source luminosity function per unit comoving
@@
 luminosity of each potential lensing galaxy using the photometric redshifts
-($z_l$) from the LRG catalog. We use the $L-\sigma$ scaling relation from the
+($z_l$) from the parent galaxy catalog. Next, we use the $L-\sigma$ scaling relation from the
 bright sample of \citep{Parker2005} to set the velocity dispersion of the halo
@@
 
-%first calculate the
-%luminosity and velocity dispersion of each potential lensing galaxy using the
-%CFHT Megacam $g$ and $r$ band magnitudes along with the photometric redshift
-%($z_l$) from the LRG catalog.  The Megacam magnitudes are converted to SDSS
-%magnitudes\footnote{
-%http://www3.cadc-ccda.hia-iha.nrc-cnrc.gc.ca/megapipe/docs/filters.html} and are
-%further k-corrected to redshift $z=0.1$ \citep{Frei1994}. We assume that the
-%evolution of galaxy luminosities is similar to that determined by
-%\citep{Faber2007}, that is, a decline of $1.5$ in the $m_{r*}$ from redshift
-%$z=1$ to $z=0$ (see Eq.~\ref{magstar}).
-
-%\be
-%\frac{L}{L_{*}}=10.0^{-0.4~(m_{r \rm SDSS}-m_{r*})}
-%\ee
-%
-%where $m_{r*}$ is
-%\be
-%\label{magstar}
-%m_{r*}=-20.44+ 1.5~(z_{l}-0.1) \,.
-%\ee
-%
-%We use the $L-\sigma$ relation from
-%\citep{Parker2005} to get the velocity dispersion as given in Eq.~\ref{magstar2}.
-
-%\be
-%\label{magstar2}
-%\sigma=142 \left(\frac{L}{L_{*}}\right)^{1/3}
-%\ee
-
-We assume a singular isothermal ellipsoid model for each of our galaxies
+We adopt a singular isothermal ellipsoid (SIE) model for each of our galaxies
 \citep{Kormann1994}, such that the convergence is given by
 \be
-\kappa (x,y) = \frac{b \sqrt{q}}{2}\frac{1}{\left( \theta_1^2 + q^2\theta_2^2\right)^2}
+\kappa (x,y) = \frac{b \sqrt{q}}{2}\frac{1}{\left( \theta_1^2 + q^2\theta_2^2\right)^2} \,.
 \ee
-Here b is called the Einstein radius, and its dependence on the velocity
+Here, $b$ is called the Einstein radius, and its dependence on the velocity
 dispersion of the SIE is given by
@@
 \ee
-The SIE model results in a caustic and a pseudo-caustic on the source plane:
-which demarcate the regions of different image multiplicities. Parametric
-solutions, $r(\theta)$ (where $\theta$ is the polar angle), for the caustics in
-such a model were given by \citet{Keeton2000b}. We use these parametric
-solutions to obtain the area of the lensing cross-section, $\sigma$, for every
-galaxy,
+The SIE model results in a caustic and a pseudo-caustic on the source
+plane: which demarcate the regions of different image multiplicities. We
+make use of the parametric solutions, $r(\theta)$, for the caustics in
+such a model from \citet{Keeton2000b} where $\theta$ is the polar angle.
+We take the maximum of the radial and tangential caustic at every polar
+angle in order to obtain the area of the lensing cross-section,
+$\sigma_{\rm lens}$, for every galaxy,
 \be
-\sigma_{\rm lens}=\frac{b^2 q}{2} \, \int_0^{2\pi} r^2(\theta) d\theta\,.
+\sigma_{\rm lens}=\frac{b^2 q}{2} \, \int_0^{2\pi} r^2(\theta) d\theta \,.
 \ee
-At every polar angle we use the maximum of the radial and tangential caustic for
-the purpose of calculating the cross-section.
-
-%where
-%\be
-%b_I =  \sqrt{q}\, 4\pi\,
-%\left(\frac{\sigma_v^2}{c^2}\right)\left(\frac{D_{ls}}{D_{s}}\right)\,.
-%\ee
-%Here $D_s$ and $D_{ls}$ are angular diameter distances to
-%the source, and between the lens and source, respectively.
-
-%Next, if the foreground galaxy can act as a lens and has at least one source in the
-%background, then we determine a redshift ($z_s$) and $i$-band magnitude of the
-%background source(s). We assume two types of background sources namely, galaxies
-%and quasars. For each source, the redshift and magnitude are generated by drawing randomly from
-%the following redshift and luminosity distributions. For
-%galaxies, we assume the redshift distribution is
-
-We use the results of \citet{Faure2009} to specify the source luminosity
-function of galaxies. We assume that the redshift distribution of sources is
+
+The luminosify functions of the background galaxies and quasars are
+determined as follows. We use the results of \citet{Faure2009} to specify the luminosity
+function of galaxies where the redshift distribution of sources is
 given by
@@
 \ee
-where $\beta=3/2$ and $z_0(m_{\rm lim})=0.13m_{\rm lim} - 2.2$ and the source
+where $\beta=3/2$ and $z_0(m_{\rm lim})=0.13~m_{\rm lim} - 2.2$ and the source
 counts as a function of the limiting magnitude are given by
@@
 and adopt k-corrections by \citep{Richards2006}.
-%alp=-0.5;
-%kcorr=-2.5*(1 + alp)*log10(1+zz);
-%Dlum=cc.Dlofz(zz)/p.hval;
-%DM=5*log10(Dlum);
-%Mabs=mag-kcorr-DM-25.0;
+
 The luminosity function is expressed as
@@
 higher redshifts, as prescribed by \citep{Oguri2010}.
-respectively.
-
-With the cross-section, and the luminosity functions specified, we calculate the
-expected number of sources behind a candidate galaxy using Equation
-\ref{eqn:nsrc}. We need to generate a large number of simulated lenses (larger
-than the number of real galaxy lenses we expect to find in CFHTLS) in order to
-use it as a training sample as well as for calibrating the performance of our
-citizen scientists (see Paper I). Therefore, we artificially boost the average
-number of sources by a factor (see Table~\ref{tab:thresh}, which increases the
-occurrence of lensing. We draw a Poisson deviate with a mean equal to the
-boosted average number of sources. If the Poisson deviate is greater than zero,
-then we mark this galaxy to act as a lens galaxy. We then draw the properties of
-the lensed source based on the redshift and the luminosity distribution of the
-sources. The source positions with respect to the lens are drawn randomly from
-an area inside the caustic.
-
-Next, we determine properties of the background source for every lens. We follow
-similar procedures for both background galaxies and quasars. We perform
-ray-tracing for all of the $N_{\rm src}$ sources using the publicly available
-code \gravlens \citep{Keeton2000} and choose sources that satisfy our
-selection criteria. We determine fluxes of the lensed images and the total
-magnification of each of the lensed source. We draw a random source for which
-the flux of the second brightest lensed image and the total magnification of all
-lensed images are above the thresholds given in Table~\ref{tab:thresh}.
+
+With the cross-section, and the luminosity functions specified, we
+calculate the expected number of sources behind a candidate lensing
+galaxy using Eq.~\ref{eqn:nsrc}. We need to generate a large number of
+simulated lenses (larger than the number of real galaxy lenses we expect
+to find in \cfhtls) in order to have a reasonably large and diverse
+training sample for thousands of \sw volunteers. Therefore, we
+artificially boost the average number of sources by a factor (see
+Table~\ref{tab:thresh}, which increases the occurrence of lensing. We
+draw a Poisson deviate with a mean equal to the boosted average number
+of sources. If the Poisson deviate is greater than zero, then 
+this galaxy is flagged as a potential lensing galaxy with
+Nsrc number of background sources. {\bf XXXX check if this is correct.}
+
+Next, we determine properties of the background sources for every lens.
+We follow similar procedures for both background galaxies and quasars.
+We draw source redshifts and luminosities from the aforementioned
+distributions. The source positions with respect to the lens are drawn
+randomly from an area inside the caustic.  We perform ray-tracing for
+all of the $N_{\rm src}$ sources using the publicly available code
+\gravlens \citep{Keeton2000} and choose sources that satisfy our
+selection criteria given below. We determine fluxes of the lensed images and the
+total magnification of each of the lensed source. We draw a
+source randomly for which the flux of the second brightest lensed image and the
+total magnification of all lensed images meet the thresholds given
+in Table~\ref{tab:thresh}.
 
 Since we want to produce realistic looking lens systems, we simulate lenses in
-each of the five \cfhtls~filters. The colors of the background source galaxies are drawn
+each of the five \cfhtls~filters. The colors of the background galaxies are drawn
 randomly from the photometric CFHTLenS catalog
@@
 and shape of the galaxies. The ellipticity and the position angle (PA) are drawn
-randomly between the range given in Table~\ref{tab:thresh}. The effective
+randomly from within the range given in Table~\ref{tab:thresh}. The effective
 radius of the galaxy is estimated from the Luminosity$-$size relation
-\citep{Bernardi2003} (with a redshift scaling to account for some size
+\citep{Bernardi2003} (with a redshift scaling, to account for size
 evolution) given by
@@
 where $L_r=L_s/10^{10.2}$. On the other hand, quasars are assumed to follow a
-Gaussian profile where the $\sigma$ is equated to that of the median seeing for
+Gaussian profile where the full-width-at-half-maximum is equated to that of the median seeing for
 every filter. The median seeing values are taken from Table 4 of the official
@@
 multiple lensed images, arises from not only the brightest group galaxy (BGG) at
-the center, but also has contribution from the dark matter component as well as
+the center, but also from the dark matter component and
 the satellite galaxies \citep{Oguri2005,Oguri2006}. We generate a basic group
@@
 
-We assume a constant mass-to-light ratio of $3 \times 0.7$~h~$M_{*}/L_{*}$, to
-convert the BGG luminosity to a stellar mass estimate. The stellar mass$-$halo
-mass relation \citep{Behroozi2013}, including random scatter, is then used to
-calculate the halo mass for the lens. We adopt an NFW density profile for the
-underlying dark matter halo. Given the halo mass, other key parameters such as
-the scale radius ($r_s$) and the density at the scale radius ($\rho_s$) can be
-determined for an NFW profile. In addition, we adopt an isothermal ellipsoid
-model for the BGG and members whenever the ellipticities are available from the
-galaxy catalog (else we use an isothermal sphere).
+We assume a constant mass-to-light ratio of $3 \times
+0.7$~h~$M_{*}/L_{*}$, to convert the BGG luminosity to a stellar mass
+estimate. The stellar mass$-$halo mass relation \citep{Behroozi2013},
+including random scatter, is then used to calculate the halo mass for
+the lens. We adopt an NFW \citep{Navarro1997} density profile for the
+underlying dark matter halo. Given the halo mass, other key parameters
+such as the scale radius ($r_s$) and the density at the scale radius
+($\rho_s$) can be determined for an NFW profile. In addition, we adopt
+an SIE model for the BGG and members whenever the ellipticities are
+available from the galaxy catalog (else we use an isothermal sphere,
+SIS).
 
@@
 member galaxies following the same prescription as in
-Section~\ref{sect:gallens}. To calculate the average number of sources that get
+\Sref{sect:gallens}. To calculate the average number of sources that get
 lensed by such a system, we need to calculate the lensing cross-section for each
@@
 determine the area covered by the caustics. We consider only galaxies as our
-background source population since group or cluster-scale quasar lenses are not
-expected to be extremely rare in the \cfhtls (check XXX).  Following the same procedure
-as described in Section~\ref{sect:gallens}, we calculate the number of galaxies
+background source population since group or cluster-scale quasar lenses are
+expected to be extremely rare in the \cfhtls.  Following the same procedure
+as described in \Sref{sect:gallens}, we calculate the number of galaxies
 expected to lie behind every potential lensing group (see Eq.~\ref{eqn:nsrc}).
@@
 image separation distribution are not affected (see \Fref{fig:remudist}). We
-follow the same procedure and apply the same thresholds to determine properties
+follow the same procedure and apply thresholds to determine properties
 of the lensed galaxies for every lens as are described for galaxy-galaxy lenses
-in the previous section. The simulated lensed images are then added on top of
-the real \cfhtls~images with the BGGs as the center.
+in the previous section. The thresholds are same as those used for
+galaxy lenses (see \Tref{tab:thresh}) and are reported within ``()'', if
+different for group-scales. The simulated lensed images are then added
+to the real \cfhtls~images with the BGGs as the center by following
+exactly the same procedure as described in the previous section.
 
@@
 In this section, we describe some of the properties of our simulated sample for
-each of the three types of lens samples.
-
-\Fref{fig:remudist} shows the Einstein radius distribution for the
+each of the three types of lens samples. We have made an attempt to
+generate as realistic a lens sample as possible within the requirements
+of the \sw project. The statistical properties of the lens sample are
+expected to be similar to real lens samples.
+
+In \Fref{fig:remudist}, we show the Einstein radius distribution for the
 galaxy-scale (dashed for background quasars and dotted for background galaxies)
-and groups-scale simulated lenses. For comparison, we show the expected
-distributions (blue dashed-dotted curves) for an SIS-like density profile at
+and groups-scale simulated lenses. For comparison, we give the expected
+distributions (blue dashed-dotted curves) for an SIS like density profile at
 galaxy-scales and an NFW+Hernquist profile at groups-scales. The
-theoretical curves are taken from \citep{More2012} wherein the models are
+theoretical curves are taken from \citet{More2012} wherein the models are
 explained in detail. We note that the model we adopt at groups-scale also
 includes SIS or SIE components for the group members unlike the theoretical
-prediction. The theoretical curves have arbitrary normalizations.
-
-We show the redshift, magnitude and ellipticity distributions of the lensing
-galaxies in the three panels of \Fref{fig:lensprop}, respectively. We also show
-the distributions of respective properties of the SARCS lenses from
-\citep{More2012} for comparison with arbitrary normalizations. We note the
-qualitative similarities between the simulated and the real lens samples.
-
-%Similarly, we show the ellipticity and the position angle of the simulated lens
-%galaxy population extracted from the T0007 release of the \cfhtls~catalogs in the
-%left and right panels of \Fref{fig:lensprop}, respectively. As before, the
-%dashed-dotted (blue) curves show the same distribution for the SARCS lens
-%population with arbitrary normalization \citep{More2012}.
-
-%We show the source redshift and magnitude distributions for each of the three
-%lens samples in the left and right panels of \Fref{fig:szmdist},
-%respectively. The peak of the source redshift distribution both for the galaxies
-%and quasars is known to be between $2<z<3$ from various lens samples (add
-%references XXX). This consistent with our simulated sample as expected. The
-%magnitude distribution of the simulated sample, on the other hand, is
-%specifically tailored to the requirements of \sw.  The goal was to generate a
-%lens sample that has a fair balance of both bright and faint lensed images since
-%the training sample should neither be too easy nor too difficult for the citizen
-%scientists.
-
-We produce catalogs with lens and source properties for each of the three types
-of lenses. These catalogs are available from
-https://github.com/anupreeta27/SIMCT. The catalogs typically have lens
-position, redshift, magnitudes, Einstein radius, ellipticity (whenever
-available) and shear (for galaxy-scale lenses only). For the background
-sources, we provide the offset from the lens center, redshift, magnitudes,
-total magnification, number of lensed images. Additionally, when possible,
-ellipticity and effective radius of the background galaxies have also been
-provided.
+prediction. The theoretical curves have arbitrary normalizations. We
+also show the distribution of the total magnification for all three
+samples.
+
+Next, we consider the redshift, magnitude and ellipticity distributions
+of the lensing galaxies as shown in \Fref{fig:lensprop}. For reference,
+we also show SARCS lenses from \citet{More2012}, with arbitrary
+normalizations. We find that the properties of the foreground lenses in
+the simulated and the real lens samples are broadly similar.
+
+We produce catalogs with lens and source properties for each of the
+three types of lenses.  The catalogs typically have lens position,
+redshift, magnitudes, Einstein radius, ellipticity (whenever available)
+and shear (for galaxy-scale lenses only). For the background sources, we
+provide the offset from the lens center, redshift, magnitudes, total
+magnification, number of lensed images. Additionally, when possible,
+ellipticity and effective radius of the background galaxies have also
+been provided. These catalogs are available from
+https://github.com/anupreeta27/SIMCT and simulated lens sample can be
+requested from the authors.
 
@@
 \subsection{Limitations of the simulated sample}
-The simulated lens sample, although realistic, is not perfect, due to the
-simplicity of the lensing models and our limited understanding of the
-uncertainties in the parameters for the models. Comments from citizen
-scientists were very helpful in order to sort some of these failures. Here, we
-describe some of the cases or aspects in which the simulations were known to
-have failed (or appeared unrealistic). This typically happens for a small
-fraction of the simulated images (roughly 5 percent of
-the cases)\footnote{Based on the hashtag simfail in the discussion forum
-TALK.}.
-
-The parameters required by various scaling relations and the models primarily
-depend on the photometry of the galaxies, groups and quasars detected in the
-survey. For galaxy-scale lenses, the lensing galaxies at higher redshifts or
-which are fainter have poor photometric redshift measurements. Consequently
-these galaxies are assigned a wrong luminosity and velocity dispersion
-estimates, which sometimes result in simulated lenses which look implausible.
-For example, the lensed images for some of the failed simulations have larger
-image separation than expected given the visual priors from the galaxy.
+The simulated lens sample, although realistic, is not perfect, due to
+the simplicity of the lensing models and our limited understanding of
+the uncertainties in the model parameters. Comments from citizen
+scientists were very helpful in order to sort some of these failures.
+Here, we describe some of the cases or aspects in which the simulations
+were known to have failed to look realistic. The fraction of such
+simulated sample is small (roughly 5 percent)\footnote{This estimate is
+based on the \#simfail from TALK, the discussion forum.}.
+
+The parameters required by various scaling relations and the models
+primarily depend on the photometry of the galaxies, groups and quasars
+detected in the survey. For galaxy-scale lenses, the lensing galaxies at
+higher redshifts or which are fainter have poor photometric redshift
+measurements. Consequently these galaxies are assigned a wrong
+luminosity and velocity dispersion estimates. This then results in
+simulated lenses which look implausible or unrealistic.  For example,
+the lensed images for some of the failed simulations have larger image
+separation than what you expect from the luminosity and/or size of the
+galaxy. We roughly expect mass to follow light so more massive galaxy
+typically looks brighter and/or bigger.
 
@@
 Spiral galaxies are typically less massive and low redshift spiral galaxies are
-unlikely to act as gravitational lenses. Hence, some of the simulated lenses
-were not as convincing.
+unlikely to act as gravitational lenses. Hence, some such instances
+do not appear convincing or the lensed images do not have the expected
+configuration or image separations.
 
@@
 such as star forming knots, spiral arms, bars and disks. The simulated lensed
-images do not display these features.
+images do not display these features. This is fine for most cases or
+mostly for images taken from ground based telescopes such as the CFHT
+but sometimes the shapes of the lensed images can appear symmetric or
+perfect, especially, if the images are very bright.
 
@@
 
-Citizen scientists not only need training to identify gravitational lenses, but
-also to reject images which either contain impostors or have no lenses. Hence,
-in addition to the simulated lenses, we added a sample of duds and false
-positives to the training sample. Duds are images which have been visually
-inspected by experts and confirmed to contain no lenses.  False positives (FPs)
-are systems which look like lenses but are not, for example, spiral galaxies,
-starforming galaxies, chance alignments of features arranged in a lensing
-configuration and stars.
+Citizen scientists need training not only to identify gravitational
+lenses, but also to reject images which either have no lenses or have
+objects which are lens impostors. Hence, in addition to the simulated
+lenses, we added a sample of duds and false positives to the training
+sample. Duds are images which have been visually inspected by experts
+and confirmed to contain no lenses. False positives (FPs) are systems
+which look like lenses but are not, for example, spiral galaxies,
+starforming galaxies, chance alignments of features arranged in a
+lensing configuration and stars.
 
@@
 systematically compiled sample of visually inspected false positives by
-the \sw volunteers and categorized by the science team. The data products are
-available at http://spacewarps.org/\#/projects/CFHTLS/. Such a sample is
-tremendously helpful for training and understanding performances of
-various lens finding algorithms \citep{Chan2014}.
+the \sw volunteers and categorized by the science team. We produce
+additional larger sample of a few thousand FPs by scanning through the
+low probability images after the completion of \StageTwo. All of these
+data products are available at
+http://spacewarps.org/\#/projects/CFHTLS/. Such a sample has tremendous
+utility for training and testing of various lens finding algorithms
+\citep[e.g.,][]{Chan2014}.
 
@@
 \label{sec:swap}
-The \sw works as a single unified neural network which uses the method of visual
-inspection to find gravitational lenses. The volunteers are shown images at two
-stages. At \StageOne, volunteers are requested to undertake a rapid inspection to
-select lens candiates ranging from possible lenses to almost certain lenses. At
-\StageTwo, volunteers carefully inspect the candidates from \StageOne and select only
-promising lens candidates. A daily snapshot of classifications performed by
-volunteers are provided to the science team every night. This daily batch is
-analyzed by the Space Warps Analysis Pipeline (SWAP). The philosophy and the
-details of SWAP are described in detail in Paper I, here we briefly summarize
-how it works.
+The \sw works as a single unified system which uses the method of visual
+inspection to find gravitational lenses. For the first \sw lens search,
+the volunteers were shown images at two stages. At \StageOne, volunteers
+are requested to undertake a rapid inspection to select lens candiates
+ranging from possible lenses to almost certain lenses. At \StageTwo,
+volunteers carefully inspect the candidates from \StageOne and select
+only promising lens candidates. A daily snapshot of classifications
+performed by volunteers are provided to the science team every night.
+This daily batch is analyzed by the Space Warps Analysis Pipeline
+(SWAP). The philosophy and the details of SWAP are described in detail
+in Paper I, here we briefly summarize how it works.
 
 Each subject (or image cutout) is assigned a prior probability of
-$2\times10^{-4}$ to contain a lens system. Every volunteer or classifier
+$2\times10^{-4}$ to contain a lens system. Every volunteer 
 is assigned an agent characterised by a $2\times2$ confusion matrix,
 which quantifies the volunteer's ability to correctly classify an image
-to contain ($P_L$) or not contain a lens system ($P_D$). The values of
+to contain a lens ($P_L$) or to not contain a lens ($P_D$). The values of
 the confusion matrix are determined based on the performance of the
@@
 correctly classified. After every classification, the agent updates the
-prior probability of the classified subject based on the classification
-and the volunteer's confusion matrix, according to the Bayes theorem.
+prior probability of the classified subject based on the volunteer's classification
+and the confusion matrix, according to the Bayes theorem.
 Note that the volunteer's confusion matrix is updated after the
-classification of every training image. Threshold values for the
-probabilities to accept (or reject) a subject  if it contains (or doesn
+classification of every training image. The thresholds for the
+probabilities to accept (or reject) a subject  if it contains (or does
 not contain) a lens can be chosen in SWAP. Those images which cross
@@
 small fraction of the real lenses (or non-lenses) to be assigned low (or high) P
-values and thus, decreasing the completeness (or purity) of the final lens
-sample.  As this is the first candidate search with \sw, we want to find a
+values thereby, decreasing the completeness (or purity) of the final lens
+sample. As this is the first lens search with \sw, we want to find a
 threshold P value which will result in acceptable levels of completeness and
@@
 
-We decided to inspect the top few hundreds of images from a catalog of
+We decided to inspect the top few hundreds of images from a catalog with
 descending P values as a reasonable sample size for visual inspection.
-We find a total of 665 subjects with P$>0.3$ in the catalog. These
-images were then visually inspected by three lens experts (AM, AV, PJM).
-The images are assigned grades on a scale of 0 to 3, thus dividing the
-subjects into candidates that almost certainly do not contain a lens,
-possibly a lens, probably a lens and almost certainly a lens,
-respectively. The final sample of \sw-\cfhtls lens candidates (see
-\Sref{sec:swlens}) is produced by selecting candidates above some
-threshold on the averaged grades.
+We choose P$>0.3$ for which we find a total of 665 subjects in the
+catalog. These images were then visually inspected by three lens experts
+(AM, AV, PJM).  The images are assigned grades on a scale of 0 to 3,
+thus dividing the subjects into candidates with the quality flag -
+unlikely lens, possibly a lens, probably a lens and almost certainly a
+lens, respectively. The final sample of \sw-\cfhtls lens candidates is
+then produced by selecting candidates above some threshold on the
+averaged grades as described in the next section.
 

### 2015-04-11 doc/sw-cfhtls.tex
read through and fixed sect 1-6

@@
 candidates with averaged grade $0<$G$<1.3$ (low probability sample)
-which means at least one of the inspector gave a grade of 1 and the
-maximum grade given by all three inspectors was 1\footnote{If grades
-from the inspectors were found to be discrepant by 2 or more, these were
-discussed and re-graded to resolve the discrepancy}. Further information
-on the low probability sample such as their positions and images are
-available at http://spacewarps.org/\#/projects/CFHTLS/.
+which means - in the worst case, at least one of the inspector thought
+the candidate is possibly a lens and in the best case, all three
+inspectors thought the candidate is possibly a lens (that is,
+a grade of 1)\footnote{If grades from the inspectors were found to be discrepant
+by 2 or more, these were discussed and re-graded to resolve the
+discrepancy.}. Further information on the low probability sample such as
+their positions and images is available at
+http://spacewarps.org/\#/projects/CFHTLS/. Note that if all of the inspectors gave
+a grade of 0 to a candidate, then it is discarded from the sample.
 
 There are a total of XXX candidates with $1.3\le$G$<2$ (medium
-probability sample) out of which 30 are new. These grades suggest that,
-most of the times, at least one of the inspectors gave a grade of 2 and
-the maximum grade by all of the inspectors was below 2. Among our high
+probability sample) out of which 30 are new. The quality of candidates
+in this category is such that at least one of the inspectors thought the
+candidate is most probably a lens (that is, a grade of 2) and a second inspector
+thought this is possibly a lens (that is, a grade of 1). Among our high
 probability sample (G$\ge$2), there are a total of XXX candidates out of
-which 28 are new which means at least two of the inspectors gave a grade
-of 2 or higher. To avoid duplication, further information on \sw
-candidates that were previously identified in the literature is
-available at http://spacewarps.org/\#/projects/CFHTLS/ whereas the new
-lens candidate sample of medium-high probability is presented in this
-paper (see \Sref{sec:results:newcand}).
-
-In Table~\ref{tab:stats}, we give overall statistics of the systems detected at
-\StageOne and \StageTwo. We give the total number of detections of the known lens
-candidates, known lenses and the new lens candidates at each stage.  We also
-show their fractions with respect to the total number of lens candidates found
-at these stages. We note that most (XXX check) of the confirmed lenses found at
-\StageOne are also recovered at \StageTwo whereas a small fraction of the known
-lens candidates are rejected at \StageTwo. Also, the sample of new lens
-candidates increases the sample of \cfhtls lens candidates by over 50\%.
-
-In \Fref{fig:stackP}, we plot the distribution of false positives and the high
-probability lens candidates, categorized by the lens experts, as a function of
-the P value assigned by SWAP at the end of \StageTwo. On average, the fraction of
-lens candidates is indeed an increasing function of P. This shows that the \sw
-generated P values for the subject are roughly correlated with the expert grades
-albeit with quite some scatter.  We note that from P$\sim$0.75 onwards to lower
-P values, the fraction of false positives starts to exceed the fraction of real
-lens candidates. This could be a good threshold to choose to maximize the purity
-of the final sample. However, the choice of P$=$0.3 as the threshold gives a
-more acceptable completeness of XXX for our sample which combined with expert
-grading allows us to achieve further purity of our sample.
+which 28 are new. In this category, the minimum grade by all of the
+inspectors was 2 suggesting that the candidates are probably or almost
+certainly lenses according to all of the inspectors. To avoid
+duplication, further information on \sw candidates that were previously
+identified in the literature is available at
+http://spacewarps.org/\#/projects/CFHTLS/ whereas the sample of new lens
+candidates with G$\ge 1.3$ (medium-high probability) is presented in this paper (see
+\Sref{sec:results:newcand}).
+
+In Table~\ref{tab:stats}, we give overall statistics of the systems
+detected at \StageOne and \StageTwo. We give the total number of
+detections of the known lens candidates, known lenses and the new lens
+candidates at each stage.  We also give the recovery fractions for the
+known samples and fraction of total detection for the new samples at
+each stage. We find that most (XXX check) of the confirmed lenses found
+at \StageOne are also recovered at \StageTwo whereas a small fraction of
+the known lens candidates are rejected at \StageTwo. Also, the sample of
+new lens candidates increases the sample of \cfhtls lens candidates by
+over 50\%.
+
+In \Fref{fig:stackP}, we plot the distribution of false positives and
+the high probability lens candidates, categorized by the lens experts,
+as a function of the P value assigned by SWAP at the end of \StageTwo.
+On average, the fraction of lens candidates is indeed an increasing
+function of P. This shows that the \sw generated P values for the
+subject are roughly correlated with the expert grades albeit with quite
+some scatter.  We note that from P$\sim$0.75 onwards to lower P values,
+the fraction of false positives starts to exceed the fraction of real
+lens candidates. This could be a good threshold to choose to maximize
+the purity of the final sample. However, we go with the choice of
+P$=$0.3 as this gives a more acceptable completeness of XXX for the
+known sample and thus, the new sample which combined with expert grading
+allows us to achieve further purity of our sample.
+
 %{\bf AM: give some numbers for the completeness/purity ? I will check what grades we gave to the stage 2 detected KLs and comment on it.}
@@
 candidates (medium-high probability) found by \sw in
-Table~\ref{tab:swcands}. We report the candidates with a \sw ID and Name of the
-lens system. We give their positions (Ra, Dec), photometric redshift
-($z_{phot}$), $i$ band magnitude of the lensing galaxy, averaged grade G from
-the lens experts, zoo ID (identifier used in TALK), P
-value at \StageTwo and a visual categorization of type of lensed images and the
-lensing galaxy in the Comments column in Table~\ref{tab:swcands}. Whenever
-available the lens properties are taken from the \cfhtls photometric catalog
-\citep{Coupon2009} otherwise the reported lens galaxy positions are measured
-manually. The visual categorization of the lens type is only suggestive and the
-explanation of the notations in the Comments column is given at the bottom of
-the table.
+Table~\ref{tab:swcands}. We report the candidates with a \sw ID and Name
+of the lens system. We give their positions (Ra, Dec), photometric
+redshift ($z_{phot}$), $i$ band magnitude of the lensing galaxy,
+averaged grade G from the lens experts, zoo ID (identifier used in
+TALK), P value at \StageTwo and a visual categorization of the type of
+lensed images and the lensing galaxy in the ``Comments'' column in
+Table~\ref{tab:swcands}. Whenever available the lens properties are
+taken from the \cfhtls photometric catalog \citep{Coupon2009} otherwise
+for the lens galaxy positions, the reported values are measured
+manually. The visual categorization of the lens type is only suggestive
+and the explanation of the notations in the Comments column is given at
+the bottom of the table.
 
@@
 hand, citizen scientists can do amazing amount of interpolation or
-extrapolation over the basic selection criteria provided to them. 
-For example,  the lower blue arc in SW7 is split by a small red galaxy.
-An algorithm typically fails to detect such arcs because the arc is
-broken into smaller arclets which then falls below the minimum length or
-area allowed for an arc to be detected typically. Human brains have no
+extrapolation over the basic selection criteria provided to them.  For
+example, the lower blue arc in SW7 is split by a small red galaxy.  An
+algorithm typically fails to detect such arcs because the arc is broken
+into smaller arclets which then falls below the minimum length or area
+allowed for an arc to be detected typically. Human brains have no
 problem in interpolating over the broken blue arc over the red galaxy
@@
 algorithm whereas the ring finding algorithm may miss this because of
-atypical color and structure of the galaxy.
-
-The power of citizen scientists lies in the high dynamic range that
-allows us to detect systems with very from small-to-large arcs, from
-highly compact-to-low surface brightness images, from round and
-point-like to elongated and curved images, from blue-to-red, from
-regular-to-exotic kinds of lenses while keeping the false positive rate
-comparatively low. Further detailed qualitative and quantitative
-analysis of the properties of the entire \sw sample (new and previously
-identified candidates) and the mass modelling analyses for the new
-candidates will be presented in a subsequent \sw paper, Paper III.
+atypical color and structure of the galaxy. Detection of red arcs, for
+example, as seen in the SW38 candidate show how the volunteers
+extrapolate on the color parameter because the training sample mostly
+has blue arcs since this is the typical expectation.
+
+The power of citizen scientists also lies in the high dynamic range that
+allows us to find systems with very from short (thick) to long (thin)
+arcs, from highly compact to low surface brightness images, from round
+and point-like to elongated and curved images, from blue to red, from
+regular to exotic kinds of lenses while keeping the false positive rate
+low compared to algorithms. Discovery of this large sample of completely
+new candidates missed by some of these algorithms demonstrates that the
+\sw system is functioning well and the self-taught citizen scientists
+have managed to beat the robots in some sense.
+
+Further detailed qualitative and quantitative analysis of the properties
+of the entire \sw sample (new and previously identified candidates) and
+the mass modelling analyses for the new candidates will be presented in
+a subsequent \sw paper, Paper III.
 
@@
 In the subsequent sections, we make comparison of various properties of the lens
-candidates. In this section, we describe how we extract these properties, namely,
+candidates. Here, we describe how we extract or measure these properties, namely,
 the lens redshift, the Einstein radii and the total flux of the lensed images or
@@
 magnitude. For the \rf sample, the arcs are detected in the scaled
-difference image between $g$ and $i$ bands where the lensing galaxy is
+difference image of $g$ and $i$ bands from which the lensing galaxy is
 subtracted \citep[for details, see]{Gavazzi2014}. Here, we use the flux
@@
 different samples. For the galaxy-scale lenses in the simulated sample,
-we use the value of the input lens model parameter for the $R_{\rm E}$.
+we use the value of the input parameter of the lens model for the $R_{\rm E}$.
 For groups-scale lenses, since the lens model is multi-component, we
@@
 
-Indeed, we have find several new lens candidates that were not known
+Indeed, we have found several new lens candidates that were not known
 before. In \Fref{fig:isd}, we show the image separation distribution for
-the known sample (green), for the \sw identified (known and new) lens
-sample (blue) only and combined known with the new \sw lens sample
-(magenta). It is interesting to note that both these samples have very
-similar profiles and thus, the profile of the combined sample has not
-changed much. This implies that previous constraints on the image
-separation distribution are robust and the \af selected sample does not
-suffer from significant incompleteness for medium to large Einstein
-radii. This is the regime that probes density profiles of galaxy groups
-to clusters.
+the known \rf and \af sample (green), for the \sw identified (known and
+new) lens sample (blue) only and combined \cfhtls sample of \rf, \af and
+the new \sw lens sample (magenta). It is interesting to note that both
+these samples have very similar profiles and thus, the profile of the
+combined sample has not changed signficantly. This implies that previous
+constraints on the image separation distribution are robust and the \af
+selected sample does not suffer from significant incompleteness for
+medium to large Einstein radii. This is the regime that probes density
+profiles of galaxy groups to clusters.
 %%{\bf AM: understand what Phil wanted to say about AF's (in)completeness}

### 2015-04-11 doc/sw-cfhtls.tex
read through and fixed sect 1-6

@@
 Table~\ref{tab:thresh}, which increases the occurrence of lensing. We
-draw a Poisson deviate with a mean equal to the boosted average number
-of sources. If the Poisson deviate is greater than zero, then 
-this galaxy is flagged as a potential lensing galaxy with
-Nsrc number of background sources. {\bf XXXX check if this is correct.}
+draw a Poisson deviate, $N_{\rm src}$ with a mean equal to the boosted
+average number of sources. If $N_{\rm src}$ is greater than zero, then
+this galaxy is flagged as a potential lensing galaxy.
 

### 2015-04-12 doc/sw-cfhtls.tex
read through and fixed sect 1-6 & 8

@@
 
-Finding gravitational lenses is a difficult and complex task. No one
+Finding gravitational lenses is a difficult and complex task. No single
 method is perfect. Each method has some advantages over the other. It
@@
 In this section, we first compare the lens candidates found by
-\sw and the lens finding robots and then attemp to understand why each
+\sw and the lens finding robots and then attempt to understand why each
 method failed to detect lenses from the other sample.
@@
 (green), the \af (red) and the \sw sample (new candidates only in blue
-and known candidates as black circles). We note that the errors on the
+and known candidates as blue circles). We note that the errors on the
 redshift measurement should not be too different across the samples
@@
 The \af, on the other hand, is capable of finding smaller image
-separation lenses but a lower limit on $R_{\rm E}$ was imposed by the
-\af team to simplify the selection function of their sample. Thus, we
-can compare the \sw and \af samples at about $R_{\rm E}>2\arcsec$. There
-is a good overlap between the two samples given that most of these are
-candidates and could turn out be not lenses. We again caution the
-readers that the uncertainties on the measurements are not quantified
-and may change the results to some extent.
+separation lenses but a lower limit at $R_{\rm E}=2\arcsec$ was imposed
+by the \af team to simplify the selection function of their sample.
+Thus, we can compare the \sw and \af samples at about $R_{\rm
+E}>2\arcsec$. There is a good overlap between the two samples given that
+most of these are candidates and could turn out be not lenses. We again
+caution the readers that the uncertainties on the measurements are not
+quantified and may change the results to some extent.
 
@@
 Einstein radius for all of the three lens samples, namely, the \rf (green dots),
-\sw (known candidates$-$black circles and new candidates only$-$blue dots)
+\sw (known candidates$-$blue circles and new candidates only$-$blue dots)
 and \af (red dots). Alls samples have broadly similar properties.}
@@
 \subsection{Why \sw candidates were missed by lens finding robots?}
-We rerun the \rf and \af on images centered on the new \sw candidates to
+We test the \rf and \af on images centered on the new \sw candidates to
 trace and understand at what stage the algorithm failed to detect them.
@@
 as lenses. We find that about 40\% of the new \sw candidates fail to
-meet this initial selection criteria, for example, SW1, SW13, SW19, SW22, SW26
-and SW29.  All of the lensing galaxies are bright enough to satisfy the
-$i<22$ criterion. However, some of them have a bright companion galaxy,
-some of them do not look like E/S0 type galaxies and some are edge on
-galaxies.
+meet this initial selection criteria, for example, SW1, SW13, SW19,
+SW22, SW26 and SW29.  All of the lensing galaxies are bright enough to
+satisfy the magnitude criterion ($i<22$). However, some of them have a
+bright companion galaxy, some of them do not look like E/S0 type
+galaxies and some are edge on galaxies which could be the reason for
+excluding these galaxies from the inital catalog.
 
@@
 lensed features. An object finder is run on this image to quantify the
-lensed image properties. About 50\% of the \sw candidates could not be
+lensed image properties. Another $\sim$~50\% of the \sw candidates could not be
 detected by the object finder because properties such as the image area,
@@
 of the thresholds in the code because of the change in the noise level.
-%{\bf does this make sense?}
+%{\bf does this make sense? - list the IDs of these systems?}
 
@@
 elongation stimator above a certain threshold are connected to form the arc
-feature. This is building of the arc candidate. Subsequently, arc
+feature. This is called the segmentation of the arc candidate. Subsequently, arc
 properties such as the area, mean flux, length and curvature are
-determined. We relax the threshold at the building stage and also relax
+determined. We relax the threshold at the segmentation stage and also relax
 thresholds mainly on the area of the arc which leads to detection of
 about 75\% of the new \sw candidates. We find that relaxing thresholds
-on other arc properties do not improve the detection rate significantly
-and thus are left unchanged.
-
-Typically, the candidates are missed from the \af sample if a) they are
-brighter in the redder band rather than the bluer $g$ band used for arc
-detection because then the arc feature will be at the noise level and
-will fail detection b) the flux of the arc and the galaxy are
-blended in the $g$ band such that the \af mistakenly connects part of the
-galaxy to the pixels belonging to the arc candidate which then results in a
-candidate with no morphological characteristics of an arc or c) if the
-candidate is not elongated which means most of the lensed quasars with
-circular looking lensed images will be missed.
-
-Relaxing the thresholds obviously increases the total number of
-candidate detections which includes a large sample of false positives.
+on other arc properties does not improve the detection rate significantly
+and thus, those thresholds are left unchanged.
+
+Typically, the candidates are missed from the \af sample if a) the arcs
+are fainter in $g$ band which is used for arc detection because then the
+arc feature is at the noise level and fails detection b) the flux of the
+arc and the galaxy are blended in the $g$ band such that the \af
+incorrectly connects part of the galaxy to the arc. This results in a
+candidate with no morphological characteristics of a typical arc c)
+unusually short or thick arcs or d) if the lensed images are almost
+circular or point-like which means most of the lensed quasars images
+will be missed.
+
+Relaxing the thresholds obviously increases the number of candidate arc
+detections but this also includes a large sample of false positives.
 For example, the number of arc candidate detections increase by a factor
@@
 \label{sec:fn}
+%{\bf: test the delta logP cut on the FPs to see if there's any increase in FP rate}
 Like any lens finding method, the \sw system can fail to detect certain
@@
 are missed both at \StageOne and II (see \Tref{tab:stats}). In fact, most
-of the known lenses from \StageOne are discovered at \StageTwo suggesting
-that most lenses are lost right at \StageOne. Below, we focus on the known
+of the known lenses from \StageOne are discovered at \StageTwo which
+means that the lenses are lost already at \StageOne. Below, we focus on the known
 lens sample at \StageOne to understand why some of them are being missed
@@
 
-For a lens finding method which uses collective skill, experience and
+For a lens finding method which uses the collective skill, experience and
 knowledge of a group of volunteers, it may be difficult to find a single
@@
 continue to remain for long in the database because these candidates are
-possibly difficult to identify. Therefore, the distribution of Nclass
-can not be the reason for losing the lenses from the missed sample.
+possibly difficult to identify. Overall, we do not find any correlation
+for the detected and the missed sample with Nclass.
 
@@
 the known lens candidates sample, respectively. We note that the density
-of points do not represent the actual number of detections because, for some
-cases, randomly selected subsamples are shown for the ease of visual
-comparison.
+of points do not represent the actual number of detections because, for
+cases with large sample size, randomly drawn subsamples are shown for
+the ease of visual comparison.
 
@@
 changes as the image receives more classifications from multiple
-volunteers.  In \Fref{fig:detmis}, we show the trajectory plots of a few
-examples of detected lenses (top left panels) and missed lenses (bottom
-left panels) by \sw at \StageOne. The number of classifications (Nclass)
-for a subject increase from top to bottom.  Also, every subject is
-assigned a prior probability P0$=2\times10^{-4}$ (grey dashed line) and
-starts at the middle of the trajectory plot. The P value of a subject is
-updated with every classification from the volunteer.  If a volunteer
-identifies a lens candidate, the trajectory moves to the right otherwise
-moves to the left. A subject is accepted if it crosses the blue-dashed
-line marking the (P$_{\rm acc thresh}=0.95$) on the right and is
-rejected, if it crosses the red-dashed line marking the P$_{\rm rej
-thresh}=10^{-7}$ on the left.
+volunteers. A graphical representation of changing probabilities for
+increasing classifications is called a trajectory plot. In
+\Fref{fig:detmis}, we show the trajectory plots of a few examples of
+detected lenses (top left panels) and missed lenses (bottom left panels)
+from \StageOne of \sw. The number of classifications (Nclass) for a
+subject increase from top to bottom.  Also, every subject is assigned a
+prior probability P0$=2\times10^{-4}$ (grey dashed line) and starts at
+the middle of the trajectory plot. The P value of a subject is updated
+with every classification from the volunteer.  If a volunteer identifies
+a lens candidate, the trajectory moves to the right otherwise moves to
+the left. A subject is accepted if it crosses the blue-dashed line
+marking the (P$_{\rm acc thresh}=0.95$) on the right and is rejected, if
+it crosses the red-dashed line marking the P$_{\rm rej thresh}=10^{-7}$
+on the left.
 
@@
 is small if $\Delta$ log(P)$=$log (P$_{\rm current}) - $log(P$_{\rm
-previous}) < \Delta$log(P)$_{\rm cut}$ (chosen to be 1.2) and is large
+previous}) < \Delta$log(P)$_{\rm cut}$ (chosen as 1.2) and is large
 if greather than $\Delta$log(P)$_{\rm cut}$.
@@
 volunteers - positive small and large kicks and negative small kicks.
-iii) the Nclass from volunteers with negative large kicks are lower both
-for the detected and the missed samples. this is consistent with our
+iii) the Nclass from volunteers with negative large kicks are lower, both
+for the detected and the missed samples. This is consistent with our
 expectation that high power volunteers should not be making incorrect
-classifications.Therefore, lack of high power volunteers classifying
+classifications. Therefore, lack of high power volunteers classifying
 the missed lenses seems to be one of the major factors.
@@
 
-We report the discovery of new gravitational lens candidates from the
-the first lens search through \sw. In this search, volunteers are shown
+We report the discovery of gravitational lens candidates from the
+the first \sw lens search. In this search, volunteers are shown
 $g-r-i$ color images of random regions of the sky taken by the CFHT Legacy
@@
 The blind lens search in the \cfhtls is done in two stages: \StageOne and
-\StageTwo. In \StageOne, volunteers inspected $\sim$ 430 000 subjects and
-selected a smaller sample of $\sim$ 3000 subjects with interesting lens
+\StageTwo. In \StageOne, volunteers inspected $\sim$ 430 000 images and
+selected a smaller sample of $\sim$ 3000 images with interesting lens
 candidates. In \StageTwo, after a careful reinspection of the candidates
@@
 candidates is obtained. In the next step, the images are graded by three
-lens experts (AM, AV and PJM) producing candidates that range from
-mildly interesting to certainly a lens system.
-
-In this paper (Paper II), we present the new \sw sample and compare this
+lens experts (AM, AV and PJM) producing candidates with quality flags
+ranging from possibly a lens to almost certainly a lens.
+
+In this paper (Paper II), we present the new \sw sample and compare it
 with the previously known samples from two robotic searches from the
-\cfhtls namely, the \rf and \af. And, further details about the new
-sample such as any follow up confirmation and investigations including
-mass modelling analysis will be presented in a subsequent \sw paper
-(Paper III).
+\cfhtls namely, the \rf and \af. More detailed description and analyses
+of the new sample such as spectroscopic confirmation and mass modelling
+analysis will be presented in a subsequent \sw paper (Paper III).
 
@@
 out of which 28 are more promising systems. These candidates received
-averaged grades, G$\ge$1.3 from three experts where 1-mildly interesting,
+averaged grades, G$\ge$1.3 from three experts where 1-possibly, a lens,
 2-probably, a lens and 3-certainly, a lens. Another sample of over 100
@@
 edge on) and small red galaxies unlike those found from robotic
-searches. Similarly, the lensed images too have different colors,
-morphologies and sizes which are again typically missed by any given
-algorithm.
+searches. Similarly, the lensed images too have diverse properties such
+as different colors, morphologies and sizes which are again typically
+missed by any given algorithm.
 
@@
 
-\item If we use the classifications from more skilled volunteers alone
+\item If we use the classifications from the high power volunteers alone
 at \StageOne, then we recover over 30\% of the lenses from the missed
@@
 \end{itemize}
+
+The discovery of several new candidates through the first \sw lens
+search has demonstrated that the citizen scientists have successfully
+taught themselves to identify lenses within a short span of time and
+that they have found lens candidates which the algorithms failed to
+discover.  However, the upcoming and planned imaging surveys such as the
+DES, HSC and LSST will have formidable amount of data. Any one approach
+for finding lenses is likely going to be inefficient. Thus, combining
+robotic methods for pre-selection with the citizen science approach for
+visual screening will be an optimal choice for finding lenses in these
+large imaging surveys.
 
@@
 negative kicks. The panel f represents a small fraction of this sample
-where the kics are only short and negative. The panel g shows how some
+where the kicks are only short and negative. The panel g shows how some
 lenses receive a bunch of large positive kicks which are led to
@@
 in each panel can be thought of counterparts of the trajectories of the missed
-lenses in the corresponding bottom panel except that the type of volunteers are
+lenses in the corresponding bottom panels except that the type of volunteers are
 different. Most detected lenses are similar to the case in panel a which are
@@
 between positive and negative kicks whereas the panel d represents the extreme
-cases when the subjects are on the verge of being rejected but are saved thanks
+cases when the images are on the verge of being rejected but are saved thanks
 to a series of large positive kicks. The red trajectories are some more
@@
 still possible for a volunteer located in the (lower) upper triangle
-with different combinations of ($P_{\rm L}$,$P_{\rm D}$) suggesting that
-the kick is not a simple function of ($P_{\rm L}$,$P_{\rm D}$).
+with different combinations of ($P_{\rm L}$, $P_{\rm D}$) suggesting that
+the kick is not a simple function of ($P_{\rm L}$, $P_{\rm D}$).
 
@@
 magnitude gives a useful measure of an agent's ``Power'' to move
-subjects closer to detection.  Note that a volunteer who is very good at
+images closer to detection.  Note that a volunteer who is very good at
 rejecting duds, but not so good at identifying lenses, may have a high
@@
 \caption{ \label{fig:skilldlnp}
-Skill of the volunteers, $\Delta\log(P)$ given a lens or not a lens in
-an image as a function of $P_{\rm L}$ and $P_{\rm D}$. Each of these
-quantities represent ability of the Volunteers but do not have a simple
+Skill of the volunteers and $\Delta\log(P)$ given a lens or not a lens in
+an image as a function of $P_{\rm L}$ and $P_{\rm D}$. These
+quantities indicate the ability of the volunteers but do not have a simple
 linear relation with $P_{\rm L}$ and $P_{\rm D}$.  

### 2015-04-12 doc/sw-cfhtls.tex
read through all sections

@@
 \label{sec:fn}
-%{\bf: test the delta logP cut on the FPs to see if there's any increase in FP rate}
 Like any lens finding method, the \sw system can fail to detect certain
@@
 volunteers. We understand that changing the rejection and acceptance
-thresholds will likely increase the rate of FPs along with
-improved completeness but most probably the increase in FPs will not be
-too significant and that it will still be worth using the new strategy.
+thresholds will likely increase the rate of FPs along with improved
+completeness. After testing on a subsample of both \StageOne and
+\StageOne FPs, we find that a small fraction of FPs are rejected when
+only classifications with $\Delta$ log(P)$>1.2$ only are considered.
+Therefore, we think it is worth adopting the new strategy in the future
+runs of SWAP in future lens searches.
 
@@
 $\Delta\log(P)$? This figure and this section still needs to be
-polished.}
+polished. }
 }

### 2015-04-12 doc/sw-cfhtls.tex
read through all sections

@@
 galaxies whose positions match with the lensing galaxies from the SARCS
-samples within 2~arcsec (XXX check).
+samples within 2~arcsec.
 
@@
 Distributions of properties of the lensing galaxies of the simulated
-sample compared to the known lens sample SARCS. %(XXXX confirm what's being plotted? which band - i?)
+sample compared to the known lens sample SARCS. 
 }
@@
 In this section, we describe the \sw-\cfhtls lens sample (henceforth,
-called the \sw lens sample). We find a total of XXX (and XXX new)
+called the \sw lens sample). We find a total of  (and XXX new)
 candidates with averaged grade $0<$G$<1.3$ (low probability sample)
@@
 profiles of galaxy groups to clusters.
-%%{\bf AM: understand what Phil wanted to say about AF's (in)completeness}
 
@@
 accurate analysis is deferred to the future.
-%{\bf check out of the 55 promising \af how many are missed by \sw ?}
 
@@
 only 2 out of this sample of 18 were detected at \StageOne (reached high P even with fewer classifications) and missed at \StageTwo (P value was low even after recieving very many classifications).
-The rest of the 16 lenses were rejected right at \StageOne XXX}
+The rest of the 16 lenses were rejected right at \StageOne }
 %One of those 6 lenses was detected at \StageOne but failed to get high enough P value at \StageTwo even after receiving a total of 50 classifications (set as the upper limit).

### 2015-04-12 doc/sw-cfhtls.tex
read through all sections

@@
 artificially boost the average number of sources by a factor (see
-Table~\ref{tab:thresh}, which increases the occurrence of lensing. We
+Table~\ref{tab:thresh}), which increases the occurrence of lensing. We
 draw a Poisson deviate, $N_{\rm src}$ with a mean equal to the boosted
@@
 located within the caustics will form multiple lensed images which is the
-criteria for strong lensing. To further understand caustics, see XXX.}.
+criteria for strong lensing. To further understand caustics, see e.g., \citet{Schneider1992}.}.
 Therefore, we generate the caustics numerically using \gravlens and then
@@
 As mentioned earlier, we artificially boost the total number of sources behind
-every lens but ensure that (check XXX) the statistical properties such as the profile of the
+every lens but ensure that the statistical properties such as the profile of the
 image separation distribution are not affected (see \Fref{fig:remudist}). We
@@
 In this section, we describe the \sw-\cfhtls lens sample (henceforth,
-called the \sw lens sample). We find a total of  (and XXX new)
+called the \sw lens sample). We find a total of XXX (and XXX new)
 candidates with averaged grade $0<$G$<1.3$ (low probability sample)
@@
 images.
-%(XXXX check how different are the estimates from the different measurement techniques for a given lens candidates.)
+%{\bf check how different are the estimates from the different
+%measurement techniques for a given lens candidates.}
 }

### 2015-04-13 doc/sw-cfhtls.tex
read through all sections

@@
 We begin by considering all elliptical galaxies at $z<1$ in our parent
-\cfhtls catalog \citep[(XXX confirm with Raphael)]{Gavazzi2014} as
-potential lens candidates for the simulated sample. To avoid using a
-known lens galaxy for our simulation purpose, we exclude all those
-galaxies whose positions match with the lensing galaxies from the SARCS
-samples within 2~arcsec.
+\cfhtls catalog \citep[]{Gavazzi2014} as potential lens candidates for
+the simulated sample. To avoid using a known lens galaxy for our
+simulation purpose, we exclude all those galaxies whose positions match
+with the lensing galaxies from the SARCS samples within 2~arcsec.
 
@@
 and a total (NFW+Hernquist) model at groups-scales taken from \citep{More2012}.
-%{\bf fix the normalization}
 }
@@
 In this section, we describe the \sw-\cfhtls lens sample (henceforth,
-called the \sw lens sample). We find a total of XXX (and XXX new)
+called the \sw lens sample). We find a total of 288 (and XXX new)
 candidates with averaged grade $0<$G$<1.3$ (low probability sample)
@@
 
-There are a total of XXX candidates with $1.3\le$G$<2$ (medium
+There are a total of 91 candidates with $1.3\le$G$<2$ (medium
 probability sample) out of which 30 are new. The quality of candidates
@@
 thought this is possibly a lens (that is, a grade of 1). Among our high
-probability sample (G$\ge$2), there are a total of XXX candidates out of
+probability sample (G$\ge$2), there are a total of 50 candidates out of
 which 28 are new. In this category, the minimum grade by all of the
@@
 known samples and fraction of total detection for the new samples at
-each stage. We find that most (XXX check) of the confirmed lenses found
+each stage. We find that all of the confirmed lenses found
 at \StageOne are also recovered at \StageTwo whereas a small fraction of
-the known lens candidates are rejected at \StageTwo. Also, the sample of
-new lens candidates increases the sample of \cfhtls lens candidates by
-over 50\%.
+the known lens candidates are rejected at \StageTwo. From the visually
+inspected known lens sample at \StageTwo (P$> 0.3$), the experts gave a
+grade of 1.3 and above to about 92\% (33 out of 36) of the systems. Overall,
+the sample of new \sw lens candidates increased the sample of total
+\cfhtls lens candidates by over 50\%.
 
@@
 the purity of the final sample. However, we go with the choice of
-P$=$0.3 as this gives a more acceptable completeness of XXX for the
-known sample and thus, the new sample which combined with expert grading
-allows us to achieve further purity of our sample.
-
-%{\bf AM: give some numbers for the completeness/purity ? I will check what grades we gave to the stage 2 detected KLs and comment on it.}
+P~$=$~0.3 as this gives a better completeness of 100\% for the ``known
+lens'' sample instead of 67\% for P~$=$~0.75. Therefore, the new sample
+should also have increased completeness which combined with expert
+grading allows us to achieve further purity of our sample.
 
@@
 which the magnitudes and the redshift are extracted.
-%{\bf Note:} $\dagger$ are systems found in \citet{Gavazzi2014} as part of the additional
+%Note: $\dagger$ are systems found in \citet{Gavazzi2014} as part of the additional
 %sample and $\ast$ is found in \citet{Maturi2014} sample.

### 2015-04-13 doc/sw-cfhtls.tex

--- 2015-04-12 doc/sw-cfhtls.tex
@@
 galaxies whose positions match with the lensing galaxies from the SARCS
-samples within 2~arcsec.
+samples within 2~arcsec (XXX check).
 
@@
 Distributions of properties of the lensing galaxies of the simulated
-sample compared to the known lens sample SARCS. 
+sample compared to the known lens sample SARCS. %(XXXX confirm what's being plotted? which band - i?)
 }
@@
 profiles of galaxy groups to clusters.
+%%{\bf AM: understand what Phil wanted to say about AF's (in)completeness}
 
@@
 
-Finding gravitational lenses is a difficult and complex task. No single
+Finding gravitational lenses is a difficult and complex task. No one
 method is perfect. Each method has some advantages over the other. It
@@
 In this section, we first compare the lens candidates found by
-\sw and the lens finding robots and then attempt to understand why each
+\sw and the lens finding robots and then attemp to understand why each
 method failed to detect lenses from the other sample.
@@
 (green), the \af (red) and the \sw sample (new candidates only in blue
-and known candidates as blue circles). We note that the errors on the
+and known candidates as black circles). We note that the errors on the
 redshift measurement should not be too different across the samples
@@
 The \af, on the other hand, is capable of finding smaller image
-separation lenses but a lower limit at $R_{\rm E}=2\arcsec$ was imposed
-by the \af team to simplify the selection function of their sample.
-Thus, we can compare the \sw and \af samples at about $R_{\rm
-E}>2\arcsec$. There is a good overlap between the two samples given that
-most of these are candidates and could turn out be not lenses. We again
-caution the readers that the uncertainties on the measurements are not
-quantified and may change the results to some extent.
+separation lenses but a lower limit on $R_{\rm E}$ was imposed by the
+\af team to simplify the selection function of their sample. Thus, we
+can compare the \sw and \af samples at about $R_{\rm E}>2\arcsec$. There
+is a good overlap between the two samples given that most of these are
+candidates and could turn out be not lenses. We again caution the
+readers that the uncertainties on the measurements are not quantified
+and may change the results to some extent.
 
@@
 accurate analysis is deferred to the future.
+%{\bf check out of the 55 promising \af how many are missed by \sw ?}
 
@@
 Einstein radius for all of the three lens samples, namely, the \rf (green dots),
-\sw (known candidates$-$blue circles and new candidates only$-$blue dots)
+\sw (known candidates$-$black circles and new candidates only$-$blue dots)
 and \af (red dots). Alls samples have broadly similar properties.}
@@
 \subsection{Why \sw candidates were missed by lens finding robots?}
-We test the \rf and \af on images centered on the new \sw candidates to
+We rerun the \rf and \af on images centered on the new \sw candidates to
 trace and understand at what stage the algorithm failed to detect them.
@@
 as lenses. We find that about 40\% of the new \sw candidates fail to
-meet this initial selection criteria, for example, SW1, SW13, SW19,
-SW22, SW26 and SW29.  All of the lensing galaxies are bright enough to
-satisfy the magnitude criterion ($i<22$). However, some of them have a
-bright companion galaxy, some of them do not look like E/S0 type
-galaxies and some are edge on galaxies which could be the reason for
-excluding these galaxies from the inital catalog.
+meet this initial selection criteria, for example, SW1, SW13, SW19, SW22, SW26
+and SW29.  All of the lensing galaxies are bright enough to satisfy the
+$i<22$ criterion. However, some of them have a bright companion galaxy,
+some of them do not look like E/S0 type galaxies and some are edge on
+galaxies.
 
@@
 lensed features. An object finder is run on this image to quantify the
-lensed image properties. Another $\sim$~50\% of the \sw candidates could not be
+lensed image properties. About 50\% of the \sw candidates could not be
 detected by the object finder because properties such as the image area,
@@
 of the thresholds in the code because of the change in the noise level.
-%{\bf does this make sense? - list the IDs of these systems?}
+%{\bf does this make sense?}
 
@@
 elongation stimator above a certain threshold are connected to form the arc
-feature. This is called the segmentation of the arc candidate. Subsequently, arc
+feature. This is building of the arc candidate. Subsequently, arc
 properties such as the area, mean flux, length and curvature are
-determined. We relax the threshold at the segmentation stage and also relax
+determined. We relax the threshold at the building stage and also relax
 thresholds mainly on the area of the arc which leads to detection of
 about 75\% of the new \sw candidates. We find that relaxing thresholds
-on other arc properties does not improve the detection rate significantly
-and thus, those thresholds are left unchanged.
-
-Typically, the candidates are missed from the \af sample if a) the arcs
-are fainter in $g$ band which is used for arc detection because then the
-arc feature is at the noise level and fails detection b) the flux of the
-arc and the galaxy are blended in the $g$ band such that the \af
-incorrectly connects part of the galaxy to the arc. This results in a
-candidate with no morphological characteristics of a typical arc c)
-unusually short or thick arcs or d) if the lensed images are almost
-circular or point-like which means most of the lensed quasars images
-will be missed.
-
-Relaxing the thresholds obviously increases the number of candidate arc
-detections but this also includes a large sample of false positives.
+on other arc properties do not improve the detection rate significantly
+and thus are left unchanged.
+
+Typically, the candidates are missed from the \af sample if a) they are
+brighter in the redder band rather than the bluer $g$ band used for arc
+detection because then the arc feature will be at the noise level and
+will fail detection b) the flux of the arc and the galaxy are
+blended in the $g$ band such that the \af mistakenly connects part of the
+galaxy to the pixels belonging to the arc candidate which then results in a
+candidate with no morphological characteristics of an arc or c) if the
+candidate is not elongated which means most of the lensed quasars with
+circular looking lensed images will be missed.
+
+Relaxing the thresholds obviously increases the total number of
+candidate detections which includes a large sample of false positives.
 For example, the number of arc candidate detections increase by a factor
@@
 are missed both at \StageOne and II (see \Tref{tab:stats}). In fact, most
-of the known lenses from \StageOne are discovered at \StageTwo which
-means that the lenses are lost already at \StageOne. Below, we focus on the known
+of the known lenses from \StageOne are discovered at \StageTwo suggesting
+that most lenses are lost right at \StageOne. Below, we focus on the known
 lens sample at \StageOne to understand why some of them are being missed
@@
 
-For a lens finding method which uses the collective skill, experience and
+For a lens finding method which uses collective skill, experience and
 knowledge of a group of volunteers, it may be difficult to find a single
@@
 continue to remain for long in the database because these candidates are
-possibly difficult to identify. Overall, we do not find any correlation
-for the detected and the missed sample with Nclass.
+possibly difficult to identify. Therefore, the distribution of Nclass
+can not be the reason for losing the lenses from the missed sample.
 
@@
 only 2 out of this sample of 18 were detected at \StageOne (reached high P even with fewer classifications) and missed at \StageTwo (P value was low even after recieving very many classifications).
-The rest of the 16 lenses were rejected right at \StageOne }
+The rest of the 16 lenses were rejected right at \StageOne XXX}
 %One of those 6 lenses was detected at \StageOne but failed to get high enough P value at \StageTwo even after receiving a total of 50 classifications (set as the upper limit).
@@
 the known lens candidates sample, respectively. We note that the density
-of points do not represent the actual number of detections because, for
-cases with large sample size, randomly drawn subsamples are shown for
-the ease of visual comparison.
+of points do not represent the actual number of detections because, for some
+cases, randomly selected subsamples are shown for the ease of visual
+comparison.
 
@@
 changes as the image receives more classifications from multiple
-volunteers. A graphical representation of changing probabilities for
-increasing classifications is called a trajectory plot. In
-\Fref{fig:detmis}, we show the trajectory plots of a few examples of
-detected lenses (top left panels) and missed lenses (bottom left panels)
-from \StageOne of \sw. The number of classifications (Nclass) for a
-subject increase from top to bottom.  Also, every subject is assigned a
-prior probability P0$=2\times10^{-4}$ (grey dashed line) and starts at
-the middle of the trajectory plot. The P value of a subject is updated
-with every classification from the volunteer.  If a volunteer identifies
-a lens candidate, the trajectory moves to the right otherwise moves to
-the left. A subject is accepted if it crosses the blue-dashed line
-marking the (P$_{\rm acc thresh}=0.95$) on the right and is rejected, if
-it crosses the red-dashed line marking the P$_{\rm rej thresh}=10^{-7}$
-on the left.
+volunteers.  In \Fref{fig:detmis}, we show the trajectory plots of a few
+examples of detected lenses (top left panels) and missed lenses (bottom
+left panels) by \sw at \StageOne. The number of classifications (Nclass)
+for a subject increase from top to bottom.  Also, every subject is
+assigned a prior probability P0$=2\times10^{-4}$ (grey dashed line) and
+starts at the middle of the trajectory plot. The P value of a subject is
+updated with every classification from the volunteer.  If a volunteer
+identifies a lens candidate, the trajectory moves to the right otherwise
+moves to the left. A subject is accepted if it crosses the blue-dashed
+line marking the (P$_{\rm acc thresh}=0.95$) on the right and is
+rejected, if it crosses the red-dashed line marking the P$_{\rm rej
+thresh}=10^{-7}$ on the left.
 
@@
 is small if $\Delta$ log(P)$=$log (P$_{\rm current}) - $log(P$_{\rm
-previous}) < \Delta$log(P)$_{\rm cut}$ (chosen as 1.2) and is large
+previous}) < \Delta$log(P)$_{\rm cut}$ (chosen to be 1.2) and is large
 if greather than $\Delta$log(P)$_{\rm cut}$.
@@
 volunteers - positive small and large kicks and negative small kicks.
-iii) the Nclass from volunteers with negative large kicks are lower, both
-for the detected and the missed samples. This is consistent with our
+iii) the Nclass from volunteers with negative large kicks are lower both
+for the detected and the missed samples. this is consistent with our
 expectation that high power volunteers should not be making incorrect
-classifications. Therefore, lack of high power volunteers classifying
+classifications.Therefore, lack of high power volunteers classifying
 the missed lenses seems to be one of the major factors.
@@
 volunteers. We understand that changing the rejection and acceptance
-thresholds will likely increase the rate of FPs along with improved
-completeness. After testing on a subsample of both \StageOne and
-\StageOne FPs, we find that a small fraction of FPs are rejected when
-only classifications with $\Delta$ log(P)$>1.2$ only are considered.
-Therefore, we think it is worth adopting the new strategy in the future
-runs of SWAP in future lens searches.
+thresholds will likely increase the rate of FPs along with
+improved completeness but most probably the increase in FPs will not be
+too significant and that it will still be worth using the new strategy.
 
@@
 negative kicks. The panel f represents a small fraction of this sample
-where the kicks are only short and negative. The panel g shows how some
+where the kics are only short and negative. The panel g shows how some
 lenses receive a bunch of large positive kicks which are led to
@@
 in each panel can be thought of counterparts of the trajectories of the missed
-lenses in the corresponding bottom panels except that the type of volunteers are
+lenses in the corresponding bottom panel except that the type of volunteers are
 different. Most detected lenses are similar to the case in panel a which are
@@
 still possible for a volunteer located in the (lower) upper triangle
-with different combinations of ($P_{\rm L}$, $P_{\rm D}$) suggesting that
-the kick is not a simple function of ($P_{\rm L}$, $P_{\rm D}$).
+with different combinations of ($P_{\rm L}$,$P_{\rm D}$) suggesting that
+the kick is not a simple function of ($P_{\rm L}$,$P_{\rm D}$).
 
@@
 \caption{ \label{fig:skilldlnp}
-Skill of the volunteers and $\Delta\log(P)$ given a lens or not a lens in
-an image as a function of $P_{\rm L}$ and $P_{\rm D}$. These
-quantities indicate the ability of the volunteers but do not have a simple
+Skill of the volunteers, $\Delta\log(P)$ given a lens or not a lens in
+an image as a function of $P_{\rm L}$ and $P_{\rm D}$. Each of these
+quantities represent ability of the Volunteers but do not have a simple
 linear relation with $P_{\rm L}$ and $P_{\rm D}$.  
@@
 $\Delta\log(P)$? This figure and this section still needs to be
-polished. }
+polished.}
 }

### 2015-04-13 doc/sw-system.tex
Added fitsjs reference, including doi. Fixes #119
fix js typo

@@
 For the more interesting subjects, the CI offers two features that  enable
-further investigation of the subjects. The first is the ``Quick Dashboard'' (QD)
-a more advanced image viewer. This allows the viewer to compare three different
-contrast and colour balance settings, to help bring out subtle features, and to
-pan and zoom in on interesting regions of the image to assess small features.
-Markers can be placed in the Quick Dashboard just the same as in the main CI
-image viewer. The second is a link to that subject's page in the project
-discussion forum, \texttt{http://talk.spacewarps.org} (known as ``Talk''). Here,
-volunteers can discuss the features they have seen either before they submit
-their classification, or after, if they ``favorite'' the subject. There is no
-``back'' button: each volunteer may only classify a given subject once. However,
-the presence of an option to see what others think about any given subject
-before submitting your own classification means that the classifications may not
-be strictly independent; the advantage of this system is that volunteers can
-learn from others what constitutes a good lens candidate. This is not, however,
-the primary educational resource; we describe the explicit training that we
-provide for the volunteers in the next section.
-The FITS images of the subject can be further explored with Zooniverse ``Dashboard Tools,'' using a more powerful image viewer that enables dynamic variation of the colour balance and contrast (stretch), and for any given view to be shared via unique URL back to Talk.
+further investigation of the subjects. The first is the ``Quick Dashboard''
+(QD) a more advanced image viewer. This allows the viewer to compare three
+different contrast and colour balance settings, to help bring out subtle
+features, and to pan and zoom in on interesting regions of the image to assess
+small features. Markers can be placed in the Quick Dashboard just the same as
+in the main CI image viewer. The second is a link to that subject's page in
+the project discussion forum, \texttt{http://talk.spacewarps.org} (known as
+``Talk''). Here, volunteers can discuss the features they have seen either
+before they submit their classification, or after, if they ``favorite'' the
+subject. There is no ``back'' button: each volunteer may only classify a given
+subject once. However, the presence of an option to see what others think
+about any given subject before submitting your own classification means that
+the classifications may not be strictly independent; the advantage of this
+system is that volunteers can learn from others what constitutes a good lens
+candidate. This is not, however, the primary educational resource; we describe
+the explicit training that we provide for the volunteers in the next section.
+The FITS images of the subject can be further explored with Zooniverse
+``Dashboard Tools,'' using a more powerful image viewer that enables dynamic
+variation of the colour balance and contrast (stretch), and for any given view
+to be shared via unique URL back to Talk. The FITS image viewing in both the
+Quick Dashboard and the Dashboard Tools are enabled by the javascript library
+\fitsjs \citep{fitsjs}.
 
@@
 fixed period of time (about 4 weeks). Without the time pressure motivating the
-online analysis, we implemented an ``offline'' version of the analysis that
-performs a joint inference of all agent confusion matrix elements and subject
 probabilities simultaneously, for comparison. We describe how this differs
@@
 
-% PJM IS HERE.
-
 \section{Results}
@@
 
-In this section we present our findings about the performance of the  \sw
-system, in terms of the information  contributed by the crowd in
-\Sref{sec:results:crowd}, and the overall classifications of the training set
-that they made.
+In this section we present our findings about the performance of the \SW system,
+in terms of the information  contributed by the crowd in
+\Sref{sec:results:crowd}, the speed of the system, and the overall
+classifications of the training set that they made.
+
+% PJM IS HERE.
 
@@
 \centering\includegraphics[width=0.9\linewidth]{sw-system-figs/all_skill_contribution_experience_education.png}
-\caption{Key properties and contributions of the \sw crowd. Plotted are the
-1-D and 2-D marginalized distributions for the logarithms of the
+\caption{Key properties and contributions of the \SW crowd. Plotted are the 1-D
+and 2-D smoothed marginalized distributions for  the logarithms of the
 properties of the agents described in the text. The  \StageOne agents are shown
-in blue, the \StageTwo agents in orange.}
+in blue, the \StageTwo agents in orange: the  smoothing scale for the \StageTwo
+curves was set slightly higher to counter the  higher shot noise. The contours
+contain 68\%, 95\% and 99\% of the distributions.}
 \label{fig:crowd:cornerplot}
@@
 We define the following properties of the crowd, as characterised by their
-agents, and plot the distributions of their logarithms in
+agents, and plot their distributions in
 \Fref{fig:crowd:cornerplot}.
@@
 %
-\item{\noindent\bf ``Effort:''} The number of test images, $\effort$, classified by a
-volunteer. In \StageOne, the mean effort per agent was 263; in the shorter \StageTwo it was 81.
+\item{\noindent\bf ``Effort:''} The number of test images, $\effort$, classified
+by a volunteer. In \StageOne, the mean effort per agent was 263; in the shorter
+\StageTwo it was 81.
 %
@@
 classified by a volunteer. In \StageOne, the mean experience per agent was 29;
-in \StageTwo (where the training image fequency was set higher) it was 34.
+in \StageTwo (where the training image frequency was set higher) it was 34.
 %
-\item{\noindent\bf ``Skill:''} The expectation value of the information gain,
-$\skill$
-should  the next subject classified have lens probability 0.5
-(\Aref{appendix:swap}),  in bits. Random classifiers have $\skill = 0.0$,
-perfect classifiers have $\skill = 1.0$. All agents start with $\skill = 0.0$;
-this increases as training subjects are classified, and the agent's estimates
-of its confusion matrix elements improve. In \StageOne, the mean skill per agent
-was 0.04 bits; in  \StageTwo it was 0.05.
+\item{\noindent\bf ``Skill:''} The expectation value of the information gained
+per classification (in bits) by that volunteer,  $\skill$ for subjects which
+have lens probability 0.5 (\Aref{appendix:swap}). Random classifiers have
+$\skill = 0.0$, while perfect classifiers have $\skill = 1.0$. All agents start
+with $\skill = 0.0$. The skill of  an agent increases as training subjects are
+classified, and the agent's estimates of its confusion matrix elements improve.
+In \StageOne, the mean skill per agent was 0.04 bits; in  \StageTwo it was 0.05.
 %
-\item{\noindent\bf ``Contribution:''} The integrated skill over a volunteer's test
-subject classification history, and represents the total  contribution to the
-project that volunteer (see the appendix for more discussion of this
-quantity). In \StageOne, the mean contribution per agent was 34.9 bits; in
-\StageTwo it was 33.5.
+\item{\noindent\bf ``Contribution:''} The integrated skill over a volunteer's
+{\it test subject} classification history, a quantity representative of the
+total contribution to the project made by that volunteer (see the appendix for
+more discussion of this quantity). The classifications of training images
+determine the skill, while the classification of test images determines
+contribution.  In \StageOne, the mean  contribution per agent was
+34.9 bits; in \StageTwo it was 33.5.
 %
-\item{\noindent\bf ``Information:''} The total information $\information$ generated by
-the  agent during the volunteer's classification activity. This quantity
-depends on the value of each subject's lens probability when that subject was
-presented to the volunteer (\Aref{appendix:swap}), and so there is an element
-of luck involved with this quantity: if you never see a high probability
-subject, it's hard to generate a large amount of information. You make your
-own luck by classifying more subjects.
+\item{\noindent\bf ``Information:''} The actual total information $\information$
+generated by the agent during the volunteer's classification activity. This
+quantity depends on the value of each subject's lens probability when that
+subject was presented to the volunteer (simply because information gain is
+defined in terms of posterior relative to prior probabilities,
+\Aref{appendix:swap}).  Because of this, we expect this quantity to be noisier
+than the ``contribution'' defined above.
 %
@@
 The leftmost column of \Fref{fig:crowd:cornerplot} shows how the last four of
-these properties depends on the effort expended by the volunteers. We see that
-experience is strongly correlated with effort (as training images are
-presented throughout each stage, albeit at decreasing frequency), and that
-this is also true for skill. In the second row of \Fref{fig:crowd:cornerplot}
-we see that while skills of greater than 0.1 can be attained after just a few
-training images, most agents of such low experience have significantly lower
-skill. The volunteers in question only classify a few subjects before leaving.
-However, at high values of experience and effort, the skill is \emph{always
-high}. There seem to be very few agents logging large numbers of
-classifications at low skill (although there are one or two exceptions): almost
-all high effort ``super-users'' have high skill. These two properties are
-reflected in both the contributions these volunteers make (third row) and the
-information they generate (fourth row).
+these properties depends on the effort expended by the volunteers. As expected,
+we see that experience is tightly correlated with effort, reflecting the design
+of training images being presented throughout each stage (albeit at decreasing
+frequency). We also see a strong correlation between effort and skill, which was
+hoped for but not guaranteed: the more images the volunteers see, the better
+able to contribute information they are.
+
+The effort distribution shows two peaks, suggestive of two types of
+participation.  The sharp spike at just a few images classified presumably
+corresponds to visitors who only classify a few subjects before leaving the site
+again. The broader hump contains people doing tens to hundreds of
+classifications: the skill vs.\ experience panel of \Fref{fig:crowd:cornerplot}
+shows this group to achieve a broad distribution of  skill, peaking at around
+0.05 but with a long tail to higher values.
+
+At high values of experience and effort, the skill is \emph{always high}. There
+seem to be very few agents logging large numbers of classifications at low skill
+(although there are one or two exceptions): almost all high effort
+``super-users'' have high skill. These two properties are reflected in both the
+contributions these volunteers make (third row) and the information they
+generate (fourth row).
 
@@
 \centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_contrib_cumul.png}
-\caption{Narrow cumulative distributions of the contributions made by the
-agents: for example, 90\% of the \StageTwo contributions were made by the
-highest contributing  7\% of the crowd. The \StageOne agents are shown in blue,
-the \StageTwo agents in orange. ``Experienced volunteers'' classified 10 or more
-training subjects.}
+\caption{Cumulative distributions of the contributions made by the agents: 90\%
+of the contribution was made by the highest contributing 1\% of the crowd at
+\StageOne (blue), and the highest contributing  7\% of the crowd at \StageTwo
+(orange). The \StageOne agents are shown in blue, the \StageTwo agents in
+orange. ``Experienced volunteers'' classified 10 or more training subjects.}
 \label{fig:crowd:cumulplot}
@@
 
-However, it is not the case that only these small groups were capable of
-making this large contribution.
-% : 9118 volunteers were ``experienced'' in that
-% they had all classified at least 10 training images; the 375 highest
-% contributing volunteers make up just 4\% of this experienced volunteer pool.
-The cumulative distribution of agent skill is shown in
-\Fref{fig:crowd:cumulskillplot}: these distributions are significantly broader
-than the corresponding distributions of agent contribution in
-\Fref{fig:crowd:cumulplot}. The most skilled 20\% of agents possess only  79\%
-of the skill at \StageOne, and 77\% at \StageTwo. The inexperienced volunteers
-also possess a significant fraction of the skill: the most skillful 20\% of
-experienced volunteers (1824 people)  possess just 43\% of the total skill.
-The level of contribution made at \sw by experienced volunteers is largely a
-matter of choice (or perhaps, availability of time!).
+However, it is not the case that only these small groups were {\it capable} of
+making large contributions. The cumulative distribution of agent skill is shown
+in \Fref{fig:crowd:cumulskillplot}: these distributions are significantly
+broader than the corresponding distributions of agent contribution, in
+\Fref{fig:crowd:cumulplot}. The most skilled 20\% of agents only possess around
+80\% of the skill at each stage. The inexperienced volunteers also possess a
+significant fraction of the skill: the most skillful 20\% of experienced
+volunteers (1824 people)  possess just 43\% of the total skill. The breadth of
+the skill distributions suggests that  the high level of contribution made at
+\SW by experienced volunteers is largely a matter of choice (or perhaps,
+availability of time!). There were many other volunteers that  were skillful
+enough to make large contributions -- they just didn't classify as many images.
 
@@
 
-How fast does the \sw crowd classify subjects? Each agent records the timestamp
+How fast does the \SW crowd classify subjects? Each agent records the timestamp
 of each classification its volunteer makes; by measuring the time lags between
 successive classifications we can make estimates of the crowd's classification
-and contribution speed. We plot these two quantities for both \StageOne and \StageTwo in \Fref{fig:results:speed}, normalizing the speed and time axes to the
-respective totals.
-The fractional classification rates in each stage of the survey fall off in approximately the same way, despite the factor of nearly 20 difference in crowd size.
-\StageOne (consisting of $\sim430,000$ subjects) was completed in around 5000 hours (by some 37,000 participants), with classification rates in the first few days averaging at $\sim10^4$ per hour, stimulated by various forms of advertising (press releases, and emails to registered Zooniverse users).
-The asymptotic classification rate was $\sim10^3$ per hour.
-The average skill was found to be approximately constant over the lifetime of \StageOne, leading to a contribution rate that tracks closely the classification rate.
-(A 10\% increase in average skill was seen over the first 40 days, and a decrease of the same amount in the last 40 days -- not enough to cause a significant difference between classification and contribution rate behavior, but perhaps reflecting a learning period at the start and a decrease in participation late on.) \StageTwo (3700 subjects) was completed in around 600 hours by around 2000 participants, with classification rates starting at $~\sim2000$ per hour and decaying to $\sim100$ per hour.
+and contribution speed. We plot these two quantities for both \StageOne and
+\StageTwo in \Fref{fig:results:speed}, normalizing the speed and time axes to
+the respective totals. The fractional classification rates in each stage of the
+survey fall off in approximately the same way, despite the factor of nearly 20
+difference in crowd size. \StageOne (consisting of $\sim430,000$ subjects) was
+completed in around 5000 hours (by some 37,000 participants), with
+classification rates in the first few days averaging at $\sim10^4$ per hour.
+This was stimulated by various forms of advertising (press releases, and emails
+to registered Zooniverse users). The asymptotic classification rate was  around
+ten times lower, at $\sim10^3$ per hour. Interestingly, the average skill was
+found to be approximately constant over the lifetime of \StageOne, leading to a
+contribution rate that tracks closely the classification rate. (A 10\% increase
+in average skill was seen over the first 40 days, and a decrease of the same
+amount in the last 40 days -- not enough to cause a significant difference
+between classification and contribution rate behavior, but perhaps reflecting a
+learning period at the start and a decrease in participation late on.) \StageTwo
+(3700 subjects) was completed in around 600 hours by around 2000 participants,
+with classification rates starting at $~\sim2000$ per hour and decaying to
+$\sim100$ per hour.
 
@@
 
-The similarities between \StageOne and 2, suggest that these numbers could be scaled to estimate the speed of future \SW projects (or at least those following a similar blind search strategy).
-For example, the completion time for a \SW project could be approximated as
+The similarities between \StageOne and 2, suggest that these numbers could be
+scaled to estimate the speed of future \SW projects (or at least those following
+a similar blind search strategy). For example, the completion time for a \SW
+project could be approximated as
 \begin{equation}
@@
 \end{equation}
-where $N_s$ is the number of subjects to be classified, and $N_p$ is the number of volunteers in the crowd.
+where $N_s$ is the number of subjects to be classified, and $N_p$ is the number
+of volunteers in the crowd.
 
@@
 curves for CFHTLS \StageOne and \StageTwo. These plots show the true positive
-rate (TPR), the number of sims correctly detected divided by the total number of
-sims in the training set, and the false positive rate (FPR), the number of duds
-incorrectly detected  divided by total number of duds in the training set, both
+rate (TPR, the number of sims correctly detected divided by the total number of
+sims in the training set), and the false positive rate (FPR, the number of duds
+incorrectly detected  divided by the total number of duds in the training set), both
 for a given sample of detections defined by a particular probability threshold,
@@
 positive rates of  around 90\% were achieved, at very low false positive rates.
+
 For comparison we show the results of an analysis where the classifications of
-training images were ignored, and none of the agents allowed to learn: they were
-instead assigned initial values of their confusion matrices of 0.75 for each
-element, which then remained constant. This emulates a very simple unweighted
-voting scheme, where all classifications are treated equally. In this case, the
-TPR remains under 80\% in \StageOne and 60\% in \StageTwo, thus quantifying  the
-benefit of including training images and allowing the agents to learn. The
-choice of initial confusion matrix is not very important: the same 0.75 initial
-values applied to normal, learning agents results in a slightly lower TPR than
-the default case, indicating that initializing the system less conservatively
-results in slightly worse performance.
+training images were ignored, and none of the agents allowed to learn: the
+agents were instead simply assigned initial values of their confusion matrices
+of 0.75 for each element, which then remained constant. This set-up emulates a
+very simple unweighted voting scheme, where all classifications are treated
+equally.  In this case, the TPR remains under 80\% in \StageOne and 60\% in
+\StageTwo, thus quantifying  the benefit of including training images and
+allowing the agents to learn via their Bayesian updates.
+
+When the agents are allowed to update their confusion matrices, the choice of
+initial confusion matrix is not very important. The same 0.75 initial values
+applied to normal, learning agents resulted in only a slightly lower TPR than
+the default case, nevertheless indicating that initializing the system less
+conservatively results in slightly worse performance.
 
@@
 line). However, at \StageTwo there is marginal evidence of there being greater
-benefit to doing the analysis offline. Over 85\% TPR is achieved at zero FPR
-in the offline analysis , while if one is willing to accept a false positive
-rate of 5\%, the true positive rate rises to over 95\%, showing that some of
-the sims that were missed in the online analysis may be being recovered by
-doing the analysis offline. The same is true at \StageOne, but to a lower
-degree. Assuming Poisson statistics for the fluctuations in the numbers of
-recovered lenses, the uncertainty in the measured \StageTwo TPR values is around
-8\%, but the online and offline samples are highly correlated, such that the
-uncertainty on the difference between the ROC curves is somewhat less than
-this. Still, a larger validation set is needed to test these algorithmic
-choices more rigorously. At \StageOne, high TPR can be measured to better than
-1\%.
+benefit to doing the analysis offline (\Sref{sec:swap}, \Aref{appendix:swap}).
+Over 85\% TPR is achieved at zero FPR in the offline analysis , while if one is
+willing to accept a false positive rate of 5\%, the true positive rate rises to
+over 95\%, showing that some of the sims that were missed in the online analysis
+may be being recovered by doing the analysis offline. The same is true at
+\StageOne, but to a lesser extent. Assuming Poisson statistics for the
+fluctuations in the numbers of recovered lenses, the uncertainty in the measured
+\StageTwo TPR values is around 8\%, but the online and offline samples are
+highly correlated, such that the uncertainty on the difference between the ROC
+curves is somewhat less than this. Still, a larger validation set is needed to
+test these algorithmic choices more rigorously. At \StageOne, high TPR can be
+measured to better than 1\%.
 
@@
 \end{minipage}
-\caption{Receiver operating characteristic curves for the \sw system, using
-the CFHTLS training set. Left: \StageOne, right: \StageTwo.}
+\caption{Receiver operating characteristic curves for the \SW system, using
+the CFHTLS training set. Left: \StageOne, right: \StageTwo. Insets show a
+magnified view of the top lefthand corner of each plot. Linestyles illustrate
+the agent properties (initial confusion matrix elements, learning or not)
+discussed in the text, as well as the difference between the online and offline
+analyses. The \StageTwo sample was defined using the online \StageOne results
+(solid blue curve), while the offline analysis was chosen for the final
+\StageTwo results (dot-dashed orange curve). }
 \label{fig:results:sample:roc}
@@
 show in \Fref{fig:results:sample:CP} a plot of the more familiar (to
-astronomers) quantities completeness versus purity in
+astronomers) quantities of completeness versus purity, again for
 the two stages. As in \Fref{fig:results:sample:roc}, the detection threshold
@@
 invariant to this transformation.
-
 The \StageOne curves are truncated by the retirement of subjects in this phase,
@@
 that over 90\% completeness was reached, albeit in a sample with around 20\%
-purity. To investigate the completeness to the three different types of lens
-in the training set, we repeat the same procedure, only now we consider only
-the detections of a certain kind of lens and of the non-lenses in the training
-set. We estimate the expected number of lenses and non-lens false positives by
-dividing the lens and dud sets into equal fractions.
-
-The lensed quasar part of the training set yielded the highest
-completeness, suggesting that these were the easiest sims to spot. The lensed
-galaxies were recovered at understandably lowest completeness, although the
-wider image separation  lensing clusters were not very different. At \StageTwo,
-where no retirement was carried out, it was possible to reach 100\% purity:
-indeed, the knee of the curve is at just under 90\% completeness. However, the
-purity decreases rapidly if higher completeness than this is sought.
-Interestingly, the lensing clusters can be seen to pose problems for the
-system, with its curve turning over at just 60\% completeness.
-
-The optimal sample in this simulated lens search experiment would have been
+purity.
+
+Does this performance level vary between the different types of gravitational
+lens? To investigate the completeness to the three different types of lens in
+the training set, we repeated the same procedure but now considering only the
+detections of a certain kind of lens and of the non-lenses in the training set.
+We estimate the expected number of lenses and non-lens false positives by
+dividing the lens and dud sets into equal fractions. The lensed quasar part of
+the training set yielded the highest completeness, suggesting that these were
+the easiest sims to spot. The lensed galaxies were recovered at the lowest
+completeness, likely due to the difficulty  of separating the lens and source
+galaxy light.
+
+At \StageTwo, where no retirement was carried out, it was possible to reach
+100\% purity: the knee of the curve is at just under 90\% completeness. However,
+the purity decreases rapidly if higher completeness than this is sought. The
+optimal sample in this simulated lens search experiment would have been
 constructed with a threshold value of $\pr(\LENS|C,T) > 0.47$. At 100\% purity
-and 89\% completeness, it would have contained around 89 lens candidates.
+and 90\% completeness, it would have contained around 89 lens candidates.
+
 % TP + FN ~ 2e-4 * 430000 ~ 100 ~ TP/C ; so TP ~ 89 candidates

### 2015-04-13 doc/sw-system.tex
Figure 12, top right false negative did not crposs detection threshold, I checked the SWAP set-up for stage 1. Corrected erroneous text and improved caption #96

@@
 classifiers have been involved, causing random walks with longer step lengths
-(top) and catastrophic mis-classifications (bottom right). Insets for the false
+(top) and catastrophic mis-classifications (bottom right). Note that both these
+subjects were {\it very nearly} detected but didn't quite reach the threshold
+set (marked by the blue dashed line). Insets for the false
 negatives show the lens feature. The inset for the lower righthand panel shows
@@
 \Fref{fig:discuss:performance:trajectories} shows 2 example simulated lenses
-that were missed ($\pr(\LENS|C,T) < 10^{-5}$) by the \SW system, and 2 example
+that were missed ($\pr(\LENS|C,T) < 10^{-5}$) by the \SW system (top row),
+and 2 example
 non-lenses that were incorrectly flagged as candidates ($\pr(\LENS|C,T) >
-0.95$) by the \SW system. While the final \StageTwo analysis was done offline,
+0.95$) by the \SW system (bottom row).
+While the final \StageTwo analysis was done offline,
 these trajectory plots still serve to illustrate the approximate
@@
 
-The false positives show similar behaviour, for example in the bottom
-lefthand panel of the figure. As well as subjects being ``unlucky'' in this
-way, there are two less common failure modes associated with mistakes made by
-higher skill users, illustrated in the righthand column of the figure. In the
-false negative subject shown in the top right-hand panel, several high skill
-classifiers update the subject upwards in log probability by some way each
-time, but other, comparable skill classifiers mis-classify the system to lower
-probability. If we had retired subjects after crossing a high probability
-detection threshold, this subject would have been correctly identified as a
-lens candidate; instead, it was kept in the system and eventually scattered
-down to retirement. The trajectory looks like a random walk, but with bigger
-steps. The bottom righthand panel shows an example of a final, apparently
-rare, failure mode: we see some short-step random walk behaviour, followed by
-a mis-classification by a very high skill ``expert'' classifier after 20
-classifications that promotes the subject to high probability.
+The false positives show similar behaviour, for example in the bottom lefthand
+panel of the figure. As well as subjects being ``unlucky'' in this way, there
+are two less common failure modes associated with mistakes made by higher skill
+users, illustrated in the righthand column of the figure. In the false negative
+subject shown in the top right-hand panel, several high skill classifiers update
+the subject upwards in log probability by some way each time, but other,
+comparable skill classifiers mis-classify the system to lower probability.   The
+trajectory looks like a random walk, but with bigger steps; this particular
+subject came very close to crossing the detection  threshold three times, but
+didn't quite make it. The bottom right-hand panel shows an example of a final,
+apparently rare, failure mode: we see some short-step random walk behaviour,
+followed by a mis-classification by a very high skill ``expert'' classifier
+after 20 classifications that promotes the subject to high probability.
 
@@
 
-We might wonder whether some of  the mistakes made by reasonably high skill
-classifiers could have been corrected by those classifiers themselves, had
+Some of  the mistakes made by reasonably high skill
+classifiers working at high speed
+could have perhaps been corrected by those classifiers themselves, had
 they had access to a ``go back'' option. While clearly enabling error
@@
 approach, and then tracking the relative performance of ``collaborative''
-classifications compared with independent ones. We leave this to further
+classifications compared with independent ones. We leave the exploration of
+this to further
 work.
@@
 training could be to provide more information about what lenses do. In this
-project, the Spotter's Guide was always available on the site, but as a
+project, the Spotter's Guide, and the Science, FAQ and About pages were always available on the site, but as a
 passive background resource. We might consider providing more links to this

### 2015-04-13 doc/sw-system.tex
Done section 6 (discussion) #96

@@
 agents' initial confusion matrix elements to those of a random classifier)
-leads to best performance, a result which shoudl be of some comfort to the
+leads to best performance, a result which should be of some comfort to the
 nervous volunteer.

### 2015-04-13 doc/acknowledgments.tex
Guessed URL in acknowledgements, for now. Finished going through all AV comments! #96

@@
 contributions to the project so far. A complete list of collaborators is
-given at... In particular we would like to recognise the efforts of XXX,
-YYY etc in moderating the discussion.
+given at \texttt{http://spacewarps.org/\#/results/CFHTLS}.
 
-We are also grateful to Brooke Simmons, David Hogg, XXX and YYY for many useful
-conversations about citizen science and gravitational lens detection. 
-%
+We are also grateful to Stuart Lynn, Kelly Borden, Laura Whyte, Brooke Simmons,
+David Hogg, Thomas Jennings, Layne  Wright, Cecile Faure, Jonathan Coles, Stuart
+Lowe and Jean-Paul Kneib for many useful conversations about citizen science and
+gravitational lens detection, and to the Dark Energy Survey and Pan-STARRS strong
+lensing science teams for their suggestions and encouragement.
+
 PJM was given support by the Royal Society, in the form of a research
@@
 The \sw project is open source.
-The web app was developed at https://github.com/Zooniverse/Lens-Zoo
+The web app was developed at \texttt{https://github.com/Zooniverse/Lens-Zoo}
 while the SWAP analysis software was developed at
-https://github.com/drphilmarshall/SpaceWarps.
+\texttt{https://github.com/drphilmarshall/SpaceWarps}.

### 2015-04-13 doc/sw-system.tex
Guessed URL in acknowledgements, for now. Finished going through all AV comments! #96

@@
 volunteers learn more about the problem as they go, but also inevitably make
-occasional mistakes (perhaps because a lens is difficult to see, or they
-became distracted during the task). To cope with this uncertainty, we assign a
+occasional mistakes (especially when classifying at high speed).
+To cope with this uncertainty, we assign a
 simple software {\it agent} to partner each volunteer. The agent's task is to
@@
 \end{align}
-{\it Obtuse} classifiers turn out to be as helpful as {\it perfect} ones.
+{\it Obtuse} classifiers turn out to be as helpful as {\it perfect} ones, because
+the agents know to trust the opposite of their classifications.
 

### 2015-04-13 doc/sw-system.tex
Closed #121

@@
 In this section we present our findings about the performance of the \SW system,
-in terms of the information  contributed by the crowd in
-\Sref{sec:results:crowd}, the speed of the system, and the overall
-classifications of the training set that they made.
-
-% PJM IS HERE.
+in terms of the classification of the training set, the  information contributed
+by the crowd, and the speed at which the image set was classified.
 
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Sample Properties}
+\label{sec:results:sample}
+
+We first quantify the performance of the \SW system in terms of the recovery of
+the training set images. At \StageOne, this set contains around 5712 simulated
+lenses, and 450 duds; at \StageTwo, we used 152 simulated lenses and 201 duds.
+\Fref{fig:results:sample:roc} shows receiver operating characteristic (ROC)
+curves for CFHTLS \StageOne and \StageTwo. These plots show the true positive
+rate (TPR, the number of sims correctly detected divided by the total number of
+sims in the training set), and the false positive rate (FPR, the number of duds
+incorrectly detected  divided by the total number of duds in the training set), both
+for a given sample of detections defined by a particular probability threshold,
+which varies along the curves.  In both stages, these curves show that true
+positive rates of  around 90\% were achieved, at very low false positive rates.
+
+For comparison we show the results of an analysis where the classifications of
+training images were ignored, and none of the agents allowed to learn: the
+agents were instead simply assigned initial values of their confusion matrices
+of 0.75 for each element, which then remained constant. This set-up emulates a
+very simple unweighted voting scheme, where all classifications are treated
+equally.  In this case, the TPR remains under 80\% in \StageOne and 60\% in
+\StageTwo, thus quantifying  the benefit of including training images and
+allowing the agents to learn via their Bayesian updates.
+
+When the agents are allowed to update their confusion matrices, the choice of
+initial confusion matrix is not very important. The same 0.75 initial values
+applied to normal, learning agents resulted in only a slightly lower TPR than
+the default case, nevertheless indicating that initializing the system less
+conservatively results in slightly worse performance.
+
+The dot-dashed curves show the impact of the offline analysis. At \StageOne the
+results are very similar to the online version that was actually run (solid
+line). However, at \StageTwo there is marginal evidence of there being greater
+benefit to doing the analysis offline (\Sref{sec:swap}, \Aref{appendix:swap}).
+Over 85\% TPR is achieved at zero FPR in the offline analysis , while if one is
+willing to accept a false positive rate of 5\%, the true positive rate rises to
+over 95\%, showing that some of the sims that were missed in the online analysis
+may be being recovered by doing the analysis offline. The same is true at
+\StageOne, but to a lesser extent. Assuming Poisson statistics for the
+fluctuations in the numbers of recovered lenses, the uncertainty in the measured
+\StageTwo TPR values is around 8\%, but the online and offline samples are
+highly correlated, such that the uncertainty on the difference between the ROC
+curves is somewhat less than this. Still, a larger validation set is needed to
+test these algorithmic choices more rigorously. At \StageOne, high TPR can be
+measured to better than 1\%.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{minipage}{0.45\linewidth}
+  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage1_ROC.png}
+\end{minipage}\hfill
+\begin{minipage}{0.45\linewidth}
+  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage2_ROC.png}
+\end{minipage}
+\caption{Receiver operating characteristic curves for the \SW system, using
+the CFHTLS training set. Left: \StageOne, right: \StageTwo. Insets show a
+magnified view of the top lefthand corner of each plot. Linestyles illustrate
+the agent properties (initial confusion matrix elements, learning or not)
+discussed in the text, as well as the difference between the online and offline
+analyses. The \StageTwo sample was defined using the online \StageOne results
+(solid blue curve), while the offline analysis was chosen for the final
+\StageTwo results (dot-dashed orange curve). }
+\label{fig:results:sample:roc}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Adopting the online \StageOne analysis, and the offline \StageTwo analysis, we
+show in \Fref{fig:results:sample:CP} a plot of the more familiar (to
+astronomers) quantities of completeness versus purity, again for
+the two stages. As in \Fref{fig:results:sample:roc}, the detection threshold
+varies along the curves. Completeness is defined as the number of correctly
+detected sims divided by the total number of sims in the training set, while
+purity is the number of correct detections divided by the total number of
+detections.\footnote{The completeness is equivalent to the TPR and is also
+known elsewhere as the ``recall.''  The purity is also known as the
+``precision.''} If the training set samples from the same systems as the test
+set, then the completeness of the training set will be equivalent to the
+completeness of the test set. The purity depends on the proportion of sims to
+duds, and so the purity of the test set must be approximated by rescaling the
+training set to the expected proportion of lens systems to not-lens systems in
+the survey. First we compute the expected number of false positives by
+multiplying the FPR by the expected number of non-lenses in the survey. Then
+we multiply the TPR by the expected number of lenses in the survey, to get the
+expected number of true positives. The sum of the true positives and the false
+positives gives the expected sample size; dividing the expected number of true
+positives by this sample size gives the purity. Note that the completeness is
+invariant to this transformation.
+The \StageOne curves are truncated by the retirement of subjects in this phase,
+which sets the minimum size of this sample. We see from the solid blue curve
+that over 90\% completeness was reached, albeit in a sample with around 20\%
+purity.
+
+Does this performance level vary between the different types of gravitational
+lens? To investigate the completeness to the three different types of lens in
+the training set, we repeated the same procedure but now considering only the
+detections of a certain kind of lens and of the non-lenses in the training set.
+We estimate the expected number of lenses and non-lens false positives by
+dividing the lens and dud sets into equal fractions. The lensed quasar part of
+the training set yielded the highest completeness, suggesting that these were
+the easiest sims to spot. The lensed galaxies were recovered at the lowest
+completeness, likely due to the difficulty  of separating the lens and source
+galaxy light.
+
+At \StageTwo, where no retirement was carried out, it was possible to reach
+100\% purity: the knee of the curve is at just under 90\% completeness. However,
+the purity decreases rapidly if higher completeness than this is sought. The
+optimal sample in this simulated lens search experiment would have been
+constructed with a threshold value of $\pr(\LENS|C,T) > 0.47$. At 100\% purity
+and 90\% completeness, it would have contained around 89 lens candidates.
+
+% TP + FN ~ 2e-4 * 430000 ~ 100 ~ TP/C ; so TP ~ 89 candidates
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering\includegraphics[width=\linewidth]{sw-system-figs/completeness_purity_simple.png}
+\caption{Completeness-estimated purity curves for the \sw system, using
+the CFHTLS training set.}
+\label{fig:results:sample:CP}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 
@@
 
-We define the following properties of the crowd, as characterised by their
-agents, and plot their distributions in
+To investigate the properties of the \sw crowd, as characterised by their
+agents, we define the following quantities and plot their distributions in
 \Fref{fig:crowd:cornerplot}.
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Sample Properties}
-\label{sec:results:sample}
-
-We now quantify the performance of the \SW system in terms of the recovery of
-the training set images. At \StageOne, this set contains around 5712 simulated
-lenses, and 450 duds; at \StageTwo, we used 152 simulated lenses and 201 duds.
-\Fref{fig:results:sample:roc} shows receiver operating characteristic (ROC)
-curves for CFHTLS \StageOne and \StageTwo. These plots show the true positive
-rate (TPR, the number of sims correctly detected divided by the total number of
-sims in the training set), and the false positive rate (FPR, the number of duds
-incorrectly detected  divided by the total number of duds in the training set), both
-for a given sample of detections defined by a particular probability threshold,
-which varies along the curves.  In both stages, these curves show that true
-positive rates of  around 90\% were achieved, at very low false positive rates.
-
-For comparison we show the results of an analysis where the classifications of
-training images were ignored, and none of the agents allowed to learn: the
-agents were instead simply assigned initial values of their confusion matrices
-of 0.75 for each element, which then remained constant. This set-up emulates a
-very simple unweighted voting scheme, where all classifications are treated
-equally.  In this case, the TPR remains under 80\% in \StageOne and 60\% in
-\StageTwo, thus quantifying  the benefit of including training images and
-allowing the agents to learn via their Bayesian updates.
-
-When the agents are allowed to update their confusion matrices, the choice of
-initial confusion matrix is not very important. The same 0.75 initial values
-applied to normal, learning agents resulted in only a slightly lower TPR than
-the default case, nevertheless indicating that initializing the system less
-conservatively results in slightly worse performance.
-
-The dot-dashed curves show the impact of the offline analysis. At \StageOne the
-results are very similar to the online version that was actually run (solid
-line). However, at \StageTwo there is marginal evidence of there being greater
-benefit to doing the analysis offline (\Sref{sec:swap}, \Aref{appendix:swap}).
-Over 85\% TPR is achieved at zero FPR in the offline analysis , while if one is
-willing to accept a false positive rate of 5\%, the true positive rate rises to
-over 95\%, showing that some of the sims that were missed in the online analysis
-may be being recovered by doing the analysis offline. The same is true at
-\StageOne, but to a lesser extent. Assuming Poisson statistics for the
-fluctuations in the numbers of recovered lenses, the uncertainty in the measured
-\StageTwo TPR values is around 8\%, but the online and offline samples are
-highly correlated, such that the uncertainty on the difference between the ROC
-curves is somewhat less than this. Still, a larger validation set is needed to
-test these algorithmic choices more rigorously. At \StageOne, high TPR can be
-measured to better than 1\%.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\begin{minipage}{0.45\linewidth}
-  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage1_ROC.png}
-\end{minipage}\hfill
-\begin{minipage}{0.45\linewidth}
-  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage2_ROC.png}
-\end{minipage}
-\caption{Receiver operating characteristic curves for the \SW system, using
-the CFHTLS training set. Left: \StageOne, right: \StageTwo. Insets show a
-magnified view of the top lefthand corner of each plot. Linestyles illustrate
-the agent properties (initial confusion matrix elements, learning or not)
-discussed in the text, as well as the difference between the online and offline
-analyses. The \StageTwo sample was defined using the online \StageOne results
-(solid blue curve), while the offline analysis was chosen for the final
-\StageTwo results (dot-dashed orange curve). }
-\label{fig:results:sample:roc}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Adopting the online \StageOne analysis, and the offline \StageTwo analysis, we
-show in \Fref{fig:results:sample:CP} a plot of the more familiar (to
-astronomers) quantities of completeness versus purity, again for
-the two stages. As in \Fref{fig:results:sample:roc}, the detection threshold
-varies along the curves. Completeness is defined as the number of correctly
-detected sims divided by the total number of sims in the training set, while
-purity is the number of correct detections divided by the total number of
-detections.\footnote{The completeness is equivalent to the TPR and is also
-known elsewhere as the ``recall.''  The purity is also known as the
-``precision.''} If the training set samples from the same systems as the test
-set, then the completeness of the training set will be equivalent to the
-completeness of the test set. The purity depends on the proportion of sims to
-duds, and so the purity of the test set must be approximated by rescaling the
-training set to the expected proportion of lens systems to not-lens systems in
-the survey. First we compute the expected number of false positives by
-multiplying the FPR by the expected number of non-lenses in the survey. Then
-we multiply the TPR by the expected number of lenses in the survey, to get the
-expected number of true positives. The sum of the true positives and the false
-positives gives the expected sample size; dividing the expected number of true
-positives by this sample size gives the purity. Note that the completeness is
-invariant to this transformation.
-The \StageOne curves are truncated by the retirement of subjects in this phase,
-which sets the minimum size of this sample. We see from the solid blue curve
-that over 90\% completeness was reached, albeit in a sample with around 20\%
-purity.
-
-Does this performance level vary between the different types of gravitational
-lens? To investigate the completeness to the three different types of lens in
-the training set, we repeated the same procedure but now considering only the
-detections of a certain kind of lens and of the non-lenses in the training set.
-We estimate the expected number of lenses and non-lens false positives by
-dividing the lens and dud sets into equal fractions. The lensed quasar part of
-the training set yielded the highest completeness, suggesting that these were
-the easiest sims to spot. The lensed galaxies were recovered at the lowest
-completeness, likely due to the difficulty  of separating the lens and source
-galaxy light.
-
-At \StageTwo, where no retirement was carried out, it was possible to reach
-100\% purity: the knee of the curve is at just under 90\% completeness. However,
-the purity decreases rapidly if higher completeness than this is sought. The
-optimal sample in this simulated lens search experiment would have been
-constructed with a threshold value of $\pr(\LENS|C,T) > 0.47$. At 100\% purity
-and 90\% completeness, it would have contained around 89 lens candidates.
-
-% TP + FN ~ 2e-4 * 430000 ~ 100 ~ TP/C ; so TP ~ 89 candidates
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=\linewidth]{sw-system-figs/completeness_purity_simple.png}
-\caption{Completeness-estimated purity curves for the \sw system, using
-the CFHTLS training set.}
-\label{fig:results:sample:CP}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-04-13 doc/sw-system.tex
Started going through Anu's comments, done Section 1... #112

@@
 initial target sample. Having divided the 150 square degree CFHTLS imaging
-survey into 430000 overlapping 70 by 70 arcminute tiles and displayed them on
+survey into 430000 overlapping 84 by 84 arcminute tiles and displayed them on
 the site, we were joined by 33000 volunteers who contributed X million image
@@
 about the mass distribution in the lens \citep[e.g.][]{AugerEtal2010,
-SonnenfeldEtal2012,SonnenfeldEtal2013}, including on sub-galactic scales
+SonnenfeldEtal2012,MoreEtal2012,SonnenfeldEtal2013}, including on sub-galactic scales
 \citep[e.g.][]{Dalal+Kochanek2002,VegettiEtal2010,HezavehEtal2013}. Any strong
@@
 CLASS \citep[e.g.]{BrowneEtal2003}, SDSS \citep[e.g.][]
-{BoltonEtal2006,AugerEtal2010b,TreuEtal2011,InadaEtal2012}, CFHTLS
-\citep[e.g.][]{MoreEtal2012,GavazziEtal2014}, Herschel
+{BoltonEtal2006,AugerEtal2010b,TreuEtal2011,InadaEtal2012,SBAS,SGAS,CASSOWARY},
+CFHTLS \citep[e.g.][]{MoreEtal2012,GavazziEtal2014}, Herschel
 \citep[][]{NegrelloEtal2014} and SPT \citep[e.g.][]{VieiraEtal2013}, among
@@
 HST images have been searched, yielding several tens of galaxy-scale lenses
-\citep[e.g.][]{MoustakasEtal2007,FaureEtal2008,Jackson2008,MoreEtal2012,
+\citep[e.g.][]{MoustakasEtal2007,FaureEtal2008,Jackson2008,MoreEtal2011,
 PawaseEtal2014}. Similarly, searches of over a hundred square degrees of CFHT
@@
 by the robots as if it contained a gravitational lens, but the visual inspection
-can be thought of as a ``mental modeling'' step. Systems classified by an
-inspector to be good lens candidates are deemed as such because the features in
-the image can be explained by a model of what gravitational lenses do contained
-in the inspector's brain. The second approach simply cuts out the robot
-middleman: \citet{MoustakasEtal2007,FaureEtal2008,Jackson2008} and
-\citet{PawaseEtal2014} all performed successful, entirely visual searches for
-lenses in HST imaging.
+can be thought of as a ``mental modeling'' step.  An inspector who classifies an
+object as a lens candidate does so because the features in the image that they
+see can be explained by a model, contained in their brain, of what gravitational
+lenses do.  The second approach simply cuts out the robot middleman:
+\citet{MoustakasEtal2007,FaureEtal2008,Jackson2008} and \citet{PawaseEtal2014}
+all performed successful visual searches for lenses in HST imaging.
 
@@
 visual lens searches in good quality imaging data are limited to a few square
-degrees per inspector per day (and less, if mre time is spent assessing difficult systems).
+degrees per inspector per day (and less, if more time is spent assessing difficult systems).
 Scaling to thousands of square degrees
@@
 visual inspection has recently been achieved by the online citizen science
-project \PH \citep{SchwambEtal2012}. \PH was designed to enable the discovery of
-transiting exoplanets in data taken by the Kepler satellite; a community of over
-200,000 inspectors from the general public found, after each undergoing a small
-amount of training, over 40 new exoplanet candidates, by visual inspection of
-the Kepler lightcurves that were presented in a custom web-based classification
-interface \citep{WangEtal2013}. The older \GZ morphological classification
+project \PH \citep{SchwambEtal2012}.
+
+\PH was designed to enable the discovery of transiting exoplanets in data taken
+by the Kepler satellite. A community of over 200,000 inspectors from the general
+public found, after each undergoing a small amount of training, over 40 new
+exoplanet candidates. They achived this   by visually inspecting the Kepler
+lightcurves that were presented in a custom web-based classification interface
+\citep{WangEtal2013}.
+The older \GZ morphological classification
 project \citep{LintottEtal2008} has also enabled the discovery of rare objects,
@@
 
-In this paper, we describe the \SW project, an web-based system  conceived to
+In this paper, we describe the \SW project, a web-based system conceived to
 address the visual inspection problem in gravitational lens detection for future
-large surveys via crowd-sourcing. Implemented as a Zooniverse project, it is
-designed to provide a {\it gravitational lens discovery service} to survey teams
-looking for lenses in wide field imaging data. In a companion paper (More et al,
-in preparation, herafter \PaperTwo) we will present the new gravitational lenses
-discovered in our first, experimental, lens search, and begin to investigate the
-differences between lens detections made in \SW and those made with automated
-techniques. Here though, we simply try to answer the following questions:
+large surveys via crowd-sourcing. Implemented as a Zooniverse citizen science
+project, it is designed to provide a {\it gravitational lens discovery service}
+to survey teams looking for lenses in wide field imaging data. In a companion
+paper (More et al, in preparation, herafter \PaperTwo) we will present the new
+gravitational lenses discovered in our first lens search, and
+begin to investigate the differences between lens detections made in \SW and
+those made with automated techniques. Here though, we simply try to answer the
+following questions:
 
@@
 finishes marking a training subject and hits ``Finished marking,'' a pop-up
-message is generated, containing either positive feedback for a successful
+message is generated, containing either congratulations for a successful
 classification (for example, ``Well done! You spotted a simulated lens,'' as
-in \Fref{fig:screenshot}) or negative feedback for an unsuccessful one (for
+in \Fref{fig:screenshot}) or feedback for an unsuccessful one (for
 example, ``There is no gravitational lens in this field!'').

### 2015-04-13 doc/sw-system.tex
First attempt at conclusions, closes #45

@@
 
-\todo{Phil}{write conclusions (\#45).}
-
-Summary of system.
+We have designed, implemented and tested a system for   detecting new strong
+gravitational lens candidates in wide field imaging surveys by crowd-sourced
+visual inspection. The \SW web-based classification interface presents carefully
+prepared color composite sky images to volunteers, who mark features they
+propose to  have been lensed. The participants receive ongoing training with a
+mixture of simulated lens and known-to-be-empty images, and we use this
+information to inform the automated interpretation of their markers. In our
+first lens search we simply divided the CFHTLS imaging into some 430,000 tiles,
+and collected over 10~million volunteer image classifications.
 
@@
 
-Crowd-sourced gravitational lens detection works, in terms of the
-classification of the training set as described here, in the following
-specific ways:
+By analyzing the  classifications made of the training set, we conclude that
+gravitational lens detection by crowd-sourced visual inspection works,  and in
+the following specific ways:
 
@@
 
-\item Participation (crowd size, activity rate) enabled project completion
-
-\item Both \StageOne and \StageTwo achieved the required rejection rates
-
-\item Integrated humanpower = X (\StageOne) and Y (\StageTwo), cf hours taken by
-small team of experts
-
-\item Nightly processing is inefficient: more classifications were made than
-was necessary during peak participation. Need kafka...
-
-\item Retirement rate. False negatives: which sims were missed?
+\item Participation levels were high (over 36,000 volunteers, contributing
+classifications at rates between $10^3$ and $10^4$ images per hour), suggesting
+that if this can be maintained, visual inspection of tens of thousands of images
+can be performed on timescales of a few weeks.
+
+\item Over the course of the two stages of the CFHTLS project, the
+set of images was reduced by a factor of $10^3$ (from a few hundred thousand to
+a few hundred), enough for an expert team to take over.
+
+\item The ``skill'' of the volunteers correlates strongly with the number of
+images they have classified.  Quantifying the ``contribution'' as the integrated
+skill over the test subjects  classified, we find that about 90\% of the
+contribution was made by a few  hundred volunteers -- but that the width of the
+skill distribution means that a  few thousand volunteers could have made
+comparable contributions, had they classified more images.
 
 \item The optimal true positive rate (completeness) and false positive rate in
-the training set were estimated to be TPR\% and FPR\% at \StageOne, assuming a
-detection threshold of xxx.
-
-\item In the ``refinement'' \StageTwo, X\% of the \StageOne candidates were
-rejected (with P less than threshold), and the remainder assigned lens
-``probabilities.'' Ranking
-subjects by their \StageTwo lens probability gives an ROC curve for the system
-with X properties. The optimal true positive rate (completeness) and false
-positive rate in the training set were estimated as TPR\% and FPR\%;
-
-\item The lens-finding crowd shows some interesting properties, with
-consequences for future scalability
-
-\item The information comes predominantly from volunteers with agents with P =
-...
-
-\item The agents show a high mean information per classification, which
-increased/decreased with time; this does/doesn?t correlate with active crowd
-size, showing how the crowd changed over time...
+the training set were estimated to be around $91--93\%$ and $<1\%$ (Stages 1 and
+2). This  FPR translates to a purity of 20\%.
+
+\item The simulated gravitational lenses that were missed were predominantly
+galaxy-scale lenses with faint blue galaxy sources, whose lensed features are
+difficult to distinguish from the light from the lens galaxy. We observed some
+additional scatter, with some simulated lenses accumulating low probability
+simply due to classification noise.
 
@@
 
-Sum up, end. \SW provides a lens candidate detection service, crowd-sourcing the
+In \PaperTwo we present the results of this CFHTLS lens search in more detail,
+in particular focusing on the detection of real lenses, and the comparison
+between \SW and various automated lens finding methods. In this paper  we have
+shown how \SW provides a lens candidate detection service, crowd-sourcing the
 time-consuming work of visually inspecting astronomical images for

### 2015-04-14 analysis/make_lens_atlas.py
updating clustering code

@@ -1,821 +1,0 @@
-#!/usr/bin/env python
-# ======================================================================
-
-# TODO: when pulling points for zoomed, do the clustering as in catalog (should
-# be deterministic) so you can filter that way
-
-import sys, getopt, numpy as np
-
-import matplotlib
-# Force matplotlib to not use any Xwindows backend:
-matplotlib.use('Agg')
-
-# Fonts, latex:
-matplotlib.rc('font', **{'family':'serif', 'serif':['TimesNewRoman']})
-matplotlib.rc('text', usetex=True)
-
-from matplotlib import pyplot as plt
-
-bfs, sfs = 20, 16
-params = { 'axes.labelsize': bfs,
-            'text.fontsize': bfs,
-          'legend.fontsize': bfs,
-          'xtick.labelsize': sfs,
-          'ytick.labelsize': sfs}
-plt.rcParams.update(params)
-
-origin = 'lower'
-
-import swap
-
-from scipy.ndimage import gaussian_filter, imread
-from os import path
-from urllib import FancyURLopener
-from matplotlib.mlab import csv2rec
-
-# ======================================================================
-
-
-# the fancy way of scraping images from the web; you gotta pretend you are a browser
-class MyOpener(FancyURLopener):
-    version = 'Mozilla/5.0 (Windows; U; Windows NT 5.1; it; rv:1.8.1.11) Gecko/20071127 Firefox/2.0.0.11'
-myopener = MyOpener()
-
-# ======================================================================
-
-def get_online_png(url, outname=None):
-    fname = url.split('/')[-1]
-    if not outname:
-        outname = fname
-
-    # download file if we don't already have it
-    if not path.exists(outname):
-        F = myopener.retrieve(url, outname)
-    else:
-        F = [outname]
-    I = imread(F[0]) * 1. / 255
-    return I
-
-def pdf2d(ax, ay, xbins=51, ybins=51,
-          weights=None, smooth=0, color='b', style='contour',
-          axis=None):
-
-    try:
-        plt.xlim([xbins[0], xbins[-1]])
-    except TypeError:
-        plt.xlim(ax.min(), ax.max())
-    try:
-        plt.ylim([ybins[0], ybins[-1]])
-    except TypeError:
-        plt.ylim(ay.min(), ay.max())
-
-    # npts = int((ax.size/4)**0.5)
[…]

### 2015-04-14 analysis/make_lens_catalog.py

@@ -1,19 +1,25 @@
-#!/usr/bin/env python
-# ======================================================================
+"""
+File: make_lens_catalog.py
+Author: Chris Davis
+Description: Given database information, creates the cluster catalog and downloads fields and cutouts.
 
-import numpy as np
+"""
+
+from __future__ import print_function, division
+
+import sys, getopt, numpy as np
 
 import matplotlib
 # Force matplotlib to not use any Xwindows backend:
 matplotlib.use('Agg')
 
 # Fonts, latex:
-matplotlib.rc('font',**{'family':'serif', 'serif':['TimesNewRoman']})
+matplotlib.rc('font', **{'family':'serif', 'serif':['TimesNewRoman']})
 matplotlib.rc('text', usetex=True)
 
 from matplotlib import pyplot as plt
 
-bfs,sfs = 20,16
+bfs, sfs = 20, 16
 params = { 'axes.labelsize': bfs,
             'text.fontsize': bfs,
           'legend.fontsize': bfs,
@@ -21,390 +27,714 @@ params = { 'axes.labelsize': bfs,
           'ytick.labelsize': sfs}
 plt.rcParams.update(params)
 
-import swap
-from matplotlib.mlab import csv2rec
-from sklearn.cluster import AgglomerativeClustering, DBSCAN
-from sklearn.metrics import pairwise_distances
-from sklearn.externals import joblib
+origin = 'lower'
+
+import numpy as np
+import pandas as pd
+from urllib import FancyURLopener
+from scipy.ndimage import imread
+from scipy.misc import imsave
+from os import path, makedirs
+from ast import literal_eval
+
+# ======================================================================
+# Some parameter definitions. Can config catalog properties here or in the
+# functions...
+# ======================================================================
+
+collection_categories = ['ID', 'ZooID', 'location', 'mean_probability', 'category', 'kind', 'flavor', 'state', 'status', 'truth', 'stage']
+annotation_categories = ['At_X', 'At_Y', 'PD', 'PL', 'ItWas']
+cluster_catalog_labels = ['object_id', 'x', 'y', 'markers_in_object', 'skill_sum', 'markers_in_field', 'people_marking_objects', 'people_marking_field', 'people_looking_at_field', 'object_size']
+field_size = 440
+# eps is largely determined by looking at the distribution of dispersion values
+# as well as looking at actual images to get a rough sense of the tradeoff
+# between accidentally misclassifying a large object as multiple and
[…]

### 2015-04-14 doc/sw-system.tex

@@
 
-We describe \SW, a novel gravitaional lens discovery service that
-yields samples of high purity and completeness through crowd-sourced
-visual inspection.
-Carefully
-produced color composite images are displayed to volunteers via a
+We describe \SW, a novel gravitaional lens discovery service that yields samples
+of high purity and completeness through crowd-sourced visual inspection.
+Carefully produced color composite images are displayed to volunteers via a
 classification interface which records their estimates of the positions of
@@
 probability systems are retired from the site periodically, concentrating the
-sample towards a set of candidates; this ``\StageOne'' set is then re-classified
-by the volunteers in a second  refinement stage. Analyzing the classification
-of the training set, we predict that the first stage alone should yield a
-sample that is C\% complete, while leading to the rejection of R\% of the
-initial target sample. Having divided the 150 square degree CFHTLS imaging
-survey into 430000 overlapping 84 by 84 arcminute tiles and displayed them on
-the site, we were joined by 33000 volunteers who contributed X million image
-classifications over the course of N months. The sample was reduced to 3500
-\StageOne candidates; these were then refined to yield a sample of 1400
-candidates rankable by their \StageTwo probability. We expect this sample to be
-X\% complete and Y\% pure at a threshold of 95\% classification probability.
-We find that, on average, and given the assumptions we make in our analysis,
-we need 9 classifications per image during the first stage, X in the second.
-We estimate the mean information contributed per person to be X bits, over a
-session lasting, on average, N classifications per volunteer, and present the
-highly skewed distributions of these quantities. We comment on the scalability
-of the \SW system to the wide field survey era, and its potential to operate
-beyond its design as a supervised classification system.
-
-\todo{Phil}{revisit abstract (\#29).}
+sample towards a set of candidates. Having divided the 171 square degree CFHTLS
+imaging survey into some 430,000 overlapping 84 by 84 arcminute tiles and
+displayed them on the site, we were joined by around 37,000 volunteers who
+contributed 10 million image classifications over the course of 8 months. The
+sample was reduced to 3300 \StageOne candidates; these were then refined to
+yield a sample of 90 \StageTwo detections, a sample we expect to be over 90\%
+complete and 20\% pure at a threshold of 95\% classification probability. We
+comment on the scalability of the \SW system to the wide field survey era.
 

### 2015-04-15 doc/sw-cfhtls.tex
fixed and closed #129

--- 2015-04-13 doc/sw-cfhtls.tex
@@
 discovery of over 500 lenses till
-date\footnote{http://masterlens.astro.utah.edu}.
+date\footnote{http://admin.masterlens.org/index.php}.
 
@@
 fields W1, W2, W3 and W4. The field W1 has the largest sky coverage of
-63.65~deg$^2$. The fields W2 and W4 have similar sky coverages of
-20.32~deg$^2$ and 20.02~deg$^2$, respectively\footnote{These numbers are
-estimated from http://terapix.iap.fr/cplt/table\_syn\_T0006.html}.  The
-field W3 has a sky coverage of 42.87~deg$^2$ and is more than twice as
+63.7~deg$^2$. The fields W2 and W4 have similar sky coverages of
+22.6~deg$^2$ and 23.3~deg$^2$, respectively\footnote{These numbers are
+estimated from http://terapix.iap.fr/cplt/T0007/doc/T0007-doc.pdf}.  The
+field W3 has a sky coverage of 44.2~deg$^2$ and is more than twice as
 large as W2 and W4.
@@
 from the final T0007 release taken from the Terapix
-website\footnote{{http://terapix.iap.fr/cplt/T0006-doc.pdf}} for this
+website\footnote{{http://terapix.iap.fr/cplt/T0007/doc/T0007-doc.pdf}} for this
 work.
@@
 of these candidates are medium-low
-probability\footnote{http://www.ita.uni-heidelberg.de/˜maturi/Public/arcs}.
+probability\footnote{http://www.ita.uni-heidelberg.de/~maturi/Public/arcs}.
 
@@
 linear relation with $P_{\rm L}$ and $P_{\rm D}$.  
-\question{AM}{PJM, should we just use power everywhere instead of the
-$\Delta\log(P)$? This figure and this section still needs to be
-polished. }
 }

### 2015-04-18 doc/sw-cfhtls.tex
fixed and closed #129
fixed most minor typos/comments from coauthors

@@
 verified sample of candidates, we choose the most promising 26 systems
-as our bonafide lens sample from the \cfhtls WIDE. Also, the total
+as our bona fide lens sample from the \cfhtls WIDE. Also, the total
 number of lens candidates is 108 from the \cfhtls WIDE alone.
@@
 around centers of isolated and massive early-type galaxies. The \rf
-subtracts the PSF-matched $i$-band images from the $g$-band images, and
+subtracts the point spread function (PSF)-matched $i$-band images from the $g$-band images, and
 looks for excess flux in the bluer $g$-band. An object detector measures
@@
 of these candidates are medium-low
-probability\footnote{http://www.ita.uni-heidelberg.de/~maturi/Public/arcs}.
+probability\footnote{http://www.ita.uni-heidelberg.de/\~maturi/Public/arcs}.
 
@@
 
-Since we want to produce realistic looking lens systems, we simulate lenses in
-each of the five \cfhtls~filters. The colors of the background galaxies are drawn
-randomly from the photometric CFHTLenS catalog
-\citep{Hildebrandt2012,Erben2013}.  Similarly, we use a quasar catalog from the
-SDSS Data Release 9 \citep{Paris2012} from which colors are drawn to simulate
-quasar lenses.  Next, we assume deVaucoleur's profile to account for the size
-and shape of the galaxies. The ellipticity and the position angle (PA) are drawn
-randomly from within the range given in Table~\ref{tab:thresh}. The effective
-radius of the galaxy is estimated from the Luminosity$-$size relation
-\citep{Bernardi2003} (with a redshift scaling, to account for size
-evolution) given by
+Since we want to produce realistic looking lens systems, we simulate
+lenses in each of the five \cfhtls~filters. The colors of the background
+galaxies are drawn randomly from the photometric CFHTLenS catalog
+\citep{Hildebrandt2012,Erben2013}.  Similarly, we use a quasar catalog
+from the SDSS Data Release 9 \citep{Paris2012} from which colors are
+drawn to simulate quasar lenses. Next, we assumed a Gaussian
+profile\footnote{This was due to an oversight. We intend to use either
+an exponential or de Vaucouleurs' profile.} for
+the galaxies. The ellipticity and the position angle (PA) are drawn
+randomly from within the range given in Table~\ref{tab:thresh}. The
+effective radius of the galaxy is estimated from the Luminosity$-$size
+relation \citep{Bernardi2003} (with a redshift scaling, to account for
+size evolution) given by
 \be
@@
 \ee
-where $L_r=L_s/10^{10.2}$. On the other hand, quasars are assumed to follow a
-Gaussian profile where the full-width-at-half-maximum is equated to that of the median seeing for
-every filter. The median seeing values are taken from Table 4 of the official
-Terapix T0007 release explanatory document \footnote{
+where $L_r=L_s/10^{10.2}$. On the other hand, quasars are assumed to be
+point sources and the PSF, with which quasars are convolved, is assumed
+to have a Gaussian profile. The full-width-at-half-maximum of PSF is
+equated to that of the median seeing for every filter. The median seeing
+values are taken from Table 4 of the official Terapix T0007 release
+explanatory document \footnote{
 http://terapix.iap.fr/cplt/T0007/doc/T0007-doc.pdf}.
@@
 \caption{ \label{fig:remudist}
-Einstein radius distribution for all types of lenses. The dashed-dotted (blue)
+Einstein radius distribution for all types of lenses. The solid (blue)
 curves show the theoretical prediction assuming an SIS model at galaxy-scales
@@
 In \Fref{fig:remudist}, we show the Einstein radius distribution for the
-galaxy-scale (dashed for background quasars and dotted for background galaxies)
-and groups-scale simulated lenses. For comparison, we give the expected
-distributions (blue dashed-dotted curves) for an SIS like density profile at
-galaxy-scales and an NFW+Hernquist profile at groups-scales. The
-theoretical curves are taken from \citet{More2012} wherein the models are
-explained in detail. We note that the model we adopt at groups-scale also
-includes SIS or SIE components for the group members unlike the theoretical
-prediction. The theoretical curves have arbitrary normalizations. We
-also show the distribution of the total magnification for all three
-samples.
+galaxy-scale and groups-scale simulated lenses. For comparison, we give
+the expected distributions (blue solid curves) for an SIS like density
+profile at galaxy-scales and an NFW+Hernquist profile at groups-scales.
+The theoretical curves are taken from \citet{More2012} wherein the
+models are explained in detail. We note that the model we adopt at
+groups-scale also includes SIS or SIE components for the group members
+unlike the theoretical prediction. The theoretical curves have arbitrary
+normalizations. We also show the distribution of the total magnification
+for all three samples.
 
@@
 
-We also use a single Sersic component to describe the light profiles of
+We also use a single component to describe the light profiles of
 background galaxies. This is clearly not the most accurate description for
@@
 estimator is assigned to every pixel. All pixels with a value of the
-elongation stimator above a certain threshold are connected to form the arc
+elongation estimator above a certain threshold are connected to form the arc
 feature. This is called the segmentation of the arc candidate. Subsequently, arc

### 2015-04-18 analysis/SWAP.py
Switched to MIT license #125

@@ -65,7 +65,7 @@ def SWAP(argv):
 
     AUTHORS
       This file is part of the Space Warps project, and is distributed
-      under the GPL v2 by the Space Warps Science Team.
+      under the MIT license by the Space Warps Science Team.
       http://spacewarps.org/
 
     HISTORY

### 2015-04-18 analysis/SWEAR.py

@@ -39,7 +39,7 @@ def SWEAR(argv):
 
     AUTHORS
       This file is part of the Space Warps project, and is distributed 
-      under the GPL v2 by the Space Warps Science Team.
+      under the MIT license by the Space Warps Science Team.
       http://spacewarps.org/
 
     HISTORY

### 2015-04-18 analysis/SWITCH.py

@@ -44,7 +44,7 @@ def SWITCH(argv):
 
     AUTHORS
       This file is part of the Space Warps project, and is distributed 
-      under the GPL v2 by the Space Warps Science Team.
+      under the MIT license by the Space Warps Science Team.
       http://spacewarps.org/
 
     HISTORY

### 2015-04-18 analysis/make_crowd_plots.py

@@ -60,7 +60,7 @@ def make_crowd_plots(argv):
 
     AUTHORS
         This file is part of the Space Warps project, and is distributed
-        under the GPL v2 by the Space Warps Science Team.
+        under the MIT license by the Space Warps Science Team.
         http://spacewarps.org/
 
     HISTORY

### 2015-04-18 analysis/make_info_plots.py

@@ -37,7 +37,7 @@ def make_info_plots(argv):
 
     AUTHORS
         This file is part of the Space Warps project, and is distributed
-        under the GPL v2 by the Space Warps Science Team.
+        under the MIT license by the Space Warps Science Team.
         http://spacewarps.org/
 
     HISTORY

### 2015-04-18 analysis/make_lens_atlas.py

@@ -203,7 +203,7 @@ def make_lens_atlas(args):
 
     AUTHORS
         This file is part of the Space Warps project, and is distributed
-        under the GPL v2 by the Space Warps Science Team.
+        under the MIT license by the Space Warps Science Team.
         http://spacewarps.org/
 
     HISTORY

### 2015-04-18 analysis/make_lens_catalog.py

@@ -173,7 +173,7 @@ def make_lens_catalog(args):
 
     AUTHORS
         This file is part of the Space Warps project, and is distributed
-        under the GPL v2 by the Space Warps Science Team.
+        under the MIT license by the Space Warps Science Team.
         http://spacewarps.org/
 
     HISTORY

### 2015-04-18 analysis/make_offline_reports.py

@@ -59,7 +59,7 @@ def make_offline_reports(args):
 
     AUTHORS
         This file is part of the Space Warps project, and is distributed
-        under the GPL v2 by the Space Warps Science Team.
+        under the MIT license by the Space Warps Science Team.
         http://spacewarps.org/
 
     HISTORY

### 2015-04-18 analysis/make_roc_curves.py

@@ -60,7 +60,7 @@ def make_roc_curves(args):
 
     AUTHORS
         This file is part of the Space Warps project, and is distributed
-        under the GPL v2 by the Space Warps Science Team.
+        under the MIT license by the Space Warps Science Team.
         http://spacewarps.org/
 
     HISTORY

### 2015-04-18 analysis/make_trajectory_plots.py

@@ -58,7 +58,7 @@ def make_trajectory_plots(argv):
 
     AUTHORS
         This file is part of the Space Warps project, and is distributed
-        under the GPL v2 by the Space Warps Science Team.
+        under the MIT license by the Space Warps Science Team.
         http://spacewarps.org/
 
     HISTORY

### 2015-04-18 analysis/swap/agent.py

@@ -82,7 +82,7 @@ class Agent(object):
 
     AUTHORS
       This file is part of the Space Warps project, and is distributed
-      under the GPL v2 by the Space Warps Science Team.
+      under the MIT license by the Space Warps Science Team.
       http://spacewarps.org/
 
     HISTORY

### 2015-04-18 analysis/swap/bureau.py

@@ -34,7 +34,7 @@ class Bureau(object):
 
     AUTHORS
       This file is part of the Space Warps project, and is distributed
-      under the GPL v2 by the Space Warps Science Team.
+      under the MIT license by the Space Warps Science Team.
       http://spacewarps.org/
 
     HISTORY

### 2015-04-18 analysis/swap/collection.py

@@ -30,7 +30,7 @@ class Collection(object):
 
     AUTHORS
       This file is part of the Space Warps project, and is distributed 
-      under the GPL v2 by the Space Warps Science Team.
+      under the MIT license by the Space Warps Science Team.
       http://spacewarps.org/
 
       2013-04-17  Started: Marshall (Oxford)

### 2015-04-18 analysis/swap/config.py

@@ -43,7 +43,7 @@ class Configuration(object):
 
     AUTHORS
       This file is part of the Space Warps project, and is distributed 
-      under the GPL v2 by the Space Warps Science Team.
+      under the MIT license by the Space Warps Science Team.
       http://spacewarps.org/
 
       SWAP configuration is modelled on that written for the

### 2015-04-18 analysis/swap/io.py

@@ -32,7 +32,7 @@ import os,cPickle,numpy as np
 
     AUTHORS
       This file is part of the Space Warps project, and is distributed
-      under the GPL v2 by the Space Warps Science Team.
+      under the MIT license by the Space Warps Science Team.
       http://spacewarps.org/
 
       SWAP io is modelled on that written for the
@@ -227,7 +227,7 @@ def write_config(filename, pars):
 # Name : Value pair to be read into the parameters dictionary.
 #
 # This file is part of the Space Warps project, and is distributed
-# under the GPL v2 by the Space Warps Science Team.
+# under the MIT license by the Space Warps Science Team.
 # http://spacewarps.org/
 #
 # SWAP configuration is modelled on that written for the

### 2015-04-18 analysis/swap/logging.py

@@ -24,7 +24,7 @@ from subject import Ntrajectory
 
     AUTHORS
       This file is part of the Space Warps project, and is distributed 
-      under the GPL v2 by the Space Warps Science Team.
+      under the MIT license by the Space Warps Science Team.
       http://spacewarps.org/
 
     HISTORY

### 2015-04-18 analysis/swap/mongodb.py

@@ -59,7 +59,7 @@ class MongoDB(object):
         
     AUTHOR
       This file is part of the Space Warps project, and is distributed 
-      under the GPL v2 by the Space Warps Science Team.
+      under the MIT license by the Space Warps Science Team.
       http://spacewarps.org/
 
     HISTORY

### 2015-04-18 analysis/swap/shannon.py

@@ -23,7 +23,7 @@ AUTHORS
   during the Citizen Science in Astronomy Workshop at ASIAA, Taipei, 
   in March 2014, hosted by Meg Schwamb. 
   This file is part of the Space Warps project, which is distributed 
-  under the GPL v2 by the Space Warps Science Team.
+  under the MIT license by the Space Warps Science Team.
   http://spacewarps.org/
 
 HISTORY

### 2015-04-18 analysis/swap/subject.py

@@ -75,7 +75,7 @@ class Subject(object):
 
     AUTHORS
       This file is part of the Space Warps project, and is distributed
-      under the GPL v2 by the Space Warps Science Team.
+      under the MIT license by the Space Warps Science Team.
       http://spacewarps.org/
 
     trajectory

### 2015-04-18 analysis/swap/toydb.py

@@ -27,7 +27,7 @@ class ToyDB(object):
 
     AUTHORS
       This file is part of the Space Warps project, and is distributed 
-      under the GPL v2 by the Space Warps Science Team.
+      under the MIT license by the Space Warps Science Team.
       http://spacewarps.org/
 
     HISTORY

### 2015-04-18 doc/sw-system.tex
Fixed #137 typos

@@
 might be scaled up for future surveys. In \Sref{sec:results:crowd} and
-\Tref{tab:crowd:contributions}, a rough picture emerged for the \SW crowd of
-it containing a few $10^4$ volunteers, with a few $10^3$ achieving
+\Tref{tab:crowd:contributions}, the following rough picture emerged for the
+\SW crowd in this project:
+it consisted of a few $10^4$ volunteers, with a few $10^3$ achieving
 considerable skill, and a few $10^2$ having the time to make a significant
@@
 volunteers make large contributions. Greater exposure of the website to the
-public through mass media woudl help. Another option is to advertise the
+public through mass media would help. Another option is to advertise the
 project to new groups of volunteers by translating the website into other

### 2015-04-18 doc/sw-system.tex
Closed #136 with short note on project renaming

@@
 team.\footnote{The \SW web application code is open source and can be accessed
-from \texttt{https://github.com/zooniverse/Lens-Zoo}}  The focus of the CI is a
+from \texttt{https://github.com/zooniverse/Lens-Zoo}. The project was renamed during development.}
+The focus of the CI is a
 large display of a pre-prepared PNG image of the ``subject'' being inspected.

### 2015-04-18 doc/sw-system.tex
Amended reference to magnification cut in Paper 2 #105

@@
 selection cuts were to only keep sims with a)  second brightest image brighter
-that $i = 23$ and b) magnification greater than 20 (\PaperTwo, Table 1).}
+that $i = 23$ and b) total combined image magnitude brighter than 19--20
+(\PaperTwo, Table 1).} The combination of these two cuts results in a sample of
+visible lensed image configurations.
 

### 2015-04-19 doc/sw-cfhtls.tex

@@
 
-In \Fref{fig:remudist}, we show the Einstein radius distribution for the
+In \Fref{fig:remudist}, we show the Einstein radius ($R_{\rm E}$) distribution for the
 galaxy-scale and groups-scale simulated lenses. For comparison, we give
@@
 difference image of $g$ and $i$ bands from which the lensing galaxy is
-subtracted \citep[for details, see]{Gavazzi2014}. Here, we use the flux
+subtracted \citep[for details, see][]{Gavazzi2014}. Here, we use the flux
 of the lensed images measured by {\sc sextractor} from the scaled
@@
 
-The Einstein radius ($R_{\rm E}$) is also measured differently for
+The Einstein radius is also measured differently for
 different samples. For the galaxy-scale lenses in the simulated sample,
@@
 candidates. As expected, we find that systems with brighter images
-and/or with larger Einstein radii are detected more often in \sw.
+and/or with larger $R_{\rm E}$ are detected more often in \sw.
 
 We find that most of the confirmed lenses and candidates that are missed
-by \sw are systems with fainter arcs and smaller Einstein radii and they
+by \sw are systems with fainter arcs and smaller $R_{\rm E}$ and they
 come from the \rf sample. The main reason why \rf found such candidates
@@
 of their candidates. This approach naturally improves the detection
-efficiency at smaller Einstein radii and for fainter systems. The \sw
+efficiency at smaller $R_{\rm E}$ and for fainter systems. The \sw
 volunteers were not shown any galaxy-subtracted images. However, showing
@@
 
-The distribution of image separations (i.e. twice the Einstein radius)
+The distribution of image separations (i.e. 2~$R_{\rm E}$)
 can be used to probe the average density profile of the lens population
@@
 selected sample does not suffer from significant incompleteness for
-medium to large Einstein radii. This is the regime that probes density
+medium to large $R_{\rm E}$. This is the regime that probes density
 profiles of galaxy groups to clusters.
@@
 visual one cannot find some of the \rf-identified-lensed images with
-sub-arcsecond Einstein radii because the flux of the typically faint
+sub-arcsecond $R_{\rm E}$ because the flux of the typically faint
 lensed images is obscured by the flux from bright lensing galaxies. The
@@
 \hline
-SW ID & Name & RA & Dec &  $z_{\rm phot}$ & $m_i$ & $R_{\rm A}$ & G & ZooID & P & Comments  \\
+SW ID & Name & RA & Dec &  $z_{\rm phot}$ & $m_i$ & $R_{\rm E}$ & G & ZooID & P & Comments  \\
   &  & (deg) & (deg) &  & (mag) &  (") &  &  & & \\
@@
 \endlastfoot
- SW1 & CFHTLS J022409-105807 &   36.0398 &  -10.9688 &  0.0 &  0.0 &  4.8 &  3.0 & ASW0004dv8 &  1.0  &  A,G   \\
- SW2 & CFHTLS J140522+574333 &  211.3426 &   57.7259 &  0.7 & 19.7 &  1.0 &  2.7 & ASW000619d &  0.7  &  A,R   \\
- SW3 & CFHTLS J142603+511420 &  216.5149 &   51.2390 &  0.0 &  0.0 &  4.4 &  2.7 & ASW0006mea &  0.7  &  A,G   \\
- SW4 & CFHTLS J142934+562541 &  217.3926 &   56.4281 &  0.5 & 19.0 &  5.9 &  2.7 & ASW0009cjs &  0.8  &  A,G   \\
- SW5 & CFHTLS J143454+522850 &  218.7270 &   52.4808 &  0.6 & 19.4 &  4.4 &  2.7 & ASW0007k4r &  0.4  &  Q,G/R   \\
- SW6 & CFHTLS J143627+563832 &  219.1164 &   56.6425 &  0.5 & 19.4 &  1.5 &  2.7 & ASW0008swn &  0.9  &  A,D   \\
- SW7 & CFHTLS J220256+023432 &  330.7369 &    2.5758 &  0.0 &  0.0 &  6.8 &  2.7 & ASW0007e08 &  0.8  &  A,G/C   \\
+SW18 & CFHTLS J020642-095157 &   31.6750 &   -9.8658 &  0.2 & 20.8 &  0.9 &  2.0 & ASW0001ld7 &  0.8  &  A,R   \\ 
+SW42 & CFHTLS J020810-040220 &   32.0450 &   -4.0389 &  1.0 & 20.8 &  1.8 &  1.3 & ASW0001c3j &  0.7  &  A,R   \\ 
  SW8 & CFHTLS J020832-043315 &   32.1340 &   -4.5543 &  1.0 & 21.0 &  1.6 &  2.3 & ASW0002asp &  1.0  &  A,R   \\ 
@@
 SW10 & CFHTLS J020849-050429 &   32.2078 &   -5.0749 &  0.8 & 20.6 &  0.9 &  2.3 & ASW0002qtn &  1.0  &  A,R   \\ 
+SW43 & CFHTLS J021021-093415 &   32.5898 &   -9.5711 &  0.4 & 18.4 &  2.7 &  1.3 & ASW0002k40 &  0.4  &  D,S   \\ 
+SW29 & CFHTLS J021057-084450 &   32.7414 &   -8.7474 &  0.0 &  0.0 &  2.5 &  1.7 & ASW0002p8y &  0.4  &  A,G   \\ 
+SW19 & CFHTLS J021221-105251 &   33.0881 &  -10.8811 &  0.3 & 17.9 &  1.8 &  2.0 & ASW0002dx7 &  0.8  &  D,E/S   \\ 
+SW44 & CFHTLS J021225-085211 &   33.1051 &   -8.8697 &  0.8 & 19.5 &  2.1 &  1.3 & ASW00024id &  1.0  &  R,R   \\ 
+SW45 & CFHTLS J021317-084819 &   33.3234 &   -8.8055 &  0.5 & 19.8 &  1.3 &  1.3 & ASW00024q6 &  0.4  &  A,R/E   \\ 
+SW30 & CFHTLS J021514-092440 &   33.8109 &   -9.4111 &  0.7 & 19.9 &  2.6 &  1.7 & ASW00021r0 &  0.4  &  A,R/G   \\ 
+SW31 & CFHTLS J022359-083651 &   35.9995 &   -8.6143 &  0.0 &  0.0 &  3.1 &  1.7 & ASW0004iye &  0.4  &  A,E   \\ 
 SW11 & CFHTLS J022406-062846 &   36.0256 &   -6.4796 &  0.4 & 19.6 &  0.9 &  2.3 & ASW0003wsu &  0.7  &  A,E   \\ 
-SW12 & CFHTLS J022805-051733 &   37.0236 &   -5.2927 &  0.4 & 18.8 &  1.4 &  2.3 & ASW0009ans &  1.0  &  Q,E   \\
-SW13 & CFHTLS J023123-082535 &   37.8468 &   -8.4266 &  0.0 &  0.0 &  1.2 &  2.3 & ASW0004xjk &  0.3  &  A,R   \\
-SW14 & CFHTLS J084841-045237 &  132.1708 &   -4.8772 &  0.3 & 19.0 &  1.0 &  2.3 & ASW0004nan &  1.0  &  A,E   \\
-SW15 & CFHTLS J140030+574437 &  210.1260 &   57.7437 &  0.4 & 18.2 &  2.0 &  2.3 & ASW0009bp2 &  0.6  &  A,E   \\
-SW16 & CFHTLS J140622+520942 &  211.5958 &   52.1617 &  0.7 & 20.3 &  1.2 &  2.3 & ASW0005rnb &  0.7  &  A,R   \\
-SW17 & CFHTLS J143658+533807 &  219.2425 &   53.6355 &  0.7 & 19.6 &  0.9 &  2.3 & ASW0007hu2 &  0.6  &  D,D   \\
-SW18 & CFHTLS J020642-095157 &   31.6750 &   -9.8658 &  0.2 & 20.8 &  0.9 &  2.0 & ASW0001ld7 &  0.8  &  A,R   \\
-SW19 & CFHTLS J021221-105251 &   33.0881 &  -10.8811 &  0.3 & 17.9 &  1.8 &  2.0 & ASW0002dx7 &  0.8  &  D,E/S   \\
+ SW1 & CFHTLS J022409-105807 &   36.0398 &  -10.9688 &  0.0 &  0.0 &  4.8 &  3.0 & ASW0004dv8 &  1.0  &  A,G   \\ 
 SW20 & CFHTLS J022533-053204 &   36.3888 &   -5.5346 &  0.5 & 19.4 &  3.6 &  2.0 & ASW0004m3x &  0.4  &  A,R/G   \\ 
 SW21 & CFHTLS J022716-105602 &   36.8186 &  -10.9341 &  0.4 & 17.2 &  1.8 &  2.0 & ASW0009ab8 &  0.7  &  A,E/G   \\ 
+SW32 & CFHTLS J022745-062518 &   36.9387 &   -6.4218 &  0.6 & 20.5 &  1.2 &  1.7 & ASW0003s0m &  0.5  &  A,R   \\ 
+SW12 & CFHTLS J022805-051733 &   37.0236 &   -5.2927 &  0.4 & 18.8 &  1.4 &  2.3 & ASW0009ans &  1.0  &  Q,E   \\ 
+SW46 & CFHTLS J022843-063316 &   37.1794 &   -6.5547 &  0.5 & 19.1 &  1.8 &  1.3 & ASW0003r6c &  0.3  &  D/A,E   \\ 
 SW22 & CFHTLS J023008-054038 &   37.5359 &   -5.6774 &  0.6 & 19.7 &  1.9 &  2.0 & ASW0003r61 &  0.5  &  A,E   \\ 
+SW13 & CFHTLS J023123-082535 &   37.8468 &   -8.4266 &  0.0 &  0.0 &  1.2 &  2.3 & ASW0004xjk &  0.3  &  A,R   \\ 
 SW23 & CFHTLS J023315-042243 &   38.3133 &   -4.3789 &  0.7 & 19.7 &  1.0 &  2.0 & ASW00050sk &  0.8  &  A,R   \\ 
-SW24 & CFHTLS J090308-043252 &  135.7844 &   -4.5479 &  0.0 &  0.0 &  1.2 &  2.0 & ASW00007mq &  0.6  &  A,E   \\
-SW25 & CFHTLS J135755+571722 &  209.4827 &   57.2897 &  0.8 & 20.2 &  1.3 &  2.0 & ASW0005ma2 &  0.8  &  D,D   \\
-SW26 & CFHTLS J141432+534004 &  213.6372 &   53.6679 &  0.7 & 21.4 &  0.9 &  2.0 & ASW0006jh5 &  0.8  &  A,R   \\
-SW27 & CFHTLS J143055+572431 &  217.7333 &   57.4088 &  0.7 & 19.3 &  1.0 &  2.0 & ASW0007wfj &  0.9  &  A,R   \\
-SW28 & CFHTLS J143838+572647 &  219.6589 &   57.4464 &  0.8 & 20.2 &  1.1 &  2.0 & ASW0008qsm &  0.9  &  A,R   \\
-SW29 & CFHTLS J021057-084450 &   32.7414 &   -8.7474 &  0.0 &  0.0 &  2.5 &  1.7 & ASW0002p8y &  0.4  &  A,G   \\
-SW30 & CFHTLS J021514-092440 &   33.8109 &   -9.4111 &  0.7 & 19.9 &  2.6 &  1.7 & ASW00021r0 &  0.4  &  A,R/G   \\
-SW31 & CFHTLS J022359-083651 &   35.9995 &   -8.6143 &  0.0 &  0.0 &  3.1 &  1.7 & ASW0004iye &  0.4  &  A,E   \\
-SW32 & CFHTLS J022745-062518 &   36.9387 &   -6.4218 &  0.6 & 20.5 &  1.2 &  1.7 & ASW0003s0m &  0.5  &  A,R   \\
 SW33 & CFHTLS J023453-093032 &   38.7232 &   -9.5089 &  0.5 & 19.8 &  0.7 &  1.7 & ASW00051ld &  0.3  &  A,D   \\ 
 SW34 & CFHTLS J084833-044051 &  132.1385 &   -4.6809 &  0.8 & 20.2 &  0.9 &  1.7 & ASW0004wgd &  0.7  &  A,R   \\ 
+SW14 & CFHTLS J084841-045237 &  132.1708 &   -4.8772 &  0.3 & 19.0 &  1.0 &  2.3 & ASW0004nan &  1.0  &  A,E   \\ 
+SW47 & CFHTLS J090219-053923 &  135.5794 &   -5.6566 &  0.0 &  0.0 &  2.0 &  1.3 & ASW0000g95 &  1.0  &  A,R/E   \\ 
 SW35 & CFHTLS J090248-010232 &  135.7020 &   -1.0424 &  0.4 & 19.1 &  1.4 &  1.7 & ASW000096t &  0.6  &  D,E   \\ 
-SW36 & CFHTLS J143100+564603 &  217.7511 &   56.7675 &  0.0 &  0.0 &  1.8 &  1.7 & ASW00086xq &  0.8  &  A,E   \\
-SW37 & CFHTLS J143353+542310 &  218.4736 &   54.3862 &  0.8 & 19.8 &  1.6 &  1.7 & ASW0009cox &  0.6  &  A,R/G   \\
-SW38 & CFHTLS J220215+012124 &  330.5635 &    1.3567 &  0.3 & 17.4 &  4.6 &  1.7 & ASW0005qiz &  0.5  &  rA,G   \\
-SW39 & CFHTLS J221306+014708 &  333.2758 &    1.7856 &  0.0 & 17.1 &  1.4 &  1.7 & ASW0008wmr &  0.9  &  A,S   \\
-SW40 & CFHTLS J221519+005758 &  333.8321 &    0.9661 &  0.4 & 20.2 &  1.0 &  1.7 & ASW0008xbu &  0.8  &  A,D   \\
-SW41 & CFHTLS J221716+015826 &  334.3189 &    1.9739 &  0.1 & 21.6 &  1.0 &  1.7 & ASW00096rm &  1.0  &  A/R,R   \\
-SW42 & CFHTLS J020810-040220 &   32.0450 &   -4.0389 &  1.0 & 20.8 &  1.8 &  1.3 & ASW0001c3j &  0.7  &  A,R   \\
-SW43 & CFHTLS J021021-093415 &   32.5898 &   -9.5711 &  0.4 & 18.4 &  2.7 &  1.3 & ASW0002k40 &  0.4  &  D,S   \\
-SW44 & CFHTLS J021225-085211 &   33.1051 &   -8.8697 &  0.8 & 19.5 &  2.1 &  1.3 & ASW00024id &  1.0  &  R,R   \\
-SW45 & CFHTLS J021317-084819 &   33.3234 &   -8.8055 &  0.5 & 19.8 &  1.3 &  1.3 & ASW00024q6 &  0.4  &  A,R/E   \\
-SW46 & CFHTLS J022843-063316 &   37.1794 &   -6.5547 &  0.5 & 19.1 &  1.8 &  1.3 & ASW0003r6c &  0.3  &  D/A,E   \\
-SW47 & CFHTLS J090219-053923 &  135.5794 &   -5.6566 &  0.0 &  0.0 &  2.0 &  1.3 & ASW0000g95 &  1.0  &  A,R/E   \\
-SW48 & CFHTLS J090319-040146 &  135.8311 &   -4.0297 &  0.0 & 19.8 &  1.2 &  1.3 & ASW00007ls &  0.5  &  A,R/E   \\
+SW24 & CFHTLS J090308-043252 &  135.7844 &   -4.5479 &  0.0 &  0.0 &  1.2 &  2.0 & ASW00007mq &  0.6  &  A,E   \\ 
+SW48 & CFHTLS J090319-040146 &  135.8311 &   -4.0297 &  0.0 & 19.8 &  1.2 &  1.3 & ASW00007ls &  0.5  &  A,R/E/nbr   \\ 
 SW49 & CFHTLS J090333-005829 &  135.8886 &   -0.9749 &  0.0 &  0.0 &  2.1 &  1.3 & ASW00008a0 &  1.0  &  A/D,E/G   \\ 
-SW50 & CFHTLS J135724+561614 &  209.3536 &   56.2707 &  0.0 &  0.0 &  2.6 &  1.3 & ASW0006e0o &  0.9  &  D,E   \\
+SW50 & CFHTLS J135724+561614 &  209.3536 &   56.2707 &  0.0 &  0.0 &  2.6 &  1.3 & ASW0006e0o &  0.9  &  D,E/unlikely   \\ 
+SW25 & CFHTLS J135755+571722 &  209.4827 &   57.2897 &  0.8 & 20.2 &  1.3 &  2.0 & ASW0005ma2 &  0.8  &  D,D   \\ 
 SW51 & CFHTLS J140027+541028 &  210.1164 &   54.1746 &  0.0 &  0.0 &  1.2 &  1.3 & ASW0006a07 &  0.6  &  Q,R/E   \\ 
+SW15 & CFHTLS J140030+574437 &  210.1260 &   57.7437 &  0.4 & 18.2 &  2.0 &  2.3 & ASW0009bp2 &  0.6  &  A,E   \\ 
+ SW2 & CFHTLS J140522+574333 &  211.3426 &   57.7259 &  0.7 & 19.7 &  1.0 &  2.7 & ASW000619d &  0.7  &  A,R   \\ 
+SW16 & CFHTLS J140622+520942 &  211.5958 &   52.1617 &  0.7 & 20.3 &  1.2 &  2.3 & ASW0005rnb &  0.7  &  A,R   \\ 
+SW26 & CFHTLS J141432+534004 &  213.6372 &   53.6679 &  0.7 & 21.4 &  0.9 &  2.0 & ASW0006jh5 &  0.8  &  A,R   \\ 
 SW52 & CFHTLS J141518+513915 &  213.8290 &   51.6542 &  0.4 & 18.3 &  3.0 &  1.3 & ASW00070vl &  0.8  &  D,E   \\ 
+ SW3 & CFHTLS J142603+511420 &  216.5149 &   51.2390 &  0.0 &  0.0 &  4.4 &  2.7 & ASW0006mea &  0.7  &  A,G   \\ 
 SW53 & CFHTLS J142620+561356 &  216.5870 &   56.2323 &  0.5 & 19.5 &  1.3 &  1.3 & ASW0007sez &  0.8  &  A/R,S   \\ 
@@
 SW55 & CFHTLS J142843+543713 &  217.1815 &   54.6204 &  0.4 & 19.7 &  1.3 &  1.3 & ASW0007pga &  0.6  &  D,D   \\ 
+ SW4 & CFHTLS J142934+562541 &  217.3926 &   56.4281 &  0.5 & 19.0 &  5.9 &  2.7 & ASW0009cjs &  0.8  &  A,G   \\ 
+SW27 & CFHTLS J143055+572431 &  217.7333 &   57.4088 &  0.7 & 19.3 &  1.0 &  2.0 & ASW0007wfj &  0.9  &  A,R   \\ 
+SW36 & CFHTLS J143100+564603 &  217.7511 &   56.7675 &  0.0 &  0.0 &  1.8 &  1.7 & ASW00086xq &  0.8  &  A,E   \\ 
+SW37 & CFHTLS J143353+542310 &  218.4736 &   54.3862 &  0.8 & 19.8 &  1.6 &  1.7 & ASW0009cox &  0.6  &  A,R/G   \\ 
+ SW5 & CFHTLS J143454+522850 &  218.7270 &   52.4808 &  0.6 & 19.4 &  4.4 &  2.7 & ASW0007k4r &  0.4  &  Q,G/R   \\ 
+ SW6 & CFHTLS J143627+563832 &  219.1164 &   56.6425 &  0.5 & 19.4 &  1.5 &  2.7 & ASW0008swn &  0.9  &  A,D   \\ 
 SW56 & CFHTLS J143631+571131 &  219.1315 &   57.1922 &  0.7 & 20.9 &  1.3 &  1.3 & ASW0008pag &  0.6  &  D/A,R   \\ 
 SW57 & CFHTLS J143651+530705 &  219.2150 &   53.1183 &  0.6 & 19.2 &  3.1 &  1.3 & ASW0007h27 &  1.0  &  A,E/G   \\ 
+SW17 & CFHTLS J143658+533807 &  219.2425 &   53.6355 &  0.7 & 19.6 &  0.9 &  2.3 & ASW0007hu2 &  0.6  &  D,D   \\ 
+SW28 & CFHTLS J143838+572647 &  219.6589 &   57.4464 &  0.8 & 20.2 &  1.1 &  2.0 & ASW0008qsm &  0.9  &  A,R   \\ 
 SW58 & CFHTLS J143950+544606 &  219.9609 &   54.7686 &  0.0 &  0.0 &  1.7 &  1.3 & ASW00085cp &  0.4  &  A,G/R   \\ 
-
+SW38 & CFHTLS J220215+012124 &  330.5635 &    1.3567 &  0.3 & 17.4 &  4.6 &  1.7 & ASW0005qiz &  0.5  &  rA,G   \\ 
+ SW7 & CFHTLS J220256+023432 &  330.7369 &    2.5758 &  0.0 &  0.0 &  6.8 &  2.7 & ASW0007e08 &  0.8  &  A,G/Clus   \\ 
+SW39 & CFHTLS J221306+014708 &  333.2758 &    1.7856 &  0.0 & 17.1 &  1.4 &  1.7 & ASW0008wmr &  0.9  &  A,S   \\ 
+SW40 & CFHTLS J221519+005758 &  333.8321 &    0.9661 &  0.4 & 20.2 &  1.0 &  1.7 & ASW0008xbu &  0.8  &  A,D   \\ 
+SW41 & CFHTLS J221716+015826 &  334.3189 &    1.9739 &  0.1 & 21.6 &  1.0 &  1.7 & ASW00096rm &  1.0  &  A/R,R/unlikely   \\ 
 \end{longtable}

### 2015-04-19 doc/sw-system.tex
Fixed #135
Fixed #134

@@
 The CFHTLS $g$, $r$ and $i$-band images have the greatest depth and best image
-quality, and we chose to focus on this set (although the $u$ and $z$-band
-images were also available for perusal in Talk). \new{We made colour composite PNG
-format images
-following the prescription of \citet{LuptonEtal2004} \citep[with extensions
-by][and some particular choices of our own]{WherryEtal2004}, using the \humvi
-software.\footnote{The \humvi colour image composition code used in
-this work is open source and available from \texttt{http://github.com/drphilmarshall/HumVI}} Specifically, we
-first rescaled the pixel values of each image, in the notation of
-\citeauthor{LuptonEtal2004}) into flux units (``picomaggies,''), via the image
-AB zeropoint $m_0$ and the pixel value calibration factor $f$  given by
-$\log_{10}{f} = 0.4(30.0 - m_0)$. We then applied further aesthetic
-``scales'' $s_{i,r,g}$ before computing the intensity image $I$ and applying
-an arcsinh stretch. (The scales are re-normalized to sum to one.) Thus, the red
-($R$), green ($G$) and blue ($B$) channel images correspond to the CFHTLS $i$,
-$r$ and $g$-band images in the following way:
+quality, and we chose to focus on this set (although the $u$ and $z$-band images
+were also available for perusal in Talk). \new{We made colour composite PNG
+format images following the prescription of \citet{LuptonEtal2004} \citep[with
+extensions by][and some particular choices of our own]{WherryEtal2004}, using
+the \humvi software.\footnote{The \humvi colour image composition code used in
+this work is open source and available from
+\texttt{http://github.com/drphilmarshall/HumVI}} Specifically, we first rescaled
+the pixel values of each image, in the notation of \citeauthor{LuptonEtal2004},
+into flux units (``picomaggies,''), via the image AB zeropoint $m_0$ and the
+pixel value calibration factor $f$  given by $\log_{10}{f} = 0.4(30.0 - m_0)$.
+We then multiplied these calibrated images by further aesthetic ``scales''
+$s_{i,r,g}$ before computing the total intensity image $I$ and applying an
+arcsinh stretch. (The scales are re-normalized to sum to one on input.) Thus,
+the red ($R$), green ($G$) and blue ($B$) channel images correspond to the
+CFHTLS $i$, $r$ and $g$-band images in the following way:
 \bea
@@
 range 0 to 1 was assigned the value 0 or 1 appropriately. This was not the
-recommendation of \citet{LuptonEtal2004}, but we found it to give very
+recommendation of \citet{LuptonEtal2004}, but we found it to still give very
 informative but also familiar-looking astronomical images.}
@@
 Each classification made is logged in a database, storing subject IDs,
-(anonymous) volunteer IDs, a timestamp and the classification results (the image pixel-coordinate positions of every marker placed).  The
-``category'' of subject -- whether it is a ``training'' subject (a simulated
-lens or a known non-lens) or a ``test'' subject (an unseen image drawn from the
-survey) -- is also recorded. For all subjects, the positions of all Markers are
-recorded, in pixel coordinates. For training subjects, we also store the
-``kind'' of the subject as a lens (``sim''), or a non-lens (``dud''), and also
-the ``flavor'' of lens object if one is present in the image (``lensed galaxy'',
-``lensed quasar'' or ``cluster lens'').  This classification is used to provide
-instant feedback, but is also the basic measurement used in a probabilistic
-classification of every subject based on all image views to date.
+(anonymous) volunteer IDs, a timestamp and the classification results (the image
+pixel-coordinate positions of every marker placed).  The ``category'' of subject --
+whether it is a ``training'' subject (a simulated lens or a known non-lens) or a
+``test'' subject (an unseen image drawn from the survey) -- is also recorded.
+For training subjects, we also store the ``kind'' of the subject as
+a lens (``sim''), or a non-lens (``dud''), and also the ``flavor'' of lens
+object if one is present in the image (``lensed galaxy'', ``lensed quasar'' or
+``cluster lens'').  This classification is used to provide instant feedback, but
+is also the basic measurement used in a probabilistic classification of every
+subject based on all image views to date.
 

### 2015-04-19 doc/sw-system.tex
Fixed #132

@@
 
-\new{At this point, the distribution of lens and source properties are quite
-realistic. At this point, we chose to make several cuts, to reject sims that
-were likely to be difficult to spot. While this ensured the educational value
-of the sims when giving feedback, it meant that we should only {\it expect} to
-detect real lens candidates that also pass these cuts. Any real lenses
-candidates we find with properties outside the ranges of the sims may in some
-sense be considered bonuses, a product of the {\it imagination} of the crowd
-in extrapolating their understanding of gravitational lenses into a regime
+At this point, the distribution of lens and source properties are quite
+realistic. We then chose to make cuts of the simulated lens pool, in order to
+reject sims that were likely to be diﬃcult to spot. While this ensured the
+educational value of the sims when feedback was given, it meant that we should
+only expect to detect real lens candidates that also pass these cuts. Any real
+lens candidates we ﬁnd with properties outside the ranges of the sims, may in
+some sense be considered bonuses, a product of the {\it imagination} of the
+crowd in extrapolating their understanding of gravitational lenses into a regime
 where they have not seen any before. In the CFHTLS project, the most important
@@
 that $i = 23$ and b) total combined image magnitude brighter than 19--20
-(\PaperTwo, Table 1).} The combination of these two cuts results in a sample of
+(\PaperTwo, Table~1).} The combination of these two cuts results in a sample of
 visible lensed image configurations.

### 2015-04-19 doc/sw-system.tex
Fixed #131

@@
 
-\new{Because we include a training set of images in amongst the survey ``test''
-images in this way, \sw can be viewed as a {\it supervised learning} system.
+Because we include a training set of images in amongst the survey ``test''
+images, \sw can be viewed as a {\it supervised learning} system.
 Consequently, we should expect to find lens candidates that look like the sims
@@
 images drawn from the survey. It also means that each dataset presented for
-inspection in the \sw interface needs to come with its own training set.}
-
-\new{Second, the lensed features themselves must be realistic; if they did not
+inspection in the \sw interface needs to come with its own training set.
+
+Second, the lensed features themselves must be realistic; if they did not
 resemble real lenses, we could not expect to find real lenses in the test
@@
 lens candidates in the survey fields. Here, we merely note the following
-aspects to place this paper's results in context.}
-
-\new{We start by selecting massive galaxies and groups in the CFHTLS catalogs,
+aspects to place this paper's results in context.
+
+We start by selecting massive galaxies and groups in the CFHTLS catalogs,
 by color, brightness and photometric redshift. We then assign plausible mass
@@
 the predicted multiple images of the source using the \gravlens ray-tracing
-code \citep{Keeton2000}.}
+code \citep{Keeton2000}.
 
@@
 that $i = 23$ and b) total combined image magnitude brighter than 19--20
-(\PaperTwo, Table~1).} The combination of these two cuts results in a sample of
+(\PaperTwo, Table~1). The combination of these two cuts results in a sample of
 visible lensed image configurations.
@@
 quality, and we chose to focus on this set (although the $u$ and $z$-band images
-were also available for perusal in Talk). \new{We made colour composite PNG
+were also available for perusal in Talk). We made colour composite PNG
 format images following the prescription of \citet{LuptonEtal2004} \citep[with
@@
 recommendation of \citet{LuptonEtal2004}, but we found it to still give very
-informative but also familiar-looking astronomical images.}
-
-\new{The non-linearity parameters $Q$ and $\alpha$ control the brightness and
+informative but also familiar-looking astronomical images.
+
+The non-linearity parameters $Q$ and $\alpha$ control the brightness and
 contrast of the images. We first tuned $\alpha$ (which acts as an additional
@@
 be suppressed enough to allow the low surface brightness features to show
-through, but not so much that they no longer looked like massive galaxies.}
+through, but not so much that they no longer looked like massive galaxies.
 

### 2015-04-19 doc/acknowledgments.tex
Switched to MIT license #125
Fixed all missing references, merged bib files back into one. Also added CFHTLS acknowledgment text and website URL footnote. Closes #130

@@
 contributions to the project so far. A complete list of collaborators is
-given at \texttt{http://spacewarps.org/\#/results/CFHTLS}.
+provided at \texttt{http://spacewarps.org/\#/results/CFHTLS}.
 
@@
 \texttt{https://github.com/drphilmarshall/SpaceWarps}.
+
+The CFHTLS data used in this work are based on observations obtained with
+MegaPrime/MegaCam, a joint project of CFHT and CEA/IRFU, at the
+Canada-France-Hawaii Telescope (CFHT) which is operated by the National Research
+Council (NRC) of Canada, the Institut National des Science de l'Univers of the
+Centre National de la Recherche Scientifique (CNRS) of France, and the
+University of Hawaii. This work is based in part on data products produced at
+Terapix available at the Canadian Astronomy Data Centre as part of the
+Canada-France-Hawaii Telescope Legacy Survey, a collaborative project of NRC and
+CNRS.

### 2015-04-19 doc/sw-cfhtls.tex
Fixed all missing references, merged bib files back into one. Also added CFHTLS acknowledgment text and website URL footnote. Closes #130

@@
 pipeline, used for generating a sample of realistic simulated lensed
-images in the CFHTLS, and a sample of duds and false positives used in
+images in the \cfhtls, and a sample of duds and false positives used in
 the training.  Such a training sample has a legacy value for testing
@@
 using data from the Canada-France-Hawaii Telescope Legacy Survey
-(\cfhtls). This paper is organised as follows. In
+(\cfhtls\footnote{\texttt{http://www.cfht.hawaii.edu/Science/CFHTLS/}}).
+This paper is organised as follows. In
 \Sref{sec:data}, we introduce the \cfhtls imaging data and the
@@
 \bibliographystyle{apj}
-%\bibliography{references}
-\bibliography{references_cfhtls}
+\bibliography{references}
 

### 2015-04-19 doc/sw-system.tex
Fixed all missing references, merged bib files back into one. Also added CFHTLS acknowledgment text and website URL footnote. Closes #130

@@
 of high purity and completeness through crowd-sourced visual inspection.
-Carefully produced color composite images are displayed to volunteers via a
+Carefully produced colour composite images are displayed to volunteers via a
 classification interface which records their estimates of the positions of
@@
 probability systems are retired from the site periodically, concentrating the
-sample towards a set of candidates. Having divided the 171 square degree CFHTLS
-imaging survey into some 430,000 overlapping 84 by 84 arcminute tiles and
+sample towards a set of candidates. Having divided the 171 square degree
+Canada-France-Hawaii Telescope Legacy Survey (\cfhtls)
+imaging survey into some 430,000 overlapping 80 by 80 arcsecond tiles and
 displayed them on the site, we were joined by around 37,000 volunteers who
@@
 CLASS \citep[e.g.]{BrowneEtal2003}, SDSS \citep[e.g.][]
-{BoltonEtal2006,AugerEtal2010b,TreuEtal2011,InadaEtal2012,SBAS,SGAS,CASSOWARY},
-CFHTLS \citep[e.g.][]{MoreEtal2012,GavazziEtal2014}, Herschel
+{BoltonEtal2006,AugerEtal2010b,TreuEtal2011,InadaEtal2012,
+HennawiEtal2008,BelokurovEtal2009,DiehlEtal2009,FurlanettoEtal2013},
+\cfhtls \citep[e.g.][]{MoreEtal2012,GavazziEtal2014}, Herschel
 \citep[][]{NegrelloEtal2014} and SPT \citep[e.g.][]{VieiraEtal2013}, among
@@
 \citep{GavazziEtal2008,CollettEtal2012} and lensed supernovae
-\citep{QuimbyEtal2014,KellyEtal2014} are good examples of this.
+\citep{QuimbyEtal2014,KellyEtal2015} are good examples of this.
 
@@
 they have so far produced yields in the tens to hundreds. An alternative
-approach is to search images already of sufficiently high resolution and color
+approach is to search images already of sufficiently high resolution and colour
 contrast, and confirm the systems as gravitational lenses by modeling the
@@
 PawaseEtal2014}. Similarly, searches of over a hundred square degrees of CFHT
-Legacy Survey (CFHTLS) ground-based imaging, also with sub-arcsecond image quality,
+Legacy Survey (\cfhtls) ground-based imaging, also with sub-arcsecond image quality,
 have revealed a smaller number of wider image separation group-scale systems
@@
 resemble real lenses, we could not expect to find real lenses in the test
-images. The details of how we generated the sims for the CFHTLS project are
+images. The details of how we generated the sims for the \cfhtls project are
 given in \PaperTwo, where we also carry out performance tests relative to real
@@
 
-We start by selecting massive galaxies and groups in the CFHTLS catalogs,
-by color, brightness and photometric redshift. We then assign plausible mass
+We start by selecting massive galaxies and groups in the \cfhtls catalogs,
+by colour, brightness and photometric redshift. We then assign plausible mass
 distributions to these ``potential lenses:'' a singular isothermal ellipsoid
@@
 crowd in extrapolating their understanding of gravitational lenses into a regime
-where they have not seen any before. In the CFHTLS project, the most important
+where they have not seen any before. In the \cfhtls project, the most important
 selection cuts were to only keep sims with a)  second brightest image brighter
@@
 
-We now describe briefly the two-stage strategy that was employed in the CFHTLS
+We now describe briefly the two-stage strategy that was employed in the \cfhtls
 project: initial classification (involving the rejection of very large numbers
@@
 
-The design of the \StageOne classification task, and its training set, should lead
-to sample of lens candidates that has high completeness but may have low purity.
-To refine this sample to higher purity, we need to reject more non-lenses, which
-means providing the volunteers with a more realistic and challenging training
-set as they re-classify it. The more demanding \StageTwo training set was
-generated as follows. The \StageTwo duds were selected from the image pool by at
-least one of three of us  (AV, AM and PM) as being a potential false positive,
-while the \StageTwo sims were chosen to be a subset of \StageOne sims, none of which
-were deemed ``obvious'' by the same expert classifiers.
-\Fref{fig:training:gallery} shows some example images from the resulting CFHTLS
-\StageTwo training set.
+The design of the \StageOne classification task, and its training set, should
+lead to sample of lens candidates that has high completeness but may have low
+purity. To refine this sample to higher purity, we need to reject more
+non-lenses, which means providing the volunteers with a more realistic and
+challenging training set as they re-classify it. The more demanding \StageTwo
+training set was generated as follows. The \StageTwo duds were selected from the
+image pool by at least one of three of us  (AV, AM and PM) as being a potential
+false positive, while the \StageTwo sims were chosen to be a subset of \StageOne
+sims, none of which were deemed ``obvious'' by the same expert classifiers.
+Figures~\ref{fig:training-gallery:sims} and~\ref{fig:training-gallery:duds}
+show some example images from the resulting \cfhtls \StageTwo training set.
 
@@
 the app, slowing down the arrival of new images, and switching the background
-color to bright orange to make it clear that a different task was being set.
+colour to bright orange to make it clear that a different task was being set.
 The frequency with which training images were shown was fixed at 1 in 3.
@@
 
-The CFHT Legacy Survey \citep[CFHTLS,][]{CFHTLS} covered 171 square degrees of
+The CFHT Legacy Survey\footnote{\texttt{http://www.cfht.hawaii.edu/Science/CFHTLS/}}
+\citep[\cfhtls,][]{Gwyn2012} covered 171 square degrees of
 approximately equatorial sky, in four patches distributed in right ascension.
@@
 lens'' samples, makes this a natural choice against which to develop and test
-the \SW system. The CFHTLS is also well-representative of the data quality
+the \SW system. The \cfhtls is also well-representative of the data quality
 expected from several next-generation sky surveys, such as DES, KiDS, HSC and
@@
 In order to investigate the completeness of the previous, semi-automated, lens
-searches in the CFHTLS area, we designed a ``blind search.'' We divided the
+searches in the \cfhtls area, we designed a ``blind search.'' We divided the
 mosaiced images into some 430,000 equal size, overlapping tiles, approximately
-70~arcsec on a side. We refer to these images as ``test images'' (as opposed to
+80~arcsec on a side. We refer to these images as ``test images'' (as opposed to
 ``training images''). In future, larger area projects we expect to implement the
@@
 
-The CFHTLS $g$, $r$ and $i$-band images have the greatest depth and best image
+The \cfhtls $g$, $r$ and $i$-band images have the greatest depth and best image
 quality, and we chose to focus on this set (although the $u$ and $z$-band images
@@
 the red ($R$), green ($G$) and blue ($B$) channel images correspond to the
-CFHTLS $i$, $r$ and $g$-band images in the following way:
+\cfhtls $i$, $r$ and $g$-band images in the following way:
 \bea
@@
 they tend to hide the faint features in those images: we needed to optimize
-the detectability of these faint features.   Examples of CFHTLS training set
+the detectability of these faint features.   Examples of \cfhtls training set
 images prepared in this way can be seen in the galleries of the previous
@@
 \begin{center}
-\caption{Example \humvi image display parameters, for the CFHTLS images.}
+\caption{Example \humvi image display parameters, for the \cfhtls images.}
 \label{tab:data:humvi}
@@
 of the volunteers with the identification interface, and then describe how we
-applied this methodology in the two classification stages in the CFHTLS
+applied this methodology in the two classification stages in the \cfhtls
 project in the \SW Analysis Pipeline (SWAP) code.\footnote{The open source
@@
 randomly-selected agents, as they were on a particular day towards the end of
-the CFHTLS project. Many volunteers classify  only a small number of images, and
+the \cfhtls project. Many volunteers classify  only a small number of images, and
 so their agents' confusion matrix elements remain close to their initial values
@@
 
-During \StageOne classification of the CFHTLS images, we assigned a prior
+During \StageOne classification of the \cfhtls images, we assigned a prior
 probability for each image to contain a lens of $2\times10^{-4}$, based on a
@@
 \Fref{fig:results:sample:roc} shows receiver operating characteristic (ROC)
-curves for CFHTLS \StageOne and \StageTwo. These plots show the true positive
+curves for \cfhtls \StageOne and \StageTwo. These plots show the true positive
 rate (TPR, the number of sims correctly detected divided by the total number of
@@
 \caption{Receiver operating characteristic curves for the \SW system, using
-the CFHTLS training set. Left: \StageOne, right: \StageTwo. Insets show a
+the \cfhtls training set. Left: \StageOne, right: \StageTwo. Insets show a
 magnified view of the top lefthand corner of each plot. Linestyles illustrate
@@
 \caption{Completeness-estimated purity curves for the \sw system, using
-the CFHTLS training set.}
+the \cfhtls training set.}
 \label{fig:results:sample:CP}
@@
 \centering\includegraphics[width=\linewidth]{sw-system-figs/rate_classification.png}
-\caption{Fractional classification rate in the \SW CFHTLS survey.}
+\caption{Fractional classification rate in the \SW \cfhtls survey.}
 \label{fig:results:speed}
@@
 false negatives (blue) and false positives (red) from the classification of
-the \SW CFHTLS training set. The trajectory plot for each of the 4 subjects is
+the \SW \cfhtls training set. The trajectory plot for each of the 4 subjects is
 shown to the right of its image. Lefthand panels show the most common types of
@@
 than another, or, more generally, as a function of lens property (such as
-color, brightness, and image separation). In the current model, all agents are
+colour, brightness, and image separation). In the current model, all agents are
 considered to be completely independent, whereas in fact we might expect there
@@
 \begin{center}
-\caption{Total crowd and subject sample properties from the CFHTLS project.}
+\caption{Total crowd and subject sample properties from the \cfhtls project.}
 \label{tab:crowd:contributions}
@@
 \Tref{tab:crowd:contributions} shows the total effort, contribution, skill and
-information generated in both \StageOne and 2 of the CFHTLS project, with the
+information generated in both \StageOne and 2 of the \cfhtls project, with the
 total numbers of agents and subjects for comparison.   These numbers allow us
@@
 visual inspection. The \SW web-based classification interface presents carefully
-prepared color composite sky images to volunteers, who mark features they
+prepared colour composite sky images to volunteers, who mark features they
 propose to  have been lensed. The participants receive ongoing training with a
@@
 information to inform the automated interpretation of their markers. In our
-first lens search we simply divided the CFHTLS imaging into some 430,000 tiles,
+first lens search we simply divided the \cfhtls imaging into some 430,000 tiles,
 and collected over 10~million volunteer image classifications.
@@
 
-\item Over the course of the two stages of the CFHTLS project, the
+\item Over the course of the two stages of the \cfhtls project, the
 set of images was reduced by a factor of $10^3$ (from a few hundred thousand to
@@
 
-In \PaperTwo we present the results of this CFHTLS lens search in more detail,
+In \PaperTwo we present the results of this \cfhtls lens search in more detail,
 in particular focusing on the detection of real lenses, and the comparison
@@
 \ee
-where we have to assign a value for $p_0$. In the CFHTLS, we might expect
+where we have to assign a value for $p_0$. In the \cfhtls, we might expect
 something like 100 lenses in 430,000 images, so $p_0 = 2\times10^{-4}$
@@
 
-The total information generated during the CFHTLS project is shown in
+The total information generated during the \cfhtls project is shown in
 \Tref{tab:crowd:contributions}. Interpreting these numbers is not easy, but we

### 2015-04-20 doc/sw-system.tex
British spellings

@@
 ``Talk''). Here, volunteers can discuss the features they have seen either
-before they submit their classification, or after, if they ``favorite'' the
+before they submit their classification, or after, if they ``favourite'' the
 subject. There is no ``back'' button: each volunteer may only classify a given
@@
 For training subjects, we also store the ``kind'' of the subject as
-a lens (``sim''), or a non-lens (``dud''), and also the ``flavor'' of lens
+a lens (``sim''), or a non-lens (``dud''), and also the ``flavour'' of lens
 object if one is present in the image (``lensed galaxy'', ``lensed quasar'' or

### 2015-04-20 doc/acknowledgments.tex
Add Sloan acknowledgement

@@
 The \sw project is open source.
-The web app was developed at \texttt{https://github.com/Zooniverse/Lens-Zoo}
+The web app was developed at \texttt{https://github.com/Zooniverse/Lens-Zoo}, and was supported by a grant from the Alfred P. Sloan Foundation, 
 while the SWAP analysis software was developed at

### 2015-04-20 doc/sw-system.tex
Added numeral I to system paper title, 'Gravitational' to CFHTLS paper title and adjusted short title. Closed #140
Abstract edits

@@
 classification interface which records their estimates of the positions of
-candidate lensed features. Simulated lenses, and expert-classified non-lenses,
+candidate lensed features. Simulated lenses, and expert-classified images which lack lenses,
 are inserted into the image stream at random intervals; this training set is

### 2015-04-20 doc/sw-system.tex
Section 1 edits

@@
 because they require expensive high resolution imaging follow-up; consequently
-they have so far produced yields in the tens to hundreds. An alternative
+they have so far produced yields of only tens to hundreds of lenses. An alternative
 approach is to search images already of sufficiently high resolution and colour
@@
 address the visual inspection problem in gravitational lens detection for future
-large surveys via crowd-sourcing. Implemented as a Zooniverse citizen science
+large surveys via crowd-sourcing. Implemented as a Zooniverse \citep{SimpsonEtal2014} citizen science
 project, it is designed to provide a {\it gravitational lens discovery service}

### 2015-04-20 doc/sw-system.tex
Section 2 edits

@@
 When the image is clicked on by the volunteer, a marker symbol appears where the
-pointer was. Several markers can be placed.
+pointer was. Several markers can be placed, and they can be removed by the user if, for example, they change their mind.
 
@@
 classification database, in an entry that also stores the ID of the subject, the
-username (or IP address) of the volunteer, a timestamp and some other metadata.
+username (or IP address if the user is not logged in) of the volunteer, a timestamp and some other metadata.
 

### 2015-04-20 doc/sw-system.tex
Working on Anu's comments, up to Section 3 #112

--- 2015-04-20 doc/sw-system.tex
@@
 \title[\SW]
-{\SW: Crowd-sourcing the Discovery of Gravitational Lenses}
+{\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses}
 
@@
 classification interface which records their estimates of the positions of
-candidate lensed features. Simulated lenses, and expert-classified images which lack lenses,
+candidate lensed features. Simulated lenses, and expert-classified non-lenses,
 are inserted into the image stream at random intervals; this training set is
@@
 ``Talk''). Here, volunteers can discuss the features they have seen either
-before they submit their classification, or after, if they ``favourite'' the
+before they submit their classification, or after, if they ``favorite'' the
 subject. There is no ``back'' button: each volunteer may only classify a given
@@
 When a volunteer begins classifying, they are initially shown training images at
-a frequency of two in five; these subjects are drawn at random from a pool
-containing equal numbers of sims and duds, such that that volunteer never sees a given image more than once. As the number of classifications made by a
-volunteer increases, this frequency is decreased, to
-$2/(5\times2^{(\textrm{int}(N_c/20)+1)/2})$ ($\approx 0.3$ for the second 20
-subjects, $0.2$ for the third 20 subjects, and so on).
+a mean frequency of two in five. Subjects are drawn at random from a pool
+consisting of (at first) 20\% sims, 20\% duds, and 60\% test images,
+and such that no volunteer ever
+sees a given image more than once. As the number of classifications made by the
+volunteer increases, the training frequency is decreased from 40\% to
+$2/(5\times2^{(\textrm{int}(N_c/20)+1)/2})$ ($\approx 30\%$ for the second 20
+subjects, $20\%$ for the third 20 subjects, and so on).
 
@@
 \subsubsection{Spotter's Guide}
+\label{sec:design:training:guide}
 
@@
 of us (AV, AM and PM) while inspecting a small set of survey images in order
-to define the ``dud'' training images. For easy reference, the lenses are
+to define the ``dud'' training images (\Sref{sec:design:stages}). For easy reference, the lenses are
 divided by type (for example, ``lensed galaxies,'' ``lensed quasars'' and
@@
 
-Most of the text of the Spotter's Guide focuses on what lenses do or don't do;
+Most of the text of the Spotter's Guide focuses on what kinds of image features
+gravitational lenses do or don't produce;
 the website ``Science page'' contains a very brief introduction to how
-gravitational lenses work, which is fleshed out a little on the ``FAQ'' page.
-This also contains answers to frequently asked questions about the interface
+gravitational lensing works, which is fleshed out a little on the ``FAQ'' page.
+The FAQ also contains answers to frequently asked questions about the interface
 and the task set.
@@
 The \StageOne training set was chosen to be quite clear cut, in order to err on
-the side of inclusivity, and so ensure high completeness. For the training duds
-we selected several hundred images at random, and three of us (AM, with AV and
-PM) inspected them and discarded anything that could be considered a lens
-candidate: this meant that objects that looks similar to lenses, such as galaxy
-mergers, tidal tails and spiral arms, pairs of blue stars and so on, were
-specifically excluded from the training set, and so we expect some of those
-types of object to appear in the \StageOne candidate list. The training sims for
-\StageOne were also selected to be relatively straightforward to spot, as we sought a balance between sensitivity to faint or difficult lenses, and the need to educate the volunteers in what gravitational lenses look like.
-We return to this balance below.
+the side of inclusivity, and so ensure high completeness. We selected the
+training duds by visual inspection, discarding anything that could be considered
+a lens candidate (see \Sref{sec:design:training:guide}): this meant that objects
+that look similar to lenses, such as galaxy mergers, tidal tails and spiral
+arms, pairs of blue stars and so on, were specifically excluded from the
+training set, and so we expect some of those types of object to appear in the
+\StageOne candidate list. The training sims for \StageOne were also selected to
+be relatively straightforward to spot, as we sought a balance between
+sensitivity to faint or difficult lenses, and the need to educate the volunteers
+in what gravitational lenses look like. We return to this balance below.
 
@@
 challenging training set as they re-classify it. The more demanding \StageTwo
-training set was generated as follows. The \StageTwo duds were selected from the
-image pool by at least one of three of us  (AV, AM and PM) as being a potential
-false positive, while the \StageTwo sims were chosen to be a subset of \StageOne
-sims, none of which were deemed ``obvious'' by the same expert classifiers.
-Figures~\ref{fig:training-gallery:sims} and~\ref{fig:training-gallery:duds}
-show some example images from the resulting \cfhtls \StageTwo training set.
+training set was generated as follows. The \StageTwo duds were again selected
+from the image pool by visual inspection as being a potential false positive,
+while the \StageTwo sims were chosen to be a subset of the \StageOne sims, none
+of which were deemed ``obvious'' by the same expert classifiers. This meant that
+the \StageTwo sims were had fainter and less well-separated image features than
+in the \StageOne training set.  Figures~\ref{fig:training-gallery:sims}
+and~\ref{fig:training-gallery:duds} show some example images from the resulting
+\cfhtls \StageTwo training set.
 
@@
 
-We also attempted to encourage discernment by changing the look and feel of
-the app, slowing down the arrival of new images, and switching the background
-colour to bright orange to make it clear that a different task was being set.
-The frequency with which training images were shown was fixed at 1 in 3.
-Finally, the Spotter's Guide was upgraded to include more examples
-of various possible false positives, divided into sub-classes.
+We also attempted to encourage discernment by changing the look and feel of the
+app, slowing down the arrival of new images, and switching the background colour
+to bright orange to make it clear that a different task was being set. The
+frequency with which training images were shown was fixed at 1 in 3. Finally,
+the Spotter's Guide was upgraded to include more examples of various possible
+false positives, divided into sub-classes. We did not retire any subjects during
+\StageTwo classification, instead continuing to accumulate classifications
+through till the end of a fixed 4-week time period.
 
@@
 For training subjects, we also store the ``kind'' of the subject as
-a lens (``sim''), or a non-lens (``dud''), and also the ``flavour'' of lens
+a lens (``sim''), or a non-lens (``dud''), and also the ``flavor'' of lens
 object if one is present in the image (``lensed galaxy'', ``lensed quasar'' or

### 2015-04-20 doc/sw-system.tex
Fixed #143

@@
 Each classification made is logged in a database, storing subject IDs,
-(anonymous) volunteer IDs, a timestamp and the classification results (the image
-pixel-coordinate positions of every marker placed).  The ``category'' of subject --
-whether it is a ``training'' subject (a simulated lens or a known non-lens) or a
-``test'' subject (an unseen image drawn from the survey) -- is also recorded.
-For training subjects, we also store the ``kind'' of the subject as
-a lens (``sim''), or a non-lens (``dud''), and also the ``flavor'' of lens
-object if one is present in the image (``lensed galaxy'', ``lensed quasar'' or
-``cluster lens'').  This classification is used to provide instant feedback, but
-is also the basic measurement used in a probabilistic classification of every
-subject based on all image views to date.
+(anonymous) volunteer IDs (their Zooniverse usernames), a timestamp and the
+classification results (the image pixel-coordinate positions of every marker
+placed).  The ``category'' of subject -- whether it is a ``training'' subject (a
+simulated lens or a known non-lens) or a ``test'' subject (an unseen image drawn
+from the survey) -- is also recorded. For training subjects, we also store the
+``kind'' of the subject as a lens (``sim''), or a non-lens (``dud''), and also
+the ``flavor'' of lens object if one is present in the image (``lensed galaxy'',
+``lensed quasar'' or ``cluster lens'').  This classification is used to provide
+instant feedback, but is also the basic measurement used in a probabilistic
+classification of every subject based on all image views to date.  Not all
+volunteers register with the Zooniverse (although all are prompted to do so);
+in these cases we record their IP addresses as substitute IDs.
 

### 2015-04-20 doc/sw-system.tex
Fixed #145 (multiple instances of how duds were selected)

@@
 Because we include a training set of images in amongst the survey ``test''
-images, \sw can be viewed as a {\it supervised learning} system.
-Consequently, we should expect to find lens candidates that look like the sims
-that we put in the training set, and so the design of this training set is
-quite important. The training images must look realistic, in two ways. First,
-apart from the simulated lenses they contain, they must look like all the
-other survey images -- otherwise they could be identified as training images
-without the volunteer learning anything about what lenses look like. For this
-reason, we make the sims by {\it adding in} simulated lensed features to real
-images drawn from the survey. It also means that each dataset presented for
-inspection in the \sw interface needs to come with its own training set.
+images, \sw can be viewed as a {\it supervised learning} system. Consequently,
+we should expect to find lens candidates that look like the sims that we put in
+the training set, and so the design of this training set is quite important. The
+training images must look realistic, in two ways. First, apart from the
+simulated lenses they contain, they must look like all the other survey images --
+otherwise they could be identified as training images without the volunteer
+learning anything about what lenses look like. For this reason, we make the sims
+by {\it adding in} simulated lensed features to real images drawn from the
+survey, and we make the duds by simply inspecting and choosing from a small
+sample of randomly-selected survey images. It also means that each dataset
+presented for inspection in the \sw interface needs to come with its own
+training set.
 
@@
 
-The instant feedback provides real-time educational responses to the
-volunteers as they start classifying; as well as this dynamic system, \SW
-provides a static reference work for volunteers to consult when in doubt about
-how to perform the task. This ``Spotter's Guide'' is a set of webpages showing
-example lenses, both real and simulated, and also some common false positives,
-drawn from the pool of survey images. The non-lenses were identified by three
-of us (AV, AM and PM) while inspecting a small set of survey images in order
-to define the ``dud'' training images (\Sref{sec:design:stages}). For easy reference, the lenses are
+The instant feedback provides real-time educational responses to the volunteers
+as they start classifying; as well as this dynamic system, \SW provides a static
+reference work for volunteers to consult when in doubt about how to perform the
+task. This ``Spotter's Guide'' is a set of webpages showing example lenses, both
+real and simulated, and also some common false positives, drawn from the pool of
+survey images. The false positives were identified during the selction of the
+``dud'' training images (previous section). For easy reference, the lenses are
 divided by type (for example, ``lensed galaxies,'' ``lensed quasars'' and
@@
 Spirals,'' ``Mergers,'' ``Artifacts'' and so on). The example images are
-accompanied by explanatory text. The Spotter's Guide is reached via a button
-on the left hand side, or the hyperlinked thumbnail images of the ``Quick
+accompanied by explanatory text. The Spotter's Guide is reached via a button on
+the left hand side, or the hyperlinked thumbnail images of the ``Quick
 Reference'' provided on the right hand side, of the classification interface.
@@
 The \StageOne training set was chosen to be quite clear cut, in order to err on
-the side of inclusivity, and so ensure high completeness. We selected the
-training duds by visual inspection, discarding anything that could be considered
-a lens candidate (see \Sref{sec:design:training:guide}): this meant that objects
-that look similar to lenses, such as galaxy mergers, tidal tails and spiral
-arms, pairs of blue stars and so on, were specifically excluded from the
-training set, and so we expect some of those types of object to appear in the
-\StageOne candidate list. The training sims for \StageOne were also selected to
-be relatively straightforward to spot, as we sought a balance between
-sensitivity to faint or difficult lenses, and the need to educate the volunteers
-in what gravitational lenses look like. We return to this balance below.
+the side of inclusivity, and so ensure high completeness. When defining the
+training duds we discarded anything that could be considered a lens candidate
+(see \Sref{sec:design:training:guide}): this meant that objects that look
+similar to lenses, such as galaxy mergers, tidal tails and spiral arms, pairs of
+blue stars and so on, were specifically excluded from the training set, and
+therefore we expect some of those types of object to appear in the \StageOne
+candidate list. The training sims for \StageOne were also selected to be
+relatively straightforward to spot, as we sought a balance between sensitivity
+to faint or difficult lenses, and the need to educate the volunteers in what
+gravitational lenses look like. We return to this balance below.
 
@@
 challenging training set as they re-classify it. The more demanding \StageTwo
-training set was generated as follows. The \StageTwo duds were again selected
-from the image pool by visual inspection as being a potential false positive,
-while the \StageTwo sims were chosen to be a subset of the \StageOne sims, none
-of which were deemed ``obvious'' by the same expert classifiers. This meant that
-the \StageTwo sims were had fainter and less well-separated image features than
-in the \StageOne training set.  Figures~\ref{fig:training-gallery:sims}
+training set was generated as follows. \new{The \StageTwo duds were selected
+from a small random subset of the \StageOne candidates (i.e., the \StageTwo duds
+were expert-defined \StageOne false positive detections),} while the \StageTwo
+sims were chosen to be a subset of the \StageOne sims, none of which were deemed
+``obvious'' by the same expert classifiers. This meant that the \StageTwo sims
+had fainter and less well-separated image features than in the \StageOne
+training set.  Figures~\ref{fig:training-gallery:sims}
 and~\ref{fig:training-gallery:duds} show some example images from the resulting

### 2015-04-20 doc/sw-system.tex
Working on Anu's comments, up to Section 4 #112

@@
 Canada-France-Hawaii Telescope Legacy Survey (\cfhtls)
-imaging survey into some 430,000 overlapping 80 by 80 arcsecond tiles and
+imaging survey into some 430,000 overlapping 84 by 84 arcsecond tiles and
 displayed them on the site, we were joined by around 37,000 volunteers who
@@
 variation of the colour balance and contrast (stretch), and for any given view
-to be shared via unique URL back to Talk. The FITS image viewing in both the
+to be shared via unique URL back to \Talk. The FITS image viewing in both the
 Quick Dashboard and the Dashboard Tools are enabled by the javascript library
@@
 boxes. Subsequent images gradually introduce the more advanced features of the
-classification interface (the QD and Talk buttons), also using pop-up
+classification interface (the QD and \Talk buttons), also using pop-up
 messages. The tutorial was purposely kept as short as possible so as to
@@
 challenging training set as they re-classify it. The more demanding \StageTwo
-training set was generated as follows. \new{The \StageTwo duds were selected
+training set was generated as follows. The \StageTwo duds were selected
 from a small random subset of the \StageOne candidates (i.e., the \StageTwo duds
-were expert-defined \StageOne false positive detections),} while the \StageTwo
+were expert-defined \StageOne false positive detections), while the \StageTwo
 sims were chosen to be a subset of the \StageOne sims, none of which were deemed
@@
 
-The CFHT Legacy Survey\footnote{\texttt{http://www.cfht.hawaii.edu/Science/CFHTLS/}}
-\citep[\cfhtls,][]{Gwyn2012} covered 171 square degrees of
-approximately equatorial sky, in four patches distributed in right ascension.
+The four CFHT Legacy Survey\footnote{\texttt{http://www.cfht.hawaii.edu/Science/CFHTLS/}}
+\citep[\cfhtls,][]{Gwyn2012} ``Wide'' fields cover a total of
+171 square degrees of sky.
 With high and homogeneous image quality (the mean seeing in the $g$-band is
@@
 mosaiced images into some 430,000 equal size, overlapping tiles, approximately
-80~arcsec on a side. We refer to these images as ``test images'' (as opposed to
-``training images''). In future, larger area projects we expect to implement the
-rather different strategy of producing image tiles centred on particular
-pre-selected ``targets,'' to make for a more efficient (but less complete)
-survey. We do not expect the performance of citizen image inspectors to change
+84~arcsec on a side. We refer to these images as ``test images.'' The ``training
+images'' were derived from a small subset of these, as  discussed above. In
+future, larger area, projects we expect to implement the somewhat different
+strategy of producing image tiles centred on particular pre-selected
+``targets,'' which might make for a more efficient (if less complete) survey.
+However, we do not expect the performance of citizen image inspectors to change
 significantly between these strategies: to first order, both strategies require
@@
 
-The \cfhtls $g$, $r$ and $i$-band images have the greatest depth and best image
-quality, and we chose to focus on this set (although the $u$ and $z$-band images
-were also available for perusal in Talk). We made colour composite PNG
+The \cfhtls $g$, $r$ and $i$-band images have the greatest average
+depth and highest average image
+quality of the survey,
+and we chose to focus on this subset. (The remaining $u$ and $z$-band images
+were also made available for perusal in \Talk). We made colour composite PNG
 format images following the prescription of \citet{LuptonEtal2004} \citep[with
@@
 as just described, but dynamically on FITS images in the browser. These FITS
-images are also available for viewing in Talk, via the main Zooniverse
+images are also available for viewing in \Talk, via the main Zooniverse
 Dashboard image display tool, which again offers the same stretch settings, as
@@
 reduction, we might worry about such a mechanism enabling classifiers to have
-a guess, then go and read the Talk discussion, and then return to the
+a guess, then go and read the \Talk discussion, and then return to the
 classification interface to change their mind to agree with the forum. In
@@
 multi-lingual user base would come with its own set of challenges, especially
-in terms of volunteers' continuing training and interactions on Talk.
+in terms of volunteers' continuing training and interactions on \Talk.
 

### 2015-04-20 doc/sw-system.tex
Section 5 edits, including adding subtative sentence

--- 2015-04-20 doc/sw-system.tex
@@
 \title[\SW]
-{\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses}
+{\SW: Crowd-sourcing the Discovery of Gravitational Lenses}
 
@@
 When a volunteer begins classifying, they are initially shown training images at
-a mean frequency of two in five. Subjects are drawn at random from a pool
-consisting of (at first) 20\% sims, 20\% duds, and 60\% test images,
-and such that no volunteer ever
-sees a given image more than once. As the number of classifications made by the
-volunteer increases, the training frequency is decreased from 40\% to
-$2/(5\times2^{(\textrm{int}(N_c/20)+1)/2})$ ($\approx 30\%$ for the second 20
-subjects, $20\%$ for the third 20 subjects, and so on).
+a frequency of two in five; these subjects are drawn at random from a pool
+containing equal numbers of sims and duds, such that that volunteer never sees a given image more than once. As the number of classifications made by a
+volunteer increases, this frequency is decreased, to
+$2/(5\times2^{(\textrm{int}(N_c/20)+1)/2})$ ($\approx 0.3$ for the second 20
+subjects, $0.2$ for the third 20 subjects, and so on).
 
@@
 \subsubsection{Spotter's Guide}
-\label{sec:design:training:guide}
 
@@
 of us (AV, AM and PM) while inspecting a small set of survey images in order
-to define the ``dud'' training images (\Sref{sec:design:stages}). For easy reference, the lenses are
+to define the ``dud'' training images. For easy reference, the lenses are
 divided by type (for example, ``lensed galaxies,'' ``lensed quasars'' and
@@
 
-Most of the text of the Spotter's Guide focuses on what kinds of image features
-gravitational lenses do or don't produce;
+Most of the text of the Spotter's Guide focuses on what lenses do or don't do;
 the website ``Science page'' contains a very brief introduction to how
-gravitational lensing works, which is fleshed out a little on the ``FAQ'' page.
-The FAQ also contains answers to frequently asked questions about the interface
+gravitational lenses work, which is fleshed out a little on the ``FAQ'' page.
+This also contains answers to frequently asked questions about the interface
 and the task set.
@@
 The \StageOne training set was chosen to be quite clear cut, in order to err on
-the side of inclusivity, and so ensure high completeness. We selected the
-training duds by visual inspection, discarding anything that could be considered
-a lens candidate (see \Sref{sec:design:training:guide}): this meant that objects
-that look similar to lenses, such as galaxy mergers, tidal tails and spiral
-arms, pairs of blue stars and so on, were specifically excluded from the
-training set, and so we expect some of those types of object to appear in the
-\StageOne candidate list. The training sims for \StageOne were also selected to
-be relatively straightforward to spot, as we sought a balance between
-sensitivity to faint or difficult lenses, and the need to educate the volunteers
-in what gravitational lenses look like. We return to this balance below.
+the side of inclusivity, and so ensure high completeness. For the training duds
+we selected several hundred images at random, and three of us (AM, with AV and
+PM) inspected them and discarded anything that could be considered a lens
+candidate: this meant that objects that looks similar to lenses, such as galaxy
+mergers, tidal tails and spiral arms, pairs of blue stars and so on, were
+specifically excluded from the training set, and so we expect some of those
+types of object to appear in the \StageOne candidate list. The training sims for
+\StageOne were also selected to be relatively straightforward to spot, as we sought a balance between sensitivity to faint or difficult lenses, and the need to educate the volunteers in what gravitational lenses look like.
+We return to this balance below.
 
@@
 challenging training set as they re-classify it. The more demanding \StageTwo
-training set was generated as follows. The \StageTwo duds were again selected
-from the image pool by visual inspection as being a potential false positive,
-while the \StageTwo sims were chosen to be a subset of the \StageOne sims, none
-of which were deemed ``obvious'' by the same expert classifiers. This meant that
-the \StageTwo sims were had fainter and less well-separated image features than
-in the \StageOne training set.  Figures~\ref{fig:training-gallery:sims}
-and~\ref{fig:training-gallery:duds} show some example images from the resulting
-\cfhtls \StageTwo training set.
+training set was generated as follows. The \StageTwo duds were selected from the
+image pool by at least one of three of us  (AV, AM and PM) as being a potential
+false positive, while the \StageTwo sims were chosen to be a subset of \StageOne
+sims, none of which were deemed ``obvious'' by the same expert classifiers.
+Figures~\ref{fig:training-gallery:sims} and~\ref{fig:training-gallery:duds}
+show some example images from the resulting \cfhtls \StageTwo training set.
 
@@
 
-We also attempted to encourage discernment by changing the look and feel of the
-app, slowing down the arrival of new images, and switching the background colour
-to bright orange to make it clear that a different task was being set. The
-frequency with which training images were shown was fixed at 1 in 3. Finally,
-the Spotter's Guide was upgraded to include more examples of various possible
-false positives, divided into sub-classes. We did not retire any subjects during
-\StageTwo classification, instead continuing to accumulate classifications
-through till the end of a fixed 4-week time period.
+We also attempted to encourage discernment by changing the look and feel of
+the app, slowing down the arrival of new images, and switching the background
+colour to bright orange to make it clear that a different task was being set.
+The frequency with which training images were shown was fixed at 1 in 3.
+Finally, the Spotter's Guide was upgraded to include more examples
+of various possible false positives, divided into sub-classes.
 
@@
 Each classification made is logged in a database, storing subject IDs,
-(anonymous) volunteer IDs (their Zooniverse usernames), a timestamp and the
-classification results (the image pixel-coordinate positions of every marker
-placed).  The ``category'' of subject -- whether it is a ``training'' subject (a
-simulated lens or a known non-lens) or a ``test'' subject (an unseen image drawn
-from the survey) -- is also recorded. For training subjects, we also store the
-``kind'' of the subject as a lens (``sim''), or a non-lens (``dud''), and also
-the ``flavor'' of lens object if one is present in the image (``lensed galaxy'',
-``lensed quasar'' or ``cluster lens'').  This classification is used to provide
-instant feedback, but is also the basic measurement used in a probabilistic
-classification of every subject based on all image views to date.  Not all
-volunteers register with the Zooniverse (although all are prompted to do so);
-in these cases we record their IP addresses as substitute IDs.
+(anonymous) volunteer IDs, a timestamp and the classification results (the image
+pixel-coordinate positions of every marker placed).  The ``category'' of subject --
+whether it is a ``training'' subject (a simulated lens or a known non-lens) or a
+``test'' subject (an unseen image drawn from the survey) -- is also recorded.
+For training subjects, we also store the ``kind'' of the subject as
+a lens (``sim''), or a non-lens (``dud''), and also the ``flavour'' of lens
+object if one is present in the image (``lensed galaxy'', ``lensed quasar'' or
+``cluster lens'').  This classification is used to provide instant feedback, but
+is also the basic measurement used in a probabilistic classification of every
+subject based on all image views to date.
 
@@
 more discussion of this quantity). The classifications of training images
-determine the skill, while the classification of test images determines
+allow us to estimate the skill, while the classification of test images determines
 contribution.  In \StageOne, the mean  contribution per agent was
@@
 contributions these volunteers make (third row) and the information they
-generate (fourth row).
+generate (fourth row), and we suggest that this would be a useful metric for determining 'well-designed' implementations of citizen science projects.
 

### 2015-04-20 doc/sw-system.tex
Section 6 comments including substantive sentence

@@
 In some cases the rejection of the false negatives is understandable: the
-lensed features are faint, or in some cases, somewhat unrealistic as lenses.
+lensed features are faint, or in some cases, appear somewhat unrealistic compared to real lenses.
 However, in other cases a reasonably obvious lens was passed over.  This
@@
 random walk down its trajectory plot. This can be seen in the top left panel
-of the figure.
+of Figure \Fref{fig:discuss:performance:trajectories}.
 
@@
 not obvious that such correlations would necessarily lead to poorer system
-performance. This could be tested by presenting a fraction of the volunteers
+performance.
+There may well also be effects on user confidence; it may be that encouraging this sort of checking would result in increased and not necessarily productive caution.
+This could be tested by presenting a fraction of the volunteers
 with a version of the site that actively suggested that they take this

### 2015-04-20 doc/sw-system.tex
Add to section on going beyond training, closes #144

@@
 educational value of the sims when feedback was given, it meant that we should
-only expect to detect real lens candidates that also pass these cuts. Any real
+only expect to detect real lens candidates that also pass these cuts.
+Indeed, for traditional machine learning or computer vision implementations then this would be a constraint, but human classifiers are capable of going beyond their training; Geach et al., for example (REF????) report the discovery of a red lens by volunteers who had only been trained on blue examples.
+This ability to go beyond training is a key advantage of human classifiers, and
+any real
 lens candidates we ﬁnd with properties outside the ranges of the sims, may in
-some sense be considered bonuses, a product of the {\it imagination} of the
+this sense be considered bonuses, a product of the {\it imagination} of the
 crowd in extrapolating their understanding of gravitational lenses into a regime

### 2015-04-20 doc/acknowledgments.tex
Fixed fuzziness of crowd plots by switching to PDF format. #127

--- 2015-04-19 doc/acknowledgments.tex
@@
-We thank all \Ncollaboration members of the \sw community for their
-contributions to the project so far. A complete list of collaborators is
-provided at \texttt{http://spacewarps.org/\#/results/CFHTLS}.
+We thank all 36,982 members of the \sw community for their
+contributions to the project so far. A complete list of registered
+collaborators is provided at \texttt{http://spacewarps.org/\#/results/CFHTLS}.
 

### 2015-04-20 doc/sw-system.tex
Fixed fuzziness of crowd plots by switching to PDF format. #127

--- 2015-04-20 doc/sw-system.tex
@@
 because they require expensive high resolution imaging follow-up; consequently
-they have so far produced yields of only tens to hundreds of lenses. An alternative
+they have so far produced yields in the tens to hundreds. An alternative
 approach is to search images already of sufficiently high resolution and colour
@@
 address the visual inspection problem in gravitational lens detection for future
-large surveys via crowd-sourcing. Implemented as a Zooniverse \citep{SimpsonEtal2014} citizen science
+large surveys via crowd-sourcing. Implemented as a Zooniverse citizen science
 project, it is designed to provide a {\it gravitational lens discovery service}
@@
 When the image is clicked on by the volunteer, a marker symbol appears where the
-pointer was. Several markers can be placed, and they can be removed by the user if, for example, they change their mind.
+pointer was. Several markers can be placed.
 
@@
 classification database, in an entry that also stores the ID of the subject, the
-username (or IP address if the user is not logged in) of the volunteer, a timestamp and some other metadata.
+username (or IP address) of the volunteer, a timestamp and some other metadata.
 
@@
 \subsubsection{Spotter's Guide}
-
-The instant feedback provides real-time educational responses to the
-volunteers as they start classifying; as well as this dynamic system, \SW
-provides a static reference work for volunteers to consult when in doubt about
-how to perform the task. This ``Spotter's Guide'' is a set of webpages showing
-example lenses, both real and simulated, and also some common false positives,
-drawn from the pool of survey images. The non-lenses were identified by three
-of us (AV, AM and PM) while inspecting a small set of survey images in order
-to define the ``dud'' training images. For easy reference, the lenses are
+\label{sec:design:training:guide}
+
+The instant feedback provides real-time educational responses to the volunteers
+as they start classifying; as well as this dynamic system, \SW provides a static
+reference work for volunteers to consult when in doubt about how to perform the
+task. This ``Spotter's Guide'' is a set of webpages showing example lenses, both
+real and simulated, and also some common false positives, drawn from the pool of
+survey images. The false positives were identified during the selction of the
+``dud'' training images (previous section). For easy reference, the lenses are
 divided by type (for example, ``lensed galaxies,'' ``lensed quasars'' and
@@
 Spirals,'' ``Mergers,'' ``Artifacts'' and so on). The example images are
-accompanied by explanatory text. The Spotter's Guide is reached via a button
-on the left hand side, or the hyperlinked thumbnail images of the ``Quick
+accompanied by explanatory text. The Spotter's Guide is reached via a button on
+the left hand side, or the hyperlinked thumbnail images of the ``Quick
 Reference'' provided on the right hand side, of the classification interface.
 
-Most of the text of the Spotter's Guide focuses on what lenses do or don't do;
+Most of the text of the Spotter's Guide focuses on what kinds of image features
+gravitational lenses do or don't produce;
 the website ``Science page'' contains a very brief introduction to how
-gravitational lenses work, which is fleshed out a little on the ``FAQ'' page.
-This also contains answers to frequently asked questions about the interface
+gravitational lensing works, which is fleshed out a little on the ``FAQ'' page.
+The FAQ also contains answers to frequently asked questions about the interface
 and the task set.
@@
 The \StageOne training set was chosen to be quite clear cut, in order to err on
-the side of inclusivity, and so ensure high completeness. For the training duds
-we selected several hundred images at random, and three of us (AM, with AV and
-PM) inspected them and discarded anything that could be considered a lens
-candidate: this meant that objects that looks similar to lenses, such as galaxy
-mergers, tidal tails and spiral arms, pairs of blue stars and so on, were
-specifically excluded from the training set, and so we expect some of those
-types of object to appear in the \StageOne candidate list. The training sims for
-\StageOne were also selected to be relatively straightforward to spot, as we sought a balance between sensitivity to faint or difficult lenses, and the need to educate the volunteers in what gravitational lenses look like.
-We return to this balance below.
+the side of inclusivity, and so ensure high completeness. When defining the
+training duds we discarded anything that could be considered a lens candidate
+(see \Sref{sec:design:training:guide}): this meant that objects that look
+similar to lenses, such as galaxy mergers, tidal tails and spiral arms, pairs of
+blue stars and so on, were specifically excluded from the training set, and
+therefore we expect some of those types of object to appear in the \StageOne
+candidate list. The training sims for \StageOne were also selected to be
+relatively straightforward to spot, as we sought a balance between sensitivity
+to faint or difficult lenses, and the need to educate the volunteers in what
+gravitational lenses look like. We return to this balance below.
 
@@
 challenging training set as they re-classify it. The more demanding \StageTwo
-training set was generated as follows. The \StageTwo duds were selected from the
-image pool by at least one of three of us  (AV, AM and PM) as being a potential
-false positive, while the \StageTwo sims were chosen to be a subset of \StageOne
-sims, none of which were deemed ``obvious'' by the same expert classifiers.
-Figures~\ref{fig:training-gallery:sims} and~\ref{fig:training-gallery:duds}
-show some example images from the resulting \cfhtls \StageTwo training set.
+training set was generated as follows. The \StageTwo duds were selected
+from a small random subset of the \StageOne candidates (i.e., the \StageTwo duds
+were expert-defined \StageOne false positive detections), while the \StageTwo
+sims were chosen to be a subset of the \StageOne sims, none of which were deemed
+``obvious'' by the same expert classifiers. This meant that the \StageTwo sims
+had fainter and less well-separated image features than in the \StageOne
+training set.  Figures~\ref{fig:training-gallery:sims}
+and~\ref{fig:training-gallery:duds} show some example images from the resulting
+\cfhtls \StageTwo training set.
 
@@
 Each classification made is logged in a database, storing subject IDs,
-(anonymous) volunteer IDs, a timestamp and the classification results (the image
-pixel-coordinate positions of every marker placed).  The ``category'' of subject --
-whether it is a ``training'' subject (a simulated lens or a known non-lens) or a
-``test'' subject (an unseen image drawn from the survey) -- is also recorded.
-For training subjects, we also store the ``kind'' of the subject as
-a lens (``sim''), or a non-lens (``dud''), and also the ``flavour'' of lens
-object if one is present in the image (``lensed galaxy'', ``lensed quasar'' or
-``cluster lens'').  This classification is used to provide instant feedback, but
-is also the basic measurement used in a probabilistic classification of every
-subject based on all image views to date.
+(anonymous) volunteer IDs (their Zooniverse usernames), a timestamp and the
+classification results (the image pixel-coordinate positions of every marker
+placed).  The ``category'' of subject -- whether it is a ``training'' subject (a
+simulated lens or a known non-lens) or a ``test'' subject (an unseen image drawn
+from the survey) -- is also recorded. For training subjects, we also store the
+``kind'' of the subject as a lens (``sim''), or a non-lens (``dud''), and also
+the ``flavor'' of lens object if one is present in the image (``lensed galaxy'',
+``lensed quasar'' or ``cluster lens'').  This classification is used to provide
+instant feedback, but is also the basic measurement used in a probabilistic
+classification of every subject based on all image views to date.  Not all
+volunteers register with the Zooniverse (although all are prompted to do so);
+in these cases we record their IP addresses as substitute IDs.
 
@@
 \item Each volunteer is assigned a simple software agent, characterised by a
-confusion matrix. The two independent elements of this matrix are the
+confusion matrix~$\CM$. The two independent elements of this matrix are the
 probabilities, as estimated by the agent, that the volunteer is going to be 1)
 correct when they report that an image contains a lens when it really does
-contain a lens, $\pr(\saidLENS|\LENS,T)$, and 2) correct when they report that
+contain a lens, $\PL = \pr(\saidLENS|\LENS,T)$, and 2) correct when they report that
 an image does not contain a lens when it really doesn't contain a lens,
-$\pr(\saidNOT|\LENS,T)$.
+$\PD = \pr(\saidNOT|\NOT,T)$.
 
@@
 duds) while classifying subjects from the training set, accounting for noise
-early on due to small number statistics: $T$ is the set of all training images
+early on due to small number statistics: $T$~is the set of all training images
 seen to date.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_histories.png}
-\caption{Typical \SW agent histories. The ``skill'' of the  same 200 random
-agents  as in \Fref{fig:swap:agent-probabilities} is plotted in green as a function
-of the number  of subjects classified (``effort''). The yellow histogram in
-the background shows the distribution of effort.}
-\label{fig:swap:agent-histories}
-\end{figure}
+%\begin{figure}
+%\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_histories.png}
+%\caption{Typical \SW agent histories. The ``skill'' of the  same 200 random
+%agents  as in \Fref{fig:swap:agent-probabilities} is plotted in green as a function
+%of the number  of subjects classified (``effort''). The yellow histogram in
+%the background shows the distribution of effort.}
+%\label{fig:swap:agent-histories}
+%\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 of (0.5,0.5). As more images are classified (shown by the yellow point size),
-the agents' matrix elements tend to move towards higher values, as the
+the agents' matrix elements tend to move towards higher values, partly as the
 volunteers attain greater skill levels (green point sizes, see
-\Sref{sec:results} below) and the agent learns more about them. In this
-quadrant, the agents perceive their volunteers to be ``astute.'' This trend is
-more clearly seen in \Fref{fig:swap:agent-histories}, which shows the skill of
-the same sample of agents as the number of images classified increases. The
-histogram shows the distribution of classification number: a long tail to very
-high ``effort'' can be seen.
+\Sref{sec:results} below) but mostly as
+the agent learns more about them. In this upper
+right-hand quadrant, the agents perceive their volunteers to be ``astute.''
+
+%\Fref{fig:swap:agent-histories} shows the ``skill'' (\Sref{sec:results:crowd})
+%of the same small sample of agents evolving as their volunteers classify images.
+%The underlying histogram shows the distribution of classification number: a long
+%tail to very high ``effort'' can be seen.
 
@@
 \centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_trajectories.png}
-\caption{Typical \SW \StageOne subject trajectories. Subjects drift downwards in
-the top panel as they are classified, while being nudged left and right by the
-agents as they interpret the volunteers input. The dotted vertical lines show
-(left to right) the retirement threshold, prior probability, and the detection
-threshold.}
+\caption{Typical \SW \StageOne subject trajectories. Top: 200 randomly-selected
+subjects drift downwards as they are classified, while being nudged left and
+right in probability by the agents as they interpret the volunteers input. The
+dotted vertical lines show (left to right) the retirement threshold, prior
+probability, and the detection threshold. Different colours denote the different
+kinds of subject. Bottom panel: histograms of all the subject probabilities
+computed to date, sub-divided by subject kind.}
 \label{fig:swap:subject-trajectories}
@@
 retirement and subsequently ignored by the analysis code. Subjects crossing the
-detection threshold were not retired from the website, but instead left in the
-system so that more volunteers could see them (and continue to update their
-probabilities). The progress of the subjects is illustrated in
+detection threshold were also subsequently ignore, but they were not
+retired from the website, just so that more volunteers could see them.
+The progress of the subjects is illustrated in
 \Fref{fig:swap:subject-trajectories}. Subjects appear on this plot at the tip of
@@
 \begin{figure*}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/all_skill_contribution_experience_education.png}
-\caption{Key properties and contributions of the \SW crowd. Plotted are the 1-D
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/all_skill_contribution_experience_education.pdf}
+\caption{Key properties and contributions of the \SW \StageOne crowd.
+Plotted are the 1-D
 and 2-D smoothed marginalized distributions for  the logarithms of the
-properties of the agents described in the text. The  \StageOne agents are shown
-in blue, the \StageTwo agents in orange: the  smoothing scale for the \StageTwo
-curves was set slightly higher to counter the  higher shot noise. The contours
+properties of the agents described in the text. The contours
 contain 68\%, 95\% and 99\% of the distributions.}
@@
 \item{\noindent\bf ``Skill:''} The expectation value of the information gained
-per classification (in bits) by that volunteer,  $\skill$ for subjects which
+per classification (in bits) by that volunteer,  $\skill$, for subjects which
 have lens probability 0.5 (\Aref{appendix:swap}). Random classifiers have
-$\skill = 0.0$, while perfect classifiers have $\skill = 1.0$. All agents start
-with $\skill = 0.0$. The skill of  an agent increases as training subjects are
+$\skill = 0.0$~bits, while perfect classifiers have $\skill = 1.0$~bit.
+All agents start
+with $\skill = 0.0$~bits. The skill of  an agent increases as training subjects are
 classified, and the agent's estimates of its confusion matrix elements improve.
-In \StageOne, the mean skill per agent was 0.04 bits; in  \StageTwo it was 0.05.
+In \StageOne, the mean skill per agent was 0.04 bits; in  \StageTwo it was
+0.05~bits.
 %
@@
 more discussion of this quantity). The classifications of training images
-allow us to estimate the skill, while the classification of test images determines
+determine the skill, while the classification of test images determines
 contribution.  In \StageOne, the mean  contribution per agent was
@@
 contributions these volunteers make (third row) and the information they
-generate (fourth row), and we suggest that this would be a useful metric for determining 'well-designed' implementations of citizen science projects.
+generate (fourth row).
 
@@
 \begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_contrib_cumul.png}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_contrib_cumul.pdf}
 \caption{Cumulative distributions of the contributions made by the agents: 90\%
@@
 \begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_skill_cumul.png}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_skill_cumul.pdf}
 \caption{Broad cumulative distributions of agent skill:
@@
 \begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/stage2_veteran_contribution.png}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/stage2_veteran_contribution.pdf}
 \caption{\StageTwo classifier skill, as a function of their \StageOne skill.
 Veterans from \StageOne  are shown in blue, while new volunteers are shown in
-orange. Point size is proportional to the number of \StageTwo classifications
-made, while dashed lines are drawn at the mean values for each sample.
-Restricting \StageTwo to classifiers with high \StageOne skill could reduce the
-noise in the system.}
+orange. Point size is proportional to the total contribution made,
+while dashed lines are drawn at the mean values for each sample.}
 \label{fig:discuss:performance:stage1vstage2}

### 2015-04-20 analysis/make_crowd_plots.py

@@ -36,8 +36,8 @@ def make_crowd_plots(argv):
         make_crowd_plots
 
     PURPOSE
-        Given stage1 and stage2 bureau pickles, this script produces the 
-        4 plots currently planned for the crowd section of the SW system 
+        Given stage1 and stage2 bureau pickles, this script produces the
+        4 plots currently planned for the crowd section of the SW system
         paper.
 
     COMMENTS
@@ -127,7 +127,7 @@ def make_crowd_plots(argv):
     effort = []
     information = []
     early_skill = []
-    
+
     final_skill_all = []
     contribution_all = []
     experience_all = []
@@ -175,16 +175,16 @@ def make_crowd_plots(argv):
     experience2 = []
     effort2 = []
     information2 = []
-    
+
     # stage 1 skill of stage 2 classifiers:
     final_skill1 = []
-    
+
     final_skill_all2 = []
     contribution_all2 = []
     experience_all2 = []
     effort_all2 = []
     information_all2 = []
-    
+
     new_s2_contribution = []
     new_s2_skill = []
     new_s2_effort = []
@@ -214,7 +214,7 @@ def make_crowd_plots(argv):
 
         oldagent = bureau1.member[ID]
         final_skill1.append(oldagent.traininghistory['Skill'][-1])
-        
+
 
     experience2 = np.array(experience2)
     effort2 = np.array(effort2)
@@ -241,10 +241,10 @@ def make_crowd_plots(argv):
     # ------------------------------------------------------------------
 
     # Plot 1.1 and 1.2: cumulative distributions of contribution and skill
-    
+
     # 1.1 Contribution
-    
-    plt.figure(figsize=(10,8))
+
+    plt.figure(figsize=(10,8),dpi=300)
 
     # All Stage 1 volunteers:
     cumulativecontribution1_all = np.cumsum(np.sort(contribution_all)[::-1])
@@ -291,14 +291,15 @@ def make_crowd_plots(argv):
     plt.xlim(0.0, 0.21)
     plt.ylim(0.0, 1.0)
     plt.legend(loc='lower right')
-    pngfile = output_directory+'crowd_contrib_cumul.png'
+    # pngfile = output_directory+'crowd_contrib_cumul.png'
[…]

### 2015-04-20 doc/sw-system.tex
Explained new crowd corner plot: stage one only, for clarity.

@@
 To investigate the properties of the \sw crowd, as characterised by their
-agents, we define the following quantities and plot their distributions in
-\Fref{fig:crowd:cornerplot}.
+agents, we define the following quantities and plot their one and 2-D marginal
+distributions in
+\Fref{fig:crowd:cornerplot}. This figure only shows the \StageOne agents for clarity,
+but the trends we found the same trends in \StageTwo.
 %
@@
 a similar blind search strategy). For example, the completion time for a \SW
-project could be approximated as
+project may be approximated as
 \begin{equation}
@@
                                \left(\frac{N_s}{10^4}\right),
+\label{eq:speed}
 \end{equation}
@@
 the \StageTwo classification round, only 774 were veterans from \StageOne.
+
 \Fref{fig:discuss:performance:stage1vstage2} shows how the \StageOne skill maps
 on to \StageTwo skill and contribution.
-
 This figure suggests that there may be some benefit to opening \StageTwo on the
@@
 
+If the system efficiency could be improved by a factor of three, we would
+expect the coefficient in \Eref{eq:speed} to decrease by roughly the same factor,
+suggesting that an dataset of $10^4$~images could be searched for lenses by a
+crowd of $10^4$ volunteers in about 6 days.
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 
-Finally, we comment on the size of the first \SW crowd, and how the system
-might be scaled up for future surveys. In \Sref{sec:results:crowd} and
-\Tref{tab:crowd:contributions}, the following rough picture emerged for the
-\SW crowd in this project:
-it consisted of a few $10^4$ volunteers, with a few $10^3$ achieving
-considerable skill, and a few $10^2$ having the time to make a significant
-contribution. Slightly more quantitively, we might note that  the total skill
-of the crowd, computed by summing the skill of all the agents, is a measure of
-the effective crowd size, in the sense that a crowd of perfect classifiers
-would be of this size. By this measure,the \StageOne crowd was equivalent to a
-team of 1470 perfect classifiers, while the \StageTwo crowd was equivalent to a
-team of 102 perfect classifiers. With this same crowd, we can see that surveys
-providing a few $10^4$ subjects would be completed quickly, if the high
-contribution rate of the current crowd were to be repeated.
+Finally, we comment on the size of the first \SW crowd, and how the system might
+be scaled up for future surveys. In \Sref{sec:results:crowd} and
+\Tref{tab:crowd:contributions}, the following rough picture emerged for the \SW
+crowd in this project: it consisted of a few $10^4$ volunteers, with a few
+$10^3$ achieving considerable skill, and a few $10^2$ having the time to make a
+significant contribution. Slightly more quantitively, we might note that  the
+total skill of the crowd, computed by summing the skill of all the agents, is a
+measure of the effective crowd size, in the sense that a crowd of perfect
+classifiers would be of this size. By this measure,the \StageOne crowd was
+equivalent to a team of 1470 perfect classifiers, while the \StageTwo crowd was
+equivalent to a team of 102 perfect classifiers. With this same crowd, we saw in
+\Sref{sec:results:speed}  that surveys providing a few $10^4$ subjects would be
+completed quickly, if the high contribution rate of the current crowd were to be
+repeated.
 
@@
 that if this can be maintained, visual inspection of tens of thousands of images
-can be performed on timescales of a few weeks.
+could be performed on timescales of weeks.
 
@@
 the training set were estimated to be around $91--93\%$ and $<1\%$ (Stages 1 and
-2). This  FPR translates to a purity of 20\%.
+2). This FPR translates to an approximate purity of 20\%.
 

### 2015-04-21 doc/sw-system.tex
moved some figs from png to pdf

@@
 \begin{minipage}{0.45\linewidth}
-  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage1_ROC.png}
+  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage1_ROC.pdf}
 \end{minipage}\hfill
 \begin{minipage}{0.45\linewidth}
-  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage2_ROC.png}
+  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage2_ROC.pdf}
 \end{minipage}
@@
 \begin{figure}
-\centering\includegraphics[width=\linewidth]{sw-system-figs/completeness_purity_simple.png}
+\centering\includegraphics[width=\linewidth]{sw-system-figs/completeness_purity_simple.pdf}
 \caption{Completeness-estimated purity curves for the \sw system, using
@@
 \begin{figure}
-\centering\includegraphics[width=\linewidth]{sw-system-figs/rate_classification.png}
+\centering\includegraphics[width=\linewidth]{sw-system-figs/rate_classification.pdf}
 \caption{Fractional classification rate in the \SW \cfhtls survey.}

### 2015-04-21 doc/sw-system.tex
Addressing Anu's comments, done Sections 5.2 and 5.3 but not 5.1 #112

@@
 %
-\item{\noindent\bf ``Contribution:''} The integrated skill over a volunteer's
+\item{\noindent\bf ``Contribution:''} This is the integrated skill over a volunteer's
 {\it test subject} classification history, a quantity representative of the
@@
 %
-\item{\noindent\bf ``Information:''} The actual total information $\information$
+\item{\noindent\bf ``Information:''} The total information $\information$
 generated by the agent during the volunteer's classification activity. This
@@
 defined in terms of posterior relative to prior probabilities,
-\Aref{appendix:swap}).  Because of this, we expect this quantity to be noisier
-than the ``contribution'' defined above.
+\Aref{appendix:swap}).  Because of this, we expect this raw quantity to be noisier
+than the ``contribution'' defined above. The lower righthand panel of
+\Fref{fig:crowd:cornerplot} confirms this: there is a strong, linear correlation
+between contribution and information gain, but at a given contribution, the
+distribution of information gain has a tail at high values, corresponding to
+volunteers that were lucky in the number of high probability subjects that they
+happened to be shown (the information gain per classification is maximized when the
+subject probability is 0.5, while most subjects have probabilities closer to or less than the prior).
+In most of the following discussion we use the contribution when characterizing
+crowd participation, but we include
+the information gain for completeness.
 %
@@
 At high values of experience and effort, the skill is \emph{always high}. There
-seem to be very few agents logging large numbers of classifications at low skill
-(although there are one or two exceptions): almost all high effort
-``super-users'' have high skill. These two properties are reflected in both the
+seem to be very few agents logging large numbers of classifications at low
+skill: {\it almost all high effort
+``super-users'' have high skill.} These two properties are reflected in both the
 contributions these volunteers make (third row) and the information they
@@
 
-The distributions for the \StageTwo agents (orange) are qualitatively similar to
-those for the \StageOne agents (blue). Differences are: 1) the maximum effort
-possible at \StageTwo is smaller, because fewer subjects were available to be
-classifed, but 2) the mean effort expended at \StageTwo was higher (perhaps
-because the subjects were higher probability, and more compelling); 3) the
-information generated per agent was higher at \StageTwo, because the subjects
-had higher probability.
+We found that the distributions for the \StageTwo agents to be qualitatively
+very similar to those for the \StageOne agents. The differences are: 1) the
+maximum effort possible at \StageTwo is smaller, simply because fewer subjects
+were available to be classifed, and 2) the information generated per agent was
+slightly higher at \StageTwo, just because the subjects had (on average) higher
+probability.
 
@@
 distribution on a linear scale in \Fref{fig:crowd:cumulplot}. This plot shows
-clearly the importance of the hardest-working, most active volunteers: at
+clearly the importance of the most active volunteers: at
 \StageOne,  1.0\% of the volunteers -- 375 people -- made 90\% of the
@@
 broader than the corresponding distributions of agent contribution, in
-\Fref{fig:crowd:cumulplot}. The most skilled 20\% of agents only possess around
-80\% of the skill at each stage. The inexperienced volunteers also possess a
-significant fraction of the skill: the most skillful 20\% of experienced
-volunteers (1824 people)  possess just 43\% of the total skill. The breadth of
-the skill distributions suggests that  the high level of contribution made at
-\SW by experienced volunteers is largely a matter of choice (or perhaps,
-availability of time!). There were many other volunteers that  were skillful
-enough to make large contributions -- they just didn't classify as many images.
+\Fref{fig:crowd:cumulplot}. For example,
+the most skilled 20\% of agents possess around 80\% of the skill.
+
+The inexperienced volunteers also possess a significant fraction of the skill.
+We find that dividing the crowd into ``experienced volunteers'' (who have seen
+10 or more training images), and ``inexperienced volunteers'' (the rest),
+results in two groups containing approximately equal total skill (see the dashed
+curve in \Fref{fig:crowd:cumulskillplot}). The most skillful 20\% of {\it
+experienced} volunteers (1824 people) only possess 43\% of the total skill.
+The breadth of the skill distributions suggests that  the high level of
+contribution made at \SW by experienced volunteers is largely a matter of choice
+(or perhaps, availability of time!). There were many other volunteers that  were
+skillful enough to make large contributions -- they just didn't classify as many
+images.
 
@@
 \caption{Broad cumulative distributions of agent skill:
-the most skilled 20\% of the crowd only possess 79\% of the skill at \StageOne.
-The \StageOne agents
+the most skilled 20\% of the crowd only possess around 80\% of the skill,
+at \StageOne. The \StageOne agents
 are shown in blue, the \StageTwo agents in orange. ``Experienced volunteers''
@@
 of each classification its volunteer makes; by measuring the time lags between
-successive classifications we can make estimates of the crowd's classification
-and contribution speed. We plot these two quantities for both \StageOne and
+successive classifications, we can make estimates of the crowd's classification
+and contribution speed. We plot the former quantity for both \StageOne and
 \StageTwo in \Fref{fig:results:speed}, normalizing the speed and time axes to
-the respective totals. The fractional classification rates in each stage of the
-survey fall off in approximately the same way, despite the factor of nearly 20
-difference in crowd size. \StageOne (consisting of $\sim430,000$ subjects) was
-completed in around 5000 hours (by some 37,000 participants), with
-classification rates in the first few days averaging at $\sim10^4$ per hour.
-This was stimulated by various forms of advertising (press releases, and emails
-to registered Zooniverse users). The asymptotic classification rate was  around
-ten times lower, at $\sim10^3$ per hour. Interestingly, the average skill was
-found to be approximately constant over the lifetime of \StageOne, leading to a
-contribution rate that tracks closely the classification rate. (A 10\% increase
-in average skill was seen over the first 40 days, and a decrease of the same
-amount in the last 40 days -- not enough to cause a significant difference
-between classification and contribution rate behavior, but perhaps reflecting a
-learning period at the start and a decrease in participation late on.) \StageTwo
-(3700 subjects) was completed in around 600 hours by around 2000 participants,
-with classification rates starting at $~\sim2000$ per hour and decaying to
-$\sim100$ per hour.
+their respective totals. The fractional classification rates
+in each stage of the survey fall off in approximately the same way, despite the
+factor of nearly 20 difference in crowd size. \StageOne (consisting of
+$\sim430,000$ subjects) was completed in around 5000 hours (by some 37,000
+participants), with classification rates in the first few days averaging at
+$\sim10^4$ per hour. This was stimulated by various forms of advertising (press
+releases, and emails to registered Zooniverse users). The asymptotic
+classification rate was  around ten times lower, at $\sim10^3$ per hour.
+Interestingly, the average skill was found to be approximately constant over the
+lifetime of \StageOne, leading to a contribution rate that tracks closely the
+classification rate. (A 10\% increase in average skill was seen over the first
+40 days, and a decrease of the same amount in the last 40 days -- not enough to
+cause a significant difference between classification and contribution rate
+behavior, but perhaps reflecting a learning period at the start and then a
+decrease
+in participation late on.) \StageTwo (3700 subjects) was completed in around 600
+hours by around 2000 participants, with classification rates starting at
+$~\sim2000$ per hour and decaying to $\sim100$ per hour.
 
@@
 \centering\includegraphics[width=\linewidth]{sw-system-figs/rate_classification.pdf}
-\caption{Fractional classification rate in the \SW \cfhtls survey.}
+\caption{Fractional classification rate in the \SW \cfhtls survey. Fractional classification rate is the number
+of classifications per unit time, divided by the final total number of
+classifications. Fractional survey time is the time elapsed since the beginning
+of the survey, divided by the total length of the survey. The unit of time in
+the fractional  classification rate is one survey, so that the curves in
+integrals under the curves are both one. }
 \label{fig:results:speed}
@@
 \begin{equation}
-    \tau \approx 18\,{\rm days} \left(\frac{10^4}{N_p}\right)
+    \tau \approx \tau_0 \left(\frac{10^4}{N_p}\right)
                                \left(\frac{N_s}{10^4}\right),
@@
 where $N_s$ is the number of subjects to be classified, and $N_p$ is the number
-of volunteers in the crowd.
+of volunteers in the crowd. Just using the numbers above, we find a characteristic
+timescale of $\tau_0 = 18\,{\rm days}$, but as we will see in the next section,
+we expect this to be significantly shorter in future projects.
 
@@
 
-If the system efficiency could be improved by a factor of three, we would
-expect the coefficient in \Eref{eq:speed} to decrease by roughly the same factor,
-suggesting that an dataset of $10^4$~images could be searched for lenses by a
-crowd of $10^4$ volunteers in about 6 days.
+If the system efficiency could be improved by a factor of three, we would expect
+the characteristic completion time $\tau_0$  in \Eref{eq:speed} to decrease by
+roughly the same factor, suggesting that a dataset of $10^4$~images could be
+searched for lenses by a crowd of $10^4$ volunteers in about 6 days.
 

### 2015-04-21 doc/sw-cfhtls.tex
Added numeral I to system paper title, 'Gravitational' to CFHTLS paper title and adjusted short title. Closed #140

@@
 
-\title[\sw II]
-{\SW: II. New lens candidates from the CFHTLS discovered
-through citizen science}
+\title[New Gravitational Lens Candidates from CFHTLS]
+{\SW: II. New Gravitational Lens Candidates from the CFHTLS Discovered
+through Citizen Science}
 
@@
 In this section, we describe the \sw-\cfhtls lens sample (henceforth,
-called the \sw lens sample). We find a total of 288 (and XXX new)
+called the \sw lens sample). We find a total of 288 (and 249 new)
 candidates with averaged grade $0<$G$<1.3$ (low probability sample)
@@
 
-There are a total of 91 candidates with $1.3\le$G$<2$ (medium
+There are a total of 50 candidates with $1.3\le$G$<2$ (medium
 probability sample) out of which 30 are new. The quality of candidates
@@
 thought this is possibly a lens (that is, a grade of 1). Among our high
-probability sample (G$\ge$2), there are a total of 50 candidates out of
+probability sample (G$\ge$2), there are a total of 91 candidates out of
 which 28 are new. In this category, the minimum grade by all of the
@@
 may be some interesting candidates lurking in TALK but these will have
-to be sifted through ({\bf is there someone actively looking into this
-whose work should be referred here ?}).
+to be sifted through
+%({\bf is there someone actively looking into this whose work should be referred here ?}).
 
@@
 \input{acknowledgments.tex}
-This work is based on observations obtained with MegaPrime/MegaCam, a joint
-project of CFHT and CEA/IRFU, at the Canada-France-Hawaii Telescope (CFHT) which
-is operated by the National Research Council (NRC) of Canada, the Institut
-National des Sciences de l'Univers of the Centre National de la Recherche
-Scientifique (CNRS) of France, and the University of Hawaii. This research used
-the facilities of the Canadian Astronomy Data Centre operated by the National
-Research Council of Canada with the support of the Canadian Space Agency.
-CFHTLenS data processing was made possible thanks to significant computing
-support from the NSERC Research Tools and Instruments grant program.
+%This work is based on observations obtained with MegaPrime/MegaCam, a joint
+%project of CFHT and CEA/IRFU, at the Canada-France-Hawaii Telescope (CFHT) which
+%is operated by the National Research Council (NRC) of Canada, the Institut
+%National des Sciences de l'Univers of the Centre National de la Recherche
+%Scientifique (CNRS) of France, and the University of Hawaii. This research used
+%the facilities of the Canadian Astronomy Data Centre operated by the National
+%Research Council of Canada with the support of the Canadian Space Agency.
+%CFHTLenS data processing was made possible thanks to significant computing
+%support from the NSERC Research Tools and Instruments grant program.
 

### 2015-04-21 doc/acknowledgments.tex
Various skypecon edits

@@
 contributions to the project so far. A complete list of registered
-collaborators is provided at \texttt{http://spacewarps.org/\#/results/CFHTLS}.
-
-We are also grateful to Stuart Lynn, Kelly Borden, Laura Whyte, Brooke Simmons,
-David Hogg, Thomas Jennings, Layne  Wright, Cecile Faure, Jonathan Coles, Stuart
-Lowe and Jean-Paul Kneib for many useful conversations about citizen science and
-gravitational lens detection, and to the Dark Energy Survey and Pan-STARRS strong
-lensing science teams for their suggestions and encouragement.
+collaborators is provided at \texttt{http://spacewarps.org/\#/projects/CFHTLS}.
 
@@
 % Other authors.
-PJM and ES thank the Institute of Astronomy and Astrophysics, Academia Sinica
-(ASIAA) and Taiwan's Ministry of Science and Technology (MOST) for their
-financial support of the workshop ``Citizen Science in Astronomy'' in March
-2014, at which some parts of the SWAP analysis was developed.
 

### 2015-04-21 doc/sw-system.tex
Various skypecon edits

@@
 probability systems are retired from the site periodically, concentrating the
-sample towards a set of candidates. Having divided the 171 square degree
+sample towards a set of candidates. Having divided 160 square degrees of
 Canada-France-Hawaii Telescope Legacy Survey (\cfhtls)
-imaging survey into some 430,000 overlapping 84 by 84 arcsecond tiles and
-displayed them on the site, we were joined by around 37,000 volunteers who
-contributed 10 million image classifications over the course of 8 months. The
-sample was reduced to 3300 \StageOne candidates; these were then refined to
-yield a sample of 90 \StageTwo detections, a sample we expect to be over 90\%
-complete and 20\% pure at a threshold of 95\% classification probability. We
+imaging into some 430,000 overlapping 84 by 84 arcsecond tiles and
+displaying them on the site, we were joined by around 37,000 volunteers who
+contributed 11~million image classifications over the course of 8 months. The
+sample was reduced to 3368 \StageOne candidates; these were then refined to
+yield a sample that we expect to be over 90\%
+complete and 20\% pure. We
 comment on the scalability of the \SW system to the wide field survey era.
@@
 The four CFHT Legacy Survey\footnote{\texttt{http://www.cfht.hawaii.edu/Science/CFHTLS/}}
-\citep[\cfhtls,][]{Gwyn2012} ``Wide'' fields cover a total of
-171 square degrees of sky.
+\citep[\cfhtls,][]{Gwyn2012} ``Wide'' fields cover a total of approximately
+160 square degrees of sky (after taking into account tile overlaps).
 With high and homogeneous image quality (the mean seeing in the $g$-band is
@@
 first lens search we simply divided the \cfhtls imaging into some 430,000 tiles,
-and collected over 10~million volunteer image classifications.
+and collected over 11~million volunteer image classifications.
 
@@
 \section*{Acknowledgements}
+
+We are also grateful to Stuart Lynn, Kelly Borden, Laura Whyte, Brooke Simmons,
+David Hogg, Thomas Jennings, Layne  Wright, Cecile Faure, Jonathan Coles, Stuart
+Lowe and Jean-Paul Kneib for many useful conversations about citizen science and
+gravitational lens detection, and to the Dark Energy Survey and Pan-STARRS strong
+lensing science teams for their suggestions and encouragement.
+
+PJM and ES thank the Institute of Astronomy and Astrophysics, Academia Sinica
+(ASIAA) and Taiwan's Ministry of Science and Technology (MOST) for their
+financial support of the workshop ``Citizen Science in Astronomy'' in March
+2014, at which some parts of the SWAP analysis was developed.
 

### 2015-04-21 doc/sw-system.tex
Working through Anu's comments, up to Section 6 #112

@@
 selection cuts were to only keep sims with a) second brightest image brighter
-that $i = 23$ and b) total combined image magnitude brighter than 19--20
+that $i = 23$ and b) total combined image magnitude fainter than 19--20
 (\PaperTwo, Table~1). The combination of these two cuts results in a sample of
@@
 \subsubsection{\StageTwo: Refinement}
+\label{sec:design:stages:two}
 
@@
 We first quantify the performance of the \SW system in terms of the recovery of
-the training set images. At \StageOne, this set contains around 5712 simulated
-lenses, and 450 duds; at \StageTwo, we used 152 simulated lenses and 201 duds.
+the training set images. At \StageOne, this set contained around 5712 simulated
+lenses, and 450 duds; at \StageTwo, we used 152 images of simulated lenses and
+201 duds selected as \StageOne false positives (\Sref{sec:design:stages:two}).
 \Fref{fig:results:sample:roc} shows receiver operating characteristic (ROC)
@@
 For comparison we show the results of an analysis where the classifications of
-training images were ignored, and none of the agents allowed to learn: the
-agents were instead simply assigned initial values of their confusion matrices
-of 0.75 for each element, which then remained constant. This set-up emulates a
+training images were ignored, and the agents' confusion matrix elements
+were instead all simply assigned initial values of 0.75
+which then remained constant. This set-up emulates a
 very simple unweighted voting scheme, where all classifications are treated
 equally.  In this case, the TPR remains under 80\% in \StageOne and 60\% in
-\StageTwo, thus quantifying  the benefit of including training images and
+\StageTwo, thus illustrating the benefit of including training images and
 allowing the agents to learn via their Bayesian updates.
@@
 When the agents are allowed to update their confusion matrices, the choice of
-initial confusion matrix is not very important. The same 0.75 initial values
+initial confusion matrix is not very important: the same 0.75 initial values
 applied to normal, learning agents resulted in only a slightly lower TPR than
-the default case, nevertheless indicating that initializing the system less
-conservatively results in slightly worse performance.
+the default case.
 
@@
 and 90\% completeness, it would have contained around 89 lens candidates.
+However, we remind the reader that all these values are dependent on the
+properties of the training subjects, which were chosen to be fairly
+visible: we expect the completeness to real lenses to be somewhat lower, as a
+result.
 
@@
 
-We are also grateful to Stuart Lynn, Kelly Borden, Laura Whyte, Brooke Simmons,
+We thank Stuart Lynn, Kelly Borden, Laura Whyte, Brooke Simmons,
 David Hogg, Thomas Jennings, Layne  Wright, Cecile Faure, Jonathan Coles, Stuart
@@
 
-PJM and ES thank the Institute of Astronomy and Astrophysics, Academia Sinica
+PJM and ES also thank the Institute of Astronomy and Astrophysics, Academia Sinica
 (ASIAA) and Taiwan's Ministry of Science and Technology (MOST) for their

### 2015-04-21 doc/sw-system.tex
Moved most of the appendix into the main paper, fixes #151

@@
 
-The details of how the lens probabilities are calculated are given in
-\Aref{appendix:swap}. In summary:
+The details of how the lens probabilities are calculated are given below.
+In summary:
 \begin{itemize}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_probabilities.png}
-\caption{Typical \SW agent confusion matrix elements. At a particular
-snapshot, 200 randomly-selected agents are shown distributed over the unit plane, with a
-tendency to move towards the ``astute'' region in the upper right hand
-quadrant as each agent's volunteer views more images. Yellow point size is
-proprtional to the number of images classified; green point size shows
-agent-perceived ``skill.''}
-\label{fig:swap:agent-probabilities}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_histories.png}
-%\caption{Typical \SW agent histories. The ``skill'' of the  same 200 random
-%agents  as in \Fref{fig:swap:agent-probabilities} is plotted in green as a function
-%of the number  of subjects classified (``effort''). The yellow histogram in
-%the background shows the distribution of effort.}
-%\label{fig:swap:agent-histories}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\Fref{fig:swap:agent-probabilities} shows the confusion matrix elements of 200
-randomly-selected agents, as they were on a particular day towards the end of
-the \cfhtls project. Many volunteers classify  only a small number of images, and
-so their agents' confusion matrix elements remain close to their initial values
-of (0.5,0.5). As more images are classified (shown by the yellow point size),
-the agents' matrix elements tend to move towards higher values, partly as the
-volunteers attain greater skill levels (green point sizes, see
-\Sref{sec:results} below) but mostly as
-the agent learns more about them. In this upper
-right-hand quadrant, the agents perceive their volunteers to be ``astute.''
-
-%\Fref{fig:swap:agent-histories} shows the ``skill'' (\Sref{sec:results:crowd})
-%of the same small sample of agents evolving as their volunteers classify images.
-%The underlying histogram shows the distribution of classification number: a long
-%tail to very high ``effort'' can be seen.
-
-In \Sref{sec:results} below, we define several quantities based on the
-probabilities listed above that serve to quantify the performance of the crowd
-in terms of the information they provide via their classifications, and report
-on the performance of the system in returning a sample of lens candidates
-as a function of $\pr(\LENS|C,T)$ threshold.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_trajectories.png}
-\caption{Typical \SW \StageOne subject trajectories. Top: 200 randomly-selected
-subjects drift downwards as they are classified, while being nudged left and
-right in probability by the agents as they interpret the volunteers input. The
-dotted vertical lines show (left to right) the retirement threshold, prior
-probability, and the detection threshold. Different colours denote the different
-kinds of subject. Bottom panel: histograms of all the subject probabilities
-computed to date, sub-divided by subject kind.}
-\label{fig:swap:subject-trajectories}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-During \StageOne classification of the \cfhtls images, we assigned a prior
-probability for each image to contain a lens of $2\times10^{-4}$, based on a
-rough estimate of the number of expected lenses in the survey, and the fraction
-of the survey area covered by each image. We then assigned two values of the
-images' posterior probability, $\pr(\LENS|C,T)$, to define ``detection'' and
-``rejection'' thresholds. These were set to be 0.95 and (approximately
-symmetrically in the logarithm of probability), $10^{-7}$. Subjects that
-attained probability of less than the rejection threshold were scheduled for
-retirement and subsequently ignored by the analysis code. Subjects crossing the
-detection threshold were also subsequently ignore, but they were not
-retired from the website, just so that more volunteers could see them.
-The progress of the subjects is illustrated in
-\Fref{fig:swap:subject-trajectories}. Subjects appear on this plot at the tip of
-the arrow, at zero classifications and prior probability; they then drift
-downwards as they are classified by the crowd, with each agent applying the
-appropriate kick in probability based on what it hears its volunteer say.
-Encouragingly, sims (blue) tend to end up with high probability, while duds
-(red) pile up at low probability; test subjects (black) mostly drift to low
-probability, but some go the other way. The latter will help make up the
-candidate sample. As this plot shows, around 10 classifications are typically required for a subject to reach the retirement (or detection) threshold.
-
-The analysis code was run every night during the project, and subjects retired
-in batches after its completion. This introduced some inefficiency, because
-some classifications were accumulated in the time between them crossing the
-rejection threshold and the subject actually being retired from the website.
-As subjects were retired from the site, more subjects were activated. In this
-way, the volunteers who down-voted images for not containing any lensed
-features enabled new images to be shown to other members of the community.
-
-When all the subjects had either been retired, or classified around 10 times
-or more, the web app was paused and reconfigured for \StageTwo. The sample of
-subjects classified during \StageTwo was selected to be all those that passed
-the detection threshold ($\pr(\LENS|C,T) > 0.95$) at \StageOne. These were
-classified for one week, with no retirement but a maximum classification
-number of 50 each. The number of subjects at \StageTwo was small enough that we
-did not need to retire any: instead, we simply collected classifications for a
-fixed period of time (about 4 weeks). Without the time pressure motivating the
-probabilities simultaneously, for comparison. We describe how this differs
-from the online analysis in the appendix.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
-\label{sec:results}
-
-In this section we present our findings about the performance of the \SW system,
-in terms of the classification of the training set, the  information contributed
-by the crowd, and the speed at which the image set was classified.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Sample Properties}
-\label{sec:results:sample}
-
-We first quantify the performance of the \SW system in terms of the recovery of
-the training set images. At \StageOne, this set contained around 5712 simulated
-lenses, and 450 duds; at \StageTwo, we used 152 images of simulated lenses and
-201 duds selected as \StageOne false positives (\Sref{sec:design:stages:two}).
-\Fref{fig:results:sample:roc} shows receiver operating characteristic (ROC)
-curves for \cfhtls \StageOne and \StageTwo. These plots show the true positive
-rate (TPR, the number of sims correctly detected divided by the total number of
-sims in the training set), and the false positive rate (FPR, the number of duds
-incorrectly detected  divided by the total number of duds in the training set), both
-for a given sample of detections defined by a particular probability threshold,
-which varies along the curves.  In both stages, these curves show that true
-positive rates of  around 90\% were achieved, at very low false positive rates.
-
-For comparison we show the results of an analysis where the classifications of
-training images were ignored, and the agents' confusion matrix elements
-were instead all simply assigned initial values of 0.75
-which then remained constant. This set-up emulates a
-very simple unweighted voting scheme, where all classifications are treated
-equally.  In this case, the TPR remains under 80\% in \StageOne and 60\% in
-\StageTwo, thus illustrating the benefit of including training images and
-allowing the agents to learn via their Bayesian updates.
-
-When the agents are allowed to update their confusion matrices, the choice of
-initial confusion matrix is not very important: the same 0.75 initial values
-applied to normal, learning agents resulted in only a slightly lower TPR than
-the default case.
-
-The dot-dashed curves show the impact of the offline analysis. At \StageOne the
-results are very similar to the online version that was actually run (solid
-line). However, at \StageTwo there is marginal evidence of there being greater
-benefit to doing the analysis offline (\Sref{sec:swap}, \Aref{appendix:swap}).
-Over 85\% TPR is achieved at zero FPR in the offline analysis , while if one is
-willing to accept a false positive rate of 5\%, the true positive rate rises to
-over 95\%, showing that some of the sims that were missed in the online analysis
-may be being recovered by doing the analysis offline. The same is true at
-\StageOne, but to a lesser extent. Assuming Poisson statistics for the
-fluctuations in the numbers of recovered lenses, the uncertainty in the measured
-\StageTwo TPR values is around 8\%, but the online and offline samples are
-highly correlated, such that the uncertainty on the difference between the ROC
-curves is somewhat less than this. Still, a larger validation set is needed to
-test these algorithmic choices more rigorously. At \StageOne, high TPR can be
-measured to better than 1\%.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\begin{minipage}{0.45\linewidth}
-  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage1_ROC.pdf}
-\end{minipage}\hfill
-\begin{minipage}{0.45\linewidth}
-  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage2_ROC.pdf}
-\end{minipage}
-\caption{Receiver operating characteristic curves for the \SW system, using
-the \cfhtls training set. Left: \StageOne, right: \StageTwo. Insets show a
-magnified view of the top lefthand corner of each plot. Linestyles illustrate
-the agent properties (initial confusion matrix elements, learning or not)
-discussed in the text, as well as the difference between the online and offline
-analyses. The \StageTwo sample was defined using the online \StageOne results
-(solid blue curve), while the offline analysis was chosen for the final
-\StageTwo results (dot-dashed orange curve). }
-\label{fig:results:sample:roc}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Adopting the online \StageOne analysis, and the offline \StageTwo analysis, we
-show in \Fref{fig:results:sample:CP} a plot of the more familiar (to
-astronomers) quantities of completeness versus purity, again for
-the two stages. As in \Fref{fig:results:sample:roc}, the detection threshold
-varies along the curves. Completeness is defined as the number of correctly
-detected sims divided by the total number of sims in the training set, while
-purity is the number of correct detections divided by the total number of
-detections.\footnote{The completeness is equivalent to the TPR and is also
-known elsewhere as the ``recall.''  The purity is also known as the
-``precision.''} If the training set samples from the same systems as the test
-set, then the completeness of the training set will be equivalent to the
-completeness of the test set. The purity depends on the proportion of sims to
-duds, and so the purity of the test set must be approximated by rescaling the
-training set to the expected proportion of lens systems to not-lens systems in
-the survey. First we compute the expected number of false positives by
-multiplying the FPR by the expected number of non-lenses in the survey. Then
-we multiply the TPR by the expected number of lenses in the survey, to get the
-expected number of true positives. The sum of the true positives and the false
-positives gives the expected sample size; dividing the expected number of true
-positives by this sample size gives the purity. Note that the completeness is
-invariant to this transformation.
-The \StageOne curves are truncated by the retirement of subjects in this phase,
-which sets the minimum size of this sample. We see from the solid blue curve
-that over 90\% completeness was reached, albeit in a sample with around 20\%
-purity.
-
-Does this performance level vary between the different types of gravitational
-lens? To investigate the completeness to the three different types of lens in
-the training set, we repeated the same procedure but now considering only the
-detections of a certain kind of lens and of the non-lenses in the training set.
-We estimate the expected number of lenses and non-lens false positives by
-dividing the lens and dud sets into equal fractions. The lensed quasar part of
-the training set yielded the highest completeness, suggesting that these were
-the easiest sims to spot. The lensed galaxies were recovered at the lowest
-completeness, likely due to the difficulty  of separating the lens and source
-galaxy light.
-
-At \StageTwo, where no retirement was carried out, it was possible to reach
-100\% purity: the knee of the curve is at just under 90\% completeness. However,
-the purity decreases rapidly if higher completeness than this is sought. The
-optimal sample in this simulated lens search experiment would have been
-constructed with a threshold value of $\pr(\LENS|C,T) > 0.47$. At 100\% purity
-and 90\% completeness, it would have contained around 89 lens candidates.
-However, we remind the reader that all these values are dependent on the
-properties of the training subjects, which were chosen to be fairly
-visible: we expect the completeness to real lenses to be somewhat lower, as a
-result.
-
-% TP + FN ~ 2e-4 * 430000 ~ 100 ~ TP/C ; so TP ~ 89 candidates
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=\linewidth]{sw-system-figs/completeness_purity_simple.pdf}
-\caption{Completeness-estimated purity curves for the \sw system, using
-the \cfhtls training set.}
-\label{fig:results:sample:CP}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+For a detailed derivation of this analysis pipeline, please continue reading
+through \Sref{sec:swap:details} below. Alternatively, \Sref{sec:swap:practicalities}
+contains illustrations of the calculation.
 
@@
 
-\subsection{Crowd Properties}
-\label{sec:results:crowd}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/all_skill_contribution_experience_education.pdf}
-\caption{Key properties and contributions of the \SW \StageOne crowd.
-Plotted are the 1-D
-and 2-D smoothed marginalized distributions for  the logarithms of the
-properties of the agents described in the text. The contours
-contain 68\%, 95\% and 99\% of the distributions.}
-\label{fig:crowd:cornerplot}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-To investigate the properties of the \sw crowd, as characterised by their
-agents, we define the following quantities and plot their one and 2-D marginal
-distributions in
-\Fref{fig:crowd:cornerplot}. This figure only shows the \StageOne agents for clarity,
-but the trends we found the same trends in \StageTwo.
-%
-\begin{description}
-%
-\item{\noindent\bf ``Effort:''} The number of test images, $\effort$, classified
-by a volunteer. In \StageOne, the mean effort per agent was 263; in the shorter
-\StageTwo it was 81.
-%
-\item{\noindent\bf ``Experience:''} The number of training images, $\experience$,
-classified by a volunteer. In \StageOne, the mean experience per agent was 29;
-in \StageTwo (where the training image frequency was set higher) it was 34.
-%
-\item{\noindent\bf ``Skill:''} The expectation value of the information gained
-per classification (in bits) by that volunteer,  $\skill$, for subjects which
-have lens probability 0.5 (\Aref{appendix:swap}). Random classifiers have
-$\skill = 0.0$~bits, while perfect classifiers have $\skill = 1.0$~bit.
-All agents start
-with $\skill = 0.0$~bits. The skill of  an agent increases as training subjects are
-classified, and the agent's estimates of its confusion matrix elements improve.
-In \StageOne, the mean skill per agent was 0.04 bits; in  \StageTwo it was
-0.05~bits.
-%
-\item{\noindent\bf ``Contribution:''} This is the integrated skill over a volunteer's
-{\it test subject} classification history, a quantity representative of the
-total contribution to the project made by that volunteer (see the appendix for
-more discussion of this quantity). The classifications of training images
-determine the skill, while the classification of test images determines
-contribution.  In \StageOne, the mean  contribution per agent was
-34.9 bits; in \StageTwo it was 33.5.
-%
-\item{\noindent\bf ``Information:''} The total information $\information$
-generated by the agent during the volunteer's classification activity. This
-quantity depends on the value of each subject's lens probability when that
-subject was presented to the volunteer (simply because information gain is
-defined in terms of posterior relative to prior probabilities,
-\Aref{appendix:swap}).  Because of this, we expect this raw quantity to be noisier
-than the ``contribution'' defined above. The lower righthand panel of
-\Fref{fig:crowd:cornerplot} confirms this: there is a strong, linear correlation
-between contribution and information gain, but at a given contribution, the
-distribution of information gain has a tail at high values, corresponding to
-volunteers that were lucky in the number of high probability subjects that they
-happened to be shown (the information gain per classification is maximized when the
-subject probability is 0.5, while most subjects have probabilities closer to or less than the prior).
-In most of the following discussion we use the contribution when characterizing
-crowd participation, but we include
-the information gain for completeness.
-%
-\end{description}
-
-The leftmost column of \Fref{fig:crowd:cornerplot} shows how the last four of
-these properties depends on the effort expended by the volunteers. As expected,
-we see that experience is tightly correlated with effort, reflecting the design
-of training images being presented throughout each stage (albeit at decreasing
-frequency). We also see a strong correlation between effort and skill, which was
-hoped for but not guaranteed: the more images the volunteers see, the better
-able to contribute information they are.
-
-The effort distribution shows two peaks, suggestive of two types of
-participation.  The sharp spike at just a few images classified presumably
-corresponds to visitors who only classify a few subjects before leaving the site
-again. The broader hump contains people doing tens to hundreds of
-classifications: the skill vs.\ experience panel of \Fref{fig:crowd:cornerplot}
-shows this group to achieve a broad distribution of  skill, peaking at around
-0.05 but with a long tail to higher values.
-
-At high values of experience and effort, the skill is \emph{always high}. There
-seem to be very few agents logging large numbers of classifications at low
-skill: {\it almost all high effort
-``super-users'' have high skill.} These two properties are reflected in both the
-contributions these volunteers make (third row) and the information they
-generate (fourth row).
-
-We found that the distributions for the \StageTwo agents to be qualitatively
-very similar to those for the \StageOne agents. The differences are: 1) the
-maximum effort possible at \StageTwo is smaller, simply because fewer subjects
-were available to be classifed, and 2) the information generated per agent was
-slightly higher at \StageTwo, just because the subjects had (on average) higher
-probability.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_contrib_cumul.pdf}
-\caption{Cumulative distributions of the contributions made by the agents: 90\%
-of the contribution was made by the highest contributing 1\% of the crowd at
-\StageOne (blue), and the highest contributing  7\% of the crowd at \StageTwo
-(orange). The \StageOne agents are shown in blue, the \StageTwo agents in
-orange. ``Experienced volunteers'' classified 10 or more training subjects.}
-\label{fig:crowd:cumulplot}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\Fref{fig:crowd:cornerplot} shows the \SW crowd to have quite broad
-distributions of logarithmic effort, skill, and contribution. To better
-quantify the contributions made by the volunteers, we show their cumulative
-distribution on a linear scale in \Fref{fig:crowd:cumulplot}. This plot shows
-clearly the importance of the most active volunteers: at
-\StageOne,  1.0\% of the volunteers -- 375 people -- made 90\% of the
-contribution.  At \StageTwo, where it was not possible to make as
-many classifications before running out of subjects, 7.2\% of the volunteers
--- 141 people -- made 90\% of the contribution.
-
-However, it is not the case that only these small groups were {\it capable} of
-making large contributions. The cumulative distribution of agent skill is shown
-in \Fref{fig:crowd:cumulskillplot}: these distributions are significantly
-broader than the corresponding distributions of agent contribution, in
-\Fref{fig:crowd:cumulplot}. For example,
-the most skilled 20\% of agents possess around 80\% of the skill.
-
-The inexperienced volunteers also possess a significant fraction of the skill.
-We find that dividing the crowd into ``experienced volunteers'' (who have seen
-10 or more training images), and ``inexperienced volunteers'' (the rest),
-results in two groups containing approximately equal total skill (see the dashed
-curve in \Fref{fig:crowd:cumulskillplot}). The most skillful 20\% of {\it
-experienced} volunteers (1824 people) only possess 43\% of the total skill.
-The breadth of the skill distributions suggests that  the high level of
-contribution made at \SW by experienced volunteers is largely a matter of choice
-(or perhaps, availability of time!). There were many other volunteers that  were
-skillful enough to make large contributions -- they just didn't classify as many
-images.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_skill_cumul.pdf}
-\caption{Broad cumulative distributions of agent skill:
-the most skilled 20\% of the crowd only possess around 80\% of the skill,
-at \StageOne. The \StageOne agents
-are shown in blue, the \StageTwo agents in orange. ``Experienced volunteers''
-classified 10 or more training subjects.}
-\label{fig:crowd:cumulskillplot}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Classification Speed}
-\label{sec:results:speed}
-
-How fast does the \SW crowd classify subjects? Each agent records the timestamp
-of each classification its volunteer makes; by measuring the time lags between
-successive classifications, we can make estimates of the crowd's classification
-and contribution speed. We plot the former quantity for both \StageOne and
-\StageTwo in \Fref{fig:results:speed}, normalizing the speed and time axes to
-their respective totals. The fractional classification rates
-in each stage of the survey fall off in approximately the same way, despite the
-factor of nearly 20 difference in crowd size. \StageOne (consisting of
-$\sim430,000$ subjects) was completed in around 5000 hours (by some 37,000
-participants), with classification rates in the first few days averaging at
-$\sim10^4$ per hour. This was stimulated by various forms of advertising (press
-releases, and emails to registered Zooniverse users). The asymptotic
-classification rate was  around ten times lower, at $\sim10^3$ per hour.
-Interestingly, the average skill was found to be approximately constant over the
-lifetime of \StageOne, leading to a contribution rate that tracks closely the
-classification rate. (A 10\% increase in average skill was seen over the first
-40 days, and a decrease of the same amount in the last 40 days -- not enough to
-cause a significant difference between classification and contribution rate
-behavior, but perhaps reflecting a learning period at the start and then a
-decrease
-in participation late on.) \StageTwo (3700 subjects) was completed in around 600
-hours by around 2000 participants, with classification rates starting at
-$~\sim2000$ per hour and decaying to $\sim100$ per hour.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=\linewidth]{sw-system-figs/rate_classification.pdf}
-\caption{Fractional classification rate in the \SW \cfhtls survey. Fractional classification rate is the number
-of classifications per unit time, divided by the final total number of
-classifications. Fractional survey time is the time elapsed since the beginning
-of the survey, divided by the total length of the survey. The unit of time in
-the fractional  classification rate is one survey, so that the curves in
-integrals under the curves are both one. }
-\label{fig:results:speed}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The similarities between \StageOne and 2, suggest that these numbers could be
-scaled to estimate the speed of future \SW projects (or at least those following
-a similar blind search strategy). For example, the completion time for a \SW
-project may be approximated as
-\begin{equation}
-    \tau \approx \tau_0 \left(\frac{10^4}{N_p}\right)
-                               \left(\frac{N_s}{10^4}\right),
-\label{eq:speed}
-\end{equation}
-where $N_s$ is the number of subjects to be classified, and $N_p$ is the number
-of volunteers in the crowd. Just using the numbers above, we find a characteristic
-timescale of $\tau_0 = 18\,{\rm days}$, but as we will see in the next section,
-we expect this to be significantly shorter in future projects.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}
-\label{sec:discuss}
-
-What can we learn from the results of the previous section, for future
-projects? Potential improvements to the \SW system can be divided into three
-categories, performance, efficiency and capacity.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}
-\begin{minipage}{\linewidth}
-  \begin{minipage}[t]{0.47\linewidth}
-    \begin{minipage}{0.46\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0008wyp_gri.png}
-    \end{minipage}\hfill
-    \begin{minipage}{0.50\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0008wyp_stage2_trajectory.png}
-    \end{minipage}
-  \end{minipage}\hfill
-  \begin{minipage}[t]{0.47\linewidth}
-    \begin{minipage}{0.46\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0006rkx_gri.png}
-    \end{minipage}\hfill
-    \begin{minipage}{0.50\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0006rkx_stage1_trajectory.png}
-    \end{minipage}
-  \end{minipage}
-\end{minipage}
-
-\vspace{\baselineskip}
-
-\begin{minipage}{\linewidth}
-  \begin{minipage}[t]{0.47\linewidth}
-    \begin{minipage}{0.46\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0000fgj_gri.png}
-    \end{minipage}\hfill
-    \begin{minipage}{0.50\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0000fgj_stage1_trajectory.png}
-    \end{minipage}
-  \end{minipage}\hfill
-  \begin{minipage}[t]{0.47\linewidth}
-    \begin{minipage}{0.46\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0003j2s_gri.png}
-    \end{minipage}\hfill
-    \begin{minipage}{0.50\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0003j2s_stage1_trajectory.png}
-    \end{minipage}
-  \end{minipage}
-\end{minipage}
-\caption{Illustrative examples of
-false negatives (blue) and false positives (red) from the classification of
-the \SW \cfhtls training set. The trajectory plot for each of the 4 subjects is
-shown to the right of its image. Lefthand panels show the most common types of
-trajectories: short step random walks resulting from no high skill classifiers
-viewing the subject. The righthand panels show examples where higher skill
-classifiers have been involved, causing random walks with longer step lengths
-(top) and catastrophic mis-classifications (bottom right). Note that both these
-subjects were {\it very nearly} detected but didn't quite reach the threshold
-set (marked by the blue dashed line). Insets for the false
-negatives show the lens feature. The inset for the lower righthand panel shows
-where most users believed a lens was located. There is no corresponding inset
-for the lower left panel because no particular feature stood out to users.
-Instead, users clicked many different features.}
-\label{fig:discuss:performance:trajectories}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Improving performance: reducing incompleteness and impurity}
-\label{sec:discuss:performance}
-
-We investigated the source of the incompleteness and impurity visible in
-\Fref{fig:results:sample:CP}, by examining the \StageTwo false negatives and
-false positives, and their behaviour as they are classified using the online
-analysis trajectory plots introduced in \Sref{sec:swap}
-(\Fref{fig:swap:subject-trajectories}).
-\Fref{fig:discuss:performance:trajectories} shows 2 example simulated lenses
-that were missed ($\pr(\LENS|C,T) < 10^{-5}$) by the \SW system (top row),
-and 2 example
-non-lenses that were incorrectly flagged as candidates ($\pr(\LENS|C,T) >
-0.95$) by the \SW system (bottom row).
-While the final \StageTwo analysis was done offline,
-these trajectory plots still serve to illustrate the approximate
-classification histories of the subjects.
-
-In some cases the rejection of the false negatives is understandable: the
-lensed features are faint, or in some cases, somewhat unrealistic as lenses.
-However, in other cases a reasonably obvious lens was passed over.  This
-mainly seems to be due to noise in the system: when only low-skill classifiers
-view a subject, all the updates to its posterior probability are small, and if
-none are very confident about the presence of lensing, the subject follows a
-random walk down its trajectory plot. This can be seen in the top left panel
-of the figure.
-
-The false positives show similar behaviour, for example in the bottom lefthand
-panel of the figure. As well as subjects being ``unlucky'' in this way, there
-are two less common failure modes associated with mistakes made by higher skill
-users, illustrated in the righthand column of the figure. In the false negative
-subject shown in the top right-hand panel, several high skill classifiers update
-the subject upwards in log probability by some way each time, but other,
-comparable skill classifiers mis-classify the system to lower probability.   The
-trajectory looks like a random walk, but with bigger steps; this particular
-subject came very close to crossing the detection  threshold three times, but
-didn't quite make it. The bottom right-hand panel shows an example of a final,
-apparently rare, failure mode: we see some short-step random walk behaviour,
-followed by a mis-classification by a very high skill ``expert'' classifier
-after 20 classifications that promotes the subject to high probability.
-
-There are a number of places where we can address these problems and
-improve system performance: adding flexibility to the classification
-interface, educating the volunteers, assigning subjects for
-classification, and interpreting the classification data.
-
-Some of  the mistakes made by reasonably high skill
-classifiers working at high speed
-could have perhaps been corrected by those classifiers themselves, had
-they had access to a ``go back'' option. While clearly enabling error
-reduction, we might worry about such a mechanism enabling classifiers to have
-a guess, then go and read the \Talk discussion, and then return to the
-classification interface to change their mind to agree with the forum. In
-fact, this is already possible on the current interface -- and indeed, it is
-not obvious that such correlations would necessarily lead to poorer system
-performance. This could be tested by presenting a fraction of the volunteers
-with a version of the site that actively suggested that they take this
-approach, and then tracking the relative performance of ``collaborative''
-classifications compared with independent ones. We leave the exploration of
-this to further
-work.
-
-Mistakes by both high and low skill classifiers could be reduced by improving
-the training in the system, which could be done in several ways. One is to
-make more training images available to those who want or need it. A basic
-level of training images are needed for SWAP to build up an accurate picture
-of each classifier's skill -- but one could imagine volunteers {\it choosing}
-to see more training images (still at random) in their stream. We could also
-experiment with providing greater training rates early on for all volunteers;
-the risk associated with this is that retention rates may drop if too few
-``fresh'' test images are shown early on. Another way of improving the
-training could be to provide more information about what lenses do. In this
-project, the Spotter's Guide, and the Science, FAQ and About pages were always available on the site, but as a
-passive background resource. We might consider providing more links to this
-guide in the feedback messages shown to the classifiers as they go -- or
-perhaps extending these messages to themselves include more explanations and
-example images. We might also investigate a more dynamic Spotter's Guide: a
-set of manipulable model lenses illustrating all the possible image
-configurations that that those deflectors can make could help volunteers gain
-understanding of what lensed features can look like very quickly. Such a toy
-is under development.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/stage2_veteran_contribution.pdf}
-\caption{\StageTwo classifier skill, as a function of their \StageOne skill.
-Veterans from \StageOne  are shown in blue, while new volunteers are shown in
-orange. Point size is proportional to the total contribution made,
-while dashed lines are drawn at the mean values for each sample.}
-\label{fig:discuss:performance:stage1vstage2}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-However, most identification failures (around 60\%) seem to be due to the
-random walk problem. Short, random direction steps arise from low skill
-classifiers, arising from classifier inexperience (\Sref{sec:results:crowd}).
-While improved training will help reduce this effect, it is here
-that targeted task assignment could also help improve system performance, by
-bringing higher skill volunteers in to the mix. We
-advertised \StageTwo of the current project to all registered users; it was
-taken up by \StageOne veterans with a broad range of skill, and also picked up a
-significant number of new users who did not have enough time to aquire high
-skill (since \StageTwo was quite short): of the 1964 volunteers who took part in
-the \StageTwo classification round, only 774 were veterans from \StageOne.
-
-\Fref{fig:discuss:performance:stage1vstage2} shows how the \StageOne skill maps
-on to \StageTwo skill and contribution.
-This figure suggests that there may be some benefit to opening \StageTwo on the
-basis of \StageOne agent skill, in order to reduce the noise in the system
-generated by new and low skill volunteers in this more difficult
-classification stage.  A simple implementation of this would be to switch the
-web app to the \StageTwo version when either a certain \StageOne skill (and/or
-effort) threshold was passed. Good strategy would probably be to switch back
-to \StageOne after some number of \StageTwo classifications (to avoid losing the
-high skill users from \StageOne entirely), and also to make it very clear which
-stage the classifier was at (since \StageTwo requires more careful attention).
-This is something we plan to experiment with in future.
-
-Finally, there could be some performance gains to be made by improving the
-SWAP agent model, or its implementation. Low skill is typically a result  of
-inexperience (\Sref{sec:results:crowd}), but it could be the agent that is
-inexperienced as well as the classifier or its agent. In a future paper we
-plan to investigate the use of the test images as well as the training images
-in accelerating the agent's learning (Davis et al, in preparation). We also
-plan to investigate the use of offline analysis at \StageOne, for the same
-reason (see also \Sref{sec:discuss:efficiency} below.)
-One might also consider looking at
-introducing more conditional dependences in the confusion matrix elements, to
-allow for some classifiers having greater skill in spotting one type of lens
-than another, or, more generally, as a function of lens property (such as
-colour, brightness, and image separation). In the current model, all agents are
-considered to be completely independent, whereas in fact we might expect there
-to be significant clustering of the confusion matrix elements. A hierarchical
-model for the crowd, with hyper-parameters describing the distribution of
-confusion matrix elements across the population, may well accelerate the agent
-learning process by including the notion of one agent being likely to be
-similar to its neighbours. Finally, it is worth noting that the model of
-\citet{IBCC} explicitly avoids the assumption of the agent confusion matrix
-elements being constant in time, allowing the development of volunteer skill
-to be more accurately tracked -- and that they did see some time-evolution in
-the supernova zoo classifiers' skill. Finding a way to incorporate such a
-learning model into SWAP, while retaining its statistically online character
-is an interesting challenge for future work.
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \begin{figure}
-% \centering\includegraphics[width=0.9\linewidth]{sw-system-figs/early_vs_final_skill.png}
-% \caption{Predictability of final skill from early skill (after 10 training
-% classifications) in \StageOne agents. The dashed lines enclose 649 agents with
-% early skill greater than 0.1
-% who retain final skill of greater than 0.05. Point size is proportional to
-% contribution (plus a constant).}
-% \label{fig:crowd:skillprediction}
-% \end{figure}
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% Having seen the importance of the high skill volunteers at both \StageOne and
-% \StageTwo, we might ask, can we predict agent skill after, say, the volunteer
-% has experienced 10 training subjects? In \Fref{fig:crowd:skillprediction} we
-% plot this ``early skill'' against final skill, for all experienced \StageOne
-% volunteers. The majority of the crowd shows little correlation, but at the
-% high early skill end, some predictability appears. The 649 experienced \StageOne
-% volunteers who had early skill greater than 0.1 went on to attain a mean
-% final skill of 0.22, with 97\% remaining at skill 0.05 or higher. This
-% suggests that it might be worth tracking volunteers' skill as a project
-% progresses, in order to encourage those showing an aptitude for the task to
-% take part in the more difficult activities, such as \StageTwo refinement.
-% However, this would not have done a very good job at identifying the
-% volunteers who went on to make the largest contributions: the point size in
-% \Fref{fig:crowd:skillprediction} is proportional to contribution (plus a constant):
-% many of the highest contributors showed relatively low skill early on.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Improving efficiency}
-\label{sec:discuss:efficiency}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table*}
-\begin{center}
-\caption{Total crowd and subject sample properties from the \cfhtls project.}
-\label{tab:crowd:contributions}
-\begin{tabular}{cccccccc}
-  \hline
-  % \hline {Stage} & Subjects & Contribution                          & Agents & Skill      & Classifications          & Candidates & Information \\
-  %                & $\Ns$    & $\sum_k^{\Nv} \contribution_k$ (bits) & $\Nv$  & $\sum_k^{\Nv} \skill_k$ (bits) & $\sum_k^{\Nv} \thiseffort$ & $\Ncands$  & $\sum_j^{\Ns}\sum_k^{\Nv} \information_{j,k}$ (bits) \\
-  % \hline
-  %           1    & $427064$ & $1292016.3$ & $36982$ & $1471.9$ & $10802125$ & $3368$ & $91122.6$ \\
-  %           2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $90$ &  $1640.4$ \\
-  \hline {Stage} & Subjects & Contribution                          & Agents & Skill      & Classifications          & Candidates & Information \\
-                           & $\Ns$    & $\sum_k^{\Nv} \contribution_k$ (bits) & $\Nv$  & $\sum_k^{\Nv} \skill_k$ (bits) & $\sum_k^{\Nv} \thiseffort$ & $\Ncands$  & $\sum_j^{\Ns}\sum_k^{\Nv} \information_{j,k}$ (bits) \\
-            \hline
-                      1    & $427064$ & $1292016.3$ & $36982$ & $1471.9$ & $10802125$ & $3368$ & $91122.6$ \\
-                      2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $90$ &  $1640.4$ \\
-  \hline \hline
-\end{tabular}
-\medskip\\
-\end{center}
-\end{table*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\Tref{tab:crowd:contributions} shows the total effort, contribution, skill and
-information generated in both \StageOne and 2 of the \cfhtls project, with the
-total numbers of agents and subjects for comparison.   These numbers allow us
-to quantify the efficiency of the system.
-
-The contribution per classification is defined in terms of a hypothetical
-subject with lens probability of 0.5; one bit of information is needed to
-update such a subject's lens probability to either zero or one. This means
-that a maximally complete classification stage would yield a total
-contribution (summed over all agents) equal to the number of subjects. The
-ratio of this hypothetical optimum to the actual total contribution is
-therefore a measure of the stage's inefficiency. We find our inefficiency (by
-dividing column 2 by column 3) to be 33\% and 17\% in \StageOne and \StageTwo
-respectively. In \StageOne, this inefficiency is due to the daily processing: we
-were not able to retire subjects fast enough, and so they, remained in the
-system, being over-classified. Indeed, only 3705745 classifications were
-needed to retire all the subjects: the ratio of this to the total number made
-is 34\%. (The remaining 1\% is due to not all subjects being classified to 1
-or 0 probability.) At \StageTwo, we did not retire any subjects at all; the
-inefficiency in this case was by design, to give everyone a chance to
-appreciate what they had found together. (An unwanted side effect of this
-policy was noted in \Fref{fig:discuss:performance:stage1vstage2} in the
-previous sub-section.)
-
-It is clear that to increase the efficiency of the system we need to reduce
-the time lag between the classification being made and its outcome being
-analyzed. The optimal way to do this would be to have the web app itself
-analyze the classifications in a fully online system. This is under
-investigation for future projects. With the classification data being analyzed
-in real time, there may still be a place for a daily or weekly offline
-analysis: this could potentially reduce the false negative and false positive
-rates by ``resurrecting'' subjects that had been retired by the online system
-before the agents had time to learn enough about their classifier's high
-skill.
-
-If the system efficiency could be improved by a factor of three, we would expect
-the characteristic completion time $\tau_0$  in \Eref{eq:speed} to decrease by
-roughly the same factor, suggesting that a dataset of $10^4$~images could be
-searched for lenses by a crowd of $10^4$ volunteers in about 6 days.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Increasing capacity}
-\label{sec:discuss:capacity}
-
-Finally, we comment on the size of the first \SW crowd, and how the system might
-be scaled up for future surveys. In \Sref{sec:results:crowd} and
-\Tref{tab:crowd:contributions}, the following rough picture emerged for the \SW
-crowd in this project: it consisted of a few $10^4$ volunteers, with a few
-$10^3$ achieving considerable skill, and a few $10^2$ having the time to make a
-significant contribution. Slightly more quantitively, we might note that  the
-total skill of the crowd, computed by summing the skill of all the agents, is a
-measure of the effective crowd size, in the sense that a crowd of perfect
-classifiers would be of this size. By this measure,the \StageOne crowd was
-equivalent to a team of 1470 perfect classifiers, while the \StageTwo crowd was
-equivalent to a team of 102 perfect classifiers. With this same crowd, we saw in
-\Sref{sec:results:speed}  that surveys providing a few $10^4$ subjects would be
-completed quickly, if the high contribution rate of the current crowd were to be
-repeated.
-
-There are (at least) two ways in which we might increase the numbers of
-high-contribution volunteers for larger projects in future. The first is
-simply to increase the total crowd size, and hope that a similar fraction of
-volunteers make large contributions. Greater exposure of the website to the
-public through mass media would help. Another option is to advertise the
-project to new groups of volunteers by translating the website into other
-languages (something which is now supported by the Zooniverse). A
-multi-lingual user base would come with its own set of challenges, especially
-in terms of volunteers' continuing training and interactions on \Talk.
-
-The second way to scale up the number of high contribution classifiers is to
-increase the rate at which new volunteers become dedicated volunteers. Based
-on feedback from the wider \SW community, this could potentially be achieved
-through closer collaboration with the science team. It's also possible that
-the dynamic \StageTwo system proposed in the previous section may act as an
-incentive to some volunteers to increase their contribution (while gaining
-skill in order to ``reach'' \StageTwo). Reducing the rate at which  new
-volunteers lose interest could also play a role. Anecdotally, it seems fairly
-common for new volunteers to be wary of classifying at all, for fear of
-introducing errors. Better explanation of how their early classifications are
-analyzed could help assuage these fears: \Sref{sec:results:crowd} shows that
-effectively down-weighting new users' classifications (by setting their
-agents' initial confusion matrix elements to those of a random classifier)
-leads to best performance, a result which should be of some comfort to the
-nervous volunteer.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusions}
-\label{sec:conclude}
-
-We have designed, implemented and tested a system for   detecting new strong
-gravitational lens candidates in wide field imaging surveys by crowd-sourced
-visual inspection. The \SW web-based classification interface presents carefully
-prepared colour composite sky images to volunteers, who mark features they
-propose to  have been lensed. The participants receive ongoing training with a
-mixture of simulated lens and known-to-be-empty images, and we use this
-information to inform the automated interpretation of their markers. In our
-first lens search we simply divided the \cfhtls imaging into some 430,000 tiles,
-and collected over 11~million volunteer image classifications.
-
-% Questions we set ourselves in the introduction:
-% \begin{itemize}
-% \item How reliably can we find gravitational lenses using the \SW
-% system? What is the completeness of the sample produced likely to be?
-% \item How noisy is the system? What is the purity of the sample
-% produced?
-% \item How quickly can lenses be detected, and non-lenses be rejected?
-% How many classifications, and so how many volunteers are needed per target?
-% \item What can we learn about the scalability of the crowd-sourcing approach?
-% \end{itemize}
-
-By analyzing the  classifications made of the training set, we conclude that
-gravitational lens detection by crowd-sourced visual inspection works,  and in
-the following specific ways:
-
-\begin{itemize}
-
-\item Participation levels were high (over 36,000 volunteers, contributing
-classifications at rates between $10^3$ and $10^4$ images per hour), suggesting
-that if this can be maintained, visual inspection of tens of thousands of images
-could be performed on timescales of weeks.
-
-\item Over the course of the two stages of the \cfhtls project, the
-set of images was reduced by a factor of $10^3$ (from a few hundred thousand to
-a few hundred), enough for an expert team to take over.
-
-\item The ``skill'' of the volunteers correlates strongly with the number of
-images they have classified.  Quantifying the ``contribution'' as the integrated
-skill over the test subjects  classified, we find that about 90\% of the
-contribution was made by a few  hundred volunteers -- but that the width of the
-skill distribution means that a  few thousand volunteers could have made
-comparable contributions, had they classified more images.
-
-\item The optimal true positive rate (completeness) and false positive rate in
-the training set were estimated to be around $91--93\%$ and $<1\%$ (Stages 1 and
-2). This FPR translates to an approximate purity of 20\%.
-
-\item The simulated gravitational lenses that were missed were predominantly
-galaxy-scale lenses with faint blue galaxy sources, whose lensed features are
-difficult to distinguish from the light from the lens galaxy. We observed some
-additional scatter, with some simulated lenses accumulating low probability
-simply due to classification noise.
-
-\end{itemize}
-
-In \PaperTwo we present the results of this \cfhtls lens search in more detail,
-in particular focusing on the detection of real lenses, and the comparison
-between \SW and various automated lens finding methods. In this paper  we have
-shown how \SW provides a lens candidate detection service, crowd-sourcing the
-time-consuming work of visually inspecting astronomical images for
-gravitationally-lensed features. We invite survey teams searching for lenses in
-their wide-field imaging data to contact us if they would like our help.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%  ACKNOWLEDGMENTS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Acknowledgements}
-
-We thank Stuart Lynn, Kelly Borden, Laura Whyte, Brooke Simmons,
-David Hogg, Thomas Jennings, Layne  Wright, Cecile Faure, Jonathan Coles, Stuart
-Lowe and Jean-Paul Kneib for many useful conversations about citizen science and
-gravitational lens detection, and to the Dark Energy Survey and Pan-STARRS strong
-lensing science teams for their suggestions and encouragement.
-
-PJM and ES also thank the Institute of Astronomy and Astrophysics, Academia Sinica
-(ASIAA) and Taiwan's Ministry of Science and Technology (MOST) for their
-financial support of the workshop ``Citizen Science in Astronomy'' in March
-2014, at which some parts of the SWAP analysis was developed.
-
-\input{acknowledgments.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%  APPENDICES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Probabilistic Classification Analysis}
-\label{appendix:swap}
+\subsection{SWAP: the \SW Analysis Pipeline}
+\label{sec:swap:details}
 
@@
 subject being a $\LENS$, given both its volunteer's classification, and its
-volunteer's experience. In this appendix we describe how these agents work,
+volunteer's experience. In this section we describe how these agents work,
 and other aspects of the \SW analysis pipeline (SWAP).
@@
 \subsection{Agents and their Confusion Matrices}
-\label{appendix:swap:probabilities}
+\label{sec:swap:details:probabilities}
 
@@
 
-\subsection{Examples}
-\label{appendix:swap:examples}
+\subsubsection{Examples}
+\label{sec:swap:details:examples}
 
@@
 
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
 \subsection{Online SWAP: Updating the Subject Probabilities}
-\label{appendix:swap:examples}
+\label{sec:swap:online}
 
@@
 
-\subsection{Information Gain per Classification, Agent ``Skill'' and ``Contribution''}
-\label{appendix:swap:examples}
+Finally, the confusion matrix obtained from the application of
+\Eref{eq:app:fraction} has some inherent noise which reduces as the
+number of training subjects classified by the agent's volunteer
+increases. For simplicity, the discussion has thus far assumed the case
+when the confusion matrix is known perfectly; in practice, we allow for
+uncertainty in the agent confusion matrices by averaging over a small
+number of samples drawn from Binomial distributions characterised by the
+matrix elements $\pr(C_k|\LENS,\trainingk)$ and  $\pr(C_k|\NOT,\trainingk)$. The
+associated standard deviation in the estimated subject probability
+provides an error bar for this quantity.
+
+In \Sref{sec:results} and \Aref{appendix:swap} below, we define several
+quantities based on the probabilities listed above that serve to quantify the
+performance of the crowd in terms of the information they provide via their
+classifications, and report on the performance of the system in returning a
+sample of lens candidates as a function of $\pr(\LENS|C,T)$ threshold.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Offline SWAP}
+\label{sec:swap:offline}
+
+The probabilistic model described above does not need to be implemented as an
+online inference. Indeed, it might be more appropriate to perform the inference
+of all agent confusion matrix elements and subject probabilities simultaneously.
+Such a joint analysis would implement in full the agents' basic model assumption
+that their volunteers have innate and unchanging talent for lens spotting, that
+is parameterised by two constant confusion matrix elements which simply need to
+be inferred given the data.
+
+We refer to this alternative calculation as ``offline'' analysis, because it
+does not need to be carried out one classification at a time (and hence can be
+done at any time after the data is collected). Note that in this offline
+inference, the effect will be that of applying the time-averaged confusion
+matrices to each classification,  rather than a set that evolves as the agents
+(and in the real world, the volunteers) learn. This will mean  that the early
+classifications will effectively not be downweighted as a result of the agent's
+ignorance. On the other hand, this ignorance could also have provided some
+conservatism, reducing the noise due to early classifications if they are
+unreliable. Whether or not an offline analysis out-performs an online one is a
+matter for experiment.
+
+The mechanics of how we carry out the offline inference  will be presented
+elsewhere (Davis et al, in preparation). Here we briefly note that the procedure
+is to maximize the joint posterior probability distribution for all the model
+parameters (some 74,000 confusion matrix elements and 430,000 subject
+probabilities) with a simple expectation-maximisation algorithm. This takes
+approximately the same CPU time as the \StageTwo online analysis, because no
+matrix inversions are required in the algorithm. The algorithm scales well, and
+is actually faster than the online analysis with the larger \StageOne dataset.
+The expectation-maximisation algorithm is robust to initial starting parameters
+in, e.g., initial agent confusion matrix elements and Subject probabilities. The
+difference in performance between the online and offline analyses is presented
+in  \Sref{sec:results:sample} below.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Practicalities}
+\label{sec:swap:practicalities}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_probabilities.png}
+\caption{Typical \SW agent confusion matrix elements. At a particular
+snapshot, 200 randomly-selected agents are shown distributed over the unit plane, with a
+tendency to move towards the ``astute'' region in the upper right hand
+quadrant as each agent's volunteer views more images. Yellow point size is
+proprtional to the number of images classified; green point size shows
+agent-perceived ``skill.''}
+\label{fig:swap:agent-probabilities}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure}
+%\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_histories.png}
+%\caption{Typical \SW agent histories. The ``skill'' of the  same 200 random
+%agents  as in \Fref{fig:swap:agent-probabilities} is plotted in green as a function
+%of the number  of subjects classified (``effort''). The yellow histogram in
+%the background shows the distribution of effort.}
+%\label{fig:swap:agent-histories}
+%\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\Fref{fig:swap:agent-probabilities} shows the confusion matrix elements of 200
+randomly-selected agents, as they were on a particular day during the
+\StageOne online analysis. Many volunteers classify  only a small number of images, and
+so their agents' confusion matrix elements have remained close to their initial values
+of (0.5,0.5). As more images are classified (shown by the yellow point size),
+the agents' matrix elements tend to move towards higher values, partly as the
+volunteers attain greater skill levels (green point sizes, see
+\Sref{sec:results} below) but mostly as
+the agent learns more about them. In this upper
+right-hand quadrant, the agents perceive their volunteers to be ``astute.''
+
+%\Fref{fig:swap:agent-histories} shows the ``skill'' (\Sref{sec:results:crowd})
+%of the same small sample of agents evolving as their volunteers classify images.
+%The underlying histogram shows the distribution of classification number: a long
+%tail to very high ``effort'' can be seen.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_trajectories.png}
+\caption{Typical \SW \StageOne subject trajectories. Top: 200 randomly-selected
+subjects drift downwards as they are classified, while being nudged left and
+right in probability by the agents as they interpret the volunteers input. The
+dotted vertical lines show (left to right) the retirement threshold, prior
+probability, and the detection threshold. Different colours denote the different
+kinds of subject. Bottom panel: histograms of all the subject probabilities
+computed to date, sub-divided by subject kind.}
+\label{fig:swap:subject-trajectories}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+During \StageOne classification of the \cfhtls images, we assigned a prior
+probability for each image to contain a lens of $2\times10^{-4}$, based on a
+rough estimate of the number of expected lenses in the survey, and the fraction
+of the survey area covered by each image. We then assigned two values of the
+images' posterior probability, $\pr(\LENS|C,T)$, to define ``detection'' and
+``rejection'' thresholds. These were set to be 0.95 and (approximately
+symmetrically in the logarithm of probability), $10^{-7}$. Subjects that
+attained probability of less than the rejection threshold were scheduled for
+retirement and subsequently ignored by the analysis code. Subjects crossing the
+detection threshold were also subsequently ignored, but they were not
+retired from the website, just so that more volunteers could see them.
+The progress of the subjects is illustrated in
+\Fref{fig:swap:subject-trajectories}. Subjects appear on this plot at the tip of
+the arrow, at zero classifications and prior probability; they then drift
+downwards as they are classified by the crowd, with each agent applying the
+appropriate kick in probability based on what it hears its volunteer say.
+Encouragingly, sims (blue) tend to end up with high probability, while duds
+(red) pile up at low probability; test subjects (black) mostly drift to low
+probability, but some go the other way. The latter will help make up the
+candidate sample. As this plot shows, around 10 classifications are typically
+required for a subject to reach the retirement (or detection) threshold.
+
+The analysis code was run every night during the project, and subjects retired
+in batches after its completion. This introduced some inefficiency, because
+some classifications were accumulated in the time between them crossing the
+rejection threshold and the subject actually being retired from the website.
+As subjects were retired from the site, more subjects were activated. In this
+way, the volunteers who down-voted images for not containing any lensed
+features enabled new images to be shown to other members of the community.
+
+When all the subjects had either been retired, or classified around 10 times or
+more, the web app was paused and reconfigured for \StageTwo. The sample of
+subjects classified during \StageTwo was selected to be all those that passed
+the detection threshold ($\pr(\LENS|C,T) > 0.95$) at \StageOne. These were
+classified for one week, with no retirement but a maximum classification number
+of 50 each. The number of subjects at \StageTwo was small enough that we did not
+need to retire any: instead, we simply collected classifications for a fixed
+period of time (about 4 weeks). Without the time pressure motivating the online
+calculation of \StageOne, we carried out an offline analysis
+(\Sref{sec:swap:offline} above) of the  \StageTwo classifications, for
+comparison and as we will see in the next section, improving the pipeline
+performance.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Results}
+\label{sec:results}
+
+In this section we present our findings about the performance of the \SW system,
+in terms of the classification of the training set, the  information contributed
+by the crowd, and the speed at which the image set was classified.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Sample Properties}
+\label{sec:results:sample}
+
+We first quantify the performance of the \SW system in terms of the recovery of
+the training set images. At \StageOne, this set contained around 5712 simulated
+lenses, and 450 duds; at \StageTwo, we used 152 images of simulated lenses and
+201 duds selected as \StageOne false positives (\Sref{sec:design:stages:two}).
+\Fref{fig:results:sample:roc} shows receiver operating characteristic (ROC)
+curves for \cfhtls \StageOne and \StageTwo. These plots show the true positive
+rate (TPR, the number of sims correctly detected divided by the total number of
+sims in the training set), and the false positive rate (FPR, the number of duds
+incorrectly detected  divided by the total number of duds in the training set), both
+for a given sample of detections defined by a particular probability threshold,
+which varies along the curves.  In both stages, these curves show that true
+positive rates of  around 90\% were achieved, at very low false positive rates.
+
+For comparison we show the results of an analysis where the classifications of
+training images were ignored, and the agents' confusion matrix elements
+were instead all simply assigned initial values of 0.75
+which then remained constant. This set-up emulates a
+very simple unweighted voting scheme, where all classifications are treated
+equally.  In this case, the TPR remains under 80\% in \StageOne and 60\% in
+\StageTwo, thus illustrating the benefit of including training images and
+allowing the agents to learn via their Bayesian updates.
+
+When the agents are allowed to update their confusion matrices, the choice of
+initial confusion matrix is not very important: the same 0.75 initial values
+applied to normal, learning agents resulted in only a slightly lower TPR than
+the default case.
+
+The dot-dashed curves show the impact of the offline analysis. At \StageOne the
+results are very similar to the online version that was actually run (solid
+line). However, at \StageTwo there is marginal evidence of there being greater
+benefit to doing the analysis offline (\Sref{sec:swap:offline}).
+Over 85\% TPR is achieved at zero FPR in the offline analysis , while if one is
+willing to accept a false positive rate of 5\%, the true positive rate rises to
+over 95\%, showing that some of the sims that were missed in the online analysis
+may be being recovered by doing the analysis offline. The same is true at
+\StageOne, but to a lesser extent. Assuming Poisson statistics for the
+fluctuations in the numbers of recovered lenses, the uncertainty in the measured
+\StageTwo TPR values is around 8\%, but the online and offline samples are
+highly correlated, such that the uncertainty on the difference between the ROC
+curves is somewhat less than this. Still, a larger validation set is needed to
+test these algorithmic choices more rigorously. At \StageOne, high TPR can be
+measured to better than 1\%.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{minipage}{0.45\linewidth}
+  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage1_ROC.pdf}
+\end{minipage}\hfill
+\begin{minipage}{0.45\linewidth}
+  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage2_ROC.pdf}
+\end{minipage}
+\caption{Receiver operating characteristic curves for the \SW system, using
+the \cfhtls training set. Left: \StageOne, right: \StageTwo. Insets show a
+magnified view of the top lefthand corner of each plot. Linestyles illustrate
+the agent properties (initial confusion matrix elements, learning or not)
+discussed in the text, as well as the difference between the online and offline
+analyses. The \StageTwo sample was defined using the online \StageOne results
+(solid blue curve), while the offline analysis was chosen for the final
+\StageTwo results (dot-dashed orange curve). }
+\label{fig:results:sample:roc}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Adopting the online \StageOne analysis, and the offline \StageTwo analysis, we
+show in \Fref{fig:results:sample:CP} a plot of the more familiar (to
+astronomers) quantities of completeness versus purity, again for
+the two stages. As in \Fref{fig:results:sample:roc}, the detection threshold
+varies along the curves. Completeness is defined as the number of correctly
+detected sims divided by the total number of sims in the training set, while
+purity is the number of correct detections divided by the total number of
+detections.\footnote{The completeness is equivalent to the TPR and is also
+known elsewhere as the ``recall.''  The purity is also known as the
+``precision.''} If the training set samples from the same systems as the test
+set, then the completeness of the training set will be equivalent to the
+completeness of the test set. The purity depends on the proportion of sims to
+duds, and so the purity of the test set must be approximated by rescaling the
+training set to the expected proportion of lens systems to not-lens systems in
+the survey. First we compute the expected number of false positives by
+multiplying the FPR by the expected number of non-lenses in the survey. Then
+we multiply the TPR by the expected number of lenses in the survey, to get the
+expected number of true positives. The sum of the true positives and the false
+positives gives the expected sample size; dividing the expected number of true
+positives by this sample size gives the purity. Note that the completeness is
+invariant to this transformation.
+The \StageOne curves are truncated by the retirement of subjects in this phase,
+which sets the minimum size of this sample. We see from the solid blue curve
+that over 90\% completeness was reached, albeit in a sample with around 20\%
+purity.
+
+Does this performance level vary between the different types of gravitational
+lens? To investigate the completeness to the three different types of lens in
+the training set, we repeated the same procedure but now considering only the
+detections of a certain kind of lens and of the non-lenses in the training set.
+We estimate the expected number of lenses and non-lens false positives by
+dividing the lens and dud sets into equal fractions. The lensed quasar part of
+the training set yielded the highest completeness, suggesting that these were
+the easiest sims to spot. The lensed galaxies were recovered at the lowest
+completeness, likely due to the difficulty  of separating the lens and source
+galaxy light.
+
+At \StageTwo, where no retirement was carried out, it was possible to reach
+100\% purity: the knee of the curve is at just under 90\% completeness. However,
+the purity decreases rapidly if higher completeness than this is sought. The
+optimal sample in this simulated lens search experiment would have been
+constructed with a threshold value of $\pr(\LENS|C,T) > 0.47$. At 100\% purity
+and 90\% completeness, it would have contained around 89 lens candidates.
+However, we remind the reader that all these values are dependent on the
+properties of the training subjects, which were chosen to be fairly
+visible: we expect the completeness to real lenses to be somewhat lower, as a
+result.
+
+% TP + FN ~ 2e-4 * 430000 ~ 100 ~ TP/C ; so TP ~ 89 candidates
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering\includegraphics[width=\linewidth]{sw-system-figs/completeness_purity_simple.pdf}
+\caption{Completeness-estimated purity curves for the \sw system, using
+the \cfhtls training set.}
+\label{fig:results:sample:CP}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Crowd Properties}
+\label{sec:results:crowd}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/all_skill_contribution_experience_education.pdf}
+\caption{Key properties and contributions of the \SW \StageOne crowd.
+Plotted are the 1-D
+and 2-D smoothed marginalized distributions for  the logarithms of the
+properties of the agents described in the text. The contours
+contain 68\%, 95\% and 99\% of the distributions.}
+\label{fig:crowd:cornerplot}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To investigate the properties of the \sw crowd, as characterised by their
+agents, we define the following quantities and plot their one and 2-D marginal
+distributions in
+\Fref{fig:crowd:cornerplot}. This figure only shows the \StageOne agents for clarity,
+but the trends we found the same trends in \StageTwo.
+%
+\begin{description}
+%
+\item{\noindent\bf ``Effort:''} The number of test images, $\effort$, classified
+by a volunteer. In \StageOne, the mean effort per agent was 263; in the shorter
+\StageTwo it was 81.
+%
+\item{\noindent\bf ``Experience:''} The number of training images, $\experience$,
+classified by a volunteer. In \StageOne, the mean experience per agent was 29;
+in \StageTwo (where the training image frequency was set higher) it was 34.
+%
+\item{\noindent\bf ``Skill:''} The expectation value of the information gained
+per classification (in bits) by that volunteer,  $\skill$, for subjects which
+have lens probability 0.5 (\Aref{appendix:swap}). Random classifiers have
+$\skill = 0.0$~bits, while perfect classifiers have $\skill = 1.0$~bit.
+All agents start
+with $\skill = 0.0$~bits. The skill of  an agent increases as training subjects are
+classified, and the agent's estimates of its confusion matrix elements improve.
+In \StageOne, the mean skill per agent was 0.04 bits; in  \StageTwo it was
+0.05~bits.
+%
+\item{\noindent\bf ``Contribution:''} This is the integrated skill over a volunteer's
+{\it test subject} classification history, a quantity representative of the
+total contribution to the project made by that volunteer (see \Aref{appendix:swap} for
+more discussion of this quantity). The classifications of training images
+determine the skill, while the classification of test images determines
+contribution.  In \StageOne, the mean  contribution per agent was
+34.9 bits; in \StageTwo it was 33.5.
+%
+\item{\noindent\bf ``Information:''} The total information $\information$
+generated by the agent during the volunteer's classification activity. This
+quantity depends on the value of each subject's lens probability when that
+subject was presented to the volunteer (simply because information gain is
+defined in terms of posterior relative to prior probabilities,
+\Aref{appendix:swap}).  Because of this, we expect this raw quantity to be noisier
+than the ``contribution'' defined above. The lower righthand panel of
+\Fref{fig:crowd:cornerplot} confirms this: there is a strong, linear correlation
+between contribution and information gain, but at a given contribution, the
+distribution of information gain has a tail at high values, corresponding to
+volunteers that were lucky in the number of high probability subjects that they
+happened to be shown (the information gain per classification is maximized when the
+subject probability is 0.5, while most subjects have probabilities closer to or less than the prior).
+In most of the following discussion we use the contribution when characterizing
+crowd participation, but we include
+the information gain for completeness.
+%
+\end{description}
+
+The leftmost column of \Fref{fig:crowd:cornerplot} shows how the last four of
+these properties depends on the effort expended by the volunteers. As expected,
+we see that experience is tightly correlated with effort, reflecting the design
+of training images being presented throughout each stage (albeit at decreasing
+frequency). We also see a strong correlation between effort and skill, which was
+hoped for but not guaranteed: the more images the volunteers see, the better
+able to contribute information they are.
+
+The effort distribution shows two peaks, suggestive of two types of
+participation.  The sharp spike at just a few images classified presumably
+corresponds to visitors who only classify a few subjects before leaving the site
+again. The broader hump contains people doing tens to hundreds of
+classifications: the skill vs.\ experience panel of \Fref{fig:crowd:cornerplot}
+shows this group to achieve a broad distribution of  skill, peaking at around
+0.05 but with a long tail to higher values.
+
+At high values of experience and effort, the skill is \emph{always high}. There
+seem to be very few agents logging large numbers of classifications at low
+skill: {\it almost all high effort
+``super-users'' have high skill.} These two properties are reflected in both the
+contributions these volunteers make (third row) and the information they
+generate (fourth row).
+
+We found that the distributions for the \StageTwo agents to be qualitatively
+very similar to those for the \StageOne agents. The differences are: 1) the
+maximum effort possible at \StageTwo is smaller, simply because fewer subjects
+were available to be classifed, and 2) the information generated per agent was
+slightly higher at \StageTwo, just because the subjects had (on average) higher
+probability.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_contrib_cumul.pdf}
+\caption{Cumulative distributions of the contributions made by the agents: 90\%
+of the contribution was made by the highest contributing 1\% of the crowd at
+\StageOne (blue), and the highest contributing  7\% of the crowd at \StageTwo
+(orange). The \StageOne agents are shown in blue, the \StageTwo agents in
+orange. ``Experienced volunteers'' classified 10 or more training subjects.}
+\label{fig:crowd:cumulplot}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\Fref{fig:crowd:cornerplot} shows the \SW crowd to have quite broad
+distributions of logarithmic effort, skill, and contribution. To better
+quantify the contributions made by the volunteers, we show their cumulative
+distribution on a linear scale in \Fref{fig:crowd:cumulplot}. This plot shows
+clearly the importance of the most active volunteers: at
+\StageOne,  1.0\% of the volunteers -- 375 people -- made 90\% of the
+contribution.  At \StageTwo, where it was not possible to make as
+many classifications before running out of subjects, 7.2\% of the volunteers
+-- 141 people -- made 90\% of the contribution.
+
+However, it is not the case that only these small groups were {\it capable} of
+making large contributions. The cumulative distribution of agent skill is shown
+in \Fref{fig:crowd:cumulskillplot}: these distributions are significantly
+broader than the corresponding distributions of agent contribution, in
+\Fref{fig:crowd:cumulplot}. For example,
+the most skilled 20\% of agents possess around 80\% of the skill.
+
+The inexperienced volunteers also possess a significant fraction of the skill.
+We find that dividing the crowd into ``experienced volunteers'' (who have seen
+10 or more training images), and ``inexperienced volunteers'' (the rest),
+results in two groups containing approximately equal total skill (see the dashed
+curve in \Fref{fig:crowd:cumulskillplot}). The most skillful 20\% of {\it
+experienced} volunteers (1824 people) only possess 43\% of the total skill.
+The breadth of the skill distributions suggests that  the high level of
+contribution made at \SW by experienced volunteers is largely a matter of choice
+(or perhaps, availability of time!). There were many other volunteers that  were
+skillful enough to make large contributions -- they just didn't classify as many
+images.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_skill_cumul.pdf}
+\caption{Broad cumulative distributions of agent skill:
+the most skilled 20\% of the crowd only possess around 80\% of the skill,
+at \StageOne. The \StageOne agents
+are shown in blue, the \StageTwo agents in orange. ``Experienced volunteers''
+classified 10 or more training subjects.}
+\label{fig:crowd:cumulskillplot}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Classification Speed}
+\label{sec:results:speed}
+
+How fast does the \SW crowd classify subjects? Each agent records the timestamp
+of each classification its volunteer makes; by measuring the time lags between
+successive classifications, we can make estimates of the crowd's classification
+and contribution speed. We plot the former quantity for both \StageOne and
+\StageTwo in \Fref{fig:results:speed}, normalizing the speed and time axes to
+their respective totals. The fractional classification rates
+in each stage of the survey fall off in approximately the same way, despite the
+factor of nearly 20 difference in crowd size. \StageOne (consisting of
+$\sim430,000$ subjects) was completed in around 5000 hours (by some 37,000
+participants), with classification rates in the first few days averaging at
+$\sim10^4$ per hour. This was stimulated by various forms of advertising (press
+releases, and emails to registered Zooniverse users). The asymptotic
+classification rate was  around ten times lower, at $\sim10^3$ per hour.
+Interestingly, the average skill was found to be approximately constant over the
+lifetime of \StageOne, leading to a contribution rate that tracks closely the
+classification rate. (A 10\% increase in average skill was seen over the first
+40 days, and a decrease of the same amount in the last 40 days -- not enough to
+cause a significant difference between classification and contribution rate
+behavior, but perhaps reflecting a learning period at the start and then a
+decrease
+in participation late on.) \StageTwo (3700 subjects) was completed in around 600
+hours by around 2000 participants, with classification rates starting at
+$~\sim2000$ per hour and decaying to $\sim100$ per hour.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering\includegraphics[width=\linewidth]{sw-system-figs/rate_classification.pdf}
+\caption{Fractional classification rate in the \SW \cfhtls survey. Fractional classification rate is the number
+of classifications per unit time, divided by the final total number of
+classifications. Fractional survey time is the time elapsed since the beginning
+of the survey, divided by the total length of the survey. The unit of time in
+the fractional  classification rate is one survey, so that the curves in
+integrals under the curves are both one. }
+\label{fig:results:speed}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The similarities between \StageOne and 2, suggest that these numbers could be
+scaled to estimate the speed of future \SW projects (or at least those following
+a similar blind search strategy). For example, the completion time for a \SW
+project may be approximated as
+\begin{equation}
+    \tau \approx \tau_0 \left(\frac{10^4}{N_p}\right)
+                               \left(\frac{N_s}{10^4}\right),
+\label{eq:speed}
+\end{equation}
+where $N_s$ is the number of subjects to be classified, and $N_p$ is the number
+of volunteers in the crowd. Just using the numbers above, we find a characteristic
+timescale of $\tau_0 = 18\,{\rm days}$, but as we will see in the next section,
+we expect this to be significantly shorter in future projects.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Discussion}
+\label{sec:discuss}
+
+What can we learn from the results of the previous section, for future
+projects? Potential improvements to the \SW system can be divided into three
+categories, performance, efficiency and capacity.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}
+\begin{minipage}{\linewidth}
+  \begin{minipage}[t]{0.47\linewidth}
+    \begin{minipage}{0.46\linewidth}
+      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0008wyp_gri.png}
+    \end{minipage}\hfill
+    \begin{minipage}{0.50\linewidth}
+      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0008wyp_stage2_trajectory.png}
+    \end{minipage}
+  \end{minipage}\hfill
+  \begin{minipage}[t]{0.47\linewidth}
+    \begin{minipage}{0.46\linewidth}
+      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0006rkx_gri.png}
+    \end{minipage}\hfill
+    \begin{minipage}{0.50\linewidth}
+      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0006rkx_stage1_trajectory.png}
+    \end{minipage}
+  \end{minipage}
+\end{minipage}
+
+\vspace{\baselineskip}
+
+\begin{minipage}{\linewidth}
+  \begin{minipage}[t]{0.47\linewidth}
+    \begin{minipage}{0.46\linewidth}
+      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0000fgj_gri.png}
+    \end{minipage}\hfill
+    \begin{minipage}{0.50\linewidth}
+      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0000fgj_stage1_trajectory.png}
+    \end{minipage}
+  \end{minipage}\hfill
+  \begin{minipage}[t]{0.47\linewidth}
+    \begin{minipage}{0.46\linewidth}
+      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0003j2s_gri.png}
+    \end{minipage}\hfill
+    \begin{minipage}{0.50\linewidth}
+      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0003j2s_stage1_trajectory.png}
+    \end{minipage}
+  \end{minipage}
+\end{minipage}
+\caption{Illustrative examples of
+false negatives (blue) and false positives (red) from the classification of
+the \SW \cfhtls training set. The trajectory plot for each of the 4 subjects is
+shown to the right of its image. Lefthand panels show the most common types of
+trajectories: short step random walks resulting from no high skill classifiers
+viewing the subject. The righthand panels show examples where higher skill
+classifiers have been involved, causing random walks with longer step lengths
+(top) and catastrophic mis-classifications (bottom right). Note that both these
+subjects were {\it very nearly} detected but didn't quite reach the threshold
+set (marked by the blue dashed line). Insets for the false
+negatives show the lens feature. The inset for the lower righthand panel shows
+where most users believed a lens was located. There is no corresponding inset
+for the lower left panel because no particular feature stood out to users.
+Instead, users clicked many different features.}
+\label{fig:discuss:performance:trajectories}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Improving performance: reducing incompleteness and impurity}
+\label{sec:discuss:performance}
+
+We investigated the source of the incompleteness and impurity visible in
+\Fref{fig:results:sample:CP}, by examining the \StageTwo false negatives and
+false positives, and their behaviour as they are classified using the online
+analysis trajectory plots introduced in \Sref{sec:swap}
+(\Fref{fig:swap:subject-trajectories}).
+\Fref{fig:discuss:performance:trajectories} shows 2 example simulated lenses
+that were missed ($\pr(\LENS|C,T) < 10^{-5}$) by the \SW system (top row),
+and 2 example
+non-lenses that were incorrectly flagged as candidates ($\pr(\LENS|C,T) >
+0.95$) by the \SW system (bottom row).
+While the final \StageTwo analysis was done offline,
+these trajectory plots still serve to illustrate the approximate
+classification histories of the subjects.
+
+In some cases the rejection of the false negatives is understandable: the
+lensed features are faint, or in some cases, somewhat unrealistic as lenses.
+However, in other cases a reasonably obvious lens was passed over.  This
+mainly seems to be due to noise in the system: when only low-skill classifiers
+view a subject, all the updates to its posterior probability are small, and if
+none are very confident about the presence of lensing, the subject follows a
+random walk down its trajectory plot. This can be seen in the top left panel
+of the figure.
+
+The false positives show similar behaviour, for example in the bottom lefthand
+panel of the figure. As well as subjects being ``unlucky'' in this way, there
+are two less common failure modes associated with mistakes made by higher skill
+users, illustrated in the righthand column of the figure. In the false negative
+subject shown in the top right-hand panel, several high skill classifiers update
+the subject upwards in log probability by some way each time, but other,
+comparable skill classifiers mis-classify the system to lower probability.   The
+trajectory looks like a random walk, but with bigger steps; this particular
+subject came very close to crossing the detection  threshold three times, but
+didn't quite make it. The bottom right-hand panel shows an example of a final,
+apparently rare, failure mode: we see some short-step random walk behaviour,
+followed by a mis-classification by a very high skill ``expert'' classifier
+after 20 classifications that promotes the subject to high probability.
+
+There are a number of places where we can address these problems and
+improve system performance: adding flexibility to the classification
+interface, educating the volunteers, assigning subjects for
+classification, and interpreting the classification data.
+
+Some of  the mistakes made by reasonably high skill
+classifiers working at high speed
+could have perhaps been corrected by those classifiers themselves, had
+they had access to a ``go back'' option. While clearly enabling error
+reduction, we might worry about such a mechanism enabling classifiers to have
+a guess, then go and read the \Talk discussion, and then return to the
+classification interface to change their mind to agree with the forum. In
+fact, this is already possible on the current interface -- and indeed, it is
+not obvious that such correlations would necessarily lead to poorer system
+performance. This could be tested by presenting a fraction of the volunteers
+with a version of the site that actively suggested that they take this
+approach, and then tracking the relative performance of ``collaborative''
+classifications compared with independent ones. We leave the exploration of
+this to further
+work.
+
+Mistakes by both high and low skill classifiers could be reduced by improving
+the training in the system, which could be done in several ways. One is to
+make more training images available to those who want or need it. A basic
+level of training images are needed for SWAP to build up an accurate picture
+of each classifier's skill -- but one could imagine volunteers {\it choosing}
+to see more training images (still at random) in their stream. We could also
+experiment with providing greater training rates early on for all volunteers;
+the risk associated with this is that retention rates may drop if too few
+``fresh'' test images are shown early on. Another way of improving the
+training could be to provide more information about what lenses do. In this
+project, the Spotter's Guide, and the Science, FAQ and About pages were always available on the site, but as a
+passive background resource. We might consider providing more links to this
+guide in the feedback messages shown to the classifiers as they go -- or
+perhaps extending these messages to themselves include more explanations and
+example images. We might also investigate a more dynamic Spotter's Guide: a
+set of manipulable model lenses illustrating all the possible image
+configurations that that those deflectors can make could help volunteers gain
+understanding of what lensed features can look like very quickly. Such a toy
+is under development.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/stage2_veteran_contribution.pdf}
+\caption{\StageTwo classifier skill, as a function of their \StageOne skill.
+Veterans from \StageOne  are shown in blue, while new volunteers are shown in
+orange. Point size is proportional to the total contribution made,
+while dashed lines are drawn at the mean values for each sample.}
+\label{fig:discuss:performance:stage1vstage2}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+However, most identification failures (around 60\%) seem to be due to the
+random walk problem. Short, random direction steps arise from low skill
+classifiers, arising from classifier inexperience (\Sref{sec:results:crowd}).
+While improved training will help reduce this effect, it is here
+that targeted task assignment could also help improve system performance, by
+bringing higher skill volunteers in to the mix. We
+advertised \StageTwo of the current project to all registered users; it was
+taken up by \StageOne veterans with a broad range of skill, and also picked up a
+significant number of new users who did not have enough time to aquire high
+skill (since \StageTwo was quite short): of the 1964 volunteers who took part in
+the \StageTwo classification round, only 774 were veterans from \StageOne.
+
+\Fref{fig:discuss:performance:stage1vstage2} shows how the \StageOne skill maps
+on to \StageTwo skill and contribution.
+This figure suggests that there may be some benefit to opening \StageTwo on the
+basis of \StageOne agent skill, in order to reduce the noise in the system
+generated by new and low skill volunteers in this more difficult
+classification stage.  A simple implementation of this would be to switch the
+web app to the \StageTwo version when either a certain \StageOne skill (and/or
+effort) threshold was passed. Good strategy would probably be to switch back
+to \StageOne after some number of \StageTwo classifications (to avoid losing the
+high skill users from \StageOne entirely), and also to make it very clear which
+stage the classifier was at (since \StageTwo requires more careful attention).
+This is something we plan to experiment with in future.
+
+Finally, there could be some performance gains to be made by improving the
+SWAP agent model, or its implementation. Low skill is typically a result  of
+inexperience (\Sref{sec:results:crowd}), but it could be the agent that is
+inexperienced as well as the classifier or its agent. In a future paper we
+plan to investigate the use of the test images as well as the training images
+in accelerating the agent's learning (Davis et al, in preparation). We also
+plan to investigate the use of offline analysis at \StageOne, for the same
+reason (see also \Sref{sec:discuss:efficiency} below.)
+One might also consider looking at
+introducing more conditional dependences in the confusion matrix elements, to
+allow for some classifiers having greater skill in spotting one type of lens
+than another, or, more generally, as a function of lens property (such as
+colour, brightness, and image separation). In the current model, all agents are
+considered to be completely independent, whereas in fact we might expect there
+to be significant clustering of the confusion matrix elements. A hierarchical
+model for the crowd, with hyper-parameters describing the distribution of
+confusion matrix elements across the population, may well accelerate the agent
+learning process by including the notion of one agent being likely to be
+similar to its neighbours. Finally, it is worth noting that the model of
+\citet{IBCC} explicitly avoids the assumption of the agent confusion matrix
+elements being constant in time, allowing the development of volunteer skill
+to be more accurately tracked -- and that they did see some time-evolution in
+the supernova zoo classifiers' skill. Finding a way to incorporate such a
+learning model into SWAP, while retaining its statistically online character
+is an interesting challenge for future work.
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \begin{figure}
+% \centering\includegraphics[width=0.9\linewidth]{sw-system-figs/early_vs_final_skill.png}
+% \caption{Predictability of final skill from early skill (after 10 training
+% classifications) in \StageOne agents. The dashed lines enclose 649 agents with
+% early skill greater than 0.1
+% who retain final skill of greater than 0.05. Point size is proportional to
+% contribution (plus a constant).}
+% \label{fig:crowd:skillprediction}
+% \end{figure}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% Having seen the importance of the high skill volunteers at both \StageOne and
+% \StageTwo, we might ask, can we predict agent skill after, say, the volunteer
+% has experienced 10 training subjects? In \Fref{fig:crowd:skillprediction} we
+% plot this ``early skill'' against final skill, for all experienced \StageOne
+% volunteers. The majority of the crowd shows little correlation, but at the
+% high early skill end, some predictability appears. The 649 experienced \StageOne
+% volunteers who had early skill greater than 0.1 went on to attain a mean
+% final skill of 0.22, with 97\% remaining at skill 0.05 or higher. This
+% suggests that it might be worth tracking volunteers' skill as a project
+% progresses, in order to encourage those showing an aptitude for the task to
+% take part in the more difficult activities, such as \StageTwo refinement.
+% However, this would not have done a very good job at identifying the
+% volunteers who went on to make the largest contributions: the point size in
+% \Fref{fig:crowd:skillprediction} is proportional to contribution (plus a constant):
+% many of the highest contributors showed relatively low skill early on.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Improving efficiency}
+\label{sec:discuss:efficiency}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table*}
+\begin{center}
+\caption{Total crowd and subject sample properties from the \cfhtls project.}
+\label{tab:crowd:contributions}
+\begin{tabular}{cccccccc}
+  \hline
+  % \hline {Stage} & Subjects & Contribution                          & Agents & Skill      & Classifications          & Candidates & Information \\
+  %                & $\Ns$    & $\sum_k^{\Nv} \contribution_k$ (bits) & $\Nv$  & $\sum_k^{\Nv} \skill_k$ (bits) & $\sum_k^{\Nv} \thiseffort$ & $\Ncands$  & $\sum_j^{\Ns}\sum_k^{\Nv} \information_{j,k}$ (bits) \\
+  % \hline
+  %           1    & $427064$ & $1292016.3$ & $36982$ & $1471.9$ & $10802125$ & $3368$ & $91122.6$ \\
+  %           2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $90$ &  $1640.4$ \\
+  \hline {Stage} & Subjects & Contribution                          & Agents & Skill      & Classifications          & Candidates & Information \\
+                           & $\Ns$    & $\sum_k^{\Nv} \contribution_k$ (bits) & $\Nv$  & $\sum_k^{\Nv} \skill_k$ (bits) & $\sum_k^{\Nv} \thiseffort$ & $\Ncands$  & $\sum_j^{\Ns}\sum_k^{\Nv} \information_{j,k}$ (bits) \\
+            \hline
+                      1    & $427064$ & $1292016.3$ & $36982$ & $1471.9$ & $10802125$ & $3368$ & $91122.6$ \\
+                      2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $90$ &  $1640.4$ \\
+  \hline \hline
+\end{tabular}
+\medskip\\
+\end{center}
+\end{table*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\Tref{tab:crowd:contributions} shows the total effort, contribution, skill and
+information generated in both \StageOne and 2 of the \cfhtls project, with the
+total numbers of agents and subjects for comparison.   These numbers allow us
+to quantify the efficiency of the system.
+
+The contribution per classification is defined in terms of a hypothetical
+subject with lens probability of 0.5; one bit of information is needed to
+update such a subject's lens probability to either zero or one. This means
+that a maximally complete classification stage would yield a total
+contribution (summed over all agents) equal to the number of subjects. The
+ratio of this hypothetical optimum to the actual total contribution is
+therefore a measure of the stage's inefficiency. We find our inefficiency (by
+dividing column 2 by column 3) to be 33\% and 17\% in \StageOne and \StageTwo
+respectively. In \StageOne, this inefficiency is due to the daily processing: we
+were not able to retire subjects fast enough, and so they, remained in the
+system, being over-classified. Indeed, only 3705745 classifications were
+needed to retire all the subjects: the ratio of this to the total number made
+is 34\%. (The remaining 1\% is due to not all subjects being classified to 1
+or 0 probability.) At \StageTwo, we did not retire any subjects at all; the
+inefficiency in this case was by design, to give everyone a chance to
+appreciate what they had found together. (An unwanted side effect of this
+policy was noted in \Fref{fig:discuss:performance:stage1vstage2} in the
+previous sub-section.)
+
+It is clear that to increase the efficiency of the system we need to reduce
+the time lag between the classification being made and its outcome being
+analyzed. The optimal way to do this would be to have the web app itself
+analyze the classifications in a fully online system. This is under
+investigation for future projects. With the classification data being analyzed
+in real time, there may still be a place for a daily or weekly offline
+analysis: this could potentially reduce the false negative and false positive
+rates by ``resurrecting'' subjects that had been retired by the online system
+before the agents had time to learn enough about their classifier's high
+skill.
+
+If the system efficiency could be improved by a factor of three, we would expect
+the characteristic completion time $\tau_0$  in \Eref{eq:speed} to decrease by
+roughly the same factor, suggesting that a dataset of $10^4$~images could be
+searched for lenses by a crowd of $10^4$ volunteers in about 6 days.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Increasing capacity}
+\label{sec:discuss:capacity}
+
+Finally, we comment on the size of the first \SW crowd, and how the system might
+be scaled up for future surveys. In \Sref{sec:results:crowd} and
+\Tref{tab:crowd:contributions}, the following rough picture emerged for the \SW
+crowd in this project: it consisted of a few $10^4$ volunteers, with a few
+$10^3$ achieving considerable skill, and a few $10^2$ having the time to make a
+significant contribution. Slightly more quantitively, we might note that  the
+total skill of the crowd, computed by summing the skill of all the agents, is a
+measure of the effective crowd size, in the sense that a crowd of perfect
+classifiers would be of this size. By this measure,the \StageOne crowd was
+equivalent to a team of 1470 perfect classifiers, while the \StageTwo crowd was
+equivalent to a team of 102 perfect classifiers. With this same crowd, we saw in
+\Sref{sec:results:speed}  that surveys providing a few $10^4$ subjects would be
+completed quickly, if the high contribution rate of the current crowd were to be
+repeated.
+
+There are (at least) two ways in which we might increase the numbers of
+high-contribution volunteers for larger projects in future. The first is
+simply to increase the total crowd size, and hope that a similar fraction of
+volunteers make large contributions. Greater exposure of the website to the
+public through mass media would help. Another option is to advertise the
+project to new groups of volunteers by translating the website into other
+languages (something which is now supported by the Zooniverse). A
+multi-lingual user base would come with its own set of challenges, especially
+in terms of volunteers' continuing training and interactions on \Talk.
+
+The second way to scale up the number of high contribution classifiers is to
+increase the rate at which new volunteers become dedicated volunteers. Based
+on feedback from the wider \SW community, this could potentially be achieved
+through closer collaboration with the science team. It's also possible that
+the dynamic \StageTwo system proposed in the previous section may act as an
+incentive to some volunteers to increase their contribution (while gaining
+skill in order to ``reach'' \StageTwo). Reducing the rate at which  new
+volunteers lose interest could also play a role. Anecdotally, it seems fairly
+common for new volunteers to be wary of classifying at all, for fear of
+introducing errors. Better explanation of how their early classifications are
+analyzed could help assuage these fears: \Sref{sec:results:crowd} shows that
+effectively down-weighting new users' classifications (by setting their
+agents' initial confusion matrix elements to those of a random classifier)
+leads to best performance, a result which should be of some comfort to the
+nervous volunteer.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Conclusions}
+\label{sec:conclude}
+
+We have designed, implemented and tested a system for   detecting new strong
+gravitational lens candidates in wide field imaging surveys by crowd-sourced
+visual inspection. The \SW web-based classification interface presents carefully
+prepared colour composite sky images to volunteers, who mark features they
+propose to  have been lensed. The participants receive ongoing training with a
+mixture of simulated lens and known-to-be-empty images, and we use this
+information to inform the automated interpretation of their markers. In our
+first lens search we simply divided the \cfhtls imaging into some 430,000 tiles,
+and collected over 11~million volunteer image classifications.
+
+% Questions we set ourselves in the introduction:
+% \begin{itemize}
+% \item How reliably can we find gravitational lenses using the \SW
+% system? What is the completeness of the sample produced likely to be?
+% \item How noisy is the system? What is the purity of the sample
+% produced?
+% \item How quickly can lenses be detected, and non-lenses be rejected?
+% How many classifications, and so how many volunteers are needed per target?
+% \item What can we learn about the scalability of the crowd-sourcing approach?
+% \end{itemize}
+
+By analyzing the  classifications made of the training set, we conclude that
+gravitational lens detection by crowd-sourced visual inspection works,  and in
+the following specific ways:
+
+\begin{itemize}
+
+\item Participation levels were high (over 36,000 volunteers, contributing
+classifications at rates between $10^3$ and $10^4$ images per hour), suggesting
+that if this can be maintained, visual inspection of tens of thousands of images
+could be performed on timescales of weeks.
+
+\item Over the course of the two stages of the \cfhtls project, the
+set of images was reduced by a factor of $10^3$ (from a few hundred thousand to
+a few hundred), enough for an expert team to take over.
+
+\item The ``skill'' of the volunteers correlates strongly with the number of
+images they have classified.  Quantifying the ``contribution'' as the integrated
+skill over the test subjects  classified, we find that about 90\% of the
+contribution was made by a few  hundred volunteers -- but that the width of the
+skill distribution means that a  few thousand volunteers could have made
+comparable contributions, had they classified more images.
+
+\item The optimal true positive rate (completeness) and false positive rate in
+the training set were estimated to be around $91--93\%$ and $<1\%$ (Stages 1 and
+2). This FPR translates to an approximate purity of 20\%.
+
+\item The simulated gravitational lenses that were missed were predominantly
+galaxy-scale lenses with faint blue galaxy sources, whose lensed features are
+difficult to distinguish from the light from the lens galaxy. We observed some
+additional scatter, with some simulated lenses accumulating low probability
+simply due to classification noise.
+
+\end{itemize}
+
+In \PaperTwo we present the results of this \cfhtls lens search in more detail,
+in particular focusing on the detection of real lenses, and the comparison
+between \SW and various automated lens finding methods. In this paper  we have
+shown how \SW provides a lens candidate detection service, crowd-sourcing the
+time-consuming work of visually inspecting astronomical images for
+gravitationally-lensed features. We invite survey teams searching for lenses in
+their wide-field imaging data to contact us if they would like our help.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%  ACKNOWLEDGMENTS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Acknowledgements}
+
+We thank Stuart Lynn, Kelly Borden, Laura Whyte, Brooke Simmons,
+David Hogg, Thomas Jennings, Layne  Wright, Cecile Faure, Jonathan Coles, Stuart
+Lowe and Jean-Paul Kneib for many useful conversations about citizen science and
+gravitational lens detection, and to the Dark Energy Survey and Pan-STARRS strong
+lensing science teams for their suggestions and encouragement.
+
+PJM and ES also thank the Institute of Astronomy and Astrophysics, Academia Sinica
+(ASIAA) and Taiwan's Ministry of Science and Technology (MOST) for their
+financial support of the workshop ``Citizen Science in Astronomy'' in March
+2014, at which some parts of the SWAP analysis was developed.
+
+\input{acknowledgments.tex}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%  APPENDICES
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\appendix
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Information Gain per Classification, Agent ``Skill'' and ``Contribution''}
+\label{appendix:swap}
 
@@
 
-\subsection{Uncertainty in the Agent Confusion Matrices}
-\label{appendix:swap:uncertainty}
-
-Finally, the confusion matrix obtained from the application of
-\Eref{eq:app:fraction} has some inherent noise which reduces as the
-number of training subjects classified by the agent's volunteer
-increases. For simplicity, the discussion has thus far assumed the case
-when the confusion matrix is known perfectly; in practice, we allow for
-uncertainty in the agent confusion matrices by averaging over a small
-number of samples drawn from Binomial distributions characterised by the
-matrix elements $\pr(C_k|\LENS,\trainingk)$ and  $\pr(C_k|\NOT,\trainingk)$. The
-associated standard deviation in the estimated subject probability
-provides an error bar for this quantity.
-
-% For ease of notation, we will denote $\pr(C_k|\LENS,T_k)\equiv p_L$ and
-% $\pr(C_k|\NOT,T_k)\equiv p_N$. In reality, there is a probability distribution
-% for both $p_L$ and $p_N$. Let $p_0$ be the prior probability of the subject
-% being a lens. Then the posterior probability, $p_0'$ of the subject being a
-% lens after the classification $C_k$ is
-% \be
-%   \label{eq:app:sec}
-% p_0' = \frac{p_L p_0}{\left[ p_L p_0 + p_N (1- p_0) \right]},
-% \ee
-% The posterior probability distribution $p_0'$ can be obtained by marginalizing
-% over the probability distributions of $p_L$, $p_N$ and the prior probability
-% distribution $p_0$ such that,
-% \be
-% P(p_0') = \int p_0' P(p_L) P(p_N) P(p_0) dp_L dp_N dp_0\,.
-% \ee
-% This marginalization is not analytically tractable. Therefore, we have
-% implemented the following Monte-Carlo solution for this problem.
-%
-
-%Finally, we also need to update the confusion matrix of an agent and obtain the
-%variance on each element of the matrix, once a training subject has been
-%classified. We would like to derive the posterior probability of the
-%probability elements $p_1$ and $p_2$ given their prior probabilities. For this
-%purpose, we can again make use of Bayes' theorem,
-%\begin{equation}
-%P(p_x'|N_{"X"},N_X,T) = \frac{P(N_{``X"}|p_x',N_X,T) P(p_x'|N_X,T)}{\sum_{N_{``X"}} P(N_{``X"}|p_x',N_X,T) P(p_x'|N_X,T)}
-%\end{equation}
-%Here, $P(N_{``X"}|p_x',N_X,T)$ is a binomial distribution, although this is not
-%true strictly speaking given that our agents are learning and the values of the
-%confusion matrix are moving. Modelling the learning curve of our users is yet
-%another complicated extension we could think about.
-
-\subsection{Offline SWAP}
-\label{appendix:swap:offline}
-
-The probabilistic model described above does not need to be implemented as an
-online inference. Indeed, it might be more appropriate to perform the inference
-of all agent confusion matrix elements and Subject probabilities
-simultaneously, so that the early classifications are not effectively
-downweighted as a result of the agent's ignorance. It might also be that this
-ignorance builds in some conservatism to the system, reducing the noise due
-the early classifications if they are unreliable. In the joint analysis, the
-basic assumption that is built into the agents, that their volunteers
-have innate and unchanging talent for lens spotting parameterised by two
-constant confusion matrix elements which simply need to be inferred given the
-data, is implemented in full. The effect is that of applying the time-averaged
-confusion matrices, rather than one that evolves as the agents (and in the
-real world, the volunteers) learn.
-
-The mathematics of the offline inference are presented elsewhere (in
-preparation). Here we briefly note that we maximize the joint posterior
-probability distribution for all the model parameters (some 66,000 confusion
-matrix elements and 430,000 subject probabilities) with a simple
-expectation-maximisation algorithm. This procedure takes approximately the
-same CPU time as the \StageTwo online analysis, because no matrix inversions are
-required in the algorithm. The algorithm scales well and is actually faster
-than the online analysis with the larger \StageOne dataset. The
-expectation-maximisation algorithm is robust to initial starting parameters
-in, e.g., initial agent confusion matrix elements and Subject probabilities.
-The plots in \Sref{sec:results:sample} show the difference in performance
-between the online and offline analyses.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-04-21 doc/sw-cfhtls.tex
Various skypecon edits

@@
 \citep{Gwyn2012}. The \cfhtls \textsc{WIDE} covers a total
-non-overlapping area of 150~deg$^2$ on the sky and consists of four
+non-overlapping area of 160~deg$^2$ on the sky and consists of four
 fields W1, W2, W3 and W4. The field W1 has the largest sky coverage of
@@
 low probability images after the completion of \StageTwo. All of these
-data products are available at
+data products will be made available at
 http://spacewarps.org/\#/projects/CFHTLS/. Such a sample has tremendous
@@
 discrepancy.}. Further information on the low probability sample such as
-their positions and images is available at
+their positions and images will be available at
 http://spacewarps.org/\#/projects/CFHTLS/. Note that if all of the inspectors gave
@@
 duplication, further information on \sw candidates that were previously
-identified in the literature is available at
+identified in the literature will be available at
 http://spacewarps.org/\#/projects/CFHTLS/ whereas the sample of new lens
@@
 the mass modelling analyses for the new candidates will be presented in
-a subsequent \sw paper, Paper III.
+a subsequent \sw paper (Verma et al., prep.).
 
@@
 of the new sample such as spectroscopic confirmation and mass modelling
-analysis will be presented in a subsequent \sw paper (Paper III).
+analysis will be presented in a subsequent \sw paper (Verma et al., in
+prep.).
 
@@
 \input{acknowledgments.tex}
-%This work is based on observations obtained with MegaPrime/MegaCam, a joint
-%project of CFHT and CEA/IRFU, at the Canada-France-Hawaii Telescope (CFHT) which
-%is operated by the National Research Council (NRC) of Canada, the Institut
-%National des Sciences de l'Univers of the Centre National de la Recherche
-%Scientifique (CNRS) of France, and the University of Hawaii. This research used
-%the facilities of the Canadian Astronomy Data Centre operated by the National
-%Research Council of Canada with the support of the Canadian Space Agency.
-%CFHTLenS data processing was made possible thanks to significant computing
-%support from the NSERC Research Tools and Instruments grant program.
 

### 2015-04-21 doc/sw-system.tex

@@
 Each classification made is logged in a database, storing subject IDs,
-(anonymous) volunteer IDs (their Zooniverse usernames), a timestamp and the
-classification results (the image pixel-coordinate positions of every marker
-placed).  The ``category'' of subject -- whether it is a ``training'' subject (a
-simulated lens or a known non-lens) or a ``test'' subject (an unseen image drawn
-from the survey) -- is also recorded. For training subjects, we also store the
-``kind'' of the subject as a lens (``sim''), or a non-lens (``dud''), and also
-the ``flavor'' of lens object if one is present in the image (``lensed galaxy'',
-``lensed quasar'' or ``cluster lens'').  This classification is used to provide
-instant feedback, but is also the basic measurement used in a probabilistic
-classification of every subject based on all image views to date.  Not all
+(anonymous) volunteer IDs, a timestamp and the classification results (the image
+pixel-coordinate positions of every marker placed).  The ``category'' of subject --
+whether it is a ``training'' subject (a simulated lens or a known non-lens) or a
+``test'' subject (an unseen image drawn from the survey) -- is also recorded.
+For training subjects, we also store the ``kind'' of the subject as
+a lens (``sim''), or a non-lens (``dud''), and also the ``flavour'' of lens
+object if one is present in the image (``lensed galaxy'', ``lensed quasar'' or
+``cluster lens'').  This classification is used to provide instant feedback, but
+is also the basic measurement used in a probabilistic classification of every
+subject based on all image views to date. Not all
 volunteers register with the Zooniverse (although all are prompted to do so);

### 2015-04-21 doc/sw-system.tex
small edits to text

@@
 
-We describe \SW, a novel gravitaional lens discovery service that yields samples
+We describe \SW, a novel gravitational lens discovery service that yields samples
 of high purity and completeness through crowd-sourced visual inspection.
@@
 are inserted into the image stream at random intervals; this training set is
-used to give the volunteers feedback on their performance, and to estimate a
-dynamically-updated probability for any given image to contain a lens. Low
+used to give the volunteers feedback on their performance, as well as to
+calibrate it in order to allow dynamical updates to the probability of any image
+they classify to contain a lens. Low
 probability systems are retired from the site periodically, concentrating the
@@
 realistic. We then chose to make cuts of the simulated lens pool, in order to
-reject sims that were likely to be diﬃcult to spot. While this ensured the
+reject sims that were likely to be difficult to spot. While this ensured the
 educational value of the sims when feedback was given, it meant that we should
@@
 any real
-lens candidates we ﬁnd with properties outside the ranges of the sims, may in
+lens candidates we find with properties outside the ranges of the sims, may in
 this sense be considered bonuses, a product of the {\it imagination} of the
 crowd in extrapolating their understanding of gravitational lenses into a regime
-where they have not seen any before. In the \cfhtls project, the most important
+that they have not been trained for. In the \cfhtls project, the most important
 selection cuts were to only keep sims with a) second brightest image brighter
@@
 real and simulated, and also some common false positives, drawn from the pool of
-survey images. The false positives were identified during the selction of the
+survey images. The false positives were identified during the selection of the
 ``dud'' training images (previous section). For easy reference, the lenses are
@@
 searches in the \cfhtls area, we designed a ``blind search.'' We divided the
-mosaiced images into some 430,000 equal size, overlapping tiles, approximately
+\cfhtls pointings into some 430,000 equal size, overlapping tiles, approximately
 84~arcsec on a side. We refer to these images as ``test images.'' The ``training
 images'' were derived from a small subset of these, as  discussed above. In
-future, larger area, projects we expect to implement the somewhat different
+future, larger area, projects we expect to implement a somewhat different
 strategy of producing image tiles centred on particular pre-selected

### 2015-04-21 doc/sw-system.tex
adding graphics path for ease of submission to arxivs

@@
 \usepackage{epsfig}
+
+\graphicspath{{./}{sw-system-figs/}{sw-system-figs/gallery/}}
 
@@
 \begin{figure*}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/sw-screengrab-marker+feedback.png}
+\centering\includegraphics[width=0.9\linewidth]{sw-screengrab-marker+feedback.png}
 \caption{Screenshot of the \SW classification interface.}
@@
 \begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=sw-system-figs/gallery/4.png,width=\linewidth,angle=0,clip=}
+\centering\epsfig{file=4.png,width=\linewidth,angle=0,clip=}
 \end{minipage} \hfill
 \begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=sw-system-figs/gallery/5.png,width=\linewidth,angle=0,clip=}
+\centering\epsfig{file=5.png,width=\linewidth,angle=0,clip=}
 \end{minipage} \hfill
 \begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=sw-system-figs/gallery/6.png,width=\linewidth,angle=0,clip=}
+\centering\epsfig{file=6.png,width=\linewidth,angle=0,clip=}
 \end{minipage} \hfill
 \begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=sw-system-figs/gallery/7.png,width=\linewidth,angle=0,clip=}
+\centering\epsfig{file=7.png,width=\linewidth,angle=0,clip=}
 \end{minipage} \hfill
@@
 \begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=sw-system-figs/gallery/0_ASW0009dgn.png,width=\linewidth,angle=0,clip=}
+\centering\epsfig{file=0_ASW0009dgn.png,width=\linewidth,angle=0,clip=}
 \end{minipage} \hfill
 \begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=sw-system-figs/gallery/1_ASW0009dgo.png,width=\linewidth,angle=0,clip=}
+\centering\epsfig{file=1_ASW0009dgo.png,width=\linewidth,angle=0,clip=}
 \end{minipage} \hfill
 \begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=sw-system-figs/gallery/2_ASW0009dgy.png,width=\linewidth,angle=0,clip=}
+\centering\epsfig{file=2_ASW0009dgy.png,width=\linewidth,angle=0,clip=}
 \end{minipage} \hfill
 \begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=sw-system-figs/gallery/3_ASW0009dh0.png,width=\linewidth,angle=0,clip=}
+\centering\epsfig{file=3_ASW0009dh0.png,width=\linewidth,angle=0,clip=}
 \end{minipage} \hfill
@@
 \begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_probabilities.png}
+\centering\includegraphics[width=0.9\linewidth]{CFHTLS_2013-10-29_10:16:35_probabilities.png}
 \caption{Typical \SW agent confusion matrix elements. At a particular
@@
 %\begin{figure}
-%\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_histories.png}
+%\centering\includegraphics[width=0.9\linewidth]{CFHTLS_2013-10-29_10:16:35_histories.png}
 %\caption{Typical \SW agent histories. The ``skill'' of the  same 200 random
@@
 \begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_trajectories.png}
+\centering\includegraphics[width=0.9\linewidth]{CFHTLS_2013-10-29_10:16:35_trajectories.png}
 \caption{Typical \SW \StageOne subject trajectories. Top: 200 randomly-selected
@@
 \begin{minipage}{0.45\linewidth}
-  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage1_ROC.pdf}
+  \centering\includegraphics[width=\linewidth]{stage1_ROC.pdf}
 \end{minipage}\hfill
 \begin{minipage}{0.45\linewidth}
-  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage2_ROC.pdf}
+  \centering\includegraphics[width=\linewidth]{stage2_ROC.pdf}
 \end{minipage}
@@
 \begin{figure}
-\centering\includegraphics[width=\linewidth]{sw-system-figs/completeness_purity_simple.pdf}
+\centering\includegraphics[width=\linewidth]{completeness_purity_simple.pdf}
 \caption{Completeness-estimated purity curves for the \sw system, using
@@
 \begin{figure*}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/all_skill_contribution_experience_education.pdf}
+\centering\includegraphics[width=0.9\linewidth]{all_skill_contribution_experience_education.pdf}
 \caption{Key properties and contributions of the \SW \StageOne crowd.
@@
 \begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_contrib_cumul.pdf}
+\centering\includegraphics[width=0.9\linewidth]{crowd_contrib_cumul.pdf}
 \caption{Cumulative distributions of the contributions made by the agents: 90\%
@@
 \begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_skill_cumul.pdf}
+\centering\includegraphics[width=0.9\linewidth]{crowd_skill_cumul.pdf}
 \caption{Broad cumulative distributions of agent skill:
@@
 \begin{figure}
-\centering\includegraphics[width=\linewidth]{sw-system-figs/rate_classification.pdf}
+\centering\includegraphics[width=\linewidth]{rate_classification.pdf}
 \caption{Fractional classification rate in the \SW \cfhtls survey. Fractional classification rate is the number
@@
     \begin{minipage}{0.46\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0008wyp_gri.png}
+      \centering\includegraphics[width=\linewidth]{ASW0008wyp_gri.png}
     \end{minipage}\hfill
     \begin{minipage}{0.50\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0008wyp_stage2_trajectory.png}
+      \centering\includegraphics[width=\linewidth]{ASW0008wyp_stage2_trajectory.png}
     \end{minipage}
@@
     \begin{minipage}{0.46\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0006rkx_gri.png}
+      \centering\includegraphics[width=\linewidth]{ASW0006rkx_gri.png}
     \end{minipage}\hfill
     \begin{minipage}{0.50\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0006rkx_stage1_trajectory.png}
+      \centering\includegraphics[width=\linewidth]{ASW0006rkx_stage1_trajectory.png}
     \end{minipage}
@@
     \begin{minipage}{0.46\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0000fgj_gri.png}
+      \centering\includegraphics[width=\linewidth]{ASW0000fgj_gri.png}
     \end{minipage}\hfill
     \begin{minipage}{0.50\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0000fgj_stage1_trajectory.png}
+      \centering\includegraphics[width=\linewidth]{ASW0000fgj_stage1_trajectory.png}
     \end{minipage}
@@
     \begin{minipage}{0.46\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0003j2s_gri.png}
+      \centering\includegraphics[width=\linewidth]{ASW0003j2s_gri.png}
     \end{minipage}\hfill
     \begin{minipage}{0.50\linewidth}
-      \centering\includegraphics[width=\linewidth]{sw-system-figs/ASW0003j2s_stage1_trajectory.png}
+      \centering\includegraphics[width=\linewidth]{ASW0003j2s_stage1_trajectory.png}
     \end{minipage}
@@
 \begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/stage2_veteran_contribution.pdf}
+\centering\includegraphics[width=0.9\linewidth]{stage2_veteran_contribution.pdf}
 \caption{\StageTwo classifier skill, as a function of their \StageOne skill.
@@
 % \begin{figure}
-% \centering\includegraphics[width=0.9\linewidth]{sw-system-figs/early_vs_final_skill.png}
+% \centering\includegraphics[width=0.9\linewidth]{early_vs_final_skill.png}
 % \caption{Predictability of final skill from early skill (after 10 training

### 2015-04-21 doc/sw-system.tex
Finished going through Anu's comments, closes #112

--- 2015-04-21 doc/sw-system.tex
@@
 proprtional to the number of images classified; green point size shows
-agent-perceived ``skill.''}
+agent-perceived ``skill'' (\Aref{appendix:swap}).}
 \label{fig:swap:agent-probabilities}
@@
 
-During \StageOne classification of the \cfhtls images, we assigned a prior
+During the \StageOne classification of the \cfhtls images, we assigned a prior
 probability for each image to contain a lens of $2\times10^{-4}$, based on a
@@
 retired from the website, just so that more volunteers could see them.
-The progress of the subjects is illustrated in
+
+The progress of the subjects during the online analysis is illustrated in
 \Fref{fig:swap:subject-trajectories}. Subjects appear on this plot at the tip of
@@
 
-The analysis code was run every night during the project, and subjects retired
+The online analysis code was run every night during the project, and subjects retired
 in batches after its completion. This introduced some inefficiency, because
@@
 rejection threshold and the subject actually being retired from the website.
+(We quantify this inefficiency in \Sref{sec:discuss:efficiency} below.)
 As subjects were retired from the site, more subjects were activated. In this
@@
 need to retire any: instead, we simply collected classifications for a fixed
-period of time (about 4 weeks). Without the time pressure motivating the online
-calculation of \StageOne, we carried out an offline analysis
-(\Sref{sec:swap:offline} above) of the  \StageTwo classifications, for
-comparison and as we will see in the next section, improving the pipeline
-performance.
+period of time (about 4 weeks). Without the time pressure motivating an
+online-only calculation (as there had been during \StageOne), we carried out an
+offline analysis (\Sref{sec:swap:offline} above) of the  \StageTwo
+classifications as well, both  for comparison and as we will see in the next
+section, to improve the pipeline performance.
 
@@
 
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 0.95$) by the \SW system (bottom row).
-While the final \StageTwo analysis was done offline,
-these trajectory plots still serve to illustrate the approximate
-classification histories of the subjects.
 
@@
 random walk down its trajectory plot. This can be seen in the top left panel
-of Figure \Fref{fig:discuss:performance:trajectories}.
+of \Fref{fig:discuss:performance:trajectories}.
 
@@
 
-Some of  the mistakes made by reasonably high skill
-classifiers working at high speed
-could have perhaps been corrected by those classifiers themselves, had
-they had access to a ``go back'' option. While clearly enabling error
-reduction, we might worry about such a mechanism enabling classifiers to have
-a guess, then go and read the \Talk discussion, and then return to the
-classification interface to change their mind to agree with the forum. In
-fact, this is already possible on the current interface -- and indeed, it is
-not obvious that such correlations would necessarily lead to poorer system
-performance.
-There may well also be effects on user confidence; it may be that encouraging this sort of checking would result in increased and not necessarily productive caution.
-This could be tested by presenting a fraction of the volunteers
-with a version of the site that actively suggested that they take this
-approach, and then tracking the relative performance of ``collaborative''
-classifications compared with independent ones. We leave the exploration of
-this to further
-work.
+Some of  the mistakes made by reasonably high skill classifiers working at high
+speed could have perhaps been corrected by those classifiers themselves, had
+they had access to a ``go back'' option. While clearly enabling error reduction,
+we might worry about such a mechanism enabling classifiers to have a guess, then
+go and read the \Talk discussion, and then return to the classification
+interface to change their mind to agree with the forum. In fact, this is already
+possible on the current interface -- and indeed, it is not obvious that such
+correlations would necessarily lead to poorer system performance. There may well
+also be effects on user confidence; it may be that encouraging this sort of
+checking would result in increased and not necessarily productive caution. This
+could be tested by presenting a fraction of the volunteers with a version of the
+site that actively suggested that they take this approach, and then tracking the
+relative performance of ``collaborative'' classifications compared with
+independent ones. We leave the exploration of this to further work.
 
 Mistakes by both high and low skill classifiers could be reduced by improving
-the training in the system, which could be done in several ways. One is to
-make more training images available to those who want or need it. A basic
-level of training images are needed for SWAP to build up an accurate picture
-of each classifier's skill -- but one could imagine volunteers {\it choosing}
-to see more training images (still at random) in their stream. We could also
-experiment with providing greater training rates early on for all volunteers;
-the risk associated with this is that retention rates may drop if too few
-``fresh'' test images are shown early on. Another way of improving the
-training could be to provide more information about what lenses do. In this
-project, the Spotter's Guide, and the Science, FAQ and About pages were always available on the site, but as a
-passive background resource. We might consider providing more links to this
-guide in the feedback messages shown to the classifiers as they go -- or
-perhaps extending these messages to themselves include more explanations and
-example images. We might also investigate a more dynamic Spotter's Guide: a
-set of manipulable model lenses illustrating all the possible image
-configurations that that those deflectors can make could help volunteers gain
-understanding of what lensed features can look like very quickly. Such a toy
-is under development.
+the training in the system, which could be done in several ways. One is to make
+more training images available to those who want or need it. A basic level of
+training images are needed for SWAP to build up an accurate picture of each
+classifier's skill -- but one could imagine volunteers {\it choosing} to see
+more training images (still at random) in their stream. We could also experiment
+with providing greater training rates early on for all volunteers; the risk
+associated with this is that retention rates may drop if too few ``fresh'' test
+images are shown early on. Another way of improving the training could be to
+provide more information about what gravitational lens systems look like. In
+this project, the Spotter's Guide, and the Science, FAQ and About pages were
+always available on the site, but as a passive background resource. We might
+consider providing more links to this guide in the feedback messages shown to
+the classifiers as they go -- or perhaps extending these messages to themselves
+include more explanations and example images. We might also investigate a more
+dynamic Spotter's Guide: a set of manipulable model lenses illustrating all the
+possible image configurations that those deflectors can make could help
+volunteers very quickly gain understanding of what lensed features can look
+like. Such a tool is under development.\footnote{\texttt{http://slowe.github.io/LensToy}}
 
@@
 
-However, most identification failures (around 60\%) seem to be due to the
-random walk problem. Short, random direction steps arise from low skill
-classifiers, arising from classifier inexperience (\Sref{sec:results:crowd}).
+However, identification failures (around 60\%, from inspection of a random sample)
+seem to be due to the statistical noise associated with
+the many short, semi-random direction steps arising from classifications made by
+low skill, inexperienced
+classifiers (\Sref{sec:results:crowd}).
 While improved training will help reduce this effect, it is here
 that targeted task assignment could also help improve system performance, by
-bringing higher skill volunteers in to the mix. We
+bringing higher skill volunteers in when needed. We
 advertised \StageTwo of the current project to all registered users; it was
@@
 \Fref{fig:discuss:performance:stage1vstage2} shows how the \StageOne skill maps
-on to \StageTwo skill and contribution.
-This figure suggests that there may be some benefit to opening \StageTwo on the
-basis of \StageOne agent skill, in order to reduce the noise in the system
-generated by new and low skill volunteers in this more difficult
-classification stage.  A simple implementation of this would be to switch the
-web app to the \StageTwo version when either a certain \StageOne skill (and/or
-effort) threshold was passed. Good strategy would probably be to switch back
-to \StageOne after some number of \StageTwo classifications (to avoid losing the
-high skill users from \StageOne entirely), and also to make it very clear which
-stage the classifier was at (since \StageTwo requires more careful attention).
+on to \StageTwo skill and contribution. This figure suggests that, while the
+gains are likely small (since  most of the contribution is still made by high
+skill volunteers),  there could have been some benefit to opening \StageTwo on
+the basis of \StageOne agent skill, in order to reduce the noise in the system
+generated by new and low skill volunteers in this more difficult classification
+stage.  In future, dynamically allocating subjects to volunteers according to
+their agents' skill could alleviate this issue.
+%A simple implementation of this would be to switch the web app to the \StageTwo
+%version when either a certain \StageOne skill (and/or effort) threshold was
+%passed. Good strategy would probably be to switch back to \StageOne after some
+%number of \StageTwo classifications (to avoid losing the high skill users from
+%\StageOne entirely), and also to make it very clear which stage the classifier
+%was at (since \StageTwo requires more careful attention).
 This is something we plan to experiment with in future.
@@
 considered to be completely independent, whereas in fact we might expect there
-to be significant clustering of the confusion matrix elements. A hierarchical
+to be significant clustering of the confusion matrix elements in the $\PD - \PL$
+plane. A hierarchical
 model for the crowd, with hyper-parameters describing the distribution of
@@
 \citet{IBCC} explicitly avoids the assumption of the agent confusion matrix
-elements being constant in time, allowing the development of volunteer skill
+elements being constant in time (as was assumed in \Sref{sec:swap}),
+allowing the development of volunteer skill
 to be more accurately tracked -- and that they did see some time-evolution in
 the supernova zoo classifiers' skill. Finding a way to incorporate such a
-learning model into SWAP, while retaining its statistically online character
+learning model into SWAP while retaining its online character
 is an interesting challenge for future work.
@@
 
-It is clear that to increase the efficiency of the system we need to reduce
-the time lag between the classification being made and its outcome being
-analyzed. The optimal way to do this would be to have the web app itself
-analyze the classifications in a fully online system. This is under
-investigation for future projects. With the classification data being analyzed
-in real time, there may still be a place for a daily or weekly offline
-analysis: this could potentially reduce the false negative and false positive
-rates by ``resurrecting'' subjects that had been retired by the online system
-before the agents had time to learn enough about their classifier's high
-skill.
-
-If the system efficiency could be improved by a factor of three, we would expect
-the characteristic completion time $\tau_0$  in \Eref{eq:speed} to decrease by
-roughly the same factor, suggesting that a dataset of $10^4$~images could be
-searched for lenses by a crowd of $10^4$ volunteers in about 6 days.
+It is clear that to increase the efficiency of the system we need to reduce the
+time lag between the classification being made and its outcome being analyzed.
+The optimal way to do this would be to have the web app itself analyze the
+classifications in real time. This is under investigation for future projects.
+There may still be a place for a daily or weekly offline analysis: this could
+potentially reduce the false negative and false positive rates by
+``resurrecting'' subjects that had been retired by the online system before the
+agents had time to learn enough about their classifier's high skill.
+
+If, as expected, the system efficiency could indeed be improved by a factor of
+three via real-time classification analysis, we would expect the characteristic
+completion time $\tau_0$  in \Eref{eq:speed} to decrease by roughly the same
+factor, suggesting that a dataset of $10^4$~images could be searched for lenses
+by a crowd of $10^4$ volunteers in about 6 days.
 

### 2015-04-21 doc/sw-system.tex

@@
 
+\graphicspath{{./}{sw-system-figs/}{sw-system-figs/gallery/}}
+
 % Macros:

### 2015-04-21 doc/sw-system.tex
New text (temporarily in blue) on future surveys, addresses #100 and #139

--- 2015-04-21 doc/sw-system.tex
@@
 searching for gravitational lenses. The technique has some drawbacks, however.
-The first is that humans make mistakes. A solution to
-this is for the inspectors to operate in teams, providing multiple
-classifications of the same images in order to catch errors and correct them.
-Second, and relatedly, is that humans get tired. With a well-designed
-classification interface, a human might be able to inspect images at a rate of
-one astronomical object per second (provided the majority are indeed
-uninteresting). At $10^4$ massive galaxies, and 10 lenses, per square degree,
-visual lens searches in good quality imaging data are limited to a few square
-degrees per inspector per day (and less, if more time is spent assessing difficult systems).
-Scaling to thousands of square degrees
-therefore means either robotically reducing the number of targets for
-inspection, or increasing the number of inspectors, or both.
+The first is that humans make mistakes. A solution to this is for the inspectors
+to operate in teams, providing multiple classifications of the same images in
+order to catch errors and correct them. Second, and relatedly, is that humans
+get tired. With a well-designed classification interface, a human might be able
+to inspect images at a rate of one astronomical object per second (provided the
+majority are indeed uninteresting). At $10^4$ massive galaxies, and 10 lenses,
+per square degree, visual lens searches in good quality imaging data are limited
+to a few square degrees per inspector per day (and less, if more time is spent
+assessing difficult systems). Scaling to thousands of square degrees therefore
+means either robotically reducing the number of targets for inspection, or
+increasing the number of inspectors, or both.
 
 For example, a $10^4$ square degree survey containing $10^8$
-photometrically-selected massive galaxies and $10^5$ lenses could only be
-searched by 10 inspectors at a mean rate of 1 galaxy per second and 10
-inspections per galaxy in about 14 years. Reducing the inspection time by a
-factor of 400 to two weeks would require a robot to reduce the target sample
-to 25 per square degree. However, at this point the required purity, 40\%,
-would very likely require the average classification time per object to be
-more like 10 seconds per object. Hiring 10 inspectors to assess complex images
-full time for five months may not be the most cost-effective or
-reliable strategy. Alternatively, a team of $10^6$ inspectors could, in
-principle, make the required $10^9$ image classifications, $10^3$ each, in a
-few weeks; robotically reducing the target list would lead to a proportional
-decrease in the required team size.
+photometrically-selected massive galaxies (and $10^5$ lenses) could only be
+searched by 10 inspectors (at a mean rate of 1 galaxy per second and 3
+inspections per galaxy) in about 5 years. Alternatively,  an automated system
+could be asked to produce a much purer sample: if it was able to reach a purity
+of 10\%, this would leave  $10^6$ lens candidates (100 targets per square
+degree) to be visually inspected.  At this point the average visual
+classification time per object could well be more like 10 seconds per object,
+requiring the same  team of 10 inspectors to work full time for 20 weeks (to
+provide 3 classifications  per lens between them) Neither of these may be the
+most cost-effective or reliable strategy. Alternatively, a team of $10^6$
+inspectors could, in principle, make the required $10^9$ image classifications,
+$10^3$ each, in a few weeks; robotically reducing the target list would lead to
+a proportional decrease in the required team size.
 
 Systematic detection of rare astronomical objects by such ``crowd-sourced''
-visual inspection has recently been achieved by the online citizen science
+visual inspection has recently been demonstrated by the online citizen science
 project \PH \citep{SchwambEtal2012}.
-
 \PH was designed to enable the discovery of transiting exoplanets in data taken
@@
 public found, after each undergoing a small amount of training, over 40 new
-exoplanet candidates. They achived this   by visually inspecting the Kepler
+exoplanet candidates. They achieved this   by visually inspecting the Kepler
 lightcurves that were presented in a custom web-based classification interface
@@
 
-If, as expected, the system efficiency could indeed be improved by a factor of
+\new{If, as expected, the system efficiency could indeed be improved by a factor of
 three via real-time classification analysis, we would expect the characteristic
@@
 factor, suggesting that a dataset of $10^4$~images could be searched for lenses
-by a crowd of $10^4$ volunteers in about 6 days.
+by a crowd of $10^4$ volunteers in about 6 days.}
+
+\new{The futuristic lens-finding problem sketched in \Sref{sec:intro}, where $10^5$
+lenses are to be found in a $10^4$ square degree wide field imaging survey, is
+approximately representative of the challenge facing both the LSST and Euclid
+strong lensing science teams \citep{LSSTSciBook,EuclidSciBook}. What role could
+citizen scientists at \SW play in lens searching in the next decade? From
+\Eref{eq:speed}, and assuming $\tau_0 = 6$ days (as above), we see that for the
+\SW crowd to be able to classify $10^8$ images of  photometrically-selected
+massive galaxies and groups in approximately 60 days, it would need to contain
+$10^7$ volunteers. This is only  a factor of ten larger than the current size of
+the Zooniverse userbase. Alternatively, suppose that automated  lens finding
+algorithms are able to select as few as $10^6$ targets for visual inspection (a
+sample with 10\% purity). Increasing $\tau_0$ by a factor of three to allow for
+more inspection time per subject,  we find that \SW could enable a crowd of just
+$10^6$ volunteers to assess them in about three  weeks.}
 
@@
 The second way to scale up the number of high contribution classifiers is to
-increase the rate at which new volunteers become dedicated volunteers. Based
-on feedback from the wider \SW community, this could potentially be achieved
-through closer collaboration with the science team. It's also possible that
-the dynamic \StageTwo system proposed in the previous section may act as an
-incentive to some volunteers to increase their contribution (while gaining
-skill in order to ``reach'' \StageTwo). Reducing the rate at which  new
-volunteers lose interest could also play a role. Anecdotally, it seems fairly
-common for new volunteers to be wary of classifying at all, for fear of
-introducing errors. Better explanation of how their early classifications are
-analyzed could help assuage these fears: \Sref{sec:results:crowd} shows that
-effectively down-weighting new users' classifications (by setting their
-agents' initial confusion matrix elements to those of a random classifier)
-leads to best performance, a result which should be of some comfort to the
-nervous volunteer.
+increase the rate at which new volunteers become dedicated volunteers. Based on
+feedback from the wider \SW community, this could potentially be achieved
+through closer collaboration with the science team. \new{It's also possible that
+dynamically assigning subjects on the basis of the volunteer's skill could act
+as an incentive to some volunteers to increase their contribution, although any
+such ``gamified'' approach would need to be taken thoughtfully.}  Reducing the
+rate at which new volunteers lose interest could also play a role. Anecdotally,
+it seems fairly common for new volunteers to be wary of classifying at all, for
+fear of introducing errors. Better explanation of how their early
+classifications are analyzed could help assuage these fears:
+\Sref{sec:results:crowd} shows that effectively down-weighting new users'
+classifications (by setting their agents' initial confusion matrix elements to
+those of a random classifier) leads to best performance, a result which should
+be of some comfort to the nervous volunteer.
 
@@
 \input{acknowledgments.tex}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%  REFERENCES
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% MNRAS does not use bibtex, input .bbl file instead.
+% Generate this in the makefile using bubble script in scriptutils:
+
+% bubble -f paper-lcr.tex references.bib
+% \input{paper-lcr.bbl}
+
+\bibliographystyle{apj}
+\bibliography{references}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%  REFERENCES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% MNRAS does not use bibtex, input .bbl file instead.
-% Generate this in the makefile using bubble script in scriptutils:
-
-% bubble -f paper-lcr.tex references.bib
-% \input{paper-lcr.bbl}
-
-\bibliographystyle{apj}
-\bibliography{references}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-04-21 doc/sw-system.tex
Add reference to Waterhouse to sec 5.1
Notes on offline performance, closes #148

--- 2015-04-21 doc/sw-system.tex
@@
 
-The dot-dashed curves show the impact of the offline analysis. At \StageOne the
+The dot-dashed curves show the results from the offline analysis. At \StageOne the
 results are very similar to the online version that was actually run (solid
@@
 over 95\%, showing that some of the sims that were missed in the online analysis
-may be being recovered by doing the analysis offline. The same is true at
-\StageOne, but to a lesser extent. Assuming Poisson statistics for the
+may be being recovered by doing the analysis offline. (The same is true at
+\StageOne, but to a lesser extent.) One interpretation for this result (if it holds up)
+would be that the offline analysis, by using each agent's entire history, is
+making less noisy probability estimates.
+
+Assuming Poisson statistics for the
 fluctuations in the numbers of recovered lenses, the uncertainty in the measured
 \StageTwo TPR values is around 8\%, but the online and offline samples are
-highly correlated, such that the uncertainty on the difference between the ROC
+highly correlated, such that the uncertainty on the {\it difference} between the ROC
 curves is somewhat less than this. Still, a larger validation set is needed to
@@
 
-Finally, there could be some performance gains to be made by improving the
-SWAP agent model, or its implementation. Low skill is typically a result  of
+Finally, there could be some performance gains to be made by improving the SWAP
+agent model, or its implementation. Low skill is typically a result  of
 inexperience (\Sref{sec:results:crowd}), but it could be the agent that is
-inexperienced as well as the classifier or its agent. In a future paper we
-plan to investigate the use of the test images as well as the training images
-in accelerating the agent's learning (Davis et al, in preparation). We also
-plan to investigate the use of offline analysis at \StageOne, for the same
-reason (see also \Sref{sec:discuss:efficiency} below.)
+inexperienced as well as the classifier or its agent. In a future paper we plan
+to investigate the use of the test images as well as the training images in
+accelerating the agent's learning (Davis et al, in preparation). We also plan to
+investigate the use of offline analysis at \StageOne, partly for the same reason
+(see also \Sref{sec:discuss:efficiency} below.) Given the above findings  about
+the effects of noise in the SWAP system, we are also motivated to explore
+further the possible noise-reducing effects of the doing the analysis offline
+(\Sref{sec:results:sample}).
+
 One might also consider looking at

### 2015-04-21 doc/sw-system.tex
Added a sentence about 0.95 threshold, closes #146

@@
 positive rates of  around 90\% were achieved, at very low false positive rates.
+The probability threshold that was used for retirement during the \StageOne online analysis
+was 0.95; this point is marked with a star on each curve.
+This turned out to be close to optimal (although a better approach would be to
+keep track of the ROC curve as the survey progressed!).
 
@@
 allowing the agents to learn via their Bayesian updates.
-
 When the agents are allowed to update their confusion matrices, the choice of
@@
 would be that the offline analysis, by using each agent's entire history, is
-making less noisy probability estimates.
+making less noisy probability estimates. This could be consistent with
+other citizen science/crowdsourcing projects where,
+in the absence of high quality information about classifiers,
+sophisticated strategies tend to under-perform naive but simpler
+ones \citep{Waterhouse} (although we note that this rule of thumb seems not to extend
+to simple voting in this case!).
 
@@
 \StageTwo TPR values is around 8\%, but the online and offline samples are
-highly correlated, such that the uncertainty on the {\it difference} between the ROC
-curves is somewhat less than this. Still, a larger validation set is needed to
+highly correlated, such that the uncertainty on the difference between the ROC
+curves is somewhat less than this.
+Still, a larger validation set is needed to
 test these algorithmic choices more rigorously. At \StageOne, high TPR can be

### 2015-04-21 doc/sw-system.tex
Updated conclusions and abstract, closes #100

@@
 
-We describe \SW, a novel gravitational lens discovery service that yields samples
-of high purity and completeness through crowd-sourced visual inspection.
+We describe \SW, a novel gravitational lens discovery service that yields
+samples of high purity and completeness through crowd-sourced visual inspection.
 Carefully produced colour composite images are displayed to volunteers via a
 classification interface which records their estimates of the positions of
-candidate lensed features. Simulated lenses, and expert-classified images which lack lenses,
-are inserted into the image stream at random intervals; this training set is
-used to give the volunteers feedback on their performance, as well as to
-calibrate it in order to allow dynamical updates to the probability of any image
-they classify to contain a lens. Low
-probability systems are retired from the site periodically, concentrating the
-sample towards a set of candidates. Having divided 160 square degrees of
-Canada-France-Hawaii Telescope Legacy Survey (\cfhtls)
-imaging into some 430,000 overlapping 84 by 84 arcsecond tiles and
-displaying them on the site, we were joined by around 37,000 volunteers who
-contributed 11~million image classifications over the course of 8 months. The
-sample was reduced to 3368 \StageOne candidates; these were then refined to
-yield a sample that we expect to be over 90\%
-complete and 20\% pure. We
-comment on the scalability of the \SW system to the wide field survey era.
-
+candidate lensed features. Simulated lenses, and expert-classified images which
+lack lenses, are inserted into the image stream at random intervals; this
+training set is used to give the volunteers feedback on their performance, as
+well as to calibrate it in order to allow dynamical updates to the probability
+of any image they classify to contain a lens. Low probability systems are
+retired from the site periodically, concentrating the sample towards a set of
+candidates. Having divided 160 square degrees of Canada-France-Hawaii Telescope
+Legacy Survey (\cfhtls) imaging into some 430,000 overlapping 84 by 84 arcsecond
+tiles and displaying them on the site, we were joined by around 37,000
+volunteers who contributed 11~million image classifications over the course of 8
+months. The sample was reduced to 3368 \StageOne candidates; these were then
+refined to yield a sample that we expect to be over 90\% complete and 30\% pure.
+We comment on the scalability of the \SW system to the wide field survey era,
+based on our finding that searches of $10^5$ images can be performed by a
+crowd of $10^5$ volunteers in 6 days.
 \end{abstract}
@@
 which sets the minimum size of this sample. We see from the solid blue curve
-that over 90\% completeness was reached, albeit in a sample with around 20\%
+that over 90\% completeness was reached, albeit in a sample with 30\%
 purity.
@@
                       1    & $427064$ & $1292016.3$ & $36982$ & $1471.9$ & $10802125$ & $3368$ & $91122.6$ \\
-                      2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $90$ &  $1640.4$ \\
+                      2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $89$ &  $1640.4$ \\
   \hline \hline
@@
 that if this can be maintained, visual inspection of tens of thousands of images
-could be performed on timescales of weeks.
+could be performed just a few weeks. An expanded crowd of $10^6$ volunteers
+(which has already been reached in the Galaxy Zoo project) would
+be able to inspect a plausible sample of $10^6$ LSST or Euclid targets
+on similar time scales.
 
@@
 skill over the test subjects classified, we find that about 90\% of the
-contribution was made by a few  hundred volunteers -- but that the width of the
-skill distribution means that a  few thousand volunteers could have made
-comparable contributions, had they classified more images.
+contribution was made by a few hundred volunteers ($1\%$ of the crowd) -- but
+that the width of the skill distribution means that a  few thousand volunteers
+could have made comparable contributions had they classified more images.
 
@@
 the training set were estimated to be around $91--93\%$ and $<1\%$ (Stages 1 and
-2). This FPR translates to an approximate purity of 20\%.
+2). This FPR translates to an approximate purity of 30\%. We find a
+higher purity at \StageTwo (perhaps as a result of the least visible candidates already
+being discarded): here, 100\% purity was reached at just under $90\%$
+completeness. Because \SW is a supervised learning system, these numbers should
+be taken to be upper limits to what we should expect for real lenses (which have
+not been selected for a high visibility training set).
 

### 2015-04-21 doc/sw-system.tex

@@
 
-% Problem of rarity. Imaging surveys. Problem of purity/false positives.
-% Review of progress to date. Methods in SL2S, SQLS. Contrast with SLACS.
-
 Because they are rare, strong lenses are expensive to find. The highest purity
@@
 \citep[e.g.][]{GavazziEtal2014}.
-
-% Scaling to wide field era. Automated methods: problems. Need for good
-% training sets. Need for quality control: always present.
 
@@
 \cfhtls \StageTwo training set.
-
-%%% Sims and Duds from Stage2
 
@@
 \end{table}
-% Quck Dashboard code: https://github.com/zooniverse/Lens-Zoo/blob/vics82/app/controllers/quick_dashboard.coffee
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}
-%\centering\includegraphics[width=0.9\linewidth]{CFHTLS_2013-10-29_10:16:35_histories.png}
-%\caption{Typical \SW agent histories. The ``skill'' of the  same 200 random
-%agents  as in \Fref{fig:swap:agent-probabilities} is plotted in green as a function
-%of the number  of subjects classified (``effort''). The yellow histogram in
-%the background shows the distribution of effort.}
-%\label{fig:swap:agent-histories}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \Fref{fig:swap:agent-probabilities} shows the confusion matrix elements of 200
@@
 right-hand quadrant, the agents perceive their volunteers to be ``astute.''
-
-%\Fref{fig:swap:agent-histories} shows the ``skill'' (\Sref{sec:results:crowd})
-%of the same small sample of agents evolving as their volunteers classify images.
-%The underlying histogram shows the distribution of classification number: a long
-%tail to very high ``effort'' can be seen.
 
@@
 result.
-
-% TP + FN ~ 2e-4 * 430000 ~ 100 ~ TP/C ; so TP ~ 89 candidates
 
@@
 
-\Fref{fig:discuss:performance:stage1vstage2} shows how the \StageOne skill maps
-on to \StageTwo skill and contribution. This figure suggests that, while the
-gains are likely small (since  most of the contribution is still made by high
-skill volunteers),  there could have been some benefit to opening \StageTwo on
-the basis of \StageOne agent skill, in order to reduce the noise in the system
-generated by new and low skill volunteers in this more difficult classification
-stage.  In future, dynamically allocating subjects to volunteers according to
-their agents' skill could alleviate this issue.
-%A simple implementation of this would be to switch the web app to the \StageTwo
-%version when either a certain \StageOne skill (and/or effort) threshold was
-%passed. Good strategy would probably be to switch back to \StageOne after some
-%number of \StageTwo classifications (to avoid losing the high skill users from
-%\StageOne entirely), and also to make it very clear which stage the classifier
-%was at (since \StageTwo requires more careful attention).
-This is something we plan to experiment with in future.
+\Fref{fig:discuss:performance:stage1vstage2} shows how the \StageOne
+skill maps on to \StageTwo skill and contribution. This figure suggests
+that, while the gains are likely small (since  most of the contribution
+is still made by high skill volunteers),  there could have been some
+benefit to opening \StageTwo on the basis of \StageOne agent skill, in
+order to reduce the noise in the system generated by new and low skill
+volunteers in this more difficult classification stage.  In future,
+dynamically allocating subjects to volunteers according to their agents'
+skill could alleviate this issue. This is something we plan to
+experiment with in future.
 
@@
 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \begin{figure}
-% \centering\includegraphics[width=0.9\linewidth]{early_vs_final_skill.png}
-% \caption{Predictability of final skill from early skill (after 10 training
-% classifications) in \StageOne agents. The dashed lines enclose 649 agents with
-% early skill greater than 0.1
-% who retain final skill of greater than 0.05. Point size is proportional to
-% contribution (plus a constant).}
-% \label{fig:crowd:skillprediction}
-% \end{figure}
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% Having seen the importance of the high skill volunteers at both \StageOne and
-% \StageTwo, we might ask, can we predict agent skill after, say, the volunteer
-% has experienced 10 training subjects? In \Fref{fig:crowd:skillprediction} we
-% plot this ``early skill'' against final skill, for all experienced \StageOne
-% volunteers. The majority of the crowd shows little correlation, but at the
-% high early skill end, some predictability appears. The 649 experienced \StageOne
-% volunteers who had early skill greater than 0.1 went on to attain a mean
-% final skill of 0.22, with 97\% remaining at skill 0.05 or higher. This
-% suggests that it might be worth tracking volunteers' skill as a project
-% progresses, in order to encourage those showing an aptitude for the task to
-% take part in the more difficult activities, such as \StageTwo refinement.
-% However, this would not have done a very good job at identifying the
-% volunteers who went on to make the largest contributions: the point size in
-% \Fref{fig:crowd:skillprediction} is proportional to contribution (plus a constant):
-% many of the highest contributors showed relatively low skill early on.
-
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
   \hline
-  % \hline {Stage} & Subjects & Contribution                          & Agents & Skill      & Classifications          & Candidates & Information \\
-  %                & $\Ns$    & $\sum_k^{\Nv} \contribution_k$ (bits) & $\Nv$  & $\sum_k^{\Nv} \skill_k$ (bits) & $\sum_k^{\Nv} \thiseffort$ & $\Ncands$  & $\sum_j^{\Ns}\sum_k^{\Nv} \information_{j,k}$ (bits) \\
-  % \hline
-  %           1    & $427064$ & $1292016.3$ & $36982$ & $1471.9$ & $10802125$ & $3368$ & $91122.6$ \\
-  %           2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $90$ &  $1640.4$ \\
   \hline {Stage} & Subjects & Contribution                          & Agents & Skill      & Classifications          & Candidates & Information \\
@@
 
-\new{If, as expected, the system efficiency could indeed be improved by a factor of
+If, as expected, the system efficiency could indeed be improved by a factor of
 three via real-time classification analysis, we would expect the characteristic
@@
 factor, suggesting that a dataset of $10^4$~images could be searched for lenses
-by a crowd of $10^4$ volunteers in about 6 days.}
-
-\new{The futuristic lens-finding problem sketched in \Sref{sec:intro}, where $10^5$
+by a crowd of $10^4$ volunteers in about 6 days.
+
+The futuristic lens-finding problem sketched in \Sref{sec:intro}, where $10^5$
 lenses are to be found in a $10^4$ square degree wide field imaging survey, is
@@
 more inspection time per subject,  we find that \SW could enable a crowd of just
-$10^6$ volunteers to assess them in about three  weeks.}
+$10^6$ volunteers to assess them in about three  weeks.
 
@@
 feedback from the wider \SW community, this could potentially be achieved
-through closer collaboration with the science team. \new{It's also possible that
+through closer collaboration with the science team. It's also possible that
 dynamically assigning subjects on the basis of the volunteer's skill could act
 as an incentive to some volunteers to increase their contribution, although any
-such ``gamified'' approach would need to be taken thoughtfully.}  Reducing the
+such ``gamified'' approach would need to be taken thoughtfully.  Reducing the
 rate at which new volunteers lose interest could also play a role. Anecdotally,
@@
 
-% Questions we set ourselves in the introduction:
-% \begin{itemize}
-% \item How reliably can we find gravitational lenses using the \SW
-% system? What is the completeness of the sample produced likely to be?
-% \item How noisy is the system? What is the purity of the sample
-% produced?
-% \item How quickly can lenses be detected, and non-lenses be rejected?
-% How many classifications, and so how many volunteers are needed per target?
-% \item What can we learn about the scalability of the crowd-sourcing approach?
-% \end{itemize}
-
 By analyzing the  classifications made of the training set, we conclude that
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% MNRAS does not use bibtex, input .bbl file instead.
-% Generate this in the makefile using bubble script in scriptutils:
-
-% bubble -f paper-lcr.tex references.bib
-% \input{paper-lcr.bbl}
 
@@
 column 7 of the table.
-% The uncertainty in the interpretation of the total
-% information generated provides some justification for our focus on the
-% expected information gain as a measure of volunteer contribution.
 

### 2015-04-21 doc/sw-system.tex
Adding to Phil's section 6 text, removing 'gamified'

@@
 as an incentive to some volunteers to increase their contribution, although any
-such ``gamified'' approach would need to be taken thoughtfully.  Reducing the
+such approach would need to take into account the need to optimise not only for efficiency but also for the most interesting or pleasurable volunteer experience; a solution which gave every volunteer a very uniform experience, for example, is unlikely to succeed even if it appears optimally efficient.
+Reducing the
 rate at which new volunteers lose interest could also play a role. Anecdotally,

### 2015-04-21 doc/addresses.tex
Zooniverse address, opt-in and opt-out author lists
Correcting Edwin's affiliation
updated ipmu address

@@
 \def\oxford{Dept.\ of Physics, University of Oxford, Keble Road, Oxford, OX1 3RH, UK}
+\def\oxfordeng{Dept.\ of Engineering Science, University of Oxford, Parks Road, Oxford, OX1 3PJ, UK}
 \def\kipac{Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA}
-\def\ipmu{Kavli IPMU (WPI), University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa 277-8583, Japan}
+\def\ipmu{Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan}
+\def\zooniverse{Zooniverse, c/o Astrophysics Department, University of Oxford, Oxford OX1 3RH, UK}
 \def\adler{Adler Planetarium, Chicago, IL, USA}

### 2015-04-21 doc/sw-cfhtls.tex

@@
 \documentclass[useAMS,usenatbib,a4paper]{mn2e}
-%% letterpaper
-%% a4paper
-
 \voffset=-0.6in
@@
 % Packages:
-\input psfig.sty
+\usepackage{psfig}
 \usepackage{xspace}
@@
 
+\graphicspath{{sw-cfhtls-figs/}{./}}
+
 % Macros:
@@
 
-%%% ENSURE WORD LIMIT IS 250
 We report the discovery of 28 promising and a total of 58 new lens
@@
 only those classifications which are performed by the high power
-volunteers, \sw can achieve a detection rate of up to 75\% of the known
+volunteers, \sw can achieve a detection rate of up to 75\% for the known
 lens sample.  Training and calibration of the performance of citizen
@@
 available.
-%%% ENSURE WORD LIMIT IS 250
 
@@
 their follow-up campaign, 33 confirmed lenses.
-%(and 17 promising candidates) AM: PJM, what is this sample of 17 ?
 
@@
 of these candidates are medium-low
-probability\footnote{http://www.ita.uni-heidelberg.de/\~maturi/Public/arcs}.
+probability\footnote{http://www.ita.uni-heidelberg.de/$\sim$maturi/Public/arcs}.
 
@@
 \label{sec:data:impres}
-%{\it Preparation of data: divide survey into overlapping tiles.
-Presentation of images.
-Uniform scales, to build intuition and avoid rescales due to bright objects.
-Arcsinh stretch, to bring out low SB features.
-Approximately optimized, how?
-Examples of images.}
-
 In order to perform a blind lens search over the entire \cfhtls
@@
 large and we receive multiple classifications for the same cutout.
-%We also provided access to the $u$ and $z$ band imaging
-%data through dashboard, when the volunteers wished to take a closer look at a particular system\footnote{The dashboard tool page can be accessed from
-%http://tools.zooniverse.org/\#/dashboards/spacewarp}.
-
-%The code rescales the pixel values of each channel image into flux units, and
-%then applies an arcsinh stretch. The stretch parameters are chosen
-%using a small random sample of images, to ensure that the background
-%noise is just visible, and that the centres of bright, intermediate
-%redshift galaxies are not saturated.
 
@@
 \begin{center}
-\includegraphics[scale=1.0]{sw-cfhtls-figs/sim_cgq.pdf}
+\includegraphics[scale=1.0]{sim_cgq.pdf}
 \caption{ \label{fig:sim}
@@
 \begin{center}
-\includegraphics[scale=1.2]{sw-cfhtls-figs/distrib_remu.pdf}
+\includegraphics[scale=1.2]{distrib_remu.pdf}
 \caption{ \label{fig:remudist}
@@
 \begin{center}
-\includegraphics[scale=1.3]{sw-cfhtls-figs/lensprop.pdf}
+\includegraphics[scale=1.3]{lensprop.pdf}
 \caption{ \label{fig:lensprop}
@@
 
-%magdiff=5*0.1;
-%zdiffq=0.1;
-
-%
-%\begin{figure}
-%\begin{center}
-%\includegraphics[scale=0.95]{sw-cfhtls-figs/distrib_reff.eps}
-%\caption{ \label{fig:reffdist}
-%Distributions of magnification (left) and source effective radius in units of
-%pixel (right).
-%}
-%\end{center}
-%\end{figure}
-
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 \begin{center}
-\includegraphics[scale=0.6]{sw-cfhtls-figs/cand_fp_P_frac.pdf}
+\includegraphics[scale=0.6]{cand_fp_P_frac.pdf}
 \caption{ \label{fig:stackP}
@@
 In this section, we describe the \sw-\cfhtls lens sample (henceforth,
-called the \sw lens sample). We find a total of 288 (and 249 new)
-candidates with averaged grade $0<$G$<1.3$ (low probability sample)
-which means - in the worst case, at least one of the inspector thought
-the candidate is possibly a lens and in the best case, all three
-inspectors thought the candidate is possibly a lens (that is,
-a grade of 1)\footnote{If grades from the inspectors were found to be discrepant
-by 2 or more, these were discussed and re-graded to resolve the
-discrepancy.}. Further information on the low probability sample such as
-their positions and images will be available at
-http://spacewarps.org/\#/projects/CFHTLS/. Note that if all of the inspectors gave
-a grade of 0 to a candidate, then it is discarded from the sample.
-
-There are a total of 50 candidates with $1.3\le$G$<2$ (medium
-probability sample) out of which 30 are new. The quality of candidates
-in this category is such that at least one of the inspectors thought the
-candidate is most probably a lens (that is, a grade of 2) and a second inspector
-thought this is possibly a lens (that is, a grade of 1). Among our high
+called the \sw lens sample). We find a total of 141 candidates with
+G$\ge1.3$ (medium-high probability sample) out of which 58 are new
+systems. This sample is further divided as follows. We have a total of
+50 candidates with $1.3\le$G$<2$ (medium probability sample) out of
+which 30 are new. The quality of candidates in this category is such
+that at least one of the inspectors thought the candidate is most
+probably a lens (that is, a grade of 2) and a second inspector thought
+this is possibly a lens (that is, a grade of 1). Among our high
 probability sample (G$\ge$2), there are a total of 91 candidates out of
@@
 duplication, further information on \sw candidates that were previously
-identified in the literature will be available at
+identified in the literature will be made available at
 http://spacewarps.org/\#/projects/CFHTLS/ whereas the sample of new lens
-candidates with G$\ge 1.3$ (medium-high probability) is presented in this paper (see
-\Sref{sec:results:newcand}).
+candidates with G$\ge 1.3$ (medium-high probability) is presented in
+this paper (see \Sref{sec:results:newcand}).
+
+We find a total of 288 (and 249 new) candidates with averaged grade
+$0<$G$<1.3$ (low probability sample) which means - in the worst case, at
+least one of the inspector thought the candidate is possibly a lens and
+in the best case, all three inspectors thought the candidate is possibly
+a lens (that is, a grade of 1)\footnote{If grades from the inspectors
+were found to be discrepant by 2 or more, these were discussed and
+re-graded to resolve the discrepancy.}. Further information on the low
+probability sample such as their positions and images will be available
+at http://spacewarps.org/\#/projects/CFHTLS/. Note that if all of the
+inspectors gave a grade of 0 to a candidate, then it is discarded from
+the sample.
 
@@
 \hline
-Number  & 58 & 168 &  & \\
+Number  & 58 & 141 &  & \\
 Percentage & & & & \\
-of detection & 12 & 34 &  & \\
+of detection & 13 & 33 &  & \\
 P$_{\rm thresh}$ & 0.3 & 0.3 &  & \\
-
-%% ####stage1
-%% cand 128/436
-%% conf  34/59
-
-%% ####stage 2
-%% sarcs conf 18/26
-%% sarcs cand  55/106
-%% RF conf 16/33
-%% RF cand  52/330
 
@@
 to be sifted through
-%({\bf is there someone actively looking into this whose work should be referred here ?}).
 
@@
 the mass modelling analyses for the new candidates will be presented in
-a subsequent \sw paper (Verma et al., prep.).
-
-%{\bf CHECK FOR STAGE 1 -- COMPLETENESS OF KNOWN LENSES and P value comparison,
-
-% what about the duplicate lenses near the borders -- stats on those?
-
-% check the detection plot of arc mag / Reinst and find out why some of
-%the bins have unexpected results.
-
-%check if some candidates were detected because they were hidden
-%underneath the sims ie. from the D11;
-%}
+a subsequent \sw paper (Verma et al., in prep.).
 
@@
 \begin{center}
-\includegraphics[scale=1.9]{sw-cfhtls-figs/lenscandfin.pdf}
+\includegraphics[scale=1.9]{lenscandfin.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics[scale=1.9]{sw-cfhtls-figs/lenscandfin_1.pdf}
+\includegraphics[scale=1.9]{lenscandfin_1.pdf}
 \caption{ \label{fig:lc}
@@
 \begin{center}
-\includegraphics[scale=1.0]{sw-cfhtls-figs/comp_reinst_mag.pdf}
+\includegraphics[scale=1.0]{comp_reinst_mag.pdf}
 \caption{ \label{fig:compre} Fraction of lens candidates recovered by \sw as a
@@
 \begin{center}
-\includegraphics[scale=1.2]{sw-cfhtls-figs/isd_cfhtls_sw.pdf}
+\includegraphics[scale=1.2]{isd_cfhtls_sw.pdf}
 \caption{ \label{fig:isd} Image separation distribution. Comparing theoretical
@@
 \begin{center}
-\includegraphics[scale=0.65]{sw-cfhtls-figs/zl_mg_re.pdf}
+\includegraphics[scale=0.65]{zl_mg_re.pdf}
 \caption{ \label{fig:zlmgre}
@@
 
-%{\bf can we say something qualitatively for why these were missed? there are a few which look regular galaxies so which criteria are they failing??}
-%% 13 are under mask so no photoz, 10 have photoz (z>0.2 except for 1).
-
 \begin{figure*}
 \begin{center}
-\includegraphics[scale=0.5]{sw-cfhtls-figs/stacked_lenscand_rein.pdf}
-\includegraphics[scale=0.5]{sw-cfhtls-figs/stacked_lenscand_mag.pdf}
+\includegraphics[scale=0.5]{stacked_lenscand_rein.pdf}
+\includegraphics[scale=0.5]{stacked_lenscand_mag.pdf}
 \caption{ \label{fig:stackremg}
@@
 images.
-%{\bf check how different are the estimates from the different
-%measurement techniques for a given lens candidates.}
 }
@@
 
-%% 23/61 miss first step, 30/61 miss auto, 5 pass auto but have poor
-%grade from visual classf.
-
 Next, we rerun the \af on the same \sw sample of new candidates. The \af
@@
 of the thresholds in the code because of the change in the noise level.
-%{\bf does this make sense? - list the IDs of these systems?}
 
@@
 
-%% 19,46 (original and relaxed criteria); 72,338 (smaller image); 1548,7845 (larger image)
-
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 for the detected and the missed sample with Nclass.
-
-%{ Let us compare the two samples to see if there are any obvious differences.
-only 2 out of this sample of 18 were detected at \StageOne (reached high P even with fewer classifications) and missed at \StageTwo (P value was low even after recieving very many classifications).
-The rest of the 16 lenses were rejected right at \StageOne }
-%One of those 6 lenses was detected at \StageOne but failed to get high enough P value at \StageTwo even after receiving a total of 50 classifications (set as the upper limit).
-The rest of the 5 lenses are already rejected at \StageOne.
-Upon visual inspection of these 5 systems, they appear to be difficult to identify as lenses because either the lensed images are faint, have low curvature, are close to the edge and/or are not visible due to proximity to an extremely bright galaxy
 
@@
 
-By how much the P value will change depends on how well the
-volunteers are performing on the training sample. Thus, high power
-volunteers will change the P by a large factor compared to the low
-power volunteers. This is evident in the trajectory plots as large and
-small distances in between the consequent points which we refer to as
-kicks. Comparison of the kick sizes between the detected
-and the missed lenses suggests that the missed lenses do not have as
-many volunteers giving large kicks. We also note that most of the large
-kicks seen in the trajectories of the missed lenses seem to be moving
-the subjects to the right. In other words, the high power volunteers
-are mostly classifying them as subjects with lens candidates. Further
-qualitative comparison and discussion of the trajectory plots is given
-in \Aref{appendix:traj}.
+The amount by which the posterior probability P value of a subject will
+change depends on how well the volunteers are performing on the training
+sample and its current probability. Thus, for a given current
+probability, high power volunteers will change the P by a large factor
+compared to the low power volunteers. This is evident in the trajectory
+plots as large and small distances in between the consequent points
+which we refer to as kicks. Comparison of the kick sizes between the
+detected and the missed lenses suggests that the missed lenses do not
+have as many volunteers giving large kicks. We also note that most of
+the large kicks seen in the trajectories of the missed lenses seem to be
+moving the subjects to the right. In other words, the high power
+volunteers are mostly classifying them as subjects with lens candidates.
+Further qualitative comparison and discussion of the trajectory plots is
+given in \Aref{appendix:traj}.
 
@@
 \begin{center}
-\includegraphics[scale=0.95]{sw-cfhtls-figs/completeness_pos.pdf}
+\includegraphics[scale=0.95]{completeness_pos.pdf}
 \caption{ \label{fig:comppos}
@@
 \begin{center}
-\includegraphics[scale=0.6]{sw-cfhtls-figs/det_mis_traj.pdf}
-\includegraphics[scale=0.6]{sw-cfhtls-figs/det_mis_hist.pdf}
+\includegraphics[scale=0.6]{det_mis_traj.pdf}
+\includegraphics[scale=0.6]{det_mis_hist.pdf}
 \caption{ \label{fig:detmis}
@@
 averaged grades, G$\ge$1.3 from three experts where 1-possibly, a lens,
-2-probably, a lens and 3-certainly, a lens. Another sample of over 100
-lens candidates is recovered from previously known samples of lens
-candidates.
+2-probably, a lens and 3-certainly, a lens. In addition, among the
+G$\ge$1.3 sample, we find 83 lens candidates from the various samples
+published in the literature.
 
@@
 which the magnitudes and the redshift are extracted.
-%Note: $\dagger$ are systems found in \citet{Gavazzi2014} as part of the additional
-%sample and $\ast$ is found in \citet{Maturi2014} sample.
 }\\
@@
 
-%%SW23$^{\dagger}$ & CFHTLS J023051-082423 &   37.7141 &   -8.4064 &  0.0 &  0.0 &  0.8 &  2.0 & ASW000412m &  0.4  &  A,E   \\
-%%SW41$^{\ast}$ & CFHTLS J221513+010240 &  333.8056 &    1.0446 &  0.0 &  0.0 &  0.8 &  1.7 & ASW0008dxh &  0.3  &  A,R/G   \\
-%%SW54$^{\dagger}$ & CFHTLS J140425+520506 &  211.1062 &   52.0850 &  0.4 & 18.9 &  1.4 &  1.3 & ASW0005o0w &  0.6  &  D,E   \\
 \twocolumn
@@
 \begin{center}
-\includegraphics[scale=1.0]{sw-cfhtls-figs/dlnp_skill.pdf}
+\includegraphics[scale=1.0]{dlnp_skill.pdf}
 \caption{ \label{fig:skilldlnp}
@@
 
-%{\bf todo:
-%check what happened to
-%those AF lenses which were labelled sims - look at the D11 counterparts
-%and their status in \StageOne swap}
-
-%%{\bf there are 70 images which have both sims and known lenses. for
-%the sims ID, 69 det and 1 rej (nearly 100% detected) whereas the
-%corresponding test IDs 30det-30rej (nearly 50% detected and 50%lost) --
-%what does this mean?}
-
-%%%%%%%%%%%%%%
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-% MNRAS does not use bibtex, input .bbl file instead.
-% Generate this in the makefile using bubble script in scriptutils:
-
-% bubble -f paper-lcr.tex references.bib
-% \input{paper-lcr.bbl}
-
 \bibliographystyle{apj}

### 2015-04-21 doc/sw-publication-policy-des.tex

@@
 \noindent \SW was conceived as a strong lens
-discovery {\it service} by harnessing the power of citizen scientists that the DES strong lensing group (hereafter DES survey science team or DES SST) can make use of
-(within the logistical constraints). In this document we discuss how the DES SST can become involved with \SW and the relationship
+discovery {\it service} that harnesses the power of citizen scientists.
+The DES strong lensing group (hereafter DES survey science team or DES SST) can make use of \SW within the logistical constraints.
+In this document we discuss how the DES SST can become involved with \SW and the relationship
 between the DES SST and the \SW collaboration. 
@@
 \SW comprises a primary `classification' interface (\texttt{http://spacewarps.org}) that allows citizen scientists to inspect images and mark those that contain potential gravitational lenses.
-In addition, these volunteers are shown simulated lenses (appropriate for the survey being conducted) as an interactive training tool that also allows us to establish the citizens' likelihood of identifying potential lenses and blank fields using the \SW Analysis Pipeline (SWAPR).
+A mandatory part of this inspection is the classification of simulated lenses (appropriate for the survey being conducted).
+The classification of simulated lenses acts as an interactive training activity that also allows us to establish the citizens' likelihood of identifying potential lenses and blank fields.
+This is fed into the \SW Analysis Pipeline (SWAPR) that analyses the classifications made per image (or subject in Zooniverse terms) giving a probability of whether an image contains a lens candidate or not.
 
@@
 Bugs can also be reported.
-This is the direct portal for communication with the \SW community.}).
+This is the direct portal for communication with the \SW community.}.
 
-In order to use \SW interface, the DES Survey Science Team \textbf{must define and propose a project to the \SW PIs} who will establish whether the use of the \SW interface is appropriate and liaise with the DES Survey Science Team to implement their project in the \SW interface.
+In order to use the \SW interface, the DES Survey Science Team \textbf{must define and propose a project to the \SW PIs} who will discuss whether the project is suitable with the SST.
+The \SW PIs will then liaise further with the SST to implement the project in the \SW interface.
 Details are given in Section \ref{sec:project}.
 
-\vspace{2mm}
+\vspace{4mm}
 The PIs of the \SW project are the authors of this document, P.\,Marshall, 
@@
 
-If required, an expanded definition of the \SW membership is given in the document ``\SW Publication Policy: CFHT-LS''\footnote{available from \texttt{\url{https://github.com/drphilmarshall/SpaceWarps/blob/master/doc/sw-publication-policy-cfhtls.pdf}}}, however this will not be relevant for publications, see Section \ref{sec:papers} for details.
+If required, an expanded definition of the \SW membership is given in the document ``\SW Publication Policy: CFHT-LS''\footnote{available from \texttt{\url{https://github.com/drphilmarshall/SpaceWarps/blob/master/doc/sw-publication-policy-cfhtls.pdf}}}, however this will not be relevant for \SW-DES publications, see Section \ref{sec:papers} for details.
 
@@
 The DES SST is expected to propose a project to the \SW collaboration that can be best or only be done using the power of citizen scientists.
-Typically this involves visual inspection tasks that are too time consuming for the SST themselves to execute.
-As such any science programme conducted through \SW should be complementary, not in competition, to the lens finding activities being carried out by the SST.
+Typically, this involves visual inspection tasks that are too time consuming for the SST themselves to execute.
+As such, any science programme conducted through \SW should be complementary, not in competition, to the lens finding activities being carried out by the SST.
 
-For example, in the first \SW project, the \SW collaboration conducted a lens finding search with \SW over the entire CFHT-LS survey area.
+For example, in the first \SW project, the collaboration conducted a lens finding search with \SW over the entire CFHT-LS survey area.
 The goal was to increase the completeness of strong lenses in the survey areas.
@@
 \SW complemented these searches with the potential to find strong lenses missed by these algorithms.
-The method, proposed by Anupreeta More (who served as the SST for this project), was to inspect the entire survey area by getting citizens to inspect $\sim$430,000 tiles of the survey area.
+The method, proposed by Anupreeta More (who served as the SST for this project), was to inspect the entire survey area by getting citizens to view $\sim$430,000 tiles of the survey area.
 This was a \textit{blind} search.
@@
 LRGs, groups, clusters, quasars.
-Again this was more images than the VICS82-SST could manage to inspect alone.
+Again, this was more images than the VICS82 SST could manage to inspect alone.
 
-Another approach is to use the \SW service to inspect the typically large output from automated algorithms or searches that are typically dominated by false positives.
+Another approach is to use the \SW service to inspect the normally large candidate lists generated by automated algorithms or searches, which are typically dominated by false positives.
 
@@
 \item The \SW facility should be used for science projects that cannot be completed by the Strong Lens Group itself. 
-\item Any \SW search should be complementary, not in competition, to the lens finding being conducted by the DES SST itself.
+\item Any \SW search should be complementary, not in competition, to the lens finding being conducted by the DES SST.
 \item While \SW uses citizen science, its primary goal is \textbf{not outreach}, it is harnessing citizen power for visual classifications (and eventually modelling) to perform science.
-\item A duplicate project is not encouraged provided there is sufficient scientific motivation and justification to do so.
+\item A duplicate project is not encouraged unless there is sufficient scientific motivation and justification to do so.
 \item \SW requires volunteers/citizens to give up their personal time to conduct the experiment, this should not be taken lightly, the crowd are motivated by contributing to real science not just doing things for the sake of them.
@@
 \item The success of \SW-DES will rely on input from the DES SST working with the \SW collaboration, dedicated effort is required for this and the DES SST should identify team members who can commit time to the \SW-DES tasks for this before embarking on a project.
-The \SW PIs will help to establish the main efforts required, these will depend on the actual project put forward by the DES SST (e.g.
-image preparation, simulations, interacting with volunteers on \Talk).
+The \SW PIs will help to establish the main efforts required, these will depend on the actual project put forward by the DES SST (e.g.\ image preparation, simulations, interacting with volunteers on \Talk).
 \end{enumerate}
@@
 
-The scientific project, process and outcome is the domain of the SST, the \SW collaboration enables this work by making it a live project on the website.
-We do not, per se, expect the \SW collaboration lead the resultant papers, we just request some of us are included on discovery papers in return for our help, see Section \ref{sec:papers} for more details on the publication policy.
+The scientific project, process and outcome is the domain of the SST.
+The \SW collaboration enables this work by making it a live project on the website.
+We do not, per se, expect the \SW collaboration lead the resultant papers, we just request some of us are included on discovery papers in return for our help, please see Section \ref{sec:papers} for more details on the publication policy.
 
-Please do remember that \SW is setup to provide a service to help your team find lenses.
-Any discovery in \SW-DES is the DES SSTs discovery.
-The goal of the \SW PIs or the \SW collaboration is to enable your science project and make it work.
-Using the automatic analysis pipeline (SWAPR) we will send the DES SST lists of the candidates selected by the citizens (at some regular intervals or at the end of a project).
-
-If the DES SST wish to have the \SW PIs input or to collaboratively work on targets the \SW team are happy to become more involved (the \SW PIs have strong lensing science interests).  
-The \SW team is happy to help with further grading of the candidates or assist with any scientific investigations and follow-up of the candidates, if the DES SST so requests.
+The goal of the \SW PIs and the \SW collaboration is to enable the DES SST's science project in \sw and make it work.
+Using the automatic analysis pipeline (SWAPR), the \SW PIs we will send the DES SST lists of the candidates selected by the citizens (at some regular intervals or at the end of a project), we will then discuss strategies for further analysis based on our experience of previous projects.
+Some members of the \SW PIs  and team may become more involved in analysis steps such as grading of the \sw candidates or assist with any scientific investigations and follow-up of the candidates, at the DES SST's request.
 
@@
 This is not the function or purpose of the \SW interface or the Zooniverse.
-However  it will be possible for DES SST members to view the images in parallel with the crowd through the public interface.
+However,  it will be possible for DES SST members to view the images in parallel with the crowd through the public interface.
 The DES SST members who wish to do this will need to register with the Zooniverse to classify.
-We can extract the classifications of SSTs only to provide and expert selected sample, if required.
+We can extract the classifications of SSTs only to provide an expert selected sample, if required.
 The images marked by any inspector (SST or citizen)  are automatically recorded in an individual's \SW/Zooniverse account.
@@
 
-\SW \Talk is a key and integral part of \SW.
-The DES SST are strongly encouraged to interact with the volunteers on \Talk.
-This exchange allows the crowd to learn from the experts, this in turn has the very positive effect of motivating the citizens to contriute further.
+\SW\ \Talk is a key and integral part of \SW.
+The DES SST is strongly encouraged to interact with the volunteers on \Talk.
+This exchange allows the crowd to learn from the experts, this in turn has the very positive effect of motivating the citizens to contribute further.
 In addition it also results in better and informed classification when they return to that task.
-
-Note that all possible candidates are in the public domain as all images are available online (but without WCS information).
+Thus, engagement of the SST is very important in log-term surveys such as DES.
 
@@
 Thus, we recommend that all DES members with an interest in strong lensing are told about \SW and how it can complement their lens finding effort.
-We are here to assist your science!
+Our goal is to enable your science.
 While we can't expect the entirety of the DES Strong Lensing Group or the STRIDES consortium to be behind \SW-DES, all should be made aware of the projects being undertaken and planned with \SW.
 
-We encourage the DES SST to strongly consider the timing for when they wish to ingest the images into \SW so that it is in line with the interests of the DES SST and consortium.
+We also encourage the DES SST to consider the timing for when they wish to ingest the images into \SW so that it is in line with the interests of the DES SST and those of the DES consortium.
 
@@
 \begin{itemize}
-\item \textbf{New Data}:Inspection of areas (targeted or blind) that the SST has not had time to inspect, i.e. use the crowd to increase the speed at which potential lens candidates are discovered
+\item \textbf{New Data}: Inspection of areas (targeted or blind) that the SST has not had time to inspect, i.e. use the crowd to increase the speed at which potential lens candidates are discovered
 \item \textbf{Comparison of Expert vs Citizen Classification}: DES SST and citizen's view images in parallel (targeted or blind)
@@
 
-Note that the projects that you propose to \SW need not be one of the above.
-You can also suggest multiple projects that we could run in a mixture or phased set of experiments.
-Please do consider your timeline with reference to data release and the searches the DES SST want to make themselves.
+Note that the projects that are proposed to \SW need not be one of the above.
+Multiple projects could also be run in a mixture or phased set of experiments.
+Please do consider the DES timeline with reference to data release and the searches the DES SST want to make themselves.
 
-If the DES SST wants to inspect targets within the consortium and is concerned about being scooped, we suggest that this should happen first before images are passed to \SW.
-We would then label any images containing candidate lenses already discovered by the SST as `known lens candidates'.
-This applies to visually inspected by the SST or algorithm searched images.
+If the DES SST wants to inspect targets within the consortium and is concerned about being scooped by the crowd, please be assured that there is little scope or motivation to do this.
+If the project is well defined, the goal of \SW-DES will be a complementary part of the DES SST lens finding strategy.
+By definition this means that \SW is working with the DES SST as it is designed to do.
+In addition, the images could be stripped of WCS info (described in Section \ref{sec:data}), meaning that no-one other than the SST can follow-up or catalogue the targets\footnote{We cannot exclude the possibility that individual sources might be serendipitously identified e.g.
+by recognisable morphologies.}.
+The DES SST could also perform their inspection before the images are passed to \SW.
+Any lens candidates discovered by the SST would then be labelled as `known lens candidates' in \sw\,\Talk.
+This applies to candidates discovered through visual inspection or algorithm based searches.
 
 \subsection{What to do next: Project Proposals}
-Once you have narrowed down what search you would like to do with \SW, please approach the \SW PIs (Phil Marshall, Anupreeta More, Aprajita Verma, collectively contacted via \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com}) with a short description of their project that includes the following information.
+Once the DES SST have narrowed down what search to be conducted \SW, please approach the \SW PIs (Phil Marshall, Anupreeta More, Aprajita Verma, collectively contacted via \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com}) with a short description of the project that includes the following information.
 
@@
 \item Survey area
-\item Bands to be included
+\item Bands that could be included
 \item Total number of images to be viewed (approx.)
-\item Targeted survey or blind field search \footnote{Targeted: inspection of a list of candidates; Blind: inspection of tiles of a survey area}
+\item Targeted survey or blind field search\footnote{Targeted: inspection of a list of candidates; Blind: inspection of tiles of a survey area}
 \item Brief outline of the overall goal(s) of that inspection, highlighting how this is complementary (not competing) with the goals of the DES lens finding group
 \item Proprietary data issues 
-\item identify an initial core team who will lead and work closely with \SW
+\item Identify an initial core team who will lead and work closely with \SW
 \end{itemize}
 
-Note, the proposed science project(s) should harness citizen classification power to achieve your science goals.
+Note, the proposed science project(s) should harness citizen classification power to achieve the science goals.
 
-The \SW PIs will then arrange a telecon with the DES SST to discuss the project further. This includes discussing effort required and roles for the the SST team for expected tasks.
+The \SW PIs will then arrange a telecon with the DES SST to discuss the project further. This includes discussing the initial effort required and roles for the the SST team for expected tasks.
 
@@
 
-However, some surveys including DES come with their own proprietary access policy. It is the responsibility
+However, some surveys, including DES, come with their own proprietary access policy. It is the responsibility
 of the DES SST to provide images to \SW in a way that is consistent
@@
 
-Implementing a new project based on different survey data will require support from the \SW Science Team, in three respects:
+Implementing a new project based on different survey data will require support from the \SW consortium, in four respects:
 
@@
 
-\item In {\bf running the \SW analysis pipeline} which will be our responsibility. This will provide citizen selected candidates to be sent to the DES SST.
+\item In {\bf running the \SW analysis pipeline} (SWAPR) which will be the \sw PIs responsibility. This will provide citizen selected candidates to be sent to the DES SST.
 
@@
 posts in  \Talk, is the primary means by which we expect \SW-DES collaboration
-members will communicate their findings to the rest of the
+members (citizens participating in the project) will communicate their findings to the rest of the
 astronomical community. The investigation of any \SW images that are
 provided without world coordinate system (WCS) information will be
-necessarily limited but the \SW Zooniverse \Letters will contribute to the collective knowledge and understanding of the presented system(s). Zooniverse \Letters are citable\SW
+necessarily limited but the \SW Zooniverse \Letters will contribute to the collective knowledge and understanding of the presented system(s). Zooniverse \Letters are citable \SW
 objects, and in some cases will appear listed on ADS\footnote{To be confirmed.}.
@@
 This web page will be linked in every ensuing \SW publication.
-If a community member makes a significant contribution e.g.\,in the further investigation of a lens candidate with modelling tools, they are strongly encouraged to write Zooniverse \Letters.
+If a community member makes a significant contribution e.g.\ in the further investigation of a lens candidate with modelling tools, they are strongly encouraged to write Zooniverse \Letters.
 This may lead to them being invited to join journal publications by the lead author of a ``discovery'' publication.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-04-23 doc/sw-system.tex
Screengrab compressed to 64k JPG #154
PNG images compressed to JPG and converted to PDF, figs folder now 3.6M, paper PDF is 4.9M #154

--- 2015-04-21 doc/sw-system.tex
@@
 \begin{figure*}
-\centering\includegraphics[width=0.9\linewidth]{sw-screengrab-marker+feedback.png}
+\centering\includegraphics[width=0.9\linewidth]{sw-screengrab-marker+feedback.pdf}
 \caption{Screenshot of the \SW classification interface.}
@@
 \begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{CFHTLS_2013-10-29_10:16:35_probabilities.png}
+\centering\includegraphics[width=0.9\linewidth]{CFHTLS_2013-10-29_10:16:35_probabilities.pdf}
 \caption{Typical \SW agent confusion matrix elements. At a particular
@@
 \begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{CFHTLS_2013-10-29_10:16:35_trajectories.png}
+\centering\includegraphics[width=0.9\linewidth]{CFHTLS_2013-10-29_10:16:35_trajectories.pdf}
 \caption{Typical \SW \StageOne subject trajectories. Top: 200 randomly-selected
@@
     \begin{minipage}{0.46\linewidth}
-      \centering\includegraphics[width=\linewidth]{ASW0008wyp_gri.png}
+      \centering\includegraphics[width=\linewidth]{ASW0008wyp_gri.pdf}
     \end{minipage}\hfill
     \begin{minipage}{0.50\linewidth}
-      \centering\includegraphics[width=\linewidth]{ASW0008wyp_stage2_trajectory.png}
+      \centering\includegraphics[width=\linewidth]{ASW0008wyp_stage2_trajectory.pdf}
     \end{minipage}
@@
     \begin{minipage}{0.46\linewidth}
-      \centering\includegraphics[width=\linewidth]{ASW0006rkx_gri.png}
+      \centering\includegraphics[width=\linewidth]{ASW0006rkx_gri.pdf}
     \end{minipage}\hfill
     \begin{minipage}{0.50\linewidth}
-      \centering\includegraphics[width=\linewidth]{ASW0006rkx_stage1_trajectory.png}
+      \centering\includegraphics[width=\linewidth]{ASW0006rkx_stage1_trajectory.pdf}
     \end{minipage}
@@
     \begin{minipage}{0.46\linewidth}
-      \centering\includegraphics[width=\linewidth]{ASW0000fgj_gri.png}
+      \centering\includegraphics[width=\linewidth]{ASW0000fgj_gri.pdf}
     \end{minipage}\hfill
     \begin{minipage}{0.50\linewidth}
-      \centering\includegraphics[width=\linewidth]{ASW0000fgj_stage1_trajectory.png}
+      \centering\includegraphics[width=\linewidth]{ASW0000fgj_stage1_trajectory.pdf}
     \end{minipage}
@@
     \begin{minipage}{0.46\linewidth}
-      \centering\includegraphics[width=\linewidth]{ASW0003j2s_gri.png}
+      \centering\includegraphics[width=\linewidth]{ASW0003j2s_gri.pdf}
     \end{minipage}\hfill
     \begin{minipage}{0.50\linewidth}
-      \centering\includegraphics[width=\linewidth]{ASW0003j2s_stage1_trajectory.png}
+      \centering\includegraphics[width=\linewidth]{ASW0003j2s_stage1_trajectory.pdf}
     \end{minipage}

### 2015-04-23 doc/sw-system.tex
Compressed PDF plots via JPG, from 2.0M to 770K #154

@@
 \begin{minipage}{0.45\linewidth}
-  \centering\includegraphics[width=\linewidth]{stage1_ROC.pdf}
+  \centering\includegraphics[width=\linewidth]{stage1_ROC_compressed.pdf}
 \end{minipage}\hfill
 \begin{minipage}{0.45\linewidth}
-  \centering\includegraphics[width=\linewidth]{stage2_ROC.pdf}
+  \centering\includegraphics[width=\linewidth]{stage2_ROC_compressed.pdf}
 \end{minipage}
@@
 \begin{figure}
-\centering\includegraphics[width=\linewidth]{completeness_purity_simple.pdf}
+\centering\includegraphics[width=\linewidth]{completeness_purity_simple_compressed.pdf}
 \caption{Completeness-estimated purity curves for the \sw system, using
@@
 \begin{figure*}
-\centering\includegraphics[width=0.9\linewidth]{all_skill_contribution_experience_education.pdf}
+\centering\includegraphics[width=0.9\linewidth]{all_skill_contribution_experience_education_compressed.pdf}
 \caption{Key properties and contributions of the \SW \StageOne crowd.
@@
 \begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{crowd_contrib_cumul.pdf}
+\centering\includegraphics[width=0.9\linewidth]{crowd_contrib_cumul_compressed.pdf}
 \caption{Cumulative distributions of the contributions made by the agents: 90\%
@@
 \begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{crowd_skill_cumul.pdf}
+\centering\includegraphics[width=0.9\linewidth]{crowd_skill_cumul_compressed.pdf}
 \caption{Broad cumulative distributions of agent skill:
@@
 \begin{figure}
-\centering\includegraphics[width=\linewidth]{rate_classification.pdf}
+\centering\includegraphics[width=\linewidth]{rate_classification_compressed.pdf}
 \caption{Fractional classification rate in the \SW \cfhtls survey. Fractional classification rate is the number
@@
 \begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{stage2_veteran_contribution.pdf}
+\centering\includegraphics[width=0.9\linewidth]{stage2_veteran_contribution_compressed.pdf}
 \caption{\StageTwo classifier skill, as a function of their \StageOne skill.

### 2015-04-23 analysis/make_crowd_plots.py

@@ -244,7 +244,7 @@ def make_crowd_plots(argv):
 
     # 1.1 Contribution
 
-    plt.figure(figsize=(10,8),dpi=300)
+    plt.figure(figsize=(10,8),dpi=100)
 
     # All Stage 1 volunteers:
     cumulativecontribution1_all = np.cumsum(np.sort(contribution_all)[::-1])
@@ -299,7 +299,7 @@ def make_crowd_plots(argv):
 
     # 1.2 Skill
 
-    plt.figure(figsize=(10,8),dpi=300)
+    plt.figure(figsize=(10,8),dpi=100)
 
     # All Stage 1 volunteers:
     cumulativeskill1_all = np.cumsum(np.sort(final_skill_all)[::-1])
@@ -352,6 +352,7 @@ def make_crowd_plots(argv):
 
     # Plot #2: is final skill predicted by early skill?
 
+    """ Commented out as we left this out of the paper.
     N = len(final_skill)
     prodigies_final_skill = final_skill[np.where(early_skill > 0.1)]
     Nprodigies = len(prodigies_final_skill)
@@ -360,7 +361,7 @@ def make_crowd_plots(argv):
     print "make_crowd_plots: the",Nprodigies,"-",phr(100*Nprodigies/N),"% - of experienced stage 1 volunteers who have early skill > 0.1 go on to attain a mean final skill of",phr(mean_prodigies_skill,ndp=2)
     print "make_crowd_plots: with",phr(100*Ngood_prodigies/Nprodigies),"% of them remaining at skill 0.05 or higher"
 
-    plt.figure(figsize=(10,8),dpi=300)
+    plt.figure(figsize=(10,8),dpi=100)
     plt.xlim(-0.02,0.25)
     plt.ylim(-0.02,0.8)
     plt.xlabel('Early Skill, $\langle I \\rangle_{j<10}$ / bits')
@@ -375,7 +376,8 @@ def make_crowd_plots(argv):
     pngfile = output_directory+'early_vs_final_skill.pdf'
     plt.savefig(pngfile, bbox_inches='tight')
     print "make_crowd_plots: skill-skill plot saved to "+pngfile
-
+    """
+    
     # ------------------------------------------------------------------
 
     # Plot #3: corner plot for 5 variables of interest; stage1 = blue shaded, stage2 = orange outlines.
@@ -425,7 +427,7 @@ def make_crowd_plots(argv):
[…]

### 2015-04-23 doc/sw-system.tex
Removed colons from filenames. Closes #154
Master branch now contains paper with full-resolution plots. Low resolution version is in the arxiv branch. #154

--- 2015-04-23 doc/sw-system.tex
@@
 \begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{CFHTLS_2013-10-29_10:16:35_probabilities.pdf}
+\centering\includegraphics[width=0.9\linewidth]{CFHTLS_2013-10-29_101635_probabilities.pdf}
 \caption{Typical \SW agent confusion matrix elements. At a particular
@@
 \begin{figure}
-\centering\includegraphics[width=0.9\linewidth]{CFHTLS_2013-10-29_10:16:35_trajectories.pdf}
+\centering\includegraphics[width=0.9\linewidth]{CFHTLS_2013-10-29_101635_trajectories.pdf}
 \caption{Typical \SW \StageOne subject trajectories. Top: 200 randomly-selected
@@
 \begin{figure*}
-\begin{minipage}{0.45\linewidth}
+\begin{minipage}{0.48\linewidth}
   \centering\includegraphics[width=\linewidth]{stage1_ROC.pdf}
 \end{minipage}\hfill
-\begin{minipage}{0.45\linewidth}
+\begin{minipage}{0.48\linewidth}
   \centering\includegraphics[width=\linewidth]{stage2_ROC.pdf}
@@
 contributions these volunteers make (third row) and the information they
-generate (fourth row), and we suggest that this would be a useful metric for determining 'well-designed' implementations of citizen science projects.
+generate (fourth row), and we suggest that this would be a useful metric for
+determining ``well-designed'' implementations of citizen science projects.
 

### 2015-04-24 doc/sw-extended.tex
updating swap extended

@@
 \label{sec:formalism}
+
+\todo{Chris}{This section will describe the different ways we can use the data
+  we got from SpaceWarps to do a beter job with classifications. So we can then
+  look at the way SpaceWarps updates the PL, PD, and p's of the objects, either
+  via offline, using both/either/neither training and test data (in either online or offline
+contexts), manipulating initializations, etc. We could also see what the
+benefits are for using the known lens information. Finally, we should examine the
+benefits of using a validation dataset (using information we already have!) to
+improve our estimates.}
 
@@
 
-\section{Validation of Training}
+\subsection{Validation of Training}
 \label{sec:validation}
+
+\todo{Chris}{In order to look at a validation dataset, I need to create a
+  blacklist of agents and subjects (and decide what sort of division of either
+/ both / neither constitutes a good validation dataset here) that SWAP.py can
+then read in and process.}
 
@@
 4. Can I just use the dud fields?
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\section{Dynamic Allocations}
+\todo{Chris}{This section will examine whether we would be better off
+  dynamically assigning images to people (based on current estimates of skill
+  and probability) rather than randomly assigning them. This means I will need
+  to create some sort of 'SpaceWarps Emulator'. (Actually, the other thing
+  I can do is use the blacklist developed earlier to throw out
+  contributions in an informed manner in order to construct different
+  simulations.) Before I even do that, another
+aspect I would like to examine and is probably useful is whether we can
+reliably identify skilled users early on. That is, instead of looking at final
+skill vs effort, look at many trajectories of skill vs effort over time. That
+would be a useful thing to show to prove that we can find the good users in the
+first place -- early on!}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 
@@
 
-\section{Probabilistic Classification Analysis}
-\label{appendix:swap}
-
-Our aim is to enable the construction of a sample of good lens candidates.
-Since we aspire to making logical  decisions, we define a  ``good candidate''
-as one which has a high posterior probability of being a lens, given the data:
-$\pr(\LENS|\data)$. Our problem is to approximate this probability. The data~$\data$
-in our case are the pixel values of a colour image. However, we can greatly
-compress these complex, noisy sets of data by asking each volunteer what they
-think about them. A complete  classification in \sw consists of a set of
-Marker positions, or none at all. The null set encodes the statement from
-the volunteer that the image in question is $\saidNOT$ a lens, while the
-placement of any  Markers indicates that the volunteer considers this image to
-contain a $\saidLENS$.  We simplify the problem by only using the Marker
-positions to assess whether the volunteer  correctly assigned the
-classification $\saidLENS$ or $\saidNOT$ after viewing (blindly) a member of
-the training set of subjects.
-
-How should we model these compressed data? The circumstances of each
-classification are quite complex, as are the human classifiers in general: the
-volunteers learn more about the problem as they go, but also inevitably make
-occasional mistakes (perhaps because a lens is difficult to see, or they
-became distracted during the task). To cope with this uncertainty, we assign a
-simple software {\it agent} to partner each volunteer. The agent's task is to
-interpret their volunteer's classification data as best it can, using a model
-that makes a number of necessary approximations. These interpretations will
-then include uncertainty arising as a result of the volunteer's efforts and
-also the agent's approximations, but they will have two important redeeming
-features. First, the interpretations will be quantitative (where before they
-were qualititative),  and thus will be useful in decision-making. Second, the
-agent will be able to predict, using its model, the probability of a test
-subject being a $\LENS$, given both its volunteer's classification, and its
-volunteer's experience. In this appendix we describe how these agents work,
-and other aspects of the \sw analysis pipeline (SWAP).
-
-\subsection{Agents and their Confusion Matrices}
-\label{appendix:swap:probabilities}
-
-Each agent assumes that the probability of a volunteer recognising any given
-simulated lens as a lens is some number, $\pr(\saidLENS|\LENS,\training)$, that
-depends only on what the volunteer is currently looking at, and all the
-previous training subjects they have seen (and not on what type of lens it is,
-how faint it is, what time it is, \etc). Likewise, it also assumes that the
-probability of a volunteer recognising any given dud image as a dud is some
-other number, $\pr(\saidNOT|\NOT,\training)$, that also depends only on what the volunteer is currently looking at, and all the
-previous training subjects they have seen. These two probabilities define a 
-2 by 2 ``confusion matrix,'' which the agent updates, every time a
-volunteer classifies a training subject, using the following 
-very simple estimate:
-\be
-  \pr(``X"|X,\training) \approx \frac{N_{``X"}}{N_X}.
-  \label{eq:app:fraction}
-\ee
-Here, $X$ stands for the true classification of the subject, \ie either
-$\LENS$ or $\NOT$, while $``X''$ is the corresponding classification
-made by the volunteer on viewing the subject. $N_X$ is the number of
-lenses the volunteer has been shown, while $N_{``X"}$ is the number of 
-times the volunteer got their classifications of this type of training subject
-right. $\training$ stands for all
-$N_{\LENS} + N_{\NOT}$ training data that the agent has heard about to
-date.
-
-The full confusion matrix of the $k^{\rm th}$ volunteer's agent is therefore:
-\begin{align}
-  \CM^k &= 
-  \begin{bmatrix}
-    \pr(\saidLENS|\NOT,\trainingk) & \pr(\saidLENS|\LENS,\trainingk) \\
-    \pr(\saidNOT |\NOT,\trainingk) & \pr(\saidNOT |\LENS,\trainingk)
-  \end{bmatrix}, \notag \\
-        &=
-  \begin{bmatrix}
-    \CM_{LN} & \CM_{LL} \\
-    \CM_{NN} & \CM_{NL}
-  \end{bmatrix}^k.
-  \label{eq:confmat}
-\end{align}
-Note that these probabilities are normalized, such that
-$\pr(\saidNOT |\NOT) = 1 - \pr(\saidLENS|\NOT)$.
-
-Now, when this volunteer views a test subject, 
-it is this confusion matrix that will allow their agent to update the
-probability of that test subject being a $\LENS$. Let us suppose that
-this subject has never been seen before: the agent assigns a 
-prior probability that it is (or contains) a lens is 
-\be
-  \pr(\LENS) = p_0
-\ee
-where we have to assign a value for $p_0$. In the CFHTLS, we might expect
-something like 100 lenses in 430,000 images, so $p_0 = 2\times10^{-4}$
-is a reasonable estimate. The volunteer then makes a classification $C_k$ 
-($= \saidLENS$ or $\saidNOT$).
-We can apply Bayes' Theorem to derive how the agent should
-update this prior probability into a posterior one using this new information:
-\begin{align}
-  \label{eq:app:first}
-  & \pr(\LENS|C_k,\trainingk) = \\
-  & \frac{\pr(C_k|\LENS,\trainingk)\cdot\pr(\LENS)}
-{\left[ \pr(C_k|\LENS,\trainingk)\cdot\pr(\LENS) + \pr(C_k|\NOT,\trainingk)\cdot\pr(\NOT) \right]},
-  \notag
-\end{align}
-which can be evaluated numerically using the elements of the confusion
-matrix.
-
-\subsection{Examples}
-\label{appendix:swap:examples}
-
-Suppose we have a volunteer who is always right about the true
-nature of a training subject. 
-Their agent's confusion matrix would be
-\be
-  \CM^{\rm perfect} = 
-  \begin{bmatrix}
-    0.0 & 1.0 \\
-    1.0 & 0.0
-  \end{bmatrix}.
-\ee
-On being given a fresh subject that actually is a $\LENS$, this hypothetical
-volunteer would submit $C = \saidLENS$.  Their agent would then calculate the
-posterior probability for the subject being a $LENS$ to be
-\begin{align}
-  \pr(\LENS|\saidLENS,\trainingk) &= \frac{1.0 \cdot p_0}
-           {\left[ 1.0\cdot p_0 + 0.0\cdot(1 - p_0) \right]}
-   &= 1.0,
-\end{align}
-as we might expect for such a {\it perfect} classifier.  Meanwhile, a
-hypothetical volunteer who (for some reason) wilfully always submits the wrong
-classification would have an agent with the column-swapped confusion matrix
-\be
-  \CM^{\rm obtuse} = 
-  \begin{bmatrix}
-    1.0 & 0.0 \\
-    0.0 & 1.0
-  \end{bmatrix},
-\ee
-and would submit $C = \saidNOT$ for this subject. However, such a volunteer
-would nevertheless be submitting useful information, since given the above
-confusion matrix, their agent would calculate
-\begin{align}
-  \pr(\LENS|\saidNOT,T_k) &= \frac{1.0 \cdot p_0}
-           {\left[ 1.0\cdot p_0 + 0.0\cdot(1 - p_0) \right]}
-   &= 1.0.
-\end{align}
-{\it Obtuse} classifiers turn out to be as helpful as {\it perfect} ones.
-
-\subsection{Online SWAP: Updating the Subject Probabilities}
-\label{appendix:swap:examples}
-
-Suppose the $k+1^{\rm th}$ volunteer now submits a classification, on the same
-subject just classified by the $k^{\rm th}$ volunteer. We can generalise
-\Eref{eq:app:first} by replacing the prior probability with the current
-posterior probability:
-\begin{align}
-  \label{eq:app:update}
-  \pr(\LENS & |C_{k+1},\training_{k+1},\data) = \\
-  & \frac{1}{Z} \pr(C_{k+1}|\LENS,\training_{k+1}) \cdot \pr(\LENS|\data) \\ \notag
-{\rm where}\;\; Z = & \pr(C_{k+1}|\LENS,\training_{k+1})\cdot\pr(\LENS|\data) \\ \notag
-      & + \pr(C_{k+1}|\NOT,\training_{k+1})\cdot\pr(\NOT|\data), \notag
-\end{align}
-and $\data = \{C_k,\trainingk\}$ is the set of all previous
-classifications, and the set of training subjects seen by each of those
-volunteers.
-$\pr(\LENS|\data)$ is the fundamental property of each test subject that
-we are trying to infer. We track $\pr(\LENS|\data)$ as a function of time,
-and by comparing it to a lower or upper thresholds, make decisions about
-whether to retire the subject from the classification interface or
-promote it in \Talk, respectively.
-
-\subsection{Information Gain per Classification, Agent ``Skill'' and ``Contribution''}
-\label{appendix:swap:examples}
-
-With an agent's confusion matrix in hand we can compute the
-\emph{information} generated in any given classification. This will
-depend on the confusion matrix elements (\Eref{eq:confmat}) but also on
-the probability of the subject being classified containing a lens. The
-quantity of interest is the relative entropy, or Kullback-Leiber
-divergence, between the prior and
-posterior probabilities for the possible truths $T$
-given the submitted classification $C$:
-\begin{align}
-\information =& \sum_T \pr(T|C) \log_2 \frac{\pr(T|C)}{\pr(T)}     \notag \\
-             =&    \pr(\LENS|C) \log_2 \frac{\pr(C|\LENS)}{\pr(C)} \notag \\
-             +&    \pr(\NOT|C)  \log_2 \frac{\pr(C|\NOT)}{\pr(C)},
-\end{align}
-where, as above, $C$ can take the values $\saidLENS$ or $\saidNOT$. 
-Substituting for the posterior probabilities using \Eref{eq:app:first} we get
-an expression that just depends on the elements of the 
-confusion matrix $\CM$ and the pre-classification subject lens
-probability $\pr(\LENS) = p$:
-\begin{align}
-\information =    &     p \frac{\CM_{CL}}{p_c} \log_2 \frac{\CM_{CL}}{p_c}  \notag \\
-                  & +(1-p)\frac{\CM_{CN}}{p_c} \log_2 \frac{\CM_{CN}}{p_c},
-  \label{eq:app:infogain}
-\end{align}
-where the common denominator $p_c = p\CM_{CL} + (1-p)\CM_{CN}$. This
-expression has many interesting features.  If $p$ is either zero or one,
-$\information(C) = 0$  regardless of the value of $C$ or the values of
-the confusion matrix elements: if we know the subject's status with
-certainty, additional classifications supply no new information. If we
-set $p$ to be the prior probability, \Eref{eq:app:infogain} tells us how
-much information is generated by classifying it all the way to $p = 1$
-(which a perfect classifier, with $\CM_{LL} = \CM_{NN} = 1$, can do in a
-single classification). For a prior probability of $2\times 10^{-4}$, 
-12.3 bits are generated in such a ``detection.''  Conversely, only
-0.0003 bits are generated during the rejection of a subject with the
-same prior: we are already fairly sure that each subject does not
-contain a lens! Imperfect classifiers (with $\CM_{LL}$ and $\CM_{NN}$
-both less than 1)  generate less than these maximum amounts of
-information each classification; the only classifiers that generate zero
-information are those that have $\CM_{LL} = 1 - \CM_{NN}$ (or
-equivalently, $\CM_{CL} = \CM_{CN}$ for all values of $C$). We might
-label such classifiers as ``random'', since they are as likely to
-classify a subject as a $\saidLENS$ no matter the true content of that
-subject.
-
-\Eref{eq:app:infogain} suggests a useful information theoretical 
-definition of the classifier skill  perceived by the agent. At a fixed
-value of $p$, we can take the expectation value of the information gain
-$\information$ over  the possible classifications that could be made:
-\begin{align}
-\langle\information\rangle   =& \sum_C \sum_T \pr(T|C) \pr(C) \log_2 \frac{\pr(T|C)}{\pr(T)} \notag \\ 
-         =& - \sum_T \pr(T) \log_2 \pr(T) \notag \\ 
-          & + \sum_C \pr(C) \sum_T \pr(T|C) \log_2 \pr(T|C) \notag \\ 
-         =&         p  \left[ \mathcal{S}(\CM_{LL}) + \mathcal{S}(1-\CM_{LL}) \right] \notag \\
-          &     +(1-p) \left[ \mathcal{S}(\CM_{NN}) + \mathcal{S}(1-\CM_{NN}) \right] \notag \\
-          & - \mathcal{S}\left[ p    \CM_{LL}       + (1-p)(1-\CM_{NN})     \right] \notag \\
-          & - \mathcal{S}\left[ p (1-\CM_{LL})      + (1-p)   \CM_{NN}      \right] 
-\end{align}
-where $\mathcal{S}(x) = x \log_2{x}$. If we choose to
-evaluate $\langle\information\rangle$ at $p = 0.5$, the result has some
-useful properties. While random classifiers presented with  $p = 0.5$
-subjects have $\skill = 0.0$  as expected, perfect classifiers appear to
-the agents to have  $\skill = 1.0$. This suggests that  $\skill$, the
-amount of information we expect to  gain when a classifier is presented
-with a 50-50 subject, is a reasonable quantification of 
-\emph{normalised skill}. A consequence of this choice is that the
-integrated skill (over all agents' histories) should come out to be
-approximately 
-equal to the number of subjects in the survey, when the search is
-``complete'' (and all subjects are fully classified). Therefore, a
-particular agent's integrated skill is a reasonable 
-measure of that classifier's
-\emph{contribution} to the lens search.
-
-We conservatively initialize both elements of each  agent's confusion
-matrix to be $\CM^0_{LL} = \CM^0_{NN} = 0.5$, that of a maximally ambivalent  random classifier, so
-that all agents start with zero skill. While  this makes no allowance
-for volunteers that actually do have previous experience of what
-gravitational lenses look like, we might expect it to help mitigate
-against false positives. Anyone who classifies more than one image (by
-progressing beyond the tutorial) makes a non-zero information
-contribution to the project.
-
-The total information generated during the CFHTLS project is shown in
-\Tref{tab:crowd:contributions}. Interpreting these numbers is not easy, but we
-might do the following. Dividing this by the amount of information it takes to
-classify a \sw subject all the way to the detection threshold (lens
-probability 0.95), and then multiplying by the survey inefficiency gives us a
-very rough estimate for the effective number of detections corresponding to
-the crowd's contribution: these are 2830 and 25 bits for stages 1 and 2
-respectively.  These figures are close to the numbers of detections given in
-column 7 of the table.  
-% The uncertainty in the interpretation of the total
-% information generated provides some justification for our focus on the
-% expected information gain as a measure of volunteer contribution.
-
-\subsection{Uncertainty in the Agent Confusion Matrices}
-\label{appendix:swap:uncertainty}
-
-Finally, the confusion matrix obtained from the application of
-\Eref{eq:app:fraction} has some inherent noise which reduces as the
-number of training subjects classified by the agent's volunteer
-increases. For simplicity, the discussion has thus far assumed the case
-when the confusion matrix is known perfectly; in practice, we allow for
-uncertainty in the agent confusion matrices by averaging over a small
-number of samples drawn from Binomial distributions characterised by the
-matrix elements $\pr(C_k|\LENS,\trainingk)$ and  $\pr(C_k|\NOT,\trainingk)$. The
-associated standard deviation in the estimated subject probability
-provides an error bar for this quantity.
-
-% For ease of notation, we will denote $\pr(C_k|\LENS,T_k)\equiv p_L$ and
-% $\pr(C_k|\NOT,T_k)\equiv p_N$. In reality, there is a probability distribution
-% for both $p_L$ and $p_N$. Let $p_0$ be the prior probability of the subject
-% being a lens. Then the posterior probability, $p_0'$ of the subject being a
-% lens after the classification $C_k$ is
-% \be
-%   \label{eq:app:sec}
-% p_0' = \frac{p_L p_0}{\left[ p_L p_0 + p_N (1- p_0) \right]},
-% \ee
-% The posterior probability distribution $p_0'$ can be obtained by marginalizing
-% over the probability distributions of $p_L$, $p_N$ and the prior probability
-% distribution $p_0$ such that,
-% \be
-% P(p_0') = \int p_0' P(p_L) P(p_N) P(p_0) dp_L dp_N dp_0\,.
-% \ee
-% This marginalization is not analytically tractable. Therefore, we have
-% implemented the following Monte-Carlo solution for this problem.
-%
-
-%Finally, we also need to update the confusion matrix of an agent and obtain the
-%variance on each element of the matrix, once a training subject has been
-%classified. We would like to derive the posterior probability of the
-%probability elements $p_1$ and $p_2$ given their prior probabilities. For this
-%purpose, we can again make use of Bayes' theorem,
-%\begin{equation}
-%P(p_x'|N_{"X"},N_X,T) = \frac{P(N_{``X"}|p_x',N_X,T) P(p_x'|N_X,T)}{\sum_{N_{``X"}} P(N_{``X"}|p_x',N_X,T) P(p_x'|N_X,T)}
-%\end{equation}
-%Here, $P(N_{``X"}|p_x',N_X,T)$ is a binomial distribution, although this is not
-%true strictly speaking given that our agents are learning and the values of the
-%confusion matrix are moving. Modelling the learning curve of our users is yet
-%another complicated extension we could think about.
-
-\subsection{Offline SWAP}
-\label{appendix:swap:offline}
-
-The probabilistic model described above does not need to be implemented as an
-online inference. Indeed, it might be more appropriate to perform the inference
-of all Agent confusion matrix elements and Subject probabilities
-simultaneously, so that the early classifications are not effectively
-downweighted as a result of the Agent's ignorance. It might also be that this
-ignorance builds in some conservatism to the system, reducing the noise due
-the early classifications if they are unreliable. In the joint analysis, the
-basic assumption that is built into the Agents, that their volunteers
-have innate and unchanging talent for lens spotting parameterised by two 
-constant confusion matrix elements which simply need to be inferred given the
-data, is implemented in full. The effect is that of applying the time-averaged
-confusion matrices, rather than one that evolves as the Agents (and in the
-real world, the volunteers) learn.
-
-The mathematics of the offline inference are presented elsewhere (in
-preparation). Here we briefly note that we maximize the joint posterior
-probability distribution for all the model parameters (some 66,000 confusion
-matrix elements and 430,000 subject probabilities) with a simple
-expectation-maximisation algorithm. This procedure takes approximately the
-same CPU time as the stage 2 online analysis, because no matrix inversions are
-required in the algorithm. The algorithm scales well and is actually faster
-than the online analysis with the larger stage 1 dataset. The
-expectation-maximisation algorithm is robust to initial starting parameters
-in, e.g., initial Agent confusion matrix elements and Subject probabilities.
-The plots in \Sref{sec:results:sample} show the difference in performance
-between the online and offline analyses.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-04-30 doc/sw-system.tex
Cleaned out old PNGs, switched latex to use new smaller PDFs, and includegraphics over epsfig (for speed). Total size of all graphics now 3.2Mb, closes #161
Reading through, line by line, for spelling, grammar etc.

@@
 \usepackage{amsmath}
-\usepackage{epsfig}
 
@@
 Carefully produced colour composite images are displayed to volunteers via a
-classification interface which records their estimates of the positions of
+web-based classification interface, which records their estimates of the positions of
 candidate lensed features. Simulated lenses, and expert-classified images which
@@
 training set is used to give the volunteers feedback on their performance, as
-well as to calibrate it in order to allow dynamical updates to the probability
-of any image they classify to contain a lens. Low probability systems are
+well as to calibrate a model of the system that provides
+dynamical updates to the probability of containing a lens
+of every image they classify. Low probability systems are
 retired from the site periodically, concentrating the sample towards a set of
@@
 \citep[e.g.][]{CabanacEtal2007,MoreEtal2012}. Detecting galaxy-scale lenses
-from the ground is hard, but feasible albeit with lower efficiency and requiring
+from the ground is difficult, but feasible albeit with lower efficiency and requiring
 HST or spectroscopic follow-up to confirm the candidates as lenses
@@
 
-How can we scale these lens searches up to imaging surveys covering a hundred
+How can we scale these lens searches up to imaging surveys that cover a hundred
 times the sky area, such as the almost-all sky surveys planned with LSST and
@@
 requiring the same  team of 10 inspectors to work full time for 20 weeks (to
-provide 3 classifications  per lens between them) Neither of these may be the
+provide 3 classifications  per lens between them). Neither of these may be the
 most cost-effective or reliable strategy. Alternatively, a team of $10^6$
@@
 via its flexible inspection interface and discussion forum
-\citep{LintottEtal2009}. Indeed, several of us (AV,CC,CM,EB,PM,TJ,LW) were
+\citep{LintottEtal2009}. Indeed, several of us (AV,CC,CM,EB,PM,LW) were
 active in an informal \GZ gravitational lens search (Verma et al, in
@@
 address the visual inspection problem in gravitational lens detection for future
-large surveys via crowd-sourcing. Implemented as a Zooniverse \citep{SimpsonEtal2014} citizen science
+large surveys by ``crowd-sourcing'' it to a community of citizen scientists.
+Implemented as a Zooniverse \citep{SimpsonEtal2014}
 project, it is designed to provide a {\it gravitational lens discovery service}
 to survey teams looking for lenses in wide field imaging data. In a companion
-paper (More et al, in preparation, herafter \PaperTwo) we will present the new
+paper \citep[][hereafter \PaperTwo](PaperII) we will present the new
 gravitational lenses discovered in our first lens search, and
@@
 \item How quickly can lenses be detected, and non-lenses be rejected?
-How many classifications, and so how many volunteers are needed per target?
+How many classifications, and so how many volunteers, are needed per target?
 
@@
 two-stage candidate selection strategy. We then briefly introduce, in
-\Sref{sec:data}, the particular dataset used in the first experimental tests
+\Sref{sec:data}, the particular dataset used in our first test
 of the \SW system, and how we prepared the images prior to displaying them in
@@
 \begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=4.png,width=\linewidth,angle=0,clip=}
+\centering\includegraphics[width=\linewidth]{4.pdf}
 \end{minipage} \hfill
 \begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=5.png,width=\linewidth,angle=0,clip=}
+\centering\includegraphics[width=\linewidth]{5.pdf}
 \end{minipage} \hfill
 \begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=6.png,width=\linewidth,angle=0,clip=}
+\centering\includegraphics[width=\linewidth]{6.pdf}
 \end{minipage} \hfill
 \begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=7.png,width=\linewidth,angle=0,clip=}
+\centering\includegraphics[width=\linewidth]{7.pdf}
 \end{minipage} \hfill
@@
 \begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=0_ASW0009dgn.png,width=\linewidth,angle=0,clip=}
+\centering\includegraphics[width=\linewidth]{0.pdf}
 \end{minipage} \hfill
 \begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=1_ASW0009dgo.png,width=\linewidth,angle=0,clip=}
+\centering\includegraphics[width=\linewidth]{1.pdf}
 \end{minipage} \hfill
 \begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=2_ASW0009dgy.png,width=\linewidth,angle=0,clip=}
+\centering\includegraphics[width=\linewidth]{2.pdf}
 \end{minipage} \hfill
 \begin{minipage}[b]{0.24\linewidth}
-\centering\epsfig{file=3_ASW0009dh0.png,width=\linewidth,angle=0,clip=}
+\centering\includegraphics[width=\linewidth]{3.pdf}
 \end{minipage} \hfill

### 2015-04-30 doc/sw-system.tex
Chehcking tense consistency in CI/training section

@@
 not) and 4) analyze that classification along with all others to produce a
-final candidate list. We describe step 1 in \Sref{sec:data} and step 4 in
-\Sref{sec:swap}. In this section we take a volunteer's eye view and begin by
+final candidate list. We describe step~1 in \Sref{sec:data}, and step~4 in
+\Sref{sec:swap}. In this section we take a volunteer's eye view, and begin by
 describing the \SW classification interface, the crowd of volunteers, and the
@@
 \centering\includegraphics[width=0.9\linewidth]{sw-screengrab-marker+feedback.pdf}
-\caption{Screenshot of the \SW classification interface.}
+\caption{Screenshot of the \SW classification interface at
+  \texttt{http://spacewarps.org}.}
 \label{fig:screenshot}
@@
 team.\footnote{The \SW web application code is open source and can be accessed
-from \texttt{https://github.com/zooniverse/Lens-Zoo}. The project was renamed during development.}
-The focus of the CI is a
-large display of a pre-prepared PNG image of the ``subject'' being inspected.
-When the image is clicked on by the volunteer, a marker symbol appears where the
-pointer was. Several markers can be placed, and they can be removed by the user if, for example, they change their mind.
+from \texttt{https://github.com/zooniverse/Lens-Zoo}.  The project was renamed
+during development to avoid the question of  who ``Len'' is.} The focus of the
+CI is a large display of a pre-prepared PNG image of the ``subject'' being
+inspected. When the image is clicked on by the volunteer, a marker symbol
+appears at that position.  Several markers can be placed, and they can be
+removed by the user if they change their mind.
 
@@
 After each classification, the positions of the markers are written out to the
-classification database, in an entry that also stores the ID of the subject, the
-username (or IP address if the user is not logged in) of the volunteer, a timestamp and some other metadata.
-
-For the more interesting subjects, the CI offers two features that  enable
-further investigation of the subjects. The first is the ``Quick Dashboard''
-(QD) a more advanced image viewer. This allows the viewer to compare three
+classification database, in an entry that also stores metadata including the ID
+of the subject, the username of the volunteer  (or IP address if thy are not
+logged in), and a timestamp.
+
+For the more interesting subjects, the CI offers two features that enable their
+further investigation. The first is the ``Quick Dashboard''
+(QD), a more advanced image viewer. This allows the viewer to compare three
 different contrast and colour balance settings, to help bring out subtle
@@
 in the main CI image viewer. The second is a link to that subject's page in
-the project discussion forum, \texttt{http://talk.spacewarps.org} (known as
-``Talk''). Here, volunteers can discuss the features they have seen either
+the project discussion forum (known as
+``\Talk\footnote{\texttt{http://talk.spacewarps.org}}'').
+Here, volunteers can discuss the features they have seen either
 before they submit their classification, or after, if they ``favourite'' the
@@
 about any given subject before submitting your own classification means that
-the classifications may not be strictly independent; the advantage of this
+the classifications may not be strictly independent; however, the advantage of this
 system is that volunteers can learn from others what constitutes a good lens
@@
 The FITS images of the subject can be further explored with Zooniverse
-``Dashboard Tools,'' using a more powerful image viewer that enables dynamic
+``Dashboard Tools,'' which include a
+more powerful image viewer that enables dynamic
 variation of the colour balance and contrast (stretch), and for any given view
@@
 
-Gravitational lenses are largely unfamiliar objects to the general public.
+Gravitational lenses are typically unfamiliar objects to the general public.
 New volunteers need to learn what lenses look like as quickly as possible, so
@@
 that they will receive instant feedback about their performance after
-classifying (blind) any of these training subjects. Indeed, after a volunteer
-finishes marking a training subject and hits ``Finished marking,'' a pop-up
+classifying (blindly) any of these training subjects. Indeed, after a volunteer
+finishes marking a training subject, a pop-up
 message is generated, containing either congratulations for a successful
@@
 
-We start by selecting massive galaxies and groups in the \cfhtls catalogs,
-by colour, brightness and photometric redshift. We then assign plausible mass
+We began by selecting massive galaxies and groups in the \cfhtls catalogs,
+by colour, brightness and photometric redshift. We then assigned plausible mass
 distributions to these ``potential lenses:'' a singular isothermal ellipsoid
 model for each massive galaxy, and an additional NFW profile dark matter halo
-for groups and clusters. The mass distributions are centred, elongated and
+for groups and clusters. The mass distributions were centred, elongated and
 aligned with the measured optical properties of the galaxies present. We then
-draw a source from a plausible background population, of either galaxies (for
+drew a source from a plausible background population, of either galaxies (for
 the group or galaxy lenses) or quasars (for the galaxy-scale lenses). The
-source redshift, luminosity and size distributions are all chosen to match
-those observed, while the source abundance is artificially increased such that
-each potential lens has a high probability of having a source occur at a
-position that will lead to it being  highly magnified. Source galaxies are
-given plausible surface brightness profiles and ellipticities. We then compute
+source redshift, luminosity and size distributions were all chosen to match
+those observed, while the source abundance was artificially increased such that
+each potential lens had a high probability of having a source occur at a
+position that will lead to it being highly magnified. Source galaxies were
+given plausible surface brightness profiles and ellipticities. We then computed
 the predicted multiple images of the source using the \gravlens ray-tracing
@@
 
-At this point, the distribution of lens and source properties are quite
-realistic. We then chose to make cuts of the simulated lens pool, in order to
-reject sims that were likely to be difficult to spot. While this ensured the
-educational value of the sims when feedback was given, it meant that we should
-only expect to detect real lens candidates that also pass these cuts.
-Indeed, for traditional machine learning or computer vision implementations then this would be a constraint, but human classifiers are capable of going beyond their training; Geach et al., for example (REF????) report the discovery of a red lens by volunteers who had only been trained on blue examples.
-This ability to go beyond training is a key advantage of human classifiers, and
-any real
-lens candidates we find with properties outside the ranges of the sims, may in
-this sense be considered bonuses, a product of the {\it imagination} of the
-crowd in extrapolating their understanding of gravitational lenses into a regime
-that they have not been trained for. In the \cfhtls project, the most important
-selection cuts were to only keep sims with a) second brightest image brighter
-that $i = 23$ and b) total combined image magnitude fainter than 19--20
-(\PaperTwo, Table~1). The combination of these two cuts results in a sample of
-visible lensed image configurations.
-
-When a volunteer begins classifying, they are initially shown training images at
-a mean frequency of two in five. Subjects are drawn at random from a pool
+At this point, we applied several cuts to the simulated lens pool, in order to
+reject sims that were likely to be difficult to spot. While this ensured that
+the educational value of the sims when feedback was given, it means that we
+should not necessarily expect to detect real lens candidates that would not pass
+these cuts (although human classifiers do possess the key advantage of  being
+able to go beyond their training\footnote{Any real lens candidates we find with
+properties outside the ranges of the training set will be of particular
+interest, being a product of the {\it imagination} of the crowd in extrapolating
+their understanding of gravitational lenses into a regime that they have not
+been trained for.  \citet{GeachEtal2015}, for example, report the discovery of a
+red lensed arc  by volunteers who had only been trained primarily on blue
+examples. We investigate this aspect of the \SW approach in \PaperTwo.}).
+In the present project, the most important selection cuts we made were to only
+keep sims with a) second brightest image brighter that $i = 23$ and b) total
+combined image magnitude fainter than 19--20 (\PaperTwo, Table~1). The
+combination of these two cuts resulted in a sample of visible lensed image
+configurations.
+
+Volunteers were initially shown training images at
+a mean frequency of two in five. Subjects were drawn at random from a pool
 consisting of (at first) 20\% sims, 20\% duds, and 60\% test images,
 and such that no volunteer ever
-sees a given image more than once. As the number of classifications made by the
-volunteer increases, the training frequency is decreased from 40\% to
+saw a given image more than once. As the number of classifications made by the
+volunteer increased, the training frequency was decreased from 40\% to
 $2/(5\times2^{(\textrm{int}(N_c/20)+1)/2})$ ($\approx 30\%$ for the second 20
@@
 
-This training regime means that in the first 60 images viewed, each volunteer
-is shown (on average) 9 simulated gravitational lenses, and 9 empty fields.
-This is a much higher rate than the natural one: to try and avoid this leading
-to over-optimism among the inspectors (and a resulting high false positive
-rate), we display the current ``Simulation Frequency'' on the classification
-interface (``1 in 5'' in \Fref{fig:screenshot}) and maintain the consistent
-theme in the feedback messages that lenses are rare.
+This training regime meant that in the first 60 images viewed, each volunteer
+was shown (on average) 9 simulated gravitational lenses (as well as 9
+pre-selected empty ``dud'' fields). This is a much higher rate than the natural
+one: to try and avoid this leading to over-optimism among the inspectors (and a
+resulting high false positive rate), we displayed the current ``Simulation
+Frequency'' on the classification interface (``1 in 5'' in
+\Fref{fig:screenshot}) and maintained the consistent theme in the feedback
+messages that lenses are rare.
 
 In Figures~\ref{fig:training-gallery:sims}~and~\ref{fig:training-gallery:duds}
-we show example training images from the first \SW project (\Sref{sec:data}
+we show example training images from this first \SW project (\Sref{sec:data}
 below).

### 2015-05-05 doc/sw-cfhtls.tex
corrections from co-authors v1

@@
 
-We report the discovery of 28 promising and a total of 58 new lens
+We report the discovery of {\bf 29} promising and a total of {\bf 59} new lens
 candidates from the CFHT Legacy Survey (\cfhtls) based on about 11
@@
 used to probe the dark matter distribution from galaxy
-\citep[e.g.][]{Koopmans2006,Barnabe2009,Sonnenfeld2015} to groups-cluster
+\citep[e.g.][]{Koopmans2006,Barnabe2009,Leier2011,Sonnenfeld2015} to groups-cluster
 scales
@@
 been developed so far
-\citep[e.g.][]{Lenzen2004,Alard2006,Seidel2007,More2012,Gavazzi2014} but they can not
+\citep[e.g.][]{Lenzen2004,Alard2006,Seidel2007,More2012,Brault2014,Gavazzi2014} but they can not
 simultaneously capture the myriad types of lenses that are known to
@@
 paper, Paper I (Marshall et al., in prep.), we describe the design of
-\sw and how the entire system functions as a discovery service.
-
-In this paper (Paper II hereafter), we describe our first lens search
-using data from the Canada-France-Hawaii Telescope Legacy Survey
+\sw and how the entire system functions as a discovery service.  In this
+paper (Paper II hereafter), we describe our first lens search using data
+from the Canada-France-Hawaii Telescope Legacy Survey
 (\cfhtls\footnote{\texttt{http://www.cfht.hawaii.edu/Science/CFHTLS/}}).
+{\bf In \citet{Kung2015}, we describe the design of a collaborative
+mass modelling tool that can be used by citizen scientists
+.}
+
 This paper is organised as follows. In
@@
 
+{\bf From the early release of the CFHTLS (T0002) covering 28~sq.~deg.,
+\citet{Cabanac2007} used an arc finding algorithm \citep{Alard2006} to
+find arcs in galaxies, groups and clusters. They found about 40 lens
+candidates with quality grades from low to high.}
+
 In the thesis dissertation of \citet{Thanjavur2009}, 9 promising and 2
@@
 the entire \cfhtls imaging without any pre-selection on the type of the lensing
-object. The algorithm measures the second order moments of the flux distribution
+object. This \af, {\bf an improved version of the algorithm by
+\citet{Alard2006}}, measures the second order moments of the flux distribution
 in pixels within small regions to estimate the direction and extent of local
@@
 From the main sample of ``\rf candidates,'' the SL2S team found, during
-their follow-up campaign, 33 confirmed lenses.
+their follow-up campaign, 33 confirmed lenses \citep{Sonnenfeld2013a,Sonnenfeld2013b}.
 
@@
 the images are shown randomly, a volunteer may not necessarily come
-across the neighbouring cutout unless the volunteer classifies a large
+across the neighbouring cutout unless {\bf they classify} a large
 number of images. This is not a problem since our user base is extremely
@@
 simulation purpose, we exclude all those galaxies whose positions match
-with the lensing galaxies from the SARCS samples within 2~arcsec.
+with the lensing galaxies from the SARCS samples {\bf within
+2~arcsec\footnote{{\bf Due to inaccuracies and uncertainties in measurements
+of the centers of some of the lens candidates, some simulated lensed
+images were superposed on the galaxies of known lens candidates. This issue was overcome by
+ingesting the same \cfhtls images with and without the simulated
+lenses.}}}.
 
@@
 ($z_l$) from the parent galaxy catalog. Next, we use the $L-\sigma$ scaling relation from the
-bright sample of \citep{Parker2005} to set the velocity dispersion of the halo
-hosting the galaxy which will be later used in the model
+bright sample of \citep{Parker2005} {\bf given by 
 \be
 \label{magstar2}
-\sigma_v=142 \left(\frac{L}{L_{*}}\right)^{1/3} \,.
+\sigma_v=142 \left(\frac{L}{L_{*}}\right)^{1/3} \, Km~s^{-1}.
 \ee
+This sets the velocity dispersion of the halo
+hosting the galaxy, which will be later used in the model.}
 We assume that the knee of the luminosity function of galaxies, $L_*$ evolves
@@
 
+{\bf We also add external shear at the center of the lensing galaxy
+drawn randomly from a set range (see \Tref{tab:thresh}. The shear is
+expected to affect the lens cross-section for a small number of cases
+when the shear strength is high in addition to high lens ellipticity or
+the PA of the shear is almost orthogonal to that of the lens
+ellipticity. However, the effect of shear on the lens cross-section is
+expected to be small for most of the cases and is ignored in the current
+implementation of SIMCT.}
+
 The luminosify functions of the background galaxies and quasars are
@@
 
-For quasars, we assume the luminosity function prescription of \citep{Oguri2010}
+For quasars, we assume the luminosity function prescription of \citet{Oguri2010}
 and adopt k-corrections by \citep{Richards2006}.
@@
 the bright end slope, we use $\alpha=-3.31$ when $z_s<3$ and $\alpha=-2.58$ at
-higher redshifts, as prescribed by \citep{Oguri2010}.
+higher redshifts, as prescribed by \citet{Oguri2010}.
 
@@
 We draw source redshifts and luminosities from the aforementioned
-distributions. The source positions with respect to the lens are drawn
+distributions. {\bf We note that the sources are being drawn from a much
+fainter magnitude range compared to the limiting magnitude of the
+\cfhtls imaging and thus, the Magnification bias is naturally taken into
+account.} The source positions with respect to the lens are drawn
 randomly from an area inside the caustic.  We perform ray-tracing for
@@
 profile\footnote{This was due to an oversight. We intend to use either
-an exponential or de Vaucouleurs' profile.} for
+an exponential or {\bf de Vaucouleurs'} profile.} for
 the galaxies. The ellipticity and the position angle (PA) are drawn
@@
 \be
-R_{\rm eff}= 10^{0.52} \frac{L_r^{2/3}}{{(1+z_s)}^2}
+R_{\rm eff}= 10^{0.52} \frac{L_r^{2/3}}{{(1+z_s)}^2} \, {\bf Kpc}
 \ee
-where $L_r=L_s/10^{10.2}$. On the other hand, quasars are assumed to be
+where $L_r=L_s/10^{10.2} {\bf L_\odot}$. On the other hand, quasars are assumed to be
 point sources and the PSF, with which quasars are convolved, is assumed
@@
 Source Flux      & 21.0 & 25.5 & 21.0 & 25.5 \\
-Source ellipticity & 0.1 & 0.6 & - & - \\
-Source PA & 0 & 180 & - & - \\
-Lens Redshift  & - & 0.9  & -  & 0.9 \\
-Lens shear strength &  0.001 (-) & 0.02 (-) &  0.001 & 0.02 \\
-Lens shear PA &  0 (-) & 180 (-) & 0 & 180  \\
-Einstein radius (arcsec) & 1.2 (2) & 5 (-) & 1.2 & 5 \\
+Source ellipticity & 0.1 & 0.6 & $-$ & $-$ \\
+Source PA & 0 & 180 & $-$ & $-$ \\
+Lens Redshift  & $-$ & 0.9  & $-$  & 0.9 \\
+Lens shear strength &  0.001 ($-$) & 0.02 ($-$) &  0.001 & 0.02 \\
+Lens shear PA &  0 ($-$) & 180 ($-$) & 0 & 180  \\
+Einstein radius (arcsec) & 1.2 (2) & 5 ($-$) & 1.2 & 5 \\
 \hline
@@
 called the \sw lens sample). We find a total of 141 candidates with
-G$\ge1.3$ (medium-high probability sample) out of which 58 are new
+G$\ge1.3$ (medium-high probability sample) out of which {\bf 59} are new
 systems. This sample is further divided as follows. We have a total of
@@
 probability sample (G$\ge$2), there are a total of 91 candidates out of
-which 28 are new. In this category, the minimum grade by all of the
+which {\bf 29} are new. In this category, the minimum grade by all of the
 inspectors was 2 suggesting that the candidates are probably or almost
@@
 
-We find a total of 288 (and 249 new) candidates with averaged grade
+We find a total of 288 (and {\bf 245} new) candidates with averaged grade
 $0<$G$<1.3$ (low probability sample) which means - in the worst case, at
@@
 P$_{\rm thresh}$ & 0.95 & 0.95 & 0.3 & 0.3 \\
+{\bf Expert Grade (G)} & $-$ & $-$ & 1.3 & 1.3 \\
 \hline
@@
 \hline
-Number  & 58 & 141 &  & \\
+Number  & {\bf 59} & 141 &  & \\
 Percentage & & & & \\
@@
 P$_{\rm thresh}$ & 0.3 & 0.3 &  & \\
+{\bf Expert Grade (G)} & 1.3 & 1.3 & 1.3 & 1.3 \\
 
@@
 {AC}-- All (known and new) lens candidates  \\
-P$_{\rm thresh}$ -- systems with P above this threshold are selected \\
+P$_{\rm thresh}$ -- systems with Posterior probability P above this threshold are selected \\
 Note: For KC and KL, Percentages are with respect to the known
@@
 
-We give basic information about the final sample of 58 new lens
+We give basic information about the final sample of {\bf 59} new lens
 candidates (medium-high probability) found by \sw in
@@
 
-Indeed, we have found several new lens candidates that were not known
+Indeed, we have found {\bf 59} new lens candidates that were not known
 before. In \Fref{fig:isd}, we show the image separation distribution for
@@
 of the new sample such as spectroscopic confirmation and mass modelling
-analysis will be presented in a subsequent \sw paper (Verma et al., in
+analyses will be presented in a subsequent \sw paper (Verma et al., in
 prep.).
@@
 
-\item We present a sample of 58 {\bf new} gravitational lens candidates
-out of which 28 are more promising systems. These candidates received
+\item We present a sample of {\bf 59 new} gravitational lens candidates
+out of which {\bf 29} are more promising systems. These candidates received
 averaged grades, G$\ge$1.3 from three experts where 1-possibly, a lens,
@@
 \multicolumn{11}{p{18cm}}{
-The column Comments has two type of notes. The first is about the lens
-image configuration where the symbols mean the following A: Arc, D: Double, Q:
-Quad, R: Ring. The second is a comment on the type of lens assessed
-visually. Note that this classification is not based on colors or spectral
-analysis. The symbols are E: Elliptical, S: (face on) Spiral, G: Group-scale, D:
-Edge on disk, R: Red starforming galaxy.  This galaxy falls within the masked region as per the catalog from
-which the magnitudes and the redshift are extracted.
+The redshift with $^s$ are spectroscopic estimates taken from SDDS Data
+Release 12 whenever available unambiguously. The column Comments has two
+type of notes. The first is about the lens image configuration where the
+symbols mean the following A: Arc, D: Double, Q: Quad, R: Ring. The
+second is a comment on the type of lens assessed visually. Note that
+this classification is not based on colors or spectral analysis. The
+symbols are E: Elliptical, S: (face on) Spiral, G: Group-scale, D: Edge
+on disk, R: Red starforming galaxy.  This galaxy falls within the masked
+region as per the catalog from which the magnitudes and the redshift are
+extracted.
 }\\
 \endlastfoot
-SW18 & CFHTLS J020642-095157 &   31.6750 &   -9.8658 &  0.2 & 20.8 &  0.9 &  2.0 & ASW0001ld7 &  0.8  &  A,R   \\
-SW42 & CFHTLS J020810-040220 &   32.0450 &   -4.0389 &  1.0 & 20.8 &  1.8 &  1.3 & ASW0001c3j &  0.7  &  A,R   \\
- SW8 & CFHTLS J020832-043315 &   32.1340 &   -4.5543 &  1.0 & 21.0 &  1.6 &  2.3 & ASW0002asp &  1.0  &  A,R   \\
- SW9 & CFHTLS J020848-042427 &   32.2011 &   -4.4075 &  0.8 & 20.5 &  1.1 &  2.3 & ASW0002bmc &  0.9  &  D,D   \\
-SW10 & CFHTLS J020849-050429 &   32.2078 &   -5.0749 &  0.8 & 20.6 &  0.9 &  2.3 & ASW0002qtn &  1.0  &  A,R   \\
-SW43 & CFHTLS J021021-093415 &   32.5898 &   -9.5711 &  0.4 & 18.4 &  2.7 &  1.3 & ASW0002k40 &  0.4  &  D,S   \\
-SW29 & CFHTLS J021057-084450 &   32.7414 &   -8.7474 &  0.0 &  0.0 &  2.5 &  1.7 & ASW0002p8y &  0.4  &  A,G   \\
-SW19 & CFHTLS J021221-105251 &   33.0881 &  -10.8811 &  0.3 & 17.9 &  1.8 &  2.0 & ASW0002dx7 &  0.8  &  D,E/S   \\
-SW44 & CFHTLS J021225-085211 &   33.1051 &   -8.8697 &  0.8 & 19.5 &  2.1 &  1.3 & ASW00024id &  1.0  &  R,R   \\
-SW45 & CFHTLS J021317-084819 &   33.3234 &   -8.8055 &  0.5 & 19.8 &  1.3 &  1.3 & ASW00024q6 &  0.4  &  A,R/E   \\
-SW30 & CFHTLS J021514-092440 &   33.8109 &   -9.4111 &  0.7 & 19.9 &  2.6 &  1.7 & ASW00021r0 &  0.4  &  A,R/G   \\
-SW31 & CFHTLS J022359-083651 &   35.9995 &   -8.6143 &  0.0 &  0.0 &  3.1 &  1.7 & ASW0004iye &  0.4  &  A,E   \\
-SW11 & CFHTLS J022406-062846 &   36.0256 &   -6.4796 &  0.4 & 19.6 &  0.9 &  2.3 & ASW0003wsu &  0.7  &  A,E   \\
- SW1 & CFHTLS J022409-105807 &   36.0398 &  -10.9688 &  0.0 &  0.0 &  4.8 &  3.0 & ASW0004dv8 &  1.0  &  A,G   \\
-SW20 & CFHTLS J022533-053204 &   36.3888 &   -5.5346 &  0.5 & 19.4 &  3.6 &  2.0 & ASW0004m3x &  0.4  &  A,R/G   \\
-SW21 & CFHTLS J022716-105602 &   36.8186 &  -10.9341 &  0.4 & 17.2 &  1.8 &  2.0 & ASW0009ab8 &  0.7  &  A,E/G   \\
-SW32 & CFHTLS J022745-062518 &   36.9387 &   -6.4218 &  0.6 & 20.5 &  1.2 &  1.7 & ASW0003s0m &  0.5  &  A,R   \\
-SW12 & CFHTLS J022805-051733 &   37.0236 &   -5.2927 &  0.4 & 18.8 &  1.4 &  2.3 & ASW0009ans &  1.0  &  Q,E   \\
-SW46 & CFHTLS J022843-063316 &   37.1794 &   -6.5547 &  0.5 & 19.1 &  1.8 &  1.3 & ASW0003r6c &  0.3  &  D/A,E   \\
-SW22 & CFHTLS J023008-054038 &   37.5359 &   -5.6774 &  0.6 & 19.7 &  1.9 &  2.0 & ASW0003r61 &  0.5  &  A,E   \\
-SW13 & CFHTLS J023123-082535 &   37.8468 &   -8.4266 &  0.0 &  0.0 &  1.2 &  2.3 & ASW0004xjk &  0.3  &  A,R   \\
-SW23 & CFHTLS J023315-042243 &   38.3133 &   -4.3789 &  0.7 & 19.7 &  1.0 &  2.0 & ASW00050sk &  0.8  &  A,R   \\
-SW33 & CFHTLS J023453-093032 &   38.7232 &   -9.5089 &  0.5 & 19.8 &  0.7 &  1.7 & ASW00051ld &  0.3  &  A,D   \\
-SW34 & CFHTLS J084833-044051 &  132.1385 &   -4.6809 &  0.8 & 20.2 &  0.9 &  1.7 & ASW0004wgd &  0.7  &  A,R   \\
-SW14 & CFHTLS J084841-045237 &  132.1708 &   -4.8772 &  0.3 & 19.0 &  1.0 &  2.3 & ASW0004nan &  1.0  &  A,E   \\
-SW47 & CFHTLS J090219-053923 &  135.5794 &   -5.6566 &  0.0 &  0.0 &  2.0 &  1.3 & ASW0000g95 &  1.0  &  A,R/E   \\
-SW35 & CFHTLS J090248-010232 &  135.7020 &   -1.0424 &  0.4 & 19.1 &  1.4 &  1.7 & ASW000096t &  0.6  &  D,E   \\
-SW24 & CFHTLS J090308-043252 &  135.7844 &   -4.5479 &  0.0 &  0.0 &  1.2 &  2.0 & ASW00007mq &  0.6  &  A,E   \\
-SW48 & CFHTLS J090319-040146 &  135.8311 &   -4.0297 &  0.0 & 19.8 &  1.2 &  1.3 & ASW00007ls &  0.5  &  A,R/E/nbr   \\
-SW49 & CFHTLS J090333-005829 &  135.8886 &   -0.9749 &  0.0 &  0.0 &  2.1 &  1.3 & ASW00008a0 &  1.0  &  A/D,E/G   \\
-SW50 & CFHTLS J135724+561614 &  209.3536 &   56.2707 &  0.0 &  0.0 &  2.6 &  1.3 & ASW0006e0o &  0.9  &  D,E/unlikely   \\
-SW25 & CFHTLS J135755+571722 &  209.4827 &   57.2897 &  0.8 & 20.2 &  1.3 &  2.0 & ASW0005ma2 &  0.8  &  D,D   \\
-SW51 & CFHTLS J140027+541028 &  210.1164 &   54.1746 &  0.0 &  0.0 &  1.2 &  1.3 & ASW0006a07 &  0.6  &  Q,R/E   \\
-SW15 & CFHTLS J140030+574437 &  210.1260 &   57.7437 &  0.4 & 18.2 &  2.0 &  2.3 & ASW0009bp2 &  0.6  &  A,E   \\
- SW2 & CFHTLS J140522+574333 &  211.3426 &   57.7259 &  0.7 & 19.7 &  1.0 &  2.7 & ASW000619d &  0.7  &  A,R   \\
-SW16 & CFHTLS J140622+520942 &  211.5958 &   52.1617 &  0.7 & 20.3 &  1.2 &  2.3 & ASW0005rnb &  0.7  &  A,R   \\
-SW26 & CFHTLS J141432+534004 &  213.6372 &   53.6679 &  0.7 & 21.4 &  0.9 &  2.0 & ASW0006jh5 &  0.8  &  A,R   \\
-SW52 & CFHTLS J141518+513915 &  213.8290 &   51.6542 &  0.4 & 18.3 &  3.0 &  1.3 & ASW00070vl &  0.8  &  D,E   \\
- SW3 & CFHTLS J142603+511420 &  216.5149 &   51.2390 &  0.0 &  0.0 &  4.4 &  2.7 & ASW0006mea &  0.7  &  A,G   \\
-SW53 & CFHTLS J142620+561356 &  216.5870 &   56.2323 &  0.5 & 19.5 &  1.3 &  1.3 & ASW0007sez &  0.8  &  A/R,S   \\
-SW54 & CFHTLS J142652+560002 &  216.7201 &   56.0006 &  0.0 &  0.0 &  1.5 &  1.3 & ASW0007t5y &  1.0  &  R,R   \\
-SW55 & CFHTLS J142843+543713 &  217.1815 &   54.6204 &  0.4 & 19.7 &  1.3 &  1.3 & ASW0007pga &  0.6  &  D,D   \\
- SW4 & CFHTLS J142934+562541 &  217.3926 &   56.4281 &  0.5 & 19.0 &  5.9 &  2.7 & ASW0009cjs &  0.8  &  A,G   \\
-SW27 & CFHTLS J143055+572431 &  217.7333 &   57.4088 &  0.7 & 19.3 &  1.0 &  2.0 & ASW0007wfj &  0.9  &  A,R   \\
-SW36 & CFHTLS J143100+564603 &  217.7511 &   56.7675 &  0.0 &  0.0 &  1.8 &  1.7 & ASW00086xq &  0.8  &  A,E   \\
-SW37 & CFHTLS J143353+542310 &  218.4736 &   54.3862 &  0.8 & 19.8 &  1.6 &  1.7 & ASW0009cox &  0.6  &  A,R/G   \\
- SW5 & CFHTLS J143454+522850 &  218.7270 &   52.4808 &  0.6 & 19.4 &  4.4 &  2.7 & ASW0007k4r &  0.4  &  Q,G/R   \\
- SW6 & CFHTLS J143627+563832 &  219.1164 &   56.6425 &  0.5 & 19.4 &  1.5 &  2.7 & ASW0008swn &  0.9  &  A,D   \\
-SW56 & CFHTLS J143631+571131 &  219.1315 &   57.1922 &  0.7 & 20.9 &  1.3 &  1.3 & ASW0008pag &  0.6  &  D/A,R   \\
-SW57 & CFHTLS J143651+530705 &  219.2150 &   53.1183 &  0.6 & 19.2 &  3.1 &  1.3 & ASW0007h27 &  1.0  &  A,E/G   \\
-SW17 & CFHTLS J143658+533807 &  219.2425 &   53.6355 &  0.7 & 19.6 &  0.9 &  2.3 & ASW0007hu2 &  0.6  &  D,D   \\
-SW28 & CFHTLS J143838+572647 &  219.6589 &   57.4464 &  0.8 & 20.2 &  1.1 &  2.0 & ASW0008qsm &  0.9  &  A,R   \\
-SW58 & CFHTLS J143950+544606 &  219.9609 &   54.7686 &  0.0 &  0.0 &  1.7 &  1.3 & ASW00085cp &  0.4  &  A,G/R   \\
-SW38 & CFHTLS J220215+012124 &  330.5635 &    1.3567 &  0.3 & 17.4 &  4.6 &  1.7 & ASW0005qiz &  0.5  &  rA,G   \\
- SW7 & CFHTLS J220256+023432 &  330.7369 &    2.5758 &  0.0 &  0.0 &  6.8 &  2.7 & ASW0007e08 &  0.8  &  A,G/Clus   \\
-SW39 & CFHTLS J221306+014708 &  333.2758 &    1.7856 &  0.0 & 17.1 &  1.4 &  1.7 & ASW0008wmr &  0.9  &  A,S   \\
-SW40 & CFHTLS J221519+005758 &  333.8321 &    0.9661 &  0.4 & 20.2 &  1.0 &  1.7 & ASW0008xbu &  0.8  &  A,D   \\
-SW41 & CFHTLS J221716+015826 &  334.3189 &    1.9739 &  0.1 & 21.6 &  1.0 &  1.7 & ASW00096rm &  1.0  &  A/R,R/unlikely   \\
+SW19 & CFHTLS J020642.0-095157 &  31.67504 &  -9.86584 &  0.2 & 21.4 &  0.9 &  2.0 & ASW0001ld7 &  0.8 &  A,R   \\ 
+SW8 & CFHTLS J020648.0-065639 &  31.70031 &  -6.94430 &  0.8 & 21.0 &  1.3 &  2.3 & ASW00099ed &  0.4 &  A,E   \\ 
+SW43 & CFHTLS J020810.7-040220 &  32.04497 &  -4.03891 &  1.0 & 21.6 &  1.8 &  1.3 & ASW0001c3j &  0.7 &  A,R   \\ 
+SW9 & CFHTLS J020832.1-043315 &  32.13396 &  -4.55429 &  1.0 & 21.9 &  1.6 &  2.3 & ASW0002asp &  1.0 &  A,R   \\ 
+SW10 & CFHTLS J020848.2-042427 &  32.20110 &  -4.40751 &  0.8 & 21.6 &  1.1 &  2.3 & ASW0002bmc &  0.9 &  D,D   \\ 
+SW11 & CFHTLS J020849.8-050429 &  32.20784 &  -5.07494 &  0.8 & 21.3 &  0.9 &  2.3 & ASW0002qtn &  1.0 &  A,R   \\ 
+SW44 & CFHTLS J021021.5-093415 &  32.58981 &  -9.57109 &  0.4 & 19.0 &  2.7 &  1.3 & ASW0002k40 &  0.4 &  D,S   \\ 
+SW30 & CFHTLS J021057.9-084450 &  32.74148 &  -8.74745 &  0.45$^s$ &  0.0 &  2.5 &  1.7 & ASW0002p8y &  0.4 &  A,G   \\ 
+SW20 & CFHTLS J021221.1-105251 &  33.08810 & -10.88106 &  0.3 & 18.2 &  1.8 &  2.0 & ASW0002dx7 &  0.8 &  D,E/S   \\ 
+SW45 & CFHTLS J021225.2-085211 &  33.10511 &  -8.86973 &  0.76$^s$ & 20.5 &  2.1 &  1.3 & ASW00024id &  1.0 &  R,R   \\ 
+SW46 & CFHTLS J021317.6-084819 &  33.32341 &  -8.80549 &  0.5 & 20.6 &  1.3 &  1.3 & ASW00024q6 &  0.4 &  A,R/E   \\ 
+SW31 & CFHTLS J021514.6-092440 &  33.81089 &  -9.41115 &  0.72$^s$ & 21.1 &  2.6 &  1.7 & ASW00021r0 &  0.4 &  A,R/G   \\ 
+SW32 & CFHTLS J022359.8-083651 &  35.99955 &  -8.61439 &  0.0 &  0.0 &  3.1 &  1.7 & ASW0004iye &  0.4 &  A,E   \\ 
+SW12 & CFHTLS J022406.1-062846 &  36.02558 &  -6.47963 &  0.4 & 20.1 &  0.9 &  2.3 & ASW0003wsu &  0.7 &  A,E   \\ 
+SW1 & CFHTLS J022409.5-105807 &  36.03978 & -10.96885 &  0.0 &  0.0 &  4.8 &  3.0 & ASW0004dv8 &  1.0 &  A,G   \\ 
+SW21 & CFHTLS J022533.3-053204 &  36.38882 &  -5.53460 &  0.57$^s$ & 20.4 &  3.6 &  2.0 & ASW0004m3x &  0.4 &  A,R/G   \\ 
+SW22 & CFHTLS J022716.4-105602 &  36.81856 & -10.93410 &  0.4 & 17.8 &  1.8 &  2.0 & ASW0009ab8 &  0.7 &  A,E/G   \\ 
+SW33 & CFHTLS J022745.2-062518 &  36.93868 &  -6.42183 &  0.6 & 21.3 &  1.2 &  1.7 & ASW0003s0m &  0.5 &  A,R   \\ 
+SW13 & CFHTLS J022805.6-051733 &  37.02362 &  -5.29266 &  0.4 & 19.2 &  1.4 &  2.3 & ASW00047ae &  1.0 &  Q,E   \\ 
+SW47 & CFHTLS J022843.0-063316 &  37.17942 &  -6.55465 &  0.5 & 19.9 &  1.8 &  1.3 & ASW0003r6c &  0.3 &  D/A,E   \\ 
+SW23 & CFHTLS J023008.6-054038 &  37.53591 &  -5.67744 &  0.50$^s$ & 20.4 &  1.9 &  2.0 & ASW0003r61 &  0.5 &  A,E   \\ 
+SW14 & CFHTLS J023123.2-082535 &  37.84682 &  -8.42663 &  0.0 & 0.0 &  1.2 &  2.3 & ASW0004xjk &  0.3 &  A,R   \\ 
+SW24 & CFHTLS J023315.2-042243 &  38.31334 &  -4.37886 &  0.7 & 20.4 &  1.0 &  2.0 & ASW00050sk &  0.8 &  A,R   \\ 
+SW34 & CFHTLS J023453.5-093032 &  38.72321 &  -9.50892 &  0.5 & 20.3 &  0.7 &  1.7 & ASW00051ld &  0.3 &  A,D   \\ 
+SW35 & CFHTLS J084833.2-044051 & 132.13847 &  -4.68085 &  0.8 & 21.1 &  0.9 &  1.7 & ASW0004wgd &  0.7 &  A,R   \\ 
+SW15 & CFHTLS J084841.0-045237 & 132.17084 &  -4.87720 &  0.3 & 19.5 &  1.0 &  2.3 & ASW0004nan &  1.0 &  A,E   \\ 
+SW48 & CFHTLS J090219.0-053923 & 135.57947 &  -5.65666 &  0.0 &  0.0 &  2.0 &  1.3 & ASW0000g95 &  1.0 &  A,R/E   \\ 
+SW36 & CFHTLS J090248.4-010232 & 135.70204 &  -1.04243 &  0.4 & 19.7 &  1.4 &  1.7 & ASW000096t &  0.6 &  D,E   \\ 
+SW25 & CFHTLS J090308.2-043252 & 135.78449 &  -4.54789 &  0.0 &  0.0 &  1.3 &  2.0 & ASW00007mq &  0.6 &  D,D   \\ 
+SW49 & CFHTLS J090319.4-040146 & 135.83105 &  -4.02971 &  0.0 & 20.6 &  1.2 &  1.3 & ASW00007ls &  0.5 &  A,R/E   \\ 
+SW50 & CFHTLS J090333.2-005829 & 135.88869 &  -0.97490 &  0.0 &  0.0 &  2.1 &  1.3 & ASW00008a0 &  1.0 &  A/D,E/G   \\ 
+SW51 & CFHTLS J135724.8+561614 & 209.35374 &  56.27066 &  0.36$^s$ &  0.0 &  2.6 &  1.3 & ASW0006e0o &  0.9 &  D,E   \\ 
+SW26 & CFHTLS J135755.8+571722 & 209.48268 &  57.28971 &  0.8 & 21.4 &  0.9 &  2.0 & ASW0005ma2 &  0.8 &  A,R   \\ 
+SW52 & CFHTLS J140027.9+541028 & 210.11636 &  54.17455 &  0.6 &  0.0 &  1.2 &  1.3 & ASW0006a07 &  0.6 &  Q,R/E   \\ 
+SW16 & CFHTLS J140030.2+574437 & 210.12601 &  57.74371 &  0.38$^s$ & 18.8 &  2.0 &  2.3 & ASW0009bp2 &  0.6 &  A,E   \\ 
+SW2 & CFHTLS J140522.2+574333 & 211.34261 &  57.72587 &  0.52$^s$ & 20.3 &  1.0 &  2.7 & ASW000619d &  0.7 &  A,R   \\ 
+SW17 & CFHTLS J140622.9+520942 & 211.59581 &  52.16169 &  0.7 & 21.3 &  1.2 &  2.3 & ASW0005rnb &  0.7 &  A,R   \\ 
+SW27 & CFHTLS J141432.9+534004 & 213.63716 &  53.66788 &  0.7 & 22.1 &  1.0 &  2.0 & ASW0006jh5 &  0.8 &  A,R   \\ 
+SW53 & CFHTLS J141518.9+513915 & 213.82903 &  51.65420 &  0.29$^s$ & 18.9 &  3.0 &  1.3 & ASW00070vl &  0.8 &  D,E   \\ 
+SW3 & CFHTLS J142603.2+511421 & 216.51375 &  51.23935 &  0.0 &  0.0 &  4.4 &  2.7 & ASW0006mea &  0.7 &  A,G   \\ 
+SW54 & CFHTLS J142620.8+561356 & 216.58699 &  56.23230 &  0.5 & 19.9 &  1.3 &  1.3 & ASW0007sez &  0.8 &  A/R,S   \\ 
+SW55 & CFHTLS J142652.8+560001 & 216.72004 &  56.00044 &  0.0 &  0.0 &  1.5 &  1.3 & ASW0007t5y &  1.0 &  R,R   \\ 
+SW56 & CFHTLS J142843.5+543713 & 217.18153 &  54.62036 &  0.4 & 20.3 &  1.3 &  1.3 & ASW0007pga &  0.6 &  D,D   \\ 
+SW4 & CFHTLS J142934.2+562541 & 217.39261 &  56.42807 &  0.51$^s$ & 19.9 &  5.9 &  2.7 & ASW0009cjs &  0.8 &  A,G   \\ 
+SW28 & CFHTLS J143055.9+572431 & 217.73332 &  57.40883 &  0.60$^s$ & 20.1 &  1.6 &  2.0 & ASW0007xrs &  0.9 &  A,R/G   \\ 
+SW37 & CFHTLS J143100.2+564603 & 217.75124 &  56.76750 &  0.0 &  0.0 &  1.2 &  1.7 & ASW00086xq &  0.8 &  A,E   \\ 
+SW38 & CFHTLS J143353.6+542310 & 218.47357 &  54.38624 &  0.65$^s$ & 20.7 &  1.8 &  1.7 & ASW0009cp0 &  0.7 &  A,E   \\ 
+SW5 & CFHTLS J143454.4+522850 & 218.72702 &  52.48080 &  0.62$^s$ & 20.5 &  4.4 &  2.7 & ASW0007k4r &  0.4 &  Q,G/R   \\ 
+SW6 & CFHTLS J143627.9+563832 & 219.11636 &  56.64249 &  0.53$^s$ & 20.2 &  1.5 &  2.7 & ASW0008swn &  0.9 &  A,D   \\ 
+SW57 & CFHTLS J143631.5+571131 & 219.13155 &  57.19215 &  0.7 & 22.0 &  1.3 &  1.3 & ASW0008pag &  0.6 &  D/A,R   \\ 
+SW58 & CFHTLS J143651.6+530705 & 219.21503 &  53.11832 &  0.58$^s$ & 20.2 &  3.1 &  1.3 & ASW0007iwp &  0.7 &  A,E/G   \\ 
+SW18 & CFHTLS J143658.1+533807 & 219.24246 &  53.63550 &  0.61$^s$ & 20.3 &  0.9 &  2.3 & ASW0007hu2 &  0.6 &  D,D   \\ 
+SW29 & CFHTLS J143838.1+572647 & 219.65887 &  57.44645 &  0.8 & 21.3 &  1.1 &  2.0 & ASW0008qsm &  0.9 &  A,R   \\ 
+SW59 & CFHTLS J143950.6+544606 & 219.96101 &  54.76858 &  0.73$^s$ &  0.0 &  1.7 &  1.3 & ASW00085cp &  0.4 &  A,G/R   \\ 
+SW39 & CFHTLS J220215.2+012124 & 330.56348 &   1.35667 &  0.31$^s$ & 18.0 &  4.6 &  1.7 & ASW0005qiz &  0.5 &  rA,G   \\ 
+SW7 & CFHTLS J220256.8+023432 & 330.73691 &   2.57581 &  0.48$^s$ &  0.0 &  6.8 &  2.7 & ASW0007e08 &  0.8 &  A,G   \\ 
+SW40 & CFHTLS J221306.1+014708 & 333.27579 &   1.78561 &  0.0 & 17.8 &  1.4 &  1.7 & ASW0008wmr &  0.9 &  A,S   \\ 
+SW41 & CFHTLS J221519.7+005758 & 333.83212 &   0.96615 &  0.4 & 20.8 &  1.0 &  1.7 & ASW0008xbu &  0.8 &  A,D   \\ 
+SW42 & CFHTLS J221716.5+015826 & 334.31894 &   1.97394 &  0.1 & 22.0 &  1.0 &  1.7 & ASW00096rm &  1.0 &  A/R,R   \\ 
 \end{longtable}
@@
 \bibliographystyle{apj}
-\bibliography{references}
+\bibliography{references_cfhtls}
 

### 2015-05-05 doc/sw-cfhtls.tex
corrections from co-authors v1

@@
 discovery of over 500 lenses till
-date\footnote{http://admin.masterlens.org/index.php}.
+date\footnote{\texttt{http://admin.masterlens.org/index.php}}.
 
@@
 have been launched under the citizen science web portal Zooniverse
-(http://zooniverse.org). The task of finding gravitational lenses is
+(\texttt{http://zooniverse.org}). The task of finding gravitational lenses is
 significantly challenging given that the lens systems show such
@@
 has a 1~deg$^2$ field-of-view and a pixel size of 0.186\arcsec
-\citep{Gwyn2012}. The \cfhtls \textsc{WIDE} covers a total
+\citep{Gwyn2012}. The \cfhtls WIDE covers a total
 non-overlapping area of 160~deg$^2$ on the sky and consists of four
@@
 22.6~deg$^2$ and 23.3~deg$^2$, respectively\footnote{These numbers are
-estimated from http://terapix.iap.fr/cplt/T0007/doc/T0007-doc.pdf}.  The
-field W3 has a sky coverage of 44.2~deg$^2$ and is more than twice as
-large as W2 and W4.
+estimated from
+\texttt{http://terapix.iap.fr/cplt/T0007/doc/T0007-doc.pdf}}.  The field
+W3 has a sky coverage of 44.2~deg$^2$ and is more than twice as large as
+W2 and W4.
 
@@
 from the final T0007 release taken from the Terapix
-website\footnote{{http://terapix.iap.fr/cplt/T0007/doc/T0007-doc.pdf}} for this
+website\footnote{\texttt{http://terapix.iap.fr/cplt/T0007/doc/T0007-doc.pdf}} for this
 work.
@@
 low probability candidates are reported which were discovered
-serendipitiously. These detections were made during the visual
+serendipitously. These detections were made during the visual
 inspection of the \cfhtls images as part of data reduction procedures
@@
 of these candidates are medium-low
-probability\footnote{http://www.ita.uni-heidelberg.de/$\sim$maturi/Public/arcs}.
+probability\footnote{\texttt{http://www.ita.uni-heidelberg.de/$\sim$maturi/Public/arcs}}.
 
@@
 containing the systems from the \rf and the \af samples were labelled as
-``Known Lens Candidates'' in the \sw discussion forum,
-TALK\footnote{http://talk.spacewarps.org/}, where volunteers have the
+``known lens candidates'' in the \sw discussion forum,
+TALK\footnote{\texttt{http://talk.spacewarps.org/}}, where volunteers have the
 opportunity to discuss their findings with fellow volunteers and the
@@
 
-\subsection{Image Presentation in \sw}
+\subsection{Image presentation in \sw}
 \label{sec:data:impres}
 In order to perform a blind lens search over the entire \cfhtls
-\textsc{wide}, we present the volunteers with cutouts of images selected
+WIDE, we present the volunteers with cutouts of images selected
 from the survey region. We briefly describe the image presentation here
@@
 cutouts. This  results in a catalog of $\sim$ 430 000 cutouts for the entire \cfhtls
-\textsc{wide} region. The size of the individual cutout is determined by
+WIDE region. The size of the individual cutout is determined by
 optimising factors such as the typical angular scales of gravitational
@@
 analyzing the classifications performed by the citizen scientists (more
-details can be found in Paper I but see \Sref{sec:swap} for a brief
+details can be found in Paper I, but see \Sref{sec:swap} for a brief
 summary). In this section, we describe the framework used for generating the
@@
 For the purpose of generating simulated lens systems, we divide them
-in to two main categories a) galaxy scale lenses b) and group or
+into two main categories a) galaxy scale lenses b) and group or
 cluster-scale lenses. We further subdivide galaxy scale lenses based on the
 type of the background sources, namely galaxies and quasars. We do not simulate
-group scale - quasar lenses as they are expected to be even more rare. We now
+group-scale  quasar lenses as they are expected to be even more rare. We now
 describe our procedure to generate these different types of lens systems.
@@
 randomly from within the range given in Table~\ref{tab:thresh}. The
-effective radius of the galaxy is estimated from the Luminosity$-$size
+effective radius of the galaxy is estimated from the luminosity$-$size
 relation \citep{Bernardi2003} (with a redshift scaling, to account for
@@
 explanatory document \footnote{
-http://terapix.iap.fr/cplt/T0007/doc/T0007-doc.pdf}.
+\texttt{http://terapix.iap.fr/cplt/T0007/doc/T0007-doc.pdf}}.
 
@@
 
-\subsection{Simulated Lens Sample and Catalog Description}
+\subsection{Simulated lens sample and catalog description}
 
@@
 been provided. These catalogs are available from
-https://github.com/anupreeta27/SIMCT and simulated lens sample can be
+\texttt{https://github.com/anupreeta27/SIMCT} and simulated lens sample can be
 requested from the authors.
@@
 simulated sample is small (roughly 5 percent)\footnote{This estimate is
-based on the \#simfail from TALK, the discussion forum.}.
+based on the number of \#simfail tags from TALK, the discussion forum.}.
 
@@
 higher redshifts or which are fainter have poor photometric redshift
-measurements. Consequently these galaxies are assigned a wrong
+measurements. Consequently these galaxies are assigned  wrong
 luminosity and velocity dispersion estimates. This then results in
@@
 data products will be made available at
-http://spacewarps.org/\#/projects/CFHTLS/. Such a sample has tremendous
+\texttt{http://spacewarps.org/\#/projects/CFHTLS/}. Such a sample has tremendous
 utility for training and testing of various lens finding algorithms
@@
 \caption{ \label{fig:stackP}
-Distribution of different types of candidates as a function of the posterior
-probability P. The types of the candidates are the FPs, the new candidates and
-the known candidates. The new and known candidates have higher detection rate
-for higher values of P, as expected.}
+Distribution of different types of candidates as a function of the
+posterior probability P. The types of the candidates are the false
+positives (FPs), the new candidates and the known candidates. The new
+and known candidates have higher detection rate for higher values of P,
+as expected.}
 \end{center}
@@
 
-\section{Methodology to produce the \sw-\cfhtls Lens Sample}
+\section{Methodology to produce the \sw-\cfhtls lens sample}
 \label{sec:swap}
@@
 
-\subsection{\sw-\cfhtls Lens Sample}
+\subsection{\sw-\cfhtls lens sample}
 \label{sec:swlens}
@@
 identified in the literature will be made available at
-http://spacewarps.org/\#/projects/CFHTLS/ whereas the sample of new lens
+\texttt{http://spacewarps.org/\#/projects/CFHTLS/} whereas the sample of new lens
 candidates with G$\ge 1.3$ (medium-high probability) is presented in
@@
 probability sample such as their positions and images will be available
-at http://spacewarps.org/\#/projects/CFHTLS/. Note that if all of the
+at \texttt{http://spacewarps.org/\#/projects/CFHTLS/}. Note that if all of the
 inspectors gave a grade of 0 to a candidate, then it is discarded from
@@
 may be some interesting candidates lurking in TALK but these will have
-to be sifted through
+to be sifted through.
 
@@
 The power of citizen scientists also lies in the high dynamic range that
-allows us to find systems with very from short (thick) to long (thin)
+allows us to find systems which vary from short (thick) to long (thin)
 arcs, from highly compact to low surface brightness images, from round

### 2015-05-05 doc/sw-cfhtls.tex
corrections from co-authors v1

@@
 mostly for images taken from ground based telescopes such as the CFHT
-but sometimes the shapes of the lensed images can appear symmetric or
-perfect, especially, if the images are very bright.
+{\bf but sometimes the profiles of the lensed arcs appear very symmetric along the
+length or width of the arc and featureless, especially, if the images
+are very bright.}
 
@@
 classification of every training image. The thresholds for the
-probabilities to accept (or reject) a subject  if it contains (or does
-not contain) a lens can be chosen in SWAP. Those images which cross
+probabilities {\bf to accept or reject a subject if it contains a lens or does
+not contain one} can be chosen in SWAP. Those images which cross
 these threshold values are retired and are not subsequently shown to the
@@
 led to increased detections of small image separation candidates. The
-\sw lens search did not show any galaxy subtracted images and hence,
+\sw {\bf interface did not show} any galaxy subtracted images and hence,
 this results in a quantitative difference between the \sw and the \rf

### 2015-05-05 doc/sw-system.tex
Minor text edits

@@
 
-We now describe briefly the two-stage strategy that was employed in the \cfhtls
+We now describe briefly the two-stage strategy that we employed in this first
 project: initial classification (involving the rejection of very large numbers
@@
 
-The goal of a \StageOne classification is to achieve a high rejection rate,
+The goal of the \StageOne classification was to achieve a high rejection rate,
 while maintaining high completeness.  In this mode, therefore, the pre-loading
@@
 quickly for the search to be completed within a reasonable time period.  We
-expect some trade-off between speed and accuracy, which we return to in the
+expect some trade-off between speed and accuracy: we return to this topic in the
 results section below. Completion of the search requires subjects to be
@@
 candidates in \StageOne is truly a community effort: to detect a lens candidate,
-many non-lenses must first be rejected, and several classifications by different inspectors are needed in either case.
+many non-lenses must first be rejected, and several classifications by
+different inspectors are needed in either case.
 
@@
 therefore we expect some of those types of object to appear in the \StageOne
-candidate list. The training sims for \StageOne were also selected to be
-relatively straightforward to spot, as we sought a balance between sensitivity
-to faint or difficult lenses, and the need to educate the volunteers in what
-gravitational lenses look like. We return to this balance below.
+candidate list. As described above, the training sims for \StageOne were also
+selected to be relatively straightforward to spot.
 
@@
 
-The design of the \StageOne classification task, and its training set, should
+The design of a \StageOne classification task, and its training set, should
 lead to sample of lens candidates that has high completeness but may have low
@@
 and~\ref{fig:training-gallery:duds} show some example images from the resulting
-\cfhtls \StageTwo training set.
+\StageTwo training set.
 
@@
 \end{minipage} \hfill
-\caption{Typical \SW ``sims'' from the \StageTwo training set. The top right-hand corner insets indicate the
+\caption{Typical \SW ``sims'' from the \StageTwo training set.
+The top right-hand corner insets indicate the
 location of the simulated lens in each of these training images. Users needed to

### 2015-05-06 doc/sw-extended.tex
added a couple more sections. closes #94
added multinomial model description

@@
 \input{addresses.tex}
+
+\def\indic#1{\mathbb{I}\left({#1}\right)}
 
@@
 
+\section{Dataset}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 % TODO:
@@
 improve our estimates.}
+\flag{Chris}{I don't like using $p^0$ to both represent the true prior prior
+and our estimate of the correct prior according to the EM algorithm.}
 
@@
 \begin{itemize}
-  \item{$x_{ij}$, the classification the $i$-th volunteer made of the $j$-th
-      image. $x_{ij}$ may take on three values:
+  \item{$C_{ij}$, the classification the $i$-th volunteer made of the $j$-th
+      image. $C_{ij}$ may take on three values:
       0, 1, or empty. Since volunteers do not see most images, the vast
-    majority of $x_{ij}$ are blank.}
+    majority of $C_{ij}$ are blank.}
     \item{$PD_{i}$, the probability, given that the image is a dud, that
@@
 system that constantly reevaluates most of the above parameters (except $p_0$
-and any non-blank $x_{ij}$) in order to promote likely lenses\footnote{Note
+and any non-blank $C_{ij}$) in order to promote likely lenses\footnote{Note
 that this does not change the probability that a volunteer will actually draw
@@
 $p_j$ at time $k$. \sw uses Bayes' Theorem to update $p_j^{(k + 1)}$ for
-some new evaluation $x_{ij}$\footnote{There is no superscript for $x_{ij}$
+some new evaluation $C_{ij}$\footnote{There is no superscript for $C_{ij}$
 because each user only sees an image once.}:
 \begin{align}
-  p_j^{(k + 1)} &= \left ( \frac{x_{ij} PL_{i}^{k}
+  p_j^{(k + 1)} &= \left ( \frac{C_{ij} PL_{i}^{k}
   }{PL_{i}^{k} p_j^k + (1 - PD_{i}^{k})(1 -
@@
   \right. \notag \\ & \; \left . +
-  \frac{(1 - x_{ij}) (1 - PL_{i}^{k})
+  \frac{(1 - C_{ij}) (1 - PL_{i}^{k})
   }{(1 - PL_{i}^{k}) p_j^k + PD_{i}^{k}(1 -
@@
 
-\sw only updates the volunteer's $PL_{i}$ and $PD_{i}$ after volunteer $x_i$
+\sw only updates the volunteer's $PL_{i}$ and $PD_{i}$ after volunteer $C_i$
 classifies a training image:
@@
 \begin{align}
-  PL_{i}^{(k + 1)} &= \frac{PL_{i}^{k} (NL_{i}^{k} + M) + \mathbb{I}[x_{ij} =
+  PL_{i}^{(k + 1)} &= \frac{PL_{i}^{k} (NL_{i}^{k} + M) + \mathbb{I}[C_{ij} =
   z_{j}]}{NL_{i}^{k} + M + 1} \\
-  PD_{i}^{(k + 1)} &= \frac{PD_{i}^{k} (ND_{i}^{k} + M) + \mathbb{I}[x_{ij} =
+  PD_{i}^{(k + 1)} &= \frac{PD_{i}^{k} (ND_{i}^{k} + M) + \mathbb{I}[C_{ij} =
   z_{j}]}{ND_{i}^{k} + M + 1}
@@
 \begin{multline}
-  \mathrm{CLL}(x_{ij}, z_{j}, PL_{i}, PD_{i}, p_{ij}^{0}) \\ = \sum_{i} \sum_{j \in \Omega_i} x_{ij} z_{j} \log PL_{i} +
-      (1 - x_{ij}) z_j \log (1 -
-      PL_{i}) \\ + (1 - x_{ij}) (1 - z_j) \log PD_{i} + x_{ij} (1 - z_j) \log (1 - PD_{i}) \\ + z_j \log p_{ij}^{0} +
+  \mathrm{CLL}(C_{ij}, z_{j}, PL_{i}, PD_{i}, p_{ij}^{0}) \\ = \sum_{i} \sum_{j \in \Omega_i} C_{ij} z_{j} \log PL_{i} +
+      (1 - C_{ij}) z_j \log (1 -
+      PL_{i}) \\ + (1 - C_{ij}) (1 - z_j) \log PD_{i} + C_{ij} (1 - z_j) \log (1 - PD_{i}) \\ + z_j \log p_{ij}^{0} +
       (1 - z_j ) \log(1 - p_{ij}^{0})
@@
 \begin{align}
-  p_j &= \frac{1}{N_j} \sum_{i \in \Omega_j} P(z_j = 1 \ | \ x_{ij} ; \Phi) =
-  \frac{1}{N_j} \sum_{i \in \Omega_j} \frac{ P(x_{ij} \ | \ z_j = 1; \Phi)
-P(z_j = 1 ; \Phi)}{P(x_{ij} ; \Phi)} \\
-&= \frac{1}{N_j} \sum_{i \in \Omega_j} \frac{ PL_{i}^{x_{ij}} (1 - PL_{i})^{(1 -
-x_{ij})} p_{ij}^{0}}{ PL_{i}^{x_{ij}} (1 -
-  PL_{i})^{(1 - x_{ij})} p_{ij}^{0} + PD_{i}^{(1 - x_{ij})} (1 -
-PD_{i})^{x_{ij}} (1 - p_{ij}^{0})}
+  p_j &= \frac{1}{N_j} \sum_{i \in \Omega_j} P(z_j = 1 \ | \ C_{ij} ; \Phi) =
+  \frac{1}{N_j} \sum_{i \in \Omega_j} \frac{ P(C_{ij} \ | \ z_j = 1; \Phi)
+P(z_j = 1 ; \Phi)}{P(C_{ij} ; \Phi)} \\
+&= \frac{1}{N_j} \sum_{i \in \Omega_j} \frac{ PL_{i}^{C_{ij}} (1 - PL_{i})^{(1 -
+C_{ij})} p_{ij}^{0}}{ PL_{i}^{C_{ij}} (1 -
+  PL_{i})^{(1 - C_{ij})} p_{ij}^{0} + PD_{i}^{(1 - C_{ij})} (1 -
+PD_{i})^{C_{ij}} (1 - p_{ij}^{0})}
 \end{align}
@@
 \begin{align}
-  PL_{i} &= \frac{\sum_{j \in \Omega_i} x_{ij} p_{j}}{\sum_{j \in
+  PL_{i} &= \frac{\sum_{j \in \Omega_i} C_{ij} p_{j}}{\sum_{j \in
 \Omega_i} p_{j}} \\
-  PD_{i} &= \frac{\sum_{j \in \Omega_i} (1 - x_{ij}) (1 - p_{j})}{\sum_{j \in
+  PD_{i} &= \frac{\sum_{j \in \Omega_i} (1 - C_{ij}) (1 - p_{j})}{\sum_{j \in
 \Omega_i} (1 - p_{j})}
@@
 \begin{align}
-  PL_{i} &= \frac{M + \sum_{j \in \Omega_i} x_{ij} p_{j}}{2M + \sum_{j \in
+  PL_{i} &= \frac{M + \sum_{j \in \Omega_i} C_{ij} p_{j}}{2M + \sum_{j \in
 \Omega_i} p_{j}} \\
-  PD_{i} &= \frac{M + \sum_{j \in \Omega_i} (1 - x_{ij}) (1 - p_{j})}{2M + \sum_{j \in
+  PD_{i} &= \frac{M + \sum_{j \in \Omega_i} (1 - C_{ij}) (1 - p_{j})}{2M + \sum_{j \in
 \Omega_i} (1 - p_{j})}
@@
 
+\subsection{Expanding Number of Classifications}
+\todo{Chris}{In this section, we expand possible classifications from LENS and
+  NOT to, say 0, 1, 2, 3. In effect, I take the stuff of \ref{sec:formalism:em}
+  and extend it to a multinomial model. I should put in the generative model
+here as well as the new confusion matrix. I have written the first several
+steps below (not properly formatted and all that).}
+
+\flag{Chris}{In the below formalism everything can only be classified once.
+  That is, classification from user $i$ on subject $j$ as type $u$ is $C_{ij} =
+  u$. If we want to expand classification numbers, we could say instead
+$C_{iju} = 1$ for 1 classification as type $u$. Then, if you draw $M$ total
+classifications, you replace $\text{Uniform}\left(p\right)$ with
+$\text{Mult}\left(p, M\right)$. \\
+Now you may ask: Chris, why would we ever make more than one classification on
+a subject? And I would agree, except that this provides an avenue for analyzing
+how to use \SW to deal with the markers (where there usually are multiple classifications).}
+
+We can extend the \SW binomial model to include multiple classifications and
+multiple categories -- we can talk about things like $P(``1" | \rm{LENSED\
+QUASAR})$ where a user assigns an object a rank $"1"$ and wish to know the
+likelihood that a lensed quasar would yield that category.
+
+Unfortunately our $PL$ and $PD$ terms must be
+generalized. We introduce instead $P_{ivu}$ to represent the $i$-th user's
+probability of making classification $``u"$ given that the object is of type
+$v$: $P_{ivu} = P(``u" | v)_i$. Naturally, the conditional probabilities are
+normalized over the possible classifications $``u"$: $\sum_u^U P_{ivu} = 1$. Overall there are $U$ types of
+classifications a user can make, representing $V$ types of objects.
+
+We also must expand $p^0$ to represent more than a binary classification.
+$p_{jv}^0$ is the prior probability that object $j$ is of type $v$. Naturally,
+$\sum_v p_{jv}^0$ = 1.
+The latent variable of subject $j$ as object $v$ is $z_{jv} = 1$ with all
+other $z_{jv} = 0$. Similarly, the classification of user $i$ on subject $j$
+as type $u$ is $C_{iju} = 1$ with all other $C_{iju} = 0$.
+% The latent variable of subject $j$ as object $v$ is $z_{j} =
+% v$. Similarly, the classification of user $i$ on subject $j$ as type $u$ is
+% $C_{ij} = u$.
+
+This is our generative model with explicit latent variables:
+\begin{itemize}
+  \item{Draw latent subject indicator vectors from the prior probability: $$z_{j}
+    \overset{\text{iid}}{\sim} \text{Uniform}\left(p^0\right)$$}
+  \item{Given latent subject indicator $z_{j}$ and the $i$-th user's confusion
+    matrix $P_i$, independently draw a classification vector from the $z_j$-th column
+  of $P_i$: $$C_{ij} | z_{j} \overset{\text{ind}}{\sim}
+\text{Uniform}\left(P_{i,z_j}\right)$$}
+\end{itemize}
+Hence, we can also make the following statements:
+\begin{equation}
+  p(z_{jv}) = p^0_{jv}
+\end{equation}
+% equiv: p(z_j = v) = p^0_v
+\begin{equation}
+  \label{eq:PCiju}
+  P(C_{iju} | z_{jv}; p^0_{jv}, P_{ivu}) = P_{ivu}^{C_{iju}}
+\end{equation}
+
+Thus our complete log likelihood is (ignoring irrelevant normalization terms)
+% \begin{align}
+%   \log p \left( C_{ij}, z_{j}; p_{jv}^0, P_{ivu} \right) &\propto
+%                                                       \sum_{i} \sum_{j \in
+%                                                       \Omega_i} \indic{z_j = v}
+%                                                       \log p_{jv}^0 \notag\\
+% &+ \indic{C_{ij} = u} \indic{z_j = v} \log P_{ivu}
+% \end{align}
+% where $\indic{}$ is the indicator function which evaluates as one when the
+% contained statement is true and zero when it is false.
+% \flag{Chris}{If you want to write it without indicators, expand the notation to
+%   vectors and you get the following:}
+\begin{align}
+  \log p \left( C_{iju}, z_{jv}; p_{jv}^0, P_{ivu} \right) &\propto \sum_{i} \sum_{j \in
+\Omega_i} \sum_{v} z_{jv} \log p_{jv}^0
+  \notag\\
+  &+ \sum_{i} \sum_{j \in \Omega_i} \sum_{v} \sum_{u} C_{iju} z_{jv} \log P_{ivu}
+\end{align}
+
+\subsubsection{E-Step}
+
+Now we repeat the exercise earlier of computing the expected complete log
+likelihood under the conditional distribution $p(z_{j} | C_{ij}; p^0,
+P_{i})$. Call $p_{jv} = p(z_{jv} | C_{iju}; p^0_{jv}, P_{ivu})$. It is
+sufficient to compute $p_{jv}$ to complete this step. By Bayes's Rule, we
+know that
+\flag{Chris}{Is this an abuse of notation? I want for a single $z_{jv}$, but
+given $C_{iju}, p^0_{jv}, P_{ivu}$ for \textit{all} $i$ and $u$. So really it
+is more correct to say $ p(z_{jv}) \prod_i \prod_u p(C_{iju} | z_{jv}; p^0_{jv},
+P_{ivu})$ since each classification $C_{ij}$ is independent. Should I do that?
+Alternatively, I could put one of those $\cdot$ in place of each $i$ and $u$...}
+$$
+p(z_{jv} | C_{iju}; p^0_{jv}, P_{ivu}) \propto p(C_{iju} | z_{jv}; p^0_{jv},
+P_{ivu}) p(z_{jv})
+$$
+But we know the values of all these terms, so we find:
+\todo{Chris}{Double check this. I'm not sure it's strictly correct when you
+have more than one classification per image / type.}
+\begin{align}
+  p_{jv} = \frac{1}{N_j} \sum_{i \in \Omega_j} \frac{\prod_u p^0_{jv}
+  P_{ivu}^{C_{iju}}}{\sum_{v'} \prod_u p^0_{jv'} P_{iv'u}^{C_{iju}}}
+\end{align}
+
+\subsubsection{M-Step}
+
+We maximize the expected complete log likelihood. This is straightforwardly
+\todo{Chris}{Maybe not so straightforwardly if you have multiple
+classifications. Check that!}
+\begin{align}
+  P_{ivu} &= \frac{\sum_{j \in \Omega_i} C_{iju} p_{jv}}{\sum_{j \in
+\Omega_i} p_{jv}} \\
+  p_{jv}^0 &= p_{jv} \\
+  p_{v}^0 &= \frac{\sum_i \sum_{j \in \Omega_i} p_{jv}}{\sum_i \sum_{j \in
+\Omega_i} 1}
+\end{align}
+where $p_{v}^0$ is a possible specialization of $p_{jv}^0$.
+
+\subsubsection{Checks}
+\todo{Chris}{This section will make some obvious checks on the generalized
+  model. First I should be able to write down the binary model using this
+  formalism. Next, I should be able to show for sure that different $u$ can
+lead to different probability assignments if $v$ can only be two categories --
+that is, I should be able to show that $`1'$ gives a mixture of probability for
+LENS and NOT that makes sense when compared with $`0'$ or $`2'$. \\
+This section can probably be removed. This is more for internal sharing to help
+keep everyone up to speed.}
+
+Let's make sure we recover the old system. In our new notation, $u$ could be
+"LENS" or "NOT" while $v$ could be LENS or NOT. So, $PL_i = P_{iLL}$ and $PD_i
+= P_{iNN}$. We use the conservation of total probability to note that
+$P_{iLN} = 1 - P_{iLL} = 1 - PL_i$ and $P_{iNL} = 1 - P_{iNN} = 1 -
+PD_i$. Meanwhile, $p_j^0$ becomes $p_{jL}^0$ and we use conservation of total
+probability to note that $p_{jN}^0 = 1 - p_{j}^0$. We now account for the
+labels: $z_{j} = z_{jL}$ and $z_{jN} = 1 - z_{j}$. (There can only be one
+label on these objects.) Similarly for the classifications: $C_{ij} = C_{ijL}$,
+so $C_{ijN} = 1 - C_{ij}$.
+
+We can hence expand the
+sums over $v \in (L, N)$ and $u \in (L, N)$ to find that our CLL is
+proportional to:
+\begin{align}
+z_{jL} \log p_{jL}^0 + z_{jN} \log p_{jN}^0 +
+C_{ijL} z_{jL} \log P_{iLL} + C_{ijN} z_{jL} \log P_{iLN} \notag\\ + C_{ijL} z_{jN} \log
+P_{iNL} + C_{ijN} z_{jN} \log P_{iNN} = \notag\\
+z_j \log p_j^0 + (1 - z_j) \log (1 - p_j^0) + C_{ij} z_j \log PL_i + (1 -
+C_{ij}) z_j \log (1 - PL_i) \notag\\
++ C_{ij} (1 - z_j) \log (1 - PD_i) + (1 - C_{ij})
+(1 - z_j) \log PD_i
+\end{align}
+which is the same CLL as before.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
 \section{Dynamic Allocations}
@@
 
+\section{Discussion}
+
+\section{Conclusions}
+
 % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\input{acknowledgments.tex}
+% \input{acknowledgments.tex}
 

### 2015-05-07 doc/sw-cfhtls.tex
Starting to edit paper 2 before subission
corrections from co-authors v2

@@
 \begin{abstract}
-
-We report the discovery of {\bf 29} promising and a total of {\bf 59} new lens
+We report the discovery of {\bf 29 promising (and 59 total)} new lens
 candidates from the CFHT Legacy Survey (\cfhtls) based on about 11
@@
 \sw discovered sample shows that our previous constraints on the average
-density profile of the lens population are robust. \sw recovers about
+density profile of the lenses are robust. \sw recovers about
 60\% of the known sample and the new candidates show a richer variety
 compared to the lenses found by the two robots. We find that analyzing
-only those classifications which are performed by the high power
+only those classifications which are performed by high power
 volunteers, \sw can achieve a detection rate of up to 75\% for the known
@@
 pipeline, used for generating a sample of realistic simulated lensed
-images in the \cfhtls, and a sample of duds and false positives used in
+images in the \cfhtls, and samples of duds and false positives used in
 the training.  Such a training sample has a legacy value for testing
@@
 multiple images. Nevertheless, systematic lens searches have led to the
-discovery of over 500 lenses till
+discovery of over 500 lenses to
 date\footnote{\texttt{http://admin.masterlens.org/index.php}}.
@@
 systems. However, even after such restrictions, robotic lens searches
-have to always rely on visual screening to find a sample of plausible
+have to always rely on visual screening to result in a sample of plausible
 lens candidates.
@@
 Recognising patterns amidst an array of noisy pixelated images is one of the
-strengths of human brains. Humans are also capable of dealing with
+strengths of the human brain. Humans are also capable of dealing with
 multi-tiered complex web of questions before arriving at a conclusion which may
@@
 
-\GZ was the first citizen science project in astronomy, and addressed
+{\bf \GZ, one of the most successful citizen science project in
+astronomy, addressed}
 the problem of how to  classify large numbers of galaxies by their
-morphology \citep{Lintott2008}.  From the early results based on
-morphological classifications of galaxies, to several new unexpected and
+morphology \citep{Lintott2008}.  From these early results to several new unexpected and
 interesting discoveries, such as that of green pea galaxies
@@
 these significant challenges at hand, we designed the \sw project to
-enable the discovery of lenses through citizen science.  In a companion
+enable the discovery of lenses through citizen science (learning from 
+previous experience in serendipitous identification of lens candidates in \GZ).  In a companion
 paper, Paper I (Marshall et al., in prep.), we describe the design of
@@
 \citet{Sygnet2010} carried out a search for edge-on galaxy lenses in the
-\cfhtls WIDE. They identified galaxies, using {\sc Sextractor}, which
+\cfhtls WIDE. They identified galaxies, using {\sc SExtractor}, which
 had $18<i<21$ and inclination angle $<25$~deg. After applying few more
@@
 verified sample of candidates, we choose the most promising 26 systems
-as our bona fide lens sample from the \cfhtls WIDE. Also, the total
-number of lens candidates is 108 from the \cfhtls WIDE alone.
+as our bona fide lens sample from the \cfhtls WIDE. The total
+number of lens candidates in the \cfhtls WIDE alone is 108.
 
@@
 The \rf \citep{Gavazzi2014} was used for finding compact rings or arcs
-around centers of isolated and massive early-type galaxies. The \rf
+around centers of isolated and massive early-type galaxies. \rf
 subtracts the point spread function (PSF)-matched $i$-band images from the $g$-band images, and
@@
 lens finding algorithm and that has been run on the entire \cfhtls
-imaging.  Thus, these can be considered as our reference sample of known
+imaging.  Thus, these are considered as our reference sample of known
 lenses from robotic searches. For the purposes of transparency and to
@@
 
-We extract contiguous cutouts of size 81.84\arcsec\ (440 pixels) with an
+We extract contiguous cutouts of size 81.84\arcsec\ (440 pixels) including
 overlapping region of 10\arcsec (54 pixels) between the neighbouring
@@
 fainter magnitude range compared to the limiting magnitude of the
-\cfhtls imaging and thus, the Magnification bias is naturally taken into
-account.} The source positions with respect to the lens are drawn
-randomly from an area inside the caustic.  We perform ray-tracing for
-all of the $N_{\rm src}$ sources using the publicly available code
-\gravlens \citep{Keeton2000} and choose sources that satisfy our
-selection criteria given below. We determine fluxes of the lensed images and the
-total magnification of each of the lensed source. We draw a
-source randomly for which the flux of the second brightest lensed image and the
-total magnification of all lensed images meet the thresholds given
-in Table~\ref{tab:thresh}.
+\cfhtls imaging and thus, the magnification bias\footnote{ {\bf In a
+flux-limited sample from a survey, sources fainter than the flux limit
+end up in the sample owing to the magnification by lensing which is
+known as the magnification bias. This affects the source luminosity
+function and needs to be accounted for when comparing the true and
+observed luminosity functions.}} is naturally taken into account.} The
+source positions with respect to the lens are drawn randomly from an
+area inside the caustic.  {\bf When populating the sources within the
+caustics, the finite size of the background galaxies is expected to
+affect the lens cross-sections to some extent. As this factor is not
+critical for the purpose of our training sample, we assume the
+background galaxies to be point like for simplicity.} We perform
+ray-tracing for all of the $N_{\rm src}$ sources using the publicly
+available code \gravlens \citep{Keeton2000} and choose sources that
+satisfy our selection criteria given below. We determine fluxes of the
+lensed images and the total magnification of each of the lensed source.
+We draw a source randomly for which the flux of the second brightest
+lensed image and the total magnification of all lensed images meet the
+thresholds given in Table~\ref{tab:thresh}.
 
@@
 mostly for images taken from ground based telescopes such as the CFHT
-{\bf but sometimes the profiles of the lensed arcs appear very symmetric along the
+{\bf but sometimes the profiles of the lensed arcs can appear very symmetric along the
 length or width of the arc and featureless, especially, if the images
@@
 problem in interpolating over the broken blue arc over the red galaxy
-and understand that it is a single long arc. The system SW19 has
+and understand that it is a single long arc. The system {\bf SW20} has
 point-like lensed images which cannot be detected by arc finding
@@
 as lenses. We find that about 40\% of the new \sw candidates fail to
-meet this initial selection criteria, for example, SW1, SW13, SW19,
-SW22, SW26 and SW29.  All of the lensing galaxies are bright enough to
+meet this initial selection criteria, for example, {\bf SW1, SW14, SW20,
+SW23, SW27 and SW30}. All of the lensing galaxies are bright enough to
 satisfy the magnitude criterion ($i<22$). However, some of them have a
@@
 galaxy are not satisfied. Some of the candidates missed at this stage
-are, for example, SW4, SW5, SW6, SW25, SW35, SW38 and SW45.
+are, for example, {\bf SW4, SW5, SW6, SW26, SW36, SW39 and SW46.}
 
@@
 \multicolumn{11}{p{18cm}}{
-The redshift with $^s$ are spectroscopic estimates taken from SDDS Data
-Release 12 whenever available unambiguously. The column Comments has two
+{\bf The redshift with $^s$ are spectroscopic estimates taken from SDDS Data
+Release 12 whenever available unambiguously.} The column Comments has two
 type of notes. The first is about the lens image configuration where the
@@
 symbols are E: Elliptical, S: (face on) Spiral, G: Group-scale, D: Edge
-on disk, R: Red starforming galaxy.  This galaxy falls within the masked
-region as per the catalog from which the magnitudes and the redshift are
-extracted.
+on disk, R: Red starforming galaxy.  
 }\\
 \endlastfoot
-SW19 & CFHTLS J020642.0-095157 &  31.67504 &  -9.86584 &  0.2 & 21.4 &  0.9 &  2.0 & ASW0001ld7 &  0.8 &  A,R   \\ 
-SW8 & CFHTLS J020648.0-065639 &  31.70031 &  -6.94430 &  0.8 & 21.0 &  1.3 &  2.3 & ASW00099ed &  0.4 &  A,E   \\ 
-SW43 & CFHTLS J020810.7-040220 &  32.04497 &  -4.03891 &  1.0 & 21.6 &  1.8 &  1.3 & ASW0001c3j &  0.7 &  A,R   \\ 
-SW9 & CFHTLS J020832.1-043315 &  32.13396 &  -4.55429 &  1.0 & 21.9 &  1.6 &  2.3 & ASW0002asp &  1.0 &  A,R   \\ 
-SW10 & CFHTLS J020848.2-042427 &  32.20110 &  -4.40751 &  0.8 & 21.6 &  1.1 &  2.3 & ASW0002bmc &  0.9 &  D,D   \\ 
-SW11 & CFHTLS J020849.8-050429 &  32.20784 &  -5.07494 &  0.8 & 21.3 &  0.9 &  2.3 & ASW0002qtn &  1.0 &  A,R   \\ 
-SW44 & CFHTLS J021021.5-093415 &  32.58981 &  -9.57109 &  0.4 & 19.0 &  2.7 &  1.3 & ASW0002k40 &  0.4 &  D,S   \\ 
-SW30 & CFHTLS J021057.9-084450 &  32.74148 &  -8.74745 &  0.45$^s$ &  0.0 &  2.5 &  1.7 & ASW0002p8y &  0.4 &  A,G   \\ 
-SW20 & CFHTLS J021221.1-105251 &  33.08810 & -10.88106 &  0.3 & 18.2 &  1.8 &  2.0 & ASW0002dx7 &  0.8 &  D,E/S   \\ 
-SW45 & CFHTLS J021225.2-085211 &  33.10511 &  -8.86973 &  0.76$^s$ & 20.5 &  2.1 &  1.3 & ASW00024id &  1.0 &  R,R   \\ 
-SW46 & CFHTLS J021317.6-084819 &  33.32341 &  -8.80549 &  0.5 & 20.6 &  1.3 &  1.3 & ASW00024q6 &  0.4 &  A,R/E   \\ 
-SW31 & CFHTLS J021514.6-092440 &  33.81089 &  -9.41115 &  0.72$^s$ & 21.1 &  2.6 &  1.7 & ASW00021r0 &  0.4 &  A,R/G   \\ 
-SW32 & CFHTLS J022359.8-083651 &  35.99955 &  -8.61439 &  0.0 &  0.0 &  3.1 &  1.7 & ASW0004iye &  0.4 &  A,E   \\ 
-SW12 & CFHTLS J022406.1-062846 &  36.02558 &  -6.47963 &  0.4 & 20.1 &  0.9 &  2.3 & ASW0003wsu &  0.7 &  A,E   \\ 
-SW1 & CFHTLS J022409.5-105807 &  36.03978 & -10.96885 &  0.0 &  0.0 &  4.8 &  3.0 & ASW0004dv8 &  1.0 &  A,G   \\ 
-SW21 & CFHTLS J022533.3-053204 &  36.38882 &  -5.53460 &  0.57$^s$ & 20.4 &  3.6 &  2.0 & ASW0004m3x &  0.4 &  A,R/G   \\ 
-SW22 & CFHTLS J022716.4-105602 &  36.81856 & -10.93410 &  0.4 & 17.8 &  1.8 &  2.0 & ASW0009ab8 &  0.7 &  A,E/G   \\ 
-SW33 & CFHTLS J022745.2-062518 &  36.93868 &  -6.42183 &  0.6 & 21.3 &  1.2 &  1.7 & ASW0003s0m &  0.5 &  A,R   \\ 
-SW13 & CFHTLS J022805.6-051733 &  37.02362 &  -5.29266 &  0.4 & 19.2 &  1.4 &  2.3 & ASW00047ae &  1.0 &  Q,E   \\ 
-SW47 & CFHTLS J022843.0-063316 &  37.17942 &  -6.55465 &  0.5 & 19.9 &  1.8 &  1.3 & ASW0003r6c &  0.3 &  D/A,E   \\ 
-SW23 & CFHTLS J023008.6-054038 &  37.53591 &  -5.67744 &  0.50$^s$ & 20.4 &  1.9 &  2.0 & ASW0003r61 &  0.5 &  A,E   \\ 
-SW14 & CFHTLS J023123.2-082535 &  37.84682 &  -8.42663 &  0.0 & 0.0 &  1.2 &  2.3 & ASW0004xjk &  0.3 &  A,R   \\ 
-SW24 & CFHTLS J023315.2-042243 &  38.31334 &  -4.37886 &  0.7 & 20.4 &  1.0 &  2.0 & ASW00050sk &  0.8 &  A,R   \\ 
-SW34 & CFHTLS J023453.5-093032 &  38.72321 &  -9.50892 &  0.5 & 20.3 &  0.7 &  1.7 & ASW00051ld &  0.3 &  A,D   \\ 
-SW35 & CFHTLS J084833.2-044051 & 132.13847 &  -4.68085 &  0.8 & 21.1 &  0.9 &  1.7 & ASW0004wgd &  0.7 &  A,R   \\ 
-SW15 & CFHTLS J084841.0-045237 & 132.17084 &  -4.87720 &  0.3 & 19.5 &  1.0 &  2.3 & ASW0004nan &  1.0 &  A,E   \\ 
-SW48 & CFHTLS J090219.0-053923 & 135.57947 &  -5.65666 &  0.0 &  0.0 &  2.0 &  1.3 & ASW0000g95 &  1.0 &  A,R/E   \\ 
-SW36 & CFHTLS J090248.4-010232 & 135.70204 &  -1.04243 &  0.4 & 19.7 &  1.4 &  1.7 & ASW000096t &  0.6 &  D,E   \\ 
-SW25 & CFHTLS J090308.2-043252 & 135.78449 &  -4.54789 &  0.0 &  0.0 &  1.3 &  2.0 & ASW00007mq &  0.6 &  D,D   \\ 
-SW49 & CFHTLS J090319.4-040146 & 135.83105 &  -4.02971 &  0.0 & 20.6 &  1.2 &  1.3 & ASW00007ls &  0.5 &  A,R/E   \\ 
-SW50 & CFHTLS J090333.2-005829 & 135.88869 &  -0.97490 &  0.0 &  0.0 &  2.1 &  1.3 & ASW00008a0 &  1.0 &  A/D,E/G   \\ 
+SW19 & CFHTLS J020642.0$-$095157 &  31.67504 &  $-$9.86584 &  0.2 & 21.4 &  0.9 &  2.0 & ASW0001ld7 &  0.8 &  A,R   \\ 
+SW8 & CFHTLS J020648.0$-$065639 &  31.70031 &  $-$6.94430 &  0.8 & 21.0 &  1.3 &  2.3 & ASW00099ed &  0.4 &  A,E   \\ 
+SW43 & CFHTLS J020810.7$-$040220 &  32.04497 &  $-$4.03891 &  1.0 & 21.6 &  1.8 &  1.3 & ASW0001c3j &  0.7 &  A,R   \\ 
+SW9 & CFHTLS J020832.1$-$043315 &  32.13396 &  $-$4.55429 &  1.0 & 21.9 &  1.6 &  2.3 & ASW0002asp &  1.0 &  A,R   \\ 
+SW10 & CFHTLS J020848.2$-$042427 &  32.20110 &  $-$4.40751 &  0.8 & 21.6 &  1.1 &  2.3 & ASW0002bmc &  0.9 &  D,D   \\ 
+SW11 & CFHTLS J020849.8$-$050429 &  32.20784 &  $-$5.07494 &  0.8 & 21.3 &  0.9 &  2.3 & ASW0002qtn &  1.0 &  A,R   \\ 
+SW44 & CFHTLS J021021.5$-$093415 &  32.58981 &  $-$9.57109 &  0.4 & 19.0 &  2.7 &  1.3 & ASW0002k40 &  0.4 &  D,S   \\ 
+SW30 & CFHTLS J021057.9$-$084450 &  32.74148 &  $-$8.74745 &  0.45$^s$ &  0.0 &  2.5 &  1.7 & ASW0002p8y &  0.4 &  A,G   \\ 
+SW20 & CFHTLS J021221.1$-$105251 &  33.08810 & $-$10.88106 &  0.3 & 18.2 &  1.8 &  2.0 & ASW0002dx7 &  0.8 &  D,E/S   \\ 
+SW45 & CFHTLS J021225.2$-$085211 &  33.10511 &  $-$8.86973 &  0.76$^s$ & 20.5 &  2.1 &  1.3 & ASW00024id &  1.0 &  R,R   \\ 
+SW46 & CFHTLS J021317.6$-$084819 &  33.32341 &  $-$8.80549 &  0.5 & 20.6 &  1.3 &  1.3 & ASW00024q6 &  0.4 &  A,R/E   \\ 
+SW31 & CFHTLS J021514.6$-$092440 &  33.81089 &  $-$9.41115 &  0.72$^s$ & 21.1 &  2.6 &  1.7 & ASW00021r0 &  0.4 &  A,R/G   \\ 
+SW32 & CFHTLS J022359.8$-$083651 &  35.99955 &  $-$8.61439 &  0.0 &  0.0 &  3.1 &  1.7 & ASW0004iye &  0.4 &  A,E   \\ 
+SW12 & CFHTLS J022406.1$-$062846 &  36.02558 &  $-$6.47963 &  0.4 & 20.1 &  0.9 &  2.3 & ASW0003wsu &  0.7 &  A,E   \\ 
+SW1 & CFHTLS J022409.5$-$105807 &  36.03978 & $-$10.96885 &  0.0 &  0.0 &  4.8 &  3.0 & ASW0004dv8 &  1.0 &  A,G   \\ 
+SW21 & CFHTLS J022533.3$-$053204 &  36.38882 &  $-$5.53460 &  0.57$^s$ & 20.4 &  3.6 &  2.0 & ASW0004m3x &  0.4 &  A,R/G   \\ 
+SW22 & CFHTLS J022716.4$-$105602 &  36.81856 & $-$10.93410 &  0.4 & 17.8 &  1.8 &  2.0 & ASW0009ab8 &  0.7 &  A,E/G   \\ 
+SW33 & CFHTLS J022745.2$-$062518 &  36.93868 &  $-$6.42183 &  0.6 & 21.3 &  1.2 &  1.7 & ASW0003s0m &  0.5 &  A,R   \\ 
+SW13 & CFHTLS J022805.6$-$051733 &  37.02362 &  $-$5.29266 &  0.4 & 19.2 &  1.4 &  2.3 & ASW00047ae &  1.0 &  Q,E   \\ 
+SW47 & CFHTLS J022843.0$-$063316 &  37.17942 &  $-$6.55465 &  0.5 & 19.9 &  1.8 &  1.3 & ASW0003r6c &  0.3 &  D/A,E   \\ 
+SW23 & CFHTLS J023008.6$-$054038 &  37.53591 &  $-$5.67744 &  0.50$^s$ & 20.4 &  1.9 &  2.0 & ASW0003r61 &  0.5 &  A,E   \\ 
+SW14 & CFHTLS J023123.2$-$082535 &  37.84682 &  $-$8.42663 &  0.0 & 0.0 &  1.2 &  2.3 & ASW0004xjk &  0.3 &  A,R   \\ 
+SW24 & CFHTLS J023315.2$-$042243 &  38.31334 &  $-$4.37886 &  0.7 & 20.4 &  1.0 &  2.0 & ASW00050sk &  0.8 &  A,R   \\ 
+SW34 & CFHTLS J023453.5$-$093032 &  38.72321 &  $-$9.50892 &  0.5 & 20.3 &  0.7 &  1.7 & ASW00051ld &  0.3 &  A,D   \\ 
+SW35 & CFHTLS J084833.2$-$044051 & 132.13847 &  $-$4.68085 &  0.8 & 21.1 &  0.9 &  1.7 & ASW0004wgd &  0.7 &  A,R   \\ 
+SW15 & CFHTLS J084841.0$-$045237 & 132.17084 &  $-$4.87720 &  0.3 & 19.5 &  1.0 &  2.3 & ASW0004nan &  1.0 &  A,E   \\ 
+SW48 & CFHTLS J090219.0$-$053923 & 135.57947 &  $-$5.65666 &  0.0 &  0.0 &  2.0 &  1.3 & ASW0000g95 &  1.0 &  A,R/E   \\ 
+SW36 & CFHTLS J090248.4$-$010232 & 135.70204 &  $-$1.04243 &  0.4 & 19.7 &  1.4 &  1.7 & ASW000096t &  0.6 &  D,E   \\ 
+SW25 & CFHTLS J090308.2$-$043252 & 135.78449 &  $-$4.54789 &  0.0 &  0.0 &  1.3 &  2.0 & ASW00007mq &  0.6 &  D,D   \\ 
+SW49 & CFHTLS J090319.4$-$040146 & 135.83105 &  $-$4.02971 &  0.0 & 20.6 &  1.2 &  1.3 & ASW00007ls &  0.5 &  A,R/E   \\ 
+SW50 & CFHTLS J090333.2$-$005829 & 135.88869 &  $-$0.97490 &  0.0 &  0.0 &  2.1 &  1.3 & ASW00008a0 &  1.0 &  A/D,E/G   \\ 
 SW51 & CFHTLS J135724.8+561614 & 209.35374 &  56.27066 &  0.36$^s$ &  0.0 &  2.6 &  1.3 & ASW0006e0o &  0.9 &  D,E   \\ 

### 2015-05-07 doc/sw-cfhtls.tex

@@
 density profile of the lenses are robust. \sw recovers about
-60\% of the known sample and the new candidates show a richer variety
+60~per~cent of the known sample and the new candidates show a richer variety
 compared to the lenses found by the two robots. We find that analyzing
 only those classifications which are performed by high power
-volunteers, \sw can achieve a detection rate of up to 75\% for the known
+volunteers, \sw can achieve a detection rate of up to 75~per~cent for the known
 lens sample.  Training and calibration of the performance of citizen
@@
 \begin{keywords}
-  gravitational lensing   --
-  methods: statistical    --
-  methods: citizen science
+  gravitational lensing: strong   --
+  methods: statistical
 \end{keywords}
@@
 
-{\bf From the early release of the CFHTLS (T0002) covering 28~sq.~deg.,
+{\bf From the early release of the CFHTLS (T0002) covering 28~deg$^2$,
 \citet{Cabanac2007} used an arc finding algorithm \citep{Alard2006} to
@@
 \cfhtls WIDE. They identified galaxies, using {\sc SExtractor}, which
-had $18<i<21$ and inclination angle $<25$~deg. After applying few more
+had $18<i<21$ and inclination angle $<25\,^{\circ}$. After applying few more
 selection criteria and visual inspection, they found about 3 promising
@@
 detection. This new approach was tested on the CFHTLS-Archive-Research
-Survey \citep[CARS,][]{Erben2009} which covers an area of 37~sq.~deg
+Survey \citep[CARS,][]{Erben2009} which covers an area of 37~deg$^2$
 only and this entire data was also visually inspected by the authors to
@@
 inspected known lens sample at \StageTwo (P$> 0.3$), the experts gave a
-grade of 1.3 and above to about 92\% (33 out of 36) of the systems. Overall,
+grade of 1.3 and above to about 92~per~cent (33 out of 36) of the systems. Overall,
 the sample of new \sw lens candidates increased the sample of total
-\cfhtls lens candidates by over 50\%.
+\cfhtls lens candidates by over 50~per~cent.
 
@@
 the purity of the final sample. However, we go with the choice of
-P~$=$~0.3 as this gives a better completeness of 100\% for the ``known
-lens'' sample instead of 67\% for P~$=$~0.75. Therefore, the new sample
+P~$=$~0.3 as this gives a better completeness of 100~per~cent for the ``known
+lens'' sample instead of 67~per~cent for P~$=$~0.75. Therefore, the new sample
 should also have increased completeness which combined with expert
@@
 combined, as mentioned in \Sref{sec:data:kls}. In Table~\ref{tab:stats},
-we show that $\sim$~25\%-30\% of the known lens candidates and
-$\sim$~60\% of the known lenses are found at \StageOne and \StageTwo in
+we show that $\sim$~25$-$30~per~cent of the known lens candidates and
+$\sim$~60~per~cent of the known lenses are found at \StageOne and \StageTwo in
 \sw. The left and the middle panels of \Fref{fig:compre} show the
@@
 \citep[see]{Gavazzi2014} to select galaxies which are most likely to act
-as lenses. We find that about 40\% of the new \sw candidates fail to
+as lenses. We find that about 40~per~cent of the new \sw candidates fail to
 meet this initial selection criteria, for example, {\bf SW1, SW14, SW20,
@@
 lensed features. An object finder is run on this image to quantify the
-lensed image properties. Another $\sim$~50\% of the \sw candidates could not be
+lensed image properties. Another $\sim$~50~per~cent of the \sw candidates could not be
 detected by the object finder because properties such as the image area,
@@
 noise and hence, affects the number and type of arc detections. We find
-that about 30\% of the new candidates are detected without changing any
+that about 30~per~cent of the new candidates are detected without changing any
 of the thresholds in the code because of the change in the noise level.
@@
 thresholds mainly on the area of the arc which leads to detection of
-about 75\% of the new \sw candidates. We find that relaxing thresholds
+about 75~per~cent of the new \sw candidates. We find that relaxing thresholds
 on other arc properties does not improve the detection rate significantly
@@
 Like any lens finding method, the \sw system can fail to detect certain
-kinds of lenses.  We find that about 40\% of the known sample of lenses
+kinds of lenses.  We find that about 40~per~cent of the known sample of lenses
 are missed both at \StageOne and II (see \Tref{tab:stats}). In fact, most
@@
 Einstein radii and faint lensed images (see \Fref{fig:compre}). Among
-the confirmed lenses from the \rf, about 50\% are missed. Out of the
+the confirmed lenses from the \rf, about 50~per~cent are missed. Out of the
 missed sample of 18 lenses, about half of them are visually difficult to
@@
 galaxies which should have been easier to identify. Similarly,
-if we consider the \af lens sample, $\sim$23\% are missed by \sw. This
+if we consider the \af lens sample, $\sim$23~per~cent are missed by \sw. This
 is a relatively small sample of $\sim 5$ systems and visual inspection
@@
 
-\item From the sample of known lenses, \sw missed about 40\% at \StageOne.
+\item From the sample of known lenses, \sw missed about 40~per~cent at \StageOne.
 Among the missed sample of about 20 lenses, roughly half of them are
@@
 \item If we use the classifications from the high power volunteers alone
-at \StageOne, then we recover over 30\% of the lenses from the missed
+at \StageOne, then we recover over 30~per~cent of the lenses from the missed
 sample. Thus, it is possible to improve the completeness of lenses by

### 2015-05-07 doc/sw-system.tex
Note on sim alpha channel

@@
 in \Fref{fig:screenshot}) or feedback for an unsuccessful one (for
-example, ``There is no gravitational lens in this field!'').
+example, ``There is no gravitational lens in this field!''). A successful
+classification of a simulated lens requires a marker to be placed fairly
+precisely on the lensed features, so as to avoid misinforming the classifier.
+The pixels in the lensed features are flagged via a mask contained in the
+PNG image transparency ``alpha'' channel. (The mask is not visible in the image.)
 
@@
 ``dud'' training images (previous section). For easy reference, the lenses are
-divided by type (for example, ``lensed galaxies,'' ``lensed quasars'' and
-``cluster lenses''), as are the false positives (for example, ``Rings and
+divided by type (for example, ``Lensed Galaxies,'' ``Lensed Quasars'' and
+``Cluster Lenses''), as are the false positives (for example, ``Rings and
 Spirals,'' ``Mergers,'' ``Artifacts'' and so on). The example images are
@@
 
-Most of the text of the Spotter's Guide focuses on what kinds of image features
-gravitational lenses do or don't produce;
+Most of the text of the Spotter's Guide focuses on the kinds of features that
+gravitational lenses do or don't produce. To complement this,
 the website ``Science page'' contains a very brief introduction to how
@@
 The \StageOne training set was chosen to be quite clear cut, in order to err on
-the side of inclusivity, and so ensure high completeness. When defining the
-training duds we discarded anything that could be considered a lens candidate
-(see \Sref{sec:design:training:guide}): this meant that objects that look
+the side of high completeness. When defining the
+training duds, we discarded anything that could be considered a lens candidate
+(see \Sref{sec:design:training:guide}). This meant that objects that look
 similar to lenses, such as galaxy mergers, tidal tails and spiral arms, pairs of
@@
 The design of a \StageOne classification task, and its training set, should
-lead to sample of lens candidates that has high completeness but may have low
+lead to a sample of lens candidates that has high completeness but may have low
 purity. To refine this sample to higher purity, we need to reject more
@@
 \bibliographystyle{apj}
-\bibliography{references}
+\bibliography{references_system}
 

### 2015-05-07 doc/sw-system.tex
Added footnote to Terapix report, closes #163
Fixed SW paper refs

@@
 to survey teams looking for lenses in wide field imaging data. In a companion
-paper \citep[][hereafter \PaperTwo](PaperII) we will present the new
+paper \citep[][hereafter \PaperTwo]{MoreEtal2015} we will present the new
 gravitational lenses discovered in our first lens search, and
@@
 expected from several next-generation sky surveys, such as DES, KiDS, HSC and
-LSST.
+LSST. We use the stacked images
+from the final T0007 release taken from the Terapix
+website\footnote{\texttt{http://terapix.iap.fr/cplt/T0007/doc/T0007-doc.pdf}} for this
+work.
 

### 2015-05-07 doc/sw-system.tex
Fixed #165

@@
 gravitational lenses do or don't produce. To complement this,
-the website ``Science page'' contains a very brief introduction to how
+the website ``Science'' section contains a very brief introduction to how
 gravitational lensing works, which is fleshed out a little on the ``FAQ'' page.
-The FAQ also contains answers to frequently asked questions about the interface
+The FAQ also contains answers to questions about the interface
 and the task set.

### 2015-05-07 doc/sw-system.tex
Fixed #167, fixed#168, fixed #169

@@
 the pixel values of each image, in the notation of \citeauthor{LuptonEtal2004},
-into flux units (``picomaggies,''), via the image AB zeropoint $m_0$ and the
+into flux units (``picomaggies''), via the image AB zeropoint $m_0$ and the
 pixel value calibration factor $f$  given by $\log_{10}{f} = 0.4(30.0 - m_0)$.
@@
 the detectability of these faint features.   Examples of \cfhtls training set
-images prepared in this way can be seen in the galleries of the previous
-section (Figures~\ref{fig:training-gallery:sims}
-and~\ref{fig:training-gallery:duds}). We also defined two alternative sets of
+images prepared in this way can be seen in Figures~\ref{fig:training-gallery:sims}
+and~\ref{fig:training-gallery:duds}. We also defined two alternative sets of
 visualization parameters, to display a ``bluer'' image and a ``brighter''
@@
 Each classification made is logged in a database, storing subject IDs,
-(anonymous) volunteer IDs, a timestamp and the classification results (the image
+volunteer IDs, a timestamp and the classification results (the image
 pixel-coordinate positions of every marker placed).  The ``category'' of subject --

### 2015-05-07 doc/sw-system.tex
Added note on stars, closes #171
Fixed #173

@@
 (solid blue curve), while the offline analysis was chosen for the final
-\StageTwo results (dot-dashed orange curve). }
+\StageTwo results (dot-dashed orange curve).
+Lens probability varies along the curves: the stars indicate the point where
+the value of this quantity is 0.95.}
 \label{fig:results:sample:roc}
@@
 Finally, there could be some performance gains to be made by improving the SWAP
-agent model, or its implementation. Low skill is typically a result  of
-inexperience (\Sref{sec:results:crowd}), but it could be the agent that is
-inexperienced as well as the classifier or its agent. In a future paper we plan
-to investigate the use of the test images as well as the training images in
-accelerating the agent's learning (Davis et al, in preparation). We also plan to
-investigate the use of offline analysis at \StageOne, partly for the same reason
-(see also \Sref{sec:discuss:efficiency} below.) Given the above findings  about
-the effects of noise in the SWAP system, we are also motivated to explore
-further the possible noise-reducing effects of the doing the analysis offline
-(\Sref{sec:results:sample}).
+agent model, or its implementation.
+
+Low skill is typically a result  of inexperience (\Sref{sec:results:crowd}) --
+but it could be the agent  that is inexperienced, as much  the classifier.  In a
+future paper we plan to investigate the use of the test images as well as the
+training images in accelerating the agent's learning (Davis et al, in
+preparation). We also plan to investigate the use of offline analysis at
+\StageOne, partly for the same reason (see also \Sref{sec:discuss:efficiency}
+below.) Given the above findings  about the effects of noise in the SWAP system,
+we are also motivated to explore further the possible noise-reducing effects of
+the doing the analysis offline (\Sref{sec:results:sample}).
 

### 2015-05-07 doc/sw-system.tex
Fixed #174, fixed #175, fixed #176

@@
 respectively. In \StageOne, this inefficiency is due to the daily processing: we
-were not able to retire subjects fast enough, and so they, remained in the
+were not able to retire subjects fast enough, and so they remained in the
 system, being over-classified. Indeed, only 3705745 classifications were
@@
 measure of the effective crowd size, in the sense that a crowd of perfect
-classifiers would be of this size. By this measure,the \StageOne crowd was
+classifiers would be of this size. By this measure, the \StageOne crowd was
 equivalent to a team of 1470 perfect classifiers, while the \StageTwo crowd was
@@
 \item The optimal true positive rate (completeness) and false positive rate in
-the training set were estimated to be around $91--93\%$ and $<1\%$ (Stages 1 and
+the training set were estimated to be around $91-93\%$ and $<1\%$ (Stages 1 and
 2). This FPR translates to an approximate purity of 30\%. We find a

### 2015-05-07 doc/sw-system.tex
Fixed #197 by changing tile size from 84 to 82 arcsec throughout

@@
 candidates. Having divided 160 square degrees of Canada-France-Hawaii Telescope
-Legacy Survey (\cfhtls) imaging into some 430,000 overlapping 84 by 84 arcsecond
+Legacy Survey (\cfhtls) imaging into some 430,000 overlapping 82 by 82 arcsecond
 tiles and displaying them on the site, we were joined by around 37,000
@@
 \cfhtls pointings into some 430,000 equal size, overlapping tiles, approximately
-84~arcsec on a side. We refer to these images as ``test images.'' The ``training
+82~arcsec on a side. We refer to these images as ``test images.'' The ``training
 images'' were derived from a small subset of these, as  discussed above. In

### 2015-05-08 doc/sw-system.tex
Note on truncation of P-C curves in Figure 7

@@
 \caption{Completeness-estimated purity curves for the \sw system, using
-the \cfhtls training set.}
+the \cfhtls training set. The curves are truncated at the high purity end by
+the ``detection'' limit subject probability (subjects in the online
+\StageOne analysis were
+deemed to be detected at $p=0.95$, while at \StageTwo rounding error led to 
+an upper limit of $p=1.0$).}
 \label{fig:results:sample:CP}

### 2015-05-08 doc/sw-system.tex
Added RF ref to future surveys prediction, closes #100. Also fixed author names to standard ones seen on ADS.

@@
 the Zooniverse userbase. Alternatively, suppose that automated  lens finding
-algorithms are able to select as few as $10^6$ targets for visual inspection (a
-sample with 10\% purity). Increasing $\tau_0$ by a factor of three to allow for
+algorithms were able to select as few as $10^5$ targets for visual
+inspection,
+sample with 10\% purity with a surface density of $\sim10$ per square degree
+\citep[a rate within reach of \RF, for example:][]{GavazziEtal2014}.
+Increasing $\tau_0$ by a factor of three to allow for
 more inspection time per subject,  we find that \SW could enable a crowd of just
-$10^6$ volunteers to assess them in about three  weeks.
+$10^5$ volunteers to assess them in about three weeks.
 

### 2015-05-08 doc/sw-cfhtls.tex
Reworded abstract

@@
 first \sw lens search.  The goal of the blind lens search was to
-identify lenses missed by lens finding robots (the \rf on galaxy scales
-and \af on group/cluster scales), which have been previously used to
-mine the \cfhtls for lenses.  We compare some properties of lens samples
-detected by these algorithms to the \sw sample and found that they are
+identify lens candidates missed by robots (the \rf on galaxy scales
+and \af on group/cluster scales) which had been previously used to
+mine the \cfhtls for lenses.  We compare some properties of the samples
+detected by these algorithms to the \sw sample and find them to be
 broadly similar.  The image separation distribution calculated from the
-\sw discovered sample shows that our previous constraints on the average
-density profile of the lenses are robust. \sw recovers about
-60~per~cent of the known sample and the new candidates show a richer variety
-compared to the lenses found by the two robots. We find that analyzing
-only those classifications which are performed by high power
-volunteers, \sw can achieve a detection rate of up to 75~per~cent for the known
-lens sample.  Training and calibration of the performance of citizen
-scientists is crucial for the success of \sw. We also present the SIMCT
-pipeline, used for generating a sample of realistic simulated lensed
-images in the \cfhtls, and samples of duds and false positives used in
-the training.  Such a training sample has a legacy value for testing
-future lens finding algorithms. We make our training sample publicly
+\sw sample shows that previous constraints on the average
+density profile of lens galaxies are robust. \sw recovers about
+60\% of known lenses, while the new candidates show a richer variety
+compared to those found by the two robots. This detection rate could be
+increased to 75\% by only using classifications performed by expert
+volunteers (albeit at the cost of a higher false positive rate), indicating that
+the training and performance calibration of the citizen
+scientists is very important for the success of \sw. In this work
+we present the SIMCT pipeline, used for generating {\it in situ}
+a sample of realistic  simulated lensed
+images.  This training sample, along with the
+false positives identified during the
+search, has a legacy value for testing
+future lens finding algorithms. We make this dataset publicly
 available.

### 2015-05-08 doc/sw-cfhtls.tex
Introduction #203

@@
 used to probe the dark matter distribution from galaxy
-\citep[e.g.][]{Koopmans2006,Barnabe2009,Leier2011,Sonnenfeld2015} to groups-cluster
-scales
+\citep[e.g.][]{Koopmans2006,Barnabe2009,Leier2011,Sonnenfeld2015} to group and
+cluster scales
 \citep[e.g.][]{Limousin2008,Zitrin2011,Oguri2012,More2012,Newman2013}, to
@@
 test the cosmological model by constraining cosmological parameters such
-as the Hubble constant and dark energy
-\citep[e.g.][]{Suyu2010,Collett2012,Collett2014,Sereno2014} and many more. Strong
-lenses are rare since a foreground massive object needs to be
+as the Hubble constant and the dark energy equation of state
+\citep[e.g.][]{Suyu2010,Collett2012,Collett2014,Sereno2014}, and many more. Strong
+lenses are rare, because a foreground massive object needs to be
 sufficiently aligned with a distant background source to produce
@@
 discovery of over 500 lenses to
-date\footnote{\texttt{http://admin.masterlens.org/index.php}}.
+date.\footnote{\texttt{http://admin.masterlens.org/index.php}}
 
 The search for gravitational lenses is a needle-in-a-haystack problem.
-Efficient automated methods are imperative to find a reasonably complete
-and pure sample of strong lenses. Several lens finding algorithms have
+Several automated lens finding algorithms have
 been developed so far
-\citep[e.g.][]{Lenzen2004,Alard2006,Seidel2007,More2012,Brault2014,Gavazzi2014} but they can not
+\citep[e.g.][]{Lenzen2004,Alard2006,Seidel2007,More2012,Brault2014,Gavazzi2014},
+but they can not
 simultaneously capture the myriad types of lenses that are known to
@@
 light around stars).  Almost all lens finding algorithms find it
-difficult to distinguish these from the real lenses and thus, suffer
-from the problems of high rate of false positives.  To minimize this problem,
+difficult to distinguish these from the real lenses and thus suffer
+from a high rate of false positive detections.  To mitigate this problem,
 algorithms are often restricted to detect a very narrow class of lens
@@
 
-Recognising patterns amidst an array of noisy pixelated images is one of the
+Recognising patterns is one of the
 strengths of the human brain. Humans are also capable of dealing with
-multi-tiered complex web of questions before arriving at a conclusion which may
+multi-tiered complex web of questions before arriving at a conclusion, a process
+which may
 not be always possible to automate. The algorithm by which our brains process a
@@
 finding algorithms are not yet advanced enough to produce better performance
-than visual classifications. Therefore, participation of a large community of
-volunteers to help with the visual identification of lenses is extremely
-beneficial for the lensing community. In particular, as we enter the era of
-large area imaging surveys (spanning thousands of square degrees), it is
-a perfect time to tap into the potential of citizen science.
-
-{\bf \GZ, one of the most successful citizen science project in
+than visual classifications. Consequently, as we enter the era of
+large area imaging surveys spanning thousands of square degrees,
+the participation of a large community of
+volunteers to help with the visual identification of lenses would be very
+beneficial for the lensing community.  Now seems
+the perfect time to investigate the potential of citizen science.
+
+{\bf \GZ, one of the most successful citizen science projects in
 astronomy, addressed}
 the problem of how to  classify large numbers of galaxies by their
-morphology \citep{Lintott2008}.  From these early results to several new unexpected and
+morphology \citep{Lintott2008}.
+From these early results to several new unexpected and
 interesting discoveries, such as that of green pea galaxies
 \citep{Cardamone2009,Jaskot2013} and Hanny's Voorwerp
-\citep{Lintott2009,Keel2012}, \GZ has been able to harness the potential
-of citizen scientists.  Since then astronomy and non-astronomy projects
+\citep{Lintott2009,Keel2012}, \GZ has been able to start to realize the potential
+of citizen scientists.  Since then, both astronomy and non-astronomy projects
 have been launched under the citizen science web portal Zooniverse
 (\texttt{http://zooniverse.org}). The task of finding gravitational lenses is
-significantly challenging given that the lens systems show such
+significantly challenging, given that the lens systems show such
 complexity and that they are rare. To add to the challenge, not many
 citizen scientists are expected to be aware of the phenomenon of
-gravitational lensing, and the resulting image configurations.  With
+gravitational lensing, and the resulting characteristic image configurations.  With
 these significant challenges at hand, we designed the \sw project to
 enable the discovery of lenses through citizen science (learning from
-previous experience in serendipitous identification of lens candidates in \GZ).  In a companion
-paper, Paper I (Marshall et al., in prep.), we describe the design of
+previous experience in serendipitous identification of lens candidates in \GZ).
+In a companion
+paper \citep[][hereafter \PaperOne]{Marshall2015}, we describe the design of
 \sw and how the entire system functions as a discovery service.  In this
-paper (Paper II hereafter), we describe our first lens search using data
+paper (\PaperTwo), we describe our first lens search using data
 from the Canada-France-Hawaii Telescope Legacy Survey
@@
 {\bf In \citet{Kung2015}, we describe the design of a collaborative
-mass modelling tool that can be used by citizen scientists
-.}
+mass modelling tool that can be used by citizen scientists.}
 
@@
 turned into a catalog of plausible candidates (for further details, see
-Paper I). In \Sref{sec:results}, we present the new lens candidates from \sw and
-compare it to the lens samples produced by a few robotic searches from
-the \cfhtls in the past. Next, we discuss what kind of lenses are detected
-or missed by the algorithms and \sw in \Sref{sec:discuss}. The summary
-and conclusions are given in \Sref{sec:conclude}.
+\PaperOne). In \Sref{sec:results}, we present the new lens candidates from \sw and
+compare it to the lens samples produced by past robotic searches of
+the \cfhtls. Next, we discuss what kind of lenses are detected
+or missed by the algorithms and \sw in \Sref{sec:discuss}.
+Our conclusions are given in \Sref{sec:conclude}.
 
@@
 from the survey region. We briefly describe the image presentation here
-for completeness but more information can be found in Paper I. We use
+for completeness but more information can be found in \PaperOne. We use
 the $g$, $r$ and $i$-band imaging from \cfhtls which are most useful for
@@
 analyzing the classifications performed by the citizen scientists (more
-details can be found in Paper I, but see \Sref{sec:swap} for a brief
+details can be found in \PaperOne, but see \Sref{sec:swap} for a brief
 summary). In this section, we describe the framework used for generating the
@@
 (SWAP). The philosophy and the details of SWAP are described in detail
-in Paper I, here we briefly summarize how it works.
+in \PaperOne, here we briefly summarize how it works.
 
@@
 \Aref{appendix:power} for the meaning of this term and how it is
-different from the ``Skill'' defined in paper I} of volunteers is systematically
+different from the ``Skill'' defined in \PaperOne} of volunteers is systematically
 different between the sample of detected and missed lenses.
 
-We check how the posterior probability P (see Paper I for the
+We check how the posterior probability P (see \PaperOne for the
 mathematical definition) of an image or a subject to contain a lens
@@
 details about the design of \sw system and how it works are given in the
-companion paper, Paper I.
+companion paper, \PaperOne.
 
@@
 
-In this paper (Paper II), we present the new \sw sample and compare it
+In this paper, we present the new \sw sample and compare it
 with the previously known samples from two robotic searches from the

### 2015-05-08 doc/sw-cfhtls.tex
Up to limitations of sims section, #203

@@
 \label{sec:data}
+
 \subsection{The CFHT Legacy Survey}
@@
 The \cfhtls imaging is very homogeneous and has good image quality. Most
-of the lensed arcs are much brighter in the $g$ band thus, deep imaging
+of the lensed arcs are much brighter in the $g$ band, so deep imaging
 in this band is desirable. The limiting magnitude is 25.47 for the $g$
@@
 from the final T0007 release taken from the Terapix
-website\footnote{\texttt{http://terapix.iap.fr/cplt/T0007/doc/T0007-doc.pdf}} for this
-work.
+website\footnote{\texttt{http://terapix.iap.fr/cplt/T0007/doc/T0007-doc.pdf}}
+for this work.
 
@@
 In the thesis dissertation of \citet{Thanjavur2009}, 9 promising and 2
-low probability candidates are reported which were discovered
+low probability candidates were reported as having been discovered
 serendipitously. These detections were made during the visual
@@
 
-\citet{Sygnet2010} carried out a search for edge-on galaxy lenses in the
+\citet{Sygnet2010} carried out a search for edge-on disk galaxy lenses in the
 \cfhtls WIDE. They identified galaxies, using {\sc SExtractor}, which
@@
 verified sample of candidates, we choose the most promising 26 systems
-as our bona fide lens sample from the \cfhtls WIDE. The total
-number of lens candidates in the \cfhtls WIDE alone is 108.
+as our bona fide lens sample from the \cfhtls WIDE.
+(The total number of lens candidates in the \cfhtls WIDE alone is 108.)
 
@@
 imaging of the \cfhtls W1 field. The goal was to find instances
-of lensed quasars. Their sample consists of a total of 18 candidates out
-of which 3 candidates are found to be promising.
-
-The \rf \citep{Gavazzi2014} was used for finding compact rings or arcs
+of lensed quasars. Their sample consists of a total of 18 candidates,
+of which 3 candidates were found to be promising.
+
+\citet{Gavazzi2014} used their \rf code to find compact rings or arcs
 around centers of isolated and massive early-type galaxies. \rf
@@
 were visually inspected, having passed the automatic feature selection
-process. This led to a total of 330 lens candidates out of which 42 are
-good quality (\texttt{q\_flag} = 3) and 288 are medium quality
+process. This led to a total of 330 lens candidates out of which 42 were deemed
+good quality (\texttt{q\_flag} = 3) and 288  medium quality
 (\texttt{q\_flag} = 2) candidates. In addition to the main well-defined
 sample of \citet{Gavazzi2014}, a further 71 candidates were reported to
-be detected by earlier version of the \rf or from the \cfhtls DEEP.
+have been detected by earlier versions of the \rf, or from the \cfhtls DEEP.
 From the main sample of ``\rf candidates,'' the SL2S team found, during
@@
 Survey \citep[CARS,][]{Erben2009} which covers an area of 37~deg$^2$
-only and this entire data was also visually inspected by the authors to
-estimate completeness and purity of their robotic search. They found 29
+only, and this entire image set was also visually inspected by the authors to
+estimate the completeness and purity of their robotic search. They found 29
 candidates with the robotic search alone and 41 candidates through pure
-visual inspection some of which are known from previous searches. Most
+visual inspection---some of which were known from previous searches. Most
 of these candidates are medium-low
@@
 The \rf and the \af searches are the only searches that make use of a
-lens finding algorithm and that has been run on the entire \cfhtls
-imaging.  Thus, these are considered as our reference sample of known
+lens finding algorithm and that have been run on the entire \cfhtls
+imaging dataset.  Thus, we considered these to be our reference sample of known
 lenses from robotic searches. For the purposes of transparency and to
@@
 ``known lens candidates'' in the \sw discussion forum,
-TALK\footnote{\texttt{http://talk.spacewarps.org/}}, where volunteers have the
+\Talk,\footnote{\texttt{http://talk.spacewarps.org/}} where volunteers have the
 opportunity to discuss their findings with fellow volunteers and the
@@
 \label{sec:data:impres}
+
 In order to perform a blind lens search over the entire \cfhtls
@@
 from the survey region. We briefly describe the image presentation here
-for completeness but more information can be found in \PaperOne. We use
+for completeness; more information can be found in \PaperOne. We use
 the $g$, $r$ and $i$-band imaging from \cfhtls which are most useful for
@@
 \texttt{http://github.com/drphilmarshall/HumVI}} following the
-prescription of \citet{Lupton2004}. The color scales are chosen to
-maximize the contrast between faint extended objects. These parameters
-are then fixed during the production of all the tiles, in order to allow
+prescription of \citet{Lupton2004}. The color scales were chosen to
+maximize the contrast between faint extended objects and bright early type galaxies.
+These parameters
+were then fixed during the production of all the tiles, in order to allow
 straightforward comparison between one image and another, and for
@@
 
-We extract contiguous cutouts of size 81.84\arcsec\ (440 pixels) including
+We extracted contiguous cutouts of size 82\arcsec\ (440 pixels), including
 overlapping region of 10\arcsec (54 pixels) between the neighbouring
-cutouts. This  results in a catalog of $\sim$ 430 000 cutouts for the entire \cfhtls
-WIDE region. The size of the individual cutout is determined by
+cutouts. This resulted in a catalog of some 430,000 cutouts for the entire \cfhtls
+WIDE region. The size of the individual cutout was determined by
 optimising factors such as the typical angular scales of gravitational
@@
 
-The simulated lenses are important to train citizen scientists who are
-novice to the task of finding lenses but they are also crucial for
+The simulated lenses are important to train citizen scientists who may be
+new to the task of finding lenses, but they are also crucial for
 analyzing the classifications performed by the citizen scientists (more
-details can be found in \PaperOne, but see \Sref{sec:swap} for a brief
+details can be found in \PaperOne, but see \Sref{sec:swap} below for a brief
 summary). In this section, we describe the framework used for generating the
 simulated lens sample and give details of the sample itself along with
-some known limitations.
+some of its known limitations.
 
@@
 of the centers of some of the lens candidates, some simulated lensed
-images were superposed on the galaxies of known lens candidates. This issue was overcome by
-ingesting the same \cfhtls images with and without the simulated
+images were superposed on the galaxies of known lens candidates. This issue was
+overcome by ingesting the same \cfhtls images with and without the simulated
 lenses.}}}.
@@
 calculate the expected number of sources behind a candidate lensing
-galaxy using Eq.~\ref{eqn:nsrc}. We need to generate a large number of
+galaxy using \Eref{eqn:nsrc}. We need to generate a large number of
 simulated lenses (larger than the number of real galaxy lenses we expect
@@
 artificially boost the average number of sources by a factor (see
-Table~\ref{tab:thresh}), which increases the occurrence of lensing. We
+\Tref{tab:thresh}), which increases the occurrence of lensing. We
 draw a Poisson deviate, $N_{\rm src}$ with a mean equal to the boosted
@@
 
-Next, we determine properties of the background sources for every lens.
+Next, we determine properties of the background sources for every lens system.
 We follow similar procedures for both background galaxies and quasars.
@@
 affect the lens cross-sections to some extent. As this factor is not
-critical for the purpose of our training sample, we assume the
-background galaxies to be point like for simplicity.} We perform
-ray-tracing for all of the $N_{\rm src}$ sources using the publicly
+critical for the purpose of our training sample, for simplicity we assume the
+background galaxies to be point like when computing cross-sections.} We perform
+ray-tracing for all of the $N_{\rm src}$ sources using the publically
 available code \gravlens \citep{Keeton2000} and choose sources that
-satisfy our selection criteria given below. We determine fluxes of the
-lensed images and the total magnification of each of the lensed source.
+satisfy our selection criteria given below. We determine the fluxes of the
+lensed images and the total magnification of each of the lensed sources.
 We draw a source randomly for which the flux of the second brightest
 lensed image and the total magnification of all lensed images meet the
-thresholds given in Table~\ref{tab:thresh}.
+thresholds given in \Tref{tab:thresh}.
 
@@
 the galaxies. The ellipticity and the position angle (PA) are drawn
-randomly from within the range given in Table~\ref{tab:thresh}. The
+randomly from within the range given in \Tref{tab:thresh}. The
 effective radius of the galaxy is estimated from the luminosity$-$size
@@
 
-\subsubsection{Groups-scale lenses}
+\subsubsection{Group-scale lenses}
 
@@
 as described in \Sref{sect:gallens}, we calculate the number of galaxies
-expected to lie behind every potential lensing group (see Eq.~\ref{eqn:nsrc}).
+expected to lie behind every potential lensing group (see \Eref{eqn:nsrc}).
 As before, for each background galaxy within the lens cross-section, a redshift
 and an $i$-band magnitude is determined by drawing galaxies randomly from the
-respective distributions (see Eqs.~\ref{eqn:ps}-\ref{eqn:ns}).
+respective distributions (see Equations~\ref{eqn:ps}-\ref{eqn:ns}).
 
@@
 been provided. These catalogs are available from
-\texttt{https://github.com/anupreeta27/SIMCT} and simulated lens sample can be
-requested from the authors.
+\texttt{https://github.com/anupreeta27/SIMCT} and the
+simulated lens image sample is available from the authors on request.
 
@@
 
-\subsection{Limitations of the simulated sample}
+\subsection{Limitations of the simulated lens sample}
+
 The simulated lens sample, although realistic, is not perfect, due to

### 2015-05-08 doc/sw-system.tex
Starting to edit paper 1 before submission

--- 2015-05-07 doc/sw-system.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% AV edits
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Carefully produced colour composite images are displayed to volunteers via a
-web-based classification interface, which records their estimates of the positions of
+classification interface which records their estimates of the positions of
 candidate lensed features. Simulated lenses, and expert-classified images which
@@
 training set is used to give the volunteers feedback on their performance, as
-well as to calibrate a model of the system that provides
-dynamical updates to the probability of containing a lens
-of every image they classify. Low probability systems are
+well as to calibrate it in order to allow dynamical updates to the probability
+of any image they classify to contain a lens. Low probability systems are
 retired from the site periodically, concentrating the sample towards a set of
 candidates. Having divided 160 square degrees of Canada-France-Hawaii Telescope
-Legacy Survey (\cfhtls) imaging into some 430,000 overlapping 82 by 82 arcsecond
+Legacy Survey (\cfhtls) imaging into some 430,000 overlapping 84 by 84 arcsecond
 tiles and displaying them on the site, we were joined by around 37,000
@@
 \citep[e.g.][]{CabanacEtal2007,MoreEtal2012}. Detecting galaxy-scale lenses
-from the ground is difficult, but feasible albeit with lower efficiency and requiring
+from the ground is hard, but feasible albeit with lower efficiency and requiring
 HST or spectroscopic follow-up to confirm the candidates as lenses
@@
 
-How can we scale these lens searches up to imaging surveys that cover a hundred
+How can we scale these lens searches up to imaging surveys covering a hundred
 times the sky area, such as the almost-all sky surveys planned with LSST and
@@
 requiring the same  team of 10 inspectors to work full time for 20 weeks (to
-provide 3 classifications  per lens between them). Neither of these may be the
+provide 3 classifications  per lens between them) Neither of these may be the
 most cost-effective or reliable strategy. Alternatively, a team of $10^6$
@@
 via its flexible inspection interface and discussion forum
-\citep{LintottEtal2009}. Indeed, several of us (AV,CC,CM,EB,PM,LW) were
+\citep{LintottEtal2009}. Indeed, several of us (AV,CC,CM,EB,PM,TJ,LW) were
 active in an informal \GZ gravitational lens search (Verma et al, in
@@
 address the visual inspection problem in gravitational lens detection for future
-large surveys by ``crowd-sourcing'' it to a community of citizen scientists.
-Implemented as a Zooniverse \citep{SimpsonEtal2014}
+large surveys via crowd-sourcing. Implemented as a Zooniverse \citep{SimpsonEtal2014} citizen science
 project, it is designed to provide a {\it gravitational lens discovery service}
 to survey teams looking for lenses in wide field imaging data. In a companion
-paper \citep[][hereafter \PaperTwo]{MoreEtal2015} we will present the new
+paper (More et al, in preparation, herafter \PaperTwo) we will present the new
 gravitational lenses discovered in our first lens search, and
@@
 \item How quickly can lenses be detected, and non-lenses be rejected?
-How many classifications, and so how many volunteers, are needed per target?
+How many classifications, and so how many volunteers are needed per target?
 
@@
 two-stage candidate selection strategy. We then briefly introduce, in
-\Sref{sec:data}, the particular dataset used in our first test
+\Sref{sec:data}, the particular dataset used in the first experimental tests
 of the \SW system, and how we prepared the images prior to displaying them in
@@
 not) and 4) analyze that classification along with all others to produce a
-final candidate list. We describe step~1 in \Sref{sec:data}, and step~4 in
-\Sref{sec:swap}. In this section we take a volunteer's eye view, and begin by
+final candidate list. We describe step 1 in \Sref{sec:data} and step 4 in
+\Sref{sec:swap}. In this section we take a volunteer's eye view and begin by
 describing the \SW classification interface, the crowd of volunteers, and the
@@
 \centering\includegraphics[width=0.9\linewidth]{sw-screengrab-marker+feedback.pdf}
-\caption{Screenshot of the \SW classification interface at
-  \texttt{http://spacewarps.org}.}
+\caption{Screenshot of the \SW classification interface.}
 \label{fig:screenshot}
@@
 team.\footnote{The \SW web application code is open source and can be accessed
-from \texttt{https://github.com/zooniverse/Lens-Zoo}.  The project was renamed
-during development to avoid the question of  who ``Len'' is.} The focus of the
-CI is a large display of a pre-prepared PNG image of the ``subject'' being
-inspected. When the image is clicked on by the volunteer, a marker symbol
-appears at that position.  Several markers can be placed, and they can be
-removed by the user if they change their mind.
+from \texttt{https://github.com/zooniverse/Lens-Zoo}. The project was renamed during development.}
+The focus of the CI is a
+large display of a pre-prepared PNG image of the ``subject'' being inspected.
+When the image is clicked on by the volunteer, a marker symbol appears where the
+pointer was. Several markers can be placed, and they can be removed by the user if, for example, they change their mind.
 
@@
 After each classification, the positions of the markers are written out to the
-classification database, in an entry that also stores metadata including the ID
-of the subject, the username of the volunteer  (or IP address if thy are not
-logged in), and a timestamp.
-
-For the more interesting subjects, the CI offers two features that enable their
-further investigation. The first is the ``Quick Dashboard''
-(QD), a more advanced image viewer. This allows the viewer to compare three
+classification database, in an entry that also stores the ID of the subject, the
+username (or IP address if the user is not logged in) of the volunteer, a timestamp and some other metadata.
+
+For the more interesting subjects, the CI offers two features that  enable
+further investigation of the subjects. The first is the ``Quick Dashboard''
+(QD) a more advanced image viewer. This allows the viewer to compare three
 different contrast and colour balance settings, to help bring out subtle
@@
 in the main CI image viewer. The second is a link to that subject's page in
-the project discussion forum (known as
-``\Talk\footnote{\texttt{http://talk.spacewarps.org}}'').
-Here, volunteers can discuss the features they have seen either
+the project discussion forum, \texttt{http://talk.spacewarps.org} (known as
+``Talk''). Here, volunteers can discuss the features they have seen either
 before they submit their classification, or after, if they ``favourite'' the
@@
 about any given subject before submitting your own classification means that
-the classifications may not be strictly independent; however, the advantage of this
+the classifications may not be strictly independent; the advantage of this
 system is that volunteers can learn from others what constitutes a good lens
@@
 The FITS images of the subject can be further explored with Zooniverse
-``Dashboard Tools,'' which include a
-more powerful image viewer that enables dynamic
+``Dashboard Tools,'' using a more powerful image viewer that enables dynamic
 variation of the colour balance and contrast (stretch), and for any given view
@@
 
-Gravitational lenses are typically unfamiliar objects to the general public.
+Gravitational lenses are largely unfamiliar objects to the general public.
 New volunteers need to learn what lenses look like as quickly as possible, so
@@
 that they will receive instant feedback about their performance after
-classifying (blindly) any of these training subjects. Indeed, after a volunteer
-finishes marking a training subject, a pop-up
+classifying (blind) any of these training subjects. Indeed, after a volunteer
+finishes marking a training subject and hits ``Finished marking,'' a pop-up
 message is generated, containing either congratulations for a successful
@@
 in \Fref{fig:screenshot}) or feedback for an unsuccessful one (for
-example, ``There is no gravitational lens in this field!''). A successful
-classification of a simulated lens requires a marker to be placed fairly
-precisely on the lensed features, so as to avoid misinforming the classifier.
-The pixels in the lensed features are flagged via a mask contained in the
-PNG image transparency ``alpha'' channel. (The mask is not visible in the image.)
+example, ``There is no gravitational lens in this field!'').
 
@@
 
-We began by selecting massive galaxies and groups in the \cfhtls catalogs,
-by colour, brightness and photometric redshift. We then assigned plausible mass
+We start by selecting massive galaxies and groups in the \cfhtls catalogs,
+by colour, brightness and photometric redshift. We then assign plausible mass
 distributions to these ``potential lenses:'' a singular isothermal ellipsoid
 model for each massive galaxy, and an additional NFW profile dark matter halo
-for groups and clusters. The mass distributions were centred, elongated and
+for groups and clusters. The mass distributions are centred, elongated and
 aligned with the measured optical properties of the galaxies present. We then
-drew a source from a plausible background population, of either galaxies (for
+draw a source from a plausible background population, of either galaxies (for
 the group or galaxy lenses) or quasars (for the galaxy-scale lenses). The
-source redshift, luminosity and size distributions were all chosen to match
-those observed, while the source abundance was artificially increased such that
-each potential lens had a high probability of having a source occur at a
-position that will lead to it being highly magnified. Source galaxies were
-given plausible surface brightness profiles and ellipticities. We then computed
+source redshift, luminosity and size distributions are all chosen to match
+those observed, while the source abundance is artificially increased such that
+each potential lens has a high probability of having a source occur at a
+position that will lead to it being  highly magnified. Source galaxies are
+given plausible surface brightness profiles and ellipticities. We then compute
 the predicted multiple images of the source using the \gravlens ray-tracing
@@
 
-At this point, we applied several cuts to the simulated lens pool, in order to
-reject sims that were likely to be difficult to spot. While this ensured that
-the educational value of the sims when feedback was given, it means that we
-should not necessarily expect to detect real lens candidates that would not pass
-these cuts (although human classifiers do possess the key advantage of  being
-able to go beyond their training\footnote{Any real lens candidates we find with
-properties outside the ranges of the training set will be of particular
-interest, being a product of the {\it imagination} of the crowd in extrapolating
-their understanding of gravitational lenses into a regime that they have not
-been trained for.  \citet{GeachEtal2015}, for example, report the discovery of a
-red lensed arc  by volunteers who had only been trained primarily on blue
-examples. We investigate this aspect of the \SW approach in \PaperTwo.}).
-In the present project, the most important selection cuts we made were to only
-keep sims with a) second brightest image brighter that $i = 23$ and b) total
-combined image magnitude fainter than 19--20 (\PaperTwo, Table~1). The
-combination of these two cuts resulted in a sample of visible lensed image
-configurations.
-
-Volunteers were initially shown training images at
-a mean frequency of two in five. Subjects were drawn at random from a pool
+At this point, the distribution of lens and source properties are quite
+realistic. We then chose to make cuts of the simulated lens pool, in order to
+reject sims that were likely to be difficult to spot. While this ensured the
+educational value of the sims when feedback was given, it meant that we should
+only expect to detect real lens candidates that also pass these cuts.
+Indeed, for traditional machine learning or computer vision implementations then this would be a constraint, but human classifiers are capable of going beyond their training; Geach et al., for example (REF????) report the discovery of a red lens by volunteers who had only been trained on blue examples.
+This ability to go beyond training is a key advantage of human classifiers, and
+any real
+lens candidates we find with properties outside the ranges of the sims, may in
+this sense be considered bonuses, a product of the {\it imagination} of the
+crowd in extrapolating their understanding of gravitational lenses into a regime
+that they have not been trained for. In the \cfhtls project, the most important
+selection cuts were to only keep sims with a) second brightest image brighter
+that $i = 23$ and b) total combined image magnitude fainter than 19--20
+(\PaperTwo, Table~1). The combination of these two cuts results in a sample of
+visible lensed image configurations.
+
+When a volunteer begins classifying, they are initially shown training images at
+a mean frequency of two in five. Subjects are drawn at random from a pool
 consisting of (at first) 20\% sims, 20\% duds, and 60\% test images,
 and such that no volunteer ever
-saw a given image more than once. As the number of classifications made by the
-volunteer increased, the training frequency was decreased from 40\% to
+sees a given image more than once. As the number of classifications made by the
+volunteer increases, the training frequency is decreased from 40\% to
 $2/(5\times2^{(\textrm{int}(N_c/20)+1)/2})$ ($\approx 30\%$ for the second 20
@@
 
-This training regime meant that in the first 60 images viewed, each volunteer
-was shown (on average) 9 simulated gravitational lenses (as well as 9
-pre-selected empty ``dud'' fields). This is a much higher rate than the natural
-one: to try and avoid this leading to over-optimism among the inspectors (and a
-resulting high false positive rate), we displayed the current ``Simulation
-Frequency'' on the classification interface (``1 in 5'' in
-\Fref{fig:screenshot}) and maintained the consistent theme in the feedback
-messages that lenses are rare.
+This training regime means that in the first 60 images viewed, each volunteer
+is shown (on average) 9 simulated gravitational lenses, and 9 empty fields.
+This is a much higher rate than the natural one: to try and avoid this leading
+to over-optimism among the inspectors (and a resulting high false positive
+rate), we display the current ``Simulation Frequency'' on the classification
+interface (``1 in 5'' in \Fref{fig:screenshot}) and maintain the consistent
+theme in the feedback messages that lenses are rare.
 
 In Figures~\ref{fig:training-gallery:sims}~and~\ref{fig:training-gallery:duds}
-we show example training images from this first \SW project (\Sref{sec:data}
+we show example training images from the first \SW project (\Sref{sec:data}
 below).
@@
 ``dud'' training images (previous section). For easy reference, the lenses are
-divided by type (for example, ``Lensed Galaxies,'' ``Lensed Quasars'' and
-``Cluster Lenses''), as are the false positives (for example, ``Rings and
+divided by type (for example, ``lensed galaxies,'' ``lensed quasars'' and
+``cluster lenses''), as are the false positives (for example, ``Rings and
 Spirals,'' ``Mergers,'' ``Artifacts'' and so on). The example images are
@@
 
-Most of the text of the Spotter's Guide focuses on the kinds of features that
-gravitational lenses do or don't produce. To complement this,
-the website ``Science'' section contains a very brief introduction to how
+Most of the text of the Spotter's Guide focuses on what kinds of image features
+gravitational lenses do or don't produce;
+the website ``Science page'' contains a very brief introduction to how
 gravitational lensing works, which is fleshed out a little on the ``FAQ'' page.
-The FAQ also contains answers to questions about the interface
+The FAQ also contains answers to frequently asked questions about the interface
 and the task set.
@@
 
-We now describe briefly the two-stage strategy that we employed in this first
+We now describe briefly the two-stage strategy that was employed in the \cfhtls
 project: initial classification (involving the rejection of very large numbers
@@
 
-The goal of the \StageOne classification was to achieve a high rejection rate,
+The goal of a \StageOne classification is to achieve a high rejection rate,
 while maintaining high completeness.  In this mode, therefore, the pre-loading
@@
 quickly for the search to be completed within a reasonable time period.  We
-expect some trade-off between speed and accuracy: we return to this topic in the
+expect some trade-off between speed and accuracy, which we return to in the
 results section below. Completion of the search requires subjects to be
@@
 candidates in \StageOne is truly a community effort: to detect a lens candidate,
-many non-lenses must first be rejected, and several classifications by
-different inspectors are needed in either case.
+many non-lenses must first be rejected, and several classifications by different inspectors are needed in either case.
 
 The \StageOne training set was chosen to be quite clear cut, in order to err on
-the side of high completeness. When defining the
-training duds, we discarded anything that could be considered a lens candidate
-(see \Sref{sec:design:training:guide}). This meant that objects that look
+the side of inclusivity, and so ensure high completeness. When defining the
+training duds we discarded anything that could be considered a lens candidate
+(see \Sref{sec:design:training:guide}): this meant that objects that look
 similar to lenses, such as galaxy mergers, tidal tails and spiral arms, pairs of
@@
 therefore we expect some of those types of object to appear in the \StageOne
-candidate list. As described above, the training sims for \StageOne were also
-selected to be relatively straightforward to spot.
+candidate list. The training sims for \StageOne were also selected to be
+relatively straightforward to spot, as we sought a balance between sensitivity
+to faint or difficult lenses, and the need to educate the volunteers in what
+gravitational lenses look like. We return to this balance below.
 
@@
 
-The design of a \StageOne classification task, and its training set, should
-lead to a sample of lens candidates that has high completeness but may have low
+The design of the \StageOne classification task, and its training set, should
+lead to sample of lens candidates that has high completeness but may have low
 purity. To refine this sample to higher purity, we need to reject more
@@
 and~\ref{fig:training-gallery:duds} show some example images from the resulting
-\StageTwo training set.
+\cfhtls \StageTwo training set.
 
@@
 \begin{minipage}[b]{0.24\linewidth}
-\centering\includegraphics[width=\linewidth]{4.pdf}
+\centering\epsfig{file=4.png,width=\linewidth,angle=0,clip=}
 \end{minipage} \hfill
 \begin{minipage}[b]{0.24\linewidth}
-\centering\includegraphics[width=\linewidth]{5.pdf}
+\centering\epsfig{file=5.png,width=\linewidth,angle=0,clip=}
 \end{minipage} \hfill
 \begin{minipage}[b]{0.24\linewidth}
-\centering\includegraphics[width=\linewidth]{6.pdf}
+\centering\epsfig{file=6.png,width=\linewidth,angle=0,clip=}
 \end{minipage} \hfill
 \begin{minipage}[b]{0.24\linewidth}
-\centering\includegraphics[width=\linewidth]{7.pdf}
+\centering\epsfig{file=7.png,width=\linewidth,angle=0,clip=}
 \end{minipage} \hfill
-\caption{Typical \SW ``sims'' from the \StageTwo training set.
-The top right-hand corner insets indicate the
+\caption{Typical \SW ``sims'' from the \StageTwo training set. The top right-hand corner insets indicate the
 location of the simulated lens in each of these training images. Users needed to
@@
 \begin{minipage}[b]{0.24\linewidth}
-\centering\includegraphics[width=\linewidth]{0.pdf}
+\centering\epsfig{file=0_ASW0009dgn.png,width=\linewidth,angle=0,clip=}
 \end{minipage} \hfill
 \begin{minipage}[b]{0.24\linewidth}
-\centering\includegraphics[width=\linewidth]{1.pdf}
+\centering\epsfig{file=1_ASW0009dgo.png,width=\linewidth,angle=0,clip=}
 \end{minipage} \hfill
 \begin{minipage}[b]{0.24\linewidth}
-\centering\includegraphics[width=\linewidth]{2.pdf}
+\centering\epsfig{file=2_ASW0009dgy.png,width=\linewidth,angle=0,clip=}
 \end{minipage} \hfill
 \begin{minipage}[b]{0.24\linewidth}
-\centering\includegraphics[width=\linewidth]{3.pdf}
+\centering\epsfig{file=3_ASW0009dh0.png,width=\linewidth,angle=0,clip=}
 \end{minipage} \hfill
@@
 expected from several next-generation sky surveys, such as DES, KiDS, HSC and
-LSST. We use the stacked images
-from the final T0007 release taken from the Terapix
-website\footnote{\texttt{http://terapix.iap.fr/cplt/T0007/doc/T0007-doc.pdf}} for this
-work.
+LSST.
 
@@
 \cfhtls pointings into some 430,000 equal size, overlapping tiles, approximately
-82~arcsec on a side. We refer to these images as ``test images.'' The ``training
+84~arcsec on a side. We refer to these images as ``test images.'' The ``training
 images'' were derived from a small subset of these, as  discussed above. In
@@
 the pixel values of each image, in the notation of \citeauthor{LuptonEtal2004},
-into flux units (``picomaggies''), via the image AB zeropoint $m_0$ and the
+into flux units (``picomaggies,''), via the image AB zeropoint $m_0$ and the
 pixel value calibration factor $f$  given by $\log_{10}{f} = 0.4(30.0 - m_0)$.
@@
 the detectability of these faint features.   Examples of \cfhtls training set
-images prepared in this way can be seen in Figures~\ref{fig:training-gallery:sims}
-and~\ref{fig:training-gallery:duds}. We also defined two alternative sets of
+images prepared in this way can be seen in the galleries of the previous
+section (Figures~\ref{fig:training-gallery:sims}
+and~\ref{fig:training-gallery:duds}). We also defined two alternative sets of
 visualization parameters, to display a ``bluer'' image and a ``brighter''
@@
 Each classification made is logged in a database, storing subject IDs,
-volunteer IDs, a timestamp and the classification results (the image
+(anonymous) volunteer IDs, a timestamp and the classification results (the image
 pixel-coordinate positions of every marker placed).  The ``category'' of subject --
@@
 (solid blue curve), while the offline analysis was chosen for the final
-\StageTwo results (dot-dashed orange curve).
-Lens probability varies along the curves: the stars indicate the point where
-the value of this quantity is 0.95.}
+\StageTwo results (dot-dashed orange curve). }
 \label{fig:results:sample:roc}
@@
 Finally, there could be some performance gains to be made by improving the SWAP
-agent model, or its implementation.
-
-Low skill is typically a result  of inexperience (\Sref{sec:results:crowd}) --
-but it could be the agent  that is inexperienced, as much  the classifier.  In a
-future paper we plan to investigate the use of the test images as well as the
-training images in accelerating the agent's learning (Davis et al, in
-preparation). We also plan to investigate the use of offline analysis at
-\StageOne, partly for the same reason (see also \Sref{sec:discuss:efficiency}
-below.) Given the above findings  about the effects of noise in the SWAP system,
-we are also motivated to explore further the possible noise-reducing effects of
-the doing the analysis offline (\Sref{sec:results:sample}).
+agent model, or its implementation. Low skill is typically a result  of
+inexperience (\Sref{sec:results:crowd}), but it could be the agent that is
+inexperienced as well as the classifier or its agent. In a future paper we plan
+to investigate the use of the test images as well as the training images in
+accelerating the agent's learning (Davis et al, in preparation). We also plan to
+investigate the use of offline analysis at \StageOne, partly for the same reason
+(see also \Sref{sec:discuss:efficiency} below.) Given the above findings  about
+the effects of noise in the SWAP system, we are also motivated to explore
+further the possible noise-reducing effects of the doing the analysis offline
+(\Sref{sec:results:sample}).
 
@@
 respectively. In \StageOne, this inefficiency is due to the daily processing: we
-were not able to retire subjects fast enough, and so they remained in the
+were not able to retire subjects fast enough, and so they, remained in the
 system, being over-classified. Indeed, only 3705745 classifications were
@@
 measure of the effective crowd size, in the sense that a crowd of perfect
-classifiers would be of this size. By this measure, the \StageOne crowd was
+classifiers would be of this size. By this measure,the \StageOne crowd was
 equivalent to a team of 1470 perfect classifiers, while the \StageTwo crowd was
@@
 \item The optimal true positive rate (completeness) and false positive rate in
-the training set were estimated to be around $91-93\%$ and $<1\%$ (Stages 1 and
+the training set were estimated to be around $91--93\%$ and $<1\%$ (Stages 1 and
 2). This FPR translates to an approximate purity of 30\%. We find a
@@
 \bibliographystyle{apj}
-\bibliography{references_system}
+\bibliography{references}
 

### 2015-05-09 doc/sw-cfhtls.tex
author corrections #203
incorporated AV's edits and Phil's correct until Section 3.3  (corresp. 211fe65)

@@
 many lensed images appear similar to features found commonly in galaxies
-(such as spiral arms) or to artifacts in astronomical images (scattered
+(such as spiral arms) or to artefacts in astronomical images (scattered
 light around stars).  Almost all lens finding algorithms find it
@@
 prescription of \citet{Lupton2004}. The color scales were chosen to
-maximize the contrast between faint extended objects and bright early type galaxies.
-These parameters
+maximize the contrast between faint extended objects. These parameters
 were then fixed during the production of all the tiles, in order to allow
@@
 candidate happens to be too close to the edge of a cutout, then the overlap
-between neighbouring cutout allows a volunteer to get a clearer view
+between neighbouring cutouts allows a volunteer to get a clearer view
 of the same candidate in at least one of the cutouts. We note that since
@@
 of the centers of some of the lens candidates, some simulated lensed
-images were superposed on the galaxies of known lens candidates. This issue was
-overcome by ingesting the same \cfhtls images with and without the simulated
-lenses.}}}.
+images were superposed on the galaxies of known lens candidates. This issue was overcome by
+presenting the same \cfhtls images with and without the simulated
+lenses to the volunteers.}}}.
 
@@
 
-The luminosify functions of the background galaxies and quasars are
+The luminosity functions of the background galaxies and quasars are
 determined as follows. We use the results of \citet{Faure2009} to specify the luminosity
@@
 drawn to simulate quasar lenses. Next, we assumed a Gaussian
-profile\footnote{This was due to an oversight. We intend to use either
-an exponential or {\bf de Vaucouleurs'} profile.} for
-the galaxies. The ellipticity and the position angle (PA) are drawn
+profile\footnote{This was due to an oversight. We intended to use either
+an exponential or {\bf de Vaucouleurs'} profile that will be adopted for
+future implementations of SIMCT.} for the galaxies. The ellipticity and
+the position angle (PA) are drawn
 randomly from within the range given in \Tref{tab:thresh}. The
@@
 follow the same procedure and apply thresholds to determine properties
-of the lensed galaxies for every lens as are described for galaxy-galaxy lenses
+of the lensed galaxies for every lens as described for galaxy-galaxy lenses
 in the previous section. The thresholds are same as those used for
@@
 Here, we describe some of the cases or aspects in which the simulations
-were known to have failed to look realistic. The fraction of such
+were known to be unrealistic. The fraction of such unrealistic simulations in the 
 simulated sample is small (roughly 5 percent)\footnote{This estimate is
-based on the number of \#simfail tags from TALK, the discussion forum.}.
+based on the number of \#simfail tags from \Talk, the discussion forum.}.
 
@@
 higher redshifts or which are fainter have poor photometric redshift
-measurements. Consequently these galaxies are assigned  wrong
+measurements. Consequently, these galaxies are assigned wrong
 luminosity and velocity dispersion estimates. This then results in
@@
 the lensed images for some of the failed simulations have larger image
-separation than what you expect from the luminosity and/or size of the
-galaxy. We roughly expect mass to follow light so more massive galaxy
-typically looks brighter and/or bigger.
-
-At group-scales, the photometric and redshift estimates are used when define
+separation than what one would expect from the luminosity and/or size of the
+galaxy. We roughly expect mass to follow light, so more massive galaxies
+typically look brighter and/or bigger.
+
+At group-scales, the photometric and redshift estimates are used when defining
 the group membership. Therefore, errors in redshift estimates generate galaxy
@@
 and confirmed to contain no lenses. False positives (FPs) are systems
-which look like lenses but are not, for example, spiral galaxies,
-starforming galaxies, chance alignments of features arranged in a
+which have features similar to lenses but they are not lenses in reality, for example, spiral galaxies,
+star$-$forming galaxies, chance alignments of features arranged in a
 lensing configuration and stars.
@@
 We selected a sample of 450 duds for the \StageOne classification in \sw
-and a sample of 500 false positives for the \StageTwo inspection. The
+and a sample of 500 false positives for the \StageTwo\footnote{Please see \Sref{sec:swap} and Paper 1 for a description of \StageOne and \StageTwo} inspection. The
 sample of false positives was selected from the candidates which passed
@@
 certainly lenses according to all of the inspectors. To avoid
-duplication, further information on \sw candidates that were previously
-identified in the literature will be made available at
-\texttt{http://spacewarps.org/\#/projects/CFHTLS/} whereas the sample of new lens
-candidates with G$\ge 1.3$ (medium-high probability) is presented in
-this paper (see \Sref{sec:results:newcand}).
+duplication, only the newly discovered lens
+candidates with G$\ge 1.3$ (medium-high probability) are presented in
+this paper (see \Sref{sec:results:newcand}), and further information on \sw-selected candidates that were previously
+identified in the literature (see \Sref{sec:data:kls}) will be made available at
+\texttt{http://spacewarps.org/\#/projects/CFHTLS/}.
 
@@
 Note: For KC and KL, Percentages are with respect to the known
-population whereas for NC and AC, percentages are with respect to the
-total population of lens candidates. \\
+population (i.e. 438 KC and 59 KL see \Sref{sec:data:kls}) whereas for
+NC and AC, percentages are with respect to the total sample of 429 lens
+candidates.
+\\
 \end{table}
@@
 We give basic information about the final sample of {\bf 59} new lens
-candidates (medium-high probability) found by \sw in
+candidates (ranked with medium-high probability) found by \sw in
 Table~\ref{tab:swcands}. We report the candidates with a \sw ID and Name
@@
 averaged grade G from the lens experts, zoo ID (identifier used in
-TALK), P value at \StageTwo and a visual categorization of the type of
+\Talk), P value at \StageTwo and a visual categorization of the type of
 lensed images and the lensing galaxy in the ``Comments'' column in
@@
 exotic lens candidates from the visually inspected P$>0.3$ sample. There
-may be some interesting candidates lurking in TALK but these will have
-to be sifted through.
+may be some more interesting candidates that were missed either at
+\StageOne or \StageTwo but have been identified by volunteers in \Talk.
+This resource is yet to be mined and is left for future work.
 
@@
 into smaller arclets which then falls below the minimum length or area
-allowed for an arc to be detected typically. Human brains have no
+allowed for an arc to be typically detected. Human brains have no
 problem in interpolating over the broken blue arc over the red galaxy
 and understand that it is a single long arc. The system {\bf SW20} has
-point-like lensed images which cannot be detected by arc finding
+point-like lensed images which cannot be detected by arc-finding
 algorithm whereas the ring finding algorithm may miss this because of
@@
 subtracted \citep[for details, see][]{Gavazzi2014}. Here, we use the flux
-of the lensed images measured by {\sc sextractor} from the scaled
+of the lensed images measured by {\sc SExtractor} from the scaled
 difference image, that is, $g-\alpha i$ and convert it to the $g$ band
@@
 the \af and the \sw sample, we integrate the flux in the image pixels
-identified by \af or {\sc sextractor}.
+identified by \af or {\sc SExtractor}.
 
@@
 these angular image separations. For the \rf sample, we use the peak
-position of the lensed images measured by running {\sc sextractor} on
+position of the lensed images measured by running {\sc SExtractor} on
 the scaled difference image. We calculate the image separation from the
@@
 sample, the same definition is used where the peak positions are
-identified either with \af or {\sc sextractor}.
+identified either with \af or {\sc SExtractor}.
 
@@
 we show that $\sim$~25$-$30~per~cent of the known lens candidates and
-$\sim$~60~per~cent of the known lenses are found at \StageOne and \StageTwo in
-\sw. The left and the middle panels of \Fref{fig:compre} show the
+$\sim$~60~per~cent of the known lenses are found at \StageOne. Eighty-four
+percent of the known lens candidates and \textbf{all} of the known lenses 
+from \StageOne passed our \StageTwo selection criterion of $P>0.3$. 
+The left and the middle panels of \Fref{fig:compre} show the
 fraction of detections as a function of arc magnitude and the Einstein
@@
 the new \sw lens sample (magenta). It is interesting to note that both
-these samples have very similar profiles and thus, the profile of the
-combined sample has not changed signficantly. This implies that previous
+the \rf$+$\af and \sw samples have very similar profiles and thus, the profile of the
+combined sample has not changed significantly. This implies that previous
 constraints on the image separation distribution are robust and the \af
@@
 robotically found lens candidates in terms of the flux of the lensed
-images or the redshift of the lensing galaxies.
+images and the redshift of the lensing galaxies.
 
 Since \sw is visual based search, it is difficult to detect many lens
-candidates with small $R_{\rm E}$ in the presence of a bright lensing
+candidates with a small $R_{\rm E}$ in the presence of a bright lensing
 galaxy. While this is true for algorithms too, the \rf team adopted a
@@
 galaxy-scale lenses which have small $R_{\rm E}$. The \rf sample is
-generated by working with lensing galaxy $-$subtracted images and this
+generated by working with lensing galaxy$-$subtracted images and this
 led to increased detections of small image separation candidates. The
@@
 E}>2\arcsec$. There is a good overlap between the two samples given that
-most of these are candidates and could turn out be not lenses. We again
+most of these are candidates and could turn out not to be lenses. We again
 caution the readers that the uncertainties on the measurements are not
@@
 function of the arc magnitudes, all three samples have detections at all
-magnitudes and median magnitudes for all samples is around 24.5.
+magnitudes and median magnitudes for all samples is around $g\sim$24.5.
 Relatively, the \rf sample spans a narrower range compared to the \sw
@@
 \sw (known candidates$-$blue circles and new candidates only$-$blue dots)
-and \af (red dots). Alls samples have broadly similar properties.}
+and \af (red dots). All samples have broadly similar properties.}
 \end{center}
@@
 galaxies and some are edge on galaxies which could be the reason for
-excluding these galaxies from the inital catalog.
+excluding these galaxies from the initial catalog.
 
@@
 kinds of lenses.  We find that about 40~per~cent of the known sample of lenses
-are missed both at \StageOne and II (see \Tref{tab:stats}). In fact, most
+are missed both at \StageOne and II (see \Tref{tab:stats}). In fact, all
 of the known lenses from \StageOne are discovered at \StageTwo which
@@
 four types of volunteers making classifications - those causing positive
-large kicks (correct classifications by high power volunteers, those
+large kicks (correct classifications by high power volunteers), those
 causing positive small kicks (correct classifications by low power
@@
 previous}) < \Delta$log(P)$_{\rm cut}$ (chosen as 1.2) and is large
-if greather than $\Delta$log(P)$_{\rm cut}$.
+if greater than $\Delta$log(P)$_{\rm cut}$.
 
@@
 completeness. After testing on a subsample of both \StageOne and
-\StageOne FPs, we find that a small fraction of FPs are rejected when
+\StageTwo FPs, we find that a small fraction of FPs are rejected when
 only classifications with $\Delta$ log(P)$>1.2$ only are considered.
@@
 \multicolumn{11}{p{18cm}}{
-{\bf The redshift with $^s$ are spectroscopic estimates taken from SDDS Data
+{\bf The redshifts with $^s$ are spectroscopic estimates taken from SDDS Data
 Release 12 whenever available unambiguously.} The column Comments has two
@@
 
-The bottom panels show the missed or rejected lenses. The green (and red)
+The {\bf bottom-left panels of \Fref{fig:detmis} show the} missed or rejected lenses. The green (and red) 
 trajectories show visually easier (and more difficult) to identify
@@
 are typical of this sample in terms of Nclass and the dominance of short
-negative kicks. The panel f represents a small fraction of this sample
+negative kicks. Panel f represents a small fraction of this sample
 where the kicks are only short and negative. The panel g shows how some
@@
 
-The top panels show the detected lenses. The cases shown with green trajectories
-in each panel can be thought of counterparts of the trajectories of the missed
-lenses in the corresponding bottom panels except that the type of volunteers are
-different. Most detected lenses are similar to the case in panel a which are
-detected within a few classifications but coming from large positive kicks.
-Panel b represents a few odd cases which are dominated mainly by short positive
-kicks. Panel c shows a lens getting more classifications because of the tug
-between positive and negative kicks whereas the panel d represents the extreme
-cases when the images are on the verge of being rejected but are saved thanks
-to a series of large positive kicks. The red trajectories are some more
-examples of randomly selected cases which demonstrate how having sufficient
-number of large positive kicks allows lenses to be detected in spite of several
-short negative kicks.
+The {\bf top-left panels of \Fref{fig:detmis}} show the detected lenses. The cases shown with green trajectories 
+in each panel can be thought of counterparts of the trajectories of the
+missed lenses in the corresponding bottom panels except that the type of
+volunteers are different. Most detected lenses are similar to the case
+in panel a that are detected within a few classifications coming from
+large positive kicks.  Panel b represents a few odd cases which are
+dominated mainly by short positive kicks. Panel c shows a lens getting
+more classifications but do not reach the detection or rejection
+thresholds because of the tug between positive and negative kicks mostly
+from experienced volunteers.  Panel d represents the extreme cases when
+the images are on the verge of being rejected but are saved thanks to a
+series of large positive kicks.  The red trajectories are some more
+examples of randomly selected cases which demonstrate how having
+sufficient number of large positive kicks allows lenses to be detected
+in spite of several short negative kicks.
 

### 2015-05-09 doc/sw-cfhtls.tex
incorporated AV's edits and Phil's correct until Section 3.3  (corresp. 211fe65)

@@
 prescription of \citet{Lupton2004}. The color scales were chosen to
-maximize the contrast between faint extended objects. These parameters
+maximize the contrast between faint extended objects and bright early
+type galaxies. These parameters
 were then fixed during the production of all the tiles, in order to allow
@@
 Here, we describe some of the cases or aspects in which the simulations
-were known to be unrealistic. The fraction of such unrealistic simulations in the 
+were known to be unrealistic. The fraction of such unrealistic cases in the 
 simulated sample is small (roughly 5 percent)\footnote{This estimate is

### 2015-05-09 doc/sw-cfhtls.tex
simfail section #203

--- 2015-05-08 doc/sw-cfhtls.tex
@@
 the uncertainties in the model parameters. Comments from citizen
-scientists were very helpful in order to sort some of these failures.
+scientists were very helpful in order to identify some of these failures, which
+make up roughly 5\% of the simulated sample.\footnote{This estimate is
+based on the number of \#simfail tags from TALK, the discussion forum.}
 Here, we describe some of the cases or aspects in which the simulations
-were known to have failed to look realistic. The fraction of such
-simulated sample is small (roughly 5 percent)\footnote{This estimate is
-based on the number of \#simfail tags from TALK, the discussion forum.}.
-
-The parameters required by various scaling relations and the models
+were known to have failed to look realistic.
+
+The parameters required by the models' various scaling relations
 primarily depend on the photometry of the galaxies, groups and quasars
-detected in the survey. For galaxy-scale lenses, the lensing galaxies at
-higher redshifts or which are fainter have poor photometric redshift
-measurements. Consequently these galaxies are assigned  wrong
-luminosity and velocity dispersion estimates. This then results in
+detected in the survey. For galaxy-scale lenses, the fainter or higher redshift
+lensing galaxies at tend to have poor photometric redshift
+measurements. Consequently these galaxies were occasionally assigned the wrong
+luminosity and velocity dispersion estimates, resulting in
 simulated lenses which look implausible or unrealistic.  For example,
 the lensed images for some of the failed simulations have larger image
-separation than what you expect from the luminosity and/or size of the
-galaxy. We roughly expect mass to follow light so more massive galaxy
-typically looks brighter and/or bigger.
-
-At group-scales, the photometric and redshift estimates are used when define
-the group membership. Therefore, errors in redshift estimates generate galaxy
-groups with BGG or member galaxies with dissimilar properties. In some cases,
-low redshift spiral galaxies have been incorrectly assigned high redshift.
+separation than would be expected from the luminosity and/or size of the
+galaxy.
+
+At group scales, the magnitudes and photometric redshifts were used when defining
+the group membership. Therefore, errors in redshift estimates occasionally
+generated galaxy
+groups having member galaxies with unrealistically dissimilar properties.
+In some cases,
+low redshift spiral galaxies were incorrectly assigned high redshift.
 Spiral galaxies are typically less massive and low redshift spiral galaxies are
 unlikely to act as gravitational lenses. Hence, some such instances
-do not appear convincing or the lensed images do not have the expected
-configuration or image separations.
-
-We also use a single component to describe the light profiles of
+did not appear convincing, as the lensed images again did not have the expected
+configurations or separations.
+
+We also use a single component to describe the light distribution of the
 background galaxies. This is clearly not the most accurate description for
-galaxies, especially, star-forming galaxies which form a significant fraction
+galaxies, especially for the irregular star-forming galaxies which comprise
+a significant fraction
 of the lensed galaxy population. Star-forming galaxies have complex structures
 such as star forming knots, spiral arms, bars and disks. The simulated lensed
-images do not display these features. This is fine for most cases or
-mostly for images taken from ground based telescopes such as the CFHT
+images do not display these features. This is fine for most cases seen in
+images taken from ground based telescopes such as the CFHT
 {\bf but sometimes the profiles of the lensed arcs can appear very symmetric along the

### 2015-05-09 doc/sw-cfhtls.tex
Renamed FPs as impostors, to avoid confusion with false positives arising from the search. We should have been calling the Stage 2 duds impostors from the start! The term false positive should be reserved for one of the *outputs* of a search. #203

@@
 previously published lens samples from the \cfhtls. We generated a training sample,
-consisting of simulated lenses, duds and false positives, in order to
+consisting of simulated lenses, duds and impostors, in order to
 aid the \sw volunteers in the process of finding lenses. We give details of this
@@
 
-\section{Training sample: Duds and False positives}
+\section{Training sample: Duds and Impostors}
 \label{sec:dfp}
@@
 Citizen scientists need training not only to identify gravitational
-lenses, but also to reject images which either have no lenses or have
-objects which are lens impostors. Hence, in addition to the simulated
-lenses, we added a sample of duds and false positives to the training
+lenses, but also to reject images which either contain no lenses, or contain
+objects which could be mistaken for lenses. Hence, in addition to the simulated
+lenses, we added a sample of ``duds'' and ``impostors'' to the training
 sample. Duds are images which have been visually inspected by experts
-and confirmed to contain no lenses. False positives (FPs) are systems
+and confirmed to contain no lenses. Impostors are systems
 which look like lenses but are not, for example, spiral galaxies,
@@
 We selected a sample of 450 duds for the \StageOne classification in \sw
-and a sample of 500 false positives for the \StageTwo inspection. The
-sample of false positives was selected from the candidates which passed
-the \StageOne of \sw. We note that this is the first time, we have a
-systematically compiled sample of visually inspected false positives by
+and a sample of 500 impostors for the \StageTwo inspection. The
+sample of impostors was selected from the candidates which passed
+the \StageOne of \sw. We note that this is the first time we have a
+systematically compiled sample of visually inspected impostors by
 the \sw volunteers and categorized by the science team. We produce

### 2015-05-09 doc/sw-cfhtls.tex
Mathematical symbols must be in italics - changed all P's. #203

@@
 systematically compiled sample of visually inspected impostors by
-the \sw volunteers and categorized by the science team. We produce
-additional larger sample of a few thousand FPs by scanning through the
+the \sw volunteers and categorized by the science team. We produced an
+additional larger sample of a few thousand false positive detections
+by scanning through the
 low probability images after the completion of \StageTwo. All of these
@@
 \label{sec:swap}
-The \sw works as a single unified system which uses the method of visual
+
+\sw works as a single unified system which uses the method of visual
 inspection to find gravitational lenses. For the first \sw lens search,
 the volunteers were shown images at two stages. At \StageOne, volunteers
-are requested to undertake a rapid inspection to select lens candiates
+were asked to carry out a rapid inspection to select lens candiates
 ranging from possible lenses to almost certain lenses. At \StageTwo,
-volunteers carefully inspect the candidates from \StageOne and select
-only promising lens candidates. A daily snapshot of classifications
-performed by volunteers are provided to the science team every night.
-This daily batch is analyzed by the Space Warps Analysis Pipeline
+volunteers were asked to inspect the candidates from \StageOne and select
+only promising lens candidates. A daily snapshot of the classifications
+performed by volunteers was provided to the science team every night.
+This daily batch was analyzed by the Space Warps Analysis Pipeline
 (SWAP). The philosophy and the details of SWAP are described in detail
-in \PaperOne, here we briefly summarize how it works.
-
-Each subject (or image cutout) is assigned a prior probability of
+in \PaperOne. Here, we briefly summarize how it works.
+
+Each subject (image cutout) is assigned a prior probability of
 $2\times10^{-4}$ to contain a lens system. Every volunteer

### 2015-05-09 doc/sw-cfhtls.tex
Clearer grade definition #203

@@
 the lensing galaxies from the galaxy-scale lenses are distinct from the central
-galaxies of groups-scale lenses which are described in the following section.
+galaxies of group-scale lenses which are described in the following section.
 
@@
 curves show the theoretical prediction assuming an SIS model at galaxy-scales
-and a total (NFW+Hernquist) model at groups-scales taken from \citep{More2012}.
+and a total (NFW+Hernquist) model at group scales taken from \citep{More2012}.
 }
@@
 galaxy lenses (see \Tref{tab:thresh}) and are reported within ``()'', if
-different for group-scales. The simulated lensed images are then added
+different for group scales. The simulated lensed images are then added
 to the real \cfhtls~images with the BGGs as the center by following
@@
 In \Fref{fig:remudist}, we show the Einstein radius ($R_{\rm E}$) distribution for the
-galaxy-scale and groups-scale simulated lenses. For comparison, we give
+galaxy-scale and group-scale simulated lenses. For comparison, we give
 the expected distributions (blue solid curves) for an SIS like density
-profile at galaxy-scales and an NFW+Hernquist profile at groups-scales.
+profile at galaxy-scales and an NFW+Hernquist profile at group scales.
 The theoretical curves are taken from \citet{More2012} wherein the
 models are explained in detail. We note that the model we adopt at
-groups-scale also includes SIS or SIE components for the group members
+the group scale also includes SIS or SIE components for the group members
 unlike the theoretical prediction. The theoretical curves have arbitrary
@@
 Distribution of different types of candidates as a function of the
-posterior probability P. The types of the candidates are the false
+posterior probability $P$. The types of the candidates are the false
 positives (FPs), the new candidates and the known candidates. The new
-and known candidates have higher detection rate for higher values of P,
+and known candidates have higher detection rate for higher values of $P$,
 as expected.}
@@
 Each subject (image cutout) is assigned a prior probability of
-$2\times10^{-4}$ to contain a lens system. Every volunteer
+$2\times10^{-4}$ of containing a lens system. Every volunteer
 is assigned an agent characterised by a $2\times2$ confusion matrix,
 which quantifies the volunteer's ability to correctly classify an image
-to contain a lens ($P_L$) or to not contain a lens ($P_D$). The values of
-the confusion matrix are determined based on the performance of the
+as containing a lens ($P_L$) or not containing a lens ($P_D$). The values of
+these confusion matrix elements are determined based on the performance of the
 volunteer on the training sample, specifically, $P_L$ (and $P_D$) is
-determined based on the fraction of simulated lenses (and duds)
+determined based on the fraction of simulated lenses (and, respectively, duds)
 correctly classified. After every classification, the agent updates the
-prior probability of the classified subject based on the volunteer's classification
-and the confusion matrix, according to the Bayes theorem.
-Note that the volunteer's confusion matrix is updated after the
+probability of the classified subject based on the volunteer's classification
+and the confusion matrix, according to Bayes' theorem.
+The agent's confusion matrix is updated after the
 classification of every training image. The thresholds for the
@@
 not contain one} can be chosen in SWAP. Those images which cross
-these threshold values are retired and are not subsequently shown to the
-volunteers, so that volunteers can use their time efficiently to
-classify previously unclassified subjects.
+these threshold values are ``retired'', and are not subsequently shown to the
+volunteers. In this way, the crowd can use its time efficiently in
+inspecting previously unclassified subjects.
 
 SWAP was run nightly during \StageOne in order to retire subjects and inject new
-ones in to the classification stream. The subjects that passed the acceptance
-threshold at the end of \StageOne are served again at \StageTwo for careful
-reinspection. Each subject, after \StageTwo, has an associated posterior
-probability P. In the ideal case, all images containing lenses will have high P
-values and those without lenses will have low P values. In practice, we expect a
-small fraction of the real lenses (or non-lenses) to be assigned low (or high) P
-values thereby, decreasing the completeness (or purity) of the final lens
+ones in to the classification stream. The subjects that passed the detection
+threshold at the end of \StageOne were served again at \StageTwo for careful
+re-inspection. Each subject, after \StageTwo, has a posterior
+probability $P$. In the ideal case, all images containing lenses will have high $P$
+values and those without lenses will have low $P$ values. In practice, we expect a
+small fraction of the real lenses (or non-lenses) to be assigned low (or high) $P$
+values, thereby decreasing the completeness (or purity) of the final lens
 sample. As this is the first lens search with \sw, we want to find a
-threshold P value which will result in acceptable levels of completeness and
+threshold $P$ value which will result in acceptable levels of completeness and
 purity of the final sample of lens candidates.
 
-We decided to inspect the top few hundreds of images from a catalog with
-descending P values as a reasonable sample size for visual inspection.
-We choose P$>0.3$ for which we find a total of 665 subjects in the
-catalog. These images were then visually inspected by three lens experts
-(AM, AV, PJM).  The images are assigned grades on a scale of 0 to 3,
-thus dividing the subjects into candidates with the quality flag -
-unlikely lens, possibly a lens, probably a lens and almost certainly a
-lens, respectively. The final sample of \sw-\cfhtls lens candidates is
-then produced by selecting candidates above some threshold on the
-averaged grades as described in the next section.
+To achieve this, we selected a total of 665 subjects with $P>0.3$
+which were then visually inspected by three of us (as ``lens experts'',
+ AM, AV, PJM).  The images were assigned grades on a scale of 0 to 3,
+representing those images
+0) unlikely to contain a lens, 1) possibly containing a lens, 2) probably
+containing a lens and 3) almost certainly containing a
+lens. The final sample of \sw-\cfhtls lens candidates was
+then produced by selecting candidates above a threshold on the
+average value of these grades, as described in the next section.
 
@@
 the high probability lens candidates, categorized by the lens experts,
-as a function of the P value assigned by SWAP at the end of \StageTwo.
+as a function of the $P$ value assigned by SWAP at the end of \StageTwo.
 On average, the fraction of lens candidates is indeed an increasing
-function of P. This shows that the \sw generated P values for the
+function of $P$. This shows that the \sw generated $P$ values for the
 subject are roughly correlated with the expert grades albeit with quite
-some scatter.  We note that from P$\sim$0.75 onwards to lower P values,
+some scatter.  We note that from $P\sim$0.75 onwards to lower $P$ values,
 the fraction of false positives starts to exceed the fraction of real
@@
 P~$=$~0.3 as this gives a better completeness of 100~per~cent for the ``known
-lens'' sample instead of 67~per~cent for P~$=$~0.75. Therefore, the new sample
+lens'' sample instead of 67~per~cent for $P=0.75$. Therefore, the new sample
 should also have increased completeness which combined with expert
@@
 {AC}-- All (known and new) lens candidates  \\
-P$_{\rm thresh}$ -- systems with Posterior probability P above this threshold are selected \\
+P$_{\rm thresh}$ -- systems with Posterior probability $P$ above this threshold are selected \\
 Note: For KC and KL, Percentages are with respect to the known
@@
 averaged grade G from the lens experts, zoo ID (identifier used in
-TALK), P value at \StageTwo and a visual categorization of the type of
+TALK), $P$ value at \StageTwo and a visual categorization of the type of
 lensed images and the lensing galaxy in the ``Comments'' column in
@@
 lenses, as expected from such a search. The final sample consists of
-both galaxy and groups-scale lens candidates. There are detections of
+both galaxy and group-scale lens candidates. There are detections of
 elongated arcs and some interesting point-like quasar lensed images.
@@
 such interesting lens candidates. We did not find any examples of
-exotic lens candidates from the visually inspected P$>0.3$ sample. There
+exotic lens candidates from the visually inspected $P>0.3$ sample. There
 may be some interesting candidates lurking in TALK but these will have
@@
 we use the value of the input parameter of the lens model for the $R_{\rm E}$.
-For groups-scale lenses, since the lens model is multi-component, we
+For group-scale lenses, since the lens model is multi-component, we
 need to determine the $R_{\rm E}$ from the image positions. We use those
@@
 a status of detected (if P$>$P$_{\rm acc thresh}$), rejected (if
-P$<$P$_{\rm rej thresh}$) and undecided (if P$_{\rm rej thresh}<$ P $<$
-P$_{\rm acc thresh}$). In \Fref{fig:comppos}, we compare the positions
+P$<$P$_{\rm rej thresh}$) and undecided (if $P_{\rm rej thresh}< P <
+P_{\rm acc thresh}$). In \Fref{fig:comppos}, we compare the positions
 of lenses which are detected (red), undecided (green) and rejected
@@
 
-We check how the posterior probability P (see \PaperOne for the
+We check how the posterior probability $P$ (see \PaperOne for the
 mathematical definition) of an image or a subject to contain a lens
@@
 subject increase from top to bottom.  Also, every subject is assigned a
-prior probability P0$=2\times10^{-4}$ (grey dashed line) and starts at
-the middle of the trajectory plot. The P value of a subject is updated
+prior probability $P_0=2\times10^{-4}$ (grey dashed line) and starts at
+the middle of the trajectory plot. The $P$ value of a subject is updated
 with every classification from the volunteer.  If a volunteer identifies
@@
 marking the (P$_{\rm acc thresh}=0.95$) on the right and is rejected, if
-it crosses the red-dashed line marking the P$_{\rm rej thresh}=10^{-7}$
+it crosses the red-dashed line marking the $P_{\rm rej thresh}=10^{-7}$
 on the left.
 
-The amount by which the posterior probability P value of a subject will
+The amount by which the posterior probability $P$ value of a subject will
 change depends on how well the volunteers are performing on the training
 sample and its current probability. Thus, for a given current
-probability, high power volunteers will change the P by a large factor
+probability, high power volunteers will change the $P$ by a large factor
 compared to the low power volunteers. This is evident in the trajectory
@@
 the total Nclass per subject by a large fraction. As a result, we also
-need to change the P$_{\rm acc thresh}$ which is chosen to be 0.1 and we
+need to change the $P_{\rm acc thresh}$ which is chosen to be 0.1 and we
 find that about a third of the missed lenses are detected while all the
@@
 \hline
-SW ID & Name & RA & Dec &  $z_{\rm phot}$ & $m_i$ & $R_{\rm E}$ & G & ZooID & P & Comments  \\
+SW ID & Name & RA & Dec &  $z_{\rm phot}$ & $m_i$ & $R_{\rm E}$ & G & ZooID & $P$ & Comments  \\
   &  & (deg) & (deg) &  & (mag) &  (") &  &  & & \\

### 2015-05-09 doc/sw-cfhtls.tex
Simplified sample definition text. #203

@@
 which were then visually inspected by three of us (as ``lens experts'',
- AM, AV, PJM).  The images were assigned grades on a scale of 0 to 3,
+ AM, AV, PJM).  Each images was assigned a grade~$G$ on a scale of 0 to 3,
 representing those images
@@
 
-In this section, we describe the \sw-\cfhtls lens sample (henceforth,
-called the \sw lens sample). We find a total of 141 candidates with
-G$\ge1.3$ (medium-high probability sample) out of which {\bf 59} are new
+In this section, we describe the \cfhtls \sw candidate lens sample.
+We find a total of 141 candidates with
+$G\ge1.3$ (medium-high grade), of which {\bf 59} are new
 systems. This sample is further divided as follows. We have a total of
-50 candidates with $1.3\le$G$<2$ (medium probability sample) out of
+50 candidates with $1.3\le$G$<2$ (medium grade), of
 which 30 are new. The quality of candidates in this category is such
-that at least one of the inspectors thought the candidate is most
+that at least one of the inspectors thought the candidate was
 probably a lens (that is, a grade of 2) and a second inspector thought
-this is possibly a lens (that is, a grade of 1). Among our high
-probability sample (G$\ge$2), there are a total of 91 candidates out of
+that it was possibly a lens (that is, a grade of 1). Among our high
+grade sample ($G\ge$2), there are a total of 91 candidates, of
 which {\bf 29} are new. In this category, the minimum grade by all of the
-inspectors was 2 suggesting that the candidates are probably or almost
-certainly lenses according to all of the inspectors. To avoid
+inspectors was 2, suggesting that the candidates are probably or almost
+certainly lenses according to all three inspectors. To avoid
 duplication, further information on \sw candidates that were previously
 identified in the literature will be made available at
-\texttt{http://spacewarps.org/\#/projects/CFHTLS/} whereas the sample of new lens
-candidates with G$\ge 1.3$ (medium-high probability) is presented in
+\texttt{http://spacewarps.org/\#/projects/CFHTLS/}, while the sample of new lens
+candidates with $G\ge 1.3$ (medium-high probability) is presented in
 this paper (see \Sref{sec:results:newcand}).
 
-We find a total of 288 (and {\bf 245} new) candidates with averaged grade
-$0<$G$<1.3$ (low probability sample) which means - in the worst case, at
-least one of the inspector thought the candidate is possibly a lens and
-in the best case, all three inspectors thought the candidate is possibly
+We also find a total of 288 (and {\bf 245} new) candidates with averaged grade
+$0<$G$<1.3$ (low grade), which means that at
+least one of the inspector thought the candidate was possibly a lens, and
+in the best cases, all three inspectors thought the candidate was possibly
 a lens (that is, a grade of 1)\footnote{If grades from the inspectors
@@
 at \texttt{http://spacewarps.org/\#/projects/CFHTLS/}. Note that if all of the
-inspectors gave a grade of 0 to a candidate, then it is discarded from
+inspectors gave a grade of 0 to a candidate, then it was discarded from
 the sample.
 
-In Table~\ref{tab:stats}, we give overall statistics of the systems
+In \Tref{tab:stats}, we give overall statistics of the systems
 detected at \StageOne and \StageTwo. We give the total number of
@@
 In \Fref{fig:stackP}, we plot the distribution of false positives and
-the high probability lens candidates, categorized by the lens experts,
+the high grade lens candidates,
 as a function of the $P$ value assigned by SWAP at the end of \StageTwo.
@@
 subject are roughly correlated with the expert grades albeit with quite
-some scatter.  We note that from $P\sim$0.75 onwards to lower $P$ values,
+some scatter.  We note that below $P\sim0.75$,
 the fraction of false positives starts to exceed the fraction of real
 lens candidates. This could be a good threshold to choose to maximize
-the purity of the final sample. However, we go with the choice of
-P~$=$~0.3 as this gives a better completeness of 100~per~cent for the ``known
-lens'' sample instead of 67~per~cent for $P=0.75$. Therefore, the new sample
-should also have increased completeness which combined with expert
-grading allows us to achieve further purity of our sample.
+the purity of the final sample. However, choosing
+$P=0.3$ gives a completeness of 100\% for the ``known
+lens'' sample instead of 67\% for $P=0.75$. Therefore, the new sample
+should also have increased completeness; expert
+grading then allows us to increase the purity of the sample.
 

### 2015-05-09 doc/sw-cfhtls.tex
Text edits on new sample #203

@@
 each stage. We find that all of the confirmed lenses found
-at \StageOne are also recovered at \StageTwo whereas a small fraction of
+at \StageOne are also recovered at \StageTwo; a small fraction of
 the known lens candidates are rejected at \StageTwo. From the visually
@@
 the sample of new \sw lens candidates increased the sample of total
-\cfhtls lens candidates by over 50~per~cent.
+\cfhtls lens candidates by over 50~per~cent. However, we find that 42\% of known
+lenses were missed at \StageOne: we return to the discussion of these false
+negatives below.
 
@@
 Number  & 128 & 34 & 107  & 34  \\
-Percentage  & & & & \\
-of recovery & 29 & 58 & 25 & 58  \\
-P$_{\rm thresh}$ & 0.95 & 0.95 & 0.3 & 0.3 \\
+Fraction  & & & & \\
+of total recovered & 29\% & 58\% & 25\% & 58\%  \\
+$P_{\rm thresh}$ & 0.95 & 0.95 & 0.3 & 0.3 \\
 {\bf Expert Grade (G)} & $-$ & $-$ & 1.3 & 1.3 \\
@@
 Number  & {\bf 59} & 141 &  & \\
-Percentage & & & & \\
-of detection & 13 & 33 &  & \\
-P$_{\rm thresh}$ & 0.3 & 0.3 &  & \\
+Fraction & & & & \\
+of detections & 13\% & 33\% &  & \\
+$P_{\rm thresh}$ & 0.3 & 0.3 &  & \\
 {\bf Expert Grade (G)} & 1.3 & 1.3 & 1.3 & 1.3 \\
@@
 {AC}-- All (known and new) lens candidates  \\
-P$_{\rm thresh}$ -- systems with Posterior probability $P$ above this threshold are selected \\
+$P_{\rm thresh}$ -- systems with Posterior probability~$P$ above this threshold are selected \\
 Note: For KC and KL, Percentages are with respect to the known
@@
 
-We give basic information about the final sample of {\bf 59} new lens
-candidates (medium-high probability) found by \sw in
-Table~\ref{tab:swcands}. We report the candidates with a \sw ID and Name
-of the lens system. We give their positions (Ra, Dec), photometric
+We give basic information about the final sample of {\bf 59} new medium grade
+lens candidates found by \sw in
+\Tref{tab:swcands}. We report the candidates with a \sw ID and Name
+of the lens system. We give their positions (RA, Dec), photometric
 redshift ($z_{phot}$), $i$ band magnitude of the lensing galaxy,
-averaged grade G from the lens experts, zoo ID (identifier used in
+averaged grade~$G$ from the lens experts, zoo ID (identifier used in
 TALK), $P$ value at \StageTwo and a visual categorization of the type of
 lensed images and the lensing galaxy in the ``Comments'' column in
-Table~\ref{tab:swcands}. Whenever available the lens properties are
-taken from the \cfhtls photometric catalog \citep{Coupon2009} otherwise
-for the lens galaxy positions, the reported values are measured
+\Tref{tab:swcands}. Whenever available the lens properties are
+taken from the \cfhtls photometric catalog \citep{Coupon2009}; otherwise,
+for the lens galaxy positions, the reported values were measured
 manually. The visual categorization of the lens type is only suggestive
@@
 
-We show images of our new sample in \Fref{fig:lc} which is arranged
-first in the decreasing order of their grades and then increasing order
-of their positions. As the first lens search was a blind search with no
+We show images of our new sample in \Fref{fig:lc}. The panels are arranged
+first in the descending order of their grades, and within each grade, in
+ascending order
+of RA. As the first lens search was a blind search with no
 preselection of candidates from any algorithm, we find various types of
@@
 elongated arcs and some interesting point-like quasar lensed images.
-Most of them are brighter in bluer $g$ band but some candidates brighter
-in the redder $i$ band are also found. Since robotic lens searches often
-look for blue colored lensed features, they are very much likely to miss
+Most of them are brighter in the bluer $g$ band, but some candidates brighter
+in the redder $i$ band are also found. Since the robotic lens searches
+focused on the blue lensed features, they are likely to miss
 such interesting lens candidates. We did not find any examples of
-exotic lens candidates from the visually inspected $P>0.3$ sample. There
-may be some interesting candidates lurking in TALK but these will have
-to be sifted through.
-
-The new \sw lens sample presented here shows the advantages of having
+exotic lens candidates from the visually inspected $P>0.3$ sample.
+
+The new \sw lens sample presented here illustrates some of
+the advantages of having
 citizen scientists find lenses through visual inspection. An algorithm,
@@
 uses either geometry or flux information from an image. On the other
-hand, citizen scientists can do amazing amount of interpolation or
-extrapolation over the basic selection criteria provided to them.  For
+hand, citizen scientists can interpolate over or
+extrapolate beyond the basic selection criteria provided to them.  For
 example, the lower blue arc in SW7 is split by a small red galaxy.  An
@@
 into smaller arclets which then falls below the minimum length or area
-allowed for an arc to be detected typically. Human brains have no
-problem in interpolating over the broken blue arc over the red galaxy
-and understand that it is a single long arc. The system {\bf SW20} has
+allowed for an arc to be detected. Human inspectors have no
+problem in interpolating over the broken blue arc over the red galaxy,
+understanding that it is a single long arc. The system SW20 has
 point-like lensed images which cannot be detected by arc finding
-algorithm whereas the ring finding algorithm may miss this because of
-atypical color and structure of the galaxy. Detection of red arcs, for
-example, as seen in the SW38 candidate show how the volunteers
-extrapolate on the color parameter because the training sample mostly
-has blue arcs since this is the typical expectation.
+algorithm, whereas the ring finding algorithm may have missed this because of
+the atypical color and structure of the galaxy. Detection of red arcs, for
+example, as seen in the SW38 candidate, show how the volunteers
+extrapolate on the color parameter: the training sample contains
+predominantly blue arcs, because the source colors were drawn from realistic
+observed distributions.
 
@@
 new candidates missed by some of these algorithms demonstrates that the
-\sw system is functioning well and the self-taught citizen scientists
-have managed to beat the robots in some sense.
+\sw system is functioning well, the self-taught citizen scientists
+reaching parts of discovery space that the robots did not.
 

### 2015-05-09 doc/sw-cfhtls.tex
Fixed some small things #203

@@
 detected in the survey. For galaxy-scale lenses, the fainter or higher redshift
-lensing galaxies at tend to have poor photometric redshift
+lensing galaxies tend to have poor photometric redshift
 measurements. Consequently these galaxies were occasionally assigned the wrong
@@
 
+% PHIL IS HERE
+
 \subsection{Measurements of properties of the lens and the lensed images}
@@
 From the SWAP, the image cutouts inspected by the \sw volunteers receive
-a status of detected (if P$>$P$_{\rm acc thresh}$), rejected (if
-P$<$P$_{\rm rej thresh}$) and undecided (if $P_{\rm rej thresh}< P <
+a status of detected (if $P>P_{\rm acc thresh}$), rejected (if
+$P<P_{\rm rej thresh}$) and undecided (if $P_{\rm rej thresh}< P <
 P_{\rm acc thresh}$). In \Fref{fig:comppos}, we compare the positions
@@
 the left. A subject is accepted if it crosses the blue-dashed line
-marking the (P$_{\rm acc thresh}=0.95$) on the right and is rejected, if
+marking the ($P_{\rm acc thresh}=0.95$) on the right and is rejected, if
 it crosses the red-dashed line marking the $P_{\rm rej thresh}=10^{-7}$
@@
 volunteers for each sample (that is, detected or missed). The kick size
-is small if $\Delta$ log(P)$=$log (P$_{\rm current}) - $log(P$_{\rm
-previous}) < \Delta$log(P)$_{\rm cut}$ (chosen as 1.2) and is large
-if greather than $\Delta$log(P)$_{\rm cut}$.
+is small if $\Delta log{P} = \log{P_{\rm current}} - \log{P_{\rm
+previous}} < \Delta\log{P}_{\rm cut}$ (chosen as 1.2) and is large
+if greather than $\Delta\log{P}_{\rm cut}$.
 

### 2015-05-09 doc/sw-cfhtls.tex

@@
 prescription of \citet{Lupton2004}. The color scales were chosen to
-maximize the contrast between faint extended objects and bright early type galaxies.
-These parameters
+maximize the contrast between faint extended objects and bright early
+type galaxies. These parameters
 were then fixed during the production of all the tiles, in order to allow
@@
 exotic lens candidates from the visually inspected $P>0.3$ sample.
+There
+may be some more interesting candidates that were missed either at
+\StageOne or \StageTwo but have been identified by volunteers in \Talk.
+This resource is yet to be mined and is left for future work.
 
@@
 we show that $\sim$~25$-$30~per~cent of the known lens candidates and
-$\sim$~60~per~cent of the known lenses are found at \StageOne and \StageTwo in
-\sw. The left and the middle panels of \Fref{fig:compre} show the
+$\sim$~60~per~cent of the known lenses are found at \StageOne. Eighty-four
+percent of the known lens candidates and \textbf{all} of the known lenses
+from \StageOne passed our \StageTwo selection criterion of $P>0.3$.
+The left and the middle panels of \Fref{fig:compre} show the
 fraction of detections as a function of arc magnitude and the Einstein
@@
 
-The bottom panels show the missed or rejected lenses. The green (and red)
+The {\bf bottom-left panels of \Fref{fig:detmis} show the} missed or rejected lenses. The green (and red)
 trajectories show visually easier (and more difficult) to identify
@@
 
-The top panels show the detected lenses. The cases shown with green trajectories
-in each panel can be thought of counterparts of the trajectories of the missed
-lenses in the corresponding bottom panels except that the type of volunteers are
-different. Most detected lenses are similar to the case in panel a which are
-detected within a few classifications but coming from large positive kicks.
-Panel b represents a few odd cases which are dominated mainly by short positive
-kicks. Panel c shows a lens getting more classifications because of the tug
-between positive and negative kicks whereas the panel d represents the extreme
-cases when the images are on the verge of being rejected but are saved thanks
-to a series of large positive kicks. The red trajectories are some more
-examples of randomly selected cases which demonstrate how having sufficient
-number of large positive kicks allows lenses to be detected in spite of several
-short negative kicks.
+The {\bf top-left panels of \Fref{fig:detmis}} show the detected lenses. The cases shown with green trajectories
+in each panel can be thought of counterparts of the trajectories of the
+missed lenses in the corresponding bottom panels except that the type of
+volunteers are different. Most detected lenses are similar to the case
+in panel a that are detected within a few classifications coming from
+large positive kicks.  Panel b represents a few odd cases which are
+dominated mainly by short positive kicks. Panel c shows a lens getting
+more classifications but do not reach the detection or rejection
+thresholds because of the tug between positive and negative kicks mostly
+from experienced volunteers.  Panel d represents the extreme cases when
+the images are on the verge of being rejected but are saved thanks to a
+series of large positive kicks.  The red trajectories are some more
+examples of randomly selected cases which demonstrate how having
+sufficient number of large positive kicks allows lenses to be detected
+in spite of several short negative kicks.
 

### 2015-05-09 doc/sw-cfhtls.tex
Consistent \log{P} notation #203

@@
 We rerun SWAP for \StageOne where we use classifications from volunteers
-who produce $\Delta$ log(P)$>1.2$ only. This obviously means reducing
+who produce $\Delta \log{P} > 1.2$ only. This obviously means reducing
 the total Nclass per subject by a large fraction. As a result, we also
@@
 \StageTwo FPs, we find that a small fraction of FPs are rejected when
-only classifications with $\Delta$ log(P)$>1.2$ only are considered.
+only classifications with $\Delta \log{P}>1.2$ only are considered.
 Therefore, we think it is worth adopting the new strategy in the future
@@
 will apply a ``kick'' of a different size to the subject probability,
-$\Delta\log(P)$, which can be either positive (if the classifier thinks
+$\Delta\log{P}$, which can be either positive (if the classifier thinks
 the subject contains a lens) or negative (if the classifier thinks the
@@
 \caption{ \label{fig:skilldlnp}
-Skill of the volunteers and $\Delta\log(P)$ given a lens or not a lens in
+Skill of the volunteers and $\Delta\log{P}$ given a lens or not a lens in
 an image as a function of $P_{\rm L}$ and $P_{\rm D}$. These

### 2015-05-09 doc/sw-cfhtls.tex
SExtractor macro #203

@@
 \citet{Sygnet2010} carried out a search for edge-on disk galaxy lenses in the
-\cfhtls WIDE. They identified galaxies, using {\sc SExtractor}, which
+\cfhtls WIDE. They identified galaxies, using \sextractor, which
 had $18<i<21$ and inclination angle $<25\,^{\circ}$. After applying few more
@@
 
-% PHIL IS HERE
-
 \subsection{Measurements of properties of the lens and the lensed images}
@@
 
-In the subsequent sections, we make comparison of various properties of the lens
+In the subsequent sections, we compare various properties of the lens
 candidates. Here, we describe how we extract or measure these properties, namely,
@@
 subtracted \citep[for details, see][]{Gavazzi2014}. Here, we use the flux
-of the lensed images measured by {\sc SExtractor} from the scaled
+of the lensed images measured by \sextractor from the scaled
 difference image, that is, $g-\alpha i$ and convert it to the $g$ band
@@
 the \af and the \sw sample, we integrate the flux in the image pixels
-identified by \af or {\sc SExtractor}.
+identified by \af or \sextractor.
 
@@
 these angular image separations. For the \rf sample, we use the peak
-position of the lensed images measured by running {\sc SExtractor} on
+position of the lensed images measured by running \sextractor on
 the scaled difference image. We calculate the image separation from the
@@
 sample, the same definition is used where the peak positions are
-identified either with \af or {\sc SExtractor}.
+identified either with \af or \sextractor.
 

### 2015-05-09 doc/sw-cfhtls.tex
Tenses in results section #203

@@
 the scaled difference image. We calculate the image separation from the
-lens center as an estimate of the $R_{\rm E}$. For the \af (SARCS)
+lens center as a rough estimate of the $R_{\rm E}$. For the \af (SARCS)
 sample, we use the same definition as above except that the peak
@@
 
-We determine what fraction of the known sample of lenses are recovered
+We noe determine the fraction of the known sample of lenses that were recovered
 by \sw. Note that this sample corresponds to the \rf and \af samples
-combined, as mentioned in \Sref{sec:data:kls}. In Table~\ref{tab:stats},
-we show that $\sim$~25$-$30~per~cent of the known lens candidates and
-$\sim$~60~per~cent of the known lenses are found at \StageOne. Eighty-four
+combined, as mentioned in \Sref{sec:data:kls}. In \Tref{tab:stats},
+we show that $\sim25-30\%$ of the known lens candidates, and
+$\sim60\%$ of the known lenses were found at \StageOne. Eighty-four
 percent of the known lens candidates and \textbf{all} of the known lenses
@@
 We find that most of the confirmed lenses and candidates that are missed
-by \sw are systems with fainter arcs and smaller $R_{\rm E}$ and they
-come from the \rf sample. The main reason why \rf found such candidates
-is because their team used lensing galaxy-subtracted images to detect
-the presence of the lensed images both during the automated
-object-finding phase and during the visual inspection and classification
-of their candidates. This approach naturally improves the detection
+by \sw are systems from the \rf sample, with fainter arcs and smaller $R_{\rm E}$.
+The main reason why \rf found such candidates
+is because it involves subtracting the light from the lens galaxy,
+making it easiere to detect the lensed images during both the automated
+object-finding and the visual inspection and classification
+phases. This approach naturally improves the detection
 efficiency at smaller $R_{\rm E}$ and for fainter systems. The \sw
-volunteers were not shown any galaxy-subtracted images. However, showing
-galaxy subtracted images might be a better strategy to adopt for future
-lens searches at galaxy-scales with \sw. In the Discussion
-\Sref{sec:fn}, we further explore and discuss why some of the confirmed
+volunteers were not shown any galaxy-subtracted images. Showing
+galaxy-subtracted images might be a better strategy to adopt for future
+lens searches at galaxy-scales with \sw. In
+\Sref{sec:fn} below, we further explore and discuss why some of the confirmed
 lenses are missed by \sw.

### 2015-05-09 doc/sw-cfhtls.tex
Up to discussion section #203

@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
 \subsection{Image separation distribution}
@@
 
-Indeed, we have found {\bf 59} new lens candidates that were not known
+Indeed, we have found 59 new medium and high grade
+lens candidates that were not known
 before. In \Fref{fig:isd}, we show the image separation distribution for
@@
 corresponding to three density profiles, namely, isothermal sphere (IS),
-NFW \citep{Navarro1997} and Total profile which has NFW and Hernquist
+NFW \citep{Navarro1997} and a ``Total'' profile which has NFW and Hernquist
 profiles combined with an adiabatically contracting model for dark
 matter component \citep{Gnedin2004}. These curves are taken from
-\citet{More2012} which gives details of the calculation of these
+\citet{More2012}, which gives details of the calculation of these
 predictions.  With the updated sample of lens candidates, we confirm our
@@
 \includegraphics[scale=1.2]{isd_cfhtls_sw.pdf}
-\caption{ \label{fig:isd} Image separation distribution. Comparing theoretical
+\caption{ \label{fig:isd} Image separation distribution (ISD). Comparing theoretical
 predictions (solid curves) with the \cfhtls known lens samples (green)
@@
 sample of new and the known lens candidates discovered from \sw alone is
-shown in blue. The new updated profile of the isd (magenta) is
+shown in blue. The new updated profile of the ISD (magenta) is
 consistent with our previous measurements and strengthens our conclusion

### 2015-05-09 doc/sw-cfhtls.tex
Edits in comparison section to re-emphasize value brought by SW. Improvements to AF will presumably be described in a future AF paper! #203

@@
 Finding gravitational lenses is a difficult and complex task. No single
-method is perfect. Each method has some advantages over the other. It
+method is perfect, each method has some advantages over the other. It
 may be the case that a single method may never be the best method for
@@
 \subsection{Comparison of the \rf, \sw and \af samples}
-Here, we compare the properties of the lens candidates from each sample
-to understand if there are any clear differences between them. We
-consider the lens redshift, the total flux of the lensed images and the
-Einstein radii of the systems for this purpose.
 
 In \Fref{fig:zlmgre}, we show the lens redshift and the arc flux
-measured in $g$ AB mag as a function of the Einstein radius for the \rf
+measured in $g$-band AB magnitude as a function of the Einstein radius for the \rf
 (green), the \af (red) and the \sw sample (new candidates only in blue
@@
 
-Since \sw is visual based search, it is difficult to detect many lens
+Since in this project \sw enabled a visual search based on simple color
+composite images drawn directly from the survey,
+it was difficult to detect many lens
 candidates with a small $R_{\rm E}$ in the presence of a bright lensing
-galaxy. While this is true for algorithms too, the \rf team adopted a
-different method to circumvent this problem whose goal was to find
-galaxy-scale lenses which have small $R_{\rm E}$. The \rf sample is
+galaxy. In contrast, the \rf sample was
 generated by working with lensing galaxy$-$subtracted images and this
 led to increased detections of small image separation candidates. The
-\sw {\bf interface did not show} any galaxy subtracted images and hence,
+\sw interface did not show any galaxy subtracted images and hence,
 this results in a quantitative difference between the \sw and the \rf
@@
 
-The \af, on the other hand, is capable of finding smaller image
-separation lenses but a lower limit at $R_{\rm E}=2\arcsec$ was imposed
+The \af is capable of finding some small image
+separation lenses, but a lower limit at $R_{\rm E}=2\arcsec$ was imposed
 by the \af team to simplify the selection function of their sample.
@@
 between the \sw candidates and the \af samples. As noted earlier, the
-\rf dominates the small $R_{\rm E} (<2\arcsec)$ range although \sw does
-find modest number of candidates in this range. At larger $R_{\rm E}$,
+\rf dominates the small $R_{\rm E} (<2\arcsec)$ detections although \sw does
+find a modest number of candidates in this range. At larger $R_{\rm E}$,
 \sw sample begins to dominate and is comparable to the \af sample.  As a
 function of the arc magnitudes, all three samples have detections at all
-magnitudes and median magnitudes for all samples is around $g\sim$24.5.
+magnitudes and median magnitudes for all samples is around $g\sim24.5$.
 Relatively, the \rf sample spans a narrower range compared to the \sw
@@
 
-\subsection{Why \sw candidates were missed by lens finding robots?}
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Why were the new \sw candidates missed by the robots?}
+
 We test the \rf and \af on images centered on the new \sw candidates to
@@
 
-First, we rerun \rf on the new \sw sample. At the beginning, a galaxy
+First, we re-ran \rf on the new \sw sample. At the beginning, a galaxy
 catalog is generated based on magnitude, redshift and SED type
 \citep[see]{Gavazzi2014} to select galaxies which are most likely to act
-as lenses. We find that about 40~per~cent of the new \sw candidates fail to
-meet this initial selection criteria, for example, {\bf SW1, SW14, SW20,
-SW23, SW27 and SW30}. All of the lensing galaxies are bright enough to
+as lenses. We find that about 40~per~cent of the new \sw candidates failed to
+meet this initial selection criteria, for example, SW1, SW14, SW20,
+SW23, SW27 and SW30. All of the lensing galaxies are bright enough to
 satisfy the magnitude criterion ($i<22$). However, some of them have a
@@
 galaxies and some are edge on galaxies which could be the reason for
-excluding these galaxies from the initial catalog.
+these galaxies having failed the photometric redshift and SED type pre-selection.
 
@@
 
-In the following steps, the flux from the galaxy is subtracted from the
+In subsequent \rf steps, the flux from the galaxy is subtracted from the
 scaled difference image to enhance the visibility of the faint blue
-lensed features. An object finder is run on this image to quantify the
-lensed image properties. Another $\sim$~50~per~cent of the \sw candidates could not be
+lensed features. An object finder is then run on this image to quantify the
+lensed image properties.
+Another $\sim$~50~per~cent of the \sw candidates could not be
 detected by the object finder because properties such as the image area,
 axis ratio, magnitude/color and alignment with respect to the lensing
-galaxy are not satisfied. Some of the candidates missed at this stage
-are, for example, {\bf SW4, SW5, SW6, SW26, SW36, SW39 and SW46.}
-
-Next, we rerun the \af on the same \sw sample of new candidates. The \af
+galaxy were not satisfied. Some of the candidates missed at this stage
+are, for example, SW4, SW5, SW6, SW26, SW36, SW39 and SW46.
+
+Next, we re-ran the \af on the same \sw sample of new candidates. The \af
 is directly run on images to look for elongated arc like objects and does
@@
 Originally, the \af was run on a large image with an area of $\sim 19350
-\times 19350$ pixels$^2$. For the rerun, we work with much smaller
-images because this is faster but this alters the measured
-noise and hence, affects the number and type of arc detections. We find
-that about 30~per~cent of the new candidates are detected without changing any
-of the thresholds in the code because of the change in the noise level.
+\times 19350$ pixels$^2$. For the rerun, we worked with much smaller
+images because this is faster. However, this alters the measured
+noise and hence affects the number and type of arc detections. We find
+that about 30~per~cent of the new candidates were detected without changing any
+of the thresholds in the code, suggesting that these could have been detected by
+\af with had its noise thresholds been set differently.
 
@@
 properties such as the area, mean flux, length and curvature are
-determined. We relax the threshold at the segmentation stage and also relax
-thresholds mainly on the area of the arc which leads to detection of
+determined. We relaxed the threshold at the segmentation stage and also relaxed
+thresholds mainly on the area of the arc. These new settings led to the detection of
 about 75~per~cent of the new \sw candidates. We find that relaxing thresholds
-on other arc properties does not improve the detection rate significantly
-and thus, those thresholds are left unchanged.
-
-Typically, the candidates are missed from the \af sample if a) the arcs
-are fainter in $g$ band which is used for arc detection because then the
-arc feature is at the noise level and fails detection b) the flux of the
-arc and the galaxy are blended in the $g$ band such that the \af
-incorrectly connects part of the galaxy to the arc. This results in a
-candidate with no morphological characteristics of a typical arc c)
-unusually short or thick arcs or d) if the lensed images are almost
-circular or point-like which means most of the lensed quasars images
-will be missed.
-
-Relaxing the thresholds obviously increases the number of candidate arc
-detections but this also includes a large sample of false positives.
-For example, the number of arc candidate detections increase by a factor
-of $\sim$2 when we relaxed the thresholds in the reruns described above
-whereas the number of false positives increase by a factor of $\sim$5.
-Thus, it is not recommended to relax these thresholds alone. A better
-alternative is to relax the thresholds to increase the completeness and
-cross-correlate the arc candidate positions with a galaxy catalog to
-discard those candidates which are not close to a putative lensing
-galaxy within typical radius in order to reduce the false positives.
+on other arc properties does not improve the detection rate significantly.
+
+Typically then, the \sw candidates were missed from the \af sample either
+because a) the arcs
+were fainter, b) the flux of the
+arc and the galaxy were blended together (such that the \af
+incorrectly connected part of the galaxy to the arc), c)
+the arcs were unusually short or thick, or d) the lensed images are almost
+circular or point-like (\af was not designed to detect lensed quasars).
+
+Relaxing the \af thresholds obviously increases the number of candidate arc
+detections but this also increases the false positive rate.
+For example, the number of arc candidate detections increased by a factor
+of $\sim$2 when we relaxed the thresholds in the rerun described above,
+while the number of false positives increased by a factor of $\sim$5.
+While the \af sample purity could be increased by
+cross-correlating the arc candidate positions with a putative lens
+galaxy catalog, these numbers illustrate the predicament facing automated
+lens-finding algorithms, and the continuing benefits of visual screening.
 

### 2015-05-09 doc/sw-cfhtls.tex
Attempt to reword section on Nclass #203

@@
 \label{sec:fn}
-Like any lens finding method, the \sw system can fail to detect certain
+
+Like any lens finding method, the \sw system could potentially be failing
+to detect certain
 kinds of lenses.  We find that about 40~per~cent of the known sample of lenses
-are missed both at \StageOne and II (see \Tref{tab:stats}). In fact, all
-of the known lenses from \StageOne are discovered at \StageTwo which
-means that the lenses are lost already at \StageOne. Below, we focus on the known
+are missed at \StageOne; no further losses were incurred during
+the \StageTwo refinement (see \Tref{tab:stats}).
+Below, we focus on the known
 lens sample at \StageOne to understand why some of them are being missed
@@
 Einstein radii and faint lensed images (see \Fref{fig:compre}). Among
-the confirmed lenses from the \rf, about 50~per~cent are missed. Out of the
+the confirmed lenses from \rf, about 50~per~cent are missed. Out of the
 missed sample of 18 lenses, about half of them are visually difficult to
-detect and the other half appear to have faint blue smudges around
+detect. The other half appear to have faint blue smudges around
 galaxies which should have been easier to identify. Similarly,
@@
 is a relatively small sample of $\sim 5$ systems and visual inspection
-suggests that, by and large, either the lensed features are faint
+of them suggests that, by and large, either the lensed features are faint
 or they have odd properties which makes them difficult to identify
@@
 attempt to understand whether there is indeed a single dominant factor
-that is resulting in the loss of these lenses or the lenses are being
+that is resulting in the loss of these lenses, or if the lenses are being
 missed due to a combination of multiple reasons. Below, we consider some
@@
 \subsubsection{Number of classifications}
-First, we check if the number of classifications (Nclass) is
+
+First, we check whether the number of classifications (Nclass) is
 significantly lower for the missed sample compared to the detected one.
-Surprisingly, most of the lenses in the known sample have few
-classifications (Nclass$<$10) which includes both the detected and
-missed lenses. Many of the remaining lenses have between 10 to 20
-classifications. And, only a few subjects have Nclass$>$20. They
-continue to remain for long in the database because these candidates are
-possibly difficult to identify. Overall, we do not find any correlation
-for the detected and the missed sample with Nclass.
+Most of the lenses in the known sample (including both those that were
+detected and those that were missed)
+% have few classifications (Nclass$<$10).
+% Many of the remaining lenses have between 10 to 20
+% classifications. And, only a
+received similar numbers of classifications to the other subjects.
+A few received Nclass$>$20, possibly a result of
+continuing to remain for a long time in the database because there was
+uncertainty over whether or not to reject them.
+Overall, we do not find any difference in the number of classifications
+between the detected and the missed lenses.
 

### 2015-05-09 doc/sw-cfhtls.tex
Rewording in discussion. Power seems to be more a property of a *classification* than it does an agent... Please merge and edit as you see fit, Anu! #203

@@
 \subsubsection{Blind lens search}
-Efficiency of a visual search can vary in different sections of an
+
+The efficiency of a visual search could potentially
+vary in different sections of an
 image. Our eyes tend to focus usually at the center of an image and lens
 candidates close to the borders could go undetected. Therefore, it is
-essential to test and understand if \sw is missing some of the known lenses
+important to check whether \sw could be missing some of the known lenses
 because they happen to be close to the borders of the image cutouts.
@@
 
-We do not find any strong visual correlation in the detection rate of
-lenses as a function of their positions in the image for both the
-simulated and the known lens sample. Thus, the completeness of the lens
-sample is most likely not significantly affected by whether a lens is
-located close to the border or well within the center.
-
-\subsubsection{Volunteer profile}
-
-Here, we investigate if the power\footnote{see the
-\Aref{appendix:power} for the meaning of this term and how it is
-different from the ``Skill'' defined in \PaperOne} of volunteers is systematically
-different between the sample of detected and missed lenses.
+We do not find any strong correlation in the detection rate of
+lenses as a function of their positions in the image, for either the
+simulated or the known lens sample. Thus, the completeness of the lens
+sample is most likely not significantly affected by lenses
+located close to the image borders.
+
+\subsubsection{Classification Uncertainty}
+
+Each \sw image classification is based on the markers placed by around 10
+volunteers (on average, \PaperOne). This number could be
+small enough to introduce some scatter in the system performance, arising from
+the variations between the small groups of people inspecting each subject.
+In \PaperOne we investigated the system performamce in terms of the ``Skill''
+of each agent; in \Aref{appendix:power} we define a complementary property,
+the ``Power'' of a classification to make a large difference in the probability
+$P$ of an image containing a lens. Here, we investigate whether the distribution
+of classification power is systematically
+different between the detected and missed lenses.
 
@@
 \Fref{fig:detmis}, we show the trajectory plots of a few examples of
-detected lenses (top left panels) and missed lenses (bottom left panels)
-from \StageOne of \sw. The number of classifications (Nclass) for a
-subject increase from top to bottom.  Also, every subject is assigned a
+detected lenses (top row of panels) and missed lenses (bottom row of panels)
+from \StageOne of \sw. Every subject is assigned a
 prior probability $P_0=2\times10^{-4}$ (grey dashed line) and starts at
-the middle of the trajectory plot. The $P$ value of a subject is updated
+the middle of the trajectory plot. The number of classifications (Nclass) for a
+subject increases from top to bottom (subjects move down the trajectory plots
+as they are classified).  The $P$ value of a subject is updated
 with every classification from the volunteer.  If a volunteer identifies
@@
 the left. A subject is accepted if it crosses the blue-dashed line
-marking the ($P_{\rm acc thresh}=0.95$) on the right and is rejected, if
+marking the ($P_{\rm acc thresh}=0.95$) on the right. It is rejected if
 it crosses the red-dashed line marking the $P_{\rm rej thresh}=10^{-7}$
@@
 sample and its current probability. Thus, for a given current
-probability, high power volunteers will change the $P$ by a large factor
-compared to the low power volunteers. This is evident in the trajectory
-plots as large and small distances in between the consequent points
+probability, some volunteers will change the $P$ by a large factor
+compared to others. This is evident in the trajectory
+plots, which show both large and small distances between consecutive points
 which we refer to as kicks. Comparison of the kick sizes between the
-detected and the missed lenses suggests that the missed lenses do not
-have as many volunteers giving large kicks. We also note that most of
+detected and the missed lenses suggests that {\it the missed lenses do not
+have as many volunteers giving large kicks}. We also note that most of
 the large kicks seen in the trajectories of the missed lenses seem to be
-moving the subjects to the right. In other words, the high power
+moving the subjects to the right. In other words, certain ``high power''
 volunteers are mostly classifying them as subjects with lens candidates.
@@
 histogram on the right of \Fref{fig:detmis}. Qualitatively, there are
-four types of volunteers making classifications - those causing positive
-large kicks (correct classifications by high power volunteers), those
+four types of volunteers making classifications: those causing large, positive
+kicks (correct classifications by high power volunteers), those
 causing positive small kicks (correct classifications by low power
@@
 four histograms in the figure correspond to these four types of
-volunteers for each sample (that is, detected or missed). The kick size
-is small if $\Delta log{P} = \log{P_{\rm current}} - \log{P_{\rm
+volunteers for each sample (that is, detected or missed). In this plot,
+the kick size
+is defined as small if
+$\Delta log{P} = \log{P_{\rm current}} - \log{P_{\rm
 previous}} < \Delta\log{P}_{\rm cut}$ (chosen as 1.2) and is large
@@
 
-Some of the key differences are i) the ratio of positive large kicks to
-positive small kicks for the detected sample is higher than the missed
-sample suggesting that the fraction of high power volunteers is large
-for the detected sample ii) in terms of Nclass, the missed sample is
-dominated by volunteers causing negative small kicks whereas for the
-detected sample there is a comparable contribution from three types of
-volunteers - positive small and large kicks and negative small kicks.
-iii) the Nclass from volunteers with negative large kicks are lower, both
-for the detected and the missed samples. This is consistent with our
-expectation that high power volunteers should not be making incorrect
-classifications. Therefore, lack of high power volunteers classifying
-the missed lenses seems to be one of the major factors.
-
-We rerun SWAP for \StageOne where we use classifications from volunteers
-who produce $\Delta \log{P} > 1.2$ only. This obviously means reducing
-the total Nclass per subject by a large fraction. As a result, we also
-need to change the $P_{\rm acc thresh}$ which is chosen to be 0.1 and we
-find that about a third of the missed lenses are detected while all the
-previously detected lenses remain detected too. The others simply do not
-have enough classifications from volunteers producing large positive
-kicks. Thus, it may be possible to detect more promising candidates if
-we preferentially show the rejected systems to a few high power
-volunteers. We understand that changing the rejection and acceptance
-thresholds will likely increase the rate of FPs along with improved
-completeness. After testing on a subsample of both \StageOne and
-\StageTwo FPs, we find that a small fraction of FPs are rejected when
-only classifications with $\Delta \log{P}>1.2$ only are considered.
-Therefore, we think it is worth adopting the new strategy in the future
-runs of SWAP in future lens searches.
+Some of the key differences are as follows.  i) The ratio of  large positive
+kicks to small positive kicks for the detected sample is higher than in the
+missed sample, suggesting that the fraction of high power volunteers is large
+for the detected sample.  ii) The number of classifications received by the
+missed sample is dominated small negative kicks. In contrast, for the detected
+sample there are comparable contributions from all three of small, positive
+kicks, large, positive kicks, and small, negative kicks. iii) The number of
+classifications providing large negative kicks is lower for both the detected
+and the missed samples. This is consistent with our expectation that high power
+volunteers should not be making incorrect classifications.
+We conclude that one of the major factors in the \SW system missing lenses is
+a lack of high power classifications.
+
+As a demonstration, we re-ran SWAP for \StageOne using only  classifications
+that produced large kicks, with $|\Delta \log{P}| > 1.2$.  This obviously meant
+reducing the total number of classifications per subject by a large fraction.
+As a result, we also needed to change the $P_{\rm acc thresh}$. Choosing this to
+be 0.1, we found that about a third of the lenses that had previously been
+missed were now detected, while all the previously detected lenses were again
+detected. The remaining missed lenses simply do not have enough classifications
+from volunteers producing large positive kicks. This experiment shows that it
+may be possible to increase the  \sw completeness  by preferentially showing
+certain rejected systems -- those that  had never received a high power
+classification --  to  volunteers capable of making such classifications.
+
+Changing the rejection and acceptance
+thresholds will likely increase the rate of false positives along with improved
+completeness.
+% After testing on a subsample of both \StageOne and
+% \StageTwo FPs, we find that a small fraction of FPs are rejected when
+% only only classifications with $|\Delta \log{P}|>1.2$ are considered.
+% Therefore, we think it is worth adopting the new strategy in the future
+% runs of SWAP in future lens searches.
+This will need to be further quantified before detailed recommendations can be
+made. However, dynamically assigning certain subjects to volunteers according to
+various measures of their skill seems like a fruitful line of investigation when
+seeking to improve the system performance in future.
 
@@
 \caption{ \label{fig:detmis}
-Examples of trajectories of some known lenses (top-left: detected and
-bottom-left: missed) at \StageOne and histogram of the known lenses for
-different types of volunteers (right). Among the sample of missed
+Left: Examples of \StageOne trajectories of some known lenses.
+Upper panels show detected
+lenses, lower panels show missed lenses (false negatives). Right:
+Histogram of classification power received by known lenses.
+Among the sample of missed
 lenses, most classifications are from the low power volunteers

### 2015-05-09 doc/sw-cfhtls.tex
Done conclusions. Some rewording #203

@@
 We report the discovery of gravitational lens candidates from the
-the first \sw lens search. In this search, volunteers are shown
+the first \sw lens search. In this search, volunteers were shown
 $g-r-i$ color images of random regions of the sky taken by the CFHT Legacy
-Survey. The aim of this blind lens search is to find lenses that have been
+Survey. The aim of this blind lens search was to find lenses that had been
 missed by previous searches done on the \cfhtls with lens finding
-algorithms. In this search, we use a training sample to train the
-volunteers and calibrate their performance which helps us in more
-efficient pruning of the lens candidates. The training sample has
-simulated lenses, duds and FPs. In this paper, we describe the details
-of the training sample generated and tuned for the \cfhtls data.
-Volunteers receive feedback messages when they click or fail to click on
-the training images during live classification of real images which
-helps them remain focused and improve their performance over time. More
-details about the design of \sw system and how it works are given in the
-companion paper, \PaperOne.
-
-The blind lens search in the \cfhtls is done in two stages: \StageOne and
-\StageTwo. In \StageOne, volunteers inspected $\sim$ 430 000 images and
-selected a smaller sample of $\sim$ 3000 images with interesting lens
-candidates. In \StageTwo, after a careful reinspection of the candidates
-from \StageOne, a smaller pool of more pure sample of $\sim$~500
-candidates is obtained. In the next step, the images are graded by three
-lens experts (AM, AV and PJM) producing candidates with quality flags
-ranging from possibly a lens to almost certainly a lens.
-
-In this paper, we present the new \sw sample and compare it
+algorithms.
+The search was carried out in two stages.
+In \StageOne, volunteers inspected $\sim$ 430,000 images, and
+selected a smaller sample of $\sim$ 3000 images as having interesting lens
+candidates. In \StageTwo, after a careful second inspection of the candidates
+from \StageOne, a purer sample of $\sim$~500
+candidates was obtained. In a final step, these images were inspected by three
+of us (AM, AV and PJM) to produce a sample of candidates with grades
+ranging from possibly a lens (1) to almost certainly a lens (3).
+In this paper, we presented this new \sw sample and compared it
 with the previously known samples from two robotic searches from the
-\cfhtls namely, the \rf and \af. More detailed description and analyses
-of the new sample such as spectroscopic confirmation and mass modelling
-analyses will be presented in a subsequent \sw paper (Verma et al., in
-prep.).
-
-Below, we give some of our conclusions from the first \sw lens search
-and the comparison with robotic searches:
+\cfhtls, namely, \rf and \af.
+
+Our conclusions are as follows:
 \begin{itemize}
@@
 
-\item We present a sample of {\bf 59 new} gravitational lens candidates
-out of which {\bf 29} are more promising systems. These candidates received
-averaged grades, G$\ge$1.3 from three experts where 1-possibly, a lens,
-2-probably, a lens and 3-certainly, a lens. In addition, among the
-G$\ge$1.3 sample, we find 83 lens candidates from the various samples
+\item We present a sample of {\bf 29 new} gravitational lens candidates,
+and an additional 30 medium grade systems. These 59 candidates received
+averaged grade G$\ge$1.3 from three experts follwing the scale
+where 1 means possibly, 2 means
+probably, and 3 means certainly, a lens. In addition, among the
+G$\ge$1.3 sample, we re-discovered 83 lens candidates from various samples
 published in the literature.
 
-\item Compared to the sample of robotically (the \rf and \af) detected
-lens candidates, the \sw sample finds lens systems with similar range in
-the lens redshift and properties of the lensed images such as the total
-magnitude and the Einstein radii. However, the \sw search being a purely
-visual one cannot find some of the \rf-identified-lensed images with
-sub-arcsecond $R_{\rm E}$ because the flux of the typically faint
-lensed images is obscured by the flux from bright lensing galaxies. The
-\rf finds these candidates because it works with lensing
-galaxy-subtracted images.
-
-\item Qualitatively, the \sw sample finds lens systems with different
+\item Compared to the sample of \rf and \af robotically detected
+lens candidates, the \sw sample finds lens systems with similar properties,
+including the range of
+lens redshifts, lensed image total
+magnitudes, and Einstein radii. However, having only displayed images without
+the lens galaxy light subtracted, the \sw sample does not contain
+many of the \rf-identified-lensed images with
+sub-arcsecond $R_{\rm E}$, just because the flux of the typically faint
+lensed images is obscured by the flux from bright lensing galaxies.
+
+\item Qualitatively, \sw seems to have found lens systems with different
 types of lensing galaxies, for example, elliptical, spiral (face on and
@@
 \item Based on the known sample of lenses and lens candidates, we find
-that we lose a very small fraction of them as we go from \StageOne to
-\StageTwo. In other words, it is more important to improve the lens
-detection efficiency right at \StageOne to increase the overall
-completeness of the final lens sample
-
-\item From the sample of known lenses, \sw missed about 40~per~cent at \StageOne.
-Among the missed sample of about 20 lenses, roughly half of them are
-visually difficult to identify because most of them are faint with small
-image separations which are identified through the \rf
-
-\item If we use the classifications from the high power volunteers alone
-at \StageOne, then we recover over 30~per~cent of the lenses from the missed
-sample. Thus, it is possible to improve the completeness of lenses by
-changing the strategy of when and who is shown an image.
+that we lose a very small fraction of them during \StageTwo refinement.
+It is more important to improve the lens
+detection sensitivity at the initial \StageOne classification step.
+About 40\% of the previously known lenses (20 in total) were missed at \StageOne.
+Roughly half of these missing lenses were found to be galaxy-scale \rf
+systems, with faint arcs blended with the bright lens galaxies.
+
+\item It is possible to improve the \sw completeness by
+changing the strategy of when and who is shown an image: only using high power
+classifications recovers 30\% of the missing lenses.
 
@@
 
-The discovery of several new candidates through the first \sw lens
+The discovery of many new lens candidates through the first \sw lens
 search has demonstrated that the citizen scientists have successfully
-taught themselves to identify lenses within a short span of time and
-that they have found lens candidates which the algorithms failed to
-discover.  However, the upcoming and planned imaging surveys such as the
-DES, HSC and LSST will have formidable amount of data. Any one approach
+taught themselves to identify lenses within a short span of time.
+They have found lens candidates which the algorithms failed to
+discover.  Upcoming and planned wide-field imaging surveys such as the
+DES, HSC and LSST will provide formidable amounts of data. Any one approach
 for finding lenses is likely going to be inefficient. Thus, combining
 robotic methods for pre-selection with the citizen science approach for
-visual screening will be an optimal choice for finding lenses in these
+visual screening could be a good strategy for finding lenses in these
 large imaging surveys.
@@
 \multicolumn{11}{p{18cm}}{
-{\bf The redshifts with $^s$ are spectroscopic estimates taken from SDDS Data
+{\bf The redshifts with $^s$ are spectroscopic estimates taken from SDSS Data
 Release 12 whenever available unambiguously.} The column Comments has two
@@
 \endlastfoot
-SW19 & CFHTLS J020642.0$-$095157 &  31.67504 &  $-$9.86584 &  0.2 & 21.4 &  0.9 &  2.0 & ASW0001ld7 &  0.8 &  A,R   \\
-SW8 & CFHTLS J020648.0$-$065639 &  31.70031 &  $-$6.94430 &  0.8 & 21.0 &  1.3 &  2.3 & ASW00099ed &  0.4 &  A,E   \\
-SW43 & CFHTLS J020810.7$-$040220 &  32.04497 &  $-$4.03891 &  1.0 & 21.6 &  1.8 &  1.3 & ASW0001c3j &  0.7 &  A,R   \\
-SW9 & CFHTLS J020832.1$-$043315 &  32.13396 &  $-$4.55429 &  1.0 & 21.9 &  1.6 &  2.3 & ASW0002asp &  1.0 &  A,R   \\
-SW10 & CFHTLS J020848.2$-$042427 &  32.20110 &  $-$4.40751 &  0.8 & 21.6 &  1.1 &  2.3 & ASW0002bmc &  0.9 &  D,D   \\
-SW11 & CFHTLS J020849.8$-$050429 &  32.20784 &  $-$5.07494 &  0.8 & 21.3 &  0.9 &  2.3 & ASW0002qtn &  1.0 &  A,R   \\
-SW44 & CFHTLS J021021.5$-$093415 &  32.58981 &  $-$9.57109 &  0.4 & 19.0 &  2.7 &  1.3 & ASW0002k40 &  0.4 &  D,S   \\
-SW30 & CFHTLS J021057.9$-$084450 &  32.74148 &  $-$8.74745 &  0.45$^s$ &  0.0 &  2.5 &  1.7 & ASW0002p8y &  0.4 &  A,G   \\
-SW20 & CFHTLS J021221.1$-$105251 &  33.08810 & $-$10.88106 &  0.3 & 18.2 &  1.8 &  2.0 & ASW0002dx7 &  0.8 &  D,E/S   \\
-SW45 & CFHTLS J021225.2$-$085211 &  33.10511 &  $-$8.86973 &  0.76$^s$ & 20.5 &  2.1 &  1.3 & ASW00024id &  1.0 &  R,R   \\
-SW46 & CFHTLS J021317.6$-$084819 &  33.32341 &  $-$8.80549 &  0.5 & 20.6 &  1.3 &  1.3 & ASW00024q6 &  0.4 &  A,R/E   \\
-SW31 & CFHTLS J021514.6$-$092440 &  33.81089 &  $-$9.41115 &  0.72$^s$ & 21.1 &  2.6 &  1.7 & ASW00021r0 &  0.4 &  A,R/G   \\
-SW32 & CFHTLS J022359.8$-$083651 &  35.99955 &  $-$8.61439 &  0.0 &  0.0 &  3.1 &  1.7 & ASW0004iye &  0.4 &  A,E   \\
-SW12 & CFHTLS J022406.1$-$062846 &  36.02558 &  $-$6.47963 &  0.4 & 20.1 &  0.9 &  2.3 & ASW0003wsu &  0.7 &  A,E   \\
-SW1 & CFHTLS J022409.5$-$105807 &  36.03978 & $-$10.96885 &  0.0 &  0.0 &  4.8 &  3.0 & ASW0004dv8 &  1.0 &  A,G   \\
-SW21 & CFHTLS J022533.3$-$053204 &  36.38882 &  $-$5.53460 &  0.57$^s$ & 20.4 &  3.6 &  2.0 & ASW0004m3x &  0.4 &  A,R/G   \\
-SW22 & CFHTLS J022716.4$-$105602 &  36.81856 & $-$10.93410 &  0.4 & 17.8 &  1.8 &  2.0 & ASW0009ab8 &  0.7 &  A,E/G   \\
-SW33 & CFHTLS J022745.2$-$062518 &  36.93868 &  $-$6.42183 &  0.6 & 21.3 &  1.2 &  1.7 & ASW0003s0m &  0.5 &  A,R   \\
-SW13 & CFHTLS J022805.6$-$051733 &  37.02362 &  $-$5.29266 &  0.4 & 19.2 &  1.4 &  2.3 & ASW00047ae &  1.0 &  Q,E   \\
-SW47 & CFHTLS J022843.0$-$063316 &  37.17942 &  $-$6.55465 &  0.5 & 19.9 &  1.8 &  1.3 & ASW0003r6c &  0.3 &  D/A,E   \\
-SW23 & CFHTLS J023008.6$-$054038 &  37.53591 &  $-$5.67744 &  0.50$^s$ & 20.4 &  1.9 &  2.0 & ASW0003r61 &  0.5 &  A,E   \\
-SW14 & CFHTLS J023123.2$-$082535 &  37.84682 &  $-$8.42663 &  0.0 & 0.0 &  1.2 &  2.3 & ASW0004xjk &  0.3 &  A,R   \\
-SW24 & CFHTLS J023315.2$-$042243 &  38.31334 &  $-$4.37886 &  0.7 & 20.4 &  1.0 &  2.0 & ASW00050sk &  0.8 &  A,R   \\
-SW34 & CFHTLS J023453.5$-$093032 &  38.72321 &  $-$9.50892 &  0.5 & 20.3 &  0.7 &  1.7 & ASW00051ld &  0.3 &  A,D   \\
-SW35 & CFHTLS J084833.2$-$044051 & 132.13847 &  $-$4.68085 &  0.8 & 21.1 &  0.9 &  1.7 & ASW0004wgd &  0.7 &  A,R   \\
-SW15 & CFHTLS J084841.0$-$045237 & 132.17084 &  $-$4.87720 &  0.3 & 19.5 &  1.0 &  2.3 & ASW0004nan &  1.0 &  A,E   \\
-SW48 & CFHTLS J090219.0$-$053923 & 135.57947 &  $-$5.65666 &  0.0 &  0.0 &  2.0 &  1.3 & ASW0000g95 &  1.0 &  A,R/E   \\
-SW36 & CFHTLS J090248.4$-$010232 & 135.70204 &  $-$1.04243 &  0.4 & 19.7 &  1.4 &  1.7 & ASW000096t &  0.6 &  D,E   \\
-SW25 & CFHTLS J090308.2$-$043252 & 135.78449 &  $-$4.54789 &  0.0 &  0.0 &  1.3 &  2.0 & ASW00007mq &  0.6 &  D,D   \\
-SW49 & CFHTLS J090319.4$-$040146 & 135.83105 &  $-$4.02971 &  0.0 & 20.6 &  1.2 &  1.3 & ASW00007ls &  0.5 &  A,R/E   \\
-SW50 & CFHTLS J090333.2$-$005829 & 135.88869 &  $-$0.97490 &  0.0 &  0.0 &  2.1 &  1.3 & ASW00008a0 &  1.0 &  A/D,E/G   \\
-SW51 & CFHTLS J135724.8+561614 & 209.35374 &  56.27066 &  0.36$^s$ &  0.0 &  2.6 &  1.3 & ASW0006e0o &  0.9 &  D,E   \\
-SW26 & CFHTLS J135755.8+571722 & 209.48268 &  57.28971 &  0.8 & 21.4 &  0.9 &  2.0 & ASW0005ma2 &  0.8 &  A,R   \\
-SW52 & CFHTLS J140027.9+541028 & 210.11636 &  54.17455 &  0.6 &  0.0 &  1.2 &  1.3 & ASW0006a07 &  0.6 &  Q,R/E   \\
-SW16 & CFHTLS J140030.2+574437 & 210.12601 &  57.74371 &  0.38$^s$ & 18.8 &  2.0 &  2.3 & ASW0009bp2 &  0.6 &  A,E   \\
-SW2 & CFHTLS J140522.2+574333 & 211.34261 &  57.72587 &  0.52$^s$ & 20.3 &  1.0 &  2.7 & ASW000619d &  0.7 &  A,R   \\
-SW17 & CFHTLS J140622.9+520942 & 211.59581 &  52.16169 &  0.7 & 21.3 &  1.2 &  2.3 & ASW0005rnb &  0.7 &  A,R   \\
-SW27 & CFHTLS J141432.9+534004 & 213.63716 &  53.66788 &  0.7 & 22.1 &  1.0 &  2.0 & ASW0006jh5 &  0.8 &  A,R   \\
-SW53 & CFHTLS J141518.9+513915 & 213.82903 &  51.65420 &  0.29$^s$ & 18.9 &  3.0 &  1.3 & ASW00070vl &  0.8 &  D,E   \\
-SW3 & CFHTLS J142603.2+511421 & 216.51375 &  51.23935 &  0.0 &  0.0 &  4.4 &  2.7 & ASW0006mea &  0.7 &  A,G   \\
-SW54 & CFHTLS J142620.8+561356 & 216.58699 &  56.23230 &  0.5 & 19.9 &  1.3 &  1.3 & ASW0007sez &  0.8 &  A/R,S   \\
-SW55 & CFHTLS J142652.8+560001 & 216.72004 &  56.00044 &  0.0 &  0.0 &  1.5 &  1.3 & ASW0007t5y &  1.0 &  R,R   \\
-SW56 & CFHTLS J142843.5+543713 & 217.18153 &  54.62036 &  0.4 & 20.3 &  1.3 &  1.3 & ASW0007pga &  0.6 &  D,D   \\
-SW4 & CFHTLS J142934.2+562541 & 217.39261 &  56.42807 &  0.51$^s$ & 19.9 &  5.9 &  2.7 & ASW0009cjs &  0.8 &  A,G   \\
-SW28 & CFHTLS J143055.9+572431 & 217.73332 &  57.40883 &  0.60$^s$ & 20.1 &  1.6 &  2.0 & ASW0007xrs &  0.9 &  A,R/G   \\
-SW37 & CFHTLS J143100.2+564603 & 217.75124 &  56.76750 &  0.0 &  0.0 &  1.2 &  1.7 & ASW00086xq &  0.8 &  A,E   \\
-SW38 & CFHTLS J143353.6+542310 & 218.47357 &  54.38624 &  0.65$^s$ & 20.7 &  1.8 &  1.7 & ASW0009cp0 &  0.7 &  A,E   \\
-SW5 & CFHTLS J143454.4+522850 & 218.72702 &  52.48080 &  0.62$^s$ & 20.5 &  4.4 &  2.7 & ASW0007k4r &  0.4 &  Q,G/R   \\
-SW6 & CFHTLS J143627.9+563832 & 219.11636 &  56.64249 &  0.53$^s$ & 20.2 &  1.5 &  2.7 & ASW0008swn &  0.9 &  A,D   \\
-SW57 & CFHTLS J143631.5+571131 & 219.13155 &  57.19215 &  0.7 & 22.0 &  1.3 &  1.3 & ASW0008pag &  0.6 &  D/A,R   \\
-SW58 & CFHTLS J143651.6+530705 & 219.21503 &  53.11832 &  0.58$^s$ & 20.2 &  3.1 &  1.3 & ASW0007iwp &  0.7 &  A,E/G   \\
-SW18 & CFHTLS J143658.1+533807 & 219.24246 &  53.63550 &  0.61$^s$ & 20.3 &  0.9 &  2.3 & ASW0007hu2 &  0.6 &  D,D   \\
-SW29 & CFHTLS J143838.1+572647 & 219.65887 &  57.44645 &  0.8 & 21.3 &  1.1 &  2.0 & ASW0008qsm &  0.9 &  A,R   \\
-SW59 & CFHTLS J143950.6+544606 & 219.96101 &  54.76858 &  0.73$^s$ &  0.0 &  1.7 &  1.3 & ASW00085cp &  0.4 &  A,G/R   \\
-SW39 & CFHTLS J220215.2+012124 & 330.56348 &   1.35667 &  0.31$^s$ & 18.0 &  4.6 &  1.7 & ASW0005qiz &  0.5 &  rA,G   \\
-SW7 & CFHTLS J220256.8+023432 & 330.73691 &   2.57581 &  0.48$^s$ &  0.0 &  6.8 &  2.7 & ASW0007e08 &  0.8 &  A,G   \\
-SW40 & CFHTLS J221306.1+014708 & 333.27579 &   1.78561 &  0.0 & 17.8 &  1.4 &  1.7 & ASW0008wmr &  0.9 &  A,S   \\
-SW41 & CFHTLS J221519.7+005758 & 333.83212 &   0.96615 &  0.4 & 20.8 &  1.0 &  1.7 & ASW0008xbu &  0.8 &  A,D   \\
-SW42 & CFHTLS J221716.5+015826 & 334.31894 &   1.97394 &  0.1 & 22.0 &  1.0 &  1.7 & ASW00096rm &  1.0 &  A/R,R   \\
+SW19 & CFHTLS\,J020642.0$-$095157 &  31.67504 &  $-$9.86584 &  0.2 & 21.4 &  0.9 &  2.0 & ASW0001ld7 &  0.8 &  A,R   \\
+SW8  & CFHTLS\,J020648.0$-$065639 &  31.70031 &  $-$6.94430 &  0.8 & 21.0 &  1.3 &  2.3 & ASW00099ed &  0.4 &  A,E   \\
+SW43 & CFHTLS\,J020810.7$-$040220 &  32.04497 &  $-$4.03891 &  1.0 & 21.6 &  1.8 &  1.3 & ASW0001c3j &  0.7 &  A,R   \\
+SW9  & CFHTLS\,J020832.1$-$043315 &  32.13396 &  $-$4.55429 &  1.0 & 21.9 &  1.6 &  2.3 & ASW0002asp &  1.0 &  A,R   \\
+SW10 & CFHTLS\,J020848.2$-$042427 &  32.20110 &  $-$4.40751 &  0.8 & 21.6 &  1.1 &  2.3 & ASW0002bmc &  0.9 &  D,D   \\
+SW11 & CFHTLS\,J020849.8$-$050429 &  32.20784 &  $-$5.07494 &  0.8 & 21.3 &  0.9 &  2.3 & ASW0002qtn &  1.0 &  A,R   \\
+SW44 & CFHTLS\,J021021.5$-$093415 &  32.58981 &  $-$9.57109 &  0.4 & 19.0 &  2.7 &  1.3 & ASW0002k40 &  0.4 &  D,S   \\
+SW30 & CFHTLS\,J021057.9$-$084450 &  32.74148 &  $-$8.74745 &  0.45$^s$ &  0.0 &  2.5 &  1.7 & ASW0002p8y &  0.4 &  A,G   \\
+SW20 & CFHTLS\,J021221.1$-$105251 &  33.08810 & $-$10.88106 &  0.3 & 18.2 &  1.8 &  2.0 & ASW0002dx7 &  0.8 &  D,E/S   \\
+SW45 & CFHTLS\,J021225.2$-$085211 &  33.10511 &  $-$8.86973 &  0.76$^s$ & 20.5 &  2.1 &  1.3 & ASW00024id &  1.0 &  R,R   \\
+SW46 & CFHTLS\,J021317.6$-$084819 &  33.32341 &  $-$8.80549 &  0.5 & 20.6 &  1.3 &  1.3 & ASW00024q6 &  0.4 &  A,R/E   \\
+SW31 & CFHTLS\,J021514.6$-$092440 &  33.81089 &  $-$9.41115 &  0.72$^s$ & 21.1 &  2.6 &  1.7 & ASW00021r0 &  0.4 &  A,R/G   \\
+SW32 & CFHTLS\,J022359.8$-$083651 &  35.99955 &  $-$8.61439 &  0.0 &  0.0 &  3.1 &  1.7 & ASW0004iye &  0.4 &  A,E   \\
+SW12 & CFHTLS\,J022406.1$-$062846 &  36.02558 &  $-$6.47963 &  0.4 & 20.1 &  0.9 &  2.3 & ASW0003wsu &  0.7 &  A,E   \\
+SW1  & CFHTLS\,J022409.5$-$105807 &  36.03978 & $-$10.96885 &  0.0 &  0.0 &  4.8 &  3.0 & ASW0004dv8 &  1.0 &  A,G   \\
+SW21 & CFHTLS\,J022533.3$-$053204 &  36.38882 &  $-$5.53460 &  0.57$^s$ & 20.4 &  3.6 &  2.0 & ASW0004m3x &  0.4 &  A,R/G   \\
+SW22 & CFHTLS\,J022716.4$-$105602 &  36.81856 & $-$10.93410 &  0.4 & 17.8 &  1.8 &  2.0 & ASW0009ab8 &  0.7 &  A,E/G   \\
+SW33 & CFHTLS\,J022745.2$-$062518 &  36.93868 &  $-$6.42183 &  0.6 & 21.3 &  1.2 &  1.7 & ASW0003s0m &  0.5 &  A,R   \\
+SW13 & CFHTLS\,J022805.6$-$051733 &  37.02362 &  $-$5.29266 &  0.4 & 19.2 &  1.4 &  2.3 & ASW00047ae &  1.0 &  Q,E   \\
+SW47 & CFHTLS\,J022843.0$-$063316 &  37.17942 &  $-$6.55465 &  0.5 & 19.9 &  1.8 &  1.3 & ASW0003r6c &  0.3 &  D/A,E   \\
+SW23 & CFHTLS\,J023008.6$-$054038 &  37.53591 &  $-$5.67744 &  0.50$^s$ & 20.4 &  1.9 &  2.0 & ASW0003r61 &  0.5 &  A,E   \\
+SW14 & CFHTLS\,J023123.2$-$082535 &  37.84682 &  $-$8.42663 &  0.0 & 0.0 &  1.2 &  2.3 & ASW0004xjk &  0.3 &  A,R   \\
+SW24 & CFHTLS\,J023315.2$-$042243 &  38.31334 &  $-$4.37886 &  0.7 & 20.4 &  1.0 &  2.0 & ASW00050sk &  0.8 &  A,R   \\
+SW34 & CFHTLS\,J023453.5$-$093032 &  38.72321 &  $-$9.50892 &  0.5 & 20.3 &  0.7 &  1.7 & ASW00051ld &  0.3 &  A,D   \\
+SW35 & CFHTLS\,J084833.2$-$044051 & 132.13847 &  $-$4.68085 &  0.8 & 21.1 &  0.9 &  1.7 & ASW0004wgd &  0.7 &  A,R   \\
+SW15 & CFHTLS\,J084841.0$-$045237 & 132.17084 &  $-$4.87720 &  0.3 & 19.5 &  1.0 &  2.3 & ASW0004nan &  1.0 &  A,E   \\
+SW48 & CFHTLS\,J090219.0$-$053923 & 135.57947 &  $-$5.65666 &  0.0 &  0.0 &  2.0 &  1.3 & ASW0000g95 &  1.0 &  A,R/E   \\
+SW36 & CFHTLS\,J090248.4$-$010232 & 135.70204 &  $-$1.04243 &  0.4 & 19.7 &  1.4 &  1.7 & ASW000096t &  0.6 &  D,E   \\
+SW25 & CFHTLS\,J090308.2$-$043252 & 135.78449 &  $-$4.54789 &  0.0 &  0.0 &  1.3 &  2.0 & ASW00007mq &  0.6 &  D,D   \\
+SW49 & CFHTLS\,J090319.4$-$040146 & 135.83105 &  $-$4.02971 &  0.0 & 20.6 &  1.2 &  1.3 & ASW00007ls &  0.5 &  A,R/E   \\
+SW50 & CFHTLS\,J090333.2$-$005829 & 135.88869 &  $-$0.97490 &  0.0 &  0.0 &  2.1 &  1.3 & ASW00008a0 &  1.0 &  A/D,E/G   \\
+SW51 & CFHTLS\,J135724.8$+$561614 & 209.35374 &    56.27066 &  0.36$^s$ &  0.0 &  2.6 &  1.3 & ASW0006e0o &  0.9 &  D,E   \\
+SW26 & CFHTLS\,J135755.8$+$571722 & 209.48268 &    57.28971 &  0.8 & 21.4 &  0.9 &  2.0 & ASW0005ma2 &  0.8 &  A,R   \\
+SW52 & CFHTLS\,J140027.9$+$541028 & 210.11636 &    54.17455 &  0.6 &  0.0 &  1.2 &  1.3 & ASW0006a07 &  0.6 &  Q,R/E   \\
+SW16 & CFHTLS\,J140030.2$+$574437 & 210.12601 &    57.74371 &  0.38$^s$ & 18.8 &  2.0 &  2.3 & ASW0009bp2 &  0.6 &  A,E   \\
+SW2  & CFHTLS\,J140522.2$+$574333 & 211.34261 &    57.72587 &  0.52$^s$ & 20.3 &  1.0 &  2.7 & ASW000619d &  0.7 &  A,R   \\
+SW17 & CFHTLS\,J140622.9$+$520942 & 211.59581 &    52.16169 &  0.7 & 21.3 &  1.2 &  2.3 & ASW0005rnb &  0.7 &  A,R   \\
+SW27 & CFHTLS\,J141432.9$+$534004 & 213.63716 &    53.66788 &  0.7 & 22.1 &  1.0 &  2.0 & ASW0006jh5 &  0.8 &  A,R   \\
+SW53 & CFHTLS\,J141518.9$+$513915 & 213.82903 &    51.65420 &  0.29$^s$ & 18.9 &  3.0 &  1.3 & ASW00070vl &  0.8 &  D,E   \\
+SW3  & CFHTLS\,J142603.2$+$511421 & 216.51375 &    51.23935 &  0.0 &  0.0 &  4.4 &  2.7 & ASW0006mea &  0.7 &  A,G   \\
+SW54 & CFHTLS\,J142620.8$+$561356 & 216.58699 &    56.23230 &  0.5 & 19.9 &  1.3 &  1.3 & ASW0007sez &  0.8 &  A/R,S   \\
+SW55 & CFHTLS\,J142652.8$+$560001 & 216.72004 &    56.00044 &  0.0 &  0.0 &  1.5 &  1.3 & ASW0007t5y &  1.0 &  R,R   \\
+SW56 & CFHTLS\,J142843.5$+$543713 & 217.18153 &    54.62036 &  0.4 & 20.3 &  1.3 &  1.3 & ASW0007pga &  0.6 &  D,D   \\
+SW4  & CFHTLS\,J142934.2$+$562541 & 217.39261 &    56.42807 &  0.51$^s$ & 19.9 &  5.9 &  2.7 & ASW0009cjs &  0.8 &  A,G   \\
+SW28 & CFHTLS\,J143055.9$+$572431 & 217.73332 &    57.40883 &  0.60$^s$ & 20.1 &  1.6 &  2.0 & ASW0007xrs &  0.9 &  A,R/G   \\
+SW37 & CFHTLS\,J143100.2$+$564603 & 217.75124 &    56.76750 &  0.0 &  0.0 &  1.2 &  1.7 & ASW00086xq &  0.8 &  A,E   \\
+SW38 & CFHTLS\,J143353.6$+$542310 & 218.47357 &    54.38624 &  0.65$^s$ & 20.7 &  1.8 &  1.7 & ASW0009cp0 &  0.7 &  A,E   \\
+SW5  & CFHTLS\,J143454.4$+$522850 & 218.72702 &    52.48080 &  0.62$^s$ & 20.5 &  4.4 &  2.7 & ASW0007k4r &  0.4 &  Q,G/R   \\
+SW6  & CFHTLS\,J143627.9$+$563832 & 219.11636 &    56.64249 &  0.53$^s$ & 20.2 &  1.5 &  2.7 & ASW0008swn &  0.9 &  A,D   \\
+SW57 & CFHTLS\,J143631.5$+$571131 & 219.13155 &    57.19215 &  0.7 & 22.0 &  1.3 &  1.3 & ASW0008pag &  0.6 &  D/A,R   \\
+SW58 & CFHTLS\,J143651.6$+$530705 & 219.21503 &    53.11832 &  0.58$^s$ & 20.2 &  3.1 &  1.3 & ASW0007iwp &  0.7 &  A,E/G   \\
+SW18 & CFHTLS\,J143658.1$+$533807 & 219.24246 &    53.63550 &  0.61$^s$ & 20.3 &  0.9 &  2.3 & ASW0007hu2 &  0.6 &  D,D   \\
+SW29 & CFHTLS\,J143838.1$+$572647 & 219.65887 &    57.44645 &  0.8 & 21.3 &  1.1 &  2.0 & ASW0008qsm &  0.9 &  A,R   \\
+SW59 & CFHTLS\,J143950.6$+$544606 & 219.96101 &    54.76858 &  0.73$^s$ &  0.0 &  1.7 &  1.3 & ASW00085cp &  0.4 &  A,G/R   \\
+SW39 & CFHTLS\,J220215.2$+$012124 & 330.56348 &     1.35667 &  0.31$^s$ & 18.0 &  4.6 &  1.7 & ASW0005qiz &  0.5 &  rA,G   \\
+SW7  & CFHTLS\,J220256.8$+$023432 & 330.73691 &     2.57581 &  0.48$^s$ &  0.0 &  6.8 &  2.7 & ASW0007e08 &  0.8 &  A,G   \\
+SW40 & CFHTLS\,J221306.1$+$014708 & 333.27579 &     1.78561 &  0.0 & 17.8 &  1.4 &  1.7 & ASW0008wmr &  0.9 &  A,S   \\
+SW41 & CFHTLS\,J221519.7$+$005758 & 333.83212 &     0.96615 &  0.4 & 20.8 &  1.0 &  1.7 & ASW0008xbu &  0.8 &  A,D   \\
+SW42 & CFHTLS\,J221716.5$+$015826 & 334.31894 &     1.97394 &  0.1 & 22.0 &  1.0 &  1.7 & ASW00096rm &  1.0 &  A/R,R   \\
 \end{longtable}

### 2015-05-09 doc/sw-cfhtls.tex
Appendices done. #203

@@
 lenses. In spite of some mild qualitative differences, both set of
-trajectories have very similar behaviour. The trajectories in panel e
+trajectories have very similar behaviour. The trajectories in panel (e)
 are typical of this sample in terms of Nclass and the dominance of short
-negative kicks. Panel f represents a small fraction of this sample
-where the kicks are only short and negative. The panel g shows how some
+negative kicks. Panel (f) represents a small fraction of this sample
+where the kicks are only short and negative. The panel (g) shows how some
 lenses receive a bunch of large positive kicks which are led to
-rejection by still mostly negative short kicks. Finally, panel h shows
+rejection by still mostly negative short kicks. Finally, panel (h) shows
 those cases of lenses which received almost sufficient number of large
@@
 
-The {\bf top-left panels of \Fref{fig:detmis}} show the detected lenses. The cases shown with green trajectories
+The {\bf top-left panels of \Fref{fig:detmis}} show the detected lenses.
+The cases shown with green trajectories
 in each panel can be thought of counterparts of the trajectories of the
@@
 volunteers are different. Most detected lenses are similar to the case
-in panel a that are detected within a few classifications coming from
-large positive kicks.  Panel b represents a few odd cases which are
-dominated mainly by short positive kicks. Panel c shows a lens getting
-more classifications but do not reach the detection or rejection
+in panel (a) that are detected within a few classifications coming from
+large positive kicks.  Panel (b) represents a few odd cases which are
+dominated mainly by small positive kicks. Panel (c) shows a lens getting
+more classifications, but not reaching the detection or rejection
 thresholds because of the tug between positive and negative kicks mostly
-from experienced volunteers.  Panel d represents the extreme cases when
+from experienced volunteers.  Panel (d) represents two extreme cases when
 the images are on the verge of being rejected but are saved thanks to a
@@
 subject does not contain a lens). For instance, given a subject
-(not) containing a lens, a volunteer with high ($P_{\rm D}$) $P_{\rm L}$
-implies a large (negative) positive kick irrespective the value of
-($P_{\rm L}$) $P_{\rm D}$ as shown in the (right most) middle panel of
+containing a lens, a volunteer with high $P_{\rm L}$
+implies a large (negative) positive kick irrespective of the value of
+$P_{\rm D}$, as shown in the middle panel of
 \Fref{fig:skilldlnp}. However, large (negative) positive kicks are

### 2015-05-09 doc/sw-cfhtls.tex
Consistency in confusion matrix notation, keywords. Closes #105. #203

@@
 $2\times10^{-4}$ of containing a lens system. Every volunteer
-is assigned an agent characterised by a $2\times2$ confusion matrix,
+is assigned an agent characterised by a $2\times2$ confusion matrix~$\CM$,
 which quantifies the volunteer's ability to correctly classify an image
-as containing a lens ($P_L$) or not containing a lens ($P_D$). The values of
+as containing a lens ($\PL = P_L$) or not containing a lens ($\PD = P_D$).
+The values of
 these confusion matrix elements are determined based on the performance of the

### 2015-05-10 doc/sw-cfhtls.tex
one more commit before Phil's final edits

--- 2015-05-09 doc/sw-cfhtls.tex
@@
 previously published lens samples from the \cfhtls. We generated a training sample,
-consisting of simulated lenses, duds and impostors, in order to
+consisting of simulated lenses, duds and false positives, in order to
 aid the \sw volunteers in the process of finding lenses. We give details of this
@@
 \citet{Sygnet2010} carried out a search for edge-on disk galaxy lenses in the
-\cfhtls WIDE. They identified galaxies, using \sextractor, which
+\cfhtls WIDE. They identified galaxies, using {\sc SExtractor}, which
 had $18<i<21$ and inclination angle $<25\,^{\circ}$. After applying few more
@@
 the lensing galaxies from the galaxy-scale lenses are distinct from the central
-galaxies of group-scale lenses which are described in the following section.
+galaxies of groups-scale lenses which are described in the following section.
 
@@
 curves show the theoretical prediction assuming an SIS model at galaxy-scales
-and a total (NFW+Hernquist) model at group scales taken from \citep{More2012}.
+and a total (NFW+Hernquist) model at groups-scales taken from \citep{More2012}.
 }
@@
 galaxy lenses (see \Tref{tab:thresh}) and are reported within ``()'', if
-different for group scales. The simulated lensed images are then added
+different for group-scales. The simulated lensed images are then added
 to the real \cfhtls~images with the BGGs as the center by following
@@
 In \Fref{fig:remudist}, we show the Einstein radius ($R_{\rm E}$) distribution for the
-galaxy-scale and group-scale simulated lenses. For comparison, we give
+galaxy-scale and groups-scale simulated lenses. For comparison, we give
 the expected distributions (blue solid curves) for an SIS like density
-profile at galaxy-scales and an NFW+Hernquist profile at group scales.
+profile at galaxy-scales and an NFW+Hernquist profile at groups-scales.
 The theoretical curves are taken from \citet{More2012} wherein the
 models are explained in detail. We note that the model we adopt at
-the group scale also includes SIS or SIE components for the group members
+groups-scale also includes SIS or SIE components for the group members
 unlike the theoretical prediction. The theoretical curves have arbitrary
@@
 
+% PHIL IS HERE
+
 \subsection{Limitations of the simulated lens sample}
@@
 the uncertainties in the model parameters. Comments from citizen
-scientists were very helpful in order to identify some of these failures, which
-make up roughly 5\% of the simulated sample.\footnote{This estimate is
-based on the number of \#simfail tags from TALK, the discussion forum.}
+scientists were very helpful in order to sort some of these failures.
 Here, we describe some of the cases or aspects in which the simulations
-were known to have failed to look realistic.
-
-The parameters required by the models' various scaling relations
+were known to be unrealistic. The fraction of such unrealistic cases in the 
+simulated sample is small (roughly 5 percent)\footnote{This estimate is
+based on the number of \#simfail tags from \Talk, the discussion forum.}.
+
+The parameters required by various scaling relations and the models
 primarily depend on the photometry of the galaxies, groups and quasars
-detected in the survey. For galaxy-scale lenses, the fainter or higher redshift
-lensing galaxies tend to have poor photometric redshift
-measurements. Consequently these galaxies were occasionally assigned the wrong
-luminosity and velocity dispersion estimates, resulting in
+detected in the survey. For galaxy-scale lenses, the lensing galaxies at
+higher redshifts or which are fainter have poor photometric redshift
+measurements. Consequently, these galaxies are assigned wrong
+luminosity and velocity dispersion estimates. This then results in
 simulated lenses which look implausible or unrealistic.  For example,
 the lensed images for some of the failed simulations have larger image
-separation than would be expected from the luminosity and/or size of the
-galaxy.
-
-At group scales, the magnitudes and photometric redshifts were used when defining
-the group membership. Therefore, errors in redshift estimates occasionally
-generated galaxy
-groups having member galaxies with unrealistically dissimilar properties.
-In some cases,
-low redshift spiral galaxies were incorrectly assigned high redshift.
+separation than what one would expect from the luminosity and/or size of the
+galaxy. We roughly expect mass to follow light, so more massive galaxies
+typically look brighter and/or bigger.
+
+At group-scales, the photometric and redshift estimates are used when defining
+the group membership. Therefore, errors in redshift estimates generate galaxy
+groups with BGG or member galaxies with dissimilar properties. In some cases,
+low redshift spiral galaxies have been incorrectly assigned high redshift.
 Spiral galaxies are typically less massive and low redshift spiral galaxies are
 unlikely to act as gravitational lenses. Hence, some such instances
-did not appear convincing, as the lensed images again did not have the expected
-configurations or separations.
-
-We also use a single component to describe the light distribution of the
+do not appear convincing or the lensed images do not have the expected
+configuration or image separations.
+
+We also use a single component to describe the light profiles of
 background galaxies. This is clearly not the most accurate description for
-galaxies, especially for the irregular star-forming galaxies which comprise
-a significant fraction
+galaxies, especially, star-forming galaxies which form a significant fraction
 of the lensed galaxy population. Star-forming galaxies have complex structures
 such as star forming knots, spiral arms, bars and disks. The simulated lensed
-images do not display these features. This is fine for most cases seen in
-images taken from ground based telescopes such as the CFHT
+images do not display these features. This is fine for most cases or
+mostly for images taken from ground based telescopes such as the CFHT
 {\bf but sometimes the profiles of the lensed arcs can appear very symmetric along the
@@
 
-\section{Training sample: Duds and Impostors}
+\section{Training sample: Duds and False positives}
 \label{sec:dfp}
@@
 Citizen scientists need training not only to identify gravitational
-lenses, but also to reject images which either contain no lenses, or contain
-objects which could be mistaken for lenses. Hence, in addition to the simulated
-lenses, we added a sample of ``duds'' and ``impostors'' to the training
+lenses, but also to reject images which either have no lenses or have
+objects which are lens impostors. Hence, in addition to the simulated
+lenses, we added a sample of duds and false positives to the training
 sample. Duds are images which have been visually inspected by experts
-and confirmed to contain no lenses. Impostors are systems
-which look like lenses but are not, for example, spiral galaxies,
-starforming galaxies, chance alignments of features arranged in a
+and confirmed to contain no lenses. False positives (FPs) are systems
+which have features similar to lenses but they are not lenses in reality, for example, spiral galaxies,
+star$-$forming galaxies, chance alignments of features arranged in a
 lensing configuration and stars.
@@
 We selected a sample of 450 duds for the \StageOne classification in \sw
-and a sample of 500 impostors for the \StageTwo inspection. The
-sample of impostors was selected from the candidates which passed
-the \StageOne of \sw. We note that this is the first time we have a
-systematically compiled sample of visually inspected impostors by
-the \sw volunteers and categorized by the science team. We produced an
-additional larger sample of a few thousand false positive detections
-by scanning through the
+and a sample of 500 false positives for the \StageTwo\footnote{Please see \Sref{sec:swap} and Paper 1 for a description of \StageOne and \StageTwo} inspection. The
+sample of false positives was selected from the candidates which passed
+the \StageOne of \sw. We note that this is the first time, we have a
+systematically compiled sample of visually inspected false positives by
+the \sw volunteers and categorized by the science team. We produce
+additional larger sample of a few thousand FPs by scanning through the
 low probability images after the completion of \StageTwo. All of these
@@
 Distribution of different types of candidates as a function of the
-posterior probability $P$. The types of the candidates are the false
+posterior probability P. The types of the candidates are the false
 positives (FPs), the new candidates and the known candidates. The new
-and known candidates have higher detection rate for higher values of $P$,
+and known candidates have higher detection rate for higher values of P,
 as expected.}
@@
 \label{sec:swap}
-
-\sw works as a single unified system which uses the method of visual
+The \sw works as a single unified system which uses the method of visual
 inspection to find gravitational lenses. For the first \sw lens search,
 the volunteers were shown images at two stages. At \StageOne, volunteers
-were asked to carry out a rapid inspection to select lens candiates
+are requested to undertake a rapid inspection to select lens candiates
 ranging from possible lenses to almost certain lenses. At \StageTwo,
-volunteers were asked to inspect the candidates from \StageOne and select
-only promising lens candidates. A daily snapshot of the classifications
-performed by volunteers was provided to the science team every night.
-This daily batch was analyzed by the Space Warps Analysis Pipeline
+volunteers carefully inspect the candidates from \StageOne and select
+only promising lens candidates. A daily snapshot of classifications
+performed by volunteers are provided to the science team every night.
+This daily batch is analyzed by the Space Warps Analysis Pipeline
 (SWAP). The philosophy and the details of SWAP are described in detail
-in \PaperOne. Here, we briefly summarize how it works.
-
-Each subject (image cutout) is assigned a prior probability of
-$2\times10^{-4}$ of containing a lens system. Every volunteer
+in \PaperOne, here we briefly summarize how it works.
+
+Each subject (or image cutout) is assigned a prior probability of
+$2\times10^{-4}$ to contain a lens system. Every volunteer
 is assigned an agent characterised by a $2\times2$ confusion matrix,
 which quantifies the volunteer's ability to correctly classify an image
-as containing a lens ($P_L$) or not containing a lens ($P_D$). The values of
-these confusion matrix elements are determined based on the performance of the
+to contain a lens ($P_L$) or to not contain a lens ($P_D$). The values of
+the confusion matrix are determined based on the performance of the
 volunteer on the training sample, specifically, $P_L$ (and $P_D$) is
-determined based on the fraction of simulated lenses (and, respectively, duds)
+determined based on the fraction of simulated lenses (and duds)
 correctly classified. After every classification, the agent updates the
-probability of the classified subject based on the volunteer's classification
-and the confusion matrix, according to Bayes' theorem.
-The agent's confusion matrix is updated after the
+prior probability of the classified subject based on the volunteer's classification
+and the confusion matrix, according to the Bayes theorem.
+Note that the volunteer's confusion matrix is updated after the
 classification of every training image. The thresholds for the
@@
 not contain one} can be chosen in SWAP. Those images which cross
-these threshold values are ``retired'', and are not subsequently shown to the
-volunteers. In this way, the crowd can use its time efficiently in
-inspecting previously unclassified subjects.
+these threshold values are retired and are not subsequently shown to the
+volunteers, so that volunteers can use their time efficiently to
+classify previously unclassified subjects.
 
 SWAP was run nightly during \StageOne in order to retire subjects and inject new
-ones in to the classification stream. The subjects that passed the detection
-threshold at the end of \StageOne were served again at \StageTwo for careful
-re-inspection. Each subject, after \StageTwo, has a posterior
-probability $P$. In the ideal case, all images containing lenses will have high $P$
-values and those without lenses will have low $P$ values. In practice, we expect a
-small fraction of the real lenses (or non-lenses) to be assigned low (or high) $P$
-values, thereby decreasing the completeness (or purity) of the final lens
+ones in to the classification stream. The subjects that passed the acceptance
+threshold at the end of \StageOne are served again at \StageTwo for careful
+reinspection. Each subject, after \StageTwo, has an associated posterior
+probability P. In the ideal case, all images containing lenses will have high P
+values and those without lenses will have low P values. In practice, we expect a
+small fraction of the real lenses (or non-lenses) to be assigned low (or high) P
+values thereby, decreasing the completeness (or purity) of the final lens
 sample. As this is the first lens search with \sw, we want to find a
-threshold $P$ value which will result in acceptable levels of completeness and
+threshold P value which will result in acceptable levels of completeness and
 purity of the final sample of lens candidates.
 
-To achieve this, we selected a total of 665 subjects with $P>0.3$
-which were then visually inspected by three of us (as ``lens experts'',
- AM, AV, PJM).  Each images was assigned a grade~$G$ on a scale of 0 to 3,
-representing those images
-0) unlikely to contain a lens, 1) possibly containing a lens, 2) probably
-containing a lens and 3) almost certainly containing a
-lens. The final sample of \sw-\cfhtls lens candidates was
-then produced by selecting candidates above a threshold on the
-average value of these grades, as described in the next section.
+We decided to inspect the top few hundreds of images from a catalog with
+descending P values as a reasonable sample size for visual inspection.
+We choose P$>0.3$ for which we find a total of 665 subjects in the
+catalog. These images were then visually inspected by three lens experts
+(AM, AV, PJM).  The images are assigned grades on a scale of 0 to 3,
+thus dividing the subjects into candidates with the quality flag -
+unlikely lens, possibly a lens, probably a lens and almost certainly a
+lens, respectively. The final sample of \sw-\cfhtls lens candidates is
+then produced by selecting candidates above some threshold on the
+averaged grades as described in the next section.
 
@@
 
-In this section, we describe the \cfhtls \sw candidate lens sample.
-We find a total of 141 candidates with
-$G\ge1.3$ (medium-high grade), of which {\bf 59} are new
+In this section, we describe the \sw-\cfhtls lens sample (henceforth,
+called the \sw lens sample). We find a total of 141 candidates with
+G$\ge1.3$ (medium-high probability sample) out of which {\bf 59} are new
 systems. This sample is further divided as follows. We have a total of
-50 candidates with $1.3\le$G$<2$ (medium grade), of
+50 candidates with $1.3\le$G$<2$ (medium probability sample) out of
 which 30 are new. The quality of candidates in this category is such
-that at least one of the inspectors thought the candidate was
+that at least one of the inspectors thought the candidate is most
 probably a lens (that is, a grade of 2) and a second inspector thought
-that it was possibly a lens (that is, a grade of 1). Among our high
-grade sample ($G\ge$2), there are a total of 91 candidates, of
+this is possibly a lens (that is, a grade of 1). Among our high
+probability sample (G$\ge$2), there are a total of 91 candidates out of
 which {\bf 29} are new. In this category, the minimum grade by all of the
-inspectors was 2, suggesting that the candidates are probably or almost
-certainly lenses according to all three inspectors. To avoid
-duplication, further information on \sw candidates that were previously
-identified in the literature will be made available at
-\texttt{http://spacewarps.org/\#/projects/CFHTLS/}, while the sample of new lens
-candidates with $G\ge 1.3$ (medium-high probability) is presented in
-this paper (see \Sref{sec:results:newcand}).
-
-We also find a total of 288 (and {\bf 245} new) candidates with averaged grade
-$0<$G$<1.3$ (low grade), which means that at
-least one of the inspector thought the candidate was possibly a lens, and
-in the best cases, all three inspectors thought the candidate was possibly
+inspectors was 2 suggesting that the candidates are probably or almost
+certainly lenses according to all of the inspectors. To avoid
+duplication, only the newly discovered lens
+candidates with G$\ge 1.3$ (medium-high probability) are presented in
+this paper (see \Sref{sec:results:newcand}), and further information on \sw-selected candidates that were previously
+identified in the literature (see \Sref{sec:data:kls}) will be made available at
+\texttt{http://spacewarps.org/\#/projects/CFHTLS/}.
+
+We find a total of 288 (and {\bf 245} new) candidates with averaged grade
+$0<$G$<1.3$ (low probability sample) which means - in the worst case, at
+least one of the inspector thought the candidate is possibly a lens and
+in the best case, all three inspectors thought the candidate is possibly
 a lens (that is, a grade of 1)\footnote{If grades from the inspectors
@@
 at \texttt{http://spacewarps.org/\#/projects/CFHTLS/}. Note that if all of the
-inspectors gave a grade of 0 to a candidate, then it was discarded from
+inspectors gave a grade of 0 to a candidate, then it is discarded from
 the sample.
 
-In \Tref{tab:stats}, we give overall statistics of the systems
+In Table~\ref{tab:stats}, we give overall statistics of the systems
 detected at \StageOne and \StageTwo. We give the total number of
@@
 each stage. We find that all of the confirmed lenses found
-at \StageOne are also recovered at \StageTwo; a small fraction of
+at \StageOne are also recovered at \StageTwo whereas a small fraction of
 the known lens candidates are rejected at \StageTwo. From the visually
@@
 the sample of new \sw lens candidates increased the sample of total
-\cfhtls lens candidates by over 50~per~cent. However, we find that 42\% of known
-lenses were missed at \StageOne: we return to the discussion of these false
-negatives below.
+\cfhtls lens candidates by over 50~per~cent.
 
 In \Fref{fig:stackP}, we plot the distribution of false positives and
-the high grade lens candidates,
-as a function of the $P$ value assigned by SWAP at the end of \StageTwo.
+the high probability lens candidates, categorized by the lens experts,
+as a function of the P value assigned by SWAP at the end of \StageTwo.
 On average, the fraction of lens candidates is indeed an increasing
-function of $P$. This shows that the \sw generated $P$ values for the
+function of P. This shows that the \sw generated P values for the
 subject are roughly correlated with the expert grades albeit with quite
-some scatter.  We note that below $P\sim0.75$,
+some scatter.  We note that from P$\sim$0.75 onwards to lower P values,
 the fraction of false positives starts to exceed the fraction of real
 lens candidates. This could be a good threshold to choose to maximize
-the purity of the final sample. However, choosing
-$P=0.3$ gives a completeness of 100\% for the ``known
-lens'' sample instead of 67\% for $P=0.75$. Therefore, the new sample
-should also have increased completeness; expert
-grading then allows us to increase the purity of the sample.
+the purity of the final sample. However, we go with the choice of
+P~$=$~0.3 as this gives a better completeness of 100~per~cent for the ``known
+lens'' sample instead of 67~per~cent for P~$=$~0.75. Therefore, the new sample
+should also have increased completeness which combined with expert
+grading allows us to achieve further purity of our sample.
 
@@
 Number  & 128 & 34 & 107  & 34  \\
-Fraction  & & & & \\
-of total recovered & 29\% & 58\% & 25\% & 58\%  \\
-$P_{\rm thresh}$ & 0.95 & 0.95 & 0.3 & 0.3 \\
+Percentage  & & & & \\
+of recovery & 29 & 58 & 25 & 58  \\
+P$_{\rm thresh}$ & 0.95 & 0.95 & 0.3 & 0.3 \\
 {\bf Expert Grade (G)} & $-$ & $-$ & 1.3 & 1.3 \\
@@
 Number  & {\bf 59} & 141 &  & \\
-Fraction & & & & \\
-of detections & 13\% & 33\% &  & \\
-$P_{\rm thresh}$ & 0.3 & 0.3 &  & \\
+Percentage & & & & \\
+of detection & 13 & 33 &  & \\
+P$_{\rm thresh}$ & 0.3 & 0.3 &  & \\
 {\bf Expert Grade (G)} & 1.3 & 1.3 & 1.3 & 1.3 \\
@@
 {AC}-- All (known and new) lens candidates  \\
-$P_{\rm thresh}$ -- systems with Posterior probability~$P$ above this threshold are selected \\
+P$_{\rm thresh}$ -- systems with Posterior probability P above this threshold are selected \\
 Note: For KC and KL, Percentages are with respect to the known
@@
 
-We give basic information about the final sample of {\bf 59} new medium grade
-lens candidates found by \sw in
-\Tref{tab:swcands}. We report the candidates with a \sw ID and Name
-of the lens system. We give their positions (RA, Dec), photometric
+We give basic information about the final sample of {\bf 59} new lens
+candidates (ranked with medium-high probability) found by \sw in
+Table~\ref{tab:swcands}. We report the candidates with a \sw ID and Name
+of the lens system. We give their positions (Ra, Dec), photometric
 redshift ($z_{phot}$), $i$ band magnitude of the lensing galaxy,
-averaged grade~$G$ from the lens experts, zoo ID (identifier used in
-TALK), $P$ value at \StageTwo and a visual categorization of the type of
+averaged grade G from the lens experts, zoo ID (identifier used in
+\Talk), P value at \StageTwo and a visual categorization of the type of
 lensed images and the lensing galaxy in the ``Comments'' column in
-\Tref{tab:swcands}. Whenever available the lens properties are
-taken from the \cfhtls photometric catalog \citep{Coupon2009}; otherwise,
-for the lens galaxy positions, the reported values were measured
+Table~\ref{tab:swcands}. Whenever available the lens properties are
+taken from the \cfhtls photometric catalog \citep{Coupon2009} otherwise
+for the lens galaxy positions, the reported values are measured
 manually. The visual categorization of the lens type is only suggestive
@@
 
-We show images of our new sample in \Fref{fig:lc}. The panels are arranged
-first in the descending order of their grades, and within each grade, in
-ascending order
-of RA. As the first lens search was a blind search with no
+We show images of our new sample in \Fref{fig:lc} which is arranged
+first in the decreasing order of their grades and then increasing order
+of their positions. As the first lens search was a blind search with no
 preselection of candidates from any algorithm, we find various types of
 lenses, as expected from such a search. The final sample consists of
-both galaxy and group-scale lens candidates. There are detections of
+both galaxy and groups-scale lens candidates. There are detections of
 elongated arcs and some interesting point-like quasar lensed images.
-Most of them are brighter in the bluer $g$ band, but some candidates brighter
-in the redder $i$ band are also found. Since the robotic lens searches
-focused on the blue lensed features, they are likely to miss
+Most of them are brighter in bluer $g$ band but some candidates brighter
+in the redder $i$ band are also found. Since robotic lens searches often
+look for blue colored lensed features, they are very much likely to miss
 such interesting lens candidates. We did not find any examples of
-exotic lens candidates from the visually inspected $P>0.3$ sample.
-There
+exotic lens candidates from the visually inspected P$>0.3$ sample. There
 may be some more interesting candidates that were missed either at
@@
 
-The new \sw lens sample presented here illustrates some of
-the advantages of having
+The new \sw lens sample presented here shows the advantages of having
 citizen scientists find lenses through visual inspection. An algorithm,
@@
 uses either geometry or flux information from an image. On the other
-hand, citizen scientists can interpolate over or
-extrapolate beyond the basic selection criteria provided to them.  For
+hand, citizen scientists can do amazing amount of interpolation or
+extrapolation over the basic selection criteria provided to them.  For
 example, the lower blue arc in SW7 is split by a small red galaxy.  An
@@
 into smaller arclets which then falls below the minimum length or area
-allowed for an arc to be detected. Human inspectors have no
-problem in interpolating over the broken blue arc over the red galaxy,
-understanding that it is a single long arc. The system SW20 has
-point-like lensed images which cannot be detected by arc finding
-algorithm, whereas the ring finding algorithm may have missed this because of
-the atypical color and structure of the galaxy. Detection of red arcs, for
-example, as seen in the SW38 candidate, show how the volunteers
-extrapolate on the color parameter: the training sample contains
-predominantly blue arcs, because the source colors were drawn from realistic
-observed distributions.
+allowed for an arc to be typically detected. Human brains have no
+problem in interpolating over the broken blue arc over the red galaxy
+and understand that it is a single long arc. The system {\bf SW20} has
+point-like lensed images which cannot be detected by arc-finding
+algorithm whereas the ring finding algorithm may miss this because of
+atypical color and structure of the galaxy. Detection of red arcs, for
+example, as seen in the SW38 candidate show how the volunteers
+extrapolate on the color parameter because the training sample mostly
+has blue arcs since this is the typical expectation.
 
@@
 new candidates missed by some of these algorithms demonstrates that the
-\sw system is functioning well, the self-taught citizen scientists
-reaching parts of discovery space that the robots did not.
+\sw system is functioning well and the self-taught citizen scientists
+have managed to beat the robots in some sense.
 
@@
 
-In the subsequent sections, we compare various properties of the lens
+In the subsequent sections, we make comparison of various properties of the lens
 candidates. Here, we describe how we extract or measure these properties, namely,
@@
 subtracted \citep[for details, see][]{Gavazzi2014}. Here, we use the flux
-of the lensed images measured by \sextractor from the scaled
+of the lensed images measured by {\sc SExtractor} from the scaled
 difference image, that is, $g-\alpha i$ and convert it to the $g$ band
@@
 the \af and the \sw sample, we integrate the flux in the image pixels
-identified by \af or \sextractor.
+identified by \af or {\sc SExtractor}.
 
@@
 we use the value of the input parameter of the lens model for the $R_{\rm E}$.
-For group-scale lenses, since the lens model is multi-component, we
+For groups-scale lenses, since the lens model is multi-component, we
 need to determine the $R_{\rm E}$ from the image positions. We use those
@@
 these angular image separations. For the \rf sample, we use the peak
-position of the lensed images measured by running \sextractor on
+position of the lensed images measured by running {\sc SExtractor} on
 the scaled difference image. We calculate the image separation from the
-lens center as a rough estimate of the $R_{\rm E}$. For the \af (SARCS)
+lens center as an estimate of the $R_{\rm E}$. For the \af (SARCS)
 sample, we use the same definition as above except that the peak
@@
 sample, the same definition is used where the peak positions are
-identified either with \af or \sextractor.
+identified either with \af or {\sc SExtractor}.
 
@@
 
-We noe determine the fraction of the known sample of lenses that were recovered
+We determine what fraction of the known sample of lenses are recovered
 by \sw. Note that this sample corresponds to the \rf and \af samples
-combined, as mentioned in \Sref{sec:data:kls}. In \Tref{tab:stats},
-we show that $\sim25-30\%$ of the known lens candidates, and
-$\sim60\%$ of the known lenses were found at \StageOne. Eighty-four
+combined, as mentioned in \Sref{sec:data:kls}. In Table~\ref{tab:stats},
+we show that $\sim$~25$-$30~per~cent of the known lens candidates and
+$\sim$~60~per~cent of the known lenses are found at \StageOne. Eighty-four
 percent of the known lens candidates and \textbf{all} of the known lenses 
@@
 We find that most of the confirmed lenses and candidates that are missed
-by \sw are systems from the \rf sample, with fainter arcs and smaller $R_{\rm E}$.
-The main reason why \rf found such candidates
-is because it involves subtracting the light from the lens galaxy,
-making it easiere to detect the lensed images during both the automated
-object-finding and the visual inspection and classification
-phases. This approach naturally improves the detection
+by \sw are systems with fainter arcs and smaller $R_{\rm E}$ and they
+come from the \rf sample. The main reason why \rf found such candidates
+is because their team used lensing galaxy-subtracted images to detect
+the presence of the lensed images both during the automated
+object-finding phase and during the visual inspection and classification
+of their candidates. This approach naturally improves the detection
 efficiency at smaller $R_{\rm E}$ and for fainter systems. The \sw
-volunteers were not shown any galaxy-subtracted images. Showing
-galaxy-subtracted images might be a better strategy to adopt for future
-lens searches at galaxy-scales with \sw. In
-\Sref{sec:fn} below, we further explore and discuss why some of the confirmed
+volunteers were not shown any galaxy-subtracted images. However, showing
+galaxy subtracted images might be a better strategy to adopt for future
+lens searches at galaxy-scales with \sw. In the Discussion
+\Sref{sec:fn}, we further explore and discuss why some of the confirmed
 lenses are missed by \sw.
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
 \subsection{Image separation distribution}
@@
 
-Indeed, we have found 59 new medium and high grade
-lens candidates that were not known
+Indeed, we have found {\bf 59} new lens candidates that were not known
 before. In \Fref{fig:isd}, we show the image separation distribution for
@@
 corresponding to three density profiles, namely, isothermal sphere (IS),
-NFW \citep{Navarro1997} and a ``Total'' profile which has NFW and Hernquist
+NFW \citep{Navarro1997} and Total profile which has NFW and Hernquist
 profiles combined with an adiabatically contracting model for dark
 matter component \citep{Gnedin2004}. These curves are taken from
-\citet{More2012}, which gives details of the calculation of these
+\citet{More2012} which gives details of the calculation of these
 predictions.  With the updated sample of lens candidates, we confirm our
@@
 \includegraphics[scale=1.2]{isd_cfhtls_sw.pdf}
-\caption{ \label{fig:isd} Image separation distribution (ISD). Comparing theoretical
+\caption{ \label{fig:isd} Image separation distribution. Comparing theoretical
 predictions (solid curves) with the \cfhtls known lens samples (green)
@@
 sample of new and the known lens candidates discovered from \sw alone is
-shown in blue. The new updated profile of the ISD (magenta) is
+shown in blue. The new updated profile of the isd (magenta) is
 consistent with our previous measurements and strengthens our conclusion
@@
 Finding gravitational lenses is a difficult and complex task. No single
-method is perfect, each method has some advantages over the other. It
+method is perfect. Each method has some advantages over the other. It
 may be the case that a single method may never be the best method for
@@
 \subsection{Comparison of the \rf, \sw and \af samples}
+Here, we compare the properties of the lens candidates from each sample
+to understand if there are any clear differences between them. We
+consider the lens redshift, the total flux of the lensed images and the
+Einstein radii of the systems for this purpose.
 
 In \Fref{fig:zlmgre}, we show the lens redshift and the arc flux
-measured in $g$-band AB magnitude as a function of the Einstein radius for the \rf
+measured in $g$ AB mag as a function of the Einstein radius for the \rf
 (green), the \af (red) and the \sw sample (new candidates only in blue
@@
 
-Since in this project \sw enabled a visual search based on simple color
-composite images drawn directly from the survey,
-it was difficult to detect many lens
+Since \sw is visual based search, it is difficult to detect many lens
 candidates with a small $R_{\rm E}$ in the presence of a bright lensing
-galaxy. In contrast, the \rf sample was
+galaxy. While this is true for algorithms too, the \rf team adopted a
+different method to circumvent this problem whose goal was to find
+galaxy-scale lenses which have small $R_{\rm E}$. The \rf sample is
 generated by working with lensing galaxy$-$subtracted images and this
 led to increased detections of small image separation candidates. The
-\sw interface did not show any galaxy subtracted images and hence,
+\sw {\bf interface did not show} any galaxy subtracted images and hence,
 this results in a quantitative difference between the \sw and the \rf
@@
 
-The \af is capable of finding some small image
-separation lenses, but a lower limit at $R_{\rm E}=2\arcsec$ was imposed
+The \af, on the other hand, is capable of finding smaller image
+separation lenses but a lower limit at $R_{\rm E}=2\arcsec$ was imposed
 by the \af team to simplify the selection function of their sample.
@@
 between the \sw candidates and the \af samples. As noted earlier, the
-\rf dominates the small $R_{\rm E} (<2\arcsec)$ detections although \sw does
-find a modest number of candidates in this range. At larger $R_{\rm E}$,
+\rf dominates the small $R_{\rm E} (<2\arcsec)$ range although \sw does
+find modest number of candidates in this range. At larger $R_{\rm E}$,
 \sw sample begins to dominate and is comparable to the \af sample.  As a
 function of the arc magnitudes, all three samples have detections at all
-magnitudes and median magnitudes for all samples is around $g\sim24.5$.
+magnitudes and median magnitudes for all samples is around $g\sim$24.5.
 Relatively, the \rf sample spans a narrower range compared to the \sw
@@
 
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Why were the new \sw candidates missed by the robots?}
-
+\subsection{Why \sw candidates were missed by lens finding robots?}
 We test the \rf and \af on images centered on the new \sw candidates to
@@
 
-First, we re-ran \rf on the new \sw sample. At the beginning, a galaxy
+First, we rerun \rf on the new \sw sample. At the beginning, a galaxy
 catalog is generated based on magnitude, redshift and SED type
 \citep[see]{Gavazzi2014} to select galaxies which are most likely to act
-as lenses. We find that about 40~per~cent of the new \sw candidates failed to
-meet this initial selection criteria, for example, SW1, SW14, SW20,
-SW23, SW27 and SW30. All of the lensing galaxies are bright enough to
+as lenses. We find that about 40~per~cent of the new \sw candidates fail to
+meet this initial selection criteria, for example, {\bf SW1, SW14, SW20,
+SW23, SW27 and SW30}. All of the lensing galaxies are bright enough to
 satisfy the magnitude criterion ($i<22$). However, some of them have a
@@
 galaxies and some are edge on galaxies which could be the reason for
-these galaxies having failed the photometric redshift and SED type pre-selection.
+excluding these galaxies from the initial catalog.
 
@@
 
-In subsequent \rf steps, the flux from the galaxy is subtracted from the
+In the following steps, the flux from the galaxy is subtracted from the
 scaled difference image to enhance the visibility of the faint blue
-lensed features. An object finder is then run on this image to quantify the
-lensed image properties.
-Another $\sim$~50~per~cent of the \sw candidates could not be
+lensed features. An object finder is run on this image to quantify the
+lensed image properties. Another $\sim$~50~per~cent of the \sw candidates could not be
 detected by the object finder because properties such as the image area,
 axis ratio, magnitude/color and alignment with respect to the lensing
-galaxy were not satisfied. Some of the candidates missed at this stage
-are, for example, SW4, SW5, SW6, SW26, SW36, SW39 and SW46.
-
-Next, we re-ran the \af on the same \sw sample of new candidates. The \af
+galaxy are not satisfied. Some of the candidates missed at this stage
+are, for example, {\bf SW4, SW5, SW6, SW26, SW36, SW39 and SW46.}
+
+Next, we rerun the \af on the same \sw sample of new candidates. The \af
 is directly run on images to look for elongated arc like objects and does
@@
 Originally, the \af was run on a large image with an area of $\sim 19350
-\times 19350$ pixels$^2$. For the rerun, we worked with much smaller
-images because this is faster. However, this alters the measured
-noise and hence affects the number and type of arc detections. We find
-that about 30~per~cent of the new candidates were detected without changing any
-of the thresholds in the code, suggesting that these could have been detected by
-\af with had its noise thresholds been set differently.
+\times 19350$ pixels$^2$. For the rerun, we work with much smaller
+images because this is faster but this alters the measured
+noise and hence, affects the number and type of arc detections. We find
+that about 30~per~cent of the new candidates are detected without changing any
+of the thresholds in the code because of the change in the noise level.
 
@@
 properties such as the area, mean flux, length and curvature are
-determined. We relaxed the threshold at the segmentation stage and also relaxed
-thresholds mainly on the area of the arc. These new settings led to the detection of
+determined. We relax the threshold at the segmentation stage and also relax
+thresholds mainly on the area of the arc which leads to detection of
 about 75~per~cent of the new \sw candidates. We find that relaxing thresholds
-on other arc properties does not improve the detection rate significantly.
-
-Typically then, the \sw candidates were missed from the \af sample either
-because a) the arcs
-were fainter, b) the flux of the
-arc and the galaxy were blended together (such that the \af
-incorrectly connected part of the galaxy to the arc), c)
-the arcs were unusually short or thick, or d) the lensed images are almost
-circular or point-like (\af was not designed to detect lensed quasars).
-
-Relaxing the \af thresholds obviously increases the number of candidate arc
-detections but this also increases the false positive rate.
-For example, the number of arc candidate detections increased by a factor
-of $\sim$2 when we relaxed the thresholds in the rerun described above,
-while the number of false positives increased by a factor of $\sim$5.
-While the \af sample purity could be increased by
-cross-correlating the arc candidate positions with a putative lens
-galaxy catalog, these numbers illustrate the predicament facing automated
-lens-finding algorithms, and the continuing benefits of visual screening.
+on other arc properties does not improve the detection rate significantly
+and thus, those thresholds are left unchanged.
+
+Typically, the candidates are missed from the \af sample if a) the arcs
+are fainter in $g$ band which is used for arc detection because then the
+arc feature is at the noise level and fails detection b) the flux of the
+arc and the galaxy are blended in the $g$ band such that the \af
+incorrectly connects part of the galaxy to the arc. This results in a
+candidate with no morphological characteristics of a typical arc c)
+unusually short or thick arcs or d) if the lensed images are almost
+circular or point-like which means most of the lensed quasars images
+will be missed.
+
+Relaxing the thresholds obviously increases the number of candidate arc
+detections but this also includes a large sample of false positives.
+For example, the number of arc candidate detections increase by a factor
+of $\sim$2 when we relaxed the thresholds in the reruns described above
+whereas the number of false positives increase by a factor of $\sim$5.
+Thus, it is not recommended to relax these thresholds alone. A better
+alternative is to relax the thresholds to increase the completeness and
+cross-correlate the arc candidate positions with a galaxy catalog to
+discard those candidates which are not close to a putative lensing
+galaxy within typical radius in order to reduce the false positives.
 
@@
 \label{sec:fn}
-
-Like any lens finding method, the \sw system could potentially be failing
-to detect certain
+Like any lens finding method, the \sw system can fail to detect certain
 kinds of lenses.  We find that about 40~per~cent of the known sample of lenses
-are missed at \StageOne; no further losses were incurred during
-the \StageTwo refinement (see \Tref{tab:stats}).
-Below, we focus on the known
+are missed both at \StageOne and II (see \Tref{tab:stats}). In fact, all
+of the known lenses from \StageOne are discovered at \StageTwo which
+means that the lenses are lost already at \StageOne. Below, we focus on the known
 lens sample at \StageOne to understand why some of them are being missed
@@
 Einstein radii and faint lensed images (see \Fref{fig:compre}). Among
-the confirmed lenses from \rf, about 50~per~cent are missed. Out of the
+the confirmed lenses from the \rf, about 50~per~cent are missed. Out of the
 missed sample of 18 lenses, about half of them are visually difficult to
-detect. The other half appear to have faint blue smudges around
+detect and the other half appear to have faint blue smudges around
 galaxies which should have been easier to identify. Similarly,
@@
 is a relatively small sample of $\sim 5$ systems and visual inspection
-of them suggests that, by and large, either the lensed features are faint
+suggests that, by and large, either the lensed features are faint
 or they have odd properties which makes them difficult to identify
@@
 attempt to understand whether there is indeed a single dominant factor
-that is resulting in the loss of these lenses, or if the lenses are being
+that is resulting in the loss of these lenses or the lenses are being
 missed due to a combination of multiple reasons. Below, we consider some
@@
 \subsubsection{Number of classifications}
-
-First, we check whether the number of classifications (Nclass) is
+First, we check if the number of classifications (Nclass) is
 significantly lower for the missed sample compared to the detected one.
-Most of the lenses in the known sample (including both those that were
-detected and those that were missed)
-% have few classifications (Nclass$<$10).
-% Many of the remaining lenses have between 10 to 20
-% classifications. And, only a
-received similar numbers of classifications to the other subjects.
-A few received Nclass$>$20, possibly a result of
-continuing to remain for a long time in the database because there was
-uncertainty over whether or not to reject them.
-Overall, we do not find any difference in the number of classifications
-between the detected and the missed lenses.
+Surprisingly, most of the lenses in the known sample have few
+classifications (Nclass$<$10) which includes both the detected and
+missed lenses. Many of the remaining lenses have between 10 to 20
+classifications. And, only a few subjects have Nclass$>$20. They
+continue to remain for long in the database because these candidates are
+possibly difficult to identify. Overall, we do not find any correlation
+for the detected and the missed sample with Nclass.
 
 \subsubsection{Blind lens search}
-
-The efficiency of a visual search could potentially
-vary in different sections of an
+Efficiency of a visual search can vary in different sections of an
 image. Our eyes tend to focus usually at the center of an image and lens
 candidates close to the borders could go undetected. Therefore, it is
-important to check whether \sw could be missing some of the known lenses
+essential to test and understand if \sw is missing some of the known lenses
 because they happen to be close to the borders of the image cutouts.
@@
 From the SWAP, the image cutouts inspected by the \sw volunteers receive
-a status of detected (if $P>P_{\rm acc thresh}$), rejected (if
-$P<P_{\rm rej thresh}$) and undecided (if $P_{\rm rej thresh}< P <
-P_{\rm acc thresh}$). In \Fref{fig:comppos}, we compare the positions
+a status of detected (if P$>$P$_{\rm acc thresh}$), rejected (if
+P$<$P$_{\rm rej thresh}$) and undecided (if P$_{\rm rej thresh}<$ P $<$
+P$_{\rm acc thresh}$). In \Fref{fig:comppos}, we compare the positions
 of lenses which are detected (red), undecided (green) and rejected
@@
 
-We do not find any strong correlation in the detection rate of
-lenses as a function of their positions in the image, for either the
-simulated or the known lens sample. Thus, the completeness of the lens
-sample is most likely not significantly affected by lenses
-located close to the image borders.
-
-\subsubsection{Classification Uncertainty}
-
-Each \sw image classification is based on the markers placed by around 10
-volunteers (on average, \PaperOne). This number could be
-small enough to introduce some scatter in the system performance, arising from
-the variations between the small groups of people inspecting each subject.
-In \PaperOne we investigated the system performamce in terms of the ``Skill''
-of each agent; in \Aref{appendix:power} we define a complementary property,
-the ``Power'' of a classification to make a large difference in the probability
-$P$ of an image containing a lens. Here, we investigate whether the distribution
-of classification power is systematically
-different between the detected and missed lenses.
-
-We check how the posterior probability $P$ (see \PaperOne for the
+We do not find any strong visual correlation in the detection rate of
+lenses as a function of their positions in the image for both the
+simulated and the known lens sample. Thus, the completeness of the lens
+sample is most likely not significantly affected by whether a lens is
+located close to the border or well within the center.
+
+\subsubsection{Volunteer profile}
+
+Here, we investigate if the power\footnote{see the
+\Aref{appendix:power} for the meaning of this term and how it is
+different from the ``Skill'' defined in \PaperOne} of volunteers is systematically
+different between the sample of detected and missed lenses.
+
+We check how the posterior probability P (see \PaperOne for the
 mathematical definition) of an image or a subject to contain a lens
@@
 \Fref{fig:detmis}, we show the trajectory plots of a few examples of
-detected lenses (top row of panels) and missed lenses (bottom row of panels)
-from \StageOne of \sw. Every subject is assigned a
-prior probability $P_0=2\times10^{-4}$ (grey dashed line) and starts at
-the middle of the trajectory plot. The number of classifications (Nclass) for a
-subject increases from top to bottom (subjects move down the trajectory plots
-as they are classified).  The $P$ value of a subject is updated
+detected lenses (top left panels) and missed lenses (bottom left panels)
+from \StageOne of \sw. The number of classifications (Nclass) for a
+subject increase from top to bottom.  Also, every subject is assigned a
+prior probability P0$=2\times10^{-4}$ (grey dashed line) and starts at
+the middle of the trajectory plot. The P value of a subject is updated
 with every classification from the volunteer.  If a volunteer identifies
@@
 the left. A subject is accepted if it crosses the blue-dashed line
-marking the ($P_{\rm acc thresh}=0.95$) on the right. It is rejected if
-it crosses the red-dashed line marking the $P_{\rm rej thresh}=10^{-7}$
+marking the (P$_{\rm acc thresh}=0.95$) on the right and is rejected, if
+it crosses the red-dashed line marking the P$_{\rm rej thresh}=10^{-7}$
 on the left.
 
-The amount by which the posterior probability $P$ value of a subject will
+The amount by which the posterior probability P value of a subject will
 change depends on how well the volunteers are performing on the training
 sample and its current probability. Thus, for a given current
-probability, some volunteers will change the $P$ by a large factor
-compared to others. This is evident in the trajectory
-plots, which show both large and small distances between consecutive points
+probability, high power volunteers will change the P by a large factor
+compared to the low power volunteers. This is evident in the trajectory
+plots as large and small distances in between the consequent points
 which we refer to as kicks. Comparison of the kick sizes between the
-detected and the missed lenses suggests that {\it the missed lenses do not
-have as many volunteers giving large kicks}. We also note that most of
+detected and the missed lenses suggests that the missed lenses do not
+have as many volunteers giving large kicks. We also note that most of
 the large kicks seen in the trajectories of the missed lenses seem to be
-moving the subjects to the right. In other words, certain ``high power''
+moving the subjects to the right. In other words, the high power
 volunteers are mostly classifying them as subjects with lens candidates.
@@
 histogram on the right of \Fref{fig:detmis}. Qualitatively, there are
-four types of volunteers making classifications: those causing large, positive
-kicks (correct classifications by high power volunteers), those
+four types of volunteers making classifications - those causing positive
+large kicks (correct classifications by high power volunteers), those
 causing positive small kicks (correct classifications by low power
@@
 four histograms in the figure correspond to these four types of
-volunteers for each sample (that is, detected or missed). In this plot,
-the kick size
-is defined as small if
-$\Delta log{P} = \log{P_{\rm current}} - \log{P_{\rm
-previous}} < \Delta\log{P}_{\rm cut}$ (chosen as 1.2) and is large
-if greather than $\Delta\log{P}_{\rm cut}$.
-
-Some of the key differences are as follows.  i) The ratio of  large positive
-kicks to small positive kicks for the detected sample is higher than in the
-missed sample, suggesting that the fraction of high power volunteers is large
-for the detected sample.  ii) The number of classifications received by the
-missed sample is dominated small negative kicks. In contrast, for the detected
-sample there are comparable contributions from all three of small, positive
-kicks, large, positive kicks, and small, negative kicks. iii) The number of
-classifications providing large negative kicks is lower for both the detected
-and the missed samples. This is consistent with our expectation that high power
-volunteers should not be making incorrect classifications.
-We conclude that one of the major factors in the \SW system missing lenses is
-a lack of high power classifications.
-
-As a demonstration, we re-ran SWAP for \StageOne using only  classifications
-that produced large kicks, with $|\Delta \log{P}| > 1.2$.  This obviously meant
-reducing the total number of classifications per subject by a large fraction.
-As a result, we also needed to change the $P_{\rm acc thresh}$. Choosing this to
-be 0.1, we found that about a third of the lenses that had previously been
-missed were now detected, while all the previously detected lenses were again
-detected. The remaining missed lenses simply do not have enough classifications
-from volunteers producing large positive kicks. This experiment shows that it
-may be possible to increase the  \sw completeness  by preferentially showing
-certain rejected systems -- those that  had never received a high power
-classification --  to  volunteers capable of making such classifications.
-
-Changing the rejection and acceptance
-thresholds will likely increase the rate of false positives along with improved
-completeness.
-% After testing on a subsample of both \StageOne and
-% \StageTwo FPs, we find that a small fraction of FPs are rejected when
-% only only classifications with $|\Delta \log{P}|>1.2$ are considered.
-% Therefore, we think it is worth adopting the new strategy in the future
-% runs of SWAP in future lens searches.
-This will need to be further quantified before detailed recommendations can be
-made. However, dynamically assigning certain subjects to volunteers according to
-various measures of their skill seems like a fruitful line of investigation when
-seeking to improve the system performance in future.
+volunteers for each sample (that is, detected or missed). The kick size
+is small if $\Delta$ log(P)$=$log (P$_{\rm current}) - $log(P$_{\rm
+previous}) < \Delta$log(P)$_{\rm cut}$ (chosen as 1.2) and is large
+if greater than $\Delta$log(P)$_{\rm cut}$.
+
+Some of the key differences are i) the ratio of positive large kicks to
+positive small kicks for the detected sample is higher than the missed
+sample suggesting that the fraction of high power volunteers is large
+for the detected sample ii) in terms of Nclass, the missed sample is
+dominated by volunteers causing negative small kicks whereas for the
+detected sample there is a comparable contribution from three types of
+volunteers - positive small and large kicks and negative small kicks.
+iii) the Nclass from volunteers with negative large kicks are lower, both
+for the detected and the missed samples. This is consistent with our
+expectation that high power volunteers should not be making incorrect
+classifications. Therefore, lack of high power volunteers classifying
+the missed lenses seems to be one of the major factors.
+
+We rerun SWAP for \StageOne where we use classifications from volunteers
+who produce $\Delta$ log(P)$>1.2$ only. This obviously means reducing
+the total Nclass per subject by a large fraction. As a result, we also
+need to change the P$_{\rm acc thresh}$ which is chosen to be 0.1 and we
+find that about a third of the missed lenses are detected while all the
+previously detected lenses remain detected too. The others simply do not
+have enough classifications from volunteers producing large positive
+kicks. Thus, it may be possible to detect more promising candidates if
+we preferentially show the rejected systems to a few high power
+volunteers. We understand that changing the rejection and acceptance
+thresholds will likely increase the rate of FPs along with improved
+completeness. After testing on a subsample of both \StageOne and
+\StageTwo FPs, we find that a small fraction of FPs are rejected when
+only classifications with $\Delta$ log(P)$>1.2$ only are considered.
+Therefore, we think it is worth adopting the new strategy in the future
+runs of SWAP in future lens searches.
 
@@
 \caption{ \label{fig:detmis}
-Left: Examples of \StageOne trajectories of some known lenses.
-Upper panels show detected
-lenses, lower panels show missed lenses (false negatives). Right:
-Histogram of classification power received by known lenses.
-Among the sample of missed
+Examples of trajectories of some known lenses (top-left: detected and
+bottom-left: missed) at \StageOne and histogram of the known lenses for
+different types of volunteers (right). Among the sample of missed
 lenses, most classifications are from the low power volunteers
@@
 We report the discovery of gravitational lens candidates from the
-the first \sw lens search. In this search, volunteers were shown
+the first \sw lens search. In this search, volunteers are shown
 $g-r-i$ color images of random regions of the sky taken by the CFHT Legacy
-Survey. The aim of this blind lens search was to find lenses that had been
+Survey. The aim of this blind lens search is to find lenses that have been
 missed by previous searches done on the \cfhtls with lens finding
-algorithms.
-The search was carried out in two stages.
-In \StageOne, volunteers inspected $\sim$ 430,000 images, and
-selected a smaller sample of $\sim$ 3000 images as having interesting lens
-candidates. In \StageTwo, after a careful second inspection of the candidates
-from \StageOne, a purer sample of $\sim$~500
-candidates was obtained. In a final step, these images were inspected by three
-of us (AM, AV and PJM) to produce a sample of candidates with grades
-ranging from possibly a lens (1) to almost certainly a lens (3).
-In this paper, we presented this new \sw sample and compared it
+algorithms. In this search, we use a training sample to train the
+volunteers and calibrate their performance which helps us in more
+efficient pruning of the lens candidates. The training sample has
+simulated lenses, duds and FPs. In this paper, we describe the details
+of the training sample generated and tuned for the \cfhtls data.
+Volunteers receive feedback messages when they click or fail to click on
+the training images during live classification of real images which
+helps them remain focused and improve their performance over time. More
+details about the design of \sw system and how it works are given in the
+companion paper, \PaperOne.
+
+The blind lens search in the \cfhtls is done in two stages: \StageOne and
+\StageTwo. In \StageOne, volunteers inspected $\sim$ 430 000 images and
+selected a smaller sample of $\sim$ 3000 images with interesting lens
+candidates. In \StageTwo, after a careful reinspection of the candidates
+from \StageOne, a smaller pool of more pure sample of $\sim$~500
+candidates is obtained. In the next step, the images are graded by three
+lens experts (AM, AV and PJM) producing candidates with quality flags
+ranging from possibly a lens to almost certainly a lens.
+
+In this paper, we present the new \sw sample and compare it
 with the previously known samples from two robotic searches from the
-\cfhtls, namely, \rf and \af.
-
-Our conclusions are as follows:
+\cfhtls namely, the \rf and \af. More detailed description and analyses
+of the new sample such as spectroscopic confirmation and mass modelling
+analyses will be presented in a subsequent \sw paper (Verma et al., in
+prep.).
+
+Below, we give some of our conclusions from the first \sw lens search
+and the comparison with robotic searches:
 \begin{itemize}
@@
 
-\item We present a sample of {\bf 29 new} gravitational lens candidates,
-and an additional 30 medium grade systems. These 59 candidates received
-averaged grade G$\ge$1.3 from three experts follwing the scale
-where 1 means possibly, 2 means
-probably, and 3 means certainly, a lens. In addition, among the
-G$\ge$1.3 sample, we re-discovered 83 lens candidates from various samples
+\item We present a sample of {\bf 59 new} gravitational lens candidates
+out of which {\bf 29} are more promising systems. These candidates received
+averaged grades, G$\ge$1.3 from three experts where 1-possibly, a lens,
+2-probably, a lens and 3-certainly, a lens. In addition, among the
+G$\ge$1.3 sample, we find 83 lens candidates from the various samples
 published in the literature.
 
-\item Compared to the sample of \rf and \af robotically detected
-lens candidates, the \sw sample finds lens systems with similar properties,
-including the range of
-lens redshifts, lensed image total
-magnitudes, and Einstein radii. However, having only displayed images without
-the lens galaxy light subtracted, the \sw sample does not contain
-many of the \rf-identified-lensed images with
-sub-arcsecond $R_{\rm E}$, just because the flux of the typically faint
-lensed images is obscured by the flux from bright lensing galaxies.
-
-\item Qualitatively, \sw seems to have found lens systems with different
+\item Compared to the sample of robotically (the \rf and \af) detected
+lens candidates, the \sw sample finds lens systems with similar range in
+the lens redshift and properties of the lensed images such as the total
+magnitude and the Einstein radii. However, the \sw search being a purely
+visual one cannot find some of the \rf-identified-lensed images with
+sub-arcsecond $R_{\rm E}$ because the flux of the typically faint
+lensed images is obscured by the flux from bright lensing galaxies. The
+\rf finds these candidates because it works with lensing
+galaxy-subtracted images.
+
+\item Qualitatively, the \sw sample finds lens systems with different
 types of lensing galaxies, for example, elliptical, spiral (face on and
@@
 \item Based on the known sample of lenses and lens candidates, we find
-that we lose a very small fraction of them during \StageTwo refinement.
-It is more important to improve the lens
-detection sensitivity at the initial \StageOne classification step.
-About 40\% of the previously known lenses (20 in total) were missed at \StageOne.
-Roughly half of these missing lenses were found to be galaxy-scale \rf
-systems, with faint arcs blended with the bright lens galaxies.
-
-\item It is possible to improve the \sw completeness by
-changing the strategy of when and who is shown an image: only using high power
-classifications recovers 30\% of the missing lenses.
+that we lose a very small fraction of them as we go from \StageOne to
+\StageTwo. In other words, it is more important to improve the lens
+detection efficiency right at \StageOne to increase the overall
+completeness of the final lens sample
+
+\item From the sample of known lenses, \sw missed about 40~per~cent at \StageOne.
+Among the missed sample of about 20 lenses, roughly half of them are
+visually difficult to identify because most of them are faint with small
+image separations which are identified through the \rf
+
+\item If we use the classifications from the high power volunteers alone
+at \StageOne, then we recover over 30~per~cent of the lenses from the missed
+sample. Thus, it is possible to improve the completeness of lenses by
+changing the strategy of when and who is shown an image.
 
@@
 
-The discovery of many new lens candidates through the first \sw lens
+The discovery of several new candidates through the first \sw lens
 search has demonstrated that the citizen scientists have successfully
-taught themselves to identify lenses within a short span of time.
-They have found lens candidates which the algorithms failed to
-discover.  Upcoming and planned wide-field imaging surveys such as the
-DES, HSC and LSST will provide formidable amounts of data. Any one approach
+taught themselves to identify lenses within a short span of time and
+that they have found lens candidates which the algorithms failed to
+discover.  However, the upcoming and planned imaging surveys such as the
+DES, HSC and LSST will have formidable amount of data. Any one approach
 for finding lenses is likely going to be inefficient. Thus, combining
 robotic methods for pre-selection with the citizen science approach for
-visual screening could be a good strategy for finding lenses in these
+visual screening will be an optimal choice for finding lenses in these
 large imaging surveys.
@@
 \hline
-SW ID & Name & RA & Dec &  $z_{\rm phot}$ & $m_i$ & $R_{\rm E}$ & G & ZooID & $P$ & Comments  \\
+SW ID & Name & RA & Dec &  $z_{\rm phot}$ & $m_i$ & $R_{\rm E}$ & G & ZooID & P & Comments  \\
   &  & (deg) & (deg) &  & (mag) &  (") &  &  & & \\
@@
 \multicolumn{11}{p{18cm}}{
-{\bf The redshifts with $^s$ are spectroscopic estimates taken from SDSS Data
+{\bf The redshifts with $^s$ are spectroscopic estimates taken from SDDS Data
 Release 12 whenever available unambiguously.} The column Comments has two
@@
 \endlastfoot
-SW19 & CFHTLS\,J020642.0$-$095157 &  31.67504 &  $-$9.86584 &  0.2 & 21.4 &  0.9 &  2.0 & ASW0001ld7 &  0.8 &  A,R   \\
-SW8  & CFHTLS\,J020648.0$-$065639 &  31.70031 &  $-$6.94430 &  0.8 & 21.0 &  1.3 &  2.3 & ASW00099ed &  0.4 &  A,E   \\
-SW43 & CFHTLS\,J020810.7$-$040220 &  32.04497 &  $-$4.03891 &  1.0 & 21.6 &  1.8 &  1.3 & ASW0001c3j &  0.7 &  A,R   \\
-SW9  & CFHTLS\,J020832.1$-$043315 &  32.13396 &  $-$4.55429 &  1.0 & 21.9 &  1.6 &  2.3 & ASW0002asp &  1.0 &  A,R   \\
-SW10 & CFHTLS\,J020848.2$-$042427 &  32.20110 &  $-$4.40751 &  0.8 & 21.6 &  1.1 &  2.3 & ASW0002bmc &  0.9 &  D,D   \\
-SW11 & CFHTLS\,J020849.8$-$050429 &  32.20784 &  $-$5.07494 &  0.8 & 21.3 &  0.9 &  2.3 & ASW0002qtn &  1.0 &  A,R   \\
-SW44 & CFHTLS\,J021021.5$-$093415 &  32.58981 &  $-$9.57109 &  0.4 & 19.0 &  2.7 &  1.3 & ASW0002k40 &  0.4 &  D,S   \\
-SW30 & CFHTLS\,J021057.9$-$084450 &  32.74148 &  $-$8.74745 &  0.45$^s$ &  0.0 &  2.5 &  1.7 & ASW0002p8y &  0.4 &  A,G   \\
-SW20 & CFHTLS\,J021221.1$-$105251 &  33.08810 & $-$10.88106 &  0.3 & 18.2 &  1.8 &  2.0 & ASW0002dx7 &  0.8 &  D,E/S   \\
-SW45 & CFHTLS\,J021225.2$-$085211 &  33.10511 &  $-$8.86973 &  0.76$^s$ & 20.5 &  2.1 &  1.3 & ASW00024id &  1.0 &  R,R   \\
-SW46 & CFHTLS\,J021317.6$-$084819 &  33.32341 &  $-$8.80549 &  0.5 & 20.6 &  1.3 &  1.3 & ASW00024q6 &  0.4 &  A,R/E   \\
-SW31 & CFHTLS\,J021514.6$-$092440 &  33.81089 &  $-$9.41115 &  0.72$^s$ & 21.1 &  2.6 &  1.7 & ASW00021r0 &  0.4 &  A,R/G   \\
-SW32 & CFHTLS\,J022359.8$-$083651 &  35.99955 &  $-$8.61439 &  0.0 &  0.0 &  3.1 &  1.7 & ASW0004iye &  0.4 &  A,E   \\
-SW12 & CFHTLS\,J022406.1$-$062846 &  36.02558 &  $-$6.47963 &  0.4 & 20.1 &  0.9 &  2.3 & ASW0003wsu &  0.7 &  A,E   \\
-SW1  & CFHTLS\,J022409.5$-$105807 &  36.03978 & $-$10.96885 &  0.0 &  0.0 &  4.8 &  3.0 & ASW0004dv8 &  1.0 &  A,G   \\
-SW21 & CFHTLS\,J022533.3$-$053204 &  36.38882 &  $-$5.53460 &  0.57$^s$ & 20.4 &  3.6 &  2.0 & ASW0004m3x &  0.4 &  A,R/G   \\
-SW22 & CFHTLS\,J022716.4$-$105602 &  36.81856 & $-$10.93410 &  0.4 & 17.8 &  1.8 &  2.0 & ASW0009ab8 &  0.7 &  A,E/G   \\
-SW33 & CFHTLS\,J022745.2$-$062518 &  36.93868 &  $-$6.42183 &  0.6 & 21.3 &  1.2 &  1.7 & ASW0003s0m &  0.5 &  A,R   \\
-SW13 & CFHTLS\,J022805.6$-$051733 &  37.02362 &  $-$5.29266 &  0.4 & 19.2 &  1.4 &  2.3 & ASW00047ae &  1.0 &  Q,E   \\
-SW47 & CFHTLS\,J022843.0$-$063316 &  37.17942 &  $-$6.55465 &  0.5 & 19.9 &  1.8 &  1.3 & ASW0003r6c &  0.3 &  D/A,E   \\
-SW23 & CFHTLS\,J023008.6$-$054038 &  37.53591 &  $-$5.67744 &  0.50$^s$ & 20.4 &  1.9 &  2.0 & ASW0003r61 &  0.5 &  A,E   \\
-SW14 & CFHTLS\,J023123.2$-$082535 &  37.84682 &  $-$8.42663 &  0.0 & 0.0 &  1.2 &  2.3 & ASW0004xjk &  0.3 &  A,R   \\
-SW24 & CFHTLS\,J023315.2$-$042243 &  38.31334 &  $-$4.37886 &  0.7 & 20.4 &  1.0 &  2.0 & ASW00050sk &  0.8 &  A,R   \\
-SW34 & CFHTLS\,J023453.5$-$093032 &  38.72321 &  $-$9.50892 &  0.5 & 20.3 &  0.7 &  1.7 & ASW00051ld &  0.3 &  A,D   \\
-SW35 & CFHTLS\,J084833.2$-$044051 & 132.13847 &  $-$4.68085 &  0.8 & 21.1 &  0.9 &  1.7 & ASW0004wgd &  0.7 &  A,R   \\
-SW15 & CFHTLS\,J084841.0$-$045237 & 132.17084 &  $-$4.87720 &  0.3 & 19.5 &  1.0 &  2.3 & ASW0004nan &  1.0 &  A,E   \\
-SW48 & CFHTLS\,J090219.0$-$053923 & 135.57947 &  $-$5.65666 &  0.0 &  0.0 &  2.0 &  1.3 & ASW0000g95 &  1.0 &  A,R/E   \\
-SW36 & CFHTLS\,J090248.4$-$010232 & 135.70204 &  $-$1.04243 &  0.4 & 19.7 &  1.4 &  1.7 & ASW000096t &  0.6 &  D,E   \\
-SW25 & CFHTLS\,J090308.2$-$043252 & 135.78449 &  $-$4.54789 &  0.0 &  0.0 &  1.3 &  2.0 & ASW00007mq &  0.6 &  D,D   \\
-SW49 & CFHTLS\,J090319.4$-$040146 & 135.83105 &  $-$4.02971 &  0.0 & 20.6 &  1.2 &  1.3 & ASW00007ls &  0.5 &  A,R/E   \\
-SW50 & CFHTLS\,J090333.2$-$005829 & 135.88869 &  $-$0.97490 &  0.0 &  0.0 &  2.1 &  1.3 & ASW00008a0 &  1.0 &  A/D,E/G   \\
-SW51 & CFHTLS\,J135724.8$+$561614 & 209.35374 &    56.27066 &  0.36$^s$ &  0.0 &  2.6 &  1.3 & ASW0006e0o &  0.9 &  D,E   \\
-SW26 & CFHTLS\,J135755.8$+$571722 & 209.48268 &    57.28971 &  0.8 & 21.4 &  0.9 &  2.0 & ASW0005ma2 &  0.8 &  A,R   \\
-SW52 & CFHTLS\,J140027.9$+$541028 & 210.11636 &    54.17455 &  0.6 &  0.0 &  1.2 &  1.3 & ASW0006a07 &  0.6 &  Q,R/E   \\
-SW16 & CFHTLS\,J140030.2$+$574437 & 210.12601 &    57.74371 &  0.38$^s$ & 18.8 &  2.0 &  2.3 & ASW0009bp2 &  0.6 &  A,E   \\
-SW2  & CFHTLS\,J140522.2$+$574333 & 211.34261 &    57.72587 &  0.52$^s$ & 20.3 &  1.0 &  2.7 & ASW000619d &  0.7 &  A,R   \\
-SW17 & CFHTLS\,J140622.9$+$520942 & 211.59581 &    52.16169 &  0.7 & 21.3 &  1.2 &  2.3 & ASW0005rnb &  0.7 &  A,R   \\
-SW27 & CFHTLS\,J141432.9$+$534004 & 213.63716 &    53.66788 &  0.7 & 22.1 &  1.0 &  2.0 & ASW0006jh5 &  0.8 &  A,R   \\
-SW53 & CFHTLS\,J141518.9$+$513915 & 213.82903 &    51.65420 &  0.29$^s$ & 18.9 &  3.0 &  1.3 & ASW00070vl &  0.8 &  D,E   \\
-SW3  & CFHTLS\,J142603.2$+$511421 & 216.51375 &    51.23935 &  0.0 &  0.0 &  4.4 &  2.7 & ASW0006mea &  0.7 &  A,G   \\
-SW54 & CFHTLS\,J142620.8$+$561356 & 216.58699 &    56.23230 &  0.5 & 19.9 &  1.3 &  1.3 & ASW0007sez &  0.8 &  A/R,S   \\
-SW55 & CFHTLS\,J142652.8$+$560001 & 216.72004 &    56.00044 &  0.0 &  0.0 &  1.5 &  1.3 & ASW0007t5y &  1.0 &  R,R   \\
-SW56 & CFHTLS\,J142843.5$+$543713 & 217.18153 &    54.62036 &  0.4 & 20.3 &  1.3 &  1.3 & ASW0007pga &  0.6 &  D,D   \\
-SW4  & CFHTLS\,J142934.2$+$562541 & 217.39261 &    56.42807 &  0.51$^s$ & 19.9 &  5.9 &  2.7 & ASW0009cjs &  0.8 &  A,G   \\
-SW28 & CFHTLS\,J143055.9$+$572431 & 217.73332 &    57.40883 &  0.60$^s$ & 20.1 &  1.6 &  2.0 & ASW0007xrs &  0.9 &  A,R/G   \\
-SW37 & CFHTLS\,J143100.2$+$564603 & 217.75124 &    56.76750 &  0.0 &  0.0 &  1.2 &  1.7 & ASW00086xq &  0.8 &  A,E   \\
-SW38 & CFHTLS\,J143353.6$+$542310 & 218.47357 &    54.38624 &  0.65$^s$ & 20.7 &  1.8 &  1.7 & ASW0009cp0 &  0.7 &  A,E   \\
-SW5  & CFHTLS\,J143454.4$+$522850 & 218.72702 &    52.48080 &  0.62$^s$ & 20.5 &  4.4 &  2.7 & ASW0007k4r &  0.4 &  Q,G/R   \\
-SW6  & CFHTLS\,J143627.9$+$563832 & 219.11636 &    56.64249 &  0.53$^s$ & 20.2 &  1.5 &  2.7 & ASW0008swn &  0.9 &  A,D   \\
-SW57 & CFHTLS\,J143631.5$+$571131 & 219.13155 &    57.19215 &  0.7 & 22.0 &  1.3 &  1.3 & ASW0008pag &  0.6 &  D/A,R   \\
-SW58 & CFHTLS\,J143651.6$+$530705 & 219.21503 &    53.11832 &  0.58$^s$ & 20.2 &  3.1 &  1.3 & ASW0007iwp &  0.7 &  A,E/G   \\
-SW18 & CFHTLS\,J143658.1$+$533807 & 219.24246 &    53.63550 &  0.61$^s$ & 20.3 &  0.9 &  2.3 & ASW0007hu2 &  0.6 &  D,D   \\
-SW29 & CFHTLS\,J143838.1$+$572647 & 219.65887 &    57.44645 &  0.8 & 21.3 &  1.1 &  2.0 & ASW0008qsm &  0.9 &  A,R   \\
-SW59 & CFHTLS\,J143950.6$+$544606 & 219.96101 &    54.76858 &  0.73$^s$ &  0.0 &  1.7 &  1.3 & ASW00085cp &  0.4 &  A,G/R   \\
-SW39 & CFHTLS\,J220215.2$+$012124 & 330.56348 &     1.35667 &  0.31$^s$ & 18.0 &  4.6 &  1.7 & ASW0005qiz &  0.5 &  rA,G   \\
-SW7  & CFHTLS\,J220256.8$+$023432 & 330.73691 &     2.57581 &  0.48$^s$ &  0.0 &  6.8 &  2.7 & ASW0007e08 &  0.8 &  A,G   \\
-SW40 & CFHTLS\,J221306.1$+$014708 & 333.27579 &     1.78561 &  0.0 & 17.8 &  1.4 &  1.7 & ASW0008wmr &  0.9 &  A,S   \\
-SW41 & CFHTLS\,J221519.7$+$005758 & 333.83212 &     0.96615 &  0.4 & 20.8 &  1.0 &  1.7 & ASW0008xbu &  0.8 &  A,D   \\
-SW42 & CFHTLS\,J221716.5$+$015826 & 334.31894 &     1.97394 &  0.1 & 22.0 &  1.0 &  1.7 & ASW00096rm &  1.0 &  A/R,R   \\
+SW19 & CFHTLS J020642.0$-$095157 &  31.67504 &  $-$9.86584 &  0.2 & 21.4 &  0.9 &  2.0 & ASW0001ld7 &  0.8 &  A,R   \\
+SW8 & CFHTLS J020648.0$-$065639 &  31.70031 &  $-$6.94430 &  0.8 & 21.0 &  1.3 &  2.3 & ASW00099ed &  0.4 &  A,E   \\
+SW43 & CFHTLS J020810.7$-$040220 &  32.04497 &  $-$4.03891 &  1.0 & 21.6 &  1.8 &  1.3 & ASW0001c3j &  0.7 &  A,R   \\
+SW9 & CFHTLS J020832.1$-$043315 &  32.13396 &  $-$4.55429 &  1.0 & 21.9 &  1.6 &  2.3 & ASW0002asp &  1.0 &  A,R   \\
+SW10 & CFHTLS J020848.2$-$042427 &  32.20110 &  $-$4.40751 &  0.8 & 21.6 &  1.1 &  2.3 & ASW0002bmc &  0.9 &  D,D   \\
+SW11 & CFHTLS J020849.8$-$050429 &  32.20784 &  $-$5.07494 &  0.8 & 21.3 &  0.9 &  2.3 & ASW0002qtn &  1.0 &  A,R   \\
+SW44 & CFHTLS J021021.5$-$093415 &  32.58981 &  $-$9.57109 &  0.4 & 19.0 &  2.7 &  1.3 & ASW0002k40 &  0.4 &  D,S   \\
+SW30 & CFHTLS J021057.9$-$084450 &  32.74148 &  $-$8.74745 &  0.45$^s$ &  0.0 &  2.5 &  1.7 & ASW0002p8y &  0.4 &  A,G   \\
+SW20 & CFHTLS J021221.1$-$105251 &  33.08810 & $-$10.88106 &  0.3 & 18.2 &  1.8 &  2.0 & ASW0002dx7 &  0.8 &  D,E/S   \\
+SW45 & CFHTLS J021225.2$-$085211 &  33.10511 &  $-$8.86973 &  0.76$^s$ & 20.5 &  2.1 &  1.3 & ASW00024id &  1.0 &  R,R   \\
+SW46 & CFHTLS J021317.6$-$084819 &  33.32341 &  $-$8.80549 &  0.5 & 20.6 &  1.3 &  1.3 & ASW00024q6 &  0.4 &  A,R/E   \\
+SW31 & CFHTLS J021514.6$-$092440 &  33.81089 &  $-$9.41115 &  0.72$^s$ & 21.1 &  2.6 &  1.7 & ASW00021r0 &  0.4 &  A,R/G   \\
+SW32 & CFHTLS J022359.8$-$083651 &  35.99955 &  $-$8.61439 &  0.0 &  0.0 &  3.1 &  1.7 & ASW0004iye &  0.4 &  A,E   \\
+SW12 & CFHTLS J022406.1$-$062846 &  36.02558 &  $-$6.47963 &  0.4 & 20.1 &  0.9 &  2.3 & ASW0003wsu &  0.7 &  A,E   \\
+SW1 & CFHTLS J022409.5$-$105807 &  36.03978 & $-$10.96885 &  0.0 &  0.0 &  4.8 &  3.0 & ASW0004dv8 &  1.0 &  A,G   \\
+SW21 & CFHTLS J022533.3$-$053204 &  36.38882 &  $-$5.53460 &  0.57$^s$ & 20.4 &  3.6 &  2.0 & ASW0004m3x &  0.4 &  A,R/G   \\
+SW22 & CFHTLS J022716.4$-$105602 &  36.81856 & $-$10.93410 &  0.4 & 17.8 &  1.8 &  2.0 & ASW0009ab8 &  0.7 &  A,E/G   \\
+SW33 & CFHTLS J022745.2$-$062518 &  36.93868 &  $-$6.42183 &  0.6 & 21.3 &  1.2 &  1.7 & ASW0003s0m &  0.5 &  A,R   \\
+SW13 & CFHTLS J022805.6$-$051733 &  37.02362 &  $-$5.29266 &  0.4 & 19.2 &  1.4 &  2.3 & ASW00047ae &  1.0 &  Q,E   \\
+SW47 & CFHTLS J022843.0$-$063316 &  37.17942 &  $-$6.55465 &  0.5 & 19.9 &  1.8 &  1.3 & ASW0003r6c &  0.3 &  D/A,E   \\
+SW23 & CFHTLS J023008.6$-$054038 &  37.53591 &  $-$5.67744 &  0.50$^s$ & 20.4 &  1.9 &  2.0 & ASW0003r61 &  0.5 &  A,E   \\
+SW14 & CFHTLS J023123.2$-$082535 &  37.84682 &  $-$8.42663 &  0.0 & 0.0 &  1.2 &  2.3 & ASW0004xjk &  0.3 &  A,R   \\
+SW24 & CFHTLS J023315.2$-$042243 &  38.31334 &  $-$4.37886 &  0.7 & 20.4 &  1.0 &  2.0 & ASW00050sk &  0.8 &  A,R   \\
+SW34 & CFHTLS J023453.5$-$093032 &  38.72321 &  $-$9.50892 &  0.5 & 20.3 &  0.7 &  1.7 & ASW00051ld &  0.3 &  A,D   \\
+SW35 & CFHTLS J084833.2$-$044051 & 132.13847 &  $-$4.68085 &  0.8 & 21.1 &  0.9 &  1.7 & ASW0004wgd &  0.7 &  A,R   \\
+SW15 & CFHTLS J084841.0$-$045237 & 132.17084 &  $-$4.87720 &  0.3 & 19.5 &  1.0 &  2.3 & ASW0004nan &  1.0 &  A,E   \\
+SW48 & CFHTLS J090219.0$-$053923 & 135.57947 &  $-$5.65666 &  0.0 &  0.0 &  2.0 &  1.3 & ASW0000g95 &  1.0 &  A,R/E   \\
+SW36 & CFHTLS J090248.4$-$010232 & 135.70204 &  $-$1.04243 &  0.4 & 19.7 &  1.4 &  1.7 & ASW000096t &  0.6 &  D,E   \\
+SW25 & CFHTLS J090308.2$-$043252 & 135.78449 &  $-$4.54789 &  0.0 &  0.0 &  1.3 &  2.0 & ASW00007mq &  0.6 &  D,D   \\
+SW49 & CFHTLS J090319.4$-$040146 & 135.83105 &  $-$4.02971 &  0.0 & 20.6 &  1.2 &  1.3 & ASW00007ls &  0.5 &  A,R/E   \\
+SW50 & CFHTLS J090333.2$-$005829 & 135.88869 &  $-$0.97490 &  0.0 &  0.0 &  2.1 &  1.3 & ASW00008a0 &  1.0 &  A/D,E/G   \\
+SW51 & CFHTLS J135724.8+561614 & 209.35374 &  56.27066 &  0.36$^s$ &  0.0 &  2.6 &  1.3 & ASW0006e0o &  0.9 &  D,E   \\
+SW26 & CFHTLS J135755.8+571722 & 209.48268 &  57.28971 &  0.8 & 21.4 &  0.9 &  2.0 & ASW0005ma2 &  0.8 &  A,R   \\
+SW52 & CFHTLS J140027.9+541028 & 210.11636 &  54.17455 &  0.6 &  0.0 &  1.2 &  1.3 & ASW0006a07 &  0.6 &  Q,R/E   \\
+SW16 & CFHTLS J140030.2+574437 & 210.12601 &  57.74371 &  0.38$^s$ & 18.8 &  2.0 &  2.3 & ASW0009bp2 &  0.6 &  A,E   \\
+SW2 & CFHTLS J140522.2+574333 & 211.34261 &  57.72587 &  0.52$^s$ & 20.3 &  1.0 &  2.7 & ASW000619d &  0.7 &  A,R   \\
+SW17 & CFHTLS J140622.9+520942 & 211.59581 &  52.16169 &  0.7 & 21.3 &  1.2 &  2.3 & ASW0005rnb &  0.7 &  A,R   \\
+SW27 & CFHTLS J141432.9+534004 & 213.63716 &  53.66788 &  0.7 & 22.1 &  1.0 &  2.0 & ASW0006jh5 &  0.8 &  A,R   \\
+SW53 & CFHTLS J141518.9+513915 & 213.82903 &  51.65420 &  0.29$^s$ & 18.9 &  3.0 &  1.3 & ASW00070vl &  0.8 &  D,E   \\
+SW3 & CFHTLS J142603.2+511421 & 216.51375 &  51.23935 &  0.0 &  0.0 &  4.4 &  2.7 & ASW0006mea &  0.7 &  A,G   \\
+SW54 & CFHTLS J142620.8+561356 & 216.58699 &  56.23230 &  0.5 & 19.9 &  1.3 &  1.3 & ASW0007sez &  0.8 &  A/R,S   \\
+SW55 & CFHTLS J142652.8+560001 & 216.72004 &  56.00044 &  0.0 &  0.0 &  1.5 &  1.3 & ASW0007t5y &  1.0 &  R,R   \\
+SW56 & CFHTLS J142843.5+543713 & 217.18153 &  54.62036 &  0.4 & 20.3 &  1.3 &  1.3 & ASW0007pga &  0.6 &  D,D   \\
+SW4 & CFHTLS J142934.2+562541 & 217.39261 &  56.42807 &  0.51$^s$ & 19.9 &  5.9 &  2.7 & ASW0009cjs &  0.8 &  A,G   \\
+SW28 & CFHTLS J143055.9+572431 & 217.73332 &  57.40883 &  0.60$^s$ & 20.1 &  1.6 &  2.0 & ASW0007xrs &  0.9 &  A,R/G   \\
+SW37 & CFHTLS J143100.2+564603 & 217.75124 &  56.76750 &  0.0 &  0.0 &  1.2 &  1.7 & ASW00086xq &  0.8 &  A,E   \\
+SW38 & CFHTLS J143353.6+542310 & 218.47357 &  54.38624 &  0.65$^s$ & 20.7 &  1.8 &  1.7 & ASW0009cp0 &  0.7 &  A,E   \\
+SW5 & CFHTLS J143454.4+522850 & 218.72702 &  52.48080 &  0.62$^s$ & 20.5 &  4.4 &  2.7 & ASW0007k4r &  0.4 &  Q,G/R   \\
+SW6 & CFHTLS J143627.9+563832 & 219.11636 &  56.64249 &  0.53$^s$ & 20.2 &  1.5 &  2.7 & ASW0008swn &  0.9 &  A,D   \\
+SW57 & CFHTLS J143631.5+571131 & 219.13155 &  57.19215 &  0.7 & 22.0 &  1.3 &  1.3 & ASW0008pag &  0.6 &  D/A,R   \\
+SW58 & CFHTLS J143651.6+530705 & 219.21503 &  53.11832 &  0.58$^s$ & 20.2 &  3.1 &  1.3 & ASW0007iwp &  0.7 &  A,E/G   \\
+SW18 & CFHTLS J143658.1+533807 & 219.24246 &  53.63550 &  0.61$^s$ & 20.3 &  0.9 &  2.3 & ASW0007hu2 &  0.6 &  D,D   \\
+SW29 & CFHTLS J143838.1+572647 & 219.65887 &  57.44645 &  0.8 & 21.3 &  1.1 &  2.0 & ASW0008qsm &  0.9 &  A,R   \\
+SW59 & CFHTLS J143950.6+544606 & 219.96101 &  54.76858 &  0.73$^s$ &  0.0 &  1.7 &  1.3 & ASW00085cp &  0.4 &  A,G/R   \\
+SW39 & CFHTLS J220215.2+012124 & 330.56348 &   1.35667 &  0.31$^s$ & 18.0 &  4.6 &  1.7 & ASW0005qiz &  0.5 &  rA,G   \\
+SW7 & CFHTLS J220256.8+023432 & 330.73691 &   2.57581 &  0.48$^s$ &  0.0 &  6.8 &  2.7 & ASW0007e08 &  0.8 &  A,G   \\
+SW40 & CFHTLS J221306.1+014708 & 333.27579 &   1.78561 &  0.0 & 17.8 &  1.4 &  1.7 & ASW0008wmr &  0.9 &  A,S   \\
+SW41 & CFHTLS J221519.7+005758 & 333.83212 &   0.96615 &  0.4 & 20.8 &  1.0 &  1.7 & ASW0008xbu &  0.8 &  A,D   \\
+SW42 & CFHTLS J221716.5+015826 & 334.31894 &   1.97394 &  0.1 & 22.0 &  1.0 &  1.7 & ASW00096rm &  1.0 &  A/R,R   \\
 \end{longtable}
@@
 will apply a ``kick'' of a different size to the subject probability,
-$\Delta\log{P}$, which can be either positive (if the classifier thinks
+$\Delta\log(P)$, which can be either positive (if the classifier thinks
 the subject contains a lens) or negative (if the classifier thinks the
@@
 \caption{ \label{fig:skilldlnp}
-Skill of the volunteers and $\Delta\log{P}$ given a lens or not a lens in
+Skill of the volunteers and $\Delta\log(P)$ given a lens or not a lens in
 an image as a function of $P_{\rm L}$ and $P_{\rm D}$. These

### 2015-05-10 doc/sw-system.tex
Addressed all Christine's comments, fixes #205

--- 2015-05-08 doc/sw-system.tex
@@
 \title[\SW]
-{\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses}
+{\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses with Citizen Science}
 
@@
 about the mass distribution in the lens \citep[e.g.][]{AugerEtal2010,
-SonnenfeldEtal2012,MoreEtal2012,SonnenfeldEtal2013}, including on sub-galactic scales
+SonnenfeldEtal2012,MoreEtal2012,SonnenfeldEtal2015}, including on sub-galactic scales
 \citep[e.g.][]{Dalal+Kochanek2002,VegettiEtal2010,HezavehEtal2013}. Any strong
@@
 
-Because they are rare, strong lenses are expensive to find. The highest purity
+Strong lenses are expensive to find, because they are rare. The highest purity
 searches to date have made use of relatively clean signals such as the
@@
 
-Because we include a training set of images in amongst the survey ``test''
-images, \sw can be viewed as a {\it supervised learning} system. Consequently,
+\sw can be viewed as a {\it supervised learning} system,
+because we include a training set of images in amongst the survey ``test''
+images. Consequently,
 we should expect to find lens candidates that look like the sims that we put in
@@
 At this point, we applied several cuts to the simulated lens pool, in order to
-reject sims that were likely to be difficult to spot. While this ensured that
-the educational value of the sims when feedback was given, it means that we
-should not necessarily expect to detect real lens candidates that would not pass
-these cuts (although human classifiers do possess the key advantage of  being
-able to go beyond their training\footnote{Any real lens candidates we find with
-properties outside the ranges of the training set will be of particular
-interest, being a product of the {\it imagination} of the crowd in extrapolating
-their understanding of gravitational lenses into a regime that they have not
-been trained for.  \citet{GeachEtal2015}, for example, report the discovery of a
+reject sims that were likely to be difficult to spot. While this ensured
+that the sims had high educational value, it means that we
+should not necessarily expect to be able to
+detect real lens candidates that would not pass these cuts.
+However, human classifiers do possess the key advantage of being
+able to {\it imagine} lens systems beyond what they were shown during their training.
+Indeed, any real lens candidates we find with
+properties outside the ranges of the training set could be of particular
+interest, if the training set is indeed completely representative of lenses that
+we already know about.
+\citet{GeachEtal2015}, for example, report the discovery of a
 red lensed arc  by volunteers who had only been trained primarily on blue
-examples. We investigate this aspect of the \SW approach in \PaperTwo.}).
+examples. We investigate this aspect of the \SW approach further in \PaperTwo.
 In the present project, the most important selection cuts we made were to only
-keep sims with a) second brightest image brighter that $i = 23$ and b) total
+keep sims with a) second brightest image having $i < 23$ and b) total
 combined image magnitude fainter than 19--20 (\PaperTwo, Table~1). The
-combination of these two cuts resulted in a sample of visible lensed image
+combination of these two reductions resulted in a sample of visible lensed image
 configurations.
@@
 volunteer increased, the training frequency was decreased from 40\% to
-$2/(5\times2^{(\textrm{int}(N_c/20)+1)/2})$ ($\approx 30\%$ for the second 20
-subjects, $20\%$ for the third 20 subjects, and so on).
+$2/(5\times2^{(\textrm{int}(N_c/20)+1)/2})$, $\approx 30\%$ for the second 20
+subjects, $20\%$ for the third 20 subjects, and the minimum rate of 10\%
+after that. We did not reduce the training frequency to zero because we wanted
+to ensure that the inspectors remained alert.
 
@@
 galaxy and group scales
-\citep{GavazziEtal2014,SonnenfeldEtal13,CabanacEtal2007,MoreEtal2012}. The
+\citep{GavazziEtal2014,SonnenfeldEtal2013a,CabanacEtal2007,MoreEtal2012}. The
 quality of the data, combined with the presence of these comparison ``known
@@
 
-In order to investigate the completeness of the previous, semi-automated, lens
-searches in the \cfhtls area, we designed a ``blind search.'' We divided the
+In order to investigate the completeness of the previous semi-automated lens
+searches in the \cfhtls area, we designed a ``blind search'' as follows.
+We divided the
 \cfhtls pointings into some 430,000 equal size, overlapping tiles, approximately
@@
 online analysis of the classifications,  updating a probabilistic model of every
-(anonymous) volunteer's data, and also updating the posterior probability that
+anonymous volunteer's data, and also updating the posterior probability that
 each subject (in both the training and test sets) contains a lens, on a daily
@@
 then include uncertainty arising as a result of the volunteer's efforts and
-also the agent's approximations, but they will have two important redeeming
-features. First, the interpretations will be quantitative (where before they
-were qualititative),  and thus will be useful in decision-making. Second, the
-agent will be able to predict, using its model, the probability of a test
-subject being a $\LENS$, given both its volunteer's classification, and its
-volunteer's experience. In this section we describe how these agents work,
+also the agent's approximations.
+The agent will be able to predict, using its model, the probability of a test
+subject being a $\LENS$ given both its volunteer's classification and its
+volunteer's past experience. In this section we describe how these agents work,
 and other aspects of the \SW analysis pipeline (SWAP).
@@
 Now, when this volunteer views a test subject,
-it is this confusion matrix that will allow their agent to update the
+it is this confusion matrix that will allow their software agent to update the
 probability of that test subject being a $\LENS$. Let us suppose that
@@
 would nevertheless be submitting useful information, since given the above
-confusion matrix, their agent would calculate
+confusion matrix, their software agent would calculate
 \begin{align}
@@
 we are trying to infer. We track $\pr(\LENS|\data)$ as a function of time,
-and by comparing it to a lower or upper thresholds, make decisions about
-whether to retire the subject from the classification interface or
-promote it in \Talk, respectively.
+and by comparing it to a lower or upper threshold, make decisions about
+whether to retire the subject from the classification interface, or
+flag it for further study, respectively.
 
@@
 of all agent confusion matrix elements and subject probabilities simultaneously.
-Such a joint analysis would implement in full the agents' basic model assumption
+Such a joint analysis would implement in full the software agents' basic model assumption
 that their volunteers have innate and unchanging talent for lens spotting, that
@@
 \StageOne online analysis. Many volunteers classify  only a small number of images, and
-so their agents' confusion matrix elements have remained close to their initial values
+so their software agents' confusion matrix elements have remained close to their initial values
 of (0.5,0.5). As more images are classified (shown by the yellow point size),
@@
 \Sref{sec:results} below) but mostly as
-the agent learns more about them. In this upper
+the agent updates its confusion matrix. In this upper
 right-hand quadrant, the agents perceive their volunteers to be ``astute.''
@@
 allowing the agents to learn via their Bayesian updates.
-When the agents are allowed to update their confusion matrices, the choice of
+When the software agents are allowed to update their confusion matrices, the choice of
 initial confusion matrix is not very important: the same 0.75 initial values
@@
 sophisticated strategies tend to under-perform naive but simpler
-ones \citep{Waterhouse} (although we note that this rule of thumb seems not to extend
-to simple voting in this case!).
+ones \citep[][although we note that this rule of thumb seems not to extend
+to simple voting in this case!]{Waterhouse}.
 
@@
 magnified view of the top lefthand corner of each plot. Linestyles illustrate
-the agent properties (initial confusion matrix elements, learning or not)
+the software agent properties (initial confusion matrix elements, learning or not)
 discussed in the text, as well as the difference between the online and offline
@@
 $\skill = 0.0$~bits, while perfect classifiers have $\skill = 1.0$~bit.
-All agents start
+All software agents start
 with $\skill = 0.0$~bits. The skill of  an agent increases as training subjects are
@@
 \item{\noindent\bf ``Information:''} The total information $\information$
-generated by the agent during the volunteer's classification activity. This
+generated by the software agent during the volunteer's classification activity. This
 quantity depends on the value of each subject's lens probability when that
@@
 defined in terms of posterior relative to prior probabilities,
-\Aref{appendix:swap}).  Because of this, we expect this raw quantity to be noisier
+\Aref{appendix:swap}).  As a result, we expect this raw quantity to be noisier
 than the ``contribution'' defined above. The lower righthand panel of
@@
 
-How fast does the \SW crowd classify subjects? Each agent records the timestamp
+How fast does the \SW crowd classify subjects? Each software agent records the timestamp
 of each classification its volunteer makes; by measuring the time lags between
@@
 more training images (still at random) in their stream. We could also experiment
-with providing greater training rates early on for all volunteers; the risk
-associated with this is that retention rates may drop if too few ``fresh'' test
+with providing greater training rates early on for all volunteers, although
+this carries significant risk: retention rates may drop if too few ``fresh'' test
 images are shown early on. Another way of improving the training could be to
@@
 dynamically allocating subjects to volunteers according to their agents'
-skill could alleviate this issue. This is something we plan to
+skill could alleviate this issue. In particular one can imagine doing this
+for subjects that have classification histories that indicate that they
+are worthy of further study.
+These are things we plan to
 experiment with in future.
@@
 ``resurrecting'' subjects that had been retired by the online system before the
-agents had time to learn enough about their classifier's high skill.
+software agents had time to learn enough about their classifier's high skill.
 

### 2015-05-10 doc/sw-system.tex
Reading through, up to SWAP details section.

@@
 quality of the survey,
-and we chose to focus on this subset. (The remaining $u$ and $z$-band images
+and we chose to focus on this subset. (The $u$ and $z$-band images
 were also made available for perusal in \Talk). We made colour composite PNG
@@
 appear to have equal red, green and blue components. Non-linearity sets in at
-about $1/(Q \alpha)$ in the  scaled intensity image: finally, tuning $Q$ at
+about $1/(Q \alpha)$ in the  scaled intensity image. Finally, tuning $Q$ at
 fixed $\alpha$ determines the appearance of bright galaxies, which we need to
@@
 for intuition to be built up about the appearance of stars and galaxies across
-the survey. Alternative algorithms, such as adjusting the stretch and scale
+the survey. (Alternative algorithms, such as adjusting the stretch and scale
 dynamically according to, for example, the root-mean-square pixel value in
@@
 they tend to hide the faint features in those images: we needed to optimize
-the detectability of these faint features.   Examples of \cfhtls training set
+the detectability of these faint features.)   Examples of \cfhtls training set
 images prepared in this way can be seen in Figures~\ref{fig:training-gallery:sims}
@@
 Having described the classification interface, the training images and the
-test images,  we now outline our methodology for interpreting the interactions
-of the volunteers with the identification interface, and then describe how we
-applied this methodology in the two classification stages in the \cfhtls
+test images,  we now outline our methodology for interpreting the
+classifications made by the
+volunteers, and describe how we
+applied this methodology in the two classification stages of the \cfhtls
 project in the \SW Analysis Pipeline (SWAP) code.\footnote{The open source
@@
 
-Each classification made is logged in a database, storing subject IDs,
-volunteer IDs, a timestamp and the classification results (the image
-pixel-coordinate positions of every marker placed).  The ``category'' of subject --
+Each classification made is logged in a database that stores the subject ID,
+volunteer ID, a timestamp and the results of each classification: the image
+pixel-coordinate positions of every marker placed.  The ``category'' of subject --
 whether it is a ``training'' subject (a simulated lens or a known non-lens) or a
@@
 object if one is present in the image (``lensed galaxy'', ``lensed quasar'' or
-``cluster lens'').  This classification is used to provide instant feedback, but
-is also the basic measurement used in a probabilistic classification of every
+``cluster lens'').  This information is used to provide the instant feedback, but
+is also the basic data used in a probabilistic classification of every
 subject based on all image views to date. Not all
@@
 
-While the \SW web app is live, and classifications are being made, we perform an
-online analysis of the classifications,  updating a probabilistic model of every
+While the \SW web app was live, and classifications were being made, we
+performed a daily online analysis of the classifications,
+updating a probabilistic model of every
 anonymous volunteer's data, and also updating the posterior probability that
-each subject (in both the training and test sets) contains a lens, on a daily
-basis. This gives us a dynamic estimate of the posterior probability for  any
+each subject (in both the training and test sets) contains a lens.
+This gave us a dynamic estimate of the posterior probability for  any
 given  subject being a lens, given all classifications of it to date. Assigning
-thresholds in this lens probability then allows us to make good decisions about
+thresholds in this lens probability then allowed us to make good decisions about
 whether or not to retire a subject from the system, in order to focus attention
@@
 For a detailed derivation of this analysis pipeline, please continue reading
-through \Sref{sec:swap:details} below. Alternatively, \Sref{sec:swap:practicalities}
-contains illustrations of the calculation.
+through \Sref{sec:swap:details} below. Alternatively,
+\Sref{sec:swap:practicalities} contains illustrations of the calculation.
 
@@
 We thank Stuart Lynn, Kelly Borden, Laura Whyte, Brooke Simmons,
-David Hogg, Thomas Jennings, Layne  Wright, Cecile Faure, Jonathan Coles, Stuart
+David Hogg, Daniel Foreman-Mackey,
+Thomas Jennings, Layne  Wright, Cecile Faure, Jonathan Coles, Stuart
 Lowe and Jean-Paul Kneib for many useful conversations about citizen science and

### 2015-05-10 doc/sw-system.tex
Reading through, up to Results section.

@@
 How should we model these compressed data? The circumstances of each
-classification are quite complex, as are the human classifiers in general: the
+classification are quite complex, as are the human classifiers themselves: the
 volunteers learn more about the problem as they go, but also inevitably make
@@
 
-When all the subjects had either been retired, or classified around 10 times or
+When all the subjects had either been retired, or at least
+classified around 10 times or
 more, the web app was paused and reconfigured for \StageTwo. The sample of

### 2015-05-10 doc/sw-system.tex
Reading through, up to crowd results section.

@@
 \begin{keywords}
-  gravitational lensing   --
+  gravitational lensing: strong   --
   methods: statistical            --
@@
 very simple unweighted voting scheme, where all classifications are treated
-equally.  In this case, the TPR remains under 80\% in \StageOne and 60\% in
+equally.  In this case, the TPR never reaches 80\% in \StageOne or 60\% in
 \StageTwo, thus illustrating the benefit of including training images and

### 2015-05-12 doc/sw-cfhtls.tex
all corrections from pjm and av - almost final

--- 2015-05-09 doc/sw-cfhtls.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %
@@
 \begin{abstract}
-We report the discovery of {\bf 29 promising (and 59 total)} new lens
+We report the discovery of 29 promising (and 59 total) new lens
 candidates from the CFHT Legacy Survey (\cfhtls) based on about 11
@@
 first \sw lens search.  The goal of the blind lens search was to
-identify lens candidates missed by robots (the \rf on galaxy scales
-and \af on group/cluster scales) which had been previously used to
-mine the \cfhtls for lenses.  We compare some properties of the samples
-detected by these algorithms to the \sw sample and find them to be
-broadly similar.  The image separation distribution calculated from the
-\sw sample shows that previous constraints on the average
-density profile of lens galaxies are robust. \sw recovers about
-60\% of known lenses, while the new candidates show a richer variety
-compared to those found by the two robots. This detection rate could be
-increased to 75\% by only using classifications performed by expert
-volunteers (albeit at the cost of a higher false positive rate), indicating that
-the training and performance calibration of the citizen
-scientists is very important for the success of \sw. In this work
-we present the SIMCT pipeline, used for generating {\it in situ}
-a sample of realistic  simulated lensed
-images.  This training sample, along with the
-false positives identified during the
-search, has a legacy value for testing
-future lens finding algorithms. We make this dataset publicly
-available.
-
+identify lens candidates missed by robots (the \rf on galaxy scales and
+\af on group/cluster scales) which had been previously used to mine the
+\cfhtls for lenses.  We compare some properties of the samples detected
+by these algorithms to the \sw sample and find them to be broadly
+similar.  The image separation distribution calculated from the \sw
+sample shows that previous constraints on the average density profile of
+lens galaxies are robust. \sw recovers about 60\% of known lenses, while
+the new candidates show a richer variety compared to those found by the
+two robots. This detection rate could be increased to 75\% by only using
+classifications performed by expert volunteers (albeit at the cost of a
+higher false positive rate), indicating that the training and
+performance calibration of the citizen scientists is very important for
+the success of \sw. In this work we present the SIMCT pipeline, used for
+generating {\it in situ} a sample of realistic  simulated lensed images.
+This training sample, along with the false positives identified during
+the search, has a legacy value for testing future lens finding
+algorithms. We make the pipeline and the training set publicly available.
 \end{abstract}
-
-% Full list of options at http://www.journals.uchicago.edu/ApJ/instruct.key.html
 
@@
   gravitational lensing: strong   --
-  methods: statistical
+  methods: statistical            --
+  methods: citizen science
 \end{keywords}
@@
 exist. For example, the lensed images of background galaxies show
-variety in their surface brightness distributions, colors, light
+variety in their surface brightness distributions, colours, light
 profiles, shapes, structures and angular image separations.  Moreover,
@@
 systems. However, even after such restrictions, robotic lens searches
-have to always rely on visual screening to result in a sample of plausible
+have to always rely on visual screening to produce a sample of plausible
 lens candidates.
@@
 
-{\bf \GZ, one of the most successful citizen science projects in
-astronomy, addressed}
+\GZ, one of the most successful citizen science projects in
+astronomy, addressed
 the problem of how to  classify large numbers of galaxies by their
@@
 (\cfhtls\footnote{\texttt{http://www.cfht.hawaii.edu/Science/CFHTLS/}}).
-{\bf In \citet{Kung2015}, we describe the design of a collaborative
-mass modelling tool that can be used by citizen scientists.}
+In \citet{Kung2015}, we describe the design of a collaborative
+mass modelling tool that can be used by citizen scientists.
 
@@
 
-{\bf From the early release of the CFHTLS (T0002) covering 28~deg$^2$,
+From the early release of the CFHTLS (T0002) covering 28~deg$^2$,
 \citet{Cabanac2007} used an arc finding algorithm \citep{Alard2006} to
 find arcs in galaxies, groups and clusters. They found about 40 lens
-candidates with quality grades from low to high.}
+candidates with quality grades from low to high.
 
@@
 The \af \citep{More2012} was used for finding blue arc-like features in
-the entire \cfhtls imaging without any pre-selection on the type of the lensing
-object. This \af, {\bf an improved version of the algorithm by
-\citet{Alard2006}}, measures the second order moments of the flux distribution
-in pixels within small regions to estimate the direction and extent of local
-elongation of features. Pixels with high values of elongation are connected to
-form an arc candidate. Finally, a set of thresholds on arc properties such as
-the area, length, width, curvature and surface brightness are used to select
-arc-like candidates. The search was carried out in the g-band which is the most
-efficient wavelength to find typical lensed features.  This sample, called
-SARCS, has 55 promising and a total of 127 lens candidates which are selected
-from both \cfhtls WIDE and DEEP fields. The SARCS sample consists of some
-galaxy-scale candidates and mostly groups/cluster scale lens candidates. This is
-because more massive systems produce arcs or lensed images with large image
-separation from the lensing galaxy which are easier to detect compared to the
-galaxy-scales. In the absence of a large systematically followed up
-verified sample of candidates, we choose the most promising 26 systems
-as our bona fide lens sample from the \cfhtls WIDE.
-(The total number of lens candidates in the \cfhtls WIDE alone is 108.)
+the entire \cfhtls imaging without any pre-selection on the type of the
+lensing object. This \af, an improved version of the algorithm by
+\citet{Alard2006}, measures the second order moments of the flux
+distribution in pixels within small regions to estimate the direction
+and extent of local elongation of features. Pixels with high values of
+elongation are connected to form an arc candidate. Finally, a set of
+thresholds on arc properties such as the area, length, width, curvature
+and surface brightness are used to select arc-like candidates. The
+search was carried out in the $g$-band which is the most efficient
+wavelength to find typical lensed features.  This sample, called SARCS,
+has 55 promising and a total of 127 lens candidates which are selected
+from both \cfhtls WIDE and DEEP fields. The SARCS sample consists of
+some galaxy-scale candidates and mostly groups/cluster scale lens
+candidates. This is because more massive systems produce arcs or lensed
+images with large image separation from the lensing galaxy which are
+easier to detect compared to the galaxy-scales. In the absence of a
+large systematically followed up verified sample of candidates, we
+choose the most promising 26 systems as our bona fide lens sample from
+the \cfhtls WIDE. The total number of lens candidates in the \cfhtls
+WIDE alone is 108.
 
@@
 \citet{Gavazzi2014} used their \rf code to find compact rings or arcs
-around centers of isolated and massive early-type galaxies. \rf
+around centres of isolated and massive early-type galaxies. \rf
 subtracts the point spread function (PSF)-matched $i$-band images from the $g$-band images, and
@@
 pre-selected $\sim$638,000 targets as either photometrically-classified
-early type galaxies, or objects selected to have red centers and blue
+early type galaxies, or objects selected to have red centres and blue
 outer parts, from the T0006 CFHTLS data release catalogs. A total of
@@
 The work by \citet{Maturi2014} used the arc finding code of
-\citet{Seidel2007} and color properties of typical arcs to optimize arc
+\citet{Seidel2007} and colour properties of typical arcs to optimize arc
 detection. This new approach was tested on the CFHTLS-Archive-Research
@@
 the $g$, $r$ and $i$-band imaging from \cfhtls which are most useful for
-visual identification of lenses.  We made color composite images using
-the publicly-available code, \humvi\footnote{The open source  color image
+visual identification of lenses.  We made colour composite images using
+the publicly-available code, \humvi\footnote{The open source  colour image
 composition code used in this work is available from
 \texttt{http://github.com/drphilmarshall/HumVI}} following the
-prescription of \citet{Lupton2004}. The color scales were chosen to
+prescription of \citet{Lupton2004}. The colour scales were chosen to
 maximize the contrast between faint extended objects and bright early
@@
 the images are shown randomly, a volunteer may not necessarily come
-across the neighbouring cutout unless {\bf they classify} a large
+across the neighbouring cutout unless they classify a large
 number of images. This is not a problem since our user base is extremely
@@
 new to the task of finding lenses, but they are also crucial for
-analyzing the classifications performed by the citizen scientists (more
+analysing the classifications performed by the citizen scientists (more
 details can be found in \PaperOne, but see \Sref{sec:swap} below for a brief
@@
 simulation purpose, we exclude all those galaxies whose positions match
-with the lensing galaxies from the SARCS samples {\bf within
-2~arcsec\footnote{{\bf Due to inaccuracies and uncertainties in measurements
-of the centers of some of the lens candidates, some simulated lensed
+with the lensing galaxies from the SARCS samples within
+2~arcsec\footnote{ Due to inaccuracies and uncertainties in measurements
+of the centres of some of the lens candidates, some simulated lensed
 images were superposed on the galaxies of known lens candidates. This issue was overcome by
 presenting the same \cfhtls images with and without the simulated
-lenses to the volunteers.}}}.
+lenses to the volunteers.}.
 
@@
 ($z_l$) from the parent galaxy catalog. Next, we use the $L-\sigma$ scaling relation from the
-bright sample of \citep{Parker2005} {\bf given by
+bright sample of \citep{Parker2005} given by
 \be
@@
 This sets the velocity dispersion of the halo
-hosting the galaxy, which will be later used in the model.}
+hosting the galaxy, which will be later used in the model.
 We assume that the knee of the luminosity function of galaxies, $L_*$ evolves
@@
 
-{\bf We also add external shear at the center of the lensing galaxy
+We also add external shear at the centre of the lensing galaxy
 drawn randomly from a set range (see \Tref{tab:thresh}. The shear is
@@
 expected to be small for most of the cases and is ignored in the current
-implementation of SIMCT.}
+implementation of SIMCT.
 
@@
 For quasars, we assume the luminosity function prescription of \citet{Oguri2010}
-and adopt k-corrections by \citep{Richards2006}.
+and adopt k-corrections by \citet{Richards2006}.
 
@@
 We draw source redshifts and luminosities from the aforementioned
-distributions. {\bf We note that the sources are being drawn from a much
+distributions. We note that the sources are being drawn from a much
 fainter magnitude range compared to the limiting magnitude of the
-\cfhtls imaging and thus, the magnification bias\footnote{ {\bf In a
+\cfhtls imaging and thus, the magnification bias\footnote{ In a
 flux-limited sample from a survey, sources fainter than the flux limit
@@
 function and needs to be accounted for when comparing the true and
-observed luminosity functions.}} is naturally taken into account.} The
+observed luminosity functions.} is naturally taken into account. The
 source positions with respect to the lens are drawn randomly from an
-area inside the caustic.  {\bf When populating the sources within the
+area inside the caustic.  When populating the sources within the
 caustics, the finite size of the background galaxies is expected to
@@
 critical for the purpose of our training sample, for simplicity we assume the
-background galaxies to be point like when computing cross-sections.} We perform
-ray-tracing for all of the $N_{\rm src}$ sources using the publically
+background galaxies to be point like when computing cross-sections. We perform
+ray-tracing for all of the $N_{\rm src}$ sources using the publicly
 available code \gravlens \citep{Keeton2000} and choose sources that
@@
 Since we want to produce realistic looking lens systems, we simulate
-lenses in each of the five \cfhtls~filters. The colors of the background
+lenses in each of the five \cfhtls~filters. The colours of the background
 galaxies are drawn randomly from the photometric CFHTLenS catalog
 \citep{Hildebrandt2012,Erben2013}.  Similarly, we use a quasar catalog
-from the SDSS Data Release 9 \citep{Paris2012} from which colors are
-drawn to simulate quasar lenses. Next, we assumed a Gaussian
+from the SDSS Data Release 9 \citep{Paris2012} from which colours are
+drawn to simulate quasar lenses. Next, we assume a Gaussian
 profile\footnote{This was due to an oversight. We intended to use either
-an exponential or {\bf de Vaucouleurs'} profile that will be adopted for
+an exponential or de Vaucouleurs' profile that will be adopted for
 future implementations of SIMCT.} for the galaxies. The ellipticity and
@@
 effective radius of the galaxy is estimated from the luminosity$-$size
-relation \citep{Bernardi2003} (with a redshift scaling, to account for
-size evolution) given by
+relation \citep[][with a redshift scaling, to account for size evolution]{Bernardi2003} given by
 \be
-R_{\rm eff}= 10^{0.52} \frac{L_r^{2/3}}{{(1+z_s)}^2} \, {\bf Kpc}
+R_{\rm eff}= 10^{0.52} \frac{L_r^{2/3}}{{(1+z_s)}^2} \, {\rm Kpc}
 \ee
-where $L_r=L_s/10^{10.2} {\bf L_\odot}$. On the other hand, quasars are assumed to be
+where $L_r=L_s/10^{10.2} L_\odot$. On the other hand, quasars are assumed to be
 point sources and the PSF, with which quasars are convolved, is assumed
-to have a Gaussian profile. The full-width-at-half-maximum of PSF is
-equated to that of the median seeing for every filter. The median seeing
+to have a Gaussian profile. The full-width-at-half-maximum of the PSF is
+equated to that of the mean seeing for every filter. The mean seeing
 values are taken from Table 4 of the official Terapix T0007 release
@@
 again use \gravlens to generate simulated lensed images.  After accounting for the shot
-noise in the lensed images and convolving them with the median seeing in each of
-the filters, the simulated image is added to the real \cfhtls~image centered
+noise in the lensed images and convolving them with the seeing in each of
+the filters, the simulated image is added to the real \cfhtls~image centred
 on the lensing galaxy. Note that we ensure that the lensed galaxies and
@@
 multiple lensed images, arises from not only the brightest group galaxy (BGG) at
-the center, but also from the dark matter component and
+the centre, but also from the dark matter component and
 the satellite galaxies \citep{Oguri2005,Oguri2006}. We generate a basic group
@@
 $\delta z = 0.01$ of the BGG and within an aperture of $250$~Kpc. If another BGG
-is found with the aperture, then the fainter BGG is removed from our list of
+is found within the aperture, then the fainter BGG is removed from our list of
 BGGs.
@@
 
-We assume a constant mass-to-light ratio of $3 \times
-0.7$~h~$M_{*}/L_{*}$, to convert the BGG luminosity to a stellar mass
+We assume a constant mass$-$to$-$light ratio of $3 \times
+0.7~h~ M_{*}/L_{*}$, to convert the BGG luminosity to a stellar mass
 estimate. The stellar mass$-$halo mass relation \citep{Behroozi2013},
@@
 
-We calculate the luminosity and velocity dispersion for the BGG and each of the
-member galaxies following the same prescription as in
+We calculate the luminosities and velocity dispersions for the BGG and each
+of the member galaxies following the same prescription as in
 \Sref{sect:gallens}. To calculate the average number of sources that get
-lensed by such a system, we need to calculate the lensing cross-section for each
-of these potential lensing groups. The complexity in the lens models makes it
-analytically intractable to calculate the size of the caustics\footnote{The lens
-mass distribution determines size and shape of the caustics. Any source
-located within the caustics will form multiple lensed images which is the
-criteria for strong lensing. To further understand caustics, see e.g., \citet{Schneider1992}.}.
+lensed by such a system, we need to calculate the lensing cross-section
+for each of these potential lensing groups. The complexity in the lens
+models makes it analytically intractable to calculate the size of the
+caustics\footnote{The lens mass distribution determines size and shape
+of the caustics. Any source located within the caustics will form
+multiple lensed images which is the criteria for strong lensing. To
+further understand caustics, see e.g., \citet{Schneider1992}.}.
 Therefore, we generate the caustics numerically using \gravlens and then
-determine the area covered by the caustics. We consider only galaxies as our
-background source population since group or cluster-scale quasar lenses are
-expected to be extremely rare in the \cfhtls.  Following the same procedure
-as described in \Sref{sect:gallens}, we calculate the number of galaxies
-expected to lie behind every potential lensing group (see \Eref{eqn:nsrc}).
-As before, for each background galaxy within the lens cross-section, a redshift
-and an $i$-band magnitude is determined by drawing galaxies randomly from the
-respective distributions (see Equations~\ref{eqn:ps}-\ref{eqn:ns}).
+determine the area covered by the caustics. We consider only galaxies as
+our background source population since group or cluster-scale quasar
+lenses are expected to be extremely rare in the \cfhtls.  Following the
+same procedure as described in \Sref{sect:gallens}, we calculate the
+number of galaxies expected to lie behind every potential lensing group
+(see \Eref{eqn:nsrc}).  As before, for each background galaxy within the
+lens cross-section, a redshift and an $i$-band magnitude is determined
+by drawing galaxies randomly from the respective distributions (see
+Equations~\ref{eqn:ps}-\ref{eqn:ns}).
 
@@
 different for group scales. The simulated lensed images are then added
-to the real \cfhtls~images with the BGGs as the center by following
+to the real \cfhtls~images with the BGGs as the centre by following
 exactly the same procedure as described in the previous section.
@@
 and shear (for galaxy-scale lenses only). For the background sources, we
-provide the offset from the lens center, redshift, magnitudes, total
+provide the offset from the lens centre, redshift, magnitudes, total
 magnification, number of lensed images. Additionally, when possible,
@@
 the lensed images for some of the failed simulations have larger image
-separation than would be expected from the luminosity and/or size of the
-galaxy.
+separation than what one would expect from the luminosity and/or size of the
+galaxy. We roughly expect mass to follow light, so more massive galaxies
+typically look brighter and/or bigger.
 
@@
 We also use a single component to describe the light distribution of the
-background galaxies. This is clearly not the most accurate description for
-galaxies, especially for the irregular star-forming galaxies which comprise
-a significant fraction
-of the lensed galaxy population. Star-forming galaxies have complex structures
-such as star forming knots, spiral arms, bars and disks. The simulated lensed
-images do not display these features. This is fine for most cases seen in
-images taken from ground based telescopes such as the CFHT
-{\bf but sometimes the profiles of the lensed arcs can appear very symmetric along the
-length or width of the arc and featureless, especially, if the images
-are very bright.}
+background galaxies. This is clearly not the most accurate description
+for galaxies, especially for the irregular star-forming galaxies which
+comprise a significant fraction of the lensed galaxy population.
+Star-forming galaxies have complex structures such as star forming
+knots, spiral arms, bars and disks. The simulated lensed images do not
+display these features. This is not problematic for most of the images
+taken from ground based telescopes such as the CFHT but sometimes the
+profiles of the lensed arcs can appear very symmetric (along the length
+or width of the arc) and featureless, especially, if the images are very
+bright.
 
@@
 and confirmed to contain no lenses. Impostors are systems
-which look like lenses but are not, for example, spiral galaxies,
-starforming galaxies, chance alignments of features arranged in a
+which have lens like features but are not lenses in reality, for example, spiral galaxies,
+star-forming galaxies, chance alignments of features arranged in a
 lensing configuration and stars.
@@
 performed by volunteers was provided to the science team every night.
-This daily batch was analyzed by the Space Warps Analysis Pipeline
+This daily batch was analysed by the Space Warps Analysis Pipeline
 (SWAP). The philosophy and the details of SWAP are described in detail
@@
 classification of every training image. The thresholds for the
-probabilities {\bf to accept or reject a subject if it contains a lens or does
-not contain one} can be chosen in SWAP. Those images which cross
+probabilities to accept or reject a subject if it contains a lens or does
+not contain one can be chosen in SWAP. Those images which cross
 these threshold values are ``retired'', and are not subsequently shown to the
@@
 which were then visually inspected by three of us (as ``lens experts'',
- AM, AV, PJM).  Each images was assigned a grade~$G$ on a scale of 0 to 3,
+ AM, AV, PJM).  Each images was assigned a grade on a scale of 0 to 3,
 representing those images
@@
 then produced by selecting candidates above a threshold on the
-average value of these grades, as described in the next section.
+averaged grade~$G$, as described in the next section.
 
@@
 
-In this section, we describe the \cfhtls \sw candidate lens sample.
-We find a total of 141 candidates with
-$G\ge1.3$ (medium-high grade), of which {\bf 59} are new
-systems. This sample is further divided as follows. We have a total of
-50 candidates with $1.3\le$G$<2$ (medium grade), of
-which 30 are new. The quality of candidates in this category is such
-that at least one of the inspectors thought the candidate was
+\begin{table}
+\begin{center}
+\caption{ \label{tab:stats}
+Statistics of detections in \sw }
+\begin{tabular}{l l l l l}
+\hline
+   &  \multicolumn{2}{c} {\StageOne}  & \multicolumn{2}{c}{\StageTwo} \\
+      & KC  &  KL  & KC & KL \\
+\hline
+\hline
+Number  & 128 & 34 & 107  & 34  \\
+Fraction  & & & & \\
+of total recovered & 29\% & 58\% & 25\% & 58\%  \\
+$P_{\rm acc thresh}$ & 0.95 & 0.95 & 0.3 & 0.3 \\
+Averaged Grade (G) & $-$ & $-$ & 1.3 & 1.3 \\
+\hline
+   &  \multicolumn{2}{c} {\StageTwo}  &   & \\
+      & NC  &  AC  &  & \\
+\hline
+\hline
+Number  & 59 & 141 &  & \\
+Fraction & & & & \\
+of detections & 14\% & 33\% &  & \\
+$P_{\rm acc thresh}$ & 0.3 & 0.3 &  & \\
+Averaged Grade (G) & 1.3 & 1.3 & 1.3 & 1.3 \\
+
+\hline
+\end{tabular}
+\end{center}
+{KC}-- Known lens candidates \\
+{KL}-- Known lenses \\
+{NC}-- New lens candidates  \\
+{AC}-- All (known and new) lens candidates  \\
+$P_{\rm acc thresh}$ -- systems with Posterior probability~$P$ above this threshold are selected \\
+Note: For KC and KL, Percentages are with respect to the known
+population (i.e. 438 KC and 59 KL see \Sref{sec:data:kls}) whereas for
+NC and AC, percentages are with respect to the total sample of 429 lens
+candidates.
+\\
+\end{table}
+
+In this section, we describe the \sw candidate lens sample from the
+\cfhtls.  We find a total of 141 candidates with $G\ge1.3$ (medium-high
+grade), of which 59 are new systems. This sample is further divided as
+follows. We have a total of 50 candidates with $1.3\le$G$<2$ (medium
+grade), of which 30 are new. The quality of candidates in this category
+is such that at least one of the inspectors (``lens expert'') thought the candidate was
 probably a lens (that is, a grade of 2) and a second inspector thought
 that it was possibly a lens (that is, a grade of 1). Among our high
-grade sample ($G\ge$2), there are a total of 91 candidates, of
-which {\bf 29} are new. In this category, the minimum grade by all of the
-inspectors was 2, suggesting that the candidates are probably or almost
-certainly lenses according to all three inspectors. To avoid
-duplication, further information on \sw candidates that were previously
-identified in the literature will be made available at
-\texttt{http://spacewarps.org/\#/projects/CFHTLS/}, while the sample of new lens
-candidates with $G\ge 1.3$ (medium-high probability) is presented in
-this paper (see \Sref{sec:results:newcand}).
-
-We also find a total of 288 (and {\bf 245} new) candidates with averaged grade
+grade sample ($G\ge$2), there are a total of 91 candidates, of which 29
+are new. In this category, the minimum grade by all of the inspectors
+was 2, suggesting that the candidates are probably or almost certainly
+lenses according to all three inspectors. To avoid duplication, only the
+newly discovered lens candidates with G$\ge 1.3$ (medium-high
+probability) are presented in this paper (see
+\Sref{sec:results:newcand}), and further information on \sw-selected
+candidates that were previously identified in the literature (as
+described in \Sref{sec:data:kls}) will be made available at
+\texttt{http://spacewarps.org/\#/projects/CFHTLS/}.
+
+We also find a total of 288 (and 245 new) candidates with averaged grade
 $0<$G$<1.3$ (low grade), which means that at
@@
 
-In \Tref{tab:stats}, we give overall statistics of the systems
-detected at \StageOne and \StageTwo. We give the total number of
-detections of the known lens candidates, known lenses and the new lens
-candidates at each stage.  We also give the recovery fractions for the
-known samples and fraction of total detection for the new samples at
-each stage. We find that all of the confirmed lenses found
-at \StageOne are also recovered at \StageTwo; a small fraction of
-the known lens candidates are rejected at \StageTwo. From the visually
-inspected known lens sample at \StageTwo (P$> 0.3$), the experts gave a
-grade of 1.3 and above to about 92~per~cent (33 out of 36) of the systems. Overall,
-the sample of new \sw lens candidates increased the sample of total
-\cfhtls lens candidates by over 50~per~cent. However, we find that 42\% of known
-lenses were missed at \StageOne: we return to the discussion of these false
-negatives below.
+In \Tref{tab:stats}, we give overall statistics of the systems detected
+at \StageOne and \StageTwo. We give the total number of detections of
+the known lens candidates, known lenses and the new lens candidates at
+each stage.  We also give the recovery fractions for the known samples
+and fraction of total detection for the new samples at each stage. We
+find that all of the confirmed lenses found at \StageOne are also
+recovered at \StageTwo; a small fraction of the known lens candidates
+are rejected at \StageTwo. From the visually inspected known lens sample
+at \StageTwo (P$> 0.3$), the experts gave a grade of 1.3 and above to
+$\sim$~92~per~cent (33 out of 36) of the systems. Overall, the sample of
+new \sw lens candidates increased the sample of total \cfhtls lens
+candidates by over 40~per~cent. However, we find that 42~per~cent of
+known lenses were missed at \StageOne: we return to the discussion of
+these false negatives below.
 
@@
 
-\begin{table}
-\begin{center}
-\caption{ \label{tab:stats}
-Statistics of detections in \sw }
-\begin{tabular}{l l l l l}
-\hline
-   &  \multicolumn{2}{c} {\StageOne}  & \multicolumn{2}{c}{\StageTwo} \\
-      & KC  &  KL  & KC & KL \\
-\hline
-\hline
-Number  & 128 & 34 & 107  & 34  \\
-Fraction  & & & & \\
-of total recovered & 29\% & 58\% & 25\% & 58\%  \\
-$P_{\rm thresh}$ & 0.95 & 0.95 & 0.3 & 0.3 \\
-{\bf Expert Grade (G)} & $-$ & $-$ & 1.3 & 1.3 \\
-\hline
-   &  \multicolumn{2}{c} {\StageTwo}  &   & \\
-      & NC  &  AC  &  & \\
-\hline
-\hline
-Number  & {\bf 59} & 141 &  & \\
-Fraction & & & & \\
-of detections & 13\% & 33\% &  & \\
-$P_{\rm thresh}$ & 0.3 & 0.3 &  & \\
-{\bf Expert Grade (G)} & 1.3 & 1.3 & 1.3 & 1.3 \\
-
-\hline
-\end{tabular}
-\end{center}
-{KC}-- Known lens candidates \\
-{KL}-- Known lenses \\
-{NC}-- New lens candidates  \\
-{AC}-- All (known and new) lens candidates  \\
-$P_{\rm thresh}$ -- systems with Posterior probability~$P$ above this threshold are selected \\
-Note: For KC and KL, Percentages are with respect to the known
-population (i.e. 438 KC and 59 KL see \Sref{sec:data:kls}) whereas for
-NC and AC, percentages are with respect to the total sample of 429 lens
-candidates.
-\\
-\end{table}
-
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 
-We give basic information about the final sample of {\bf 59} new medium grade
+We give basic information about the final sample of 59 new medium-high grade
 lens candidates found by \sw in
@@
 of the lens system. We give their positions (RA, Dec), photometric
-redshift ($z_{phot}$), $i$ band magnitude of the lensing galaxy,
+redshift ($z_{\rm phot}$), $i$-band magnitude of the lensing galaxy,
 averaged grade~$G$ from the lens experts, zoo ID (identifier used in
@@
 of RA. As the first lens search was a blind search with no
-preselection of candidates from any algorithm, we find various types of
+pre-selection of candidates from any algorithm, we find various types of
 lenses, as expected from such a search. The final sample consists of
@@
 algorithm, whereas the ring finding algorithm may have missed this because of
-the atypical color and structure of the galaxy. Detection of red arcs, for
-example, as seen in the SW38 candidate, show how the volunteers
-extrapolate on the color parameter: the training sample contains
-predominantly blue arcs, because the source colors were drawn from realistic
+the atypical colour and structure of the galaxy. Detection of red arcs, for
+example, as seen in the SW39 candidate, shows how the volunteers
+extrapolate on the colour parameter: the training sample contains
+predominantly blue arcs, because the source colours were drawn from realistic
 observed distributions.
@@
 The power of citizen scientists also lies in the high dynamic range that
-allows us to find systems which vary from short (thick) to long (thin)
+allows us to find systems which have very short (thick) to long (thin)
 arcs, from highly compact to low surface brightness images, from round
 and point-like to elongated and curved images, from blue to red, from
-regular to exotic kinds of lenses while keeping the false positive rate
+regular to exotic kinds of lenses; while keeping the false positive rate
 low compared to algorithms. Discovery of this large sample of completely
@@
 \cfhtls photometric catalogs \citep{Coupon2009}. The total flux of the
-lensed image or arc is measured in the $g$ band but the adopted method
+lensed image or arc is measured in the $g$-band but the adopted method
 is different for different samples. For the simulated sample, we
@@
 magnitude. For the \rf sample, the arcs are detected in the scaled
-difference image of $g$ and $i$ bands from which the lensing galaxy is
+difference image of $g$ and $i$-bands from which the lensing galaxy is
 subtracted \citep[for details, see][]{Gavazzi2014}. Here, we use the flux
 of the lensed images measured by \sextractor from the scaled
-difference image, that is, $g-\alpha i$ and convert it to the $g$ band
-flux using mean colors of the foreground and background population. For
+difference image, that is, $g-\alpha i$ and convert it to the $g$-band
+flux using mean colours of the foreground and background population. For
 the \af and the \sw sample, we integrate the flux in the image pixels
 identified by \af or \sextractor.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=1.0]{comp_reinst_mag.pdf}
+\caption{ \label{fig:compre} Fraction of lens candidates recovered by \sw as a
+function of the arc magnitude ($g$ band) and the Einstein radius for three lens
+samples, namely, the known lenses, the known lens candidates and the simulated
+sample. }
+\end{center}
+\end{figure*}
 
@@
 the scaled difference image. We calculate the image separation from the
-lens center as a rough estimate of the $R_{\rm E}$. For the \af (SARCS)
+lens centre as a rough estimate of the $R_{\rm E}$. For the \af (SARCS)
 sample, we use the same definition as above except that the peak
@@
 
-We noe determine the fraction of the known sample of lenses that were recovered
+We now determine the fraction of the known sample of lenses that were recovered
 by \sw. Note that this sample corresponds to the \rf and \af samples
-combined, as mentioned in \Sref{sec:data:kls}. In \Tref{tab:stats},
+combined, as defined in \Sref{sec:data:kls}. In \Tref{tab:stats},
 we show that $\sim25-30\%$ of the known lens candidates, and
-$\sim60\%$ of the known lenses were found at \StageOne. Eighty-four
-percent of the known lens candidates and \textbf{all} of the known lenses
+$\sim60\%$ of the known lenses were found at \StageOne. We find that
+$84$\% of the known lens candidates and \textbf{all} of the known lenses
 from \StageOne passed our \StageTwo selection criterion of $P>0.3$.
@@
 is because it involves subtracting the light from the lens galaxy,
-making it easiere to detect the lensed images during both the automated
-object-finding and the visual inspection and classification
+making it easier to detect the lensed images during both the automated
+object-finding, and the visual inspection and classification
 phases. This approach naturally improves the detection
 efficiency at smaller $R_{\rm E}$ and for fainter systems. The \sw
-volunteers were not shown any galaxy-subtracted images. Showing
-galaxy-subtracted images might be a better strategy to adopt for future
+volunteers were not shown any galaxy$-$subtracted images. Showing
+galaxy$-$subtracted images might be a better strategy to adopt for future
 lens searches at galaxy-scales with \sw. In
 \Sref{sec:fn} below, we further explore and discuss why some of the confirmed
-lenses are missed by \sw.
-
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=1.0]{comp_reinst_mag.pdf}
-\caption{ \label{fig:compre} Fraction of lens candidates recovered by \sw as a
-function of the arc magnitude ($g$ band) and the Einstein radius for three lens
-samples, namely, the known lenses, the known lens candidates and the simulated
-sample. }
-\end{center}
-\end{figure*}
+lenses were missed by \sw.
 
@@
 
-Indeed, we have found 59 new medium and high grade
+Indeed, we have found 59 new medium-high grade
 lens candidates that were not known
@@
 the known \rf and \af sample (green), for the \sw identified (known and
-new) lens sample (blue) only and combined \cfhtls sample of \rf, \af and
+new) lens sample (blue) only and the combined \cfhtls sample of \rf, \af and
 the new \sw lens sample (magenta). It is interesting to note that both
@@
 corresponding to three density profiles, namely, isothermal sphere (IS),
-NFW \citep{Navarro1997} and a ``Total'' profile which has NFW and Hernquist
-profiles combined with an adiabatically contracting model for dark
+NFW and a ``Total'' profile which has NFW and Hernquist
+profiles combined with an adiabatically contracting model for the dark
 matter component \citep{Gnedin2004}. These curves are taken from
@@
 previous prediction that the mass density profiles of galaxy groups is
-indeed similar to the Total profile.
+indeed consistent with the ``Total'' profile.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Discussion}
+\label{sec:discuss}
+
+Finding gravitational lenses is a difficult and complex task. No single
+method is perfect, each method has some advantages over the other. It
+may be the case that a single method may never be the best method for
+optimising completeness and purity. Visual inspection will likely be
+required for pruning candidates at some stage of lens candidate
+selection even in the future. Therefore, we would like to understand how
+best we should combine the strengths of robots and humans to optimize
+the lens finding method.
+
+In this section, we first compare the lens candidates found by
+\sw and the lens finding robots and then attempt to understand why each
+method failed to detect lenses from the other sample.
+
+\subsection{Comparison of the \rf, \sw and \af samples}
+
+In \Fref{fig:zlmgre}, we show the lens redshift and the arc flux
+measured in $g$-band AB magnitude as a function of the Einstein radius for the \rf
+(green), the \af (red) and the \sw sample (new candidates only in blue
+and known candidates as blue circles). We note that the errors on the
+redshift measurement should not be too different across the samples
+since they are measured by a single method. However, the error on the
+total flux of the lensed images are likely to be different across the
+samples and the types of systematics are also different.  We have not
+attempted to quantify these errors in this work. With that caveat, we
+find that the \sw candidates sample is broadly similar to the
+robotically found lens candidates in terms of the flux of the lensed
+images and the redshift of the lensing galaxies.
+
+Since in this project \sw enabled a visual search based on simple colour
+composite images drawn directly from the survey,
+it was difficult to detect many lens
+candidates with a small $R_{\rm E}$ in the presence of a bright lensing
+galaxy. In contrast, the \rf sample was
+generated by working with lensing galaxy$-$subtracted images and this
+led to increased detections of small image separation candidates. The
+\sw interface did not show any galaxy subtracted images and hence,
+this results in a quantitative difference between the \sw and the \rf
+sample as a function of $R_{\rm E}$.
+
+The \af is capable of finding some small image
+separation lenses, but a lower limit at $R_{\rm E}=2\arcsec$ was imposed
+by the \af team to simplify the selection function of their sample.
+Thus, we can compare the \sw and \af samples at about $R_{\rm
+E}>2\arcsec$. There is a good overlap between the two samples given that
+most of these are candidates and could turn out not to be lenses. We again
+caution the readers that the uncertainties on the measurements are not
+quantified and may change the results to some extent.
+
+The properties considered here do not show any clear differences between
+the types of lenses being found by each method. Other properties such as
+the flux of the lensing galaxies and the surface brightness of the
+lensed images may be useful in showing some qualitative differences but
+this is beyond the scope of our current analysis. A more detailed and
+accurate analysis is deferred to the future.
+
+Lastly, in \Fref{fig:stackremg}, we show the relative distribution of
+number of candidates from each sample as a function of the Einstein
+radius and arc magnitude. The light blue colour shows the overlap between
+the \sw and the \rf samples and the purple colour shows the overlap
+between the \sw candidates and the \af samples. As noted earlier, the
+\rf dominates the small $R_{\rm E} (<2\arcsec)$ detections although \sw does
+find a modest number of candidates in this range. At larger $R_{\rm E}$,
+\sw sample begins to dominate and is comparable to the \af sample.  As a
+function of the arc magnitudes, all three samples have detections at all
+magnitudes and median magnitudes for all samples is around $g\sim24.5$.
+Relatively, the \rf sample spans a narrower range compared to the \sw
+and \af sample. However, this can be verified only after understanding
+and accounting for the systematic uncertainties in our measurements.
 
@@
 
-\section{Discussion}
-\label{sec:discuss}
-
-Finding gravitational lenses is a difficult and complex task. No single
-method is perfect, each method has some advantages over the other. It
-may be the case that a single method may never be the best method for
-optimising completeness and purity. Visual inspection will likely be
-required for pruning candidates at some stage of lens candidate
-selection even in the future. Therefore, we would like to understand how
-best we should combine the strengths of robots and humans to optimize
-the lens finding method.
-
-In this section, we first compare the lens candidates found by
-\sw and the lens finding robots and then attempt to understand why each
-method failed to detect lenses from the other sample.
-
-\subsection{Comparison of the \rf, \sw and \af samples}
-
-In \Fref{fig:zlmgre}, we show the lens redshift and the arc flux
-measured in $g$-band AB magnitude as a function of the Einstein radius for the \rf
-(green), the \af (red) and the \sw sample (new candidates only in blue
-and known candidates as blue circles). We note that the errors on the
-redshift measurement should not be too different across the samples
-since they are measured by a single method. However, the error on the
-total flux of the lensed images are likely to be different across the
-samples and the types of systematics are also different.  We have not
-attempted to quantify these errors in this work. With that caveat, we
-find that the \sw candidates sample is broadly similar to the
-robotically found lens candidates in terms of the flux of the lensed
-images and the redshift of the lensing galaxies.
-
-Since in this project \sw enabled a visual search based on simple color
-composite images drawn directly from the survey,
-it was difficult to detect many lens
-candidates with a small $R_{\rm E}$ in the presence of a bright lensing
-galaxy. In contrast, the \rf sample was
-generated by working with lensing galaxy$-$subtracted images and this
-led to increased detections of small image separation candidates. The
-\sw interface did not show any galaxy subtracted images and hence,
-this results in a quantitative difference between the \sw and the \rf
-sample as a function of $R_{\rm E}$.
-
-The \af is capable of finding some small image
-separation lenses, but a lower limit at $R_{\rm E}=2\arcsec$ was imposed
-by the \af team to simplify the selection function of their sample.
-Thus, we can compare the \sw and \af samples at about $R_{\rm
-E}>2\arcsec$. There is a good overlap between the two samples given that
-most of these are candidates and could turn out not to be lenses. We again
-caution the readers that the uncertainties on the measurements are not
-quantified and may change the results to some extent.
-
-The properties considered here do not show any clear differences between
-the types of lenses being found by each method. Other properties such as
-the flux of the lensing galaxies and the surface brightness of the
-lensed images may be useful in showing some qualitative differences but
-this is beyond the scope of our current analysis. A more detailed and
-accurate analysis is deferred to the future.
-
-Lastly, in \Fref{fig:stackremg}, we show the relative distribution of
-number of candidates from each sample as a function of the Einstein
-radius and arc magnitude. The light blue color shows the overlap between
-the \sw and the \rf samples and the purple color shows the overlap
-between the \sw candidates and the \af samples. As noted earlier, the
-\rf dominates the small $R_{\rm E} (<2\arcsec)$ detections although \sw does
-find a modest number of candidates in this range. At larger $R_{\rm E}$,
-\sw sample begins to dominate and is comparable to the \af sample.  As a
-function of the arc magnitudes, all three samples have detections at all
-magnitudes and median magnitudes for all samples is around $g\sim24.5$.
-Relatively, the \rf sample spans a narrower range compared to the \sw
-and \af sample. However, this can be verified only after understanding
-and accounting for the systematic uncertainties in our measurements.
-
 \begin{figure}
@@
 
-We test the \rf and \af on images centered on the new \sw candidates to
+We test the \rf and \af on images centred on the new \sw candidates to
 trace and understand at what stage the algorithm failed to detect them.
@@
 detected by the object finder because properties such as the image area,
-axis ratio, magnitude/color and alignment with respect to the lensing
+axis ratio, magnitude/colour and alignment with respect to the lensing
 galaxy were not satisfied. Some of the candidates missed at this stage
@@
 Next, we re-ran the \af on the same \sw sample of new candidates. The \af
-is directly run on images to look for elongated arc like objects and does
+is directly run on the images to look for elongated arc like objects and does
 not require a list of targets to begin with. Objects are identified by
@@
 of the thresholds in the code, suggesting that these could have been detected by
-\af with had its noise thresholds been set differently.
+\af had its noise thresholds been set differently.
 
@@
 detected and those that were missed)
-% have few classifications (Nclass$<$10).
-% Many of the remaining lenses have between 10 to 20
-% classifications. And, only a
 received similar numbers of classifications to the other subjects.
-A few received Nclass$>$20, possibly a result of
+A few received Nclass$>$20, possibly as a result of
 continuing to remain for a long time in the database because there was
@@
 vary in different sections of an
-image. Our eyes tend to focus usually at the center of an image and lens
+image. Our eyes tend to focus usually at the centre of an image and lens
 candidates close to the borders could go undetected. Therefore, it is
@@
 of points do not represent the actual number of detections because, for
-cases with large sample size, randomly drawn subsamples are shown for
+cases with large sample size, randomly drawn sub-samples are shown for
 the ease of visual comparison.
@@
 
-\subsubsection{Classification Uncertainty}
+\subsubsection{Classification Power}
 
@@
 small enough to introduce some scatter in the system performance, arising from
-the variations between the small groups of people inspecting each subject.
-In \PaperOne we investigated the system performamce in terms of the ``Skill''
+the variations between the small groups of volunteers inspecting each subject.
+In \PaperOne we investigated the system performance in terms of the ``Skill''
 of each agent; in \Aref{appendix:power} we define a complementary property,
@@
 $P$ of an image containing a lens. Here, we investigate whether the distribution
-of classification power is systematically
-different between the detected and missed lenses.
+of classification power is systematically different between the detected and missed lenses.
 
@@
 the left. A subject is accepted if it crosses the blue-dashed line
-marking the ($P_{\rm acc thresh}=0.95$) on the right. It is rejected if
-it crosses the red-dashed line marking the $P_{\rm rej thresh}=10^{-7}$
-on the left.
+marking the $P_{\rm acc thresh}$ (set to 0.95 for \StageOne) on the
+right. It is rejected if it crosses the red-dashed line marking the
+$P_{\rm rej thresh}$ (set to $10^{-7}$ for \StageOne) on the left.
 
@@
 volunteers are mostly classifying them as subjects with lens candidates.
-Further qualitative comparison and discussion of the trajectory plots is
-given in \Aref{appendix:traj}.
+
+The green (and red) trajectories of the missed lenses, in the bottom panels
+of \Fref{fig:detmis}, show visually easier (and more difficult) to identify
+lenses. In spite of some mild qualitative differences, both set of
+trajectories have very similar behaviour. The trajectories in panel (e)
+are typical of this sample in terms of Nclass and the dominance of small
+negative kicks. Panel (f) represents a small fraction of this sample
+where the kicks are only small and negative. The panel (g) shows how some
+lenses receive a bunch of large positive kicks which are led to
+rejection by still mostly small negative kicks. Finally, panel (h) shows
+those cases of lenses which received almost sufficient number of large
+positive kicks to be detected but ended up being rejected.
+
+The detected lenses shown with green trajectories, in the upper
+panels of \Fref{fig:detmis}, can be thought of as counterparts of the trajectories of the
+missed lenses in the corresponding bottom panels except that their
+classification power is different. Most detected lenses are similar to the case
+in panel (a) that are detected within a few classifications coming from
+large positive kicks.  Panel (b) represents a few odd cases which are
+dominated mainly by small positive kicks. Panel (c) shows a lens getting
+more classifications, but not reaching the detection or rejection
+thresholds because of the tug between positive and negative kicks mostly
+from experienced volunteers.  Panel (d) represents two extreme cases when
+the images are on the verge of being rejected but are saved thanks to a
+series of large positive kicks.  The red trajectories are some more
+examples of randomly selected cases which demonstrate how having
+sufficient number of large positive kicks allows lenses to be detected
+in spite of several small negative kicks.
 
@@
 kicks (correct classifications by high power volunteers), those
-causing positive small kicks (correct classifications by low power
-volunteers), those causing negative small kicks (incorrect
-classifications by low power volunteers) and those causing negative
-large kicks (incorrect classifications by high power volunteers). The
+causing small, positive kicks (correct classifications by low power
+volunteers), those causing small, negative kicks (incorrect
+classifications by low power volunteers) and those causing large, negative
+kicks (incorrect classifications by high power volunteers). The
 four histograms in the figure correspond to these four types of
@@
 is defined as small if
-$\Delta log{P} = \log{P_{\rm current}} - \log{P_{\rm
-previous}} < \Delta\log{P}_{\rm cut}$ (chosen as 1.2) and is large
-if greather than $\Delta\log{P}_{\rm cut}$.
-
-Some of the key differences are as follows.  i) The ratio of  large positive
-kicks to small positive kicks for the detected sample is higher than in the
-missed sample, suggesting that the fraction of high power volunteers is large
-for the detected sample.  ii) The number of classifications received by the
-missed sample is dominated small negative kicks. In contrast, for the detected
-sample there are comparable contributions from all three of small, positive
-kicks, large, positive kicks, and small, negative kicks. iii) The number of
-classifications providing large negative kicks is lower for both the detected
-and the missed samples. This is consistent with our expectation that high power
-volunteers should not be making incorrect classifications.
-We conclude that one of the major factors in the \SW system missing lenses is
-a lack of high power classifications.
+$\Delta \log{P} (= \log{P_{\rm current}} - \log{P_{\rm
+previous}}) < \Delta\log{P}_{\rm cut}$ (chosen as 1.2) and is large
+if greater than $\Delta\log{P}_{\rm cut}$.
+
+Some of the key inferences are as follows.  i) The ratio of  large
+positive kicks to small positive kicks for the detected sample is higher
+than in the missed sample, suggesting that the fraction of high power
+volunteers is large for the detected sample.  ii) The number of
+classifications received by the missed sample is dominated by small
+negative kicks. In contrast, for the detected sample there are
+comparable contributions from all three types -- small positive kicks,
+large positive kicks, and small negative kicks.  iii) The number of
+classifications providing large negative kicks is lower for both the
+detected and the missed samples. This is consistent with our expectation
+that high power volunteers should not be making incorrect
+classifications.  We conclude that one of the major factors in the \SW
+system missing the known lenses is a lack of high power classifications.
 
@@
 
-Changing the rejection and acceptance
-thresholds will likely increase the rate of false positives along with improved
-completeness.
-% After testing on a subsample of both \StageOne and
-% \StageTwo FPs, we find that a small fraction of FPs are rejected when
-% only only classifications with $|\Delta \log{P}|>1.2$ are considered.
-% Therefore, we think it is worth adopting the new strategy in the future
-% runs of SWAP in future lens searches.
-This will need to be further quantified before detailed recommendations can be
-made. However, dynamically assigning certain subjects to volunteers according to
-various measures of their skill seems like a fruitful line of investigation when
-seeking to improve the system performance in future.
+Changing the rejection and acceptance thresholds will likely increase
+the rate of false positives along with improved completeness.  This will
+need to be further quantified before detailed recommendations can be
+made. However, dynamically assigning certain subjects to volunteers
+according to various measures of their skill seems like a fruitful line
+of investigation when seeking to improve the system performance in
+future.
 
@@
 lenses, most classifications are from the low power volunteers
-identifying these images incorrectly (i.e. $-\Delta$~logP) which
+identifying these images incorrectly (i.e. $-\Delta$~log(P)) which
 overshadows the small number of correct identifications (i.e.
-$\Delta$~logP) coming from both the less and the high power volunteers
+$\Delta$~log(P)) coming from both the less and the high power volunteers
 combined. For the detected lens sample, most classifications are correct
@@
 We report the discovery of gravitational lens candidates from the
-the first \sw lens search. In this search, volunteers were shown
-$g-r-i$ color images of random regions of the sky taken by the CFHT Legacy
-Survey. The aim of this blind lens search was to find lenses that had been
-missed by previous searches done on the \cfhtls with lens finding
+first \sw lens search. In this search, volunteers were shown $g-r-i$
+colour images of random regions of the sky taken by the CFHT Legacy
+Survey. The aim of this blind lens search was to find lenses that had
+been missed by previous searches done on the \cfhtls with lens finding
 algorithms.
-The search was carried out in two stages.
-In \StageOne, volunteers inspected $\sim$ 430,000 images, and
-selected a smaller sample of $\sim$ 3000 images as having interesting lens
-candidates. In \StageTwo, after a careful second inspection of the candidates
-from \StageOne, a purer sample of $\sim$~500
-candidates was obtained. In a final step, these images were inspected by three
-of us (AM, AV and PJM) to produce a sample of candidates with grades
-ranging from possibly a lens (1) to almost certainly a lens (3).
-In this paper, we presented this new \sw sample and compared it
-with the previously known samples from two robotic searches from the
-\cfhtls, namely, \rf and \af.
+
+The search was carried out in two stages.  In \StageOne, volunteers
+inspected $\sim$ 430,000 images, and selected a smaller sample of $\sim$
+3000 images as having interesting lens candidates. In \StageTwo, after a
+careful second inspection of the candidates from \StageOne, a purer
+sample of $\sim$~500 candidates was obtained. In a final step, these
+images were inspected by three of us (AM, AV and PJM) to produce a
+sample of candidates with grades ranging from possibly a lens (1) to
+almost certainly a lens (3).  In this paper, we presented this new \sw
+sample and compared it with the previously known samples from two
+robotic searches from the \cfhtls, namely, \rf and \af.
 
@@
 \begin{itemize}
-
 \item \sw works well as a discovery engine for gravitational lenses
@@
 
+\item We use a sample of simulated lenses, duds and impostors tailored
+to the \cfhtls data to train the volunteers and calibrate their
+performance. The volunteers not only perform well on the training sample
+(see Paper I) but also find lenses that are fainter, more compact or
+redder than covered by the training sample demonstrating their
+adaptability in this task.
+
 \item We present a sample of {\bf 29 new} gravitational lens candidates,
 and an additional 30 medium grade systems. These 59 candidates received
-averaged grade G$\ge$1.3 from three experts follwing the scale
-where 1 means possibly, 2 means
-probably, and 3 means certainly, a lens. In addition, among the
-G$\ge$1.3 sample, we re-discovered 83 lens candidates from various samples
+averaged grade G$\ge$1.3 from three experts following the scale
+where (1) means possibly, (2) means
+probably, and (3) means almost certainly, a lens. In addition, among the
+G$\ge$1.3 sample, we re-discovered 82 lens candidates from various samples
 published in the literature.
@@
 \item Compared to the sample of \rf and \af robotically detected
-lens candidates, the \sw sample finds lens systems with similar properties,
+lens candidates, the \sw sample finds lens systems with statistically similar properties,
 including the range of
@@
 searches. Similarly, the lensed images too have diverse properties such
-as different colors, morphologies and sizes which are again typically
+as different colours, morphologies and sizes which are again typically
 missed by any given algorithm.
@@
 detection sensitivity at the initial \StageOne classification step.
-About 40\% of the previously known lenses (20 in total) were missed at \StageOne.
-Roughly half of these missing lenses were found to be galaxy-scale \rf
+About 40\% of the previously known lenses ($\sim$20 in total) were missed at \StageOne.
+Roughly half of these missed lenses were found to be galaxy-scale \rf
 systems, with faint arcs blended with the bright lens galaxies.
@@
 changing the strategy of when and who is shown an image: only using high power
-classifications recovers 30\% of the missing lenses.
+classifications recovers 30\% of the missed lenses.
 
@@
 search has demonstrated that the citizen scientists have successfully
-taught themselves to identify lenses within a short span of time.
-They have found lens candidates which the algorithms failed to
-discover.  Upcoming and planned wide-field imaging surveys such as the
-DES, HSC and LSST will provide formidable amounts of data. Any one approach
-for finding lenses is likely going to be inefficient. Thus, combining
-robotic methods for pre-selection with the citizen science approach for
-visual screening could be a good strategy for finding lenses in these
-large imaging surveys.
+taught themselves to identify lenses within a short span of time.  They
+have found lens candidates which the algorithms failed to discover.
+Upcoming and planned wide-field imaging surveys such as the DES, HSC and
+LSST will produce formidable amounts of data.  Blind lens searches as
+described here will be infeasible with these very large surveys although
+it may be possible to do a blind search on a subset of a large survey in
+order to assess the performance of either the algorithms or the
+volunteers which can be extrapolated to the entire survey. However, any
+one approach for finding lenses from the entire survey data is likely
+going to be inefficient. Thus, combining robotic methods for
+pre-selection with the citizen science approach for visual screening
+could be a good strategy for finding lenses in these large imaging
+surveys.
 
@@
 \begin{longtable}{llrrrrrrlrr}
+%\begin{sideways}
+%\begin{tabular}{llrrrrrrlrr}
 \caption{ \label{tab:swcands}
@@
 \hline
-SW ID & Name & RA & Dec &  $z_{\rm phot}$ & $m_i$ & $R_{\rm E}$ & G & ZooID & $P$ & Comments  \\
+SW ID & Name & RA & Dec &  $z_{\rm phot}$ & $m_i$ & $R_{\rm E}$ & $G$ & ZooID & $P$ & Comments  \\
   &  & (deg) & (deg) &  & (mag) &  (") &  &  & & \\
@@
 \multicolumn{11}{p{18cm}}{
-{\bf The redshifts with $^s$ are spectroscopic estimates taken from SDSS Data
-Release 12 whenever available unambiguously.} The column Comments has two
-type of notes. The first is about the lens image configuration where the
-symbols mean the following A: Arc, D: Double, Q: Quad, R: Ring. The
-second is a comment on the type of lens assessed visually. Note that
-this classification is not based on colors or spectral analysis. The
-symbols are E: Elliptical, S: (face on) Spiral, G: Group-scale, D: Edge
-on disk, R: Red starforming galaxy.
+The column Comments has two type of notes. The first is about the lens
+image configuration where the symbols mean the following A: Arc, D:
+Double, Q: Quad, R: Ring. The second is a comment on the type of lens
+assessed visually. Note that this classification is not based on colours
+or spectral analysis. The symbols are E: Elliptical, S: (face on)
+Spiral, G: Group-scale, D: Edge on disk, R: Red star-forming galaxy.
 }\\
 \endlastfoot
-SW19 & CFHTLS\,J020642.0$-$095157 &  31.67504 &  $-$9.86584 &  0.2 & 21.4 &  0.9 &  2.0 & ASW0001ld7 &  0.8 &  A,R   \\
-SW8  & CFHTLS\,J020648.0$-$065639 &  31.70031 &  $-$6.94430 &  0.8 & 21.0 &  1.3 &  2.3 & ASW00099ed &  0.4 &  A,E   \\
-SW43 & CFHTLS\,J020810.7$-$040220 &  32.04497 &  $-$4.03891 &  1.0 & 21.6 &  1.8 &  1.3 & ASW0001c3j &  0.7 &  A,R   \\
-SW9  & CFHTLS\,J020832.1$-$043315 &  32.13396 &  $-$4.55429 &  1.0 & 21.9 &  1.6 &  2.3 & ASW0002asp &  1.0 &  A,R   \\
-SW10 & CFHTLS\,J020848.2$-$042427 &  32.20110 &  $-$4.40751 &  0.8 & 21.6 &  1.1 &  2.3 & ASW0002bmc &  0.9 &  D,D   \\
-SW11 & CFHTLS\,J020849.8$-$050429 &  32.20784 &  $-$5.07494 &  0.8 & 21.3 &  0.9 &  2.3 & ASW0002qtn &  1.0 &  A,R   \\
-SW44 & CFHTLS\,J021021.5$-$093415 &  32.58981 &  $-$9.57109 &  0.4 & 19.0 &  2.7 &  1.3 & ASW0002k40 &  0.4 &  D,S   \\
-SW30 & CFHTLS\,J021057.9$-$084450 &  32.74148 &  $-$8.74745 &  0.45$^s$ &  0.0 &  2.5 &  1.7 & ASW0002p8y &  0.4 &  A,G   \\
-SW20 & CFHTLS\,J021221.1$-$105251 &  33.08810 & $-$10.88106 &  0.3 & 18.2 &  1.8 &  2.0 & ASW0002dx7 &  0.8 &  D,E/S   \\
-SW45 & CFHTLS\,J021225.2$-$085211 &  33.10511 &  $-$8.86973 &  0.76$^s$ & 20.5 &  2.1 &  1.3 & ASW00024id &  1.0 &  R,R   \\
-SW46 & CFHTLS\,J021317.6$-$084819 &  33.32341 &  $-$8.80549 &  0.5 & 20.6 &  1.3 &  1.3 & ASW00024q6 &  0.4 &  A,R/E   \\
-SW31 & CFHTLS\,J021514.6$-$092440 &  33.81089 &  $-$9.41115 &  0.72$^s$ & 21.1 &  2.6 &  1.7 & ASW00021r0 &  0.4 &  A,R/G   \\
+SW19 & CFHTLS\,J020642.0$-$095157 &  31.67504 &  $-$9.86584 &  0.2 & 20.8 &  0.9 &  2.0 & ASW0001ld7 &  0.8 &  A,R   \\ 
+SW8  & CFHTLS\,J020648.0$-$065639 &  31.70031 &  $-$6.94430 &  0.8 & 20.2 &  1.3 &  2.3 & ASW00099ed &  0.4 &  A,E   \\ 
+SW43 & CFHTLS\,J020810.7$-$040220 &  32.04497 &  $-$4.03891 &  1.0 & 20.8 &  1.8 &  1.3 & ASW0001c3j &  0.7 &  A,R   \\ 
+SW9  & CFHTLS\,J020832.1$-$043315 &  32.13396 &  $-$4.55429 &  1.0 & 21.0 &  1.6 &  2.3 & ASW0002asp &  1.0 &  A,R   \\ 
+SW10 & CFHTLS\,J020848.2$-$042427 &  32.20110 &  $-$4.40751 &  0.8 & 20.5 &  1.1 &  2.3 & ASW0002bmc &  0.9 &  D,D   \\ 
+SW11 & CFHTLS\,J020849.8$-$050429 &  32.20784 &  $-$5.07494 &  0.8 & 20.6 &  0.9 &  2.3 & ASW0002qtn &  1.0 &  A,R   \\ 
+SW44 & CFHTLS\,J021021.5$-$093415 &  32.58981 &  $-$9.57109 &  0.4 & 18.4 &  2.7 &  1.3 & ASW0002k40 &  0.4 &  D,S   \\ 
+SW30 & CFHTLS\,J021057.9$-$084450 &  32.74148 &  $-$8.74745 &  0.0 &  0.0 &  2.5 &  1.7 & ASW0002p8y &  0.4 &  A,G   \\ 
+SW20 & CFHTLS\,J021221.1$-$105251 &  33.08810 & $-$10.88106 &  0.3 & 17.9 &  1.8 &  2.0 & ASW0002dx7 &  0.8 &  D,E/S   \\ 
+SW45 & CFHTLS\,J021225.2$-$085211 &  33.10511 &  $-$8.86973 &  0.8 & 19.5 &  2.1 &  1.3 & ASW00024id &  1.0 &  R,R   \\ 
+SW46 & CFHTLS\,J021317.6$-$084819 &  33.32341 &  $-$8.80549 &  0.5 & 19.8 &  1.3 &  1.3 & ASW00024q6 &  0.4 &  A,R/E   \\ 
+SW31 & CFHTLS\,J021514.6$-$092440 &  33.81089 &  $-$9.41115 &  0.7 & 19.9 &  2.6 &  1.7 & ASW00021r0 &  0.4 &  A,R/G   \\ 
 SW32 & CFHTLS\,J022359.8$-$083651 &  35.99955 &  $-$8.61439 &  0.0 &  0.0 &  3.1 &  1.7 & ASW0004iye &  0.4 &  A,E   \\ 
-SW12 & CFHTLS\,J022406.1$-$062846 &  36.02558 &  $-$6.47963 &  0.4 & 20.1 &  0.9 &  2.3 & ASW0003wsu &  0.7 &  A,E   \\
+SW12 & CFHTLS\,J022406.1$-$062846 &  36.02558 &  $-$6.47963 &  0.4 & 19.6 &  0.9 &  2.3 & ASW0003wsu &  0.7 &  A,E   \\ 
 SW1  & CFHTLS\,J022409.5$-$105807 &  36.03978 & $-$10.96885 &  0.0 &  0.0 &  4.8 &  3.0 & ASW0004dv8 &  1.0 &  A,G   \\ 
-SW21 & CFHTLS\,J022533.3$-$053204 &  36.38882 &  $-$5.53460 &  0.57$^s$ & 20.4 &  3.6 &  2.0 & ASW0004m3x &  0.4 &  A,R/G   \\
-SW22 & CFHTLS\,J022716.4$-$105602 &  36.81856 & $-$10.93410 &  0.4 & 17.8 &  1.8 &  2.0 & ASW0009ab8 &  0.7 &  A,E/G   \\
-SW33 & CFHTLS\,J022745.2$-$062518 &  36.93868 &  $-$6.42183 &  0.6 & 21.3 &  1.2 &  1.7 & ASW0003s0m &  0.5 &  A,R   \\
-SW13 & CFHTLS\,J022805.6$-$051733 &  37.02362 &  $-$5.29266 &  0.4 & 19.2 &  1.4 &  2.3 & ASW00047ae &  1.0 &  Q,E   \\
-SW47 & CFHTLS\,J022843.0$-$063316 &  37.17942 &  $-$6.55465 &  0.5 & 19.9 &  1.8 &  1.3 & ASW0003r6c &  0.3 &  D/A,E   \\
-SW23 & CFHTLS\,J023008.6$-$054038 &  37.53591 &  $-$5.67744 &  0.50$^s$ & 20.4 &  1.9 &  2.0 & ASW0003r61 &  0.5 &  A,E   \\
+SW21 & CFHTLS\,J022533.3$-$053204 &  36.38882 &  $-$5.53460 &  0.5 & 19.4 &  3.6 &  2.0 & ASW0004m3x &  0.4 &  A,R/G   \\ 
+SW22 & CFHTLS\,J022716.4$-$105602 &  36.81856 & $-$10.93410 &  0.4 & 17.3 &  1.8 &  2.0 & ASW0009ab8 &  0.7 &  A,E/G   \\ 
+SW33 & CFHTLS\,J022745.2$-$062518 &  36.93868 &  $-$6.42183 &  0.6 & 20.5 &  1.2 &  1.7 & ASW0003s0m &  0.5 &  A,R   \\ 
+SW13 & CFHTLS\,J022805.6$-$051733 &  37.02362 &  $-$5.29266 &  0.4 & 18.8 &  1.4 &  2.3 & ASW00047ae &  1.0 &  Q,E   \\ 
+SW47 & CFHTLS\,J022843.0$-$063316 &  37.17942 &  $-$6.55465 &  0.5 & 19.1 &  1.8 &  1.3 & ASW0003r6c &  0.3 &  D/A,E   \\ 
+SW23 & CFHTLS\,J023008.6$-$054038 &  37.53591 &  $-$5.67744 &  0.6 & 19.7 &  1.9 &  2.0 & ASW0003r61 &  0.5 &  A,E   \\ 
 SW14 & CFHTLS\,J023123.2$-$082535 &  37.84682 &  $-$8.42663 &  0.0 &  0.0 &  1.2 &  2.3 & ASW0004xjk &  0.3 &  A,R   \\ 
-SW24 & CFHTLS\,J023315.2$-$042243 &  38.31334 &  $-$4.37886 &  0.7 & 20.4 &  1.0 &  2.0 & ASW00050sk &  0.8 &  A,R   \\
-SW34 & CFHTLS\,J023453.5$-$093032 &  38.72321 &  $-$9.50892 &  0.5 & 20.3 &  0.7 &  1.7 & ASW00051ld &  0.3 &  A,D   \\
-SW35 & CFHTLS\,J084833.2$-$044051 & 132.13847 &  $-$4.68085 &  0.8 & 21.1 &  0.9 &  1.7 & ASW0004wgd &  0.7 &  A,R   \\
-SW15 & CFHTLS\,J084841.0$-$045237 & 132.17084 &  $-$4.87720 &  0.3 & 19.5 &  1.0 &  2.3 & ASW0004nan &  1.0 &  A,E   \\
+SW24 & CFHTLS\,J023315.2$-$042243 &  38.31334 &  $-$4.37886 &  0.7 & 19.7 &  1.0 &  2.0 & ASW00050sk &  0.8 &  A,R   \\ 
+SW34 & CFHTLS\,J023453.5$-$093032 &  38.72321 &  $-$9.50892 &  0.5 & 19.8 &  0.7 &  1.7 & ASW00051ld &  0.3 &  A,D   \\ 
+SW35 & CFHTLS\,J084833.2$-$044051 & 132.13847 &  $-$4.68085 &  0.8 & 20.2 &  0.9 &  1.7 & ASW0004wgd &  0.7 &  A,R   \\ 
+SW15 & CFHTLS\,J084841.0$-$045237 & 132.17084 &  $-$4.87720 &  0.3 & 19.0 &  1.0 &  2.3 & ASW0004nan &  1.0 &  A,E   \\ 
 SW48 & CFHTLS\,J090219.0$-$053923 & 135.57947 &  $-$5.65666 &  0.0 &  0.0 &  2.0 &  1.3 & ASW0000g95 &  1.0 &  A,R/E   \\ 
-SW36 & CFHTLS\,J090248.4$-$010232 & 135.70204 &  $-$1.04243 &  0.4 & 19.7 &  1.4 &  1.7 & ASW000096t &  0.6 &  D,E   \\
+SW36 & CFHTLS\,J090248.4$-$010232 & 135.70204 &  $-$1.04243 &  0.4 & 19.1 &  1.4 &  1.7 & ASW000096t &  0.6 &  D,E   \\ 
 SW25 & CFHTLS\,J090308.2$-$043252 & 135.78449 &  $-$4.54789 &  0.0 &  0.0 &  1.3 &  2.0 & ASW00007mq &  0.6 &  D,D   \\ 
-SW49 & CFHTLS\,J090319.4$-$040146 & 135.83105 &  $-$4.02971 &  0.0 & 20.6 &  1.2 &  1.3 & ASW00007ls &  0.5 &  A,R/E   \\
+SW49 & CFHTLS\,J090319.4$-$040146 & 135.83105 &  $-$4.02971 &  0.0 & 19.8 &  1.2 &  1.3 & ASW00007ls &  0.5 &  A,R/E   \\ 
 SW50 & CFHTLS\,J090333.2$-$005829 & 135.88869 &  $-$0.97490 &  0.0 &  0.0 &  2.1 &  1.3 & ASW00008a0 &  1.0 &  A/D,E/G   \\ 
-SW51 & CFHTLS\,J135724.8$+$561614 & 209.35374 &    56.27066 &  0.36$^s$ &  0.0 &  2.6 &  1.3 & ASW0006e0o &  0.9 &  D,E   \\
-SW26 & CFHTLS\,J135755.8$+$571722 & 209.48268 &    57.28971 &  0.8 & 21.4 &  0.9 &  2.0 & ASW0005ma2 &  0.8 &  A,R   \\
-SW52 & CFHTLS\,J140027.9$+$541028 & 210.11636 &    54.17455 &  0.6 &  0.0 &  1.2 &  1.3 & ASW0006a07 &  0.6 &  Q,R/E   \\
-SW16 & CFHTLS\,J140030.2$+$574437 & 210.12601 &    57.74371 &  0.38$^s$ & 18.8 &  2.0 &  2.3 & ASW0009bp2 &  0.6 &  A,E   \\
-SW2  & CFHTLS\,J140522.2$+$574333 & 211.34261 &    57.72587 &  0.52$^s$ & 20.3 &  1.0 &  2.7 & ASW000619d &  0.7 &  A,R   \\
-SW17 & CFHTLS\,J140622.9$+$520942 & 211.59581 &    52.16169 &  0.7 & 21.3 &  1.2 &  2.3 & ASW0005rnb &  0.7 &  A,R   \\
-SW27 & CFHTLS\,J141432.9$+$534004 & 213.63716 &    53.66788 &  0.7 & 22.1 &  1.0 &  2.0 & ASW0006jh5 &  0.8 &  A,R   \\
-SW53 & CFHTLS\,J141518.9$+$513915 & 213.82903 &    51.65420 &  0.29$^s$ & 18.9 &  3.0 &  1.3 & ASW00070vl &  0.8 &  D,E   \\
+SW51 & CFHTLS\,J135724.8$+$561614 & 209.35374 &    56.27066 &  0.0 &  0.0 &  2.6 &  1.3 & ASW0006e0o &  0.9 &  D,E   \\ 
+SW26 & CFHTLS\,J135755.8$+$571722 & 209.48268 &    57.28971 &  0.8 & 20.2 &  0.9 &  2.0 & ASW0005ma2 &  0.8 &  A,R   \\ 
+SW52 & CFHTLS\,J140027.9$+$541028 & 210.11636 &    54.17455 &  0.0 &  0.0 &  1.2 &  1.3 & ASW0006a07 &  0.6 &  Q,R/E   \\ 
+SW16 & CFHTLS\,J140030.2$+$574437 & 210.12601 &    57.74371 &  0.4 & 18.2 &  2.0 &  2.3 & ASW0009bp2 &  0.6 &  A,E   \\ 
+SW2  & CFHTLS\,J140522.2$+$574333 & 211.34261 &    57.72587 &  0.7 & 19.7 &  1.0 &  2.7 & ASW000619d &  0.7 &  A,R   \\ 
+SW17 & CFHTLS\,J140622.9$+$520942 & 211.59581 &    52.16169 &  0.7 & 20.3 &  1.2 &  2.3 & ASW0005rnb &  0.7 &  A,R   \\ 
+SW27 & CFHTLS\,J141432.9$+$534004 & 213.63716 &    53.66788 &  0.7 & 21.4 &  1.0 &  2.0 & ASW0006jh5 &  0.8 &  A,R   \\ 
+SW53 & CFHTLS\,J141518.9$+$513915 & 213.82903 &    51.65420 &  0.4 & 18.3 &  3.0 &  1.3 & ASW00070vl &  0.8 &  D,E   \\ 
 SW3  & CFHTLS\,J142603.2$+$511421 & 216.51375 &    51.23935 &  0.0 &  0.0 &  4.4 &  2.7 & ASW0006mea &  0.7 &  A,G   \\ 
-SW54 & CFHTLS\,J142620.8$+$561356 & 216.58699 &    56.23230 &  0.5 & 19.9 &  1.3 &  1.3 & ASW0007sez &  0.8 &  A/R,S   \\
+SW54 & CFHTLS\,J142620.8$+$561356 & 216.58699 &    56.23230 &  0.5 & 19.5 &  1.3 &  1.3 & ASW0007sez &  0.8 &  A/R,S   \\ 
 SW55 & CFHTLS\,J142652.8$+$560001 & 216.72004 &    56.00044 &  0.0 &  0.0 &  1.5 &  1.3 & ASW0007t5y &  1.0 &  R,R   \\ 
-SW56 & CFHTLS\,J142843.5$+$543713 & 217.18153 &    54.62036 &  0.4 & 20.3 &  1.3 &  1.3 & ASW0007pga &  0.6 &  D,D   \\
-SW4  & CFHTLS\,J142934.2$+$562541 & 217.39261 &    56.42807 &  0.51$^s$ & 19.9 &  5.9 &  2.7 & ASW0009cjs &  0.8 &  A,G   \\
-SW28 & CFHTLS\,J143055.9$+$572431 & 217.73332 &    57.40883 &  0.60$^s$ & 20.1 &  1.6 &  2.0 & ASW0007xrs &  0.9 &  A,R/G   \\
+SW56 & CFHTLS\,J142843.5$+$543713 & 217.18153 &    54.62036 &  0.4 & 19.7 &  1.3 &  1.3 & ASW0007pga &  0.6 &  D,D   \\ 
+SW4  & CFHTLS\,J142934.2$+$562541 & 217.39261 &    56.42807 &  0.5 & 19.0 &  5.9 &  2.7 & ASW0009cjs &  0.8 &  A,G   \\ 
+SW28 & CFHTLS\,J143055.9$+$572431 & 217.73332 &    57.40883 &  0.7 & 19.3 &  1.6 &  2.0 & ASW0007xrs &  0.9 &  A,R/G   \\ 
 SW37 & CFHTLS\,J143100.2$+$564603 & 217.75124 &    56.76750 &  0.0 &  0.0 &  1.2 &  1.7 & ASW00086xq &  0.8 &  A,E   \\ 
-SW38 & CFHTLS\,J143353.6$+$542310 & 218.47357 &    54.38624 &  0.65$^s$ & 20.7 &  1.8 &  1.7 & ASW0009cp0 &  0.7 &  A,E   \\
-SW5  & CFHTLS\,J143454.4$+$522850 & 218.72702 &    52.48080 &  0.62$^s$ & 20.5 &  4.4 &  2.7 & ASW0007k4r &  0.4 &  Q,G/R   \\
-SW6  & CFHTLS\,J143627.9$+$563832 & 219.11636 &    56.64249 &  0.53$^s$ & 20.2 &  1.5 &  2.7 & ASW0008swn &  0.9 &  A,D   \\
-SW57 & CFHTLS\,J143631.5$+$571131 & 219.13155 &    57.19215 &  0.7 & 22.0 &  1.3 &  1.3 & ASW0008pag &  0.6 &  D/A,R   \\
-SW58 & CFHTLS\,J143651.6$+$530705 & 219.21503 &    53.11832 &  0.58$^s$ & 20.2 &  3.1 &  1.3 & ASW0007iwp &  0.7 &  A,E/G   \\
-SW18 & CFHTLS\,J143658.1$+$533807 & 219.24246 &    53.63550 &  0.61$^s$ & 20.3 &  0.9 &  2.3 & ASW0007hu2 &  0.6 &  D,D   \\
-SW29 & CFHTLS\,J143838.1$+$572647 & 219.65887 &    57.44645 &  0.8 & 21.3 &  1.1 &  2.0 & ASW0008qsm &  0.9 &  A,R   \\
-SW59 & CFHTLS\,J143950.6$+$544606 & 219.96101 &    54.76858 &  0.73$^s$ &  0.0 &  1.7 &  1.3 & ASW00085cp &  0.4 &  A,G/R   \\
-SW39 & CFHTLS\,J220215.2$+$012124 & 330.56348 &     1.35667 &  0.31$^s$ & 18.0 &  4.6 &  1.7 & ASW0005qiz &  0.5 &  rA,G   \\
-SW7  & CFHTLS\,J220256.8$+$023432 & 330.73691 &     2.57581 &  0.48$^s$ &  0.0 &  6.8 &  2.7 & ASW0007e08 &  0.8 &  A,G   \\
-SW40 & CFHTLS\,J221306.1$+$014708 & 333.27579 &     1.78561 &  0.0 & 17.8 &  1.4 &  1.7 & ASW0008wmr &  0.9 &  A,S   \\
-SW41 & CFHTLS\,J221519.7$+$005758 & 333.83212 &     0.96615 &  0.4 & 20.8 &  1.0 &  1.7 & ASW0008xbu &  0.8 &  A,D   \\
-SW42 & CFHTLS\,J221716.5$+$015826 & 334.31894 &     1.97394 &  0.1 & 22.0 &  1.0 &  1.7 & ASW00096rm &  1.0 &  A/R,R   \\
+SW38 & CFHTLS\,J143353.6$+$542310 & 218.47357 &    54.38624 &  0.8 & 19.8 &  1.8 &  1.7 & ASW0009cp0 &  0.7 &  A,E   \\ 
+SW5  & CFHTLS\,J143454.4$+$522850 & 218.72702 &    52.48080 &  0.6 & 19.4 &  4.4 &  2.7 & ASW0007k4r &  0.4 &  Q,G/R   \\ 
+SW6  & CFHTLS\,J143627.9$+$563832 & 219.11636 &    56.64249 &  0.5 & 19.5 &  1.5 &  2.7 & ASW0008swn &  0.9 &  A,D   \\ 
+SW57 & CFHTLS\,J143631.5$+$571131 & 219.13155 &    57.19215 &  0.7 & 20.9 &  1.3 &  1.3 & ASW0008pag &  0.6 &  D/A,R   \\ 
+SW58 & CFHTLS\,J143651.6$+$530705 & 219.21503 &    53.11832 &  0.6 & 19.2 &  3.1 &  1.3 & ASW0007iwp &  0.7 &  A,E/G   \\ 
+SW18 & CFHTLS\,J143658.1$+$533807 & 219.24246 &    53.63550 &  0.7 & 19.6 &  0.9 &  2.3 & ASW0007hu2 &  0.6 &  D,D   \\ 
+SW29 & CFHTLS\,J143838.1$+$572647 & 219.65887 &    57.44645 &  0.8 & 20.2 &  1.1 &  2.0 & ASW0008qsm &  0.9 &  A,R   \\ 
+SW59 & CFHTLS\,J143950.6$+$544606 & 219.96101 &    54.76858 &  0.0 &  0.0 &  1.7 &  1.3 & ASW00085cp &  0.4 &  A,G/R   \\ 
+SW39 & CFHTLS\,J220215.2$+$012124 & 330.56348 &     1.35667 &  0.3 & 17.4 &  4.6 &  1.7 & ASW0005qiz &  0.5 &  rA,G   \\ 
+SW7  & CFHTLS\,J220256.8$+$023432 & 330.73691 &     2.57581 &  0.0 &  0.0 &  6.8 &  2.7 & ASW0007e08 &  0.8 &  A,G   \\ 
+SW40 & CFHTLS\,J221306.1$+$014708 & 333.27579 &     1.78561 &  0.0 & 17.1 &  1.4 &  1.7 & ASW0008wmr &  0.9 &  A,S   \\ 
+SW41 & CFHTLS\,J221519.7$+$005758 & 333.83212 &     0.96615 &  0.4 & 20.2 &  1.0 &  1.7 & ASW0008xbu &  0.8 &  A,D   \\ 
+SW42 & CFHTLS\,J221716.5$+$015826 & 334.31894 &     1.97394 &  0.1 & 21.6 &  1.0 &  1.7 & ASW00096rm &  1.0 &  A/R,R   \\ 
 \end{longtable}
 \end{center}
+%\end{tabular}
+%\end{sideways}
 
@@
 \appendix
-
-\section{Qualitative comparison of detected and missed known lenses}
-\label{appendix:traj}
-
-The {\bf bottom-left panels of \Fref{fig:detmis} show the} missed or rejected lenses. The green (and red)
-trajectories show visually easier (and more difficult) to identify
-lenses. In spite of some mild qualitative differences, both set of
-trajectories have very similar behaviour. The trajectories in panel (e)
-are typical of this sample in terms of Nclass and the dominance of short
-negative kicks. Panel (f) represents a small fraction of this sample
-where the kicks are only short and negative. The panel (g) shows how some
-lenses receive a bunch of large positive kicks which are led to
-rejection by still mostly negative short kicks. Finally, panel (h) shows
-those cases of lenses which received almost sufficient number of large
-positive kicks to be detected but ended up being rejected.
-
-The {\bf top-left panels of \Fref{fig:detmis}} show the detected lenses.
-The cases shown with green trajectories
-in each panel can be thought of counterparts of the trajectories of the
-missed lenses in the corresponding bottom panels except that the type of
-volunteers are different. Most detected lenses are similar to the case
-in panel (a) that are detected within a few classifications coming from
-large positive kicks.  Panel (b) represents a few odd cases which are
-dominated mainly by small positive kicks. Panel (c) shows a lens getting
-more classifications, but not reaching the detection or rejection
-thresholds because of the tug between positive and negative kicks mostly
-from experienced volunteers.  Panel (d) represents two extreme cases when
-the images are on the verge of being rejected but are saved thanks to a
-series of large positive kicks.  The red trajectories are some more
-examples of randomly selected cases which demonstrate how having
-sufficient number of large positive kicks allows lenses to be detected
-in spite of several short negative kicks.
 
@@
 
-As described in the appendix of \PaperOne, the posterior probability $P$
+As described in \PaperOne, the posterior probability $P$
 of a subject is determined by the $P_{\rm L}$ and $P_{\rm D}$ of all the
@@
 containing a lens, a volunteer with high $P_{\rm L}$
-implies a large (negative) positive kick irrespective of the value of
+implies a large positive kick irrespective of the value of
 $P_{\rm D}$, as shown in the middle panel of
-\Fref{fig:skilldlnp}. However, large (negative) positive kicks are
-still possible for a volunteer located in the (lower) upper triangle
+\Fref{fig:skilldlnp}. However, large positive kicks are
+still possible for a volunteer located in the upper triangle
 with different combinations of ($P_{\rm L}$, $P_{\rm D}$) suggesting that

### 2015-05-12 doc/sw-system.tex
Reverted title after more chat with Christine

@@
 \title[\SW]
-{\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses with Citizen Science}
+{\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses}
 
@@
 an image does not contain a lens when it really doesn't contain a lens,
-$\PD = \pr(\saidNOT|\NOT,T)$.
+$\PD = \pr(\saidNOT|\NOT,T)$. The confusion matrix contains all the information
+the agent has about how good its volunteer is at classifying images.
 
@@
 \Fref{fig:swap:agent-probabilities} shows the confusion matrix elements of 200
-randomly-selected agents, as they were on a particular day during the
-\StageOne online analysis. Many volunteers classify  only a small number of images, and
-so their software agents' confusion matrix elements have remained close to their initial values
-of (0.5,0.5). As more images are classified (shown by the yellow point size),
-the agents' matrix elements tend to move towards higher values, partly as the
-volunteers attain greater skill levels (green point sizes, see
-\Sref{sec:results} below) but mostly as
-the agent updates its confusion matrix. In this upper
-right-hand quadrant, the agents perceive their volunteers to be ``astute.''
+randomly-selected agents, as they were on a particular day during the \StageOne
+online analysis. Many volunteers classify  only a small number of images, and so
+their software agents' confusion matrix elements have remained close to their
+initial values of (0.5,0.5). As more images are classified (shown by the yellow
+point size), the agents' matrix elements tend to move towards higher values,
+partly as the volunteers attain greater skill levels (green point sizes, see
+\Sref{sec:results} below) but mostly as the agent updates its confusion matrix.
+In this upper right-hand quadrant, the agents perceive their volunteers to be
+``astute.''
 
@@
 training images were ignored, and the agents' confusion matrix elements
-were instead all simply assigned initial values of 0.75
+were instead all simply assigned initial values of 0.75,
 which then remained constant. This set-up emulates a
@@
 allowing the agents to learn via their Bayesian updates.
-When the software agents are allowed to update their confusion matrices, the choice of
+When the software agents are allowed to update their confusion matrices,
+the choice of
 initial confusion matrix is not very important: the same 0.75 initial values
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+% PHIL IS HERE
 

### 2015-05-13 doc/sw-system.tex
Some edits and small comments on Paper1

@@
 lack lenses, are inserted into the image stream at random intervals; this
-training set is used to give the volunteers feedback on their performance, as
+training set is used to give the volunteers instantaneous feedback on their performance, as
 well as to calibrate a model of the system that provides
-dynamical updates to the probability of containing a lens
-of every image they classify. Low probability systems are
-retired from the site periodically, concentrating the sample towards a set of
+dynamical updates to the probability that a classified image contains a lens. Low probability systems are
+retired from the site periodically, concentrating the sample towards a set of lens
 candidates. Having divided 160 square degrees of Canada-France-Hawaii Telescope
@@
 volunteers who contributed 11~million image classifications over the course of 8
-months. The sample was reduced to 3368 \StageOne candidates; these were then
-refined to yield a sample that we expect to be over 90\% complete and 30\% pure.
+months. This \StageOne search reduced the sample to 3368 images containing candidates; these were then
+refined in \StageTwo to yield a sample that we expect to be over 90\% complete and 30\% pure, based on our analysis of the volunteers performance on training images (refer for \Sref{sec:design:stages} for more information on the two stage strategy) .
 We comment on the scalability of the \SW system to the wide field survey era,
-based on our finding that searches of $10^5$ images can be performed by a
-crowd of $10^5$ volunteers in 6 days.
+based on our finding that searches of $10^4$ images can be performed by a
+crowd of $10^4$ volunteers in 6 days.
 \end{abstract}
@@
 telescopes'' \citep[e.g.][]{StarkEtal2008,NewtonEtal2011}. Lensed quasars
-enable cosmography via the time delays between the multiple images'
-lightcurves \citep[e.g.][]{TewesEtal2013,SuyuEtal2013}, and study of the
+enable cosmography via the time delays between the lightcurves of multiple images \citep[e.g.][]{TewesEtal2013,SuyuEtal2013}, and study of the
 accretion disk itself through the microlensing effect
@@
 \cfhtls \citep[e.g.][]{MoreEtal2012,GavazziEtal2014}, Herschel
-\citep[][]{NegrelloEtal2014} and SPT \citep[e.g.][]{VieiraEtal2013}, among
+\citep[][e.g.]{NegrelloEtal2014} and SPT \citep[e.g.][]{VieiraEtal2013}, among
 others.  As the number of known lenses has increased, new types have been
@@
 same optical spectrum \citep[e.g.][]{BoltonEtal2004}, or the strong
-``magnification bias'' towards detecting strongly-lensed sources in the sub-mm
+``magnification bias'' towards detecting strongly-lensed sources in the sub-mm/mm
 waveband \citep[e.g.][]{NegrelloEtal2010}. Such searches have to yield pure samples,
@@
 
-Visual image inspection thus seems, at present, unavoidable at some level when
+Until this problem is solved by machine learning tools, at present visual image inspection seems unavoidable at some level when
 searching for gravitational lenses. The technique has some drawbacks, however.
@@
 inspected. When the image is clicked on by the volunteer, a marker symbol
-appears at that position.  Several markers can be placed, and they can be
+appears at that position.  Multiple markers can be placed, and they can be moved or
 removed by the user if they change their mind.
@@
 The next image moves rapidly in from a queue formed at the right hand side of
-the screen when the ``Finished marking'' button is pressed. Gravitational lenses
+the screen when the ``Next'' or ``Finished Marking'' button is pressed (If a marker is placed somewhere in the image, the Next button changes to a ``Finished marking'' button). Gravitational lenses
 are rare: typically, most of the images will not contain a lens candidate, and
@@
 images to be pre-loaded while the volunteer is classifying the current subject,
-and the rapid movement is designed to encourage volunteers to classify rapidly.
-After each classification, the positions of the markers are written out to the
+and the rapid movement is deliberately designed to encourage volunteers to classify quickly. There is no ``back'' button in the CI: each volunteer may only classify a given
+subject once and subjects cannot be returned to after the `Next or Finished marking' button has been pressed (this can be a source of missed lens candidates when classifying at speed).
+Note that by `classify' we mean that we interpret no markers being placed as a rejection, and placing at least one marker to mean a possible lensing event has been identified.
+After each classification, the positions of any markers are written out to the
 classification database, in an entry that also stores metadata including the ID
@@
 before they submit their classification, or after, if they ``favourite'' the
-subject. There is no ``back'' button: each volunteer may only classify a given
-subject once. However, the presence of an option to see what others think
-about any given subject before submitting your own classification means that
+subject. The option of reading other opinions on any given image or lens candidate before submitting a classification means that
 the classifications may not be strictly independent; however, the advantage of this
 system is that volunteers can learn from others what constitutes a good lens
-candidate. This is not, however, the primary educational resource; we describe
+candidate (we are not able to track who visited talk before pressing ``Finished marking''). This is not, however, the primary educational resource; we describe
 the explicit training that we provide for the volunteers in the next section.
@@
 \citet{GeachEtal2015}, for example, report the discovery of a
-red lensed arc  by volunteers who had only been trained primarily on blue
+red lensed arc  by volunteers who had only been trained primarily on blue/green
 examples. We investigate this aspect of the \SW approach further in \PaperTwo.
@@
 The top right-hand corner insets indicate the
-location of the simulated lens in each of these training images. Users needed to
+location of the simulated lens in each of these training images. Volunteers needed to
 click on these specific features in order to make a correct classification.}
@@
 The agent will be able to predict, using its model, the probability of a test
-subject being a $\LENS$ given both its volunteer's classification and its
+subject being a $\LENS$ or an empty field given both its volunteer's classification and its
 volunteer's past experience. In this section we describe how these agents work,
@@
 quadrant as each agent's volunteer views more images. Yellow point size is
-proprtional to the number of images classified; green point size shows
+proportional to the number of images classified; green point size shows
 agent-perceived ``skill'' (\Aref{appendix:swap}).}
@@
 maximum effort possible at \StageTwo is smaller, simply because fewer subjects
-were available to be classifed, and 2) the information generated per agent was
+were available to be classified, and 2) the information generated per agent was
 slightly higher at \StageTwo, just because the subjects had (on average) higher
-probability.
+probability
+MENTION HARDER TRAINING HERE MEANING THAT THE SPREAD IS LARGER??.
 
@@
 cause a significant difference between classification and contribution rate
-behavior, but perhaps reflecting a learning period at the start and then a
+behaviour, but perhaps reflecting a learning period at the start and then a
 decrease
@@
 false negatives (blue) and false positives (red) from the classification of
-the \SW \cfhtls training set. The trajectory plot for each of the 4 subjects is
+the \SW\ \cfhtls training set. The trajectory plot for each of the 4 subjects is
 shown to the right of its image. Lefthand panels show the most common types of
@@
 negatives show the lens feature. The inset for the lower righthand panel shows
-where most users believed a lens was located. There is no corresponding inset
-for the lower left panel because no particular feature stood out to users.
-Instead, users clicked many different features.}
+where most volunteers believed a lens was located. There is no corresponding inset
+for the lower left panel because no particular feature stood out to the citizens.
+Instead, volunteers clicked many different features.}
 \label{fig:discuss:performance:trajectories}
@@
 speed could have perhaps been corrected by those classifiers themselves, had
-they had access to a ``go back'' option. While clearly enabling error reduction,
+they had access to a ``go back'' option. While clearly enabling error reduction, particularly those caused by simply skimming too fast,
 we might worry about such a mechanism enabling classifiers to have a guess, then
@@
 possible on the current interface -- and indeed, it is not obvious that such
-correlations would necessarily lead to poorer system performance. There may well
-also be effects on user confidence; it may be that encouraging this sort of
+correlations would necessarily lead to poorer system performance. (REPETITION OF TALK FACTOR FROM EARLIER SECTION, IT"S NOT NEEDED TWICE). There may well
+also be effects on volunteer confidence; it may be that encouraging this sort of
 checking would result in increased and not necessarily productive caution. This
@@
 
-However, identification failures (around 60\%, from inspection of a random sample)
+However, identification failures (DEFINE WHAT YOU MEAN BY IDENTIFICATION FAILURES around 60\%, from inspection of a random sample)
 seem to be due to the statistical noise associated with
@@
 low skill, inexperienced
-classifiers (\Sref{sec:results:crowd}).
+classifiers (\Sref{sec:results:crowd}). ARE YOU SAYING THAT THERE ARE MORE OF THESE THAN THE RIGHT COLUMN EXAMPLES?  WE SHOULD GIVE NUMBERS.
 While improved training will help reduce this effect, it is here
@@
 taken up by \StageOne veterans with a broad range of skill, and also picked up a
-significant number of new users who did not have enough time to aquire high
+significant number of new users who did not have enough time to acquire high
 skill (since \StageTwo was quite short): of the 1964 volunteers who took part in

### 2015-05-14 doc/sw-cfhtls.tex
fixed some numbers in Table 2, corresp. and other minor edits

@@
 sample shows that previous constraints on the average density profile of
-lens galaxies are robust. \sw recovers about 60\% of known lenses, while
+lens galaxies are robust. \new{ \sw recovers about 65\% of known lenses, while
 the new candidates show a richer variety compared to those found by the
-two robots. This detection rate could be increased to 75\% by only using
+two robots. This detection rate could be increased to 80\% by only using}
 classifications performed by expert volunteers (albeit at the cost of a
@@
 \label{magstar2}
-\sigma_v=142 \left(\frac{L}{L_{*}}\right)^{1/3} \, Km~s^{-1}.
+\sigma_v=142 \left(\frac{L}{L_{*}}\right)^{1/3} \, {\rm Km~s^{-1}}.
 \ee
@@
 \caption{ \label{tab:stats}
-Statistics of detections in \sw }
+\new {Statistics of detections in \sw} }
 \begin{tabular}{l l l l l}
@@
 \hline
-Number  & 128 & 34 & 107  & 34  \\
+Number  & 142 & 39 & 79  & 34  \\
 Fraction  & & & & \\
-of total recovered & 29\% & 58\% & 25\% & 58\%  \\
+of total recovered & 32\% & 66\% & 18\% & 58\% \\
 $P_{\rm acc thresh}$ & 0.95 & 0.95 & 0.3 & 0.3 \\
@@
 $P_{\rm acc thresh}$ & 0.3 & 0.3 &  & \\
-Averaged Grade (G) & 1.3 & 1.3 & 1.3 & 1.3 \\
+Averaged Grade (G) & 1.3 & 1.3 & &  \\
 
@@
 
-In \Tref{tab:stats}, we give overall statistics of the systems detected
-at \StageOne and \StageTwo. We give the total number of detections of
-the known lens candidates, known lenses and the new lens candidates at
-each stage.  We also give the recovery fractions for the known samples
-and fraction of total detection for the new samples at each stage. We
-find that all of the confirmed lenses found at \StageOne are also
-recovered at \StageTwo; a small fraction of the known lens candidates
-are rejected at \StageTwo. From the visually inspected known lens sample
-at \StageTwo (P$> 0.3$), the experts gave a grade of 1.3 and above to
-$\sim$~92~per~cent (33 out of 36) of the systems. Overall, the sample of
-new \sw lens candidates increased the sample of total \cfhtls lens
-candidates by over 40~per~cent. However, we find that 42~per~cent of
-known lenses were missed at \StageOne: we return to the discussion of
-these false negatives below.
+\new{In \Tref{tab:stats}, we give overall statistics of the systems
+detected at \StageOne and \StageTwo. We give the total number of
+detections of the known lens candidates, known lenses and the new lens
+candidates at each stage.  We also give the recovery fractions for the
+known samples and fraction of total detection for the new samples at
+each stage.  Overall, the sample of new \sw lens candidates comprises
+over 40~per~cent of the total \sw$-$\cfhtls lens candidates.  Nearly
+45~per~cent of the known lens candidates from \StageOne are rejected at
+\StageTwo. Such fractions are acceptable for ``candidates'' as their
+quality grades vary from high to low.  We find that most of the
+confirmed lenses found at \StageOne are also recovered at \StageTwo.
+However, $\sim35$~per~cent of the known lenses were missed already at
+\StageOne: we return to the discussion of these false negatives below in
+\Sref{sec:fn}.
+}
 
 In \Fref{fig:stackP}, we plot the distribution of false positives and
-the high grade lens candidates,
-as a function of the $P$ value assigned by SWAP at the end of \StageTwo.
-On average, the fraction of lens candidates is indeed an increasing
-function of $P$. This shows that the \sw generated $P$ values for the
-subject are roughly correlated with the expert grades albeit with quite
-some scatter.  We note that below $P\sim0.75$,
-the fraction of false positives starts to exceed the fraction of real
-lens candidates. This could be a good threshold to choose to maximize
-the purity of the final sample. However, choosing
-$P=0.3$ gives a completeness of 100\% for the ``known
-lens'' sample instead of 67\% for $P=0.75$. Therefore, the new sample
-should also have increased completeness; expert
-grading then allows us to increase the purity of the sample.
+the high grade lens candidates, as a function of the $P$ value assigned
+by SWAP at the end of \StageTwo.  On average, the fraction of lens
+candidates is indeed an increasing function of $P$. This shows that the
+\sw generated $P$ values for the subject are roughly correlated with the
+expert grades albeit with quite some scatter.  We note that below
+$P\sim0.75$, the fraction of false positives starts to exceed the
+fraction of real lens candidates. This could be a good threshold to
+choose to maximize \new{the purity of the final sample. However,
+choosing $P=0.3$ gives a completeness of 92\% for the ``known lens''
+sample instead of 64\% for $P=0.75$.} Therefore, the new sample should
+also have increased completeness; expert grading then allows us to
+increase the purity of the sample.
 
@@
 exotic lens candidates from the visually inspected $P>0.3$ sample.
-There
-may be some more interesting candidates that were missed either at
+There may be some more interesting candidates that were missed either at
 \StageOne or \StageTwo but have been identified by volunteers in \Talk.
@@
 
-We now determine the fraction of the known sample of lenses that were recovered
-by \sw. Note that this sample corresponds to the \rf and \af samples
-combined, as defined in \Sref{sec:data:kls}. In \Tref{tab:stats},
-we show that $\sim25-30\%$ of the known lens candidates, and
-$\sim60\%$ of the known lenses were found at \StageOne. We find that
-$84$\% of the known lens candidates and \textbf{all} of the known lenses
-from \StageOne passed our \StageTwo selection criterion of $P>0.3$.
-The left and the middle panels of \Fref{fig:compre} show the
+We now determine the fraction of the known sample of lenses that were
+recovered by \sw. Note that this sample corresponds to the \rf and \af
+samples combined, as defined in \Sref{sec:data:kls}. In
+\new{ \Tref{tab:stats}, we show that $\sim32\%$ of the known lens candidates,
+and $\sim65\%$ of the known lenses were found at \StageOne. We find that
+$56$\% of the known lens candidates and $87$\% of the known lenses from
+\StageOne passed our \StageTwo selection criterion of $P>0.3$ and
+$G>1.3$.} The left and the middle panels of \Fref{fig:compre} show the
 fraction of detections as a function of arc magnitude and the Einstein
@@
 lensed image properties.
+
 Another $\sim$~50~per~cent of the \sw candidates could not be
@@
 
-Typically then, the \sw candidates were missed from the \af sample either
-because a) the arcs
-were fainter, b) the flux of the
-arc and the galaxy were blended together (such that the \af
-incorrectly connected part of the galaxy to the arc), c)
-the arcs were unusually short or thick, or d) the lensed images are almost
-circular or point-like (\af was not designed to detect lensed quasars).
+Typically then, the \sw candidates were missed from the \af sample
+either because a) the arcs were fainter, b) the flux of the arc and the
+galaxy were blended together (such that the \af incorrectly connected
+part of the galaxy to the arc), c) the arcs were unusually short or
+thick, or d) the lensed images are almost circular or point-like (\af
+was not designed to detect lensed quasars).
 
@@
 
-Like any lens finding method, the \sw system could potentially be failing
-to detect certain
-kinds of lenses.  We find that about 40~per~cent of the known sample of lenses
-are missed at \StageOne; no further losses were incurred during
-the \StageTwo refinement (see \Tref{tab:stats}).
-Below, we focus on the known
-lens sample at \StageOne to understand why some of them are being missed
-and possibly find a way to improve the detection rate which can be
-adopted in the future \sw lens searches.
-
-Many of the missed lenses are from the \rf sample with small
+\new{Like any lens finding method, the \sw system could potentially be
+failing to detect certain kinds of lenses.  We find that about
+35~per~cent of the known sample of lenses are missed at \StageOne; 
+about 10~per~cent losses were incurred during the \StageTwo refinement
+(see \Tref{tab:stats}).  Below, we focus on the known lens sample at
+\StageOne to understand why some of them are being missed and possibly
+find a way to improve the detection rate which can be adopted in the
+future \sw lens searches.}
+
+\new{Many of the missed lenses are from the \rf sample with small
 Einstein radii and faint lensed images (see \Fref{fig:compre}). Among
-the confirmed lenses from \rf, about 50~per~cent are missed. Out of the
-missed sample of 18 lenses, about half of them are visually difficult to
+the confirmed lenses from \rf, about 45~per~cent are missed. Out of the
+missed sample of 15 lenses, about half of them are visually difficult to
 detect. The other half appear to have faint blue smudges around
 galaxies which should have been easier to identify. Similarly,
-if we consider the \af lens sample, $\sim$23~per~cent are missed by \sw. This
+if we consider the \af lens sample, $\sim$20~per~cent are missed by \sw. This
 is a relatively small sample of $\sim 5$ systems and visual inspection
@@
 or they have odd properties which makes them difficult to identify
-correctly. For further tests, we combine the \rf and \af sample.
+correctly. For further tests, we combine the \rf and \af sample.}
 
@@
 
-\item We use a sample of simulated lenses, duds and impostors tailored
+\new {\item We use a sample of simulated lenses, duds and impostors tailored
 to the \cfhtls data to train the volunteers and calibrate their
@@
 redder than covered by the training sample demonstrating their
-adaptability in this task.
+adaptability in this task. }
 
@@
 
-\item Based on the known sample of lenses and lens candidates, we find
-that we lose a very small fraction of them during \StageTwo refinement.
+\new{\item Based on the known sample of lenses and lens candidates, we find
+that we lose a small fraction of them during \StageTwo refinement.
 It is more important to improve the lens
 detection sensitivity at the initial \StageOne classification step.
-About 40\% of the previously known lenses ($\sim$20 in total) were missed at \StageOne.
-Roughly half of these missed lenses were found to be galaxy-scale \rf
-systems, with faint arcs blended with the bright lens galaxies.
-
+About 35\% of the known lenses (20 in total) were missed at \StageOne.
+Two thirds of these missed lenses were found to be galaxy-scale \rf
+systems, with faint arcs blended with the bright lens galaxies.}
+
+\new{
 \item It is possible to improve the \sw completeness by
 changing the strategy of when and who is shown an image: only using high power
-classifications recovers 30\% of the missed lenses.
+classifications recovers 40\% of the missed lenses.
+}
 
@@
 have found lens candidates which the algorithms failed to discover.
-Upcoming and planned wide-field imaging surveys such as the DES, HSC and
+\new{Upcoming and planned wide-field imaging surveys such as the DES, HSC and
 LSST will produce formidable amounts of data.  Blind lens searches as
@@
 one approach for finding lenses from the entire survey data is likely
-going to be inefficient. Thus, combining robotic methods for
+going to be inefficient.} Thus, combining robotic methods for
 pre-selection with the citizen science approach for visual screening

### 2015-05-14 doc/sw-system.tex
abstract+concl. and few other edits in between

--- 2015-05-12 doc/sw-system.tex
@@
 HST images have been searched, yielding several tens of galaxy-scale lenses
-\citep[e.g.][]{MoustakasEtal2007,FaureEtal2008,Jackson2008,MoreEtal2011,
+\citep[e.g.][]{MoustakasEtal2007,Jackson2008,MoreEtal2011,
 PawaseEtal2014}. Similarly, searches of over a hundred square degrees of CFHT
@@
 from the final T0007 release taken from the Terapix
-website\footnote{\texttt{http://terapix.iap.fr/cplt/T0007/doc/T0007-doc.pdf}} for this
+website\footnote{\texttt{ftp://t07.terapix.fr/pub/T07/}} for this
 work.
@@
 visible: we expect the completeness to real lenses to be somewhat lower, as a
-result.
+result (see \PaperTwo).
 
@@
 decrease
-in participation late on.) \StageTwo (3700 subjects) was completed in around 600
+in participation later on.) \StageTwo (3400 subjects) was completed in around 600
 hours by around 2000 participants, with classification rates starting at
@@
 \centering\includegraphics[width=\linewidth]{rate_classification.pdf}
-\caption{Fractional classification rate in the \SW \cfhtls survey. Fractional classification rate is the number
+\caption{Fractional classification rate in the \SW$-$\cfhtls survey. Fractional classification rate is the number
 of classifications per unit time, divided by the final total number of
@@
 \Fref{fig:discuss:performance:trajectories} shows 2 example simulated lenses
-that were missed ($\pr(\LENS|C,T) < 10^{-5}$) by the \SW system (top row),
+that were missed ($\pr(\LENS|C,T) < 10^{-7}$) by the \SW system (top row),
 and 2 example
@@
 mixture of simulated lens and known-to-be-empty images, and we use this
-information to inform the automated interpretation of their markers. In our
+information to automate the interpretation of their markers. In our
 first lens search we simply divided the \cfhtls imaging into some 430,000 tiles,
@@
 
-\item Participation levels were high (over 36,000 volunteers, contributing
+\item Participation levels were high (about 37,000 volunteers, contributing
 classifications at rates between $10^3$ and $10^4$ images per hour), suggesting
 that if this can be maintained, visual inspection of tens of thousands of images
-could be performed just a few weeks. An expanded crowd of $10^6$ volunteers
-(which has already been reached in the Galaxy Zoo project) would
+could be performed in just a few weeks. An expanded crowd of $10^6$ volunteers
+(which has already been reached in Zooniverse) would
 be able to inspect a plausible sample of $10^6$ LSST or Euclid targets
@@
 contribution was made by a few hundred volunteers ($1\%$ of the crowd) -- but
-that the width of the skill distribution means that a  few thousand volunteers
+that the broad width of the skill distribution means that a few thousand volunteers
 could have made comparable contributions had they classified more images.
@@
 \item The optimal true positive rate (completeness) and false positive rate in
-the training set were estimated to be around $91-93\%$ and $<1\%$ (Stages 1 and
-2). This FPR translates to an approximate purity of 30\%. We find a
+the training set were estimated to be around $91-93\%$ and $<1\%$
+(Stages I and II). This FPR translates to an approximate purity of 30\%. We find a
 higher purity at \StageTwo (perhaps as a result of the least visible candidates already
@@
 galaxy-scale lenses with faint blue galaxy sources, whose lensed features are
-difficult to distinguish from the light from the lens galaxy. We observed some
+difficult to distinguish from the light from the lens galaxy (consistent
+with what we find also for real lenses, see \PaperTwo). We observed some
 additional scatter, with some simulated lenses accumulating low probability

### 2015-05-14 doc/sw-system.tex
discussion section done -see text in blue

@@
 false negatives (blue) and false positives (red) from the classification of
-the \SW \cfhtls training set. The trajectory plot for each of the 4 subjects is
+the \SW$-$\cfhtls training set. The trajectory plot for each of the 4 subjects is
 shown to the right of its image. Lefthand panels show the most common types of
@@
 learning process by including the notion of one agent being likely to be
-similar to its neighbours. Finally, it is worth noting that the model of
+similar to its neighbours in the parameter space. Finally, it is worth noting that the model of
 \citet{IBCC} explicitly avoids the assumption of the agent confusion matrix
@@
 \Tref{tab:crowd:contributions} shows the total effort, contribution, skill and
-information generated in both \StageOne and 2 of the \cfhtls project, with the
+information generated in both Stages I and II of the \cfhtls project, with the
 total numbers of agents and subjects for comparison.   These numbers allow us
@@
 lenses are to be found in a $10^4$ square degree wide field imaging survey, is
-approximately representative of the challenge facing both the LSST and Euclid
+approximately representative of the challenge facing both the \new{
+expand the acronym LSST in the Introduction -- LSST} and Euclid
 strong lensing science teams \citep{LSSTSciBook,EuclidSciBook}. What role could
@@
 $10^7$ volunteers. This is only  a factor of ten larger than the current size of
-the Zooniverse userbase. Alternatively, suppose that automated  lens finding
+the Zooniverse userbase. \new{Sentence sounds incomplete -- Alternatively, suppose that automated  lens finding
 algorithms were able to select as few as $10^5$ targets for visual
@@
 sample with 10\% purity with a surface density of $\sim10$ per square degree
-\citep[a rate within reach of \RF, for example:][]{GavazziEtal2014}.
+\citep[a rate within reach of \RF, for example:][]{GavazziEtal2014}.}
 Increasing $\tau_0$ by a factor of three to allow for
@@
 feedback from the wider \SW community, this could potentially be achieved
-through closer collaboration with the science team. It's also possible that
+through closer collaboration with the science team. It is also possible that
 dynamically assigning subjects on the basis of the volunteer's skill could act

### 2015-05-14 doc/sw-system.tex
Corrections #208

@@
 How can we scale these lens searches up to imaging surveys that cover a hundred
-times the sky area, such as the almost-all sky surveys planned with LSST and
+times the sky area, such as the almost-all sky surveys planned with the Large
+Synoptic Survey Telescope (LSST) and
 Euclid?  There are two approaches to detecting lenses in imaging surveys. The
@@
 lenses are to be found in a $10^4$ square degree wide field imaging survey, is
-approximately representative of the challenge facing both the \new{
-expand the acronym LSST in the Introduction -- LSST} and Euclid
+approximately representative of the challenge facing both the LSST and Euclid
 strong lensing science teams \citep{LSSTSciBook,EuclidSciBook}. What role could
@@
 $10^7$ volunteers. This is only  a factor of ten larger than the current size of
-the Zooniverse userbase. \new{Sentence sounds incomplete -- Alternatively, suppose that automated  lens finding
-algorithms were able to select as few as $10^5$ targets for visual
-inspection,
-sample with 10\% purity with a surface density of $\sim10$ per square degree
-\citep[a rate within reach of \RF, for example:][]{GavazziEtal2014}.}
-Increasing $\tau_0$ by a factor of three to allow for
-more inspection time per subject,  we find that \SW could enable a crowd of just
-$10^5$ volunteers to assess them in about three weeks.
+the Zooniverse userbase.
+Alternatively, suppose that automated  lens finding algorithms were able to
+select as few as $10^5$ targets for visual inspection, corresponding to a sample
+with 10\% purity and a surface density of $\sim10$ per square degree \citep[a
+rate within reach of \RF, for example:][]{GavazziEtal2014}. Increasing $\tau_0$
+by a factor of three to allow for more inspection time per subject,  we find
+that in this case \SW could enable a crowd of just $10^5$ volunteers to assess
+them in about three weeks.
 

### 2015-05-14 doc/sw-system.tex
Corrected 'users' to 'volunteers' throughout, #207

@@
 appears at that position.  Several markers can be placed, and they can be
-removed by the user if they change their mind.
+removed by the classifier if they change their mind.
 
@@
 negatives show the lens feature. The inset for the lower righthand panel shows
-where most users believed a lens was located. There is no corresponding inset
-for the lower left panel because no particular feature stood out to users.
-Instead, users clicked many different features.}
+where most volunteers believed a lens was located. There is no corresponding inset
+for the lower left panel because no particular feature stood out to the
+classifiers. Instead, the volunteers clicked many different features.}
 \label{fig:discuss:performance:trajectories}
@@
 are two less common failure modes associated with mistakes made by higher skill
-users, illustrated in the righthand column of the figure. In the false negative
+volunteers, illustrated in the righthand column of the figure. In the false negative
 subject shown in the top right-hand panel, several high skill classifiers update
@@
 correlations would necessarily lead to poorer system performance. There may well
-also be effects on user confidence; it may be that encouraging this sort of
+also be effects on volunteer confidence; it may be that encouraging this sort of
 checking would result in increased and not necessarily productive caution. This
@@
 languages (something which is now supported by the Zooniverse). A
-multi-lingual user base would come with its own set of challenges, especially
+multi-lingual userbase would come with its own set of challenges, especially
 in terms of volunteers' continuing training and interactions on \Talk.
@@
 classifications are analyzed could help assuage these fears:
-\Sref{sec:results:crowd} shows that effectively down-weighting new users'
+\Sref{sec:results:crowd} shows that effectively down-weighting new volunteers'
 classifications (by setting their agents' initial confusion matrix elements to

### 2015-05-14 doc/sw-system.tex
Changed 'Stage II' to 'Stage 2', for consistency with figures but also to reserve roman numerals for papers. #207

@@
 \Tref{tab:crowd:contributions} shows the total effort, contribution, skill and
-information generated in both Stages I and II of the \cfhtls project, with the
+information generated in both \StageOne and \StageTwo of the \cfhtls project, with the
 total numbers of agents and subjects for comparison.   These numbers allow us

### 2015-05-14 doc/sw-system.tex
Replaced 'step' with 'kick' wherever possible - 'step' makes sense when describing the trajectory as a random walk. #207

@@
 we are trying to infer. We track $\pr(\LENS|\data)$ as a function of time,
-and by comparing it to a lower or upper threshold, make decisions about
+as it is updated;
+by comparing it to a lower or upper threshold, we can make decisions about
 whether to retire the subject from the classification interface, or
@@
 downwards as they are classified by the crowd, with each agent applying the
-appropriate kick in probability based on what it hears its volunteer say.
+appropriate ``kick'' in probability based on what it hears its volunteer say.
 Encouragingly, sims (blue) tend to end up with high probability, while duds
@@
 shown to the right of its image. Lefthand panels show the most common types of
-trajectories: short step random walks resulting from no high skill classifiers
+trajectories: random walks with short steps resulting from no high skill classifiers
 viewing the subject. The righthand panels show examples where higher skill
-classifiers have been involved, causing random walks with longer step lengths
-(top) and catastrophic mis-classifications (bottom right). Note that both these
+classifiers have been involved, causing larger, more efficient ``kicks''
+(top) but also catastrophic mis-classifications (bottom right).
+Note that both these
 subjects were {\it very nearly} detected but didn't quite reach the threshold
@@
 comparable skill classifiers mis-classify the system to lower probability.   The
-trajectory looks like a random walk, but with bigger steps; this particular
+trajectory looks like a random walk, but with bigger step sizes; this particular
 subject came very close to crossing the detection  threshold three times, but
@@
 followed by a mis-classification by a very high skill ``expert'' classifier
-after 20 classifications that promotes the subject to high probability.
+after 20 classifications that ``kicks'' the subject to high probability.
 
@@
 seem to be due to the statistical noise associated with
-the many short, semi-random direction steps arising from classifications made by
+the many short, semi-random direction kicks arising from classifications made by
 low skill, inexperienced

### 2015-05-14 doc/sw-system.tex

@@
 inspected. When the image is clicked on by the volunteer, a marker symbol
-appears at that position.  Several markers can be placed, and they can be
+appears at that position.  Multiple markers can be placed, and they can be moved or
 removed by the classifier if they change their mind.
@@
 for the lower left panel because no particular feature stood out to the
-classifiers. Instead, the volunteers clicked many different features.}
+citizens. Instead, the volunteers clicked many different features.}
 \label{fig:discuss:performance:trajectories}
@@
 possible on the current interface -- and indeed, it is not obvious that such
-correlations would necessarily lead to poorer system performance. There may well
+correlations would necessarily lead to poorer system performance.
+\flag{AV}{REPETITION OF
+TALK FACTOR FROM EARLIER SECTION, IT"S NOT NEEDED TWICE}. There may well
 also be effects on volunteer confidence; it may be that encouraging this sort of

### 2015-05-14 doc/sw-system.tex
More AV comments flagged in red, #209

@@
 slightly higher at \StageTwo, just because the subjects had (on average) higher
-probability
-MENTION HARDER TRAINING HERE MEANING THAT THE SPREAD IS LARGER??.
+probability.
+
+\flag{AV}{MENTION HARDER TRAINING HERE MEANING THAT THE SPREAD IS LARGER?}
 
@@
 
-However, identification failures (DEFINE WHAT YOU MEAN BY IDENTIFICATION FAILURES around 60\%, from inspection of a random sample)
-seem to be due to the statistical noise associated with
-the many short, semi-random direction kicks arising from classifications made by
-low skill, inexperienced
-classifiers (\Sref{sec:results:crowd}). ARE YOU SAYING THAT THERE ARE MORE OF THESE THAN THE RIGHT COLUMN EXAMPLES?  WE SHOULD GIVE NUMBERS.
-While improved training will help reduce this effect, it is here
-that targeted task assignment could also help improve system performance, by
-bringing higher skill volunteers in when needed. We
-advertised \StageTwo of the current project to all registered users; it was
-taken up by \StageOne veterans with a broad range of skill, and also picked up a
-significant number of new users who did not have enough time to acquire high
-skill (since \StageTwo was quite short): of the 1964 volunteers who took part in
-the \StageTwo classification round, only 774 were veterans from \StageOne.
+However, identification failures \flag{AV}{DEFINE WHAT YOU MEAN BY IDENTIFICATION
+FAILURES} around 60\%, from inspection of a random sample) seem to be due to the
+statistical noise associated with the many short, semi-random direction kicks
+arising from classifications made by low skill, inexperienced classifiers
+(\Sref{sec:results:crowd}). \flag{AV}{ARE YOU SAYING THAT THERE ARE MORE OF THESE THAN THE
+RIGHT COLUMN EXAMPLES?  WE SHOULD GIVE NUMBERS.} While improved training will
+help reduce this effect, it is here that targeted task assignment could also
+help improve system performance, by bringing higher skill volunteers in when
+needed. We advertised \StageTwo of the current project to all registered users;
+it was taken up by \StageOne veterans with a broad range of skill, and also
+picked up a significant number of new users who did not have enough time to
+acquire high skill (since \StageTwo was quite short): of the 1964 volunteers who
+took part in the \StageTwo classification round, only 774 were veterans from
+\StageOne.
 

### 2015-05-14 doc/sw-system.tex
AV issue comments inserted in red, #209

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% AV edits
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 section, to improve the pipeline performance.
+
+\flag{AV}{Do we say somewhere that once a subject reaches 0.95 it cannot be down
+graded even if there are more classifications?}
 
@@
 
+\flag{AV}{wonder if we should include some definitions for less familiar readers
+for false positive: a non-lens that is selected by the crowd,
+false negative: a lens candidate that is rejected by the crowd,
+true positive: a lens candidate selected by the crowd,
+true negative (not used in the paper): an empty field that's correctly
+identified as being empty...}
+
 In some cases the rejection of the false negatives is understandable: the

### 2015-05-14 doc/sw-cfhtls.tex
fixed the text in blue after the recent skype disc.; no more text in blue

@@
 sample shows that previous constraints on the average density profile of
-lens galaxies are robust. \new{ \sw recovers about 65\% of known lenses, while
+lens galaxies are robust. \sw recovers about 65\% of known lenses, while
 the new candidates show a richer variety compared to those found by the
-two robots. This detection rate could be increased to 80\% by only using}
+two robots. This detection rate could be increased to 80\% by only using
 classifications performed by expert volunteers (albeit at the cost of a
@@
 the search, has a legacy value for testing future lens finding
-algorithms. We make the pipeline and the training set publicly available.
+algorithms. We make the pipeline and the training set publicly
+available.
 \end{abstract}
@@
 \caption{ \label{tab:stats}
-\new {Statistics of detections in \sw} }
+Statistics of detections in \sw }
 \begin{tabular}{l l l l l}
@@
 
-\new{In \Tref{tab:stats}, we give overall statistics of the systems
-detected at \StageOne and \StageTwo. We give the total number of
-detections of the known lens candidates, known lenses and the new lens
-candidates at each stage.  We also give the recovery fractions for the
-known samples and fraction of total detection for the new samples at
-each stage.  Overall, the sample of new \sw lens candidates comprises
-over 40~per~cent of the total \sw$-$\cfhtls lens candidates.  Nearly
-45~per~cent of the known lens candidates from \StageOne are rejected at
-\StageTwo. Such fractions are acceptable for ``candidates'' as their
-quality grades vary from high to low.  We find that most of the
-confirmed lenses found at \StageOne are also recovered at \StageTwo.
-However, $\sim35$~per~cent of the known lenses were missed already at
-\StageOne: we return to the discussion of these false negatives below in
-\Sref{sec:fn}.
-}
+In \Tref{tab:stats}, we give overall statistics of the systems detected
+at \StageOne and \StageTwo. We give the total number of detections of
+the known lens candidates, known lenses and the new lens candidates at
+each stage.  We also give the recovery fractions for the known samples
+and fraction of total detection for the new samples at each stage.
+Overall, the sample of new \sw lens candidates comprises over
+40~per~cent of the total \sw$-$\cfhtls lens candidates. We find that
+90~per~cent of the confirmed lenses found at \StageOne are also
+recovered at \StageTwo.  However, $\sim35$~per~cent of the known lenses
+were missed already at \StageOne: we return to the discussion of these
+false negatives below in \Sref{sec:fn}. Nearly 45~per~cent of the known
+lens candidates from \StageOne are rejected at \StageTwo. Such fractions
+are acceptable for ``candidates'' as their quality grades vary from high
+to low.
 
@@
 fraction of real lens candidates. This could be a good threshold to
-choose to maximize \new{the purity of the final sample. However,
+choose to maximize the purity of the final sample. However,
 choosing $P=0.3$ gives a completeness of 92\% for the ``known lens''
-sample instead of 64\% for $P=0.75$.} Therefore, the new sample should
+sample instead of 64\% for $P=0.75$. Therefore, the new sample should
 also have increased completeness; expert grading then allows us to
@@
 samples combined, as defined in \Sref{sec:data:kls}. In
-\new{ \Tref{tab:stats}, we show that $\sim32\%$ of the known lens candidates,
+\Tref{tab:stats}, we show that $\sim32\%$ of the known lens candidates,
 and $\sim65\%$ of the known lenses were found at \StageOne. We find that
@@
 \StageOne passed our \StageTwo selection criterion of $P>0.3$ and
-$G>1.3$.} The left and the middle panels of \Fref{fig:compre} show the
+$G>1.3$. The left and the middle panels of \Fref{fig:compre} show the
 fraction of detections as a function of arc magnitude and the Einstein
@@
 
-\new{Like any lens finding method, the \sw system could potentially be
+Like any lens finding method, the \sw system could potentially be
 failing to detect certain kinds of lenses.  We find that about
@@
 find a way to improve the detection rate which can be adopted in the
-future \sw lens searches.}
-
-\new{Many of the missed lenses are from the \rf sample with small
+future \sw lens searches.
+
+Many of the missed lenses are from the \rf sample with small
 Einstein radii and faint lensed images (see \Fref{fig:compre}). Among
@@
 or they have odd properties which makes them difficult to identify
-correctly. For further tests, we combine the \rf and \af sample.}
+correctly. For further tests, we combine the \rf and \af sample.
 
@@
 
-\new {\item We use a sample of simulated lenses, duds and impostors tailored
+\item We use a sample of simulated lenses, duds and impostors tailored
 to the \cfhtls data to train the volunteers and calibrate their
@@
 redder than covered by the training sample demonstrating their
-adaptability in this task. }
+adaptability in this task.
 
@@
 and an additional 30 medium grade systems. These 59 candidates received
-averaged grade G$\ge$1.3 from three experts following the scale
-where (1) means possibly, (2) means
-probably, and (3) means almost certainly, a lens. In addition, among the
-G$\ge$1.3 sample, we re-discovered 82 lens candidates from various samples
-published in the literature.
-
-\item Compared to the sample of \rf and \af robotically detected
-lens candidates, the \sw sample finds lens systems with statistically similar properties,
-including the range of
-lens redshifts, lensed image total
-magnitudes, and Einstein radii. However, having only displayed images without
-the lens galaxy light subtracted, the \sw sample does not contain
-many of the \rf-identified-lensed images with
-sub-arcsecond $R_{\rm E}$, just because the flux of the typically faint
-lensed images is obscured by the flux from bright lensing galaxies.
+averaged grade G$\ge$1.3 from three experts following the scale where
+(1) means possibly, (2) means probably, and (3) means almost certainly,
+a lens. In addition, among the G$\ge$1.3 sample, we re-discovered 82
+lens candidates from various samples published in the literature.
+
+\item Compared to the sample of \rf and \af robotically detected lens
+candidates, the \sw sample finds lens systems with statistically similar
+properties, including the range of lens redshifts, lensed image total
+magnitudes, and Einstein radii. However, having only displayed images
+without the lens galaxy light subtracted, the \sw sample does not
+contain many of the \rf-identified-lensed images with sub-arcsecond
+$R_{\rm E}$, just because the flux of the typically faint lensed images
+is obscured by the flux from bright lensing galaxies.
 
@@
 
-\new{\item Based on the known sample of lenses and lens candidates, we find
-that we lose a small fraction of them during \StageTwo refinement.
-It is more important to improve the lens
-detection sensitivity at the initial \StageOne classification step.
-About 35\% of the known lenses (20 in total) were missed at \StageOne.
-Two thirds of these missed lenses were found to be galaxy-scale \rf
-systems, with faint arcs blended with the bright lens galaxies.}
-
-\new{
+\item Based on the known sample of lenses and lens candidates, we find
+that we lose a small fraction of them during \StageTwo refinement.  It
+is more important to improve the lens detection sensitivity at the
+initial \StageOne classification step.  About 35\% of the known lenses
+(20 in total) were missed at \StageOne.  Two thirds of these missed
+lenses were found to be galaxy-scale \rf systems, with faint arcs
+blended with the bright lens galaxies.
+
 \item It is possible to improve the \sw completeness by
@@
 classifications recovers 40\% of the missed lenses.
-}
 
@@
 have found lens candidates which the algorithms failed to discover.
-\new{Upcoming and planned wide-field imaging surveys such as the DES, HSC and
+Upcoming and planned wide-field imaging surveys such as the DES, HSC and
 LSST will produce formidable amounts of data.  Blind lens searches as
@@
 order to assess the performance of either the algorithms or the
-volunteers which can be extrapolated to the entire survey. However, any
-one approach for finding lenses from the entire survey data is likely
-going to be inefficient.} Thus, combining robotic methods for
-pre-selection with the citizen science approach for visual screening
-could be a good strategy for finding lenses in these large imaging
-surveys.
+volunteers which can be extrapolated to the entire survey.  As
+demonstrated in this paper, any one approach for finding lenses from the
+entire survey data may not be sufficiently complete. Thus, combining
+robotic methods for pre-selection with the citizen science approach for
+visual screening might be a good strategy for finding lenses in these
+large imaging surveys.
 

### 2015-05-14 doc/sw-system.tex
Resolved all AV's comments #209

--- 2015-05-14 doc/sw-system.tex
@@
 retirement and subsequently ignored by the analysis code. Subjects crossing the
-detection threshold were also subsequently ignored, but they were not
+$P=0.95$ detection threshold were also subsequently ignored, but they were not
 retired from the website, just so that more volunteers could see them.
@@
 
-\flag{AV}{MENTION HARDER TRAINING HERE MEANING THAT THE SPREAD IS LARGER?}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We investigated the source of the incompleteness and impurity visible in
-\Fref{fig:results:sample:CP}, by examining the \StageTwo false negatives and
-false positives, and their behaviour as they are classified using the online
+\Fref{fig:results:sample:CP}, by examining the \StageTwo ``false negatives''
+(simulated lenses that incorrectly acquired $P < 10^{-7}$) and
+false positives (duds or impostors that incorrectly acquired $P > 0.95$),
+and their behaviour as they are classified using the online
 analysis trajectory plots introduced in \Sref{sec:swap}
@@
 speed could have perhaps been corrected by those classifiers themselves, had
-they had access to a ``go back'' option. While clearly enabling error reduction, particularly those caused by simply skimming too fast,
-we might worry about such a mechanism enabling classifiers to have a guess, then
-go and read the \Talk discussion, and then return to the classification
-interface to change their mind to agree with the forum. In fact, this is already
-possible on the current interface -- and indeed, it is not obvious that such
-correlations would necessarily lead to poorer system performance.
-\flag{AV}{REPETITION OF
-TALK FACTOR FROM EARLIER SECTION, IT"S NOT NEEDED TWICE}. There may well
-also be effects on volunteer confidence; it may be that encouraging this sort of
+they had access to a ``go back'' option. While clearly enabling error reduction,
+we might worry about such a mechanism having a negative effect on
+volunteer confidence: it may be that encouraging this sort of
 checking would result in increased and not necessarily productive caution. This
@@
 
-However, identification failures \flag{AV}{DEFINE WHAT YOU MEAN BY IDENTIFICATION
-FAILURES} around 60\%, from inspection of a random sample) seem to be due to the
-statistical noise associated with the many short, semi-random direction kicks
-arising from classifications made by low skill, inexperienced classifiers
-(\Sref{sec:results:crowd}). \flag{AV}{ARE YOU SAYING THAT THERE ARE MORE OF THESE THAN THE
-RIGHT COLUMN EXAMPLES?  WE SHOULD GIVE NUMBERS.} While improved training will
-help reduce this effect, it is here that targeted task assignment could also
-help improve system performance, by bringing higher skill volunteers in when
-needed. We advertised \StageTwo of the current project to all registered users;
-it was taken up by \StageOne veterans with a broad range of skill, and also
-picked up a significant number of new users who did not have enough time to
+However, many false negatives (around 60\%, from inspection of a random sample)
+seem to be due to the statistical noise associated with the many short,
+semi-random direction kicks arising from classifications made by low skill,
+inexperienced classifiers (\Sref{sec:results:crowd}). While improved training
+will help reduce this effect, it is here that targeted task assignment could
+also help improve system performance, by bringing higher skill volunteers in
+when needed. We advertised \StageTwo of the current project to all registered
+users; it was taken up by \StageOne veterans with a broad range of skill, and
+also picked up a significant number of new users who did not have enough time to
 acquire high skill (since \StageTwo was quite short): of the 1964 volunteers who
 took part in the \StageTwo classification round, only 774 were veterans from
-\StageOne.
+\StageOne. This issue is discussed further in \PaperTwo, where we investigate
+the known lenses missed by the \SW system.
 

### 2015-05-14 doc/sw-system.tex
Addressed Anu's final queries, closes #210. Papers now look consistent, closed #207

@@
 volunteers who contributed 11~million image classifications over the course of 8
-months. This \StageOne search reduced the sample to 3368 images containing candidates; these were then
+months. This \StageOne search reduced the sample to 3381 images containing candidates; these were then
 refined in \StageTwo to yield a sample that we expect to be over 90\% complete and 30\% pure, based on our analysis of the volunteers performance on training images (refer for \Sref{sec:design:stages} for more information on the two stage strategy) .
@@
 first one is robotic: automated analysis of the object catalogs and the survey
-images. The candidate samples produced by these methods have, to date, not been
-of high purity  \citep[see
-e.g.][]{MarshallEtal2009,MoreEtal2012,GavazziEtal2014}, with visual inspection
-by teams of humans still required to narrow down the robotically-generated
-samples. In this approach, the image data may or may not be explicitly modelled
+images. The candidate samples produced by these methods have, to date, only
+reached purities of 1-10\%, with visual inspection
+by teams of humans still required to reduce the robotically-generated
+samples by factors of 10-100 \citep[see
+e.g.][]{MarshallEtal2009,MoreEtal2012,GavazziEtal2014}.
+In this approach, the image data may or may not be explicitly modelled
 by the robots as if it contained a gravitational lens, but the visual inspection
@@
 
-Until this problem is solved by machine learning tools, at present visual image inspection seems unavoidable at some level when
+Until this problem is solved by machine learning tools,
+at present visual image inspection seems unavoidable at some level when
 searching for gravitational lenses. The technique has some drawbacks, however.
@@
 classifications will effectively not be downweighted as a result of the agent's
-ignorance. On the other hand, this ignorance could also have provided some
-conservatism, reducing the noise due to early classifications if they are
-unreliable. Whether or not an offline analysis out-performs an online one is a
+ignorance. On the other hand, this ignorance provides some conservatism,
+reducing the noise due to early classifications if they are unreliable: in
+practice we ignore the first two classifications made by  each volunteer, for
+this reason. Whether or not an offline analysis out-performs an online one is a
 matter for experiment.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
-\label{sec:results}
-
-In this section we present our findings about the performance of the \SW system,
-in terms of the classification of the training set, the  information contributed
-by the crowd, and the speed at which the image set was classified.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\subsection{Sample Properties}
-\label{sec:results:sample}
-
-We first quantify the performance of the \SW system in terms of the recovery of
-the training set images. At \StageOne, this set contained around 5712 simulated
-lenses, and 450 duds; at \StageTwo, we used 152 images of simulated lenses and
-201 duds selected as \StageOne false positives (\Sref{sec:design:stages:two}).
-\Fref{fig:results:sample:roc} shows receiver operating characteristic (ROC)
-curves for \cfhtls \StageOne and \StageTwo. These plots show the true positive
-rate (TPR, the number of sims correctly detected divided by the total number of
-sims in the training set), and the false positive rate (FPR, the number of duds
-incorrectly detected divided by the total number of duds in the training set), both
-for a given sample of detections defined by a particular probability threshold,
-which varies along the curves.  In both stages, these curves show that true
-positive rates of  around 90\% were achieved, at very low false positive rates.
-The probability threshold that was used for retirement during the \StageOne online analysis
-was 0.95; this point is marked with a star on each curve.
-This turned out to be close to optimal (although a better approach would be to
-keep track of the ROC curve as the survey progressed!).
-
-For comparison we show the results of an analysis where the classifications of
-training images were ignored, and the agents' confusion matrix elements
-were instead all simply assigned initial values of 0.75,
-which then remained constant. This set-up emulates a
-very simple unweighted voting scheme, where all classifications are treated
-equally.  In this case, the TPR never reaches 80\% in \StageOne or 60\% in
-\StageTwo, thus illustrating the benefit of including training images and
-allowing the agents to learn via their Bayesian updates.
-When the software agents are allowed to update their confusion matrices,
-the choice of
-initial confusion matrix is not very important: the same 0.75 initial values
-applied to normal, learning agents resulted in only a slightly lower TPR than
-the default case.
-
-The dot-dashed curves show the results from the offline analysis. At \StageOne the
-results are very similar to the online version that was actually run (solid
-line). However, at \StageTwo there is marginal evidence of there being greater
-benefit to doing the analysis offline (\Sref{sec:swap:offline}).
-Over 85\% TPR is achieved at zero FPR in the offline analysis , while if one is
-willing to accept a false positive rate of 5\%, the true positive rate rises to
-over 95\%, showing that some of the sims that were missed in the online analysis
-may be being recovered by doing the analysis offline. (The same is true at
-\StageOne, but to a lesser extent.) One interpretation for this result (if it holds up)
-would be that the offline analysis, by using each agent's entire history, is
-making less noisy probability estimates. This could be consistent with
-other citizen science/crowdsourcing projects where,
-in the absence of high quality information about classifiers,
-sophisticated strategies tend to under-perform naive but simpler
-ones \citep[][although we note that this rule of thumb seems not to extend
-to simple voting in this case!]{Waterhouse}.
-
-Assuming Poisson statistics for the
-fluctuations in the numbers of recovered lenses, the uncertainty in the measured
-\StageTwo TPR values is around 8\%, but the online and offline samples are
-highly correlated, such that the uncertainty on the difference between the ROC
-curves is somewhat less than this.
-Still, a larger validation set is needed to
-test these algorithmic choices more rigorously. At \StageOne, high TPR can be
-measured to better than 1\%.
 
@@
 \end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Results}
+\label{sec:results}
+
+In this section we present our findings about the performance of the \SW system,
+in terms of the classification of the training set, the  information contributed
+by the crowd, and the speed at which the image set was classified.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\subsection{Sample Properties}
+\label{sec:results:sample}
+
+We first quantify the performance of the \SW system in terms of the recovery of
+the training set images. At \StageOne, this set contained around 5712 simulated
+lenses, and 450 duds; at \StageTwo, we used 152 images of simulated lenses and
+201 duds selected as \StageOne false positives (\Sref{sec:design:stages:two}).
+\Fref{fig:results:sample:roc} shows receiver operating characteristic (ROC)
+curves for \cfhtls \StageOne and \StageTwo. These plots show the true positive
+rate (TPR, the number of sims correctly detected divided by the total number of
+sims in the training set), and the false positive rate (FPR, the number of duds
+incorrectly detected divided by the total number of duds in the training set), both
+for a given sample of detections defined by a particular probability threshold,
+which varies along the curves.  In both stages, these curves show that true
+positive rates of  around 90\% were achieved, at very low false positive rates.
+The probability threshold that was used for retirement during the \StageOne online analysis
+was 0.95; this point is marked with a star on each curve.
+This turned out to be close to optimal (although a better approach would be to
+keep track of the ROC curve as the survey progressed!).
+
+For comparison we show the results of an analysis where the classifications of
+training images were ignored, and the agents' confusion matrix elements
+were instead all simply assigned initial values of 0.75,
+which then remained constant. This set-up emulates a
+very simple unweighted voting scheme, where all classifications are treated
+equally.  In this case, the TPR never reaches 80\% in \StageOne or 60\% in
+\StageTwo, thus illustrating the benefit of including training images and
+allowing the agents to learn via their Bayesian updates.
+When the software agents are allowed to update their confusion matrices,
+the choice of
+initial confusion matrix is not very important: the same 0.75 initial values
+applied to normal, learning agents resulted in only a slightly lower TPR than
+the default case.
+
+The dot-dashed curves show the results from the offline analysis. At \StageOne the
+results are very similar to the online version that was actually run (solid
+line). However, at \StageTwo there is marginal evidence of there being greater
+benefit to doing the analysis offline (\Sref{sec:swap:offline}).
+Over 85\% TPR is achieved at zero FPR in the offline analysis , while if one is
+willing to accept a false positive rate of 5\%, the true positive rate rises to
+over 95\%, showing that some of the sims that were missed in the online analysis
+may be being recovered by doing the analysis offline. (The same is true at
+\StageOne, but to a lesser extent.) One interpretation for this result (if it holds up)
+would be that the offline analysis, by using each agent's entire history, is
+making less noisy probability estimates. This could be consistent with
+other citizen science/crowdsourcing projects where,
+in the absence of high quality information about classifiers,
+sophisticated strategies tend to under-perform naive but simpler
+ones \citep[][although we note that this rule of thumb seems not to extend
+to simple voting in this case!]{Waterhouse}.
+
+Assuming Poisson statistics for the
+fluctuations in the numbers of recovered lenses, the uncertainty in the measured
+\StageTwo TPR values is around 8\%, but the online and offline samples are
+highly correlated, such that the uncertainty on the difference between the ROC
+curves is somewhat less than this.
+Still, a larger validation set is needed to
+test these algorithmic choices more rigorously. At \StageOne, high TPR can be
+measured to better than 1\%.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering\includegraphics[width=\linewidth]{completeness_purity_simple.pdf}
+\caption{Completeness-estimated purity curves for the \sw system, using
+the \cfhtls training set. The curves are truncated at the high purity end by
+the ``detection'' limit subject probability (subjects in the online
+\StageOne analysis were
+deemed to be detected at $p=0.95$, while at \StageTwo rounding error led to
+an upper limit of $p=1.0$).}
+\label{fig:results:sample:CP}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 result (see \PaperTwo).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering\includegraphics[width=\linewidth]{completeness_purity_simple.pdf}
-\caption{Completeness-estimated purity curves for the \sw system, using
-the \cfhtls training set. The curves are truncated at the high purity end by
-the ``detection'' limit subject probability (subjects in the online
-\StageOne analysis were
-deemed to be detected at $p=0.95$, while at \StageTwo rounding error led to
-an upper limit of $p=1.0$).}
-\label{fig:results:sample:CP}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 decrease
-in participation later on.) \StageTwo (3400 subjects) was completed in around 600
+in participation later on.) \StageTwo (nearly 3400 subjects) was completed in around 600
 hours by around 2000 participants, with classification rates starting at
@@
             \hline
-                      1    & $427064$ & $1292016.3$ & $36982$ & $1471.9$ & $10802125$ & $3368$ & $91122.6$ \\
+                      1    & $427064$ & $1292016.3$ & $36982$ & $1471.9$ & $10802125$ & $3381$ & $91122.6$ \\
                       2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $89$ &  $1640.4$ \\
@@
 the training set were estimated to be around $91-93\%$ and $<1\%$
-(Stages I and II). This FPR translates to an approximate purity of 30\%. We find a
+(Stages I and II). This FPR translates to a purity of approximately 30\%.
+We find an even
 higher purity at \StageTwo (perhaps as a result of the least visible candidates already

### 2015-05-14 doc/sw-system.tex
Last few edits

@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-% PHIL IS HERE
 
@@
 broader than the corresponding distributions of agent contribution, in
-\Fref{fig:crowd:cumulplot}. For example,
-the most skilled 20\% of agents possess around 80\% of the skill.
-
+\Fref{fig:crowd:cumulplot}. For example, 80\% of the skill is distributed among
+20\% of the agents.
 The inexperienced volunteers also possess a significant fraction of the skill.
@@
 results in two groups containing approximately equal total skill (see the dashed
-curve in \Fref{fig:crowd:cumulskillplot}). The most skillful 20\% of {\it
+curve in \Fref{fig:crowd:cumulskillplot}): the most skillful 20\% of {\it
 experienced} volunteers (1824 people) only possess 43\% of the total skill.
@@
 decrease
-in participation later on.) \StageTwo (nearly 3400 subjects) was completed in around 600
+in participation later on.)
+\StageTwo (nearly 3400 subjects) was completed in around 600
 hours by around 2000 participants, with classification rates starting at
@@
 
-The similarities between \StageOne and 2, suggest that these numbers could be
-scaled to estimate the speed of future \SW projects (or at least those following
-a similar blind search strategy). For example, the completion time for a \SW
+The similarities between between \StageOne and 2 regarding the results above,
+and despite the difference in the task set,
+suggest that these numbers can be scaled to estimate cautiously
+the speed of future \SW projects. For example, the completion time for a \SW
 project may be approximated as
@@
 projects? Potential improvements to the \SW system can be divided into three
-categories, performance, efficiency and capacity.
+categories: performance, efficiency and capacity.
 
@@
 In some cases the rejection of the false negatives is understandable: the
-lensed features are faint, or in some cases, appear somewhat unrealistic compared to real lenses.
+lensed features are faint, or in some cases, appear somewhat unrealistic
+compared to real lenses.
 However, in other cases a reasonably obvious lens was passed over.  This
@@
 agent model, or its implementation.
-
 Low skill is typically a result  of inexperience (\Sref{sec:results:crowd}) --
@@
 with 10\% purity and a surface density of $\sim10$ per square degree \citep[a
-rate within reach of \RF, for example:][]{GavazziEtal2014}. Increasing $\tau_0$
+rate within reach of \RF, for example:][]{GavazziEtal2014}. Now
+increasing $\tau_0$
 by a factor of three to allow for more inspection time per subject,  we find
@@
 the training set were estimated to be around $91-93\%$ and $<1\%$
-(Stages I and II). This FPR translates to a purity of approximately 30\%.
-We find an even
+(in both classification stages).
+This FPR translates to a purity of approximately 30\%. We find an even
 higher purity at \StageTwo (perhaps as a result of the least visible candidates already
@@
 
-We thank Stuart Lynn, Kelly Borden, Laura Whyte, Brooke Simmons,
-David Hogg, Daniel Foreman-Mackey,
-Thomas Jennings, Layne  Wright, Cecile Faure, Jonathan Coles, Stuart
-Lowe and Jean-Paul Kneib for many useful conversations about citizen science and
-gravitational lens detection, and to the Dark Energy Survey and Pan-STARRS strong
-lensing science teams for their suggestions and encouragement.
+We thank Stuart Lynn, Kelly Borden, Laura Whyte, Brooke Simmons, David Hogg,
+Daniel Foreman-Mackey, Thomas Jennings, Layne  Wright, Cecile Faure, Jonathan
+Coles, Stuart Lowe and Jean-Paul Kneib for many useful conversations about
+citizen science and gravitational lens detection, and to the Dark Energy Survey
+and Pan-STARRS strong lensing science teams for their suggestions and
+encouragement.
 
@@
 evaluate $\langle\information\rangle$ at $p = 0.5$, the result has some
-useful properties. While random classifiers presented with  $p = 0.5$
+pleasing properties. While random classifiers presented with  $p = 0.5$
 subjects have $\skill = 0.0$  as expected, perfect classifiers appear to
@@
 We conservatively initialize both elements of each  agent's confusion
-matrix to be $\CM^0_{LL} = \CM^0_{NN} = 0.5$, that of a maximally ambivalent  random classifier, so
+matrix to be $\CM^0_{LL} = \CM^0_{NN} = 0.5$, that of a maximally ambivalent
+random classifier, so
 that all agents start with zero skill. While  this makes no allowance

### 2015-05-14 doc/sw-system.tex
Corrected offline downweighting sentence to mention Laplace/add-one smoothing #210

@@
 reducing the noise due to early classifications if they are unreliable: in
-practice we ignore the first two classifications made by  each volunteer, for
+practice we do downweight (via Laplace/add-one smoothing)
+the early classifications made by each volunteer, for
 this reason. Whether or not an offline analysis out-performs an online one is a

### 2015-05-14 doc/sw-system.tex
Speed conclusions couched in terms of 10^5 subjects

@@
 We comment on the scalability of the \SW system to the wide field survey era,
-based on our finding that searches of $10^4$ images can be performed by a
-crowd of $10^4$ volunteers in 6 days.
+based on our finding that searches of $10^5$ images can be performed by a
+crowd of $10^5$ volunteers in 6 days.
 \end{abstract}
@@
 completion time $\tau_0$  in \Eref{eq:speed} to decrease by roughly the same
-factor, suggesting that a dataset of $10^4$~images could be searched for lenses
-by a crowd of $10^4$ volunteers in about 6 days.
+factor, suggesting that a dataset of $10^5$~images could be searched for lenses
+by a crowd of $10^5$ volunteers in about 6 days.
 

### 2015-05-14 doc/sw-system.tex
Closes #211

@@
 Carefully produced colour composite images are displayed to volunteers via a
-web-based classification interface, which records their estimates of the positions of
-candidate lensed features. Simulated lenses, and expert-classified images which
-lack lenses, are inserted into the image stream at random intervals; this
-training set is used to give the volunteers instantaneous feedback on their performance, as
-well as to calibrate a model of the system that provides
-dynamical updates to the probability that a classified image contains a lens. Low probability systems are
-retired from the site periodically, concentrating the sample towards a set of lens
-candidates. Having divided 160 square degrees of Canada-France-Hawaii Telescope
-Legacy Survey (\cfhtls) imaging into some 430,000 overlapping 82 by 82 arcsecond
-tiles and displaying them on the site, we were joined by around 37,000
-volunteers who contributed 11~million image classifications over the course of 8
-months. This \StageOne search reduced the sample to 3381 images containing candidates; these were then
-refined in \StageTwo to yield a sample that we expect to be over 90\% complete and 30\% pure, based on our analysis of the volunteers performance on training images (refer for \Sref{sec:design:stages} for more information on the two stage strategy) .
-We comment on the scalability of the \SW system to the wide field survey era,
-based on our finding that searches of $10^5$ images can be performed by a
-crowd of $10^5$ volunteers in 6 days.
+web-based classification interface, which records their estimates of the
+positions of candidate lensed features. Simulated lenses, and expert-classified
+images which lack lenses, are inserted into the image stream at random
+intervals; this training set is used to give the volunteers instantaneous
+feedback on their performance, as well as to calibrate a model of the system
+that provides dynamical updates to the probability that a classified image
+contains a lens. Low probability systems are retired from the site periodically,
+concentrating the sample towards a set of lens candidates. Having divided 160
+square degrees of Canada-France-Hawaii Telescope Legacy Survey (\cfhtls) imaging
+into some 430,000 overlapping 82 by 82 arcsecond tiles and displaying them on
+the site, we were joined by around 37,000 volunteers who contributed 11~million
+image classifications over the course of 8 months. This \StageOne search reduced
+the sample to 3381 images containing candidates; these were then refined in
+\StageTwo to yield a sample that we expect to be over 90\% complete and 30\%
+pure, based on our analysis of the volunteers performance on training images.
+We comment on the scalability of the \SW system to the wide field
+survey era, based on our projection that searches of $10^5$ images could be performed
+by a crowd of $10^5$ volunteers in 6 days.
+
 \end{abstract}

### 2015-05-14 doc/sw-cfhtls.tex
Final minor Edits to Paper 2

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% AV IS HERE!
 
@@
 the ``known lens candidates'' sample.
+Note that the lens candidates in found in the other papers listed above were not included in our known lens candidate list and were not flagged to volunteers in \Talk.
+However, we did remove candidates in all the papers listed above when compiling the list of new lens candidates discovered in \sw described in \Sref{sec:results:newcand}.
 
@@
 
-The green (and red) trajectories of the missed lenses, in the bottom panels
-of \Fref{fig:detmis}, show visually easier (and more difficult) to identify
-lenses. In spite of some mild qualitative differences, both set of
+The bottom panels of \Fref{fig:detmis}, show the trajectories of missed lenses for visually easier and more difficult examples in red and green, respectively.
+In spite of some mild qualitative differences, both set of
 trajectories have very similar behaviour. The trajectories in panel (e)
@@
 LSST will produce formidable amounts of data.  Blind lens searches as
-described here will be infeasible with these very large surveys although
-it may be possible to do a blind search on a subset of a large survey in
+described here will be impractical with these very large surveys. However,
+it should be possible to conduct a blind search on a sub-area of a large survey in
 order to assess the performance of either the algorithms or the
-volunteers which can be extrapolated to the entire survey.  As
+volunteers, the results of which can be extrapolated to the entire survey.  As
 demonstrated in this paper, any one approach for finding lenses from the

### 2015-05-14 doc/sw-cfhtls.tex

@@
 of ``known lenses''. Note that the ``known lens'' sample is a subset of
-the ``known lens candidates'' sample.
-Note that the lens candidates in found in the other papers listed above were not included in our known lens candidate list and were not flagged to volunteers in \Talk.
-However, we did remove candidates in all the papers listed above when compiling the list of new lens candidates discovered in \sw described in \Sref{sec:results:newcand}.
+the ``known lens candidates'' sample. Also, note that the lens
+candidates from the other papers listed above were not included in our
+reference ``known'' sample and were not labelled as such in \Talk.
+However, we did exclude these candidates when compiling the list of new
+\sw lens candidates, as described in \Sref{sec:results:newcand}.
 
@@
 
-The bottom panels of \Fref{fig:detmis}, show the trajectories of missed lenses for visually easier and more difficult examples in red and green, respectively.
-In spite of some mild qualitative differences, both set of
-trajectories have very similar behaviour. The trajectories in panel (e)
-are typical of this sample in terms of Nclass and the dominance of small
-negative kicks. Panel (f) represents a small fraction of this sample
-where the kicks are only small and negative. The panel (g) shows how some
-lenses receive a bunch of large positive kicks which are led to
+The bottom panels of \Fref{fig:detmis}, show the trajectories of missed
+lenses for visually easier and more difficult examples in red and green,
+respectively.  In spite of some mild qualitative differences, both set
+of trajectories have very similar behaviour. The trajectories in panel
+(e) are typical of this sample in terms of Nclass and the dominance of
+small negative kicks. Panel (f) represents a small fraction of this
+sample where the kicks are only small and negative. The panel (g) shows
+how some lenses receive a bunch of large positive kicks which are led to
 rejection by still mostly small negative kicks. Finally, panel (h) shows
@@
 demonstrated in this paper, any one approach for finding lenses from the
-entire survey data may not be sufficiently complete. Thus, combining
+entire survey data may not be sufficiently complete and pure. Thus, combining
 robotic methods for pre-selection with the citizen science approach for

### 2015-05-25 doc/sw-extended.tex
online rule added

@@
   PL_{i}^{(k + 1)} &= \frac{PL_{i}^{k} (NL_{i}^{k} + M) + \mathbb{I}[C_{ij} =
-  z_{j}]}{NL_{i}^{k} + M + 1} \\
+  z_{j}]}{NL_{i}^{k} + M + z_{j}} \\
   PD_{i}^{(k + 1)} &= \frac{PD_{i}^{k} (ND_{i}^{k} + M) + \mathbb{I}[C_{ij} =
-  z_{j}]}{ND_{i}^{k} + M + 1}
+  z_{j}]}{ND_{i}^{k} + M + z_{j}}
 \end{align}
 where $ND_{i}^{k}$ and $NL_{i}^{k}$ refer to the number of training lenses and
-training duds observed by the $i$-th volunteer at time $k$, $z_{j}$ refers
-to the true state of the $j$-th image, and $M = 4$ is a smoothing factor
-empirically derived to smooth the skill classification of new volunteers.
+training duds observed by the $i$-th volunteer at time $k$, $z_{j}$ refers to
+the true state of the $j$-th image (1 is LENS, 0 is DUD), and $M = 4$ is a
+smoothing factor empirically derived to smooth the skill classification of new
+volunteers.
 
@@
 In practice we have training images where $p_{j}$ is known. In those
-cases we can use the true value when doing the M-Step.
+cases we can use the true value when doing the M-Step. We can also choose to
+perform the M-step using only the training images (a supervised learning
+approach), giving us another handle on quantifying the impact and importance of
+simulated training images.
 
@@
 the current estimate.
+
+An easy way to conceptualize the previous section is to note that the
+Expectation Maximization takes advantage of the fact that each classification
+is supposed to be independent of the others and so can be treated as though all
+classifications were made at the same time.  The repetition of the steps
+ensures that the parameters are self-consistent.
 
@@
 
+\subsubsection{Online}
+
+Like in the binomial case, the multinomial case can be performed online, where
+each new piece of information updates an existing assessment of lens
+classification and user skill. If a new classification $C_{iju}^{(k + 1)}$ is
+made, then by Bayes' Theorem the updates are as follows (with $i$, $j$, $u$,
+and $v$ acting as fixed indices):
+\begin{align}
+  p_{jv}^{(k + 1)} &= \left( \frac{P^{k}_{ivu}^{C_{iju}^{(k + 1)}}}{\sum_{v'}
+  p_{jv'}^{k} P^{k}_{iv'u}^{C_{iju}^{(k+1)}}} \right) p_{jv}^{k} \\
+  P^{(k+1)}_{ivu}  &= \frac{C^{(k+1)}_{iju} p^{k}_{jv} + P^{k}_{ivu} \sum_{j'\in
+  \Omega_i} p^{k}_{j'v} }{p^{k}_{jv} + \sum_{j'
+  \in \Omega_i} p^{k}_{j'v}}
+\end{align}
+If we are using only a supervised learning set, then $p^k_{j'v} \in (0, 1)$.
+
 \subsubsection{Checks}

### 2015-05-25 analysis/swap/toydb.py

@@ -12,21 +12,21 @@ class ToyDB(object):
         ToyDB
 
     PURPOSE
-        Make a toy database, and serve up data just like Mongo does 
+        Make a toy database, and serve up data just like Mongo does
         (except using standard dictionaries).
 
     COMMENTS
 
     INITIALISATION
         From scratch.
-    
+
     METHODS AND VARIABLES
         ToyDB.get_classification()
-        
+
     BUGS
 
     AUTHORS
-      This file is part of the Space Warps project, and is distributed 
+      This file is part of the Space Warps project, and is distributed
       under the MIT license by the Space Warps Science Team.
       http://spacewarps.org/
 
@@ -43,28 +43,28 @@ class ToyDB(object):
 
         try: self.surveysize = int(pars['surveysize']) # No. of subjects
         except: self.surveysize = 400
-        
+
         try: self.trainingsize = int(pars['trainingsize']) # No. of subjects
         except: self.trainingsize = 400
-        
+
         try: self.population = int(pars['population']) # No. of classifiers
         except: self.population = 100
-        
+
         try: self.enthusiasm = int(pars['enthusiasm']) # Mean no. of classifications per person
         except: self.enthusiasm = 40
-        
+
         try: self.prior = int(pars['lensrate']) # Mean no. of classifications per person
         except: self.prior = 1e-3 # Probability of an image containing a lens
 
         try: self.difficulty = int(pars['difficulty']) # Mean no. of classifications per person
         except: self.difficulty = 0.5
-        
+
         self.classifiers = self.populate('classifiers')
-        
+
         self.trainingset = self.populate('subjects',category='training')
         self.testset = self.populate('subjects',category='test')
         self.subjects = self.trainingset + self.testset
-        
+
         self.classifications = self.populate('classifications')
 
         return None
@@ -72,15 +72,15 @@ class ToyDB(object):
 # ----------------------------------------------------------------------------
 
     def __str__(self):
-        return 'database of %d Toy classifications' % (self.size())       
-        
+        return 'database of %d Toy classifications' % (self.size())
+
 # ----------------------------------------------------------------------------
 # Generate various tables in the database:
 
     def populate(self,things,category=None):
 
         array = []
-        
+
         if things == 'classifiers':
             # Store their name, and other information:
             for k in range(self.population):
@@ -90,16 +90,16 @@ class ToyDB(object):
                 classifier['truePL'],classifier['truePD'] = self.draw_from_Beta2D()
                 array.append(classifier)
 
-        
+
         elif things == 'subjects':
 
[…]

### 2015-05-26 doc/sw-extended.tex
added figure placeholder

@@
 dataset.} we augment $p$, $PL$, and $PD$ as $p_j^k$, the evaluation of
-$p_j$ at time $k$. \sw uses Bayes' Theorem to update $p_j^{(k + 1)}$ for
+$p_j$ at time $k$. \sw uses Bayes's Theorem to update $p_j^{(k + 1)}$ for
 some new evaluation $C_{ij}$\footnote{There is no superscript for $C_{ij}$
@@
 \label{sec:formalism:em:estep}
-% TODO: reword. The maximization here is over the zj's, so word to make that clear.
-% The E-Step is just taking the expected complete log-likelihood, or the
-% expectation value over $P(\cdot \ | x, \phi)$.
+\todo{Chris}{reword. The maximization here is over the zj's, so word to
+  make that clear. The E-Step is just taking the expected complete
+log-likelihood, or the expectation value over $P(\cdot \ | x, \phi)$.}
 The E-Step is maximizing the complete log-likelihood with respect to the image
-probability $p_j$.  This is equivalent to replacing $z_j$ with $p_j$:
-% TODO: replace this with equivalent like eq1
+probability $p_j$.  This is equivalent to replacing binary $z_j$ with
+probability $p_j$:
+\todo{Chris}{replace this with equivalent like eq1}
 \begin{align}
@@
 
-An easy way to conceptualize the previous section is to note that the
-Expectation Maximization takes advantage of the fact that each classification
-is supposed to be independent of the others and so can be treated as though all
-classifications were made at the same time.  The repetition of the steps
-ensures that the parameters are self-consistent.
+An easy way to conceptualize this section is to note that the Expectation
+Maximization takes advantage of the fact that each classification is supposed
+to be independent of the others and so the dataset can be treated as though all
+classifications were made at the same time.  The repetition of the $E$ and $M$
+steps ensures that the parameters are self-consistent.
 
@@
 
-\subsection{Validation of Training}
-\label{sec:validation}
+\section{Tests}
 
-\todo{Chris}{In order to look at a validation dataset, I need to create a
-  blacklist of agents and subjects (and decide what sort of division of either
-/ both / neither constitutes a good validation dataset here) that SWAP.py can
-then read in and process.}
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{Offline vs online}
 
-A validation dataset is needed to prevent overfitting training data and to try
-to test how the training data does against real lenses. These need to come in
-two categories: actual lens environments, and simulated lenses. The need for
-two sets arises because of the paucity of actual lenses. In \SW, most training
-objects are explicitly given to a user -- if a user incorrectly identifies a
-training object, they are informed of that failure, and likewise for a correct
-classification.
+\flag{Chris}{This section was somewhat talked about in \SW paper 1, but it
+needs reiterating here.}
 
-Problems:
-0. By telling users about failures in the sim/dud, we explicitly break the
-notion that users come in fully-formed. But we also need to give users
-incentives to keep working, by rewarding them for good behavior. Replace by
-current crowd assessments and telling them how they did compared with the
-crowd?
-1. \SW does not have any 'silent' training images which could function as
-validation datasets, since you have broken the training by telling users.
-2. How to manage the difference between 'dud known lens fields' and 'dud sim
-fields'? Just put them together?
-3. If you tell users about the correct sim classification, do you also tell
-them about a correct lens classification, and do you tell them it was a real
-lens?
-4. Can I just use the dud fields?
+\begin{figure}
+\begin{center}
+    \includegraphics[scale=]{Figures/}
+\end{center}
+\caption{ROC curve of online vs offline for both stages}
+\label{fig:}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[scale=]{Figures/}
+\end{center}
+\caption{Scatter plot of p values from online and offline for both stage 1 and
+stage 2. Then a second plot of a similar thing but for the confusion matrices.
+Show if there are any systematic differences that need to be explained}
+\label{fig:}
+\end{figure}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{Unsupervised vs supervised}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[scale=]{Figures/}
+\end{center}
+\caption{This figure will show three sets of ROC curves: supervised only,
+unsupervised only, and both together.}
+\label{fig:}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[scale=]{Figures/}
+\end{center}
+\caption{Scatter plot of p values using supervised only vs unsupervised +
+supervised and unsupervised only. Then a second plot of a similar thing but for
+the confusion matrices. The idea is to show that (probably) there is no major
+systematic shift in evaluations.}
+\label{fig:}
+\end{figure}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{Importance of initialization}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[scale=]{Figures/}
+\end{center}
+\caption{This figure will show ROC curves for different initialization parameters.}
+\label{fig:}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[scale=]{Figures/}
+\end{center}
+\caption{Scatter plot of p values. Then a second plot of a similar thing but for
+the confusion matrices. The idea is to show that (probably) there is no major
+systematic shift in evaluations.}
+\label{fig:}
+\end{figure}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{Simulated vs known strong lenses}
+
+\flag{Chris}{This section will talk about training on the small set of known
+  strong lenses.  I cut down the users only to those who observed strong
+  lenses. I could use as a prior the distribution of confusion matrices and
+  probabilities from the training, or maybe some sort of dirichlet model. I
+think it will be vital that I use an informative prior, since in my previous
+explorations of this matter there simply wasn't enough data to go off of.}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\section{Extensions to Existing Model}
 
@@
 multiple categories -- we can talk about things like $P(``1" | \rm{LENSED\
-QUASAR})$ where a user assigns an object a rank $"1"$ and wish to know the
+QUASAR})$ where a user assigns an object a rank $``1"$ and wish to know the
 likelihood that a lensed quasar would yield that category.
@@
 P_{i})$. Call $p_{jv} = p(z_{jv} | C_{iju}; p^0_{jv}, P_{ivu})$. It is
-sufficient to compute $p_{jv}$ to complete this step. By Bayes's Rule, we
+sufficient to compute $p_{jv}$ to compute this step. By Bayes's Theorem, we
 know that
@@
 \end{align}
+where $N_j = \sum_{i \in \Omega_j} 1$.
 
@@
 classification and user skill. If a new classification $C_{iju}^{(k + 1)}$ is
-made, then by Bayes' Theorem the updates are as follows (with $i$, $j$, $u$,
+made, then by Bayes's Theorem the updates are as follows (with $i$, $j$, $u$,
 and $v$ acting as fixed indices):
+\question{Chris}{In our case, there is only one classification $u$ such that
+  $C_{iju'} = 1$ if $u' = u$ and $0$ else. Is it more clear if I instead call
+our classification $C_{ij}$ and multiply over all $u$ indices?}
+\todo{Chris}{Double check whether the updates to $p$ and $P$ use the $k+1$ term
+of the other, and if so, the ordering of it.}
 \begin{align}
@@
   \Omega_i} p^{k}_{j'v} }{p^{k}_{jv} + \sum_{j'
-  \in \Omega_i} p^{k}_{j'v}}
-\end{align}
-If we are using only a supervised learning set, then $p^k_{j'v} \in (0, 1)$.
+  \in \Omega_i} p^{k}_{j'v}} \\
+  P^{(k+1)}_{ivu}  &= \left( \frac{p^{k}_{jv}}{p^{k}_{jv} + \sum_{j'
+  \in \Omega_i} p^{k}_{j'v}} \right) C^{(k+1)}_{iju} +
+  \left( \frac{\sum_{j'\in \Omega_i} p^{k}_{j'v}}
+    {p^{k}_{jv} + \sum_{j'\in \Omega_i} p^{k}_{j'v}}
+ \right) P^{k}_{ivu} \end{align}
+\question{Chris}{Do we like the first or second way of writing out
+$P^{(k+1)}_{ivu}$?}
+If we are using only a supervised learning set, then $p^k_{jv} \in (0, 1)$, and
+$\Omega_i$ becomes instead of the set of all images classified by user $i$ the
+set of all training images classified by user $i$.
+\todo{Chris}{Put in the Laplace smoothing. Double check that it again is just
+$M$ and $2M$ in the numerator and denominator, respectively.}
 
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{The Prior}
 
-\section{Dynamic Allocations}
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{Validation of Training}
+\label{sec:validation}
+
+\todo{Chris}{In order to look at a validation dataset, I need to create a
+  blacklist of agents and subjects (and decide what sort of division of either
+/ both / neither constitutes a good validation dataset here) that SWAP.py can
+then read in and process.}
+
+A validation dataset is needed to prevent overfitting training data, to try
+to test how the training data does against real lenses, and to train the
+hyperparameters from any priors we might use. These need to come in
+two categories: actual lens environments, and simulated lenses. The need for
+two sets arises because of the paucity of actual lenses. In \SW, most training
+objects are explicitly given to a user -- if a user incorrectly identifies a
+training object, they are informed of that failure, and likewise for a correct
+classification.
+
+Problems:
+0. By telling users about failures in the sim/dud, we explicitly break the
+notion that users come in fully-formed. But we also need to give users
+incentives to keep working, by rewarding them for good behavior. Replace by
+current crowd assessments and telling them how they did compared with the
+crowd?
+1. \SW does not have any 'silent' training images which could function as
+validation datasets, since you have broken the training by telling users.
+2. How to manage the difference between 'dud known lens fields' and 'dud sim
+fields'? Just put them together?
+3. If you tell users about the correct sim classification, do you also tell
+them about a correct lens classification, and do you tell them it was a real
+lens?
+4. Can I just use the dud fields?
+
+\begin{figure}
+\begin{center}
+    \includegraphics[scale=]{Figures/}
+\end{center}
+\caption{This figure }
+\label{fig:validation}
+\end{figure}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{Dynamic Allocations}
 \todo{Chris}{This section will examine whether we would be better off

### 2015-05-26 doc/sw-extended.tex
added figure placeholder

@@
 
+\subsubsection{Test}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[scale=]{Figures/}
+\end{center}
+\caption{This figure will be an ROC curve of the two subtypes in stage2 using
+the above way of doing the confusion matrix. Also plotted will be the ROC
+curves of the subtypes using just the binary classification. Do we do better by actually specifying? Or are we basically as well
+off just taking our binary distribution and dividing up? Failure modes are:
+either we don't have enough sims of each subtype to make this worthwhile, or it
+doesn't help.}
+\label{fig:}
+\end{figure}
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 
+\subsection{Relaxing Constant Confusion Matrices}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
 \section{Discussion}

### 2015-07-22 doc/sw-system.tex
Started Paper 1 referee response, done all easy ones, issued figures. #216

@@
 web-based classification interface, which records their estimates of the
-positions of candidate lensed features. Simulated lenses, and expert-classified
+positions of candidate lensed features. Images of simulated lenses, as
+well as real
 images which lack lenses, are inserted into the image stream at random
@@
 made by the volunteer on viewing the subject. $N_X$ is the number of
-lenses the volunteer has been shown, while $N_{``X"}$ is the number of
+training subjects of the relevant type the volunteer has been shown,
+while $N_{``X"}$ is the number of
 times the volunteer got their classifications of this type of training subject
@@
 
-\subsubsection{Examples}
-\label{sec:swap:details:examples}
-
-Suppose we have a volunteer who is always right about the true
+For example, suppose we have a volunteer who is always right about the true
 nature of a training subject.
@@
 
-\subsection{Practicalities}
+\subsection{Application to the CFHTLS Classifications}
 \label{sec:swap:practicalities}
@@
 \StageTwo results (dot-dashed orange curve).
-Lens probability varies along the curves: the stars indicate the point where
+Lens probability threshold varies along the curves: the stars indicate the point where
 the value of this quantity is 0.95.}
@@
 deemed to be detected at $p=0.95$, while at \StageTwo rounding error led to
-an upper limit of $p=1.0$).}
+an upper limit of $p=1.0$). The inset shows a magnified view of the
+bottom righthand corner of the plot.}
 \label{fig:results:sample:CP}
@@
 known elsewhere as the ``recall.''  The purity is also known as the
-``precision.''} If the training set samples from the same systems as the test
-set, then the completeness of the training set will be equivalent to the
-completeness of the test set. The purity depends on the proportion of sims to
+``precision.''}
+%
+If the training set were to be sampled fairly from test set, the
+completeness of the training set would be equal to the completeness of
+the test set. (In practice this will likely only be approximately
+true, as simulated lenses [and the distributions of their properties]
+are used instead of real ones.)
+
+The purity depends on the proportion of sims to
 duds, and so the purity of the test set must be approximated by rescaling the
@@
 
-The similarities between between \StageOne and 2 regarding the results above,
+The similarities between \StageOne and 2 regarding the results above,
 and despite the difference in the task set,
@@
 of \Fref{fig:discuss:performance:trajectories}.
-
 The false positives show similar behaviour, for example in the bottom lefthand
-panel of the figure. As well as subjects being ``unlucky'' in this way, there
+panel of the figure.
+
+As well as subjects being ``unlucky'' in this way, there
 are two less common failure modes associated with mistakes made by higher skill
@@
 
-\subsection{Increasing capacity}
+\subsection{Increasing crowd capacity}
 \label{sec:discuss:capacity}
@@
 $10^3$ achieving considerable skill, and a few $10^2$ having the time to make a
-significant contribution. Slightly more quantitively, we might note that  the
+significant contribution. Slightly more quantitatively, we might note that  the
 total skill of the crowd, computed by summing the skill of all the agents, is a

### 2015-07-22 analysis/swap/collection.py
Tweaked trajectory plot to make color contrast greater #219

@@ -16,20 +16,20 @@ class Collection(object):
         Model a collection of subjects.
 
     COMMENTS
-        All subjects in a Collection are all Zooniverse subjects. 
+        All subjects in a Collection are all Zooniverse subjects.
 
     INITIALISATION
         From scratch.
-    
+
     METHODS
         Collection.member(Name)     Returns the Subject called Name
         Collection.size()           Returns the size of the Collection
         Collection.list()           Returns the IDs of the members
-        
+
     BUGS
 
     AUTHORS
-      This file is part of the Space Warps project, and is distributed 
+      This file is part of the Space Warps project, and is distributed
       under the MIT license by the Space Warps Science Team.
       http://spacewarps.org/
 
@@ -39,51 +39,51 @@ class Collection(object):
 # ----------------------------------------------------------------------------
 
     def __init__(self):
-        
+
         self.member = {}
         self.probabilities = {'sim':np.array([]), 'dud':np.array([]), 'test':np.array([])}
         self.exposure = {'sim':np.array([]), 'dud':np.array([]), 'test':np.array([])}
-         
+
         return None
 
 # ----------------------------------------------------------------------------
 
     def __str__(self):
-        return 'collection of %d subjects' % (self.size())       
-        
+        return 'collection of %d subjects' % (self.size())
+
 # ----------------------------------------------------------------------------
 # Return the number of collection members:
 
     def size(self):
         return len(self.member)
-        
+
 # ----------------------------------------------------------------------------
 # # Return an array giving each samples' exposure to the agents:
-# 
+#
 #     def get_exposure(self):
-#     
+#
 #         N = np.array([])
 #         for ID in self.list():
 #             subject = self.member[ID]
 #             N = np.append(N,subject.exposure)
-#             
-#         self.exposure = N    
+#
+#         self.exposure = N
 #         return N
-#         
+#
 # ----------------------------------------------------------------------------
 # Return a complete list of collection members:
 
     def list(self):
         return self.member.keys()
-        
+
 # ----------------------------------------------------------------------------
-# Return a list of N collection members, selected at regular intervals. This 
-# *should* contain a significant number of training subjects, since on average 
+# Return a list of N collection members, selected at regular intervals. This
[…]

### 2015-07-22 analysis/swap/subject.py

@@ -342,10 +342,19 @@ class Subject(object):
 
         if self.kind == 'sim':
             colour = 'blue'
+            linewidth = 1.5
+            alpha = 0.3
+            size = 30
         elif self.kind == 'dud':
             colour = 'red'
+            linewidth = 1.5
+            alpha = 0.3
+            size = 30
         elif self.kind == 'test':
             colour = 'black'
+            linewidth = 1.0
+            alpha = 0.1
+            size = 20
 
         if self.status == 'undecided':
             facecolour = colour
@@ -355,20 +364,22 @@ class Subject(object):
         if highlight:
             # Thicker, darker line:
             plt.plot(mdn_trajectory,N,color=colour,alpha=0.5,linewidth=2.0, linestyle="-")
+            # Bigger point:
+            size = 40
         else:
             # Thinner, fainter line:
-            plt.plot(mdn_trajectory,N,color=colour,alpha=0.1,linewidth=1.0, linestyle="-")
+            plt.plot(mdn_trajectory,N,color=colour,alpha=alpha,linewidth=linewidth, linestyle="-")
 
         NN = N[-1]
         if NN > swap.Ncmax: NN = swap.Ncmax
         if highlight:
             # Heavier symbol:
-            plt.scatter(mdn_trajectory[-1], NN, edgecolors=colour, facecolors=facecolour, alpha=0.8);
+            plt.scatter(mdn_trajectory[-1], NN, s=size, edgecolors=colour, facecolors=facecolour, alpha=0.8);
             plt.plot([mdn_trajectory[-1]-sigma_trajectory_m[-1],mdn_trajectory[-1]+sigma_trajectory_p[-1]],[NN,NN],color=colour,alpha=0.5);
         else:
             # Fainter symbol:
-            plt.scatter(mdn_trajectory[-1], NN, edgecolors=colour, facecolors=facecolour, alpha=0.5);
-            plt.plot([mdn_trajectory[-1]-sigma_trajectory_m[-1],mdn_trajectory[-1]+sigma_trajectory_p[-1]],[NN,NN],color=colour,alpha=0.3);
+            plt.scatter(mdn_trajectory[-1], NN, s=size, edgecolors=colour, facecolors=facecolour, alpha=alpha+0.4);
+            plt.plot([mdn_trajectory[-1]-sigma_trajectory_m[-1],mdn_trajectory[-1]+sigma_trajectory_p[-1]],[NN,NN],color=colour,alpha=alpha);
 
 
 

### 2015-07-22 doc/sw-system-referee-response.txt
Added note on RingFinder to last conclusion bullet #216

We thank the referee for their very helpful comments, all of which we
address below.  Their comments are shown unindented, while our
responses are shown indented.

 - - - - - - - - - - - - - - - - - - - -

This work merits publication after some minor revisions.

Following the order of the text, my comments (on both form and
content) are:

In the abstract, "expert-classified images which lack lenses" should
be replaced by something like "real images that lack lenses" or
"observed images that lack lenses", talking about "expert classified
images" when referring to non lenses seems a bit confusing.

    Done.

Page 9, 4 lines after equation (2), "Nx is the number of lenses the
volunteer has been shown" should be replaced by "Nx is the number of
training subjects of the relevant type the volunteer has been shown",
since it can refer either to lenses or non lenses.

    Done.

Page 9, I do not think it is necessary to create a specific
subsubsection 4.2.1 to present the examples, which can be presented in
the rest of the text of subsection 4.2.

    Done.

Page 10, maybe the title of subsection 4.5 : "Practicalities" should
be changed for a more specific title here.

    Done. We've gone with "Application to the CFHTLS Classifications".

Page 11, Figure 5, the figure is interesting but it should be better
highlighted with clearer color contrasts, for the histograms and for
the circles.

    TO DO! Edit SWAP to make red and blue points bigger, red and blue
    trajectories thicker and less alpha'd, red and blue histograms
    in the foregroun with alpha=1. Issued as #219

Page 12, Figure 6, the different linestyles should be replaced by
different colors to make the whole plots more readable, and to be able
to distinguish the 4 "stars" corresponding to a lens probability
threshold of 0.95 in each case. Still for this figure, in the caption,
"Lens probability varies along the curve" should be replaced by "Lens
probability threshold varies..."

     TO DO! Plot edits issued as #220.
     Caption: Done.

Page 12, in the caption of Figure 7, the authors should add a sentence
about the inset as in the caption of Figure 6 : "The inset shows a
magnified view of the bottom righthand corner of the plot".

    Done.

Page 12, subsection 5.1, paragraph 5, line 9, I would replace "If the
training set samples from the same systems as the test set" by "AS the
training set samples..."

    This was not a typo: we have clarified what we mean (using better
    grammar!) in the text as follows:

    "If the training set were to be sampled fairly from test set, the
    completeness of the training set would be equal to the completeness of
    the test set. (In practice this will likely only be approximately
    true, as simulated lenses [and the distributions of their properties]
    are used instead of real ones.)"

    We think this will make sense to the reader, as we discuss the
    efforts we made to make the training sims realistic elsewhere.

Page 15, last paragraph before Section 6, first sentence, there is a
repetition of "between".

    Fixed.

Page 16, subsection 6.1, I would write the first sentence of the 3rd
paragraph: "The false positives show similar behavior.." at the end of
the second paragraph, and begin the 3rd paragraph with "As well as
subjects being 'unlucky'...".

    Done.

Page 18, the last paragraph of subsection 6.2 quickly deals with the
subject of automated lens searches. I would have liked to read more
development on that subject, which I could find though in Space Warps
II. Nevertheless, I think the authors should at least add a sentence
or two about it in their conclusion, maybe by completing the last
indent of Section 7 concerning the missed lenses.

    We have added the following to the last conclusion bullet, to
    close this loop as the referee suggests:

    "Future searches will need to address of these issues. We expect
    it to be especially interesting to try crowd-sourcing the visual
    inspection of target systems which have had their candidate lens
    galaxy light automatically subtracted off (as, for example,
    RingFinder does), in a collaboration between humans and
    machines."

Page 18, I think the title of subsection 6.3 : "Increasing capacity"
should be changed to "Increasing crowd capacity" to avoid confusion.

    Done.

Page 18, subsection 6.3, 1st paragraph, line 7, there is a 'typo' :
"quantitively".

    Fixed.

The authors should add a discussion about the complexity of computing
of a selection function in the case of visual inspection compared to
the automated methods.

    TO DO.

### 2015-07-22 doc/sw-system.tex
Added note on RingFinder to last conclusion bullet #216

@@
 additional scatter, with some simulated lenses accumulating low probability
-simply due to classification noise.
+simply due to classification noise. Future searches will need to address
+of these issues. We expect it to be especially interesting to try
+crowd-sourcing the visual inspection of target systems which have
+had their candidate lens galaxy light automatically subtracted off (as, for example, \RF
+does), in a collaboration between humans and machines.
 

### 2015-07-22 doc/sw-system-referee-response.txt

@@
 
-    We have added the following to the last conclusion bullet, to
-    close this loop as the referee suggests:
-
-    "Future searches will need to address of these issues. We expect
-    it to be especially interesting to try crowd-sourcing the visual
-    inspection of target systems which have had their candidate lens
-    galaxy light automatically subtracted off (as, for example,
-    RingFinder does), in a collaboration between humans and
-    machines."
+    TO DO.
 

### 2015-07-22 doc/sw-system-referee-response.txt
Added selection function paragraph: #216 now all done bar the plots from @cpadavis

--- 2015-07-22 doc/sw-system-referee-response.txt
@@
     trajectories thicker and less alpha'd, red and blue histograms
-    in the foregroun with alpha=1. Issued as #219
+    in the foreground with alpha=1. Issued as #219
 
@@
 
-    TO DO.
+    We are happy to provide a new paragraph on this topic at the end
+    of Section 5.1 (Results: Sample Properties). In short, we believe
+    that computing a selection function based on the quantitative,
+    probabilistic classification labels produced by the Space Warps
+    system should be no more difficult or complex than doing so based
+    on the outputs of a machine classifier, which would correspond
+    exactly in character.

### 2015-07-22 doc/sw-system.tex
Added selection function paragraph: #216 now all done bar the plots from @cpadavis

@@
 result (see \PaperTwo).
+
+Finally, it is worth noting the implications of the results in this
+section for future studies of samples of lenses (and lens candidates)
+discovered through visual inspection at \SW. The ROC curve analysis we
+have carried out should be very familiar to those working in machine
+classification, and in fact is identical to that which would be
+performed on the classifications made by a new automated method.
+Supervised machine learning methods and the \SW system as described
+here both require a training set, and both return quantitative,
+probabilistic classifications (consisting of a label and some measure
+of confidence in that label) that can be used in further analysis. A
+good example of where such quantitification is important is in the
+derivation of the selection function for a given sample. While such a
+derivation is beyond the scope of this work, it is sufficient to note
+that from the point of view of an astronomer seeking to derive a
+selection function, {\it the labels produced by \SW and those produced
+by a machine learning method can be treated equivalently}: that is, we
+have succeeded in elevating visual inspection to a quantitative
+science. Indeed, the discussion of completeness given above is all in
+terms of recovery of a large set of simulated lenses, just as it would
+be in the case of an automated method---and in both cases, the
+limiting factor is the realism of the training set. In \PaperTwo we
+investigate this further by assessing the performance of the \SW
+system against the (small) set of real lens candidates known to lie in
+the field; for now, we note that the training set used in this work
+constitutes a valid sample of objects for any alternative machine
+learning lens detection method to be tested against. In future, we may
+well find it necessary to employ a larger training set, to enable the
+selection efficiency to be characterised as a function of multiple
+observables. This should not be a problem, since in the current work
+the small training set we used was classified around 20 times more
+than  was the test set: we could have defined a larger training set,
+and collected  many fewer classifications per training image.
 

### 2015-07-23 analysis/swap/collection.py
small changes to roc and collection etc

@@ -327,7 +327,7 @@ class Collection(object):
 
             bins = np.linspace(np.log10(swap.pmin),np.log10(swap.pmax),32,endpoint=True)
             bins = 10.0**bins
-            colors = ['blue','red','dimgray']
+            colors = ['dimgray','blue','red']
             labels = ['Test: Survey','Training: Sims','Training: Duds']
             thresholds = self.thresholds()
 
@@ -347,7 +347,7 @@ class Collection(object):
 
                 # Pylab histogram:
                 plt.hist(p, bins=bins, histtype='stepfilled', color=colors[j], alpha=1.0, label=labels[j])
-                plt.legend(prop={'size':10})
+                plt.legend(prop={'size':10}, framealpha=1.0)
 
         if t is not None:
             # Add timestamp in top righthand corner:

### 2015-07-23 analysis/swap/subject.py

@@ -344,12 +344,12 @@ class Subject(object):
             colour = 'blue'
             linewidth = 1.5
             alpha = 0.3
-            size = 30
+            size = 40
         elif self.kind == 'dud':
             colour = 'red'
             linewidth = 1.5
             alpha = 0.3
-            size = 30
+            size = 40
         elif self.kind == 'test':
             colour = 'black'
             linewidth = 1.0
@@ -365,7 +365,7 @@ class Subject(object):
             # Thicker, darker line:
             plt.plot(mdn_trajectory,N,color=colour,alpha=0.5,linewidth=2.0, linestyle="-")
             # Bigger point:
-            size = 40
+            size = 60
         else:
             # Thinner, fainter line:
             plt.plot(mdn_trajectory,N,color=colour,alpha=alpha,linewidth=linewidth, linestyle="-")
@@ -374,11 +374,11 @@ class Subject(object):
         if NN > swap.Ncmax: NN = swap.Ncmax
         if highlight:
             # Heavier symbol:
-            plt.scatter(mdn_trajectory[-1], NN, s=size, edgecolors=colour, facecolors=facecolour, alpha=0.8);
+            plt.scatter(mdn_trajectory[-1], NN, s=size, edgecolors=colour, facecolors=colour, alpha=1.0);
             plt.plot([mdn_trajectory[-1]-sigma_trajectory_m[-1],mdn_trajectory[-1]+sigma_trajectory_p[-1]],[NN,NN],color=colour,alpha=0.5);
         else:
             # Fainter symbol:
-            plt.scatter(mdn_trajectory[-1], NN, s=size, edgecolors=colour, facecolors=facecolour, alpha=alpha+0.4);
+            plt.scatter(mdn_trajectory[-1], NN, s=size, edgecolors=colour, facecolors=colour, alpha=1.0);
             plt.plot([mdn_trajectory[-1]-sigma_trajectory_m[-1],mdn_trajectory[-1]+sigma_trajectory_p[-1]],[NN,NN],color=colour,alpha=alpha);
 
 

### 2015-07-23 doc/sw-system.tex
Updated purity numbers and discussion as suggested by Anu, folded in Aprajita's comments on selection function text. Finished response with promise of latexdiff'ed PDF... #216

@@
 
-The purity depends on the proportion of sims to
-duds, and so the purity of the test set must be approximated by rescaling the
-training set to the expected proportion of lens systems to not-lens systems in
-the survey. First we compute the expected number of false positives by
-multiplying the FPR by the expected number of non-lenses in the survey. Then
-we multiply the TPR by the expected number of lenses in the survey, to get the
-expected number of true positives. The sum of the true positives and the false
-positives gives the expected sample size; dividing the expected number of true
-positives by this sample size gives the purity. Note that the completeness is
-invariant to this transformation.
-The \StageOne curves are truncated by the retirement of subjects in this phase,
-which sets the minimum size of this sample. We see from the solid blue curve
-that over 90\% completeness was reached, albeit in a sample with 30\%
-purity.
+The purity depends on the proportion of sims to duds, and so the
+purity of the test set must be approximated by rescaling the training
+set to the expected proportion of lens systems to not-lens systems in
+the survey. We expect there to be around 90 lenses in the CFHTLS
+already (a rate of 1 lens in every 5000 images or so); to a very good
+approximation  the number of non-lens images in the survey is just the
+number of images in  the survey (some 430,000). First we compute the
+expected number of false positives by multiplying the FPR by the
+expected number of non-lenses in the survey (430,000).  Then we
+multiply the TPR by the expected number of lenses in the survey (90),
+to get the expected number of true positives. The sum of the true
+positives and the false positives gives the expected sample size;
+dividing the expected number of true positives by this sample size
+gives the purity. Note that the completeness is invariant to this
+transformation. The \StageOne curves are truncated by the retirement
+of subjects in this phase, which sets the minimum size of this sample.
+We see from the solid blue curve that over 90\% completeness was
+able to be reached, albeit in samples with not more than 30\% purity.
+We set the detection threshold for \StageOne to be 0.95 (shown by the blue star
+in \Fref{fig:results:sample:CP}), leading to a sample with 94\% completeness
+and 15\% purity.
 
@@
 here both require a training set, and both return quantitative,
-probabilistic classifications (consisting of a label and some measure
+probabilistic classifications (consisting of a ``label'' and some measure
 of confidence in that label) that can be used in further analysis. A
@@
 limiting factor is the realism of the training set. In \PaperTwo we
-investigate this further by assessing the performance of the \SW
+investigate this limit further by assessing the performance of the \SW
 system against the (small) set of real lens candidates known to lie in
@@
 constitutes a valid sample of objects for any alternative machine
-learning lens detection method to be tested against. In future, we may
-well find it necessary to employ a larger training set, to enable the
+learning lens detection method to be tested against. In future, we
+could employ a larger training set, to enable the
 selection efficiency to be characterised as a function of multiple
-observables. This should not be a problem, since in the current work
-the small training set we used was classified around 20 times more
-than  was the test set: we could have defined a larger training set,
-and collected  many fewer classifications per training image.
+observables. This will be achievable, since
+the small training set we used in the current study
+was classified around 20 times more
+than  was the test set: we could therefore collect many fewer
+classifications per training image in a much larger training set.
 
@@
 \item The optimal true positive rate (completeness) and false positive rate in
-the training set were estimated to be around $91-93\%$ and $<1\%$
+the training set were estimated to be around $92-94\%$ and $<1\%$
 (in both classification stages).
-This FPR translates to a purity of approximately 30\%. We find an even
-higher purity at \StageTwo (perhaps as a result of the least visible candidates already
+This FPR translates to a purity of approximately $15-30$\%. We find that even
+higher purities were achievable at \StageTwo
+(perhaps as a result of the least visible candidates already
 being discarded): here, 100\% purity was reached at just under $90\%$

### 2015-07-23 doc/sw-system.tex
Added Matthias to acknowledgments

@@
 
-We thank Stuart Lynn, Kelly Borden, Laura Whyte, Brooke Simmons, David Hogg,
+We thank Matthias Tecza, Stuart Lynn, Kelly Borden, Laura Whyte, Brooke Simmons, David Hogg,
 Daniel Foreman-Mackey, Thomas Jennings, Layne  Wright, Cecile Faure, Jonathan

### 2015-07-23 doc/sw-cfhtls.tex
AV's and my final edits
closes #217

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% AV IS HERE!
 
@@
 classifications performed by expert volunteers (albeit at the cost of a
-higher false positive rate), indicating that the training and
+lower purity), indicating that the training and
 performance calibration of the citizen scientists is very important for
@@
 
-\section{Training sample: Simulated lenses}
+\section{Training sample}
 \label{sec:ts}
@@
 summary). In this section, we describe the framework used for generating the
-simulated lens sample and give details of the sample itself along with
-some of its known limitations.
+simulated lens sample, give details of the sample itself along with
+some of its known limitations and also describe the sample of duds and
+impostors.
 
@@
 
-\subsection{Methodology}
+\subsection{Methodology to simulate lenses}
 \label{sec:simmethod}
@@
 
-We also add external shear at the centre of the lensing galaxy
+We also add external shear at the centre of the potential lensing galaxy
 drawn randomly from a set range (see \Tref{tab:thresh}. The shear is
@@
 
-Once all the parameters are determined for the lens and source models, we once
-again use \gravlens to generate simulated lensed images.  After accounting for the shot
-noise in the lensed images and convolving them with the seeing in each of
-the filters, the simulated image is added to the real \cfhtls~image centred
-on the lensing galaxy. Note that we ensure that the lensed galaxies and
-lensed quasars do not have the same lensing galaxy in the foreground. Similarly,
-the lensing galaxies from the galaxy-scale lenses are distinct from the central
-galaxies of group-scale lenses which are described in the following section.
+Once all the parameters are determined for the lens and source models,
+we once again use \gravlens to generate simulated lensed images.  After
+accounting for the shot noise in the lensed images and convolving them
+with the seeing in each of the filters, the simulated image is added to
+the real \cfhtls~image centred on the galaxy chosen to act as a
+lens. Note that we ensure that the lensed galaxies and lensed quasars
+are not superposed on the same ``lensing'' galaxy.  Similarly,
+these ``lensing'' galaxies at the galaxy scales are ensured to be
+distinct from those chosen for the group scales. The framework for the
+group-scale is described below.
 
@@
 \caption{ \label{fig:remudist}
-Einstein radius distribution for all types of lenses. The solid (blue)
+Einstein radius and total magnification distributions for all types of lenses. The solid (blue)
 curves show the theoretical prediction assuming an SIS model at galaxy-scales
@@
 \caption{ \label{fig:lensprop}
-Distributions of properties of the lensing galaxies of the simulated
+Distributions of properties of the ``lensing'' galaxies of the simulated
 sample compared to the known lens sample SARCS.
@@
 Next, we consider the redshift, magnitude and ellipticity distributions
-of the lensing galaxies as shown in \Fref{fig:lensprop}. For reference,
+of the ``lensing'' galaxies from the simulated sample as shown in \Fref{fig:lensprop}. For reference,
 we also show SARCS lenses from \citet{More2012}, with arbitrary
@@
 We produce catalogs with lens and source properties for each of the
-three types of lenses.  The catalogs typically have lens position,
+three types of simulated lenses.  The catalogs typically have lens position,
 redshift, magnitudes, Einstein radius, ellipticity (whenever available)
@@
 detected in the survey. For galaxy-scale lenses, the fainter or higher redshift
-lensing galaxies tend to have poor photometric redshift
+galaxies, chosen to act as lenses, tend to have poor photometric redshift
 measurements. Consequently these galaxies were occasionally assigned the wrong
@@
 
-\section{Training sample: Duds and Impostors}
+\subsection{Duds and Impostors}
 \label{sec:dfp}
@@
 Distribution of different types of candidates as a function of the
-posterior probability $P$. The types of the candidates are the false
+posterior probability $P$, obtained at the end of \StageTwo. The types of the candidates are the false
 positives (FPs), the new candidates and the known candidates. The new
@@
 probabilities to accept or reject a subject if it contains a lens or does
-not contain one can be chosen in SWAP. Those images which cross
+not contain one can be chosen in SWAP. In \StageOne, those images which cross
 these threshold values are ``retired'', and are not subsequently shown to the
@@
 threshold at the end of \StageOne were served again at \StageTwo for careful
-re-inspection. Each subject, after \StageTwo, has a posterior
+re-inspection. The goal of \StageOne inspection was to maximise completeness
+and that of \StageTwo was to maximise purity. Each subject, after \StageTwo, has a final posterior
 probability $P$. In the ideal case, all images containing lenses will have high $P$
@@
 To achieve this, we selected a total of 665 subjects with $P>0.3$
-which were then visually inspected by three of us (as ``lens experts'',
+at \StageTwo which were then visually inspected by three of us (as ``lens experts'',
  AM, AV, PJM).  Each images was assigned a grade on a scale of 0 to 3,
@@
 first in the descending order of their grades, and within each grade, in
-ascending order
-of RA. As the first lens search was a blind search with no
+ascending order of RA. As the first lens search was a blind search with no
 pre-selection of candidates from any algorithm, we find various types of
@@
 algorithm, whereas the ring finding algorithm may have missed this because of
-the atypical colour and structure of the galaxy. Detection of red arcs, for
+the atypical colour and structure of the lensing galaxy. Detection of red arcs, for
 example, as seen in the SW39 candidate, shows how the volunteers
@@
 We find that most of the confirmed lenses and candidates that are missed
-by \sw are systems from the \rf sample, with fainter arcs and smaller $R_{\rm E}$.
-The main reason why \rf found such candidates
-is because it involves subtracting the light from the lens galaxy,
-making it easier to detect the lensed images during both the automated
-object-finding, and the visual inspection and classification
-phases. This approach naturally improves the detection
-efficiency at smaller $R_{\rm E}$ and for fainter systems. The \sw
-volunteers were not shown any galaxy$-$subtracted images. Showing
-galaxy$-$subtracted images might be a better strategy to adopt for future
-lens searches at galaxy-scales with \sw. In
-\Sref{sec:fn} below, we further explore and discuss why some of the confirmed
-lenses were missed by \sw.
+by \sw are systems from the \rf sample, with fainter arcs and smaller
+$R_{\rm E}$.  The main reason why \rf found such candidates is because
+it involves subtracting the light from the lens galaxy, making it easier
+to detect the lensed images during both the automated object-finding,
+and the visual inspection and classification phases. This approach
+naturally improves the detection efficiency at smaller $R_{\rm E}$ and
+for fainter systems. The \sw volunteers were not shown any
+galaxy$-$subtracted images. Showing galaxy$-$subtracted images might be
+a better strategy to adopt for future lens searches at galaxy-scales
+with \sw. However, we note that accurate modelling and subtraction
+of the galaxy light profile in different bands is challenging and better
+techniques are being actively developed to enhance detections of lenses
+at small image separations. In \Sref{sec:fn} below, we further explore
+and discuss why some of the confirmed lenses were missed by \sw.
 
@@
 
-Indeed, we have found 59 new medium-high grade
-lens candidates that were not known
-before. In \Fref{fig:isd}, we show the image separation distribution for
-the known \rf and \af sample (green), for the \sw identified (known and
-new) lens sample (blue) only and the combined \cfhtls sample of \rf, \af and
-the new \sw lens sample (magenta). It is interesting to note that both
-the \rf$+$\af and \sw samples have very similar profiles and thus, the profile of the
-combined sample has not changed significantly. This implies that previous
-constraints on the image separation distribution are robust and the \af
-selected sample does not suffer from significant incompleteness for
-medium to large $R_{\rm E}$. This is the regime that probes density
-profiles of galaxy groups to clusters.
+Indeed, we have found 59 new medium-high grade lens candidates that were
+not known before. In \Fref{fig:isd}, we show the image separation
+distribution using all the known and new lens candidates. The different
+data points are  the known \rf and \af sample (green), the \sw
+identified (known and new) lens sample (blue) only and the combined
+\cfhtls sample of \rf, \af and the new \sw lens sample (magenta). It is
+interesting to note that both the \rf$+$\af and \sw samples have very
+similar profiles and thus, the profile of the combined sample has not
+changed significantly. This implies that previous constraints on the
+image separation distribution are robust and the \af selected sample
+does not suffer from significant incompleteness for medium to large
+$R_{\rm E}$. This is the regime that probes density profiles of galaxy
+groups to clusters.
 
@@
 corresponding to three density profiles, namely, isothermal sphere (IS),
-NFW and a ``Total'' profile which has NFW and Hernquist
-profiles combined with an adiabatically contracting model for the dark
-matter component \citep{Gnedin2004}. These curves are taken from
+NFW and a ``Total'' profile which has NFW and Hernquist profiles
+combined with an adiabatically contracting model for the dark matter
+component \citep{Gnedin2004}. These curves are taken from
 \citet{More2012}, which gives details of the calculation of these
@@
 previous prediction that the mass density profiles of galaxy groups is
-indeed consistent with the ``Total'' profile.
+indeed consistent with the ``Total'' profile.  At smaller image
+separations ($\lesssim 2$~arcsec), the ``Total'' profile converges to
+isothermal like case and assuming these predictions are reliable, we
+find that the lens samples have very low completeness. This is not too
+surprising compared to the 40\% completeness expected for the \rf sample
+\citep{Gavazzi2014}.
 
@@
 
-Since in this project \sw enabled a visual search based on simple colour
-composite images drawn directly from the survey,
-it was difficult to detect many lens
-candidates with a small $R_{\rm E}$ in the presence of a bright lensing
-galaxy. In contrast, the \rf sample was
-generated by working with lensing galaxy$-$subtracted images and this
-led to increased detections of small image separation candidates. The
-\sw interface did not show any galaxy subtracted images and hence,
-this results in a quantitative difference between the \sw and the \rf
-sample as a function of $R_{\rm E}$.
-
-The \af is capable of finding some small image
-separation lenses, but a lower limit at $R_{\rm E}=2\arcsec$ was imposed
-by the \af team to simplify the selection function of their sample.
-Thus, we can compare the \sw and \af samples at about $R_{\rm
-E}>2\arcsec$. There is a good overlap between the two samples given that
-most of these are candidates and could turn out not to be lenses. We again
-caution the readers that the uncertainties on the measurements are not
-quantified and may change the results to some extent.
+%Since in this project \sw enabled a visual search based on simple colour
+%composite images drawn directly from the survey,
+%it was difficult to detect many lens
+%candidates with a small $R_{\rm E}$ in the presence of a bright lensing
+%galaxy. In contrast, the \rf sample was
+%generated by working with lensing galaxy$-$subtracted images and this
+%led to increased detections of small image separation candidates. The
+%\sw interface did not show any galaxy subtracted images and hence,
+%this results in a quantitative difference between the \sw and the \rf
+%sample as a function of $R_{\rm E}$.
+%
+%The \af is capable of finding some small image
+%separation lenses, but a lower limit at $R_{\rm E}=2\arcsec$ was imposed
+%by the \af team to simplify the selection function of their sample.
+%Thus, we can compare the \sw and \af samples at about $R_{\rm
+%E}>2\arcsec$. There is a good overlap between the two samples given that
+%most of these are candidates and could turn out not to be lenses. We again
+%caution the readers that the uncertainties on the measurements are not
+%quantified and may change the results to some extent.
+%
 
@@
 
-Lastly, in \Fref{fig:stackremg}, we show the relative distribution of
+In \Fref{fig:stackremg}, we show the relative distribution of
 number of candidates from each sample as a function of the Einstein
@@
 
-\subsubsection{Blind lens search}
+\subsubsection{Lens positions within the image cutouts}
 
@@
 The bottom panels of \Fref{fig:detmis}, show the trajectories of missed
-lenses for visually easier and more difficult examples in red and green,
-respectively.  In spite of some mild qualitative differences, both set
-of trajectories have very similar behaviour. The trajectories in panel
-(e) are typical of this sample in terms of Nclass and the dominance of
-small negative kicks. Panel (f) represents a small fraction of this
-sample where the kicks are only small and negative. The panel (g) shows
-how some lenses receive a bunch of large positive kicks which are led to
-rejection by still mostly small negative kicks. Finally, panel (h) shows
-those cases of lenses which received almost sufficient number of large
-positive kicks to be detected but ended up being rejected.
+lenses for the cases which are visually easier (red) and more
+difficult (green) to identify.  In spite of some mild
+qualitative differences, both set of trajectories have very similar
+behaviour. The trajectories in panel (e) are typical of this sample in
+terms of Nclass and the dominance of small negative kicks. Panel (f)
+represents a small fraction of this sample where the kicks are only
+small and negative. The panel (g) shows how some lenses receive a bunch
+of large positive kicks which are led to rejection by still mostly small
+negative kicks. Finally, panel (h) shows those cases of lenses which
+received almost sufficient number of large positive kicks to be detected
+but ended up being rejected.
 
@@
 
-Some of the key inferences are as follows.  i) The ratio of  large
-positive kicks to small positive kicks for the detected sample is higher
-than in the missed sample, suggesting that the fraction of high power
-volunteers is large for the detected sample.  ii) The number of
+Some of the key inferences are as follows. i) The ratio of positive
+kicks to negative kicks for the detected sample is higher than in the
+missed sample, suggesting that the fraction of volunteers making
+positive kicks is higher for the detected sample. ii) The number of
 classifications received by the missed sample is dominated by small
@@
 
-Changing the rejection and acceptance thresholds will likely increase
-the rate of false positives along with improved completeness.  This will
+Changing the rejection and acceptance thresholds will likely 
+decrease the purity along with improved completeness. This will
 need to be further quantified before detailed recommendations can be
@@
 \caption{ \label{fig:detmis}
-Left: Examples of \StageOne trajectories of some known lenses.
-Upper panels show detected
-lenses, lower panels show missed lenses (false negatives). Right:
-Histogram of classification power received by known lenses.
-Among the sample of missed
-lenses, most classifications are from the low power volunteers
-identifying these images incorrectly (i.e. $-\Delta$~log(P)) which
-overshadows the small number of correct identifications (i.e.
-$\Delta$~log(P)) coming from both the less and the high power volunteers
-combined. For the detected lens sample, most classifications are correct
-identifications coming from both low and high power volunteers.
-}
+Left: Examples of \StageOne trajectories of some known lenses.  Upper
+panels show detected lenses, lower panels show missed lenses (false
+negatives). The green trajectories for the detected sample are
+counterparts of the red and green trajectories of the missed sample
+except that the kicks are positive for the detected sample. The red
+trajectories of the detected sample demonstrate that sufficient number
+of positive large kicks can lead to the detection of the lenses. Within the
+missed sample, the red and green correspond to visually easier and more
+difficult to identify systems, respectively. Right: Histogram of classification
+power received by known lenses.  Among the sample of missed lenses, most
+classifications are from the low power volunteers identifying these
+images incorrectly (i.e.  $-\Delta$~log(P)) which overshadows the small
+number of correct identifications (i.e.  $\Delta$~log(P)) coming from
+both the less and the high power volunteers combined. For the detected
+lens sample, most classifications are correct identifications coming
+from both low and high power volunteers. }
 \end{center}
@@
 have found lens candidates which the algorithms failed to discover.
-Upcoming and planned wide-field imaging surveys such as the DES, HSC and
-LSST will produce formidable amounts of data.  Blind lens searches as
+Upcoming and planned wide-field imaging surveys such as the DES, HSC,
+Euclid and LSST will produce formidable amounts of data. Blind lens searches as
 described here will be impractical with these very large surveys. However,
@@
 \begin{longtable}{llrrrrrrlrr}
-%\begin{sideways}
-%\begin{tabular}{llrrrrrrlrr}
 \caption{ \label{tab:swcands}
@@
 \end{center}
-%\end{tabular}
-%\end{sideways}
 

### 2016-04-26 doc/sw-cfhtls-referee-response.txt

We thank the referee for providing useful comments on the manuscript. We have implemented all of the suggestions and the textual changes are shown in bold in the revised version of the manuscript. Below are our answers to referee's comments.

-------------
In the abstract, I would replace "albeit at the cost of a higher false positive rates" by "albeit at the cost of a lower purity", the purity is a quantity well known by the astronomers and I think it makes things clearer here (especially for an abstract).

Ans: Done

The short Section 4 should become the 4th subsection of Section 3 with slight changes in the titles, like :
          3. Training Sample
                  3.1.  Methodology to simulate lenses
                  3.2. Simulated lens sample and catalog description [no change]
                  3.3. Limitation of the simulated lens sample [no change]
                  3.4. Duds and impostors
and by adding a word about duds at the end of the introduction of Section 3.

Ans: Done. This means that Sections 5,6,7 and 8 now become 4,5,6 and 7, respectively.

There is sometimes a confusion between real lensing galaxies and real galaxies chosen to be lensing galaxies in the training set of simulations. For example, in the last paragraph before subsubsection 3.1.2., in the sentence "the simulated image is added to the real CFHTLS image centered on the lensing galaxy", the authors should write 'lensing galaxy' between quotes or rephrase it : "..centered on the galaxy chosen to act as a lens". The same remarks applies to other occurrences in the same paragraph (and maybe others in the rest of the text).

Ans: Done.

The caption of Figure 2 should be completed : "Einsten radius and total magnification distributions..."

Ans: Done.

Last paragraph before subsection 3.3, first sentence, I would precise : "We produce catalogs with lens and source properties for each of the three types of SIMULATED lenses."

Ans: Done.

There is sometimes a confusion between the (evolving) posterior probability after each classification and the final posterior probability after stage 2, and both are noted P (even if I understand that somehow this is the same quantity). Maybe the authors could note the final posterior Pf and/or be more specific in the text. For example, in the caption of Figure 4, or, in subsection 5, paragraph 3, line 5 : "Each subject, after Stage 2, has a FINAL posterior probability P".

Ans: Done.

In Figure 4, there should be a better color contrast between the new candidates and the known candidates to make the results more readable.

Ans:  The low color contrast was chosen on purpose to suggest that these are all Space Warps identified candidates and the slight difference is to point out that one of them is a new sample and the other is a known one. The figure is modified to increase the color contrast but both are still shades of blue.

Page 9, subsection 5, 4 lines before the end of paragraph 2, I would precise "In stage 1, ..." before "...those images which cross these threshold values are 'retired'"

Ans: Done.

Maybe the authors should re-explain (Paper I) quickly at this stage of the article (3rd paragraph of subsection 5) that the stage 1 favors completeness while the stage 2 favors purity of the final sample.

Ans: Done.

Subsection 6.2, paragraph 3, penultimate sentence, I would precise : "...the atypical color and structure of the LENS galaxy"

Ans: Done.

At the end of subsection 6.4., as well as in the conclusion, the authors quickly deal with the subject of the deflector subtraction. I would like them to make clearer in their article that this is not a trivial issue in the detection of galaxy-scale lenses, and that solutions are being actively sought for a better subtraction of this foreground light.

Ans: A sentence is added, as per the suggestion, towards the end of subsection 5.4 (which was 6.4 earlier). The conclusion part is left unchanged as the galaxy subtraction is mentioned only for completeness, to merely point out the main difference between Space Warps and Ringfinder.

There is sometimes a confusion between the various subsamples considered in the article. For example, in Subsection 6.5, paragraph 2, lines 4-5, it is hard to distinguish in the text if the "known" samples considered refer to confirmed lenses or the whole candidates.

Ans: Done.

In subsection 6.5, describing Figure 7, could the authors say one word about the few points at lower image separation which are not consistent with the "total" profile?

Ans: Done.

There is some overlap between Section 6 and Section 7, even if the developments are interesting. But maybe Section 7 should be somehow shortened for clarity?

Ans: We have removed the 2nd and 3rd paragraph from the Discussion, Sect. 6.1 (which was 7.1 earlier) to avoid repetition

The title of subsubsection 7.3.2. "Blind lens search" seems a bit too general and maybe not relevant. It should be replaced by something more specific like "Lens positions in the image cutouts".

Ans: Done.

In Figure 11 and its description in the text (subsubsection 7.3.3, paragraphs 4 and 5), the distinction between the red and green curves is unclear, especially for what concerns the detected lenses. There should be a word about it in the caption of the figure too.

Ans: The text in para 4 is modified to explain better the difference for the missed sample. The beginning and the end of para 5 state the difference between the green and the red for the detected sample. The caption of the figure is modified too.

Subsubsection 7.3.3, paragraph 7, I think there is a mistake in "i) The ratio of large positive kicks to small positive kicks for the detected sample is higher than in the missed sample"... I think the authors meant "negative" instead of the second "positive"?!

Ans: Text is corrected.

Last paragraph before Section 8, I would again replace "increase the rate of false positives" by "decrease the purity".

Ans: Done.

The authors could mention EUCLID with the other future surveys in their conclusion.

Ans: Done.

### 2016-04-26 doc/sw-system-referee-response.txt

@@
 responses are shown indented.
+
+In addition, we clarified the purity calculation with the assumptions
+we made about the expected number of lenses present in the survey, and
+also made it clear that the purity of the Stage 1 sample (15%) was
+chosen to be lower than the maximum purity obtainable. The abstract
+and conclusions remain unchanged, as these refer to the final purity,
+after Stage 2 refinement. We include a PDF version of the paper with
+all changes highlighted, for the referee's convenience.
 
@@
 
-    TO DO! Edit SWAP to make red and blue points bigger, red and blue
-    trajectories thicker and less alpha'd, red and blue histograms
-    in the foreground with alpha=1. Issued as #219
+    Done.
 
@@
 
-     TO DO! Plot edits issued as #220.
-     Caption: Done.
+     Done.
 

### 2016-04-26 doc/sw-cfhtls.tex

@@
 The bottom panels of \Fref{fig:detmis}, show the trajectories of missed
-lenses for the cases which are visually easier (red) and more
-difficult (green) to identify.  In spite of some mild
+lenses for the cases which are visually easier (light green) and more
+difficult (dark green) to identify.  In spite of some mild
 qualitative differences, both set of trajectories have very similar
@@
 negatives). The green trajectories for the detected sample are
-counterparts of the red and green trajectories of the missed sample
+counterparts of the light and dark green trajectories of the missed sample
 except that the kicks are positive for the detected sample. The red
@@
 of positive large kicks can lead to the detection of the lenses. Within the
-missed sample, the red and green correspond to visually easier and more
+missed sample, the light and dark green correspond to visually easier and more
 difficult to identify systems, respectively. Right: Histogram of classification

### 2016-04-26 doc/sw-system.tex

--- 2015-07-23 doc/sw-system.tex
@@
 kinds of subject. Bottom panel: histograms of all the subject probabilities
-computed to date, sub-divided by subject kind.}
+computed to date, sub-divided by subject kind. The blue bar (of correctly-detected
+sims) hides a grey bar of around 3000 new lens candidates, which are the
+subject of \PaperTwo.}
 \label{fig:swap:subject-trajectories}
@@
 \StageTwo results (dot-dashed orange curve).
-Lens probability threshold varies along the curves: the stars indicate the point where
-the value of this quantity is 0.95.}
+Lens probability threshold varies along the curves: the symbols
+indicate the points where
+the value of this quantity is 0.95. In the lefthand panel, the circle
+point is masked by the square point.}
 \label{fig:results:sample:roc}
@@
 The probability threshold that was used for retirement during the \StageOne online analysis
-was 0.95; this point is marked with a star on each curve.
+was 0.95; this point is marked with a symbol on each curve.
 This turned out to be close to optimal (although a better approach would be to
@@
 
-We thank Stuart Lynn, Kelly Borden, Laura Whyte, Brooke Simmons, David Hogg,
+We thank Matthias Tecza, Stuart Lynn, Kelly Borden, Laura Whyte, Brooke Simmons, David Hogg,
 Daniel Foreman-Mackey, Thomas Jennings, Layne Wright, Cecile Faure, Jonathan
-Coles, Stuart Lowe and Jean-Paul Kneib for many useful conversations about
-citizen science and gravitational lens detection, and to the Dark Energy Survey
+Coles, Stuart Lowe, Alexander Fritz and Jean-Paul Kneib for many useful conversations about
+citizen science and gravitational lens detection, and for helping guide the
+discussion at \SW \Talk,
+and to the Dark Energy Survey
 and Pan-STARRS strong lensing science teams for their suggestions and
-encouragement.
+encouragement. We are grateful to the anonymous referee, whose comments
+and suggestions helped improve the paper significantly.
 

### 2016-05-23 doc/sw-publication-policy-kids.tex
KIDS Guidelines

--- 2015-04-21 doc/sw-publication-policy-des.tex
@@
 
-\title{Guidelines and Policy for the Dark Energy Survey Strong Lensing Science Team using \SW}
+\title{Guidelines and Policy for the KIDS Strong Lensing Science Team using \SW}
 \author{Aprajita Verma, Phil Marshall \& Anupreeta More}
-\date{March 25, 2015}
+\date{May 23, 2016}
 \maketitle
@@
 \begin{abstract} 
-\noindent \SW was conceived as a strong lens
-discovery {\it service} that harnesses the power of citizen scientists.
-The DES strong lensing group (hereafter DES survey science team or DES SST) can make use of \SW within the logistical constraints.
-In this document we discuss how the DES SST can become involved with \SW and the relationship
-between the DES SST and the \SW collaboration. 
-This document includes guidelines for proposing projects, data provision, data policy and for publications of \SW-enabled discoveries.
+\noindent \SW was conceived as a strong lens discovery {\it service}
+that harnesses the power of citizen scientists. The KIDS strong
+lensing group (hereafter KIDS survey science team or KIDS SST) can
+make use of \SW within the logistical constraints. In this document,
+we discuss how the KIDS SST might become involved with \SW and the
+relationship between the KIDS SST and the \SW collaboration.  This
+document includes guidelines for proposing projects, data provision,
+data policy and for publications of \SW-enabled discoveries.
 \end{abstract}
@@
 
-The \SW website is designed to motivate and  enable tens of thousands of
-people to perform the scientific tasks of strong gravitational lens
-identification.
-\SW comprises a primary `classification' interface (\texttt{http://spacewarps.org}) that allows citizen scientists to inspect images and mark those that contain potential gravitational lenses.
-A mandatory part of this inspection is the classification of simulated lenses (appropriate for the survey being conducted).
-The classification of simulated lenses acts as an interactive training activity that also allows us to establish the citizens' likelihood of identifying potential lenses and blank fields.
-This is fed into the \SW Analysis Pipeline (SWAPR) that analyses the classifications made per image (or subject in Zooniverse terms) giving a probability of whether an image contains a lens candidate or not.
+The \SW website is designed to motivate and enable tens of thousands
+of people to perform the scientific tasks of strong gravitational lens
+identification.  \SW comprises a primary `classification' interface
+(\texttt{http://spacewarps.org}) that allows citizen scientists to
+inspect images and mark those that contain potential gravitational
+lenses. A mandatory part of this inspection is the classification of
+simulated lenses (appropriate for the survey being conducted). The
+classification of simulated lenses acts as an interactive training
+activity that also allows us to establish the citizens' likelihood of
+identifying potential lenses and blank fields. This is fed into the
+\SW Analysis Pipeline (SWAPR) that analyses the classifications made
+per image (or subject in Zooniverse terms) giving a probability of
+whether an image contains a lens candidate or not.
 
-A key part of the \SW project is the ability for all members of the \SW collaboration (see Section \ref{sec:members}) to communicate with each other and discuss interesting candidates through \Talk\footnote{\Talk (found at \texttt{http://talk.spacewarps.org}) is a forum for \SW collaborators to discuss individual sources and the \SW project in general.
-Bugs can also be reported.
-This is the direct portal for communication with the \SW community.}.
+A key part of the \SW project is the ability for all members of the
+\SW collaboration (see Section \ref{sec:members}) to communicate with
+each other and discuss interesting candidates through
+\Talk\footnote{\Talk (found at \texttt{http://talk.spacewarps.org}) is
+  a forum for \SW collaborators to discuss individual sources and the
+  \SW project in general. Bugs can also be reported. This is the
+  direct portal for communication with the \SW community.}.
 
-In order to use the \SW interface, the DES Survey Science Team \textbf{must define and propose a project to the \SW PIs} who will discuss whether the project is suitable with the SST.
-The \SW PIs will then liaise further with the SST to implement the project in the \SW interface.
-Details are given in Section \ref{sec:project}.
+In order to use the \SW interface, the KIDS Survey Science Team
+\textbf{must define and propose a project to the \SW PIs} who will
+discuss whether the project is suitable with the KIDS SST. The \SW PIs will
+then liaise further with the SST to implement the project in the \SW
+interface. Details are given in Section \ref{sec:project}.
 
-\vspace{4mm}
-The PIs of the \SW project are the authors of this document, P.\,Marshall, 
-A.\,More and A.\,Verma, please do not hesitate to contact us if you require any further information or have any questions.
-The PIs may be collectively contacted via the email address \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com}
+\vspace{4mm} The PIs of the \SW project are the authors of this
+document, P.\,Marshall, A.\,More and A.\,Verma, please do not hesitate
+to contact us if you require any further information or have any
+questions. The PIs may be collectively contacted via the email address
+\href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com}
 
@@
 
-In this document, we will refer to the entirety of the DES strong lensing science group and the STRIDES team as the DES Survey Science Team (DES SST) to encompass all of the DES strong lensing community.
+In this document, we will refer to the entirety of the KIDS strong
+lensing science group as the KIDS Survey Science Team (KIDS SST) to
+encompass all of the KIDS strong lensing community.
 
-We now discuss the relationship between the \SW collaboration and the DES SST, who wish to use the \SW interface to investigate their data.
-The DES SSTs will liaise with the \SW science and development teams to ingest their survey data into the \SW interface.
-There may be some overlap between current \SW members and SSTs.
-In the case of DES, \SW PI Anupreeta More is a member of both the \SW collaboration and the DES Strong Lensing Science Group.
+We now discuss the relationship between the \SW collaboration and the
+KIDS SST, who wish to use the \SW interface to investigate their
+data. The KIDS SSTs will liaise with the \SW science and development
+teams to ingest their survey data into the \SW interface. There may be
+some overlap between current \SW members and SSTs.
 
-When we refer to the \SW collaboration, it comprises the \SW science team, \SW development team, and all the volunteers who have 
-logged in\footnote{with a Zooniverse ID.
-It is possible to classify anonymously, and we count those classification but as we don't know who they are, we are unable to collaborate with them directly.} and contributed classifications to the project.
+In the case of KIDS, \SW PI Anupreeta More is a member of both the \SW
+collaboration and the KIDS Strong Lensing Science Group.
 
-If required, an expanded definition of the \SW membership is given in the document ``\SW Publication Policy: CFHT-LS''\footnote{available from \texttt{\url{https://github.com/drphilmarshall/SpaceWarps/blob/master/doc/sw-publication-policy-cfhtls.pdf}}}, however this will not be relevant for \SW-DES publications, see Section \ref{sec:papers} for details.
+When we refer to the \SW collaboration, it comprises the \SW science
+team, \SW development team, and all the volunteers who have logged
+in\footnote{with a Zooniverse ID. It is possible to classify
+  anonymously, and we count those classification but as we don't know
+  who they are, we are unable to collaborate with them directly.} and
+contributed classifications to the project.
+
+If required, an expanded definition of the \SW membership is given in
+the document ``\SW Publication Policy: CFHT-LS''\footnote{available
+  from
+  \texttt{\url{https://github.com/drphilmarshall/SpaceWarps/blob/master/doc/sw-publication-policy-cfhtls.pdf}}},
+however this will not be relevant for \SW-KIDS publications, see
+Section \ref{sec:papers} for details.
 
@@
 
-The DES SST is expected to propose a project to the \SW collaboration that can be best or only be done using the power of citizen scientists.
-Typically, this involves visual inspection tasks that are too time consuming for the SST themselves to execute.
-As such, any science programme conducted through \SW should be complementary, not in competition, to the lens finding activities being carried out by the SST.
+The KIDS SST is expected to propose a project to the \SW collaboration
+that can be best or only be done using the power of citizen
+scientists. Typically, this involves visual inspection tasks that are
+too time consuming for the SST themselves to execute. As such, any
+science programme conducted through \SW should be complementary, not
+in competition, to the lens finding activities being carried out by
+the SST.
 
-For example, in the first \SW project, the collaboration conducted a lens finding search with \SW over the entire CFHT-LS survey area.
-The goal was to increase the completeness of strong lenses in the survey areas.
-Both RingFinder and ArcFinder algorithms had been used to discover lenses of different types.
-\SW complemented these searches with the potential to find strong lenses missed by these algorithms.
-The method, proposed by Anupreeta More (who served as the SST for this project), was to inspect the entire survey area by getting citizens to view $\sim$430,000 tiles of the survey area.
-This was a \textit{blind} search.
-Such a search could not be conducted by a normal sized SST.
+For example, in the first \SW project, the collaboration conducted a
+lens finding search with \SW over the entire CFHT-LS survey area. The
+goal was to increase the completeness of strong lenses in the survey
+areas. Both RingFinder and ArcFinder algorithms had been used to
+discover lenses of different types. \SW complemented these searches
+with the potential to find strong lenses missed by these
+algorithms. The method, proposed by Anupreeta More (who served as the
+SST for this project), was to inspect the entire survey area by
+getting citizens to view $\sim$430,000 tiles of the survey area. This
+was a \textit{blind} search. Such a search could not be conducted by a
+normal sized SST.
 
-\textit{Targeted} searches are also possible, as we performed in the second \SW project on the VICS82 survey area.
-Here we inspected $\sim$40,000 images from the VICS82 survey centred on likely strong lens targets, e.g.
-LRGs, groups, clusters, quasars.
-Again, this was more images than the VICS82 SST could manage to inspect alone.
+\textit{Targeted} searches are also possible, as we performed in the
+second \SW project on the VICS82 survey area. Here we inspected
+$\sim$40,000 images from the VICS82 survey centred on likely strong
+lens targets, e.g. LRGs, groups, clusters, quasars.  Again, this was
+more images than the VICS82 SST could manage to inspect alone.
 
-Another approach is to use the \SW service to inspect the normally large candidate lists generated by automated algorithms or searches, which are typically dominated by false positives.
+Another approach is to use the \SW service to inspect the normally
+large candidate lists generated by automated algorithms or searches,
+which are typically dominated by false positives.
 
-\subsection{DES specific thoughts}
-In the case of DES, with its long data release plan and large strong lens group, we request the SST to consider the following:
+\subsection{KIDS specific thoughts}
+
 \begin{enumerate}
 \item The \SW facility should be used for science projects that cannot be completed by the Strong Lens Group itself. 
-\item Any \SW search should be complementary, not in competition, to the lens finding being conducted by the DES SST.
+\item Any \SW search should be complementary, not in competition, to the lens finding being conducted by the KIDS SST.
 \item While \SW uses citizen science, its primary goal is \textbf{not outreach}, it is harnessing citizen power for visual classifications (and eventually modelling) to perform science.
@@
 This is the reason the suitability of the project for citizen scientists should be carefully considered.
-The \SW PIs will be able to discuss any planned \SW-DES projects with the DES SST.
-It is important to bear this in mind for long-term surveys like DES, if needed the crowd needs to be engaged and feel like they are contributing while the entire \SW-DES project runs.
-\item The success of \SW-DES will rely on input from the DES SST working with the \SW collaboration, dedicated effort is required for this and the DES SST should identify team members who can commit time to the \SW-DES tasks for this before embarking on a project.
-The \SW PIs will help to establish the main efforts required, these will depend on the actual project put forward by the DES SST (e.g.\ image preparation, simulations, interacting with volunteers on \Talk).
+The \SW PIs will be able to discuss any planned \SW-KIDS projects with the KIDS SST.
+The crowd needs to be engaged and feel like they are contributing while the entire \SW-KIDS project runs.
+\item The success of \SW-KIDS will rely on input from the KIDS SST working with the \SW collaboration, dedicated effort is required for this and the KIDS SST should identify team members who can commit time to the \SW-KIDS tasks for this before embarking on a project.
+The \SW PIs will help to establish the main efforts required, these will depend on the actual project put forward by the KIDS SST (e.g.\ image preparation, simulations, interacting with volunteers on \Talk).
 \end{enumerate}
 
-\textbf{As such, \SW should be considered to be an integral part of the DES SST lens finding strategy, rather than an alternative method.}
+\textbf{As such, \SW should be considered to be an integral/complementary part of the KIDS SST lens finding strategy, rather than an alternative method.}
 
-The scientific project, process and outcome is the domain of the SST.
-The \SW collaboration enables this work by making it a live project on the website.
-We do not, per se, expect the \SW collaboration lead the resultant papers, we just request some of us are included on discovery papers in return for our help, please see Section \ref{sec:papers} for more details on the publication policy.
+The scientific project, process and outcome is the domain of the
+SST. The \SW collaboration enables this work by making it a live
+project on the website. We do not, per se, expect the \SW
+collaboration lead the resultant papers, we just request some of us
+are included on discovery papers in return for our help, please see
+Section \ref{sec:papers} for more details on the publication policy.
 
-The goal of the \SW PIs and the \SW collaboration is to enable the DES SST's science project in \sw and make it work.
-Using the automatic analysis pipeline (SWAPR), the \SW PIs we will send the DES SST lists of the candidates selected by the citizens (at some regular intervals or at the end of a project), we will then discuss strategies for further analysis based on our experience of previous projects.
-Some members of the \SW PIs  and team may become more involved in analysis steps such as grading of the \sw candidates or assist with any scientific investigations and follow-up of the candidates, at the DES SST's request.
+The goal of the \SW PIs and the \SW collaboration is to enable the
+KIDS SST's science project in \sw and make it work. Using the
+automatic analysis pipeline (SWAPR), the \SW PIs we will send the KIDS
+SST lists of the candidates selected by the citizens (at some regular
+intervals or at the end of a project), we will then discuss strategies
+for further analysis based on our experience of previous
+projects. Some members of the \SW PIs and team may become more
+involved in analysis steps such as grading of the \sw candidates or
+assist with any scientific investigations and follow-up of the
+candidates, at the KIDS SST's request.
 
-\subsection{Previewing images and \Talk}
-We are aware that there is some interest in the DES SST for using the \SW web interface to preview images for the SST themselves.
-This is not the function or purpose of the \SW interface or the Zooniverse.
-However,  it will be possible for DES SST members to view the images in parallel with the crowd through the public interface.
-The DES SST members who wish to do this will need to register with the Zooniverse to classify.
-We can extract the classifications of SSTs only to provide an expert selected sample, if required.
-The images marked by any inspector (SST or citizen)  are automatically recorded in an individual's \SW/Zooniverse account.
-These can be accessed through the \SW interface and as a 'collection' in \Talk.
-This collection can be explored (and discussed if required) through the \Talk interface.
+\subsection{Possible \SW-KIDS survey strategies}
 
-\SW\ \Talk is a key and integral part of \SW.
-The DES SST is strongly encouraged to interact with the volunteers on \Talk.
-This exchange allows the crowd to learn from the experts, this in turn has the very positive effect of motivating the citizens to contribute further.
-In addition it also results in better and informed classification when they return to that task.
-Thus, engagement of the SST is very important in log-term surveys such as DES.
+In our experience, a citizen science project like SW cannot function
+successfully without significant support and co-ordination of the
+SST. Thus, we recommend that all KIDS members with an interest in
+strong lensing are told about \SW and how it can complement their lens
+finding effort. Our goal is to enable your science.
 
-\subsection{Possible \SW-DES survey strategies}
+We also encourage the KIDS SST to consider the timing for when they
+wish to ingest the images into \SW so that it is in line with the
+interests of the KIDS SST and those of the KIDS consortium.
 
-In our experience, a citizen science project like SW cannot function successfully without significant support and co-ordination of the SST.
-Thus, we recommend that all DES members with an interest in strong lensing are told about \SW and how it can complement their lens finding effort.
-Our goal is to enable your science.
-While we can't expect the entirety of the DES Strong Lensing Group or the STRIDES consortium to be behind \SW-DES, all should be made aware of the projects being undertaken and planned with \SW.
-
-We also encourage the DES SST to consider the timing for when they wish to ingest the images into \SW so that it is in line with the interests of the DES SST and those of the DES consortium.
-
-Possible projects for the DES SST could consider (just to get a flavour of what can be done)
+Possible projects for the KIDS SST could consider (just to get a flavour of what can be done)
 \begin{itemize}
 \item \textbf{New Data}: Inspection of areas (targeted or blind) that the SST has not had time to inspect, i.e. use the crowd to increase the speed at which potential lens candidates are discovered
-\item \textbf{Comparison of Expert vs Citizen Classification}: DES SST and citizen's view images in parallel (targeted or blind)
-\item \textbf{Completeness of Expert Classification}: Citizen's classify images already inspected by the DES SST (targeted or blind)
-\item \textbf{Helping the robots}: Use citizens to weed out false positives from candidate samples generated by algorithm based searches
+\item \textbf{Comparison of Expert vs Citizen Classification}: KIDS SST and citizen's view images in parallel (targeted or blind)
+\item \textbf{Completeness of Expert Classification}: Citizen's classify images already inspected by the KIDS SST (targeted or blind)
+\item \textbf{Helping the robots}: Use citizens to weed out false positives from candidate samples generated by algorithm-based or machine learning searches
 \item \textbf{Training sets}: Blind inspection to generate a large training set for machine learning algorithms.
@@
 
-Note that the projects that are proposed to \SW need not be one of the above.
-Multiple projects could also be run in a mixture or phased set of experiments.
-Please do consider the DES timeline with reference to data release and the searches the DES SST want to make themselves.
+Note that the projects that are proposed to \SW need not be one of the
+above. Multiple projects could also be  run in a mixture or phased set
+of experiments. Please do consider the KIDS timeline with reference to
+data release and the searches the KIDS SST want to make themselves.
 
-If the DES SST wants to inspect targets within the consortium and is concerned about being scooped by the crowd, please be assured that there is little scope or motivation to do this.
-If the project is well defined, the goal of \SW-DES will be a complementary part of the DES SST lens finding strategy.
-By definition this means that \SW is working with the DES SST as it is designed to do.
-In addition, the images could be stripped of WCS info (described in Section \ref{sec:data}), meaning that no-one other than the SST can follow-up or catalogue the targets\footnote{We cannot exclude the possibility that individual sources might be serendipitously identified e.g.
-by recognisable morphologies.}.
-The DES SST could also perform their inspection before the images are passed to \SW.
-Any lens candidates discovered by the SST would then be labelled as `known lens candidates' in \sw\,\Talk.
-This applies to candidates discovered through visual inspection or algorithm based searches.
+If the KIDS SST wants to inspect targets within the consortium and is
+concerned about being scooped by the crowd, please be assured that
+there is little scope or motivation to do this. If the project is well
+defined, the goal of \SW-KIDS will be a complementary part of the KIDS
+SST lens finding strategy. By definition this means that \SW is
+working with the KIDS SST as it is designed to do. In addition, the
+images could be stripped of WCS info (described in Section
+\ref{sec:data}), meaning that no-one other than the SST can follow-up
+or catalogue the targets\footnote{We cannot exclude the possibility
+  that individual sources might be serendipitously identified e.g. by
+  recognisable morphologies.}.  The KIDS SST could also perform their
+inspection before the images are passed to \SW. Any lens candidates
+discovered by the SST would then be labelled as `known lens
+candidates' in \sw\,\Talk. This applies to candidates discovered
+through visual inspection or algorithm based searches.
 
 \subsection{What to do next: Project Proposals}
-Once the DES SST have narrowed down what search to be conducted \SW, please approach the \SW PIs (Phil Marshall, Anupreeta More, Aprajita Verma, collectively contacted via \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com}) with a short description of the project that includes the following information.
+Once the KIDS SST have narrowed down what search to be conducted \SW,
+please approach the \SW PIs (Phil Marshall, Anupreeta More, Aprajita
+Verma, collectively contacted via
+\href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com})
+with a short description of the project that includes the following
+information.
 
@@
 \item Targeted survey or blind field search\footnote{Targeted: inspection of a list of candidates; Blind: inspection of tiles of a survey area}
-\item Brief outline of the overall goal(s) of that inspection, highlighting how this is complementary (not competing) with the goals of the DES lens finding group
+\item Brief outline of the overall goal(s) of that inspection, highlighting how this is complementary (not competing) with the goals of the KIDS lens finding group
 \item Proprietary data issues 
@@
 
-Note, the proposed science project(s) should harness citizen classification power to achieve the science goals.
-
-The \SW PIs will then arrange a telecon with the DES SST to discuss the project further. This includes discussing the initial effort required and roles for the the SST team for expected tasks.
+The \SW PIs will then arrange a telecon with the KIDS SST to discuss
+the project further. This includes discussing the initial effort
+required and roles for the the SST team for expected tasks.
 
@@
 to read these papers before designing their own \SW project, and cite them as justification for some of their experimental decisions. 
-As the \SW paper series get published, links to the papers will be given in this draft.
-Prior to publications, draft papers can also be shared on request by the \SW PIs (\href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com})
+See \href{https://github.com/drphilmarshall/SpaceWarps/raw/master/doc/sw-system-published.pdf}{Paper I} \& \href{https://github.com/drphilmarshall/SpaceWarps/raw/master/doc/sw-cfhtls-published.pdf}{Paper II}.
 
@@
 
-However, some surveys, including DES, come with their own proprietary access policy. It is the responsibility
-of the DES SST to provide images to \SW in a way that is consistent
-with their own data access rules. There are two things that SSTs can
-do to in order to respect any proprietary period that they have imposed on
-themselves:
+However, some surveys, including KIDS, come with their own proprietary
+access policy. It is the responsibility of the KIDS SST to provide
+images to \SW in a way that is consistent with their own data access
+rules. There are two things that SSTs can do to in order to respect
+any proprietary period that they have imposed on themselves:
 \begin{enumerate}
@@
 Zooniverse servers.
-There is a reasonable amount of work in preparing data and images by the DES SST for delivery to \SW.
-The \SW team will provide assistance to the DES SST in data preparation.
+There is a reasonable amount of work in preparing data and images by the KIDS SST for delivery to \SW.
+The \SW team will provide assistance to the KIDS SST in data preparation.
 The benefits of using the \SW service will far outweigh the time needed to prepare data.
@@
 
-\item In {\bf reconfiguring the site itself} ready for the new data. The DES
+\item In {\bf reconfiguring the site itself} ready for the new data. The KIDS
 SST will need to include new Spotter's Guide images and text,
@@
 
-\item In {\bf running the \SW analysis pipeline} (SWAPR) which will be the \sw PIs responsibility. This will provide citizen selected candidates to be sent to the DES SST.
+\item In {\bf running the \SW analysis pipeline} (SWAPR) which will be the \sw PIs responsibility. This will provide citizen selected candidates to be sent to the KIDS SST.
 
@@
 
-\section{Resulting publications for \SW-DES }
+\section{Resulting publications for \SW-KIDS }
 \label{sec:series}
@@
 investigation of any lens candidate they find in \SW. This, along with
-posts in  \Talk, is the primary means by which we expect \SW-DES collaboration
+posts in  \Talk, is the primary means by which we expect \SW-KIDS collaboration
 members (citizens participating in the project) will communicate their findings to the rest of the
@@
 necessarily limited but the \SW Zooniverse \Letters will contribute to the collective knowledge and understanding of the presented system(s). Zooniverse \Letters are citable \SW
-objects, and in some cases will appear listed on ADS\footnote{To be confirmed.}.
+objects.
 
@@
 \item a small number of \SW authors proposed by the \SW PIs (see \ref{sec:papers}).
-\item the collaboration should be acknowledged in the acknowledgement section with a link to the collaboration membership page (URL: to be confirmed when available).
+\item the collaboration should be acknowledged in the acknowledgement section with a link to the collaboration membership page (e.g.
+\href{https://spacewarps.org/#/projects/CFHTLS/contributors}{List of Contributors to CFHT-LS}).
 \end{itemize}

### 2018-05-29 doc/sw-guidelines-policy-HSC.tex
HSC Guidelines added

--- 2016-05-23 doc/sw-publication-policy-kids.tex
@@
 
-\title{Guidelines and Policy for the KIDS Strong Lensing Science Team using \SW}
+\title{Guidelines and Policy for the HSC Strong Lensing Science Team using \SW}
 \author{Aprajita Verma, Phil Marshall \& Anupreeta More}
-\date{May 23, 2016}
+\date{v1: May 29, 2018}
 \maketitle
@@
 \noindent \SW was conceived as a strong lens discovery {\it service}
-that harnesses the power of citizen scientists. The KIDS strong
-lensing group (hereafter KIDS survey science team or KIDS SST) can
+that harnesses the power of citizen scientists. The HSC strong
+lensing group (hereafter HSC survey science team or HSC SST) can
 make use of \SW within the logistical constraints. In this document,
-we discuss how the KIDS SST might become involved with \SW and the
-relationship between the KIDS SST and the \SW collaboration.  This
+we discuss how the HSC SST will interact with \SW and the
+relationship between the HSC SST and the \SW collaboration.  This
 document includes guidelines for proposing projects, data provision,
@@
 simulated lenses (appropriate for the survey being conducted). The
-classification of simulated lenses acts as an interactive training
+classification of simulated lenses (and pre-inspecetd blank or false positives) acts as an interactive training
 activity that also allows us to establish the citizens' likelihood of
 identifying potential lenses and blank fields. This is fed into the
-\SW Analysis Pipeline (SWAPR) that analyses the classifications made
+\SW Analysis Pipeline (SWAP) that analyses the classifications made
 per image (or subject in Zooniverse terms) giving a probability of
@@
 each other and discuss interesting candidates through
-\Talk\footnote{\Talk (found at \texttt{http://talk.spacewarps.org}) is
+\Talk\footnote{\Talk (e.g. \texttt{https://www.zooniverse.org/projects/aprajita/space-warps-hsc/talk}) is
   a forum for \SW collaborators to discuss individual sources and the
@@
 
-In order to use the \SW interface, the KIDS Survey Science Team
+In order to use the \SW interface, the HSC Survey Science Team
 \textbf{must define and propose a project to the \SW PIs} who will
-discuss whether the project is suitable with the KIDS SST. The \SW PIs will
+discuss whether the project is suitable with the HSC SST. The \SW PIs will
 then liaise further with the SST to implement the project in the \SW
@@
 
-\vspace{4mm} The PIs of the \SW project are the authors of this
+\vspace{4mm} The PIs  and co-founders of the \SW project are the authors of this
 document, P.\,Marshall, A.\,More and A.\,Verma, please do not hesitate
@@
 
-In this document, we will refer to the entirety of the KIDS strong
-lensing science group as the KIDS Survey Science Team (KIDS SST) to
-encompass all of the KIDS strong lensing community.
+In this document, we will refer to the entirety of the HSC strong
+lensing science group as the HSC Survey Science Team (HSC SST) to
+encompass all of the HSC strong lensing community.
 
 We now discuss the relationship between the \SW collaboration and the
-KIDS SST, who wish to use the \SW interface to investigate their
-data. The KIDS SSTs will liaise with the \SW science and development
+HSC SST, who wish to use the \SW interface to investigate their
+data. The HSC SSTs will liaise with the \SW science and development
 teams to ingest their survey data into the \SW interface. There may be
 some overlap between current \SW members and SSTs.
-
-In the case of KIDS, \SW PI Anupreeta More is a member of both the \SW
-collaboration and the KIDS Strong Lensing Science Group.
 
@@
   \texttt{\url{https://github.com/drphilmarshall/SpaceWarps/blob/master/doc/sw-publication-policy-cfhtls.pdf}}},
-however this will not be relevant for \SW-KIDS publications, see
+however this will not be relevant for \SW-HSC publications, see
 Section \ref{sec:papers} for details.
@@
 
-The KIDS SST is expected to propose a project to the \SW collaboration
+The HSC SST is expected to propose a project to the \SW collaboration
 that can be best or only be done using the power of citizen
@@
 
-\subsection{KIDS specific thoughts}
+\subsection{HSC specific thoughts}
 
@@
 \item The \SW facility should be used for science projects that cannot be completed by the Strong Lens Group itself. 
-\item Any \SW search should be complementary, not in competition, to the lens finding being conducted by the KIDS SST.
+\item Any \SW search should be complementary, not in competition, to the lens finding being conducted by the HSC SST.
 \item While \SW uses citizen science, its primary goal is \textbf{not outreach}, it is harnessing citizen power for visual classifications (and eventually modelling) to perform science.
@@
 This is the reason the suitability of the project for citizen scientists should be carefully considered.
-The \SW PIs will be able to discuss any planned \SW-KIDS projects with the KIDS SST.
-The crowd needs to be engaged and feel like they are contributing while the entire \SW-KIDS project runs.
-\item The success of \SW-KIDS will rely on input from the KIDS SST working with the \SW collaboration, dedicated effort is required for this and the KIDS SST should identify team members who can commit time to the \SW-KIDS tasks for this before embarking on a project.
-The \SW PIs will help to establish the main efforts required, these will depend on the actual project put forward by the KIDS SST (e.g.\ image preparation, simulations, interacting with volunteers on \Talk).
+The \SW PIs will be able to discuss any planned \SW-HSC projects with the HSC SST.
+The crowd needs to be engaged and feel like they are contributing while the entire \SW-HSC project runs.
+\item The success of \SW-HSC will rely on input from the HSC SST working with the \SW collaboration, dedicated effort is required for this and the HSC SST should identify team members who can commit time to the \SW-HSC tasks for this before embarking on a project.
+The \SW PIs will help to establish the main efforts required, these will depend on the actual project put forward by the HSC SST (e.g.\ image preparation, simulations, interacting with volunteers on \Talk).
 \end{enumerate}
 
-\textbf{As such, \SW should be considered to be an integral/complementary part of the KIDS SST lens finding strategy, rather than an alternative method.}
+\textbf{As such, \SW should be considered to be an integral/complementary part of the HSC SST lens finding strategy, rather than an alternative method.}
 
@@
 The goal of the \SW PIs and the \SW collaboration is to enable the
-KIDS SST's science project in \sw and make it work. Using the
-automatic analysis pipeline (SWAPR), the \SW PIs we will send the KIDS
+HSC SST's science project in \sw and make it work. Using the
+automatic analysis pipeline (SWAP), the \SW PIs we will send the HSC
 SST lists of the candidates selected by the citizens (at some regular
@@
 assist with any scientific investigations and follow-up of the
-candidates, at the KIDS SST's request.
+candidates, at the HSC SST's request.
 
-\subsection{Possible \SW-KIDS survey strategies}
+\subsection{Possible \SW-HSC survey strategies}
 
@@
 successfully without significant support and co-ordination of the
-SST. Thus, we recommend that all KIDS members with an interest in
+SST. Thus, we recommend that all HSC members with an interest in
 strong lensing are told about \SW and how it can complement their lens
@@
 
-We also encourage the KIDS SST to consider the timing for when they
+We also encourage the HSC SST to consider the timing for when they
 wish to ingest the images into \SW so that it is in line with the
-interests of the KIDS SST and those of the KIDS consortium.
+interests of the HSC SST and those of the HSC consortium.
 
-Possible projects for the KIDS SST could consider (just to get a flavour of what can be done)
+Possible projects for the HSC SST could consider (just to get a flavour of what can be done)
 \begin{itemize}
 \item \textbf{New Data}: Inspection of areas (targeted or blind) that the SST has not had time to inspect, i.e. use the crowd to increase the speed at which potential lens candidates are discovered
-\item \textbf{Comparison of Expert vs Citizen Classification}: KIDS SST and citizen's view images in parallel (targeted or blind)
-\item \textbf{Completeness of Expert Classification}: Citizen's classify images already inspected by the KIDS SST (targeted or blind)
+\item \textbf{Comparison of Expert vs Citizen Classification}: HSC SST and citizen's view images in parallel (targeted or blind)
+\item \textbf{Completeness of Expert Classification}: Citizen's classify images already inspected by the HSC SST (targeted or blind)
 \item \textbf{Helping the robots}: Use citizens to weed out false positives from candidate samples generated by algorithm-based or machine learning searches
@@
 above. Multiple projects could also be  run in a mixture or phased set
-of experiments. Please do consider the KIDS timeline with reference to
-data release and the searches the KIDS SST want to make themselves.
+of experiments. Please do consider the HSC timeline with reference to
+data release and the searches the HSC SST want to make themselves.
 
-If the KIDS SST wants to inspect targets within the consortium and is
+If the HSC SST wants to inspect targets within the consortium and is
 concerned about being scooped by the crowd, please be assured that
 there is little scope or motivation to do this. If the project is well
-defined, the goal of \SW-KIDS will be a complementary part of the KIDS
+defined, the goal of \SW-HSC will be a complementary part of the HSC
 SST lens finding strategy. By definition this means that \SW is
-working with the KIDS SST as it is designed to do. In addition, the
+working with the HSC SST as it is designed to do. In addition, the
 images could be stripped of WCS info (described in Section
@@
   that individual sources might be serendipitously identified e.g. by
-  recognisable morphologies.}.  The KIDS SST could also perform their
+  recognisable morphologies.}.  The HSC SST could also perform their
 inspection before the images are passed to \SW. Any lens candidates
@@
 \subsection{What to do next: Project Proposals}
-Once the KIDS SST have narrowed down what search to be conducted \SW,
+Once the HSC SST have narrowed down what search to be conducted \SW,
 please approach the \SW PIs (Phil Marshall, Anupreeta More, Aprajita
@@
 \item Targeted survey or blind field search\footnote{Targeted: inspection of a list of candidates; Blind: inspection of tiles of a survey area}
-\item Brief outline of the overall goal(s) of that inspection, highlighting how this is complementary (not competing) with the goals of the KIDS lens finding group
+\item Brief outline of the overall goal(s) of that inspection, highlighting how this is complementary (not competing) with the goals of the HSC lens finding group
 \item Proprietary data issues 
@@
 
-The \SW PIs will then arrange a telecon with the KIDS SST to discuss
+The \SW PIs will then arrange a telecon with the HSC SST to discuss
 the project further. This includes discussing the initial effort
@@
 See \href{https://github.com/drphilmarshall/SpaceWarps/raw/master/doc/sw-system-published.pdf}{Paper I} \& \href{https://github.com/drphilmarshall/SpaceWarps/raw/master/doc/sw-cfhtls-published.pdf}{Paper II}.
+
+\subsection{What to do next: Example Timeline}
+The SST is expected to interact with \SW in a timely manner with the following rough guidelines in collaboration with \SW team
+\begin{itemize}
+\item at least 6 months before launch: determine project goals
+\item 2-4 months before launch: select training images and write appropriate feedback messages
+\item 2 months before launch: deliver and ingest subject images 
+\item 1-2 month before launch: update website content with survey specific text and images
+\item 1 month before launch: check inspection data batches and determine retirement strategy
+\item 1 month before launch: revisit survey strategy plans, implementation with \SW team
+\item 2 weeks before launch: run a beta test (interface, data sets, training frequency, SWAP), all hands on deck for interaction on talk
+\item Launch and subsequently while project is running: all hands on deck for interaction on talk, blog posts, interaction with \SW PIs and zooniverse
+\end{itemize}
+see also Section \ref{sec:data}.
+
+\hspace{6mm}
 
@@
 
-However, some surveys, including KIDS, come with their own proprietary
-access policy. It is the responsibility of the KIDS SST to provide
+However, some surveys, including HSC, come with their own proprietary
+access policy. It is the responsibility of the HSC SST to provide
 images to \SW in a way that is consistent with their own data access
@@
 Zooniverse servers.
-There is a reasonable amount of work in preparing data and images by the KIDS SST for delivery to \SW.
-The \SW team will provide assistance to the KIDS SST in data preparation.
+There is a reasonable amount of work in preparing data and images by the HSC SST for delivery to \SW.
+The \SW team will provide assistance to the HSC SST in data preparation.
 The benefits of using the \SW service will far outweigh the time needed to prepare data.
@@
 
-\item In {\bf reconfiguring the site itself} ready for the new data. The KIDS
+\item In {\bf reconfiguring the site itself} ready for the new data. The HSC
 SST will need to include new Spotter's Guide images and text,
@@
 
-\item In {\bf running the \SW analysis pipeline} (SWAPR) which will be the \sw PIs responsibility. This will provide citizen selected candidates to be sent to the KIDS SST.
+\item In {\bf running the \SW analysis pipeline} (SWAP) which will be the \sw PIs responsibility. This will provide citizen selected candidates to be sent to the HSC SST.
 
@@
 
-\section{Resulting publications for \SW-KIDS }
+\section{Resulting publications for \SW-HSC }
 \label{sec:series}
@@
 
-\SW runs an analysis pipeline (SWAPR) that will be tailored to the science goals of each new survey.
+\SW runs an analysis pipeline (SWAP) that will be tailored to the science goals of each new survey.
 Any large changes to the analysis code will be documented  by the \SW Science Team.
@@
 
-\subsection{Zooniverse \Letters}
+\subsection{Zooniverse Communications}
 \label{sec:comm}
@@
 registration, may write a Zooniverse
-Letter\footnote{\texttt{http://letters.zooniverse.org}} describing their
+blog post or \Talk reports describing their
 investigation of any lens candidate they find in \SW. This, along with
-posts in  \Talk, is the primary means by which we expect \SW-KIDS collaboration
+posts in  \Talk, is the primary means by which we expect \SW-HSC collaboration
 members (citizens participating in the project) will communicate their findings to the rest of the
@@
 provided without world coordinate system (WCS) information will be
-necessarily limited but the \SW Zooniverse \Letters will contribute to the collective knowledge and understanding of the presented system(s). Zooniverse \Letters are citable \SW
-objects.
+necessarily limited but the \SW Zooniverse \Talk and blog posts will contribute to the collective knowledge and understanding of the presented system(s).
 
@@
 This web page will be linked in every ensuing \SW publication.
-If a community member makes a significant contribution e.g.\ in the further investigation of a lens candidate with modelling tools, they are strongly encouraged to write Zooniverse \Letters.
+If a community member makes a significant contribution e.g.\ in the further investigation of a lens candidate with modelling tools, they are strongly encouraged to write Zooniverse posts.
 This may lead to them being invited to join journal publications by the lead author of a ``discovery'' publication.
